### 2020-07-28 manuscript/manuscript.Rmd
hello world

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "apa.csl"
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
# Load packages
library(papaja)
library(reticulate)
library(MASS)
library(Matrix)
library(lme4)
library(buildmer)
library(emmeans)
library(magrittr)
library(tidyverse)

# Chunk options
knitr::opts_chunk$set(include = FALSE, echo = FALSE)

# Specify conda environment for Python
use_condaenv("r-reticulate", required = TRUE)

# Bibliography file
r_refs("manuscript/r-references.bib")
```

```{python exp1-preprocessing}
# Import libraries
import mne
import glob
import os

# Define parameters for preprocessing
preproc_params = dict(n_components=15, method='fastica',           # ICA parameters
                      l_freq=0.1, h_freq=30,                       # Filter edges
                      event_id={'match': 221, 'mismatch': 222},    # EEG triggers
                      tmin=-0.5, tmax=1.498,                       # Length of epochs
                      baseline=(-0.2,0))                           # Baseline correction
reject = dict(eeg=200e-6)                                          # Rejection threshold

# # Debug
# locals().update(preproc_params)
# vhdr_fname = 'data/exp1/EEG/Vp0001.vhdr'

# Define preprocessing function
def preproc(vhdr_fname, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline):
  # Load EEG data
  raw = mne.io.read_raw_brainvision(vhdr_fname, preload=True)
  # Create new virtual EOG channels
  raw = mne.set_bipolar_reference(raw, 'Auge_u', 'Fp1', ch_name='VEOG', drop_refs=False)
  raw = mne.set_bipolar_reference(raw, 'F9', 'F10', ch_name='HEOG', drop_refs=False)
  raw.set_channel_types(mapping={'VEOG': 'eog', 'HEOG': 'eog'})
  # Add EasyCap electrode layout, removing any excessive channels
  montage = mne.channels.make_standard_montage('easycap-M1')
  raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(['VEOG', 'HEOG'])))
  raw.set_montage(montage=montage)
  # Re-reference to common average
  raw, _ = mne.set_eeg_reference(raw, 'average')
  # Run ICA on a copy of the data
  filt_raw = raw.copy()
  filt_raw.load_data().filter(l_freq=1, h_freq=None)
  ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
  ica.fit(filt_raw)
  # Remove bad components based on correlations with EOG
  eog_indices, eog_scores = ica.find_bads_eog(raw)
  ica.exclude = eog_indices
  raw = ica.apply(raw)
  # Apply band-pass filter
  raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
  # Epoching including baseline correction
  events, _ = mne.events_from_annotations(raw, verbose=False)
  epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax,
                      baseline=baseline, preload=True)

  # # Autoreject                    
  # import autoreject
  # 
  # ar = autoreject.AutoReject(thresh_method='random_search', verbose=False)
  # epochs_clean = ar.fit_transform(epochs)
  # 
  # rejected = epochs_clean.drop_log
  # rejected[:] = [item for item in rejected if item != ['IGNORED']]
  # rejected = [i for i in range(len(rejected)) if rejected[i] != []]
  # 
  # ransac = autoreject.Ransac(verbose=False)
  # epochs = ransac.fit_transform(epochs)
  # 
  # reject = autoreject.get_rejection_threshold(epochs)

  return epochs

# List of raw EEG filenames
fnames_exp1 = sorted(glob.glob('data/exp1/EEG/*.vhdr'))

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists('output/exp1-epo.fif'):
  # Load preprocessed data from file
  epochs_exp1 = mne.read_epochs('output/exp1-epo.fif', preload=True)
else:
  # Actually apply the preprocessing function
  epochs_exp1 = [preproc(fname, **preproc_params) for fname in fnames_exp1]
  # Combine into a single data set
  epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
  # Backup epochs to the export folder
  epochs_exp1.save('output/exp1-epo.fif')

# Get indices of bad epochs despite ICA
rej_exp1 = epochs_exp1.copy().drop_bad(reject=reject).drop_log
rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
```

```{r exp1-analysis}
# Define function for processing behavioral data
preproc_behav <- function(txt_fname){
  # Read log file
  dat <-  suppressMessages(suppressWarnings(read_tsv(txt_fname)))
  # Remove filler stimuli (well-known objects)
  dat %<>% filter(bek_unbek != "bekannt")
  # Add a column for the part of the experiment
  dat %<>% mutate(part = as_factor(Wdh - 210))

  # Assign stimuli to conditions based on keywords and button presses
  known <- dat %>% filter(part == "1" & Tastencode == 201) %>% pull(StimID)
  insight <- dat %>%filter(part == "2" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>% pull(StimID)
  naive <- dat %>% filter(part == "2" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>% pull(StimID)
  dat %<>% mutate(condition = as_factor(case_when(StimID %in% known ~ "Known",
                                                  StimID %in% insight ~ "Insight",
                                                  StimID %in% naive ~ "Naive")))
  # Remove unrealistically short RTs
  dat %<>% mutate(RT = replace(RT, RT < 200, NA))
  return(dat)}

# List of filenames for behavioral data
fnames_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE)

# Actually apply the preprocessing function
data_exp1 <- map_dfr(fnames_exp1, preproc_behav)

# Add factorized columns for participants and items (the random variables)
data_exp1 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))

# Tabulate percentage of stimuli per condition
stims_exp1 <- table(data_exp1$participant, data_exp1$condition)
stims_exp1 <- colMeans(stims_exp1)
stims_exp1["Known"]/(3*120) # Three repititions and 120 objects
stims_exp1[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each

# Import epochs from Python, converting Volts to Microvolts
epochs_exp1 <- py$epochs_exp1$get_data()*1e6

# Set rejected epochs to NA
rej_exp1 <- py$rej_exp1 + 1
epochs_exp1[rej_exp1,,] <- NA

# Create vectors with sample time points (in ms) and electrodes
tmin <- py$preproc_params$tmin*1000
tmax <- py$preproc_params$tmax*1000
sfreq <- py$epochs_exp1$info['sfreq']
times <- seq(tmin, tmax, 1000/sfreq)
els <- py$epochs_exp1$ch_names

# Define ERP components of interest
comps <- tibble(name = c("P1", "N1", "N400"),
                start = c(100, 150, 400),
                stop = c(150, 200, 700),
                roi = list(c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
                           c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
                           c("C1", "C2", "Cz", "CP1", "CP2", "CPz")))

# Define function to compute single-trial ERPs
compute_erps <- function(epochs, els, name, start, stop, roi){
  erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
  erps <- apply(erps, 1, mean, na.rm = TRUE)
  return(erps)}

# Apply the function and bind ERPs to the behavioral data
data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>% set_names(comps$name) %>% cbind(data_exp1, .)

# Remove trials with missing ERPs or RTs
rej_exp1_erp <- data_exp1 %>% filter(is.na(P1)) %>% count(participant, .drop = FALSE) %>% pull(n)
data_exp1 %<>% filter(!is.na(P1))
rej_exp1_rt <- data_exp1 %>% filter(is.na(RT)) %>% count(participant, .drop = FALSE) %>% pull(n)
data_exp1 %<>% filter(!is.na(RT))

# Remove any trials that don't beling to either of the two conditions
data_exp1 %<>% filter(condition != "Known") %>% droplevels()

# Set sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
t(contrasts.condition <- t(cbind(c("Insight" = 1, "Naive" = -1))))
t(contrasts.part <- t(cbind(c("1" = -1, "2" = 1, "3" = 0),
                            c("1" = 0, "2" = -1, "3" = 1))))
contrasts(data_exp1$condition) <- ginv(contrasts.condition)
contrasts(data_exp1$part) <- ginv(contrasts.part)

# Parameters for linear mixed-effects models (LMMs)
form <- tabulate.formula(~ part*condition + (part*condition|participant) + (part*condition|item))
form %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
ctrl_params <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Parameters for follow-up contrasts
specs = pairwise ~ condition|part

# Define function to compute LMMs and contrasts
compute_models <- function(dep, formula, data, control, specs){
  build <- buildmer(dep = dep, formula = formula, data = data, ddf = "Satterthwaite", calc.anova = TRUE, control = control)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  conts <- emmeans(build@model, specs = specs, infer = TRUE)
  mod <- list("model" = build@model, "anova" = build@anova, "summary" = build@summary, "contrasts" = conts)
  return(mod)}

# Check if models were computed already (delete the file to re-run)
if (file.exists("output/exp1-stats.RDS")){
   # Load models from file
  models_exp1 <- readRDS("output/exp1-stats.RDS")
} else {
  # Actually apply the modelling function
  models_exp1 <- map(comps$name, compute_models, formula = form, data = data_exp1, control = ctrl_params, specs = specs) %>%
    set_names(comps$name)
  # Backup epochs to the export folder
  saveRDS(models_exp1, "output/exp1-stats.RDS")}
```

```{python exp2-preprocessing}
# List of raw EEG filenames
fnames_exp2 = sorted(glob.glob('data/exp2/EEG/*.vhdr'))

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists('output/exp2-epo.fif'):
  # Load preprocessed data from file
  epochs_exp2 = mne.read_epochs('output/exp2-epo.fif', preload=True)
else:
  # Actually apply the preprocessing function
  epochs_exp2 = [preproc(fname, **preproc_params) for fname in fnames_exp2]
  # Combine into a single data set
  epochs_exp2 = mne.concatenate_epochs(epochs_exp2)
  # Backup epochs to the export folder
  epochs_exp2.save('output/exp2-epo.fif')

# Get indices of bad epochs despite ICA
rej_exp2 = epochs_exp2.copy().drop_bad(reject=reject).drop_log
rej_exp2[:] = [item for item in rej_exp2 if item != ['IGNORED']]
rej_exp2 = [i for i in range(len(rej_exp2)) if rej_exp2[i] != []]
```

```{r exp2-analysis}
# List of filenames for behavioral data
fnames_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE)

# Actually apply the preprocessing function
data_exp2 <- map_dfr(fnames_exp2, preproc_behav)

# Add factorized columns for participants and items (the random variables)
data_exp2 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))

# Tabulate percentage of stimuli per condition
stims_exp2 <- table(data_exp2$participant, data_exp2$condition)
stims_exp2 <- colMeans(stims_exp2)
stims_exp2["Known"]/(3*120) # Three repititions and 120 objects
stims_exp2[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each

# Import epochs from Python, converting Volts to Microvolts
epochs_exp2 <- py$epochs_exp2$get_data()*1e6

# Set rejected epochs to NA
rej_exp2 <- py$rej_exp2 + 1
epochs_exp2[rej_exp2,,] <- NA

# Apply function to compute single-trial ERPs and to the behavioral data
data_exp2 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp2, els = els) %>% set_names(comps$name) %>% cbind(data_exp2, .)

# Remove trials with missing ERPs or RTs
rej_exp2_erp <- data_exp2 %>% filter(is.na(P1)) %>% count(participant, .drop = FALSE) %>% pull(n)
data_exp2 %<>% filter(!is.na(P1))
rej_exp2_rt <- data_exp2 %>% filter(is.na(RT)) %>% count(participant, .drop = FALSE) %>% pull(n)
data_exp2 %<>% filter(!is.na(RT))

# Remove any trials that don't beling to either of the two conditions
data_exp2 %<>% filter(condition != "Known") %>% droplevels()

# Set sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
contrasts(data_exp2$condition) <- ginv(contrasts.condition)
contrasts(data_exp2$part) <- ginv(contrasts.part)

# Check if models were computed already (delete the file to re-run)
if (file.exists("output/exp2-stats.RDS")){
   # Load models from file
  models_exp2 <- readRDS("output/exp2-stats.RDS")
} else {
  # Actually apply the modelling function
  models_exp2 <- map(comps$name, compute_models, formula = form, data = data_exp2, control = ctrl_params, specs = specs) %>%
    set_names(comps$name)
  # Backup epochs to the export folder
  saveRDS(models_exp2, "output/exp2-stats.RDS")}
```

```{r joint-analysis}
# Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
data_joint <- data_exp2 %>%
  mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
  bind_rows(data_exp1, ., .id = "experiment") %>%
  mutate(experiment = as_factor(experiment))

# Set sliding difference coding for experiment (2-1), condition (insight-naive), and part (2-1, 3-1)
t(contrasts.experiment <- t(cbind(c("1" = -1, "2" = 1))))
contrasts(data_joint$experiment) <- ginv(contrasts.experiment)
contrasts(data_joint$condition) <- ginv(contrasts.condition)
contrasts(data_joint$part) <- ginv(contrasts.part)

# New formula for LMMs
form_joint <- tabulate.formula(~ experiment*part*condition + (part*condition|participant) + (experiment*part*condition|item))
form_joint %<>% mutate(block = replace(block, is.na(grouping), "fixed"))

# Check if models were computed already (delete the file to re-run)
if (file.exists("output/joint-stats.RDS")){
   # Load models from file
  models_joint <- readRDS("output/joint-stats.RDS")
} else {
  # Actually apply the modelling function
  models_joint <- map(comps$name, compute_models, formula = form_joint, data = data_joint, control = ctrl_params, specs = specs) %>%
    set_names(comps$name)
  # Backup epochs to the export folder
  saveRDS(models_joint, "output/joint-stats.RDS")}
```

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

\endgroup

### 2020-07-28 manuscript/manuscript.tex
hello world

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa7}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Title}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {}%
  {\par}

\title{The title}
\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{cslreferences}
\end{cslreferences}

\endgroup

\end{document}

### 2020-07-29 manuscript/manuscript.Rmd
behavior first

@@
 
+```{r exp1-behavior}
+# Define function for processing behavioral data
+preproc_behav <- function(txt_fname){
+  # Read log file
+  dat <-  suppressMessages(suppressWarnings(read_tsv(txt_fname)))
+  # Remove filler stimuli (well-known objects)
+  dat %<>% filter(bek_unbek != "bekannt")
+  # Add a column for the part of the experiment
+  dat %<>% mutate(part = as_factor(Wdh - 210))
+  # Assign stimuli to conditions based on keywords and button presses
+  known <- dat %>% filter(part == "1" & Tastencode == 201) %>% pull(StimID)
+  insight <- dat %>%filter(part == "2" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>% pull(StimID)
+  naive <- dat %>% filter(part == "2" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>% pull(StimID)
+  dat %<>% mutate(condition = as_factor(case_when(StimID %in% known ~ "Known",
+                                                  StimID %in% insight ~ "Insight",
+                                                  StimID %in% naive ~ "Naive")))
+  # Remove unrealistically short RTs
+  dat %<>% mutate(RT = replace(RT, RT < 200, NA))
+  return(dat)}
+
+# List of filenames for behavioral data
+fnames_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE)
+
+# Actually apply the preprocessing function
+data_exp1 <- map_dfr(fnames_exp1, preproc_behav)
+
+# Add factorized columns for participants and items (the random variables)
+data_exp1 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))
+
+# Tabulate percentage of stimuli per condition
+stims_exp1 <- table(data_exp1$participant, data_exp1$condition)
+stims_exp1 <- colMeans(stims_exp1)
+stims_exp1["Known"]/(3*120) # Three repititions and 120 objects
+stims_exp1[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each
+
+# Select only relevant columns
+data_exp1 %<>% select(part, condition, participant, item, RT)
+
+# Tell MNE to exclude trials without a proper condition or RT
+data_exp1 %<>% mutate(condition = replace(condition, condition == "Known" | is.na(RT), NA)) %>%
+  mutate(condition = fct_explicit_na(condition, na_level = "Exclude")) %>% droplevels()
+```
+
 ```{python exp1-preprocessing}
@@
   epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
+  # Add metadata from R
+  epochs_exp1.metadata = r.data_exp1
   # Backup epochs to the export folder
@@
 
-# Get indices of bad epochs despite ICA
-rej_exp1 = epochs_exp1.copy().drop_bad(reject=reject).drop_log
-rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
-rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
+# Remove trials with invalid condition or RTs
+epochs_exp1 = epochs_exp1['condition != "Exclude"']
+
+# # Compute evoked potentials for each part x condition
+# evokeds_exp1 = dict()
+# for pt in ['1', '2', '3']:
+#   for cn in ['Insight', 'Naive']:
+#     query = 'part == "' + pt + '" and condition == "' + cn + '"'
+#     evokeds_exp1['Part' + pt + '_' + cn] = epochs_exp1[query].average()
+# mne.viz.plot_compare_evokeds(evokeds_exp1, cmap=('condition', 'viridis'), picks='P8')
+
+# # Get indices of bad epochs despite ICA
+# rej_exp1 = epochs_exp1.copy().drop_bad(reject=reject).drop_log
+# rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
+# rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
 ```
@@
 ```{r exp1-analysis}
-# Define function for processing behavioral data
-preproc_behav <- function(txt_fname){
-  # Read log file
-  dat <-  suppressMessages(suppressWarnings(read_tsv(txt_fname)))
-  # Remove filler stimuli (well-known objects)
-  dat %<>% filter(bek_unbek != "bekannt")
-  # Add a column for the part of the experiment
-  dat %<>% mutate(part = as_factor(Wdh - 210))
-
-  # Assign stimuli to conditions based on keywords and button presses
-  known <- dat %>% filter(part == "1" & Tastencode == 201) %>% pull(StimID)
-  insight <- dat %>%filter(part == "2" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>% pull(StimID)
-  naive <- dat %>% filter(part == "2" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>% pull(StimID)
-  dat %<>% mutate(condition = as_factor(case_when(StimID %in% known ~ "Known",
-                                                  StimID %in% insight ~ "Insight",
-                                                  StimID %in% naive ~ "Naive")))
-  # Remove unrealistically short RTs
-  dat %<>% mutate(RT = replace(RT, RT < 200, NA))
-  return(dat)}
-
-# List of filenames for behavioral data
-fnames_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE)
-
-# Actually apply the preprocessing function
-data_exp1 <- map_dfr(fnames_exp1, preproc_behav)
-
-# Add factorized columns for participants and items (the random variables)
-data_exp1 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))
-
-# Tabulate percentage of stimuli per condition
-stims_exp1 <- table(data_exp1$participant, data_exp1$condition)
-stims_exp1 <- colMeans(stims_exp1)
-stims_exp1["Known"]/(3*120) # Three repititions and 120 objects
-stims_exp1[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each
 

### 2020-09-02 manuscript/manuscript.Rmd
add plots

--- 2020-07-28 manuscript/manuscript.Rmd
@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 
-```{r setup, include = FALSE}
+```{r setup, include=FALSE}
 # Load packages
@@
 library(lme4)
+library(lmerTest)
 library(buildmer)
@@
 library(tidyverse)
+library(cowplot)
 
 # Chunk options
-knitr::opts_chunk$set(include = FALSE, echo = FALSE)
+knitr::opts_chunk$set(include = FALSE, echo = FALSE, fig.out = "100%", fig.width = 10)
 
-# Specify conda environment for Python
-use_condaenv("r-reticulate", required = TRUE)
+# Conda environment for Python
+#use_condaenv("r-reticulate", required = TRUE)
+renv::use_python(python = "/Users/alexander/opt/anaconda3/bin/python", type = "conda")
 
@@
 r_refs("manuscript/r-references.bib")
+```
+
+```{r exp1-behavior}
+# Function for processing behavioral data
+preproc_behav <- function(txt_fname){
+  # Read log file
+  dat <- suppressMessages(suppressWarnings(read_tsv(txt_fname)))
+  # Rename some columns
+  dat %<>% rename(participant = VPNummer, item = StimID) %>%
+    # Add a column for the part of the experiment
+    mutate(part = as_factor(Wdh - min(Wdh) + 1)) %>%
+    # Remove filler stimuli (i.e. well-known objects)
+    filter(bek_unbek != "bekannt")
+  # Assign stimuli to conditions based on keywords and button presses
+  known <- dat %>% filter(part == "1" & Tastencode %in% c(201, 251)) %>% pull(item)
+  insight <- dat %>% filter(part == "2" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
+  naive <- dat %>% filter(part == "2" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
+  # Create a new condition column, excluding trials with knwon stimuli or without condition
+  dat %<>% mutate(condition = as_factor(case_when(item %in% known ~ "Excl_known",
+                                                  item %in% insight ~ "Insight",
+                                                  item %in% naive ~ "Naive",
+                                                  TRUE ~ "Excl_cond")))
+  # In Experiment 3, we need an additional column for position (upright vs. inverted)
+  if("richtig_inv" %in% dat$Bed){
+    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
+      # Return only relevant columns
+      select(part, position, condition, participant, item, RT)
+  } else {
+    dat %<>% select(part, condition, participant, item, RT)}
+  return(dat)}
+
+# List of filenames for behavioral data
+fnames_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE)
+
+# Apply the preprocessing function
+data_exp1 <- map(fnames_exp1, preproc_behav)
+
+# Tabulate percentage of stimuli per condition
+(stims_exp1 <- bind_rows(data_exp1) %>% filter(condition != "Excl_cond") %>% 
+    group_by(participant, condition) %>% tally() %>%
+    group_by(condition) %>% summarise(mean = mean(n)/(60*3)) %>% # 60 items per condition
+    mutate(mean = if_else(condition == "Excl_known", mean/2, mean))) # 120 items in total
 ```
@@
 
-# Define parameters for preprocessing
+# Define parameters for EEG preprocessing
 preproc_params = dict(n_components=15, method='fastica',           # ICA parameters
@@
                       tmin=-0.5, tmax=1.498,                       # Length of epochs
-                      baseline=(-0.2,0))                           # Baseline correction
-reject = dict(eeg=200e-6)                                          # Rejection threshold
+                      baseline=(-0.2,0),                           # Baseline correction
+                      reject=dict(eeg=200e-6))                     # Rejection threshold
 
@@
 # vhdr_fname = 'data/exp1/EEG/Vp0001.vhdr'
+# metadata = metadata_exp1[0]
 
 # Define preprocessing function
-def preproc(vhdr_fname, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline):
+def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline, reject):
   # Load EEG data
@@
   events, _ = mne.events_from_annotations(raw, verbose=False)
-  epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax,
-                      baseline=baseline, preload=True)
+  epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True)
+  # Add behavioral data
+  epochs.metadata = metadata
+  # Reject bad epochs
+  epochs = epochs.drop_bad(reject=reject)
 
@@
   # ar = autoreject.AutoReject(thresh_method='random_search', verbose=False)
-  # epochs_clean = ar.fit_transform(epochs)
-  # 
-  # rejected = epochs_clean.drop_log
-  # rejected[:] = [item for item in rejected if item != ['IGNORED']]
-  # rejected = [i for i in range(len(rejected)) if rejected[i] != []]
+  # epochs = ar.fit_transform(epochs)
   # 
@@
   # reject = autoreject.get_rejection_threshold(epochs)
+  # epochs = epochs.drop_bad(reject=reject)
 
@@
 
+# Import behavioral data from R
+metadata_exp1 = r.data_exp1
+
 # Check if preprocessing was done already (delete the file to re-run)
@@
 else:
-  # Actually apply the preprocessing function
-  epochs_exp1 = [preproc(fname, **preproc_params) for fname in fnames_exp1]
-  # Combine into a single data set
+  # Apply the preprocessing function
+  epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp1, metadata_exp1)]
+  # Combine epochs into a single data set
   epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
-  # Backup epochs to the export folder
+  # Backup epochs to the output folder
   epochs_exp1.save('output/exp1-epo.fif')
 
-# Get indices of bad epochs despite ICA
-rej_exp1 = epochs_exp1.copy().drop_bad(reject=reject).drop_log
-rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
-rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
+# # Get indices of bad epochs despite ICA
+# rej_exp1 = epochs_exp1.drop_log
+# rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
+# rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
+
+# Define function to compute grand-averaged ERPs per condition
+def compute_evokeds(epochs):
+  evokeds = dict()
+  evokeds_dat = dict()
+  # Each part becomes a dictionary of conditions
+  for pt in ['1', '2', '3']:
+    evokeds['Pt' + pt] = dict()
+    evokeds_dat['Pt' + pt] = dict()
+    # Each condition becomes a list of participants
+    for cn in ['Insight', 'Naive']:
+      evokeds['Pt' + pt][cn] = list()
+      evokeds_dat['Pt' + pt][cn] = list()
+      # For every participant we average trials separately for all parts and conditions
+      for vp in epochs.metadata['participant'].unique():
+        query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
+        evokeds['Pt' + pt][cn].append(epochs[query].average())
+      # Compute grand averages across participants for this part and condition
+      evokeds['Pt' + pt][cn] = mne.grand_average(evokeds['Pt' + pt][cn])
+      # Export only the actual data for R
+      evokeds_dat['Pt' + pt][cn] = evokeds['Pt' + pt][cn].data
+  return(evokeds, evokeds_dat)
+
+# Apply the function to compute grand averages
+evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)
+
+# Export electrode positions for R
+elpos = epochs_exp1._get_channel_positions()
+
+# # Plot evoked potentials
+# mne.viz.plot_compare_evokeds(evokeds=evokeds_exp1['Pt1'], picks='P8'); plt.show()
+# mne.viz.plot_evoked_topomap(evoked=evokeds_exp1['Pt2']['Insight']-evokeds_exp1['Pt2']['Naive'])
+# evokeds_exp1['Pt2']['Insight'].data = evokeds_exp1['Pt2']['Insight'].data - evokeds_exp1['Pt2']['Naive'].data
+# evokeds_exp1['Pt2']['Insight'].plot_topomap(times=[0.125, 0.175, 0.5], average=0.05, vmin=-1, vmax=1, cmap='viridis'); plt.show()
 ```
@@
 ```{r exp1-analysis}
-# Define function for processing behavioral data
-preproc_behav <- function(txt_fname){
-  # Read log file
-  dat <-  suppressMessages(suppressWarnings(read_tsv(txt_fname)))
-  # Remove filler stimuli (well-known objects)
-  dat %<>% filter(bek_unbek != "bekannt")
-  # Add a column for the part of the experiment
-  dat %<>% mutate(part = as_factor(Wdh - 210))
+# Re-import behavioral data
+data_exp1 <- py$epochs_exp1$metadata
 
-  # Assign stimuli to conditions based on keywords and button presses
-  known <- dat %>% filter(part == "1" & Tastencode == 201) %>% pull(StimID)
-  insight <- dat %>%filter(part == "2" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>% pull(StimID)
-  naive <- dat %>% filter(part == "2" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>% pull(StimID)
-  dat %<>% mutate(condition = as_factor(case_when(StimID %in% known ~ "Known",
-                                                  StimID %in% insight ~ "Insight",
-                                                  StimID %in% naive ~ "Naive")))
-  # Remove unrealistically short RTs
-  dat %<>% mutate(RT = replace(RT, RT < 200, NA))
-  return(dat)}
+# Factorize some columns
+data_exp1 %<>% mutate(part = factor(part, levels = c("1", "2", "3")),
+                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_known", "Excl_cond")),
+                      participant = factor(participant), item = factor(item))
 
-# List of filenames for behavioral data
-fnames_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE)
-
-# Actually apply the preprocessing function
-data_exp1 <- map_dfr(fnames_exp1, preproc_behav)
-
-# Add factorized columns for participants and items (the random variables)
-data_exp1 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))
-
-# Tabulate percentage of stimuli per condition
-stims_exp1 <- table(data_exp1$participant, data_exp1$condition)
-stims_exp1 <- colMeans(stims_exp1)
-stims_exp1["Known"]/(3*120) # Three repititions and 120 objects
-stims_exp1[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each
-
-# Import epochs from Python, converting Volts to Microvolts
-epochs_exp1 <- py$epochs_exp1$get_data()*1e6
-
-# Set rejected epochs to NA
-rej_exp1 <- py$rej_exp1 + 1
-epochs_exp1[rej_exp1,,] <- NA
+# Check number of rejected epochs
+rejected_exp1 <- data_exp1 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
+mean(rejected_exp1); median(rejected_exp1); range(rejected_exp1)
 
@@
 
-# Apply the function and bind ERPs to the behavioral data
-data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>% set_names(comps$name) %>% cbind(data_exp1, .)
-
-# Remove trials with missing ERPs or RTs
-rej_exp1_erp <- data_exp1 %>% filter(is.na(P1)) %>% count(participant, .drop = FALSE) %>% pull(n)
-data_exp1 %<>% filter(!is.na(P1))
-rej_exp1_rt <- data_exp1 %>% filter(is.na(RT)) %>% count(participant, .drop = FALSE) %>% pull(n)
-data_exp1 %<>% filter(!is.na(RT))
+# Check if ERPs were computed already (delete the file to re-run)
+if (file.exists("output/exp1-erps.RDS")){
+  # Load ERPs from file
+  data_exp1 <- readRDS("output/exp1-erps.RDS")
+} else {
+  # Import epochs from Python, converting Volts to Microvolts
+  epochs_exp1 <- py$epochs_exp1$get_data()*1e6
+  # Apply the ERP function and save to output folder
+  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>%
+    set_names(comps$name) %>% cbind(data_exp1, .) %T>% saveRDS("output/exp1-erps.RDS")}
 
 # Remove any trials that don't beling to either of the two conditions
-data_exp1 %<>% filter(condition != "Known") %>% droplevels()
+data_exp1 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
 
-# Set sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
-t(contrasts.condition <- t(cbind(c("Insight" = 1, "Naive" = -1))))
-t(contrasts.part <- t(cbind(c("1" = -1, "2" = 1, "3" = 0),
+# Sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
+t(contrasts_condition <- t(cbind(c("Insight" = 1, "Naive" = -1))))
+t(contrasts_part <- t(cbind(c("1" = -1, "2" = 1, "3" = 0),
                             c("1" = 0, "2" = -1, "3" = 1))))
-contrasts(data_exp1$condition) <- ginv(contrasts.condition)
-contrasts(data_exp1$part) <- ginv(contrasts.part)
+contrasts(data_exp1$condition) <- ginv(contrasts_condition)
+contrasts(data_exp1$part) <- ginv(contrasts_part)
 
-# Parameters for linear mixed-effects models (LMMs)
-form <- tabulate.formula(~ part*condition + (part*condition|participant) + (part*condition|item))
-form %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
+# Formula and parameters for linear mixed-effects regression models (LMMs)
+form_exp12 <- tabulate.formula(~ part*condition + (part*condition|participant) + (part*condition|item))
+form_exp12 %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
 ctrl_params <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
 
-# Parameters for follow-up contrasts
-specs = pairwise ~ condition|part
+# Formula for follow-up contrasts
+specs_exp12 = pairwise ~ condition|part
 
-# Define function to compute LMMs and contrasts
+# Define function to compute LMMs and contrasts for each component
 compute_models <- function(dep, formula, data, control, specs){
+  browser()
   build <- buildmer(dep = dep, formula = formula, data = data, ddf = "Satterthwaite", calc.anova = TRUE, control = control)
   emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  conts <- emmeans(build@model, specs = specs, infer = TRUE)
+  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts %>% as.data.frame()
   mod <- list("model" = build@model, "anova" = build@anova, "summary" = build@summary, "contrasts" = conts)
@@
 } else {
-  # Actually apply the modelling function
-  models_exp1 <- map(comps$name, compute_models, formula = form, data = data_exp1, control = ctrl_params, specs = specs) %>%
-    set_names(comps$name)
-  # Backup epochs to the export folder
-  saveRDS(models_exp1, "output/exp1-stats.RDS")}
+  # Apply the modelling function and save to output folder
+  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
+                     specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/exp1-stats.RDS")}
+
+# Store significance levels for plotting
+stars_exp1 = list(P1 = c(Pt1 = NA, Pt2 = NA, Pt3 = "*"),
+                  N1 = c(Pt1 = NA, Pt2 = "**", Pt3 = NA),
+                  N400 = c(Pt1 = NA, Pt2 = "***", Pt3 = "**"))
+```
+
+```{r exp1-table, include=TRUE, results="asis"}
+# Check if models were computed already (delete the file to re-run)
+if (file.exists("output/exp1-stats.RDS")){
+  # Load models from file
+  models_exp1 <- readRDS("output/exp1-stats.RDS")
+} else {
+  # Apply the modelling function and save to output folder
+  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
+                     specs = specs_exp12) %>% set_names(comps$name) %>% saveRDS("output/exp1-stats.RDS")}
+
+# Define function to create ANOVA-style table
+create_table <- function(models, stub.anova, stub.contrasts, caption, note){
+  anov <- map(models, function(model){
+    data.frame("stat" = paste0(format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2), " (", model$anova$NumDF,
+                               ", ", format(round(model$anova$DenDF, 1), trim = FALSE, nsmall = 1), ")"),
+               "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)) %>%
+      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p))))}) %>%
+    bind_cols() %>% set_rownames(c(stub.anova))
+  cnames <- c("\\textit{Type III}", rep(c("\\textit{F} (\\textit{df})", "p" = "\\textit{p}"), 3))
+  conts <- map(models, function(model){
+    data.frame("stat" = paste0(format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2), " [",
+                               format(round(model$contrasts$lower.CL, 2), trim = FALSE, nsmall = 2), ", ",
+                               format(round(model$contrasts$upper.CL, 2), trim = FALSE, nsmall = 2), "]"),
+               "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)) %>%
+      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p)))) %>%
+      add_row("stat" = "Est. [95% CI]", "p" = "\\textit{p}", .before = 1)}) %>% 
+    bind_cols() %>% set_rownames(c("\\textit{Insight $-$  naive}", stub.contrasts))
+  apa_table(list(anov, conts), col.names = cnames, escape = FALSE,
+            col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N1}" = 4:5, "\\textbf{N400}" = 6:7),
+            midrules = c(nrow(anov) + 1), font_size = "footnotesize", align = "lcccccc",
+            caption = caption, note = note)}
+
+# Apply the function to print the table
+create_table(models_exp1, stub.anova = c("Part", "Insight", "Pt. × ins."),
+             stub.contrasts = c("Part 1", "Part 2", "Part 3"),
+             caption = "Results of linear mixed-effects regression models for Experiment 1",
+             note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
+```
+
+```{r exp1-plotting, include=TRUE, fig.height=12}
+# Import grand averaged evoked potentials from Python
+evokeds_exp1 <- py$evokeds_dat_exp1
+
+# Retrive locations for the relevant electrodes from standard montage
+montage <- py$evokeds_exp1$Pt1$Insight$ch_names %>% as_tibble() %>% rename(electrode = value) %>%
+  left_join(read.delim("renv/python/condaenvs/renv-python/lib/python3.8/site-packages/mne/channels/data/montages/easycap-M1.txt") %>% 
+              as_tibble() %>% rename(electrode = Site)) %>%
+  mutate(x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
+         y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)))
+
+# Define function to plot trial structure
+plot_trial <- function(){
+  colour_insight <- viridisLite::viridis(1, begin = 0, end = 0)
+  colour_naive <- viridisLite::viridis(1, begin = 0.5, end = 0.5)
+  trial_pt1 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
+    geom_text(aes(x = 37, y = 68, label = "Part 1"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
+    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
+    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
+    draw_image("materials/exp1/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
+    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
+  trial_pt2 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
+    geom_text(aes(x = 37, y = 68, label = "Part 2"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
+    geom_rect(aes(xmin = 0, xmax = 20, ymin = 0, ymax = 20), color = "black", fill = "white") +
+    geom_text(aes(x = 10, y = 10.5, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
+    geom_text(aes(x = 10, y = -3, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = colour_insight, fill = "white") +
+    geom_text(aes(x = 28, y = 23, label = "Potato\nmashing"), color = colour_insight, size = 10/.pt, family = "Helvetica") +
+    geom_text(aes(x = 28, y = 10, label = "2.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 39, ymax = 59), color = colour_naive, fill = "white") +
+    geom_text(aes(x = 28, y = 49, label = "Message\nmorsing"), color = colour_naive, size = 10/.pt, family = "Helvetica") +
+    geom_text(aes(x = 28, y = 36, label = "or"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
+    geom_text(aes(x = 46, y = 34, label = "*"), size = 8, family = "Helvetica") +
+    geom_text(aes(x = 46, y = 23, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 54, xmax = 74, ymin = 39, ymax = 59), color = "black", fill = "white") +
+    draw_image("materials/exp1/potato_masher.png", x = 54, y = 39, width = 20, height = 20) +
+    geom_text(aes(x = 65, y = 36, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica", lineheight = 1) +
+    geom_segment(aes(x = 28, y = 0, xend = 74, yend = 33.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
+  trial_pt3 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
+    geom_text(aes(x = 37, y = 68, label = "Part 3"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
+    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
+    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
+    draw_image("materials/exp1/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
+    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
+  plot_grid(trial_pt1, NULL, trial_pt2, NULL, trial_pt3, nrow = 1, rel_widths = c(10, 1, 10, 1, 10))}
+
+# Define function to plot mean ERP amplitudes
+plot_bars <- function(data, stars, ymin){
+  parts <- map(unique(data$part), function(part){
+    # For which components in the current part do we have a significant effect?
+    sig <- map(stars, paste0("Pt", part)) %>% as.data.frame() %>% t() %>% as.data.frame() %>%
+      set_colnames("label") %>% rownames_to_column("comp") %>% na.omit()
+    # Create bar plot for the current part
+    map(c("P1", "N1", "N400"), function(comp){
+      p <- data %>% filter(part == !!part) %>%
+        Rmisc::summarySEwithin(measurevar = comp, withinvars = "condition", idvar = "participant") %>%
+        mutate(comp = !!comp) %>% rename(amplitude = !!comp)}) %>% bind_rows() %>%
+      mutate(comp = fct_relevel(comp, "P1", "N1", "N400")) %>%
+      ggplot(aes(x = comp, y = amplitude, fill = condition)) +
+      # geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
+      # annotate("tile", x = sig$comp, y = -0.4, width = 0.45, height = 0.8, colour = "black", fill = "white", size = 0.5) +
+      # annotate("rect", xmin = -Inf, xmax = Inf, ymin = -0.2, ymax = Inf, fill = "white") +
+      # geom_bar(aes(y = amplitude - se - 0.2), stat = "identity", position = position_dodge()) + scale_fill_manual(values = c("white", "white")) +
+      # new_scale_fill() +
+      # annotate("label", x = sig$comp, y = -0.96, label = sig$label, size = 7, family = "Helvetica", label.size = 0) +
+      geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
+      scale_fill_viridis_d(end = 0.5) +
+      geom_errorbar(aes(ymin = amplitude - se, ymax = amplitude + se), position = position_dodge(width = 0.9), width = 0.5) +
+      annotate("text", x = sig$comp, y = ymin, label = sig$label, size = 6, family = "Helvetica") +
+      geom_hline(yintercept = 0) +
+      coord_cartesian(ylim = c(ymin, ymin + 7)) +
+      ylab("ROI ampl.\n(µV)") +
+      scale_y_continuous(breaks = seq(trunc(ymin), trunc(ymin) + 6, 2)) +
+      theme_classic() +
+      theme(legend.position = "none",
+            panel.grid = element_blank(),
+            axis.ticks = element_line(color = "black"),
+            axis.title.x = element_blank(),
+            axis.title.y = element_text(family = "Helvetica", color = "black", size = 10),
+            axis.text = element_text(family = "Helvetica", color = "black", size = 10),
+            plot.margin = margin(t = 0.3, r = 0, b = 0.4, l = 0.2, "cm"))})
+  plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))}
+
+# Define function to plot ERP waveforms and topographies
+plot_erps <- function(comps, evokeds, montage, stars){
+  pmap(comps, function(name, start, stop, roi){
+    # N400 gets a different scale than P1 and N1
+    ymin <- ifelse(name == "N400", -3, -4)
+    # Loop through parts
+    parts <- map(c("Pt1", "Pt2", "Pt3"), function(part){
+      # Create (conditions x time points) x electrodes tibble
+      data_plot <- evokeds[[part]] %>% map(function(data){
+        data %>% "*"(1e6) %>% t() %>% as_tibble(.name_repair = "unique") %>% set_colnames(montage$electrode) %>%
+          mutate(.time = times, roi = rowMeans(select(., all_of(roi))))}) %>%
+        bind_rows(.id = "condition")
+      # Prepare waveform
+      wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
+        annotate("rect", xmin = start, xmax = stop, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
+      # Shade significant area
+      star <- stars[[name]][[part]]
+      if (!is.na(star)){
+        wave <- wave + geom_ribbon(data = data_plot %>% filter(.time >= start & .time <= stop) %>%
+                                     group_by(.time) %>% summarise(ymin = min(roi), ymax = max(roi)),
+                                   aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
+                                   inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1))} #+
+          #annotate("text", label = star, x = start + (stop - start)/2, y = -3.2, size = 7, family = "Helvetica")}
+      # Add waves and styling
+      wave <- wave +
+        annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
+        annotate("segment", x = 0, xend = 0, y = ymin, yend = ymin + 12) +
+        annotate("segment", x = seq(-100, 700, 200), xend = seq(-100, 700, 200), y = -0.3, yend = 0) +
+        annotate("segment", x = -12, xend = 0, y = seq(-2, 8, 4), yend = seq(-2, 8, 4)) +
+        annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10/.pt, family = "Helvetica") +
+        annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10/.pt, family = "Helvetica", hjust = 1) +
+        annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10/.pt, family = "Helvetica", lineheight = 0.9) +
+        annotate("text", x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10/.pt, family = "Helvetica", angle = 90, lineheight = 0.9) +
+        geom_line() +
+        scale_color_viridis_d(end = 0.5) +
+        coord_cartesian(xlim = c(-200, 800), ylim = c(ymin, ymin + 14), expand = FALSE) +
+        theme_void() +
+        theme(legend.position = "none")
+      # Plot topography
+      topo <- data_plot %>% filter(.time >= start & .time <= stop) %>%
+        group_by(condition) %>% summarise(across(montage$electrode, mean)) %>%
+        pivot_longer(-condition) %>% pivot_wider(names_from = condition) %>%
+        transmute(amplitude = Insight - Naive) %>% bind_cols(montage) %>%
+        eegUtils::topoplot(limits = c(-1, 1), palette = "viridis", contour = FALSE, highlights = roi, scaling = 0.1) +
+        theme(legend.position = "none")
+      topo$layers[[3]]$aes_params$size <- topo$layers[[4]]$aes_params$size <- topo$layers[[5]]$aes_params$size <- 0.6
+      # Combine waveform and topography
+      wave + draw_plot(topo, width = 320, height = 9, x = 500, y = ymin + 6.4)})
+    # Compbine plots for the different parts
+    plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
+    # Combine plots for the different components
+  }) %>% plot_grid(plotlist = ., nrow = 3)}
+
+# Define functions to plot legends for conditions and topoplots
+plot_legends <- function(){
+  legend_conditions <- get_legend(tibble(Conditions = c("Insight", "Naive")) %>% ggplot(aes(x = 0, y = 0, fill = Conditions)) +
+                                    geom_raster() + scale_fill_viridis_d(end = 0.5) +
+                                    theme(legend.direction = "horizontal", legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
+                                          legend.text = element_text(family = "Helvetica", size = 10), legend.spacing.x = unit(0.3, "cm")))
+  legend_topo <- get_legend(tibble(amplitude = c(-1, 1)) %>% ggplot(aes(x = 0, y = 0, fill = amplitude)) + geom_raster() + labs(fill = "Insight - naive\nampl. (µV)") +
+                              scale_fill_viridis_c(guide = guide_colorbar(ticks = FALSE, title.position = "left", title.vjust = 1, title.hjust = 0.5)) +
+                              theme(legend.direction = "horizontal", legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
+                                    legend.text = element_text(family = "Helvetica", size = 10), legend.key.width = unit(0.8, "cm"), legend.spacing.x = unit(0.3, "cm")))
+  plot_grid(NULL, legend_conditions, legend_topo, NULL, nrow = 1, rel_widths = c(1, 3, 3, 1))}
+
+# Apply the functions to the data from experiment 1
+plot_grid(plot_trial(),
+          plot_bars(data = data_exp1, stars = stars_exp1, ymin = -1.5),
+          plot_erps(comps = comps, evokeds = evokeds_exp1, montage = montage, stars = stars_exp1),
+          plot_legends(),
+          nrow = 4, rel_heights = c(3, 2, 6, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica")
+```
+
+```{r exp2-behavior}
+# List of filenames for behavioral data
+fnames_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE)
+
+# Apply the preprocessing function
+data_exp2 <- map(fnames_exp2, preproc_behav)
+
+# Tabulate percentage of stimuli per condition
+(stims_exp2 <- bind_rows(data_exp2) %>% filter(condition != "Excl_cond") %>%
+    group_by(participant, condition) %>% tally() %>%
+    group_by(condition) %>% summarise(mean = mean(n)/(60*3)) %>% # 60 items per condition
+    mutate(mean = if_else(condition == "Excl_known", mean/2, mean))) # 120 items in total
 ```
@@
 
+# Import behavioral data from R
+metadata_exp2 = r.data_exp2
+
 # Check if preprocessing was done already (delete the file to re-run)
@@
 else:
-  # Actually apply the preprocessing function
-  epochs_exp2 = [preproc(fname, **preproc_params) for fname in fnames_exp2]
-  # Combine into a single data set
+  # Apply the preprocessing function
+  epochs_exp2 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp2, metadata_exp2)]
+  # Combine epochs into a single data set
   epochs_exp2 = mne.concatenate_epochs(epochs_exp2)
-  # Backup epochs to the export folder
+  # Backup epochs to the output folder
   epochs_exp2.save('output/exp2-epo.fif')
 
-# Get indices of bad epochs despite ICA
-rej_exp2 = epochs_exp2.copy().drop_bad(reject=reject).drop_log
-rej_exp2[:] = [item for item in rej_exp2 if item != ['IGNORED']]
-rej_exp2 = [i for i in range(len(rej_exp2)) if rej_exp2[i] != []]
+# # Get indices of bad epochs despite ICA
+# rej_exp2 = epochs_exp2.drop_log
+# rej_exp2[:] = [item for item in rej_exp2 if item != ['IGNORED']]
+# rej_exp2 = [i for i in range(len(rej_exp2)) if rej_exp2[i] != []]
+
+# Apply the function to compute grand averages
+evokeds_exp2, evokeds_dat_exp2 = compute_evokeds(epochs=epochs_exp2)
 ```
@@
 ```{r exp2-analysis}
-# List of filenames for behavioral data
-fnames_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE)
+# Re-import behavioral data
+data_exp2 <- py$epochs_exp2$metadata
 
-# Actually apply the preprocessing function
-data_exp2 <- map_dfr(fnames_exp2, preproc_behav)
+# Factorize some columns
+data_exp2 %<>% mutate(part = factor(part, levels = c("1", "2", "3")),
+                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_known", "Excl_cond")),
+                      participant = factor(participant), item = factor(item))
 
-# Add factorized columns for participants and items (the random variables)
-data_exp2 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))
+# Check number of rejected epochs
+rejected_exp2 <- data_exp2 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
+mean(rejected_exp2); median(rejected_exp2); range(rejected_exp2)
 
-# Tabulate percentage of stimuli per condition
-stims_exp2 <- table(data_exp2$participant, data_exp2$condition)
-stims_exp2 <- colMeans(stims_exp2)
-stims_exp2["Known"]/(3*120) # Three repititions and 120 objects
-stims_exp2[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each
-
-# Import epochs from Python, converting Volts to Microvolts
+# Check if ERPs were computed already (delete the file to re-run)
+if (file.exists("output/exp2-erps.RDS")){
+  # Load ERPs from file
+  data_exp2 <- readRDS("output/exp2-erps.RDS")
+} else {
+  # Import epochs from Python, converting Volts to Microvolts (takes a while)
   epochs_exp2 <- py$epochs_exp2$get_data()*1e6
-
-# Set rejected epochs to NA
-rej_exp2 <- py$rej_exp2 + 1
-epochs_exp2[rej_exp2,,] <- NA
-
-# Apply function to compute single-trial ERPs and to the behavioral data
-data_exp2 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp2, els = els) %>% set_names(comps$name) %>% cbind(data_exp2, .)
-
-# Remove trials with missing ERPs or RTs
-rej_exp2_erp <- data_exp2 %>% filter(is.na(P1)) %>% count(participant, .drop = FALSE) %>% pull(n)
-data_exp2 %<>% filter(!is.na(P1))
-rej_exp2_rt <- data_exp2 %>% filter(is.na(RT)) %>% count(participant, .drop = FALSE) %>% pull(n)
-data_exp2 %<>% filter(!is.na(RT))
+  # Apply the ERP function and save to output folder
+  data_exp2 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp2, els = els) %>%
+    set_names(comps$name) %>% cbind(data_exp2, .) %T>% saveRDS("output/exp2-erps.RDS")}
 
 # Remove any trials that don't beling to either of the two conditions
-data_exp2 %<>% filter(condition != "Known") %>% droplevels()
+data_exp2 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
 
-# Set sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
-contrasts(data_exp2$condition) <- ginv(contrasts.condition)
-contrasts(data_exp2$part) <- ginv(contrasts.part)
+# Sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
+contrasts(data_exp2$condition) <- ginv(contrasts_condition)
+contrasts(data_exp2$part) <- ginv(contrasts_part)
 
@@
 } else {
-  # Actually apply the modelling function
-  models_exp2 <- map(comps$name, compute_models, formula = form, data = data_exp2, control = ctrl_params, specs = specs) %>%
-    set_names(comps$name)
-  # Backup epochs to the export folder
-  saveRDS(models_exp2, "output/exp2-stats.RDS")}
+  # Apply the modelling function and save to output folder
+  models_exp2 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp2, control = ctrl_params,
+                     specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/exp2-stats.RDS")}
+
+# Store significance levels for plotting
+stars_exp2 = list(P1 = c(Pt1 = NA, Pt2 = NA, Pt3 = NA),
+                  N1 = c(Pt1 = NA, Pt2 = "*", Pt3 = NA),
+                  N400 = c(Pt1 = NA, Pt2 = "***", Pt3 = NA))
+```
+
+```{r exp2-table, include=TRUE, results="asis"}
+# Apply the function to print the table
+create_table(models_exp2, stub.anova = c("Part", "Insight", "Pt. × ins."),
+            stub.contrasts = c("Part 1", "Part 2", "Part 3"),
+            caption = "Results of linear mixed-effects regression models for Experiment 2",
+            note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
+```
+
+```{r exp2-plotting, include=TRUE, fig.height=9}
+# Import grand averaged evoked potentials from Python
+evokeds_exp2 <- py$evokeds_dat_exp2
+
+# Apply the plotting functions to the data from experiment 2
+plot_grid(plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
+          plot_erps(comps = comps, evokeds = evokeds_exp2, montage = montage, stars = stars_exp2),
+          plot_legends(),
+          nrow = 3, rel_heights = c(2, 6, 1), labels = c("A", "B", ""), label_fontfamily = "Helvetica")
 ```
@@
 
-# Set sliding difference coding for experiment (2-1), condition (insight-naive), and part (2-1, 3-1)
-t(contrasts.experiment <- t(cbind(c("1" = -1, "2" = 1))))
-contrasts(data_joint$experiment) <- ginv(contrasts.experiment)
-contrasts(data_joint$condition) <- ginv(contrasts.condition)
-contrasts(data_joint$part) <- ginv(contrasts.part)
+# Sliding difference coding for experiment (2-1), condition (insight-naive), and part (2-1, 3-1)
+t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
+contrasts(data_joint$experiment) <- ginv(contrasts_experiment)
+contrasts(data_joint$condition) <- ginv(contrasts_condition)
+contrasts(data_joint$part) <- ginv(contrasts_part)
 
 # New formula for LMMs
-form_joint <- tabulate.formula(~ experiment*part*condition + (part*condition|participant) + (experiment*part*condition|item))
+form_joint <- tabulate.formula(~ part*condition*experiment + (part*condition|participant) + (part*condition*experiment|item))
 form_joint %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
@@
 } else {
-  # Actually apply the modelling function
-  models_joint <- map(comps$name, compute_models, formula = form_joint, data = data_joint, control = ctrl_params, specs = specs) %>%
-    set_names(comps$name)
-  # Backup epochs to the export folder
-  saveRDS(models_joint, "output/joint-stats.RDS")}
+  # Apply the modelling function and save to output folder
+  models_joint <- map(comps$name, compute_models, formula = form_joint, data = data_joint, control = ctrl_params,
+                      specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/joint-stats.RDS")}
+```
+
+```{r joint-table, include=TRUE, results="asis"}
+# Apply the function to print the table
+create_table(models_joint, stub.anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.",
+                                         "Ins. × exp.", "Pt. × ins. × exp."),
+            stub.contrasts = c("Part 1", "Part 2", "Part 3"),
+            caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
+            note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.")
+```
+
+```{r exp3-behavior}
+# List of filenames for behavioral data
+fnames_exp3 <- list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE)
+
+# Apply the preprocessing function
+data_exp3 <- map(fnames_exp3, preproc_behav)
+
+# Tabulate percentage of stimuli per condition
+(stims_exp3 <- bind_rows(data_exp3) %>% filter(condition != "Excl_cond" & part != "4") %>%
+    group_by(participant, condition) %>% tally() %>%
+    group_by(condition) %>% summarise(mean = mean(n)/(112*3)) %>% # 112 items per condition
+    mutate(mean = if_else(condition == "Excl_known", mean/2, mean))) # 224 items in total
+```
+
+```{python exp3-preprocessing}
+# List of raw EEG filenames
+fnames_exp3 = sorted(glob.glob('data/exp3/EEG/*.vhdr'))
+
+# Import behavioral data from R
+metadata_exp3 = r.data_exp3
+
+# Update stimulus triggers
+preproc_params['event_id'] = {'match/upright': 241, 'match/inverted': 242, 'mismatch/upright': 243, 'mismatch/inverted': 244}
+
+# Check if preprocessing was done already (delete the file to re-run)
+if os.path.exists('output/exp3-epo.fif'):
+  # Load preprocessed data from file
+  epochs_exp3 = mne.read_epochs('output/exp3-epo.fif', preload=True)
+else:
+  # Apply the preprocessing function
+  epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp3, metadata_exp3)]
+  # Combine epochs into a single data set
+  epochs_exp3 = mne.concatenate_epochs(epochs_exp3)
+  # Backup epochs and evokeds to the output folder
+  epochs_exp3.save('output/exp3-epo.fif')
+
+# # Get indices of bad epochs despite ICA
+# rej_exp3 = epochs_exp3.drop_log
+# rej_exp3[:] = [item for item in rej_exp3 if item != ['IGNORED']]
+# rej_exp3 = [i for i in range(len(rej_exp3)) if rej_exp3[i] != []]
+```
+
+```{r exp3-analysis}
+# Re-import behavioral data
+data_exp3 <- py$epochs_exp3$metadata
+
+# Factorize some columns
+data_exp3 %<>% mutate(part = factor(part, levels = c("1", "2", "3")),
+                      position = factor(position, levels = c("Inverted", "Upright")),
+                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_known", "Excl_cond")),
+                      participant = factor(participant), item = factor(item))
+
+# Check if ERPs were computed already (delete the file to re-run)
+if (file.exists("output/exp3-erps.RDS")){
+  # Load ERPs from file
+  data_exp3 <- readRDS("output/exp3-erps.RDS")
+} else {
+  # Import epochs from Python, converting Volts to Microvolts (takes a while)
+  epochs_exp3 <- py$epochs_exp3$get_data()*1e6
+  # Apply the ERP function and save to output folder
+  data_exp3 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp3, els = els) %>%
+    set_names(comps$name) %>% cbind(data_exp3, .) %T>% saveRDS("output/exp3-erps.RDS")}
+
+# Remove any trials from part 4
+data_exp3 %<>% filter(part != "4") %>% droplevels()
+
+# Check number of rejected epochs
+rejected_exp3 <- data_exp3 %>% group_by(participant) %>% tally() %>% mutate(n = 672 - n) %>% pull(n)
+mean(rejected_exp3); median(rejected_exp3); range(rejected_exp3)
+
+# Remove any trials that don't beling to either of the two conditions
+data_exp3 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
+
+# Sliding difference coding for position (inverted-updright), condition (insight-naive), and part (2-1, 3-1)
+t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
+contrasts(data_exp3$position) <- ginv(contrasts_position)
+contrasts(data_exp3$condition) <- ginv(contrasts_condition)
+contrasts(data_exp3$part) <- ginv(contrasts_part)
+
+# New formula for LMMs
+form_exp3 <- tabulate.formula(~ part*condition*position + (part*condition*position|participant) + (part*condition*position|item))
+form_exp3 %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
+
+# New follow-up contrasts
+specs_exp3 = pairwise ~ condition|position*part
+
+# Check if models were computed already (delete the file to re-run)
+if (file.exists("output/exp3-stats.RDS")){
+  # Load models from file
+  models_exp3 <- readRDS("output/exp3-stats.RDS")
+} else {
+  # Apply the modelling function and save to output folder
+  models_exp3 <- map(comps$name, compute_models, formula = form_exp3, data = data_exp3, control = ctrl_params,
+                     specs = specs_exp3) %>% set_names(comps$name) %T>% saveRDS("output/exp3-stats.RDS")}
+```
+
+```{r exp3-table, include=TRUE, results= asis"}
+# Apply the function to print the table
+create_table(models_exp3, stub.anova = c("Part", "Insight", "Position", "Pt. × ins.", "Pt. × pos.",
+                                        "Ins. × pos.", "Pt. × ins. × pos."),
+            stub.contrasts = c("Part 1, inverted", "Part 1, upright", "Part 2, inverted",
+                               "Part 2, upright", "Part 3, inverted", "Part 3, upright"),
+            caption = "Results of linear mixed-effects regression models for Experiment 3",
+            note = "Pt. = part, ins. = insight, pos. = position, est. = estimate, CI = confidence interval.")
 ```

### 2020-09-02 manuscript/manuscript.Rmd
test hackmd
render plots

@@
 # Chunk options
-knitr::opts_chunk$set(include = FALSE, echo = FALSE, fig.out = "100%", fig.width = 10)
+knitr::opts_chunk$set(include = FALSE, fig.align = "center", fig.out = "100%", fig.width = 10)
 
@@
 
-```{r exp1-behavior}
+```{r exp1-preparation}
 # Function for processing behavioral data
@@
 
-```{r exp1-table, include=TRUE, results="asis"}
+```{r exp1-output, include=TRUE, results="asis", fig.height=12}
 # Check if models were computed already (delete the file to re-run)
@@
     bind_cols() %>% set_rownames(c(stub.anova))
-  cnames <- c("\\textit{Type III}", rep(c("\\textit{F} (\\textit{df})", "p" = "\\textit{p}"), 3))
+  cnames <- c("\\textit{Fixed effects}", rep(c("\\textit{F} (\\textit{df})", "p" = "\\textit{p}"), 3))
   conts <- map(models, function(model){
@@
              note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
-```
 
-```{r exp1-plotting, include=TRUE, fig.height=12}
 # Import grand averaged evoked potentials from Python
@@
 
-```{r exp2-behavior}
+```{r exp2-preparation}
 # List of filenames for behavioral data
@@
 
-```{r exp2-table, include=TRUE, results="asis"}
+```{r exp2-output, include=TRUE, results="asis", fig.height=9}
 # Apply the function to print the table
@@
             note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
-```
 
-```{r exp2-plotting, include=TRUE, fig.height=9}
 # Import grand averaged evoked potentials from Python
@@
 
-```{r joint-table, include=TRUE, results="asis"}
+```{r joint-output, include=TRUE, results="asis"}
 # Apply the function to print the table
@@
 
-```{r exp3-behavior}
+```{r exp3-preparation, eval=FALSE}
 # List of filenames for behavioral data
@@
 
-```{python exp3-preprocessing}
+```{python exp3-preprocessing, eval=FALSE}
 # List of raw EEG filenames
@@
 
-```{r exp3-analysis}
+```{r exp3-analysis, eval=FALSE}
 # Re-import behavioral data
@@
 
-```{r exp3-table, include=TRUE, results= asis"}
+```{r exp3-output, include=TRUE, results="asis", eval=FALSE}
 # Apply the function to print the table

### 2020-09-02 manuscript/manuscript.tex
add plots
render plots

@@
   english,
-  man]{apa7}
+  man,floatsintext]{apa7}
 \usepackage{lmodern}
@@
 \keywords{keywords\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
   \usepackage[shorthands=off,main=english]{babel}
+\fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
 \fi
@@
 
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:exp1-output}Results of linear mixed-effects regression models for Experiment 1}
+
+\footnotesize{
+
+\begin{tabular}{lcccccc}
+\toprule
+ & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
+\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
+\textit{Type III} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\midrule
+Part & 10.30 (2,   23.4) & .001 & 13.56 (2,   23.9) & <.001 & 31.61 (2,   24.4) & <.001\\
+Insight & 0.87 (1, 5299.9) & .352 & 0.96 (1, 5341.1) & .327 & 21.83 (1, 5210.4) & <.001\\
+Pt. × ins. & 2.37 (2, 4616.5) & .094 & 5.34 (2, 4949.3) & .005 & 11.16 (2, 5058.3) & <.001\\
+\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Part 1 & 0.00 [-0.50, 0.49] & .991 & -0.17 [-0.62,  0.29] & .480 & -0.21 [-0.61, 0.18] & .292\\
+Part 2 & -0.15 [-0.65, 0.35] & .553 & -0.66 [-1.12, -0.20] & .005 & 0.91 [ 0.51, 1.31] & <.001\\
+Part 3 & 0.57 [ 0.08, 1.07] & .024 & 0.41 [-0.05,  0.87] & .080 & 0.99 [ 0.59, 1.39] & <.001\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_files/figure-latex/exp1-output-1}
+
+}
+
+\caption{ }\label{fig:exp1-output}
+\end{figure}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:exp2-output}Results of linear mixed-effects regression models for Experiment 2}
+
+\footnotesize{
+
+\begin{tabular}{lcccccc}
+\toprule
+ & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
+\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
+\textit{Type III} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\midrule
+Part & 4.71 (2,   22.6) & .020 & 15.69 (2,   23.9) & <.001 & 67.52 (2,   24.1) & <.001\\
+Insight & 0.05 (1, 5221.8) & .826 & 1.24 (1, 5215.3) & .266 & 18.64 (1, 5203.6) & <.001\\
+Pt. × ins. & 1.72 (2, 3556.7) & .180 & 1.33 (2, 4746.9) & .266 & 8.01 (2, 4652.4) & <.001\\
+\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Part 1 & -0.17 [-0.72, 0.37] & .534 & -0.04 [-0.54, 0.45] & .858 & 0.02 [-0.44, 0.48] & .935\\
+Part 2 & -0.32 [-0.87, 0.24] & .264 & -0.50 [-0.99, 0.00] & .050 & 1.31 [ 0.85, 1.77] & <.001\\
+Part 3 & 0.38 [-0.18, 0.94] & .181 & 0.04 [-0.45, 0.54] & .864 & 0.45 [-0.01, 0.92] & .054\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_files/figure-latex/exp2-output-1}
+
+}
+
+\caption{ }\label{fig:exp2-output}
+\end{figure}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:joint-output}Results of linear mixed-effects regression models for Experiments 1 and 2 combined}
+
+\footnotesize{
+
+\begin{tabular}{lcccccc}
+\toprule
+ & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
+\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
+\textit{Type III} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\midrule
+Part & 11.83 (2,    47.0) & <.001 & 28.64 (2,    47.8) & <.001 & 91.32 (2,    48.4) & <.001\\
+Insight & 0.35 (1, 10554.2) & .554 & 1.64 (1,   124.2) & .203 & 38.73 (1, 10511.3) & <.001\\
+Experiment & 0.34 (1,    46.2) & .564 & 2.29 (1,    46.1) & .137 & 4.56 (1,    46.4) & .038\\
+Pt. × ins. & 3.96 (2,  9094.4) & .019 & 5.59 (2,  9889.2) & .004 & 15.71 (2, 10020.2) & <.001\\
+Pt. × exp. & 0.03 (2,    47.0) & .971 & 0.53 (2,    47.8) & .595 & 2.47 (2,    48.4) & .095\\
+Ins. × exp. & 0.62 (1, 10530.2) & .432 & 0.04 (1, 10325.9) & .838 & 0.03 (1, 10567.6) & .867\\
+Pt. × ins. × exp. & 0.02 (2,  9094.8) & .976 & 0.63 (2,  9889.5) & .533 & 2.64 (2, 10020.5) & .072\\
+\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Part 1 & -0.07 [-0.44, 0.30] & .703 & -0.10 [-0.44,  0.24] & .563 & -0.10 [-0.41, 0.20] & .507\\
+Part 2 & -0.22 [-0.59, 0.15] & .251 & -0.56 [-0.90, -0.21] & .002 & 1.09 [ 0.78, 1.39] & <.001\\
+Part 3 & 0.49 [ 0.12, 0.86] & .010 & 0.25 [-0.10,  0.59] & .158 & 0.72 [ 0.41, 1.02] & <.001\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \newpage

### 2020-09-11 manuscript/manuscript.Rmd

--- 2020-07-29 manuscript/manuscript.Rmd
@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "Title of the Thesis Goes Here"
+shorttitle        : "Short title goes here"
 
 author: 
-  - name          : "First Author"
+  - name          : "Alexander Enge"
     affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
-    role:
-      - Writing - Review & Editing
+    address       : "Rudower Chaussee 18, 12489 Berlin"
+    email         : "alexander.enge@hu-berlin.de"
 
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
-  - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "Humboldt-Universität zu Berlin"
 
@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : "r-references.bib"
+zotero            : "aha"
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 documentclass     : "apa7"
-classoption       : "man"
-output            : papaja::apa6_pdf
+classoption       : "man,11pt"
+output:
+  papaja::apa6_pdf:
+    latex_engine:   "xelatex"
+
+header-includes:
+  - \usepackage{setspace}
+  - \AtBeginEnvironment{tabular}{\doublespacing}
+  - \AtBeginEnvironment{lltable}{\doublespacing}
+  - \AtBeginEnvironment{tablenotes}{\doublespacing}
+  - \captionsetup[table]{font={stretch=1.5}}
+  - \captionsetup[figure]{font={stretch=1,scriptsize}}
+  - \raggedbottom
 ---
 
-```{r setup, include = FALSE}
+```{r setup, include=FALSE}
 # Load packages
@@
 library(reticulate)
-library(MASS)
-library(Matrix)
 library(lme4)
 library(buildmer)
-library(emmeans)
+library(tidyverse)
 library(magrittr)
-library(tidyverse)
+library(cowplot)
 
 # Chunk options
-knitr::opts_chunk$set(include = FALSE, echo = FALSE)
+knitr::opts_chunk$set(include = FALSE, fig.align = "center", fig.out = "100%", fig.width = 10)
 
-# Specify conda environment for Python
-use_condaenv("r-reticulate", required = TRUE)
+# Specify Python environment
+renv::use_python(type = "virtualenv")
 
@@
 
-```{r exp1-behavior}
-# Define function for processing behavioral data
-preproc_behav <- function(txt_fname){
+Introduction section goes here.
+
+# Experiment 1
+
+```{r exp1-preparation}
+# Define function for reading and formatting behavioral data
+read_behav <- function(txt_fname){
   # Read log file
   dat <- suppressMessages(suppressWarnings(read_tsv(txt_fname)))
-  # Remove filler stimuli (well-known objects)
-  dat %<>% filter(bek_unbek != "bekannt")
+  # Rename some columns
+  dat %<>% rename(participant = VPNummer, item = StimID) %>%
     # Add a column for the part of the experiment
-  dat %<>% mutate(part = as_factor(Wdh - 210))
+    mutate(part = case_when(Wdh %in% c(211, 231) ~ "I",
+                            Wdh %in% c(212, 232) ~ "II",
+                            Wdh %in% c(213, 233) ~ "III",
+                            Wdh == 234 ~ "IV") %>% as_factor()) %>%
+    # Remove filler stimuli (i.e. well-known objects)
+    filter(bek_unbek != "bekannt")
   # Assign stimuli to conditions based on keywords and button presses
-  known <- dat %>% filter(part == "1" & Tastencode == 201) %>% pull(StimID)
-  insight <- dat %>%filter(part == "2" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>% pull(StimID)
-  naive <- dat %>% filter(part == "2" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>% pull(StimID)
-  dat %<>% mutate(condition = as_factor(case_when(StimID %in% known ~ "Known",
-                                                  StimID %in% insight ~ "Insight",
-                                                  StimID %in% naive ~ "Naive")))
-  # Remove unrealistically short RTs
-  dat %<>% mutate(RT = replace(RT, RT < 200, NA))
+  excl_known <- dat %>% filter(part == "I" & Tastencode %in% c(201, 251)) %>% pull(item)
+  excl_insight <- dat %>% filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
+  excl_naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
+  insight <- dat %>% filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
+  naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
+  # Create a new condition column, excluding trials with known stimuli or without condition
+  dat %<>% mutate(condition = case_when(item %in% excl_known ~ "Excl_known",
+                                        item %in% excl_insight ~ "Excl_insight",
+                                        item %in% excl_naive ~ "Excl_naive",
+                                        item %in% insight ~ "Insight",
+                                        item %in% naive ~ "Naive") %>%
+                    factor(levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")))
+  # In Experiment 3, we need an additional column for position (upright vs. inverted)
+  if("richtig_inv" %in% dat$Bed){
+    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
+      # Return only relevant columns
+      select(part, position, condition, participant, item, RT)
+  } else {
+    dat %<>% select(part, condition, participant, item, RT)}
   return(dat)}
 
-# List of filenames for behavioral data
+# Read behavioral data for Experiment 1
 fnames_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE)
+data_exp1 <- map(fnames_exp1, read_behav)
 
-# Actually apply the preprocessing function
-data_exp1 <- map_dfr(fnames_exp1, preproc_behav)
-
-# Add factorized columns for participants and items (the random variables)
-data_exp1 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))
-
-# Tabulate percentage of stimuli per condition
-stims_exp1 <- table(data_exp1$participant, data_exp1$condition)
-stims_exp1 <- colMeans(stims_exp1)
-stims_exp1["Known"]/(3*120) # Three repititions and 120 objects
-stims_exp1[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each
-
-# Select only relevant columns
-data_exp1 %<>% select(part, condition, participant, item, RT)
-
-# Tell MNE to exclude trials without a proper condition or RT
-data_exp1 %<>% mutate(condition = replace(condition, condition == "Known" | is.na(RT), NA)) %>%
-  mutate(condition = fct_explicit_na(condition, na_level = "Exclude")) %>% droplevels()
+# Check average number of stimuli per condition
+(stims_exp1 <- map(data_exp1, function(x){table(x$condition)/3}) %>% bind_rows() %>% colMeans())
 ```
@@
 
-# Define parameters for preprocessing
+# Set parameters for EEG preprocessing
 preproc_params = dict(n_components=15, method='fastica',           # ICA parameters
@@
 
-# Define preprocessing function
-def preproc(vhdr_fname, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline):
-  # Load EEG data
+# Define function for preprocessing EEG data
+def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline, reject):
+  # Read EEG data
   raw = mne.io.read_raw_brainvision(vhdr_fname, preload=True)
-  # Create new virtual EOG channels
+  # Create virtual EOG channels
   raw = mne.set_bipolar_reference(raw, 'Auge_u', 'Fp1', ch_name='VEOG', drop_refs=False)
@@
   events, _ = mne.events_from_annotations(raw, verbose=False)
-  epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax,
-                      baseline=baseline, preload=True)
-
-  # # Autoreject                    
-  # import autoreject
-  # 
-  # ar = autoreject.AutoReject(thresh_method='random_search', verbose=False)
-  # epochs_clean = ar.fit_transform(epochs)
-  # 
-  # rejected = epochs_clean.drop_log
-  # rejected[:] = [item for item in rejected if item != ['IGNORED']]
-  # rejected = [i for i in range(len(rejected)) if rejected[i] != []]
-  # 
-  # ransac = autoreject.Ransac(verbose=False)
-  # epochs = ransac.fit_transform(epochs)
-  # 
-  # reject = autoreject.get_rejection_threshold(epochs)
-
+  epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True)
+  # Add behavioral data
+  epochs.metadata = metadata
+  # Reject bad epochs
+  epochs = epochs.drop_bad(reject=reject)
   return epochs
 
-# List of raw EEG filenames
+# List raw EEG filenames
 fnames_exp1 = sorted(glob.glob('data/exp1/EEG/*.vhdr'))
+
+# Import behavioral data from R
+metadata_exp1 = r.data_exp1
 
@@
 if os.path.exists('output/exp1-epo.fif'):
-  # Load preprocessed data from file
+  # Read preprocessed data from file
   epochs_exp1 = mne.read_epochs('output/exp1-epo.fif', preload=True)
 else:
-  # Actually apply the preprocessing function
-  epochs_exp1 = [preproc(fname, **preproc_params) for fname in fnames_exp1]
-  # Combine into a single data set
+  # Preprocess EEG data for Experiment 1
+  epochs_exp14 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp1, metadata_exp1)]
+  # Combine epochs into a single data set
   epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
-  # Add metadata from R
-  epochs_exp1.metadata = r.data_exp1
-  # Backup epochs to the export folder
+  # Backup epochs to the output folder
   epochs_exp1.save('output/exp1-epo.fif')
 
-# Remove trials with invalid condition or RTs
-epochs_exp1 = epochs_exp1['condition != "Exclude"']
-
-# # Compute evoked potentials for each part x condition
-# evokeds_exp1 = dict()
-# for pt in ['1', '2', '3']:
-#   for cn in ['Insight', 'Naive']:
-#     query = 'part == "' + pt + '" and condition == "' + cn + '"'
-#     evokeds_exp1['Part' + pt + '_' + cn] = epochs_exp1[query].average()
-# mne.viz.plot_compare_evokeds(evokeds_exp1, cmap=('condition', 'viridis'), picks='P8')
-
 # # Get indices of bad epochs despite ICA
-# rej_exp1 = epochs_exp1.copy().drop_bad(reject=reject).drop_log
+# rej_exp1 = epochs_exp1.drop_log
 # rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
 # rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
+
+# Define function to compute grand averages per condition
+def compute_evokeds(epochs):
+  evokeds = dict()
+  evokeds_dat = dict()
+  # Each part becomes a dictionary of conditions
+  for pt in ['I', 'II', 'III']:
+    evokeds[pt] = dict()
+    evokeds_dat[pt] = dict()
+    # Each condition becomes a list of participants
+    for cn in ['Insight', 'Naive']:
+      evokeds[pt][cn] = list()
+      evokeds_dat[pt][cn] = list()
+      # For every participant we average trials separately for all parts and conditions
+      for vp in epochs.metadata['participant'].unique():
+        query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
+        evokeds[pt][cn].append(epochs[query].average())
+      # Compute grand averages across participants for this part and condition
+      evokeds[pt][cn] = mne.grand_average(evokeds[pt][cn])
+      # Export only the actual data for R
+      evokeds_dat[pt][cn] = evokeds[pt][cn].data
+  return(evokeds, evokeds_dat)
+
+# Compute grand averages for Experiment 1
+evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)
+
+# # Plot evoked potentials
+# import matplotlib.pyplot as plt
+# mne.viz.plot_compare_evokeds(evokeds=evokeds_exp1['II'], picks='P8'); plt.show()
+# evokeds_exp1['II']['Insight'].data = evokeds_exp1['II']['Insight'].data - evokeds_exp1['II']['Naive'].data
+# evokeds_exp1['II']['Insight'].plot_topomap(times=[0.125, 0.175, 0.5], average=0.05, vmin=-1, vmax=1, cmap='viridis'); plt.show()
 ```
@@
 ```{r exp1-analysis}
+# Re-import behavioral data
+data_exp1 <- py$epochs_exp1$metadata
 
-# Import epochs from Python, converting Volts to Microvolts
-epochs_exp1 <- py$epochs_exp1$get_data()*1e6
+# Factorize some columns
+data_exp1 %<>% mutate(part = factor(part, levels = c("I", "II", "III")),
+                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")),
+                      participant = factor(participant),
+                      item = factor(item))
 
-# Set rejected epochs to NA
-rej_exp1 <- py$rej_exp1 + 1
-epochs_exp1[rej_exp1,,] <- NA
+# Check number of rejected epochs
+rejected_exp1 <- data_exp1 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
+mean(rejected_exp1); median(rejected_exp1); range(rejected_exp1)
 
@@
 
-# Define function to compute single-trial ERPs
+# Define function to compute single-trial mean ERP amplitudes
 compute_erps <- function(epochs, els, name, start, stop, roi){
@@
 
-# Apply the function and bind ERPs to the behavioral data
-data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>% set_names(comps$name) %>% cbind(data_exp1, .)
+# Check if single-trial ERPs were computed already (delete the file to re-run)
+if (file.exists("output/exp1-erps.RDS")){
+  # Read data from file
+  data_exp1 <- readRDS("output/exp1-erps.RDS")
+} else {
+  # Import epochs from Python, converting Volts to Microvolts
+  epochs_exp1 <- py$epochs_exp1$get_data()*1e6
+  # Compute single-trial ERPs for Experiment 1
+  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>%
+    set_names(comps$name) %>% cbind(data_exp1, .) %T>% saveRDS("output/exp1-erps.RDS")}
 
-# Remove trials with missing ERPs or RTs
-rej_exp1_erp <- data_exp1 %>% filter(is.na(P1)) %>% count(participant, .drop = FALSE) %>% pull(n)
-data_exp1 %<>% filter(!is.na(P1))
-rej_exp1_rt <- data_exp1 %>% filter(is.na(RT)) %>% count(participant, .drop = FALSE) %>% pull(n)
-data_exp1 %<>% filter(!is.na(RT))
+# Remove any trials excluded from conditions
+data_exp1 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
 
-# Remove any trials that don't beling to either of the two conditions
-data_exp1 %<>% filter(condition != "Known") %>% droplevels()
+# Contrast coding for condition (insight-naive) and part (2-1, 3-1)
+contrasts_condition <- t(cbind(c("Insight" = 1, "Naive" = -1)))
+contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
+contrasts(data_exp1$condition) <- MASS::ginv(contrasts_condition)
+contrasts(data_exp1$part) <- MASS::ginv(contrasts_part)
 
-# Set sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
-t(contrasts.condition <- t(cbind(c("Insight" = 1, "Naive" = -1))))
-t(contrasts.part <- t(cbind(c("1" = -1, "2" = 1, "3" = 0),
-                            c("1" = 0, "2" = -1, "3" = 1))))
-contrasts(data_exp1$condition) <- ginv(contrasts.condition)
-contrasts(data_exp1$part) <- ginv(contrasts.part)
-
-# Parameters for linear mixed-effects models (LMMs)
-form <- tabulate.formula(~ part*condition + (part*condition|participant) + (part*condition|item))
-form %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
+# Set formula and parameters for linear mixed-effects regression models (LMMs)
+form_exp12 <- tabulate.formula(~ part*condition + (part*condition|participant) + (part*condition|item))
+form_exp12 %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
 ctrl_params <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
 
-# Parameters for follow-up contrasts
-specs = pairwise ~ condition|part
+# Set formula for follow-up contrasts
+specs_exp12 = pairwise ~ condition|part
 
-# Define function to compute LMMs and contrasts
+# Define function to compute LMMs and follow-up contrasts for each component
 compute_models <- function(dep, formula, data, control, specs){
-  build <- buildmer(dep = dep, formula = formula, data = data, ddf = "Satterthwaite", calc.anova = TRUE, control = control)
+  require(emmeans)
   emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  conts <- emmeans(build@model, specs = specs, infer = TRUE)
+  build <- buildmer(dep = dep, formula = formula, data = data, control = control, REML = FALSE,
+                    ddf = "Satterthwaite", calc.anova = TRUE)
+  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts %>% as.data.frame()
   mod <- list("model" = build@model, "anova" = build@anova, "summary" = build@summary, "contrasts" = conts)
@@
 if (file.exists("output/exp1-stats.RDS")){
-   # Load models from file
+  # Read models from file
   models_exp1 <- readRDS("output/exp1-stats.RDS")
 } else {
-  # Actually apply the modelling function
-  models_exp1 <- map(comps$name, compute_models, formula = form, data = data_exp1, control = ctrl_params, specs = specs) %>%
-    set_names(comps$name)
-  # Backup epochs to the export folder
-  saveRDS(models_exp1, "output/exp1-stats.RDS")}
+  # Compute LMMs for Experiment 1
+  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
+                     specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/exp1-stats.RDS")}
+```
+
+## Methods
+
+### Participants
+
+Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history psychological disorder or treatment.
+All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
+They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+All experiments subsequently reported were carried out in accordance with the Declaration of Helsinki and approved by the local ethics committee.
+
+### Materials and Procedure
+
+Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g. a bicycle, a toothbrush), whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g. a galvanometer, an udu drum).
+A list of all objects can be found in Appendix A.
+They were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
+At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degress of participants' horizontal and vertical visual angle.
+
+For each unfamiliar object, a noun--verb pair was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g. current--measuring, pottery--drumming).
+In the *insight* condition, the presentation of each unfamiliar object was preceded by its respective description, whereas in the *naive* condition, it was preceded by a non-matching description belonging to one of the other objects.
+In both conditions, the noun and the verb were presented one above the other in black letters on a light blue background.
+For each participant, half of the unfamiliar objects were presented in the insight condition (i.e. with a matching description) and the other half were presented in the naive condition (i.e. with a non-matching description).
+All participants saw each unfamiliar object in only one of the two conditions and the assignment of objects to either of the two conditions was counterbalanced across participants.
+The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
+
+Each experimental session consisted of three parts (Figure \@ref(fig:exp1-plot)A).
+In Part I, after written informed consent was obtained and the EEG was prepared, all 240 familiar and unfamiliar objects were presented once in random order and without verbal descriptions.
+Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
+The intertrial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
+The task, which was kept the same throughout all three parts and experiments, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have a strong assumption," (c) "I have rather no assumption what this is," or (d) "I do not know what this is and have no assumotion." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
+Because we were interested in the acquisition of semantic knowledge about novel objects only, all objects for which the participant indicated knowing the object in Part I were excluded from further analysis (`r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)` of rare objects per participant).
+
+(ref:figure-1-caption) Procedure and results of Experiment 1.
+(A) In Part I, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In Part II, half of the objects were preceded by a matching description (in purple color for illustration), leading to semantic insight, and the other half with a non-matching description (in petrol color for illustration), leading to naive perception.
+In Part III, the same objects were presented again without the descriptions.
+(B) Bar plots and (C) ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III.
+Semantic insight was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
+Error bars show standard errors of the mean.
+\newline\**p* \< .05.
+\*\**p* \< .01.
+\*\*\**p* \< .001.
+
+```{r exp1-plot, include=TRUE, fig.height=12, fig.cap = "(ref:figure-1-caption)"}
+# Manually extract significance levels from contrasts for plotting
+stars_exp1 = list(P1 = c(I = NA, II = NA, III = "*"),
+                  N1 = c(I = NA, II = "**", III = NA),
+                  N400 = c(I = NA, II = "***", III = "**"))
+
+# Import grand averaged evoked potentials from Python
+evokeds_exp1 <- py$evokeds_dat_exp1
+
+# Retrive locations for the relevant electrodes from standard montage
+fname_montage <- list.files(path = "renv/python", pattern = "easycap-M1.txt", recursive = TRUE, full.names = TRUE)
+montage <- py$evokeds_exp1$I$Insight$ch_names %>% as_tibble() %>% rename(electrode = value) %>%
+  left_join(read.delim(fname_montage) %>% as_tibble() %>% rename(electrode = Site)) %>%
+  mutate(x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
+         y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)))
+
+# Define function to plot trial structure
+plot_trial <- function(){
+  colour_insight <- viridisLite::viridis(1, begin = 0, end = 0)
+  colour_naive <- viridisLite::viridis(1, begin = 0.5, end = 0.5)
+  trial_I <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
+    geom_text(aes(x = 37, y = 68, label = "Part I"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
+    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
+    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
+    draw_image("materials/exp1/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
+    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
+  trial_II <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
+    geom_text(aes(x = 37, y = 68, label = "Part II"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
+    geom_rect(aes(xmin = 0, xmax = 20, ymin = 0, ymax = 20), color = "black", fill = "white") +
+    geom_text(aes(x = 10, y = 10.5, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
+    geom_text(aes(x = 10, y = -3, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = colour_insight, fill = "white") +
+    geom_text(aes(x = 28, y = 23, label = "Potato\nmashing"), color = colour_insight, size = 10/.pt, family = "Helvetica") +
+    geom_text(aes(x = 28, y = 10, label = "2.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 39, ymax = 59), color = colour_naive, fill = "white") +
+    geom_text(aes(x = 28, y = 49, label = "Message\nmorsing"), color = colour_naive, size = 10/.pt, family = "Helvetica") +
+    geom_text(aes(x = 28, y = 36, label = "or"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
+    geom_text(aes(x = 46, y = 34, label = "*"), size = 8, family = "Helvetica") +
+    geom_text(aes(x = 46, y = 23, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 54, xmax = 74, ymin = 39, ymax = 59), color = "black", fill = "white") +
+    draw_image("materials/exp1/potato_masher.png", x = 54, y = 39, width = 20, height = 20) +
+    geom_text(aes(x = 65, y = 36, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica", lineheight = 1) +
+    geom_segment(aes(x = 28, y = 0, xend = 74, yend = 33.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
+  trial_III <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
+    geom_text(aes(x = 37, y = 68, label = "Part III"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
+    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
+    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
+    draw_image("materials/exp1/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
+    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica") +
+    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
+  plot_grid(trial_I, NULL, trial_II, NULL, trial_III, nrow = 1, rel_widths = c(10, 1, 10, 1, 10))}
+
+# Define function to plot mean ERP amplitudes
+plot_bars <- function(data, stars, ymin){
+  parts <- map(c("I", "II", "III"), function(part){
+    # For which components in the current part do we have a significant effect?
+    sig <- map(stars, part) %>% as.data.frame() %>% t() %>% as.data.frame() %>%
+      set_colnames("label") %>% rownames_to_column("comp") %>% na.omit()
+    # Create bar plot for the current part
+    map(c("P1", "N1", "N400"), function(comp){
+      p <- data %>% filter(part == !!part) %>%
+        Rmisc::summarySEwithin(measurevar = comp, withinvars = "condition", idvar = "participant") %>%
+        mutate(comp = !!comp) %>% rename(amplitude = !!comp)}) %>% bind_rows() %>%
+      mutate(comp = fct_relevel(comp, "P1", "N1", "N400")) %>%
+      ggplot(aes(x = comp, y = amplitude, fill = condition)) +
+      # geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
+      # annotate("tile", x = sig$comp, y = -0.4, width = 0.45, height = 0.8, colour = "black", fill = "white", size = 0.5) +
+      # annotate("rect", xmin = -Inf, xmax = Inf, ymin = -0.2, ymax = Inf, fill = "white") +
+      # geom_bar(aes(y = amplitude - se - 0.2), stat = "identity", position = position_dodge()) + scale_fill_manual(values = c("white", "white")) +
+      # new_scale_fill() +
+      # annotate("label", x = sig$comp, y = -0.96, label = sig$label, size = 7, family = "Helvetica", label.size = 0) +
+      geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
+      scale_fill_viridis_d(end = 0.5) +
+      geom_errorbar(aes(ymin = amplitude - se, ymax = amplitude + se), position = position_dodge(width = 0.9), width = 0.5) +
+      annotate("text", x = sig$comp, y = ymin, label = sig$label, size = 6, family = "Helvetica") +
+      geom_hline(yintercept = 0) +
+      coord_cartesian(ylim = c(ymin, ymin + 7)) +
+      ylab("ROI ampl.\n(µV)") +
+      scale_y_continuous(breaks = seq(trunc(ymin), trunc(ymin) + 6, 2)) +
+      theme_classic() +
+      theme(legend.position = "none",
+            panel.grid = element_blank(),
+            axis.ticks = element_line(color = "black"),
+            axis.title.x = element_blank(),
+            axis.title.y = element_text(family = "Helvetica", color = "black", size = 10),
+            axis.text = element_text(family = "Helvetica", color = "black", size = 10),
+            plot.margin = margin(t = 0.3, r = 0, b = 0.4, l = 0.2, "cm"))})
+  plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))}
+
+# Define function to plot ERP waveforms and topographies
+plot_erps <- function(comps, evokeds, montage, stars){
+  pmap(comps, function(name, start, stop, roi){
+    # N400 gets a different scale than P1 and N1
+    ymin <- ifelse(name == "N400", -3, -4)
+    # Loop through parts
+    parts <- map(c("I", "II", "III"), function(part){
+      # Create (conditions x time points) x electrodes tibble
+      data_plot <- evokeds[[part]] %>% map(function(data){
+        data %>% "*"(1e6) %>% t() %>% as_tibble(.name_repair = "unique") %>% set_colnames(montage$electrode) %>%
+          mutate(.time = times, roi = rowMeans(select(., all_of(roi))))}) %>%
+        bind_rows(.id = "condition")
+      # Prepare waveform
+      wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
+        annotate("rect", xmin = start, xmax = stop, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
+      # Shade significant area
+      star <- stars[[name]][[part]]
+      if (!is.na(star)){
+        wave <- wave + geom_ribbon(data = data_plot %>% filter(.time >= start & .time <= stop) %>%
+                                     group_by(.time) %>% summarise(ymin = min(roi), ymax = max(roi)),
+                                   aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
+                                   inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1))} #+
+          #annotate("text", label = star, x = start + (stop - start)/2, y = -3.2, size = 7, family = "Helvetica")}
+      # Add waves and styling
+      wave <- wave +
+        annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
+        annotate("segment", x = 0, xend = 0, y = ymin, yend = ymin + 12) +
+        annotate("segment", x = seq(-100, 700, 200), xend = seq(-100, 700, 200), y = -0.3, yend = 0) +
+        annotate("segment", x = -12, xend = 0, y = seq(-2, 8, 4), yend = seq(-2, 8, 4)) +
+        annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10/.pt, family = "Helvetica") +
+        annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10/.pt, family = "Helvetica", hjust = 1) +
+        annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10/.pt, family = "Helvetica", lineheight = 0.9) +
+        annotate("text", x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10/.pt,
+                 family = "Helvetica", angle = 90, lineheight = 0.9) +
+        geom_line() +
+        scale_color_viridis_d(end = 0.5) +
+        coord_cartesian(xlim = c(-200, 800), ylim = c(ymin, ymin + 14), expand = FALSE) +
+        theme_void() +
+        theme(legend.position = "none")
+      # Plot topography
+      topo <- data_plot %>% filter(.time >= start & .time <= stop) %>%
+        group_by(condition) %>% summarise(across(montage$electrode, mean)) %>%
+        pivot_longer(-condition) %>% pivot_wider(names_from = condition) %>%
+        transmute(amplitude = Insight - Naive) %>% bind_cols(montage) %>%
+        eegUtils::topoplot(limits = c(-1, 1), palette = "viridis", contour = FALSE, highlights = roi, scaling = 0.1) +
+        theme(legend.position = "none")
+      topo$layers[[3]]$aes_params$size <- topo$layers[[4]]$aes_params$size <- topo$layers[[5]]$aes_params$size <- 0.6
+      # Combine waveform and topography
+      wave + draw_plot(topo, width = 320, height = 9, x = 500, y = ymin + 6.4)})
+    # Compbine plots for the different parts
+    plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
+    # Combine plots for the different components
+  }) %>% plot_grid(plotlist = ., nrow = 3)}
+
+# Define functions to plot legends for conditions and topoplots
+plot_legends <- function(){
+  legend_conditions <- get_legend(tibble(Conditions = c("Insight", "Naive")) %>% ggplot(aes(x = 0, y = 0, fill = Conditions)) +
+                                    geom_raster() + scale_fill_viridis_d(end = 0.5) +
+                                    theme(legend.direction = "horizontal",
+                                          legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
+                                          legend.text = element_text(family = "Helvetica", size = 10),
+                                          legend.spacing.x = unit(0.3, "cm")))
+  legend_topo <- get_legend(tibble(amplitude = c(-1, 1)) %>% ggplot(aes(x = 0, y = 0, fill = amplitude)) + geom_raster() +
+                              labs(fill = "Insight - naive\nampl. (µV)") +
+                              scale_fill_viridis_c(guide = guide_colorbar(ticks = FALSE, title.position = "left",
+                                                                          title.vjust = 1, title.hjust = 0.5)) +
+                              theme(legend.direction = "horizontal",
+                                    legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
+                                    legend.text = element_text(family = "Helvetica", size = 10),
+                                    legend.key.width = unit(0.8, "cm"), legend.spacing.x = unit(0.3, "cm")))
+  plot_grid(NULL, legend_conditions, legend_topo, NULL, nrow = 1, rel_widths = c(1, 3, 3, 1))}
+
+# Create plot for Experiment 1
+plot_grid(plot_trial(),
+          plot_bars(data = data_exp1, stars = stars_exp1, ymin = -1.5),
+          plot_erps(comps = comps, evokeds = evokeds_exp1, montage = montage, stars = stars_exp1),
+          plot_legends(),
+          nrow = 4, rel_heights = c(3, 2, 6, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica")
+```
+
+In Part II, only the 120 unfamiliar objects were presented for a second time, now preceded either by a matching verbal description (in the insight condition) or by a non-matching verbal description (in the naive condition).
+Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the verbal description for 2.5 s.
+Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
+The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g. medical devices, musical instruments).
+To make sure that insight did (did not) occur in the insight (naive) condition, we excluded any objects from the insight condition if participants indicated not knowing the object or having rather no assumption (despite reading the matching description) and any objects from the naive condition if participants indicated knowing the object or having an assumption (despite reading the non-matching description).
+This resulted in an average of `r format(round(stims_exp1["Insight"], 1), nsmall = 1)` objects (`r scales::percent(stims_exp1["Insight"]/60, accuracy = 0.1)`) per participant remaining in the insight condition and an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects (`r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)`) per participant remaining in the naive condition.
+
+In Part III, the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e. without the verbal descriptions.
+Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with descriptions), participants took a self-timed break and continued with the same block of 30 objects in Part III (without descriptions) before moving on to the next block consisting of 30 different objects.
+They continued like this until all four blocks were completed in both Parts II and III.
+In total, the experiment consisted of 480 trials (120 familiar objects in Part I and 120 unfamiliar objects in Parts I, II, and III) and took participants approximately 35 minutes to complete.
+
+### EEG Recording and Preprocessing
+
+The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system [@americanelectroencephalographicsociety1991] and referenced online to an external electrode placed on the left mastoid (M1).
+Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively.
+During the recording, electrode impedances were kept below 5 kΩ.
+An online bandpass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1,000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
+
+Offline, the data were preprocessed using the MNE software [Version 0.20.8; @gramfort2013] in Python [Version 3.7.7; @vanrossum2009].
+First, all scalp electrodes were re-referenced to the common average.
+Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
+The first 15 components were extracted using the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
+Those components showing substansive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the *find\_bads\_eog* function.
+After artifact correction, a zero-phase, non-causal FIR filter with a lower passband edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper passband edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
+Next, the continuous EEG was epoched into segments of 2,000 ms, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
+The epochs were baseline-corrected by substracting the average voltage during the 200 ms before stimulus onset.
+Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
+This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials (`r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`) per participant (range `r min(rejected_exp1)` to `r max(rejected_exp1)`).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N1 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+
+### Statistical Analysis
+
+The event-related potentials were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
+For the purpose of the present study, these models have a number of desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+First, they can account simultanously for the non-independence of data points coming from the same participant or from the same item, whereas the neglect of item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
+Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is based on the participants' responses rather than on the experimental manipulation [e.g.  @fröber2017].
+
+Three separate models were computed predicting P1, N1, and N400 mean amplitudes, respectively.
+All models included three fixed effects: (a) the part of the experiment, coded as a sliding difference contrast (i.e. subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the trial, coded as a simple contrast (i.e. subtracting the naive from the insight condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
+To determine the random effects structure, we always started with a model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
+To increase statistical power and to avoid overfitting, we then iteratively removed each term from the random effects and re-added it only if the resulting model fitted the data significanlty worse than the maximal model, as indicated by likelihood ratio tests [@matuschek2017].
+All models were fitted in R [Version `r packageVersion("base")`; @R-base] using the lme4 package [Version `r packageVersion("lme4")`; @R-lme4].
+The optimizer function *bobyqa* with 2·10^6^ iterations was used for maximum likelihood estimation.
+Automatic model selection via likelihood ratio tests was performed using the buildmer package [Version `r packageVersion("buildmer")`; @R-buildmer].
+Finally, to answer the research question of whether or not semantic insight had an influence on the ERP components within each part, planned follow-up comparisons contrasting the insight against the naive condition within Parts I, II, and III were calculated.
+
+All materials and code for the present experiments can be accessed via the Open Science Framework ([https://osf.io/.../](https://osf.io/myprojects/)).
+
+## Results
+
+Single-trial ERPs were analyzed in response to unfamiliar objects before (Part I), during (Part II), and after (Part III) participants gained semantic insight into what the objects were doing.
+Half of the objects were preceded by a matching description, fostering semantic insight to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
+To make sure participants did indeed experience insight or naive perception, the analysis was constrained by participants' behavioral responses in Part II: Objects presented with a matching description were assigned to the insight condition only if the participant indicated that they knew what the object was (or had an assumption), whereas objects presented with a non-matching description were assigned to the naive condition only if the participant indicated that they did not know what the object was (or had rather no assumption).
+The analysis focused on differences between the insight and the naive condition in the P1 component (100--150 ms) as an index of lower-level visual perception, the N1 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.
+
+```{r exp1-table, include=TRUE, results="asis"}
+# Define function to print ANOVA-style table
+create_table <- function(models, stub.anova, stub.contrasts, caption, note){
+  anov <- map(models, function(model){
+    data.frame("f" = format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2),
+               "df" = paste0("(", model$anova$NumDF, ", ", format(round(model$anova$DenDF, 1), trim = TRUE, nsmall = 1), ")"),
+               "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)) %>%
+      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>% set_rownames(c(stub.anova))})
+  anov_print <- anov %>% map(unite, col = fdf, f, df, sep = " ") %>%
+    map(add_row, fdf = "\\textit{F} (\\textit{df})", p = "\\textit{p}", .before = 1) %>% bind_cols() %>%
+    set_rownames(c("\\textit{Fixed effects}", stub.anova))
+  anov %<>% bind_cols() %>% set_colnames(paste(rep(names(models), each = length(names(models))), c("f", "df", "p"), sep = "_")) 
+  conts <- map(models, function(model){
+    data.frame("est" = format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2),
+               "ci" = paste0("[", format(round(model$contrasts$lower.CL, 2), trim = TRUE, nsmall = 2), ", ",
+                               format(round(model$contrasts$upper.CL, 2), trim = TRUE, nsmall = 2), "]"),
+               "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)) %>%
+      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>% set_rownames(stub.contrasts)})
+  conts_print <- conts %>% map(unite, col = estci, est, ci, sep = " ") %>%
+    map(add_row, estci = "Est. [95% CI]", p = "\\textit{p}", .before = 1) %>% bind_cols() %>%
+    set_rownames(c("\\textit{Insight $-$  naive}", stub.contrasts))
+  conts %<>% bind_cols() %>% set_colnames(paste(rep(names(models), each = length(names(models))), c("est", "ci", "p"), sep = "_"))
+  cnames <- c("\\textit{Fixed effects}", as.character(anov_print[1,]))
+  list(anov_print[2:nrow(anov_print),], conts_print) %>% map(set_colnames, paste0("V", 1:ncol(anov_print))) %>%
+    apa_table(col.names = cnames, col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N1}" = 4:5, "\\textbf{N400}" = 6:7),
+              midrules = nrow(anov_print), font_size = "footnotesize", align = "lcccccc", escape = FALSE,
+              caption = caption, note = note) %>% cat()
+  return(list("anov" = anov, "conts" = conts))}
+
+# Create table of models for Experiment 1
+table_exp1 <- create_table(models = models_exp1,
+                           stub.anova = c("Part", "Insight", "Pt. × ins."), stub.contrasts = c("Part I", "Part II", "Part III"),
+                           caption = "Results of linear mixed-effects regression models for Experiment 1",
+                           note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
+```
+
+Averaged accross conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all *F*s \> `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (Table \@ref(tab:exp1-table)).
+In addition, N400 amplitudes differed between the insight and the naive conditions averaged across the three parts of the experiment, *F*`r table_exp1$anov["Insight", "N400_df"]` = `r table_exp1$anov["Insight", "N400_f"]`, *p* `r table_exp1$anov["Insight", "N400_p"]`.
+Crucially, the part × insight interaction was significant in the N1 component, *F*`r table_exp1$anov["Pt.
+× ins.", "N1_df"]` = `r table_exp1$anov["Pt.
+× ins.", "N1_f"]`, *p* = `r table_exp1$anov["Pt.
+× ins.", "N1_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt.
+× ins.", "N400_df"]` = `r table_exp1$anov["Pt.
+× ins.", "N400_f"]`, *p* `r table_exp1$anov["Pt.
+× ins.", "N400_p"]`, while also being marginally significant in the P1 component, *F*`r table_exp1$anov["Pt.
+× ins.", "P1_df"]` = `r table_exp1$anov["Pt.
+× ins.", "P1_f"]`, *p* = `r table_exp1$anov["Pt.
+× ins.", "P1_p"]`.
+To answer our main research question, we decomposed these interactions into the differences between the insight and the naive condition within the three different parts of the experiment.
+
+### Effects of Insight in Part I
+
+In Part I, when objects were unfamiliar to the participant and presented without verbal descriptions, no differences emerged between the insight and the naive condition in the P1, N1, or N400 component, all *p*s \> `r table_exp1$conts["Part I", "N400_p"]` (Table \@ref(tab:exp1-table), Figure \@ref(fig:exp1-plot)B--D).
+On the one hand, this was to be expected given that the critical presentation of the objects with the descriptions (leading to semantic insight vs. naive perception) had not yet taken place.
+On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of insight in Parts II and III cannot be explained solely by visual differences between the objects in the two conditions.
+Although the presentation of a matching or non-matching description for each object was counterbalanced across participants, the fact that different numbers of objects were excluded from the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor.
+If they did, however, one would expect to detect them even before any descriptions were presented, which we now know was not the case.
+
+### Effects of Insight in Part II
+
+In Part II, half of the unfamiliar objects were presented with a matching verbal description (in the insight condition) and the other half were presented with a non-matching verbal description (in the naive condition).
+In response to objects for which participants experienced insight, the amplitude of the N1 component was significantly enlarged (i.e. more negative), *b* = `r table_exp1$conts["Part II", "N1_est"]` µV, *p* = `r table_exp1$conts["Part II", "N1_p"]`, and the amplitude of the N400 component was significantly reduced (i.e. less negative), *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`, compared to objects which participants viewed naively.
+As in Part I, there were no reliable differences in the P1 component, *p* = `r table_exp1$conts["Part II", "P1_p"]`.
+
+### Effects of Insight in Part III
+
+In Part III, the unfamiliar objects were presented for a third time, again without the verbal descriptions (as in Part I) to test whether the occurence of semantic insight had any lasting effects on the processing of the objects.
+As in Part II, the N400 component remained significantly reduced in response to objects for which semantic insight had occurred, *b* = `r table_exp1$conts["Part III", "N400_est"]` µV, *p* `r table_exp1$conts["Part III", "N400_p"]`, whereas the early effect of insight in the N1 component did not reocurr, *p* = `r table_exp1$conts["Part III", "N1_p"]`.
+Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e. more positive) in response to objects for which semantic insight had occured, *b* = `r table_exp1$conts["Part III", "P1_est"]` µV, *p* = `r table_exp1$conts["Part III", "P1_p"]`.
+
+## Discussion
+
+In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they gained semantic insight into what kind of object they were seeing.
+To induce insight, half of the objects in Part II were preceded by a matching verbal description of the object's typical function or use, whereas the other half were preceded by a non-matching description (as a naive baseline condition).
+
+Participants' experience of semantic insight in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001].
+The fact that this effect did not reocurr in Part III, when the objects were presented once more without descriptions, suggests it being a marker of semantic insight altering object processing online.
+In contrast, we also observed a modulation of the N400 component, which was reduced for objects when semantic insight was ocurring (in Part II) and remained so when the same objects were presented repeatedly (in Part III).
+The N400 is often viewed as an index of increased demands for semantic processing [@kutas2011; @rabovsky2018].
+Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had unterstood what kind of object they were viewing.
+Finally, semantic insight was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which semantic insight had ocurred (in Part II).
+This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images [@samaha2018], may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had ocurred.
+
+Because of the exploratory nature of the present study and the novelty of the ERP effects observed in Experiment 1, we ran a replication study to assess the robustness of these findings in another samples of participants.
+
+# Experiment 2
+
+## Methods
+
+```{r exp2-preparation}
+# Read behavioral data for Experiment 2
+fnames_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE)
+data_exp2 <- map(fnames_exp2, read_behav)
+
+# Check average number of stimuli per condition
+(stims_exp2 <- map(data_exp2, function(x){table(x$condition)/3}) %>% bind_rows() %>% colMeans())
 ```
@@
 ```{python exp2-preprocessing}
-# List of raw EEG filenames
+# List raw EEG filenames
 fnames_exp2 = sorted(glob.glob('data/exp2/EEG/*.vhdr'))
+
+# Import behavioral data from R
+metadata_exp2 = r.data_exp2
 
@@
 if os.path.exists('output/exp2-epo.fif'):
-  # Load preprocessed data from file
+  # Read preprocessed data from file
   epochs_exp2 = mne.read_epochs('output/exp2-epo.fif', preload=True)
 else:
-  # Actually apply the preprocessing function
-  epochs_exp2 = [preproc(fname, **preproc_params) for fname in fnames_exp2]
-  # Combine into a single data set
+  # Preprocess EEG data for Experiment 2
+  epochs_exp2 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp2, metadata_exp2)]
+  # Combine epochs into a single data set
   epochs_exp2 = mne.concatenate_epochs(epochs_exp2)
-  # Backup epochs to the export folder
+  # Backup epochs to the output folder
   epochs_exp2.save('output/exp2-epo.fif')
 
-# Get indices of bad epochs despite ICA
-rej_exp2 = epochs_exp2.copy().drop_bad(reject=reject).drop_log
-rej_exp2[:] = [item for item in rej_exp2 if item != ['IGNORED']]
-rej_exp2 = [i for i in range(len(rej_exp2)) if rej_exp2[i] != []]
+# # Get indices of bad epochs despite ICA
+# rej_exp2 = epochs_exp2.drop_log
+# rej_exp2[:] = [item for item in rej_exp2 if item != ['IGNORED']]
+# rej_exp2 = [i for i in range(len(rej_exp2)) if rej_exp2[i] != []]
+
+# Compute grand averages for Experiment 2
+evokeds_exp2, evokeds_dat_exp2 = compute_evokeds(epochs=epochs_exp2)
 ```
@@
 ```{r exp2-analysis}
-# List of filenames for behavioral data
-fnames_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE)
+# Re-import behavioral data
+data_exp2 <- py$epochs_exp2$metadata
 
-# Actually apply the preprocessing function
-data_exp2 <- map_dfr(fnames_exp2, preproc_behav)
+# Factorize some columns
+data_exp2 %<>% mutate(part = factor(part, levels = c("I", "II", "III")),
+                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")),
+                      participant = factor(participant),
+                      item = factor(item))
 
-# Add factorized columns for participants and items (the random variables)
-data_exp2 %<>% mutate(participant = as_factor(VPNummer), item = as_factor(StimID))
+# Check number of rejected epochs
+rejected_exp2 <- data_exp2 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
+mean(rejected_exp2); median(rejected_exp2); range(rejected_exp2)
 
-# Tabulate percentage of stimuli per condition
-stims_exp2 <- table(data_exp2$participant, data_exp2$condition)
-stims_exp2 <- colMeans(stims_exp2)
-stims_exp2["Known"]/(3*120) # Three repititions and 120 objects
-stims_exp2[c("Insight", "Naive")]/(3*60) # Three repitions and 60 objects each
-
+# Check if single-trial ERPs were computed already (delete the file to re-run)
+if (file.exists("output/exp2-erps.RDS")){
+  # Read data from file
+  data_exp2 <- readRDS("output/exp2-erps.RDS")
+} else {
   # Import epochs from Python, converting Volts to Microvolts
   epochs_exp2 <- py$epochs_exp2$get_data()*1e6
+  # Compute single-trial ERPs for Experiment 2
+  data_exp2 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp2, els = els) %>%
+    set_names(comps$name) %>% cbind(data_exp2, .) %T>% saveRDS("output/exp2-erps.RDS")}
 
-# Set rejected epochs to NA
-rej_exp2 <- py$rej_exp2 + 1
-epochs_exp2[rej_exp2,,] <- NA
+# Remove any trials excluded from conditions
+data_exp2 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
 
-# Apply function to compute single-trial ERPs and to the behavioral data
-data_exp2 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp2, els = els) %>% set_names(comps$name) %>% cbind(data_exp2, .)
-
-# Remove trials with missing ERPs or RTs
-rej_exp2_erp <- data_exp2 %>% filter(is.na(P1)) %>% count(participant, .drop = FALSE) %>% pull(n)
-data_exp2 %<>% filter(!is.na(P1))
-rej_exp2_rt <- data_exp2 %>% filter(is.na(RT)) %>% count(participant, .drop = FALSE) %>% pull(n)
-data_exp2 %<>% filter(!is.na(RT))
-
-# Remove any trials that don't beling to either of the two conditions
-data_exp2 %<>% filter(condition != "Known") %>% droplevels()
-
-# Set sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
-contrasts(data_exp2$condition) <- ginv(contrasts.condition)
-contrasts(data_exp2$part) <- ginv(contrasts.part)
+# Contrast coding for condition (insight-naive) and part (2-1, 3-1)
+contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
+contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)
 
@@
 if (file.exists("output/exp2-stats.RDS")){
-   # Load models from file
+  # Read models from file
   models_exp2 <- readRDS("output/exp2-stats.RDS")
 } else {
-  # Actually apply the modelling function
-  models_exp2 <- map(comps$name, compute_models, formula = form, data = data_exp2, control = ctrl_params, specs = specs) %>%
-    set_names(comps$name)
-  # Backup epochs to the export folder
-  saveRDS(models_exp2, "output/exp2-stats.RDS")}
+  # Compute LMMs for Experiment 2
+  models_exp2 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp2, control = ctrl_params,
+                     specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/exp2-stats.RDS")}
 ```
+
+### Participants
+
+Participants for Experiment 2 were 24 German native speakers (18 female, 6 male) with a mean age of 23 years (range 19 to 32) who had not participated in Experiment 1.
+They had no history of psychological disorder or treatment, were right-handed and reported normal or corrected-to-normal vision.
+They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+
+### Materials, Procedure, and Analysis
+
+All materials, procedures, and methods for EEG recording and statistical analysis were identical to Experiment 1.
+An average of `r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)` of rare objects per participant was classified as known in Part I and excluded from all further analyses.
+Based on participants' responses in Part II, an average of `r format(round(stims_exp2["Insight"], 1), nsmall = 1)` objects (`r scales::percent(stims_exp1["Insight"]/60, accuracy = 0.1)` of objects presented with matching a descirption) were assigned to the insight condition and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects (`r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with a non-matching description) were assigned to the naive condition.
+Automatic rejection of EEG epochs containing artifacts led to the exlucsion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials (`r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`) per participant (range `r min(rejected_exp2)` to `r max(rejected_exp2)`).
+
+## Results
+
+```{r exp2-table, include=TRUE, results="asis"}
+# # Create table of models for Experiment 2
+table_exp2 <- create_table(models_exp2, stub.anova = c("Part", "Insight", "Pt. × ins."),
+            stub.contrasts = c("Part I", "Part II", "Part III"),
+            caption = "Results of linear mixed-effects regression models for Experiment 2",
+            note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
+```
+
+As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all *F*s \> `r table_exp2$anov["Part", "N1_f"]`, all *p*s `r table_exp2$anov["Part", "N1_p"]` (Table \@ref(tab:exp2-table)).
+Also as in Experiment 1, N400 amplitudes differed between the insight and the naive condition averaged across parts, *F*`r table_exp2$anov["Insight", "N400_df"]` = `r table_exp2$anov["Insight", "N400_f"]`, *p* `r table_exp2$anov["Pt.
+× ins.", "N400_p"]`.
+The part × insight interaction was significant in the P1 component, *F*`r table_exp2$anov["Pt.
+× ins.", "P1_df"]` = `r table_exp2$anov["Pt.
+× ins.", "P1_f"]`, *p* = `r table_exp2$anov["Pt.
+× ins.", "P1_p"]`, and in the N400 component, *F*`r table_exp2$anov["Pt.
+× ins.", "N400_df"]` = `r table_exp2$anov["Pt.
+× ins.", "N400_f"]`, *p* `r table_exp2$anov["Pt.
+× ins.", "N400_p"]`, but not in the N1 component, *F*`r table_exp2$anov["Pt.
+× ins.", "N1_df"]` = `r table_exp2$anov["Pt.
+× ins.", "N1_f"]`, *p* = `r table_exp2$anov["Pt.
+× ins.", "N1_p"]`.
+
+```{r exp2-plot, include=TRUE, fig.height=9, fig.cap = "(ref:figure-2-caption)"}
+# Manually extract significance levels from contrasts for plotting
+stars_exp2 = list(P1 = c(I = NA, II = NA, III = "*"),
+                  N1 = c(I = NA, II = NA, III = NA),
+                  N400 = c(I = NA, II = "***", III = NA))
+
+# Import grand averaged evoked potentials from Python
+evokeds_exp2 <- py$evokeds_dat_exp2
+
+# Create plot for Experiment 2
+plot_grid(plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
+          plot_erps(comps = comps, evokeds = evokeds_exp2, montage = montage, stars = stars_exp2),
+          plot_legends(),
+          nrow = 3, rel_heights = c(2, 6, 1), labels = c("A", "B", ""), label_fontfamily = "Helvetica")
+```
+
+### Effects of Insight in Part I
+
+As in Experiment 1, no differences between objects in the insight and the naive condition emerged in the P1, N1, or N400 component, all *p*s \> `r table_exp2$conts["Part I", "P1_p"]` (Table \@ref(tab:exp2-table), Figure \@ref(fig:exp2-plot)).
+
+(ref:figure-2-caption) Results of Experiment 2.
+A.
+Bar plots and B.
+ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III.
+In a direct replication of Experiment 1, the effect of semantic insight on the N400 component in Part II and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II and on the N400 component in Part III remained only marginally significant.
+\newline\**p* \< .05.
+\*\*\**p* \< .001.
+
+### Effects of Insight in Part II
+
+As in Experiment 1, the occurence of semantic insight in Part II due to the presentation of objects with matching (vs. non-matching) verbal descriptions was associated with a (marginally) significant enhancement of the N1 component, *b* = `r table_exp2$conts["Part II", "N1_est"]` µV, *p* = `r table_exp2$conts["Part II", "N1_p"]`, and a signficant reduction of the N400 component, *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`.
+
+### Effects of Insight in Part III
+
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without verbal descriptions as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantic insight had occured, *b* = `r table_exp2$conts["Part III", "P1_est"]` µV, *p* = `r table_exp2$conts["Part III", "P1_p"]`.
+Also, N400 amplitudes in response to these objects remained reduced, although marginally significant, *b* = `r table_exp2$conts["Part III", "N400_est"]` µV, *p* = `r table_exp2$conts["Part III", "N400_p"]`.
+
+### Joint Analysis of Experiments 1 and 2
+
+In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2.
+This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
+Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a simple contrast (i.e. subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments).
+This factor and its possible interactions with part, insight, and part × insight were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
+They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2.
+Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit [@matuschek2017, @R-buildmer].
 
@@
 
-# Set sliding difference coding for experiment (2-1), condition (insight-naive), and part (2-1, 3-1)
-t(contrasts.experiment <- t(cbind(c("1" = -1, "2" = 1))))
-contrasts(data_joint$experiment) <- ginv(contrasts.experiment)
-contrasts(data_joint$condition) <- ginv(contrasts.condition)
-contrasts(data_joint$part) <- ginv(contrasts.part)
+# Contrast coding for experiment (2-1), condition (insight-naive), and part (2-1, 3-1)
+t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
+contrasts(data_joint$experiment) <- MASS::ginv(contrasts_experiment)
+contrasts(data_joint$condition) <- MASS::ginv(contrasts_condition)
+contrasts(data_joint$part) <- MASS::ginv(contrasts_part)
 
 # New formula for LMMs
-form_joint <- tabulate.formula(~ experiment*part*condition + (part*condition|participant) + (experiment*part*condition|item))
+form_joint <- tabulate.formula(~ part*condition*experiment + (part*condition|participant) + (part*condition*experiment|item))
 form_joint %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
@@
 if (file.exists("output/joint-stats.RDS")){
-   # Load models from file
+  # Read models from file
   models_joint <- readRDS("output/joint-stats.RDS")
 } else {
-  # Actually apply the modelling function
-  models_joint <- map(comps$name, compute_models, formula = form_joint, data = data_joint, control = ctrl_params, specs = specs) %>%
-    set_names(comps$name)
-  # Backup epochs to the export folder
-  saveRDS(models_joint, "output/joint-stats.RDS")}
+  # Compute LMMs for Experiments 1 and 2 combined
+  models_joint <- map(comps$name, compute_models, formula = form_joint, data = data_joint, control = ctrl_params,
+                      specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/joint-stats.RDS")}
 ```
+
+```{r joint-table, include=TRUE, results="asis"}
+# Create table of models for Experiments 1 and 2 combined
+table_joint <- create_table(models_joint, stub.anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.",
+                                                         "Ins. × exp.", "Pt. × ins. × exp."),
+                            stub.contrasts = c("Part I", "Part II", "Part III"),
+                            caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
+                            note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.")
+```
+
+As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_exp2$anov["Part", "P1_p"]`, as was the main effect of insight in the N400, *F*`r table_joint$anov["Insight", "N400_df"]` = `r table_joint$anov["Insight", "N400_f"]`, *p* `r table_joint$anov["Insight", "N400_p"]`.
+Furthermore, the part × insight interaction was new observed reliably in all three components, all *F*s \> `r table_joint$anov["Pt.
+× ins.", "P1_f"]`, all *p*s \< `r table_joint$anov["Pt.
+× ins.", "P1_p"]`.
+While there was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, the absence of any reliable interactions of experiment with part or insight indicated that the effect of our experimental manipulations did not differ between Experiments 1 and 2.
+
+Based on the part × insight interaction, we again computed follow-up comparisons between the insight and the naive condition within each part, now collapsed across the data from both experiments.
+This confirmed the absence of any reliable difference between the two conditions in Part I, all *p*s \> `r table_joint$conts["Part I", "N400_p"]`, the significant enhancement of the N1 component in Part II, while insight was ocurring, *b* = `r table_joint$conts["Part II", "N1_est"]` µV, *p* = `r table_joint$conts["Part II", "N1_p"]`, the significant reduction of the N400 component in Parts II, while insight was occurring, *b* = `r table_joint$conts["Part II", "N400_est"]` µV, *p* `r table_joint$conts["Part II", "N400_p"]`, and Part III, after insight had ocurred, *b* `r table_joint$conts["Part III", "N400_est"]` µV, *p* = `r table_joint$conts["Part III", "N400_p"]`, as well as the sigificant enhancement of the P1 component in Part III, after insight had occurred, *b* = `r table_joint$conts["Part III", "P1_est"]` µV, *p* = `r table_joint$conts["Part III", "P1_p"]`.
+
+## Discussion
+
+Experiment 2, a direct replication of Experiment 1, confirmed the impact of gaining semantic insight into previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N1), and semantic processing (N400).
+While the enhancement of the N1 component, being more negative in repsonse to objects for which participants were experiencing semantic insight, was present only during the critical presentation of the objects with their verbal descriptions (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after insight had taken place and the objects were presented again in Part III.
+This indicates a modulation of different stages of visual object perception through semantic knowledge, while and after an understanding of the object has been obtained.
+Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantic insight may reflect lower semantic processing demands compared to unfamiliar objects which participants did not yet understand.
+
+# Experiment 3
+
+```{r exp3-preparation}
+# Read behavioral data for Experiment 3
+fnames_exp3 <- list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE)
+data_exp3 <- map(fnames_exp3, read_behav)
+
+# Check average number of stimuli per condition
+(stims_exp3 <- map(data_exp3, function(x){
+  x %<>% filter(part != "IV")
+  table(x$condition)/3
+  }) %>% bind_rows() %>% colMeans())
+```
+
+```{python exp3-preprocessing}
+# List raw EEG filenames
+fnames_exp3 = sorted(glob.glob('data/exp3/EEG/*.vhdr'))
+
+# Import behavioral data from R
+metadata_exp3 = r.data_exp3
+
+# Update stimulus triggers
+preproc_params['event_id'] = {'match/upright': 241, 'match/inverted': 242, 'mismatch/upright': 243, 'mismatch/inverted': 244}
+
+# Check if preprocessing was done already (delete the file to re-run)
+if os.path.exists('output/exp3-epo.fif'):
+  # Read preprocessed data from file
+  epochs_exp3 = mne.read_epochs('output/exp3-epo.fif', preload=True)
+else:
+  # Preprocess EEG data for Experiment 3
+  epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp3, metadata_exp3)]
+  # Combine epochs into a single data set
+  epochs_exp3 = mne.concatenate_epochs(epochs_exp3)
+  # Backup epochs and evokeds to the output folder
+  epochs_exp3.save('output/exp3-epo.fif')
+
+# # Get indices of bad epochs despite ICA
+# rej_exp3 = epochs_exp3.drop_log
+# rej_exp3[:] = [item for item in rej_exp3 if item != ['IGNORED']]
+# rej_exp3 = [i for i in range(len(rej_exp3)) if rej_exp3[i] != []]
+```
+
+```{r exp3-analysis, eval=FALSE}
+# Re-import behavioral data
+data_exp3 <- py$epochs_exp3$metadata
+
+# Factorize some columns
+data_exp3 %<>% mutate(part = factor(part, levels = c("I", "II", "III", "IV")),
+                      position = factor(position, levels = c("Inverted", "Upright")),
+                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")),
+                      participant = factor(participant), item = factor(item))
+
+# Check if ERPs were computed already (delete the file to re-run)
+if (file.exists("output/exp3-erps.RDS")){
+  # Read ERPs from file
+  data_exp3 <- readRDS("output/exp3-erps.RDS")
+} else {
+  # Import epochs from Python, converting Volts to Microvolts (takes a while)
+  epochs_exp3 <- py$epochs_exp3$get_data()*1e6
+  # Compute single-trial ERPs for Experiment 3
+  data_exp3 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp3, els = els) %>%
+    set_names(comps$name) %>% cbind(data_exp3, .) %T>% saveRDS("output/exp3-erps.RDS")}
+
+# Remove any trials from part IV
+data_exp3 %<>% filter(part != "IV") %>% droplevels()
+
+# Check number of rejected epochs
+rejected_exp3 <- data_exp3 %>% group_by(participant) %>% tally() %>% mutate(n = 672 - n) %>% pull(n)
+mean(rejected_exp3); median(rejected_exp3); range(rejected_exp3)
+
+# Remove any trials excluded from conditions
+data_exp3 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
+
+# Contrast coding for position (inverted-updright), condition (insight-naive), and part (2-1, 3-1)
+t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
+contrasts(data_exp3$position) <- MASS::ginv(contrasts_position)
+contrasts(data_exp3$condition) <- MASS::ginv(contrasts_condition)
+contrasts(data_exp3$part) <- MASS::ginv(contrasts_part)
+
+# New formula for LMMs
+form_exp3 <- tabulate.formula(~ part*condition*position + (part*condition*position|participant) + (part*condition*position|item))
+form_exp3 %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
+
+# New follow-up contrasts
+specs_exp3 = pairwise ~ condition|position*part
+
+# Check if models were computed already (delete the file to re-run)
+if (file.exists("output/exp3-stats.RDS")){
+  # Read models from file
+  models_exp3 <- readRDS("output/exp3-stats.RDS")
+} else {
+  # Compute LMMs for Experiment 3
+  models_exp3 <- map(comps$name, compute_models, formula = form_exp3, data = data_exp3, control = ctrl_params,
+                     specs = specs_exp3) %>% set_names(comps$name) %T>% saveRDS("output/exp3-stats.RDS")}
+```
+
+```{r exp3-table, include=TRUE, results="asis"}
+# Create tanle of models for Experiment 3
+table_exp3 <- create_table(models_exp3, stub.anova = c("Part", "Insight", "Position", "Pt. × ins.", "Pt. × pos.",
+                                                       "Ins. × pos.", "Pt. × ins. × pos."),
+                           stub.contrasts = c("Part I, inverted", "Part I, upright", "Part II, inverted",
+                                              "Part II, upright", "Part III, inverted", "Part III, upright"),
+                           caption = "Results of linear mixed-effects regression models for Experiment 3",
+                           note = "Pt. = part, ins. = insight, pos. = position, est. = estimate, CI = confidence interval.")
+```
+
+# General Discussion
+
+General discussion goes here.
 

### 2020-09-11 manuscript/manuscript.tex

--- 2020-07-28 manuscript/manuscript.tex
@@
   english,
-  man]{apa7}
+  man,11pt,floatsintext]{apa7}
 \usepackage{lmodern}
@@
 \keywords{keywords\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
+\usepackage{setspace}
+\AtBeginEnvironment{tabular}{\doublespacing}
+\AtBeginEnvironment{lltable}{\doublespacing}
+\AtBeginEnvironment{tablenotes}{\doublespacing}
+\captionsetup[table]{font={stretch=1.5}}
+\captionsetup[figure]{font={stretch=1,scriptsize}}
+\raggedbottom
 \ifxetex
@@
 \fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 \newlength{\cslhangindent}
@@
 \newenvironment{cslreferences}%
-  {}%
+  {\setlength{\parindent}{0pt}%
+  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
   {\par}
@@
 
+Blablabla
+
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
+
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
+
+\hypertarget{participants}{%
+\subsubsection{Participants}\label{participants}}
+
+Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history psychological disorder or treatment.
+All participants were right-handed with a mean laterality index of +80.0 on the Edinburgh inventory (Oldfield, 1971) and reported normal or corrected-to-normal vision.
+They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+All experiments subsequently reported were carried out in accordance with the Declaration of Helsinki and approved by the local ethics committee.
+
+\hypertarget{materials-and-procedure}{%
+\subsubsection{Materials and Procedure}\label{materials-and-procedure}}
+
+Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objectsm 120 of which were well-known everyday objects (e.g.~a bicycle, a toothbrush), whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g.~a galvanometer, an udu drum).
+A list of all objects used in Experiments 1 and 2 can be found in Appendix A.
+The objects were presented on a light blue background with a size of 207 × 207 pixels on 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
+At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degress of participants' horizontal and vertical visual angle.
+
+For each unfamiliar object, a noun--verb pair was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g.~current--measuring, pottery--drumming).
+In the \emph{insight} condition, the presentation of each unfamiliar object was preceded by its respective description, whereas in the \emph{naive} condition, it was preceded by a non-matching description belonging to one of the other objects.
+In both conditions, the noun and the verb were presented one above the other in black letters on a light blue background.
+For each participant, half of the unfamiliar objects were presented in the insight condition (i.e.~with a matching description) and the other half were presented in the naive condition (i.e.~with a non-matching description).
+All participants saw each unfamiliar object in only one of the two conditions and the assignment of object to one of the two conditions was counterbalanced across participants.
+The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
+
+Each experimental session consisted of three parts (Figure \ref{fig:exp1-plot}A).
+In Part I, after written informed consent was obtained and the EEG was prepared, all 240 familiar and unfamiliar objects were presented once in random order and without verbal descriptions.
+Each trial consisted of a fixation cross presented in the middle of the screen for 500 ms, followed by the presentation of the object until participants made a response or until a time out after 3,000 ms.
+The intertrial interval until the presentation of the next fixation cross was 500 ms and participants took a self-timed break after each block of 60 objects.
+The task, which was kept the same throughout all three parts and experiments, was to classify each object using one of four response alternatives: (a) ``I know what this is or have a strong assumption'', (b) ``I have a strong assumption'', (c) ``I have rather no assumption what this is'', or (d) ``I do not know what this is and have no assumotion.'' Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of the left and or right hand, respectively.
+The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
+Because we were interested in the acquisition of semantic knowledge about novel objects only, all objects for which the participant indicated knowing the object in Part I were excluded from further analysis (6.3\% of rare objects per participant).
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_files/figure-latex/exp1-plot-1}
+
+}
+
+\caption{Procedure and results of Experiment 1.
+(A) In Part I, participants viewed 120 unfamiliar objects and indicated whether they the object they were viewing.
+In Part II, half of the objects were preceded by a matching description (purple color, for illustrative purposes only), leading to semantic insight, and the other half with a non-matching description (petrol color, for illustrative purposes only), leading to naive perception.
+In Part III, the same objects were presented again without the descriptions.
+(B) Bar plots and (C) ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III.
+Semantic insight was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
+Error bars show standard errors of the mean.
+\newline*\emph{p} \textless{} .05.
+**\emph{p} \textless{} .01.
+***\emph{p} \textless{} .001.}\label{fig:exp1-plot}
+\end{figure}
+
+In Part II, only the 120 unfamiliar objects were presented for a second time, now preceded either by a matching verbal description (in the insight condition) or by a non-matching verbal description (in the naive condition).
+Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the verbal description for 2.5 s.
+Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
+The objects were presented in blocks of 30 trials so that (a) there were 15 objects from each of the two experimental conditions and (b) objects within each block were heterogeneous in terms of their shape, visual complexity, and functional category (e.g.~medical devices, musical instruments).
+To make sure that insight indeed did (did not) occur in the insight (naive) condition, we excluded any objects from the insight condition if participants indicated not knowing the object or having rather no assumption (despite reading the matching description) and any objects from the naive condition if participants indicated knowing the object or having an assumption (despite reading the non-matching description).
+This resulted in an average of 27.0 objects (44.9\%) per participant in the insight condition and an average of 48.8 objects (81.2\%) per participant in the naive condition.
+
+In Part III, the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e.~without the verbal descriptions.
+Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with descriptions), participants took a self-timed break and continued with the same block of 30 objects in Part III (without descriptions) before moving on to the next block consisting of 30 different objects.
+They continued like this until all four blocks were completed in both Parts II and III.
+In total, the experiment consisted of 480 trials (120 familiar objects in Part I and 120 unfamiliar objects in Parts I, II, and III) and took participants approximately 35 minutes to complete.
+
+\hypertarget{eeg-recording-and-preprocessing}{%
+\subsubsection{EEG Recording and Preprocessing}\label{eeg-recording-and-preprocessing}}
+
+The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system (American Electroencephalographic Society, 1991) and referenced online to an external electrode placed on the left mastoid (M1).
+Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively.
+During the recording, electrode impedances were kept below 5 kΩ.
+An online bandpass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1,000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
+
+Offline, the data were preprocessed using the MNE software (Version 0.20.8; Gramfort et al., 2013) in Python (Version 3.7.7; van Rossum \& Drake, 2009).
+First, all scalp electrodes were re-referenced to the common average.
+Next, artifacts from blinks and eye movements were removed using independent component analysis (ICA).
+The first 15 components were extracted using the FastICA algorithm (Hyvärinen, 1999) after temporarily low-pass filtering the data at 1 Hz.
+Those components showing substansive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the \emph{find\_bads\_eog} function.
+After artifact correction, a zero-phase, non-causal FIR filter with a lower passband edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper passband edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
+Next, the continuous EEG was epoched into segments of 2,000 ms, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
+The epochs were baseline-corrected by substracting the average activity during the 200 ms before stimulus onset.
+Epochs containing artifacts despite ICA (defined as peak-to-peak amplitudes exceeding 200 µV) were removed from further analysis.
+This led to the exclusion of an average of 2.4 trials (0.7\%) per participant (range 0 to 24).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N1 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+
+\hypertarget{statistical-analysis}{%
+\subsubsection{Statistical Analysis}\label{statistical-analysis}}
+
+The event-related potentials were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018).
+For the purpose of the present study, these models have a number of desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+First, they can account simultanously for the non-independence of data points coming from the same participant or from the same item, whereas the neglect of item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
+Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is based on the participants' responses rather than on the experimental manipulation (e.g.~Fröber et al., 2017).
+
+Three separate models were computed predicting P1, N1, and N400 mean amplitudes.
+All models included three fixed effects: (a) the part of the experiment, coded as a sliding difference contrast (i.e.~subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the trial, coded as a simple contrast (i.e.~subtracting the naive from the insight condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
+To determine the random effects structure, we always started with a model containing by-participant and by-item random intercepts and random slopes for all fixed effects (Barr et al., 2013).
+To increase statistical power and to avoid overfitting, we then iteratively removed each random effects term and re-added it only if the resulting model fitted the data significanlty worse than the maximal model as indicated by likelihood ratio tests (Matuschek et al., 2017).
+All models were fitted in R (Version 4.0.2; R Core Team, 2020) using the lme4 package (Version 1.1.23; Bates et al., 2015).
+The optimizer function \emph{bobyqa} with 2·10\textsuperscript{6} iterations was used for maximum likelihood estimation.
+Model selection via likelihood ratio tests was performed using the buildmer package (Version 1.7.1; Voeten, 2020).
+Finally, to answer the research question of whether or not semantic insight had an influence on the ERP components within each part, planned follow-up comparisons contrasting the insight versus the naive condition within Parts I, II, and III were calculated.
+
+All materials and code for the present experiments can be accessed via the Open Science Framework (\href{https://osf.io/myprojects/}{https://osf.io/\ldots/}).
+
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+Single-trial ERPs were analyzed in response to unfamiliar objects before (Part I), during (Part II), and after (Part III) participants gained semantic insight into what the objects were doing.
+Half the objects were preceded by a matching description, fostering semantic insight to occur, whereas the other half were preceded by non-matching description, leading to naive perception of the object.
+To make sure participants did indeed experience insight or naive perception, the analysis was constrained by participants' behavioral responses in Part II: Objects presented with matching a description were assigned to the insight condition only if the participant indicated that they knew what the object was doing (or had an assumption), whereas objects presented with a non-matching description were assigned to the naive condition only if the participant indicated that they did not know what the object was (or had rather no assumption).
+The analysis focused on differences between the insight and the naive condition in the P1 component (100--150 ms) as an index of low-level visual perception, in the N1 component (150--200 ms) as index of high-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:exp1-table}Results of linear mixed-effects regression models for Experiment 1}
+
+\footnotesize{
+
+\begin{tabular}{lcccccc}
+\toprule
+ & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
+\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
+\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\midrule
+Part & 10.82 (2, 24.5) & < .001 & 14.15 (2, 24.9) & < .001 & 33.00 (2, 25.5) & < .001\\
+Insight & 0.87 (1, 5302.9) & .351 & 0.96 (1, 5344.3) & .327 & 21.82 (1, 5214.0) & < .001\\
+Pt. × ins. & 2.40 (2, 4590.9) & .091 & 5.33 (2, 4940.9) & .005 & 11.16 (2, 5055.1) & < .001\\
+\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Part I & 0.00 [-0.50, 0.49] & .987 & -0.16 [-0.62, 0.30] & .485 & -0.21 [-0.61, 0.18] & .292\\
+Part II & -0.15 [-0.65, 0.34] & .550 & -0.66 [-1.12, -0.20] & .005 & 0.91 [0.51, 1.31] & < .001\\
+Part III & 0.57 [0.08, 1.07] & .023 & 0.41 [-0.05, 0.87] & .080 & 0.99 [0.58, 1.39] & < .001\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Averaged accross conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.82, all \emph{p}s \textless{} .001 (Table \ref{tab:exp1-table}).
+In addition, N400 amplitudes differed between the insight and the naive conditions averaged across the three parts of the experiment, \emph{F}(1, 5214.0) = 21.82.
+Crucially, the part × insight interaction was significant in the N1, \emph{F}(2, 4940.9) = 5.33, \emph{p} = .005, and in the N400, \emph{F}(2, 5055.1) = 11.16, \emph{p} \textless{} .001, while also being marginally significant in the P1, \emph{F}(2, 4590.9) = 2.40, \emph{p} = .091.
+To answer our main research question, we decomposed these interactions into the differences between the insight and the naive condition within the three different parts of the experiment.
+
+\hypertarget{effects-of-insight-in-part-i}{%
+\subsubsection{Effects of Insight in Part I}\label{effects-of-insight-in-part-i}}
+
+In Part I, when all objects were unfamiliar to the participants and presented without verbal descriptions, no differences emerged between the insight and the naive condition in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .292 (Table \ref{tab:exp1-table}, Figure \ref{fig:exp1-plot}B--D).
+On the one hand, this was to be expected given that the critical presentation of the descriptions (leading to semantic insight vs.~naive perception) had not yet taken place.
+On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effects of insight in Parts II and III cannot be explained solely by visual differences between the objects in the two conditions.
+Although the presentation of a matching or non-matching description for each object was counterbalanced across participants, the fact that different numbers of objects were excluded from the two conditions based on participants self report in Part II would have made it possible for such visual differences to emerge as a confounding factor.
+If they did, however, one would expect to detect them even before any descriptions were presented, which we now know was not the case.
+
+\hypertarget{effects-of-insight-in-part-ii}{%
+\subsubsection{Effects of Insight in Part II}\label{effects-of-insight-in-part-ii}}
+
+In Part II, half of the unfamiliar objects were presented with matching verbal description (in the insight condition) and the other half were presented with non-matching verbal descriptions (in the naive condition).
+In response to objects for which participants experienced insight, the amplitude of the N1 component was significantly enlarged (i.e.~more negative), \emph{b} = -0.66, \emph{p} = .005, and the amplitude of the N400 component was significantly reduced (i.e.~less negative), \emph{b} = 0.91, \emph{p} \textless{} .001, compared to objects which participants viewed naively.
+As in Part I, there were no reliable differences in the P1 component, \emph{p} = .550.
+
+\hypertarget{effects-of-insight-in-part-iii}{%
+\subsubsection{Effects of Insight in Part III}\label{effects-of-insight-in-part-iii}}
+
+In Part III, the unfamiliar objects were presented for a third time, again without the verbal descriptions (as in Part I) to test whether the occurence of semantic insight had any lasting effects on the perception of the objects.
+As in Part II, the N400 component remained significantly reduced in response to objects for which semantic insight had occurred, \emph{b} = 0.99, \emph{p} \textless{} .001, whereas the effect of insight in the N1 component did not reocurr, \emph{p} = .080.
+Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e.~more positive) in response to objects for which semantic insight had occured, \emph{b} = 0.57, \emph{p} = .023.
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
+
+In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they gained semantic insight into what kind of object they were seeing.
+To induce insight, half of the objects in Part II were preceded by a matching verbal description of the object's typical function or use, whereas the other half were preceded by a non-matching description (as a naive baseline condition).
+
+Participants' experience of semantic insight in Part II was associated with a significantly larger N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its high-level visual processing (Rossion \& Jacques, 2011; Tanaka \& Curran, 2001).
+The fact that this effect did not reocurr in Part III, when the objects were presented once more without descriptions, suggests its role as a marker of semantic insight altering object processing online.
+In contrast, we also observed a modulation of the N400 component, which was reduced for objects when semantic insight was ocurring (in Part II) and remained so when the same objects were presented repeatedly (in Part III).
+The N400 is often viewed as an index of increased demands for semantic processing (Kutas \& Federmeier, 2011; Rabovsky et al., 2018).
+Its reduction can thus be interpreted as lower semantic processing demands in response to unfamiliar objects once participants had unterstood what kind of objects they were viewing.
+Finally, semantic insight was also associated with increased amplitudes in the P1 component, but once the objects were repeated again (in Part III) after the critical presentation during which semantic insight had ocurred (in Part II).
+This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images (Samaha et al., 2018), may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had ocurred.
+
+However, because of the exploratory nature of the present study and the novelty of the ERP effects observed in Experiment 1, we first ran a replication study to assess the robustness of these findings in another samples of participants.
+
+\hypertarget{experiment-2}{%
+\section{Experiment 2}\label{experiment-2}}
+
+\hypertarget{methods-1}{%
+\subsection{Methods}\label{methods-1}}
+
+\hypertarget{participants-1}{%
+\subsubsection{Participants}\label{participants-1}}
+
+Participants for Experiment 2 were 24 German native speakers (18 female, 6 male) with a mean age of 23 years (range 19 to 32) who had not participated in Experiment 1.
+They had no history of psychological disorder or treatment, were right-handed and reported normal or corrected-to-normal vision.
+They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+
+\hypertarget{materials-procedure-and-analysis}{%
+\subsubsection{Materials, Procedure, and Analysis}\label{materials-procedure-and-analysis}}
+
+All materials, procedures, and methods for EEG recording and statistical analysis were identical to Experiment 1.
+An average of 5.8\% of rare objects per participant was classified as known in Part I and excluded from all further analyses.
+Based on participants' responses in Part II, an average of 26.4 objects (44.9\% of objects presented with matching descirptions) were assigned to the insight condition and an average of 49.2 objects (81.2\% of objects presented with non-matching descriptions) were assigned to the naive condition.
+Automatic rejection of EEG epochs containing artifacts led to the exlucsion of 11.0 trials (3.0\%) per participant (range 0 to 85).
+
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:exp2-table}Results of linear mixed-effects regression models for Experiment 2}
+
+\footnotesize{
+
+\begin{tabular}{lcccccc}
+\toprule
+ & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
+\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
+\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\midrule
+Part & 18.14 (2, 5151.1) & < .001 & 16.39 (2, 25.0) & < .001 & 70.58 (2, 25.2) & < .001\\
+Insight & 0.03 (1, 5272.5) & .853 & 1.23 (1, 5218.6) & .267 & 18.66 (1, 5207.5) & < .001\\
+Pt. × ins. & 3.74 (2, 5151.2) & .024 & 1.34 (2, 4736.8) & .263 & 8.07 (2, 4637.6) & < .001\\
+\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Part I & -0.17 [-0.72, 0.38] & .552 & -0.04 [-0.53, 0.45] & .864 & 0.02 [-0.44, 0.48] & .936\\
+Part II & -0.49 [-1.04, 0.07] & .084 & -0.50 [-0.99, 0.00] & .050 & 1.31 [0.86, 1.77] & < .001\\
+Part III & 0.56 [0.01, 1.11] & .048 & 0.04 [-0.45, 0.54] & .865 & 0.45 [-0.01, 0.91] & .055\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.39, all \emph{p}s \textless{} .001 (Table \ref{tab:exp2-table}).
+Also as in Experiment 1, N400 amplitudes differed between the insight and the naive condition averaged across parts, \emph{F}(1, 5207.5) = 18.66.
+The part × insight interaction was significant in the P1, \emph{F}(2, 5151.2) = 3.74, \emph{p} = .024, and in the N400, \emph{F}(2, 4637.6) = 8.07, \emph{p} \textless{} .001, but not in the N1, \emph{F}(2, 4736.8) = 1.34, \emph{p} = .263.
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_files/figure-latex/exp2-plot-1}
+
+}
+
+\caption{Results of Experiment 2.
+A.
+Bar plots and B.
+ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III.
+In a direct replication of Experiment 1, the effect of semantic insight on the N400 component in Part II and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II and on the N400 component in Part III remained only marginally significant.
+\newline*\emph{p} \textless{} .05.
+***\emph{p} \textless{} .001.}\label{fig:exp2-plot}
+\end{figure}
+
+\hypertarget{effects-of-insight-in-part-i-1}{%
+\subsubsection{Effects of Insight in Part I}\label{effects-of-insight-in-part-i-1}}
+
+As in Experiment 1, no differences between objects in the insight and the naive condition emerged in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .552 (Table \ref{tab:exp2-table}, Figure \ref{fig:exp2-plot}).
+
+\hypertarget{effects-of-insight-in-part-ii-1}{%
+\subsubsection{Effects of Insight in Part II}\label{effects-of-insight-in-part-ii-1}}
+
+As in Experiment 1, the occurence of semantic insight in Part II due to the presentation of objects with matching (vs.~non-matching) verbal descriptions was associated with a (marginally) significant enhancement of the N1 component, \emph{b} = -0.50, \emph{p} = .050, and a signficant reduction of the N400 component, \emph{b} = 0.91, \emph{p} \textless{} .001.
+
+\hypertarget{effects-of-insight-in-part-iii-1}{%
+\subsubsection{Effects of Insight in Part III}\label{effects-of-insight-in-part-iii-1}}
+
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without verbal descriptions as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantic insight had occured, \emph{b} = 0.56, \emph{p} = .048.
+Also, the N400 amplitude in response to these objects remained reduced, although marginally significant, \emph{b} = 0.45, \emph{p} .055.
+
+\hypertarget{joint-analysis-of-experiments-1-and-2}{%
+\subsubsection{Joint Analysis of Experiments 1 and 2}\label{joint-analysis-of-experiments-1-and-2}}
+
+In an attempt to maximize statistical power, we combined the data sets from Experiments 1 and 2.
+This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
+Methods for statistical analysis were kept the same as above, despite the addition of a new factor for experiment, coded as a simple contrast (i.e.~subtracting the Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments).
+This factor and its possible interactions with part, insight, and part × insight were included in the linear mixed-effects regression models as fixed effects and as potential by-item random effects.
+Note that, as above, random effects were included only if their omission led to a significant decline in model fit (Matuschek et al., 2017).
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:joint-table}Results of linear mixed-effects regression models for Experiments 1 and 2 combined}
+
+\footnotesize{
+
+\begin{tabular}{lcccccc}
+\toprule
+ & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
+\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
+\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\midrule
+Part & 12.38 (2, 49.0) & < .001 & 29.89 (2, 50.0) & < .001 & 95.34 (2, 50.6) & < .001\\
+Insight & 0.35 (1, 10560.3) & .552 & 1.77 (1, 10560.5) & .183 & 38.72 (1, 10518.8) & < .001\\
+Experiment & 0.35 (1, 48.2) & .555 & 2.39 (1, 48.1) & .129 & 4.75 (1, 48.4) & .034\\
+Pt. × ins. & 4.02 (2, 9042.4) & .018 & 5.59 (2, 9966.0) & .004 & 15.73 (2, 10010.1) & < .001\\
+Pt. × exp. & 0.03 (2, 49.0) & .971 & 0.55 (2, 50.0) & .581 & 2.58 (2, 50.6) & .086\\
+Ins. × exp. & 0.62 (1, 10536.2) & .432 & 0.04 (1, 10501.0) & .836 & 0.03 (1, 10574.9) & .865\\
+Pt. × ins. × exp. & 0.03 (2, 9042.9) & .972 & 0.62 (2, 9966.2) & .536 & 2.65 (2, 10010.4) & .070\\
+\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Part I & -0.07 [-0.44, 0.30] & .699 & -0.10 [-0.43, 0.24] & .565 & -0.10 [-0.41, 0.20] & .507\\
+Part II & -0.22 [-0.59, 0.15] & .248 & -0.56 [-0.90, -0.22] & .001 & 1.09 [0.79, 1.39] & < .001\\
+Part III & 0.49 [0.12, 0.86] & .010 & 0.25 [-0.09, 0.59] & .148 & 0.72 [0.41, 1.02] & < .001\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+As shown in Table \ref{tab:joint-table}, all main effects for part in the P1, N1, and N400 were significant, all \emph{F}s \textgreater{} 12.38, all \emph{p}s \textless{} .001, as was the main effect of insight in the N400, \emph{F}(1, 10518.8) = 38.72, \emph{p} \textless{} .001.
+Furthermore, the part × insight now was reliably observed in all three components, all \emph{F}s \textgreater{} 4.02, all \emph{p}s \textless{} .018.
+While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.75, \emph{p} = .034, the absence of any reliable interactions of experiment with part or insight indicated that the effect of our experimental manipulations did not differ between Experiments 1 and 2.
+
+We therefore computed the same planned comparisons between the insight and the naive condition within each part, now collapsed across the data from both experiments.
+This confirmed the absence of any reliable difference between the two conditions in Part I, all \emph{p}s \textgreater{} .507, the significant enhancement in the N1 in Part II, while insight was ocurring, \emph{b} = -0.56, \emph{p} = .001, the significant reduction in the N400 for insight in Parts II, while insight was occurring, \emph{b} = 1.09, \emph{p} \textless{} .001, and Part III, after insight had ocurred, \emph{b} 0.72, \emph{p} = \textless{} .001, as well as the sigificant enhancement in the P1 in Part III, after insight had occurred, \emph{b} = 0.49, \emph{p} = .010.
+
+\hypertarget{discussion-1}{%
+\subsection{Discussion}\label{discussion-1}}
+
+Experiment 2, a direct replication of Experiment 1, confirmed the impact of gaining the semantic insight into previously unfamiliar objects on ERPs associated with low-level visual perception (P1), high-level visual perception (N1), and semantic processing (N400).
+While the enhancement of the N1, being more negative in repsonse to objects for which participants experienced semantic insight, was present only during the critical presentation of the objects with their verbal descriptions (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after insight had taken place and the objects were presented again in Part III.
+This indicates a modulation of different stages of visual perception of objects through semantic knowledge while and after an understanding of the object has been obtained.
+Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantic insight may reflect lesser semantic processing demands as compared to unfamiliar objects which participants did not yet understand.
+
+\hypertarget{experiment-3}{%
+\section{Experiment 3}\label{experiment-3}}
+
 \newpage
@@
 \begin{cslreferences}
+\leavevmode\hypertarget{ref-americanelectroencephalographicsociety1991}{}%
+American Electroencephalographic Society.
+(1991).
+American Electroencephalographic Society guidelines for standard electrode position nomenclature.
+\emph{Journal of Clinical Neurophysiology}, \emph{8}(2), 200--202.
+
+\leavevmode\hypertarget{ref-baayen2008}{}%
+Baayen, R.
+H., Davidson, D.
+J., \& Bates, D.
+M.
+(2008).
+Mixed-effects modeling with crossed random effects for subjects and items.
+\emph{Journal of Memory and Language}, \emph{59}(4), 390--412.
+\url{https://doi.org/10.1016/j.jml.2007.12.005}
+
+\leavevmode\hypertarget{ref-barr2013}{}%
+Barr, D.
+J., Levy, R., Scheepers, C., \& Tily, H.
+J.
+(2013).
+Random effects structure for confirmatory hypothesis testing: Keep it maximal.
+\emph{Journal of Memory and Language}, \emph{68}(3), 255--278.
+\url{https://doi.org/10.1016/j.jml.2012.11.001}
+
+\leavevmode\hypertarget{ref-R-lme4}{}%
+Bates, D., Mächler, M., Bolker, B., \& Walker, S.
+(2015).
+Fitting linear mixed-effects models using lme4.
+\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
+\url{https://doi.org/10.18637/jss.v067.i01}
+
+\leavevmode\hypertarget{ref-buxfcrki2018}{}%
+Bürki, A., Frossard, J., \& Renaud, O.
+(2018).
+Accounting for stimulus and participant effects in event-related potential analyses to increase the replicability of studies.
+\emph{Journal of Neuroscience Methods}, \emph{309}, 218--227.
+\url{https://doi.org/10.1016/j.jneumeth.2018.09.016}
+
+\leavevmode\hypertarget{ref-fruxf6ber2017}{}%
+Fröber, K., Stürmer, B., Frömer, R., \& Dreisbach, G.
+(2017).
+The role of affective evaluation in conflict adaptation: An LRP study.
+\emph{Brain and Cognition}, \emph{116}, 9--16.
+\url{https://doi.org/10.1016/j.bandc.2017.05.003}
+
+\leavevmode\hypertarget{ref-fruxf6mer2018}{}%
+Frömer, R., Maier, M., \& Abdel Rahman, R.
+(2018).
+Group-level EEG-processing pipeline for flexible single trial-based analyses including linear mixed models.
+\emph{Frontiers in Neuroscience}, \emph{12}.
+\url{https://doi.org/10.3389/fnins.2018.00048}
+
+\leavevmode\hypertarget{ref-gramfort2013}{}%
+Gramfort, A., Luessi, M., Larson, E., Engemann, D.
+A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& al.
+(2013).
+MEG and EEG data analysis with MNE-Python.
+\emph{Frontiers in Neuroscience}, \emph{7}.
+\url{https://doi.org/10.3389/fnins.2013.00267}
+
+\leavevmode\hypertarget{ref-hyvuxe4rinen1999}{}%
+Hyvärinen, A.
+(1999).
+Fast and robust fixed-point algorithms for independent component analysis.
+\emph{IEEE Transactions on Neural Networks}, \emph{10}(3), 626--634.
+\url{https://doi.org/10.1109/72.761722}
+
+\leavevmode\hypertarget{ref-judd2012}{}%
+Judd, C.
+M., Westfall, J., \& Kenny, D.
+A.
+(2012).
+Treating stimuli as a random factor in social psychology: A new and comprehensive solution to a pervasive but largely ignored problem.
+\emph{Journal of Personality and Social Psychology}, \emph{103}(1), 54--69.
+\url{https://doi.org/10.1037/a0028347}
+
+\leavevmode\hypertarget{ref-kutas2011}{}%
+Kutas, M., \& Federmeier, K.
+D.
+(2011).
+Thirty years and counting: Finding meaning in the n400 component of the event-related brain potential (erp).
+\emph{Annual Review of Psychology}, \emph{62}, 621--647.
+\url{https://doi.org/10.1146/annurev.psych.093008.131123}
+
+\leavevmode\hypertarget{ref-matuschek2017}{}%
+Matuschek, H., Kliegl, R., Vasishth, S., Baayen, H., \& Bates, D.
+(2017).
+Balancing Type I error and power in linear mixed models.
+\emph{Journal of Memory and Language}, \emph{94}, 305--315.
+\url{https://doi.org/10.1016/j.jml.2017.01.001}
+
+\leavevmode\hypertarget{ref-oldfield1971}{}%
+Oldfield, R. C. (1971). The assessment and analysis of handedness: The Edinburgh inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}
+
+\leavevmode\hypertarget{ref-rabovsky2018}{}%
+Rabovsky, M., Hansen, S.
+S., \& McClelland, J.
+L.
+(2018).
+Modelling the n400 brain potential as change in a probabilistic representation of meaning.
+\emph{Nature Human Behaviour}, \emph{2}(9), 693--705.
+\url{https://doi.org/10.1038/s41562-018-0406-4}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-rossion2011}{}%
+Rossion, B., \& Jacques, C.
+(2011).
+The n170: Understanding the time course of face perception in the human brain.
+In \emph{The oxford handbook of event-related potential components} (pp.
+115--142).
+Oxford University Press.
+\url{https://doi.org/10.1093/oxfordhb/9780195374148.001.0001}
+
+\leavevmode\hypertarget{ref-samaha2018}{}%
+Samaha, J., Boutonnet, B., Postle, B.
+R., \& Lupyan, G.
+(2018).
+Effects of meaningfulness on perception: Alpha-band oscillations carry perceptual expectations and influence early visual responses.
+\emph{Scientific Reports}, \emph{8}(1), 1--14.
+\url{https://doi.org/10.1038/s41598-018-25093-5}
+
+\leavevmode\hypertarget{ref-tanaka2001}{}%
+Tanaka, J. W., \& Curran, T. (2001). A neural basis for expert object recognition. \emph{Psychological Science}, \emph{12}(1), 43--47. \url{https://doi.org/10.1111/1467-9280.00308}
+
+\leavevmode\hypertarget{ref-vanrossum2009}{}%
+van Rossum, G., \& Drake, F. L. (2009). \emph{Python 3 reference manual}. CreateSpace.
+
+\leavevmode\hypertarget{ref-R-buildmer}{}%
+Voeten, C. C. (2020). \emph{buildmer: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
 \end{cslreferences}

### 2020-10-15 analysis/manuscript.Rmd
initialize docker

---
title             : |
  | Event-Related Potentials of the Semantically
  | Informed Perception of Unfamiliar Objects
shorttitle        : "Semantic Knowledge and Unfamiliar Objects"

author: 
  - name          : "Alexander Enge"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Rudower Chaussee 18, 12489 Berlin"
    email         : "alexander.enge@hu-berlin.de"

affiliation:
  - id            : "1"
    institution   : "Humboldt-Universität zu Berlin"

authornote: |
  Alexander Enge, Department of Psychology, Humboldt-Universität zu Berlin, Germany, https://orcid.org/0000-0003-0100-2297, student no. 581331.

  The thesis was handed December 18, 2020 and has been supervised by Prof. Dr. Rasha Abdel Rahman, Humboldt-Universität zu Berlin, Germany, and Prof. Dr. Franziska Süß, Fachhochschule des Mittelstands, Bamberg, Germany.

abstract: |
  Abstract goes here.

keywords          : "keywords"
wordcount         : "X"

bibliography      : "manuscript_files/r-references.bib"
zotero            : "aha"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "manuscript_files/apa.csl"
documentclass     : "apa7"
classoption       : "man,11pt"
output:
  papaja::apa6_pdf:
    latex_engine:   "xelatex"

header-includes:
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  - \AtBeginEnvironment{lltable}{\doublespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1,scriptsize}}
  - \raggedbottom
---

```{r setup, include=FALSE}
# Load packages
library(papaja)
library(reticulate)
library(tidyverse)
library(magrittr)
library(cowplot)

# Chunk options
knitr::opts_chunk$set(include = FALSE, fig.align = "center", fig.out = "100%", fig.width = 10)

# Specify Python environment
renv::use_python(type = "virtualenv")

# Bibliography file
r_refs("analysis/manuscript_files/r-references.bib")

# Create export folder for results
dir.create("analysis/export", showWarnings = FALSE)

# Do we want to run analysis for Experiment 3?
run_exp3 <- FALSE
```

How does our perception of an object change as soon as we discover what it is for? In this study, we presented participants with unfamiliar objects, preceded either by valid information about their function (leading to semantically informed perception) or by misleading information (leading to naive perception). Capitalizing on the high temporal resolution of event-related potentials (ERPs), we investigated how different stages in the processing hierarchy are modulated by this semantic understanding of objects before, during, and after it has been acquired.

-   One paragraph explaining that previous research has shown that semantic knowledge modulates early stages of visual perception (e.g. Abdel Rahman & Sommer, 2008; Gauthier et al., 2003; Maier & Abdel Rahman, 2019; Maier et al., 2014; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka & Curran, 2001; Weller et al., 2019).

-   Potentially one paragraph describing Abdel Rahman & Sommer (2008) in more detail (participants acquiring knowledge about existing but unfamiliar objects).

-   One paragraph describing Samaha et al. (2018) in more detail (participants being trained to see familiar objects in otherwise meaningless images). Possibly hypothesize a special role of insight (= the moment when understanding is acquired), although this is not directly captured by the study.

-   One paragraph explaining how all of these studies measured ERPs only *after* an extensive learning phase, making it difficult to determine (a) how much learning is necessary for semantic knowledge to influence perception and, related to that, (b) if the modulation of early ERP components reflects genuine online effects of semantic knowledge or rather the activation of altered visual representations (Firestone & Scholl, 2015) (?).

-   One paragraph on theories of top-down/language effects on visual perception (reverse hierarchy theory).

-   Possibly another paragraph on theories of top-down effects on visual perception (label feedback hypothesis) if it fits thematically.

-   Do we need to refer to the role of attention already in the introduction? If so, potentially another paragraph here. I might prefer to leave that for the discussion.

-   Possibly one more paragraph on why ERPs are so suitable to answer this research question, including a brief characterization of the relevant components (P1: lower-level visual perception, N1: higher-level visual perception, N400: semantic processing).

-   The present study: Design of the study with a focus on distinguishing between online effects and altered representations; no specific hypotheses but looking for influences of semantic knowledge on the three ERP components at three different stages (before, during, and after acquisition).

# Experiment 1

```{r exp1-preparation}
# Define function for reading and formatting behavioral data
read_behav <- function(txt_fname) {
  # Read log file
  dat <- suppressMessages(suppressWarnings(read_tsv(txt_fname)))
  # Rename columns for participant and item IDs
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = case_when(
      Wdh %in% c(211, 231) ~ "I",
      Wdh %in% c(212, 232) ~ "II",
      Wdh %in% c(213, 233) ~ "III",
      Wdh == 234 ~ "IV"
    ) %>% as_factor()) %>%
    # Remove filler stimuli (i.e. well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  excl_known <- dat %>%
    filter(part == "I" & Tastencode %in% c(201, 251)) %>%
    pull(item)
  excl_insight <- dat %>%
    filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
    pull(item)
  excl_naive <- dat %>%
    filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>%
    pull(item)
  insight <- dat %>%
    filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
    pull(item)
  naive <- dat %>%
    filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>%
    pull(item)
  # Create a new condition for the experimental condition
  dat %<>% mutate(condition = case_when(
    item %in% excl_known ~ "Excl_known",
    item %in% excl_insight ~ "Excl_insight",
    item %in% excl_naive ~ "Excl_naive",
    item %in% insight ~ "Insight",
    item %in% naive ~ "Naive"
  ) %>%
    factor(levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if ("richtig_inv" %in% dat$Bed) {
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    # Return only relevant columns
    dat %<>% select(part, condition, participant, item, RT)
  }
  return(dat)
}

# Read behavioral data for Experiment 1
data_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)

# Check average number of stimuli per condition
(stims_exp1 <- map(data_exp1, function(x) {
  table(x$condition) / 3
}) %>% bind_rows() %>% colMeans())
```

```{python exp1-preprocessing}
# Import libraries
import mne
import glob
import os

# Set parameters for EEG preprocessing
preproc_params = dict(
    n_components=15, method="fastica",         # ICA parameters
    l_freq=0.1, h_freq=30,                     # Filter edges
    event_id={"match": 221, "mismatch": 222},  # EEG triggers
    tmin=-0.5, tmax=1.498,                     # Length of epochs
    baseline=(-0.2, 0),                        # Baseline correction
    reject=dict(eeg=200)                       # Rejection threshold
)

# # Debug
# locals().update(preproc_params)
# vhdr_fname = 'data/exp1/EEG/Vp0001.vhdr'

# Define function for preprocessing EEG data
def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline, reject):
    # Read EEG data in microvolts
    raw = mne.io.read_raw_brainvision(vhdr_fname, scale=1e6, preload=True)
    # Create virtual EOG channels
    raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
    raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
    raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
    # Add EasyCap electrode layout, removing any excessive channels
    montage = mne.channels.make_standard_montage("easycap-M1")
    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
    raw.set_montage(montage=montage)
    # # Interpolate bad channels
    # if vhdr_fname=='data/exp3/EEG/VP05.vhdr':
    #   raw.info['bads'].extend(['AF8', 'TP9'])
    #   raw = raw.interpolate_bads()
    # Re-reference to common average
    raw, _ = mne.set_eeg_reference(raw, "average")
    # Run ICA on a copy of the data
    filt_raw = raw.copy()
    filt_raw.load_data().filter(l_freq=1, h_freq=None)
    ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
    ica.fit(filt_raw)
    # Remove bad components based on correlations with EOG
    eog_indices, eog_scores = ica.find_bads_eog(raw)
    ica.exclude = eog_indices
    raw = ica.apply(raw)
    # Apply band-pass filter
    raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
    # Epoching including baseline correction
    events, _ = mne.events_from_annotations(raw, verbose=False)
    epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True)
    # Add behavioral data
    epochs.metadata = metadata
    # Reject bad epochs
    epochs = epochs.drop_bad(reject=reject)
    return epochs

# List raw EEG filenames
fnames_exp1 = sorted(glob.glob("data/exp1/EEG/*.vhdr"))

# Import behavioral data from R
metadata_exp1 = r.data_exp1

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists("analysis/export/exp1-epo.fif"):
    # Read preprocessed data from file
    epochs_exp1 = mne.read_epochs("analysis/export/exp1-epo.fif", preload=True)
else:
    # Preprocess EEG data for Experiment 1
    epochs_exp1 = [
        preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp1, metadata_exp1)
    ]
    # Combine epochs into a single data set
    epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
    # Backup epochs to the export folder
    epochs_exp1.save("analysis/export/exp1-epo.fif")

# # Get indices of bad epochs despite ICA
# rej_exp1 = epochs_exp1.drop_log
# rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
# rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]

# Define function to compute grand averages per condition
def compute_evokeds(epochs):
    evokeds = dict()
    evokeds_dat = dict()
    # Each part becomes a dictionary of conditions
    for pt in ["I", "II", "III"]:
        evokeds[pt] = dict()
        evokeds_dat[pt] = dict()
        # Each condition becomes a list of participants
        for cn in ["Insight", "Naive"]:
            evokeds[pt][cn] = list()
            evokeds_dat[pt][cn] = list()
            # For every participant we average trials separately for all parts and conditions
            for vp in epochs.metadata["participant"].unique():
                query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
                evokeds[pt][cn].append(epochs[query].average())
            # Compute grand averages across participants for this part and condition
            evokeds[pt][cn] = mne.grand_average(evokeds[pt][cn])
            # Export only the actual data for R
            evokeds_dat[pt][cn] = evokeds[pt][cn].data
    return (evokeds, evokeds_dat)

# Compute grand averages for Experiment 1
evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)

# # Plot evoked potentials
# import matplotlib.pyplot as plt
# mne.viz.plot_compare_evokeds(evokeds=evokeds_exp1['II'], picks='P8'); plt.show()
# evokeds_exp1['II']['Insight'].data = evokeds_exp1['II']['Insight'].data - evokeds_exp1['II']['Naive'].data
# evokeds_exp1['II']['Insight'].plot_topomap(times=[0.125, 0.175, 0.5], average=0.05, vmin=-1, vmax=1, cmap='viridis'); plt.show()
```

```{r exp1-analysis}
# Re-import behavioral data and re-factorize some columns
data_exp1 <- py$epochs_exp1$metadata %>% mutate(
  part = factor(part, levels = c("I", "II", "III")),
  condition = factor(condition, levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")),
  participant = factor(participant),
  item = factor(item)
)

# Check number of rejected epochs
rejected_exp1 <- data_exp1 %>%
  group_by(participant) %>%
  tally() %>%
  mutate(n = 360 - n) %>%
  pull(n)
mean(rejected_exp1)    # Mean
median(rejected_exp1)  # Median
range(rejected_exp1)   # Range

# Create vectors with sample time points (in ms) and electrodes
tmin <- py$preproc_params$tmin * 1000
tmax <- py$preproc_params$tmax * 1000
sfreq <- py$epochs_exp1$info["sfreq"]
times <- seq(tmin, tmax, 1000 / sfreq)
els <- py$epochs_exp1$ch_names

# Define ERP components of interest
comps <- tibble(
  name = c("P1", "N1", "N400"),
  start = c(100, 150, 400),
  stop = c(150, 200, 700),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)

# Define function to compute single-trial mean ERP amplitudes
compute_erps <- function(epochs, els, name, start, stop, roi) {
  erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
  erps <- apply(erps, 1, mean, na.rm = TRUE)
  return(erps)
}

# Check if single-trial ERPs were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp1-erps.RDS")) {
  # Read data from file
  data_exp1 <- readRDS("analysis/export/exp1-erps.RDS")
} else {
  # Import epoched data from Python
  epochs_exp1 <- py$epochs_exp1$get_data()
  # Compute single-trial ERPs for Experiment 1
  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>%
    set_names(comps$name) %>%
    cbind(data_exp1, .) %T>%
    saveRDS("analysis/export/exp1-erps.RDS")
}

# Remove the Python object to free up memory
py_run_string("del epochs_exp1")
import("gc")$collect()

# Remove any trials excluded from conditions
data_exp1 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()

# Contrast coding for condition (insight-naive) and part (2-1, 3-1)
contrasts_condition <- t(cbind(c("Insight" = 1, "Naive" = -1)))
contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
contrasts(data_exp1$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp1$part) <- MASS::ginv(contrasts_part)

# Set formula and parameters for linear mixed-effects regression models (LMMs)
form_exp12 <- buildmer::tabulate.formula(
  ~ part * condition + (part * condition | participant) + (part * condition | item)
) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
ctrl_params <- lme4::lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Set formula for follow-up contrasts
specs_exp12 <- pairwise ~ condition | part

# Define function to compute LMMs and follow-up contrasts for each component
compute_models <- function(dep, formula, data, control, specs) {
  require(lmerTest)
  require(buildmer)
  require(emmeans)
  build <- buildmer(
    control = control,
    REML = FALSE,
    buildmerControl = buildmerControl(
      formula = formula,
      data = data,
      direction = c("order", "backward"),
      elim = function(logp) exp(logp) >= .20,
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts %>% as.data.frame()
  mod <- list("model" = build@model, "anova" = build@anova, "summary" = build@summary, "contrasts" = conts)
  return(mod)
}

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp1-stats.RDS")) {
  # Read models from file
  models_exp1 <- readRDS("analysis/export/exp1-stats.RDS")
} else {
  # Compute LMMs for Experiment 1
  models_exp1 <- map(
    comps$name,
    compute_models,
    formula = form_exp12,
    data = data_exp1,
    control = ctrl_params,
    specs = specs_exp12
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/exp1-stats.RDS")
}
```

## Methods

### Participants

Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment. All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision. They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating. All experiments subsequently reported were carried out in accordance with the Declaration of Helsinki and approved by the local ethics committee.

### Materials and Procedure

Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g. a bicycle, a toothbrush), whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g. a galvanometer, an udu drum). The well-known objects were included as filler stimuli of no interest. A list of the unfamiliar objects can be found in Appendix A. All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz. At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.

For each unfamiliar object, a noun--verb pair was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g. current--measuring, pottery--drumming). In the *insight* condition, the presentation of each unfamiliar object was preceded by its respective description, whereas in the *naive* condition, it was preceded by a non-matching description belonging to one of the other objects. In both conditions, the noun and the verb were presented one above the other in black letters on a light blue background. For each participant, half of the unfamiliar objects were presented in the insight condition (i.e. with a matching description) and the other half were presented in the naive condition (i.e. with a non-matching description). All participants saw each unfamiliar object in only one of the two conditions and the assignment of objects to conditions was counterbalanced across participants. The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).

Each experimental session consisted of three parts (Figure \@ref(fig:exp1-plot)A). In Part I, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without verbal descriptions. Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s. The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects. The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I do not know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively. The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants. Because we were interested in the acquisition of semantic knowledge about unfamiliar objects only, all objects for which the participant indicated knowing the object in Part I were excluded from further analysis (`r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)` of rare objects per participant).

(ref:figure-1-caption) Procedure and results of Experiment 1. *(A)* In Part I, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing. In Part II, half of the objects were preceded by a matching description (in purple color for illustration), leading to semantic insight, and the other half with a non-matching description (in petrol color for illustration), leading to naive perception. In Part III, the same objects were presented again without the descriptions. *(B)* Bar plots and *(C)* ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III. Insight was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III. Error bars show the standard error of the mean. Ampl. = amplitude.\newline\**p* \< .05. \*\**p* \< .01. \*\*\**p* \< .001.

```{r exp1-plot, include=TRUE, fig.height=12, fig.cap = "(ref:figure-1-caption)"}
# Manually extract significance levels from contrasts for plotting
stars_exp1 <- list(
  P1 = c(I = NA, II = NA, III = "*"),
  N1 = c(I = NA, II = "*", III = NA),
  N400 = c(I = NA, II = "***", III = "***")
)

# Import grand averaged evoked potentials from Python
evokeds_exp1 <- py$evokeds_dat_exp1

# Retrieve locations for the relevant electrodes from standard montage
fname_montage <- list.files(path = "renv/python", pattern = "easycap-M1.txt", recursive = TRUE, full.names = TRUE)[1]
montage <- py$evokeds_exp1$I$Insight$ch_names %>%
  as_tibble() %>%
  rename(electrode = value) %>%
  left_join(read_tsv(fname_montage) %>% rename(electrode = Site)) %>%
  mutate(
    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi))
  )

# Define function to plot trial structure
plot_trial <- function() {
  require(magick)
  colour_insight <- viridisLite::viridis(1, begin = 0.1, end = 0.1)
  colour_naive <- viridisLite::viridis(1, begin = 0.5, end = 0.5)
  trial_I <- ggplot() +
    coord_fixed() +
    theme_void() +
    xlim(c(0, 74)) +
    ylim(c(-5, 68)) +
    geom_text(aes(x = 37, y = 68, label = "Part I"), size = 14 / .pt, family = "Helvetica", fontface = "bold") +
    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
    draw_image("analysis/manuscript_files/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")),
                 color = "black")
  trial_II <- ggplot() +
    coord_fixed() +
    theme_void() +
    xlim(c(0, 74)) +
    ylim(c(-5, 68)) +
    geom_text(aes(x = 37, y = 68, label = "Part II"), size = 14 / .pt, family = "Helvetica", fontface = "bold") +
    geom_rect(aes(xmin = 0, xmax = 20, ymin = 0, ymax = 20), color = "black", fill = "white") +
    geom_text(aes(x = 10, y = 10.5, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
    geom_text(aes(x = 10, y = -3, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = colour_insight, fill = "white") +
    geom_text(aes(x = 28, y = 23, label = "Potato\nmashing"), color = colour_insight, size = 10 / .pt,
              family = "Helvetica") +
    geom_text(aes(x = 28, y = 10, label = "2.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
    geom_rect(aes(xmin = 18, xmax = 38, ymin = 39, ymax = 59), color = colour_naive, fill = "white") +
    geom_text(aes(x = 28, y = 49, label = "Message\nmorsing"), color = colour_naive, size = 10 / .pt,
              family = "Helvetica") +
    geom_text(aes(x = 28, y = 36, label = "or"), color = "black", size = 10 / .pt, family = "Helvetica") +
    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
    geom_text(aes(x = 46, y = 34, label = "*"), size = 8, family = "Helvetica") +
    geom_text(aes(x = 46, y = 23, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
    geom_rect(aes(xmin = 54, xmax = 74, ymin = 39, ymax = 59), color = "black", fill = "white") +
    draw_image("analysis/manuscript_files/potato_masher.png", x = 54, y = 39, width = 20, height = 20) +
    geom_text(aes(x = 65, y = 36, label = "max. 3 s"), color = "black", size = 10 / .pt, family = "Helvetica",
              lineheight = 1) +
    geom_segment(aes(x = 28, y = 0, xend = 74, yend = 33.222), arrow = arrow(length = unit(0.2, "cm")),
                 color = "black")
  trial_III <- ggplot() +
    coord_fixed() +
    theme_void() +
    xlim(c(0, 74)) +
    ylim(c(-5, 68)) +
    geom_text(aes(x = 37, y = 68, label = "Part III"), size = 14 / .pt, family = "Helvetica", fontface = "bold") +
    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
    draw_image("analysis/manuscript_files/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")),
                 color = "black")
  plot_grid(trial_I, NULL, trial_II, NULL, trial_III, nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
}

# Define function to plot mean ERP amplitudes
plot_bars <- function(data, stars, ymin) {
  parts <- map(c("I", "II", "III"), function(part) {
    # For which components in the current part do we have a significant effect?
    sig <- map(stars, part) %>%
      as.data.frame() %>%
      t() %>%
      as.data.frame() %>%
      set_colnames("label") %>%
      rownames_to_column("comp") %>%
      na.omit()
    # Create bar plot for the current part
    map(c("P1", "N1", "N400"), function(comp) {
      p <- data %>%
        filter(part == !!part) %>%
        Rmisc::summarySEwithin(measurevar = comp, withinvars = "condition", idvar = "participant") %>%
        mutate(comp = !!comp) %>%
        rename(amplitude = !!comp)
    }) %>%
      bind_rows() %>%
      mutate(comp = fct_relevel(comp, "P1", "N1", "N400")) %>%
      ggplot(aes(x = comp, y = amplitude, fill = condition)) +
      # geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
      # annotate("tile", x = sig$comp, y = -0.4, width = 0.45, height = 0.8, colour = "black", fill = "white", size = 0.5) +
      # annotate("rect", xmin = -Inf, xmax = Inf, ymin = -0.2, ymax = Inf, fill = "white") +
      # geom_bar(aes(y = amplitude - se - 0.2), stat = "identity", position = position_dodge()) + scale_fill_manual(values = c("white", "white")) +
      # new_scale_fill() +
      # annotate("label", x = sig$comp, y = -0.96, label = sig$label, size = 7, family = "Helvetica", label.size = 0) +
      geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
      scale_fill_viridis_d(begin = 0.1, end = 0.5) +
      geom_errorbar(aes(ymin = amplitude - se, ymax = amplitude + se),
                    position = position_dodge(width = 0.9), width = 0.5) +
      annotate("text", x = sig$comp, y = ymin, label = sig$label, size = 6, family = "Helvetica") +
      geom_hline(yintercept = 0) +
      coord_cartesian(ylim = c(ymin, ymin + 7)) +
      ylab("ROI ampl.\n(µV)") +
      scale_y_continuous(breaks = seq(trunc(ymin), trunc(ymin) + 6, 2)) +
      theme_classic() +
      theme(
        legend.position = "none",
        panel.grid = element_blank(),
        axis.ticks = element_line(color = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(family = "Helvetica", color = "black", size = 10),
        axis.text = element_text(family = "Helvetica", color = "black", size = 10),
        plot.margin = margin(t = 0.3, r = 0, b = 0.4, l = 0.2, "cm")
      )
  })
  plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
}

# Define function to plot ERP waveforms and topographies
plot_erps <- function(comps, evokeds, montage, stars) {
  pmap(comps, function(name, start, stop, roi) {
    # N400 gets a different scale than P1 and N1
    ymin <- ifelse(name == "N400", -3, -4)
    # Loop through parts
    parts <- map(c("I", "II", "III"), function(part) {
      # Create (conditions x time points) x electrodes tibble
      data_plot <- evokeds[[part]] %>%
        map(function(data) {
          data %>%
            t() %>%
            as_tibble(.name_repair = "unique") %>%
            set_colnames(montage$electrode) %>%
            mutate(.time = times, roi = rowMeans(select(., all_of(roi))))
        }) %>%
        bind_rows(.id = "condition")
      # Prepare waveform
      wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
        annotate("rect", xmin = start, xmax = stop, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
      # Shade significant area
      star <- stars[[name]][[part]]
      if (!is.na(star)) {
        wave <- wave + geom_ribbon(
          data = data_plot %>% filter(.time >= start & .time <= stop) %>%
            group_by(.time) %>% summarise(ymin = min(roi), ymax = max(roi)),
          aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
          inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1)
        )
      } #+
      # annotate("text", label = star, x = start + (stop - start)/2, y = -3.2, size = 7, family = "Helvetica")}
      # Add waves and styling
      wave <- wave +
        annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
        annotate("segment", x = 0, xend = 0, y = ymin, yend = ymin + 12) +
        annotate("segment", x = seq(-100, 700, 200), xend = seq(-100, 700, 200), y = -0.3, yend = 0) +
        annotate("segment", x = -12, xend = 0, y = seq(-2, 8, 4), yend = seq(-2, 8, 4)) +
        annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10 / .pt,
                 family = "Helvetica") +
        annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10 / .pt, family = "Helvetica",
                 hjust = 1) +
        annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10 / .pt, family = "Helvetica",
                 lineheight = 0.9) +
        annotate("text",
          x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10 / .pt,
          family = "Helvetica", angle = 90, lineheight = 0.9
        ) +
        geom_line() +
        scale_color_viridis_d(begin = 0.1, end = 0.5) +
        coord_cartesian(xlim = c(-200, 800), ylim = c(ymin, ymin + 14), expand = FALSE) +
        theme_void() +
        theme(legend.position = "none")
      # Plot topography
      topo <- data_plot %>%
        filter(.time >= start & .time <= stop) %>%
        group_by(condition) %>%
        summarise(across(montage$electrode, mean)) %>%
        pivot_longer(-condition) %>%
        pivot_wider(names_from = condition) %>%
        transmute(amplitude = Insight - Naive) %>%
        bind_cols(montage) %>%
        eegUtils::topoplot(limits = c(-1, 1), palette = "viridis", contour = FALSE, highlights = roi, scaling = 0.1) +
        theme(legend.position = "none")
      topo$layers[[3]]$aes_params$size <- topo$layers[[4]]$aes_params$size <- topo$layers[[5]]$aes_params$size <- 0.6
      # Combine waveform and topography
      wave + draw_plot(topo, width = 320, height = 9, x = 500, y = ymin + 6.4)
    })
    # Combine plots for the different parts
    plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
    # Combine plots for the different components
  }) %>% plot_grid(plotlist = ., nrow = 3)
}

# Define functions to plot legends for conditions and topoplots
plot_legends <- function() {
  legend_conditions <- get_legend(tibble(Conditions = c("Insight", "Naive")) %>% 
                                    ggplot(aes(x = 0, y = 0, fill = Conditions)) +
    geom_raster() +
    scale_fill_viridis_d(begin = 0.1, end = 0.5) +
    theme(
      legend.direction = "horizontal",
      legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
      legend.text = element_text(family = "Helvetica", size = 10),
      legend.spacing.x = unit(0.3, "cm")
    ))
  legend_topo <- get_legend(tibble(amplitude = c(-1, 1)) %>% ggplot(aes(x = 0, y = 0, fill = amplitude)) +
    geom_raster() +
    labs(fill = "Insight - naive\nampl. (µV)") +
    scale_fill_viridis_c(guide = guide_colorbar(
      ticks = FALSE, title.position = "left",
      title.vjust = 1, title.hjust = 0.5
    )) +
    theme(
      legend.direction = "horizontal",
      legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
      legend.text = element_text(family = "Helvetica", size = 10),
      legend.key.width = unit(0.8, "cm"), legend.spacing.x = unit(0.3, "cm")
    ))
  plot_grid(NULL, legend_conditions, legend_topo, NULL, nrow = 1, rel_widths = c(1, 3, 3, 1))
}

# Read SVG file with the trial structure (created using MS PowerPoint)
plot_trials <- grImport2::readPicture("analysis/manuscript_files/figure-1a.svg") %>%
  grImport2::pictureGrob(expansion = 0)

# Create plot for Experiment 1
plot_grid(
  #plot_trial(),
  plot_trials,
  #plot_bars(data = data_exp1, stars = stars_exp1, ymin = -1.5),
  plot_erps(comps = comps, evokeds = evokeds_exp1, montage = montage, stars = stars_exp1),
  plot_legends(),
  #nrow = 4, rel_heights = c(3, 2, 6, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica"
  nrow = 3, rel_heights = c(5, 6, 1), labels = c("A", "B", ""), label_fontfamily = "Helvetica"
  #nrow = 4, rel_heights = c(4, 2, 5, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica"
)
```

In Part II, only the 120 unfamiliar objects were presented for a second time, now preceded either by a matching verbal description (in the insight condition) or by a non-matching verbal description (in the naive condition). Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the verbal description for 2.5 s. Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s. The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g. medical devices, musical instruments). To make sure that insight did (did not) occur in the insight (naive) condition, we excluded any objects from the insight condition if participants indicated not knowing the object or having rather no assumption (despite reading the matching description) and any objects from the naive condition if participants indicated knowing the object or having an assumption (despite reading the non-matching description). This resulted in an average of `r format(round(stims_exp1["Insight"], 1), nsmall = 1)` objects (`r scales::percent(stims_exp1["Insight"]/60, accuracy = 0.1)`) per participant remaining in the insight condition and an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects (`r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)`) per participant remaining in the naive condition.

In Part III, the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e. without the verbal descriptions. Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with descriptions), participants took a self-timed break and continued with the same block of 30 objects in Part III (without descriptions) before moving on to the next block consisting of 30 different objects. They continued like this until all four blocks were completed in both Parts II and III. In total, the experiment consisted of 480 trials (120 familiar objects in Part I and 120 unfamiliar objects in Parts I, II, and III) and took participants approximately 35 minutes to complete.

### EEG Recording and Preprocessing

The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system [@americanelectroencephalographicsociety1991] and referenced online to an external electrode placed on the left mastoid (M1). Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively. During the recording, electrode impedance was kept below 5 kΩ. An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1,000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.

Offline, the data were preprocessed using the MNE software [Version 0.21.0; @gramfort2013] in Python [Version 3.7.7; @vanrossum2009]. First, all scalp electrodes were re-referenced to the common average. Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA). The first 15 components were extracted using the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz. Those components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the *find\_bads\_eog* function. After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied. Next, the continuous EEG was epoched into segments of 2,000 ms, starting 500 ms before the onset of the visual presentation of each unfamiliar object. The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset. Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis. This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials (`r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`) per participant (range `r min(rejected_exp1)` to `r max(rejected_exp1)`). Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N1 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.

### Statistical Analysis

The event-related potentials were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018]. For the purpose of the present study, these models have two desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages. First, they can account simultaneously for the non-independence of data points coming from the same participant or from the same item, whereas the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012]. Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is based on participants' own responses rather than on the experimental manipulation [e.g.  @fröber2017].

Three separate models were computed predicting P1, N1, and N400 mean amplitudes, respectively. All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e. subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e. subtracting the naive from the insight condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition. For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to @schad2020. To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013]. We then performed a model selection algorithm as proposed by @matuschek2017 for increasing statistical power and avoiding overparameterization: Iteratively, each random effects was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test. Only if the parsimonious model explained the data equally well as the complex model [determined by *p* \> .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model. All models were calculated in R [Version `r packageVersion("base")`; @R-base] using the lme4 package [Version `r packageVersion("lme4")`; @R-lme4]. The optimizer function *bobyqa* with 2·10^5^ iterations was used for maximum likelihood estimation. The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r packageVersion("buildmer")`; @R-buildmer]. Finally, to answer our research question of whether or not semantic insight had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the insight against the naive condition within Parts I, II, and III. Reported *p* values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's methods as implemented in the lmerTest package [@R-lmerTest].

The materials and code for the present experiments can be accessed via the Open Science Framework ([https://osf.io/.../](https://osf.io/myprojects/)).

## Results

Single-trial ERPs were analyzed in response to unfamiliar objects before (Part I), while (Part II), and after (Part III) participants gained semantic insight into the function or use of the objects. Half of the objects were preceded by a matching description, fostering semantic insight to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object. To make sure participants did indeed experience insight or naive perception, the analysis was constrained by participants' behavioral responses in Part II: Objects presented with a matching description were assigned to the insight condition only if the participant indicated that they understood what the object was (or had an assumption), whereas objects presented with a non-matching description were assigned to the naive condition only if the participant indicated that they did not understand what the object was (or had rather no assumption). The analysis focused on differences between the insight and the naive condition in the P1 component (100--150 ms) as an index of lower-level visual perception, the N1 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.

```{r exp1-table, include=TRUE, results="asis"}
# Define function to print ANOVA-style table
create_table <- function(models, stub_anova, stub_contrasts, caption, note) {
  anov <- map(models, function(model) {
    data.frame(
      "f" = format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2),
      "df" = paste0("(", model$anova$NumDF, ", ", format(round(model$anova$DenDF, 1), trim = TRUE, nsmall = 1), ")"),
      "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)
    ) %>%
      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
      set_rownames(c(stub_anova))
  })
  anov_print <- anov %>%
    map(unite, col = fdf, f, df, sep = " ") %>%
    map(add_row, fdf = "\\textit{F} (\\textit{df})", p = "\\textit{p}", .before = 1) %>%
    bind_cols() %>%
    set_rownames(c("\\textit{Fixed effects}", stub_anova))
  anov %<>% 
    bind_cols() %>% 
    set_colnames(paste(rep(names(models), each = length(names(models))), c("f", "df", "p"), sep = "_"))
  conts <- map(models, function(model) {
    data.frame(
      "est" = format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2),
      "ci" = paste0(
        "[", format(round(model$contrasts$lower.CL, 2), trim = TRUE, nsmall = 2), ", ",
        format(round(model$contrasts$upper.CL, 2), trim = TRUE, nsmall = 2), "]"
      ),
      "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)
    ) %>%
      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
      set_rownames(stub_contrasts)
  })
  conts_print <- conts %>%
    map(unite, col = estci, est, ci, sep = " ") %>%
    map(add_row, estci = "Est. [95% CI]", p = "\\textit{p}", .before = 1) %>%
    bind_cols() %>%
    set_rownames(c("\\textit{Insight $-$  naive}", stub_contrasts))
  conts %<>% 
    bind_cols() %>% 
    set_colnames(paste(rep(names(models), each = length(names(models))), c("est", "ci", "p"), sep = "_"))
  cnames <- c("\\textit{Fixed effects}", as.character(anov_print[1, ]))
  list(anov_print[2:nrow(anov_print), ], conts_print) %>%
    map(set_colnames, paste0("V", 1:ncol(anov_print))) %>%
    apa_table(
      col.names = cnames, col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N1}" = 4:5, "\\textbf{N400}" = 6:7),
      midrules = nrow(anov_print), font_size = "footnotesize", align = "lcccccc", escape = FALSE,
      caption = caption, note = note
    ) %>% cat()
  return(list("anov" = anov, "conts" = conts))
}

# Create table of models for Experiment 1
table_exp1 <- create_table(
  models = models_exp1,
  stub_anova = c("Part", "Insight", "Pt. × ins."),
  stub_contrasts = c("Part I", "Part II", "Part III"),
  caption = "Results of linear mixed-effects regression models for Experiment 1",
  note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval."
)
```

Averaged across conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all *F*s \> `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (Table \@ref(tab:exp1-table)). In addition, N400 amplitudes differed between the insight and the naive conditions averaged across the three parts of the experiment, *F*`r table_exp1$anov["Insight", "N400_df"]` = `r table_exp1$anov["Insight", "N400_f"]`, *p* = `r table_exp1$anov["Insight", "N400_p"]`. Crucially, the part × insight interaction was significant in the N1 component, *F*`r table_exp1$anov["Pt. × ins.", "N1_df"]` = `r table_exp1$anov["Pt. × ins.", "N1_f"]`, *p* = `r table_exp1$anov["Pt. × ins.", "N1_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt. × ins.", "N400_df"]` = `r table_exp1$anov["Pt. × ins.", "N400_f"]`, *p* `r table_exp1$anov["Pt. × ins.", "N400_p"]`, while also being marginally significant in the P1 component, *F*`r table_exp1$anov["Pt. × ins.", "P1_df"]` = `r table_exp1$anov["Pt. × ins.", "P1_f"]`, *p* = `r table_exp1$anov["Pt. × ins.", "P1_p"]`. To answer our main research question, we decomposed these interactions into the differences between the insight and the naive condition within the three different parts of the experiment.

### Effects of Insight in Part I

In Part I, when objects were unfamiliar to the participant and presented without verbal descriptions, no differences emerged between the insight and the naive condition in the P1, N1, or N400 component, all *p*s \> `r table_exp1$conts["Part I", "N400_p"]` (Table \@ref(tab:exp1-table), Figure \@ref(fig:exp1-plot)B & C). On the one hand, this was to be expected given that the critical presentation of the objects with the descriptions (leading to semantic insight vs. naive perception) had not yet taken place. On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of insight in Parts II and III cannot be explained solely by visual differences between the objects in the two conditions. Although the presentation of a matching or non-matching description for each object was counterbalanced across participants, the fact that different numbers of objects were excluded from the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor. If they did, however, one would expect to detect these differences even before any descriptions were presented, which we now know was not the case.

### Effects of Insight in Part II

In Part II, half of the unfamiliar objects were presented with a matching verbal description (in the insight condition) and the other half were presented with a non-matching verbal description (in the naive condition). In response to objects for which participants experienced semantic insight, the amplitude of the N1 component was significantly enlarged (i.e. more negative), *b* = `r table_exp1$conts["Part II", "N1_est"]` µV, *p* = `r table_exp1$conts["Part II", "N1_p"]`, and the amplitude of the N400 component was significantly reduced (i.e. less negative), *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`, compared to objects which participants viewed naively. As in Part I, there were no reliable differences in the P1 component, *p* = `r table_exp1$conts["Part II", "P1_p"]`.

### Effects of Insight in Part III

In Part III, the unfamiliar objects were presented for a third time, again without the verbal descriptions (as in Part I), to test whether the occurrence of semantic insight had any lasting effects on the processing of the objects. As in Part II, the N400 component remained significantly reduced in response to objects for which semantic insight had occurred, *b* = `r table_exp1$conts["Part III", "N400_est"]` µV, *p* `r table_exp1$conts["Part III", "N400_p"]`, whereas the early effect of insight in the N1 component did not reoccur, *p* = `r table_exp1$conts["Part III", "N1_p"]`. Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e. more positive) in response to objects for which semantic insight had occurred, *b* = `r table_exp1$conts["Part III", "P1_est"]` µV, *p* = `r table_exp1$conts["Part III", "P1_p"]`.

## Discussion

In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they gained semantic insight into what kind of object they were seeing. To induce insight, half of the objects in Part II were preceded by a matching verbal description of the object's typical function or use, whereas the other half were preceded by a non-matching description (as a naive baseline condition).

Participants' experience of semantic insight in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001]. The fact that this effect did not reoccur in Part III, when the objects were presented once more without descriptions, suggests it being a marker of semantic insight altering object processing online. In contrast, we also observed a modulation of the N400 component, which was reduced for objects when semantic insight was occurring (in Part II) and remained so when the same objects were presented repeatedly (in Part III). The N400 is most often discussed as an index of increased demands for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018]. Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had understood what kind of object they were viewing. Finally, semantic insight was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which semantic insight had occurred (in Part II). This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images [@samaha2018], may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had occurred.

Because of the exploratory nature of the present study and the novelty of the ERP effects observed in Experiment 1, we ran a replication study to assess the robustness of these findings in another samples of participants.

# Experiment 2

## Methods

```{r exp2-preparation}
# Read behavioral data for Experiment 2
data_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)

# Check average number of stimuli per condition
(stims_exp2 <- map(data_exp2, function(x) {
  table(x$condition) / 3
}) %>% bind_rows() %>% colMeans())
```

```{python exp2-preprocessing}
# List raw EEG filenames
fnames_exp2 = sorted(glob.glob("data/exp2/EEG/*.vhdr"))

# Import behavioral data from R
metadata_exp2 = r.data_exp2

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists("analysis/export/exp2-epo.fif"):
    # Read preprocessed data from file
    epochs_exp2 = mne.read_epochs("analysis/export/exp2-epo.fif", preload=True)
else:
    # Preprocess EEG data for Experiment 2
    epochs_exp2 = [
        preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
        for fname, meta in zip(fnames_exp2, metadata_exp2)
    ]
    # Combine epochs into a single data set
    epochs_exp2 = mne.concatenate_epochs(epochs_exp2)
    # Backup epochs to the export folder
    epochs_exp2.save("analysis/export/exp2-epo.fif")

# # Get indices of bad epochs despite ICA
# rej_exp2 = epochs_exp2.drop_log
# rej_exp2[:] = [item for item in rej_exp2 if item != ['IGNORED']]
# rej_exp2 = [i for i in range(len(rej_exp2)) if rej_exp2[i] != []]

# Compute grand averages for Experiment 2
evokeds_exp2, evokeds_dat_exp2 = compute_evokeds(epochs=epochs_exp2)
```

```{r exp2-analysis}
# Re-import behavioral data and re-factorize some columns
data_exp2 <- py$epochs_exp2$metadata %>% mutate(
  part = factor(part, levels = c("I", "II", "III")),
  condition = factor(condition, levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")),
  participant = factor(participant),
  item = factor(item)
)

# Check number of rejected epochs
rejected_exp2 <- data_exp2 %>%
  group_by(participant) %>%
  tally() %>%
  mutate(n = 360 - n) %>%
  pull(n)
mean(rejected_exp2)    # Mean
median(rejected_exp2)  # Median
range(rejected_exp2)   # Range

# Check if single-trial ERPs were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp2-erps.RDS")) {
  # Read data from file
  data_exp2 <- readRDS("analysis/export/exp2-erps.RDS")
} else {
  # Import epochs from Python, converting Volts to Microvolts
  epochs_exp2 <- py$epochs_exp2$get_data()
  # Compute single-trial ERPs for Experiment 2
  data_exp2 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp2, els = els) %>%
    set_names(comps$name) %>%
    cbind(data_exp2, .) %T>%
    saveRDS("analysis/export/exp2-erps.RDS")
}

# Remove the Python object to free up memory
py_run_string("del epochs_exp2")
import("gc")$collect()

# Remove any trials excluded from conditions
data_exp2 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()

# Contrast coding for condition (insight-naive) and part (2-1, 3-1)
contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp2-stats.RDS")) {
  # Read models from file
  models_exp2 <- readRDS("analysis/export/exp2-stats.RDS")
} else {
  # Compute LMMs for Experiment 2
  models_exp2 <- map(
    comps$name,
    compute_models,
    formula = form_exp12,
    data = data_exp2,
    control = ctrl_params,
    specs = specs_exp12
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/exp2-stats.RDS")
}
```

### Participants

Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29) who had not participated in Experiment 1. They had no history of psychological disorder or treatment, were right-handed and reported normal or corrected-to-normal vision. They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.

### Materials, Procedure, and Analysis

All materials, procedures, and methods for EEG recording and statistical analysis were identical to Experiment 1. An average of `r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)` of rare objects per participant was classified as known in Part I and excluded from all further analyses. Based on participants' responses in Part II, an average of `r format(round(stims_exp2["Insight"], 1), nsmall = 1)` objects were assigned to the insight condition (`r scales::percent(stims_exp2["Insight"]/60, accuracy = 0.1)` of objects presented with a matching description) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (`r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with a non-matching description). Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials (`r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`) per participant (range `r min(rejected_exp2)` to `r max(rejected_exp2)`).

## Results

```{r exp2-table, include=TRUE, results="asis"}
# Create table of models for Experiment 2
table_exp2 <- create_table(
  models_exp2,
  stub_anova = c("Part", "Insight", "Pt. × ins."),
  stub_contrasts = c("Part I", "Part II", "Part III"),
  caption = "Results of linear mixed-effects regression models for Experiment 2",
  note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval."
)
```

As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all *F*s \> `r table_exp2$anov["Part", "N1_f"]`, all *p*s `r table_exp2$anov["Part", "N1_p"]` (Table \@ref(tab:exp2-table)). Also as in Experiment 1, N400 amplitudes differed between the insight and the naive condition averaged across parts, *F*`r table_exp2$anov["Insight", "N400_df"]` = `r table_exp2$anov["Insight", "N400_f"]`, *p* `r table_exp2$anov["Insight", "N400_p"]`. The part × insight interaction was significant in the P1 component, *F*`r table_exp2$anov["Pt. × ins.", "P1_df"]` = `r table_exp2$anov["Pt. × ins.", "P1_f"]`, *p* = `r table_exp2$anov["Pt. × ins.", "P1_p"]`, and in the N400 component, *F*`r table_exp2$anov["Pt. × ins.", "N400_df"]` = `r table_exp2$anov["Pt. × ins.", "N400_f"]`, *p* `r table_exp2$anov["Pt. × ins.", "N400_p"]`, but not in the N1 component, *F*`r table_exp2$anov["Pt. × ins.", "N1_df"]` = `r table_exp2$anov["Pt. × ins.", "N1_f"]`, *p* = `r table_exp2$anov["Pt. × ins.", "N1_p"]`.

(ref:figure-2-caption) Results of Experiment 2. *(A)* Bar plots and *(B)* ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III. In a direct replication of Experiment 1, the effect of semantic insight on the N400 component in Part II and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II and on the N400 component in Part III remained only marginally significant. Error bars show the standard error of the mean. Ampl. = amplitude.\newline\**p* \< .05. \*\*\**p* \< .001.

```{r exp2-plot, include=TRUE, fig.height=8, fig.cap = "(ref:figure-2-caption)"}
# Manually extract significance levels from contrasts for plotting
stars_exp2 <- list(
  P1 = c(I = NA, II = NA, III = "*"),
  N1 = c(I = NA, II = NA, III = NA),
  N400 = c(I = NA, II = "***", III = "*")
)

# Import grand averaged evoked potentials from Python
evokeds_exp2 <- py$evokeds_dat_exp2

# Create plot for Experiment 2
plot_grid(
  plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
  plot_erps(comps = comps, evokeds = evokeds_exp2, montage = montage, stars = stars_exp2),
  plot_legends(),
  nrow = 3, rel_heights = c(2, 5, 1), labels = c("A", "B", ""), label_fontfamily = "Helvetica"
)
```

### Effects of Insight in Part I

As in Experiment 1, no differences between objects in the insight and the naive condition emerged in the P1, N1, or N400 component, all *p*s \> `r table_exp2$conts["Part I", "P1_p"]` (Table \@ref(tab:exp2-table), Figure \@ref(fig:exp2-plot)).

### Effects of Insight in Part II

As in Experiment 1, the occurrence of semantic insight in Part II due to the presentation of objects with matching (vs. non-matching) verbal descriptions was associated with a (marginally) significant enhancement of the N1 component, *b* = `r table_exp2$conts["Part II", "N1_est"]` µV, *p* = `r table_exp2$conts["Part II", "N1_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`.

### Effects of Insight in Part III

As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without verbal descriptions as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantic insight had occurred, *b* = `r table_exp2$conts["Part III", "P1_est"]` µV, *p* = `r table_exp2$conts["Part III", "P1_p"]`. Also, N400 amplitudes in response to these objects remained significantly reduced, *b* = `r table_exp2$conts["Part III", "N400_est"]` µV, *p* = `r table_exp2$conts["Part III", "N400_p"]`.

### Joint Analysis of Experiments 1 and 2

In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2. This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2. Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e. subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; @schad2020]. This factor and its possible interactions with part, insight, and part × insight were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes. They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2. Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit [@matuschek2017; @R-buildmer].

```{r joint-analysis}
# Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
data_joint <- data_exp2 %>%
  mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
  bind_rows(data_exp1, ., .id = "experiment") %>%
  mutate(experiment = as_factor(experiment))

# Contrast coding for experiment (2-1), condition (insight-naive), and part (2-1, 3-1)
t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
contrasts(data_joint$experiment) <- MASS::ginv(contrasts_experiment)
contrasts(data_joint$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_joint$part) <- MASS::ginv(contrasts_part)

# New formula for LMMs
form_joint <- buildmer::tabulate.formula(
  ~ part * condition * experiment + (part * condition | participant) + (part * condition * experiment | item)
) %>% mutate(block = replace(block, is.na(grouping), "fixed"))

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/joint-stats.RDS")) {
  # Read models from file
  models_joint <- readRDS("analysis/export/joint-stats.RDS")
} else {
  # Compute LMMs for Experiments 1 and 2 combined
  models_joint <- map(
    comps$name,
    compute_models,
    formula = form_joint,
    data = data_joint,
    control = ctrl_params,
    specs = specs_exp12
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/joint-stats.RDS")
}
```

```{r joint-table, include=TRUE, results="asis"}
# Create table of models for Experiments 1 and 2 combined
table_joint <- create_table(
  models_joint,
  stub_anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.", "Ins. × exp.", "Pt. × ins. × exp."),
  stub_contrasts = c("Part I", "Part II", "Part III"),
  caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
  note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval."
)
```

As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of insight in the N400, *F*`r table_joint$anov["Insight", "N400_df"]` = `r table_joint$anov["Insight", "N400_f"]`, *p* `r table_joint$anov["Insight", "N400_p"]`. Furthermore, the part × insight interaction was now observed reliably in all three components, all *F*s \> `r table_joint$anov["Pt. × ins.", "P1_f"]`, all *p*s \< `r table_joint$anov["Pt. × ins.", "P1_p"]`. While there was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, the absence of any significant interactions of experiment with part or insight indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.

Based on the part × insight interaction, we again computed follow-up comparisons between the insight and the naive condition within each part, now collapsed across the data from both experiments. This confirmed the absence of any reliable differences between the two conditions in Part I, all *p*s \> `r table_joint$conts["Part I", "N400_p"]`, the significant enhancement of the N1 component in Part II, while insight was occurring, *b* = `r table_joint$conts["Part II", "N1_est"]` µV, *p* = `r table_joint$conts["Part II", "N1_p"]`, the significant reduction of the N400 component in Part II, while insight was occurring, *b* = `r table_joint$conts["Part II", "N400_est"]` µV, *p* `r table_joint$conts["Part II", "N400_p"]`, and Part III, after insight had occurred, *b* = `r table_joint$conts["Part III", "N400_est"]` µV, *p* = `r table_joint$conts["Part III", "N400_p"]`, as well as the significant enhancement of the P1 component in Part III, after insight had occurred, *b* = `r table_joint$conts["Part III", "P1_est"]` µV, *p* = `r table_joint$conts["Part III", "P1_p"]`.

### Control Analysis

```{r control-analysis}
# Calculate average number of objects per condition in Experiments 1 and 2
stims_joint <- (stims_exp1 + stims_exp2) / 2

# Re-load saved ERPs from Experiments 1 and 2
data_joint_control <- bind_rows(
  readRDS("analysis/export/exp1-erps.RDS"),
  readRDS("analysis/export/exp2-erps.RDS") %>% mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))),
  .id = "experiment"
) %>% mutate(experiment = as_factor(experiment))

# # Keep all three conditions
# data_joint_control %<>% filter(condition %in% c("Insight", "Naive", "Excl_insight")) %>% droplevels()
# contrasts_condition <- t(cbind(c("Insight" = 1, "Naive" = -1, "Excl_insight" = 0),
#                                c("Insight" = 1, "Naive" = 0, "Excl_insight" = -1)))
# contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
# model_joint_control_N1 <- buildmer::buildmer(
#   N1 ~ part * condition * experiment + (part * condition | participant) + (part * condition * experiment | item),
#   REML = FALSE,
#   control = ctrl_params,
#   buildmerControl = buildmer::buildmerControl(
#     data = data_joint_control,
#     direction = c("order", "backward"),
#     elim = function(logp) exp(logp) >= .20,
#     calc.anova = TRUE,
#     ddf = "Satterthwaite"
#   )
# )
# emmeans::emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
# emmeans::emmeans(model_joint_control_N1@model, pairwise ~ condition | part, infer = TRUE)$contrasts

# This time, we keep the unsuccessful ahas as the control condition
data_joint_control %<>% filter(condition %in% c("Insight", "Excl_insight")) %>% droplevels()

# Contrast coding for condition (insight-no_insight) and part (2-1, 3-1)
contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_joint_control$part) <- MASS::ginv(contrasts_part)

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/joint-control-stats.RDS")) {
  # Read models from file
  models_joint_control <- readRDS("analysis/export/joint-control-stats.RDS")
} else {
  # Re-compute LMMs for Experiments 1 and 2 combined
  models_joint_control <- map(
    comps$name,
    compute_models,
    formula = form_joint,
    data = data_joint_control,
    control = ctrl_params,
    specs = specs_exp12
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/joint-control-stats.RDS")
}

# Create table but don't print
table_joint_control <- create_table(
  models = models_joint_control,
  stub_anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.", "Ins. × exp.", "Pt. × ins. × exp."),
  stub_contrasts = c("Part I", "Part II", "Part III"),
  caption = "Results of linear mixed-effects regression models with a different baseline",
  note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval."
)
```

One may raise concerns whether the modulation of the N1 component in Part II genuinely reflects semantic insight for objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition. Remember that these objects were preceded by a non-matching description which was picked so that it could not be related to the object's visual features and their configuration. Thus, the modulation of the ERP components in Part II may reflect a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of morsing messages. To preclude this alternative explanation, we repeated the analysis above using a different baseline against which the objects in the insight condition were contrasted. Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the insight condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing. Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_insight"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Insight"]/60, accuracy = 0.1)` of objects which did indeed lead to semantic insight (note that the remaining objects were excluded as not being unfamiliar in the beginning of the experiment). Just as above, this control analysis revealed a robust enhancement of the N1 component associated with semantic insight in Part II, *b* = `r table_joint_control$conts["Part II", "N1_est"]` µV, *p* `r table_joint_control$conts["Part II", "N1_p"]`. Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading descriptions or compared to objects presented with accurate descriptions on which participants failed to capitalize. Note that the reduction of the N400 component also remained robust in this control analysis, *b* = `r table_joint_control$conts["Part II", "N400_est"]` µV, *p* `r table_joint_control$conts["Part II", "N400_p"]`.

## Discussion

Experiment 2, which was a direct replication of Experiment 1, confirmed the impact of gaining semantic insight into previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N1), and semantic processing (N400). While the enhancement of the N1 component, being more negative in response to objects for which participants were experiencing semantic insight, was present only during the critical presentation of the objects with their verbal descriptions (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after insight had taken place and the objects were presented again in Part III. This indicates a modulation of different stages of visual object perception through semantic knowledge, while and after an understanding of the object has been obtained. Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantic insight may reflect lowered semantic processing demands compared to unfamiliar objects which participants did not yet understand.

```{r exp3-preparation, eval=run_exp3}
# Read behavioral data for Experiment 3
data_exp3 <- list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)

# Check average number of stimuli per condition
(stims_exp3 <- map(data_exp3, function(x) {
  x %<>% filter(part != "IV")
  table(x$condition) / 3
}) %>% bind_rows() %>% colMeans())
```

```{python exp3-preprocessing, eval=run_exp3}
# List raw EEG filenames
fnames_exp3 = sorted(glob.glob("data/exp3/EEG/*.vhdr"))

# Import behavioral data from R
metadata_exp3 = r.data_exp3

# Update stimulus triggers
preproc_params["event_id"] = {
    "match/upright": 241,
    "match/inverted": 242,
    "mismatch/upright": 243,
    "mismatch/inverted": 244,
}

# Check if preprocessing was done already (delete the file to re-run)
if os.path.exists("analysis/export/exp3-epo.fif"):
    # Read preprocessed data from file
    epochs_exp3 = mne.read_epochs("analysis/export/exp3-epo.fif", preload=True)
else:
    # Preprocess EEG data for Experiment 3
    epochs_exp3 = [
        preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
        for fname, meta in zip(fnames_exp3, metadata_exp3)
    ]
    # Combine epochs into a single data set
    epochs_exp3 = mne.concatenate_epochs(epochs_exp3)
    # Backup epochs and evokeds to the export folder
    epochs_exp3.save("analysis/export/exp3-epo.fif")

# # Get indices of bad epochs despite ICA
# rej_exp3 = epochs_exp3.drop_log
# rej_exp3[:] = [item for item in rej_exp3 if item != ['IGNORED']]
# rej_exp3 = [i for i in range(len(rej_exp3)) if rej_exp3[i] != []]
```

```{r exp3-analysis, eval=run_exp3}
# Re-import behavioral data and re-factorize some columns
data_exp3 <- py$epochs_exp3$metadata %>% mutate(
  part = factor(part, levels = c("I", "II", "III", "IV")),
  position = factor(position, levels = c("Inverted", "Upright")),
  condition = factor(condition, levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")),
  participant = factor(participant), item = factor(item)
)

# Check if ERPs were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp3-erps.RDS")) {
  # Read ERPs from file
  data_exp3 <- readRDS("analysis/export/exp3-erps.RDS")
} else {
  # Import epochs from Python, converting Volts to Microvolts (takes a while)
  epochs_exp3 <- py$epochs_exp3$get_data()
  # Compute single-trial ERPs for Experiment 3
  data_exp3 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp3, els = els) %>%
    set_names(comps$name) %>%
    cbind(data_exp3, .) %T>%
    saveRDS("analysis/export/exp3-erps.RDS")
}

# Remove any trials from part IV
data_exp3 %<>% filter(part != "IV") %>% droplevels()

# Check number of rejected epochs
rejected_exp3 <- data_exp3 %>%
  group_by(participant) %>%
  tally() %>%
  mutate(n = 672 - n) %>%
  pull(n)
mean(rejected_exp3)
median(rejected_exp3)
range(rejected_exp3)

# Remove any trials excluded from conditions
data_exp3 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()

# Contrast coding for position (inverted-updright), condition (insight-naive), and part (2-1, 3-1)
t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
contrasts(data_exp3$position) <- MASS::ginv(contrasts_position)
contrasts(data_exp3$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp3$part) <- MASS::ginv(contrasts_part)

# New formula for LMMs
form_exp3 <- buildmer::tabulate.formula(
  ~ part * condition * position + (part * condition * position | participant) + (part * condition * position | item)
) %>% mutate(block = replace(block, is.na(grouping), "fixed"))

# New follow-up contrasts
specs_exp3 <- pairwise ~ condition | position * part

# Check if models were computed already (delete the file to re-run)
if (file.exists("analysis/export/exp3-stats.RDS")) {
  # Read models from file
  models_exp3 <- readRDS("analysis/export/exp3-stats.RDS")
} else {
  # Compute LMMs for Experiment 3
  models_exp3 <- map(
    comps$name,
    compute_models,
    formula = form_exp3,
    data = data_exp3,
    control = ctrl_params,
    specs = specs_exp3
  ) %>% set_names(comps$name) %T>%
    saveRDS("analysis/export/exp3-stats.RDS")
}
```

```{r exp3-table, include=TRUE, results="asis", eval=run_exp3}
# Create table of models for Experiment 3
table_exp3 <- create_table(
  models_exp3,
  stub_anova = c("Part", "Insight", "Position", "Pt. × ins.", "Pt. × pos.", "Ins. × pos.", "Pt. × ins. × pos."),
  stub_contrasts = c(
    "Part I, inverted", "Part I, upright", "Part II, inverted",
    "Part II, upright", "Part III, inverted", "Part III, upright"
  ),
  caption = "Results of linear mixed-effects regression models for Experiment 3",
  note = "Pt. = part, ins. = insight, pos. = position, est. = estimate, CI = confidence interval."
)
```

# General Discussion

General discussion section goes here.

\newpage

# References

\setlength{\parindent}{-0.5in}

### 2020-10-15 analysis/manuscript.tex
initialize docker

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,11pt,floatsintext]{apa7}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Alexander Enge1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Semantic Knowledge and Unfamiliar Objects}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\doublespacing}
\AtBeginEnvironment{lltable}{\doublespacing}
\AtBeginEnvironment{tablenotes}{\doublespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1,scriptsize}}
\raggedbottom
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{Event-Related Potentials of the Semantically\\
Informed Perception of Unfamiliar Objects}
\author{Alexander Enge\textsuperscript{1}}
\date{}

\authornote{

Alexander Enge, Department of Psychology, Humboldt-Universität zu Berlin, Germany, \url{https://orcid.org/0000-0003-0100-2297}, student no. 581331.

The thesis was handed December 18, 2020 and has been supervised by Prof.~Dr.~Rasha Abdel Rahman, Humboldt-Universität zu Berlin, Germany, and Prof.~Dr.~Franziska Süß, Fachhochschule des Mittelstands, Bamberg, Germany.

Correspondence concerning this article should be addressed to Alexander Enge, Rudower Chaussee 18, 12489 Berlin. E-mail: \href{mailto:alexander.enge@hu-berlin.de}{\nolinkurl{alexander.enge@hu-berlin.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Humboldt-Universität zu Berlin}

\abstract{
Abstract goes here.
}

\begin{document}
\maketitle

How does our perception of an object change as soon as we discover what it is for? In this study, we presented participants with unfamiliar objects, preceded either by valid information about their function (leading to semantically informed perception) or by misleading information (leading to naive perception). Capitalizing on the high temporal resolution of event-related potentials (ERPs), we investigated how different stages in the processing hierarchy are modulated by this semantic understanding of objects before, during, and after it has been acquired.

\begin{itemize}
\item
  One paragraph explaining that previous research has shown that semantic knowledge modulates early stages of visual perception (e.g.~Abdel Rahman \& Sommer, 2008; Gauthier et al., 2003; Maier \& Abdel Rahman, 2019; Maier et al., 2014; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
\item
  Potentially one paragraph describing Abdel Rahman \& Sommer (2008) in more detail (participants acquiring knowledge about existing but unfamiliar objects).
\item
  One paragraph describing Samaha et al.~(2018) in more detail (participants being trained to see familiar objects in otherwise meaningless images). Possibly hypothesize a special role of insight (= the moment when understanding is acquired), although this is not directly captured by the study.
\item
  One paragraph explaining how all of these studies measured ERPs only \emph{after} an extensive learning phase, making it difficult to determine (a) how much learning is necessary for semantic knowledge to influence perception and, related to that, (b) if the modulation of early ERP components reflects genuine online effects of semantic knowledge or rather the activation of altered visual representations (Firestone \& Scholl, 2015) (?).
\item
  One paragraph on theories of top-down/language effects on visual perception (reverse hierarchy theory).
\item
  Possibly another paragraph on theories of top-down effects on visual perception (label feedback hypothesis) if it fits thematically.
\item
  Do we need to refer to the role of attention already in the introduction? If so, potentially another paragraph here. I might prefer to leave that for the discussion.
\item
  Possibly one more paragraph on why ERPs are so suitable to answer this research question, including a brief characterization of the relevant components (P1: lower-level visual perception, N1: higher-level visual perception, N400: semantic processing).
\item
  The present study: Design of the study with a focus on distinguishing between online effects and altered representations; no specific hypotheses but looking for influences of semantic knowledge on the three ERP components at three different stages (before, during, and after acquisition).
\end{itemize}

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment. All participants were right-handed according to the Edinburgh inventory (Oldfield, 1971) and reported normal or corrected-to-normal vision. They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating. All experiments subsequently reported were carried out in accordance with the Declaration of Helsinki and approved by the local ethics committee.

\hypertarget{materials-and-procedure}{%
\subsubsection{Materials and Procedure}\label{materials-and-procedure}}

Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g.~a bicycle, a toothbrush), whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g.~a galvanometer, an udu drum). The well-known objects were included as filler stimuli of no interest. A list of the unfamiliar objects can be found in Appendix A. All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz. At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.

For each unfamiliar object, a noun--verb pair was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g.~current--measuring, pottery--drumming). In the \emph{insight} condition, the presentation of each unfamiliar object was preceded by its respective description, whereas in the \emph{naive} condition, it was preceded by a non-matching description belonging to one of the other objects. In both conditions, the noun and the verb were presented one above the other in black letters on a light blue background. For each participant, half of the unfamiliar objects were presented in the insight condition (i.e.~with a matching description) and the other half were presented in the naive condition (i.e.~with a non-matching description). All participants saw each unfamiliar object in only one of the two conditions and the assignment of objects to conditions was counterbalanced across participants. The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).

Each experimental session consisted of three parts (Figure \ref{fig:exp1-plot}A). In Part I, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without verbal descriptions. Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s. The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects. The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) ``I know what this is or have a strong assumption,'' (b) ``I have an assumption what this is,'' (c) ``I have rather no assumption what this is,'' or (d) ``I do not know what this is and have no assumption.'' Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively. The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants. Because we were interested in the acquisition of semantic knowledge about unfamiliar objects only, all objects for which the participant indicated knowing the object in Part I were excluded from further analysis (6.3\% of rare objects per participant).

\begin{figure}

{\centering \includegraphics{manuscript_files/figure-latex/exp1-plot-1}

}

\caption{Procedure and results of Experiment 1. \emph{(A)} In Part I, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing. In Part II, half of the objects were preceded by a matching description (in purple color for illustration), leading to semantic insight, and the other half with a non-matching description (in petrol color for illustration), leading to naive perception. In Part III, the same objects were presented again without the descriptions. \emph{(B)} Bar plots and \emph{(C)} ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III. Insight was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III. Error bars show the standard error of the mean. Ampl. = amplitude.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.}\label{fig:exp1-plot}
\end{figure}

In Part II, only the 120 unfamiliar objects were presented for a second time, now preceded either by a matching verbal description (in the insight condition) or by a non-matching verbal description (in the naive condition). Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the verbal description for 2.5 s. Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s. The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g.~medical devices, musical instruments). To make sure that insight did (did not) occur in the insight (naive) condition, we excluded any objects from the insight condition if participants indicated not knowing the object or having rather no assumption (despite reading the matching description) and any objects from the naive condition if participants indicated knowing the object or having an assumption (despite reading the non-matching description). This resulted in an average of 27.0 objects (44.9\%) per participant remaining in the insight condition and an average of 48.8 objects (81.2\%) per participant remaining in the naive condition.

In Part III, the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e.~without the verbal descriptions. Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with descriptions), participants took a self-timed break and continued with the same block of 30 objects in Part III (without descriptions) before moving on to the next block consisting of 30 different objects. They continued like this until all four blocks were completed in both Parts II and III. In total, the experiment consisted of 480 trials (120 familiar objects in Part I and 120 unfamiliar objects in Parts I, II, and III) and took participants approximately 35 minutes to complete.

\hypertarget{eeg-recording-and-preprocessing}{%
\subsubsection{EEG Recording and Preprocessing}\label{eeg-recording-and-preprocessing}}

The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system (American Electroencephalographic Society, 1991) and referenced online to an external electrode placed on the left mastoid (M1). Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively. During the recording, electrode impedance was kept below 5 kΩ. An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1,000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.

Offline, the data were preprocessed using the MNE software (Version 0.21.0; Gramfort et al., 2013) in Python (Version 3.7.7; van Rossum \& Drake, 2009). First, all scalp electrodes were re-referenced to the common average. Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA). The first 15 components were extracted using the FastICA algorithm (Hyvärinen, 1999) after temporarily low-pass filtering the data at 1 Hz. Those components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the \emph{find\_bads\_eog} function. After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied. Next, the continuous EEG was epoched into segments of 2,000 ms, starting 500 ms before the onset of the visual presentation of each unfamiliar object. The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset. Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis. This led to the exclusion of an average of 2.4 trials (0.7\%) per participant (range 0 to 24). Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N1 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.

\hypertarget{statistical-analysis}{%
\subsubsection{Statistical Analysis}\label{statistical-analysis}}

The event-related potentials were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018). For the purpose of the present study, these models have two desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages. First, they can account simultaneously for the non-independence of data points coming from the same participant or from the same item, whereas the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012). Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is based on participants' own responses rather than on the experimental manipulation (e.g.~Fröber et al., 2017).

Three separate models were computed predicting P1, N1, and N400 mean amplitudes, respectively. All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.~subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.~subtracting the naive from the insight condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition. For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to Schad et al. (2020). To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects (Barr et al., 2013). We then performed a model selection algorithm as proposed by Matuschek et al. (2017) for increasing statistical power and avoiding overparameterization: Iteratively, each random effects was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test. Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model. All models were calculated in R (Version 4.0.2; R Core Team, 2020) using the lme4 package (Version 1.1.23; Bates et al., 2015). The optimizer function \emph{bobyqa} with 2·10\textsuperscript{5} iterations was used for maximum likelihood estimation. The model selection algorithm via likelihood ratio tests was performed using the buildmer package (Version 1.7.1; Voeten, 2020). Finally, to answer our research question of whether or not semantic insight had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the insight against the naive condition within Parts I, II, and III. Reported \emph{p} values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's methods as implemented in the lmerTest package (Kuznetsova et al., 2017).

The materials and code for the present experiments can be accessed via the Open Science Framework (\href{https://osf.io/myprojects/}{https://osf.io/\ldots/}).

\hypertarget{results}{%
\subsection{Results}\label{results}}

Single-trial ERPs were analyzed in response to unfamiliar objects before (Part I), while (Part II), and after (Part III) participants gained semantic insight into the function or use of the objects. Half of the objects were preceded by a matching description, fostering semantic insight to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object. To make sure participants did indeed experience insight or naive perception, the analysis was constrained by participants' behavioral responses in Part II: Objects presented with a matching description were assigned to the insight condition only if the participant indicated that they understood what the object was (or had an assumption), whereas objects presented with a non-matching description were assigned to the naive condition only if the participant indicated that they did not understand what the object was (or had rather no assumption). The analysis focused on differences between the insight and the naive condition in the P1 component (100--150 ms) as an index of lower-level visual perception, the N1 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp1-table}Results of linear mixed-effects regression models for Experiment 1}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 10.89 (2, 24.5) & < .001 & 14.18 (2, 24.9) & < .001 & 32.85 (2, 25.6) & < .001\\
Insight & 0.60 (1, 5343.5) & .438 & 0.30 (1, 24.2) & .586 & 13.00 (1, 24.4) & .001\\
Pt. × ins. & 2.30 (2, 4605.1) & .100 & 4.84 (2, 4878.2) & .008 & 10.91 (2, 5120.9) & < .001\\
\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Part I & -0.03 [-0.53, 0.47] & .913 & -0.12 [-0.68, 0.44] & .665 & -0.20 [-0.65, 0.26] & .400\\
Part II & -0.18 [-0.68, 0.32] & .490 & -0.64 [-1.20, -0.08] & .026 & 0.93 [0.48, 1.39] & < .001\\
Part III & 0.55 [0.05, 1.05] & .031 & 0.43 [-0.14, 0.99] & .136 & 1.00 [0.54, 1.46] & < .001\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Averaged across conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.89, all \emph{p}s \textless{} .001 (Table \ref{tab:exp1-table}). In addition, N400 amplitudes differed between the insight and the naive conditions averaged across the three parts of the experiment, \emph{F}(1, 24.4) = 13.00, \emph{p} = .001. Crucially, the part × insight interaction was significant in the N1 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4605.1) = 2.30, \emph{p} = .100. To answer our main research question, we decomposed these interactions into the differences between the insight and the naive condition within the three different parts of the experiment.

\hypertarget{effects-of-insight-in-part-i}{%
\subsubsection{Effects of Insight in Part I}\label{effects-of-insight-in-part-i}}

In Part I, when objects were unfamiliar to the participant and presented without verbal descriptions, no differences emerged between the insight and the naive condition in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .400 (Table \ref{tab:exp1-table}, Figure \ref{fig:exp1-plot}B \& C). On the one hand, this was to be expected given that the critical presentation of the objects with the descriptions (leading to semantic insight vs.~naive perception) had not yet taken place. On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of insight in Parts II and III cannot be explained solely by visual differences between the objects in the two conditions. Although the presentation of a matching or non-matching description for each object was counterbalanced across participants, the fact that different numbers of objects were excluded from the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor. If they did, however, one would expect to detect these differences even before any descriptions were presented, which we now know was not the case.

\hypertarget{effects-of-insight-in-part-ii}{%
\subsubsection{Effects of Insight in Part II}\label{effects-of-insight-in-part-ii}}

In Part II, half of the unfamiliar objects were presented with a matching verbal description (in the insight condition) and the other half were presented with a non-matching verbal description (in the naive condition). In response to objects for which participants experienced semantic insight, the amplitude of the N1 component was significantly enlarged (i.e.~more negative), \emph{b} = -0.64 µV, \emph{p} = .026, and the amplitude of the N400 component was significantly reduced (i.e.~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to objects which participants viewed naively. As in Part I, there were no reliable differences in the P1 component, \emph{p} = .490.

\hypertarget{effects-of-insight-in-part-iii}{%
\subsubsection{Effects of Insight in Part III}\label{effects-of-insight-in-part-iii}}

In Part III, the unfamiliar objects were presented for a third time, again without the verbal descriptions (as in Part I), to test whether the occurrence of semantic insight had any lasting effects on the processing of the objects. As in Part II, the N400 component remained significantly reduced in response to objects for which semantic insight had occurred, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the early effect of insight in the N1 component did not reoccur, \emph{p} = .136. Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e.~more positive) in response to objects for which semantic insight had occurred, \emph{b} = 0.55 µV, \emph{p} = .031.

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they gained semantic insight into what kind of object they were seeing. To induce insight, half of the objects in Part II were preceded by a matching verbal description of the object's typical function or use, whereas the other half were preceded by a non-matching description (as a naive baseline condition).

Participants' experience of semantic insight in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing (Rossion \& Jacques, 2011; Tanaka \& Curran, 2001). The fact that this effect did not reoccur in Part III, when the objects were presented once more without descriptions, suggests it being a marker of semantic insight altering object processing online. In contrast, we also observed a modulation of the N400 component, which was reduced for objects when semantic insight was occurring (in Part II) and remained so when the same objects were presented repeatedly (in Part III). The N400 is most often discussed as an index of increased demands for semantic processing or integration (Kutas \& Federmeier, 2011; Lau et al., 2008; Rabovsky et al., 2018). Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had understood what kind of object they were viewing. Finally, semantic insight was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which semantic insight had occurred (in Part II). This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images (Samaha et al., 2018), may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had occurred.

Because of the exploratory nature of the present study and the novelty of the ERP effects observed in Experiment 1, we ran a replication study to assess the robustness of these findings in another samples of participants.

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

\hypertarget{methods-1}{%
\subsection{Methods}\label{methods-1}}

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}

Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29) who had not participated in Experiment 1. They had no history of psychological disorder or treatment, were right-handed and reported normal or corrected-to-normal vision. They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.

\hypertarget{materials-procedure-and-analysis}{%
\subsubsection{Materials, Procedure, and Analysis}\label{materials-procedure-and-analysis}}

All materials, procedures, and methods for EEG recording and statistical analysis were identical to Experiment 1. An average of 5.8\% of rare objects per participant was classified as known in Part I and excluded from all further analyses. Based on participants' responses in Part II, an average of 26.4 objects were assigned to the insight condition (44.0\% of objects presented with a matching description) and an average of 49.2 objects were assigned to the naive condition (82.0\% of objects presented with a non-matching description). Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials (3.0\%) per participant (range 0 to 85).

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp2-table}Results of linear mixed-effects regression models for Experiment 2}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 17.45 (2, 5267.1) & < .001 & 16.57 (2, 25.1) & < .001 & 70.12 (2, 25.2) & < .001\\
Insight & 0.02 (1, 5276.9) & .900 & 0.98 (1, 5228.5) & .322 & 19.95 (1, 5242.5) & < .001\\
Pt. × ins. & 3.60 (2, 5267.1) & .027 & 1.25 (2, 4756.5) & .287 & 7.92 (2, 4714.9) & < .001\\
\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Part I & -0.16 [-0.71, 0.40] & .582 & -0.03 [-0.53, 0.48] & .920 & 0.04 [-0.43, 0.50] & .877\\
Part II & -0.48 [-1.03, 0.08] & .094 & -0.48 [-0.99, 0.03] & .064 & 1.33 [0.87, 1.79] & < .001\\
Part III & 0.57 [0.01, 1.13] & .047 & 0.06 [-0.45, 0.57] & .818 & 0.47 [0.01, 0.93] & .047\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.57, all \emph{p}s \textless{} .001 (Table \ref{tab:exp2-table}). Also as in Experiment 1, N400 amplitudes differed between the insight and the naive condition averaged across parts, \emph{F}(1, 5242.5) = 19.95, \emph{p} \textless{} .001. The part × insight interaction was significant in the P1 component, \emph{F}(2, 5267.1) = 3.60, \emph{p} = .027, and in the N400 component, \emph{F}(2, 4714.9) = 7.92, \emph{p} \textless{} .001, but not in the N1 component, \emph{F}(2, 4756.5) = 1.25, \emph{p} = .287.

\begin{figure}

{\centering \includegraphics{manuscript_files/figure-latex/exp2-plot-1}

}

\caption{Results of Experiment 2. \emph{(A)} Bar plots and \emph{(B)} ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III. In a direct replication of Experiment 1, the effect of semantic insight on the N400 component in Part II and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II and on the N400 component in Part III remained only marginally significant. Error bars show the standard error of the mean. Ampl. = amplitude.\newline*\emph{p} \textless{} .05. ***\emph{p} \textless{} .001.}\label{fig:exp2-plot}
\end{figure}

\hypertarget{effects-of-insight-in-part-i-1}{%
\subsubsection{Effects of Insight in Part I}\label{effects-of-insight-in-part-i-1}}

As in Experiment 1, no differences between objects in the insight and the naive condition emerged in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .582 (Table \ref{tab:exp2-table}, Figure \ref{fig:exp2-plot}).

\hypertarget{effects-of-insight-in-part-ii-1}{%
\subsubsection{Effects of Insight in Part II}\label{effects-of-insight-in-part-ii-1}}

As in Experiment 1, the occurrence of semantic insight in Part II due to the presentation of objects with matching (vs.~non-matching) verbal descriptions was associated with a (marginally) significant enhancement of the N1 component, \emph{b} = -0.48 µV, \emph{p} = .064, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.

\hypertarget{effects-of-insight-in-part-iii-1}{%
\subsubsection{Effects of Insight in Part III}\label{effects-of-insight-in-part-iii-1}}

As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without verbal descriptions as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantic insight had occurred, \emph{b} = 0.57 µV, \emph{p} = .047. Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.47 µV, \emph{p} = .047.

\hypertarget{joint-analysis-of-experiments-1-and-2}{%
\subsubsection{Joint Analysis of Experiments 1 and 2}\label{joint-analysis-of-experiments-1-and-2}}

In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2. This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2. Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast (i.e.~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al., 2020). This factor and its possible interactions with part, insight, and part × insight were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes. They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2. Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit (Matuschek et al., 2017; Voeten, 2020).

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:joint-table}Results of linear mixed-effects regression models for Experiments 1 and 2 combined}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 12.38 (2, 49.0) & < .001 & 29.90 (2, 50.0) & < .001 & 95.34 (2, 50.6) & < .001\\
Insight & 0.35 (1, 10560.3) & .552 & 1.65 (1, 125.3) & .202 & 38.72 (1, 10518.8) & < .001\\
Experiment & 0.35 (1, 48.2) & .555 & 2.38 (1, 48.1) & .129 & 4.75 (1, 48.4) & .034\\
Pt. × ins. & 4.02 (2, 9042.4) & .018 & 5.60 (2, 9877.5) & .004 & 15.73 (2, 10010.1) & < .001\\
Pt. × exp. & 0.03 (2, 49.0) & .971 & 0.55 (2, 50.0) & .581 & 2.58 (2, 50.6) & .085\\
Ins. × exp. & 0.62 (1, 10536.2) & .432 & 0.04 (1, 10332.1) & .838 & 0.03 (1, 10574.9) & .865\\
Pt. × ins. × exp. & 0.03 (2, 9042.9) & .972 & 0.62 (2, 9877.8) & .537 & 2.65 (2, 10010.4) & .070\\
\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Part I & -0.07 [-0.44, 0.30] & .699 & -0.10 [-0.44, 0.24] & .568 & -0.10 [-0.41, 0.20] & .507\\
Part II & -0.22 [-0.59, 0.15] & .248 & -0.56 [-0.90, -0.21] & .002 & 1.09 [0.79, 1.39] & < .001\\
Part III & 0.49 [0.12, 0.86] & .010 & 0.25 [-0.10, 0.59] & .158 & 0.72 [0.41, 1.02] & < .001\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all \emph{F}s \textgreater{} 12.38, all \emph{p}s \textless{} .001, as was the main effect of insight in the N400, \emph{F}(1, 10518.8) = 38.72, \emph{p} \textless{} .001. Furthermore, the part × insight interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 4.02, all \emph{p}s \textless{} .018. While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.75, \emph{p} = .034, the absence of any significant interactions of experiment with part or insight indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.

Based on the part × insight interaction, we again computed follow-up comparisons between the insight and the naive condition within each part, now collapsed across the data from both experiments. This confirmed the absence of any reliable differences between the two conditions in Part I, all \emph{p}s \textgreater{} .507, the significant enhancement of the N1 component in Part II, while insight was occurring, \emph{b} = -0.56 µV, \emph{p} = .002, the significant reduction of the N400 component in Part II, while insight was occurring, \emph{b} = 1.09 µV, \emph{p} \textless{} .001, and Part III, after insight had occurred, \emph{b} = 0.72 µV, \emph{p} = \textless{} .001, as well as the significant enhancement of the P1 component in Part III, after insight had occurred, \emph{b} = 0.49 µV, \emph{p} = .010.

\hypertarget{control-analysis}{%
\subsubsection{Control Analysis}\label{control-analysis}}

One may raise concerns whether the modulation of the N1 component in Part II genuinely reflects semantic insight for objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition. Remember that these objects were preceded by a non-matching description which was picked so that it could not be related to the object's visual features and their configuration. Thus, the modulation of the ERP components in Part II may reflect a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages. To preclude this alternative explanation, we repeated the analysis above using a different baseline against which the objects in the insight condition were contrasted. Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the insight condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing. Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantic insight (note that the remaining objects were excluded as not being unfamiliar in the beginning of the experiment). Just as above, this control analysis revealed a robust enhancement of the N1 component associated with semantic insight in Part II, \emph{b} = -0.99 µV, \emph{p} \textless{} .001. Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading descriptions or compared to objects presented with accurate descriptions on which participants failed to capitalize. Note that the reduction of the N400 component also remained robust in this control analysis, \emph{b} = 1.19 µV, \emph{p} \textless{} .001.

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}

Experiment 2, which was a direct replication of Experiment 1, confirmed the impact of gaining semantic insight into previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N1), and semantic processing (N400). While the enhancement of the N1 component, being more negative in response to objects for which participants were experiencing semantic insight, was present only during the critical presentation of the objects with their verbal descriptions (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after insight had taken place and the objects were presented again in Part III. This indicates a modulation of different stages of visual object perception through semantic knowledge, while and after an understanding of the object has been obtained. Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantic insight may reflect lowered semantic processing demands compared to unfamiliar objects which participants did not yet understand.

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

General discussion section goes here.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-americanelectroencephalographicsociety1991}{}%
American Electroencephalographic Society. (1991). American Electroencephalographic Society guidelines for standard electrode position nomenclature. \emph{Journal of Clinical Neurophysiology}, \emph{8}(2), 200--202.

\leavevmode\hypertarget{ref-baayen2008}{}%
Baayen, R. H., Davidson, D. J., \& Bates, D. M. (2008). Mixed-effects modeling with crossed random effects for subjects and items. \emph{Journal of Memory and Language}, \emph{59}(4), 390--412. \url{https://doi.org/10.1016/j.jml.2007.12.005}

\leavevmode\hypertarget{ref-barr2013}{}%
Barr, D. J., Levy, R., Scheepers, C., \& Tily, H. J. (2013). Random effects structure for confirmatory hypothesis testing: Keep it maximal. \emph{Journal of Memory and Language}, \emph{68}(3), 255--278. \url{https://doi.org/10.1016/j.jml.2012.11.001}

\leavevmode\hypertarget{ref-R-lme4}{}%
Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear mixed-effects models using lme4. \emph{Journal of Statistical Software}, \emph{67}(1), 1--48. \url{https://doi.org/10.18637/jss.v067.i01}

\leavevmode\hypertarget{ref-buxfcrki2018}{}%
Bürki, A., Frossard, J., \& Renaud, O. (2018). Accounting for stimulus and participant effects in event-related potential analyses to increase the replicability of studies. \emph{Journal of Neuroscience Methods}, \emph{309}, 218--227. \url{https://doi.org/10.1016/j.jneumeth.2018.09.016}

\leavevmode\hypertarget{ref-fruxf6ber2017}{}%
Fröber, K., Stürmer, B., Frömer, R., \& Dreisbach, G. (2017). The role of affective evaluation in conflict adaptation: An LRP study. \emph{Brain and Cognition}, \emph{116}, 9--16. \url{https://doi.org/10.1016/j.bandc.2017.05.003}

\leavevmode\hypertarget{ref-fruxf6mer2018}{}%
Frömer, R., Maier, M., \& Abdel Rahman, R. (2018). Group-level EEG-processing pipeline for flexible single trial-based analyses including linear mixed models. \emph{Frontiers in Neuroscience}, \emph{12}. \url{https://doi.org/10.3389/fnins.2018.00048}

\leavevmode\hypertarget{ref-gramfort2013}{}%
Gramfort, A., Luessi, M., Larson, E., Engemann, D. A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& al. (2013). MEG and EEG data analysis with MNE-Python. \emph{Frontiers in Neuroscience}, \emph{7}. \url{https://doi.org/10.3389/fnins.2013.00267}

\leavevmode\hypertarget{ref-hyvuxe4rinen1999}{}%
Hyvärinen, A. (1999). Fast and robust fixed-point algorithms for independent component analysis. \emph{IEEE Transactions on Neural Networks}, \emph{10}(3), 626--634. \url{https://doi.org/10.1109/72.761722}

\leavevmode\hypertarget{ref-judd2012}{}%
Judd, C. M., Westfall, J., \& Kenny, D. A. (2012). Treating stimuli as a random factor in social psychology: A new and comprehensive solution to a pervasive but largely ignored problem. \emph{Journal of Personality and Social Psychology}, \emph{103}(1), 54--69. \url{https://doi.org/10.1037/a0028347}

\leavevmode\hypertarget{ref-kutas2011}{}%
Kutas, M., \& Federmeier, K. D. (2011). Thirty years and counting: Finding meaning in the N400 component of the event-related brain potential (ERP). \emph{Annual Review of Psychology}, \emph{62}, 621--647. \url{https://doi.org/10.1146/annurev.psych.093008.131123}

\leavevmode\hypertarget{ref-R-lmerTest}{}%
Kuznetsova, A., Brockhoff, P. B., \& Christensen, R. H. B. (2017). lmerTest package: Tests in linear mixed effects models. \emph{Journal of Statistical Software}, \emph{82}(13), 1--26. \url{https://doi.org/10.18637/jss.v082.i13}

\leavevmode\hypertarget{ref-lau2008}{}%
Lau, E. F., Phillips, C., \& Poeppel, D. (2008). A cortical network for semantics: (De)constructing the N400. \emph{Nature Reviews Neuroscience}, \emph{9}(12), 920--933. \url{https://doi.org/10.1038/nrn2532}

\leavevmode\hypertarget{ref-matuschek2017}{}%
Matuschek, H., Kliegl, R., Vasishth, S., Baayen, H., \& Bates, D. (2017). Balancing Type I error and power in linear mixed models. \emph{Journal of Memory and Language}, \emph{94}, 305--315. \url{https://doi.org/10.1016/j.jml.2017.01.001}

\leavevmode\hypertarget{ref-oldfield1971}{}%
Oldfield, R. C. (1971). The assessment and analysis of handedness: The Edinburgh inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}

\leavevmode\hypertarget{ref-rabovsky2018}{}%
Rabovsky, M., Hansen, S. S., \& McClelland, J. L. (2018). Modelling the N400 brain potential as change in a probabilistic representation of meaning. \emph{Nature Human Behaviour}, \emph{2}(9), 693--705. \url{https://doi.org/10.1038/s41562-018-0406-4}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-rossion2011}{}%
Rossion, B., \& Jacques, C. (2011). The N170: Understanding the time course of face perception in the human brain. In \emph{The oxford handbook of event-related potential components} (pp. 115--142). Oxford University Press. \url{https://doi.org/10.1093/oxfordhb/9780195374148.001.0001}

\leavevmode\hypertarget{ref-samaha2018}{}%
Samaha, J., Boutonnet, B., Postle, B. R., \& Lupyan, G. (2018). Effects of meaningfulness on perception: Alpha-band oscillations carry perceptual expectations and influence early visual responses. \emph{Scientific Reports}, \emph{8}(1), 1--14. \url{https://doi.org/10.1038/s41598-018-25093-5}

\leavevmode\hypertarget{ref-schad2020}{}%
Schad, D. J., Vasishth, S., Hohenstein, S., \& Kliegl, R. (2020). How to capitalize on a priori contrasts in linear (mixed) models: A tutorial. \emph{Journal of Memory and Language}, \emph{110}, 104038. \url{https://doi.org/10.1016/j.jml.2019.104038}

\leavevmode\hypertarget{ref-tanaka2001}{}%
Tanaka, J. W., \& Curran, T. (2001). A neural basis for expert object recognition. \emph{Psychological Science}, \emph{12}(1), 43--47. \url{https://doi.org/10.1111/1467-9280.00308}

\leavevmode\hypertarget{ref-vanrossum2009}{}%
van Rossum, G., \& Drake, F. L. (2009). \emph{Python 3 reference manual}. CreateSpace.

\leavevmode\hypertarget{ref-R-buildmer}{}%
Voeten, C. C. (2020). \emph{buildmer: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
\end{cslreferences}

\end{document}

### 2020-10-18 analysis/manuscript.Rmd
update plots, change condition names

@@
 How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects, preceded either by valid information about their function (leading to semantically informed perception) or by misleading information (leading to naive perception).
-Capitalizing on the high temporal resolution of event-related potentials (ERPs), we investigated how different stages in the processing hierarchy are modulated by this semantic understanding of objects before, during, and after it has been acquired.
+In this study, we presented participants with unfamiliar objects, preceded in half of the cases by valid information about their function (leading to semantically informed perception) and in the other half of the cases by misleading information (leading to naive perception).
+Capitalizing on the high temporal resolution of event-related potentials (ERPs), we investigated if semantically informed versus naive perception led to differential effects at different stages in the processing hierarchy of visual objects.
+
+Learning semantic knowledge about objects has an influence on how we process them [@abdelrahman2008; @gauthier2003; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
+Recently, evidence has accumulated that it does so not only at "higher" stages in the visual processing hierarchy, i.e. after "lower" stages of perceptual processing have been completed.
+It rather seems as though knowledge can also alter early processes, previously thought to be determined solely by the visual input itself, in a top-down manner.
+Such a top-down influence of semantic knowledge or expertise may manifest itself in behavioral changes such as improved visual matching [e.g.  @gauthier2003] and visual search performance [@maier2014; @holmes2012] when having learned that two objects share the same semantic category or verbal label.
+Furthermore, acquiring semantically meaningful knowledge about previously unfamiliar objects has been shown to increase their likelihood of gaining access to conuscious visual awareness under circumstances when attentional resources are limited [@weller2019].
+Although these behavioral effects hint at an early locus of semantic knowledge effects in object processing, they in and of themselves cannot convincingly demonstrate that not just downstream, postperceptual steps are being affected [@firestone2016].
+
+Stronger evidence comes from some of the above and other studies concurrently measuring event-related brain potentials (ERPs) while participants are performing different tasks on the objects about which they had previously acquired semantic knowledge.
+In their ERP study, [@abdelrahman2008] had participants first learn in-depth knowledge about 20 unfamiliar objects by listening to a verbal descripition of the function of each object while it was presented visually on the screen, whereas for 20 different objects they did not receive any relevant semantic information, instead listening to unrelated cooking recipes while the objects were presented.
+As in the present study, the assignment of unfamiliar objects to either of the two conditions was counterbalanced ascross participants as to prevent any subsequent effects of semantic knowledge from being confounded with visual differences between the objects.
+In a separate test session, event-related potentials were measured while participants performed three different tasks on those objects (intermixed with well known objects that had not been part of the training session).
+ERP amplitudes in response to objects for which in-depth versus minimal knowledge had been acquired differed in the time window of the N400 component (300--500 ms after stimulus onset), typically associated with semantic processing, but, interestingly, aslo in the time window of the visual P1 component (100--150 ms after stimulus onset), typcially associated with lower-level visual processing [[@abdelrahman2008]; Experiment 1].
+This effect ocurred across three different tasks (none of which explicitly required accessing any of the aqcuired information) and was qualitatively similar to the ERPs observed for untrained but well-known objects.
+A modulation of the P1 component has also been replicated using similar sets of objects in the above mentioned studies showing effects of object knowledge in visual search and the visual awareness tasks [@maier2019; @weller2019].
+It thus seems as though learning semantic information can influence steps of the processing hierarchy previously thought to be determined by the low-level visual input.
+
+A different strategy to investaige the influence of semantic knowledge on perception has been taken in a recent ERP study by [@samaha2018].
+Instead of using unfamiliar objects as stimuli, participants viewed images of familiar everyday objects that had been converted to two-tone "Mooney" images, making the object itself difficult to recognize.
+For half of the images, participants performed a semantic training where they were told which object to look for in each image.
+For the other half of images, they performed a perceptual (1-back) control task to equate the amount familiarity across all images.
+In a subsequent visual discrimination task, participants tended to respond faster and more accurate to the semantically trained images than to the perceptually trained ones [[@samaha2018]; Experiment 4].
+Crucially, the semantic training also manifested itself in increased pre-stimulus alpha-band power and larger P1 amplitudes at left temporo-occipital electrodes, further coroborating an early influence of semantically informed as compared to naive perception of objects.
+
+What all the previous studies have in common is that they investigated the effects of semantic knoweldge on object perception *after* an extensive learning phase [@abdelrahman2008; @gauthier2003; @maier2014; @maier2019; @rossion2002; @rossion2004; @samaha2018; @weller2019].
+Participants usually performed a seperate training session where they encountered each object together with its respective label or description multiple times.
+The EEG was usually not measured (or at least not analyzed and reported) during this training phase, which sometimes took place on a separate day [@abdelrahman2008; @maier2014; @maier2019] or was even spread out across multiple days or weeks [@rossion2002; @rossion2004].
+While designs with such substantive learning maximizes the chances of detecting even subtle top-down effects of the acquired knowledge, they necessarily leave at least three important conceptual questions unresolved.
+The first question is if we can detect any electrophysiological correlates of semantic insight, i.e. the critical presentation during which an understanding of a previously unfamiliar or meaningless objects is happening, instead of asking if this understanding leads to differential effects later in an orthogonal task.
+The second question is how much learning is actually necessary before reliable top-down effects of knowledge (e.g. on object-related P1 amplitudes) can be obtained: Does it actually take dozens of repitions per object or may a single exposure to the object together with the relevant semantic information be enough?
+The third and closely related question is related to one of the critiques sometimes raised against the nature of knowledge effects: Are they reflecting genuine top-down effects of semantic processes, altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been created or altered throughout the learning process?
+By measuring the ERPs before, during, and after participants received semantic hints about the unfamiliar objects, we hope to provide tentative answers to all of these questions.
 
@@
     pull(item)
-  excl_insight <- dat %>%
+  excl_informed <- dat %>%
     filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
@@
     pull(item)
-  insight <- dat %>%
+  informed <- dat %>%
     filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
@@
     item %in% excl_known ~ "Excl_known",
-    item %in% excl_insight ~ "Excl_insight",
+    item %in% excl_informed ~ "Excl_informed",
     item %in% excl_naive ~ "Excl_naive",
-    item %in% insight ~ "Insight",
+    item %in% informed ~ "Informed",
     item %in% naive ~ "Naive"
   ) %>%
-    factor(levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")))
+    factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
   # In Experiment 3, we need an additional column for position (upright vs. inverted)
@@
         # Each condition becomes a list of participants
-        for cn in ["Insight", "Naive"]:
+        for cn in ["Informed", "Naive"]:
             evokeds[pt][cn] = list()
@@
 # mne.viz.plot_compare_evokeds(evokeds=evokeds_exp1['II'], picks='P8'); plt.show()
-# evokeds_exp1['II']['Insight'].data = evokeds_exp1['II']['Insight'].data - evokeds_exp1['II']['Naive'].data
-# evokeds_exp1['II']['Insight'].plot_topomap(times=[0.125, 0.175, 0.5], average=0.05, vmin=-1, vmax=1, cmap='viridis'); plt.show()
+# evokeds_exp1['II']['Informed'].data = evokeds_exp1['II']['Informed'].data - evokeds_exp1['II']['Naive'].data
+# evokeds_exp1['II']['Informed'].plot_topomap(times=[0.125, 0.175, 0.5], average=0.05, vmin=-1, vmax=1, cmap='viridis'); plt.show()
 ```
@@
   part = factor(part, levels = c("I", "II", "III")),
-  condition = factor(condition, levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")),
+  condition = factor(condition, levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")),
   participant = factor(participant),
@@
 # Remove any trials excluded from conditions
-data_exp1 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
-
-# Contrast coding for condition (insight-naive) and part (2-1, 3-1)
-contrasts_condition <- t(cbind(c("Insight" = 1, "Naive" = -1)))
+data_exp1 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()
+
+# Contrast coding for condition (informed-naive) and part (2-1, 3-1)
+contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
 contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
@@
       data = data,
-      direction = c("order", "backward"),
+      direction = c("backward", "backward"),
       elim = function(logp) exp(logp) >= .20,
@@
   emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
+  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans %>% as.data.frame()
   conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts %>% as.data.frame()
-  mod <- list("model" = build@model, "anova" = build@anova, "summary" = build@summary, "contrasts" = conts)
+  mod <- list(model = build@model, anova = build@anova, summary = build@summary, means = means, contrasts = conts)
   return(mod)
@@
 Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
+No a priori power analysis was carreid out and the sample size was chosen according to the default for EEG studies in our lab at the time of data collection.
 All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
@@
 
-Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g. a bicycle, a toothbrush), whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g. a galvanometer, an udu drum).
-The well-known objects were included as filler stimuli of no interest.
-A list of the unfamiliar objects can be found in Appendix A.
+Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g. a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g. a galvanometer, an udu drum).
+A list of these unfamiliar objects can be found in Appendix A.
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a noun--verb pair was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g. current--measuring, pottery--drumming).
-In the *insight* condition, the presentation of each unfamiliar object was preceded by its respective description, whereas in the *naive* condition, it was preceded by a non-matching description belonging to one of the other objects.
-In both conditions, the noun and the verb were presented one above the other in black letters on a light blue background.
-For each participant, half of the unfamiliar objects were presented in the insight condition (i.e. with a matching description) and the other half were presented in the naive condition (i.e. with a non-matching description).
+For each unfamiliar object, a pair of keywords---a noun and a verb---was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g. current--measuring, pottery--drumming).
+As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects.
+The matching keywords were expected to induce semantically informed perception (i.e. participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an effect and keep the perception of the object semantically naive.
 All participants saw each unfamiliar object in only one of the two conditions and the assignment of objects to conditions was counterbalanced across participants.
@@
 Each experimental session consisted of three parts (Figure \@ref(fig:exp1-plot)A).
-In Part I, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without verbal descriptions.
+In the *pre-insight* part (Part I), after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
 Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
@@
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
-Because we were interested in the acquisition of semantic knowledge about unfamiliar objects only, all objects for which the participant indicated knowing the object in Part I were excluded from further analysis (`r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)` of rare objects per participant).
 
 (ref:figure-1-caption) Procedure and results of Experiment 1.
-*(A)* In Part I, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In Part II, half of the objects were preceded by a matching description (in purple color for illustration), leading to semantic insight, and the other half with a non-matching description (in petrol color for illustration), leading to naive perception.
-In Part III, the same objects were presented again without the descriptions.
-*(B)* Bar plots and *(C)* ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III.
-Insight was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
-Error bars show the standard error of the mean.
+*(A)* In the pre-insight part (Part I) participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In the insight part (Part II), half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
+In the post-insight part (Part III), the same objects were presented again without the keywords.
+*(B)* ERP waveforms and scalp topographies separately for objects with semantically informed versus naive perception in Parts I, II, and III.
+Semantically informed perception was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
 Ampl.
@@
 
-```{r exp1-plot, include=TRUE, fig.height=12, fig.cap = "(ref:figure-1-caption)"}
+```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
 # Manually extract significance levels from contrasts for plotting
@@
 fname_montage <- list.files(path = "renv/python", pattern = "easycap-M1.txt", recursive = TRUE, full.names = TRUE)[1]
-montage <- py$evokeds_exp1$I$Insight$ch_names %>%
+montage <- py$evokeds_exp1$I$Informed$ch_names %>%
   as_tibble() %>%
@@
 
+# Read SVG file with the trial structure (created using MS PowerPoint)
+plot_trials <- grImport2::readPicture("analysis/manuscript_files/figure-1a.svg") %>%
+  grImport2::pictureGrob(expansion = 0)
+
 # Define function to plot trial structure
@@
   require(magick)
-  colour_insight <- viridisLite::viridis(1, begin = 0.1, end = 0.1)
+  colour_informed <- viridisLite::viridis(1, begin = 0.1, end = 0.1)
   colour_naive <- viridisLite::viridis(1, begin = 0.5, end = 0.5)
@@
     geom_text(aes(x = 10, y = -3, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = colour_insight, fill = "white") +
-    geom_text(aes(x = 28, y = 23, label = "Potato\nmashing"), color = colour_insight, size = 10 / .pt,
+    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = colour_informed, fill = "white") +
+    geom_text(aes(x = 28, y = 23, label = "Potato\nmashing"), color = colour_informed, size = 10 / .pt,
               family = "Helvetica") +
@@
 plot_erps <- function(comps, evokeds, montage, stars) {
+  suppressWarnings(suppressMessages(
     pmap(comps, function(name, start, stop, roi) {
@@
           bind_rows(.id = "condition")
-      # Prepare waveform
-      wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
-        annotate("rect", xmin = start, xmax = stop, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
-      # Shade significant area
+        # Shade background depending on whether the effect is significant or not
         star <- stars[[name]][[part]]
-      if (!is.na(star)) {
-        wave <- wave + geom_ribbon(
-          data = data_plot %>% filter(.time >= start & .time <= stop) %>%
-            group_by(.time) %>% summarise(ymin = min(roi), ymax = max(roi)),
-          aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
-          inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1)
-        )
-      } #+
+        if (is.na(star)) {
+          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.9, color = "black", fill = NA)
+        } else {
+          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.9, color = "black", fill = "gray90")
+        }
+        xstar <- case_when(str_length(star) == 1 ~ start + 11, str_length(star) == 3 ~ start + 15)
+        # # Prepare waveform
+        # wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
+        #   annotate("rect", xmin = start, xmax = stop, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
+        # # Shade significant area
+        # star <- stars[[name]][[part]]
+        # if (!is.na(star)) {
+        #   wave <- wave + geom_ribbon(
+        #     data = data_plot %>% filter(.time >= start & .time <= stop) %>%
+        #       group_by(.time) %>% summarise(ymin = min(roi), ymax = max(roi)),
+        #     aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
+        #     inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1)
+        #   )
+        # } +
         # annotate("text", label = star, x = start + (stop - start)/2, y = -3.2, size = 7, family = "Helvetica")}
         # Add waves and styling
-      wave <- wave +
+
+        # Plot waveform
+        wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
+          shade +
+          annotate("text", label = star, x = xstar, y = ymin + 11, size = 6, hjust = 0, family = "Helvetica") +
           annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
@@
           annotate("segment", x = -12, xend = 0, y = seq(-2, 8, 4), yend = seq(-2, 8, 4)) +
-        annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10 / .pt,
-                 family = "Helvetica") +
-        annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10 / .pt, family = "Helvetica",
-                 hjust = 1) +
-        annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10 / .pt, family = "Helvetica",
-                 lineheight = 0.9) +
-        annotate("text",
-          x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10 / .pt,
-          family = "Helvetica", angle = 90, lineheight = 0.9
-        ) +
+          annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10 / .pt, family = "Helvetica") +
+          annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10 / .pt, family = "Helvetica", hjust = 1) +
+          annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10 / .pt, family = "Helvetica", lineheight = 0.9) +
+          annotate("text", x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10 / .pt, family = "Helvetica", angle = 90, lineheight = 0.9) +
           geom_line() +
@@
           pivot_wider(names_from = condition) %>%
-        transmute(amplitude = Insight - Naive) %>%
+          transmute(amplitude = Informed - Naive) %>%
           bind_cols(montage) %>%
@@
     }) %>% plot_grid(plotlist = ., nrow = 3)
-}
-
-# Define functions to plot legends for conditions and topoplots
-plot_legends <- function() {
-  legend_conditions <- get_legend(tibble(Conditions = c("Insight", "Naive")) %>% 
-                                    ggplot(aes(x = 0, y = 0, fill = Conditions)) +
+  ))
+}
+
+# Creata a combined legend and colorbar
+legends <- function(direction){
+  if (direction == "vertical"){mar <- margin(l = 6, r = 4, b = 10, t = 6); vjust <- 3.5}
+  else {mar <- margin(l = 5, r = 14, b = 3, t = 5); vjust <- 0.7}
+  get_legend(
+    tibble(amplitude = c(-1, 1), condition = c("Informed", "Naive")) %>% 
+      ggplot(aes(x = 0, y = 0, color = condition, fill = amplitude)) +
+      geom_line() +
       geom_raster() +
-    scale_fill_viridis_d(begin = 0.1, end = 0.5) +
+      labs(color = "Conditions", fill = "Informed - naive (µV)") +
+      scale_color_viridis_d(
+        begin = 0.1, end = 0.5,
+        guide = guide_legend(direction = "vertical", title.position = "top")
+      ) +
+      scale_fill_viridis_c(
+        guide = guide_colorbar(direction = direction, ticks = FALSE, title.position = "top", title.vjust = vjust)
+      ) +
       theme(
-      legend.direction = "horizontal",
+        legend.direction = direction,
+        legend.box = direction,
+        legend.box.background = element_rect(colour = "black", size = 0.5),
+        legend.box.margin = mar,
+        legend.background = element_blank(),
         legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
         legend.text = element_text(family = "Helvetica", size = 10),
+        legend.key = element_rect(fill = NA),
+        legend.key.width = unit(0.8, "cm"),
+        legend.key.height = unit(0.4, "cm"),
         legend.spacing.x = unit(0.3, "cm")
       ))
-  legend_topo <- get_legend(tibble(amplitude = c(-1, 1)) %>% ggplot(aes(x = 0, y = 0, fill = amplitude)) +
-    geom_raster() +
-    labs(fill = "Insight - naive\nampl. (µV)") +
-    scale_fill_viridis_c(guide = guide_colorbar(
-      ticks = FALSE, title.position = "left",
-      title.vjust = 1, title.hjust = 0.5
-    )) +
-    theme(
-      legend.direction = "horizontal",
-      legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
-      legend.text = element_text(family = "Helvetica", size = 10),
-      legend.key.width = unit(0.8, "cm"), legend.spacing.x = unit(0.3, "cm")
-    ))
-  plot_grid(NULL, legend_conditions, legend_topo, NULL, nrow = 1, rel_widths = c(1, 3, 3, 1))
-}
-
-# Read SVG file with the trial structure (created using MS PowerPoint)
-plot_trials <- grImport2::readPicture("analysis/manuscript_files/figure-1a.svg") %>%
-  grImport2::pictureGrob(expansion = 0)
+}
 
@@
   plot_erps(comps = comps, evokeds = evokeds_exp1, montage = montage, stars = stars_exp1),
-  plot_legends(),
+  #plot_legends(),
   #nrow = 4, rel_heights = c(3, 2, 6, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica"
-  nrow = 3, rel_heights = c(5, 6, 1), labels = c("A", "B", ""), label_fontfamily = "Helvetica"
+  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
   #nrow = 4, rel_heights = c(4, 2, 5, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica"
-)
-```
-
-In Part II, only the 120 unfamiliar objects were presented for a second time, now preceded either by a matching verbal description (in the insight condition) or by a non-matching verbal description (in the naive condition).
-Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the verbal description for 2.5 s.
+) + # Add some lines to separate the parts (+ the legends)
+  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.52, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.52, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.52, yend = 0.57, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.52, yend = 0.57, linetype = "dashed") +  
+  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.57, yend = Inf, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.57, yend = Inf, linetype = "dashed") +
+  draw_plot(legends(direction = "vertical"), x = 0.41, y = 0.397, width = 1, height = 1)
+```
+
+In the *insight* part (Part II), only the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
 Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
 The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g. medical devices, musical instruments).
-To make sure that insight did (did not) occur in the insight (naive) condition, we excluded any objects from the insight condition if participants indicated not knowing the object or having rather no assumption (despite reading the matching description) and any objects from the naive condition if participants indicated knowing the object or having an assumption (despite reading the non-matching description).
-This resulted in an average of `r format(round(stims_exp1["Insight"], 1), nsmall = 1)` objects (`r scales::percent(stims_exp1["Insight"]/60, accuracy = 0.1)`) per participant remaining in the insight condition and an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects (`r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)`) per participant remaining in the naive condition.
-
-In Part III, the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e. without the verbal descriptions.
-Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with descriptions), participants took a self-timed break and continued with the same block of 30 objects in Part III (without descriptions) before moving on to the next block consisting of 30 different objects.
+
+In the post-insight part (Part III), the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e. without any keywords.
+Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with keywords), participants took a self-timed break and continued with the same block of 30 objects in Part III (without keywords) before moving on to the next block consisting of 30 different objects.
 They continued like this until all four blocks were completed in both Parts II and III.
@@
 
-Offline, the data were preprocessed using the MNE software [Version 0.21.0; @gramfort2013] in Python [Version 3.7.7; @vanrossum2009].
+Offline, the data were preprocessed using the MNE software [Version 0.21.0; @gramfort2013] in Python [Version 3.8.5; @vanrossum2009].
 First, all scalp electrodes were re-referenced to the common average.
 Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
-The first 15 components were extracted using the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
+The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
 Those components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the *find\_bads\_eog* function.
@@
 
-The event-related potentials were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
-For the purpose of the present study, these models have two desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in Part I (i.e. before any keywords were presented), which led to the exclusion of an average of `r format(round(stims_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (`r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)`).
+Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in Part II) and the behavioral responses of the participants themselves (Figure 1A).
+Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
+This was the case for an average of `r format(round(stims_exp1["Informed"], 1), nsmall = 1)` objects per participant (`r scales::percent(stims_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
+Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
+This was the case for an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects per participant (`r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+Although the assignment was purely based on the manipulation and responses in Part II, when insight was thought to occurr, the same assignment was used to analyze the data from the other two parts.
+This allowed us to test on the one hand if the objects from both conditions differed in important aspects even before any keywords were presented (in Part I), and on the other hand if the semantic understanding acquired in Part II had any lasting effects on a subsequent, third presentation of the objects (in Part III).
+
+The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
+For the purpose of the present study, these models have at least two desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages.
 First, they can account simultaneously for the non-independence of data points coming from the same participant or from the same item, whereas the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
-Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is based on participants' own responses rather than on the experimental manipulation [e.g.  @fröber2017].
+Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is (co-)determined by the responses of the participants rather than by the experimental manipulation alone [e.g.  @fröber2017].
 
 Three separate models were computed predicting P1, N1, and N400 mean amplitudes, respectively.
-All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e. subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e. subtracting the naive from the insight condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
-For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to @schad2020.
+All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e. subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e. subtracting the naive from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
+For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to [@schad2020].
 To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
-We then performed a model selection algorithm as proposed by @matuschek2017 for increasing statistical power and avoiding overparameterization: Iteratively, each random effects was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+We then performed a model selection algorithm as proposed by [@matuschek2017] in order to increase statistical power and avoid overparameterization: Iteratively, each random effects was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
 Only if the parsimonious model explained the data equally well as the complex model [determined by *p* \> .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model.
@@
 The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r packageVersion("buildmer")`; @R-buildmer].
-Finally, to answer our research question of whether or not semantic insight had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the insight against the naive condition within Parts I, II, and III.
-Reported *p* values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's methods as implemented in the lmerTest package [@R-lmerTest].
-
-The materials and code for the present experiments can be accessed via the Open Science Framework ([https://osf.io/.../](https://osf.io/myprojects/)).
+Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within Parts I, II, and III.
+All *p* values subsequently reported were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's methods as implemented in the lmerTest package [@R-lmerTest].
+
+The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework ([https://osf.io/.../](https://osf.io/myprojects/)).
+To avoid potential misuse, the raw EEG are only made available by the corresponding author upon request.
 
@@
 
-Single-trial ERPs were analyzed in response to unfamiliar objects before (Part I), while (Part II), and after (Part III) participants gained semantic insight into the function or use of the objects.
-Half of the objects were preceded by a matching description, fostering semantic insight to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
-To make sure participants did indeed experience insight or naive perception, the analysis was constrained by participants' behavioral responses in Part II: Objects presented with a matching description were assigned to the insight condition only if the participant indicated that they understood what the object was (or had an assumption), whereas objects presented with a non-matching description were assigned to the naive condition only if the participant indicated that they did not understand what the object was (or had rather no assumption).
-The analysis focused on differences between the insight and the naive condition in the P1 component (100--150 ms) as an index of lower-level visual perception, the N1 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.
+Single-trial ERPs were analyzed in response to unfamiliar objects before (Part I), while (Part II), and after (Part III) participants obtained relevant semantic information about their function.
+Only in Part II, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
+The objects were analyzed according to this manipulation in combination with participants' self-report in Part II (Figure 1A), thus making sure that semantically informed (or naive) perception did indeed occur.
+The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N1 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.
 
@@
     bind_cols() %>%
-    set_rownames(c("\\textit{Insight $-$  naive}", stub_contrasts))
+    set_rownames(c("\\textit{Informed $-$  naive}", stub_contrasts))
   conts %<>% 
@@
   models = models_exp1,
-  stub_anova = c("Part", "Insight", "Pt. × ins."),
+  stub_anova = c("Part", "Condition", "Pt. × con."),
   stub_contrasts = c("Part I", "Part II", "Part III"),
   caption = "Results of linear mixed-effects regression models for Experiment 1",
-  note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval."
+  note = "Pt. = part, con. = condition, est. = estimate, CI = confidence interval."
 )
@@
 Averaged across conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all *F*s \> `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (Table \@ref(tab:exp1-table)).
-In addition, N400 amplitudes differed between the insight and the naive conditions averaged across the three parts of the experiment, *F*`r table_exp1$anov["Insight", "N400_df"]` = `r table_exp1$anov["Insight", "N400_f"]`, *p* = `r table_exp1$anov["Insight", "N400_p"]`.
-Crucially, the part × insight interaction was significant in the N1 component, *F*`r table_exp1$anov["Pt.
-× ins.", "N1_df"]` = `r table_exp1$anov["Pt.
-× ins.", "N1_f"]`, *p* = `r table_exp1$anov["Pt.
-× ins.", "N1_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt.
-× ins.", "N400_df"]` = `r table_exp1$anov["Pt.
-× ins.", "N400_f"]`, *p* `r table_exp1$anov["Pt.
-× ins.", "N400_p"]`, while also being marginally significant in the P1 component, *F*`r table_exp1$anov["Pt.
-× ins.", "P1_df"]` = `r table_exp1$anov["Pt.
-× ins.", "P1_f"]`, *p* = `r table_exp1$anov["Pt.
-× ins.", "P1_p"]`.
-To answer our main research question, we decomposed these interactions into the differences between the insight and the naive condition within the three different parts of the experiment.
-
-### Effects of Insight in Part I
-
-In Part I, when objects were unfamiliar to the participant and presented without verbal descriptions, no differences emerged between the insight and the naive condition in the P1, N1, or N400 component, all *p*s \> `r table_exp1$conts["Part I", "N400_p"]` (Table \@ref(tab:exp1-table), Figure \@ref(fig:exp1-plot)B & C).
-On the one hand, this was to be expected given that the critical presentation of the objects with the descriptions (leading to semantic insight vs. naive perception) had not yet taken place.
-On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of insight in Parts II and III cannot be explained solely by visual differences between the objects in the two conditions.
-Although the presentation of a matching or non-matching description for each object was counterbalanced across participants, the fact that different numbers of objects were excluded from the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor.
-If they did, however, one would expect to detect these differences even before any descriptions were presented, which we now know was not the case.
-
-### Effects of Insight in Part II
-
-In Part II, half of the unfamiliar objects were presented with a matching verbal description (in the insight condition) and the other half were presented with a non-matching verbal description (in the naive condition).
-In response to objects for which participants experienced semantic insight, the amplitude of the N1 component was significantly enlarged (i.e. more negative), *b* = `r table_exp1$conts["Part II", "N1_est"]` µV, *p* = `r table_exp1$conts["Part II", "N1_p"]`, and the amplitude of the N400 component was significantly reduced (i.e. less negative), *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`, compared to objects which participants viewed naively.
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r table_exp1$anov["Informed", "N400_df"]` = `r table_exp1$anov["Informed", "N400_f"]`, *p* = `r table_exp1$anov["Informed", "N400_p"]`.
+Crucially, the part × condition interaction was significant in the N1 component, *F*`r table_exp1$anov["Pt.
+× con.", "N1_df"]` = `r table_exp1$anov["Pt.
+× con.", "N1_f"]`, *p* = `r table_exp1$anov["Pt.
+× con.", "N1_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt.
+× con.", "N400_df"]` = `r table_exp1$anov["Pt.
+× con.", "N400_f"]`, *p* `r table_exp1$anov["Pt.
+× con.", "N400_p"]`, while also being marginally significant in the P1 component, *F*`r table_exp1$anov["Pt.
+× con.", "P1_df"]` = `r table_exp1$anov["Pt.
+× con.", "P1_f"]`, *p* = `r table_exp1$anov["Pt.
+× con.", "P1_p"]`.
+To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
+
+### ERPs in Part I (Pre-Insight)
+
+In Part I, when objects were unfamiliar to the participant and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N1, or N400 component, all *p*s \> `r table_exp1$conts["Part I", "N400_p"]` (Table \@ref(tab:exp1-table), Figure \@ref(fig:exp1-plot)B & C).
+On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
+On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in Parts II and III cannot be accounted for by visual differences between the objects in the two conditions.
+Although the presentation of a matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor.
+If they did, however, one would expect to detect these differences even before any keywords were presented, which we have now seen was not the case.
+
+### ERPs in Part II (Insight)
+
+In Part II, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
+When semantic information informed the perception of the object (akin to an insight experience), the amplitude of the N1 component was significantly enlarged (i.e. more negative), *b* = `r table_exp1$conts["Part II", "N1_est"]` µV, *p* = `r table_exp1$conts["Part II", "N1_p"]`, and the amplitude of the N400 component was significantly reduced (i.e. less negative), *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`, compared to when an object was viewed naively without relevant semantic information.
 As in Part I, there were no reliable differences in the P1 component, *p* = `r table_exp1$conts["Part II", "P1_p"]`.
 
-### Effects of Insight in Part III
-
-In Part III, the unfamiliar objects were presented for a third time, again without the verbal descriptions (as in Part I), to test whether the occurrence of semantic insight had any lasting effects on the processing of the objects.
-As in Part II, the N400 component remained significantly reduced in response to objects for which semantic insight had occurred, *b* = `r table_exp1$conts["Part III", "N400_est"]` µV, *p* `r table_exp1$conts["Part III", "N400_p"]`, whereas the early effect of insight in the N1 component did not reoccur, *p* = `r table_exp1$conts["Part III", "N1_p"]`.
-Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e. more positive) in response to objects for which semantic insight had occurred, *b* = `r table_exp1$conts["Part III", "P1_est"]` µV, *p* = `r table_exp1$conts["Part III", "P1_p"]`.
+### ERPs in Part III (Post-Insight)
+
+In Part III, the unfamiliar objects were presented for a third time, again without the keywords (as in Part I), to test whether the semantic information had any lasting effects on the processing of the objects.
+As in Part II, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Part III", "N400_est"]` µV, *p* `r table_exp1$conts["Part III", "N400_p"]`, whereas the early effect in the N1 component did not reoccur, *p* = `r table_exp1$conts["Part III", "N1_p"]`.
+Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e. more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Part III", "P1_est"]` µV, *p* = `r table_exp1$conts["Part III", "P1_p"]`.
 
@@
 
-In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they gained semantic insight into what kind of object they were seeing.
-To induce insight, half of the objects in Part II were preceded by a matching verbal description of the object's typical function or use, whereas the other half were preceded by a non-matching description (as a naive baseline condition).
-
-Participants' experience of semantic insight in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001].
-The fact that this effect did not reoccur in Part III, when the objects were presented once more without descriptions, suggests it being a marker of semantic insight altering object processing online.
-In contrast, we also observed a modulation of the N400 component, which was reduced for objects when semantic insight was occurring (in Part II) and remained so when the same objects were presented repeatedly (in Part III).
+In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they were able to understand what kind of object they saw.
+To induce this semantically informed perception, half of the objects in Part II were preceded by matching verbal keywords about their typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
+
+Participants' semantically informed perception of the objects in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001].
+The fact that this effect did not reoccur in Part III, when the objects were presented once more without keywords, suggests it being a marker of insight through semantic information that is altering object processing online.
+In contrast, we also observed a modulation of the N400 component, which was reduced for objects while insight was taking place (in Part II) and remained so when the same objects were presented repeatedly (in Part III).
 The N400 is most often discussed as an index of increased demands for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018].
 Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had understood what kind of object they were viewing.
-Finally, semantic insight was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which semantic insight had occurred (in Part II).
-This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images [@samaha2018], may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had occurred.
+Finally, semantically informed perception was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which insight had occurred (in Part II).
+This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images [e.g.  @samaha2018], may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had occurred.
 
@@
 # Remove any trials excluded from conditions
-data_exp2 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
-
-# Contrast coding for condition (insight-naive) and part (2-1, 3-1)
+data_exp2 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()
+
+# Contrast coding for condition (informed-naive) and part (2-1, 3-1)
 contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
@@
 
-All materials, procedures, and methods for EEG recording and statistical analysis were identical to Experiment 1.
-An average of `r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)` of rare objects per participant was classified as known in Part I and excluded from all further analyses.
-Based on participants' responses in Part II, an average of `r format(round(stims_exp2["Insight"], 1), nsmall = 1)` objects were assigned to the insight condition (`r scales::percent(stims_exp2["Insight"]/60, accuracy = 0.1)` of objects presented with a matching description) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (`r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with a non-matching description).
-Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials (`r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`) per participant (range `r min(rejected_exp2)` to `r max(rejected_exp2)`).
+All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
+An average of `r format(round(stims_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (`r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)`) was classified as being known in Part I and excluded from all further analyses.
+Based on participants' responses in Part II, an average of `r format(round(stims_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (`r scales::percent(stims_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (`r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with a non-matching description).
+Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (`r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`, range `r min(rejected_exp2)` to `r max(rejected_exp2)`).
 
@@
   models_exp2,
-  stub_anova = c("Part", "Insight", "Pt. × ins."),
+  stub_anova = c("Part", "Condition", "Pt. × con."),
   stub_contrasts = c("Part I", "Part II", "Part III"),
   caption = "Results of linear mixed-effects regression models for Experiment 2",
-  note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval."
+  note = "Pt. = part, con. = condition, est. = estimate, CI = confidence interval."
 )
@@
 As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all *F*s \> `r table_exp2$anov["Part", "N1_f"]`, all *p*s `r table_exp2$anov["Part", "N1_p"]` (Table \@ref(tab:exp2-table)).
-Also as in Experiment 1, N400 amplitudes differed between the insight and the naive condition averaged across parts, *F*`r table_exp2$anov["Insight", "N400_df"]` = `r table_exp2$anov["Insight", "N400_f"]`, *p* `r table_exp2$anov["Insight", "N400_p"]`.
-The part × insight interaction was significant in the P1 component, *F*`r table_exp2$anov["Pt.
-× ins.", "P1_df"]` = `r table_exp2$anov["Pt.
-× ins.", "P1_f"]`, *p* = `r table_exp2$anov["Pt.
-× ins.", "P1_p"]`, and in the N400 component, *F*`r table_exp2$anov["Pt.
-× ins.", "N400_df"]` = `r table_exp2$anov["Pt.
-× ins.", "N400_f"]`, *p* `r table_exp2$anov["Pt.
-× ins.", "N400_p"]`, but not in the N1 component, *F*`r table_exp2$anov["Pt.
-× ins.", "N1_df"]` = `r table_exp2$anov["Pt.
-× ins.", "N1_f"]`, *p* = `r table_exp2$anov["Pt.
-× ins.", "N1_p"]`.
+Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, *F*`r table_exp2$anov["Informed", "N400_df"]` = `r table_exp2$anov["Informed", "N400_f"]`, *p* `r table_exp2$anov["Informed", "N400_p"]`.
+The part × condition interaction was significant in the P1 component, *F*`r table_exp2$anov["Pt.
+× con.", "P1_df"]` = `r table_exp2$anov["Pt.
+× con.", "P1_f"]`, *p* = `r table_exp2$anov["Pt.
+× con.", "P1_p"]`, and in the N400 component, *F*`r table_exp2$anov["Pt.
+× con.", "N400_df"]` = `r table_exp2$anov["Pt.
+× con.", "N400_f"]`, *p* `r table_exp2$anov["Pt.
+× con.", "N400_p"]`, but not in the N1 component, *F*`r table_exp2$anov["Pt.
+× con.", "N1_df"]` = `r table_exp2$anov["Pt.
+× con.", "N1_f"]`, *p* = `r table_exp2$anov["Pt.
+× con.", "N1_p"]`.
 
 (ref:figure-2-caption) Results of Experiment 2.
-*(A)* Bar plots and *(B)* ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III.
-In a direct replication of Experiment 1, the effect of semantic insight on the N400 component in Part II and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II and on the N400 component in Part III remained only marginally significant.
-Error bars show the standard error of the mean.
+ERP waveforms and scalp topographies separately for objects for which participants experienced semantically informed versus naive perception in Parts I, II, and III.
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in Parts II and III and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II remained only marginally significant.
 Ampl.
@@
 
-```{r exp2-plot, include=TRUE, fig.height=8, fig.cap = "(ref:figure-2-caption)"}
+```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:figure-2-caption)"}
 # Manually extract significance levels from contrasts for plotting
@@
 
+# Create headings for Parts I, II, and III
+plot_headings <- function(){
+  plot_grid(
+    ggplot() + annotate("text", label = "Part I (pre-insight)", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(), NULL,
+    ggplot() + annotate("text", label = "Part II (insight)", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(), NULL,
+    ggplot() + annotate("text", label = "Part III (post-insight)", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(),
+    nrow = 1, rel_widths = c(10, 1, 10, 1, 10)
+  )
+}
+
 # Create plot for Experiment 2
 plot_grid(
-  plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
+  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
+  plot_headings(),
   plot_erps(comps = comps, evokeds = evokeds_exp2, montage = montage, stars = stars_exp2),
-  plot_legends(),
-  nrow = 3, rel_heights = c(2, 5, 1), labels = c("A", "B", ""), label_fontfamily = "Helvetica"
-)
-```
-
-### Effects of Insight in Part I
-
-As in Experiment 1, no differences between objects in the insight and the naive condition emerged in the P1, N1, or N400 component, all *p*s \> `r table_exp2$conts["Part I", "P1_p"]` (Table \@ref(tab:exp2-table), Figure \@ref(fig:exp2-plot)).
-
-### Effects of Insight in Part II
-
-As in Experiment 1, the occurrence of semantic insight in Part II due to the presentation of objects with matching (vs. non-matching) verbal descriptions was associated with a (marginally) significant enhancement of the N1 component, *b* = `r table_exp2$conts["Part II", "N1_est"]` µV, *p* = `r table_exp2$conts["Part II", "N1_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`.
-
-### Effects of Insight in Part III
-
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without verbal descriptions as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantic insight had occurred, *b* = `r table_exp2$conts["Part III", "P1_est"]` µV, *p* = `r table_exp2$conts["Part III", "P1_p"]`.
+  legends(direction = "horizontal"),
+  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
+) +
+  annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.672, xend = 0.672, y = 0.15, yend = Inf, linetype = "dashed")
+```
+
+### ERPs in Part I (Pre-Insight)
+
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N1, or N400 component, all *p*s \> `r table_exp2$conts["Part I", "P1_p"]` (Table \@ref(tab:exp2-table), Figure \@ref(fig:exp2-plot)).
+
+### ERPs in Part II (Insight)
+
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching versus non-matching keywords) was associated with a (marginally) significant enhancement of the N1 component, *b* = `r table_exp2$conts["Part II", "N1_est"]` µV, *p* = `r table_exp2$conts["Part II", "N1_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`.
+
+### ERPs in Part III (Post-Insight)
+
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Part III", "P1_est"]` µV, *p* = `r table_exp2$conts["Part III", "P1_p"]`.
 Also, N400 amplitudes in response to these objects remained significantly reduced, *b* = `r table_exp2$conts["Part III", "N400_est"]` µV, *p* = `r table_exp2$conts["Part III", "N400_p"]`.
@@
 Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e. subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; @schad2020].
-This factor and its possible interactions with part, insight, and part × insight were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
+This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
 They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2.
@@
 
-# Contrast coding for experiment (2-1), condition (insight-naive), and part (2-1, 3-1)
+# Contrast coding for experiment (2-1), condition (informed-naive), and part (2-1, 3-1)
 t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
@@
   models_joint,
-  stub_anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.", "Ins. × exp.", "Pt. × ins. × exp."),
+  stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
   stub_contrasts = c("Part I", "Part II", "Part III"),
   caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
-  note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval."
-)
-```
-
-As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of insight in the N400, *F*`r table_joint$anov["Insight", "N400_df"]` = `r table_joint$anov["Insight", "N400_f"]`, *p* `r table_joint$anov["Insight", "N400_p"]`.
-Furthermore, the part × insight interaction was now observed reliably in all three components, all *F*s \> `r table_joint$anov["Pt.
-× ins.", "P1_f"]`, all *p*s \< `r table_joint$anov["Pt.
-× ins.", "P1_p"]`.
-While there was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, the absence of any significant interactions of experiment with part or insight indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
-
-Based on the part × insight interaction, we again computed follow-up comparisons between the insight and the naive condition within each part, now collapsed across the data from both experiments.
-This confirmed the absence of any reliable differences between the two conditions in Part I, all *p*s \> `r table_joint$conts["Part I", "N400_p"]`, the significant enhancement of the N1 component in Part II, while insight was occurring, *b* = `r table_joint$conts["Part II", "N1_est"]` µV, *p* = `r table_joint$conts["Part II", "N1_p"]`, the significant reduction of the N400 component in Part II, while insight was occurring, *b* = `r table_joint$conts["Part II", "N400_est"]` µV, *p* `r table_joint$conts["Part II", "N400_p"]`, and Part III, after insight had occurred, *b* = `r table_joint$conts["Part III", "N400_est"]` µV, *p* = `r table_joint$conts["Part III", "N400_p"]`, as well as the significant enhancement of the P1 component in Part III, after insight had occurred, *b* = `r table_joint$conts["Part III", "P1_est"]` µV, *p* = `r table_joint$conts["Part III", "P1_p"]`.
+  note = "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval."
+)
+```
+
+```{r joint-plot, eval=FALSE}
+map(c("I", "II", "III"), function(part){
+  map(c("P1", "N1", "N400"), function(comp){
+
+    ymin <- case_when(comp == "P1" ~ -6, comp == "N1" ~ -11, comp == "N400" ~ -10)
+
+    data_joint %>%
+      filter(part == !!part) %>%
+      rename(amplitude = !!comp) %>%
+      group_by(participant, part, condition) %>% summarise(across(amplitude, mean)) %>%
+      ggplot(aes(x = condition, y = amplitude, fill = condition)) +
+      geom_violin() +
+      geom_boxplot(width = 0.3) +
+      coord_cartesian(ylim = c(ymin, ymin + 24)) +
+      scale_y_continuous(breaks = seq(ymin, ymin + 24, 4)) +
+      theme_classic() +
+      theme(
+        legend.position = "none"
+      )
+
+  }) %>% plot_grid(plotlist = ., nrow = 3)
+}) %>% plot_grid(plotlist = ., nrow = 1)
+
+# data_joint %>%
+#   pivot_longer(cols = c(P1, N1, N400), names_to = "comp", values_to = "amplitude") %>%
+#   mutate(comp = factor(comp, levels = c("P1", "N1", "N400"))) %>%
+#   group_by(participant, part, condition, comp) %>% summarise(amplitude = mean(amplitude)) %>%
+#   ggplot(aes(x = condition, y = amplitude, fill = condition)) +
+#   geom_violin() +
+#   geom_boxplot(width = 0.3) +
+#   coord_cartesian(ylim = c(-10, 10)) +
+#   facet_grid(comp ~ part)
+```
+
+As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Informed", "N400_df"]` = `r table_joint$anov["Informed", "N400_f"]`, *p* `r table_joint$anov["Informed", "N400_p"]`.
+Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s \> `r table_joint$anov["Pt.
+× con.", "P1_f"]`, all *p*s \< `r table_joint$anov["Pt.
+× con.", "P1_p"]`.
+While there was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
+
+Based on the part × condition interaction, we again computed follow-up comparisons between the semantically inforemd and the naive condition within each part, now collapsed across the data from both experiments.
+This confirmed the absence of any reliable differences between the two conditions in Part I, all *p*s \> `r table_joint$conts["Part I", "N400_p"]`, the significant enhancement of the N1 component in Part II, while the semantic information was obtained, *b* = `r table_joint$conts["Part II", "N1_est"]` µV, *p* = `r table_joint$conts["Part II", "N1_p"]`, the significant reduction of the N400 component in Part II, while the semantic information was obtained, *b* = `r table_joint$conts["Part II", "N400_est"]` µV, *p* `r table_joint$conts["Part II", "N400_p"]`, and Part III, after the information had been obtained, *b* = `r table_joint$conts["Part III", "N400_est"]` µV, *p* = `r table_joint$conts["Part III", "N400_p"]`, as well as the significant enhancement of the P1 component in Part III, after the information had been obtained, *b* = `r table_joint$conts["Part III", "P1_est"]` µV, *p* = `r table_joint$conts["Part III", "P1_p"]`.
 
@@
 # # Keep all three conditions
-# data_joint_control %<>% filter(condition %in% c("Insight", "Naive", "Excl_insight")) %>% droplevels()
-# contrasts_condition <- t(cbind(c("Insight" = 1, "Naive" = -1, "Excl_insight" = 0),
-#                                c("Insight" = 1, "Naive" = 0, "Excl_insight" = -1)))
+# data_joint_control %<>% filter(condition %in% c("Informed", "Naive", "Excl_informed")) %>% droplevels()
+# contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1, "Excl_informed" = 0),
+#                                c("Informed" = 1, "Naive" = 0, "Excl_informed" = -1)))
 # contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
@@
 # This time, we keep the unsuccessful ahas as the control condition
-data_joint_control %<>% filter(condition %in% c("Insight", "Excl_insight")) %>% droplevels()
-
-# Contrast coding for condition (insight-no_insight) and part (2-1, 3-1)
+data_joint_control %<>% filter(condition %in% c("Informed", "Excl_informed")) %>% droplevels()
+
+# Contrast coding for condition (informed-no_informed) and part (2-1, 3-1)
 contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
@@
   models = models_joint_control,
-  stub_anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.", "Ins. × exp.", "Pt. × ins. × exp."),
+  stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
   stub_contrasts = c("Part I", "Part II", "Part III"),
   caption = "Results of linear mixed-effects regression models with a different baseline",
-  note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval."
-)
-```
-
-One may raise concerns whether the modulation of the N1 component in Part II genuinely reflects semantic insight for objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition.
-Remember that these objects were preceded by a non-matching description which was picked so that it could not be related to the object's visual features and their configuration.
+  note = "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval."
+)
+```
+
+One may raise concerns whether the modulation of the N1 component in Part II genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition.
+Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the object's visual features and their configuration.
 Thus, the modulation of the ERP components in Part II may reflect a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of morsing messages.
-To preclude this alternative explanation, we repeated the analysis above using a different baseline against which the objects in the insight condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the insight condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_insight"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Insight"]/60, accuracy = 0.1)` of objects which did indeed lead to semantic insight (note that the remaining objects were excluded as not being unfamiliar in the beginning of the experiment).
-Just as above, this control analysis revealed a robust enhancement of the N1 component associated with semantic insight in Part II, *b* = `r table_joint_control$conts["Part II", "N1_est"]` µV, *p* `r table_joint_control$conts["Part II", "N1_p"]`.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading descriptions or compared to objects presented with accurate descriptions on which participants failed to capitalize.
-Note that the reduction of the N400 component also remained robust in this control analysis, *b* = `r table_joint_control$conts["Part II", "N400_est"]` µV, *p* `r table_joint_control$conts["Part II", "N400_p"]`.
+To preclude this alternative explanation, we repeated the analysis above using a different baseline against which the objects in the semantically informed condition were contrasted.
+Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
+Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.^[Note that the remaining objects to make it up to 100% were excluded as not being unfamiliar in Part I of the experiment (see Statistical Analysis)] Just as above, this control analysis revealed a robust N1 effect in Part II, *b* = `r table_joint_control$conts["Part II", "N1_est"]` µV, *p* `r table_joint_control$conts["Part II", "N1_p"]`.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords on which participants failed to capitalize.
+Note that the reduction of the N400 component in Part II also remained robust in this control analysis, *b* = `r table_joint_control$conts["Part II", "N400_est"]` µV, *p* `r table_joint_control$conts["Part II", "N400_p"]`.
 
@@
 
-Experiment 2, which was a direct replication of Experiment 1, confirmed the impact of gaining semantic insight into previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N1), and semantic processing (N400).
-While the enhancement of the N1 component, being more negative in response to objects for which participants were experiencing semantic insight, was present only during the critical presentation of the objects with their verbal descriptions (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after insight had taken place and the objects were presented again in Part III.
+Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N1), and semantic processing (N400).
+While the enhancement of the N1 component, being more negative for semantically informed as compared to naive perception, was present only during the critical presentation of the objects with their respective keywords (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after the information had been obtained and the objects were presented again (in Part III).
 This indicates a modulation of different stages of visual object perception through semantic knowledge, while and after an understanding of the object has been obtained.
-Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantic insight may reflect lowered semantic processing demands compared to unfamiliar objects which participants did not yet understand.
+Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantically informed perception may reflect lowered semantic processing demands compared to unfamiliar objects which participants did not yet understand.
 
@@
   position = factor(position, levels = c("Inverted", "Upright")),
-  condition = factor(condition, levels = c("Insight", "Naive", "Excl_insight", "Excl_naive", "Excl_known")),
+  condition = factor(condition, levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")),
   participant = factor(participant), item = factor(item)
@@
 
+# Remove the Python object to free up memory
+py_run_string("del epochs_exp3")
+import("gc")$collect()
+
 # Remove any trials from part IV
@@
 # Remove any trials excluded from conditions
-data_exp3 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
-
-# Contrast coding for position (inverted-updright), condition (insight-naive), and part (2-1, 3-1)
+data_exp3 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()
+
+# Contrast coding for position (inverted-updright), condition (informed-naive), and part (2-1, 3-1)
 t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
@@
   models_exp3,
-  stub_anova = c("Part", "Insight", "Position", "Pt. × ins.", "Pt. × pos.", "Ins. × pos.", "Pt. × ins. × pos."),
+  stub_anova = c("Part", "Condition", "Position", "Pt. × con.", "Pt. × pos.", "Ins. × pos.", "Pt. × con. × pos."),
   stub_contrasts = c(
@@
   caption = "Results of linear mixed-effects regression models for Experiment 3",
-  note = "Pt. = part, ins. = insight, pos. = position, est. = estimate, CI = confidence interval."
+  note = "Pt. = part, con. = condition, pos. = position, est. = estimate, CI = confidence interval."
 )

### 2020-10-18 analysis/manuscript.tex
update plots, change condition names

@@
 How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects, preceded either by valid information about their function (leading to semantically informed perception) or by misleading information (leading to naive perception).
-Capitalizing on the high temporal resolution of event-related potentials (ERPs), we investigated how different stages in the processing hierarchy are modulated by this semantic understanding of objects before, during, and after it has been acquired.
+In this study, we presented participants with unfamiliar objects, preceded in half of the cases by valid information about their function (leading to semantically informed perception) and in the other half of the cases by misleading information (leading to naive perception).
+Capitalizing on the high temporal resolution of event-related potentials (ERPs), we investigated if semantically informed versus naive perception led to differential effects at different stages in the processing hierarchy of visual objects.
+
+Learning semantic knowledge about objects has an influence on how we process them (Abdel Rahman \& Sommer, 2008; Gauthier et al., 2003; Gratton et al., 2009; Maier et al., 2014; Maier \& Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
+Recently, evidence has accumulated that it does so not only at ``higher'' stages in the visual processing hierarchy, i.e.~after ``lower'' stages of perceptual processing have been completed.
+It rather seems as though knowledge can also alter early processes, previously thought to be determined solely by the visual input itself, in a top-down manner.
+Such a top-down influence of semantic knowledge or expertise may manifest itself in behavioral changes such as improved visual matching (e.g.~Gauthier et al., 2003) and visual search performance (Holmes \& Wolff, 2012; Maier et al., 2014) when having learned that two objects share the same semantic category or verbal label.
+Furthermore, acquiring semantically meaningful knowledge about previously unfamiliar objects has been shown to increase their likelihood of gaining access to conuscious visual awareness under circumstances when attentional resources are limited (Weller et al., 2019).
+Although these behavioral effects hint at an early locus of semantic knowledge effects in object processing, they in and of themselves cannot convincingly demonstrate that not just downstream, postperceptual steps are being affected (Firestone \& Scholl, 2016).
+
+Stronger evidence comes from some of the above and other studies concurrently measuring event-related brain potentials (ERPs) while participants are performing different tasks on the objects about which they had previously acquired semantic knowledge.
+In their ERP study, (Abdel Rahman \& Sommer, 2008) had participants first learn in-depth knowledge about 20 unfamiliar objects by listening to a verbal descripition of the function of each object while it was presented visually on the screen, whereas for 20 different objects they did not receive any relevant semantic information, instead listening to unrelated cooking recipes while the objects were presented.
+As in the present study, the assignment of unfamiliar objects to either of the two conditions was counterbalanced ascross participants as to prevent any subsequent effects of semantic knowledge from being confounded with visual differences between the objects.
+In a separate test session, event-related potentials were measured while participants performed three different tasks on those objects (intermixed with well known objects that had not been part of the training session).
+ERP amplitudes in response to objects for which in-depth versus minimal knowledge had been acquired differed in the time window of the N400 component (300--500 ms after stimulus onset), typically associated with semantic processing, but, interestingly, aslo in the time window of the visual P1 component (100--150 ms after stimulus onset), typcially associated with lower-level visual processing {[}(Abdel Rahman \& Sommer, 2008); Experiment 1{]}.
+This effect ocurred across three different tasks (none of which explicitly required accessing any of the aqcuired information) and was qualitatively similar to the ERPs observed for untrained but well-known objects.
+A modulation of the P1 component has also been replicated using similar sets of objects in the above mentioned studies showing effects of object knowledge in visual search and the visual awareness tasks (Maier \& Rahman, 2019; Weller et al., 2019).
+It thus seems as though learning semantic information can influence steps of the processing hierarchy previously thought to be determined by the low-level visual input.
+
+A different strategy to investaige the influence of semantic knowledge on perception has been taken in a recent ERP study by (Samaha et al., 2018).
+Instead of using unfamiliar objects as stimuli, participants viewed images of familiar everyday objects that had been converted to two-tone ``Mooney'' images, making the object itself difficult to recognize.
+For half of the images, participants performed a semantic training where they were told which object to look for in each image.
+For the other half of images, they performed a perceptual (1-back) control task to equate the amount familiarity across all images.
+In a subsequent visual discrimination task, participants tended to respond faster and more accurate to the semantically trained images than to the perceptually trained ones {[}(Samaha et al., 2018); Experiment 4{]}.
+Crucially, the semantic training also manifested itself in increased pre-stimulus alpha-band power and larger P1 amplitudes at left temporo-occipital electrodes, further coroborating an early influence of semantically informed as compared to naive perception of objects.
+
+What all the previous studies have in common is that they investigated the effects of semantic knoweldge on object perception \emph{after} an extensive learning phase (Abdel Rahman \& Sommer, 2008; Gauthier et al., 2003; Maier et al., 2014; Maier \& Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Weller et al., 2019).
+Participants usually performed a seperate training session where they encountered each object together with its respective label or description multiple times.
+The EEG was usually not measured (or at least not analyzed and reported) during this training phase, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Rahman, 2019) or was even spread out across multiple days or weeks (Rossion et al., 2002, 2004).
+While designs with such substantive learning maximizes the chances of detecting even subtle top-down effects of the acquired knowledge, they necessarily leave at least three important conceptual questions unresolved.
+The first question is if we can detect any electrophysiological correlates of semantic insight, i.e.~the critical presentation during which an understanding of a previously unfamiliar or meaningless objects is happening, instead of asking if this understanding leads to differential effects later in an orthogonal task.
+The second question is how much learning is actually necessary before reliable top-down effects of knowledge (e.g.~on object-related P1 amplitudes) can be obtained: Does it actually take dozens of repitions per object or may a single exposure to the object together with the relevant semantic information be enough?
+The third and closely related question is related to one of the critiques sometimes raised against the nature of knowledge effects: Are they reflecting genuine top-down effects of semantic processes, altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been created or altered throughout the learning process?
+By measuring the ERPs before, during, and after participants received semantic hints about the unfamiliar objects, we hope to provide tentative answers to all of these questions.
 
@@
 Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
+No a priori power analysis was carreid out and the sample size was chosen according to the default for EEG studies in our lab at the time of data collection.
 All participants were right-handed according to the Edinburgh inventory (Oldfield, 1971) and reported normal or corrected-to-normal vision.
@@
 
-Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g.~a bicycle, a toothbrush), whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g.~a galvanometer, an udu drum).
-The well-known objects were included as filler stimuli of no interest.
-A list of the unfamiliar objects can be found in Appendix A.
+Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g.~a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g.~a galvanometer, an udu drum).
+A list of these unfamiliar objects can be found in Appendix A.
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a noun--verb pair was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g.~current--measuring, pottery--drumming).
-In the \emph{insight} condition, the presentation of each unfamiliar object was preceded by its respective description, whereas in the \emph{naive} condition, it was preceded by a non-matching description belonging to one of the other objects.
-In both conditions, the noun and the verb were presented one above the other in black letters on a light blue background.
-For each participant, half of the unfamiliar objects were presented in the insight condition (i.e.~with a matching description) and the other half were presented in the naive condition (i.e.~with a non-matching description).
+For each unfamiliar object, a pair of keywords---a noun and a verb---was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g.~current--measuring, pottery--drumming).
+As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects.
+The matching keywords were expected to induce semantically informed perception (i.e.~participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an effect and keep the perception of the object semantically naive.
 All participants saw each unfamiliar object in only one of the two conditions and the assignment of objects to conditions was counterbalanced across participants.
@@
 Each experimental session consisted of three parts (Figure \ref{fig:exp1-plot}A).
-In Part I, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without verbal descriptions.
+In the \emph{pre-insight} part (Part I), after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
 Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
@@
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
-Because we were interested in the acquisition of semantic knowledge about unfamiliar objects only, all objects for which the participant indicated knowing the object in Part I were excluded from further analysis (6.3\% of rare objects per participant).
 
@@
 \caption{Procedure and results of Experiment 1.
-\emph{(A)} In Part I, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In Part II, half of the objects were preceded by a matching description (in purple color for illustration), leading to semantic insight, and the other half with a non-matching description (in petrol color for illustration), leading to naive perception.
-In Part III, the same objects were presented again without the descriptions.
-\emph{(B)} Bar plots and \emph{(C)} ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III.
-Insight was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
-Error bars show the standard error of the mean.
+\emph{(A)} In the pre-insight part (Part I) participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In the insight part (Part II), half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
+In the post-insight part (Part III), the same objects were presented again without the keywords.
+\emph{(B)} ERP waveforms and scalp topographies separately for objects with semantically informed versus naive perception in Parts I, II, and III.
+Semantically informed perception was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
 Ampl.
@@
 
-In Part II, only the 120 unfamiliar objects were presented for a second time, now preceded either by a matching verbal description (in the insight condition) or by a non-matching verbal description (in the naive condition).
-Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the verbal description for 2.5 s.
+In the \emph{insight} part (Part II), only the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
 Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
 The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g.~medical devices, musical instruments).
-To make sure that insight did (did not) occur in the insight (naive) condition, we excluded any objects from the insight condition if participants indicated not knowing the object or having rather no assumption (despite reading the matching description) and any objects from the naive condition if participants indicated knowing the object or having an assumption (despite reading the non-matching description).
-This resulted in an average of 27.0 objects (44.9\%) per participant remaining in the insight condition and an average of 48.8 objects (81.2\%) per participant remaining in the naive condition.
 
-In Part III, the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e.~without the verbal descriptions.
-Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with descriptions), participants took a self-timed break and continued with the same block of 30 objects in Part III (without descriptions) before moving on to the next block consisting of 30 different objects.
+In the post-insight part (Part III), the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e.~without any keywords.
+Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with keywords), participants took a self-timed break and continued with the same block of 30 objects in Part III (without keywords) before moving on to the next block consisting of 30 different objects.
 They continued like this until all four blocks were completed in both Parts II and III.
@@
 
-Offline, the data were preprocessed using the MNE software (Version 0.21.0; Gramfort et al., 2013) in Python (Version 3.7.7; van Rossum \& Drake, 2009).
+Offline, the data were preprocessed using the MNE software (Version 0.21.0; Gramfort et al., 2013) in Python (Version 3.8.5; van Rossum \& Drake, 2009).
 First, all scalp electrodes were re-referenced to the common average.
 Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
-The first 15 components were extracted using the FastICA algorithm (Hyvärinen, 1999) after temporarily low-pass filtering the data at 1 Hz.
+The first 15 components were extracted by the FastICA algorithm (Hyvärinen, 1999) after temporarily low-pass filtering the data at 1 Hz.
 Those components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the \emph{find\_bads\_eog} function.
@@
 
-The event-related potentials were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018).
-For the purpose of the present study, these models have two desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in Part I (i.e.~before any keywords were presented), which led to the exclusion of an average of 7.5 objects per participant (6.3\%).
+Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in Part II) and the behavioral responses of the participants themselves (Figure 1A).
+Objects were assigned to the semantically informed condition only if they were presented with matching keywords \emph{and} if participants indicated knowing what the object was or having an assumption.
+This was the case for an average of 27.0 objects per participant (44.9\% of objects presented with matching keywords).
+Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords \emph{and} if participants indicated not knowing what the object was or having rather no assumption.
+This was the case for an average of 48.8 objects per participant (81.2\% of objects presented with non-matching keywords).
+Although the assignment was purely based on the manipulation and responses in Part II, when insight was thought to occurr, the same assignment was used to analyze the data from the other two parts.
+This allowed us to test on the one hand if the objects from both conditions differed in important aspects even before any keywords were presented (in Part I), and on the other hand if the semantic understanding acquired in Part II had any lasting effects on a subsequent, third presentation of the objects (in Part III).
+
+The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018).
+For the purpose of the present study, these models have at least two desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages.
 First, they can account simultaneously for the non-independence of data points coming from the same participant or from the same item, whereas the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
-Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is based on participants' own responses rather than on the experimental manipulation (e.g.~Fröber et al., 2017).
+Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is (co-)determined by the responses of the participants rather than by the experimental manipulation alone (e.g.~Fröber et al., 2017).
 
 Three separate models were computed predicting P1, N1, and N400 mean amplitudes, respectively.
-All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.~subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.~subtracting the naive from the insight condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
-For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to Schad et al.
-(2020).
+All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.~subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.~subtracting the naive from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
+For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to (Schad et al., 2020).
 To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects (Barr et al., 2013).
-We then performed a model selection algorithm as proposed by Matuschek et al.
-(2017) for increasing statistical power and avoiding overparameterization: Iteratively, each random effects was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+We then performed a model selection algorithm as proposed by (Matuschek et al., 2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effects was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
 Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model.
@@
 The model selection algorithm via likelihood ratio tests was performed using the buildmer package (Version 1.7.1; Voeten, 2020).
-Finally, to answer our research question of whether or not semantic insight had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the insight against the naive condition within Parts I, II, and III.
-Reported \emph{p} values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's methods as implemented in the lmerTest package (Kuznetsova et al., 2017).
+Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within Parts I, II, and III.
+All \emph{p} values subsequently reported were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's methods as implemented in the lmerTest package (Kuznetsova et al., 2017).
 
-The materials and code for the present experiments can be accessed via the Open Science Framework (\href{https://osf.io/myprojects/}{https://osf.io/\ldots/}).
+The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\href{https://osf.io/myprojects/}{https://osf.io/\ldots/}).
+To avoid potential misuse, the raw EEG are only made available by the corresponding author upon request.
 
@@
 \midrule
-Part & 10.89 (2, 24.5) & < .001 & 14.18 (2, 24.9) & < .001 & 32.85 (2, 25.6) & < .001\\
-Insight & 0.60 (1, 5343.5) & .438 & 0.30 (1, 24.2) & .586 & 13.00 (1, 24.4) & .001\\
-Pt. × ins. & 2.30 (2, 4605.1) & .100 & 4.84 (2, 4878.2) & .008 & 10.91 (2, 5120.9) & < .001\\
-\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Part I & -0.03 [-0.53, 0.47] & .913 & -0.12 [-0.68, 0.44] & .665 & -0.20 [-0.65, 0.26] & .400\\
-Part II & -0.18 [-0.68, 0.32] & .490 & -0.64 [-1.20, -0.08] & .026 & 0.93 [0.48, 1.39] & < .001\\
-Part III & 0.55 [0.05, 1.05] & .031 & 0.43 [-0.14, 0.99] & .136 & 1.00 [0.54, 1.46] & < .001\\
+Part & 10.82 (2, 24.5) & < .001 & 14.15 (2, 24.9) & < .001 & 33.01 (2, 25.5) & < .001\\
+Condition & 0.87 (1, 5302.9) & .351 & 0.89 (1, 114.3) & .349 & 13.09 (1, 24.8) & .001\\
+Pt. × con. & 2.40 (2, 4590.9) & .091 & 5.34 (2, 4853.1) & .005 & 11.18 (2, 5030.2) & < .001\\
+\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Part I & 0.00 [-0.50, 0.49] & .987 & -0.17 [-0.64, 0.30] & .485 & -0.20 [-0.65, 0.26] & .393\\
+Part II & -0.15 [-0.65, 0.34] & .550 & -0.66 [-1.14, -0.19] & .006 & 0.93 [0.48, 1.39] & < .001\\
+Part III & 0.57 [0.08, 1.07] & .023 & 0.41 [-0.07, 0.88] & .094 & 1.00 [0.55, 1.46] & < .001\\
 \bottomrule
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
+\normalsize{\textit{Note.} Pt. = part, con. = condition, est. = estimate, CI = confidence interval.}
 \end{tablenotes}
@@
 
-Averaged across conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.89, all \emph{p}s \textless{} .001 (Table \ref{tab:exp1-table}).
-In addition, N400 amplitudes differed between the insight and the naive conditions averaged across the three parts of the experiment, \emph{F}(1, 24.4) = 13.00, \emph{p} = .001.
-Crucially, the part × insight interaction was significant in the N1 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4605.1) = 2.30, \emph{p} = .100.
-To answer our main research question, we decomposed these interactions into the differences between the insight and the naive condition within the three different parts of the experiment.
+Averaged across conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.82, all \emph{p}s \textless{} .001 (Table \ref{tab:exp1-table}).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}NA = NA, \emph{p} = NA.
+Crucially, the part × condition interaction was significant in the N1 component, \emph{F}(2, 4853.1) = 5.34, \emph{p} = .005, and in the N400 component, \emph{F}(2, 5030.2) = 11.18, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4590.9) = 2.40, \emph{p} = .091.
+To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
 
-\hypertarget{effects-of-insight-in-part-i}{%
-\subsubsection{Effects of Insight in Part I}\label{effects-of-insight-in-part-i}}
+\hypertarget{erps-in-part-i-pre-insight}{%
+\subsubsection{ERPs in Part I (Pre-Insight)}\label{erps-in-part-i-pre-insight}}
 
-In Part I, when objects were unfamiliar to the participant and presented without verbal descriptions, no differences emerged between the insight and the naive condition in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .400 (Table \ref{tab:exp1-table}, Figure \ref{fig:exp1-plot}B \& C).
-On the one hand, this was to be expected given that the critical presentation of the objects with the descriptions (leading to semantic insight vs.~naive perception) had not yet taken place.
-On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of insight in Parts II and III cannot be explained solely by visual differences between the objects in the two conditions.
-Although the presentation of a matching or non-matching description for each object was counterbalanced across participants, the fact that different numbers of objects were excluded from the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor.
-If they did, however, one would expect to detect these differences even before any descriptions were presented, which we now know was not the case.
+In Part I, when objects were unfamiliar to the participant and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .393 (Table \ref{tab:exp1-table}, Figure \ref{fig:exp1-plot}B \& C).
+On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs.~naive perception) had not yet taken place.
+On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in Parts II and III cannot be accounted for by visual differences between the objects in the two conditions.
+Although the presentation of a matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor.
+If they did, however, one would expect to detect these differences even before any keywords were presented, which we have now seen was not the case.
 
-\hypertarget{effects-of-insight-in-part-ii}{%
-\subsubsection{Effects of Insight in Part II}\label{effects-of-insight-in-part-ii}}
+\hypertarget{erps-in-part-ii-insight}{%
+\subsubsection{ERPs in Part II (Insight)}\label{erps-in-part-ii-insight}}
 
-In Part II, half of the unfamiliar objects were presented with a matching verbal description (in the insight condition) and the other half were presented with a non-matching verbal description (in the naive condition).
-In response to objects for which participants experienced semantic insight, the amplitude of the N1 component was significantly enlarged (i.e.~more negative), \emph{b} = -0.64 µV, \emph{p} = .026, and the amplitude of the N400 component was significantly reduced (i.e.~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to objects which participants viewed naively.
-As in Part I, there were no reliable differences in the P1 component, \emph{p} = .490.
+In Part II, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
+When semantic information informed the perception of the object (akin to an insight experience), the amplitude of the N1 component was significantly enlarged (i.e.~more negative), \emph{b} = -0.66 µV, \emph{p} = .006, and the amplitude of the N400 component was significantly reduced (i.e.~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when an object was viewed naively without relevant semantic information.
+As in Part I, there were no reliable differences in the P1 component, \emph{p} = .550.
 
-\hypertarget{effects-of-insight-in-part-iii}{%
-\subsubsection{Effects of Insight in Part III}\label{effects-of-insight-in-part-iii}}
+\hypertarget{erps-in-part-iii-post-insight}{%
+\subsubsection{ERPs in Part III (Post-Insight)}\label{erps-in-part-iii-post-insight}}
 
-In Part III, the unfamiliar objects were presented for a third time, again without the verbal descriptions (as in Part I), to test whether the occurrence of semantic insight had any lasting effects on the processing of the objects.
-As in Part II, the N400 component remained significantly reduced in response to objects for which semantic insight had occurred, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the early effect of insight in the N1 component did not reoccur, \emph{p} = .136.
-Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e.~more positive) in response to objects for which semantic insight had occurred, \emph{b} = 0.55 µV, \emph{p} = .031.
+In Part III, the unfamiliar objects were presented for a third time, again without the keywords (as in Part I), to test whether the semantic information had any lasting effects on the processing of the objects.
+As in Part II, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the early effect in the N1 component did not reoccur, \emph{p} = .094.
+Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e.~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.57 µV, \emph{p} = .023.
 
@@
 
-In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they gained semantic insight into what kind of object they were seeing.
-To induce insight, half of the objects in Part II were preceded by a matching verbal description of the object's typical function or use, whereas the other half were preceded by a non-matching description (as a naive baseline condition).
+In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they were able to understand what kind of object they saw.
+To induce this semantically informed perception, half of the objects in Part II were preceded by matching verbal keywords about their typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
 
-Participants' experience of semantic insight in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing (Rossion \& Jacques, 2011; Tanaka \& Curran, 2001).
-The fact that this effect did not reoccur in Part III, when the objects were presented once more without descriptions, suggests it being a marker of semantic insight altering object processing online.
-In contrast, we also observed a modulation of the N400 component, which was reduced for objects when semantic insight was occurring (in Part II) and remained so when the same objects were presented repeatedly (in Part III).
+Participants' semantically informed perception of the objects in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing (Rossion \& Jacques, 2011; Tanaka \& Curran, 2001).
+The fact that this effect did not reoccur in Part III, when the objects were presented once more without keywords, suggests it being a marker of insight through semantic information that is altering object processing online.
+In contrast, we also observed a modulation of the N400 component, which was reduced for objects while insight was taking place (in Part II) and remained so when the same objects were presented repeatedly (in Part III).
 The N400 is most often discussed as an index of increased demands for semantic processing or integration (Kutas \& Federmeier, 2011; Lau et al., 2008; Rabovsky et al., 2018).
 Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had understood what kind of object they were viewing.
-Finally, semantic insight was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which semantic insight had occurred (in Part II).
-This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images (Samaha et al., 2018), may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had occurred.
+Finally, semantically informed perception was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which insight had occurred (in Part II).
+This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images (e.g.~Samaha et al., 2018), may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had occurred.
 
@@
 
-All materials, procedures, and methods for EEG recording and statistical analysis were identical to Experiment 1.
-An average of 5.8\% of rare objects per participant was classified as known in Part I and excluded from all further analyses.
-Based on participants' responses in Part II, an average of 26.4 objects were assigned to the insight condition (44.0\% of objects presented with a matching description) and an average of 49.2 objects were assigned to the naive condition (82.0\% of objects presented with a non-matching description).
-Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials (3.0\%) per participant (range 0 to 85).
+All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
+An average of 7.0 objects per participant (5.8\%) was classified as being known in Part I and excluded from all further analyses.
+Based on participants' responses in Part II, an average of 26.4 objects were assigned to the semantically informed condition (44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (82.0\% of objects presented with a non-matching description).
+Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials per participant (3.0\%, range 0 to 85).
 
@@
 \midrule
-Part & 17.45 (2, 5267.1) & < .001 & 16.57 (2, 25.1) & < .001 & 70.12 (2, 25.2) & < .001\\
-Insight & 0.02 (1, 5276.9) & .900 & 0.98 (1, 5228.5) & .322 & 19.95 (1, 5242.5) & < .001\\
-Pt. × ins. & 3.60 (2, 5267.1) & .027 & 1.25 (2, 4756.5) & .287 & 7.92 (2, 4714.9) & < .001\\
-\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Part I & -0.16 [-0.71, 0.40] & .582 & -0.03 [-0.53, 0.48] & .920 & 0.04 [-0.43, 0.50] & .877\\
-Part II & -0.48 [-1.03, 0.08] & .094 & -0.48 [-0.99, 0.03] & .064 & 1.33 [0.87, 1.79] & < .001\\
-Part III & 0.57 [0.01, 1.13] & .047 & 0.06 [-0.45, 0.57] & .818 & 0.47 [0.01, 0.93] & .047\\
+Part & 18.14 (2, 5151.1) & < .001 & 16.39 (2, 25.0) & < .001 & 70.58 (2, 25.2) & < .001\\
+Condition & 0.03 (1, 5272.5) & .853 & 1.23 (1, 5218.6) & .267 & 18.66 (1, 5207.5) & < .001\\
+Pt. × con. & 3.74 (2, 5151.2) & .024 & 1.34 (2, 4736.8) & .263 & 8.07 (2, 4637.6) & < .001\\
+\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Part I & -0.17 [-0.72, 0.38] & .552 & -0.04 [-0.53, 0.45] & .864 & 0.02 [-0.44, 0.48] & .936\\
+Part II & -0.49 [-1.04, 0.07] & .084 & -0.50 [-0.99, 0.00] & .050 & 1.31 [0.86, 1.77] & < .001\\
+Part III & 0.56 [0.01, 1.11] & .048 & 0.04 [-0.45, 0.54] & .865 & 0.45 [-0.01, 0.91] & .055\\
 \bottomrule
@@
 
-As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.57, all \emph{p}s \textless{} .001 (Table \ref{tab:exp2-table}).
-Also as in Experiment 1, N400 amplitudes differed between the insight and the naive condition averaged across parts, \emph{F}(1, 5242.5) = 19.95, \emph{p} \textless{} .001.
-The part × insight interaction was significant in the P1 component, \emph{F}(2, 5267.1) = 3.60, \emph{p} = .027, and in the N400 component, \emph{F}(2, 4714.9) = 7.92, \emph{p} \textless{} .001, but not in the N1 component, \emph{F}(2, 4756.5) = 1.25, \emph{p} = .287.
+As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.39, all \emph{p}s \textless{} .001 (Table \ref{tab:exp2-table}).
+Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}NA = NA, \emph{p} NA.
+The part × condition interaction was significant in the P1 component, \emph{F}(2, 5151.2) = 3.74, \emph{p} = .024, and in the N400 component, \emph{F}(2, 4637.6) = 8.07, \emph{p} \textless{} .001, but not in the N1 component, \emph{F}(2, 4736.8) = 1.34, \emph{p} = .263.
 
@@
 \caption{Results of Experiment 2.
-\emph{(A)} Bar plots and \emph{(B)} ERP waveforms and scalp topographies separately for objects for which participants experienced semantic insight and naive perception in Parts I, II, and III.
-In a direct replication of Experiment 1, the effect of semantic insight on the N400 component in Part II and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II and on the N400 component in Part III remained only marginally significant.
-Error bars show the standard error of the mean.
+ERP waveforms and scalp topographies separately for objects for which participants experienced semantically informed versus naive perception in Parts I, II, and III.
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in Parts II and III and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II remained only marginally significant.
 Ampl.
@@
 
-\hypertarget{effects-of-insight-in-part-i-1}{%
-\subsubsection{Effects of Insight in Part I}\label{effects-of-insight-in-part-i-1}}
+\hypertarget{erps-in-part-i-pre-insight-1}{%
+\subsubsection{ERPs in Part I (Pre-Insight)}\label{erps-in-part-i-pre-insight-1}}
 
-As in Experiment 1, no differences between objects in the insight and the naive condition emerged in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .582 (Table \ref{tab:exp2-table}, Figure \ref{fig:exp2-plot}).
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .552 (Table \ref{tab:exp2-table}, Figure \ref{fig:exp2-plot}).
 
-\hypertarget{effects-of-insight-in-part-ii-1}{%
-\subsubsection{Effects of Insight in Part II}\label{effects-of-insight-in-part-ii-1}}
+\hypertarget{erps-in-part-ii-insight-1}{%
+\subsubsection{ERPs in Part II (Insight)}\label{erps-in-part-ii-insight-1}}
 
-As in Experiment 1, the occurrence of semantic insight in Part II due to the presentation of objects with matching (vs.~non-matching) verbal descriptions was associated with a (marginally) significant enhancement of the N1 component, \emph{b} = -0.48 µV, \emph{p} = .064, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching versus non-matching keywords) was associated with a (marginally) significant enhancement of the N1 component, \emph{b} = -0.50 µV, \emph{p} = .050, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.
 
-\hypertarget{effects-of-insight-in-part-iii-1}{%
-\subsubsection{Effects of Insight in Part III}\label{effects-of-insight-in-part-iii-1}}
+\hypertarget{erps-in-part-iii-post-insight-1}{%
+\subsubsection{ERPs in Part III (Post-Insight)}\label{erps-in-part-iii-post-insight-1}}
 
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without verbal descriptions as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantic insight had occurred, \emph{b} = 0.57 µV, \emph{p} = .047.
-Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.47 µV, \emph{p} = .047.
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.56 µV, \emph{p} = .048.
+Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.45 µV, \emph{p} = .055.
 
@@
 Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast (i.e.~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al., 2020).
-This factor and its possible interactions with part, insight, and part × insight were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
+This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
 They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2.
@@
 Part & 12.38 (2, 49.0) & < .001 & 29.90 (2, 50.0) & < .001 & 95.34 (2, 50.6) & < .001\\
-Insight & 0.35 (1, 10560.3) & .552 & 1.65 (1, 125.3) & .202 & 38.72 (1, 10518.8) & < .001\\
+Condition & 0.35 (1, 10560.3) & .552 & 1.65 (1, 125.3) & .202 & 38.72 (1, 10518.8) & < .001\\
 Experiment & 0.35 (1, 48.2) & .555 & 2.38 (1, 48.1) & .129 & 4.75 (1, 48.4) & .034\\
-Pt. × ins. & 4.02 (2, 9042.4) & .018 & 5.60 (2, 9877.5) & .004 & 15.73 (2, 10010.1) & < .001\\
+Pt. × con. & 4.02 (2, 9042.4) & .018 & 5.60 (2, 9877.5) & .004 & 15.73 (2, 10010.1) & < .001\\
 Pt. × exp. & 0.03 (2, 49.0) & .971 & 0.55 (2, 50.0) & .581 & 2.58 (2, 50.6) & .085\\
 Ins. × exp. & 0.62 (1, 10536.2) & .432 & 0.04 (1, 10332.1) & .838 & 0.03 (1, 10574.9) & .865\\
-Pt. × ins. × exp. & 0.03 (2, 9042.9) & .972 & 0.62 (2, 9877.8) & .537 & 2.65 (2, 10010.4) & .070\\
-\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
+Pt. × con. × exp. & 0.03 (2, 9042.9) & .972 & 0.62 (2, 9877.8) & .537 & 2.65 (2, 10010.4) & .070\\
+\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
 Part I & -0.07 [-0.44, 0.30] & .699 & -0.10 [-0.44, 0.24] & .568 & -0.10 [-0.41, 0.20] & .507\\
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.}
+\normalsize{\textit{Note.} Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval.}
 \end{tablenotes}
@@
 
-As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all \emph{F}s \textgreater{} 12.38, all \emph{p}s \textless{} .001, as was the main effect of insight in the N400, \emph{F}(1, 10518.8) = 38.72, \emph{p} \textless{} .001.
-Furthermore, the part × insight interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 4.02, all \emph{p}s \textless{} .018.
-While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.75, \emph{p} = .034, the absence of any significant interactions of experiment with part or insight indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
+As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all \emph{F}s \textgreater{} 12.38, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}NA = NA, \emph{p} NA.
+Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 4.02, all \emph{p}s \textless{} .018.
+While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.75, \emph{p} = .034, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
 
-Based on the part × insight interaction, we again computed follow-up comparisons between the insight and the naive condition within each part, now collapsed across the data from both experiments.
-This confirmed the absence of any reliable differences between the two conditions in Part I, all \emph{p}s \textgreater{} .507, the significant enhancement of the N1 component in Part II, while insight was occurring, \emph{b} = -0.56 µV, \emph{p} = .002, the significant reduction of the N400 component in Part II, while insight was occurring, \emph{b} = 1.09 µV, \emph{p} \textless{} .001, and Part III, after insight had occurred, \emph{b} = 0.72 µV, \emph{p} = \textless{} .001, as well as the significant enhancement of the P1 component in Part III, after insight had occurred, \emph{b} = 0.49 µV, \emph{p} = .010.
+Based on the part × condition interaction, we again computed follow-up comparisons between the semantically inforemd and the naive condition within each part, now collapsed across the data from both experiments.
+This confirmed the absence of any reliable differences between the two conditions in Part I, all \emph{p}s \textgreater{} .507, the significant enhancement of the N1 component in Part II, while the semantic information was obtained, \emph{b} = -0.56 µV, \emph{p} = .002, the significant reduction of the N400 component in Part II, while the semantic information was obtained, \emph{b} = 1.09 µV, \emph{p} \textless{} .001, and Part III, after the information had been obtained, \emph{b} = 0.72 µV, \emph{p} = \textless{} .001, as well as the significant enhancement of the P1 component in Part III, after the information had been obtained, \emph{b} = 0.49 µV, \emph{p} = .010.
 
@@
 
-One may raise concerns whether the modulation of the N1 component in Part II genuinely reflects semantic insight for objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition.
-Remember that these objects were preceded by a non-matching description which was picked so that it could not be related to the object's visual features and their configuration.
+One may raise concerns whether the modulation of the N1 component in Part II genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition.
+Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the object's visual features and their configuration.
 Thus, the modulation of the ERP components in Part II may reflect a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages.
-To preclude this alternative explanation, we repeated the analysis above using a different baseline against which the objects in the insight condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the insight condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantic insight (note that the remaining objects were excluded as not being unfamiliar in the beginning of the experiment).
-Just as above, this control analysis revealed a robust enhancement of the N1 component associated with semantic insight in Part II, \emph{b} = -0.99 µV, \emph{p} \textless{} .001.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading descriptions or compared to objects presented with accurate descriptions on which participants failed to capitalize.
-Note that the reduction of the N400 component also remained robust in this control analysis, \emph{b} = 1.19 µV, \emph{p} \textless{} .001.
+To preclude this alternative explanation, we repeated the analysis above using a different baseline against which the objects in the semantically informed condition were contrasted.
+Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
+Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that the remaining objects to make it up to 100\% were excluded as not being unfamiliar in Part I of the experiment (see Statistical Analysis)} Just as above, this control analysis revealed a robust N1 effect in Part II, \emph{b} = -0.99 µV, \emph{p} \textless{} .001.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords on which participants failed to capitalize.
+Note that the reduction of the N400 component in Part II also remained robust in this control analysis, \emph{b} = 1.19 µV, \emph{p} \textless{} .001.
 
@@
 \begin{cslreferences}
+\leavevmode\hypertarget{ref-abdelrahman2008}{}%
+Abdel Rahman, R., \& Sommer, W.
+(2008).
+Seeing what we know and understand: How knowledge shapes perception.
+\emph{Psychonomic Bulletin \& Review}, \emph{15}(6), 1055--1063.
+\url{https://doi.org/10.3758/PBR.15.6.1055}
+
 \leavevmode\hypertarget{ref-americanelectroencephalographicsociety1991}{}%
@@
 
+\leavevmode\hypertarget{ref-firestone2016}{}%
+Firestone, C., \& Scholl, B.
+J.
+(2016).
+Cognition does not affect perception: Evaluating the evidence for ``top-down'' effects.
+\emph{Behavioral and Brain Sciences}, \emph{39}.
+\url{https://doi.org/10.1017/S0140525X15000965}
+
 \leavevmode\hypertarget{ref-fruxf6ber2017}{}%
@@
 
+\leavevmode\hypertarget{ref-gauthier2003}{}%
+Gauthier, I., James, T.
+W., Curby, K.
+M., \& Tarr, M.
+J.
+(2003).
+The influence of conceptual knowledge on visual discrimination.
+\emph{Cognitive Neuropsychology}, \emph{20}(3-6), 507--523.
+\url{https://doi.org/10.1080/02643290244000275}
+
 \leavevmode\hypertarget{ref-gramfort2013}{}%
@@
 \url{https://doi.org/10.3389/fnins.2013.00267}
+
+\leavevmode\hypertarget{ref-gratton2009}{}%
+Gratton, C., Evans, K.
+M., \& Federmeier, K.
+D.
+(2009).
+See what I mean?
+An ERP study of the effect of background knowledge on novel object processing.
+\emph{Memory \& Cognition}, \emph{37}(3), 277--291.
+\url{https://doi.org/10.3758/MC.37.3.277}
+
+\leavevmode\hypertarget{ref-holmes2012}{}%
+Holmes, K.
+J., \& Wolff, P.
+(2012).
+Does categorical perception in the left hemisphere depend on language?
+\emph{Journal of Experimental Psychology.
+General}, \emph{141}(3), 439--443.
+\url{https://doi.org/10.1037/a0027289}
 
@@
 
+\leavevmode\hypertarget{ref-maier2014}{}%
+Maier, M., Glage, P., Hohlfeld, A., \& Abdel Rahman, R.
+(2014).
+Does the semantic content of verbal categories influence categorical perception?
+An ERP study.
+\emph{Brain and Cognition}, \emph{91}, 1--10.
+\url{https://doi.org/10.1016/j.bandc.2014.07.008}
+
+\leavevmode\hypertarget{ref-maier2019}{}%
+Maier, M., \& Rahman, R.
+A.
+(2019).
+No matter how: Top-down effects of verbal and semantic category knowledge on early visual perception.
+\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{19}(4), 859--876.
+\url{https://doi.org/10.3758/s13415-018-00679-8}
+
 \leavevmode\hypertarget{ref-matuschek2017}{}%
@@
 
+\leavevmode\hypertarget{ref-rossion2002}{}%
+Rossion, B., Gauthier, I., Goffaux, V., Tarr, M.
+J., \& Crommelinck, M.
+(2002).
+Expertise training with novel objects leads to left-lateralized facelike electrophysiological responses.
+\emph{Psychological Science}.
+\url{https://journals.sagepub.com/doi/10.1111/1467-9280.00446}
+
 \leavevmode\hypertarget{ref-rossion2011}{}%
@@
 The N170: Understanding the time course of face perception in the human brain.
-In \emph{The oxford handbook of event-related potential components} (pp.
+In E.
+S.
+Kappenman \& S.
+J.
+Luck (Eds.), \emph{The Oxford handbook of event-related potential components} (pp.
 115--142).
@@
 \url{https://doi.org/10.1093/oxfordhb/9780195374148.001.0001}
+
+\leavevmode\hypertarget{ref-rossion2004}{}%
+Rossion, B., Kung, C.-C., \& Tarr, M.
+J.
+(2004).
+Visual expertise with nonface objects leads to competition with the early perceptual processing of faces in the human occipitotemporal cortex.
+\emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{101}(40), 14521--14526.
+\url{https://doi.org/10.1073/pnas.0405613101}
 
@@
 Voeten, C. C. (2020). \emph{buildmer: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
+
+\leavevmode\hypertarget{ref-weller2019}{}%
+Weller, P.
+D., Rabovsky, M., \& Abdel Rahman, R.
+(2019).
+Semantic knowledge enhances conscious awareness of visual objects.
+\emph{Journal of Cognitive Neuroscience}, \emph{31}(8), 1216--1226.
+\url{https://doi.org/10.1162/jocn_a_01404}
 \end{cslreferences}

### 2020-10-19 analysis/manuscript.Rmd
re-run with docker

@@
 } else {
-  # Import epoched data from Python
-  epochs_exp1 <- py$epochs_exp1$get_data()
   # Compute single-trial ERPs for Experiment 1
-  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>%
+  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp1$get_data(), els = els) %>%
     set_names(comps$name) %>%
@@
 
-# Remove the Python object to free up memory
+# Remove the epochs to free up memory
 py_run_string("del epochs_exp1")
@@
 } else {
-  # Import epochs from Python, converting Volts to Microvolts
-  epochs_exp2 <- py$epochs_exp2$get_data()
   # Compute single-trial ERPs for Experiment 2
-  data_exp2 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp2, els = els) %>%
+  data_exp2 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp2$get_data(), els = els) %>%
     set_names(comps$name) %>%
@@
 
-# Remove the Python object to free up memory
+# Remove the epochs to free up memory
 py_run_string("del epochs_exp2")
@@
 Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.^[Note that the remaining objects to make it up to 100% were excluded as not being unfamiliar in Part I of the experiment (see Statistical Analysis)] Just as above, this control analysis revealed a robust N1 effect in Part II, *b* = `r table_joint_control$conts["Part II", "N1_est"]` µV, *p* `r table_joint_control$conts["Part II", "N1_p"]`.
+Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N1 effect in Part II, *b* = `r table_joint_control$conts["Part II", "N1_est"]` µV, *p* `r table_joint_control$conts["Part II", "N1_p"]`.
 Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords on which participants failed to capitalize.
 Note that the reduction of the N400 component in Part II also remained robust in this control analysis, *b* = `r table_joint_control$conts["Part II", "N400_est"]` µV, *p* `r table_joint_control$conts["Part II", "N400_p"]`.
+
+[^1]: Note that the remaining objects to make it up to 100% were excluded as not being unfamiliar in Part I of the experiment (see Statistical Analysis)
 
@@
 } else {
-  # Import epochs from Python, converting Volts to Microvolts (takes a while)
-  epochs_exp3 <- py$epochs_exp3$get_data()
   # Compute single-trial ERPs for Experiment 3
-  data_exp3 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp3, els = els) %>%
+  data_exp3 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp3$get_data(), els = els) %>%
     set_names(comps$name) %>%
@@
 
-# Remove the Python object to free up memory
+# Remove the epochs to free up memory
 py_run_string("del epochs_exp3")
@@
 
+Although most of the previous studies in the object processing domain have focused on the P1 component as an index of semantic knowledge modulating perceptual processes, at least two studies provide evidence for top-down effects of meaningfulness on the visual N1 (or N170) component in response to schematic drawings of faces [@bentin2002] and objects [@beaucousin2011].
+Using a similar design as in the present study, drawings of distored faces elicited a facelike (i.e.
+enlarged) N170 component only after participants were primed with a vaild hint---in this case the same face with all of its visual features in place [@bentin2002].
+Similarly, N1 amplitudes in a global-local detection task where shown to be enhanced in response to line drawings of meaningful objects (a boat or a butterfly) as compared to visually matched by meaningless drawings of non-objects.
+Interestingly, this effect was reversed in polarity when participants had to focus on the smaller, constituent parts and ignoring the object which emerged out of their global arrangement, which may be interpreted as further evidence for a functional role of the N1 component in the holistic perception of an object and its early visual categorization, integrating across its visual features.
+
 \newpage

### 2020-11-03 analysis/manuscript.Rmd
rename N1 to N170

@@
 
-  The thesis was handed December 18, 2020 and has been supervised by Prof.
+  The thesis was handed in December 18, 2020 and has been supervised by Prof.
 Dr.
@@
 # Chunk options
-knitr::opts_chunk$set(include = FALSE, fig.align = "center", fig.out = "100%", fig.width = 10)
+knitr::opts_chunk$set(include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10)
 
@@
 How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects, preceded in half of the cases by valid information about their function (leading to semantically informed perception) and in the other half of the cases by misleading information (leading to naive perception).
-Capitalizing on the high temporal resolution of event-related potentials (ERPs), we investigated if semantically informed versus naive perception led to differential effects at different stages in the processing hierarchy of visual objects.
-
-Learning semantic knowledge about objects has an influence on how we process them [@abdelrahman2008; @gauthier2003; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
-Recently, evidence has accumulated that it does so not only at "higher" stages in the visual processing hierarchy, i.e. after "lower" stages of perceptual processing have been completed.
-It rather seems as though knowledge can also alter early processes, previously thought to be determined solely by the visual input itself, in a top-down manner.
-Such a top-down influence of semantic knowledge or expertise may manifest itself in behavioral changes such as improved visual matching [e.g.  @gauthier2003] and visual search performance [@maier2014; @holmes2012] when having learned that two objects share the same semantic category or verbal label.
-Furthermore, acquiring semantically meaningful knowledge about previously unfamiliar objects has been shown to increase their likelihood of gaining access to conuscious visual awareness under circumstances when attentional resources are limited [@weller2019].
-Although these behavioral effects hint at an early locus of semantic knowledge effects in object processing, they in and of themselves cannot convincingly demonstrate that not just downstream, postperceptual steps are being affected [@firestone2016].
-
-Stronger evidence comes from some of the above and other studies concurrently measuring event-related brain potentials (ERPs) while participants are performing different tasks on the objects about which they had previously acquired semantic knowledge.
-In their ERP study, [@abdelrahman2008] had participants first learn in-depth knowledge about 20 unfamiliar objects by listening to a verbal descripition of the function of each object while it was presented visually on the screen, whereas for 20 different objects they did not receive any relevant semantic information, instead listening to unrelated cooking recipes while the objects were presented.
-As in the present study, the assignment of unfamiliar objects to either of the two conditions was counterbalanced ascross participants as to prevent any subsequent effects of semantic knowledge from being confounded with visual differences between the objects.
-In a separate test session, event-related potentials were measured while participants performed three different tasks on those objects (intermixed with well known objects that had not been part of the training session).
-ERP amplitudes in response to objects for which in-depth versus minimal knowledge had been acquired differed in the time window of the N400 component (300--500 ms after stimulus onset), typically associated with semantic processing, but, interestingly, aslo in the time window of the visual P1 component (100--150 ms after stimulus onset), typcially associated with lower-level visual processing [[@abdelrahman2008]; Experiment 1].
-This effect ocurred across three different tasks (none of which explicitly required accessing any of the aqcuired information) and was qualitatively similar to the ERPs observed for untrained but well-known objects.
-A modulation of the P1 component has also been replicated using similar sets of objects in the above mentioned studies showing effects of object knowledge in visual search and the visual awareness tasks [@maier2019; @weller2019].
-It thus seems as though learning semantic information can influence steps of the processing hierarchy previously thought to be determined by the low-level visual input.
-
-A different strategy to investaige the influence of semantic knowledge on perception has been taken in a recent ERP study by [@samaha2018].
-Instead of using unfamiliar objects as stimuli, participants viewed images of familiar everyday objects that had been converted to two-tone "Mooney" images, making the object itself difficult to recognize.
-For half of the images, participants performed a semantic training where they were told which object to look for in each image.
-For the other half of images, they performed a perceptual (1-back) control task to equate the amount familiarity across all images.
-In a subsequent visual discrimination task, participants tended to respond faster and more accurate to the semantically trained images than to the perceptually trained ones [[@samaha2018]; Experiment 4].
-Crucially, the semantic training also manifested itself in increased pre-stimulus alpha-band power and larger P1 amplitudes at left temporo-occipital electrodes, further coroborating an early influence of semantically informed as compared to naive perception of objects.
-
-What all the previous studies have in common is that they investigated the effects of semantic knoweldge on object perception *after* an extensive learning phase [@abdelrahman2008; @gauthier2003; @maier2014; @maier2019; @rossion2002; @rossion2004; @samaha2018; @weller2019].
-Participants usually performed a seperate training session where they encountered each object together with its respective label or description multiple times.
-The EEG was usually not measured (or at least not analyzed and reported) during this training phase, which sometimes took place on a separate day [@abdelrahman2008; @maier2014; @maier2019] or was even spread out across multiple days or weeks [@rossion2002; @rossion2004].
-While designs with such substantive learning maximizes the chances of detecting even subtle top-down effects of the acquired knowledge, they necessarily leave at least three important conceptual questions unresolved.
-The first question is if we can detect any electrophysiological correlates of semantic insight, i.e. the critical presentation during which an understanding of a previously unfamiliar or meaningless objects is happening, instead of asking if this understanding leads to differential effects later in an orthogonal task.
-The second question is how much learning is actually necessary before reliable top-down effects of knowledge (e.g. on object-related P1 amplitudes) can be obtained: Does it actually take dozens of repitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is related to one of the critiques sometimes raised against the nature of knowledge effects: Are they reflecting genuine top-down effects of semantic processes, altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been created or altered throughout the learning process?
-By measuring the ERPs before, during, and after participants received semantic hints about the unfamiliar objects, we hope to provide tentative answers to all of these questions.
-
--   One paragraph explaining that previous research has shown that semantic knowledge modulates early stages of visual perception (e.g. Abdel Rahman & Sommer, 2008; Gauthier et al., 2003; Maier & Abdel Rahman, 2019; Maier et al., 2014; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka & Curran, 2001; Weller et al., 2019).
-
--   Potentially one paragraph describing Abdel Rahman & Sommer (2008) in more detail (participants acquiring knowledge about existing but unfamiliar objects).
-
--   One paragraph describing Samaha et al. (2018) in more detail (participants being trained to see familiar objects in otherwise meaningless images).
-Possibly hypothesize a special role of insight (= the moment when understanding is acquired), although this is not directly captured by the study.
-
--   One paragraph explaining how all of these studies measured ERPs only *after* an extensive learning phase, making it difficult to determine (a) how much learning is necessary for semantic knowledge to influence perception and, related to that, (b) if the modulation of early ERP components reflects genuine online effects of semantic knowledge or rather the activation of altered visual representations (Firestone & Scholl, 2015) (?).
-
--   One paragraph on theories of top-down/language effects on visual perception (reverse hierarchy theory).
-
--   Possibly another paragraph on theories of top-down effects on visual perception (label feedback hypothesis) if it fits thematically.
-
--   Do we need to refer to the role of attention already in the introduction? If so, potentially another paragraph here. I might prefer to leave that for the discussion.
-
--   Possibly one more paragraph on why ERPs are so suitable to answer this research question, including a brief characterization of the relevant components (P1: lower-level visual perception, N1: higher-level visual perception, N400: semantic processing).
-
--   The present study: Design of the study with a focus on distinguishing between online effects and altered representations; no specific hypotheses but looking for influences of semantic knowledge on the three ERP components at three different stages (before, during, and after acquisition).
+In this study, we presented participants with unfamiliar objects, preceded in half of the cases by valid information about their function, leading to semantically informed perception, and in the other half of the cases by misleading information, leading to naive perception.
+Capitalizing on the high temporal resolution of event-related brain potentials (ERPs), we investigated at which stages in the processing hierarchy semantically informed and naive perception of visual objects differed from one another.
+
+The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-standing debate.
+This debate revolves around the question whether or not our perception of the (visual) world should be thought of as an encapsulated module being completely determined by the visual input reaching our retina.
+According to the former view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [@firestone2016; @fodor1983; @fodor1984; @machery2015; @pylyshyn1999].
+Conversely, this view is challenged by theoretical and empirical work suggesting that perceptual processing dynamically interacts with other aspects of cognition from early on [@churchland1988; @churchland1994; @collins2014; @lupyan2012; @lupyan2015; @lupyan2020; @thierry2016; @vetter2014].
+These aspects may include transient states such as emotions [e.g.  @phelps2016; @bocanegra2009] or intentions [@balcetis2010; @cole2012] as well as learned capacities such as language [e.g.  @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g.  @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g.  @abdelrahman2008; @lin1997; @weller2019].
+Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained sceptical, pointing out important methodological shortcomings in large parts of this literature [@firestone2016].
+
+One productive way of investigating top-down effects of cognition on perception while addressing some of these concerns is through neurophysiological recording methods such as ERPs: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+This is because when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
+
+The visual P1 component refers to a positive deflection peaking approximately 100--150 ms after stimulus onset at occipital channels.
+It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri [@dirusso2001; @foxe2002; @mangun1995].
+The P1 is mostly thought to reflect the processing of low-level visual characteristics of the stimulus [such as size, luminance, and contrast; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception.
+It should be noted, however, that the P1 is reliably modulated by spatial [@luck2000; @mangun1995; @mangun1991] and non-spatial [@taylor2002] attention.
+
+The visual N170 (or N1) component refers to the negative deflection following the P1 and is maximal around 150--200 ms after stimulus onset at occipito-temporal channels.
+While still influenced by visual parameters of the stimulus [@johannes1995], it is also sensitive to selective attention, at least when participants are required to discriminate between different visual stimuli [@vogel2000; @mangun1991].
+Importantly, the N170 is enlarged (i.e. more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g. birds, dogs, or cars; @gauthier2003a; @tanaka2001].
+This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as their configuration [@eimer2011; @jacques2010; @rossion1999; @sagiv2001].
+Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimuli.
+
+Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018], starting approximately 300 ms after stimulus onset and being most pronounced at centro-parietal channels.
+A modulation of this component by cognitive capapacities such as knowedge can be taken as evidence for a post-perceptual influence on stimulus processing.
+
+Previous studies have focused on these and other ERP components to investiage which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
+Together, they suggest that not only higher-level semantic ERPs like the N400 component are influenced by acquiring semantic information about objects, but also early components that typcially reflect bottom-up visual processing.
+This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (cooking recipes) for the other half of the objects [@abdelrahman2008, Experiment 1].
+After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information.
+In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this has not been the case.
+Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
+Of note, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects.
+The modulation of the P1 component was also replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
+Of note, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink, which can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.
+
+A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects, which were rendered difficult to recognize by converting them to two-tone, "Mooney" images [@samaha2018, Experiment 4].
+Here, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the image beforehand, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
+When the EEG was measured in a separate delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images of objects than for perceptually-trained images of objects.
+This alternative approach further coroborates an early influence of semantic information on visual object perception.
+
+All the previously mentioned studies have in common that they investigated the effects of semantic knoweldge on object perception only *after* an extensive learning phase [@abdelrahman2008; @gauthier2003; @maier2014; @maier2019; @rossion2002; @rossion2004; @samaha2018; @weller2019].
+Participants performed one or multiple training session where they encountered each object together with its respective label or description multiple times.
+The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day [@abdelrahman2008; @maier2014; @maier2019] or were spread out across multiple days or weeks [@rossion2002; @rossion2004].
+While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three important conceptual questions unresolved.
+
+The first question is if we can detect any electrophysiological correlates of semantic insight, i.e. the critical presentation during which an understanding of the previously unfamiliar object is happening, instead of asking if this understanding leads to differential effects in an orthogonal task later on.
+The second question is how much learning is actually necessary before reliable top-down effects of knowledge (such as on object-related P1 amplitudes) can be obtained: Does it actually take dozens of repitions per object or may a single exposure to the object together with the relevant semantic information be enough?
+The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of semantics, altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects, having been altered throughout the learning process [@haber1966]?
+By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we hope to provide tentative answers to all three of these questions.
+
+In the two experiments subsequently reported, participants were presented with real-word objects that were presumed to be unfamiliar to most of them.
+They first viewed each of these objects once without any semantic information.
+This part served as a naive baseline to outrule that ERPs would differ in response to the objects based solely on their low-level visual differences.
+Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
+These keywords could either correctly describe the object's typical function, thus making it possible for participants to understand what kind of object they are viewing, or mislead them by describing the function of a different object, thus keeping the perception of the object semantically naive.
+During this "insight" part, we were able measure the online influence of semantic knowledge on object-evoked ERPs as it happened.
+Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them, thus mimicking previous studies [e.g.
+@abdelrahman2008, @samaha2018; @weller2019].
+In all three parts, we compared the influences of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (400--700 ms).
 
@@
   # Assign stimuli to conditions based on keywords and button presses
-  excl_known <- dat %>%
-    filter(part == "I" & Tastencode %in% c(201, 251)) %>%
-    pull(item)
-  excl_informed <- dat %>%
-    filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
-    pull(item)
-  excl_naive <- dat %>%
-    filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>%
-    pull(item)
-  informed <- dat %>%
-    filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
-    pull(item)
-  naive <- dat %>%
-    filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>%
-    pull(item)
+  excl_known <- dat %>% filter(part == "I" & Tastencode %in% c(201, 251)) %>% pull(item)
+  excl_informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
+  excl_naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
+  informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
+  naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
   # Create a new condition for the experimental condition
@@
     item %in% naive ~ "Naive"
-  ) %>%
-    factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
+  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
   # In Experiment 3, we need an additional column for position (upright vs. inverted)
@@
 # Check average number of stimuli per condition
-(stims_exp1 <- map(data_exp1, function(x) {
-  table(x$condition) / 3
-}) %>% bind_rows() %>% colMeans())
+(stims_exp1 <- map(data_exp1, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
+```
+
+```{r}
+# vec_participant <- data_exp1 %>% bind_rows() %>% pull(participant) %>% unique()
+# vec_participant <- c(vec_participant[seq(1, 23, 2)], vec_participant[seq(2, 24, 2)])
+# 
+# data_exp1 %>%
+#   bind_rows() %>%
+#   mutate(participant = factor(participant, levels = vec_participant),
+#          item_new = ifelse(participant %in% vec_participant[1:12], item - 15, item)) %>%
+#   filter(part == "II" & Tastencode != 0) %>%
+#   ggplot(aes(x = participant, y = item, fill = Tastencode)) +
+#   geom_raster() +
+#   scale_fill_viridis_c(begin = 0.1, end = 0.5)
+#   #scale_fill_manual(values = c("Informed" = "purple", "Naive" = "green", "Excl_informed" = "gray70", "Excl_naive" = "gray90", "Excl_known" = "white"))
 ```
@@
 
-# # Get indices of bad epochs despite ICA
-# rej_exp1 = epochs_exp1.drop_log
-# rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
-# rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
-
 # Define function to compute grand averages per condition
 def compute_evokeds(epochs):
-    evokeds = dict()
-    evokeds_dat = dict()
+    evokeds = dict(); evokeds_dat = dict()
     # Each part becomes a dictionary of conditions
     for pt in ["I", "II", "III"]:
-        evokeds[pt] = dict()
-        evokeds_dat[pt] = dict()
+        evokeds[pt] = dict(); evokeds_dat[pt] = dict()
         # Each condition becomes a list of participants
         for cn in ["Informed", "Naive"]:
-            evokeds[pt][cn] = list()
-            evokeds_dat[pt][cn] = list()
+            evokeds[pt][cn] = list(); evokeds_dat[pt][cn] = list()
             # For every participant we average trials separately for all parts and conditions
@@
 
+```{r exp1-tryout, eval=FALSE}
+# # Create vector of sample time points
+# times <- seq(py$preproc_params$tmin, py$preproc_params$tmax, 1 / py$epochs_exp1$info["sfreq"]) * 1000
+# 
+# # Average channels in the N170 ROI
+# py_run_string('epochs_roi = mne.channels.combine_channels(epochs_exp1, groups=dict(roi=mne.pick_channels(epochs_exp1.ch_names, ["P7", "P8", "PO7", "PO8", "PO9", "PO10"])))')
+# 
+# # Extract data for Part II from Python
+# dat <- py$epochs_exp1$metadata %>%
+#   as_tibble() %>%
+#   bind_cols(py$epochs_roi$get_data(picks = "roi") %>% drop() %>% as_tibble()) %>%
+#   pivot_longer(-c(part, condition, participant, item, RT), values_to = "amplitude") %>%
+#   filter(condition %in% c("Informed", "Naive")) %>%
+#   mutate(
+#     part(factor(part)),
+#     condition = factor(condition),
+#     participant = factor(participant),
+#     item = factor(item),
+#     time = rep(times, nrow(.) / length(times))
+#   )
+# 
+# # Compute LMM
+# library(lme4)
+# contrasts(dat$condition) <- contr.sum(2)
+# contrasts(dat$part) <- MASS::contr.sdif(3)
+# mod <- lmer(
+#   amplitude ~ part/condition + (part/condition|time:participant) + (part/condition|time:item),
+#   data = dat, control = lmerControl(calc.derivs = FALSE)
+# )
+# summary(mod)
+# 
+# # Predict values from LMM
+# probe <- expand.grid(
+#   part = unique(dat$part),
+#   condition = unique(dat$condition),
+#   participant = unique(dat$participant),
+#   item = unique(dat$item),
+#   time = dat$time %>% unique()
+# ) %>% mutate(amplitude = predict(mod, .))
+# 
+# # Plot real and modelled data
+# ggplot(mapping = aes(x = time, y = amplitude, color = condition)) +
+#   geom_line(data = dat, aes(group = interaction(condition, participant, item)), size = 0.1, alpha = 0.1) +
+#   stat_summary(data = probe, geom = "line", fun = mean, na.rm = TRUE, size = 1) +
+#   theme_minimal() +
+#   labs(x = "Time (ms)", y = "Predicted amplitude (µV)") +
+#   coord_cartesian(xlim = c(-200, 800), ylim = c(-15, 15), expand = FALSE)
+# 
+# # Old models
+# mod1_P1 <- lmerTest::lmer(P1 ~ part/condition + (part/condition|participant) + (part/condition|item),
+#                           data = data_exp1, control = ctrl_params)
+# mod1_N170 <- lmerTest::lmer(N170 ~ part/condition + (part/condition|participant) + (part/condition|item),
+#                           data = data_exp1, control = ctrl_params)
+# mod1_N400 <- lmerTest::lmer(N400 ~ part/condition + (part/condition|participant) + (part/condition|item),
+#                             data = data_exp1, control = ctrl_params)
+# mod2_P1 <- lmerTest::lmer(P1 ~ part/condition + (part/condition|participant) + (part/condition|item),
+#                           data = data_exp2, control = ctrl_params)
+# mod2_N170 <- lmerTest::lmer(N170 ~ part/condition + (part/condition|participant) + (part/condition|item),
+#                           data = data_exp2, control = ctrl_params)
+# mod2_N400 <- lmerTest::lmer(N400 ~ part/condition + (part/condition|participant) + (part/condition|item),
+#                             data = data_exp2, control = ctrl_params)
+# summary(mod1_P1)
+# summary(mod1_N170)
+# summary(mod1_N400)
+# summary(mod2_P1)
+# summary(mod2_N170)
+# summary(mod2_N400)
+```
+
 ```{r exp1-analysis}
@@
 # Check number of rejected epochs
-rejected_exp1 <- data_exp1 %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n)
+rejected_exp1 <- data_exp1 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
 mean(rejected_exp1)    # Mean
@@
 # Create vectors with sample time points (in ms) and electrodes
-tmin <- py$preproc_params$tmin * 1000
-tmax <- py$preproc_params$tmax * 1000
-sfreq <- py$epochs_exp1$info["sfreq"]
-times <- seq(tmin, tmax, 1000 / sfreq)
+times <- seq(py$preproc_params$tmin * 1000, py$preproc_params$tmax * 1000, 1 / py$epochs_exp1$info["sfreq"] * 1000)
 els <- py$epochs_exp1$ch_names
@@
 comps <- tibble(
-  name = c("P1", "N1", "N400"),
+  name = c("P1", "N170", "N400"),
   start = c(100, 150, 400),
@@
 (ref:figure-1-caption) Procedure and results of Experiment 1.
-*(A)* In the pre-insight part (Part I) participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+*(A)* In the pre-insight part (Part I), participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
 In the insight part (Part II), half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
 In the post-insight part (Part III), the same objects were presented again without the keywords.
-*(B)* ERP waveforms and scalp topographies separately for objects with semantically informed versus naive perception in Parts I, II, and III.
-Semantically informed perception was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
+*(B)* ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within Parts I, II, and III.
+Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
 Ampl.
@@
 ```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
-# Manually extract significance levels from contrasts for plotting
-stars_exp1 <- list(
-  P1 = c(I = NA, II = NA, III = "*"),
-  N1 = c(I = NA, II = "*", III = NA),
-  N400 = c(I = NA, II = "***", III = "***")
-)
-
-# Import grand averaged evoked potentials from Python
-evokeds_exp1 <- py$evokeds_dat_exp1
-
 # Retrieve locations for the relevant electrodes from standard montage
@@
   rename(electrode = value) %>%
-  left_join(read_tsv(fname_montage) %>% rename(electrode = Site)) %>%
+  left_join(read_tsv(fname_montage) %>% rename(electrode = Site), by = "electrode") %>%
   mutate(
@@
 
-# Read SVG file with the trial structure (created using MS PowerPoint)
-plot_trials <- grImport2::readPicture("analysis/manuscript_files/figure-1a.svg") %>%
-  grImport2::pictureGrob(expansion = 0)
-
-# Define function to plot trial structure
-plot_trial <- function() {
+# Trial structure
+plot_trials <- function(){
   require(magick)
-  colour_informed <- viridisLite::viridis(1, begin = 0.1, end = 0.1)
-  colour_naive <- viridisLite::viridis(1, begin = 0.5, end = 0.5)
-  trial_I <- ggplot() +
-    coord_fixed() +
-    theme_void() +
-    xlim(c(0, 74)) +
-    ylim(c(-5, 68)) +
-    geom_text(aes(x = 37, y = 68, label = "Part I"), size = 14 / .pt, family = "Helvetica", fontface = "bold") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
-    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
-    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
-    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")),
-                 color = "black")
-  trial_II <- ggplot() +
-    coord_fixed() +
-    theme_void() +
-    xlim(c(0, 74)) +
-    ylim(c(-5, 68)) +
-    geom_text(aes(x = 37, y = 68, label = "Part II"), size = 14 / .pt, family = "Helvetica", fontface = "bold") +
-    geom_rect(aes(xmin = 0, xmax = 20, ymin = 0, ymax = 20), color = "black", fill = "white") +
-    geom_text(aes(x = 10, y = 10.5, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
-    geom_text(aes(x = 10, y = -3, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = colour_informed, fill = "white") +
-    geom_text(aes(x = 28, y = 23, label = "Potato\nmashing"), color = colour_informed, size = 10 / .pt,
-              family = "Helvetica") +
-    geom_text(aes(x = 28, y = 10, label = "2.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 39, ymax = 59), color = colour_naive, fill = "white") +
-    geom_text(aes(x = 28, y = 49, label = "Message\nmorsing"), color = colour_naive, size = 10 / .pt,
-              family = "Helvetica") +
-    geom_text(aes(x = 28, y = 36, label = "or"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
-    geom_text(aes(x = 46, y = 34, label = "*"), size = 8, family = "Helvetica") +
-    geom_text(aes(x = 46, y = 23, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 54, xmax = 74, ymin = 39, ymax = 59), color = "black", fill = "white") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = 54, y = 39, width = 20, height = 20) +
-    geom_text(aes(x = 65, y = 36, label = "max. 3 s"), color = "black", size = 10 / .pt, family = "Helvetica",
-              lineheight = 1) +
-    geom_segment(aes(x = 28, y = 0, xend = 74, yend = 33.222), arrow = arrow(length = unit(0.2, "cm")),
-                 color = "black")
-  trial_III <- ggplot() +
-    coord_fixed() +
-    theme_void() +
-    xlim(c(0, 74)) +
-    ylim(c(-5, 68)) +
-    geom_text(aes(x = 37, y = 68, label = "Part III"), size = 14 / .pt, family = "Helvetica", fontface = "bold") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
-    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
-    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
-    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10 / .pt, family = "Helvetica") +
-    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")),
-                 color = "black")
-  plot_grid(trial_I, NULL, trial_II, NULL, trial_III, nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
-}
-
-# Define function to plot mean ERP amplitudes
-plot_bars <- function(data, stars, ymin) {
-  parts <- map(c("I", "II", "III"), function(part) {
-    # For which components in the current part do we have a significant effect?
-    sig <- map(stars, part) %>%
-      as.data.frame() %>%
-      t() %>%
-      as.data.frame() %>%
-      set_colnames("label") %>%
-      rownames_to_column("comp") %>%
-      na.omit()
-    # Create bar plot for the current part
-    map(c("P1", "N1", "N400"), function(comp) {
-      p <- data %>%
-        filter(part == !!part) %>%
-        Rmisc::summarySEwithin(measurevar = comp, withinvars = "condition", idvar = "participant") %>%
-        mutate(comp = !!comp) %>%
-        rename(amplitude = !!comp)
-    }) %>%
-      bind_rows() %>%
-      mutate(comp = fct_relevel(comp, "P1", "N1", "N400")) %>%
-      ggplot(aes(x = comp, y = amplitude, fill = condition)) +
-      # geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
-      # annotate("tile", x = sig$comp, y = -0.4, width = 0.45, height = 0.8, colour = "black", fill = "white", size = 0.5) +
-      # annotate("rect", xmin = -Inf, xmax = Inf, ymin = -0.2, ymax = Inf, fill = "white") +
-      # geom_bar(aes(y = amplitude - se - 0.2), stat = "identity", position = position_dodge()) + scale_fill_manual(values = c("white", "white")) +
-      # new_scale_fill() +
-      # annotate("label", x = sig$comp, y = -0.96, label = sig$label, size = 7, family = "Helvetica", label.size = 0) +
-      geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
-      scale_fill_viridis_d(begin = 0.1, end = 0.5) +
-      geom_errorbar(aes(ymin = amplitude - se, ymax = amplitude + se),
-                    position = position_dodge(width = 0.9), width = 0.5) +
-      annotate("text", x = sig$comp, y = ymin, label = sig$label, size = 6, family = "Helvetica") +
-      geom_hline(yintercept = 0) +
-      coord_cartesian(ylim = c(ymin, ymin + 7)) +
-      ylab("ROI ampl.\n(µV)") +
-      scale_y_continuous(breaks = seq(trunc(ymin), trunc(ymin) + 6, 2)) +
-      theme_classic() +
-      theme(
-        legend.position = "none",
-        panel.grid = element_blank(),
-        axis.ticks = element_line(color = "black"),
-        axis.title.x = element_blank(),
-        axis.title.y = element_text(family = "Helvetica", color = "black", size = 10),
-        axis.text = element_text(family = "Helvetica", color = "black", size = 10),
-        plot.margin = margin(t = 0.3, r = 0, b = 0.4, l = 0.2, "cm")
-      )
-  })
-  plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
+  color_informed <- viridisLite::viridis(1, begin = 0.1)
+  color_naive <- viridisLite::viridis(1, begin = 0.5)
+  ggplot() +
+    coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
+    ## PART II ##
+    # Title
+    annotate("text", x = 0, y = 97.2, label = "Part II (insight)", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
+    # Arrow
+    annotate("segment", x = -30, xend = 24, y = 79, yend = 85, arrow = arrow(length = unit(0.1, "inches"))) +
+    # Squares
+    annotate("rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75, color = "black", fill = "white") +
+    annotate("rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65, color = color_informed, fill = "white") +
+    annotate("rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89, color = color_naive, fill = "white") +
+    annotate("rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79, color = "black", fill = "white") +
+    annotate("rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81, color = "black", fill = "white") +
+    annotate("text", x = -27, y = 65.3, label = "+", size = 20 / .pt, family = "Helvetica") +
+    annotate("text", x = -9, y = 55, label = "Potato\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
+    annotate("text", x = -9, y = 79, label = "Message\nmorsing", size = 10 / .pt, family = "Helvetica", color = color_naive) +
+    annotate("text", x = 9, y = 67, label = "*", size = 30 / .pt, family = "Helvetica") +
+    draw_image("analysis/manuscript_files/potato_masher.png", x = 18, y = 62, width = 18, height = 18) +
+    # Timings
+    annotate("text", x = -9, y = 67.3, label = "or", size = 10 / .pt, family = "Helvetica") +
+    annotate("text", x = -27, y = 52, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
+    annotate("text", x = -9, y = 42, label = "2.5 s", size = 10 / .pt, family = "Helvetica") +
+    annotate("text", x = 9, y = 56, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
+    annotate("text", x = 27, y = 56.3, label = "3 s or\nresponse", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
+    # Response options
+    annotate("segment", x = 27, y = 39, xend = 27, yend = 51.5) +
+    annotate("segment", x = 0, y = 39, xend = 27, yend = 39) +
+    annotate("segment", x = 0, y = 35, xend = 0, yend = 39) +
+    annotate("segment", x = -32, y = 35, xend = 32, yend = 35) +
+    annotate("segment", x = -32, y = 30.5, xend = -32, yend = 35) +
+    annotate("segment", x = -12, y = 32, xend = -12, yend = 35) +
+    annotate("segment", x = 12, y = 32, xend = 12, yend = 35) +
+    annotate("segment", x = 32, y = 32, xend = 32, yend = 35) +
+    annotate("text", x = -32, y = 26, label = "A. \"I know\nwhat this is\"", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
+    annotate("text", x = -12, y = 26, label = "B. \"I have an\nassumption\nwhat this is\"", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
+    annotate("text", x = 12, y = 26, label = "C. \"I have rather\nno assumption\nwhat this is\"", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
+    annotate("text", x = 32, y = 26, label = "D. \"I don\'t\n know what\nthis is\"", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
+    # Conditions
+    annotate("segment", x = -32, y = 17, xend = -32, yend = 22, color = color_informed) +
+    annotate("segment", x = -12, y = 17, xend = -12, yend = 20, color = color_informed) +
+    annotate("segment", x = 12, y = 17, xend = 12, yend = 20, color = color_naive) +
+    annotate("segment", x = 32, y = 17, xend = 32, yend = 20, color = color_naive) +
+    annotate("segment", x = -32, y = 17, xend = -12, yend = 17, color = color_informed) +
+    annotate("segment", x = 12, y = 17, xend = 32, yend = 17, color = color_naive) +
+    annotate("segment", x = -22, y = 15, xend = -22, yend = 17, color = color_informed) +
+    annotate("segment", x = 22, y = 15, xend = 22, yend = 17, color = color_naive) +
+    annotate("text", x = -22, y = 13, label = "Informed condition", size = 10 / .pt, family = "Helvetica", fontface = "bold", color = color_informed) +
+    annotate("text", x = 22, y = 13, label = "Naive condition", size = 10 / .pt, family = "Helvetica", fontface = "bold", color = color_naive) +
+    annotate("text", x = -22, y = 7.9, label = "Matching keywords\nand response A or B", size = 10 / .pt, family = "Helvetica", color = color_informed, lineheight = 1) +
+    annotate("text", x = 22, y = 7.9, label = "Non-matching keywords\nand response C or D", size = 10 / .pt, family = "Helvetica", color = color_naive, lineheight = 1) +
+    ## PART I ##
+    # Title
+    annotate("text", x = -72, y = 56, label = "Part I (pre-insight)", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
+    # Arrow
+    annotate("segment", x = -84, xend = -66, y = 46, yend = 48, arrow = arrow(length = unit(0.1, "inches"))) +
+    # Squares
+    annotate("rect", xmin = -91, xmax = -71, ymin = 22, ymax = 42, color = "black", fill = "white") +
+    annotate("rect", xmin = -53, xmax = -73, ymin = 24, ymax = 44, color = "black", fill = "white") +
+    annotate("text", x = -81, y = 32.3, label = "+", size = 20 / .pt, family = "Helvetica") +
+    draw_image("analysis/manuscript_files/potato_masher.png", x = -72, y = 25, width = 18, height = 18) +
+    # Timings
+    annotate("text", x = -81, y = 19, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
+    annotate("text", x = -63, y = 19.3, label = "3 s or\nresponse", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
+    # Conditions
+    annotate("text", x = -72, y = 7.9, label = "Objects classified according\nto conditions in Part II", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
+    # PART III
+    # Title
+    annotate("text", x = 72, y = 56, label = "Part III (post-insight)", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
+    # Arrow
+    annotate("segment", x = 60, xend = 78, y = 46, yend = 48, arrow = arrow(length = unit(0.1, "inches"))) +
+    # Squares
+    annotate("rect", xmin = 53, xmax = 73, ymin = 22, ymax = 42, color = "black", fill = "white") +
+    annotate("rect", xmin = 71, xmax = 91, ymin = 24, ymax = 44, color = "black", fill = "white") +
+    annotate("text", x = 63, y = 32.3, label = "+", size = 20 / .pt, family = "Helvetica") +
+    draw_image("analysis/manuscript_files/potato_masher.png", x = 72, y = 25, width = 18, height = 18) +
+    # Timings
+    annotate("text", x = 63, y = 19, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
+    annotate("text", x = 81, y = 19.3, label = "3 s or\nresponse", size = 10 / .pt, family = "Helvetica", lineheight = 1) +    
+    # Conditions
+    annotate("text", x = 72, y = 7.9, label = "Objects classified according\nto conditions in Part II", size = 10 / .pt, family = "Helvetica", lineheight = 1) +    
+    theme_void()
 }
@@
 # Define function to plot ERP waveforms and topographies
-plot_erps <- function(comps, evokeds, montage, stars) {
+plot_erps <- function(comps, evokeds, models, montage) {
   suppressWarnings(suppressMessages(
     pmap(comps, function(name, start, stop, roi) {
-      # N400 gets a different scale than P1 and N1
+      # N400 gets a different scale than P1 and N170
       ymin <- ifelse(name == "N400", -3, -4)
@@
               mutate(.time = times, roi = rowMeans(select(., all_of(roi))))
-          }) %>%
-          bind_rows(.id = "condition")
+          }) %>% bind_rows(.id = "condition")
         # Shade background depending on whether the effect is significant or not
-        star <- stars[[name]][[part]]
-        if (is.na(star)) {
-          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.9, color = "black", fill = NA)
+        asterisks <- models[[name]]$contrasts %>%
+          filter(part == !!part) %>%
+          mutate(asterisks = case_when(p.value < .001 ~ "***", p.value < .01 ~ "**", p.value < .05 ~ "*")) %>%
+          pull(asterisks)
+        xasterisks <- case_when(str_length(asterisks) == 1 ~ start + 11, str_length(asterisks) == 3 ~ start + 15)
+        if (is.na(asterisks)) {
+          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = NA)
         } else {
-          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.9, color = "black", fill = "gray90")
-        }
-        xstar <- case_when(str_length(star) == 1 ~ start + 11, str_length(star) == 3 ~ start + 15)
+          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = "gray90")
+        }
+
         # # Prepare waveform
@@
           shade +
-          annotate("text", label = star, x = xstar, y = ymin + 11, size = 6, hjust = 0, family = "Helvetica") +
+          annotate("text", label = asterisks, x = xasterisks, y = ymin + 11, size = 6, hjust = 0, family = "Helvetica") +
           annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
@@
 # Creata a combined legend and colorbar
-legends <- function(direction){
-  if (direction == "vertical"){mar <- margin(l = 6, r = 4, b = 10, t = 6); vjust <- 3.5}
-  else {mar <- margin(l = 5, r = 14, b = 3, t = 5); vjust <- 0.7}
+plot_legends_erps <- function(direction) {
+  if (direction == "vertical") {
+    mar <- margin(l = 12, r = 10, b = 6, t = 7); vjust <- 3.5
+  }
+  else {
+    mar <- margin(l = 8, r = 12, b = 4, t = 6); vjust <- 0.7
+  }
   get_legend(
@@
       labs(color = "Conditions", fill = "Informed - naive (µV)") +
-      scale_color_viridis_d(
-        begin = 0.1, end = 0.5,
-        guide = guide_legend(direction = "vertical", title.position = "top")
-      ) +
-      scale_fill_viridis_c(
-        guide = guide_colorbar(direction = direction, ticks = FALSE, title.position = "top", title.vjust = vjust)
-      ) +
+      scale_color_viridis_d(begin = 0.1, end = 0.5, guide = guide_legend(direction = "vertical", title.position = "top")) +
+      scale_fill_viridis_c(guide = guide_colorbar(direction = "horizontal", ticks = FALSE, title.position = "top", title.vjust = vjust)) +
       theme(
@@
         legend.key = element_rect(fill = NA),
-        legend.key.width = unit(0.8, "cm"),
+        legend.key.width = unit(0.7, "cm"),
         legend.key.height = unit(0.4, "cm"),
         legend.spacing.x = unit(0.3, "cm")
-      ))
+      )
+  )
 }
@@
 plot_grid(
-  #plot_trial(),
-  plot_trials,
-  #plot_bars(data = data_exp1, stars = stars_exp1, ymin = -1.5),
-  plot_erps(comps = comps, evokeds = evokeds_exp1, montage = montage, stars = stars_exp1),
-  #plot_legends(),
-  #nrow = 4, rel_heights = c(3, 2, 6, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica"
+  plot_trials(),
+  plot_erps(comps = comps, evokeds = py$evokeds_dat_exp1, models = models_exp1, montage = montage),
   nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
-  #nrow = 4, rel_heights = c(4, 2, 5, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica"
-) + # Add some lines to separate the parts (+ the legends)
-  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.52, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.52, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.52, yend = 0.57, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.52, yend = 0.57, linetype = "dashed") +  
-  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.57, yend = Inf, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.57, yend = Inf, linetype = "dashed") +
-  draw_plot(legends(direction = "vertical"), x = 0.41, y = 0.397, width = 1, height = 1)
+) + # Add some lines (to separate the parts) and the legend
+  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.53, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.53, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.53, yend = 0.58, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.53, yend = 0.58, linetype = "dashed") +  
+  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.58, yend = Inf, linetype = "dashed") +
+  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.58, yend = Inf, linetype = "dashed") +
+  draw_plot(plot_legends_erps(direction = "vertical"), x = 0.405, y = 0.422, width = 1, height = 1)
 ```
@@
 This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials (`r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`) per participant (range `r min(rejected_exp1)` to `r max(rejected_exp1)`).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N1 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
 
@@
 
-Three separate models were computed predicting P1, N1, and N400 mean amplitudes, respectively.
+Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
 All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e. subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e. subtracting the naive from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
@@
 The objects were analyzed according to this manipulation in combination with participants' self-report in Part II (Figure 1A), thus making sure that semantically informed (or naive) perception did indeed occur.
-The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N1 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.
+The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N170 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.
 
@@
       "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)
-    ) %>%
-      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
-      set_rownames(c(stub_anova))
+    ) %>% mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>% set_rownames(c(stub_anova))
   })
@@
       "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)
-    ) %>%
-      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
-      set_rownames(stub_contrasts)
+    ) %>% mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>% set_rownames(stub_contrasts)
   })
@@
     apa_table(
-      col.names = cnames, col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N1}" = 4:5, "\\textbf{N400}" = 6:7),
+      col.names = cnames, col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N170}" = 4:5, "\\textbf{N400}" = 6:7),
       midrules = nrow(anov_print), font_size = "footnotesize", align = "lcccccc", escape = FALSE,
@@
   stub_anova = c("Part", "Condition", "Pt. × con."),
-  stub_contrasts = c("Part I", "Part II", "Part III"),
+  stub_contrasts = c("Part I (pre-insight)", "Part II (insight)", "Part II (post-insight)"),
   caption = "Results of linear mixed-effects regression models for Experiment 1",
@@
 
-Averaged across conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all *F*s \> `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (Table \@ref(tab:exp1-table)).
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s \> `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (Table \@ref(tab:exp1-table)).
 In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r table_exp1$anov["Informed", "N400_df"]` = `r table_exp1$anov["Informed", "N400_f"]`, *p* = `r table_exp1$anov["Informed", "N400_p"]`.
-Crucially, the part × condition interaction was significant in the N1 component, *F*`r table_exp1$anov["Pt.
-× con.", "N1_df"]` = `r table_exp1$anov["Pt.
-× con.", "N1_f"]`, *p* = `r table_exp1$anov["Pt.
-× con.", "N1_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt.
+Crucially, the part × condition interaction was significant in the N170 component, *F*`r table_exp1$anov["Pt.
+× con.", "N170_df"]` = `r table_exp1$anov["Pt.
+× con.", "N170_f"]`, *p* = `r table_exp1$anov["Pt.
+× con.", "N170_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt.
 × con.", "N400_df"]` = `r table_exp1$anov["Pt.
@@
 
-In Part I, when objects were unfamiliar to the participant and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N1, or N400 component, all *p*s \> `r table_exp1$conts["Part I", "N400_p"]` (Table \@ref(tab:exp1-table), Figure \@ref(fig:exp1-plot)B & C).
+In Part I, when objects were unfamiliar to the participant and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s \> `r table_exp1$conts["Part I (pre-insight)", "N400_p"]` (Table \@ref(tab:exp1-table), Figure \@ref(fig:exp1-plot)B & C).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
@@
 In Part II, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object (akin to an insight experience), the amplitude of the N1 component was significantly enlarged (i.e. more negative), *b* = `r table_exp1$conts["Part II", "N1_est"]` µV, *p* = `r table_exp1$conts["Part II", "N1_p"]`, and the amplitude of the N400 component was significantly reduced (i.e. less negative), *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`, compared to when an object was viewed naively without relevant semantic information.
-As in Part I, there were no reliable differences in the P1 component, *p* = `r table_exp1$conts["Part II", "P1_p"]`.
+When semantic information informed the perception of the object (akin to an insight experience), the amplitude of the N170 component was significantly enlarged (i.e. more negative), *b* = `r table_exp1$conts["Part II (insight)", "N170_est"]` µV, *p* = `r table_exp1$conts["Part II (insight)", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e. less negative), *b* = `r table_exp1$conts["Part II (insight)", "N400_est"]` µV, *p* `r table_exp1$conts["Part II (insight)", "N400_p"]`, compared to when an object was viewed naively without relevant semantic information.
+As in Part I, there were no reliable differences in the P1 component, *p* = `r table_exp1$conts["Part II (insight)", "P1_p"]`.
 
@@
 In Part III, the unfamiliar objects were presented for a third time, again without the keywords (as in Part I), to test whether the semantic information had any lasting effects on the processing of the objects.
-As in Part II, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Part III", "N400_est"]` µV, *p* `r table_exp1$conts["Part III", "N400_p"]`, whereas the early effect in the N1 component did not reoccur, *p* = `r table_exp1$conts["Part III", "N1_p"]`.
-Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e. more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Part III", "P1_est"]` µV, *p* = `r table_exp1$conts["Part III", "P1_p"]`.
+As in Part II, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Part II (post-insight)", "N400_est"]` µV, *p* `r table_exp1$conts["Part II (post-insight)", "N400_p"]`, whereas the early effect in the N170 component did not reoccur, *p* = `r table_exp1$conts["Part II (post-insight)", "N170_p"]`.
+Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e. more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Part II (post-insight)", "P1_est"]` µV, *p* = `r table_exp1$conts["Part II (post-insight)", "P1_p"]`.
 
@@
 
-Participants' semantically informed perception of the objects in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001].
+Participants' semantically informed perception of the objects in Part II was associated with a significantly enlarged N170 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001].
 The fact that this effect did not reoccur in Part III, when the objects were presented once more without keywords, suggests it being a marker of insight through semantic information that is altering object processing online.
@@
 # Check average number of stimuli per condition
-(stims_exp2 <- map(data_exp2, function(x) {
-  table(x$condition) / 3
-}) %>% bind_rows() %>% colMeans())
+(stims_exp2 <- map(data_exp2, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
 ```
@@
     epochs_exp2 = [
-        preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
-        for fname, meta in zip(fnames_exp2, metadata_exp2)
+        preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp2, metadata_exp2)
     ]
@@
     epochs_exp2.save("analysis/export/exp2-epo.fif")
-
-# # Get indices of bad epochs despite ICA
-# rej_exp2 = epochs_exp2.drop_log
-# rej_exp2[:] = [item for item in rej_exp2 if item != ['IGNORED']]
-# rej_exp2 = [i for i in range(len(rej_exp2)) if rej_exp2[i] != []]
 
@@
 # Check number of rejected epochs
-rejected_exp2 <- data_exp2 %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n)
+rejected_exp2 <- data_exp2 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
 mean(rejected_exp2)    # Mean
@@
   stub_anova = c("Part", "Condition", "Pt. × con."),
-  stub_contrasts = c("Part I", "Part II", "Part III"),
+  stub_contrasts = c("Part I (pre-insight)", "Part II (insight)", "Part II (post-insight)"),
   caption = "Results of linear mixed-effects regression models for Experiment 2",
@@
 
-As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all *F*s \> `r table_exp2$anov["Part", "N1_f"]`, all *p*s `r table_exp2$anov["Part", "N1_p"]` (Table \@ref(tab:exp2-table)).
+As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all *F*s \> `r table_exp2$anov["Part", "N170_f"]`, all *p*s `r table_exp2$anov["Part", "N170_p"]` (Table \@ref(tab:exp2-table)).
 Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, *F*`r table_exp2$anov["Informed", "N400_df"]` = `r table_exp2$anov["Informed", "N400_f"]`, *p* `r table_exp2$anov["Informed", "N400_p"]`.
@@
 × con.", "N400_f"]`, *p* `r table_exp2$anov["Pt.
-× con.", "N400_p"]`, but not in the N1 component, *F*`r table_exp2$anov["Pt.
-× con.", "N1_df"]` = `r table_exp2$anov["Pt.
-× con.", "N1_f"]`, *p* = `r table_exp2$anov["Pt.
-× con.", "N1_p"]`.
+× con.", "N400_p"]`, but not in the N170 component, *F*`r table_exp2$anov["Pt.
+× con.", "N170_df"]` = `r table_exp2$anov["Pt.
+× con.", "N170_f"]`, *p* = `r table_exp2$anov["Pt.
+× con.", "N170_p"]`.
 
 (ref:figure-2-caption) Results of Experiment 2.
-ERP waveforms and scalp topographies separately for objects for which participants experienced semantically informed versus naive perception in Parts I, II, and III.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in Parts II and III and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II remained only marginally significant.
+ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within Parts I, II, and III.
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in Parts II and III and on the P1 component in Part III remained statistically significant, while the effect on the N170 component in Part II remained only marginally significant (*p* = `r table_exp2$conts["Part II (insight)", "N170_p"]`).
 Ampl.
 = amplitude.\newline\**p* \< .05.
+\*\**p* \< .01.
 \*\*\**p* \< .001.
@@
 ```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:figure-2-caption)"}
-# Manually extract significance levels from contrasts for plotting
-stars_exp2 <- list(
-  P1 = c(I = NA, II = NA, III = "*"),
-  N1 = c(I = NA, II = NA, III = NA),
-  N400 = c(I = NA, II = "***", III = "*")
-)
-
-# Import grand averaged evoked potentials from Python
-evokeds_exp2 <- py$evokeds_dat_exp2
-
 # Create headings for Parts I, II, and III
-plot_headings <- function(){
+plot_headings <- function(spacing){
   plot_grid(
@@
     ggplot() + annotate("text", label = "Part III (post-insight)", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(),
-    nrow = 1, rel_widths = c(10, 1, 10, 1, 10)
+    nrow = 1, rel_widths = spacing
   )
@@
   #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
-  plot_headings(),
-  plot_erps(comps = comps, evokeds = evokeds_exp2, montage = montage, stars = stars_exp2),
-  legends(direction = "horizontal"),
+  plot_headings(spacing = c(10, 1, 10, 1, 10)),
+  plot_erps(comps = comps, evokeds = py$evokeds_dat_exp2, models = models_exp2, montage = montage),
+  plot_legends_erps(direction = "horizontal"),
   nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
-) +
+) + # Add some lines (to seperate the parts)
   annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
@@
 
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N1, or N400 component, all *p*s \> `r table_exp2$conts["Part I", "P1_p"]` (Table \@ref(tab:exp2-table), Figure \@ref(fig:exp2-plot)).
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all *p*s \> `r table_exp2$conts["Part I (pre-insight)", "P1_p"]` (Table \@ref(tab:exp2-table), Figure \@ref(fig:exp2-plot)).
 
@@
 
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching versus non-matching keywords) was associated with a (marginally) significant enhancement of the N1 component, *b* = `r table_exp2$conts["Part II", "N1_est"]` µV, *p* = `r table_exp2$conts["Part II", "N1_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Part II", "N400_est"]` µV, *p* `r table_exp1$conts["Part II", "N400_p"]`.
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching versus non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, *b* = `r table_exp2$conts["Part II (insight)", "N170_est"]` µV, *p* = `r table_exp2$conts["Part II (insight)", "N170_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Part II (insight)", "N400_est"]` µV, *p* `r table_exp1$conts["Part II (insight)", "N400_p"]`.
 
@@
 
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Part III", "P1_est"]` µV, *p* = `r table_exp2$conts["Part III", "P1_p"]`.
-Also, N400 amplitudes in response to these objects remained significantly reduced, *b* = `r table_exp2$conts["Part III", "N400_est"]` µV, *p* = `r table_exp2$conts["Part III", "N400_p"]`.
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Part II (post-insight)", "P1_est"]` µV, *p* = `r table_exp2$conts["Part II (post-insight)", "P1_p"]`.
+Also, N400 amplitudes in response to these objects remained significantly reduced, *b* = `r table_exp2$conts["Part II (post-insight)", "N400_est"]` µV, *p* = `r table_exp2$conts["Part II (post-insight)", "N400_p"]`.
 
@@
   stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
-  stub_contrasts = c("Part I", "Part II", "Part III"),
+  stub_contrasts = c("Part I (pre-insight)", "Part II (insight)", "Part II (post-insight)"),
   caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
@@
 
-```{r joint-plot, eval=FALSE}
-map(c("I", "II", "III"), function(part){
-  map(c("P1", "N1", "N400"), function(comp){
-
-    ymin <- case_when(comp == "P1" ~ -6, comp == "N1" ~ -11, comp == "N400" ~ -10)
-
-    data_joint %>%
-      filter(part == !!part) %>%
-      rename(amplitude = !!comp) %>%
-      group_by(participant, part, condition) %>% summarise(across(amplitude, mean)) %>%
-      ggplot(aes(x = condition, y = amplitude, fill = condition)) +
-      geom_violin() +
-      geom_boxplot(width = 0.3) +
-      coord_cartesian(ylim = c(ymin, ymin + 24)) +
-      scale_y_continuous(breaks = seq(ymin, ymin + 24, 4)) +
-      theme_classic() +
-      theme(
-        legend.position = "none"
-      )
-
-  }) %>% plot_grid(plotlist = ., nrow = 3)
-}) %>% plot_grid(plotlist = ., nrow = 1)
-
-# data_joint %>%
-#   pivot_longer(cols = c(P1, N1, N400), names_to = "comp", values_to = "amplitude") %>%
-#   mutate(comp = factor(comp, levels = c("P1", "N1", "N400"))) %>%
-#   group_by(participant, part, condition, comp) %>% summarise(amplitude = mean(amplitude)) %>%
-#   ggplot(aes(x = condition, y = amplitude, fill = condition)) +
-#   geom_violin() +
-#   geom_boxplot(width = 0.3) +
-#   coord_cartesian(ylim = c(-10, 10)) +
-#   facet_grid(comp ~ part)
-```
-
-As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Informed", "N400_df"]` = `r table_joint$anov["Informed", "N400_f"]`, *p* `r table_joint$anov["Informed", "N400_p"]`.
+As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Informed", "N400_df"]` = `r table_joint$anov["Informed", "N400_f"]`, *p* `r table_joint$anov["Informed", "N400_p"]`.
 Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s \> `r table_joint$anov["Pt.
@@
 
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically inforemd and the naive condition within each part, now collapsed across the data from both experiments.
-This confirmed the absence of any reliable differences between the two conditions in Part I, all *p*s \> `r table_joint$conts["Part I", "N400_p"]`, the significant enhancement of the N1 component in Part II, while the semantic information was obtained, *b* = `r table_joint$conts["Part II", "N1_est"]` µV, *p* = `r table_joint$conts["Part II", "N1_p"]`, the significant reduction of the N400 component in Part II, while the semantic information was obtained, *b* = `r table_joint$conts["Part II", "N400_est"]` µV, *p* `r table_joint$conts["Part II", "N400_p"]`, and Part III, after the information had been obtained, *b* = `r table_joint$conts["Part III", "N400_est"]` µV, *p* = `r table_joint$conts["Part III", "N400_p"]`, as well as the significant enhancement of the P1 component in Part III, after the information had been obtained, *b* = `r table_joint$conts["Part III", "P1_est"]` µV, *p* = `r table_joint$conts["Part III", "P1_p"]`.
+(ref:figure-3-caption) Measured and modelled ERP amplitudes for Experiments 1 and 2 combined.
+The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for Parts I (before insight was occurring), II (while insight was occurring), and III (after insight had occurred).
+The yellow dots show the corresponding condition means as predicted by linear mixed-effects modelling (see main text and Table \@ref(tab:joint-table)), together with their respective 95% confidence interval.
+Ampl.
+= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline\**p* \< .05.
+\*\**p* \< .01.
+\*\*\**p* \< .001.
+
+```{r joint-plot, include=TRUE, fig.height=8, fig.cap = "(ref:figure-3-caption)"}
+# Define two functions for split violin plots (kudos to https://stackoverflow.com/a/45614547)
+GeomSplitViolin <- ggproto(
+  "GeomSplitViolin", GeomViolin,
+  draw_group = function(self, data, ..., draw_quantiles = NULL) {
+    data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
+    grp <- data[1, "group"]
+    newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
+    newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
+    newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
+    if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
+      stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 1))
+      quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
+      aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
+      aesthetics$alpha <- rep(1, nrow(quantiles))
+      both <- cbind(quantiles, aesthetics)
+      quantile_grob <- GeomPath$draw_panel(both, ...)
+      ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
+    }
+    else {
+      ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
+    }
+  }
+)
+geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ...,
+                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE,
+                              show.legend = NA, inherit.aes = TRUE) {
+  layer(
+    data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin,
+    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
+    params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...)
+  )
+}
+
+# Define our custom function for the violin plot
+plot_violins <- function(data, models) {
+  suppressWarnings(suppressMessages(
+    parts <- map(c("I", "II", "III"), function(part) {
+      map(c("P1", "N170", "N400"), function(comp) {
+        modmeans <- models[[comp]]$means %>% filter(part == !!part) %>% rename(amplitude = emmean)
+        ymin <- case_when(comp == "P1" ~ -5, comp == "N170" ~ -11, comp == "N400" ~ -11)
+        asterisks <- models[[comp]]$contrasts %>%
+          filter(part == !!part) %>%
+          mutate(asterisks = case_when(p.value < .001 ~ "***", p.value < .01 ~ "**", p.value < .05 ~ "*")) %>%
+          pull(asterisks)
+        yastersisks <- case_when(
+          comp == "P1" ~ 17.6,
+          comp == "N170" ~ 10,
+          comp == "N400" & part == "II" ~ 9.7,
+          comp == "N400" & part == "III" ~ 8.9
+        )
+        data %>%
+          filter(part == !!part) %>%
+          rename(amplitude = !!comp) %>%
+          group_by(participant, part, condition) %>%
+          summarise(across(amplitude, mean)) %>%
+          ggplot(aes(x = 0, y = amplitude, fill = condition)) +
+          annotate("text", x = 0, y = yastersisks, label = asterisks, size = 6, family = "Helvetica") +
+          geom_split_violin(trim = TRUE, color = "gray70") +
+          geom_boxplot(position = position_dodge(width = 0.8), width = 0.3, color = "gray70") +
+          geom_pointrange(
+            data = modmeans,
+            aes(ymin = lower.CL, ymax = upper.CL),
+            position = position_dodge(width = 0.25),
+            size = 0.4,
+            color = viridisLite::viridis(n = 1, begin = 1)
+          ) +
+          coord_cartesian(ylim = c(ymin, ymin + 25), xlim = c(-0.6, 0.6)) +
+          scale_x_continuous(breaks = c(-0.2, 0.2), labels = c("Informed", "Naive")) +
+          scale_y_continuous(breaks = seq(ymin, ymin + 25, 5)) +
+          ylab(paste(comp, "ampl. (µV)")) +
+          scale_fill_viridis_d(begin = 0.1, end = 0.5) +
+          theme_classic() +
+          theme(
+            legend.position = "none",
+            axis.title.x = element_blank(),
+            axis.title.y = element_text(size = 10, color = "black", family = "Helvetica"),
+            axis.text = element_text(size = 10, color = "black", family = "Helvetica")
+          )
+      }) %>% plot_grid(plotlist = ., align = "v", nrow = 3)
+    })
+  ))
+  plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], ncol = 5, rel_widths = c(10, 2, 10, 2, 10))
+}
+
+# Define function for the legend for the violin plot
+plot_legends_violins <- function() {
+  get_legend(
+    tibble(Conditions = c("Informed", "Naive")) %>%
+      ggplot(aes(x = 0, y = 0, color = "LMM mean\n± 95% CI", fill = Conditions)) +
+      geom_raster() +
+      geom_pointrange(aes(ymin = -1, ymax = 1)) +
+      scale_fill_viridis_d(begin = 0.1, end = 0.5) +
+      scale_color_viridis_d(begin = 1) +
+      guides(
+        fill = guide_legend(override.aes = list(color = NA)),
+        color = guide_legend(title = NULL)
+      ) +
+      theme(
+        legend.box.background = element_rect(colour = "black", size = 0.5),
+        legend.box.margin = margin(l = 9, r = 9, b = 9, t = 7),
+        legend.background = element_blank(),
+        legend.spacing = unit(0.01, "inches"),
+        legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
+        legend.text = element_text(family = "Helvetica", size = 10),
+        legend.key = element_rect(fill = "gray70")
+      )
+  )
+}
+
+# Create violin plot for Experiments 1 and 2 combined
+plot_grid(
+  plot_headings(spacing = c(10, 2, 10, 2, 10)),
+  plot_violins(data = data_joint, models = models_joint),
+  nrow = 2, rel_heights = c(0.3, 6.7)
+) %>% plot_grid(
+  plot_legends_violins(),
+  nrow = 1, rel_widths = c(8.5, 1.5)
+) + # Add some lines (to seperate the parts)
+  annotate(geom = "segment", x = 11/34*0.85, xend = 11/34*0.85, y = -Inf, yend = Inf, linetype = "dashed") +
+  annotate(geom = "segment", x = 23/34*0.85, xend = 23/34*0.85, y = -Inf, yend = Inf, linetype = "dashed")
+```
+
+Based on the part × condition interaction, we again computed follow-up comparisons between the semantically inforemd and the naive condition within each part, now collapsed across the data from both experiments (Figure \@ref(fig:joint-plot)).
+This confirmed the absence of any reliable differences between the two conditions in Part I, all *p*s \> `r table_joint$conts["Part I (pre-insight)", "N400_p"]`, the significant enhancement of the N170 component in Part II, while the semantic information was obtained, *b* = `r table_joint$conts["Part II (insight)", "N170_est"]` µV, *p* = `r table_joint$conts["Part II (insight)", "N170_p"]`, the significant reduction of the N400 component in Part II, while the semantic information was obtained, *b* = `r table_joint$conts["Part II (insight)", "N400_est"]` µV, *p* `r table_joint$conts["Part II (insight)", "N400_p"]`, and Part III, after the information had been obtained, *b* = `r table_joint$conts["Part II (post-insight)", "N400_est"]` µV, *p* = `r table_joint$conts["Part II (post-insight)", "N400_p"]`, as well as the significant enhancement of the P1 component in Part III, after the information had been obtained, *b* = `r table_joint$conts["Part II (post-insight)", "P1_est"]` µV, *p* = `r table_joint$conts["Part II (post-insight)", "P1_p"]`.
 
@@
   readRDS("analysis/export/exp1-erps.RDS"),
-  readRDS("analysis/export/exp2-erps.RDS") %>% mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))),
+  readRDS("analysis/export/exp2-erps.RDS") %>%
+    mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))),
   .id = "experiment"
@@
 # contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
-# model_joint_control_N1 <- buildmer::buildmer(
-#   N1 ~ part * condition * experiment + (part * condition | participant) + (part * condition * experiment | item),
+# model_joint_control_N170 <- buildmer::buildmer(
+#   N170 ~ part * condition * experiment + (part * condition | participant) + (part * condition * experiment | item),
 #   REML = FALSE,
@@
 # emmeans::emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-# emmeans::emmeans(model_joint_control_N1@model, pairwise ~ condition | part, infer = TRUE)$contrasts
-
-# This time, we keep the unsuccessful ahas as the control condition
+# emmeans::emmeans(model_joint_control_N170@model, pairwise ~ condition | part, infer = TRUE)$contrasts
+
+# This time, we keep only the two conditions with matching keywords
 data_joint_control %<>% filter(condition %in% c("Informed", "Excl_informed")) %>% droplevels()
@@
 
-# Create table but don't print
+# Create a table but don't print
 table_joint_control <- create_table(
@@
   stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
-  stub_contrasts = c("Part I", "Part II", "Part III"),
+  stub_contrasts = c("Part I (pre-insight)", "Part II (insight)", "Part II (post-insight)"),
   caption = "Results of linear mixed-effects regression models with a different baseline",
@@
 
-One may raise concerns whether the modulation of the N1 component in Part II genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition.
+One may raise concerns whether the modulation of the N170 component in Part II genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition.
 Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the object's visual features and their configuration.
@@
 Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N1 effect in Part II, *b* = `r table_joint_control$conts["Part II", "N1_est"]` µV, *p* `r table_joint_control$conts["Part II", "N1_p"]`.
+Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in Part II, *b* = `r table_joint_control$conts["Part II (insight)", "N170_est"]` µV, *p* `r table_joint_control$conts["Part II (insight)", "N170_p"]`.
 Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords on which participants failed to capitalize.
-Note that the reduction of the N400 component in Part II also remained robust in this control analysis, *b* = `r table_joint_control$conts["Part II", "N400_est"]` µV, *p* `r table_joint_control$conts["Part II", "N400_p"]`.
-
-[^1]: Note that the remaining objects to make it up to 100% were excluded as not being unfamiliar in Part I of the experiment (see Statistical Analysis)
+Note that the reduction of the N400 component in Part II also remained robust in this control analysis, *b* = `r table_joint_control$conts["Part II (insight)", "N400_est"]` µV, *p* `r table_joint_control$conts["Part II (insight)", "N400_p"]`.
+
+[^1]: Note that the remaining objects to make it up to 100% were excluded as not being unfamiliar in Part I of the experiment (see Methods).
 
@@
 
-Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N1), and semantic processing (N400).
-While the enhancement of the N1 component, being more negative for semantically informed as compared to naive perception, was present only during the critical presentation of the objects with their respective keywords (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after the information had been obtained and the objects were presented again (in Part III).
+Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400).
+While the enhancement of the N170 component, being more negative for semantically informed as compared to naive perception, was present only during the critical presentation of the objects with their respective keywords (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after the information had been obtained and the objects were presented again (in Part III).
 This indicates a modulation of different stages of visual object perception through semantic knowledge, while and after an understanding of the object has been obtained.
@@
     epochs_exp3.save("analysis/export/exp3-epo.fif")
-
-# # Get indices of bad epochs despite ICA
-# rej_exp3 = epochs_exp3.drop_log
-# rej_exp3[:] = [item for item in rej_exp3 if item != ['IGNORED']]
-# rej_exp3 = [i for i in range(len(rej_exp3)) if rej_exp3[i] != []]
 ```
@@
 # Check number of rejected epochs
-rejected_exp3 <- data_exp3 %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 672 - n) %>%
-  pull(n)
-mean(rejected_exp3)
-median(rejected_exp3)
-range(rejected_exp3)
+rejected_exp3 <- data_exp3 %>% group_by(participant) %>% tally() %>% mutate(n = 672 - n) %>% pull(n)
+mean(rejected_exp3)    # Mean
+median(rejected_exp3)  # Median
+range(rejected_exp3)   # Range
 
@@
 
-Although most of the previous studies in the object processing domain have focused on the P1 component as an index of semantic knowledge modulating perceptual processes, at least two studies provide evidence for top-down effects of meaningfulness on the visual N1 (or N170) component in response to schematic drawings of faces [@bentin2002] and objects [@beaucousin2011].
-Using a similar design as in the present study, drawings of distored faces elicited a facelike (i.e.
-enlarged) N170 component only after participants were primed with a vaild hint---in this case the same face with all of its visual features in place [@bentin2002].
-Similarly, N1 amplitudes in a global-local detection task where shown to be enhanced in response to line drawings of meaningful objects (a boat or a butterfly) as compared to visually matched by meaningless drawings of non-objects.
-Interestingly, this effect was reversed in polarity when participants had to focus on the smaller, constituent parts and ignoring the object which emerged out of their global arrangement, which may be interpreted as further evidence for a functional role of the N1 component in the holistic perception of an object and its early visual categorization, integrating across its visual features.
+Although most of the previous studies in the object processing domain have focused on the P1 component as an index of semantic knowledge modulating perceptual processes, at least two studies provide evidence for top-down effects of meaningfulness on the visual N170 (or N1) component in response to schematic drawings of faces [@bentin2002] and objects [@beaucousin2011].
+Using a similar design as in the present study, drawings of distored faces elicited a facelike (i.e. enlarged) N170 component only after participants were primed with a vaild hint---in this case the same face with all of its visual features in place [@bentin2002].
+Similarly, N170 amplitudes in a global-local detection task where shown to be enhanced in response to line drawings of meaningful objects (a boat or a butterfly) as compared to visually matched by meaningless drawings of non-objects.
+Interestingly, this effect was reversed in polarity when participants had to focus on the smaller, constituent parts and ignoring the object which emerged out of their global arrangement, which may be interpreted as further evidence for a functional role of the N170 component in the holistic perception of an object and its early visual categorization, integrating across its visual features.
 
@@
 
+```{=tex}
 \setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+```

### 2020-11-03 analysis/manuscript.tex
rename N1 to N170

@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 \fi
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newenvironment{cslreferences}%
-  {\setlength{\parindent}{0pt}%
-  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
-  {\par}
 
@@
 
-The thesis was handed December 18, 2020 and has been supervised by Prof.~Dr.~Rasha Abdel Rahman, Humboldt-Universität zu Berlin, Germany, and Prof.~Dr.~Franziska Süß, Fachhochschule des Mittelstands, Bamberg, Germany.
+The thesis was handed in December 18, 2020 and has been supervised by Prof.~Dr.~Rasha Abdel Rahman, Humboldt-Universität zu Berlin, Germany, and Prof.~Dr.~Franziska Süß, Fachhochschule des Mittelstands, Bamberg, Germany.
 
@@
 How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects, preceded in half of the cases by valid information about their function (leading to semantically informed perception) and in the other half of the cases by misleading information (leading to naive perception).
-Capitalizing on the high temporal resolution of event-related potentials (ERPs), we investigated if semantically informed versus naive perception led to differential effects at different stages in the processing hierarchy of visual objects.
+In this study, we presented participants with unfamiliar objects, preceded in half of the cases by valid information about their function, leading to semantically informed perception, and in the other half of the cases by misleading information, leading to naive perception.
+Capitalizing on the high temporal resolution of event-related brain potentials (ERPs), we investigated at which stages in the processing hierarchy semantically informed and naive perception of visual objects differed from one another.
 
-Learning semantic knowledge about objects has an influence on how we process them (Abdel Rahman \& Sommer, 2008; Gauthier et al., 2003; Gratton et al., 2009; Maier et al., 2014; Maier \& Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
-Recently, evidence has accumulated that it does so not only at ``higher'' stages in the visual processing hierarchy, i.e.~after ``lower'' stages of perceptual processing have been completed.
-It rather seems as though knowledge can also alter early processes, previously thought to be determined solely by the visual input itself, in a top-down manner.
-Such a top-down influence of semantic knowledge or expertise may manifest itself in behavioral changes such as improved visual matching (e.g.~Gauthier et al., 2003) and visual search performance (Holmes \& Wolff, 2012; Maier et al., 2014) when having learned that two objects share the same semantic category or verbal label.
-Furthermore, acquiring semantically meaningful knowledge about previously unfamiliar objects has been shown to increase their likelihood of gaining access to conuscious visual awareness under circumstances when attentional resources are limited (Weller et al., 2019).
-Although these behavioral effects hint at an early locus of semantic knowledge effects in object processing, they in and of themselves cannot convincingly demonstrate that not just downstream, postperceptual steps are being affected (Firestone \& Scholl, 2016).
+The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-standing debate.
+This debate revolves around the question whether or not our perception of the (visual) world should be thought of as an encapsulated module being completely determined by the visual input reaching our retina.
+According to the former view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (Firestone \& Scholl, 2016; Fodor, 1984, 1983; Machery, 2015; Pylyshyn, 1999).
+Conversely, this view is challenged by theoretical and empirical work suggesting that perceptual processing dynamically interacts with other aspects of cognition from early on (Churchland, 1988; Churchland et al., 1994; Collins \& Olson, 2014; Lupyan, 2012, 2015; Lupyan et al., 2020; Thierry, 2016; Vetter \& Newen, 2014).
+These aspects may include transient states such as emotions (e.g.~Phelps et al., 2016; Bocanegra \& Zeelenberg, 2009) or intentions (Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g.~Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g.~Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g.~Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019).
+Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained sceptical, pointing out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016).
 
-Stronger evidence comes from some of the above and other studies concurrently measuring event-related brain potentials (ERPs) while participants are performing different tasks on the objects about which they had previously acquired semantic knowledge.
-In their ERP study, (Abdel Rahman \& Sommer, 2008) had participants first learn in-depth knowledge about 20 unfamiliar objects by listening to a verbal descripition of the function of each object while it was presented visually on the screen, whereas for 20 different objects they did not receive any relevant semantic information, instead listening to unrelated cooking recipes while the objects were presented.
-As in the present study, the assignment of unfamiliar objects to either of the two conditions was counterbalanced ascross participants as to prevent any subsequent effects of semantic knowledge from being confounded with visual differences between the objects.
-In a separate test session, event-related potentials were measured while participants performed three different tasks on those objects (intermixed with well known objects that had not been part of the training session).
-ERP amplitudes in response to objects for which in-depth versus minimal knowledge had been acquired differed in the time window of the N400 component (300--500 ms after stimulus onset), typically associated with semantic processing, but, interestingly, aslo in the time window of the visual P1 component (100--150 ms after stimulus onset), typcially associated with lower-level visual processing {[}(Abdel Rahman \& Sommer, 2008); Experiment 1{]}.
-This effect ocurred across three different tasks (none of which explicitly required accessing any of the aqcuired information) and was qualitatively similar to the ERPs observed for untrained but well-known objects.
-A modulation of the P1 component has also been replicated using similar sets of objects in the above mentioned studies showing effects of object knowledge in visual search and the visual awareness tasks (Maier \& Rahman, 2019; Weller et al., 2019).
-It thus seems as though learning semantic information can influence steps of the processing hierarchy previously thought to be determined by the low-level visual input.
+One productive way of investigating top-down effects of cognition on perception while addressing some of these concerns is through neurophysiological recording methods such as ERPs: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+This is because when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
 
-A different strategy to investaige the influence of semantic knowledge on perception has been taken in a recent ERP study by (Samaha et al., 2018).
-Instead of using unfamiliar objects as stimuli, participants viewed images of familiar everyday objects that had been converted to two-tone ``Mooney'' images, making the object itself difficult to recognize.
-For half of the images, participants performed a semantic training where they were told which object to look for in each image.
-For the other half of images, they performed a perceptual (1-back) control task to equate the amount familiarity across all images.
-In a subsequent visual discrimination task, participants tended to respond faster and more accurate to the semantically trained images than to the perceptually trained ones {[}(Samaha et al., 2018); Experiment 4{]}.
-Crucially, the semantic training also manifested itself in increased pre-stimulus alpha-band power and larger P1 amplitudes at left temporo-occipital electrodes, further coroborating an early influence of semantically informed as compared to naive perception of objects.
+The visual P1 component refers to a positive deflection peaking approximately 100--150 ms after stimulus onset at occipital channels.
+It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri (Di Russo et al., 2001; Foxe \& Simpson, 2002; Mangun, 1995).
+The P1 is mostly thought to reflect the processing of low-level visual characteristics of the stimulus (such as size, luminance, and contrast; Di Russo et al., 2001; Johannes et al., 1995; Luck, 2014), which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception.
+It should be noted, however, that the P1 is reliably modulated by spatial (Luck et al., 2000; Mangun, 1995; Mangun \& Hillyard, 1991) and non-spatial (Taylor, 2002) attention.
 
-What all the previous studies have in common is that they investigated the effects of semantic knoweldge on object perception \emph{after} an extensive learning phase (Abdel Rahman \& Sommer, 2008; Gauthier et al., 2003; Maier et al., 2014; Maier \& Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Weller et al., 2019).
-Participants usually performed a seperate training session where they encountered each object together with its respective label or description multiple times.
-The EEG was usually not measured (or at least not analyzed and reported) during this training phase, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Rahman, 2019) or was even spread out across multiple days or weeks (Rossion et al., 2002, 2004).
-While designs with such substantive learning maximizes the chances of detecting even subtle top-down effects of the acquired knowledge, they necessarily leave at least three important conceptual questions unresolved.
-The first question is if we can detect any electrophysiological correlates of semantic insight, i.e.~the critical presentation during which an understanding of a previously unfamiliar or meaningless objects is happening, instead of asking if this understanding leads to differential effects later in an orthogonal task.
-The second question is how much learning is actually necessary before reliable top-down effects of knowledge (e.g.~on object-related P1 amplitudes) can be obtained: Does it actually take dozens of repitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is related to one of the critiques sometimes raised against the nature of knowledge effects: Are they reflecting genuine top-down effects of semantic processes, altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been created or altered throughout the learning process?
-By measuring the ERPs before, during, and after participants received semantic hints about the unfamiliar objects, we hope to provide tentative answers to all of these questions.
+The visual N170 (or N1) component refers to the negative deflection following the P1 and is maximal around 150--200 ms after stimulus onset at occipito-temporal channels.
+While still influenced by visual parameters of the stimulus (Johannes et al., 1995), it is also sensitive to selective attention, at least when participants are required to discriminate between different visual stimuli (Mangun \& Hillyard, 1991; Vogel \& Luck, 2000).
+Importantly, the N170 is enlarged (i.e.~more negative) in response to faces (Bentin et al., 1996; Rossion \& Jacques, 2011) and other visual stimuli for which one happens to be an expert (e.g.~birds, dogs, or cars; I.
+Gauthier, Curran, et al., 2003; Tanaka \& Curran, 2001).
+This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as their configuration (Eimer et al., 2011; Jacques \& Rossion, 2010; Rossion et al., 1999; Sagiv \& Bentin, 2001).
+Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimuli.
 
-\begin{itemize}
-\item
-  One paragraph explaining that previous research has shown that semantic knowledge modulates early stages of visual perception (e.g.~Abdel Rahman \& Sommer, 2008; Gauthier et al., 2003; Maier \& Abdel Rahman, 2019; Maier et al., 2014; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
-\item
-  Potentially one paragraph describing Abdel Rahman \& Sommer (2008) in more detail (participants acquiring knowledge about existing but unfamiliar objects).
-\item
-  One paragraph describing Samaha et al.~(2018) in more detail (participants being trained to see familiar objects in otherwise meaningless images).
-Possibly hypothesize a special role of insight (= the moment when understanding is acquired), although this is not directly captured by the study.
-\item
-  One paragraph explaining how all of these studies measured ERPs only \emph{after} an extensive learning phase, making it difficult to determine (a) how much learning is necessary for semantic knowledge to influence perception and, related to that, (b) if the modulation of early ERP components reflects genuine online effects of semantic knowledge or rather the activation of altered visual representations (Firestone \& Scholl, 2015) (?).
-\item
-  One paragraph on theories of top-down/language effects on visual perception (reverse hierarchy theory).
-\item
-  Possibly another paragraph on theories of top-down effects on visual perception (label feedback hypothesis) if it fits thematically.
-\item
-  Do we need to refer to the role of attention already in the introduction? If so, potentially another paragraph here. I might prefer to leave that for the discussion.
-\item
-  Possibly one more paragraph on why ERPs are so suitable to answer this research question, including a brief characterization of the relevant components (P1: lower-level visual perception, N1: higher-level visual perception, N400: semantic processing).
-\item
-  The present study: Design of the study with a focus on distinguishing between online effects and altered representations; no specific hypotheses but looking for influences of semantic knowledge on the three ERP components at three different stages (before, during, and after acquisition).
-\end{itemize}
+Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration (Kutas \& Federmeier, 2011; Lau et al., 2008; Rabovsky et al., 2018), starting approximately 300 ms after stimulus onset and being most pronounced at centro-parietal channels.
+A modulation of this component by cognitive capapacities such as knowedge can be taken as evidence for a post-perceptual influence on stimulus processing.
+
+Previous studies have focused on these and other ERP components to investiage which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects (Abdel Rahman \& Sommer, 2008; Gratton et al., 2009; Maier et al., 2014; Maier \& Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
+Together, they suggest that not only higher-level semantic ERPs like the N400 component are influenced by acquiring semantic information about objects, but also early components that typcially reflect bottom-up visual processing.
+This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (cooking recipes) for the other half of the objects (Abdel Rahman \& Sommer, 2008, Experiment 1).
+After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information.
+In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this has not been the case.
+Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
+Of note, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects.
+The modulation of the P1 component was also replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm (Weller et al., 2019).
+Of note, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink, which can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.
+
+A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects, which were rendered difficult to recognize by converting them to two-tone, \enquote{Mooney} images (Samaha et al., 2018, Experiment 4).
+Here, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the image beforehand, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
+When the EEG was measured in a separate delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images of objects than for perceptually-trained images of objects.
+This alternative approach further coroborates an early influence of semantic information on visual object perception.
+
+All the previously mentioned studies have in common that they investigated the effects of semantic knoweldge on object perception only \emph{after} an extensive learning phase (Abdel Rahman \& Sommer, 2008; I.
+Gauthier, James, et al., 2003; Maier et al., 2014; Maier \& Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Weller et al., 2019).
+Participants performed one or multiple training session where they encountered each object together with its respective label or description multiple times.
+The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Rahman, 2019) or were spread out across multiple days or weeks (Rossion et al., 2002, 2004).
+While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three important conceptual questions unresolved.
+
+The first question is if we can detect any electrophysiological correlates of semantic insight, i.e.~the critical presentation during which an understanding of the previously unfamiliar object is happening, instead of asking if this understanding leads to differential effects in an orthogonal task later on.
+The second question is how much learning is actually necessary before reliable top-down effects of knowledge (such as~on object-related P1 amplitudes) can be obtained: Does it actually take dozens of repitions per object or may a single exposure to the object together with the relevant semantic information be enough?
+The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of semantics, altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects, having been altered throughout the learning process (Haber, 1966)?
+By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we hope to provide tentative answers to all three of these questions.
+
+In the two experiments subsequently reported, participants were presented with real-word objects that were presumed to be unfamiliar to most of them.
+They first viewed each of these objects once without any semantic information.
+This part served as a naive baseline to outrule that ERPs would differ in response to the objects based solely on their low-level visual differences.
+Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
+These keywords could either correctly describe the object's typical function, thus making it possible for participants to understand what kind of object they are viewing, or mislead them by describing the function of a different object, thus keeping the perception of the object semantically naive.
+During this \enquote{insight} part, we were able measure the online influence of semantic knowledge on object-evoked ERPs as it happened.
+Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them, thus mimicking previous studies (e.g.~Abdel Rahman \& Sommer, 2008, p.
+@samaha2018; Weller et al., 2019).
+In all three parts, we compared the influences of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (400--700 ms).
 
@@
 The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) ``I know what this is or have a strong assumption,'' (b) ``I have an assumption what this is,'' (c) ``I have rather no assumption what this is,'' or (d) ``I do not know what this is and have no assumption.'' Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) \enquote{I know what this is or have a strong assumption,} (b) \enquote{I have an assumption what this is,} (c) \enquote{I have rather no assumption what this is,} or (d) \enquote{I do not know what this is and have no assumption.} Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/exp1-plot-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/exp1-plot-1}
 
@@
 \caption{Procedure and results of Experiment 1.
-\emph{(A)} In the pre-insight part (Part I) participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+\emph{(A)} In the pre-insight part (Part I), participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
 In the insight part (Part II), half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
 In the post-insight part (Part III), the same objects were presented again without the keywords.
-\emph{(B)} ERP waveforms and scalp topographies separately for objects with semantically informed versus naive perception in Parts I, II, and III.
-Semantically informed perception was associated with significantly more negative amplitudes in the N1 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
+\emph{(B)} ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within Parts I, II, and III.
+Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
 Ampl.
@@
 This led to the exclusion of an average of 2.4 trials (0.7\%) per participant (range 0 to 24).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N1 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
 
@@
 
-Three separate models were computed predicting P1, N1, and N400 mean amplitudes, respectively.
+Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
 All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.~subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.~subtracting the naive from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
@@
 \toprule
- & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
+ & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N170}} & \multicolumn{2}{c}{\textbf{N400}} \\
 \cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
@@
 \midrule
-Part & 10.82 (2, 24.5) & < .001 & 14.15 (2, 24.9) & < .001 & 33.01 (2, 25.5) & < .001\\
-Condition & 0.87 (1, 5302.9) & .351 & 0.89 (1, 114.3) & .349 & 13.09 (1, 24.8) & .001\\
-Pt. × con. & 2.40 (2, 4590.9) & .091 & 5.34 (2, 4853.1) & .005 & 11.18 (2, 5030.2) & < .001\\
+Part & 10.89 (2, 24.5) & < .001 & 14.18 (2, 24.9) & < .001 & 32.85 (2, 25.6) & < .001\\
+Condition & 0.60 (1, 5343.5) & .438 & 0.30 (1, 24.2) & .586 & 13.00 (1, 24.4) & .001\\
+Pt. × con. & 2.30 (2, 4605.0) & .100 & 4.84 (2, 4878.2) & .008 & 10.91 (2, 5120.9) & < .001\\
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Part I & 0.00 [-0.50, 0.49] & .987 & -0.17 [-0.64, 0.30] & .485 & -0.20 [-0.65, 0.26] & .393\\
-Part II & -0.15 [-0.65, 0.34] & .550 & -0.66 [-1.14, -0.19] & .006 & 0.93 [0.48, 1.39] & < .001\\
-Part III & 0.57 [0.08, 1.07] & .023 & 0.41 [-0.07, 0.88] & .094 & 1.00 [0.55, 1.46] & < .001\\
+Part I (pre-insight) & -0.03 [-0.53, 0.47] & .913 & -0.12 [-0.68, 0.44] & .665 & -0.20 [-0.65, 0.26] & .400\\
+Part II (insight) & -0.18 [-0.68, 0.32] & .490 & -0.64 [-1.20, -0.08] & .026 & 0.93 [0.48, 1.39] & < .001\\
+Part II (post-insight) & 0.55 [0.05, 1.05] & .031 & 0.43 [-0.14, 0.99] & .136 & 1.00 [0.54, 1.46] & < .001\\
 \bottomrule
@@
 
-Averaged across conditions, P1, N1, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.82, all \emph{p}s \textless{} .001 (Table \ref{tab:exp1-table}).
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.89, all \emph{p}s \textless{} .001 (Table \ref{tab:exp1-table}).
 In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}NA = NA, \emph{p} = NA.
-Crucially, the part × condition interaction was significant in the N1 component, \emph{F}(2, 4853.1) = 5.34, \emph{p} = .005, and in the N400 component, \emph{F}(2, 5030.2) = 11.18, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4590.9) = 2.40, \emph{p} = .091.
+Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4605.0) = 2.30, \emph{p} = .100.
 To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
@@
 
-In Part I, when objects were unfamiliar to the participant and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .393 (Table \ref{tab:exp1-table}, Figure \ref{fig:exp1-plot}B \& C).
+In Part I, when objects were unfamiliar to the participant and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .400 (Table \ref{tab:exp1-table}, Figure \ref{fig:exp1-plot}B \& C).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs.~naive perception) had not yet taken place.
@@
 In Part II, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object (akin to an insight experience), the amplitude of the N1 component was significantly enlarged (i.e.~more negative), \emph{b} = -0.66 µV, \emph{p} = .006, and the amplitude of the N400 component was significantly reduced (i.e.~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when an object was viewed naively without relevant semantic information.
-As in Part I, there were no reliable differences in the P1 component, \emph{p} = .550.
+When semantic information informed the perception of the object (akin to an insight experience), the amplitude of the N170 component was significantly enlarged (i.e.~more negative), \emph{b} = -0.64 µV, \emph{p} = .026, and the amplitude of the N400 component was significantly reduced (i.e.~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when an object was viewed naively without relevant semantic information.
+As in Part I, there were no reliable differences in the P1 component, \emph{p} = .490.
 
@@
 In Part III, the unfamiliar objects were presented for a third time, again without the keywords (as in Part I), to test whether the semantic information had any lasting effects on the processing of the objects.
-As in Part II, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the early effect in the N1 component did not reoccur, \emph{p} = .094.
-Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e.~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.57 µV, \emph{p} = .023.
+As in Part II, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the early effect in the N170 component did not reoccur, \emph{p} = .136.
+Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e.~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.55 µV, \emph{p} = .031.
 
@@
 
-Participants' semantically informed perception of the objects in Part II was associated with a significantly enlarged N1 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing (Rossion \& Jacques, 2011; Tanaka \& Curran, 2001).
+Participants' semantically informed perception of the objects in Part II was associated with a significantly enlarged N170 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing (Rossion \& Jacques, 2011; Tanaka \& Curran, 2001).
 The fact that this effect did not reoccur in Part III, when the objects were presented once more without keywords, suggests it being a marker of insight through semantic information that is altering object processing online.
@@
 \midrule
-Part & 18.14 (2, 5151.1) & < .001 & 16.39 (2, 25.0) & < .001 & 70.58 (2, 25.2) & < .001\\
-Condition & 0.03 (1, 5272.5) & .853 & 1.23 (1, 5218.6) & .267 & 18.66 (1, 5207.5) & < .001\\
-Pt. × con. & 3.74 (2, 5151.2) & .024 & 1.34 (2, 4736.8) & .263 & 8.07 (2, 4637.6) & < .001\\
+Part & 17.45 (2, 5267.1) & < .001 & 16.57 (2, 25.1) & < .001 & 70.12 (2, 25.2) & < .001\\
+Condition & 0.02 (1, 5276.9) & .900 & 0.98 (1, 5228.5) & .322 & 19.95 (1, 5242.5) & < .001\\
+Pt. × con. & 3.60 (2, 5267.1) & .027 & 1.25 (2, 4756.5) & .287 & 7.92 (2, 4714.9) & < .001\\
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Part I & -0.17 [-0.72, 0.38] & .552 & -0.04 [-0.53, 0.45] & .864 & 0.02 [-0.44, 0.48] & .936\\
-Part II & -0.49 [-1.04, 0.07] & .084 & -0.50 [-0.99, 0.00] & .050 & 1.31 [0.86, 1.77] & < .001\\
-Part III & 0.56 [0.01, 1.11] & .048 & 0.04 [-0.45, 0.54] & .865 & 0.45 [-0.01, 0.91] & .055\\
+Part I (pre-insight) & -0.16 [-0.71, 0.40] & .582 & -0.03 [-0.53, 0.48] & .920 & 0.04 [-0.43, 0.50] & .877\\
+Part II (insight) & -0.48 [-1.03, 0.08] & .094 & -0.48 [-0.99, 0.03] & .064 & 1.33 [0.87, 1.79] & < .001\\
+Part II (post-insight) & 0.57 [0.01, 1.13] & .047 & 0.06 [-0.45, 0.57] & .818 & 0.47 [0.01, 0.93] & .047\\
 \bottomrule
@@
 
-As in Experiment 1, P1, N1, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.39, all \emph{p}s \textless{} .001 (Table \ref{tab:exp2-table}).
+As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.57, all \emph{p}s \textless{} .001 (Table \ref{tab:exp2-table}).
 Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}NA = NA, \emph{p} NA.
-The part × condition interaction was significant in the P1 component, \emph{F}(2, 5151.2) = 3.74, \emph{p} = .024, and in the N400 component, \emph{F}(2, 4637.6) = 8.07, \emph{p} \textless{} .001, but not in the N1 component, \emph{F}(2, 4736.8) = 1.34, \emph{p} = .263.
+The part × condition interaction was significant in the P1 component, \emph{F}(2, 5267.1) = 3.60, \emph{p} = .027, and in the N400 component, \emph{F}(2, 4714.9) = 7.92, \emph{p} \textless{} .001, but not in the N170 component, \emph{F}(2, 4756.5) = 1.25, \emph{p} = .287.
 
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/exp2-plot-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/exp2-plot-1}
 
@@
 \caption{Results of Experiment 2.
-ERP waveforms and scalp topographies separately for objects for which participants experienced semantically informed versus naive perception in Parts I, II, and III.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in Parts II and III and on the P1 component in Part III remained statistically significant, while the effect on the N1 component in Part II remained only marginally significant.
+ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within Parts I, II, and III.
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in Parts II and III and on the P1 component in Part III remained statistically significant, while the effect on the N170 component in Part II remained only marginally significant (\emph{p} = .064).
 Ampl.
 = amplitude.\newline*\emph{p} \textless{} .05.
+**\emph{p} \textless{} .01.
 ***\emph{p} \textless{} .001.}\label{fig:exp2-plot}
@@
 
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N1, or N400 component, all \emph{p}s \textgreater{} .552 (Table \ref{tab:exp2-table}, Figure \ref{fig:exp2-plot}).
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .582 (Table \ref{tab:exp2-table}, Figure \ref{fig:exp2-plot}).
 
@@
 
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching versus non-matching keywords) was associated with a (marginally) significant enhancement of the N1 component, \emph{b} = -0.50 µV, \emph{p} = .050, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching versus non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, \emph{b} = -0.48 µV, \emph{p} = .064, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.
 
@@
 
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.56 µV, \emph{p} = .048.
-Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.45 µV, \emph{p} = .055.
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.57 µV, \emph{p} = .047.
+Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.47 µV, \emph{p} = .047.
 
@@
 \midrule
-Part & 12.38 (2, 49.0) & < .001 & 29.90 (2, 50.0) & < .001 & 95.34 (2, 50.6) & < .001\\
-Condition & 0.35 (1, 10560.3) & .552 & 1.65 (1, 125.3) & .202 & 38.72 (1, 10518.8) & < .001\\
-Experiment & 0.35 (1, 48.2) & .555 & 2.38 (1, 48.1) & .129 & 4.75 (1, 48.4) & .034\\
-Pt. × con. & 4.02 (2, 9042.4) & .018 & 5.60 (2, 9877.5) & .004 & 15.73 (2, 10010.1) & < .001\\
-Pt. × exp. & 0.03 (2, 49.0) & .971 & 0.55 (2, 50.0) & .581 & 2.58 (2, 50.6) & .085\\
-Ins. × exp. & 0.62 (1, 10536.2) & .432 & 0.04 (1, 10332.1) & .838 & 0.03 (1, 10574.9) & .865\\
-Pt. × con. × exp. & 0.03 (2, 9042.9) & .972 & 0.62 (2, 9877.8) & .537 & 2.65 (2, 10010.4) & .070\\
+Part & 12.34 (2, 49.1) & < .001 & 30.08 (2, 50.3) & < .001 & 94.61 (2, 50.6) & < .001\\
+Condition & 0.15 (1, 10573.1) & .699 & 1.16 (1, 45.2) & .287 & 41.38 (1, 10593.6) & < .001\\
+Experiment & 0.33 (1, 48.2) & .567 & 2.50 (1, 48.0) & .121 & 4.96 (1, 48.4) & .031\\
+Pt. × con. & 3.90 (2, 9004.9) & .020 & 5.26 (2, 9904.1) & .005 & 15.34 (2, 10091.0) & < .001\\
+Pt. × exp. & 0.04 (2, 49.1) & .966 & 0.58 (2, 50.3) & .565 & 2.55 (2, 50.6) & .088\\
+Ins. × exp. & 0.43 (1, 10573.1) & .514 & 0.06 (1, 45.2) & .805 & 0.07 (1, 10593.6) & .785\\
+Pt. × con. × exp. & 0.03 (2, 9004.9) & .968 & 0.58 (2, 9904.1) & .559 & 2.54 (2, 10091.0) & .079\\
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Part I & -0.07 [-0.44, 0.30] & .699 & -0.10 [-0.44, 0.24] & .568 & -0.10 [-0.41, 0.20] & .507\\
-Part II & -0.22 [-0.59, 0.15] & .248 & -0.56 [-0.90, -0.21] & .002 & 1.09 [0.79, 1.39] & < .001\\
-Part III & 0.49 [0.12, 0.86] & .010 & 0.25 [-0.10, 0.59] & .158 & 0.72 [0.41, 1.02] & < .001\\
+Part I (pre-insight) & -0.10 [-0.47, 0.28] & .616 & -0.10 [-0.48, 0.29] & .611 & -0.09 [-0.39, 0.22] & .577\\
+Part II (insight) & -0.24 [-0.62, 0.13] & .202 & -0.57 [-0.96, -0.18] & .004 & 1.10 [0.80, 1.41] & < .001\\
+Part II (post-insight) & 0.47 [0.09, 0.84] & .014 & 0.24 [-0.15, 0.63] & .225 & 0.73 [0.42, 1.04] & < .001\\
 \bottomrule
@@
 
-As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N1, and N400 component, all \emph{F}s \textgreater{} 12.38, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}NA = NA, \emph{p} NA.
-Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 4.02, all \emph{p}s \textless{} .018.
-While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.75, \emph{p} = .034, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
+As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.34, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}NA = NA, \emph{p} NA.
+Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 3.90, all \emph{p}s \textless{} .020.
+While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.96, \emph{p} = .031, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
 
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically inforemd and the naive condition within each part, now collapsed across the data from both experiments.
-This confirmed the absence of any reliable differences between the two conditions in Part I, all \emph{p}s \textgreater{} .507, the significant enhancement of the N1 component in Part II, while the semantic information was obtained, \emph{b} = -0.56 µV, \emph{p} = .002, the significant reduction of the N400 component in Part II, while the semantic information was obtained, \emph{b} = 1.09 µV, \emph{p} \textless{} .001, and Part III, after the information had been obtained, \emph{b} = 0.72 µV, \emph{p} = \textless{} .001, as well as the significant enhancement of the P1 component in Part III, after the information had been obtained, \emph{b} = 0.49 µV, \emph{p} = .010.
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/joint-plot-1}
+
+}
+
+\caption{Measured and modelled ERP amplitudes for Experiments 1 and 2 combined.
+The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for Parts I (before insight was occurring), II (while insight was occurring), and III (after insight had occurred).
+The yellow dots show the corresponding condition means as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
+Ampl.
+= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\emph{p} \textless{} .05.
+**\emph{p} \textless{} .01.
+***\emph{p} \textless{} .001.}\label{fig:joint-plot}
+\end{figure}
+
+Based on the part × condition interaction, we again computed follow-up comparisons between the semantically inforemd and the naive condition within each part, now collapsed across the data from both experiments (Figure \ref{fig:joint-plot}).
+This confirmed the absence of any reliable differences between the two conditions in Part I, all \emph{p}s \textgreater{} .577, the significant enhancement of the N170 component in Part II, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in Part II, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and Part III, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} = \textless{} .001, as well as the significant enhancement of the P1 component in Part III, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.
 
@@
 Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that the remaining objects to make it up to 100\% were excluded as not being unfamiliar in Part I of the experiment (see Statistical Analysis)} Just as above, this control analysis revealed a robust N1 effect in Part II, \emph{b} = -0.99 µV, \emph{p} \textless{} .001.
+Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that the remaining objects to make it up to 100\% were excluded as not being unfamiliar in Part I of the experiment (see Methods).} Just as above, this control analysis revealed a robust N170 effect in Part II, \emph{b} = -1.00 µV, \emph{p} \textless{} .001.
 Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords on which participants failed to capitalize.
-Note that the reduction of the N400 component in Part II also remained robust in this control analysis, \emph{b} = 1.19 µV, \emph{p} \textless{} .001.
+Note that the reduction of the N400 component in Part II also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.
 
@@
 
+Although most of the previous studies in the object processing domain have focused on the P1 component as an index of semantic knowledge modulating perceptual processes, at least two studies provide evidence for top-down effects of meaningfulness on the visual N170 (or N1) component in response to schematic drawings of faces (Bentin \& Golland, 2002) and objects (Beaucousin et al., 2011).
+Using a similar design as in the present study, drawings of distored faces elicited a facelike (i.e.~enlarged) N170 component only after participants were primed with a vaild hint---in this case the same face with all of its visual features in place (Bentin \& Golland, 2002).
+Similarly, N170 amplitudes in a global-local detection task where shown to be enhanced in response to line drawings of meaningful objects (a boat or a butterfly) as compared to visually matched by meaningless drawings of non-objects.
+Interestingly, this effect was reversed in polarity when participants had to focus on the smaller, constituent parts and ignoring the object which emerged out of their global arrangement, which may be interpreted as further evidence for a functional role of the N170 component in the holistic perception of an object and its early visual categorization, integrating across its visual features.
+
 \newpage
@@
 \setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\begin{cslreferences}
+\leavevmode\hypertarget{ref-abdelrahman2011}{}%
+Abdel Rahman, R.
+(2011).
+Facing good and evil: Early brain signatures of affective biographical knowledge in face recognition.
+\emph{Emotion}, \emph{11}(6), 1397--1405.
+\url{https://doi.org/10.1037/a0024717}
+
 \leavevmode\hypertarget{ref-abdelrahman2008}{}%
@@
 
+\leavevmode\hypertarget{ref-balcetis2010}{}%
+Balcetis, E., \& Dunning, D. (2010). Wishful seeing: More desired objects are seen as closer. \emph{Psychological Science}, \emph{21}(1), 147--152. \url{https://doi.org/10.1177/0956797609356283}
+
 \leavevmode\hypertarget{ref-barr2013}{}%
@@
 
+\leavevmode\hypertarget{ref-beaucousin2011}{}%
+Beaucousin, V., Cassotti, M., Simon, G., Pineau, A., Kostova, M., Houdé, O., \& Poirel, N.
+(2011).
+ERP evidence of a meaningfulness impact on visual global/local processing: When meaning captures attention.
+\emph{Neuropsychologia}, \emph{49}(5), 1258--1266.
+\url{https://doi.org/10.1016/j.neuropsychologia.2011.01.039}
+
+\leavevmode\hypertarget{ref-bentin1996}{}%
+Bentin, S., Allison, T., Puce, A., Perez, E., \& McCarthy, G.
+(1996).
+Electrophysiological studies of face perception in humans.
+\emph{Journal of Cognitive Neuroscience}, \emph{8}(6), 551--565.
+\url{https://doi.org/10.1162/jocn.1996.8.6.551}
+
+\leavevmode\hypertarget{ref-bentin2002}{}%
+Bentin, S., \& Golland, Y.
+(2002).
+Meaningful processing of meaningless stimuli: The influence of perceptual experience on early visual processing of faces.
+\emph{Cognition}, \emph{86}(1), B1--B14.
+\url{https://doi.org/10.1016/S0010-0277(02)00124-5}
+
+\leavevmode\hypertarget{ref-bocanegra2009}{}%
+Bocanegra, B. R., \& Zeelenberg, R. (2009). Emotion improves and impairs early vision. \emph{Psychological Science}, \emph{20}(6), 707--713. \url{https://doi.org/10.1111/j.1467-9280.2009.02354.x}
+
+\leavevmode\hypertarget{ref-boutonnet2015}{}%
+Boutonnet, B., \& Lupyan, G.
+(2015).
+Words jump-start vision: A label advantage in object recognition.
+\emph{Journal of Neuroscience}, \emph{35}(25), 9329--9335.
+\url{https://doi.org/10.1523/JNEUROSCI.5111-14.2015}
+
 \leavevmode\hypertarget{ref-buxfcrki2018}{}%
@@
 \url{https://doi.org/10.1016/j.jneumeth.2018.09.016}
+
+\leavevmode\hypertarget{ref-churchland1988}{}%
+Churchland, P. M. (1988). Perceptual plasticity and theoretical neutrality: A reply to jerry fodor. \emph{Philosophy of Science}, \emph{55}(2), 167--187. \url{https://doi.org/10.1086/289425}
+
+\leavevmode\hypertarget{ref-churchland1994}{}%
+Churchland, P. S., Ramachandran, V. S., \& Sejnowski, T. J. (1994). A critique of pure vision. In \emph{Large-scale neuronal theories of the brain} (pp. 23--60). The MIT Press.
+
+\leavevmode\hypertarget{ref-cole2012}{}%
+Cole, S., Balcetis, E., \& Dunning, D. (2012). Affective signals of threat increase perceived proximity: \emph{Psychological Science}. \url{https://doi.org/10.1177/0956797612446953}
+
+\leavevmode\hypertarget{ref-collins2014}{}%
+Collins, J.
+A., \& Olson, I.
+R.
+(2014).
+Knowledge is power: How conceptual knowledge transforms visual cognition.
+\emph{Psychonomic Bulletin \& Review}, \emph{21}(4), 843--860.
+\url{https://doi.org/10.3758/s13423-013-0564-3}
+
+\leavevmode\hypertarget{ref-dirusso2001}{}%
+Di Russo, F., Martínez, A., Sereno, M.
+I., Pitzalis, S., \& Hillyard, S.
+A.
+(2001).
+Cortical sources of the early components of the visual evoked potential.
+\emph{Human Brain Mapping}, \emph{15}(2), 95--111.
+\url{https://doi.org/10.1002/hbm.10010}
+
+\leavevmode\hypertarget{ref-eimer2011}{}%
+Eimer, M., Gosling, A., Nicholas, S., \& Kiss, M.
+(2011).
+The n170 component and its links to configural face processing: A rapid neural adaptation study.
+\emph{Brain Research}, \emph{1376}, 76--87.
+\url{https://doi.org/10.1016/j.brainres.2010.12.046}
+
+\leavevmode\hypertarget{ref-eiserbeck2020}{}%
+Eiserbeck, A., \& Abdel Rahman, R.
+(2020).
+Visual consciousness of faces in the attentional blink: Knowledge-based effects of trustworthiness dominate over appearance-based impressions.
+\emph{Consciousness and Cognition}, \emph{83}, 102977.
+\url{https://doi.org/10.1016/j.concog.2020.102977}
 
@@
 \url{https://doi.org/10.1017/S0140525X15000965}
+
+\leavevmode\hypertarget{ref-fodor1984}{}%
+Fodor, J. (1984). Observation reconsidered. \emph{Philosophy of Science}, \emph{51}(1), 23--43. \url{https://doi.org/10.1086/289162}
+
+\leavevmode\hypertarget{ref-fodor1983}{}%
+Fodor, J. A. (1983). \emph{The modularity of mind}. MIT Press.
+
+\leavevmode\hypertarget{ref-foxe2002}{}%
+Foxe, J.
+J., \& Simpson, G.
+V.
+(2002).
+Flow of activation from v1 to frontal cortex in humans.
+\emph{Experimental Brain Research}, \emph{142}(1), 139--150.
+\url{https://doi.org/10.1007/s00221-001-0906-7}
 
@@
 \url{https://doi.org/10.3389/fnins.2018.00048}
+
+\leavevmode\hypertarget{ref-gauthier2003a}{}%
+Gauthier, I., Curran, T., Curby, K.
+M., \& Collins, D.
+(2003).
+Perceptual interference supports a non-modular account of face processing.
+\emph{Nature Neuroscience}, \emph{6}(4), 428--432.
+\url{https://doi.org/10.1038/nn1029}
 
@@
 
-\leavevmode\hypertarget{ref-holmes2012}{}%
-Holmes, K.
-J., \& Wolff, P.
-(2012).
-Does categorical perception in the left hemisphere depend on language?
-\emph{Journal of Experimental Psychology.
-General}, \emph{141}(3), 439--443.
-\url{https://doi.org/10.1037/a0027289}
+\leavevmode\hypertarget{ref-haber1966}{}%
+Haber, R. N. (1966). Nature of the effect of set on perception. \emph{Psychological Review}, \emph{73}(4), 335--351. \url{https://doi.org/10.1037/h0023442}
 
@@
 \url{https://doi.org/10.1109/72.761722}
+
+\leavevmode\hypertarget{ref-jacques2010}{}%
+Jacques, C., \& Rossion, B.
+(2010).
+Misaligning face halves increases and delays the n170 specifically for upright faces: Implications for the nature of early face representations.
+\emph{Brain Research}, \emph{1318}, 96--109.
+\url{https://doi.org/10.1016/j.brainres.2009.12.070}
+
+\leavevmode\hypertarget{ref-johannes1995}{}%
+Johannes, S., Münte, T.
+F., Heinze, H.
+J., \& Mangun, G.
+R.
+(1995).
+Luminance and spatial attention effects on early visual processing.
+\emph{Cognitive Brain Research}, \emph{2}(3), 189--205.
+\url{https://doi.org/10.1016/0926-6410(95)90008-X}
 
@@
 
+\leavevmode\hypertarget{ref-lin1997}{}%
+Lin, E.
+L., \& Murphy, G.
+L.
+(1997).
+Effects of background knowledge on object categorization and part detection.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{23}(4), 1153--1169.
+\url{https://doi.org/10.1037/0096-1523.23.4.1153}
+
+\leavevmode\hypertarget{ref-luck2014}{}%
+Luck, S. J. (2014). Overview of common erp components. In \emph{An introduction to the event-related potential technique} (2nd ed., pp. 71--118). MIT Press.
+
+\leavevmode\hypertarget{ref-luck2000}{}%
+Luck, S.
+J., Woodman, G.
+F., \& Vogel, E.
+K.
+(2000).
+Event-related potential studies of attention.
+\emph{Trends in Cognitive Sciences}, \emph{4}(11), 432--440.
+\url{https://doi.org/10.1016/S1364-6613(00)01545-X}
+
+\leavevmode\hypertarget{ref-lupyan2012}{}%
+Lupyan, G. (2012). Linguistically modulated perception and cognition: The label-feedback hypothesis. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00054}
+
+\leavevmode\hypertarget{ref-lupyan2015}{}%
+Lupyan, G.
+(2015).
+Cognitive penetrability of perception in the age of prediction: Predictive systems are penetrable systems.
+\emph{Review of Philosophy and Psychology}, \emph{6}(4), 547--569.
+\url{https://doi.org/10.1007/s13164-015-0253-4}
+
+\leavevmode\hypertarget{ref-lupyan2020}{}%
+Lupyan, G., Abdel Rahman, R., Boroditsky, L., \& Clark, A.
+(2020).
+Effects of language on visual perception.
+\emph{Trends in Cognitive Sciences}, \emph{24}(11), 930--944.
+\url{https://doi.org/10.1016/j.tics.2020.08.005}
+
+\leavevmode\hypertarget{ref-machery2015}{}%
+Machery, E.
+(2015).
+Cognitive penetrability: A no-progress report.
+In J.
+Zeimbekis \& A.
+Raftopoulos (Eds.), \emph{The cognitive penetrability of perception: New philosophical perspectives}.
+Oxford University Press.
+\url{10.1093/acprof:oso/9780198738916.003.0002}
+
+\leavevmode\hypertarget{ref-maier2018}{}%
+Maier, M., \& Abdel Rahman, R. (2018). Native language promotes access to visual consciousness. \emph{Psychological Science}, \emph{29}(11), 1757--1772. \url{https://doi.org/10.1177/0956797618782181}
+
 \leavevmode\hypertarget{ref-maier2014}{}%
@@
 
+\leavevmode\hypertarget{ref-mangun1995}{}%
+Mangun, G. R. (1995). Neural mechanisms of visual selective attention. \emph{Psychophysiology}, \emph{32}(1), 4--18. \url{https://doi.org/10.1111/j.1469-8986.1995.tb03400.x}
+
+\leavevmode\hypertarget{ref-mangun1991}{}%
+Mangun, G.
+R., \& Hillyard, S.
+A.
+(1991).
+Modulations of sensory-evoked brain potentials indicate changes in perceptual processing during visual-spatial priming.
+\emph{Journal of Experimental Psychology.
+Human Perception and Performance}, \emph{17}(4), 1057--1074.
+\url{https://doi.org/10.1037//0096-1523.17.4.1057}
+
 \leavevmode\hypertarget{ref-matuschek2017}{}%
@@
 
+\leavevmode\hypertarget{ref-mo2011}{}%
+Mo, L., Xu, G., Kay, P., \& Tan, L.-H.
+(2011).
+Electrophysiological evidence for the left-lateralized effect of language on preattentive categorical perception of color.
+\emph{Proceedings of the National Academy of Sciences}, \emph{108}(34), 14026--14030.
+\url{https://doi.org/10.1073/pnas.1111860108}
+
 \leavevmode\hypertarget{ref-oldfield1971}{}%
 Oldfield, R. C. (1971). The assessment and analysis of handedness: The Edinburgh inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}
+
+\leavevmode\hypertarget{ref-phelps2016}{}%
+Phelps, E.
+A., Ling, S., \& Carrasco, M.
+(2016).
+Emotion facilitates perception and potentiates the perceptual benefits of attention: \emph{Psychological Science}.
+\url{https://journals.sagepub.com/doi/10.1111/j.1467-9280.2006.01701.x}
+
+\leavevmode\hypertarget{ref-pylyshyn1999}{}%
+Pylyshyn, Z.
+(1999).
+Is vision continuous with cognition?: The case for cognitive impenetrability of visual perception.
+\emph{Behavioral and Brain Sciences}, \emph{22}(3), 341--365.
+\url{https://doi.org/10.1017/S0140525X99002022}
 
@@
 R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-rossion1999}{}%
+Rossion, B., Delvenne, J.
+F., Debatisse, D., Goffaux, V., Bruyer, R., Crommelinck, M., \& Guérit, J.
+M.
+(1999).
+Spatio-temporal localization of the face inversion effect: An event-related potentials study.
+\emph{Biological Psychology}, \emph{50}(3), 173--189.
+\url{https://doi.org/10.1016/S0301-0511(99)00013-7}
 
@@
 
+\leavevmode\hypertarget{ref-sagiv2001}{}%
+Sagiv, N., \& Bentin, S.
+(2001).
+Structural encoding of human and schematic faces: Holistic and part-based processes.
+\emph{Journal of Cognitive Neuroscience}, \emph{13}(7), 937--951.
+\url{https://doi.org/10.1162/089892901753165854}
+
 \leavevmode\hypertarget{ref-samaha2018}{}%
@@
 
+\leavevmode\hypertarget{ref-suess2015}{}%
+Suess, F., Rabovsky, M., \& Abdel Rahman, R.
+(2015).
+Perceiving emotions in neutral faces: Expression processing is biased by affective person knowledge.
+\emph{Social Cognitive and Affective Neuroscience}, \emph{10}(4), 531--536.
+\url{https://doi.org/10.1093/scan/nsu088}
+
 \leavevmode\hypertarget{ref-tanaka2001}{}%
 Tanaka, J. W., \& Curran, T. (2001). A neural basis for expert object recognition. \emph{Psychological Science}, \emph{12}(1), 43--47. \url{https://doi.org/10.1111/1467-9280.00308}
+
+\leavevmode\hypertarget{ref-taylor2002}{}%
+Taylor, M. J. (2002). Non-spatial attentional effects on p1. \emph{Clinical Neurophysiology}, \emph{113}(12), 1903--1908. \url{https://doi.org/10.1016/S1388-2457(02)00309-7}
+
+\leavevmode\hypertarget{ref-thierry2016}{}%
+Thierry, G. (2016). Neurolinguistic relativity: How language flexes human perception and cognition. \emph{Language Learning}, \emph{66}(3), 690--713. \url{https://doi.org/10.1111/lang.12186}
 
@@
 
+\leavevmode\hypertarget{ref-vetter2014}{}%
+Vetter, P., \& Newen, A. (2014). Varieties of cognitive penetration in visual perception. \emph{Consciousness and Cognition}, \emph{27}, 62--75. \url{https://doi.org/10.1016/j.concog.2014.04.007}
+
 \leavevmode\hypertarget{ref-R-buildmer}{}%
 Voeten, C. C. (2020). \emph{buildmer: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
+
+\leavevmode\hypertarget{ref-vogel2000}{}%
+Vogel, E. K., \& Luck, S. J. (2000). The visual n1 component as an index of a discrimination process. \emph{Psychophysiology}, \emph{37}(2), 190--203.
 
@@
 \url{https://doi.org/10.1162/jocn_a_01404}
-\end{cslreferences}
 

### 2021-01-05 analysis/apa_7_figures/manuscript.tex
add discussion section + rmd for master thesis

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%

% Store the code of efloat re-definitions into \efloatredefinitions
% (This code must be defined before the efloat package is loaded.)
\makeatletter
\newcommand\efloatredefinitions{}
\newcommand\efloat@AtBeginDocument{\g@addto@macro\efloatredefinitions}
\makeatother

\documentclass[
  english,
  man,12pt,twoside]{apa7}

\usepackage[capposition=top]{floatrow}

% Do the efloat re-definitions after the re-definitions of floatrow were done
%\show\efloatredefinitions
\AtBeginDocument{\efloatredefinitions} % or simply \efloatredefinitions after \begin{document}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Alexander Enge1},
  pdflang={en-EN},
  pdfkeywords={objects, semantic knowledge, visual perception, event-related potentials},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{}
\keywords{objects, semantic knowledge, visual perception, event-related potentials\newline\indent Word count: }
\usepackage{csquotes}
\raggedbottom
\linespread{1.5}
\fancyhead{}
\fancyhead[RO,LE]{\thepage}
\fancyhead[LO,RE]{Semantic Knowledge and Unfamiliar Objects}
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\doublespacing}
\captionsetup[figure]{font={stretch=1,scriptsize}}
\usepackage[all]{nowidow}
\usepackage[bottom]{footmisc}
\interfootnotelinepenalty10000
\usepackage[export]{adjustbox}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Event-Related Potentials of the Semantically\\
Informed Perception of Unfamiliar Objects}
\author{Alexander Enge}
\date{}

\authornote{

\addORCIDlink{Alexander Enge}{0000-0003-0100-2297}, student no. 581331.

The preprocessed data and code for this study are openly available at \url{https://osf.io/uksbc/}.

We have no conflict of interest to disclose.

Correspondence concerning this article should be addressed to Alexander Enge, Rudower Chaussee 18, 12489 Berlin. E-mail: \href{mailto:alexander.enge@hu-berlin.de}{\nolinkurl{alexander.enge@hu-berlin.de}}

}

\affiliation{\vspace{0.5cm}Humboldt-Universität zu Berlin}

\abstract{
Does our perception of an object change as soon as we discover what it is for? This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it pertains to the long-standing debate around the (im)penetrability of perception by ``higher'' cognitive capacities. In this experiment, we showed participants (\emph{n} = 24) pictures of 120 unfamiliar objects either together with valid information about their function---leading to semantically informed perception---or together with invalid information---resulting in naive perception. We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of perceiving objects differed from one another. We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component. When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place. We replicated these novel findings in an independent sample (\emph{n} = 24). Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
}

\begin{document}
\maketitle

\setcounter{page}{1}

How does our perception of an object change as soon as we discover what it is for? In this study, we presented participants with unfamiliar objects which were preceded either by valid information about their function, leading to semantically informed perception, or by misleading information, leading to naive perception. Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temopral resoulation of event-related brain potentials (ERPs).

The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate. This debate revolves around the question of whether or not our perception of the (visual) world should be thought of as an encapsulated module whose processing is determined solely by the visual input reaching our retina. According to this view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1984, 1983; Machery, 2015; Pylyshyn, 1999). Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects (Goodale \& Milner, 1992; Marr, 1982).

Conversely, this position is challenged by the view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., P. M. Churchland, 1988; P. S. Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017). The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas (e.g., visual areas V1 and V2; Bullier, 2001; Gilbert \& Li, 2013), as well as behavioral evidence, have inspired theories of visual perception that emphasize the top-down influence of cognitive processes. The reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002), for instance, assumes that conscious visual perception occurs initially at the level of whole objects or object categories. Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections. Along similar lines, the label feedback hypothesis (Lupyan, 2012) posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially. Finally, an active role of top-down influences is also promoted by theories of vision falling under the umbrella of Bayesian inference and predictive coding (e.g., Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).

Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition (for review, see Collins \& Olson, 2014; Vetter \& Newen, 2014). These aspects of cognition may include transient states such as emotions (Bocanegra \& Zeelenberg, 2009; e.g., Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019). Despite this wealth of theory and empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).

One productive way to investigate top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge. This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).

The visual P1 component of the ERP refers to a positive deflection peaking as early as 100--150 ms after stimulus onset at occipital channels. It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri (Di Russo et al., 2001; Foxe \& Simpson, 2002; Mangun, 1995). The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus (e.g., size, luminance, and contrast; Di Russo et al., 2001; Johannes et al., 1995; Luck, 2014), which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception. For instance, it is enhanced when participants pay attention to the spatial location (Luck et al., 2000; Mangun, 1995; Mangun \& Hillyard, 1991) or certain non-spatial features (Taylor, 2002) of the stimulus.

The visual N170 (or N1) component refers to the negative deflection following the P1 and is maximal around 150--200 ms after stimulus onset at occipito-temporal channels. Just as the P1, it is influenced by visual parameters of the stimulus (Johannes et al., 1995) and by selective attention, especially when participants are required to discriminate between different visual stimuli (Mangun \& Hillyard, 1991; Vogel \& Luck, 2000). Importantly, the N170 is enlarged (i.e.,~more negative) in response to faces (Bentin et al., 1996; Bruno Rossion \& Jacques, 2011) and other visual stimuli for which one happens to be an expert (e.g., birds, dogs, or cars; Gauthier, Curran, et al., 2003; Tanaka \& Curran, 2001). This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as the holistic configuration of these features (Eimer et al., 2011; Jacques \& Rossion, 2010; B. Rossion et al., 1999; Sagiv \& Bentin, 2001). Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimulus.

Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration (Kutas \& Federmeier, 2011; Lau et al., 2008; Rabovsky et al., 2018). It begins approximately 300 ms after stimulus onset and is most pronounced at centro-parietal channels. A modulation of the N400 component by cognitive capacities such as knowledge can be taken as evidence for a post-perceptual influence on stimulus processing.

Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects (Abdel Rahman \& Sommer, 2008; Gratton et al., 2009; Maier et al., 2014; Maier \& Rahman, 2019; Bruno Rossion et al., 2004; B. Rossion et al., 2002; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019). Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing. This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (i.e., cooking recipes) for the other half of the objects (Abdel Rahman \& Sommer, 2008, Experiment 1). After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information. In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this has not been the case. Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing. Interestingly, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects. The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm (Weller et al., 2019). Here, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink. This can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.

A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects which were rendered difficult to recognize by converting them to two-tone, ``Mooney'' images (Samaha et al., 2018, Experiment 4). In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content. When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images of objects than for perceptually-trained images of objects. As before, these effects of perceiving objects in a semantically informed way seems to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task. This alternative approach further corroborates an early influence of semantic information on the visual perception of objects.

All the previously mentioned studies have in common that they investigated the effects of semantic knowledge on the visual perception of objects only \emph{after} an extensive learning phase had taken place (Abdel Rahman \& Sommer, 2008; Gauthier, James, et al., 2003; Maier et al., 2014; Maier \& Rahman, 2019; Bruno Rossion et al., 2004; B. Rossion et al., 2002; Samaha et al., 2018; Weller et al., 2019). Participants performed one or multiple training sessions during which they encountered each object together with its respective label or description multiple times. The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Rahman, 2019) or were spread out across multiple days or weeks (Bruno Rossion et al., 2004; B. Rossion et al., 2002). While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three conceptual questions unresolved.

The first question is if we can detect any electrophysiological correlates of semantic insight, that is,~the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on). The second question is how much learning is actually necessary before reliable top-down effects of knowledge on ERP amplitudes can be obtained: Does it actually take dozens of repetitions per object or may a single exposure to the object together with the relevant semantic information be enough? The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process? By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we hope to provide tentative answers to all three of these questions.

In the two experiments subsequently reported, participants were presented with real-word objects that were presumed to be unfamiliar to most of them. They first viewed each of these objects without any semantic information. This first part served as a naive baseline to rule out that ERPs would differ in response to the objects based solely on low-level visual differences. Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords. These keywords could either correctly describe the typcial function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could mislead participants by describing the function of a different object, thus keeping the perception of the object semantically naive. During this second part, we were able measure the online influence of semantic insight on object-evoked ERPs as it happened. Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them---thereby mimicking previous studies (e.g., Abdel Rahman \& Sommer, 2008; Samaha et al., 2018; Weller et al., 2019). In all three parts, we examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (N400 component, 400--700 ms).

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

\hypertarget{method}{%
\subsection{Method}\label{method}}

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment. No a priori power analysis was carried out and the sample size was chosen in line with other EEG studies in our lab at the time of data collection. All participants were right-handed according to the Edinburgh inventory (Oldfield, 1971) and reported normal or corrected-to-normal vision. They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum). A list of these unfamiliar objects can be found in the appendix. All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz. At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.

For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g., current--measuring, pottery--drumming). As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects. The matching keywords were expected to induce semantically informed perception (i.e.,~participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive. All participants saw each unfamiliar object with only one type of keywords (matching or non-matching). This assignment of keywords and objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants. The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

Each experimental session consisted of three parts (see Figure \ref{fig:exp1-plot}A). In the \emph{pre-insight} part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords. Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s. The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects. The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) ``I know what this is or have a strong assumption,'' (b) ``I have an assumption what this is,'' (c) ``I have rather no assumption what this is,'' or (d) ``I don't know what this is and have no assumption.'' Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively. The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/exp1-plot-1}

}

\caption{Procedure and Results of Experiment 1}\label{fig:exp1-plot}
\floatfoot{\scriptsize\emph{Note.} (A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing. In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception. In the post-insight part, the same objects were presented again without the keywords. (B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts. Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part. Ampl. = amplitude.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.}
\end{figure}

In the \emph{insight} part, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception). Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s. Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s. The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).

Finally, in the \emph{post-insight} part, the unfamiliar objects were presented for a third time with an identical trial structure as in the pre-insight part, that is, without any keywords. Note that the insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight part (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight part (without keywords) before moving on to the next block consisting of 30 different objects. They continued like this until all four blocks were completed in both parts. In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight part and 120 unfamiliar objects in the pre-insight, insight, and post-insight parts). It took participants approximately 35 minutes to complete.

\hypertarget{eeg-recording-and-preprocessing}{%
\subsubsection{EEG Recording and Preprocessing}\label{eeg-recording-and-preprocessing}}

The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system (American Electroencephalographic Society, 1991) and referenced online to an external electrode placed on the left mastoid (M1). Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively. During the recording, electrode impedance was kept below 5 kΩ. An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1,000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.

Offline, the data were preprocessed using the MNE software (Version 0.21.0; Gramfort et al., 2013) in Python (Version 3.8.5; van Rossum \& Drake, 2009). First, all scalp electrodes were re-referenced to the common average. Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA). The first 15 components were extracted by the FastICA algorithm (Hyvärinen, 1999) after temporarily low-pass filtering the data at 1 Hz. Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the \emph{find\_bads\_eog} function. After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied. Next, the continuous EEG was epoched into segments of 2,000 ms, starting 500 ms before the onset of the visual presentation of each unfamiliar object. The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset. Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis. This led to the exclusion of an average of 2.4 trials per participant (= 0.7\%; range 0 to 24 trials). Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see scalp topographies in Figure \ref{fig:exp1-plot}B).

\hypertarget{statistical-analysis}{%
\subsubsection{Statistical Analysis}\label{statistical-analysis}}

First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in the pre-insight part (i.e.,~before any keywords were presented). This led to the exclusion of an average of 7.5 objects per participant (= 6.3\% of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \ref{fig:exp1-plot}A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords \emph{and} if participants indicated knowing what the object was or having an assumption. This was the case for an average of 27.0 objects per participant (= 44.9\% of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords \emph{and} if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of 48.8 objects per participant (= 81.2\% of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occurr---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).

The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018). For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages. First, they can account not only for the non-independence of data points coming from the same participant but also simultaneously for the non-independence of data points coming from the same item. In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012). Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions. Such a situation is inevitable in designs where the assignment of trials to conditions is (co-)determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone (e.g., Fröber et al., 2017).

Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively. All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.,~subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.,~subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition. For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to Schad et al. (2020). To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects (Barr et al., 2013). We then performed a model selection algorithm as proposed by Matuschek et al. (2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test. Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model. All models were computed in R (Version 4.0.2; R Core Team, 2020) using the lme4 package (Version 1.1.23; Bates et al., 2015). The optimizer function \emph{bobyqa} with 20,000 iterations was used for maximum likelihood estimation. The model selection algorithm via likelihood ratio tests was performed using the buildmer package (Version 1.7.1; Voeten, 2020). Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts. All \emph{p}-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package (Version 3.1.2; Kuznetsova et al., 2017).

The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\url{https://osf.io/uksbc/}). Unfortuntaly, lack of informed consent prevents us from sharing the raw EEG data.

\hypertarget{results}{%
\subsection{Results}\label{results}}

Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function. Only in the insight part, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object. The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \ref{fig:exp1-plot}A), thereby making sure that semantically informed and naive perception did indeed occur. The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N170 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp1-table}Results of linear mixed-effects regression models for Experiment 1}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N170}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 10.89 (2, 24.5) & < .001 & 14.18 (2, 24.9) & < .001 & 32.85 (2, 25.6) & < .001\\
Condition & 0.60 (1, 5343.5) & .438 & 0.30 (1, 24.2) & .586 & 13.00 (1, 24.4) & .001\\
Pt. × con. & 2.30 (2, 4605.0) & .100 & 4.84 (2, 4878.2) & .008 & 10.91 (2, 5120.9) & < .001\\
\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Pre-insight part & -0.03 [-0.53, 0.47] & .913 & -0.12 [-0.68, 0.44] & .665 & -0.20 [-0.65, 0.26] & .400\\
Insight part & -0.18 [-0.68, 0.32] & .490 & -0.64 [-1.20, -0.08] & .026 & 0.93 [0.48, 1.39] & < .001\\
Post-insight part & 0.55 [0.05, 1.05] & .031 & 0.43 [-0.14, 0.99] & .136 & 1.00 [0.54, 1.46] & < .001\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, con. = condition, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.89, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp1-table}). In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}(1, 24.4) = 13.00, \emph{p} = .001. Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4605.0) = 2.30, \emph{p} = .100. To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.

\hypertarget{erps-before-insight-was-occurring}{%
\subsubsection{ERPs Before Insight Was Occurring}\label{erps-before-insight-was-occurring}}

In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .400 (see Table \ref{tab:exp1-table} and Figure \ref{fig:exp1-plot}B). On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs.~naive perception) had not yet taken place. On the other hand, the absence of reliable differences in this part can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in the other two parts cannot be accounted for by visual differences between the objects in the two conditions. Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report would have made it possible for such visual differences to emerge as a confounding factor. If they did, however, one would expect to detect these differences even before any keywords were presented, which we have now seen was not the case.

\hypertarget{erps-while-insight-was-occurring}{%
\subsubsection{ERPs While Insight Was Occurring}\label{erps-while-insight-was-occurring}}

In the insight part, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition). When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e.,~more negative), \emph{b} = -0.64 µV, \emph{p} = .026, and the amplitude of the N400 component was significantly reduced (i.e.,~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when the object was viewed naively without relevant semantic information. As in the pre-insight part, there were no reliable differences in the P1 component, \emph{p} = .490.

\hypertarget{erps-after-insight-had-occurred}{%
\subsubsection{ERPs After Insight Had Occurred}\label{erps-after-insight-had-occurred}}

In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part), to test whether the semantic information had any lasting effects on the processing of the objects. As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the effect in the N170 component did not reoccur, \emph{p} = .136. Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e.,~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.55 µV, \emph{p} = .031.

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-inisight part) they were able to understand what kind of object they saw. To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.

In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms). When the same objects were presented once more in the post-insigt part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for whic semantically informed perception had taken place.

Because of the novelty of our experimental paradigm and the findings of Experiment 1, we ran a replication study to assess the robustness of these effects in another samples of participants.

\hypertarget{experiment-2}{%
\section{Experiment 2}\label{experiment-2}}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}

Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29 years) who had not participated in Experiment 1. They had no history of psychological disorder or treatment, were right-handed, and reported normal or corrected-to-normal vision. They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.

\hypertarget{materials-procedure-and-analysis}{%
\subsubsection{Materials, Procedure, and Analysis}\label{materials-procedure-and-analysis}}

All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1. An average of 7.0 objects per participant (= 5.8\% of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses. Based on participants' responses in the insight part, an average of 26.4 objects were assigned to the semantically informed condition (= 44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (= 82.0\% of objects presented with a non-matching description). Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials per participant (= 3.0\%; range 0 to 85 trials).

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp2-table}Results of linear mixed-effects regression models for Experiment 2}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N170}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 17.45 (2, 5267.1) & < .001 & 16.57 (2, 25.1) & < .001 & 70.12 (2, 25.2) & < .001\\
Condition & 0.02 (1, 5276.9) & .900 & 0.98 (1, 5228.5) & .322 & 19.95 (1, 5242.5) & < .001\\
Pt. × con. & 3.60 (2, 5267.1) & .027 & 1.25 (2, 4756.5) & .287 & 7.92 (2, 4714.9) & < .001\\
\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Pre-insight part & -0.16 [-0.71, 0.40] & .582 & -0.03 [-0.53, 0.48] & .920 & 0.04 [-0.43, 0.50] & .877\\
Insight part & -0.48 [-1.03, 0.08] & .094 & -0.48 [-0.99, 0.03] & .064 & 1.33 [0.87, 1.79] & < .001\\
Post-insight part & 0.57 [0.01, 1.13] & .047 & 0.06 [-0.45, 0.57] & .818 & 0.47 [0.01, 0.93] & .047\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, con. = condition, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.57, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp2-table}). Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}(1, 5242.5) = 19.95, \emph{p} \textless{} .001. The part × condition interaction was significant in the P1 component, \emph{F}(2, 5267.1) = 3.60, \emph{p} = .027, and in the N400 component, \emph{F}(2, 4714.9) = 7.92, \emph{p} \textless{} .001, but not in the N170 component, \emph{F}(2, 4756.5) = 1.25, \emph{p} = .287.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/exp2-plot-1}

}

\caption{Results of Experiment 2}\label{fig:exp2-plot}
\floatfoot{\scriptsize\emph{Note.} ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment. In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-inisght part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064). Ampl. = amplitude.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.}
\end{figure}

\hypertarget{erps-before-insight-was-occurring-1}{%
\subsubsection{ERPs Before Insight Was Occurring}\label{erps-before-insight-was-occurring-1}}

As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .582 (see Table \ref{tab:exp2-table} and Figure \ref{fig:exp2-plot}).

\hypertarget{erps-while-insight-was-occurring-1}{%
\subsubsection{ERPs While Insight Was Occurring}\label{erps-while-insight-was-occurring-1}}

As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs.~non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, \emph{b} = -0.48 µV, \emph{p} = .064, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.

\hypertarget{erps-after-insight-had-occurred-1}{%
\subsubsection{ERPs After Insight Had Occurred}\label{erps-after-insight-had-occurred-1}}

As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.57 µV, \emph{p} = .047. Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.47 µV, \emph{p} = .047.

\hypertarget{joint-analysis-of-experiments-1-and-2}{%
\subsubsection{Joint Analysis of Experiments 1 and 2}\label{joint-analysis-of-experiments-1-and-2}}

In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2. This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2. Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast {[}i.e.,~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al. (2020){]}. This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes. They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2. Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit (Matuschek et al., 2017; Voeten, 2020).

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:joint-table}Results of linear mixed-effects regression models for Experiments 1 and 2 combined}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N170}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 12.34 (2, 49.1) & < .001 & 30.08 (2, 50.3) & < .001 & 94.61 (2, 50.6) & < .001\\
Condition & 0.15 (1, 10573.1) & .699 & 1.16 (1, 45.2) & .287 & 41.38 (1, 10593.6) & < .001\\
Experiment & 0.33 (1, 48.2) & .567 & 2.50 (1, 48.0) & .121 & 4.96 (1, 48.4) & .031\\
Pt. × con. & 3.90 (2, 9004.9) & .020 & 5.26 (2, 9904.1) & .005 & 15.34 (2, 10091.0) & < .001\\
Pt. × exp. & 0.04 (2, 49.1) & .966 & 0.58 (2, 50.3) & .565 & 2.55 (2, 50.6) & .088\\
Ins. × exp. & 0.43 (1, 10573.1) & .514 & 0.06 (1, 45.2) & .805 & 0.07 (1, 10593.6) & .785\\
Pt. × con. × exp. & 0.03 (2, 9004.9) & .968 & 0.58 (2, 9904.1) & .559 & 2.54 (2, 10091.0) & .079\\
\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Pre-insight part & -0.10 [-0.47, 0.28] & .616 & -0.10 [-0.48, 0.29] & .611 & -0.09 [-0.39, 0.22] & .577\\
Insight part & -0.24 [-0.62, 0.13] & .202 & -0.57 [-0.96, -0.18] & .004 & 1.10 [0.80, 1.41] & < .001\\
Post-insight part & 0.47 [0.09, 0.84] & .014 & 0.24 [-0.15, 0.63] & .225 & 0.73 [0.42, 1.04] & < .001\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.34, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}(1, 10593.6) = 41.38, \emph{p} \textless{} .001. Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 3.90, all \emph{p}s \textless{} .020. While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.96, \emph{p} = .031, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.

Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Figure \ref{fig:joint-plot}). This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s \textgreater{} .577, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/joint-plot-1}

}

\caption{Measured and Modelled ERP Amplitudes for Experiments 1 and 2 Combined}\label{fig:joint-plot}
\floatfoot{\scriptsize\emph{Note.} The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred). The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval. Ampl. = amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.}
\end{figure}

\hypertarget{control-analysis}{%
\subsubsection{Control Analysis}\label{control-analysis}}

One may raise concerns whether the modulation of the N170 component in the insight part genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it may be driven by the objects in the other, semantically naive condition. Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration. Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages. To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted. Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing. Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Methods).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001. Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize. Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}

Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400). Objects for which participants experienced semantically informed perception via matcing keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes. When these objects were presented once more, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

\hypertarget{summary-of-main-findings}{%
\paragraph{Summary of Main Findings}\label{summary-of-main-findings}}

Here we investigated if obtaining a semantic understanding of what a previously unfamiliar object is or does on how has an influence on how we perceive and process it. To this end, we have measured ERPs while participants watched unfamiliar objects before, while, and after receiving semantic information about them. For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was misleading, thus leading to naive perception. We found semantically informed percpetion to be accompanied by enlarged (i.e.,more negative) N170 amplitudes and reduced (i.e.,less negative) N400 amplitudes. If the same objects were presented again without the semantic information, only the N400 component remaind significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e.,more positive) in response to objects that had previously triggered semantically informed as compared to naive perception.

\hypertarget{interpretation-of-the-n170-effect}{%
\paragraph{Interpretation of the N170 Effect}\label{interpretation-of-the-n170-effect}}

\hypertarget{interpretation-of-the-n400-effect}{%
\paragraph{Interpretation of the N400 Effect}\label{interpretation-of-the-n400-effect}}

\hypertarget{interpretation-of-the-p1-effect}{%
\paragraph{Interpretation of the P1 Effect}\label{interpretation-of-the-p1-effect}}

\hypertarget{theoretical-considerations}{%
\paragraph{Theoretical Considerations}\label{theoretical-considerations}}

While the limited spatial resolution of the EEG does not allow for localizing these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI studies that semantic information can feed back into the earliest of visual areas. (Hsieh et al., 2010) showed participants indiscernible two-tone (``Mooney'') versions of images before and after showing them the original versions. They found that the brain responses to the original image was correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place). Interestingly, this increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (V1/V2/V3). Both of these cortical sites are consistent with the neural generators of the P1 and N170 components of the ERP, both of which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.

\hypertarget{limitations}{%
\paragraph{Limitations}\label{limitations}}

\hypertarget{conclusion-outlook}{%
\paragraph{Conclusion \& Outlook}\label{conclusion-outlook}}

\newpage

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\begin{center}
\begin{ThreePartTable}

\begin{longtable}{llll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:appendix}Unfamiliar object stimuli}\\
\toprule
 & \# & Matching keywords & Non-matching keywords\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:appendix} continued}}\\
\toprule
 & \# & Matching keywords & Non-matching keywords\\
\midrule
\endhead
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/1.png} & 1 & elektrische Spannung prüfen & Makkaroni formen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/2.png} & 2 & Makkaroni formen & Kuh vom Zaun abhalten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/3.png} & 3 & Knochen sägen & Streckenmaß Sonnenlicht nutzen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/4.png} & 4 & Unkraut jäten & Uhr mit Wärme betreiben\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/5.png} & 5 & Mausefalle zuschnappen & Brillenglas zuschneiden\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/6.png} & 6 & Goldmünzen wiegen & Farbe vom Fenster abschleifen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/7.png} & 7 & Knie fixieren & Buchstaben tippen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/8.png} & 8 & Eierkarton pressen & Tabak zermahlen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/9.png} & 9 & Baum erklettern & Rotation Ladung erzeugen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/10.png} & 10 & Buchstaben tippen & Pferdehuf Halt geben\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/11.png} & 11 & Akkordeon spielen & Seil schneiden\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/12.png} & 12 & Körper trainieren & Buch offen halten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/13.png} & 13 & Farbe vom Fenster abschleifen & von Hand zentrifugieren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/14.png} & 14 & Außenbereich heizen & Rasierklinge schärfen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/15.png} & 15 & Pflanzenteile vergrößern & Katzenklo sich selbst reinigen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/16.png} & 16 & Krawatten aufhängen & Zeichnungen vermessen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/17.png} & 17 & Schallplatte abtasten & Ball katapultieren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/18.png} & 18 & Glas schneiden & Eier wiegen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/19.png} & 19 & Briketts pressen & Narkosemittel abgeben\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/20.png} & 20 & Orgelton erzeugen & Bandage rollen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/21.png} & 21 & Spannung erzeugen & Fußstütze reiten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/22.png} & 22 & Narkosemittel abgeben & Nüsse aufbrechen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/23.png} & 23 & Bandage rollen & Schnee rodeln\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/24.png} & 24 & Weinfass Loch einschlagen & Tier einfangen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/25.png} & 25 & Flaschenkorken einführen & Pferd im Moor laufen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/26.png} & 26 & Automat Eier ausbrüten & Windgeschwindigkeit messen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/27.png} & 27 & Korngarbe greifen & Treibhaus heizen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/28.png} & 28 & Brief wiegen & Korngarbe greifen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/29.png} & 29 & Löcher bohren & Sonnenlicht Intensität messen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/30.png} & 30 & Angelschnur kurbeln & Glaskörper musizieren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/31.png} & 31 & Kurven malen & Nussöl pressen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/32.png} & 32 & Radiofrequenz einstellen & Erektion helfen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/33.png} & 33 & Zäpfchen pressen & Unkraut jäten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/34.png} & 34 & Fass öffnen & Pflanzenteile vergrößern\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/35.png} & 35 & Bergbaustollen beleuchten & Knie fixieren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/36.png} & 36 & Kuh vom Zaun abhalten & Radiofrequenz einstellen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/37.png} & 37 & Saatgut gleichmäßig aussäen & Fass öffnen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/38.png} & 38 & Flaschen trocknen & Bleistift anspitzen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/39.png} & 39 & Uhr mit Wärme betreiben & Körper untersuchen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/40.png} & 40 & Tonpott trommeln & Piano stimmen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/41.png} & 41 & Sprengstoffexplosion auslösen & Fisch wiegen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/42.png} & 42 & Pferdehuf Halt geben & Zäpfchen pressen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/43.png} & 43 & Bleistift anspitzen & Angel Köder markieren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/44.png} & 44 & Nussöl pressen & Zeichen einbrennen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/45.png} & 45 & Rasierklinge schärfen & Kurven malen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/46.png} & 46 & heiße Platten anheben & Kleidung im Eimer waschen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/47.png} & 47 & Film aufspulen & Mund offen halten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/48.png} & 48 & Waffe entflammen & Uhrzeit anzeigen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/49.png} & 49 & Mikroskop-Proben schneiden & heiße Platten anheben\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/50.png} & 50 & Glaskörper musizieren & Kork flach pressen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/51.png} & 51 & Dampf zerstäuben & Buch binden\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/52.png} & 52 & Mandeln operieren & Film aufspulen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/53.png} & 53 & Toastbrot rösten & Autobatterie Spannung testen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/54.png} & 54 & Fußstütze reiten & Stromstärke messen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/55.png} & 55 & Türgelenk Feuer überstehen & Botschaft telegrafieren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/56.png} & 56 & Schnee rodeln & Dampf zerstäuben\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/57.png} & 57 & Nüsse aufbrechen & Ziegelsteine formen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/58.png} & 58 & Radiergummi mit Strom betreiben & Münzen aufbewahren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/59.png} & 59 & Treibhaus heizen & Messer schleifen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/60.png} & 60 & Botschaft telegrafieren & Toastbrot rösten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/61.png} & 61 & Angel Köder markieren & Baum erklettern\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/62.png} & 62 & Katzenklo sich selbst reinigen & Tankfüllstand messen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/63.png} & 63 & Körper untersuchen & Schuhe auf Eis laufen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/64.png} & 64 & Brillenglas zuschneiden & Saatgut gleichmäßig aussäen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/65.png} & 65 & Draht wickeln & Bergbaustollen beleuchten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/66.png} & 66 & Buch offen halten & Sprengstoffexplosion auslösen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/67.png} & 67 & Feldanbau häckseln & Draht wickeln\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/68.png} & 68 & Schnurlot absenken & Korken formen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/69.png} & 69 & Sternenbilder vermessen & Schnurlot absenken\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/70.png} & 70 & Nachricht morsen & Feldanbau häckseln\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/71.png} & 71 & Musikgerät stampfen & Goldmünzen wiegen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/72.png} & 72 & Schuhe auf Eis laufen & Geschwindigkeit ermitteln\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/73.png} & 73 & Geschwindigkeit ermitteln & Mausefalle zuschnappen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/74.png} & 74 & Zeichen einbrennen & Luftdruck messen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/75.png} & 75 & Tabak zermahlen & Flaschen trocknen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/76.png} & 76 & Stromstärke messen & Mandeln operieren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/77.png} & 77 & Tier einfangen & Maiskolben entkörnen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/78.png} & 78 & Messer schleifen & Schritte vergrößern\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/79.png} & 79 & Leierkasten klingen & Fass anheben\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/80.png} & 80 & Buch binden & Löcher bohren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/81.png} & 81 & Kork flach pressen & Elektroschock spielen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/82.png} & 82 & Tabletten zerteilen & Blumentopf sich selbst wässern\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/83.png} & 83 & Fass anheben & Mikroskop-Proben schneiden\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/84.png} & 84 & Pferd im Moor laufen & Luft abpumpen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/85.png} & 85 & altes Ritual hacken & Spannung erzeugen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/86.png} & 86 & Kleidung im Eimer waschen & Türgelenk Feuer überstehen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/87.png} & 87 & Maiskolben entkörnen & Brief wiegen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/88.png} & 88 & Ball katapultieren & Radiergummi mit Strom betreiben\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/89.png} & 89 & Zeichnungen vermessen & Brenner löten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/90.png} & 90 & Elektroschock spielen & Weinfass Loch einschlagen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/91.png} & 91 & Lieferungen abzählen & Außenbereich heizen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/92.png} & 92 & Rotation Ladung erzeugen & Musikgerät stampfen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/93.png} & 93 & Herz durch Maschine ersetzen & Kerzen löschen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/94.png} & 94 & Seil schneiden & Akkordeon spielen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/95.png} & 95 & Fisch wiegen & Herz durch Maschine ersetzen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/96.png} & 96 & Kerzen löschen & Körper trainieren\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/97.png} & 97 & Korken formen & Sternenbilder vermessen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/98.png} & 98 & Erektion helfen & Waffe werfen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/99.png} & 99 & Streckenmaß Sonnenlicht nutzen & Kartoffeln stampfen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/100.png} & 100 & Luftdruck messen & Knochen sägen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/101.png} & 101 & Piano stimmen & Eierkarton pressen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/102.png} & 102 & von Hand zentrifugieren & Lieferungen abzählen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/103.png} & 103 & Kartoffeln stampfen & Nachricht morsen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/104.png} & 104 & Waffe werfen & elektrische Spannung prüfen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/105.png} & 105 & Tankfüllstand messen & Tonpott trommeln\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/106.png} & 106 & Uhrzeit anzeigen & altes Ritual hacken\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/107.png} & 107 & Windgeschwindigkeit messen & Waffe entflammen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/108.png} & 108 & Schlüsselloch stanzen & Automat Eier ausbrüten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/109.png} & 109 & Ziegelsteine formen & Schallplatte abtasten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/110.png} & 110 & Becher Schall auffangen & Schlüsselloch stanzen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/111.png} & 111 & Luft abpumpen & Briketts pressen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/112.png} & 112 & Mund offen halten & Orgelton erzeugen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/113.png} & 113 & Autobatterie Spannung testen & Becher Schall auffangen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/114.png} & 114 & Sonnenlicht Intensität messen & Krawatten aufhängen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/115.png} & 115 & Kutschrad anschließen & Angelschnur kurbeln\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/116.png} & 116 & Eier wiegen & Leierkasten klingen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/117.png} & 117 & Blumentopf sich selbst wässern & Glas schneiden\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/118.png} & 118 & Schritte vergrößern & Tabletten zerteilen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/119.png} & 119 & Münzen aufbewahren & Kutschrad anschließen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/120.png} & 120 & Brenner löten & Flaschenkorken einführen einführen\\
\bottomrule
\end{longtable}

\end{ThreePartTable}
\end{center}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}
%\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-abdelrahman2011}{}%
Abdel Rahman, R. (2011). Facing good and evil: Early brain signatures of affective biographical knowledge in face recognition. \emph{Emotion}, \emph{11}(6), 1397--1405. \url{https://doi.org/10.1037/a0024717}

\leavevmode\hypertarget{ref-abdelrahman2008}{}%
Abdel Rahman, R., \& Sommer, W. (2008). Seeing what we know and understand: How knowledge shapes perception. \emph{Psychonomic Bulletin \& Review}, \emph{15}(6), 1055--1063. \url{https://doi.org/10.3758/PBR.15.6.1055}

\leavevmode\hypertarget{ref-ahissar2004}{}%
Ahissar, M., \& Hochstein, S. (2004). The reverse hierarchy theory of visual perceptual learning. \emph{Trends in Cognitive Sciences}, \emph{8}(10), 457--464. \url{https://doi.org/10.1016/j.tics.2004.08.011}

\leavevmode\hypertarget{ref-americanelectroencephalographicsociety1991}{}%
American Electroencephalographic Society. (1991). {American Electroencephalographic Society} guidelines for standard electrode position nomenclature. \emph{Journal of Clinical Neurophysiology}, \emph{8}(2), 200--202.

\leavevmode\hypertarget{ref-baayen2008}{}%
Baayen, R. H., Davidson, D. J., \& Bates, D. M. (2008). Mixed-effects modeling with crossed random effects for subjects and items. \emph{Journal of Memory and Language}, \emph{59}(4), 390--412. \url{https://doi.org/10.1016/j.jml.2007.12.005}

\leavevmode\hypertarget{ref-balcetis2010}{}%
Balcetis, E., \& Dunning, D. (2010). Wishful seeing: More desired objects are seen as closer. \emph{Psychological Science}, \emph{21}(1), 147--152. \url{https://doi.org/10.1177/0956797609356283}

\leavevmode\hypertarget{ref-barr2013}{}%
Barr, D. J., Levy, R., Scheepers, C., \& Tily, H. J. (2013). Random effects structure for confirmatory hypothesis testing: Keep it maximal. \emph{Journal of Memory and Language}, \emph{68}(3), 255--278. \url{https://doi.org/10.1016/j.jml.2012.11.001}

\leavevmode\hypertarget{ref-R-lme4}{}%
Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear mixed-effects models using {lme4}. \emph{Journal of Statistical Software}, \emph{67}(1), 1--48. \url{https://doi.org/10.18637/jss.v067.i01}

\leavevmode\hypertarget{ref-bentin1996}{}%
Bentin, S., Allison, T., Puce, A., Perez, E., \& McCarthy, G. (1996). Electrophysiological studies of face perception in humans. \emph{Journal of Cognitive Neuroscience}, \emph{8}(6), 551--565. \url{https://doi.org/10.1162/jocn.1996.8.6.551}

\leavevmode\hypertarget{ref-bocanegra2009}{}%
Bocanegra, B. R., \& Zeelenberg, R. (2009). Emotion improves and impairs early vision. \emph{Psychological Science}, \emph{20}(6), 707--713. \url{https://doi.org/10.1111/j.1467-9280.2009.02354.x}

\leavevmode\hypertarget{ref-boutonnet2015}{}%
Boutonnet, B., \& Lupyan, G. (2015). Words jump-start vision: A label advantage in object recognition. \emph{Journal of Neuroscience}, \emph{35}(25), 9329--9335. \url{https://doi.org/10.1523/JNEUROSCI.5111-14.2015}

\leavevmode\hypertarget{ref-bullier2001}{}%
Bullier, J. (2001). Integrated model of visual processing. \emph{Brain Research Reviews}, \emph{36}(2), 96--107. \url{https://doi.org/10.1016/S0165-0173(01)00085-6}

\leavevmode\hypertarget{ref-buxfcrki2018}{}%
Bürki, A., Frossard, J., \& Renaud, O. (2018). Accounting for stimulus and participant effects in event-related potential analyses to increase the replicability of studies. \emph{Journal of Neuroscience Methods}, \emph{309}, 218--227. \url{https://doi.org/10.1016/j.jneumeth.2018.09.016}

\leavevmode\hypertarget{ref-churchland1988}{}%
Churchland, P. M. (1988). Perceptual plasticity and theoretical neutrality: A reply to {Jerry} {Fodor}. \emph{Philosophy of Science}, \emph{55}(2), 167--187. \url{https://doi.org/10.1086/289425}

\leavevmode\hypertarget{ref-churchland1994}{}%
Churchland, P. S., Ramachandran, V. S., \& Sejnowski, T. J. (1994). A critique of pure vision. In C. Koch \& J. L. Davis (Eds.), \emph{Computational neuroscience. Large-scale neuronal theories of the brain} (pp. 23--60). MIT Press.

\leavevmode\hypertarget{ref-cole2012}{}%
Cole, S., Balcetis, E., \& Dunning, D. (2012). Affective signals of threat increase perceived proximity. \emph{Psychological Science}. \url{https://doi.org/10.1177/0956797612446953}

\leavevmode\hypertarget{ref-collins2014}{}%
Collins, J. A., \& Olson, I. R. (2014). Knowledge is power: How conceptual knowledge transforms visual cognition. \emph{Psychonomic Bulletin \& Review}, \emph{21}(4), 843--860. \url{https://doi.org/10.3758/s13423-013-0564-3}

\leavevmode\hypertarget{ref-dirusso2001}{}%
Di Russo, F., Martínez, A., Sereno, M. I., Pitzalis, S., \& Hillyard, S. A. (2001). Cortical sources of the early components of the visual evoked potential. \emph{Human Brain Mapping}, \emph{15}(2), 95--111. \url{https://doi.org/10.1002/hbm.10010}

\leavevmode\hypertarget{ref-eimer2011}{}%
Eimer, M., Gosling, A., Nicholas, S., \& Kiss, M. (2011). The {N170} component and its links to configural face processing: A rapid neural adaptation study. \emph{Brain Research}, \emph{1376}, 76--87. \url{https://doi.org/10.1016/j.brainres.2010.12.046}

\leavevmode\hypertarget{ref-eiserbeck2020}{}%
Eiserbeck, A., \& Abdel Rahman, R. (2020). Visual consciousness of faces in the attentional blink: Knowledge-based effects of trustworthiness dominate over appearance-based impressions. \emph{Consciousness and Cognition}, \emph{83}, 102977. \url{https://doi.org/10.1016/j.concog.2020.102977}

\leavevmode\hypertarget{ref-firestone2016}{}%
Firestone, C., \& Scholl, B. J. (2016). Cognition does not affect perception: Evaluating the evidence for {``top-down''} effects. \emph{Behavioral and Brain Sciences}, \emph{39}. \url{https://doi.org/10.1017/S0140525X15000965}

\leavevmode\hypertarget{ref-fodor1984}{}%
Fodor, J. A. (1984). Observation reconsidered. \emph{Philosophy of Science}, \emph{51}(1), 23--43. \url{https://doi.org/10.1086/289162}

\leavevmode\hypertarget{ref-fodor1983}{}%
Fodor, J. A. (1983). \emph{The modularity of mind}. MIT Press.

\leavevmode\hypertarget{ref-foxe2002}{}%
Foxe, J. J., \& Simpson, G. V. (2002). Flow of activation from {V1} to frontal cortex in humans. \emph{Experimental Brain Research}, \emph{142}(1), 139--150. \url{https://doi.org/10.1007/s00221-001-0906-7}

\leavevmode\hypertarget{ref-fruxf6ber2017}{}%
Fröber, K., Stürmer, B., Frömer, R., \& Dreisbach, G. (2017). The role of affective evaluation in conflict adaptation: An {LRP} study. \emph{Brain and Cognition}, \emph{116}, 9--16. \url{https://doi.org/10.1016/j.bandc.2017.05.003}

\leavevmode\hypertarget{ref-fruxf6mer2018}{}%
Frömer, R., Maier, M., \& Abdel Rahman, R. (2018). Group-level {EEG}-processing pipeline for flexible single trial-based analyses including linear mixed models. \emph{Frontiers in Neuroscience}, \emph{12}. \url{https://doi.org/10.3389/fnins.2018.00048}

\leavevmode\hypertarget{ref-gauthier2003a}{}%
Gauthier, I., Curran, T., Curby, K. M., \& Collins, D. (2003). Perceptual interference supports a non-modular account of face processing. \emph{Nature Neuroscience}, \emph{6}(4), 428--432. \url{https://doi.org/10.1038/nn1029}

\leavevmode\hypertarget{ref-gauthier2003}{}%
Gauthier, I., James, T. W., Curby, K. M., \& Tarr, M. J. (2003). The influence of conceptual knowledge on visual discrimination. \emph{Cognitive Neuropsychology}, \emph{20}(3-6), 507--523. \url{https://doi.org/10.1080/02643290244000275}

\leavevmode\hypertarget{ref-gilbert2013}{}%
Gilbert, C. D., \& Li, W. (2013). Top-down influences on visual processing. \emph{Nature Reviews Neuroscience}, \emph{14}(5), 350--363. \url{https://doi.org/10.1038/nrn3476}

\leavevmode\hypertarget{ref-goodale1992}{}%
Goodale, M. A., \& Milner, A. D. (1992). Separate visual pathways for perception and action. \emph{Trends in Neurosciences}, \emph{15}(1), 20--25. \url{https://doi.org/10.1016/0166-2236(92)90344-8}

\leavevmode\hypertarget{ref-gramfort2013}{}%
Gramfort, A., Luessi, M., Larson, E., Engemann, D. A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& al., et. (2013). MEG and {EEG} data analysis with {MNE-Python}. \emph{Frontiers in Neuroscience}, \emph{7}. \url{https://doi.org/10.3389/fnins.2013.00267}

\leavevmode\hypertarget{ref-gratton2009}{}%
Gratton, C., Evans, K. M., \& Federmeier, K. D. (2009). See what {I} mean? An {ERP} study of the effect of background knowledge on novel object processing. \emph{Memory \& Cognition}, \emph{37}(3), 277--291. \url{https://doi.org/10.3758/MC.37.3.277}

\leavevmode\hypertarget{ref-hochstein2002}{}%
Hochstein, S., \& Ahissar, M. (2002). View from the top: Hierarchies and reverse hierarchies in the visual system. \emph{Neuron}, \emph{36}(5), 791--804. \url{https://doi.org/10.1016/S0896-6273(02)01091-7}

\leavevmode\hypertarget{ref-hsieh2010}{}%
Hsieh, P.-J., Vul, E., \& Kanwisher, N. (2010). Recognition alters the spatial pattern of {fMRI} activation in early retinotopic cortex. \emph{Journal of Neurophysiology}, \emph{103}(3), 1501--1507. \url{https://doi.org/10.1152/jn.00812.2009}

\leavevmode\hypertarget{ref-hyvuxe4rinen1999}{}%
Hyvärinen, A. (1999). Fast and robust fixed-point algorithms for independent component analysis. \emph{IEEE Transactions on Neural Networks}, \emph{10}(3), 626--634. \url{https://doi.org/10.1109/72.761722}

\leavevmode\hypertarget{ref-jacques2010}{}%
Jacques, C., \& Rossion, B. (2010). Misaligning face halves increases and delays the {N170} specifically for upright faces: Implications for the nature of early face representations. \emph{Brain Research}, \emph{1318}, 96--109. \url{https://doi.org/10.1016/j.brainres.2009.12.070}

\leavevmode\hypertarget{ref-johannes1995}{}%
Johannes, S., Münte, T. F., Heinze, H. J., \& Mangun, G. R. (1995). Luminance and spatial attention effects on early visual processing. \emph{Cognitive Brain Research}, \emph{2}(3), 189--205. \url{https://doi.org/10.1016/0926-6410(95)90008-X}

\leavevmode\hypertarget{ref-judd2012}{}%
Judd, C. M., Westfall, J., \& Kenny, D. A. (2012). Treating stimuli as a random factor in social psychology: A new and comprehensive solution to a pervasive but largely ignored problem. \emph{Journal of Personality and Social Psychology}, \emph{103}(1), 54--69. \url{https://doi.org/10.1037/a0028347}

\leavevmode\hypertarget{ref-kutas2011}{}%
Kutas, M., \& Federmeier, K. D. (2011). Thirty years and counting: Finding meaning in the {N400} component of the event-related brain potential ({ERP}). \emph{Annual Review of Psychology}, \emph{62}, 621--647. \url{https://doi.org/10.1146/annurev.psych.093008.131123}

\leavevmode\hypertarget{ref-R-lmerTest}{}%
Kuznetsova, A., Brockhoff, P. B., \& Christensen, R. H. B. (2017). {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software}, \emph{82}(13), 1--26. \url{https://doi.org/10.18637/jss.v082.i13}

\leavevmode\hypertarget{ref-lau2008}{}%
Lau, E. F., Phillips, C., \& Poeppel, D. (2008). A cortical network for semantics: (De)constructing the {N400}. \emph{Nature Reviews Neuroscience}, \emph{9}(12), 920--933. \url{https://doi.org/10.1038/nrn2532}

\leavevmode\hypertarget{ref-lin1997}{}%
Lin, E. L., \& Murphy, G. L. (1997). Effects of background knowledge on object categorization and part detection. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{23}(4), 1153--1169. \url{https://doi.org/10.1037/0096-1523.23.4.1153}

\leavevmode\hypertarget{ref-luck2014}{}%
Luck, S. J. (2014). Overview of common ERP components. In \emph{An introduction to the event-related potential technique} (2nd ed., pp. 71--118). MIT Press.

\leavevmode\hypertarget{ref-luck2000}{}%
Luck, S. J., Woodman, G. F., \& Vogel, E. K. (2000). Event-related potential studies of attention. \emph{Trends in Cognitive Sciences}, \emph{4}(11), 432--440. \url{https://doi.org/10.1016/S1364-6613(00)01545-X}

\leavevmode\hypertarget{ref-lupyan2015}{}%
Lupyan, G. (2015). Cognitive penetrability of perception in the age of prediction: Predictive systems are penetrable systems. \emph{Review of Philosophy and Psychology}, \emph{6}(4), 547--569. \url{https://doi.org/10.1007/s13164-015-0253-4}

\leavevmode\hypertarget{ref-lupyan2012}{}%
Lupyan, G. (2012). Linguistically modulated perception and cognition: The label-feedback hypothesis. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00054}

\leavevmode\hypertarget{ref-machery2015}{}%
Machery, E. (2015). Cognitive penetrability: A no-progress report. In J. Zeimbekis \& A. Raftopoulos (Eds.), \emph{The cognitive penetrability of perception: New philosophical perspectives}. Oxford University Press. \url{https://doi.org/10.1093/acprof:oso/9780198738916.003.0002}

\leavevmode\hypertarget{ref-maier2018}{}%
Maier, M., \& Abdel Rahman, R. (2018). Native language promotes access to visual consciousness. \emph{Psychological Science}, \emph{29}(11), 1757--1772. \url{https://doi.org/10.1177/0956797618782181}

\leavevmode\hypertarget{ref-maier2014}{}%
Maier, M., Glage, P., Hohlfeld, A., \& Abdel Rahman, R. (2014). Does the semantic content of verbal categories influence categorical perception? An {ERP} study. \emph{Brain and Cognition}, \emph{91}, 1--10. \url{https://doi.org/10.1016/j.bandc.2014.07.008}

\leavevmode\hypertarget{ref-maier2019}{}%
Maier, M., \& Rahman, R. A. (2019). No matter how: Top-down effects of verbal and semantic category knowledge on early visual perception. \emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{19}(4), 859--876. \url{https://doi.org/10.3758/s13415-018-00679-8}

\leavevmode\hypertarget{ref-mangun1995}{}%
Mangun, G. R. (1995). Neural mechanisms of visual selective attention. \emph{Psychophysiology}, \emph{32}(1), 4--18. \url{https://doi.org/10.1111/j.1469-8986.1995.tb03400.x}

\leavevmode\hypertarget{ref-mangun1991}{}%
Mangun, G. R., \& Hillyard, S. A. (1991). Modulations of sensory-evoked brain potentials indicate changes in perceptual processing during visual-spatial priming. \emph{Journal of Experimental Psychology. Human Perception and Performance}, \emph{17}(4), 1057--1074. \url{https://doi.org/10.1037//0096-1523.17.4.1057}

\leavevmode\hypertarget{ref-marr1982}{}%
Marr, D. (1982). \emph{Vision: A computational investigation into the human representation and processing of visual information}. W.H. Freeman.

\leavevmode\hypertarget{ref-matuschek2017}{}%
Matuschek, H., Kliegl, R., Vasishth, S., Baayen, H., \& Bates, D. (2017). Balancing {Type I} error and power in linear mixed models. \emph{Journal of Memory and Language}, \emph{94}, 305--315. \url{https://doi.org/10.1016/j.jml.2017.01.001}

\leavevmode\hypertarget{ref-mo2011}{}%
Mo, L., Xu, G., Kay, P., \& Tan, L.-H. (2011). Electrophysiological evidence for the left-lateralized effect of language on preattentive categorical perception of color. \emph{Proceedings of the National Academy of Sciences}, \emph{108}(34), 14026--14030. \url{https://doi.org/10.1073/pnas.1111860108}

\leavevmode\hypertarget{ref-oldfield1971}{}%
Oldfield, R. C. (1971). The assessment and analysis of handedness: The {Edinburgh} inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}

\leavevmode\hypertarget{ref-panichello2013}{}%
Panichello, M. F., Cheung, O. S., \& Bar, M. (2013). Predictive feedback and conscious visual experience. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00620}

\leavevmode\hypertarget{ref-phelps2016}{}%
Phelps, E. A., Ling, S., \& Carrasco, M. (2016). Emotion facilitates perception and potentiates the perceptual benefits of attention. \emph{Psychological Science}. \url{https://journals.sagepub.com/doi/10.1111/j.1467-9280.2006.01701.x}

\leavevmode\hypertarget{ref-pylyshyn1999}{}%
Pylyshyn, Z. (1999). Is vision continuous with cognition? The case for cognitive impenetrability of visual perception. \emph{Behavioral and Brain Sciences}, \emph{22}(3), 341--365. \url{https://doi.org/10.1017/S0140525X99002022}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-rabovsky2018}{}%
Rabovsky, M., Hansen, S. S., \& McClelland, J. L. (2018). Modelling the {N400} brain potential as change in a probabilistic representation of meaning. \emph{Nature Human Behaviour}, \emph{2}(9), 693--705. \url{https://doi.org/10.1038/s41562-018-0406-4}

\leavevmode\hypertarget{ref-rossion1999}{}%
Rossion, B., Delvenne, J.-F., Debatisse, D., Goffaux, V., Bruyer, R., Crommelinck, M., \& Guérit, J.-M. (1999). Spatio-temporal localization of the face inversion effect: An event-related potentials study. \emph{Biological Psychology}, \emph{50}(3), 173--189. \url{https://doi.org/10.1016/S0301-0511(99)00013-7}

\leavevmode\hypertarget{ref-rossion2002}{}%
Rossion, B., Gauthier, I., Goffaux, V., Tarr, M. J., \& Crommelinck, M. (2002). Expertise training with novel objects leads to left-lateralized facelike electrophysiological responses. \emph{Psychological Science}. \url{https://journals.sagepub.com/doi/10.1111/1467-9280.00446}

\leavevmode\hypertarget{ref-rossion2011}{}%
Rossion, Bruno, \& Jacques, C. (2011). The {N170}: Understanding the time course of face perception in the human brain. In E. S. Kappenman \& S. J. Luck (Eds.), \emph{The {Oxford} handbook of event-related potential components} (pp. 115--142). Oxford University Press. \url{https://doi.org/10.1093/oxfordhb/9780195374148.001.0001}

\leavevmode\hypertarget{ref-rossion2004}{}%
Rossion, Bruno, Kung, C.-C., \& Tarr, M. J. (2004). Visual expertise with nonface objects leads to competition with the early perceptual processing of faces in the human occipitotemporal cortex. \emph{Proceedings of the National Academy of Sciences}, \emph{101}(40), 14521--14526. \url{https://doi.org/10.1073/pnas.0405613101}

\leavevmode\hypertarget{ref-sagiv2001}{}%
Sagiv, N., \& Bentin, S. (2001). Structural encoding of human and schematic faces: Holistic and part-based processes. \emph{Journal of Cognitive Neuroscience}, \emph{13}(7), 937--951. \url{https://doi.org/10.1162/089892901753165854}

\leavevmode\hypertarget{ref-samaha2018}{}%
Samaha, J., Boutonnet, B., Postle, B. R., \& Lupyan, G. (2018). Effects of meaningfulness on perception: Alpha-band oscillations carry perceptual expectations and influence early visual responses. \emph{Scientific Reports}, \emph{8}(1), 1--14. \url{https://doi.org/10.1038/s41598-018-25093-5}

\leavevmode\hypertarget{ref-schad2020}{}%
Schad, D. J., Vasishth, S., Hohenstein, S., \& Kliegl, R. (2020). How to capitalize on a priori contrasts in linear (mixed) models: A tutorial. \emph{Journal of Memory and Language}, \emph{110}, 104038. \url{https://doi.org/10.1016/j.jml.2019.104038}

\leavevmode\hypertarget{ref-suess2015}{}%
Suess, F., Rabovsky, M., \& Abdel Rahman, R. (2015). Perceiving emotions in neutral faces: Expression processing is biased by affective person knowledge. \emph{Social Cognitive and Affective Neuroscience}, \emph{10}(4), 531--536. \url{https://doi.org/10.1093/scan/nsu088}

\leavevmode\hypertarget{ref-tanaka2001}{}%
Tanaka, J. W., \& Curran, T. (2001). A neural basis for expert object recognition. \emph{Psychological Science}, \emph{12}(1), 43--47. \url{https://doi.org/10.1111/1467-9280.00308}

\leavevmode\hypertarget{ref-taylor2002}{}%
Taylor, M. J. (2002). Non-spatial attentional effects on {P1}. \emph{Clinical Neurophysiology}, \emph{113}(12), 1903--1908. \url{https://doi.org/10.1016/S1388-2457(02)00309-7}

\leavevmode\hypertarget{ref-teufel2017}{}%
Teufel, C., \& Nanay, B. (2017). How to (and how not to) think about top-down influences on visual perception. \emph{Consciousness and Cognition}, \emph{47}, 17--25. \url{https://doi.org/10.1016/j.concog.2016.05.008}

\leavevmode\hypertarget{ref-vanrossum2009}{}%
van Rossum, G., \& Drake, F. L. (2009). \emph{Python 3 reference manual}. CreateSpace.

\leavevmode\hypertarget{ref-vetter2014}{}%
Vetter, P., \& Newen, A. (2014). Varieties of cognitive penetration in visual perception. \emph{Consciousness and Cognition}, \emph{27}, 62--75. \url{https://doi.org/10.1016/j.concog.2014.04.007}

\leavevmode\hypertarget{ref-R-buildmer}{}%
Voeten, C. C. (2020). \emph{{buildmer}: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}

\leavevmode\hypertarget{ref-vogel2000}{}%
Vogel, E. K., \& Luck, S. J. (2000). The visual {N1} component as an index of a discrimination process. \emph{Psychophysiology}, \emph{37}(2), 190--203.

\leavevmode\hypertarget{ref-weller2019}{}%
Weller, P. D., Rabovsky, M., \& Abdel Rahman, R. (2019). Semantic knowledge enhances conscious awareness of visual objects. \emph{Journal of Cognitive Neuroscience}, \emph{31}(8), 1216--1226. \url{https://doi.org/10.1162/jocn_a_01404}

\leavevmode\hypertarget{ref-yuille2006}{}%
Yuille, A., \& Kersten, D. (2006). Vision as bayesian inference: Analysis by synthesis? \emph{Trends in Cognitive Sciences}, \emph{10}(7), 301--308. \url{https://doi.org/10.1016/j.tics.2006.05.002}

\end{CSLReferences}

\end{document}

### 2021-01-05 analysis/manuscript.Rmd
add discussion section + rmd for master thesis

@@
 title             : |
-  | Event-Related Potentials of the Semantically
-  | Informed Perception of Unfamiliar Objects
+  | Event-Related Potentials of the Semantically Informed
+  | Perception of Unfamiliar Objects
 shorttitle        : "Semantic Knowledge and Unfamiliar Objects"
@@
   - name          : "Alexander Enge"
+    affiliation   : "1,2"
+  - name          : "Franziska Süß"
+    affiliation   : "3"
+  - name          : "Rasha Abdel Rahman"
     affiliation   : "1"
@@
     address       : "Rudower Chaussee 18, 12489 Berlin"
-    email         : "alexander.enge@hu-berlin.de"
+    email         : "rasha.abdel.rahman@hu-berlin.de"
 
@@
     institution   : "Humboldt-Universität zu Berlin"
+  - id            : "2"
+    institution   : "Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
+  - id            : "3"
+    institution   : "Fachhochschule des Mittelstands, Bamberg, Germany"
 
 authornote: |
-  Alexander Enge, Department of Psychology, Humboldt-Universität zu Berlin, Germany, https://orcid.org/0000-0003-0100-2297, student no. 581331.
-
-  The thesis was handed in December 18, 2020 and has been supervised by Prof.
-Dr.
-Rasha Abdel Rahman, Humboldt-Universität zu Berlin, Germany, and Prof.
-Dr.
-Franziska Süß, Fachhochschule des Mittelstands, Bamberg, Germany.
+  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
+
+  \addORCIDlink{Rasha Abdel Rahman}{0000-0002-8438-1570}
+
+  The preprocessed data and code for this study are openly available at https://osf.io/uksbc/.
+
+  We have no conflict of interest to disclose.
 
 abstract: |
-  Abstract goes here.
-
-keywords          : "keywords"
-wordcount         : "X"
+  Does our perception of an object change as soon as we discover what it is for?
+This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it pertains to the long-standing debate around the (im)penetrability of perception by "higher" cognitive capacities.
+In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with valid information about their function---leading to semantically informed perception---or together with invalid information---resulting in naive perception.
+We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of perceiving objects differed from one another.
+We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
+When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place.
+We replicated these novel findings in an independent sample (*n* = 24).
+Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
+
+keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
+wordcount         : ""
 
@@
 documentclass     : "apa7"
-classoption       : "man,11pt"
+classoption       : "man"
 output:
@@
 header-includes:
+  - \geometry{a4paper}
+  - \fancyheadoffset[R,L]{0pt}
+  - \raggedbottom
   - \usepackage{setspace}
   - \AtBeginEnvironment{tabular}{\doublespacing}
-  - \AtBeginEnvironment{lltable}{\doublespacing}
-  - \AtBeginEnvironment{tablenotes}{\doublespacing}
-  - \captionsetup[table]{font={stretch=1.5}}
+  # - \AtBeginEnvironment{lltable}{\doublespacing}
+  # - \AtBeginEnvironment{tablenotes}{\doublespacing}
+  # - \captionsetup[table]{font={stretch=1.5}}
   - \captionsetup[figure]{font={stretch=1,scriptsize}}
-  - \raggedbottom
+  - \usepackage[all]{nowidow}
+  - \usepackage[bottom]{footmisc}
+  - \interfootnotelinepenalty=10000
+  - \usepackage[export]{adjustbox}
 ---
@@
 
-# Specify Python environment
-renv::use_python(type = "virtualenv")
-
 # Bibliography file
@@
 How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects, preceded in half of the cases by valid information about their function, leading to semantically informed perception, and in the other half of the cases by misleading information, leading to naive perception.
-Capitalizing on the high temporal resolution of event-related brain potentials (ERPs), we investigated at which stages in the processing hierarchy semantically informed and naive perception of visual objects differed from one another.
-
-The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-standing debate.
-This debate revolves around the question whether or not our perception of the (visual) world should be thought of as an encapsulated module being completely determined by the visual input reaching our retina.
-According to the former view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [@firestone2016; @fodor1983; @fodor1984; @machery2015; @pylyshyn1999].
-Conversely, this view is challenged by theoretical and empirical work suggesting that perceptual processing dynamically interacts with other aspects of cognition from early on [@churchland1988; @churchland1994; @collins2014; @lupyan2012; @lupyan2015; @lupyan2020; @thierry2016; @vetter2014].
-These aspects may include transient states such as emotions [e.g.  @phelps2016; @bocanegra2009] or intentions [@balcetis2010; @cole2012] as well as learned capacities such as language [e.g.  @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g.  @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g.  @abdelrahman2008; @lin1997; @weller2019].
-Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained sceptical, pointing out important methodological shortcomings in large parts of this literature [@firestone2016].
-
-One productive way of investigating top-down effects of cognition on perception while addressing some of these concerns is through neurophysiological recording methods such as ERPs: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
-This is because when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
-
-The visual P1 component refers to a positive deflection peaking approximately 100--150 ms after stimulus onset at occipital channels.
+In this study, we presented participants with unfamiliar objects which were preceded either by valid information about their function, leading to semantically informed perception, or by misleading information, leading to naive perception.
+Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temopral resoulation of event-related brain potentials (ERPs).
+
+The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
+This debate revolves around the question of whether or not our perception of the (visual) world should be thought of as an encapsulated module whose processing is determined solely by the visual input reaching our retina.
+According to this view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @fodor1984; @machery2015; @pylyshyn1999].
+Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @goodale1992; @marr1982].
+
+Conversely, this position is challenged by the view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1988; @churchland1994; @lupyan2015; @teufel2017].
+The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas [e.g., visual areas V1 and V2; @bullier2001; @gilbert2013], as well as behavioral evidence, have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+The reverse hierarchy theory [@ahissar2004; @hochstein2002], for instance, assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
+Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
+Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
+Finally, an active role of top-down influences is also promoted by theories of vision falling under the umbrella of Bayesian inference and predictive coding [e.g., @lupyan2015; @panichello2013; @yuille2006].
+
+Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition [for review, see @collins2014; @vetter2014].
+These aspects of cognition may include transient states such as emotions [e.g., @phelps2016; @bocanegra2009] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @lin1997; @weller2019].
+Despite this wealth of theory and empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
+
+One productive way to investigate top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
+
+The visual P1 component of the ERP refers to a positive deflection peaking as early as 100--150 ms after stimulus onset at occipital channels.
 It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri [@dirusso2001; @foxe2002; @mangun1995].
-The P1 is mostly thought to reflect the processing of low-level visual characteristics of the stimulus [such as size, luminance, and contrast; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception.
-It should be noted, however, that the P1 is reliably modulated by spatial [@luck2000; @mangun1995; @mangun1991] and non-spatial [@taylor2002] attention.
+The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus [e.g., size, luminance, and contrast; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception.
+For instance, it is enhanced when participants pay attention to the spatial location [@luck2000; @mangun1995; @mangun1991] or certain non-spatial features [@taylor2002] of the stimulus.
 
 The visual N170 (or N1) component refers to the negative deflection following the P1 and is maximal around 150--200 ms after stimulus onset at occipito-temporal channels.
-While still influenced by visual parameters of the stimulus [@johannes1995], it is also sensitive to selective attention, at least when participants are required to discriminate between different visual stimuli [@vogel2000; @mangun1991].
-Importantly, the N170 is enlarged (i.e. more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g. birds, dogs, or cars; @gauthier2003a; @tanaka2001].
-This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as their configuration [@eimer2011; @jacques2010; @rossion1999; @sagiv2001].
-Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimuli.
-
-Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018], starting approximately 300 ms after stimulus onset and being most pronounced at centro-parietal channels.
-A modulation of this component by cognitive capapacities such as knowedge can be taken as evidence for a post-perceptual influence on stimulus processing.
-
-Previous studies have focused on these and other ERP components to investiage which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
-Together, they suggest that not only higher-level semantic ERPs like the N400 component are influenced by acquiring semantic information about objects, but also early components that typcially reflect bottom-up visual processing.
-This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (cooking recipes) for the other half of the objects [@abdelrahman2008, Experiment 1].
+Just as the P1, it is influenced by visual parameters of the stimulus [@johannes1995] and by selective attention, especially when participants are required to discriminate between different visual stimuli [@vogel2000; @mangun1991].
+Importantly, the N170 is enlarged (i.e., more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g., birds, dogs, or cars; @gauthier2003a; @tanaka2001].
+This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as the holistic configuration of these features [@eimer2011; @jacques2010; @rossion1999; @sagiv2001].
+Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimulus.
+
+Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018].
+It begins approximately 300 ms after stimulus onset and is most pronounced at centro-parietal channels.
+A modulation of the N400 component by cognitive capacities such as knowledge can be taken as evidence for a post-perceptual influence on stimulus processing.
+
+Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
+Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing.
+This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (i.e., cooking recipes) for the other half of the objects [@abdelrahman2008, Experiment 1].
 After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information.
@@
 Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
-Of note, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects.
-The modulation of the P1 component was also replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
-Of note, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink, which can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.
-
-A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects, which were rendered difficult to recognize by converting them to two-tone, "Mooney" images [@samaha2018, Experiment 4].
-Here, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the image beforehand, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
-When the EEG was measured in a separate delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images of objects than for perceptually-trained images of objects.
-This alternative approach further coroborates an early influence of semantic information on visual object perception.
-
-All the previously mentioned studies have in common that they investigated the effects of semantic knoweldge on object perception only *after* an extensive learning phase [@abdelrahman2008; @gauthier2003; @maier2014; @maier2019; @rossion2002; @rossion2004; @samaha2018; @weller2019].
-Participants performed one or multiple training session where they encountered each object together with its respective label or description multiple times.
+Interestingly, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects.
+The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
+Here, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
+This can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.
+
+A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects which were rendered difficult to recognize by converting them to two-tone, "Mooney" images [@samaha2018, Experiment 4].
+In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
+When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images of objects than for perceptually-trained images of objects.
+As before, these effects of perceiving objects in a semantically informed way seems to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
+This alternative approach further corroborates an early influence of semantic information on the visual perception of objects.
+
+All the previously mentioned studies have in common that they investigated the effects of semantic knowledge on the visual perception of objects only *after* an extensive learning phase had taken place [@abdelrahman2008; @gauthier2003; @maier2014; @maier2019; @rossion2002; @rossion2004; @samaha2018; @weller2019].
+Participants performed one or multiple training sessions during which they encountered each object together with its respective label or description multiple times.
 The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day [@abdelrahman2008; @maier2014; @maier2019] or were spread out across multiple days or weeks [@rossion2002; @rossion2004].
-While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three important conceptual questions unresolved.
-
-The first question is if we can detect any electrophysiological correlates of semantic insight, i.e. the critical presentation during which an understanding of the previously unfamiliar object is happening, instead of asking if this understanding leads to differential effects in an orthogonal task later on.
-The second question is how much learning is actually necessary before reliable top-down effects of knowledge (such as on object-related P1 amplitudes) can be obtained: Does it actually take dozens of repitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of semantics, altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects, having been altered throughout the learning process [@haber1966]?
+While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three conceptual questions unresolved.
+
+The first question is if we can detect any electrophysiological correlates of semantic insight, that is, the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on).
+The second question is how much learning is actually necessary before reliable top-down effects of knowledge on ERP amplitudes can be obtained: Does it actually take dozens of repetitions per object or may a single exposure to the object together with the relevant semantic information be enough?
+The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
 By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we hope to provide tentative answers to all three of these questions.
@@
 In the two experiments subsequently reported, participants were presented with real-word objects that were presumed to be unfamiliar to most of them.
-They first viewed each of these objects once without any semantic information.
-This part served as a naive baseline to outrule that ERPs would differ in response to the objects based solely on their low-level visual differences.
+They first viewed each of these objects without any semantic information.
+This first part served as a naive baseline to rule out that ERPs would differ in response to the objects based solely on low-level visual differences.
 Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
-These keywords could either correctly describe the object's typical function, thus making it possible for participants to understand what kind of object they are viewing, or mislead them by describing the function of a different object, thus keeping the perception of the object semantically naive.
-During this "insight" part, we were able measure the online influence of semantic knowledge on object-evoked ERPs as it happened.
-Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them, thus mimicking previous studies [e.g.
-@abdelrahman2008, @samaha2018; @weller2019].
-In all three parts, we compared the influences of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (400--700 ms).
+These keywords could either correctly describe the typcial function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could mislead participants by describing the function of a different object, thus keeping the perception of the object semantically naive.
+During this second part, we were able measure the online influence of semantic insight on object-evoked ERPs as it happened.
+Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them---thereby mimicking previous studies [e.g., @abdelrahman2008; @samaha2018; @weller2019].
+In all three parts, we examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (N400 component, 400--700 ms).
 
@@
   # Read log file
-  dat <- suppressMessages(suppressWarnings(read_tsv(txt_fname)))
+  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
   # Rename columns for participant and item IDs
@@
     ) %>% as_factor()) %>%
-    # Remove filler stimuli (i.e. well-known objects)
+    # Remove filler stimuli (i.e.,well-known objects)
     filter(bek_unbek != "bekannt")
@@
 
-```{r}
-# vec_participant <- data_exp1 %>% bind_rows() %>% pull(participant) %>% unique()
-# vec_participant <- c(vec_participant[seq(1, 23, 2)], vec_participant[seq(2, 24, 2)])
-# 
-# data_exp1 %>%
-#   bind_rows() %>%
-#   mutate(participant = factor(participant, levels = vec_participant),
-#          item_new = ifelse(participant %in% vec_participant[1:12], item - 15, item)) %>%
-#   filter(part == "II" & Tastencode != 0) %>%
-#   ggplot(aes(x = participant, y = item, fill = Tastencode)) +
-#   geom_raster() +
-#   scale_fill_viridis_c(begin = 0.1, end = 0.5)
-#   #scale_fill_manual(values = c("Informed" = "purple", "Naive" = "green", "Excl_informed" = "gray70", "Excl_naive" = "gray90", "Excl_known" = "white"))
-```
-
 ```{python exp1-preprocessing}
@@
 import os
+
+montage = mne.channels.make_standard_montage("easycap-M1")
+montage._get_ch_pos()
 
@@
 evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)
-
-# # Plot evoked potentials
-# import matplotlib.pyplot as plt
-# mne.viz.plot_compare_evokeds(evokeds=evokeds_exp1['II'], picks='P8'); plt.show()
-# evokeds_exp1['II']['Informed'].data = evokeds_exp1['II']['Informed'].data - evokeds_exp1['II']['Naive'].data
-# evokeds_exp1['II']['Informed'].plot_topomap(times=[0.125, 0.175, 0.5], average=0.05, vmin=-1, vmax=1, cmap='viridis'); plt.show()
-```
-
-```{r exp1-tryout, eval=FALSE}
-# # Create vector of sample time points
-# times <- seq(py$preproc_params$tmin, py$preproc_params$tmax, 1 / py$epochs_exp1$info["sfreq"]) * 1000
+```
+
+```{python exp1-tfr, eval=FALSE}
+# TFR
+import numpy as np
+import matplotlib.pyplot as plt
+
+# chans = mne.pick_channels(epochs_exp1.ch_names, include=["PO3", "PO4", "POz", "O1", "O2", "Oz", "P7", "P8", "PO7", "PO8", "PO9", "PO10"])
 # 
-# # Average channels in the N170 ROI
-# py_run_string('epochs_roi = mne.channels.combine_channels(epochs_exp1, groups=dict(roi=mne.pick_channels(epochs_exp1.ch_names, ["P7", "P8", "PO7", "PO8", "PO9", "PO10"])))')
-# 
-# # Extract data for Part II from Python
-# dat <- py$epochs_exp1$metadata %>%
-#   as_tibble() %>%
-#   bind_cols(py$epochs_roi$get_data(picks = "roi") %>% drop() %>% as_tibble()) %>%
-#   pivot_longer(-c(part, condition, participant, item, RT), values_to = "amplitude") %>%
-#   filter(condition %in% c("Informed", "Naive")) %>%
-#   mutate(
-#     part(factor(part)),
-#     condition = factor(condition),
-#     participant = factor(participant),
-#     item = factor(item),
-#     time = rep(times, nrow(.) / length(times))
-#   )
-# 
-# # Compute LMM
-# library(lme4)
-# contrasts(dat$condition) <- contr.sum(2)
-# contrasts(dat$part) <- MASS::contr.sdif(3)
-# mod <- lmer(
-#   amplitude ~ part/condition + (part/condition|time:participant) + (part/condition|time:item),
-#   data = dat, control = lmerControl(calc.derivs = FALSE)
-# )
-# summary(mod)
-# 
-# # Predict values from LMM
-# probe <- expand.grid(
-#   part = unique(dat$part),
-#   condition = unique(dat$condition),
-#   participant = unique(dat$participant),
-#   item = unique(dat$item),
-#   time = dat$time %>% unique()
-# ) %>% mutate(amplitude = predict(mod, .))
-# 
-# # Plot real and modelled data
-# ggplot(mapping = aes(x = time, y = amplitude, color = condition)) +
-#   geom_line(data = dat, aes(group = interaction(condition, participant, item)), size = 0.1, alpha = 0.1) +
-#   stat_summary(data = probe, geom = "line", fun = mean, na.rm = TRUE, size = 1) +
-#   theme_minimal() +
-#   labs(x = "Time (ms)", y = "Predicted amplitude (µV)") +
-#   coord_cartesian(xlim = c(-200, 800), ylim = c(-15, 15), expand = FALSE)
-# 
-# # Old models
-# mod1_P1 <- lmerTest::lmer(P1 ~ part/condition + (part/condition|participant) + (part/condition|item),
-#                           data = data_exp1, control = ctrl_params)
-# mod1_N170 <- lmerTest::lmer(N170 ~ part/condition + (part/condition|participant) + (part/condition|item),
-#                           data = data_exp1, control = ctrl_params)
-# mod1_N400 <- lmerTest::lmer(N400 ~ part/condition + (part/condition|participant) + (part/condition|item),
-#                             data = data_exp1, control = ctrl_params)
-# mod2_P1 <- lmerTest::lmer(P1 ~ part/condition + (part/condition|participant) + (part/condition|item),
-#                           data = data_exp2, control = ctrl_params)
-# mod2_N170 <- lmerTest::lmer(N170 ~ part/condition + (part/condition|participant) + (part/condition|item),
-#                           data = data_exp2, control = ctrl_params)
-# mod2_N400 <- lmerTest::lmer(N400 ~ part/condition + (part/condition|participant) + (part/condition|item),
-#                             data = data_exp2, control = ctrl_params)
-# summary(mod1_P1)
-# summary(mod1_N170)
-# summary(mod1_N400)
-# summary(mod2_P1)
-# summary(mod2_N170)
-# summary(mod2_N400)
+# epochs = mne.channels.combine_channels(epochs_exp1, dict(roi=chans))
+# epochs.metadata = epochs_exp1.metadata
+
+# epochs.plot_psd(fmin=2., fmax=40., average=True, spatial_colors=False); plt.show()
+# epochs.plot_psd_topomap(normalize=True); plt.show()
+
+freqs = np.logspace(*np.log10([4, 30]), num=8)
+n_cycles = freqs / 2.  # different number of cycle per frequency
+
+epochs_informed = epochs_exp1["part == 'II' & condition == 'Informed'"]
+epochs_naive = epochs_exp1["part == 'II' & condition == 'Naive'"]
+
+power_informed = mne.time_frequency.tfr_morlet(epochs_informed, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
+power_naive = mne.time_frequency.tfr_morlet(epochs_naive, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
+
+freqs = np.arange(start=4, stop=30, step=1)
+n_cycles = freqs / 2.  # different number of cycle per frequency
+
+evokeds_informed = evokeds_exp1["I"]["Informed"]
+evokeds_naive = evokeds_exp1["I"]["Naive"]
+
+power_informed = mne.time_frequency.tfr_morlet(evokeds_informed, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
+power_naive = mne.time_frequency.tfr_morlet(evokeds_naive, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
+
+power_diff = power_informed - power_naive
+power_diff.plot(baseline=(-0.3, 0), mode = "percent", tmin=-0.3, tmax = 0.7, vmin=-200, vmax=200); plt.show()
+
+power_diff.plot_joint(baseline=(-0.5, 0), mode = "percent", vmin=-100, vmax=100, timefreqs=(0.175, 12)); plt.show()
+
+#power_diff.plot_topomap(fmin=8, fmax=14, baseline=(-0.5, 0), mode="mean", vmin=-200, vmax=200, title="alpha"); plt.show()
+#power_diff.plot_topomap(fmin=15, fmax=30, baseline=(-0.5, 0), mode="mean", vmin=-200, vmax=200, title="beta"); plt.show()
 ```
@@
   erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
-  erps <- apply(erps, 1, mean, na.rm = TRUE)
-  return(erps)
-}
+  amps <- apply(erps, 1, mean, na.rm = TRUE)
+  return(amps)
+}
+
+# # Define function to compute single-trial ERP latencies
+# compute_lats <- function(epochs, els, name, start, stop, roi) {
+#   erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
+#   samples <- apply(erps, MARGIN = c(1, 3), mean) %>% abs()
+#   areas <- apply(samples, MARGIN = 1, sum)
+#   cumss <- apply(samples, MARGIN = 1, cumsum) %>% asplit(MARGIN = 2)
+#   lats <- map2_int(cumss, areas, function(cums, area){which(cums < area / 2) %>% max()})
+#   lats <- start + lats * 2
+#   return(lats)
+# }
 
@@
       data = data,
-      direction = c("backward", "backward"),
+      direction = c("order", "backward"),
       elim = function(logp) exp(logp) >= .20,
@@
 
-## Methods
+## Method
 
@@
 Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
-No a priori power analysis was carreid out and the sample size was chosen according to the default for EEG studies in our lab at the time of data collection.
+No a priori power analysis was carried out and the sample size was chosen in line with other EEG studies in our lab at the time of data collection.
 All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
 They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-All experiments subsequently reported were carried out in accordance with the Declaration of Helsinki and approved by the local ethics committee.
-
-### Materials and Procedure
-
-Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g. a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g. a galvanometer, an udu drum).
-A list of these unfamiliar objects can be found in Appendix A.
+
+### Materials
+
+Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum).
+A list of these unfamiliar objects can be found in the appendix.
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of keywords---a noun and a verb---was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g. current--measuring, pottery--drumming).
+For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g., current--measuring, pottery--drumming).
 As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e. participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an effect and keep the perception of the object semantically naive.
-All participants saw each unfamiliar object in only one of the two conditions and the assignment of objects to conditions was counterbalanced across participants.
+The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive.
+All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
+This assignment of keywords and objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
 
-Each experimental session consisted of three parts (Figure \@ref(fig:exp1-plot)A).
-In the *pre-insight* part (Part I), after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
+### Procedure
+
+Each experimental session consisted of three parts (see Figure \@ref(fig:exp1-plot)A).
+In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
 Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
 The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I do not know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
@@
 (ref:figure-1-caption) Procedure and results of Experiment 1.
-*(A)* In the pre-insight part (Part I), participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In the insight part (Part II), half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
-In the post-insight part (Part III), the same objects were presented again without the keywords.
-*(B)* ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within Parts I, II, and III.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
+*(A)* In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
+In the post-insight part, the same objects were presented again without the keywords.
+*(B)* ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
+Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
 Ampl.
@@
 ```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
-# Retrieve locations for the relevant electrodes from standard montage
-fname_montage <- list.files(path = "renv/python", pattern = "easycap-M1.txt", recursive = TRUE, full.names = TRUE)[1]
+# Locate standard montage file from MNE Python
+fname_montage <- list.files(
+  path = reticulate::py_discover_config()$python %>% str_remove("bin/.*"),
+  pattern = "easycap-M1.txt", full.names = TRUE, recursive = TRUE
+)[1]
+
+# Retrieve locations for the relevant electrodes from this montage
 montage <- py$evokeds_exp1$I$Informed$ch_names %>%
@@
   rename(electrode = value) %>%
-  left_join(read_tsv(fname_montage) %>% rename(electrode = Site), by = "electrode") %>%
+  left_join(
+    read_tsv(fname_montage, col_types = cols()) %>%
+      rename(electrode = Site),
+    by = "electrode"
+  ) %>%
   mutate(
@@
     # Title
-    annotate("text", x = 0, y = 97.2, label = "Part II (insight)", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
+    annotate("text", x = 0, y = 97.2, label = "Insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
     # Arrow
@@
     # Title
-    annotate("text", x = -72, y = 56, label = "Part I (pre-insight)", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
+    annotate("text", x = -72, y = 56, label = "Pre-insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
     # Arrow
@@
     # Title
-    annotate("text", x = 72, y = 56, label = "Part III (post-insight)", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
+    annotate("text", x = 72, y = 56, label = "Post-insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
     # Arrow
@@
 
-In the *insight* part (Part II), only the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+In the *insight* part, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
 Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
 Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
-The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g. medical devices, musical instruments).
-
-In the post-insight part (Part III), the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e. without any keywords.
-Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with keywords), participants took a self-timed break and continued with the same block of 30 objects in Part III (without keywords) before moving on to the next block consisting of 30 different objects.
-They continued like this until all four blocks were completed in both Parts II and III.
-In total, the experiment consisted of 480 trials (120 familiar objects in Part I and 120 unfamiliar objects in Parts I, II, and III) and took participants approximately 35 minutes to complete.
+The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).
+
+Finally, in the *post-insight* part, the unfamiliar objects were presented for a third time with an identical trial structure as in the pre-insight part, that is, without any keywords.
+Note that the insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight part (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight part (without keywords) before moving on to the next block consisting of 30 different objects.
+They continued like this until all four blocks were completed in both parts.
+In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight part and 120 unfamiliar objects in the pre-insight, insight, and post-insight parts).
+It took participants approximately 35 minutes to complete.
 
@@
 The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Those components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the *find\_bads\_eog* function.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the *find\_bads\_eog* function.
 After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
@@
 Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
-This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials (`r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`) per participant (range `r min(rejected_exp1)` to `r max(rejected_exp1)`).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see scalp topographies in Figure \@ref(fig:exp1-plot)B).
 
@@
 
-First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in Part I (i.e. before any keywords were presented), which led to the exclusion of an average of `r format(round(stims_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (`r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)`).
-Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in Part II) and the behavioral responses of the participants themselves (Figure 1A).
+First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in the pre-insight part (i.e., before any keywords were presented).
+This led to the exclusion of an average of `r format(round(stims_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
+Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
 Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
-This was the case for an average of `r format(round(stims_exp1["Informed"], 1), nsmall = 1)` objects per participant (`r scales::percent(stims_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
+This was the case for an average of `r format(round(stims_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
 Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects per participant (`r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Although the assignment was purely based on the manipulation and responses in Part II, when insight was thought to occurr, the same assignment was used to analyze the data from the other two parts.
-This allowed us to test on the one hand if the objects from both conditions differed in important aspects even before any keywords were presented (in Part I), and on the other hand if the semantic understanding acquired in Part II had any lasting effects on a subsequent, third presentation of the objects (in Part III).
+This was the case for an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occurr---the same assignment was used to analyze the data from the other two parts.
+This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).
 
 The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
-For the purpose of the present study, these models have at least two desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages.
-First, they can account simultaneously for the non-independence of data points coming from the same participant or from the same item, whereas the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
-Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is (co-)determined by the responses of the participants rather than by the experimental manipulation alone [e.g.  @fröber2017].
+For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+First, they can account not only for the non-independence of data points coming from the same participant but also simultaneously for the non-independence of data points coming from the same item.
+In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
+Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
+Such a situation is inevitable in designs where the assignment of trials to conditions is (co-)determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone [e.g., @fröber2017].
 
 Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
-All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e. subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e. subtracting the naive from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
+All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e., subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
 For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to [@schad2020].
 To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
-We then performed a model selection algorithm as proposed by [@matuschek2017] in order to increase statistical power and avoid overparameterization: Iteratively, each random effects was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+We then performed a model selection algorithm as proposed by [@matuschek2017] in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
 Only if the parsimonious model explained the data equally well as the complex model [determined by *p* \> .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model.
-All models were calculated in R [Version `r packageVersion("base")`; @R-base] using the lme4 package [Version `r packageVersion("lme4")`; @R-lme4].
-The optimizer function *bobyqa* with 2·10^5^ iterations was used for maximum likelihood estimation.
-The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r packageVersion("buildmer")`; @R-buildmer].
-Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within Parts I, II, and III.
-All *p* values subsequently reported were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's methods as implemented in the lmerTest package [@R-lmerTest].
-
-The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework ([https://osf.io/.../](https://osf.io/myprojects/)).
-To avoid potential misuse, the raw EEG are only made available by the corresponding author upon request.
+All models were computed in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4].
+The optimizer function *bobyqa* with 20,000 iterations was used for maximum likelihood estimation.
+The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`; @R-buildmer].
+Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts.
+All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`; @R-lmerTest].
+
+The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (<https://osf.io/uksbc/>).
+Unfortuntaly, lack of informed consent prevents us from sharing the raw EEG data.
 
@@
 
-Single-trial ERPs were analyzed in response to unfamiliar objects before (Part I), while (Part II), and after (Part III) participants obtained relevant semantic information about their function.
-Only in Part II, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
-The objects were analyzed according to this manipulation in combination with participants' self-report in Part II (Figure 1A), thus making sure that semantically informed (or naive) perception did indeed occur.
+Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
+Only in the insight part, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
+The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \@ref(fig:exp1-plot)A), thereby making sure that semantically informed and naive perception did indeed occur.
 The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N170 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.
@@
   stub_anova = c("Part", "Condition", "Pt. × con."),
-  stub_contrasts = c("Part I (pre-insight)", "Part II (insight)", "Part II (post-insight)"),
+  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
   caption = "Results of linear mixed-effects regression models for Experiment 1",
@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s \> `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (Table \@ref(tab:exp1-table)).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r table_exp1$anov["Informed", "N400_df"]` = `r table_exp1$anov["Informed", "N400_f"]`, *p* = `r table_exp1$anov["Informed", "N400_p"]`.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s \> `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (see Table \@ref(tab:exp1-table)).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r table_exp1$anov["Condition", "N400_df"]` = `r table_exp1$anov["Condition", "N400_f"]`, *p* = `r table_exp1$anov["Condition", "N400_p"]`.
 Crucially, the part × condition interaction was significant in the N170 component, *F*`r table_exp1$anov["Pt.
@@
 
-### ERPs in Part I (Pre-Insight)
-
-In Part I, when objects were unfamiliar to the participant and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s \> `r table_exp1$conts["Part I (pre-insight)", "N400_p"]` (Table \@ref(tab:exp1-table), Figure \@ref(fig:exp1-plot)B & C).
+### ERPs Before Insight Was Occurring
+
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s \> `r table_exp1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:exp1-table) and Figure \@ref(fig:exp1-plot)B).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
-On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in Parts II and III cannot be accounted for by visual differences between the objects in the two conditions.
-Although the presentation of a matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor.
+On the other hand, the absence of reliable differences in this part can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in the other two parts cannot be accounted for by visual differences between the objects in the two conditions.
+Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report would have made it possible for such visual differences to emerge as a confounding factor.
 If they did, however, one would expect to detect these differences even before any keywords were presented, which we have now seen was not the case.
 
-### ERPs in Part II (Insight)
-
-In Part II, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object (akin to an insight experience), the amplitude of the N170 component was significantly enlarged (i.e. more negative), *b* = `r table_exp1$conts["Part II (insight)", "N170_est"]` µV, *p* = `r table_exp1$conts["Part II (insight)", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e. less negative), *b* = `r table_exp1$conts["Part II (insight)", "N400_est"]` µV, *p* `r table_exp1$conts["Part II (insight)", "N400_p"]`, compared to when an object was viewed naively without relevant semantic information.
-As in Part I, there were no reliable differences in the P1 component, *p* = `r table_exp1$conts["Part II (insight)", "P1_p"]`.
-
-### ERPs in Part III (Post-Insight)
-
-In Part III, the unfamiliar objects were presented for a third time, again without the keywords (as in Part I), to test whether the semantic information had any lasting effects on the processing of the objects.
-As in Part II, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Part II (post-insight)", "N400_est"]` µV, *p* `r table_exp1$conts["Part II (post-insight)", "N400_p"]`, whereas the early effect in the N170 component did not reoccur, *p* = `r table_exp1$conts["Part II (post-insight)", "N170_p"]`.
-Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e. more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Part II (post-insight)", "P1_est"]` µV, *p* = `r table_exp1$conts["Part II (post-insight)", "P1_p"]`.
+### ERPs While Insight Was Occurring
+
+In the insight part, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
+When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e., more negative), *b* = `r table_exp1$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Insight part", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e., less negative), *b* = `r table_exp1$conts["Insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Insight part", "N400_p"]`, compared to when the object was viewed naively without relevant semantic information.
+As in the pre-insight part, there were no reliable differences in the P1 component, *p* = `r table_exp1$conts["Insight part", "P1_p"]`.
+
+### ERPs After Insight Had Occurred
+
+In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part), to test whether the semantic information had any lasting effects on the processing of the objects.
+As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Post-insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *p* = `r table_exp1$conts["Post-insight part", "N170_p"]`.
+Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "P1_p"]`.
 
@@
 
-In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they were able to understand what kind of object they saw.
-To induce this semantically informed perception, half of the objects in Part II were preceded by matching verbal keywords about their typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
-
-Participants' semantically informed perception of the objects in Part II was associated with a significantly enlarged N170 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001].
-The fact that this effect did not reoccur in Part III, when the objects were presented once more without keywords, suggests it being a marker of insight through semantic information that is altering object processing online.
-In contrast, we also observed a modulation of the N400 component, which was reduced for objects while insight was taking place (in Part II) and remained so when the same objects were presented repeatedly (in Part III).
-The N400 is most often discussed as an index of increased demands for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018].
-Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had understood what kind of object they were viewing.
-Finally, semantically informed perception was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which insight had occurred (in Part II).
-This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images [e.g.  @samaha2018], may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had occurred.
-
-Because of the exploratory nature of the present study and the novelty of the ERP effects observed in Experiment 1, we ran a replication study to assess the robustness of these findings in another samples of participants.
+In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-inisight part) they were able to understand what kind of object they saw.
+To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
+
+In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms).
+When the same objects were presented once more in the post-insigt part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for whic semantically informed perception had taken place.
+
+Because of the novelty of our experimental paradigm and the findings of Experiment 1, we ran a replication study to assess the robustness of these effects in another samples of participants.
 
@@
 
-Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29) who had not participated in Experiment 1.
-They had no history of psychological disorder or treatment, were right-handed and reported normal or corrected-to-normal vision.
+Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29 years) who had not participated in Experiment 1.
+They had no history of psychological disorder or treatment, were right-handed, and reported normal or corrected-to-normal vision.
 They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
@@
 All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
-An average of `r format(round(stims_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (`r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)`) was classified as being known in Part I and excluded from all further analyses.
-Based on participants' responses in Part II, an average of `r format(round(stims_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (`r scales::percent(stims_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (`r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with a non-matching description).
-Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (`r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`, range `r min(rejected_exp2)` to `r max(rejected_exp2)`).
+An average of `r format(round(stims_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
+Based on participants' responses in the insight part, an average of `r format(round(stims_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (= `r scales::percent(stims_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (= `r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with a non-matching description).
+Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
 
@@
   stub_anova = c("Part", "Condition", "Pt. × con."),
-  stub_contrasts = c("Part I (pre-insight)", "Part II (insight)", "Part II (post-insight)"),
+  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
   caption = "Results of linear mixed-effects regression models for Experiment 2",
@@
 
-As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all *F*s \> `r table_exp2$anov["Part", "N170_f"]`, all *p*s `r table_exp2$anov["Part", "N170_p"]` (Table \@ref(tab:exp2-table)).
-Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, *F*`r table_exp2$anov["Informed", "N400_df"]` = `r table_exp2$anov["Informed", "N400_f"]`, *p* `r table_exp2$anov["Informed", "N400_p"]`.
+As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all *F*s \> `r table_exp2$anov["Part", "N170_f"]`, all *p*s `r table_exp2$anov["Part", "N170_p"]` (see Table \@ref(tab:exp2-table)).
+Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, *F*`r table_exp2$anov["Condition", "N400_df"]` = `r table_exp2$anov["Condition", "N400_f"]`, *p* `r table_exp2$anov["Condition", "N400_p"]`.
 The part × condition interaction was significant in the P1 component, *F*`r table_exp2$anov["Pt.
@@
 (ref:figure-2-caption) Results of Experiment 2.
-ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within Parts I, II, and III.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in Parts II and III and on the P1 component in Part III remained statistically significant, while the effect on the N170 component in Part II remained only marginally significant (*p* = `r table_exp2$conts["Part II (insight)", "N170_p"]`).
+ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-inisght part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
 Ampl.
@@
   plot_grid(
-    ggplot() + annotate("text", label = "Part I (pre-insight)", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(), NULL,
-    ggplot() + annotate("text", label = "Part II (insight)", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(), NULL,
-    ggplot() + annotate("text", label = "Part III (post-insight)", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(),
+    ggplot() + annotate("text", label = "Pre-insight part", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(), NULL,
+    ggplot() + annotate("text", label = "Insight part", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(), NULL,
+    ggplot() + annotate("text", label = "Post-insight part", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(),
     nrow = 1, rel_widths = spacing
@@
 
-### ERPs in Part I (Pre-Insight)
-
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all *p*s \> `r table_exp2$conts["Part I (pre-insight)", "P1_p"]` (Table \@ref(tab:exp2-table), Figure \@ref(fig:exp2-plot)).
-
-### ERPs in Part II (Insight)
-
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching versus non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, *b* = `r table_exp2$conts["Part II (insight)", "N170_est"]` µV, *p* = `r table_exp2$conts["Part II (insight)", "N170_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Part II (insight)", "N400_est"]` µV, *p* `r table_exp1$conts["Part II (insight)", "N400_p"]`.
-
-### ERPs in Part III (Post-Insight)
-
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Part II (post-insight)", "P1_est"]` µV, *p* = `r table_exp2$conts["Part II (post-insight)", "P1_p"]`.
-Also, N400 amplitudes in response to these objects remained significantly reduced, *b* = `r table_exp2$conts["Part II (post-insight)", "N400_est"]` µV, *p* = `r table_exp2$conts["Part II (post-insight)", "N400_p"]`.
+### ERPs Before Insight Was Occurring
+
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all *p*s \> `r table_exp2$conts["Pre-insight part", "P1_p"]` (see Table \@ref(tab:exp2-table) and Figure \@ref(fig:exp2-plot)).
+
+### ERPs While Insight Was Occurring
+
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Insight part", "N400_p"]`.
+
+### ERPs After Insight Had Occurred
+
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "P1_p"]`.
+Also, N400 amplitudes in response to these objects remained significantly reduced, *b* = `r table_exp2$conts["Post-insight part", "N400_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "N400_p"]`.
 
@@
 This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
-Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e. subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; @schad2020].
+Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; @schad2020].
 This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
@@
   stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
-  stub_contrasts = c("Part I (pre-insight)", "Part II (insight)", "Part II (post-insight)"),
+  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
   caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
@@
 
-As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Informed", "N400_df"]` = `r table_joint$anov["Informed", "N400_f"]`, *p* `r table_joint$anov["Informed", "N400_p"]`.
+As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Condition", "N400_df"]` = `r table_joint$anov["Condition", "N400_f"]`, *p* `r table_joint$anov["Condition", "N400_p"]`.
 Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s \> `r table_joint$anov["Pt.
@@
 
+Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Figure \@ref(fig:joint-plot)).
+This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all *p*s \> `r table_joint$conts["Pre-insight part", "N400_p"]`, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N170_est"]` µV, *p* = `r table_joint$conts["Insight part", "N170_p"]`, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N400_est"]` µV, *p* `r table_joint$conts["Insight part", "N400_p"]`, and in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "N400_est"]` µV, *p* `r table_joint$conts["Post-insight part", "N400_p"]`, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_joint$conts["Post-insight part", "P1_p"]`.
+
 (ref:figure-3-caption) Measured and modelled ERP amplitudes for Experiments 1 and 2 combined.
-The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for Parts I (before insight was occurring), II (while insight was occurring), and III (after insight had occurred).
-The yellow dots show the corresponding condition means as predicted by linear mixed-effects modelling (see main text and Table \@ref(tab:joint-table)), together with their respective 95% confidence interval.
+The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
+The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \@ref(tab:joint-table)), together with their respective 95% confidence interval.
 Ampl.
@@
 
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically inforemd and the naive condition within each part, now collapsed across the data from both experiments (Figure \@ref(fig:joint-plot)).
-This confirmed the absence of any reliable differences between the two conditions in Part I, all *p*s \> `r table_joint$conts["Part I (pre-insight)", "N400_p"]`, the significant enhancement of the N170 component in Part II, while the semantic information was obtained, *b* = `r table_joint$conts["Part II (insight)", "N170_est"]` µV, *p* = `r table_joint$conts["Part II (insight)", "N170_p"]`, the significant reduction of the N400 component in Part II, while the semantic information was obtained, *b* = `r table_joint$conts["Part II (insight)", "N400_est"]` µV, *p* `r table_joint$conts["Part II (insight)", "N400_p"]`, and Part III, after the information had been obtained, *b* = `r table_joint$conts["Part II (post-insight)", "N400_est"]` µV, *p* = `r table_joint$conts["Part II (post-insight)", "N400_p"]`, as well as the significant enhancement of the P1 component in Part III, after the information had been obtained, *b* = `r table_joint$conts["Part II (post-insight)", "P1_est"]` µV, *p* = `r table_joint$conts["Part II (post-insight)", "P1_p"]`.
-
 ### Control Analysis
@@
   stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
-  stub_contrasts = c("Part I (pre-insight)", "Part II (insight)", "Part II (post-insight)"),
+  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
   caption = "Results of linear mixed-effects regression models with a different baseline",
@@
 
-One may raise concerns whether the modulation of the N170 component in Part II genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition.
-Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the object's visual features and their configuration.
-Thus, the modulation of the ERP components in Part II may reflect a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of morsing messages.
-To preclude this alternative explanation, we repeated the analysis above using a different baseline against which the objects in the semantically informed condition were contrasted.
+One may raise concerns whether the modulation of the N170 component in the insight part genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it may be driven by the objects in the other, semantically naive condition.
+Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
+Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of morsing messages.
+To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
 Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in Part II, *b* = `r table_joint_control$conts["Part II (insight)", "N170_est"]` µV, *p* `r table_joint_control$conts["Part II (insight)", "N170_p"]`.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords on which participants failed to capitalize.
-Note that the reduction of the N400 component in Part II also remained robust in this control analysis, *b* = `r table_joint_control$conts["Part II (insight)", "N400_est"]` µV, *p* `r table_joint_control$conts["Part II (insight)", "N400_p"]`.
-
-[^1]: Note that the remaining objects to make it up to 100% were excluded as not being unfamiliar in Part I of the experiment (see Methods).
+Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize.
+Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, *b* = `r table_joint_control$conts["Insight part", "N400_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N400_p"]`.
+
+[^1]: Note that these percentages do not add up to 100% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).
 
@@
 Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400).
-While the enhancement of the N170 component, being more negative for semantically informed as compared to naive perception, was present only during the critical presentation of the objects with their respective keywords (in Part II), the enhancement of the P1, being more positive in response to these same objects, emerged only after the information had been obtained and the objects were presented again (in Part III).
-This indicates a modulation of different stages of visual object perception through semantic knowledge, while and after an understanding of the object has been obtained.
-Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantically informed perception may reflect lowered semantic processing demands compared to unfamiliar objects which participants did not yet understand.
+Objects for which participants experienced semantically informed perception via matcing keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes.
+When these objects were presented once more, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.
 
@@
 
-General discussion section goes here.
-
-Although most of the previous studies in the object processing domain have focused on the P1 component as an index of semantic knowledge modulating perceptual processes, at least two studies provide evidence for top-down effects of meaningfulness on the visual N170 (or N1) component in response to schematic drawings of faces [@bentin2002] and objects [@beaucousin2011].
-Using a similar design as in the present study, drawings of distored faces elicited a facelike (i.e. enlarged) N170 component only after participants were primed with a vaild hint---in this case the same face with all of its visual features in place [@bentin2002].
-Similarly, N170 amplitudes in a global-local detection task where shown to be enhanced in response to line drawings of meaningful objects (a boat or a butterfly) as compared to visually matched by meaningless drawings of non-objects.
-Interestingly, this effect was reversed in polarity when participants had to focus on the smaller, constituent parts and ignoring the object which emerged out of their global arrangement, which may be interpreted as further evidence for a functional role of the N170 component in the holistic perception of an object and its early visual categorization, integrating across its visual features.
-
+Here we investigated if obtaining a semantic understanding of what a previously unfamiliar object is or does has an influence on how we perceive it.
+To this end, we measured ERPs while participants watched unfamiliar objects before, while, and after receiving semantic information about them.
+For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was misleading, thus keeping the perception of the object semantically naive.
+We found semantically informed percpetion to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
+If the same objects were presented again without the semantic information, only the N400 component remaind significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+
+The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
+Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing [@kutas2011].
+It replicates previous findings that pictures elicit an N400 effect (as in our semantically naive condition) when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+The time course of this effect and the computational role of the N400 [@lau2008; @rabovsky2018] suggest that it has a post-perceptual locus.
+
+In contrast to the N400, the N170 component (150--200 ms after object onset) was modulated while but not after the objects were presented together with the relevant semantic information.
+As such, it can be seen as an online marker of semantic insight, that is, participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
+The N170 is typically associated with the holistic perception of faces [@eimer2011; @sagiv2001] and other stimuli of visual expertise [@rossion2002; @tanaka2001].
+It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
+This interpretation is supported by previous work in face perception, using a similar experimental paradigm as the present study: Participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face [@bentin2002].
+This effect was absent when a visual control stimulus (a non-face object instead of the intact face) was shown between the two presentations of the scrambled face.
+With regards to non-face stimuli, enlarged N170 amplitudes were also observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
+Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constitutent parts of the object.
+Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level (i.e., holistic) perception of visual objects, integrating across their visual features.
+
+Unlike the N400 and N170 components, the P1 component (100--150 ms after object onset) was modulated by semantic information only one trial after it had been obtained.
+This is consistent with previous studies showing P1 effects when participants learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
+What the present study adds to these findings is that it does not take an extensive learning phase (with multiple presentations of the objects together with the respective information) for the P1 effect to develop but that it can be observed immediately after (but not during) a semantic understanding of the object has happend.
+Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its succeptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
+
+Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of the visual objects as we perceive them.
+However, the finding that these two components were modulated in different parts of our experiment suggests that they reflect different aspects top-down processing with different time courses and neuroanatomical implementations.
+It has been suggested that the onset of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas a modulation of the P1 component seems reflect recurrent processing *within* the visual system [@wyatte2014].
+Here we show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
+
+While the limited spatial resolution of the EEG does not allow for localizing these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI that semantic information can feed back into the earliest of visual areas.
+[@hsieh2010] showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
+They found that the brain responses to the original image was correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
+This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (V1/V2/V3).
+Both of these cortical sites are consistent with the neural generators of the P1 and N170 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
+
+The top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999, but see @clarke2020].
+Proponents of this view have pointed out important conceptual and methodological shortcomings of previous studies claiming to show top-down effects of cognition on perception [@firestone2016; @machery2015].
+We took care to address as many of these shortcomings as possible: First, we showed that no effect was present had been present before any semantic information was presented (in the pre-insight part).
+Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual versus post-perceptual locus.
+Third, we reduced demand and response bias by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
+Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
+Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order and at the same location.
+Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
+We hope that these methods have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the "cognitive impenetrability" of perception.
+
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in machine vision [@dicarlo2012; @marr1982].
+In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of low-level visual features may be a key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+Single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach for these network models until they overcome this "barrier of meaning" [@mitchell2020].
+Drawing inspiration from cognitive psychology and human neuroscientific data may help making them more biologically plausible and, at the same time, more resource and data efficient.
+
+At present, a theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking.
+The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004; @hochstein2002] which posits that objects first enter our visual consciousness at an abstract, conceptual level.
+Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract relevant lower-level features ("vision with scrutiny").
+This reverse trajectory down the visual hierarchy may explain the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
+Besides the reverse hierarchy theory, an important role of top-down mechanism sfor vision or, more specifically, object recognition is also posited by the family of predictive coding and Baysian inference theories [e.g., @lupyan2015; @panichello2013; @yuille2006].
+Despite the theoretical advances, the mechanistic details of these top-down effects at the algorithmic and implementational level [@marr1982] remain to be clarified.
+
+The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
+Another one is our reliance on rare and highly specialized objects (see appendix), which was necessary to induce experiences of semantic insight in an adult population of undergraduate students, but may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of adressing this issue would be to adapt this paradigm to younger participants, using everyday objects which they have not yet learned about.
+Finally, the number participants (*n* = 24 per experiment) and trials (*k* = 30 per part in the insight condition and *k* = 50 per part in the naive condition) can be considered small by todays standards [@baker2020].
+Our analysis may therefore not have been particularly sensitive, especially since linear mixed-effects models often have limited statistical power [@matuschek2017].
+
+[^2]: Note, however, the converging evidence from the complementary approach of rendering images of everyday obbjects difficult to recognize [@samaha2018].
+
+Nevertheless, this study provides preliminary evidence that whenever we acquire semantic information about a previously unfamiliar object, this information has an influence on multiple stages of processing.
+Intriguingly, this influence is not confined to later, post-perceptual stages---typically associated with semantic processing---but can also be observed at earlier stages---typically reflecting lower levels of visual perception and happening within 200 ms after the object is presented to us.
+
+```{=html}
+<!-- Participants' semantically informed perception of the objects in the insight part was associated with a significantly enlarged N170 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001].
+The fact that this effect did not reoccur in the post-insight part, when the objects were presented once more without keywords, suggests it being a marker of semantic insight altering object processing online.
+In contrast, we also observed a modulation of the N400 component, which was reduced for objects while insight was taking place (insight part) and remained so when the same objects were presented repeatedly (post-inisght part).
+The N400 is typically discussed as an index of increased demands for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018].
+Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had understood what kind of object they were viewing.
+Finally, semantically informed perception was also associated with increased amplitudes in the P1 component but only once the objects were presented for a third time (post-insight part) after the critical presentation during which insight had occurred.
+This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images [e.g., @samaha2018], may reflect that this newly acquired semantic knowledge is exerting an influence on lower-level visual perception.
+Note that this influence may manifest itself either online (within the same trial) or via the re-activation of a stored representation (created during the previous presentation of the object together with its keywords).
+Either way it is remarkable that such an early ERP effect emerges after only a single trial of "learning" in the insight part.[^2]
+
+[^2]: Interesingly, the ability to infer the category of an object from one or few encounters remains one of the ample differences between learning in biological and artifical neural networks [but see @lifei-fei2006; @koch2015].
+
+While the enhancement of the N170 component, being more negative for semantically informed as compared to naive perception, was present only during the critical presentation of the objects with their respective keywords (in the insight part), the enhancement of the P1, being more positive in response to these same objects, emerged only after the information had been obtained and the objects were presented again (in the post-insight part).
+This indicates a modulation of different stages of visual object perception while and after an understanding of the object has been obtained.
+Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantically informed perception may reflect lowered semantic processing demands compared to unfamiliar objects which participants did not yet understand.
+-->
+```
 \newpage
 
-# References
+# Appendix
+
+```{r appendix, include=TRUE, results="asis"}
+# Print table of materials
+read_tsv("materials/items.txt", col_types = cols()) %>%
+  transmute(
+    img = paste0("\\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/", item, ".png}"),
+    item = as.character(item),
+    match = paste(match_noun, match_verb),
+    nonmatch = paste(nonmatch_noun, nonmatch_verb)
+  ) %>%
+  apa_table(
+    col.names = c("", "\\#", "Matching keywords", "Non-matching keywords"),
+    escape = FALSE,
+    longtable = TRUE,
+    caption = "Unfamiliar Object Stimuli"
+  )
+```
+
+\newpage
+
+# References {.unnumbered}
 
@@
 \setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
+%\setlength{\leftskip}{0.5in}
+```

### 2021-01-05 analysis/manuscript.tex
add discussion section + rmd for master thesis

@@
   english,
-  man,11pt,floatsintext]{apa7}
+  man,floatsintext]{apa7}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
@@
 \hypersetup{
-  pdfauthor={Alexander Enge1},
+  pdfauthor={Alexander Enge1,2, Franziska Süß3, \& Rasha Abdel Rahman1},
   pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdfkeywords={objects, semantic knowledge, visual perception, event-related potentials},
   hidelinks,
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \shorttitle{Semantic Knowledge and Unfamiliar Objects}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{objects, semantic knowledge, visual perception, event-related potentials\newline\indent Word count: }
 \usepackage{csquotes}
+\geometry{a4paper}
+\fancyheadoffset[R,L]{0pt}
+\raggedbottom
 \usepackage{setspace}
 \AtBeginEnvironment{tabular}{\doublespacing}
-\AtBeginEnvironment{lltable}{\doublespacing}
-\AtBeginEnvironment{tablenotes}{\doublespacing}
-\captionsetup[table]{font={stretch=1.5}}
 \captionsetup[figure]{font={stretch=1,scriptsize}}
-\raggedbottom
+\usepackage[all]{nowidow}
+\usepackage[bottom]{footmisc}
+\interfootnotelinepenalty=10000
+\usepackage[export]{adjustbox}
 \ifxetex
@@
 \else
-  \usepackage[shorthands=off,main=english]{babel}
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 \fi
-
-\title{Event-Related Potentials of the Semantically\\
-Informed Perception of Unfamiliar Objects}
-\author{Alexander Enge\textsuperscript{1}}
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\title{Event-Related Potentials of the Semantically Informed\\
+Perception of Unfamiliar Objects}
+\author{Alexander Enge\textsuperscript{1,2}, Franziska Süß\textsuperscript{3}, \& Rasha Abdel Rahman\textsuperscript{1}}
 \date{}
@@
 
-Alexander Enge, Department of Psychology, Humboldt-Universität zu Berlin, Germany, \url{https://orcid.org/0000-0003-0100-2297}, student no. 581331.
-
-The thesis was handed in December 18, 2020 and has been supervised by Prof.~Dr.~Rasha Abdel Rahman, Humboldt-Universität zu Berlin, Germany, and Prof.~Dr.~Franziska Süß, Fachhochschule des Mittelstands, Bamberg, Germany.
-
-Correspondence concerning this article should be addressed to Alexander Enge, Rudower Chaussee 18, 12489 Berlin.
-E-mail: \href{mailto:alexander.enge@hu-berlin.de}{\nolinkurl{alexander.enge@hu-berlin.de}}
+\addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
+
+\addORCIDlink{Rasha Abdel Rahman}{0000-0002-8438-1570}
+
+The preprocessed data and code for this study are openly available at \url{https://osf.io/uksbc/}.
+
+We have no conflict of interest to disclose.
+
+Correspondence concerning this article should be addressed to Rasha Abdel Rahman, Rudower Chaussee 18, 12489 Berlin.
+E-mail: \href{mailto:rasha.abdel.rahman@hu-berlin.de}{\nolinkurl{rasha.abdel.rahman@hu-berlin.de}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Humboldt-Universität zu Berlin}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Humboldt-Universität zu Berlin\\\textsuperscript{2} Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany\\\textsuperscript{3} Fachhochschule des Mittelstands, Bamberg, Germany}
 
 \abstract{
-Abstract goes here.
+Does our perception of an object change as soon as we discover what it is for?
+This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it pertains to the long-standing debate around the (im)penetrability of perception by ``higher'' cognitive capacities.
+In this experiment, we showed participants (\emph{n} = 24) pictures of 120 unfamiliar objects either together with valid information about their function---leading to semantically informed perception---or together with invalid information---resulting in naive perception.
+We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of perceiving objects differed from one another.
+We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
+When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place.
+We replicated these novel findings in an independent sample (\emph{n} = 24).
+Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
 }
@@
 How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects, preceded in half of the cases by valid information about their function, leading to semantically informed perception, and in the other half of the cases by misleading information, leading to naive perception.
-Capitalizing on the high temporal resolution of event-related brain potentials (ERPs), we investigated at which stages in the processing hierarchy semantically informed and naive perception of visual objects differed from one another.
-
-The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-standing debate.
-This debate revolves around the question whether or not our perception of the (visual) world should be thought of as an encapsulated module being completely determined by the visual input reaching our retina.
-According to the former view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (Firestone \& Scholl, 2016; Fodor, 1984, 1983; Machery, 2015; Pylyshyn, 1999).
-Conversely, this view is challenged by theoretical and empirical work suggesting that perceptual processing dynamically interacts with other aspects of cognition from early on (Churchland, 1988; Churchland et al., 1994; Collins \& Olson, 2014; Lupyan, 2012, 2015; Lupyan et al., 2020; Thierry, 2016; Vetter \& Newen, 2014).
-These aspects may include transient states such as emotions (e.g.~Phelps et al., 2016; Bocanegra \& Zeelenberg, 2009) or intentions (Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g.~Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g.~Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g.~Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019).
-Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained sceptical, pointing out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016).
-
-One productive way of investigating top-down effects of cognition on perception while addressing some of these concerns is through neurophysiological recording methods such as ERPs: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
-This is because when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
-
-The visual P1 component refers to a positive deflection peaking approximately 100--150 ms after stimulus onset at occipital channels.
+In this study, we presented participants with unfamiliar objects which were preceded either by valid information about their function, leading to semantically informed perception, or by misleading information, leading to naive perception.
+Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temopral resoulation of event-related brain potentials (ERPs).
+
+The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
+This debate revolves around the question of whether or not our perception of the (visual) world should be thought of as an encapsulated module whose processing is determined solely by the visual input reaching our retina.
+According to this view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1984, 1983; Machery, 2015; Pylyshyn, 1999).
+Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects (DiCarlo et al., 2012; Goodale \& Milner, 1992; Marr, 1982).
+
+Conversely, this position is challenged by the view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., P.
+M.
+Churchland, 1988; P.
+S.
+Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017).
+The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas {[}e.g., visual areas V1 and V2; Bullier (2001); Gilbert and Li (2013){]}, as well as behavioral evidence, have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+The reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002), for instance, assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
+Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
+Along similar lines, the label feedback hypothesis (Lupyan, 2012) posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
+Finally, an active role of top-down influences is also promoted by theories of vision falling under the umbrella of Bayesian inference and predictive coding (e.g., Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
+
+Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition (for review, see Collins \& Olson, 2014; Vetter \& Newen, 2014).
+These aspects of cognition may include transient states such as emotions (Bocanegra \& Zeelenberg, 2009; e.g., Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019).
+Despite this wealth of theory and empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).
+
+One productive way to investigate top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
+
+The visual P1 component of the ERP refers to a positive deflection peaking as early as 100--150 ms after stimulus onset at occipital channels.
 It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri (Di Russo et al., 2001; Foxe \& Simpson, 2002; Mangun, 1995).
-The P1 is mostly thought to reflect the processing of low-level visual characteristics of the stimulus (such as size, luminance, and contrast; Di Russo et al., 2001; Johannes et al., 1995; Luck, 2014), which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception.
-It should be noted, however, that the P1 is reliably modulated by spatial (Luck et al., 2000; Mangun, 1995; Mangun \& Hillyard, 1991) and non-spatial (Taylor, 2002) attention.
+The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus {[}e.g., size, luminance, and contrast; Di Russo et al.
+(2001); Luck (2014); Johannes et al.
+(1995){]}, which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception.
+For instance, it is enhanced when participants pay attention to the spatial location (Luck et al., 2000; Mangun, 1995; Mangun \& Hillyard, 1991) or certain non-spatial features (Taylor, 2002) of the stimulus.
 
 The visual N170 (or N1) component refers to the negative deflection following the P1 and is maximal around 150--200 ms after stimulus onset at occipito-temporal channels.
-While still influenced by visual parameters of the stimulus (Johannes et al., 1995), it is also sensitive to selective attention, at least when participants are required to discriminate between different visual stimuli (Mangun \& Hillyard, 1991; Vogel \& Luck, 2000).
-Importantly, the N170 is enlarged (i.e.~more negative) in response to faces (Bentin et al., 1996; Rossion \& Jacques, 2011) and other visual stimuli for which one happens to be an expert (e.g.~birds, dogs, or cars; I.
-Gauthier, Curran, et al., 2003; Tanaka \& Curran, 2001).
-This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as their configuration (Eimer et al., 2011; Jacques \& Rossion, 2010; Rossion et al., 1999; Sagiv \& Bentin, 2001).
-Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimuli.
-
-Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration (Kutas \& Federmeier, 2011; Lau et al., 2008; Rabovsky et al., 2018), starting approximately 300 ms after stimulus onset and being most pronounced at centro-parietal channels.
-A modulation of this component by cognitive capapacities such as knowedge can be taken as evidence for a post-perceptual influence on stimulus processing.
-
-Previous studies have focused on these and other ERP components to investiage which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects (Abdel Rahman \& Sommer, 2008; Gratton et al., 2009; Maier et al., 2014; Maier \& Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
-Together, they suggest that not only higher-level semantic ERPs like the N400 component are influenced by acquiring semantic information about objects, but also early components that typcially reflect bottom-up visual processing.
-This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (cooking recipes) for the other half of the objects (Abdel Rahman \& Sommer, 2008, Experiment 1).
+Just as the P1, it is influenced by visual parameters of the stimulus (Johannes et al., 1995) and by selective attention, especially when participants are required to discriminate between different visual stimuli (Mangun \& Hillyard, 1991; Vogel \& Luck, 2000).
+Importantly, the N170 is enlarged (i.e.,~more negative) in response to faces (Bentin et al., 1996; Rossion \& Jacques, 2011) and other visual stimuli for which one happens to be an expert {[}e.g., birds, dogs, or cars; Gauthier, Curran, et al.
+(2003); Tanaka and Curran (2001){]}.
+This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as the holistic configuration of these features (Eimer et al., 2011; Jacques \& Rossion, 2010; Rossion et al., 1999; Sagiv \& Bentin, 2001).
+Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimulus.
+
+Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration (Kutas \& Federmeier, 2011; Lau et al., 2008; Rabovsky et al., 2018).
+It begins approximately 300 ms after stimulus onset and is most pronounced at centro-parietal channels.
+A modulation of the N400 component by cognitive capacities such as knowledge can be taken as evidence for a post-perceptual influence on stimulus processing.
+
+Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects (Abdel Rahman \& Sommer, 2008; Gratton et al., 2009; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Rossion et al., 2004, 2002; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
+Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing.
+This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (i.e., cooking recipes) for the other half of the objects (Abdel Rahman \& Sommer, 2008, Experiment 1).
 After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information.
@@
 Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
-Of note, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects.
-The modulation of the P1 component was also replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm (Weller et al., 2019).
-Of note, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink, which can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.
-
-A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects, which were rendered difficult to recognize by converting them to two-tone, \enquote{Mooney} images (Samaha et al., 2018, Experiment 4).
-Here, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the image beforehand, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
-When the EEG was measured in a separate delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images of objects than for perceptually-trained images of objects.
-This alternative approach further coroborates an early influence of semantic information on visual object perception.
-
-All the previously mentioned studies have in common that they investigated the effects of semantic knoweldge on object perception only \emph{after} an extensive learning phase (Abdel Rahman \& Sommer, 2008; I.
-Gauthier, James, et al., 2003; Maier et al., 2014; Maier \& Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Weller et al., 2019).
-Participants performed one or multiple training session where they encountered each object together with its respective label or description multiple times.
-The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Rahman, 2019) or were spread out across multiple days or weeks (Rossion et al., 2002, 2004).
-While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three important conceptual questions unresolved.
-
-The first question is if we can detect any electrophysiological correlates of semantic insight, i.e.~the critical presentation during which an understanding of the previously unfamiliar object is happening, instead of asking if this understanding leads to differential effects in an orthogonal task later on.
-The second question is how much learning is actually necessary before reliable top-down effects of knowledge (such as~on object-related P1 amplitudes) can be obtained: Does it actually take dozens of repitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of semantics, altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects, having been altered throughout the learning process (Haber, 1966)?
+Interestingly, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects.
+The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm (Weller et al., 2019).
+Here, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
+This can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.
+
+A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects which were rendered difficult to recognize by converting them to two-tone, ``Mooney'' images (Samaha et al., 2018, Experiment 4).
+In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
+When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images of objects than for perceptually-trained images of objects.
+As before, these effects of perceiving objects in a semantically informed way seems to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
+This alternative approach further corroborates an early influence of semantic information on the visual perception of objects.
+
+All the previously mentioned studies have in common that they investigated the effects of semantic knowledge on the visual perception of objects only \emph{after} an extensive learning phase had taken place (Abdel Rahman \& Sommer, 2008; Gauthier, James, et al., 2003; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Rossion et al., 2004, 2002; Samaha et al., 2018; Weller et al., 2019).
+Participants performed one or multiple training sessions during which they encountered each object together with its respective label or description multiple times.
+The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Abdel Rahman, 2019) or were spread out across multiple days or weeks (Rossion et al., 2004, 2002).
+While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three conceptual questions unresolved.
+
+The first question is if we can detect any electrophysiological correlates of semantic insight, that is,~the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on).
+The second question is how much learning is actually necessary before reliable top-down effects of knowledge on ERP amplitudes can be obtained: Does it actually take dozens of repetitions per object or may a single exposure to the object together with the relevant semantic information be enough?
+The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
 By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we hope to provide tentative answers to all three of these questions.
@@
 In the two experiments subsequently reported, participants were presented with real-word objects that were presumed to be unfamiliar to most of them.
-They first viewed each of these objects once without any semantic information.
-This part served as a naive baseline to outrule that ERPs would differ in response to the objects based solely on their low-level visual differences.
+They first viewed each of these objects without any semantic information.
+This first part served as a naive baseline to rule out that ERPs would differ in response to the objects based solely on low-level visual differences.
 Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
-These keywords could either correctly describe the object's typical function, thus making it possible for participants to understand what kind of object they are viewing, or mislead them by describing the function of a different object, thus keeping the perception of the object semantically naive.
-During this \enquote{insight} part, we were able measure the online influence of semantic knowledge on object-evoked ERPs as it happened.
-Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them, thus mimicking previous studies (e.g.~Abdel Rahman \& Sommer, 2008, p.
-@samaha2018; Weller et al., 2019).
-In all three parts, we compared the influences of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (400--700 ms).
+These keywords could either correctly describe the typcial function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could mislead participants by describing the function of a different object, thus keeping the perception of the object semantically naive.
+During this second part, we were able measure the online influence of semantic insight on object-evoked ERPs as it happened.
+Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them---thereby mimicking previous studies (e.g., Abdel Rahman \& Sommer, 2008; Samaha et al., 2018; Weller et al., 2019).
+In all three parts, we examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (N400 component, 400--700 ms).
 
@@
 
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
+\hypertarget{method}{%
+\subsection{Method}\label{method}}
 
@@
 Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
-No a priori power analysis was carreid out and the sample size was chosen according to the default for EEG studies in our lab at the time of data collection.
+No a priori power analysis was carried out and the sample size was chosen in line with other EEG studies in our lab at the time of data collection.
 All participants were right-handed according to the Edinburgh inventory (Oldfield, 1971) and reported normal or corrected-to-normal vision.
 They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-All experiments subsequently reported were carried out in accordance with the Declaration of Helsinki and approved by the local ethics committee.
-
-\hypertarget{materials-and-procedure}{%
-\subsubsection{Materials and Procedure}\label{materials-and-procedure}}
-
-Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g.~a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar for the majority of participants (e.g.~a galvanometer, an udu drum).
-A list of these unfamiliar objects can be found in Appendix A.
+
+\hypertarget{materials}{%
+\subsubsection{Materials}\label{materials}}
+
+Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum).
+A list of these unfamiliar objects can be found in the appendix.
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of keywords---a noun and a verb---was selected describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g.~current--measuring, pottery--drumming).
+For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g., current--measuring, pottery--drumming).
 As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e.~participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an effect and keep the perception of the object semantically naive.
-All participants saw each unfamiliar object in only one of the two conditions and the assignment of objects to conditions was counterbalanced across participants.
+The matching keywords were expected to induce semantically informed perception (i.e.,~participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive.
+All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
+This assignment of keywords and objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
 
-Each experimental session consisted of three parts (Figure \ref{fig:exp1-plot}A).
-In the \emph{pre-insight} part (Part I), after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
+\hypertarget{procedure}{%
+\subsubsection{Procedure}\label{procedure}}
+
+Each experimental session consisted of three parts (see Figure \ref{fig:exp1-plot}A).
+In the \emph{pre-insight} part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
 Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
 The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) \enquote{I know what this is or have a strong assumption,} (b) \enquote{I have an assumption what this is,} (c) \enquote{I have rather no assumption what this is,} or (d) \enquote{I do not know what this is and have no assumption.} Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) ``I know what this is or have a strong assumption,'' (b) ``I have an assumption what this is,'' (c) ``I have rather no assumption what this is,'' or (d) ``I don't know what this is and have no assumption.'' Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
@@
 \caption{Procedure and results of Experiment 1.
-\emph{(A)} In the pre-insight part (Part I), participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In the insight part (Part II), half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
-In the post-insight part (Part III), the same objects were presented again without the keywords.
-\emph{(B)} ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within Parts I, II, and III.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in Part II, significantly less negative amplitudes in the N400 component in Parts II and III, and significantly more positive amplitudes in the P1 component in Part III.
+\emph{(A)} In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
+In the post-insight part, the same objects were presented again without the keywords.
+\emph{(B)} ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
+Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
 Ampl.
@@
 
-In the \emph{insight} part (Part II), only the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+In the \emph{insight} part, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
 Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
 Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
-The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g.~medical devices, musical instruments).
-
-In the post-insight part (Part III), the unfamiliar objects were presented for a third time with an identical trial structure as in Part I, i.e.~without any keywords.
-Note that Parts II and III were presented in an interleaved fashion so that after the presentation of one block of 30 objects in Part II (with keywords), participants took a self-timed break and continued with the same block of 30 objects in Part III (without keywords) before moving on to the next block consisting of 30 different objects.
-They continued like this until all four blocks were completed in both Parts II and III.
-In total, the experiment consisted of 480 trials (120 familiar objects in Part I and 120 unfamiliar objects in Parts I, II, and III) and took participants approximately 35 minutes to complete.
+The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).
+
+Finally, in the \emph{post-insight} part, the unfamiliar objects were presented for a third time with an identical trial structure as in the pre-insight part, that is, without any keywords.
+Note that the insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight part (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight part (without keywords) before moving on to the next block consisting of 30 different objects.
+They continued like this until all four blocks were completed in both parts.
+In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight part and 120 unfamiliar objects in the pre-insight, insight, and post-insight parts).
+It took participants approximately 35 minutes to complete.
 
@@
 
-Offline, the data were preprocessed using the MNE software (Version 0.21.0; Gramfort et al., 2013) in Python (Version 3.8.5; van Rossum \& Drake, 2009).
+Offline, the data were preprocessed using the MNE software {[}Version 0.21.0; Gramfort et al.
+(2013){]} in Python {[}Version 3.8.5; van Rossum and Drake (2009){]}.
 First, all scalp electrodes were re-referenced to the common average.
@@
 The first 15 components were extracted by the FastICA algorithm (Hyvärinen, 1999) after temporarily low-pass filtering the data at 1 Hz.
-Those components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the \emph{find\_bads\_eog} function.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the \emph{find\_bads\_eog} function.
 After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
@@
 Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
-This led to the exclusion of an average of 2.4 trials (0.7\%) per participant (range 0 to 24).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+This led to the exclusion of an average of 2.4 trials per participant (= 0.7\%; range 0 to 24 trials).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see scalp topographies in Figure \ref{fig:exp1-plot}B).
 
@@
 
-First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in Part I (i.e.~before any keywords were presented), which led to the exclusion of an average of 7.5 objects per participant (6.3\%).
-Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in Part II) and the behavioral responses of the participants themselves (Figure 1A).
+First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in the pre-insight part (i.e.,~before any keywords were presented).
+This led to the exclusion of an average of 7.5 objects per participant (= 6.3\% of all unfamiliar objects).
+Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \ref{fig:exp1-plot}A).
 Objects were assigned to the semantically informed condition only if they were presented with matching keywords \emph{and} if participants indicated knowing what the object was or having an assumption.
-This was the case for an average of 27.0 objects per participant (44.9\% of objects presented with matching keywords).
+This was the case for an average of 27.0 objects per participant (= 44.9\% of objects presented with matching keywords).
 Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords \emph{and} if participants indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of 48.8 objects per participant (81.2\% of objects presented with non-matching keywords).
-Although the assignment was purely based on the manipulation and responses in Part II, when insight was thought to occurr, the same assignment was used to analyze the data from the other two parts.
-This allowed us to test on the one hand if the objects from both conditions differed in important aspects even before any keywords were presented (in Part I), and on the other hand if the semantic understanding acquired in Part II had any lasting effects on a subsequent, third presentation of the objects (in Part III).
+This was the case for an average of 48.8 objects per participant (= 81.2\% of objects presented with non-matching keywords).
+Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occurr---the same assignment was used to analyze the data from the other two parts.
+This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).
 
 The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018).
-For the purpose of the present study, these models have at least two desirable properties compared to more traditional approaches, such as analyses of variance (ANOVAs) performed on by-participant grand averages.
-First, they can account simultaneously for the non-independence of data points coming from the same participant or from the same item, whereas the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
-Second, they can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions, which is inevitable in designs where the assignment of trials to conditions is (co-)determined by the responses of the participants rather than by the experimental manipulation alone (e.g.~Fröber et al., 2017).
+For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+First, they can account not only for the non-independence of data points coming from the same participant but also simultaneously for the non-independence of data points coming from the same item.
+In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
+Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
+Such a situation is inevitable in designs where the assignment of trials to conditions is (co-)determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone (e.g., Fröber et al., 2017).
 
 Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
-All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.~subtracting Part I from Part II and Part II from Part III, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.~subtracting the naive from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
+All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.,~subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.,~subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
 For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to (Schad et al., 2020).
 To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects (Barr et al., 2013).
-We then performed a model selection algorithm as proposed by (Matuschek et al., 2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effects was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model.
-All models were calculated in R (Version 4.0.2; R Core Team, 2020) using the lme4 package (Version 1.1.23; Bates et al., 2015).
-The optimizer function \emph{bobyqa} with 2·10\textsuperscript{5} iterations was used for maximum likelihood estimation.
-The model selection algorithm via likelihood ratio tests was performed using the buildmer package (Version 1.7.1; Voeten, 2020).
-Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within Parts I, II, and III.
-All \emph{p} values subsequently reported were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's methods as implemented in the lmerTest package (Kuznetsova et al., 2017).
-
-The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\href{https://osf.io/myprojects/}{https://osf.io/\ldots/}).
-To avoid potential misuse, the raw EEG are only made available by the corresponding author upon request.
+We then performed a model selection algorithm as proposed by (Matuschek et al., 2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+Only if the parsimonious model explained the data equally well as the complex model {[}determined by \emph{p} \textgreater{} .20; Matuschek et al.
+(2017){]} did we leave the random effect out, otherwise it was kept in the final model.
+All models were computed in R {[}Version 4.0.2; R Core Team (2020){]} using the lme4 package {[}Version 1.1.23; Bates et al.
+(2015){]}.
+The optimizer function \emph{bobyqa} with 20,000 iterations was used for maximum likelihood estimation.
+The model selection algorithm via likelihood ratio tests was performed using the buildmer package {[}Version 1.7.1; Voeten (2020){]}.
+Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts.
+All \emph{p}-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package {[}Version 3.1.2; Kuznetsova et al.
+(2017){]}.
+
+The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\url{https://osf.io/uksbc/}).
+Unfortuntaly, lack of informed consent prevents us from sharing the raw EEG data.
 
@@
 
-Single-trial ERPs were analyzed in response to unfamiliar objects before (Part I), while (Part II), and after (Part III) participants obtained relevant semantic information about their function.
-Only in Part II, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
-The objects were analyzed according to this manipulation in combination with participants' self-report in Part II (Figure 1A), thus making sure that semantically informed (or naive) perception did indeed occur.
+Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
+Only in the insight part, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
+The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \ref{fig:exp1-plot}A), thereby making sure that semantically informed and naive perception did indeed occur.
 The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N170 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.
@@
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Part I (pre-insight) & -0.03 [-0.53, 0.47] & .913 & -0.12 [-0.68, 0.44] & .665 & -0.20 [-0.65, 0.26] & .400\\
-Part II (insight) & -0.18 [-0.68, 0.32] & .490 & -0.64 [-1.20, -0.08] & .026 & 0.93 [0.48, 1.39] & < .001\\
-Part II (post-insight) & 0.55 [0.05, 1.05] & .031 & 0.43 [-0.14, 0.99] & .136 & 1.00 [0.54, 1.46] & < .001\\
+Pre-insight part & -0.03 [-0.53, 0.47] & .913 & -0.12 [-0.68, 0.44] & .665 & -0.20 [-0.65, 0.26] & .400\\
+Insight part & -0.18 [-0.68, 0.32] & .490 & -0.64 [-1.20, -0.08] & .026 & 0.93 [0.48, 1.39] & < .001\\
+Post-insight part & 0.55 [0.05, 1.05] & .031 & 0.43 [-0.14, 0.99] & .136 & 1.00 [0.54, 1.46] & < .001\\
 \bottomrule
@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.89, all \emph{p}s \textless{} .001 (Table \ref{tab:exp1-table}).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}NA = NA, \emph{p} = NA.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.89, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp1-table}).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}(1, 24.4) = 13.00, \emph{p} = .001.
 Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4605.0) = 2.30, \emph{p} = .100.
@@
 
-\hypertarget{erps-in-part-i-pre-insight}{%
-\subsubsection{ERPs in Part I (Pre-Insight)}\label{erps-in-part-i-pre-insight}}
-
-In Part I, when objects were unfamiliar to the participant and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .400 (Table \ref{tab:exp1-table}, Figure \ref{fig:exp1-plot}B \& C).
+\hypertarget{erps-before-insight-was-occurring}{%
+\subsubsection{ERPs Before Insight Was Occurring}\label{erps-before-insight-was-occurring}}
+
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .400 (see Table \ref{tab:exp1-table} and Figure \ref{fig:exp1-plot}B).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs.~naive perception) had not yet taken place.
-On the other hand, the absence of reliable differences in Part I can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in Parts II and III cannot be accounted for by visual differences between the objects in the two conditions.
-Although the presentation of a matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report in Part II would have made it possible for such visual differences to emerge as a confounding factor.
+On the other hand, the absence of reliable differences in this part can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in the other two parts cannot be accounted for by visual differences between the objects in the two conditions.
+Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report would have made it possible for such visual differences to emerge as a confounding factor.
 If they did, however, one would expect to detect these differences even before any keywords were presented, which we have now seen was not the case.
 
-\hypertarget{erps-in-part-ii-insight}{%
-\subsubsection{ERPs in Part II (Insight)}\label{erps-in-part-ii-insight}}
-
-In Part II, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object (akin to an insight experience), the amplitude of the N170 component was significantly enlarged (i.e.~more negative), \emph{b} = -0.64 µV, \emph{p} = .026, and the amplitude of the N400 component was significantly reduced (i.e.~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when an object was viewed naively without relevant semantic information.
-As in Part I, there were no reliable differences in the P1 component, \emph{p} = .490.
-
-\hypertarget{erps-in-part-iii-post-insight}{%
-\subsubsection{ERPs in Part III (Post-Insight)}\label{erps-in-part-iii-post-insight}}
-
-In Part III, the unfamiliar objects were presented for a third time, again without the keywords (as in Part I), to test whether the semantic information had any lasting effects on the processing of the objects.
-As in Part II, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the early effect in the N170 component did not reoccur, \emph{p} = .136.
-Instead, we now observed an even earlier modulation in the P1 component, which was significantly enlarged (i.e.~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.55 µV, \emph{p} = .031.
+\hypertarget{erps-while-insight-was-occurring}{%
+\subsubsection{ERPs While Insight Was Occurring}\label{erps-while-insight-was-occurring}}
+
+In the insight part, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
+When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e.,~more negative), \emph{b} = -0.64 µV, \emph{p} = .026, and the amplitude of the N400 component was significantly reduced (i.e.,~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when the object was viewed naively without relevant semantic information.
+As in the pre-insight part, there were no reliable differences in the P1 component, \emph{p} = .490.
+
+\hypertarget{erps-after-insight-had-occurred}{%
+\subsubsection{ERPs After Insight Had Occurred}\label{erps-after-insight-had-occurred}}
+
+In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part), to test whether the semantic information had any lasting effects on the processing of the objects.
+As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the effect in the N170 component did not reoccur, \emph{p} = .136.
+Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e.,~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.55 µV, \emph{p} = .031.
 
@@
 
-In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (Part I), while (Part II) and after (Part III) they were able to understand what kind of object they saw.
-To induce this semantically informed perception, half of the objects in Part II were preceded by matching verbal keywords about their typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
-
-Participants' semantically informed perception of the objects in Part II was associated with a significantly enlarged N170 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing (Rossion \& Jacques, 2011; Tanaka \& Curran, 2001).
-The fact that this effect did not reoccur in Part III, when the objects were presented once more without keywords, suggests it being a marker of insight through semantic information that is altering object processing online.
-In contrast, we also observed a modulation of the N400 component, which was reduced for objects while insight was taking place (in Part II) and remained so when the same objects were presented repeatedly (in Part III).
-The N400 is most often discussed as an index of increased demands for semantic processing or integration (Kutas \& Federmeier, 2011; Lau et al., 2008; Rabovsky et al., 2018).
-Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had understood what kind of object they were viewing.
-Finally, semantically informed perception was also associated with increased amplitudes in the P1 component, but only once the objects were presented for a third time (in Part III), after the critical presentation during which insight had occurred (in Part II).
-This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images (e.g.~Samaha et al., 2018), may be associated with the newly acquired semantic knowledge exerting an influence on lower-level visual perception, either online or through altered visual representations of the objects for which insight had occurred.
-
-Because of the exploratory nature of the present study and the novelty of the ERP effects observed in Experiment 1, we ran a replication study to assess the robustness of these findings in another samples of participants.
+In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-inisight part) they were able to understand what kind of object they saw.
+To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
+
+In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms).
+When the same objects were presented once more in the post-insigt part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for whic semantically informed perception had taken place.
+
+Because of the novelty of our experimental paradigm and the findings of Experiment 1, we ran a replication study to assess the robustness of these effects in another samples of participants.
 
@@
 
-\hypertarget{methods-1}{%
-\subsection{Methods}\label{methods-1}}
+\hypertarget{method-1}{%
+\subsection{Method}\label{method-1}}
 
@@
 All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
-An average of 7.0 objects per participant (5.8\%) was classified as being known in Part I and excluded from all further analyses.
-Based on participants' responses in Part II, an average of 26.4 objects were assigned to the semantically informed condition (44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (82.0\% of objects presented with a non-matching description).
-Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials per participant (3.0\%, range 0 to 85).
+An average of 7.0 objects per participant (= 5.8\% of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
+Based on participants' responses in the insight part, an average of 26.4 objects were assigned to the semantically informed condition (= 44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (= 82.0\% of objects presented with a non-matching description).
+Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials per participant (= 3.0\%; range 0 to 85 trials).
 
@@
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Part I (pre-insight) & -0.16 [-0.71, 0.40] & .582 & -0.03 [-0.53, 0.48] & .920 & 0.04 [-0.43, 0.50] & .877\\
-Part II (insight) & -0.48 [-1.03, 0.08] & .094 & -0.48 [-0.99, 0.03] & .064 & 1.33 [0.87, 1.79] & < .001\\
-Part II (post-insight) & 0.57 [0.01, 1.13] & .047 & 0.06 [-0.45, 0.57] & .818 & 0.47 [0.01, 0.93] & .047\\
+Pre-insight part & -0.16 [-0.71, 0.40] & .582 & -0.03 [-0.53, 0.48] & .920 & 0.04 [-0.43, 0.50] & .877\\
+Insight part & -0.48 [-1.03, 0.08] & .094 & -0.48 [-0.99, 0.03] & .064 & 1.33 [0.87, 1.79] & < .001\\
+Post-insight part & 0.57 [0.01, 1.13] & .047 & 0.06 [-0.45, 0.57] & .818 & 0.47 [0.01, 0.93] & .047\\
 \bottomrule
@@
 
-As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.57, all \emph{p}s \textless{} .001 (Table \ref{tab:exp2-table}).
-Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}NA = NA, \emph{p} NA.
+As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.57, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp2-table}).
+Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}(1, 5242.5) = 19.95, \emph{p} \textless{} .001.
 The part × condition interaction was significant in the P1 component, \emph{F}(2, 5267.1) = 3.60, \emph{p} = .027, and in the N400 component, \emph{F}(2, 4714.9) = 7.92, \emph{p} \textless{} .001, but not in the N170 component, \emph{F}(2, 4756.5) = 1.25, \emph{p} = .287.
@@
 \caption{Results of Experiment 2.
-ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within Parts I, II, and III.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in Parts II and III and on the P1 component in Part III remained statistically significant, while the effect on the N170 component in Part II remained only marginally significant (\emph{p} = .064).
+ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-inisght part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
 Ampl.
@@
 
-\hypertarget{erps-in-part-i-pre-insight-1}{%
-\subsubsection{ERPs in Part I (Pre-Insight)}\label{erps-in-part-i-pre-insight-1}}
-
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .582 (Table \ref{tab:exp2-table}, Figure \ref{fig:exp2-plot}).
-
-\hypertarget{erps-in-part-ii-insight-1}{%
-\subsubsection{ERPs in Part II (Insight)}\label{erps-in-part-ii-insight-1}}
-
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching versus non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, \emph{b} = -0.48 µV, \emph{p} = .064, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.
-
-\hypertarget{erps-in-part-iii-post-insight-1}{%
-\subsubsection{ERPs in Part III (Post-Insight)}\label{erps-in-part-iii-post-insight-1}}
-
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in Part I) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.57 µV, \emph{p} = .047.
+\hypertarget{erps-before-insight-was-occurring-1}{%
+\subsubsection{ERPs Before Insight Was Occurring}\label{erps-before-insight-was-occurring-1}}
+
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .582 (see Table \ref{tab:exp2-table} and Figure \ref{fig:exp2-plot}).
+
+\hypertarget{erps-while-insight-was-occurring-1}{%
+\subsubsection{ERPs While Insight Was Occurring}\label{erps-while-insight-was-occurring-1}}
+
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs.~non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, \emph{b} = -0.48 µV, \emph{p} = .064, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.
+
+\hypertarget{erps-after-insight-had-occurred-1}{%
+\subsubsection{ERPs After Insight Had Occurred}\label{erps-after-insight-had-occurred-1}}
+
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.57 µV, \emph{p} = .047.
 Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.47 µV, \emph{p} = .047.
@@
 This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
-Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast (i.e.~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al., 2020).
+Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast {[}i.e.,~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al.
+(2020){]}.
 This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
@@
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Part I (pre-insight) & -0.10 [-0.47, 0.28] & .616 & -0.10 [-0.48, 0.29] & .611 & -0.09 [-0.39, 0.22] & .577\\
-Part II (insight) & -0.24 [-0.62, 0.13] & .202 & -0.57 [-0.96, -0.18] & .004 & 1.10 [0.80, 1.41] & < .001\\
-Part II (post-insight) & 0.47 [0.09, 0.84] & .014 & 0.24 [-0.15, 0.63] & .225 & 0.73 [0.42, 1.04] & < .001\\
+Pre-insight part & -0.10 [-0.47, 0.28] & .616 & -0.10 [-0.48, 0.29] & .611 & -0.09 [-0.39, 0.22] & .577\\
+Insight part & -0.24 [-0.62, 0.13] & .202 & -0.57 [-0.96, -0.18] & .004 & 1.10 [0.80, 1.41] & < .001\\
+Post-insight part & 0.47 [0.09, 0.84] & .014 & 0.24 [-0.15, 0.63] & .225 & 0.73 [0.42, 1.04] & < .001\\
 \bottomrule
@@
 
-As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.34, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}NA = NA, \emph{p} NA.
+As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.34, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}(1, 10593.6) = 41.38, \emph{p} \textless{} .001.
 Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 3.90, all \emph{p}s \textless{} .020.
@@
 
+Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Figure \ref{fig:joint-plot}).
+This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s \textgreater{} .577, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.
+
 \begin{figure}
@@
 \caption{Measured and modelled ERP amplitudes for Experiments 1 and 2 combined.
-The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for Parts I (before insight was occurring), II (while insight was occurring), and III (after insight had occurred).
-The yellow dots show the corresponding condition means as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
+The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
+The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
 Ampl.
@@
 
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically inforemd and the naive condition within each part, now collapsed across the data from both experiments (Figure \ref{fig:joint-plot}).
-This confirmed the absence of any reliable differences between the two conditions in Part I, all \emph{p}s \textgreater{} .577, the significant enhancement of the N170 component in Part II, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in Part II, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and Part III, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} = \textless{} .001, as well as the significant enhancement of the P1 component in Part III, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.
-
 \hypertarget{control-analysis}{%
@@
 
-One may raise concerns whether the modulation of the N170 component in Part II genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it could be driven by the objects in the other, semantically naive condition.
-Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the object's visual features and their configuration.
-Thus, the modulation of the ERP components in Part II may reflect a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages.
-To preclude this alternative explanation, we repeated the analysis above using a different baseline against which the objects in the semantically informed condition were contrasted.
+One may raise concerns whether the modulation of the N170 component in the insight part genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it may be driven by the objects in the other, semantically naive condition.
+Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
+Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages.
+To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
 Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that the remaining objects to make it up to 100\% were excluded as not being unfamiliar in Part I of the experiment (see Methods).} Just as above, this control analysis revealed a robust N170 effect in Part II, \emph{b} = -1.00 µV, \emph{p} \textless{} .001.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords on which participants failed to capitalize.
-Note that the reduction of the N400 component in Part II also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.
+Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize.
+Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.
 
@@
 
-General discussion section goes here.
-
-Although most of the previous studies in the object processing domain have focused on the P1 component as an index of semantic knowledge modulating perceptual processes, at least two studies provide evidence for top-down effects of meaningfulness on the visual N170 (or N1) component in response to schematic drawings of faces (Bentin \& Golland, 2002) and objects (Beaucousin et al., 2011).
-Using a similar design as in the present study, drawings of distored faces elicited a facelike (i.e.~enlarged) N170 component only after participants were primed with a vaild hint---in this case the same face with all of its visual features in place (Bentin \& Golland, 2002).
-Similarly, N170 amplitudes in a global-local detection task where shown to be enhanced in response to line drawings of meaningful objects (a boat or a butterfly) as compared to visually matched by meaningless drawings of non-objects.
-Interestingly, this effect was reversed in polarity when participants had to focus on the smaller, constituent parts and ignoring the object which emerged out of their global arrangement, which may be interpreted as further evidence for a functional role of the N170 component in the holistic perception of an object and its early visual categorization, integrating across its visual features.
+Here we investigated if obtaining a semantic understanding of what a previously unfamiliar object is or does has an influence on how we perceive it.
+To this end, we measured ERPs while participants watched unfamiliar objects before, while, and after receiving semantic information about them.
+For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was misleading, thus keeping the perception of the object semantically naive.
+We found semantically informed percpetion to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
+If the same objects were presented again without the semantic information, only the N400 component remaind significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+
+The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
+Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing (Kutas \& Federmeier, 2011).
+It replicates previous findings that pictures elicit an N400 effect (as in our semantically naive condition) when they are either difficult to understand in and of themselves (e.g., Abdel Rahman \& Sommer, 2008; Supp et al., 2005) or difficult to integrate into the preceding context (e.g., Barrett \& Rugg, 1990; Ganis et al., 1996; Hirschfeld et al., 2011).
+The time course of this effect and the computational role of the N400 (Lau et al., 2008; Rabovsky et al., 2018) suggest that it has a post-perceptual locus.
+
+In contrast to the N400, the N170 component (150--200 ms after object onset) was modulated while but not after the objects were presented together with the relevant semantic information.
+As such, it can be seen as an online marker of semantic insight, that is, participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
+The N170 is typically associated with the holistic perception of faces (Eimer et al., 2011; Sagiv \& Bentin, 2001) and other stimuli of visual expertise (Rossion et al., 2002; Tanaka \& Curran, 2001).
+It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
+This interpretation is supported by previous work in face perception, using a similar experimental paradigm as the present study: Participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face (Bentin \& Golland, 2002).
+This effect was absent when a visual control stimulus (a non-face object instead of the intact face) was shown between the two presentations of the scrambled face.
+With regards to non-face stimuli, enlarged N170 amplitudes were also observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects (Beaucousin et al., 2011).
+Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constitutent parts of the object.
+Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level (i.e., holistic) perception of visual objects, integrating across their visual features.
+
+Unlike the N400 and N170 components, the P1 component (100--150 ms after object onset) was modulated by semantic information only one trial after it had been obtained.
+This is consistent with previous studies showing P1 effects when participants learned meaningful information about previously unfamiliar objects (Abdel Rahman \& Sommer, 2008; Maier \& Abdel Rahman, 2019, 2018; Weller et al., 2019) or about familiar objects that were rendered difficult to recognize (Samaha et al., 2018).
+What the present study adds to these findings is that it does not take an extensive learning phase (with multiple presentations of the objects together with the respective information) for the P1 effect to develop but that it can be observed immediately after (but not during) a semantic understanding of the object has happend.
+Because the P1 is typically associated with lower-level sensory processing (e.g., Johannes et al., 1995; Luck, 2014; Pratt, 2011), we take its succeptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
+
+Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of the visual objects as we perceive them.
+However, the finding that these two components were modulated in different parts of our experiment suggests that they reflect different aspects top-down processing with different time courses and neuroanatomical implementations.
+It has been suggested that the onset of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas a modulation of the P1 component seems reflect recurrent processing \emph{within} the visual system (Wyatte et al., 2014).
+Here we show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
+
+While the limited spatial resolution of the EEG does not allow for localizing these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI that semantic information can feed back into the earliest of visual areas.
+(Hsieh et al., 2010) showed participants indiscernible two-tone (``Mooney'') versions of images before and after showing them the original versions.
+They found that the brain responses to the original image was correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
+This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (V1/V2/V3).
+Both of these cortical sites are consistent with the neural generators of the P1 and N170 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
+
+The top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception (Firestone \& Scholl, 2016; Fodor, 1983; Pylyshyn, 1999).
+Proponents of this view have pointed out important conceptual and methodological shortcomings of previous studies claiming to show top-down effects of cognition on perception (Firestone \& Scholl, 2016; Machery, 2015).
+We took care to address as many of these shortcomings as possible: First, we showed that no effect was present had been present before any semantic information was presented (in the pre-insight part).
+Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual versus post-perceptual locus.
+Third, we reduced demand and response bias by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
+Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
+Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order and at the same location.
+Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
+We hope that these methods have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the ``cognitive impenetrability'' of perception.
+
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in machine vision (DiCarlo et al., 2012; Marr, 1982).
+In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of low-level visual features may be a key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+Single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach for these network models until they overcome this ``barrier of meaning'' (Mitchell, 2020).
+Drawing inspiration from cognitive psychology and human neuroscientific data may help making them more biologically plausible and, at the same time, more resource and data efficient.
+
+\hypertarget{theoretical-considerations}{%
+\paragraph{Theoretical Considerations}\label{theoretical-considerations}}
+
+\hypertarget{limitations}{%
+\paragraph{Limitations}\label{limitations}}
+
+\hypertarget{conclusion-outlook}{%
+\paragraph{Conclusion \& Outlook}\label{conclusion-outlook}}
 
@@
 
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\begin{center}
+\begin{ThreePartTable}
+
+\begin{longtable}{llll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:appendix}Unfamiliar Object Stimuli}\\
+\toprule
+ & \# & Matching keywords & Non-matching keywords\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:appendix} continued}}\\
+\toprule
+ & \# & Matching keywords & Non-matching keywords\\
+\midrule
+\endhead
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/1.png} & 1 & elektrische Spannung prüfen & Makkaroni formen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/2.png} & 2 & Makkaroni formen & Kuh vom Zaun abhalten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/3.png} & 3 & Knochen sägen & Streckenmaß Sonnenlicht nutzen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/4.png} & 4 & Unkraut jäten & Uhr mit Wärme betreiben\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/5.png} & 5 & Mausefalle zuschnappen & Brillenglas zuschneiden\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/6.png} & 6 & Goldmünzen wiegen & Farbe vom Fenster abschleifen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/7.png} & 7 & Knie fixieren & Buchstaben tippen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/8.png} & 8 & Eierkarton pressen & Tabak zermahlen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/9.png} & 9 & Baum erklettern & Rotation Ladung erzeugen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/10.png} & 10 & Buchstaben tippen & Pferdehuf Halt geben\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/11.png} & 11 & Akkordeon spielen & Seil schneiden\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/12.png} & 12 & Körper trainieren & Buch offen halten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/13.png} & 13 & Farbe vom Fenster abschleifen & von Hand zentrifugieren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/14.png} & 14 & Außenbereich heizen & Rasierklinge schärfen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/15.png} & 15 & Pflanzenteile vergrößern & Katzenklo sich selbst reinigen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/16.png} & 16 & Krawatten aufhängen & Zeichnungen vermessen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/17.png} & 17 & Schallplatte abtasten & Ball katapultieren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/18.png} & 18 & Glas schneiden & Eier wiegen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/19.png} & 19 & Briketts pressen & Narkosemittel abgeben\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/20.png} & 20 & Orgelton erzeugen & Bandage rollen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/21.png} & 21 & Spannung erzeugen & Fußstütze reiten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/22.png} & 22 & Narkosemittel abgeben & Nüsse aufbrechen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/23.png} & 23 & Bandage rollen & Schnee rodeln\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/24.png} & 24 & Weinfass Loch einschlagen & Tier einfangen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/25.png} & 25 & Flaschenkorken einführen & Pferd im Moor laufen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/26.png} & 26 & Automat Eier ausbrüten & Windgeschwindigkeit messen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/27.png} & 27 & Korngarbe greifen & Treibhaus heizen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/28.png} & 28 & Brief wiegen & Korngarbe greifen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/29.png} & 29 & Löcher bohren & Sonnenlicht Intensität messen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/30.png} & 30 & Angelschnur kurbeln & Glaskörper musizieren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/31.png} & 31 & Kurven malen & Nussöl pressen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/32.png} & 32 & Radiofrequenz einstellen & Erektion helfen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/33.png} & 33 & Zäpfchen pressen & Unkraut jäten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/34.png} & 34 & Fass öffnen & Pflanzenteile vergrößern\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/35.png} & 35 & Bergbaustollen beleuchten & Knie fixieren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/36.png} & 36 & Kuh vom Zaun abhalten & Radiofrequenz einstellen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/37.png} & 37 & Saatgut gleichmäßig aussäen & Fass öffnen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/38.png} & 38 & Flaschen trocknen & Bleistift anspitzen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/39.png} & 39 & Uhr mit Wärme betreiben & Körper untersuchen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/40.png} & 40 & Tonpott trommeln & Piano stimmen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/41.png} & 41 & Sprengstoffexplosion auslösen & Fisch wiegen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/42.png} & 42 & Pferdehuf Halt geben & Zäpfchen pressen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/43.png} & 43 & Bleistift anspitzen & Angel Köder markieren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/44.png} & 44 & Nussöl pressen & Zeichen einbrennen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/45.png} & 45 & Rasierklinge schärfen & Kurven malen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/46.png} & 46 & heiße Platten anheben & Kleidung im Eimer waschen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/47.png} & 47 & Film aufspulen & Mund offen halten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/48.png} & 48 & Waffe entflammen & Uhrzeit anzeigen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/49.png} & 49 & Mikroskop-Proben schneiden & heiße Platten anheben\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/50.png} & 50 & Glaskörper musizieren & Kork flach pressen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/51.png} & 51 & Dampf zerstäuben & Buch binden\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/52.png} & 52 & Mandeln operieren & Film aufspulen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/53.png} & 53 & Toastbrot rösten & Autobatterie Spannung testen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/54.png} & 54 & Fußstütze reiten & Stromstärke messen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/55.png} & 55 & Türgelenk Feuer überstehen & Botschaft telegrafieren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/56.png} & 56 & Schnee rodeln & Dampf zerstäuben\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/57.png} & 57 & Nüsse aufbrechen & Ziegelsteine formen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/58.png} & 58 & Radiergummi mit Strom betreiben & Münzen aufbewahren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/59.png} & 59 & Treibhaus heizen & Messer schleifen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/60.png} & 60 & Botschaft telegrafieren & Toastbrot rösten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/61.png} & 61 & Angel Köder markieren & Baum erklettern\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/62.png} & 62 & Katzenklo sich selbst reinigen & Tankfüllstand messen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/63.png} & 63 & Körper untersuchen & Schuhe auf Eis laufen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/64.png} & 64 & Brillenglas zuschneiden & Saatgut gleichmäßig aussäen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/65.png} & 65 & Draht wickeln & Bergbaustollen beleuchten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/66.png} & 66 & Buch offen halten & Sprengstoffexplosion auslösen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/67.png} & 67 & Feldanbau häckseln & Draht wickeln\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/68.png} & 68 & Schnurlot absenken & Korken formen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/69.png} & 69 & Sternenbilder vermessen & Schnurlot absenken\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/70.png} & 70 & Nachricht morsen & Feldanbau häckseln\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/71.png} & 71 & Musikgerät stampfen & Goldmünzen wiegen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/72.png} & 72 & Schuhe auf Eis laufen & Geschwindigkeit ermitteln\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/73.png} & 73 & Geschwindigkeit ermitteln & Mausefalle zuschnappen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/74.png} & 74 & Zeichen einbrennen & Luftdruck messen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/75.png} & 75 & Tabak zermahlen & Flaschen trocknen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/76.png} & 76 & Stromstärke messen & Mandeln operieren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/77.png} & 77 & Tier einfangen & Maiskolben entkörnen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/78.png} & 78 & Messer schleifen & Schritte vergrößern\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/79.png} & 79 & Leierkasten klingen & Fass anheben\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/80.png} & 80 & Buch binden & Löcher bohren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/81.png} & 81 & Kork flach pressen & Elektroschock spielen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/82.png} & 82 & Tabletten zerteilen & Blumentopf sich selbst wässern\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/83.png} & 83 & Fass anheben & Mikroskop-Proben schneiden\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/84.png} & 84 & Pferd im Moor laufen & Luft abpumpen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/85.png} & 85 & altes Ritual hacken & Spannung erzeugen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/86.png} & 86 & Kleidung im Eimer waschen & Türgelenk Feuer überstehen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/87.png} & 87 & Maiskolben entkörnen & Brief wiegen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/88.png} & 88 & Ball katapultieren & Radiergummi mit Strom betreiben\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/89.png} & 89 & Zeichnungen vermessen & Brenner löten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/90.png} & 90 & Elektroschock spielen & Weinfass Loch einschlagen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/91.png} & 91 & Lieferungen abzählen & Außenbereich heizen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/92.png} & 92 & Rotation Ladung erzeugen & Musikgerät stampfen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/93.png} & 93 & Herz durch Maschine ersetzen & Kerzen löschen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/94.png} & 94 & Seil schneiden & Akkordeon spielen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/95.png} & 95 & Fisch wiegen & Herz durch Maschine ersetzen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/96.png} & 96 & Kerzen löschen & Körper trainieren\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/97.png} & 97 & Korken formen & Sternenbilder vermessen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/98.png} & 98 & Erektion helfen & Waffe werfen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/99.png} & 99 & Streckenmaß Sonnenlicht nutzen & Kartoffeln stampfen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/100.png} & 100 & Luftdruck messen & Knochen sägen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/101.png} & 101 & Piano stimmen & Eierkarton pressen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/102.png} & 102 & von Hand zentrifugieren & Lieferungen abzählen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/103.png} & 103 & Kartoffeln stampfen & Nachricht morsen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/104.png} & 104 & Waffe werfen & elektrische Spannung prüfen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/105.png} & 105 & Tankfüllstand messen & Tonpott trommeln\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/106.png} & 106 & Uhrzeit anzeigen & altes Ritual hacken\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/107.png} & 107 & Windgeschwindigkeit messen & Waffe entflammen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/108.png} & 108 & Schlüsselloch stanzen & Automat Eier ausbrüten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/109.png} & 109 & Ziegelsteine formen & Schallplatte abtasten\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/110.png} & 110 & Becher Schall auffangen & Schlüsselloch stanzen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/111.png} & 111 & Luft abpumpen & Briketts pressen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/112.png} & 112 & Mund offen halten & Orgelton erzeugen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/113.png} & 113 & Autobatterie Spannung testen & Becher Schall auffangen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/114.png} & 114 & Sonnenlicht Intensität messen & Krawatten aufhängen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/115.png} & 115 & Kutschrad anschließen & Angelschnur kurbeln\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/116.png} & 116 & Eier wiegen & Leierkasten klingen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/117.png} & 117 & Blumentopf sich selbst wässern & Glas schneiden\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/118.png} & 118 & Schritte vergrößern & Tabletten zerteilen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/119.png} & 119 & Münzen aufbewahren & Kutschrad anschließen\\
+\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/120.png} & 120 & Brenner löten & Flaschenkorken einführen einführen\\
+\bottomrule
+\end{longtable}
+
+\end{ThreePartTable}
+\end{center}
+
+\newpage
+
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 
 \setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+%\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-abdelrahman2011}{}%
@@
 
+\leavevmode\hypertarget{ref-ahissar2004}{}%
+Ahissar, M., \& Hochstein, S.
+(2004).
+The reverse hierarchy theory of visual perceptual learning.
+\emph{Trends in Cognitive Sciences}, \emph{8}(10), 457--464.
+\url{https://doi.org/10.1016/j.tics.2004.08.011}
+
 \leavevmode\hypertarget{ref-americanelectroencephalographicsociety1991}{}%
@@
 (1991).
-American Electroencephalographic Society guidelines for standard electrode position nomenclature.
+{American Electroencephalographic Society} guidelines for standard electrode position nomenclature.
 \emph{Journal of Clinical Neurophysiology}, \emph{8}(2), 200--202.
@@
 
+\leavevmode\hypertarget{ref-barrett1990}{}%
+Barrett, S.
+E., \& Rugg, M.
+D.
+(1990).
+Event-related potentials and the semantic matching of pictures.
+\emph{Brain and Cognition}, \emph{14}(2), 201--212.
+\url{https://doi.org/10.1016/0278-2626(90)90029-N}
+
 \leavevmode\hypertarget{ref-R-lme4}{}%
@@
 (2015).
-Fitting linear mixed-effects models using lme4.
+Fitting linear mixed-effects models using {lme4}.
 \emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
@@
 
+\leavevmode\hypertarget{ref-bullier2001}{}%
+Bullier, J. (2001). Integrated model of visual processing. \emph{Brain Research Reviews}, \emph{36}(2), 96--107. \url{https://doi.org/10.1016/S0165-0173(01)00085-6}
+
 \leavevmode\hypertarget{ref-buxfcrki2018}{}%
@@
 \leavevmode\hypertarget{ref-churchland1988}{}%
-Churchland, P. M. (1988). Perceptual plasticity and theoretical neutrality: A reply to jerry fodor. \emph{Philosophy of Science}, \emph{55}(2), 167--187. \url{https://doi.org/10.1086/289425}
+Churchland, P. M. (1988). Perceptual plasticity and theoretical neutrality: A reply to {Jerry} {Fodor}. \emph{Philosophy of Science}, \emph{55}(2), 167--187. \url{https://doi.org/10.1086/289425}
 
 \leavevmode\hypertarget{ref-churchland1994}{}%
-Churchland, P. S., Ramachandran, V. S., \& Sejnowski, T. J. (1994). A critique of pure vision. In \emph{Large-scale neuronal theories of the brain} (pp. 23--60). The MIT Press.
+Churchland, P.
+S., Ramachandran, V.
+S., \& Sejnowski, T.
+J.
+(1994).
+A critique of pure vision.
+In C.
+Koch \& J.
+L.
+Davis (Eds.), \emph{Computational neuroscience.
+Large-scale neuronal theories of the brain} (pp.
+23--60).
+MIT Press.
 
 \leavevmode\hypertarget{ref-cole2012}{}%
-Cole, S., Balcetis, E., \& Dunning, D. (2012). Affective signals of threat increase perceived proximity: \emph{Psychological Science}. \url{https://doi.org/10.1177/0956797612446953}
+Cole, S., Balcetis, E., \& Dunning, D. (2012). Affective signals of threat increase perceived proximity. \emph{Psychological Science}. \url{https://doi.org/10.1177/0956797612446953}
 
@@
 
+\leavevmode\hypertarget{ref-dicarlo2012}{}%
+DiCarlo, J. J., Zoccolan, D., \& Rust, N. C. (2012). How does the brain solve visual object recognition? \emph{Neuron}, \emph{73}(3), 415--434. \url{https://doi.org/10.1016/j.neuron.2012.01.010}
+
 \leavevmode\hypertarget{ref-eimer2011}{}%
@@
 (2011).
-The n170 component and its links to configural face processing: A rapid neural adaptation study.
+The {N170} component and its links to configural face processing: A rapid neural adaptation study.
 \emph{Brain Research}, \emph{1376}, 76--87.
@@
 (2016).
-Cognition does not affect perception: Evaluating the evidence for ``top-down'' effects.
+Cognition does not affect perception: Evaluating the evidence for {``top-down''} effects.
 \emph{Behavioral and Brain Sciences}, \emph{39}.
@@
 \leavevmode\hypertarget{ref-fodor1984}{}%
-Fodor, J. (1984). Observation reconsidered. \emph{Philosophy of Science}, \emph{51}(1), 23--43. \url{https://doi.org/10.1086/289162}
+Fodor, J. A. (1984). Observation reconsidered. \emph{Philosophy of Science}, \emph{51}(1), 23--43. \url{https://doi.org/10.1086/289162}
 
@@
 (2002).
-Flow of activation from v1 to frontal cortex in humans.
+Flow of activation from {V1} to frontal cortex in humans.
 \emph{Experimental Brain Research}, \emph{142}(1), 139--150.
@@
 (2017).
-The role of affective evaluation in conflict adaptation: An LRP study.
+The role of affective evaluation in conflict adaptation: An {LRP} study.
 \emph{Brain and Cognition}, \emph{116}, 9--16.
@@
 (2018).
-Group-level EEG-processing pipeline for flexible single trial-based analyses including linear mixed models.
+Group-level {EEG}-processing pipeline for flexible single trial-based analyses including linear mixed models.
 \emph{Frontiers in Neuroscience}, \emph{12}.
 \url{https://doi.org/10.3389/fnins.2018.00048}
+
+\leavevmode\hypertarget{ref-ganis1996}{}%
+Ganis, G., Kutas, M., \& Sereno, M.
+I.
+(1996).
+The search for {``common sense''}: An electrophysiological study of the comprehension of words and pictures in reading.
+\emph{Journal of Cognitive Neuroscience}, \emph{8}(2), 89--106.
+\url{https://doi.org/10.1162/jocn.1996.8.2.89}
 
@@
 
+\leavevmode\hypertarget{ref-gilbert2013}{}%
+Gilbert, C. D., \& Li, W. (2013). Top-down influences on visual processing. \emph{Nature Reviews Neuroscience}, \emph{14}(5), 350--363. \url{https://doi.org/10.1038/nrn3476}
+
+\leavevmode\hypertarget{ref-goodale1992}{}%
+Goodale, M. A., \& Milner, A. D. (1992). Separate visual pathways for perception and action. \emph{Trends in Neurosciences}, \emph{15}(1), 20--25. \url{https://doi.org/10.1016/0166-2236(92)90344-8}
+
 \leavevmode\hypertarget{ref-gramfort2013}{}%
 Gramfort, A., Luessi, M., Larson, E., Engemann, D.
-A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& al.
+A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& al., et.
 (2013).
-MEG and EEG data analysis with MNE-Python.
+MEG and {EEG} data analysis with {MNE-Python}.
 \emph{Frontiers in Neuroscience}, \emph{7}.
@@
 (2009).
-See what I mean?
-An ERP study of the effect of background knowledge on novel object processing.
+See what {I} mean?
+An {ERP} study of the effect of background knowledge on novel object processing.
 \emph{Memory \& Cognition}, \emph{37}(3), 277--291.
@@
 
-\leavevmode\hypertarget{ref-haber1966}{}%
-Haber, R. N. (1966). Nature of the effect of set on perception. \emph{Psychological Review}, \emph{73}(4), 335--351. \url{https://doi.org/10.1037/h0023442}
+\leavevmode\hypertarget{ref-hirschfeld2011}{}%
+Hirschfeld, G., Zwitserlood, P., \& Dobel, C.
+(2011).
+Effects of language comprehension on visual processing -- MEG dissociates early perceptual and late N400 effects.
+\emph{Brain and Language}, \emph{116}(2), 91--96.
+\url{https://doi.org/10.1016/j.bandl.2010.07.002}
+
+\leavevmode\hypertarget{ref-hochstein2002}{}%
+Hochstein, S., \& Ahissar, M.
+(2002).
+View from the top: Hierarchies and reverse hierarchies in the visual system.
+\emph{Neuron}, \emph{36}(5), 791--804.
+\url{https://doi.org/10.1016/S0896-6273(02)01091-7}
+
+\leavevmode\hypertarget{ref-hsieh2010}{}%
+Hsieh, P.-J., Vul, E., \& Kanwisher, N.
+(2010).
+Recognition alters the spatial pattern of {fMRI} activation in early retinotopic cortex.
+\emph{Journal of Neurophysiology}, \emph{103}(3), 1501--1507.
+\url{https://doi.org/10.1152/jn.00812.2009}
 
@@
 (2010).
-Misaligning face halves increases and delays the n170 specifically for upright faces: Implications for the nature of early face representations.
+Misaligning face halves increases and delays the {N170} specifically for upright faces: Implications for the nature of early face representations.
 \emph{Brain Research}, \emph{1318}, 96--109.
@@
 (2011).
-Thirty years and counting: Finding meaning in the N400 component of the event-related brain potential (ERP).
+Thirty years and counting: Finding meaning in the {N400} component of the event-related brain potential ({ERP}).
 \emph{Annual Review of Psychology}, \emph{62}, 621--647.
@@
 (2017).
-lmerTest package: Tests in linear mixed effects models.
+{lmerTest} package: Tests in linear mixed effects models.
 \emph{Journal of Statistical Software}, \emph{82}(13), 1--26.
@@
 (2008).
-A cortical network for semantics: (De)constructing the N400.
+A cortical network for semantics: (De)constructing the {N400}.
 \emph{Nature Reviews Neuroscience}, \emph{9}(12), 920--933.
@@
 \leavevmode\hypertarget{ref-luck2014}{}%
-Luck, S. J. (2014). Overview of common erp components. In \emph{An introduction to the event-related potential technique} (2nd ed., pp. 71--118). MIT Press.
+Luck, S. J. (2014). Overview of common ERP components. In \emph{An introduction to the event-related potential technique} (2nd ed., pp. 71--118). MIT Press.
 
@@
 
-\leavevmode\hypertarget{ref-lupyan2012}{}%
-Lupyan, G. (2012). Linguistically modulated perception and cognition: The label-feedback hypothesis. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00054}
-
 \leavevmode\hypertarget{ref-lupyan2015}{}%
@@
 
-\leavevmode\hypertarget{ref-lupyan2020}{}%
-Lupyan, G., Abdel Rahman, R., Boroditsky, L., \& Clark, A.
-(2020).
-Effects of language on visual perception.
-\emph{Trends in Cognitive Sciences}, \emph{24}(11), 930--944.
-\url{https://doi.org/10.1016/j.tics.2020.08.005}
+\leavevmode\hypertarget{ref-lupyan2012}{}%
+Lupyan, G. (2012). Linguistically modulated perception and cognition: The label-feedback hypothesis. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00054}
 
@@
 Oxford University Press.
-\url{10.1093/acprof:oso/9780198738916.003.0002}
+\url{https://doi.org/10.1093/acprof:oso/9780198738916.003.0002}
+
+\leavevmode\hypertarget{ref-maier2019}{}%
+Maier, M., \& Abdel Rahman, R.
+(2019).
+No matter how: Top-down effects of verbal and semantic category knowledge on early visual perception.
+\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{19}(4), 859--876.
+\url{https://doi.org/10.3758/s13415-018-00679-8}
 
@@
 Does the semantic content of verbal categories influence categorical perception?
-An ERP study.
+An {ERP} study.
 \emph{Brain and Cognition}, \emph{91}, 1--10.
 \url{https://doi.org/10.1016/j.bandc.2014.07.008}
-
-\leavevmode\hypertarget{ref-maier2019}{}%
-Maier, M., \& Rahman, R.
-A.
-(2019).
-No matter how: Top-down effects of verbal and semantic category knowledge on early visual perception.
-\emph{Cognitive, Affective, \& Behavioral Neuroscience}, \emph{19}(4), 859--876.
-\url{https://doi.org/10.3758/s13415-018-00679-8}
 
@@
 
+\leavevmode\hypertarget{ref-marr1982}{}%
+Marr, D. (1982). \emph{Vision: A computational investigation into the human representation and processing of visual information}. W.H. Freeman.
+
 \leavevmode\hypertarget{ref-matuschek2017}{}%
@@
 (2017).
-Balancing Type I error and power in linear mixed models.
+Balancing {Type I} error and power in linear mixed models.
 \emph{Journal of Memory and Language}, \emph{94}, 305--315.
 \url{https://doi.org/10.1016/j.jml.2017.01.001}
+
+\leavevmode\hypertarget{ref-mitchell2020}{}%
+Mitchell, M. (2020). On crashing the barrier of meaning in artificial intelligence. \emph{AI Magazine}, \emph{41}(2), 86--92. \url{https://doi.org/10.1609/aimag.v41i2.5259}
 
@@
 \leavevmode\hypertarget{ref-oldfield1971}{}%
-Oldfield, R. C. (1971). The assessment and analysis of handedness: The Edinburgh inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}
+Oldfield, R. C. (1971). The assessment and analysis of handedness: The {Edinburgh} inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}
+
+\leavevmode\hypertarget{ref-panichello2013}{}%
+Panichello, M. F., Cheung, O. S., \& Bar, M. (2013). Predictive feedback and conscious visual experience. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00620}
 
@@
 (2016).
-Emotion facilitates perception and potentiates the perceptual benefits of attention: \emph{Psychological Science}.
+Emotion facilitates perception and potentiates the perceptual benefits of attention.
+\emph{Psychological Science}.
 \url{https://journals.sagepub.com/doi/10.1111/j.1467-9280.2006.01701.x}
+
+\leavevmode\hypertarget{ref-pratt2011}{}%
+Pratt, H. (2011). Sensory ERP components. In E. S. Kappenman \& S. J. Luck (Eds.), \emph{The oxford handbook of event-related potential components} (pp. 89--114). Oxford University Press.
 
@@
 (1999).
-Is vision continuous with cognition?: The case for cognitive impenetrability of visual perception.
+Is vision continuous with cognition?
+The case for cognitive impenetrability of visual perception.
 \emph{Behavioral and Brain Sciences}, \emph{22}(3), 341--365.
 \url{https://doi.org/10.1017/S0140525X99002022}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
@@
 (2018).
-Modelling the N400 brain potential as change in a probabilistic representation of meaning.
+Modelling the {N400} brain potential as change in a probabilistic representation of meaning.
 \emph{Nature Human Behaviour}, \emph{2}(9), 693--705.
@@
 
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
 \leavevmode\hypertarget{ref-rossion1999}{}%
-Rossion, B., Delvenne, J.
-F., Debatisse, D., Goffaux, V., Bruyer, R., Crommelinck, M., \& Guérit, J.
-M.
+Rossion, B., Delvenne, J.-F., Debatisse, D., Goffaux, V., Bruyer, R., Crommelinck, M., \& Guérit, J.-M.
 (1999).
@@
 (2011).
-The N170: Understanding the time course of face perception in the human brain.
+The {N170}: Understanding the time course of face perception in the human brain.
 In E.
@@
 J.
-Luck (Eds.), \emph{The Oxford handbook of event-related potential components} (pp.
+Luck (Eds.), \emph{The {Oxford} handbook of event-related potential components} (pp.
 115--142).
@@
 Visual expertise with nonface objects leads to competition with the early perceptual processing of faces in the human occipitotemporal cortex.
-\emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{101}(40), 14521--14526.
+\emph{Proceedings of the National Academy of Sciences}, \emph{101}(40), 14521--14526.
 \url{https://doi.org/10.1073/pnas.0405613101}
@@
 
+\leavevmode\hypertarget{ref-supp2005}{}%
+Supp, G.
+G., Schlögl, A., Fiebach, C.
+J., Gunter, T.
+C., Vigliocco, G., Pfurtscheller, G., \& Petsche, H.
+(2005).
+Semantic memory retrieval: Cortical couplings in object recognition in the N400 window.
+\emph{European Journal of Neuroscience}, \emph{21}(4), 1139--1143.
+https://doi.org/\url{https://doi.org/10.1111/j.1460-9568.2005.03906.x}
+
 \leavevmode\hypertarget{ref-tanaka2001}{}%
@@
 \leavevmode\hypertarget{ref-taylor2002}{}%
-Taylor, M. J. (2002). Non-spatial attentional effects on p1. \emph{Clinical Neurophysiology}, \emph{113}(12), 1903--1908. \url{https://doi.org/10.1016/S1388-2457(02)00309-7}
-
-\leavevmode\hypertarget{ref-thierry2016}{}%
-Thierry, G. (2016). Neurolinguistic relativity: How language flexes human perception and cognition. \emph{Language Learning}, \emph{66}(3), 690--713. \url{https://doi.org/10.1111/lang.12186}
+Taylor, M. J. (2002). Non-spatial attentional effects on {P1}. \emph{Clinical Neurophysiology}, \emph{113}(12), 1903--1908. \url{https://doi.org/10.1016/S1388-2457(02)00309-7}
+
+\leavevmode\hypertarget{ref-teufel2017}{}%
+Teufel, C., \& Nanay, B.
+(2017).
+How to (and how not to) think about top-down influences on visual perception.
+\emph{Consciousness and Cognition}, \emph{47}, 17--25.
+\url{https://doi.org/10.1016/j.concog.2016.05.008}
 
@@
 \leavevmode\hypertarget{ref-R-buildmer}{}%
-Voeten, C. C. (2020). \emph{buildmer: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
+Voeten, C. C. (2020). \emph{{buildmer}: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
 
 \leavevmode\hypertarget{ref-vogel2000}{}%
-Vogel, E. K., \& Luck, S. J. (2000). The visual n1 component as an index of a discrimination process. \emph{Psychophysiology}, \emph{37}(2), 190--203.
+Vogel, E. K., \& Luck, S. J. (2000). The visual {N1} component as an index of a discrimination process. \emph{Psychophysiology}, \emph{37}(2), 190--203.
 
@@
 
+\leavevmode\hypertarget{ref-wyatte2014}{}%
+Wyatte, D., Jilk, D.
+J., \& O'Reilly, R.
+C.
+(2014).
+Early recurrent feedback facilitates visual object recognition under challenging conditions.
+\emph{Frontiers in Psychology}, \emph{5}, 674.
+\url{https://doi.org/10.3389/fpsyg.2014.00674}
+
+\leavevmode\hypertarget{ref-yuille2006}{}%
+Yuille, A., \& Kersten, D. (2006). Vision as bayesian inference: Analysis by synthesis? \emph{Trends in Cognitive Sciences}, \emph{10}(7), 301--308. \url{https://doi.org/10.1016/j.tics.2006.05.002}
+
+\end{CSLReferences}
+
 \end{document}

### 2021-01-05 analysis/master_thesis.Rmd
add discussion section + rmd for master thesis

---
title: "This page and the next page should be removed"
shorttitle:  ""

author: 
  - name        : ""
    affiliation : ""

affiliation:
  - id          : ""
    institution : ""

bibliography      : "manuscript_files/r-references.bib"
zotero            : "aha"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
numbersections    : true

csl               : "manuscript_files/apa.csl"
documentclass     : "apa7"
classoption       : "doc,12pt,twoside"
mainfont          : "Times New Roman"
output:
  papaja::apa6_pdf:
    latex_engine:   "xelatex"

header-includes:
  - \setcounter{tocdepth}{2}
  - \raggedbottom
  - \linespread{1.5}
  - \geometry{a4paper,margin=25mm}
  - \fancyhead{}
  - \fancyheadoffset[RO,LE]{0pt}
  - \fancyhead[RO,LE]{\thepage}
  - \fancyhead[LO,RE]{Semantic Knowledge and Unfamiliar Objects}
  # - \addtolength\oddsidemargin {0.5cm}
  # - \addtolength\evensidemargin {-0.5cm}
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\doublespacing}
  # - \AtBeginEnvironment{lltable}{\doublespacing}
  # - \AtBeginEnvironment{tablenotes}{\doublespacing}
  # - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1,scriptsize}}
  - \usepackage[all]{nowidow}
  - \usepackage[bottom]{footmisc}
  - \interfootnotelinepenalty=10000
  - \usepackage[export]{adjustbox}
---

<!-- Empty page -->
\clearpage\mbox{}\thispagestyle{empty}\clearpage

<!-- Title page -->
\thispagestyle{empty}
\begin{center}
\vspace*{10mm}
\textbf{Event-Related Potentials of the Semantically Informed}\\
\textbf{Perception of Unfamiliar Objects}\\
\vspace*{5mm}
\begin{figure}[h]
\begin{center}
\includegraphics[width=!,totalheight=!,scale=0.25]{master_thesis_files/hu_logo}
\end{center}
\end{figure}
{\setstretch{1.5}
Masterarbeit\\
an der\\
Humboldt-Universität zu Berlin\\
zur Erlangung des akademischen Grades \\
Master of Science (M.Sc.)\\
im Fach Psychologie\\
\vspace*{25mm}
}
\end{center}
\begin{flushleft}
{\setstretch{1.5}
\begin{tabular}{ll}
Vorgelegt von:&\textbf{Alexander Enge}\\
&geb. am 09.11.1996 in Räckelwitz\\
&Matrikelnummer 581331\\
Unter Betreuung von:&Prof. Dr. Rasha Abdel Rahman (Humboldt-Universität zu Berlin)\\
&Prof. Dr. Franziska Süß (Fachhochschule des Mittelstands)\\
&\\
Berlin, den 21.01.2021&\\
\end{tabular}
}
\end{flushleft}

<!-- Empty page -->
\clearpage\mbox{}\thispagestyle{empty}\clearpage

<!-- Acknowledgement -->
\thispagestyle{empty}

\begin{center}\textbf{Acknowledgment}\end{center}

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor danke frederik invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

<!-- Empty page -->
\clearpage\mbox{}\thispagestyle{empty}\clearpage

<!-- Table of contents -->
\thispagestyle{empty}
\begin{flushleft}
{\setstretch{1.0}
\tableofcontents
}
\end{flushleft}

<!-- Empty page -->
\clearpage\mbox{}\thispagestyle{empty}\clearpage

<!-- Abstract -->
\setcounter{page}{1}

# Abstract {.unnumbered}

Does our perception of an object change as soon as we discover what it is for? This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it pertains to the long-standing debate around the (im)penetrability of perception by "higher" cognitive capacities. In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with valid information about their function---leading to semantically informed perception---or together with invalid information---resulting in naive perception. We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of perceiving objects differed from one another. We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component. When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place. We replicated these novel findings in an independent sample (*n* = 24). Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).

<!-- Acutal paper -->
\newpage

# Introduction

```{r manuscript, child="manuscript.Rmd"}
```

### 2021-01-05 analysis/master_thesis.tex
add discussion section + rmd for master thesis

--- 2021-01-05 analysis/manuscript.tex
@@
   english,
-  man,floatsintext]{apa7}
+  doc,12pt,twoside,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \setmainfont[]{Times New Roman}
 \fi
@@
 \hypersetup{
-  pdfauthor={Alexander Enge1,2, Franziska Süß3, \& Rasha Abdel Rahman1},
+  pdftitle={This page and the next page should be removed},
   pdflang={en-EN},
-  pdfkeywords={objects, semantic knowledge, visual perception, event-related potentials},
   hidelinks,
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
@@
 \makeatother
-\shorttitle{Semantic Knowledge and Unfamiliar Objects}
-\keywords{objects, semantic knowledge, visual perception, event-related potentials\newline\indent Word count: }
+\shorttitle{}
 \usepackage{csquotes}
-\geometry{a4paper}
-\fancyheadoffset[R,L]{0pt}
+\setcounter{tocdepth}{2}
 \raggedbottom
+\linespread{1.5}
+\geometry{a4paper,margin=25mm}
+\fancyhead{}
+\fancyheadoffset[RO,LE]{0pt}
+\fancyhead[RO,LE]{\thepage}
+\fancyhead[LO,RE]{Semantic Knowledge and Unfamiliar Objects}
 \usepackage{setspace}
@@
 
-\title{Event-Related Potentials of the Semantically Informed\\
-Perception of Unfamiliar Objects}
-\author{Alexander Enge\textsuperscript{1,2}, Franziska Süß\textsuperscript{3}, \& Rasha Abdel Rahman\textsuperscript{1}}
+\title{This page and the next page should be removed}
+\author{\textsuperscript{}}
 \date{}
 
-\authornote{
-
-\addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
-
-\addORCIDlink{Rasha Abdel Rahman}{0000-0002-8438-1570}
-
-The preprocessed data and code for this study are openly available at \url{https://osf.io/uksbc/}.
-
-We have no conflict of interest to disclose.
-
-Correspondence concerning this article should be addressed to Rasha Abdel Rahman, Rudower Chaussee 18, 12489 Berlin.
-E-mail: \href{mailto:rasha.abdel.rahman@hu-berlin.de}{\nolinkurl{rasha.abdel.rahman@hu-berlin.de}}
-
+\affiliation{\vspace{0.5cm}\textsuperscript{} }
+
+\begin{document}
+\maketitle
+
+\clearpage
+
+\mbox{}\thispagestyle{empty}\clearpage
+
+\thispagestyle{empty}
+\begin{center}
+\vspace*{10mm}
+\textbf{Event-Related Potentials of the Semantically Informed}\\
+\textbf{Perception of Unfamiliar Objects}\\
+\vspace*{5mm}
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=!,totalheight=!,scale=0.25]{master_thesis_files/hu_logo}
+\end{center}
+\end{figure}
+{\setstretch{1.5}
+Masterarbeit\\
+an der\\
+Humboldt-Universität zu Berlin\\
+zur Erlangung des akademischen Grades \\
+Master of Science (M.Sc.)\\
+im Fach Psychologie\\
+\vspace*{25mm}
 }
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Humboldt-Universität zu Berlin\\\textsuperscript{2} Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany\\\textsuperscript{3} Fachhochschule des Mittelstands, Bamberg, Germany}
-
-\abstract{
+\end{center}
+\begin{flushleft}
+{\setstretch{1.5}
+\begin{tabular}{ll}
+Vorgelegt von:&\textbf{Alexander Enge}\\
+&geb. am 09.11.1996 in Räckelwitz\\
+&Matrikelnummer 581331\\
+Unter Betreuung von:&Prof. Dr. Rasha Abdel Rahman (Humboldt-Universität zu Berlin)\\
+&Prof. Dr. Franziska Süß (Fachhochschule des Mittelstands)\\
+&\\
+Berlin, den 21.01.2021&\\
+\end{tabular}
+}
+\end{flushleft}
+
+\clearpage
+
+\mbox{}\thispagestyle{empty}\clearpage
+
+\thispagestyle{empty}
+
+\begin{center}\textbf{Acknowledgment}\end{center}
+
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor danke frederik invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+
+\clearpage
+
+\mbox{}\thispagestyle{empty}\clearpage
+
+\thispagestyle{empty}
+\begin{flushleft}
+{\setstretch{1.0}
+\tableofcontents
+}
+\end{flushleft}
+
+\clearpage
+
+\mbox{}\thispagestyle{empty}\clearpage
+
+\setcounter{page}{1}
+
+\hypertarget{abstract}{%
+\section*{Abstract}\label{abstract}}
+\addcontentsline{toc}{section}{Abstract}
+
 Does our perception of an object change as soon as we discover what it is for?
@@
 Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
-}
-
-\begin{document}
-\maketitle
+
+\newpage
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/exp1-plot-1}
+{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp1-plot-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/exp2-plot-1}
+{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp2-plot-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/joint-plot-1}
+{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/joint-plot-1}
 

### 2021-01-07 analysis/appendix.tex
proofread + apa7 figure captions

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Appendix},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{}
\usepackage{csquotes}
\AtBeginEnvironment{tabular}{\doublespacing}
\usepackage[export]{adjustbox}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Appendix}
\author{\textsuperscript{}}
\date{}

\affiliation{\vspace{0.5cm}\textsuperscript{} }

\begin{document}
\maketitle

\hypertarget{appendix}{%
\section*{Appendix}\label{appendix}}
\addcontentsline{toc}{section}{Appendix}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\begin{center}
\begin{ThreePartTable}

\begin{longtable}{llll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:appendix}Unfamiliar Object Stimuli\smallskip}\\
\toprule
 & \# & Matching keywords & Non-matching keywords\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:appendix} continued}}\\
\toprule
 & \# & Matching keywords & Non-matching keywords\\
\midrule
\endhead
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/1.png} & 1 & elektrische Spannung prüfen & Makkaroni formen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/2.png} & 2 & Makkaroni formen & Kuh vom Zaun abhalten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/3.png} & 3 & Knochen sägen & Streckenmaß Sonnenlicht nutzen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/4.png} & 4 & Unkraut jäten & Uhr mit Wärme betreiben\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/5.png} & 5 & Mausefalle zuschnappen & Brillenglas zuschneiden\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/6.png} & 6 & Goldmünzen wiegen & Farbe vom Fenster abschleifen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/7.png} & 7 & Knie fixieren & Buchstaben tippen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/8.png} & 8 & Eierkarton pressen & Tabak zermahlen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/9.png} & 9 & Baum erklettern & Rotation Ladung erzeugen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/10.png} & 10 & Buchstaben tippen & Pferdehuf Halt geben\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/11.png} & 11 & Akkordeon spielen & Seil schneiden\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/12.png} & 12 & Körper trainieren & Buch offen halten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/13.png} & 13 & Farbe vom Fenster abschleifen & von Hand zentrifugieren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/14.png} & 14 & Außenbereich heizen & Rasierklinge schärfen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/15.png} & 15 & Pflanzenteile vergrößern & Katzenklo sich selbst reinigen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/16.png} & 16 & Krawatten aufhängen & Zeichnungen vermessen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/17.png} & 17 & Schallplatte abtasten & Ball katapultieren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/18.png} & 18 & Glas schneiden & Eier wiegen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/19.png} & 19 & Briketts pressen & Narkosemittel abgeben\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/20.png} & 20 & Orgelton erzeugen & Bandage rollen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/21.png} & 21 & Spannung erzeugen & Fußstütze reiten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/22.png} & 22 & Narkosemittel abgeben & Nüsse aufbrechen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/23.png} & 23 & Bandage rollen & Schnee rodeln\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/24.png} & 24 & Weinfass Loch einschlagen & Tier einfangen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/25.png} & 25 & Flaschenkorken einführen & Pferd im Moor laufen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/26.png} & 26 & Automat Eier ausbrüten & Windgeschwindigkeit messen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/27.png} & 27 & Korngarbe greifen & Treibhaus heizen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/28.png} & 28 & Brief wiegen & Korngarbe greifen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/29.png} & 29 & Löcher bohren & Sonnenlicht Intensität messen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/30.png} & 30 & Angelschnur kurbeln & Glaskörper musizieren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/31.png} & 31 & Kurven malen & Nussöl pressen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/32.png} & 32 & Radiofrequenz einstellen & Erektion helfen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/33.png} & 33 & Zäpfchen pressen & Unkraut jäten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/34.png} & 34 & Fass öffnen & Pflanzenteile vergrößern\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/35.png} & 35 & Bergbaustollen beleuchten & Knie fixieren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/36.png} & 36 & Kuh vom Zaun abhalten & Radiofrequenz einstellen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/37.png} & 37 & Saatgut gleichmäßig aussäen & Fass öffnen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/38.png} & 38 & Flaschen trocknen & Bleistift anspitzen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/39.png} & 39 & Uhr mit Wärme betreiben & Körper untersuchen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/40.png} & 40 & Tonpott trommeln & Piano stimmen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/41.png} & 41 & Sprengstoffexplosion auslösen & Fisch wiegen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/42.png} & 42 & Pferdehuf Halt geben & Zäpfchen pressen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/43.png} & 43 & Bleistift anspitzen & Angel Köder markieren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/44.png} & 44 & Nussöl pressen & Zeichen einbrennen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/45.png} & 45 & Rasierklinge schärfen & Kurven malen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/46.png} & 46 & heiße Platten anheben & Kleidung im Eimer waschen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/47.png} & 47 & Film aufspulen & Mund offen halten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/48.png} & 48 & Waffe entflammen & Uhrzeit anzeigen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/49.png} & 49 & Mikroskop-Proben schneiden & heiße Platten anheben\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/50.png} & 50 & Glaskörper musizieren & Kork flach pressen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/51.png} & 51 & Dampf zerstäuben & Buch binden\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/52.png} & 52 & Mandeln operieren & Film aufspulen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/53.png} & 53 & Toastbrot rösten & Autobatterie Spannung testen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/54.png} & 54 & Fußstütze reiten & Stromstärke messen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/55.png} & 55 & Türgelenk Feuer überstehen & Botschaft telegrafieren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/56.png} & 56 & Schnee rodeln & Dampf zerstäuben\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/57.png} & 57 & Nüsse aufbrechen & Ziegelsteine formen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/58.png} & 58 & Radiergummi mit Strom betreiben & Münzen aufbewahren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/59.png} & 59 & Treibhaus heizen & Messer schleifen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/60.png} & 60 & Botschaft telegrafieren & Toastbrot rösten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/61.png} & 61 & Angel Köder markieren & Baum erklettern\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/62.png} & 62 & Katzenklo sich selbst reinigen & Tankfüllstand messen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/63.png} & 63 & Körper untersuchen & Schuhe auf Eis laufen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/64.png} & 64 & Brillenglas zuschneiden & Saatgut gleichmäßig aussäen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/65.png} & 65 & Draht wickeln & Bergbaustollen beleuchten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/66.png} & 66 & Buch offen halten & Sprengstoffexplosion auslösen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/67.png} & 67 & Feldanbau häckseln & Draht wickeln\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/68.png} & 68 & Schnurlot absenken & Korken formen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/69.png} & 69 & Sternenbilder vermessen & Schnurlot absenken\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/70.png} & 70 & Nachricht morsen & Feldanbau häckseln\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/71.png} & 71 & Musikgerät stampfen & Goldmünzen wiegen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/72.png} & 72 & Schuhe auf Eis laufen & Geschwindigkeit ermitteln\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/73.png} & 73 & Geschwindigkeit ermitteln & Mausefalle zuschnappen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/74.png} & 74 & Zeichen einbrennen & Luftdruck messen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/75.png} & 75 & Tabak zermahlen & Flaschen trocknen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/76.png} & 76 & Stromstärke messen & Mandeln operieren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/77.png} & 77 & Tier einfangen & Maiskolben entkörnen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/78.png} & 78 & Messer schleifen & Schritte vergrößern\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/79.png} & 79 & Leierkasten klingen & Fass anheben\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/80.png} & 80 & Buch binden & Löcher bohren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/81.png} & 81 & Kork flach pressen & Elektroschock spielen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/82.png} & 82 & Tabletten zerteilen & Blumentopf sich selbst wässern\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/83.png} & 83 & Fass anheben & Mikroskop-Proben schneiden\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/84.png} & 84 & Pferd im Moor laufen & Luft abpumpen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/85.png} & 85 & altes Ritual hacken & Spannung erzeugen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/86.png} & 86 & Kleidung im Eimer waschen & Türgelenk Feuer überstehen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/87.png} & 87 & Maiskolben entkörnen & Brief wiegen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/88.png} & 88 & Ball katapultieren & Radiergummi mit Strom betreiben\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/89.png} & 89 & Zeichnungen vermessen & Brenner löten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/90.png} & 90 & Elektroschock spielen & Weinfass Loch einschlagen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/91.png} & 91 & Lieferungen abzählen & Außenbereich heizen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/92.png} & 92 & Rotation Ladung erzeugen & Musikgerät stampfen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/93.png} & 93 & Herz durch Maschine ersetzen & Kerzen löschen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/94.png} & 94 & Seil schneiden & Akkordeon spielen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/95.png} & 95 & Fisch wiegen & Herz durch Maschine ersetzen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/96.png} & 96 & Kerzen löschen & Körper trainieren\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/97.png} & 97 & Korken formen & Sternenbilder vermessen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/98.png} & 98 & Erektion helfen & Waffe werfen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/99.png} & 99 & Streckenmaß Sonnenlicht nutzen & Kartoffeln stampfen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/100.png} & 100 & Luftdruck messen & Knochen sägen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/101.png} & 101 & Piano stimmen & Eierkarton pressen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/102.png} & 102 & von Hand zentrifugieren & Lieferungen abzählen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/103.png} & 103 & Kartoffeln stampfen & Nachricht morsen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/104.png} & 104 & Waffe werfen & elektrische Spannung prüfen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/105.png} & 105 & Tankfüllstand messen & Tonpott trommeln\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/106.png} & 106 & Uhrzeit anzeigen & altes Ritual hacken\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/107.png} & 107 & Windgeschwindigkeit messen & Waffe entflammen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/108.png} & 108 & Schlüsselloch stanzen & Automat Eier ausbrüten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/109.png} & 109 & Ziegelsteine formen & Schallplatte abtasten\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/110.png} & 110 & Becher Schall auffangen & Schlüsselloch stanzen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/111.png} & 111 & Luft abpumpen & Briketts pressen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/112.png} & 112 & Mund offen halten & Orgelton erzeugen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/113.png} & 113 & Autobatterie Spannung testen & Becher Schall auffangen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/114.png} & 114 & Sonnenlicht Intensität messen & Krawatten aufhängen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/115.png} & 115 & Kutschrad anschließen & Angelschnur kurbeln\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/116.png} & 116 & Eier wiegen & Leierkasten klingen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/117.png} & 117 & Blumentopf sich selbst wässern & Glas schneiden\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/118.png} & 118 & Schritte vergrößern & Tabletten zerteilen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/119.png} & 119 & Münzen aufbewahren & Kutschrad anschließen\\
\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/120.png} & 120 & Brenner löten & Flaschenkorken einführen einführen\\
\bottomrule
\end{longtable}

\end{ThreePartTable}
\end{center}

\end{document}

### 2021-01-07 analysis/manuscript.Rmd
proofread + apa7 figure captions

@@
 classoption       : "man"
-output:
+output            :
   papaja::apa6_pdf:
-    latex_engine:   "xelatex"
+    latex_engine  : "xelatex"
 
@@
   - \AtBeginEnvironment{tabular}{\doublespacing}
-  # - \AtBeginEnvironment{lltable}{\doublespacing}
-  # - \AtBeginEnvironment{tablenotes}{\doublespacing}
-  # - \captionsetup[table]{font={stretch=1.5}}
-  - \captionsetup[figure]{font={stretch=1,scriptsize}}
+  - \captionsetup[table]{font={stretch=1.5}}
+  - \captionsetup[figure]{font={stretch=1.5}}
   - \usepackage[all]{nowidow}
@@
   - \interfootnotelinepenalty=10000
-  - \usepackage[export]{adjustbox}
 ---
@@
 In this study, we presented participants with unfamiliar objects which were preceded either by valid information about their function, leading to semantically informed perception, or by misleading information, leading to naive perception.
-Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temopral resoulation of event-related brain potentials (ERPs).
+Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temporal resolution of event-related brain potentials (ERPs).
 
 The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world should be thought of as an encapsulated module whose processing is determined solely by the visual input reaching our retina.
-According to this view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @fodor1984; @machery2015; @pylyshyn1999].
+This debate revolves around the question of whether or not our perception of the (visual) world is "cognitively impenetrable" or, in other words, determined solely by the visual input reaching our retina.
+According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @fodor1984; @pylyshyn1999].
 Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @goodale1992; @marr1982].
 
-Conversely, this position is challenged by the view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1988; @churchland1994; @lupyan2015; @teufel2017].
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas [e.g., visual areas V1 and V2; @bullier2001; @gilbert2013], as well as behavioral evidence, have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
-The reverse hierarchy theory [@ahissar2004; @hochstein2002], for instance, assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
+This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1988; @churchland1994; @lupyan2015; @teufel2017].
+The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas [e.g., visual areas V1 and V2\; @bullier2001; @gilbert2013]---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+For instance, the reverse hierarchy theory [@ahissar2004; @hochstein2002] assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
 Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
-Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
+Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
 Finally, an active role of top-down influences is also promoted by theories of vision falling under the umbrella of Bayesian inference and predictive coding [e.g., @lupyan2015; @panichello2013; @yuille2006].
@@
 Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition [for review, see @collins2014; @vetter2014].
-These aspects of cognition may include transient states such as emotions [e.g., @phelps2016; @bocanegra2009] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @lin1997; @weller2019].
-Despite this wealth of theory and empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
-
-One productive way to investigate top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+These aspects of cognition may include transient states such as emotions [e.g., @bocanegra2009; @phelps2016] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @lin1997; @weller2019].
+Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
+
+One productive way to investigate the top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
 This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
@@
 It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri [@dirusso2001; @foxe2002; @mangun1995].
-The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus [e.g., size, luminance, and contrast; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception.
-For instance, it is enhanced when participants pay attention to the spatial location [@luck2000; @mangun1995; @mangun1991] or certain non-spatial features [@taylor2002] of the stimulus.
+The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus [e.g., size, luminance, and contrast\; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated view of visual perception.
+It is well-established that the P1 is enhanced when participants pay attention to the spatial location of a stimulus [@luck2000; @mangun1995; @mangun1991] but there is also more recent evidence for higher-level cognitive influences that go beyond spatial attention (see below).
 
@@
 Just as the P1, it is influenced by visual parameters of the stimulus [@johannes1995] and by selective attention, especially when participants are required to discriminate between different visual stimuli [@vogel2000; @mangun1991].
-Importantly, the N170 is enlarged (i.e., more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g., birds, dogs, or cars; @gauthier2003a; @tanaka2001].
+The N170 is enlarged (i.e., more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g., birds, dogs, or cars\; @gauthier2003a; @tanaka2001].
 This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as the holistic configuration of these features [@eimer2011; @jacques2010; @rossion1999; @sagiv2001].
-Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimulus.
+Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these capacities having an influence on higher-level, holistic perception of the visual stimulus.
 
@@
 
-Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
+Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge about visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
 Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing.
@@
 After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information.
-In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this has not been the case.
+In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this had not been the case.
 Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
-Interestingly, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects.
+Interestingly, the ERPs in the in-depth knowledge condition even were qualitatively similar to those for untrained but well-known objects.
 The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
 Here, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
-This can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.
+This can be taken as further evidence for an influence of semantic knowledge on the early visual perception of unfamiliar objects.
 
@@
 In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
-When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images of objects than for perceptually-trained images of objects.
-As before, these effects of perceiving objects in a semantically informed way seems to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
+When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images than for perceptually-trained images.
+As before, these effects of perceiving objects in a semantically informed way seem to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
 This alternative approach further corroborates an early influence of semantic information on the visual perception of objects.
@@
 The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day [@abdelrahman2008; @maier2014; @maier2019] or were spread out across multiple days or weeks [@rossion2002; @rossion2004].
-While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three conceptual questions unresolved.
-
-The first question is if we can detect any electrophysiological correlates of semantic insight, that is, the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on).
+While experimental designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they leave at least three conceptual questions unresolved.
+
+The first question is if we can detect any electrophysiological correlates of *semantic insight*, that is, the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on).
 The second question is how much learning is actually necessary before reliable top-down effects of knowledge on ERP amplitudes can be obtained: Does it actually take dozens of repetitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
-By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we hope to provide tentative answers to all three of these questions.
+The third and closely related question is about the nature of the effects of knowledge on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
+By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we were able to provide tentative answers to all three of these questions.
 
@@
 Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
-These keywords could either correctly describe the typcial function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could mislead participants by describing the function of a different object, thus keeping the perception of the object semantically naive.
+These keywords could either correctly describe the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could mislead participants by describing the function of a different object, thus keeping the perception of the object semantically naive.
 During this second part, we were able measure the online influence of semantic insight on object-evoked ERPs as it happened.
@@
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords and objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
+This assignment of keywords to objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
@@
 The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
 
-(ref:figure-1-caption) Procedure and results of Experiment 1.
-*(A)* In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+(ref:figure-1-caption) Procedure and Results of Experiment 1\smallskip
+
+<!--
+
+The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
+Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
+
+\bigskip\small\emph{Note.} 
+(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
 In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
 In the post-insight part, the same objects were presented again without the keywords.
-*(B)* ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
+(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
 Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
 Ampl.
-= amplitude.\newline\**p* \< .05.
-\*\**p* \< .01.
-\*\*\**p* \< .001.
+= amplitude.\newline
+*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.
+
+-->
 
@@
     # Conditions
-    annotate("text", x = -72, y = 7.9, label = "Objects classified according\nto conditions in Part II", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
+    annotate("text", x = -72, y = 7.9, label = "Objects classified according\nto conditions in the insight part", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
     # PART III
@@
     # Conditions
-    annotate("text", x = 72, y = 7.9, label = "Objects classified according\nto conditions in Part II", size = 10 / .pt, family = "Helvetica", lineheight = 1) +    
+    annotate("text", x = 72, y = 7.9, label = "Objects classified according\nto conditions in the insight part", size = 10 / .pt, family = "Helvetica", lineheight = 1) +    
     theme_void()
@@
         #     data = data_plot %>% filter(.time >= start & .time <= stop) %>%
-        #       group_by(.time) %>% summarise(ymin = min(roi), ymax = max(roi)),
+        #       group_by(.time) %>% summarize(ymin = min(roi), ymax = max(roi)),
         #     aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
@@
 
-# Creata a combined legend and colorbar
+# Create a combined legend and colorbar
 plot_legends_erps <- function(direction) {
@@
 During the recording, electrode impedance was kept below 5 kΩ.
-An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1,000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
-
-Offline, the data were preprocessed using the MNE software [Version 0.21.0; @gramfort2013] in Python [Version 3.8.5; @vanrossum2009].
+An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
+
+Offline, the data were preprocessed using the MNE software [Version 0.21.0\; @gramfort2013] in Python [Version 3.8.5\; @vanrossum2009].
 First, all scalp electrodes were re-referenced to the common average.
@@
 This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see scalp topographies in Figure \@ref(fig:exp1-plot)B).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see the scalp topographies in Figure \@ref(fig:exp1-plot)B).
 
@@
 
-First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in the pre-insight part (i.e., before any keywords were presented).
+First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all further analyses those objects which participants classified as being known to them in the pre-insight part (i.e., before any keywords were presented).
 This led to the exclusion of an average of `r format(round(stims_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
@@
 This was the case for an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occurr---the same assignment was used to analyze the data from the other two parts.
+Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
 This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).
@@
 For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
-First, they can account not only for the non-independence of data points coming from the same participant but also simultaneously for the non-independence of data points coming from the same item.
+First, they can account not only for the non-independence of data points coming from the same participant, but also simultaneously for the non-independence of data points coming from the same item.
 In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
 Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable in designs where the assignment of trials to conditions is (co-)determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone [e.g., @fröber2017].
+Such a situation is inevitable in designs where the assignment of trials to conditions is co-determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone [e.g., @fröber2017].
 
@@
 All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e., subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
-For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to [@schad2020].
+For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to @schad2020.
 To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
-We then performed a model selection algorithm as proposed by [@matuschek2017] in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model [determined by *p* \> .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model.
-All models were computed in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4].
+We then performed a model selection algorithm as proposed by @matuschek2017 in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+Only if the parsimonious model explained the data equally well as the complex model [determined by *p* \> .20\; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model.
+All models were computed in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4].
 The optimizer function *bobyqa* with 20,000 iterations was used for maximum likelihood estimation.
-The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`; @R-buildmer].
+The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`\; @R-buildmer].
 Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts.
-All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`; @R-lmerTest].
+This was achieved using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
+All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
 
 The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (<https://osf.io/uksbc/>).
-Unfortuntaly, lack of informed consent prevents us from sharing the raw EEG data.
+Unfortunately, lack of informed consent prevents us from sharing the raw EEG data.
 
@@
 Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
-Only in the insight part, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
+Only in the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception to occur, whereas the other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
 The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \@ref(fig:exp1-plot)A), thereby making sure that semantically informed and naive perception did indeed occur.
-The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N170 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.
+The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, the N170 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.
 
@@
   stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of linear mixed-effects regression models for Experiment 1",
+  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 1\\smallskip",
   note = "Pt. = part, con. = condition, est. = estimate, CI = confidence interval."
@@
 
-In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-inisight part) they were able to understand what kind of object they saw.
+In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-insight part) they were able to understand what kind of object they saw.
 To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
@@
 In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms).
-When the same objects were presented once more in the post-insigt part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for whic semantically informed perception had taken place.
+When the same objects were presented once more in the post-insight part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for which semantically informed perception had taken place.
 
@@
 An average of `r format(round(stims_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of `r format(round(stims_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (= `r scales::percent(stims_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (= `r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with a non-matching description).
+Based on participants' responses in the insight part, an average of `r format(round(stims_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (= `r scales::percent(stims_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (= `r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
 Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
@@
   stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of linear mixed-effects regression models for Experiment 2",
+  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 2\\smallskip",
   note = "Pt. = part, con. = condition, est. = estimate, CI = confidence interval."
@@
 
-(ref:figure-2-caption) Results of Experiment 2.
+(ref:figure-2-caption) Results of Experiment 2\smallskip
+
+<!--
+
+The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
+Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
+
+\bigskip\small\emph{Note.} 
 ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-inisght part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
 Ampl.
-= amplitude.\newline\**p* \< .05.
-\*\**p* \< .01.
-\*\*\**p* \< .001.
+= amplitude.\newline*\emph{p} \textless{} .05.
+**\emph{p} \textless{} .01.
+***\emph{p} \textless{} .001.
+
+-->
 
@@
   nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
-) + # Add some lines (to seperate the parts)
+) + # Add some lines (to separate the parts)
   annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
@@
 This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
-Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; @schad2020].
+Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments\; @schad2020].
 This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
@@
   stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
+  caption = "Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\\smallskip",
   note = "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval."
@@
 
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Figure \@ref(fig:joint-plot)).
+Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \@ref(tab:joint-table) and Figure \@ref(fig:joint-plot)).
 This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all *p*s \> `r table_joint$conts["Pre-insight part", "N400_p"]`, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N170_est"]` µV, *p* = `r table_joint$conts["Insight part", "N170_p"]`, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N400_est"]` µV, *p* `r table_joint$conts["Insight part", "N400_p"]`, and in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "N400_est"]` µV, *p* `r table_joint$conts["Post-insight part", "N400_p"]`, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_joint$conts["Post-insight part", "P1_p"]`.
 
-(ref:figure-3-caption) Measured and modelled ERP amplitudes for Experiments 1 and 2 combined.
-The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \@ref(tab:joint-table)), together with their respective 95% confidence interval.
+(ref:figure-3-caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip
+
+<!--
+
+The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
+Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
+
+\bigskip\small\emph{Note.} 
+The violins and box plots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
+The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
 Ampl.
-= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline\**p* \< .05.
-\*\**p* \< .01.
-\*\*\**p* \< .001.
+= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\emph{p} \textless{} .05.
+**\emph{p} \textless{} .01.
+***\emph{p} \textless{} .001.
+
+-->
 
@@
   nrow = 1, rel_widths = c(8.5, 1.5)
-) + # Add some lines (to seperate the parts)
+) + # Add some lines (to separate the parts)
   annotate(geom = "segment", x = 11/34*0.85, xend = 11/34*0.85, y = -Inf, yend = Inf, linetype = "dashed") +
@@
 To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching descriptions as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
+Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were preceded by matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
+Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
 Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize.
@@
 Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400).
-Objects for which participants experienced semantically informed perception via matcing keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes.
+Objects for which participants experienced semantically informed perception via matching keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes.
 When these objects were presented once more, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.
@@
 
-# Contrast coding for position (inverted-updright), condition (informed-naive), and part (2-1, 3-1)
+# Contrast coding for position (inverted-upright), condition (informed-naive), and part (2-1, 3-1)
 t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
@@
 
-Here we investigated if obtaining a semantic understanding of what a previously unfamiliar object is or does has an influence on how we perceive it.
-To this end, we measured ERPs while participants watched unfamiliar objects before, while, and after receiving semantic information about them.
+Here we investigated if obtaining a semantic understanding of previously unfamiliar objects has an influence on how we perceive them.
+To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
 For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was misleading, thus keeping the perception of the object semantically naive.
-We found semantically informed percpetion to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
-If the same objects were presented again without the semantic information, only the N400 component remaind significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
+When the same objects were presented again without the semantic information, the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
 
 The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
-Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing [@kutas2011].
-It replicates previous findings that pictures elicit an N400 effect (as in our semantically naive condition) when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing compared to the naive condition [@kutas2011].
+This replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
 The time course of this effect and the computational role of the N400 [@lau2008; @rabovsky2018] suggest that it has a post-perceptual locus.
@@
 It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous work in face perception, using a similar experimental paradigm as the present study: Participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face [@bentin2002].
+This interpretation is supported by previous findings using a similar experimental paradigm in the realm of face perception [@bentin2002]: Here, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
 This effect was absent when a visual control stimulus (a non-face object instead of the intact face) was shown between the two presentations of the scrambled face.
-With regards to non-face stimuli, enlarged N170 amplitudes were also observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
-Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constitutent parts of the object.
+In the realm of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
+Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
 Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level (i.e., holistic) perception of visual objects, integrating across their visual features.
@@
 This is consistent with previous studies showing P1 effects when participants learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
-What the present study adds to these findings is that it does not take an extensive learning phase (with multiple presentations of the objects together with the respective information) for the P1 effect to develop but that it can be observed immediately after (but not during) a semantic understanding of the object has happend.
-Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its succeptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
-
-Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of the visual objects as we perceive them.
+What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information) but that it can be observed as soon as one trial after semantic insight has happened.
+Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
+
+Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects as we perceive them.
 However, the finding that these two components were modulated in different parts of our experiment suggests that they reflect different aspects top-down processing with different time courses and neuroanatomical implementations.
-It has been suggested that the onset of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas a modulation of the P1 component seems reflect recurrent processing *within* the visual system [@wyatte2014].
+It has been pointed out that the onset of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem reflect recurrent processing *within* the visual system [@wyatte2014].
 Here we show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
 
-While the limited spatial resolution of the EEG does not allow for localizing these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI that semantic information can feed back into the earliest of visual areas.
-[@hsieh2010] showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
-They found that the brain responses to the original image was correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
-This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (V1/V2/V3).
-Both of these cortical sites are consistent with the neural generators of the P1 and N170 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
-
-The top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999, but see @clarke2020].
-Proponents of this view have pointed out important conceptual and methodological shortcomings of previous studies claiming to show top-down effects of cognition on perception [@firestone2016; @machery2015].
-We took care to address as many of these shortcomings as possible: First, we showed that no effect was present had been present before any semantic information was presented (in the pre-insight part).
-Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual versus post-perceptual locus.
-Third, we reduced demand and response bias by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
+While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
+@hsieh2010 showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
+They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
+This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
+Both of these cortical regions are consistent with the neural generators of the N170 and P1 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
+
+On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999, but see @clarke2020].
+However, proponents of such a modular view have pointed out important conceptual and methodological shortcomings of previous studies claiming to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
+We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was presented (in the pre-insight part).
+Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual locus from those with a post-perceptual locus.
+Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
 Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
@@
 Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these methods have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the "cognitive impenetrability" of perception.
-
-An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in machine vision [@dicarlo2012; @marr1982].
-In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of low-level visual features may be a key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
-Single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach for these network models until they overcome this "barrier of meaning" [@mitchell2020].
-Drawing inspiration from cognitive psychology and human neuroscientific data may help making them more biologically plausible and, at the same time, more resource and data efficient.
-
-At present, a theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking.
+We hope that these procedures have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the cognitive impenetrability of perception.
+
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in machine vision [e.g., @dicarlo2012; @marr1982].
+In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this "barrier of meaning" [@mitchell2020].
+Drawing inspiration from cognitive psychology and human neuroscientific data may help making these models more biologically plausible and, at the same time, more resource and data efficient.
+
+A theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking at present.
 The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004; @hochstein2002] which posits that objects first enter our visual consciousness at an abstract, conceptual level.
 Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract relevant lower-level features ("vision with scrutiny").
-This reverse trajectory down the visual hierarchy may explain the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
-Besides the reverse hierarchy theory, an important role of top-down mechanism sfor vision or, more specifically, object recognition is also posited by the family of predictive coding and Baysian inference theories [e.g., @lupyan2015; @panichello2013; @yuille2006].
+This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
+Besides the reverse hierarchy theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories [e.g., @lupyan2015; @panichello2013; @yuille2006].
 Despite the theoretical advances, the mechanistic details of these top-down effects at the algorithmic and implementational level [@marr1982] remain to be clarified.
@@
 The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
-Another one is our reliance on rare and highly specialized objects (see appendix), which was necessary to induce experiences of semantic insight in an adult population of undergraduate students, but may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of adressing this issue would be to adapt this paradigm to younger participants, using everyday objects which they have not yet learned about.
-Finally, the number participants (*n* = 24 per experiment) and trials (*k* = 30 per part in the insight condition and *k* = 50 per part in the naive condition) can be considered small by todays standards [@baker2020].
-Our analysis may therefore not have been particularly sensitive, especially since linear mixed-effects models often have limited statistical power [@matuschek2017].
-
-[^2]: Note, however, the converging evidence from the complementary approach of rendering images of everyday obbjects difficult to recognize [@samaha2018].
-
-Nevertheless, this study provides preliminary evidence that whenever we acquire semantic information about a previously unfamiliar object, this information has an influence on multiple stages of processing.
-Intriguingly, this influence is not confined to later, post-perceptual stages---typically associated with semantic processing---but can also be observed at earlier stages---typically reflecting lower levels of visual perception and happening within 200 ms after the object is presented to us.
-
-```{=html}
-<!-- Participants' semantically informed perception of the objects in the insight part was associated with a significantly enlarged N170 component, indicating that the sudden acquisition of knowledge about the object influenced aspects of its higher-level visual processing [@rossion2011; @tanaka2001].
-The fact that this effect did not reoccur in the post-insight part, when the objects were presented once more without keywords, suggests it being a marker of semantic insight altering object processing online.
-In contrast, we also observed a modulation of the N400 component, which was reduced for objects while insight was taking place (insight part) and remained so when the same objects were presented repeatedly (post-inisght part).
-The N400 is typically discussed as an index of increased demands for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018].
-Its reduction can thus be interpreted as lowered semantic processing demands in response to unfamiliar objects once participants had understood what kind of object they were viewing.
-Finally, semantically informed perception was also associated with increased amplitudes in the P1 component but only once the objects were presented for a third time (post-insight part) after the critical presentation during which insight had occurred.
-This effect, which replicates previous work on obtaining knowledge about previously unfamiliar images [e.g., @samaha2018], may reflect that this newly acquired semantic knowledge is exerting an influence on lower-level visual perception.
-Note that this influence may manifest itself either online (within the same trial) or via the re-activation of a stored representation (created during the previous presentation of the object together with its keywords).
-Either way it is remarkable that such an early ERP effect emerges after only a single trial of "learning" in the insight part.[^2]
-
-[^2]: Interesingly, the ability to infer the category of an object from one or few encounters remains one of the ample differences between learning in biological and artifical neural networks [but see @lifei-fei2006; @koch2015].
-
-While the enhancement of the N170 component, being more negative for semantically informed as compared to naive perception, was present only during the critical presentation of the objects with their respective keywords (in the insight part), the enhancement of the P1, being more positive in response to these same objects, emerged only after the information had been obtained and the objects were presented again (in the post-insight part).
-This indicates a modulation of different stages of visual object perception while and after an understanding of the object has been obtained.
-Finally, a sustained reduction of the N400 component in response to objects for which participants experienced semantically informed perception may reflect lowered semantic processing demands compared to unfamiliar objects which participants did not yet understand.
--->
-```
+Another one is our reliance on rare and highly specialized objects (see appendix).
+This was necessary to induce the experience of semantic insight in an adult population of undergraduate students but may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
+Finally, the number participants (*n* = 24 per experiment) and trials (*k* $\approx$ 30 per part in the insight condition and *k* $\approx$ 50 per part in the naive condition) can be considered small by today's standards [@baker2020].
+Our analysis may therefore not have been particularly sensitive, especially since linear mixed-effects regression models often have limited statistical power [see, e.g., the simulations by @matuschek2017].
+
+[^2]:  Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize [@samaha2018].
+
+Nevertheless, this study provides preliminary evidence that whenever we acquire semantic information about a previously unfamiliar object, this information influences multiple stages of processing.
+These influences do not seem to be confined to later, post-perceptual stages---typically associated with semantic processing---but can also be observed at earlier stages---typically reflecting lower levels of visual perception and happening within 200 ms after the object is presented to us.
+
 \newpage
 
-# Appendix
-
-```{r appendix, include=TRUE, results="asis"}
-# Print table of materials
-read_tsv("materials/items.txt", col_types = cols()) %>%
-  transmute(
-    img = paste0("\\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/", item, ".png}"),
-    item = as.character(item),
-    match = paste(match_noun, match_verb),
-    nonmatch = paste(nonmatch_noun, nonmatch_verb)
-  ) %>%
-  apa_table(
-    col.names = c("", "\\#", "Matching keywords", "Non-matching keywords"),
-    escape = FALSE,
-    longtable = TRUE,
-    caption = "Unfamiliar Object Stimuli"
-  )
-```
-
-\newpage
-
-# References {.unnumbered}
-
-```{=tex}
-\setlength{\parindent}{-0.5in}
-%\setlength{\leftskip}{0.5in}
-```
+# References
+
+\setlength{\cslhangindent}{0.5in}

### 2021-01-07 analysis/manuscript.tex
proofread + apa7 figure captions

@@
 \AtBeginEnvironment{tabular}{\doublespacing}
-\captionsetup[figure]{font={stretch=1,scriptsize}}
+\captionsetup[table]{font={stretch=1.5}}
+\captionsetup[figure]{font={stretch=1.5}}
 \usepackage[all]{nowidow}
@@
 \interfootnotelinepenalty=10000
-\usepackage[export]{adjustbox}
 \ifxetex
@@
 In this study, we presented participants with unfamiliar objects which were preceded either by valid information about their function, leading to semantically informed perception, or by misleading information, leading to naive perception.
-Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temopral resoulation of event-related brain potentials (ERPs).
+Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temporal resolution of event-related brain potentials (ERPs).
 
 The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world should be thought of as an encapsulated module whose processing is determined solely by the visual input reaching our retina.
-According to this view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1984, 1983; Machery, 2015; Pylyshyn, 1999).
+This debate revolves around the question of whether or not our perception of the (visual) world is ``cognitively impenetrable'' or, in other words, determined solely by the visual input reaching our retina.
+According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1984, 1983; Pylyshyn, 1999).
 Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects (DiCarlo et al., 2012; Goodale \& Milner, 1992; Marr, 1982).
 
-Conversely, this position is challenged by the view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., P.
+This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., P.
 M.
@@
 Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017).
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas {[}e.g., visual areas V1 and V2; Bullier (2001); Gilbert and Li (2013){]}, as well as behavioral evidence, have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
-The reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002), for instance, assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
+The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas (e.g., visual areas V1 and V2; Bullier, 2001; Gilbert \& Li, 2013)---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+For instance, the reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002) assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
 Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
-Along similar lines, the label feedback hypothesis (Lupyan, 2012) posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
+Along similar lines, the label feedback hypothesis (Lupyan, 2012) posits that the activation of an object's name (a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
 Finally, an active role of top-down influences is also promoted by theories of vision falling under the umbrella of Bayesian inference and predictive coding (e.g., Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
@@
 Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition (for review, see Collins \& Olson, 2014; Vetter \& Newen, 2014).
-These aspects of cognition may include transient states such as emotions (Bocanegra \& Zeelenberg, 2009; e.g., Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019).
-Despite this wealth of theory and empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).
-
-One productive way to investigate top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+These aspects of cognition may include transient states such as emotions (e.g., Bocanegra \& Zeelenberg, 2009; Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019).
+Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).
+
+One productive way to investigate the top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
 This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
@@
 It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri (Di Russo et al., 2001; Foxe \& Simpson, 2002; Mangun, 1995).
-The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus {[}e.g., size, luminance, and contrast; Di Russo et al.
-(2001); Luck (2014); Johannes et al.
-(1995){]}, which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated conception of visual perception.
-For instance, it is enhanced when participants pay attention to the spatial location (Luck et al., 2000; Mangun, 1995; Mangun \& Hillyard, 1991) or certain non-spatial features (Taylor, 2002) of the stimulus.
+The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus (e.g., size, luminance, and contrast; Di Russo et al., 2001; Johannes et al., 1995; Luck, 2014), which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated view of visual perception.
+It is well-established that the P1 is enhanced when participants pay attention to the spatial location of a stimulus (Luck et al., 2000; Mangun, 1995; Mangun \& Hillyard, 1991) but there is also more recent evidence for higher-level cognitive influences that go beyond spatial attention (see below).
 
@@
 Just as the P1, it is influenced by visual parameters of the stimulus (Johannes et al., 1995) and by selective attention, especially when participants are required to discriminate between different visual stimuli (Mangun \& Hillyard, 1991; Vogel \& Luck, 2000).
-Importantly, the N170 is enlarged (i.e.,~more negative) in response to faces (Bentin et al., 1996; Rossion \& Jacques, 2011) and other visual stimuli for which one happens to be an expert {[}e.g., birds, dogs, or cars; Gauthier, Curran, et al.
-(2003); Tanaka and Curran (2001){]}.
+The N170 is enlarged (i.e.,~more negative) in response to faces (Bentin et al., 1996; Rossion \& Jacques, 2011) and other visual stimuli for which one happens to be an expert (e.g., birds, dogs, or cars; Gauthier, Curran, et al., 2003; Tanaka \& Curran, 2001).
 This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as the holistic configuration of these features (Eimer et al., 2011; Jacques \& Rossion, 2010; Rossion et al., 1999; Sagiv \& Bentin, 2001).
-Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these factors having an influence on higher-level, holistic perception of the visual stimulus.
+Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these capacities having an influence on higher-level, holistic perception of the visual stimulus.
 
@@
 
-Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge or expertise in the domain of visual objects (Abdel Rahman \& Sommer, 2008; Gratton et al., 2009; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Rossion et al., 2004, 2002; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
+Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge about visual objects (Abdel Rahman \& Sommer, 2008; Gratton et al., 2009; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Rossion et al., 2004, 2002; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
 Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing.
@@
 After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information.
-In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this has not been the case.
+In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this had not been the case.
 Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
-Interestingly, the ERPs in the in-depth knowledge condition were qualitatively similar to those for untrained but well-known objects.
+Interestingly, the ERPs in the in-depth knowledge condition even were qualitatively similar to those for untrained but well-known objects.
 The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm (Weller et al., 2019).
 Here, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
-This can be taken as further evidence of an influence of semantic knowledge on the early visual perception of unfamiliar objects.
+This can be taken as further evidence for an influence of semantic knowledge on the early visual perception of unfamiliar objects.
 
@@
 The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Abdel Rahman, 2019) or were spread out across multiple days or weeks (Rossion et al., 2004, 2002).
-While designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they necessarily leave at least three conceptual questions unresolved.
-
-The first question is if we can detect any electrophysiological correlates of semantic insight, that is,~the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on).
+While experimental designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they leave at least three conceptual questions unresolved.
+
+The first question is if we can detect any electrophysiological correlates of \emph{semantic insight}, that is,~the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on).
 The second question is how much learning is actually necessary before reliable top-down effects of knowledge on ERP amplitudes can be obtained: Does it actually take dozens of repetitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is about the nature of knowledge effects on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
-By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we hope to provide tentative answers to all three of these questions.
+The third and closely related question is about the nature of the effects of knowledge on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
+By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we were able to provide tentative answers to all three of these questions.
 
@@
 The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same throughout all parts and experiments, was to classify each object using one of four response alternatives: (a) ``I know what this is or have a strong assumption,'' (b) ``I have an assumption what this is,'' (c) ``I have rather no assumption what this is,'' or (d) ``I don't know what this is and have no assumption.'' Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) ``I know what this is or have a strong assumption,'' (b) ``I have an assumption what this is,'' (c) ``I have rather no assumption what this is,'' or (d) ``I don't know what this is and have no assumption.'' Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
@@
 
-\caption{Procedure and results of Experiment 1.
-\emph{(A)} In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
-In the post-insight part, the same objects were presented again without the keywords.
-\emph{(B)} ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
-Ampl.
-= amplitude.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.}\label{fig:exp1-plot}
+\caption{Procedure and Results of Experiment 1\smallskip}\label{fig:exp1-plot}
 \end{figure}
@@
 During the recording, electrode impedance was kept below 5 kΩ.
-An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1,000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
-
-Offline, the data were preprocessed using the MNE software {[}Version 0.21.0; Gramfort et al.
-(2013){]} in Python {[}Version 3.8.5; van Rossum and Drake (2009){]}.
+An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
+
+Offline, the data were preprocessed using the MNE software (Version 0.21.0; Gramfort et al., 2013) in Python (Version 3.8.5; van Rossum \& Drake, 2009).
 First, all scalp electrodes were re-referenced to the common average.
@@
 This led to the exclusion of an average of 2.4 trials per participant (= 0.7\%; range 0 to 24 trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see scalp topographies in Figure \ref{fig:exp1-plot}B).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see the scalp topographies in Figure \ref{fig:exp1-plot}B).
 
@@
 
-First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in the pre-insight part (i.e.,~before any keywords were presented).
+First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all further analyses those objects which participants classified as being known to them in the pre-insight part (i.e.,~before any keywords were presented).
 This led to the exclusion of an average of 7.5 objects per participant (= 6.3\% of all unfamiliar objects).
@@
 This was the case for an average of 48.8 objects per participant (= 81.2\% of objects presented with non-matching keywords).
-Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occurr---the same assignment was used to analyze the data from the other two parts.
+Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
 This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).
@@
 For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
-First, they can account not only for the non-independence of data points coming from the same participant but also simultaneously for the non-independence of data points coming from the same item.
+First, they can account not only for the non-independence of data points coming from the same participant, but also simultaneously for the non-independence of data points coming from the same item.
 In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
 Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable in designs where the assignment of trials to conditions is (co-)determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone (e.g., Fröber et al., 2017).
+Such a situation is inevitable in designs where the assignment of trials to conditions is co-determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone (e.g., Fröber et al., 2017).
 
@@
 All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.,~subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.,~subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
-For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to (Schad et al., 2020).
+For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to Schad et al.
+(2020).
 To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects (Barr et al., 2013).
-We then performed a model selection algorithm as proposed by (Matuschek et al., 2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model {[}determined by \emph{p} \textgreater{} .20; Matuschek et al.
-(2017){]} did we leave the random effect out, otherwise it was kept in the final model.
-All models were computed in R {[}Version 4.0.2; R Core Team (2020){]} using the lme4 package {[}Version 1.1.23; Bates et al.
-(2015){]}.
+We then performed a model selection algorithm as proposed by Matuschek et al.
+(2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model.
+All models were computed in R (Version 4.0.2; R Core Team, 2020) using the lme4 package (Version 1.1.23; Bates et al., 2015).
 The optimizer function \emph{bobyqa} with 20,000 iterations was used for maximum likelihood estimation.
-The model selection algorithm via likelihood ratio tests was performed using the buildmer package {[}Version 1.7.1; Voeten (2020){]}.
+The model selection algorithm via likelihood ratio tests was performed using the buildmer package (Version 1.7.1; Voeten, 2020).
 Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts.
-All \emph{p}-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package {[}Version 3.1.2; Kuznetsova et al.
-(2017){]}.
+This was achieved using the emmeans package (Version 1.5.0; Lenth, 2020).
+All \emph{p}-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package (Version 3.1.2; Kuznetsova et al., 2017).
 
 The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\url{https://osf.io/uksbc/}).
-Unfortuntaly, lack of informed consent prevents us from sharing the raw EEG data.
+Unfortunately, lack of informed consent prevents us from sharing the raw EEG data.
 
@@
 Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
-Only in the insight part, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object.
+Only in the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception to occur, whereas the other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
 The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \ref{fig:exp1-plot}A), thereby making sure that semantically informed and naive perception did indeed occur.
-The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N170 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.
+The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, the N170 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.
 
@@
 
-\caption{\label{tab:exp1-table}Results of linear mixed-effects regression models for Experiment 1}
+\caption{\label{tab:exp1-table}Results of Linear Mixed-Effects Regression Models for Experiment 1\smallskip}
 
@@
 An average of 7.0 objects per participant (= 5.8\% of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of 26.4 objects were assigned to the semantically informed condition (= 44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (= 82.0\% of objects presented with a non-matching description).
+Based on participants' responses in the insight part, an average of 26.4 objects were assigned to the semantically informed condition (= 44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (= 82.0\% of objects presented with non-matching keywords).
 Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials per participant (= 3.0\%; range 0 to 85 trials).
@@
 
-\caption{\label{tab:exp2-table}Results of linear mixed-effects regression models for Experiment 2}
+\caption{\label{tab:exp2-table}Results of Linear Mixed-Effects Regression Models for Experiment 2\smallskip}
 
@@
 
-\caption{Results of Experiment 2.
-ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-inisght part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
-Ampl.
-= amplitude.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.}\label{fig:exp2-plot}
+\caption{Results of Experiment 2\smallskip}\label{fig:exp2-plot}
 \end{figure}
@@
 This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
-Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast {[}i.e.,~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al.
-(2020){]}.
+Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast (i.e.,~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al., 2020).
 This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
@@
 
-\caption{\label{tab:joint-table}Results of linear mixed-effects regression models for Experiments 1 and 2 combined}
+\caption{\label{tab:joint-table}Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\smallskip}
 
@@
 
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Figure \ref{fig:joint-plot}).
+Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \ref{tab:joint-table} and Figure \ref{fig:joint-plot}).
 This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s \textgreater{} .577, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.
@@
 
-\caption{Measured and modelled ERP amplitudes for Experiments 1 and 2 combined.
-The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
-Ampl.
-= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.}\label{fig:joint-plot}
+\caption{Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip}\label{fig:joint-plot}
 \end{figure}
@@
 To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001.
+Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were preceded by matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
+Across both experiments, this was the case for 49.6\% of objects presented with matching keywords as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001.
 Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize.
@@
 
-Here we investigated if obtaining a semantic understanding of what a previously unfamiliar object is or does has an influence on how we perceive it.
-To this end, we measured ERPs while participants watched unfamiliar objects before, while, and after receiving semantic information about them.
+Here we investigated if obtaining a semantic understanding of previously unfamiliar objects has an influence on how we perceive them.
+To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
 For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was misleading, thus keeping the perception of the object semantically naive.
-We found semantically informed percpetion to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
-If the same objects were presented again without the semantic information, only the N400 component remaind significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
+When the same objects were presented again without the semantic information, the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
 
 The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
-Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing (Kutas \& Federmeier, 2011).
-It replicates previous findings that pictures elicit an N400 effect (as in our semantically naive condition) when they are either difficult to understand in and of themselves (e.g., Abdel Rahman \& Sommer, 2008; Supp et al., 2005) or difficult to integrate into the preceding context (e.g., Barrett \& Rugg, 1990; Ganis et al., 1996; Hirschfeld et al., 2011).
+Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing compared to the naive condition (Kutas \& Federmeier, 2011).
+This replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves (e.g., Abdel Rahman \& Sommer, 2008; Supp et al., 2005) or difficult to integrate into the preceding context (e.g., Barrett \& Rugg, 1990; Ganis et al., 1996; Hirschfeld et al., 2011).
 The time course of this effect and the computational role of the N400 (Lau et al., 2008; Rabovsky et al., 2018) suggest that it has a post-perceptual locus.
@@
 It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous work in face perception, using a similar experimental paradigm as the present study: Participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face (Bentin \& Golland, 2002).
+This interpretation is supported by previous findings using a similar experimental paradigm in the realm of face perception (Bentin \& Golland, 2002): Here, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
 This effect was absent when a visual control stimulus (a non-face object instead of the intact face) was shown between the two presentations of the scrambled face.
-With regards to non-face stimuli, enlarged N170 amplitudes were also observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects (Beaucousin et al., 2011).
-Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constitutent parts of the object.
+In the realm of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects (Beaucousin et al., 2011).
+Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
 Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level (i.e., holistic) perception of visual objects, integrating across their visual features.
@@
 This is consistent with previous studies showing P1 effects when participants learned meaningful information about previously unfamiliar objects (Abdel Rahman \& Sommer, 2008; Maier \& Abdel Rahman, 2019, 2018; Weller et al., 2019) or about familiar objects that were rendered difficult to recognize (Samaha et al., 2018).
-What the present study adds to these findings is that it does not take an extensive learning phase (with multiple presentations of the objects together with the respective information) for the P1 effect to develop but that it can be observed immediately after (but not during) a semantic understanding of the object has happend.
-Because the P1 is typically associated with lower-level sensory processing (e.g., Johannes et al., 1995; Luck, 2014; Pratt, 2011), we take its succeptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
-
-Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of the visual objects as we perceive them.
+What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information) but that it can be observed as soon as one trial after semantic insight has happened.
+Because the P1 is typically associated with lower-level sensory processing (e.g., Johannes et al., 1995; Luck, 2014; Pratt, 2011), we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
+
+Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects as we perceive them.
 However, the finding that these two components were modulated in different parts of our experiment suggests that they reflect different aspects top-down processing with different time courses and neuroanatomical implementations.
-It has been suggested that the onset of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas a modulation of the P1 component seems reflect recurrent processing \emph{within} the visual system (Wyatte et al., 2014).
+It has been pointed out that the onset of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem reflect recurrent processing \emph{within} the visual system (Wyatte et al., 2014).
 Here we show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
 
-While the limited spatial resolution of the EEG does not allow for localizing these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI that semantic information can feed back into the earliest of visual areas.
-(Hsieh et al., 2010) showed participants indiscernible two-tone (``Mooney'') versions of images before and after showing them the original versions.
-They found that the brain responses to the original image was correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
-This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (V1/V2/V3).
-Both of these cortical sites are consistent with the neural generators of the P1 and N170 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
-
-The top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception (Firestone \& Scholl, 2016; Fodor, 1983; Pylyshyn, 1999).
-Proponents of this view have pointed out important conceptual and methodological shortcomings of previous studies claiming to show top-down effects of cognition on perception (Firestone \& Scholl, 2016; Machery, 2015).
-We took care to address as many of these shortcomings as possible: First, we showed that no effect was present had been present before any semantic information was presented (in the pre-insight part).
-Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual versus post-perceptual locus.
-Third, we reduced demand and response bias by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
+While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
+Hsieh et al.
+(2010) showed participants indiscernible two-tone (``Mooney'') versions of images before and after showing them the original versions.
+They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
+This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
+Both of these cortical regions are consistent with the neural generators of the N170 and P1 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
+
+On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception Clarke (2020).
+However, proponents of such a modular view have pointed out important conceptual and methodological shortcomings of previous studies claiming to demonstrate top-down effects of cognition on perception (Firestone \& Scholl, 2016; Machery, 2015).
+We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was presented (in the pre-insight part).
+Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual locus from those with a post-perceptual locus.
+Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
 Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
@@
 Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these methods have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the ``cognitive impenetrability'' of perception.
-
-An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in machine vision (DiCarlo et al., 2012; Marr, 1982).
-In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of low-level visual features may be a key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
-Single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach for these network models until they overcome this ``barrier of meaning'' (Mitchell, 2020).
-Drawing inspiration from cognitive psychology and human neuroscientific data may help making them more biologically plausible and, at the same time, more resource and data efficient.
-
-\hypertarget{theoretical-considerations}{%
-\paragraph{Theoretical Considerations}\label{theoretical-considerations}}
-
-\hypertarget{limitations}{%
-\paragraph{Limitations}\label{limitations}}
-
-\hypertarget{conclusion-outlook}{%
-\paragraph{Conclusion \& Outlook}\label{conclusion-outlook}}
+We hope that these procedures have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the cognitive impenetrability of perception.
+
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in machine vision (e.g., DiCarlo et al., 2012; Marr, 1982).
+In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this ``barrier of meaning'' (Mitchell, 2020).
+Drawing inspiration from cognitive psychology and human neuroscientific data may help making these models more biologically plausible and, at the same time, more resource and data efficient.
+
+A theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking at present.
+The effects are consistent, however, with the reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002) which posits that objects first enter our visual consciousness at an abstract, conceptual level.
+Once this initial ``vision at a glance'' has taken place, feedback connections to earlier layers of the visual system are being accessed to extract relevant lower-level features (``vision with scrutiny'').
+This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex (Hsieh et al., 2010) as well as (b) the modulations of early visual ERP components observed in the present study and others (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Samaha et al., 2018; Weller et al., 2019).
+Besides the reverse hierarchy theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories (e.g., Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
+Despite the theoretical advances, the mechanistic details of these top-down effects at the algorithmic and implementational level (Marr, 1982) remain to be clarified.
+
+The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
+Another one is our reliance on rare and highly specialized objects (see appendix).
+This was necessary to induce the experience of semantic insight in an adult population of undergraduate students but may not necessarily generalize to the way in which we learn about everyday objects.\footnote{Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize (Samaha et al., 2018).} One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
+Finally, the number participants (\emph{n} = 24 per experiment) and trials (\emph{k} \(\approx\) 30 per part in the insight condition and \emph{k} \(\approx\) 50 per part in the naive condition) can be considered small by today's standards (Baker et al., 2020).
+Our analysis may therefore not have been particularly sensitive, especially since linear mixed-effects regression models often have limited statistical power (see, e.g., the simulations by Matuschek et al., 2017).
+
+Nevertheless, this study provides preliminary evidence that whenever we acquire semantic information about a previously unfamiliar object, this information influences multiple stages of processing.
+These influences do not seem to be confined to later, post-perceptual stages---typically associated with semantic processing---but can also be observed at earlier stages---typically reflecting lower levels of visual perception and happening within 200 ms after the object is presented to us.
 
@@
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\begin{center}
-\begin{ThreePartTable}
-
-\begin{longtable}{llll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:appendix}Unfamiliar Object Stimuli}\\
-\toprule
- & \# & Matching keywords & Non-matching keywords\\
-\midrule
-\endfirsthead
-\caption*{\normalfont{Table \ref{tab:appendix} continued}}\\
-\toprule
- & \# & Matching keywords & Non-matching keywords\\
-\midrule
-\endhead
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/1.png} & 1 & elektrische Spannung prüfen & Makkaroni formen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/2.png} & 2 & Makkaroni formen & Kuh vom Zaun abhalten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/3.png} & 3 & Knochen sägen & Streckenmaß Sonnenlicht nutzen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/4.png} & 4 & Unkraut jäten & Uhr mit Wärme betreiben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/5.png} & 5 & Mausefalle zuschnappen & Brillenglas zuschneiden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/6.png} & 6 & Goldmünzen wiegen & Farbe vom Fenster abschleifen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/7.png} & 7 & Knie fixieren & Buchstaben tippen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/8.png} & 8 & Eierkarton pressen & Tabak zermahlen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/9.png} & 9 & Baum erklettern & Rotation Ladung erzeugen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/10.png} & 10 & Buchstaben tippen & Pferdehuf Halt geben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/11.png} & 11 & Akkordeon spielen & Seil schneiden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/12.png} & 12 & Körper trainieren & Buch offen halten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/13.png} & 13 & Farbe vom Fenster abschleifen & von Hand zentrifugieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/14.png} & 14 & Außenbereich heizen & Rasierklinge schärfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/15.png} & 15 & Pflanzenteile vergrößern & Katzenklo sich selbst reinigen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/16.png} & 16 & Krawatten aufhängen & Zeichnungen vermessen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/17.png} & 17 & Schallplatte abtasten & Ball katapultieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/18.png} & 18 & Glas schneiden & Eier wiegen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/19.png} & 19 & Briketts pressen & Narkosemittel abgeben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/20.png} & 20 & Orgelton erzeugen & Bandage rollen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/21.png} & 21 & Spannung erzeugen & Fußstütze reiten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/22.png} & 22 & Narkosemittel abgeben & Nüsse aufbrechen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/23.png} & 23 & Bandage rollen & Schnee rodeln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/24.png} & 24 & Weinfass Loch einschlagen & Tier einfangen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/25.png} & 25 & Flaschenkorken einführen & Pferd im Moor laufen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/26.png} & 26 & Automat Eier ausbrüten & Windgeschwindigkeit messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/27.png} & 27 & Korngarbe greifen & Treibhaus heizen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/28.png} & 28 & Brief wiegen & Korngarbe greifen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/29.png} & 29 & Löcher bohren & Sonnenlicht Intensität messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/30.png} & 30 & Angelschnur kurbeln & Glaskörper musizieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/31.png} & 31 & Kurven malen & Nussöl pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/32.png} & 32 & Radiofrequenz einstellen & Erektion helfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/33.png} & 33 & Zäpfchen pressen & Unkraut jäten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/34.png} & 34 & Fass öffnen & Pflanzenteile vergrößern\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/35.png} & 35 & Bergbaustollen beleuchten & Knie fixieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/36.png} & 36 & Kuh vom Zaun abhalten & Radiofrequenz einstellen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/37.png} & 37 & Saatgut gleichmäßig aussäen & Fass öffnen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/38.png} & 38 & Flaschen trocknen & Bleistift anspitzen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/39.png} & 39 & Uhr mit Wärme betreiben & Körper untersuchen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/40.png} & 40 & Tonpott trommeln & Piano stimmen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/41.png} & 41 & Sprengstoffexplosion auslösen & Fisch wiegen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/42.png} & 42 & Pferdehuf Halt geben & Zäpfchen pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/43.png} & 43 & Bleistift anspitzen & Angel Köder markieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/44.png} & 44 & Nussöl pressen & Zeichen einbrennen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/45.png} & 45 & Rasierklinge schärfen & Kurven malen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/46.png} & 46 & heiße Platten anheben & Kleidung im Eimer waschen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/47.png} & 47 & Film aufspulen & Mund offen halten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/48.png} & 48 & Waffe entflammen & Uhrzeit anzeigen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/49.png} & 49 & Mikroskop-Proben schneiden & heiße Platten anheben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/50.png} & 50 & Glaskörper musizieren & Kork flach pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/51.png} & 51 & Dampf zerstäuben & Buch binden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/52.png} & 52 & Mandeln operieren & Film aufspulen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/53.png} & 53 & Toastbrot rösten & Autobatterie Spannung testen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/54.png} & 54 & Fußstütze reiten & Stromstärke messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/55.png} & 55 & Türgelenk Feuer überstehen & Botschaft telegrafieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/56.png} & 56 & Schnee rodeln & Dampf zerstäuben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/57.png} & 57 & Nüsse aufbrechen & Ziegelsteine formen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/58.png} & 58 & Radiergummi mit Strom betreiben & Münzen aufbewahren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/59.png} & 59 & Treibhaus heizen & Messer schleifen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/60.png} & 60 & Botschaft telegrafieren & Toastbrot rösten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/61.png} & 61 & Angel Köder markieren & Baum erklettern\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/62.png} & 62 & Katzenklo sich selbst reinigen & Tankfüllstand messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/63.png} & 63 & Körper untersuchen & Schuhe auf Eis laufen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/64.png} & 64 & Brillenglas zuschneiden & Saatgut gleichmäßig aussäen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/65.png} & 65 & Draht wickeln & Bergbaustollen beleuchten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/66.png} & 66 & Buch offen halten & Sprengstoffexplosion auslösen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/67.png} & 67 & Feldanbau häckseln & Draht wickeln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/68.png} & 68 & Schnurlot absenken & Korken formen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/69.png} & 69 & Sternenbilder vermessen & Schnurlot absenken\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/70.png} & 70 & Nachricht morsen & Feldanbau häckseln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/71.png} & 71 & Musikgerät stampfen & Goldmünzen wiegen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/72.png} & 72 & Schuhe auf Eis laufen & Geschwindigkeit ermitteln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/73.png} & 73 & Geschwindigkeit ermitteln & Mausefalle zuschnappen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/74.png} & 74 & Zeichen einbrennen & Luftdruck messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/75.png} & 75 & Tabak zermahlen & Flaschen trocknen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/76.png} & 76 & Stromstärke messen & Mandeln operieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/77.png} & 77 & Tier einfangen & Maiskolben entkörnen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/78.png} & 78 & Messer schleifen & Schritte vergrößern\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/79.png} & 79 & Leierkasten klingen & Fass anheben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/80.png} & 80 & Buch binden & Löcher bohren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/81.png} & 81 & Kork flach pressen & Elektroschock spielen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/82.png} & 82 & Tabletten zerteilen & Blumentopf sich selbst wässern\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/83.png} & 83 & Fass anheben & Mikroskop-Proben schneiden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/84.png} & 84 & Pferd im Moor laufen & Luft abpumpen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/85.png} & 85 & altes Ritual hacken & Spannung erzeugen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/86.png} & 86 & Kleidung im Eimer waschen & Türgelenk Feuer überstehen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/87.png} & 87 & Maiskolben entkörnen & Brief wiegen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/88.png} & 88 & Ball katapultieren & Radiergummi mit Strom betreiben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/89.png} & 89 & Zeichnungen vermessen & Brenner löten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/90.png} & 90 & Elektroschock spielen & Weinfass Loch einschlagen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/91.png} & 91 & Lieferungen abzählen & Außenbereich heizen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/92.png} & 92 & Rotation Ladung erzeugen & Musikgerät stampfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/93.png} & 93 & Herz durch Maschine ersetzen & Kerzen löschen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/94.png} & 94 & Seil schneiden & Akkordeon spielen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/95.png} & 95 & Fisch wiegen & Herz durch Maschine ersetzen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/96.png} & 96 & Kerzen löschen & Körper trainieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/97.png} & 97 & Korken formen & Sternenbilder vermessen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/98.png} & 98 & Erektion helfen & Waffe werfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/99.png} & 99 & Streckenmaß Sonnenlicht nutzen & Kartoffeln stampfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/100.png} & 100 & Luftdruck messen & Knochen sägen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/101.png} & 101 & Piano stimmen & Eierkarton pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/102.png} & 102 & von Hand zentrifugieren & Lieferungen abzählen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/103.png} & 103 & Kartoffeln stampfen & Nachricht morsen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/104.png} & 104 & Waffe werfen & elektrische Spannung prüfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/105.png} & 105 & Tankfüllstand messen & Tonpott trommeln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/106.png} & 106 & Uhrzeit anzeigen & altes Ritual hacken\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/107.png} & 107 & Windgeschwindigkeit messen & Waffe entflammen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/108.png} & 108 & Schlüsselloch stanzen & Automat Eier ausbrüten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/109.png} & 109 & Ziegelsteine formen & Schallplatte abtasten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/110.png} & 110 & Becher Schall auffangen & Schlüsselloch stanzen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/111.png} & 111 & Luft abpumpen & Briketts pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/112.png} & 112 & Mund offen halten & Orgelton erzeugen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/113.png} & 113 & Autobatterie Spannung testen & Becher Schall auffangen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/114.png} & 114 & Sonnenlicht Intensität messen & Krawatten aufhängen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/115.png} & 115 & Kutschrad anschließen & Angelschnur kurbeln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/116.png} & 116 & Eier wiegen & Leierkasten klingen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/117.png} & 117 & Blumentopf sich selbst wässern & Glas schneiden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/118.png} & 118 & Schritte vergrößern & Tabletten zerteilen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/119.png} & 119 & Münzen aufbewahren & Kutschrad anschließen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/120.png} & 120 & Brenner löten & Flaschenkorken einführen einführen\\
-\bottomrule
-\end{longtable}
-
-\end{ThreePartTable}
-\end{center}
-
-\newpage
-
 \hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\section{References}\label{references}}
 
 \setlength{\parindent}{-0.5in}
-%\setlength{\leftskip}{0.5in}
+\setlength{\leftskip}{0.5in}
 
@@
 \url{https://doi.org/10.1016/j.jml.2007.12.005}
+
+\leavevmode\hypertarget{ref-baker2020}{}%
+Baker, D.
+H., Vilidaite, G., Lygo, F.
+A., Smith, A.
+K., Flack, T.
+R., Gouws, A.
+D., \& Andrews, T.
+J.
+(2020).
+Power contours: Optimising sample size and precision in experimental psychology and human neuroscience.
+\emph{Psychological Methods}.
+\url{https://doi.org/10.1037/met0000337}
 
@@
 
+\leavevmode\hypertarget{ref-clarke2020}{}%
+Clarke, S. (2020). Cognitive penetration and informational encapsulation: Have we been failing the module? \emph{Philosophical Studies}. \url{https://doi.org/10.1007/s11098-020-01565-1}
+
 \leavevmode\hypertarget{ref-cole2012}{}%
@@
 
+\leavevmode\hypertarget{ref-R-emmeans}{}%
+Lenth, R. (2020). \emph{Emmeans: Estimated marginal means, aka least-squares means}. \url{https://CRAN.R-project.org/package=emmeans}
+
 \leavevmode\hypertarget{ref-lin1997}{}%
@@
 \leavevmode\hypertarget{ref-pratt2011}{}%
-Pratt, H. (2011). Sensory ERP components. In E. S. Kappenman \& S. J. Luck (Eds.), \emph{The oxford handbook of event-related potential components} (pp. 89--114). Oxford University Press.
+Pratt, H.
+(2011).
+Sensory ERP components.
+In E.
+S.
+Kappenman \& S.
+J.
+Luck (Eds.), \emph{The {Oxford handbook} of event-related potential components} (pp.
+89--114).
+Oxford University Press.
+\url{https://doi.org/10.1093/oxfordhb/9780195374148.013.0050}
 
@@
 
-\leavevmode\hypertarget{ref-taylor2002}{}%
-Taylor, M. J. (2002). Non-spatial attentional effects on {P1}. \emph{Clinical Neurophysiology}, \emph{113}(12), 1903--1908. \url{https://doi.org/10.1016/S1388-2457(02)00309-7}
-
 \leavevmode\hypertarget{ref-teufel2017}{}%

### 2021-01-07 analysis/master_thesis.Rmd
proofread + apa7 figure captions

@@
 mainfont          : "Times New Roman"
-output:
+output            :
   papaja::apa6_pdf:
-    latex_engine:   "xelatex"
+    latex_engine  : "xelatex"
 
 header-includes:
+  - \geometry{a4paper,margin=25mm}
   - \setcounter{tocdepth}{2}
   - \raggedbottom
+  - \usepackage{ragged2e}
   - \linespread{1.5}
-  - \geometry{a4paper,margin=25mm}
   - \fancyhead{}
@@
   - \fancyhead[RO,LE]{\thepage}
-  - \fancyhead[LO,RE]{Semantic Knowledge and Unfamiliar Objects}
-  # - \addtolength\oddsidemargin {0.5cm}
-  # - \addtolength\evensidemargin {-0.5cm}
+  - \fancyhead[RE,LO]{Semantic Knowledge and Unfamiliar Objects}
   - \usepackage{setspace}
   - \AtBeginEnvironment{tabular}{\doublespacing}
-  # - \AtBeginEnvironment{lltable}{\doublespacing}
-  # - \AtBeginEnvironment{tablenotes}{\doublespacing}
-  # - \captionsetup[table]{font={stretch=1.5}}
-  - \captionsetup[figure]{font={stretch=1,scriptsize}}
+  - \captionsetup[table]{font={stretch=1.5}}
+  - \captionsetup[figure]{font={stretch=1.5}}
   - \usepackage[all]{nowidow}
@@
 &Matrikelnummer 581331\\
-Unter Betreuung von:&Prof. Dr. Rasha Abdel Rahman (Humboldt-Universität zu Berlin)\\
+Fachliche Betreuung:&Prof. Dr. Rasha Abdel Rahman (Humboldt-Universität zu Berlin)\\
 &Prof. Dr. Franziska Süß (Fachhochschule des Mittelstands)\\
 &\\
-Berlin, den 21.01.2021&\\
+Berlin, den 29.01.2021&\\
 \end{tabular}
@@
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor danke frederik invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+I would like to thank ... (tbc)
 
@@
 ```
+
+<!-- References -->
+\raggedright
+\setlength{\cslhangindent}{0.5in}
+<div id="refs"></div>
+\justify
+
+<!-- Appendix -->
+\newpage
+
+```{r appendix, child = "appendix.Rmd"}
+```
+
+<!-- Declaration of authorship -->
+\newpage
+\setlength{\parindent}{0.5in}
+
+# Declaration of Authorship {.unnumbered}
+
+I hereby declare that the present thesis has not been submitted as a part of any other examination procedure and has been independently written.
+All passages, including those from the internet, which were used directly or in modified form, especially those sources using text, graphs, charts or pictures, are indicated as such.
+I realize that an infringement of these principles which would amount to either an attempt of deception or deceit will lead to the institution of proceedings against myself.
+
+\vspace*{20mm}
+
+\noindent
+Alexander Enge\newline
+Berlin, 29.01.2021
+
+<!-- Empty page -->
+\clearpage\mbox{}\thispagestyle{empty}\clearpage

### 2021-01-07 analysis/master_thesis.tex
proofread + apa7 figure captions

@@
 \usepackage{csquotes}
+\geometry{a4paper,margin=25mm}
 \setcounter{tocdepth}{2}
 \raggedbottom
+\usepackage{ragged2e}
 \linespread{1.5}
-\geometry{a4paper,margin=25mm}
 \fancyhead{}
@@
 \fancyhead[RO,LE]{\thepage}
-\fancyhead[LO,RE]{Semantic Knowledge and Unfamiliar Objects}
+\fancyhead[RE,LO]{Semantic Knowledge and Unfamiliar Objects}
 \usepackage{setspace}
 \AtBeginEnvironment{tabular}{\doublespacing}
-\captionsetup[figure]{font={stretch=1,scriptsize}}
+\captionsetup[table]{font={stretch=1.5}}
+\captionsetup[figure]{font={stretch=1.5}}
 \usepackage[all]{nowidow}
@@
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor danke frederik invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+I would like to thank \ldots{} (tbc)
 
@@
 
+\caption{Procedure and Results of Experiment 1\smallskip}\label{fig:exp1-plot}
+
 {\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp1-plot-1}
@@
 
-\caption{Procedure and results of Experiment 1.
-\emph{(A)} In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+\bigskip\small\emph{Note.} 
+(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
 In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
 In the post-insight part, the same objects were presented again without the keywords.
-\emph{(B)} ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
+(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
 Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
 Ampl.
-= amplitude.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.}\label{fig:exp1-plot}
+= amplitude.\newline
+*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.
+
 \end{figure}
@@
 
+\caption{Results of Experiment 2\smallskip}\label{fig:exp2-plot}
+
 {\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp2-plot-1}
@@
 
-\caption{Results of Experiment 2.
+\bigskip\small\emph{Note.} 
 ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-inisght part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
 Ampl.
@@
 **\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.}\label{fig:exp2-plot}
+***\emph{p} \textless{} .001.
+
 \end{figure}
@@
 
+\caption{Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip}\label{fig:joint-plot}
+
 {\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/joint-plot-1}
@@
 
-\caption{Measured and modelled ERP amplitudes for Experiments 1 and 2 combined.
-The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
+\bigskip\small\emph{Note.} 
+The violins and box plots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
 The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
@@
 **\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.}\label{fig:joint-plot}
+***\emph{p} \textless{} .001.
+
 \end{figure}
@@
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\begin{center}
-\begin{ThreePartTable}
-
-\begin{longtable}{llll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:appendix}Unfamiliar Object Stimuli}\\
-\toprule
- & \# & Matching keywords & Non-matching keywords\\
-\midrule
-\endfirsthead
-\caption*{\normalfont{Table \ref{tab:appendix} continued}}\\
-\toprule
- & \# & Matching keywords & Non-matching keywords\\
-\midrule
-\endhead
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/1.png} & 1 & elektrische Spannung prüfen & Makkaroni formen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/2.png} & 2 & Makkaroni formen & Kuh vom Zaun abhalten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/3.png} & 3 & Knochen sägen & Streckenmaß Sonnenlicht nutzen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/4.png} & 4 & Unkraut jäten & Uhr mit Wärme betreiben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/5.png} & 5 & Mausefalle zuschnappen & Brillenglas zuschneiden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/6.png} & 6 & Goldmünzen wiegen & Farbe vom Fenster abschleifen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/7.png} & 7 & Knie fixieren & Buchstaben tippen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/8.png} & 8 & Eierkarton pressen & Tabak zermahlen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/9.png} & 9 & Baum erklettern & Rotation Ladung erzeugen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/10.png} & 10 & Buchstaben tippen & Pferdehuf Halt geben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/11.png} & 11 & Akkordeon spielen & Seil schneiden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/12.png} & 12 & Körper trainieren & Buch offen halten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/13.png} & 13 & Farbe vom Fenster abschleifen & von Hand zentrifugieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/14.png} & 14 & Außenbereich heizen & Rasierklinge schärfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/15.png} & 15 & Pflanzenteile vergrößern & Katzenklo sich selbst reinigen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/16.png} & 16 & Krawatten aufhängen & Zeichnungen vermessen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/17.png} & 17 & Schallplatte abtasten & Ball katapultieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/18.png} & 18 & Glas schneiden & Eier wiegen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/19.png} & 19 & Briketts pressen & Narkosemittel abgeben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/20.png} & 20 & Orgelton erzeugen & Bandage rollen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/21.png} & 21 & Spannung erzeugen & Fußstütze reiten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/22.png} & 22 & Narkosemittel abgeben & Nüsse aufbrechen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/23.png} & 23 & Bandage rollen & Schnee rodeln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/24.png} & 24 & Weinfass Loch einschlagen & Tier einfangen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/25.png} & 25 & Flaschenkorken einführen & Pferd im Moor laufen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/26.png} & 26 & Automat Eier ausbrüten & Windgeschwindigkeit messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/27.png} & 27 & Korngarbe greifen & Treibhaus heizen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/28.png} & 28 & Brief wiegen & Korngarbe greifen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/29.png} & 29 & Löcher bohren & Sonnenlicht Intensität messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/30.png} & 30 & Angelschnur kurbeln & Glaskörper musizieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/31.png} & 31 & Kurven malen & Nussöl pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/32.png} & 32 & Radiofrequenz einstellen & Erektion helfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/33.png} & 33 & Zäpfchen pressen & Unkraut jäten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/34.png} & 34 & Fass öffnen & Pflanzenteile vergrößern\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/35.png} & 35 & Bergbaustollen beleuchten & Knie fixieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/36.png} & 36 & Kuh vom Zaun abhalten & Radiofrequenz einstellen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/37.png} & 37 & Saatgut gleichmäßig aussäen & Fass öffnen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/38.png} & 38 & Flaschen trocknen & Bleistift anspitzen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/39.png} & 39 & Uhr mit Wärme betreiben & Körper untersuchen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/40.png} & 40 & Tonpott trommeln & Piano stimmen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/41.png} & 41 & Sprengstoffexplosion auslösen & Fisch wiegen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/42.png} & 42 & Pferdehuf Halt geben & Zäpfchen pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/43.png} & 43 & Bleistift anspitzen & Angel Köder markieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/44.png} & 44 & Nussöl pressen & Zeichen einbrennen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/45.png} & 45 & Rasierklinge schärfen & Kurven malen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/46.png} & 46 & heiße Platten anheben & Kleidung im Eimer waschen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/47.png} & 47 & Film aufspulen & Mund offen halten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/48.png} & 48 & Waffe entflammen & Uhrzeit anzeigen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/49.png} & 49 & Mikroskop-Proben schneiden & heiße Platten anheben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/50.png} & 50 & Glaskörper musizieren & Kork flach pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/51.png} & 51 & Dampf zerstäuben & Buch binden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/52.png} & 52 & Mandeln operieren & Film aufspulen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/53.png} & 53 & Toastbrot rösten & Autobatterie Spannung testen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/54.png} & 54 & Fußstütze reiten & Stromstärke messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/55.png} & 55 & Türgelenk Feuer überstehen & Botschaft telegrafieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/56.png} & 56 & Schnee rodeln & Dampf zerstäuben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/57.png} & 57 & Nüsse aufbrechen & Ziegelsteine formen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/58.png} & 58 & Radiergummi mit Strom betreiben & Münzen aufbewahren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/59.png} & 59 & Treibhaus heizen & Messer schleifen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/60.png} & 60 & Botschaft telegrafieren & Toastbrot rösten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/61.png} & 61 & Angel Köder markieren & Baum erklettern\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/62.png} & 62 & Katzenklo sich selbst reinigen & Tankfüllstand messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/63.png} & 63 & Körper untersuchen & Schuhe auf Eis laufen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/64.png} & 64 & Brillenglas zuschneiden & Saatgut gleichmäßig aussäen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/65.png} & 65 & Draht wickeln & Bergbaustollen beleuchten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/66.png} & 66 & Buch offen halten & Sprengstoffexplosion auslösen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/67.png} & 67 & Feldanbau häckseln & Draht wickeln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/68.png} & 68 & Schnurlot absenken & Korken formen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/69.png} & 69 & Sternenbilder vermessen & Schnurlot absenken\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/70.png} & 70 & Nachricht morsen & Feldanbau häckseln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/71.png} & 71 & Musikgerät stampfen & Goldmünzen wiegen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/72.png} & 72 & Schuhe auf Eis laufen & Geschwindigkeit ermitteln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/73.png} & 73 & Geschwindigkeit ermitteln & Mausefalle zuschnappen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/74.png} & 74 & Zeichen einbrennen & Luftdruck messen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/75.png} & 75 & Tabak zermahlen & Flaschen trocknen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/76.png} & 76 & Stromstärke messen & Mandeln operieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/77.png} & 77 & Tier einfangen & Maiskolben entkörnen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/78.png} & 78 & Messer schleifen & Schritte vergrößern\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/79.png} & 79 & Leierkasten klingen & Fass anheben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/80.png} & 80 & Buch binden & Löcher bohren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/81.png} & 81 & Kork flach pressen & Elektroschock spielen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/82.png} & 82 & Tabletten zerteilen & Blumentopf sich selbst wässern\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/83.png} & 83 & Fass anheben & Mikroskop-Proben schneiden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/84.png} & 84 & Pferd im Moor laufen & Luft abpumpen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/85.png} & 85 & altes Ritual hacken & Spannung erzeugen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/86.png} & 86 & Kleidung im Eimer waschen & Türgelenk Feuer überstehen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/87.png} & 87 & Maiskolben entkörnen & Brief wiegen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/88.png} & 88 & Ball katapultieren & Radiergummi mit Strom betreiben\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/89.png} & 89 & Zeichnungen vermessen & Brenner löten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/90.png} & 90 & Elektroschock spielen & Weinfass Loch einschlagen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/91.png} & 91 & Lieferungen abzählen & Außenbereich heizen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/92.png} & 92 & Rotation Ladung erzeugen & Musikgerät stampfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/93.png} & 93 & Herz durch Maschine ersetzen & Kerzen löschen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/94.png} & 94 & Seil schneiden & Akkordeon spielen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/95.png} & 95 & Fisch wiegen & Herz durch Maschine ersetzen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/96.png} & 96 & Kerzen löschen & Körper trainieren\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/97.png} & 97 & Korken formen & Sternenbilder vermessen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/98.png} & 98 & Erektion helfen & Waffe werfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/99.png} & 99 & Streckenmaß Sonnenlicht nutzen & Kartoffeln stampfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/100.png} & 100 & Luftdruck messen & Knochen sägen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/101.png} & 101 & Piano stimmen & Eierkarton pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/102.png} & 102 & von Hand zentrifugieren & Lieferungen abzählen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/103.png} & 103 & Kartoffeln stampfen & Nachricht morsen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/104.png} & 104 & Waffe werfen & elektrische Spannung prüfen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/105.png} & 105 & Tankfüllstand messen & Tonpott trommeln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/106.png} & 106 & Uhrzeit anzeigen & altes Ritual hacken\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/107.png} & 107 & Windgeschwindigkeit messen & Waffe entflammen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/108.png} & 108 & Schlüsselloch stanzen & Automat Eier ausbrüten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/109.png} & 109 & Ziegelsteine formen & Schallplatte abtasten\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/110.png} & 110 & Becher Schall auffangen & Schlüsselloch stanzen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/111.png} & 111 & Luft abpumpen & Briketts pressen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/112.png} & 112 & Mund offen halten & Orgelton erzeugen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/113.png} & 113 & Autobatterie Spannung testen & Becher Schall auffangen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/114.png} & 114 & Sonnenlicht Intensität messen & Krawatten aufhängen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/115.png} & 115 & Kutschrad anschließen & Angelschnur kurbeln\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/116.png} & 116 & Eier wiegen & Leierkasten klingen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/117.png} & 117 & Blumentopf sich selbst wässern & Glas schneiden\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/118.png} & 118 & Schritte vergrößern & Tabletten zerteilen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/119.png} & 119 & Münzen aufbewahren & Kutschrad anschließen\\
-\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/120.png} & 120 & Brenner löten & Flaschenkorken einführen einführen\\
-\bottomrule
-\end{longtable}
-
-\end{ThreePartTable}
-\end{center}
-
-\newpage
-
 \hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\setlength{\parindent}{-0.5in}
-%\setlength{\leftskip}{0.5in}
+\section{References}\label{references}}
+
+\setlength{\cslhangindent}{0.5in}
+
+\raggedright
+\setlength{\cslhangindent}{0.5in}
 
@@
 
+\justify
+
+\newpage
+
+\hypertarget{appendix}{%
+\section*{Appendix}\label{appendix}}
+\addcontentsline{toc}{section}{Appendix}
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+
+\begin{center}
+\begin{ThreePartTable}
+
+\begin{longtable}{llll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:appendix}Unfamiliar Object Stimuli\smallskip}\\
+\toprule
+ & \# & Matching keywords & Non-matching keywords\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:appendix} continued}}\\
+\toprule
+ & \# & Matching keywords & Non-matching keywords\\
+\midrule
+\endhead
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/1.png} & 1 & elektrische Spannung prüfen & Makkaroni formen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/2.png} & 2 & Makkaroni formen & Kuh vom Zaun abhalten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/3.png} & 3 & Knochen sägen & Streckenmaß Sonnenlicht nutzen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/4.png} & 4 & Unkraut jäten & Uhr mit Wärme betreiben\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/5.png} & 5 & Mausefalle zuschnappen & Brillenglas zuschneiden\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/6.png} & 6 & Goldmünzen wiegen & Farbe vom Fenster abschleifen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/7.png} & 7 & Knie fixieren & Buchstaben tippen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/8.png} & 8 & Eierkarton pressen & Tabak zermahlen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/9.png} & 9 & Baum erklettern & Rotation Ladung erzeugen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/10.png} & 10 & Buchstaben tippen & Pferdehuf Halt geben\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/11.png} & 11 & Akkordeon spielen & Seil schneiden\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/12.png} & 12 & Körper trainieren & Buch offen halten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/13.png} & 13 & Farbe vom Fenster abschleifen & von Hand zentrifugieren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/14.png} & 14 & Außenbereich heizen & Rasierklinge schärfen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/15.png} & 15 & Pflanzenteile vergrößern & Katzenklo sich selbst reinigen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/16.png} & 16 & Krawatten aufhängen & Zeichnungen vermessen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/17.png} & 17 & Schallplatte abtasten & Ball katapultieren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/18.png} & 18 & Glas schneiden & Eier wiegen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/19.png} & 19 & Briketts pressen & Narkosemittel abgeben\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/20.png} & 20 & Orgelton erzeugen & Bandage rollen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/21.png} & 21 & Spannung erzeugen & Fußstütze reiten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/22.png} & 22 & Narkosemittel abgeben & Nüsse aufbrechen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/23.png} & 23 & Bandage rollen & Schnee rodeln\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/24.png} & 24 & Weinfass Loch einschlagen & Tier einfangen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/25.png} & 25 & Flaschenkorken einführen & Pferd im Moor laufen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/26.png} & 26 & Automat Eier ausbrüten & Windgeschwindigkeit messen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/27.png} & 27 & Korngarbe greifen & Treibhaus heizen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/28.png} & 28 & Brief wiegen & Korngarbe greifen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/29.png} & 29 & Löcher bohren & Sonnenlicht Intensität messen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/30.png} & 30 & Angelschnur kurbeln & Glaskörper musizieren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/31.png} & 31 & Kurven malen & Nussöl pressen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/32.png} & 32 & Radiofrequenz einstellen & Erektion helfen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/33.png} & 33 & Zäpfchen pressen & Unkraut jäten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/34.png} & 34 & Fass öffnen & Pflanzenteile vergrößern\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/35.png} & 35 & Bergbaustollen beleuchten & Knie fixieren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/36.png} & 36 & Kuh vom Zaun abhalten & Radiofrequenz einstellen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/37.png} & 37 & Saatgut gleichmäßig aussäen & Fass öffnen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/38.png} & 38 & Flaschen trocknen & Bleistift anspitzen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/39.png} & 39 & Uhr mit Wärme betreiben & Körper untersuchen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/40.png} & 40 & Tonpott trommeln & Piano stimmen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/41.png} & 41 & Sprengstoffexplosion auslösen & Fisch wiegen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/42.png} & 42 & Pferdehuf Halt geben & Zäpfchen pressen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/43.png} & 43 & Bleistift anspitzen & Angel Köder markieren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/44.png} & 44 & Nussöl pressen & Zeichen einbrennen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/45.png} & 45 & Rasierklinge schärfen & Kurven malen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/46.png} & 46 & heiße Platten anheben & Kleidung im Eimer waschen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/47.png} & 47 & Film aufspulen & Mund offen halten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/48.png} & 48 & Waffe entflammen & Uhrzeit anzeigen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/49.png} & 49 & Mikroskop-Proben schneiden & heiße Platten anheben\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/50.png} & 50 & Glaskörper musizieren & Kork flach pressen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/51.png} & 51 & Dampf zerstäuben & Buch binden\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/52.png} & 52 & Mandeln operieren & Film aufspulen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/53.png} & 53 & Toastbrot rösten & Autobatterie Spannung testen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/54.png} & 54 & Fußstütze reiten & Stromstärke messen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/55.png} & 55 & Türgelenk Feuer überstehen & Botschaft telegrafieren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/56.png} & 56 & Schnee rodeln & Dampf zerstäuben\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/57.png} & 57 & Nüsse aufbrechen & Ziegelsteine formen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/58.png} & 58 & Radiergummi mit Strom betreiben & Münzen aufbewahren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/59.png} & 59 & Treibhaus heizen & Messer schleifen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/60.png} & 60 & Botschaft telegrafieren & Toastbrot rösten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/61.png} & 61 & Angel Köder markieren & Baum erklettern\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/62.png} & 62 & Katzenklo sich selbst reinigen & Tankfüllstand messen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/63.png} & 63 & Körper untersuchen & Schuhe auf Eis laufen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/64.png} & 64 & Brillenglas zuschneiden & Saatgut gleichmäßig aussäen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/65.png} & 65 & Draht wickeln & Bergbaustollen beleuchten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/66.png} & 66 & Buch offen halten & Sprengstoffexplosion auslösen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/67.png} & 67 & Feldanbau häckseln & Draht wickeln\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/68.png} & 68 & Schnurlot absenken & Korken formen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/69.png} & 69 & Sternenbilder vermessen & Schnurlot absenken\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/70.png} & 70 & Nachricht morsen & Feldanbau häckseln\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/71.png} & 71 & Musikgerät stampfen & Goldmünzen wiegen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/72.png} & 72 & Schuhe auf Eis laufen & Geschwindigkeit ermitteln\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/73.png} & 73 & Geschwindigkeit ermitteln & Mausefalle zuschnappen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/74.png} & 74 & Zeichen einbrennen & Luftdruck messen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/75.png} & 75 & Tabak zermahlen & Flaschen trocknen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/76.png} & 76 & Stromstärke messen & Mandeln operieren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/77.png} & 77 & Tier einfangen & Maiskolben entkörnen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/78.png} & 78 & Messer schleifen & Schritte vergrößern\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/79.png} & 79 & Leierkasten klingen & Fass anheben\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/80.png} & 80 & Buch binden & Löcher bohren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/81.png} & 81 & Kork flach pressen & Elektroschock spielen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/82.png} & 82 & Tabletten zerteilen & Blumentopf sich selbst wässern\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/83.png} & 83 & Fass anheben & Mikroskop-Proben schneiden\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/84.png} & 84 & Pferd im Moor laufen & Luft abpumpen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/85.png} & 85 & altes Ritual hacken & Spannung erzeugen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/86.png} & 86 & Kleidung im Eimer waschen & Türgelenk Feuer überstehen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/87.png} & 87 & Maiskolben entkörnen & Brief wiegen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/88.png} & 88 & Ball katapultieren & Radiergummi mit Strom betreiben\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/89.png} & 89 & Zeichnungen vermessen & Brenner löten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/90.png} & 90 & Elektroschock spielen & Weinfass Loch einschlagen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/91.png} & 91 & Lieferungen abzählen & Außenbereich heizen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/92.png} & 92 & Rotation Ladung erzeugen & Musikgerät stampfen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/93.png} & 93 & Herz durch Maschine ersetzen & Kerzen löschen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/94.png} & 94 & Seil schneiden & Akkordeon spielen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/95.png} & 95 & Fisch wiegen & Herz durch Maschine ersetzen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/96.png} & 96 & Kerzen löschen & Körper trainieren\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/97.png} & 97 & Korken formen & Sternenbilder vermessen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/98.png} & 98 & Erektion helfen & Waffe werfen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/99.png} & 99 & Streckenmaß Sonnenlicht nutzen & Kartoffeln stampfen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/100.png} & 100 & Luftdruck messen & Knochen sägen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/101.png} & 101 & Piano stimmen & Eierkarton pressen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/102.png} & 102 & von Hand zentrifugieren & Lieferungen abzählen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/103.png} & 103 & Kartoffeln stampfen & Nachricht morsen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/104.png} & 104 & Waffe werfen & elektrische Spannung prüfen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/105.png} & 105 & Tankfüllstand messen & Tonpott trommeln\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/106.png} & 106 & Uhrzeit anzeigen & altes Ritual hacken\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/107.png} & 107 & Windgeschwindigkeit messen & Waffe entflammen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/108.png} & 108 & Schlüsselloch stanzen & Automat Eier ausbrüten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/109.png} & 109 & Ziegelsteine formen & Schallplatte abtasten\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/110.png} & 110 & Becher Schall auffangen & Schlüsselloch stanzen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/111.png} & 111 & Luft abpumpen & Briketts pressen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/112.png} & 112 & Mund offen halten & Orgelton erzeugen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/113.png} & 113 & Autobatterie Spannung testen & Becher Schall auffangen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/114.png} & 114 & Sonnenlicht Intensität messen & Krawatten aufhängen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/115.png} & 115 & Kutschrad anschließen & Angelschnur kurbeln\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/116.png} & 116 & Eier wiegen & Leierkasten klingen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/117.png} & 117 & Blumentopf sich selbst wässern & Glas schneiden\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/118.png} & 118 & Schritte vergrößern & Tabletten zerteilen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/119.png} & 119 & Münzen aufbewahren & Kutschrad anschließen\\
+\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/120.png} & 120 & Brenner löten & Flaschenkorken einführen einführen\\
+\bottomrule
+\end{longtable}
+
+\end{ThreePartTable}
+\end{center}
+
+\newpage
+\setlength{\parindent}{0.5in}
+
+\hypertarget{declaration-of-authorship}{%
+\section*{Declaration of Authorship}\label{declaration-of-authorship}}
+\addcontentsline{toc}{section}{Declaration of Authorship}
+
+I hereby declare that the present thesis has not been submitted as a part of any other examination procedure and has been independently written.
+All passages, including those from the internet, which were used directly or in modified form, especially those sources using text, graphs, charts or pictures, are indicated as such.
+I realize that an infringement of these principles which would amount to either an attempt of deception or deceit will lead to the institution of proceedings against myself.
+
+\vspace*{20mm}
+
+\noindent
+Alexander Enge\newline
+Berlin, 29.01.2021
+
+\clearpage
+
+\mbox{}\thispagestyle{empty}\clearpage
+
 \end{document}

### 2021-01-14 analysis/manuscript.Rmd
implement feedback by rasha and garrett

@@
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
+    corresponding : yes
     address       : "Rudower Chaussee 18, 12489 Berlin"
@@
   - id            : "1"
-    institution   : "Humboldt-Universität zu Berlin"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
   - id            : "2"
-    institution   : "Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
   - id            : "3"
@@
 keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
-wordcount         : ""
-
-bibliography      : "manuscript_files/r-references.bib"
-zotero            : "aha"
 
@@
 
+bibliography      : "manuscript_files/r-references.bib"
 csl               : "manuscript_files/apa.csl"
+zotero            : "aha"
 documentclass     : "apa7"
@@
   - \raggedbottom
+  - \usepackage[all]{nowidow}
+  - \usepackage[bottom]{footmisc}
+  - \interfootnotelinepenalty=10000
   - \usepackage{setspace}
@@
   - \captionsetup[figure]{font={stretch=1.5}}
-  - \usepackage[all]{nowidow}
-  - \usepackage[bottom]{footmisc}
-  - \interfootnotelinepenalty=10000
 ---
@@
 How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects which were preceded either by valid information about their function, leading to semantically informed perception, or by misleading information, leading to naive perception.
+In this study, we presented participants with unfamiliar objects which were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
 Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temporal resolution of event-related brain potentials (ERPs).
@@
 These aspects of cognition may include transient states such as emotions [e.g., @bocanegra2009; @phelps2016] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @lin1997; @weller2019].
-Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
-
-One productive way to investigate the top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical and pointed out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
+They have argued, for example, that most behavioral paradigms have not been able to discern between perceptual and postperceptual (e.g., memory-related) effects.
+Furthermore, cognitive influences in some studies have been confounded with differences in the lower-level visual input.
+We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our methodology and results.
+
+In general, however, it is important to note that one productive way to circumvent some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
 This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
@@
 Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
-These keywords could either correctly describe the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could mislead participants by describing the function of a different object, thus keeping the perception of the object semantically naive.
+These keywords could either be matching the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could be non-matching by describing the function of a different object, thus keeping the perception of the object semantically naive.
 During this second part, we were able measure the online influence of semantic insight on object-evoked ERPs as it happened.
@@
 Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
-Only in the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception to occur, whereas the other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
+In the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception.
+The other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
 The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \@ref(fig:exp1-plot)A), thereby making sure that semantically informed and naive perception did indeed occur.
@@
 Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29 years) who had not participated in Experiment 1.
-They had no history of psychological disorder or treatment, were right-handed, and reported normal or corrected-to-normal vision.
+They had no history of psychological disorders or treatment, were right-handed, and reported normal or corrected-to-normal vision.
 They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
@@
 Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords but on which participants failed to capitalize.
 Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, *b* = `r table_joint_control$conts["Insight part", "N400_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N400_p"]`.
@@
 To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
-For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was misleading, thus keeping the perception of the object semantically naive.
+For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was non-matching, thus keeping the perception of the object semantically naive.
 We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.

### 2021-01-16 analysis/manuscript.Rmd
attempt to add evokeds for exp3

@@
 
-# Chunk options
+# Set global chunk options
 knitr::opts_chunk$set(include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10)
 
-# Bibliography file
+# Link to the bibliography file
 r_refs("analysis/manuscript_files/r-references.bib")
 
-# Create export folder for results
+# Create an export folder for results
 dir.create("analysis/export", showWarnings = FALSE)
 
-# Do we want to run analysis for Experiment 3?
-run_exp3 <- FALSE
+# Do you want to re-run the EEG preprocessing? Note that this can only be used with the raw EEG data, which are
+# available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
+rerun_preproc <- FALSE
+
+# Do you want to re-run the linear mixed-effect models? This can be done even if only the preprocessed single-trial
+# data are available (from GitHub and/or the OSF). Note, however, that the model fitting may take more than 24 hours.
+rerun_models <- FALSE
 ```
@@
 ```{r exp1-preparation}
-# Define function for reading and formatting behavioral data
+# Define function for reading and formatting the behavioral data
 read_behav <- function(txt_fname) {
-  # Read log file
+  # Read the log file
   dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
@@
 evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)
+```
+
+```{python}
+# Define function to compute grand averages per condition
+def compute_evokeds(epochs):
+    evokeds = dict(); evokeds_dat = dict()
+    # Each part becomes a dictionary of conditions
+    for pt in ["I", "II", "III"]:
+        evokeds[pt] = dict(); evokeds_dat[pt] = dict()
+        # Each part becomes a dictionary of conditions
+        for pos in ["Inverted", "Upright"]:
+            evokeds[pt][pos] = dict(); evokeds_dat[pt][pos] = dict()
+            # Each condition becomes a list of participants
+            for cn in ["Informed", "Naive"]:
+                evokeds[pt][pos][cn] = list(); evokeds_dat[pt][pos][cn] = list()
+                # For every participant we average trials separately for all parts and conditions
+                for vp in epochs.metadata["participant"].unique():
+                    query = 'participant == "' + vp + '" and part == "' + pt + '" and position == "' + pos + '" and condition == "' + cn + '"'
+                    evokeds[pt][pos][cn].append(epochs[query].average())
+                # Compute grand averages across participants for this part and condition
+                evokeds[pt][pos][cn] = mne.grand_average(evokeds[pt][pos][cn])
+                # Export only the actual data for R
+                evokeds_dat[pt][pos][cn] = evokeds[pt][pos][cn].data
+    return (evokeds, evokeds_dat)
+
+# Compute grand averages for Experiment 1
+evokeds_exp3, evokeds_dat_exp3 = compute_evokeds_3(epochs=epochs_exp3)
+```
+
+```{r}
+evokeds_exp3 <- py$evokeds_exp3_anova
+
+compute_erps <- function(evokeds, els, name, start, stop, roi) {
+  map(evokeds, function(part){
+    map(part, function(position) {
+      map(position, function(condition) {
+        map_dbl(condition, function(participant) {
+          participant[which(els %in% roi), which(times %in% start:stop)] %>% mean()
+        })
+      }) %>% 
+        bind_rows(.id = "condition") %>%
+        mutate(participant = factor(1:24)) %>%
+        pivot_longer(cols = c("Informed", "Naive"), names_to = "condition", values_to = "amplitude")
+    }) %>% bind_rows(.id = "position")
+  }) %>% bind_rows(.id = "part")
+}
 ```

### 2021-01-16 analysis/manuscript.Rmd
before moving the preproc step into an r chunk

--- 2021-01-14 analysis/manuscript.Rmd
@@
 
-```{r exp1-preparation}
-# Define function for reading and formatting behavioral data
+```{r exp1-preparation, eval=rerun_preproc}
+# Define function for reading and formatting the behavioral data
 read_behav <- function(txt_fname) {
-  # Read log file
+  # Read the log file
   dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
@@
 
-# Check average number of stimuli per condition
-(stims_exp1 <- map(data_exp1, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
-```
-
-```{python exp1-preprocessing}
+# Check average number of stimuli per condition and save to the export folder
+map(data_exp1, function(x) table(x$condition) / 3) %>%
+  bind_rows() %>%
+  colMeans() %>%
+  saveRDS("analysis/export/exp1-stims.RDS")
+```
+
+```{python exp1-preprocessing, eval=rerun_preproc}
 # Import libraries
@@
 
-montage = mne.channels.make_standard_montage("easycap-M1")
-montage._get_ch_pos()
-
 # Set parameters for EEG preprocessing
 preproc_params = dict(
-    n_components=15, method="fastica",         # ICA parameters
+    n_components=15, method='fastica',         # ICA parameters
     l_freq=0.1, h_freq=30,                     # Filter edges
-    event_id={"match": 221, "mismatch": 222},  # EEG triggers
+    event_id={'match': 221, 'mismatch': 222},  # EEG triggers
     tmin=-0.5, tmax=1.498,                     # Length of epochs
@@
 
-# # Debug
+# # For debugging
 # locals().update(preproc_params)
@@
 
-# Define function for preprocessing EEG data
-def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline, reject):
+# Define function for preprocessing the EEG data
+def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq,
+            event_id, tmin, tmax, baseline, reject):
     # Read EEG data in microvolts
@@
     # Create virtual EOG channels
-    raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
-    raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
-    raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
+    raw = mne.set_bipolar_reference(raw, 'Auge_u', 'Fp1', ch_name='VEOG', drop_refs=False)
+    raw = mne.set_bipolar_reference(raw, 'F9', 'F10', ch_name='HEOG', drop_refs=False)
+    raw.set_channel_types(mapping={'VEOG': 'eog', 'HEOG': 'eog'})
     # Add EasyCap electrode layout, removing any excessive channels
-    montage = mne.channels.make_standard_montage("easycap-M1")
-    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
+    montage = mne.channels.make_standard_montage('easycap-M1')
+    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(['VEOG', 'HEOG'])))
     raw.set_montage(montage=montage)
-    # # Interpolate bad channels
-    # if vhdr_fname=='data/exp3/EEG/VP05.vhdr':
-    #   raw.info['bads'].extend(['AF8', 'TP9'])
-    #   raw = raw.interpolate_bads()
     # Re-reference to common average
-    raw, _ = mne.set_eeg_reference(raw, "average")
+    raw, _ = mne.set_eeg_reference(raw, 'average')
     # Run ICA on a copy of the data
@@
     events, _ = mne.events_from_annotations(raw, verbose=False)
-    epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True)
+    epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin,
+                        tmax=tmax, baseline=baseline, preload=True)
     # Add behavioral data
@@
 # List raw EEG filenames
-fnames_exp1 = sorted(glob.glob("data/exp1/EEG/*.vhdr"))
+fnames_exp1 = sorted(glob.glob('data/exp1/EEG/*.vhdr'))
 
@@
 
+# Apply the function to preprocess the EEG data for Experiment 1
+epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
+               for fname, meta in zip(fnames_exp1, metadata_exp1)]
+
+# Combine epochs into a single data set
+epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
+
+# Backup epochs to the export folder
+epochs_exp1.save('analysis/export/exp1-epo.fif')
+
+# Backup the channel names separately
+
 # Check if preprocessing was done already (delete the file to re-run)
-if os.path.exists("analysis/export/exp1-epo.fif"):
+if os.path.exists('analysis/export/exp1-epo.fif'):
     # Read preprocessed data from file
-    epochs_exp1 = mne.read_epochs("analysis/export/exp1-epo.fif", preload=True)
+    epochs_exp1 = mne.read_epochs('analysis/export/exp1-epo.fif', preload=True)
 else:
     # Preprocess EEG data for Experiment 1
-    epochs_exp1 = [
-        preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp1, metadata_exp1)
-    ]
+    epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
+                   for fname, meta in zip(fnames_exp1, metadata_exp1)]
     # Combine epochs into a single data set
@@
     # Backup epochs to the export folder
-    epochs_exp1.save("analysis/export/exp1-epo.fif")
+    epochs_exp1.save('analysis/export/exp1-epo.fif')
 
@@
     # Each part becomes a dictionary of conditions
-    for pt in ["I", "II", "III"]:
+    for pt in ['I', 'II', 'III']:
         evokeds[pt] = dict(); evokeds_dat[pt] = dict()
         # Each condition becomes a list of participants
-        for cn in ["Informed", "Naive"]:
+        for cn in ['Informed', 'Naive']:
             evokeds[pt][cn] = list(); evokeds_dat[pt][cn] = list()
             # For every participant we average trials separately for all parts and conditions
-            for vp in epochs.metadata["participant"].unique():
+            for vp in epochs.metadata['participant'].unique():
                 query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
@@
 evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)
+
+import pickle
+with open('analysis/export/exp1-avgs.pickle', 'wb') as handle:
+    pickle.dump(evokeds_dat_exp1, handle, protocol=pickle.HIGHEST_PROTOCOL)
+```
+
+```{r backup}
+
+test <- py$preproc(
+  vhdr_fname = "data/exp1/EEG/Vp0001.vhdr",
+  metadata = data_exp1[[1]],
+  n_components = as.integer(15),
+  method = "fastica",
+  l_freq = 0.1,
+  h_freq = 30,
+  event_id = list(match = as.integer(221), mismatch = as.integer(222)),
+  tmin = -0.5,
+  tmax = 1.498,
+  baseline = tuple(-0.2, 0),
+  reject = list(eeg = 200))
+
+test$ch_names
 ```

### 2021-01-17 analysis/manuscript.Rmd
update grand averaging with dict comprehension

@@
 ```{r setup, include=FALSE}
+# Do you want to re-run the EEG preprocessing? Note that this can only be done with the raw data,
+# which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
+rerun_preproc <- FALSE
+
+# Do you want to re-run the linear mixed-effect models? This can be done even if only the
+# preprocessed single-trial data are available (from GitHub and/or the OSF). Note, however, that
+# fitting all models may take 24 hours or more.
+rerun_models <- FALSE
+
 # Load packages
@@
 
-# Do you want to re-run the EEG preprocessing? Note that this can only be used with the raw EEG data, which are
-# available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
-rerun_preproc <- FALSE
-
-# Do you want to re-run the linear mixed-effect models? This can be done even if only the preprocessed single-trial
-# data are available (from GitHub and/or the OSF). Note, however, that the model fitting may take more than 24 hours.
-rerun_models <- FALSE
+# Define ERP components of interest
+comps <- tibble(
+  name = c("P1", "N170", "N400"),
+  start = c(100, 150, 400),
+  stop = c(150, 200, 700),
+  roi = list(
+    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
+    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
+    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
+  )
+)
 ```
@@
 
-```{r exp1-preparation, eval=rerun_preproc}
-# Define function for reading and formatting the behavioral data
-read_behav <- function(txt_fname) {
-  # Read the log file
-  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
-  # Rename columns for participant and item IDs
-  dat %<>% rename(participant = VPNummer, item = StimID) %>%
-    # Add a column for the part of the experiment
-    mutate(part = case_when(
-      Wdh %in% c(211, 231) ~ "I",
-      Wdh %in% c(212, 232) ~ "II",
-      Wdh %in% c(213, 233) ~ "III",
-      Wdh == 234 ~ "IV"
-    ) %>% as_factor()) %>%
-    # Remove filler stimuli (i.e.,well-known objects)
-    filter(bek_unbek != "bekannt")
-  # Assign stimuli to conditions based on keywords and button presses
-  excl_known <- dat %>% filter(part == "I" & Tastencode %in% c(201, 251)) %>% pull(item)
-  excl_informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
-  excl_naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
-  informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
-  naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
-  # Create a new condition for the experimental condition
-  dat %<>% mutate(condition = case_when(
-    item %in% excl_known ~ "Excl_known",
-    item %in% excl_informed ~ "Excl_informed",
-    item %in% excl_naive ~ "Excl_naive",
-    item %in% informed ~ "Informed",
-    item %in% naive ~ "Naive"
-  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
-  # In Experiment 3, we need an additional column for position (upright vs. inverted)
-  if ("richtig_inv" %in% dat$Bed) {
-    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
-      # Return only relevant columns
-      select(part, position, condition, participant, item, RT)
-  } else {
-    # Return only relevant columns
-    dat %<>% select(part, condition, participant, item, RT)
-  }
-  return(dat)
-}
-
-# Read behavioral data for Experiment 1
-data_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)
-
-# Check average number of stimuli per condition and save to the export folder
-map(data_exp1, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  colMeans() %>%
-  saveRDS("analysis/export/exp1-stims.RDS")
-```
-
-```{python exp1-preprocessing, eval=rerun_preproc}
+```{python def_functions, eval=rerun_preproc}
 # Import libraries
 import mne
-import glob
-import os
-
-# Set parameters for EEG preprocessing
-preproc_params = dict(
-    n_components=15, method='fastica',         # ICA parameters
-    l_freq=0.1, h_freq=30,                     # Filter edges
-    event_id={'match': 221, 'mismatch': 222},  # EEG triggers
-    tmin=-0.5, tmax=1.498,                     # Length of epochs
-    baseline=(-0.2, 0),                        # Baseline correction
-    reject=dict(eeg=200)                       # Rejection threshold
-)
-
-# # For debugging
-# locals().update(preproc_params)
-# vhdr_fname = 'data/exp1/EEG/Vp0001.vhdr'
 
@@
 
-# List raw EEG filenames
-fnames_exp1 = sorted(glob.glob('data/exp1/EEG/*.vhdr'))
-
-# Import behavioral data from R
-metadata_exp1 = r.data_exp1
-
-# Apply the function to preprocess the EEG data for Experiment 1
-epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
-               for fname, meta in zip(fnames_exp1, metadata_exp1)]
-
-# Combine epochs into a single data set
-epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
+# # Define function to compute grand averages per condition
+# def compute_evokeds(epochs):
+#     evokeds = dict(); evokeds_dat = dict()
+#     # Each part becomes a dictionary of conditions
+#     for pt in ['I', 'II', 'III']:
+#         evokeds[pt] = dict(); evokeds_dat[pt] = dict()
+#         # Each condition becomes a list of participants
+#         for cn in ['Informed', 'Naive']:
+#             evokeds[pt][cn] = list(); evokeds_dat[pt][cn] = list()
+#             # For every participant we average trials separately for all parts and conditions
+#             for vp in epochs.metadata['participant'].unique():
+#                 query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
+#                 evokeds[pt][cn].append(epochs[query].average())
+#             # Compute grand averages across participants for this part and condition
+#             evokeds[pt][cn] = mne.grand_average(evokeds[pt][cn])
+#             # Export only the actual data for R
+#             evokeds_dat[pt][cn] = evokeds[pt][cn].data
+#     return (evokeds, evokeds_dat)
+
+# Define function to compute averaged waveforms by part and condition
+def compute_evokeds(epochs, grand=True, data_only=True):
+  # Define lists of participants, parts, and conditions
+  ps = epochs.metadata['participant'].unique()
+  pts = ['I', 'II', 'III']
+  cns = ['Informed', 'Naive']
+  # Define function to compute a single by-participant waveform
+  def compute_evoked(epochs, pt, cn, p):
+    query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
+    return(epochs[query].average())
+  # Create a dict with by-participant waveforms nested in conditions nested in parts
+  avgs = {pt:{cn:[compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
+  # If needed, compute grand-averaged waveforms across participants
+  if grand:
+    avgs = {pt:{cn:mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
+  # If needed, extract only the data from the evoked MNE objects
+  if data_only:
+    if grand:
+      avgs = {pt:{cn:avgs[pt][cn].data for cn in cns} for pt in pts}
+    else:
+      avgs = {pt:{cn:[avgs[pt][cn][p].data for p in range(0, len(ps))] for cn in cns} for pt in pts}
+  return(avgs)
+
+```
+
+```{r exp1-preproc, eval=rerun_preproc}
+# Define function for reading and formatting the behavioral data
+read_behav <- function(txt_fname) {
+  # Read the log file
+  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
+  # Rename columns for participant and item IDs
+  dat %<>% rename(participant = VPNummer, item = StimID) %>%
+    # Add a column for the part of the experiment
+    mutate(part = case_when(
+      Wdh %in% c(211, 231) ~ "I",
+      Wdh %in% c(212, 232) ~ "II",
+      Wdh %in% c(213, 233) ~ "III",
+      Wdh == 234 ~ "IV"
+    ) %>% as_factor()) %>%
+    # Remove filler stimuli (i.e.,well-known objects)
+    filter(bek_unbek != "bekannt")
+  # Assign stimuli to conditions based on keywords and button presses
+  excl_known <- dat %>%
+    filter(part == "I" & Tastencode %in% c(201, 251)) %>%
+    pull(item)
+  excl_informed <- dat %>%
+    filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
+    pull(item)
+  excl_naive <- dat %>%
+    filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>%
+    pull(item)
+  informed <- dat %>%
+    filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
+    pull(item)
+  naive <- dat %>%
+    filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>%
+    pull(item)
+  # Create a new condition for the experimental condition
+  dat %<>% mutate(condition = case_when(
+    item %in% excl_known ~ "Excl_known",
+    item %in% excl_informed ~ "Excl_informed",
+    item %in% excl_naive ~ "Excl_naive",
+    item %in% informed ~ "Informed",
+    item %in% naive ~ "Naive"
+  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
+  # In Experiment 3, we need an additional column for position (upright vs. inverted)
+  if ("richtig_inv" %in% dat$Bed) {
+    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
+      # Return only relevant columns
+      select(part, position, condition, participant, item, RT)
+  } else {
+    # Return only relevant columns
+    dat %<>% select(part, condition, participant, item, RT)
+  }
+  return(dat)
+}
+
+# Read behavioral data for Experiment 1
+list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp1
+
+# Backup number of stimuli assigned to each condition for all participants
+map(behav_exp1, function(x) table(x$condition) / 3) %>%
+  bind_rows() %>%
+  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
+  #summarise(across(.fns = mean)) %>%
+  #pivot_longer(cols = everything(), names_to = "condition", values_to = "objects") %T>%
+  write_tsv("analysis/export/exp1-objects.tsv")
+
+# Define global parameters for EEG preprocessing
+preproc_params <- list(
+  # Number of ICA components
+  n_components = as.integer(15),
+  # ICA methods
+  method = "fastica",
+  # Lower edge of pass-band filter
+  l_freq = 0.1,
+  # Upper edge of pass-band filter
+  h_freq = 30,
+  # Event trigger codes
+  event_id = dict(match = 221, mismatch = 222),
+  # Beginning of epochs in s
+  tmin = -0.5,
+  # End of epochs in s
+  tmax = 1.498,
+  # Baseline interval in s
+  baseline = tuple(-0.2, 0),
+  # Artifact rejection threshold in microvolts
+  reject = dict(eeg = 200)
+)
+
+# Actually apply the preprocessing function for Epxeriment 1 in Python
+map2(
+  .x = list.files("data/exp1/EEG", pattern = ".vhdr", full.names = TRUE),
+  .y = behav_exp1,
+  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
+) %>%
+  # Concatenate epochs of all participants
+  py$mne$epochs$concatenate_epochs() -> epochs_exp1
 
 # Backup epochs to the export folder
-epochs_exp1.save('analysis/export/exp1-epo.fif')
-
-# Backup the channel names separately
-
-# Check if preprocessing was done already (delete the file to re-run)
-if os.path.exists('analysis/export/exp1-epo.fif'):
-    # Read preprocessed data from file
-    epochs_exp1 = mne.read_epochs('analysis/export/exp1-epo.fif', preload=True)
-else:
-    # Preprocess EEG data for Experiment 1
-    epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
-                   for fname, meta in zip(fnames_exp1, metadata_exp1)]
-    # Combine epochs into a single data set
-    epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
-    # Backup epochs to the export folder
-    epochs_exp1.save('analysis/export/exp1-epo.fif')
-
-# Define function to compute grand averages per condition
-def compute_evokeds(epochs):
-    evokeds = dict(); evokeds_dat = dict()
-    # Each part becomes a dictionary of conditions
-    for pt in ['I', 'II', 'III']:
-        evokeds[pt] = dict(); evokeds_dat[pt] = dict()
-        # Each condition becomes a list of participants
-        for cn in ['Informed', 'Naive']:
-            evokeds[pt][cn] = list(); evokeds_dat[pt][cn] = list()
-            # For every participant we average trials separately for all parts and conditions
-            for vp in epochs.metadata['participant'].unique():
-                query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
-                evokeds[pt][cn].append(epochs[query].average())
-            # Compute grand averages across participants for this part and condition
-            evokeds[pt][cn] = mne.grand_average(evokeds[pt][cn])
-            # Export only the actual data for R
-            evokeds_dat[pt][cn] = evokeds[pt][cn].data
-    return (evokeds, evokeds_dat)
-
-# Compute grand averages for Experiment 1
-evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)
-
-import pickle
-with open('analysis/export/exp1-avgs.pickle', 'wb') as handle:
-    pickle.dump(evokeds_dat_exp1, handle, protocol=pickle.HIGHEST_PROTOCOL)
-```
-
-```{r backup}
-
-test <- py$preproc(
-  vhdr_fname = "data/exp1/EEG/Vp0001.vhdr",
-  metadata = data_exp1[[1]],
-  n_components = as.integer(15),
-  method = "fastica",
-  l_freq = 0.1,
-  h_freq = 30,
-  event_id = list(match = as.integer(221), mismatch = as.integer(222)),
-  tmin = -0.5,
-  tmax = 1.498,
-  baseline = tuple(-0.2, 0),
-  reject = list(eeg = 200))
-
-test$ch_names
+epochs_exp1$save("analysis/export/exp1-epo.fif")
+
+# Get standard EasyCap electrode positions and project to 2D space
+py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
+  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
+  read_tsv(col_types = cols()) %>%
+  rename(electrode = Site) %>%
+  inner_join(tibble(electrode = epochs_exp1$ch_names), ., by = "electrode") %>%
+  mutate(
+    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
+    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
+  ) %>%
+  write_tsv("analysis/export/montage.tsv")
+
+# Create a vector with sample time points (in ms)
+sfreq <- epochs_exp1$info["sfreq"]
+seq(preproc_params$tmin * 1000, preproc_params$tmax * 1000, 1 / sfreq * 1000) %T>%
+  cat(file = "analysis/export/sample_times.tsv", sep = "\n") -> times
+
+# Define function to compute single-trial mean ERP amplitudes
+compute_erps <- function(epochs, name, start, stop, roi) {
+  dat <- epochs$get_data()
+  els <- epochs$ch_names
+  erps <- dat[, which(els %in% roi), which(times %in% start:stop)]
+  amps <- apply(erps, 1, mean, na.rm = TRUE)
+  return(amps)
+}
+
+# Actually apply the function to compute mean ERP amplitudes for Experiment 1
+pmap_dfc(comps, compute_erps, epochs = epochs_exp1) %>%
+  set_names(comps$name) %>%
+  # Bind to the behavioral data
+  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
+  # Backup to the export folder
+  write_tsv("analysis/export/exp1-erps.tsv") -> data_exp1
+
+# Compute grand averages per part and condition
+py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
+  saveRDS("analysis/export/exp1-gavgs.RDS")
 ```
@@
 
-```{r exp1-analysis}
-# Re-import behavioral data and re-factorize some columns
-data_exp1 <- py$epochs_exp1$metadata %>% mutate(
+```{r exp1-models, eval=rerun_models}
+# Load preprocessed single-trial data
+read_tsv("analysis/export/exp1-erps.tsv", col_types = cols()) %>%
+  # Factorize columns
+  mutate(
     part = factor(part, levels = c("I", "II", "III")),
-  condition = factor(condition, levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")),
+    condition = factor(condition, levels = c(
+      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
+    ),
     participant = factor(participant),
     item = factor(item)
-)
-
-# Check number of rejected epochs
-rejected_exp1 <- data_exp1 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
-mean(rejected_exp1)    # Mean
-median(rejected_exp1)  # Median
-range(rejected_exp1)   # Range
-
-# Create vectors with sample time points (in ms) and electrodes
-times <- seq(py$preproc_params$tmin * 1000, py$preproc_params$tmax * 1000, 1 / py$epochs_exp1$info["sfreq"] * 1000)
-els <- py$epochs_exp1$ch_names
-
-# Define ERP components of interest
-comps <- tibble(
-  name = c("P1", "N170", "N400"),
-  start = c(100, 150, 400),
-  stop = c(150, 200, 700),
-  roi = list(
-    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
-    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
-    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
-  )
-)
-
-# Define function to compute single-trial mean ERP amplitudes
-compute_erps <- function(epochs, els, name, start, stop, roi) {
-  erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
-  amps <- apply(erps, 1, mean, na.rm = TRUE)
-  return(amps)
-}
-
-# # Define function to compute single-trial ERP latencies
-# compute_lats <- function(epochs, els, name, start, stop, roi) {
-#   erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
-#   samples <- apply(erps, MARGIN = c(1, 3), mean) %>% abs()
-#   areas <- apply(samples, MARGIN = 1, sum)
-#   cumss <- apply(samples, MARGIN = 1, cumsum) %>% asplit(MARGIN = 2)
-#   lats <- map2_int(cumss, areas, function(cums, area){which(cums < area / 2) %>% max()})
-#   lats <- start + lats * 2
-#   return(lats)
-# }
-
-# Check if single-trial ERPs were computed already (delete the file to re-run)
-if (file.exists("analysis/export/exp1-erps.RDS")) {
-  # Read data from file
-  data_exp1 <- readRDS("analysis/export/exp1-erps.RDS")
-} else {
-  # Compute single-trial ERPs for Experiment 1
-  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp1$get_data(), els = els) %>%
-    set_names(comps$name) %>%
-    cbind(data_exp1, .) %T>%
-    saveRDS("analysis/export/exp1-erps.RDS")
-}
-
-# Remove the epochs to free up memory
-py_run_string("del epochs_exp1")
-import("gc")$collect()
-
+  ) %>%
   # Remove any trials excluded from conditions
-data_exp1 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()
-
-# Contrast coding for condition (informed-naive) and part (2-1, 3-1)
-contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
-contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
+  filter(condition %in% c("Informed", "Naive")) %>%
+  droplevels() -> data_exp1
+
+# Define contrast coding for condition (informed-naive) and part (2-1, 3-1)
+contrasts_condition <- t(cbind(
+  c("Informed" = 1, "Naive" = -1)
+))
+contrasts_part <- t(cbind(
+  c("I" = -1, "II" = 1, "III" = 0),
+  c("I" = 0, "II" = -1, "III" = 1)
+))
+
+# Apply these contrasts to the factors in the data
 contrasts(data_exp1$condition) <- MASS::ginv(contrasts_condition)
@@
 
-# Set formula and parameters for linear mixed-effects regression models (LMMs)
-form_exp12 <- buildmer::tabulate.formula(
+# Define formula and parameters for linear mixed-effects regression models (LMMs)
+formula_exp12 <- buildmer::tabulate.formula(
   ~ part * condition + (part * condition | participant) + (part * condition | item)
 ) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-ctrl_params <- lme4::lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
-
-# Set formula for follow-up contrasts
+control <- lme4::lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
+
+# Define formula for follow-up contrasts
 specs_exp12 <- pairwise ~ condition | part
@@
   require(emmeans)
+  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
   build <- buildmer(
@@
   )
-  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans %>% as.data.frame()
-  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts %>% as.data.frame()
-  mod <- list(model = build@model, anova = build@anova, summary = build@summary, means = means, contrasts = conts)
-  return(mod)
-}
-
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("analysis/export/exp1-stats.RDS")) {
-  # Read models from file
-  models_exp1 <- readRDS("analysis/export/exp1-stats.RDS")
-} else {
-  # Compute LMMs for Experiment 1
-  models_exp1 <- map(
+  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans
+  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts
+  modlist <- list(
+    model = build@model,
+    anova = build@anova,
+    summary = build@summary,
+    means = means %>% as.data.frame(),
+    contrasts = conts %>% as.data.frame()
+  )
+  return(modlist)
+}
+
+# Actually apply the function to compute the models for Experiment 1
+map(
   comps$name,
   compute_models,
-    formula = form_exp12,
+  formula = formula_exp12,
   data = data_exp1,
-    control = ctrl_params,
+  control = control,
   specs = specs_exp12
-  ) %>% set_names(comps$name) %T>%
-    saveRDS("analysis/export/exp1-stats.RDS")
-}
+) %>%
+  set_names(comps$name) %T>%
+  saveRDS("analysis/export/exp1-mods.RDS") -> models_exp1
 ```
@@
 ```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
-# Locate standard montage file from MNE Python
-fname_montage <- list.files(
-  path = reticulate::py_discover_config()$python %>% str_remove("bin/.*"),
-  pattern = "easycap-M1.txt", full.names = TRUE, recursive = TRUE
-)[1]
-
-# Retrieve locations for the relevant electrodes from this montage
-montage <- py$evokeds_exp1$I$Informed$ch_names %>%
-  as_tibble() %>%
-  rename(electrode = value) %>%
-  left_join(
-    read_tsv(fname_montage, col_types = cols()) %>%
-      rename(electrode = Site),
-    by = "electrode"
-  ) %>%
+# # For debugging
+# epochs_exp1 <- py$mne$read_epochs("analysis/export/exp1-epo.fif")
+
+# Compute average number of objects per condition
+(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
+   summarise(across(.cols = -Participant, .fns = mean)) %>%
+   slice(1) %>% unlist() -> objects_exp1)
+
+# Load preprocessed single-trial data
+read_tsv("analysis/export/exp1-erps.tsv", col_types = cols()) %>%
+  # Factorize columns
   mutate(
-    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
-    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi))
-  )
+    part = factor(part, levels = c("I", "II", "III")),
+    condition = factor(condition, levels = c(
+      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
+    ),
+    participant = factor(participant),
+    item = factor(item)
+  ) -> data_exp1
+
+# Check number of rejected epochs
+data_exp1 %>%
+  group_by(participant) %>%
+  tally() %>%
+  mutate(n = 360 - n) %>%
+  pull(n) -> rejected_exp1
+mean(rejected_exp1)    # Mean
+median(rejected_exp1)  # Median
+range(rejected_exp1)   # Range
+
+# Load sample time points and electrode montage
+times <- scan("analysis/export/sample_times.tsv", quiet = TRUE)
+montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())
+
+# Load grand-averaged ERPs and linear mixed models
+evokeds_exp1 <- readRDS("analysis/export/exp1-gavgs.RDS")
+models_exp1 <- readRDS("analysis/export/exp1-mods.RDS")
 
@@
   plot_trials(),
-  plot_erps(comps = comps, evokeds = py$evokeds_dat_exp1, models = models_exp1, montage = montage),
+  plot_erps(comps = comps, evokeds = evokeds_exp1, models = models_exp1, montage = montage),
   nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
@@
 First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all further analyses those objects which participants classified as being known to them in the pre-insight part (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r format(round(stims_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
+This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
 Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
 Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
-This was the case for an average of `r format(round(stims_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
+This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
 Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of `r format(round(stims_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
 Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
@@
 # Check average number of stimuli per condition
-(stims_exp2 <- map(data_exp2, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
+(objects_exp2 <- map(data_exp2, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
 ```
@@
 All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
-An average of `r format(round(stims_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(stims_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of `r format(round(stims_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (= `r scales::percent(stims_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(stims_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (= `r scales::percent(stims_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+An average of `r format(round(objects_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
+Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (= `r scales::percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (= `r scales::percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
 Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
@@
 # Calculate average number of objects per condition in Experiments 1 and 2
-stims_joint <- (stims_exp1 + stims_exp2) / 2
+stims_joint <- (objects_exp1 + objects_exp2) / 2
 
@@
 # Check average number of stimuli per condition
-(stims_exp3 <- map(data_exp3, function(x) {
+(objects_exp3 <- map(data_exp3, function(x) {
   x %<>% filter(part != "IV")

### 2021-01-17 analysis/manuscript.Rmd
remove messages from tables, add latex packages to dockerfile

@@
   - id            : "1"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
+    institution   : "Humboldt-Universität zu Berlin"
   - id            : "2"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
+    institution   : "Max Planck Institute for Human Cognitive and Brain Sciences"
   - id            : "3"
-    institution   : "Fachhochschule des Mittelstands, Bamberg, Germany"
+    institution   : "Fachhochschule des Mittelstands"
 
@@
 
+# Do you want to run the analysis for Experiment 3?
+run_exp3 <- FALSE
+
 # Load packages
@@
 # Experiment 1
+
+## Method
+
+### Participants
+
+Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
+No a priori power analysis was carried out and the sample size was chosen in line with other EEG studies in our lab at the time of data collection.
+All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
+They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+
+### Materials
+
+Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum).
+A list of these unfamiliar objects can be found in the appendix.
+All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
+At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
+
+For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g., current--measuring, pottery--drumming).
+As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects.
+The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive.
+All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
+This assignment of keywords to objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
+The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
+
+### Procedure
+
+Each experimental session consisted of three parts (see Figure \@ref(fig:exp1-plot)A).
+In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
+Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
+The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
+The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
 
@@
     return epochs
-
-# # Define function to compute grand averages per condition
-# def compute_evokeds(epochs):
-#     evokeds = dict(); evokeds_dat = dict()
-#     # Each part becomes a dictionary of conditions
-#     for pt in ['I', 'II', 'III']:
-#         evokeds[pt] = dict(); evokeds_dat[pt] = dict()
-#         # Each condition becomes a list of participants
-#         for cn in ['Informed', 'Naive']:
-#             evokeds[pt][cn] = list(); evokeds_dat[pt][cn] = list()
-#             # For every participant we average trials separately for all parts and conditions
-#             for vp in epochs.metadata['participant'].unique():
-#                 query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
-#                 evokeds[pt][cn].append(epochs[query].average())
-#             # Compute grand averages across participants for this part and condition
-#             evokeds[pt][cn] = mne.grand_average(evokeds[pt][cn])
-#             # Export only the actual data for R
-#             evokeds_dat[pt][cn] = evokeds[pt][cn].data
-#     return (evokeds, evokeds_dat)
 
@@
 
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp1, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
-  #summarise(across(.fns = mean)) %>%
-  #pivot_longer(cols = everything(), names_to = "condition", values_to = "objects") %T>%
-  write_tsv("analysis/export/exp1-objects.tsv")
-
 # Define global parameters for EEG preprocessing
@@
   # Event trigger codes
-  event_id = dict(match = 221, mismatch = 222),
+  event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
   # Beginning of epochs in s
@@
   saveRDS("analysis/export/exp1-gavgs.RDS")
-```
-
-```{python exp1-tfr, eval=FALSE}
-# TFR
-import numpy as np
-import matplotlib.pyplot as plt
-
-# chans = mne.pick_channels(epochs_exp1.ch_names, include=["PO3", "PO4", "POz", "O1", "O2", "Oz", "P7", "P8", "PO7", "PO8", "PO9", "PO10"])
-# 
-# epochs = mne.channels.combine_channels(epochs_exp1, dict(roi=chans))
-# epochs.metadata = epochs_exp1.metadata
-
-# epochs.plot_psd(fmin=2., fmax=40., average=True, spatial_colors=False); plt.show()
-# epochs.plot_psd_topomap(normalize=True); plt.show()
-
-freqs = np.logspace(*np.log10([4, 30]), num=8)
-n_cycles = freqs / 2.  # different number of cycle per frequency
-
-epochs_informed = epochs_exp1["part == 'II' & condition == 'Informed'"]
-epochs_naive = epochs_exp1["part == 'II' & condition == 'Naive'"]
-
-power_informed = mne.time_frequency.tfr_morlet(epochs_informed, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
-power_naive = mne.time_frequency.tfr_morlet(epochs_naive, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
-
-freqs = np.arange(start=4, stop=30, step=1)
-n_cycles = freqs / 2.  # different number of cycle per frequency
-
-evokeds_informed = evokeds_exp1["I"]["Informed"]
-evokeds_naive = evokeds_exp1["I"]["Naive"]
-
-power_informed = mne.time_frequency.tfr_morlet(evokeds_informed, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
-power_naive = mne.time_frequency.tfr_morlet(evokeds_naive, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
-
-power_diff = power_informed - power_naive
-power_diff.plot(baseline=(-0.3, 0), mode = "percent", tmin=-0.3, tmax = 0.7, vmin=-200, vmax=200); plt.show()
-
-power_diff.plot_joint(baseline=(-0.5, 0), mode = "percent", vmin=-100, vmax=100, timefreqs=(0.175, 12)); plt.show()
-
-#power_diff.plot_topomap(fmin=8, fmax=14, baseline=(-0.5, 0), mode="mean", vmin=-200, vmax=200, title="alpha"); plt.show()
-#power_diff.plot_topomap(fmin=15, fmax=30, baseline=(-0.5, 0), mode="mean", vmin=-200, vmax=200, title="beta"); plt.show()
+
+# Backup number of stimuli assigned to each condition for all participants
+map(behav_exp1, function(x) table(x$condition) / 3) %>%
+  bind_rows() %>%
+  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
+  write_tsv("analysis/export/exp1-objects.tsv")
 ```
@@
 
-## Method
-
-### Participants
-
-Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
-No a priori power analysis was carried out and the sample size was chosen in line with other EEG studies in our lab at the time of data collection.
-All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
-They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-
-### Materials
-
-Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum).
-A list of these unfamiliar objects can be found in the appendix.
-All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
-At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
-
-For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g., current--measuring, pottery--drumming).
-As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive.
-All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
-The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
-
-### Procedure
-
-Each experimental session consisted of three parts (see Figure \@ref(fig:exp1-plot)A).
-In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
-Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
-The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
-The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
-
-(ref:figure-1-caption) Procedure and Results of Experiment 1\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\emph{Note.} 
-(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
-In the post-insight part, the same objects were presented again without the keywords.
-(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
-Ampl.
-= amplitude.\newline
-*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.
-
--->
-
-```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
-# # For debugging
-# epochs_exp1 <- py$mne$read_epochs("analysis/export/exp1-epo.fif")
-
-# Compute average number of objects per condition
+```{r exp1-import}
+# Load average number of objects per condition
 (read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
@@
 
+# Load grand-averaged ERPs and linear mixed models
+evokeds_exp1 <- readRDS("analysis/export/exp1-gavgs.RDS")
+models_exp1 <- readRDS("analysis/export/exp1-mods.RDS")
+```
+
+```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
 # Load sample time points and electrode montage
@@
 
-# Load grand-averaged ERPs and linear mixed models
-evokeds_exp1 <- readRDS("analysis/export/exp1-gavgs.RDS")
-models_exp1 <- readRDS("analysis/export/exp1-mods.RDS")
-
 # Trial structure
 plot_trials <- function(){
-  require(magick)
+  suppressMessages(require(magick))
   color_informed <- viridisLite::viridis(1, begin = 0.1)
@@
   get_legend(
-    tibble(amplitude = c(-1, 1), condition = c("Informed", "Naive")) %>%
+    tibble(amplitude = c(-1, 0, 1), condition = c("Informed", "Naive", "Informed")) %>%
       ggplot(aes(x = 0, y = 0, color = condition, fill = amplitude)) +
@@
 
+(ref:figure-1-caption) Procedure and Results of Experiment 1\smallskip
+
+<!--
+
+The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
+Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
+
+\bigskip\small\emph{Note.} 
+(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
+In the post-insight part, the same objects were presented again without the keywords.
+(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
+Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
+Ampl.
+= amplitude.\newline
+*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.
+
+-->
+
 In the *insight* part, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
@@
       "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)
-    ) %>% mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>% set_rownames(c(stub_anova))
+    ) %>%
+      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
+      set_rownames(c(stub_anova))
   })
+  suppressMessages(
     anov_print <- anov %>%
@@
       set_rownames(c("\\textit{Fixed effects}", stub_anova))
+  )
+  suppressMessages(
     anov %<>%
@@
       set_colnames(paste(rep(names(models), each = length(names(models))), c("f", "df", "p"), sep = "_"))
+  )
   conts <- map(models, function(model) {
@@
       "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)
-    ) %>% mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>% set_rownames(stub_contrasts)
+    ) %>%
+      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
+      set_rownames(stub_contrasts)
   })
+  suppressMessages(
     conts_print <- conts %>%
@@
       set_rownames(c("\\textit{Informed $-$  naive}", stub_contrasts))
+  )
+  suppressMessages(
     conts %<>%
@@
       set_colnames(paste(rep(names(models), each = length(names(models))), c("est", "ci", "p"), sep = "_"))
+  )
   cnames <- c("\\textit{Fixed effects}", as.character(anov_print[1, ]))
@@
       caption = caption, note = note
-    ) %>% cat()
+    ) %>%
+    cat()
   return(list("anov" = anov, "conts" = conts))
@@
 
-```{r exp2-preparation}
+### Participants
+
+Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29 years) who had not participated in Experiment 1.
+They had no history of psychological disorders or treatment, were right-handed, and reported normal or corrected-to-normal vision.
+They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+
+### Materials, Procedure, and Analysis
+
+```{r exp2-preproc, eval=rerun_preproc}
 # Read behavioral data for Experiment 2
-data_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)
-
-# Check average number of stimuli per condition
-(objects_exp2 <- map(data_exp2, function(x) {table(x$condition) / 3}) %>% bind_rows() %>% colMeans())
-```
-
-```{python exp2-preprocessing}
-# List raw EEG filenames
-fnames_exp2 = sorted(glob.glob("data/exp2/EEG/*.vhdr"))
-
-# Import behavioral data from R
-metadata_exp2 = r.data_exp2
-
-# Check if preprocessing was done already (delete the file to re-run)
-if os.path.exists("analysis/export/exp2-epo.fif"):
-    # Read preprocessed data from file
-    epochs_exp2 = mne.read_epochs("analysis/export/exp2-epo.fif", preload=True)
-else:
-    # Preprocess EEG data for Experiment 2
-    epochs_exp2 = [
-        preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp2, metadata_exp2)
-    ]
-    # Combine epochs into a single data set
-    epochs_exp2 = mne.concatenate_epochs(epochs_exp2)
+list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp2
+
+# Apply the preprocessing function for Epxeriment 2 in Python
+map2(
+  .x = list.files("data/exp2/EEG", pattern = ".vhdr", full.names = TRUE),
+  .y = behav_exp2,
+  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
+) %>%
+  # Concatenate epochs of all participants
+  py$mne$epochs$concatenate_epochs() -> epochs_exp2
+
 # Backup epochs to the export folder
-    epochs_exp2.save("analysis/export/exp2-epo.fif")
-
-# Compute grand averages for Experiment 2
-evokeds_exp2, evokeds_dat_exp2 = compute_evokeds(epochs=epochs_exp2)
-```
-
-```{r exp2-analysis}
-# Re-import behavioral data and re-factorize some columns
-data_exp2 <- py$epochs_exp2$metadata %>% mutate(
+epochs_exp2$save("analysis/export/exp2-epo.fif")
+
+# Apply the function to compute mean ERP amplitudes for Experiment 2
+pmap_dfc(comps, compute_erps, epochs = epochs_exp2) %>%
+  set_names(comps$name) %>%
+  # Bind to the behavioral data
+  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
+  # Backup to the export folder
+  write_tsv("analysis/export/exp2-erps.tsv") -> data_exp2
+
+# Compute grand averages per part and condition
+py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
+  saveRDS("analysis/export/exp2-gavgs.RDS")
+
+# Backup number of stimuli assigned to each condition for all participants
+map(behav_exp2, function(x) table(x$condition) / 3) %>%
+  bind_rows() %>%
+  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
+  write_tsv("analysis/export/exp2-objects.tsv")
+```
+
+```{r exp2-models, eval=rerun_models}
+# Load preprocessed single-trial data
+read_tsv("analysis/export/exp2-erps.tsv", col_types = cols()) %>%
+  # Factorize columns
+  mutate(
     part = factor(part, levels = c("I", "II", "III")),
-  condition = factor(condition, levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")),
+    condition = factor(condition, levels = c(
+      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
+    ),
     participant = factor(participant),
     item = factor(item)
-)
+  ) %>%
+  # Remove any trials excluded from conditions
+  filter(condition %in% c("Informed", "Naive")) %>%
+  droplevels() -> data_exp2
+
+# Apply these contrasts to the factors in the data
+contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
+contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)
+
+# Apply the function to compute the models for Experiment 2
+map(
+  comps$name,
+  compute_models,
+  formula = formula_exp12,
+  data = data_exp2,
+  control = control,
+  specs = specs_exp12
+) %>%
+  set_names(comps$name) %T>%
+  saveRDS("analysis/export/exp2-mods.RDS") -> models_exp2
+```
+
+```{r exp2-import}
+# Load average number of objects per condition
+(read_tsv("analysis/export/exp2-objects.tsv", col_types = cols()) %>%
+   summarise(across(.cols = -Participant, .fns = mean)) %>%
+   slice(1) %>% unlist() -> objects_exp2)
+
+# Load preprocessed single-trial data
+read_tsv("analysis/export/exp2-erps.tsv", col_types = cols()) %>%
+  # Factorize columns
+  mutate(
+    part = factor(part, levels = c("I", "II", "III")),
+    condition = factor(condition, levels = c(
+      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
+    ),
+    participant = factor(participant),
+    item = factor(item)
+  ) -> data_exp2
 
 # Check number of rejected epochs
-rejected_exp2 <- data_exp2 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
+data_exp2 %>%
+  group_by(participant) %>%
+  tally() %>%
+  mutate(n = 360 - n) %>%
+  pull(n) -> rejected_exp2
 mean(rejected_exp2)    # Mean
@@
 
-# Check if single-trial ERPs were computed already (delete the file to re-run)
-if (file.exists("analysis/export/exp2-erps.RDS")) {
-  # Read data from file
-  data_exp2 <- readRDS("analysis/export/exp2-erps.RDS")
-} else {
-  # Compute single-trial ERPs for Experiment 2
-  data_exp2 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp2$get_data(), els = els) %>%
-    set_names(comps$name) %>%
-    cbind(data_exp2, .) %T>%
-    saveRDS("analysis/export/exp2-erps.RDS")
-}
-
-# Remove the epochs to free up memory
-py_run_string("del epochs_exp2")
-import("gc")$collect()
-
-# Remove any trials excluded from conditions
-data_exp2 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()
-
-# Contrast coding for condition (informed-naive) and part (2-1, 3-1)
-contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)
-
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("analysis/export/exp2-stats.RDS")) {
-  # Read models from file
-  models_exp2 <- readRDS("analysis/export/exp2-stats.RDS")
-} else {
-  # Compute LMMs for Experiment 2
-  models_exp2 <- map(
-    comps$name,
-    compute_models,
-    formula = form_exp12,
-    data = data_exp2,
-    control = ctrl_params,
-    specs = specs_exp12
-  ) %>% set_names(comps$name) %T>%
-    saveRDS("analysis/export/exp2-stats.RDS")
-}
-```
-
-### Participants
-
-Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29 years) who had not participated in Experiment 1.
-They had no history of psychological disorders or treatment, were right-handed, and reported normal or corrected-to-normal vision.
-They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-
-### Materials, Procedure, and Analysis
+# Load grand-averaged ERPs and linear mixed models
+evokeds_exp2 <- readRDS("analysis/export/exp2-gavgs.RDS")
+models_exp2 <- readRDS("analysis/export/exp2-mods.RDS")
+```
 
@@
 
-(ref:figure-2-caption) Results of Experiment 2\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\emph{Note.} 
-ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
-Ampl.
-= amplitude.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.
-
--->
-
 ```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:figure-2-caption)"}
@@
   plot_headings(spacing = c(10, 1, 10, 1, 10)),
-  plot_erps(comps = comps, evokeds = py$evokeds_dat_exp2, models = models_exp2, montage = montage),
+  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
   plot_legends_erps(direction = "horizontal"),
@@
 
+(ref:figure-2-caption) Results of Experiment 2\smallskip
+
+<!--
+
+The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
+Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
+
+\bigskip\small\emph{Note.} 
+ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
+Ampl.
+= amplitude.\newline*\emph{p} \textless{} .05.
+**\emph{p} \textless{} .01.
+***\emph{p} \textless{} .001.
+
+-->
+
 ### ERPs Before Insight Was Occurring
@@
 
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp1$conts["Insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Insight part", "N400_p"]`.
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp2$conts["Insight part", "N400_est"]` µV, *p* `r table_exp2$conts["Insight part", "N400_p"]`.
 
@@
 
-```{r joint-analysis}
+```{r joint-import}
 # Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
-data_joint <- data_exp2 %>%
+data_exp2 %>%
   mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
   bind_rows(data_exp1, ., .id = "experiment") %>%
-  mutate(experiment = as_factor(experiment))
-
+  mutate(experiment = as_factor(experiment)) -> data_joint
+
+# Subset only the relevant conditions
+data_joint %>%
+  filter(condition %in% c("Informed", "Naive")) %>%
+  droplevels() -> data_joint_subs
+```
+
+```{r joint-models, eval=rerun_models}
 # Contrast coding for experiment (2-1), condition (informed-naive), and part (2-1, 3-1)
 t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
-contrasts(data_joint$experiment) <- MASS::ginv(contrasts_experiment)
-contrasts(data_joint$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_joint$part) <- MASS::ginv(contrasts_part)
+contrasts(data_joint_subs$experiment) <- MASS::ginv(contrasts_experiment)
+contrasts(data_joint_subs$condition) <- MASS::ginv(contrasts_condition)
+contrasts(data_joint_subs$part) <- MASS::ginv(contrasts_part)
 
@@
 form_joint <- buildmer::tabulate.formula(
-  ~ part * condition * experiment + (part * condition | participant) + (part * condition * experiment | item)
+  ~ part * condition * experiment + 
+    (part * condition | participant) + 
+    (part * condition * experiment | item)
 ) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
 
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("analysis/export/joint-stats.RDS")) {
-  # Read models from file
-  models_joint <- readRDS("analysis/export/joint-stats.RDS")
-} else {
-  # Compute LMMs for Experiments 1 and 2 combined
-  models_joint <- map(
+# Apply the function to compute the joint models for Experiments 1 and 2
+map(
   comps$name,
@@
   formula = form_joint,
-    data = data_joint,
-    control = ctrl_params,
+  data = data_joint_subs,
+  control = control,
   specs = specs_exp12
-  ) %>% set_names(comps$name) %T>%
-    saveRDS("analysis/export/joint-stats.RDS")
-}
+) %>%
+  set_names(comps$name) %T>%
+  saveRDS("analysis/export/joint-mods.RDS") -> models_joint
 ```
@@
 ```{r joint-table, include=TRUE, results="asis"}
+# Load linear mixed models
+models_joint <- readRDS("analysis/export/joint-mods.RDS")
+
 # Create table of models for Experiments 1 and 2 combined
@@
   plot_headings(spacing = c(10, 2, 10, 2, 10)),
-  plot_violins(data = data_joint, models = models_joint),
+  plot_violins(data = data_joint_subs, models = models_joint),
   nrow = 2, rel_heights = c(0.3, 6.7)
@@
 
-```{r control-analysis}
-# Calculate average number of objects per condition in Experiments 1 and 2
-stims_joint <- (objects_exp1 + objects_exp2) / 2
-
-# Re-load saved ERPs from Experiments 1 and 2
-data_joint_control <- bind_rows(
-  readRDS("analysis/export/exp1-erps.RDS"),
-  readRDS("analysis/export/exp2-erps.RDS") %>%
-    mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))),
-  .id = "experiment"
-) %>% mutate(experiment = as_factor(experiment))
-
+```{r control-models, eval=rerun_models}
 # # Keep all three conditions
@@
 # This time, we keep only the two conditions with matching keywords
-data_joint_control %<>% filter(condition %in% c("Informed", "Excl_informed")) %>% droplevels()
+data_joint %>%
+  filter(condition %in% c("Informed", "Excl_informed")) %>%
+  droplevels() -> data_joint_control
 
@@
 
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("analysis/export/joint-control-stats.RDS")) {
-  # Read models from file
-  models_joint_control <- readRDS("analysis/export/joint-control-stats.RDS")
-} else {
-  # Re-compute LMMs for Experiments 1 and 2 combined
-  models_joint_control <- map(
+# Apply the function to re-compute the joint models
+map(
   comps$name,
@@
   formula = form_joint,
-    data = data_joint_control,
-    control = ctrl_params,
+  data = data_joint_subs,
+  control = control,
   specs = specs_exp12
-  ) %>% set_names(comps$name) %T>%
-    saveRDS("analysis/export/joint-control-stats.RDS")
-}
+) %>%
+  set_names(comps$name) %T>%
+  saveRDS("analysis/export/joint-control-mods.RDS") -> models_joint_control
+```
+
+```{r control-table}
+# Calculate average number of objects per condition in Experiments 1 and 2
+(stims_joint <- (objects_exp1 + objects_exp2) / 2)
+
+# Load linear mixed models
+models_joint_control <- readRDS("analysis/export/joint-control-mods.RDS")
 
@@
 
+```{python exp1-tfr, eval=FALSE}
+# TFR
+import numpy as np
+import matplotlib.pyplot as plt
+
+# chans = mne.pick_channels(epochs_exp1.ch_names, include=["PO3", "PO4", "POz", "O1", "O2", "Oz", "P7", "P8", "PO7", "PO8", "PO9", "PO10"])
+# 
+# epochs = mne.channels.combine_channels(epochs_exp1, dict(roi=chans))
+# epochs.metadata = epochs_exp1.metadata
+
+# epochs.plot_psd(fmin=2., fmax=40., average=True, spatial_colors=False); plt.show()
+# epochs.plot_psd_topomap(normalize=True); plt.show()
+
+freqs = np.logspace(*np.log10([4, 30]), num=8)
+n_cycles = freqs / 2.  # different number of cycle per frequency
+
+epochs_informed = epochs_exp1["part == 'II' & condition == 'Informed'"]
+epochs_naive = epochs_exp1["part == 'II' & condition == 'Naive'"]
+
+power_informed = mne.time_frequency.tfr_morlet(epochs_informed, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
+power_naive = mne.time_frequency.tfr_morlet(epochs_naive, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
+
+freqs = np.arange(start=4, stop=30, step=1)
+n_cycles = freqs / 2.  # different number of cycle per frequency
+
+evokeds_informed = evokeds_exp1["I"]["Informed"]
+evokeds_naive = evokeds_exp1["I"]["Naive"]
+
+power_informed = mne.time_frequency.tfr_morlet(evokeds_informed, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
+power_naive = mne.time_frequency.tfr_morlet(evokeds_naive, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
+
+power_diff = power_informed - power_naive
+power_diff.plot(baseline=(-0.3, 0), mode = "percent", tmin=-0.3, tmax = 0.7, vmin=-200, vmax=200); plt.show()
+
+power_diff.plot_joint(baseline=(-0.5, 0), mode = "percent", vmin=-100, vmax=100, timefreqs=(0.175, 12)); plt.show()
+
+#power_diff.plot_topomap(fmin=8, fmax=14, baseline=(-0.5, 0), mode="mean", vmin=-200, vmax=200, title="alpha"); plt.show()
+#power_diff.plot_topomap(fmin=15, fmax=30, baseline=(-0.5, 0), mode="mean", vmin=-200, vmax=200, title="beta"); plt.show()
+```
+
 # General Discussion
@@
 
-\setlength{\cslhangindent}{0.5in}
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2021-01-17 analysis/manuscript.tex
remove messages from tables, add latex packages to dockerfile

@@
   man,floatsintext]{apa7}
-\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
+\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
@@
 \shorttitle{Semantic Knowledge and Unfamiliar Objects}
-\keywords{objects, semantic knowledge, visual perception, event-related potentials\newline\indent Word count: }
+\keywords{objects, semantic knowledge, visual perception, event-related potentials}
 \usepackage{csquotes}
@@
 \raggedbottom
+\usepackage[all]{nowidow}
+\usepackage[bottom]{footmisc}
+\interfootnotelinepenalty=10000
 \usepackage{setspace}
@@
 \captionsetup[figure]{font={stretch=1.5}}
-\usepackage[all]{nowidow}
-\usepackage[bottom]{footmisc}
-\interfootnotelinepenalty=10000
 \ifxetex
@@
 \else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
+  \usepackage[shorthands=off,main=english]{babel}
 \fi
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Humboldt-Universität zu Berlin\\\textsuperscript{2} Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany\\\textsuperscript{3} Fachhochschule des Mittelstands, Bamberg, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Humboldt-Universität zu Berlin\\\textsuperscript{2} Max Planck Institute for Human Cognitive and Brain Sciences\\\textsuperscript{3} Fachhochschule des Mittelstands}
 
@@
 The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world is ``cognitively impenetrable'' or, in other words, determined solely by the visual input reaching our retina.
-According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1984, 1983; Pylyshyn, 1999).
+This debate revolves around the question of whether or not our perception of the (visual) world is \enquote{cognitively impenetrable} or, in other words, determined solely by the visual input reaching our retina.
+According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1983, 1984; Pylyshyn, 1999).
 Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects (DiCarlo et al., 2012; Goodale \& Milner, 1992; Marr, 1982).
 
-This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., P.
-M.
-Churchland, 1988; P.
-S.
-Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017).
+This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., Churchland, 1988; Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017).
 The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas (e.g., visual areas V1 and V2; Bullier, 2001; Gilbert \& Li, 2013)---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
@@
 These aspects of cognition may include transient states such as emotions (e.g., Bocanegra \& Zeelenberg, 2009; Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019).
-Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).
-
-One productive way to investigate the top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical and pointed out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).
+They have argued, for example, that most behavioral paradigms have not been able to discern between perceptual and postperceptual (e.g., memory-related) effects.
+Furthermore, cognitive influences in some studies have been confounded with differences in the lower-level visual input.
+We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our methodology and results.
+
+In general, however, it is important to note that one productive way to circumvent some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
 This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
@@
 
-Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge about visual objects (Abdel Rahman \& Sommer, 2008; Gratton et al., 2009; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Rossion et al., 2004, 2002; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
+Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge about visual objects (Abdel Rahman \& Sommer, 2008; Gratton et al., 2009; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Tanaka \& Curran, 2001; Weller et al., 2019).
 Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing.
@@
 
-A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects which were rendered difficult to recognize by converting them to two-tone, ``Mooney'' images (Samaha et al., 2018, Experiment 4).
+A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects which were rendered difficult to recognize by converting them to two-tone, \enquote{Mooney} images (Samaha et al., 2018, Experiment 4).
 In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
@@
 
-All the previously mentioned studies have in common that they investigated the effects of semantic knowledge on the visual perception of objects only \emph{after} an extensive learning phase had taken place (Abdel Rahman \& Sommer, 2008; Gauthier, James, et al., 2003; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Rossion et al., 2004, 2002; Samaha et al., 2018; Weller et al., 2019).
+All the previously mentioned studies have in common that they investigated the effects of semantic knowledge on the visual perception of objects only \emph{after} an extensive learning phase had taken place (Abdel Rahman \& Sommer, 2008; Gauthier, James, et al., 2003; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Rossion et al., 2002, 2004; Samaha et al., 2018; Weller et al., 2019).
 Participants performed one or multiple training sessions during which they encountered each object together with its respective label or description multiple times.
-The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Abdel Rahman, 2019) or were spread out across multiple days or weeks (Rossion et al., 2004, 2002).
+The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Abdel Rahman, 2019) or were spread out across multiple days or weeks (Rossion et al., 2002, 2004).
 While experimental designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they leave at least three conceptual questions unresolved.
@@
 The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) ``I know what this is or have a strong assumption,'' (b) ``I have an assumption what this is,'' (c) ``I have rather no assumption what this is,'' or (d) ``I don't know what this is and have no assumption.'' Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) \enquote{I know what this is or have a strong assumption,} (b) \enquote{I have an assumption what this is,} (c) \enquote{I have rather no assumption what this is,} or (d) \enquote{I don't know what this is and have no assumption.} Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
@@
 Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
-Only in the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception to occur, whereas the other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
+In the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception.
+The other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
 The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \ref{fig:exp1-plot}A), thereby making sure that semantically informed and naive perception did indeed occur.
@@
 \midrule
-Part & 10.89 (2, 24.5) & < .001 & 14.18 (2, 24.9) & < .001 & 32.85 (2, 25.6) & < .001\\
-Condition & 0.60 (1, 5343.5) & .438 & 0.30 (1, 24.2) & .586 & 13.00 (1, 24.4) & .001\\
-Pt. × con. & 2.30 (2, 4605.0) & .100 & 4.84 (2, 4878.2) & .008 & 10.91 (2, 5120.9) & < .001\\
+Part & 10.82 (2, 24.5) & < .001 & 14.15 (2, 24.9) & < .001 & 33.01 (2, 25.5) & < .001\\
+Condition & 0.87 (1, 5302.9) & .351 & 0.89 (1, 114.3) & .349 & 13.09 (1, 24.8) & .001\\
+Pt. × con. & 2.40 (2, 4590.9) & .091 & 5.34 (2, 4853.1) & .005 & 11.18 (2, 5030.2) & < .001\\
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & -0.03 [-0.53, 0.47] & .913 & -0.12 [-0.68, 0.44] & .665 & -0.20 [-0.65, 0.26] & .400\\
-Insight part & -0.18 [-0.68, 0.32] & .490 & -0.64 [-1.20, -0.08] & .026 & 0.93 [0.48, 1.39] & < .001\\
-Post-insight part & 0.55 [0.05, 1.05] & .031 & 0.43 [-0.14, 0.99] & .136 & 1.00 [0.54, 1.46] & < .001\\
+Pre-insight part & 0.00 [-0.50, 0.49] & .987 & -0.17 [-0.64, 0.30] & .485 & -0.20 [-0.65, 0.26] & .393\\
+Insight part & -0.15 [-0.65, 0.34] & .550 & -0.66 [-1.14, -0.19] & .006 & 0.93 [0.48, 1.39] & < .001\\
+Post-insight part & 0.57 [0.08, 1.07] & .023 & 0.41 [-0.07, 0.88] & .094 & 1.00 [0.55, 1.46] & < .001\\
 \bottomrule
@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.89, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp1-table}).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}(1, 24.4) = 13.00, \emph{p} = .001.
-Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4605.0) = 2.30, \emph{p} = .100.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.82, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp1-table}).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}(1, 24.8) = 13.09, \emph{p} = .001.
+Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4853.1) = 5.34, \emph{p} = .005, and in the N400 component, \emph{F}(2, 5030.2) = 11.18, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4590.9) = 2.40, \emph{p} = .091.
 To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
@@
 
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .400 (see Table \ref{tab:exp1-table} and Figure \ref{fig:exp1-plot}B).
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .393 (see Table \ref{tab:exp1-table} and Figure \ref{fig:exp1-plot}B).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs.~naive perception) had not yet taken place.
@@
 In the insight part, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e.,~more negative), \emph{b} = -0.64 µV, \emph{p} = .026, and the amplitude of the N400 component was significantly reduced (i.e.,~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when the object was viewed naively without relevant semantic information.
-As in the pre-insight part, there were no reliable differences in the P1 component, \emph{p} = .490.
+When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e.,~more negative), \emph{b} = -0.66 µV, \emph{p} = .006, and the amplitude of the N400 component was significantly reduced (i.e.,~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when the object was viewed naively without relevant semantic information.
+As in the pre-insight part, there were no reliable differences in the P1 component, \emph{p} = .550.
 
@@
 In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part), to test whether the semantic information had any lasting effects on the processing of the objects.
-As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the effect in the N170 component did not reoccur, \emph{p} = .136.
-Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e.,~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.55 µV, \emph{p} = .031.
+As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the effect in the N170 component did not reoccur, \emph{p} = .094.
+Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e.,~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.57 µV, \emph{p} = .023.
 
@@
 \midrule
-Part & 17.45 (2, 5267.1) & < .001 & 16.57 (2, 25.1) & < .001 & 70.12 (2, 25.2) & < .001\\
-Condition & 0.02 (1, 5276.9) & .900 & 0.98 (1, 5228.5) & .322 & 19.95 (1, 5242.5) & < .001\\
-Pt. × con. & 3.60 (2, 5267.1) & .027 & 1.25 (2, 4756.5) & .287 & 7.92 (2, 4714.9) & < .001\\
+Part & 18.14 (2, 5151.1) & < .001 & 16.39 (2, 25.0) & < .001 & 70.58 (2, 25.2) & < .001\\
+Condition & 0.03 (1, 5272.5) & .853 & 1.23 (1, 5218.6) & .267 & 18.66 (1, 5207.5) & < .001\\
+Pt. × con. & 3.74 (2, 5151.2) & .024 & 1.34 (2, 4736.8) & .263 & 8.07 (2, 4637.6) & < .001\\
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & -0.16 [-0.71, 0.40] & .582 & -0.03 [-0.53, 0.48] & .920 & 0.04 [-0.43, 0.50] & .877\\
-Insight part & -0.48 [-1.03, 0.08] & .094 & -0.48 [-0.99, 0.03] & .064 & 1.33 [0.87, 1.79] & < .001\\
-Post-insight part & 0.57 [0.01, 1.13] & .047 & 0.06 [-0.45, 0.57] & .818 & 0.47 [0.01, 0.93] & .047\\
+Pre-insight part & -0.17 [-0.72, 0.38] & .552 & -0.04 [-0.53, 0.45] & .864 & 0.02 [-0.44, 0.48] & .936\\
+Insight part & -0.49 [-1.04, 0.07] & .084 & -0.50 [-0.99, 0.00] & .050 & 1.31 [0.86, 1.77] & < .001\\
+Post-insight part & 0.56 [0.01, 1.11] & .048 & 0.04 [-0.45, 0.54] & .865 & 0.45 [-0.01, 0.91] & .055\\
 \bottomrule
@@
 
-As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.57, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp2-table}).
-Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}(1, 5242.5) = 19.95, \emph{p} \textless{} .001.
-The part × condition interaction was significant in the P1 component, \emph{F}(2, 5267.1) = 3.60, \emph{p} = .027, and in the N400 component, \emph{F}(2, 4714.9) = 7.92, \emph{p} \textless{} .001, but not in the N170 component, \emph{F}(2, 4756.5) = 1.25, \emph{p} = .287.
+As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.39, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp2-table}).
+Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}(1, 5207.5) = 18.66, \emph{p} \textless{} .001.
+The part × condition interaction was significant in the P1 component, \emph{F}(2, 5151.2) = 3.74, \emph{p} = .024, and in the N400 component, \emph{F}(2, 4637.6) = 8.07, \emph{p} \textless{} .001, but not in the N170 component, \emph{F}(2, 4736.8) = 1.34, \emph{p} = .263.
 
@@
 
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .582 (see Table \ref{tab:exp2-table} and Figure \ref{fig:exp2-plot}).
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .552 (see Table \ref{tab:exp2-table} and Figure \ref{fig:exp2-plot}).
 
@@
 
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs.~non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, \emph{b} = -0.48 µV, \emph{p} = .064, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs.~non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, \emph{b} = -0.50 µV, \emph{p} = .050, and a significant reduction of the N400 component, \emph{b} = 1.31 µV, \emph{p} \textless{} .001.
 
@@
 
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.57 µV, \emph{p} = .047.
-Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.47 µV, \emph{p} = .047.
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.56 µV, \emph{p} = .048.
+Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.45 µV, \emph{p} = .055.
 
@@
 \midrule
-Part & 12.34 (2, 49.1) & < .001 & 30.08 (2, 50.3) & < .001 & 94.61 (2, 50.6) & < .001\\
-Condition & 0.15 (1, 10573.1) & .699 & 1.16 (1, 45.2) & .287 & 41.38 (1, 10593.6) & < .001\\
-Experiment & 0.33 (1, 48.2) & .567 & 2.50 (1, 48.0) & .121 & 4.96 (1, 48.4) & .031\\
-Pt. × con. & 3.90 (2, 9004.9) & .020 & 5.26 (2, 9904.1) & .005 & 15.34 (2, 10091.0) & < .001\\
-Pt. × exp. & 0.04 (2, 49.1) & .966 & 0.58 (2, 50.3) & .565 & 2.55 (2, 50.6) & .088\\
-Ins. × exp. & 0.43 (1, 10573.1) & .514 & 0.06 (1, 45.2) & .805 & 0.07 (1, 10593.6) & .785\\
-Pt. × con. × exp. & 0.03 (2, 9004.9) & .968 & 0.58 (2, 9904.1) & .559 & 2.54 (2, 10091.0) & .079\\
+Part & 12.38 (2, 49.0) & < .001 & 29.90 (2, 50.0) & < .001 & 95.34 (2, 50.6) & < .001\\
+Condition & 0.35 (1, 10560.3) & .552 & 1.65 (1, 125.3) & .202 & 38.72 (1, 10518.8) & < .001\\
+Experiment & 0.35 (1, 48.2) & .555 & 2.38 (1, 48.1) & .129 & 4.75 (1, 48.4) & .034\\
+Pt. × con. & 4.02 (2, 9042.4) & .018 & 5.60 (2, 9877.5) & .004 & 15.73 (2, 10010.1) & < .001\\
+Pt. × exp. & 0.03 (2, 49.0) & .971 & 0.55 (2, 50.0) & .581 & 2.58 (2, 50.6) & .085\\
+Ins. × exp. & 0.62 (1, 10536.2) & .432 & 0.04 (1, 10332.1) & .838 & 0.03 (1, 10574.9) & .865\\
+Pt. × con. × exp. & 0.03 (2, 9042.9) & .972 & 0.62 (2, 9877.8) & .537 & 2.65 (2, 10010.4) & .070\\
 \textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & -0.10 [-0.47, 0.28] & .616 & -0.10 [-0.48, 0.29] & .611 & -0.09 [-0.39, 0.22] & .577\\
-Insight part & -0.24 [-0.62, 0.13] & .202 & -0.57 [-0.96, -0.18] & .004 & 1.10 [0.80, 1.41] & < .001\\
-Post-insight part & 0.47 [0.09, 0.84] & .014 & 0.24 [-0.15, 0.63] & .225 & 0.73 [0.42, 1.04] & < .001\\
+Pre-insight part & -0.07 [-0.44, 0.30] & .699 & -0.10 [-0.44, 0.24] & .568 & -0.10 [-0.41, 0.20] & .507\\
+Insight part & -0.22 [-0.59, 0.15] & .248 & -0.56 [-0.90, -0.21] & .002 & 1.09 [0.79, 1.39] & < .001\\
+Post-insight part & 0.49 [0.12, 0.86] & .010 & 0.25 [-0.10, 0.59] & .158 & 0.72 [0.41, 1.02] & < .001\\
 \bottomrule
@@
 
-As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.34, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}(1, 10593.6) = 41.38, \emph{p} \textless{} .001.
-Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 3.90, all \emph{p}s \textless{} .020.
-While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.96, \emph{p} = .031, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
+As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.38, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}(1, 10518.8) = 38.72, \emph{p} \textless{} .001.
+Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 4.02, all \emph{p}s \textless{} .018.
+While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.75, \emph{p} = .034, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
 
 Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \ref{tab:joint-table} and Figure \ref{fig:joint-plot}).
-This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s \textgreater{} .577, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.
+This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s \textgreater{} .507, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.56 µV, \emph{p} = .002, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.09 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.72 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.49 µV, \emph{p} = .010.
 
@@
 Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were preceded by matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for 49.6\% of objects presented with matching keywords as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize.
-Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.
+Across both experiments, this was the case for 49.6\% of objects presented with matching keywords as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -0.56 µV, \emph{p} .002.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords but on which participants failed to capitalize.
+Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.09 µV, \emph{p} \textless{} .001.
 
@@
 Hsieh et al.
-(2010) showed participants indiscernible two-tone (``Mooney'') versions of images before and after showing them the original versions.
+(2010) showed participants indiscernible two-tone (\enquote{Mooney}) versions of images before and after showing them the original versions.
 They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
@@
 
-On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception Clarke (2020).
+On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception (Firestone \& Scholl, 2016; Fodor, 1983; Pylyshyn, 1999, but see @clarke2020).
 However, proponents of such a modular view have pointed out important conceptual and methodological shortcomings of previous studies claiming to demonstrate top-down effects of cognition on perception (Firestone \& Scholl, 2016; Machery, 2015).
@@
 In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
-For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this ``barrier of meaning'' (Mitchell, 2020).
+For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this \enquote{barrier of meaning} (Mitchell, 2020).
 Drawing inspiration from cognitive psychology and human neuroscientific data may help making these models more biologically plausible and, at the same time, more resource and data efficient.
@@
 The effects are consistent, however, with the reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002) which posits that objects first enter our visual consciousness at an abstract, conceptual level.
-Once this initial ``vision at a glance'' has taken place, feedback connections to earlier layers of the visual system are being accessed to extract relevant lower-level features (``vision with scrutiny'').
+Once this initial \enquote{vision at a glance} has taken place, feedback connections to earlier layers of the visual system are being accessed to extract relevant lower-level features (\enquote{vision with scrutiny}).
 This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex (Hsieh et al., 2010) as well as (b) the modulations of early visual ERP components observed in the present study and others (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Samaha et al., 2018; Weller et al., 2019).
@@
 
+\begingroup
 \setlength{\parindent}{-0.5in}
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-abdelrahman2011}{}%
@@
 (1991).
-{American Electroencephalographic Society} guidelines for standard electrode position nomenclature.
+American Electroencephalographic Society guidelines for standard electrode position nomenclature.
 \emph{Journal of Clinical Neurophysiology}, \emph{8}(2), 200--202.
@@
 (2015).
-Fitting linear mixed-effects models using {lme4}.
+Fitting linear mixed-effects models using lme4.
 \emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
@@
 \leavevmode\hypertarget{ref-churchland1988}{}%
-Churchland, P. M. (1988). Perceptual plasticity and theoretical neutrality: A reply to {Jerry} {Fodor}. \emph{Philosophy of Science}, \emph{55}(2), 167--187. \url{https://doi.org/10.1086/289425}
+Churchland, P. M. (1988). Perceptual plasticity and theoretical neutrality: A reply to Jerry Fodor. \emph{Philosophy of Science}, \emph{55}(2), 167--187. \url{https://doi.org/10.1086/289425}
 
@@
 
+\leavevmode\hypertarget{ref-dicarlo2012}{}%
+DiCarlo, J. J., Zoccolan, D., \& Rust, N. C. (2012). How does the brain solve visual object recognition? \emph{Neuron}, \emph{73}(3), 415--434. \url{https://doi.org/10.1016/j.neuron.2012.01.010}
+
 \leavevmode\hypertarget{ref-dirusso2001}{}%
@@
 
-\leavevmode\hypertarget{ref-dicarlo2012}{}%
-DiCarlo, J. J., Zoccolan, D., \& Rust, N. C. (2012). How does the brain solve visual object recognition? \emph{Neuron}, \emph{73}(3), 415--434. \url{https://doi.org/10.1016/j.neuron.2012.01.010}
-
 \leavevmode\hypertarget{ref-eimer2011}{}%
@@
 (2011).
-The {N170} component and its links to configural face processing: A rapid neural adaptation study.
+The N170 component and its links to configural face processing: A rapid neural adaptation study.
 \emph{Brain Research}, \emph{1376}, 76--87.
@@
 (2016).
-Cognition does not affect perception: Evaluating the evidence for {``top-down''} effects.
+Cognition does not affect perception: Evaluating the evidence for ``top-down'' effects.
 \emph{Behavioral and Brain Sciences}, \emph{39}.
@@
 
+\leavevmode\hypertarget{ref-fodor1983}{}%
+Fodor, J. A. (1983). \emph{The modularity of mind}. MIT Press.
+
 \leavevmode\hypertarget{ref-fodor1984}{}%
 Fodor, J. A. (1984). Observation reconsidered. \emph{Philosophy of Science}, \emph{51}(1), 23--43. \url{https://doi.org/10.1086/289162}
-
-\leavevmode\hypertarget{ref-fodor1983}{}%
-Fodor, J. A. (1983). \emph{The modularity of mind}. MIT Press.
 
@@
 (2002).
-Flow of activation from {V1} to frontal cortex in humans.
+Flow of activation from V1 to frontal cortex in humans.
 \emph{Experimental Brain Research}, \emph{142}(1), 139--150.
@@
 (2017).
-The role of affective evaluation in conflict adaptation: An {LRP} study.
+The role of affective evaluation in conflict adaptation: An LRP study.
 \emph{Brain and Cognition}, \emph{116}, 9--16.
@@
 (2018).
-Group-level {EEG}-processing pipeline for flexible single trial-based analyses including linear mixed models.
+Group-level EEG-processing pipeline for flexible single trial-based analyses including linear mixed models.
 \emph{Frontiers in Neuroscience}, \emph{12}.
@@
 (1996).
-The search for {``common sense''}: An electrophysiological study of the comprehension of words and pictures in reading.
+The search for ``common sense'': An electrophysiological study of the comprehension of words and pictures in reading.
 \emph{Journal of Cognitive Neuroscience}, \emph{8}(2), 89--106.
@@
 Gramfort, A., Luessi, M., Larson, E., Engemann, D.
-A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& al., et.
+A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& al.
 (2013).
-MEG and {EEG} data analysis with {MNE-Python}.
+MEG and EEG data analysis with MNE-Python.
 \emph{Frontiers in Neuroscience}, \emph{7}.
@@
 (2009).
-See what {I} mean?
-An {ERP} study of the effect of background knowledge on novel object processing.
+See what I mean?
+An ERP study of the effect of background knowledge on novel object processing.
 \emph{Memory \& Cognition}, \emph{37}(3), 277--291.
@@
 (2011).
-Effects of language comprehension on visual processing -- MEG dissociates early perceptual and late N400 effects.
+Effects of language comprehension on visual processing -- meg dissociates early perceptual and late n400 effects.
 \emph{Brain and Language}, \emph{116}(2), 91--96.
@@
 (2010).
-Recognition alters the spatial pattern of {fMRI} activation in early retinotopic cortex.
+Recognition alters the spatial pattern of fMRI activation in early retinotopic cortex.
 \emph{Journal of Neurophysiology}, \emph{103}(3), 1501--1507.
@@
 (2010).
-Misaligning face halves increases and delays the {N170} specifically for upright faces: Implications for the nature of early face representations.
+Misaligning face halves increases and delays the N170 specifically for upright faces: Implications for the nature of early face representations.
 \emph{Brain Research}, \emph{1318}, 96--109.
@@
 (2011).
-Thirty years and counting: Finding meaning in the {N400} component of the event-related brain potential ({ERP}).
+Thirty years and counting: Finding meaning in the N400 component of the event-related brain potential (ERP).
 \emph{Annual Review of Psychology}, \emph{62}, 621--647.
@@
 (2017).
-{lmerTest} package: Tests in linear mixed effects models.
+lmerTest package: Tests in linear mixed effects models.
 \emph{Journal of Statistical Software}, \emph{82}(13), 1--26.
@@
 (2008).
-A cortical network for semantics: (De)constructing the {N400}.
+A cortical network for semantics: (De)constructing the N400.
 \emph{Nature Reviews Neuroscience}, \emph{9}(12), 920--933.
@@
 \leavevmode\hypertarget{ref-luck2014}{}%
-Luck, S. J. (2014). Overview of common ERP components. In \emph{An introduction to the event-related potential technique} (2nd ed., pp. 71--118). MIT Press.
+Luck, S. J. (2014). Overview of common erp components. In \emph{An introduction to the event-related potential technique} (2nd ed., pp. 71--118). MIT Press.
 
@@
 
+\leavevmode\hypertarget{ref-lupyan2012}{}%
+Lupyan, G. (2012). Linguistically modulated perception and cognition: The label-feedback hypothesis. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00054}
+
 \leavevmode\hypertarget{ref-lupyan2015}{}%
@@
 \url{https://doi.org/10.1007/s13164-015-0253-4}
-
-\leavevmode\hypertarget{ref-lupyan2012}{}%
-Lupyan, G. (2012). Linguistically modulated perception and cognition: The label-feedback hypothesis. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00054}
 
@@
 Does the semantic content of verbal categories influence categorical perception?
-An {ERP} study.
+An ERP study.
 \emph{Brain and Cognition}, \emph{91}, 1--10.
@@
 (2017).
-Balancing {Type I} error and power in linear mixed models.
+Balancing Type I error and power in linear mixed models.
 \emph{Journal of Memory and Language}, \emph{94}, 305--315.
@@
 \leavevmode\hypertarget{ref-oldfield1971}{}%
-Oldfield, R. C. (1971). The assessment and analysis of handedness: The {Edinburgh} inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}
+Oldfield, R. C. (1971). The assessment and analysis of handedness: The Edinburgh inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}
 
@@
 (2011).
-Sensory ERP components.
+Sensory erp components.
 In E.
@@
 J.
-Luck (Eds.), \emph{The {Oxford handbook} of event-related potential components} (pp.
+Luck (Eds.), \emph{The Oxford handbook of event-related potential components} (pp.
 89--114).
@@
 
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
 \leavevmode\hypertarget{ref-rabovsky2018}{}%
@@
 (2018).
-Modelling the {N400} brain potential as change in a probabilistic representation of meaning.
+Modelling the N400 brain potential as change in a probabilistic representation of meaning.
 \emph{Nature Human Behaviour}, \emph{2}(9), 693--705.
 \url{https://doi.org/10.1038/s41562-018-0406-4}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
@@
 \emph{Psychological Science}.
-\url{https://journals.sagepub.com/doi/10.1111/1467-9280.00446}
+\url{https://doi.org/10.1111/1467-9280.00446}
 
@@
 (2011).
-The {N170}: Understanding the time course of face perception in the human brain.
+The N170: Understanding the time course of face perception in the human brain.
 In E.
@@
 J.
-Luck (Eds.), \emph{The {Oxford} handbook of event-related potential components} (pp.
+Luck (Eds.), \emph{The Oxford handbook of event-related potential components} (pp.
 115--142).
@@
 (2005).
-Semantic memory retrieval: Cortical couplings in object recognition in the N400 window.
+Semantic memory retrieval: Cortical couplings in object recognition in the n400 window.
 \emph{European Journal of Neuroscience}, \emph{21}(4), 1139--1143.
-https://doi.org/\url{https://doi.org/10.1111/j.1460-9568.2005.03906.x}
+\url{https://doi.org/https://doi.org/10.1111/j.1460-9568.2005.03906.x}
 
@@
 \leavevmode\hypertarget{ref-R-buildmer}{}%
-Voeten, C. C. (2020). \emph{{buildmer}: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
+Voeten, C. C. (2020). \emph{buildmer: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
 
 \leavevmode\hypertarget{ref-vogel2000}{}%
-Vogel, E. K., \& Luck, S. J. (2000). The visual {N1} component as an index of a discrimination process. \emph{Psychophysiology}, \emph{37}(2), 190--203.
+Vogel, E. K., \& Luck, S. J. (2000). The visual N1 component as an index of a discrimination process. \emph{Psychophysiology}, \emph{37}(2), 190--203.
 
@@
 
-\end{CSLReferences}
+\endgroup
 

### 2021-01-17 analysis/master_thesis.tex
remove messages from tables, add latex packages to dockerfile

@@
 
+{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp1-plot-1}
+
+}
+
 \caption{Procedure and Results of Experiment 1\smallskip}\label{fig:exp1-plot}
-
-{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp1-plot-1}
-
-}
-
-\bigskip\small\emph{Note.} 
-(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
-In the post-insight part, the same objects were presented again without the keywords.
-(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
-Ampl.
-= amplitude.\newline
-*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.
-
 \end{figure}
@@
 
+{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp2-plot-1}
+
+}
+
 \caption{Results of Experiment 2\smallskip}\label{fig:exp2-plot}
-
-{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp2-plot-1}
-
-}
-
-\bigskip\small\emph{Note.} 
-ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
-Ampl.
-= amplitude.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.
-
 \end{figure}
@@
 
+{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/joint-plot-1}
+
+}
+
 \caption{Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip}\label{fig:joint-plot}
-
-{\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/joint-plot-1}
-
-}
-
-\bigskip\small\emph{Note.} 
-The violins and box plots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
-Ampl.
-= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.
-
 \end{figure}

### 2021-01-18 analysis/manuscript.Rmd
write function to compute single trial amplitudes in python

@@
 # which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
-rerun_preproc <- FALSE
+rerun_preproc <- TRUE
 
@@
 # fitting all models may take 24 hours or more.
-rerun_models <- FALSE
+rerun_models <- TRUE
 
@@
   name = c("P1", "N170", "N400"),
-  start = c(100, 150, 400),
-  stop = c(150, 200, 700),
+  tmin = c(100, 150, 400),
+  tmax = c(150, 200, 700),
   roi = list(
@@
 # Define function for preprocessing the EEG data
-def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq,
-            event_id, tmin, tmax, baseline, reject):
+def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax,
+    baseline, reject):
     # Read EEG data in microvolts
@@
     # Create virtual EOG channels
-    raw = mne.set_bipolar_reference(raw, 'Auge_u', 'Fp1', ch_name='VEOG', drop_refs=False)
-    raw = mne.set_bipolar_reference(raw, 'F9', 'F10', ch_name='HEOG', drop_refs=False)
-    raw.set_channel_types(mapping={'VEOG': 'eog', 'HEOG': 'eog'})
+    raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
+    raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
+    raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
     # Add EasyCap electrode layout, removing any excessive channels
-    montage = mne.channels.make_standard_montage('easycap-M1')
-    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(['VEOG', 'HEOG'])))
+    montage = mne.channels.make_standard_montage("easycap-M1")
+    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
     raw.set_montage(montage=montage)
     # Re-reference to common average
-    raw, _ = mne.set_eeg_reference(raw, 'average')
+    raw, _ = mne.set_eeg_reference(raw, "average")
     # Run ICA on a copy of the data
@@
     events, _ = mne.events_from_annotations(raw, verbose=False)
-    epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin,
-                        tmax=tmax, baseline=baseline, preload=True)
+    epochs = mne.Epochs(
+        raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True
+    )
     # Add behavioral data
@@
     # Define lists of participants, parts, and conditions
-  ps = epochs.metadata['participant'].unique()
-  pts = ['I', 'II', 'III']
-  cns = ['Informed', 'Naive']
+    ps = epochs.metadata["participant"].unique()
+    pts = ["I", "II", "III"]
+    cns = ["Informed", "Naive"]
     # Define function to compute a single by-participant waveform
@@
         query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
-    return(epochs[query].average())
+        return epochs[query].average()
     # Create a dict with by-participant waveforms nested in conditions nested in parts
-  avgs = {pt:{cn:[compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
+    avgs = {pt: {cn: [compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
     # If needed, compute grand-averaged waveforms across participants
     if grand:
-    avgs = {pt:{cn:mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
+        avgs = {pt: {cn: mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
     # If needed, extract only the data from the evoked MNE objects
@@
         if grand:
-      avgs = {pt:{cn:avgs[pt][cn].data for cn in cns} for pt in pts}
+            avgs = {pt: {cn: avgs[pt][cn].data for cn in cns} for pt in pts}
         else:
-      avgs = {pt:{cn:[avgs[pt][cn][p].data for p in range(0, len(ps))] for cn in cns} for pt in pts}
-  return(avgs)
+            ps_num = range(0, len(ps))
+            avgs = {pt: {cn: [avgs[pt][cn][p].data for p in ps_num] for cn in cns} for pt in pts}
+    return avgs
+
+# Define function to compute single-trial mean ERP ampltiudes from epochs
+def compute_erps(epochs, name, tmin, tmax, roi):
+    # Average across electrodes in the ROI
+    roi_idx = mne.pick_channels(epochs.ch_names, roi)
+    epochs_roi = mne.channels.combine_channels(epochs, dict(roi=roi_idx))
+    # Average across samples in the time window
+    import numpy as np
+    tmin_s, tmax_s = tmin / 1000, tmax / 1000
+    times_idx = np.where(np.logical_and(epochs.times >= tmin_s, epochs.times <= tmax_s))
+    erps = epochs_roi.get_data()[:, 0, times_idx].mean(axis=(1, 2))
+    return erps
 
@@
 
-# Actually apply the preprocessing function for Epxeriment 1 in Python
+# Preprocess the EEG for Epxeriment 1 in Python
 map2(
@@
 epochs_exp1$save("analysis/export/exp1-epo.fif")
+
+# Compute mean ERP amplitudes and bind to the behavioral data
+pmap_dfc(comps, py$compute_erps, epochs = epochs_exp1) %>%
+  set_names(comps$name) %>%
+  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
+  write_tsv("analysis/export/exp1-data.tsv") -> data_exp1
+
+# Compute grand averages per part and condition
+py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
+  saveRDS("analysis/export/exp1-gaverages.RDS")
+
+# Backup number of stimuli assigned to each condition for all participants
+map(behav_exp1, function(x) table(x$condition) / 3) %>%
+  bind_rows() %>%
+  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
+  write_tsv("analysis/export/exp1-objects.tsv")
 
@@
 
-# Create a vector with sample time points (in ms)
-sfreq <- epochs_exp1$info["sfreq"]
-seq(preproc_params$tmin * 1000, preproc_params$tmax * 1000, 1 / sfreq * 1000) %T>%
-  cat(file = "analysis/export/sample_times.tsv", sep = "\n") -> times
-
-# Define function to compute single-trial mean ERP amplitudes
-compute_erps <- function(epochs, name, start, stop, roi) {
-  dat <- epochs$get_data()
-  els <- epochs$ch_names
-  erps <- dat[, which(els %in% roi), which(times %in% start:stop)]
-  amps <- apply(erps, 1, mean, na.rm = TRUE)
-  return(amps)
-}
-
-# Actually apply the function to compute mean ERP amplitudes for Experiment 1
-pmap_dfc(comps, compute_erps, epochs = epochs_exp1) %>%
-  set_names(comps$name) %>%
-  # Bind to the behavioral data
-  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
-  # Backup to the export folder
-  write_tsv("analysis/export/exp1-erps.tsv") -> data_exp1
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp1-gavgs.RDS")
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp1, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp1-objects.tsv")
+# Remove the epochs to free up memory
+rm(epochs_exp1)
 ```
@@
 # Load preprocessed single-trial data
-read_tsv("analysis/export/exp1-erps.tsv", col_types = cols()) %>%
+read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
   # Factorize columns
@@
     condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
-    ),
+      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
+    )),
     participant = factor(participant),
@@
 
-# Actually apply the function to compute the models for Experiment 1
+# Compute the models for Experiment 1
 map(
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp1-mods.RDS") -> models_exp1
+  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
 ```
@@
 # Load grand-averaged ERPs and linear mixed models
-evokeds_exp1 <- readRDS("analysis/export/exp1-gavgs.RDS")
-models_exp1 <- readRDS("analysis/export/exp1-mods.RDS")
+evokeds_exp1 <- readRDS("analysis/export/exp1-gaverages.RDS")
+models_exp1 <- readRDS("analysis/export/exp1-models.RDS")
 ```
@@
   suppressWarnings(suppressMessages(
-    pmap(comps, function(name, start, stop, roi) {
+    pmap(comps, function(name, tmin, tmax, roi) {
       # N400 gets a different scale than P1 and N170
@@
               set_colnames(montage$electrode) %>%
-              mutate(.time = times, roi = rowMeans(select(., all_of(roi))))
+              mutate(.time = seq(-500, 1498, 2), roi = rowMeans(select(., all_of(roi))))
           }) %>% bind_rows(.id = "condition")
@@
           pull(asterisks)
-        xasterisks <- case_when(str_length(asterisks) == 1 ~ start + 11, str_length(asterisks) == 3 ~ start + 15)
+        xasterisks <- case_when(str_length(asterisks) == 1 ~ tmin + 11, str_length(asterisks) == 3 ~ tmin + 15)
         if (is.na(asterisks)) {
-          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = NA)
+          shade <- annotate("rect", xmin = tmin, xmax = tmax, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = NA)
         } else {
-          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = "gray90")
+          shade <- annotate("rect", xmin = tmin, xmax = tmax, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = "gray90")
         }
@@
         # wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
-        #   annotate("rect", xmin = start, xmax = stop, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
+        #   annotate("rect", xmin = tmin, xmax = tmax, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
         # # Shade significant area
@@
         #   wave <- wave + geom_ribbon(
-        #     data = data_plot %>% filter(.time >= start & .time <= stop) %>%
+        #     data = data_plot %>% filter(.time >= tmin & .time <= tmax) %>%
         #       group_by(.time) %>% summarize(ymin = min(roi), ymax = max(roi)),
-        #     aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
+        #     aes(x = .time, xmin = tmin, xmax = tmax, ymin = ymin, ymax = ymax),
         #     inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1)
@@
         # } +
-        # annotate("text", label = star, x = start + (stop - start)/2, y = -3.2, size = 7, family = "Helvetica")}
+        # annotate("text", label = star, x = tmin + (tmax - tmin)/2, y = -3.2, size = 7, family = "Helvetica")}
         # Add waves and styling
@@
         topo <- data_plot %>%
-          filter(.time >= start & .time <= stop) %>%
+          filter(.time >= tmin & .time <= tmax) %>%
           group_by(condition) %>%
@@
 
-# Apply the preprocessing function for Epxeriment 2 in Python
+# Preprocess the EEG for Epxeriment 2 in Python
 map2(
@@
 
-# Apply the function to compute mean ERP amplitudes for Experiment 2
-pmap_dfc(comps, compute_erps, epochs = epochs_exp2) %>%
+# Compute mean ERP amplitudes and bind to the behavioral data
+pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
   set_names(comps$name) %>%
-  # Bind to the behavioral data
   bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
-  # Backup to the export folder
-  write_tsv("analysis/export/exp2-erps.tsv") -> data_exp2
+  write_tsv("analysis/export/exp2-data.tsv") -> data_exp2
 
@@
 py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp2-gavgs.RDS")
+  saveRDS("analysis/export/exp2-gaverages.RDS")
 
@@
   write_tsv("analysis/export/exp2-objects.tsv")
+
+# Remove the epochs to free up memory
+rm(epochs_exp2)
 ```
@@
 # Load preprocessed single-trial data
-read_tsv("analysis/export/exp2-erps.tsv", col_types = cols()) %>%
+read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
   # Factorize columns
@@
 
-# Apply these contrasts to the factors in the data
+# Apply contrasts to the factors in the data
 contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
@@
 
-# Apply the function to compute the models for Experiment 2
+# Compute the models for Experiment 2
 map(
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp2-mods.RDS") -> models_exp2
+  saveRDS("analysis/export/exp2-models.RDS") -> models_exp2
 ```
@@
 # Load grand-averaged ERPs and linear mixed models
-evokeds_exp2 <- readRDS("analysis/export/exp2-gavgs.RDS")
-models_exp2 <- readRDS("analysis/export/exp2-mods.RDS")
+evokeds_exp2 <- readRDS("analysis/export/exp2-gaverages.RDS")
+models_exp2 <- readRDS("analysis/export/exp2-models.RDS")
 ```
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-mods.RDS") -> models_joint
+  saveRDS("analysis/export/joint-models.RDS") -> models_joint
 ```
@@
 # Load linear mixed models
-models_joint <- readRDS("analysis/export/joint-mods.RDS")
+models_joint <- readRDS("analysis/export/joint-models.RDS")
 
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-control-mods.RDS") -> models_joint_control
+  saveRDS("analysis/export/joint-control-models.RDS") -> models_joint_control
 ```
@@
 # Load linear mixed models
-models_joint_control <- readRDS("analysis/export/joint-control-mods.RDS")
+models_joint_control <- readRDS("analysis/export/joint-control-models.RDS")
 

### 2021-01-18 analysis/manuscript.Rmd
update experiment 3 to new python functions

@@
 # Do you want to run the analysis for Experiment 3?
-run_exp3 <- FALSE
+run_exp3 <- TRUE
 
@@
 
-```{r exp3-preparation, eval=run_exp3}
-# Read behavioral data for Experiment 3
-data_exp3 <- list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav)
-
-# Check average number of stimuli per condition
-(objects_exp3 <- map(data_exp3, function(x) {
-  x %<>% filter(part != "IV")
-  table(x$condition) / 3
-}) %>% bind_rows() %>% colMeans())
-```
-
-```{python exp3-preprocessing, eval=run_exp3}
-# List raw EEG filenames
-fnames_exp3 = sorted(glob.glob("data/exp3/EEG/*.vhdr"))
-
-# Import behavioral data from R
-metadata_exp3 = r.data_exp3
+```{r exp3-preproc, eval=run_exp3}
+# Read behavioral data for Experiment 1
+list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp3
 
 # Update stimulus triggers
-preproc_params["event_id"] = {
-    "match/upright": 241,
-    "match/inverted": 242,
-    "mismatch/upright": 243,
-    "mismatch/inverted": 244,
-}
-
-# Check if preprocessing was done already (delete the file to re-run)
-if os.path.exists("analysis/export/exp3-epo.fif"):
-    # Read preprocessed data from file
-    epochs_exp3 = mne.read_epochs("analysis/export/exp3-epo.fif", preload=True)
-else:
-    # Preprocess EEG data for Experiment 3
-    epochs_exp3 = [
-        preproc(vhdr_fname=fname, metadata=meta, **preproc_params)
-        for fname, meta in zip(fnames_exp3, metadata_exp3)
-    ]
-    # Combine epochs into a single data set
-    epochs_exp3 = mne.concatenate_epochs(epochs_exp3)
-    # Backup epochs and evokeds to the export folder
-    epochs_exp3.save("analysis/export/exp3-epo.fif")
-```
-
-```{r exp3-analysis, eval=run_exp3}
-# Re-import behavioral data and re-factorize some columns
-data_exp3 <- py$epochs_exp3$metadata %>% mutate(
-  part = factor(part, levels = c("I", "II", "III", "IV")),
+preproc_params$event_id <- dict(
+  "match/upright" = as.integer(241),
+  "match/inverted" = as.integer(242),
+  "mismatch/upright" = as.integer(243),
+  "mismatch/inverted" = as.integer(244)
+)
+
+# Preprocess the EEG for Epxeriment 3 in Python
+map2(
+  .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
+  .y = behav_exp3,
+  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
+) %>%
+  # Concatenate epochs of all participants
+  py$mne$epochs$concatenate_epochs() -> epochs_exp3
+
+# Backup epochs to the export folder
+epochs_exp3$save("analysis/export/exp3-epo.fif")
+
+# Compute mean ERP amplitudes and bind to the behavioral data
+pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
+  set_names(comps$name) %>%
+  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
+  write_tsv("analysis/export/exp3-data.tsv") -> data_exp3
+
+# Compute grand averages per part and condition
+py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
+  saveRDS("analysis/export/exp3-gaverages.RDS")
+
+# Backup number of stimuli assigned to each condition for all participants
+map(behav_exp3, function(x) table(x$condition) / 3) %>%
+  bind_rows() %>%
+  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
+  write_tsv("analysis/export/exp3-objects.tsv")
+
+# Remove the epochs to free up memory
+rm(epochs_exp3)
+```
+
+```{r exp3-models, eval=run_exp3}
+# Load preprocessed single-trial data
+read_tsv("analysis/export/exp3-data.tsv", col_types = cols()) %>%
+  # Factorize columns
+  mutate(
+    part = factor(part, levels = c("I", "II", "III")),
     position = factor(position, levels = c("Inverted", "Upright")),
-  condition = factor(condition, levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")),
-  participant = factor(participant), item = factor(item)
-)
-
-# Check if ERPs were computed already (delete the file to re-run)
-if (file.exists("analysis/export/exp3-erps.RDS")) {
-  # Read ERPs from file
-  data_exp3 <- readRDS("analysis/export/exp3-erps.RDS")
-} else {
-  # Compute single-trial ERPs for Experiment 3
-  data_exp3 <- pmap_dfc(comps, compute_erps, epochs = py$epochs_exp3$get_data(), els = els) %>%
-    set_names(comps$name) %>%
-    cbind(data_exp3, .) %T>%
-    saveRDS("analysis/export/exp3-erps.RDS")
-}
-
-# Remove the epochs to free up memory
-py_run_string("del epochs_exp3")
-import("gc")$collect()
-
-# Remove any trials from part IV
-data_exp3 %<>% filter(part != "IV") %>% droplevels()
-
-# Check number of rejected epochs
-rejected_exp3 <- data_exp3 %>% group_by(participant) %>% tally() %>% mutate(n = 672 - n) %>% pull(n)
-mean(rejected_exp3)    # Mean
-median(rejected_exp3)  # Median
-range(rejected_exp3)   # Range
-
-# Remove any trials excluded from conditions
-data_exp3 %<>% filter(condition %in% c("Informed", "Naive")) %>% droplevels()
-
-# Contrast coding for position (inverted-upright), condition (informed-naive), and part (2-1, 3-1)
+    condition = factor(condition, levels = c(
+      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
+    )),
+    participant = factor(participant),
+    item = factor(item)
+  ) %>%
+  # Remove any trials excluded from conditions and parts
+  filter(condition %in% c("Informed", "Naive") & part != "IV") %>%
+  droplevels() -> data_exp3
+
+# Define contrasts for position (inverted-upright), condition (informed-naive), and part (2-1, 3-1)
 t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
@@
 
-# New formula for LMMs
+# Define new formula for LMMs
 form_exp3 <- buildmer::tabulate.formula(
-  ~ part * condition * position + (part * condition * position | participant) + (part * condition * position | item)
+  ~ part * condition * position +
+    (part * condition * position | participant) +
+    (part * condition * position | item)
 ) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
 
-# New follow-up contrasts
+# Define new follow-up contrasts
 specs_exp3 <- pairwise ~ condition | position * part
 
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("analysis/export/exp3-stats.RDS")) {
-  # Read models from file
-  models_exp3 <- readRDS("analysis/export/exp3-stats.RDS")
-} else {
-  # Compute LMMs for Experiment 3
-  models_exp3 <- map(
+# Compute the models for Experiment 3
+map(
   comps$name,
   compute_models,
-    formula = form_exp3,
+  formula = formula_exp3,
   data = data_exp3,
-    control = ctrl_params,
+  control = control,
   specs = specs_exp3
-  ) %>% set_names(comps$name) %T>%
-    saveRDS("analysis/export/exp3-stats.RDS")
-}
+) %>%
+  set_names(comps$name) %T>%
+  saveRDS("analysis/export/exp3-models.RDS") -> models_exp3
 ```

### 2021-01-25 analysis/manuscript.Rmd
tweeks to the text + remove excess code from erp plot and control analysis

@@
 abstract: |
-  Does our perception of an object change as soon as we discover what it is for?
-This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it pertains to the long-standing debate around the (im)penetrability of perception by "higher" cognitive capacities.
-In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with valid information about their function---leading to semantically informed perception---or together with invalid information---resulting in naive perception.
-We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of perceiving objects differed from one another.
+  Does our perception of an object change as soon as we discover what function it serves?
+This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception.
+We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
 We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
@@
 We replicated these novel findings in an independent sample (*n* = 24).
-Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
+Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
 
@@
 # which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
-rerun_preproc <- TRUE
+rerun_preproc <- FALSE
 
@@
 # fitting all models may take 24 hours or more.
-rerun_models <- TRUE
+rerun_models <- FALSE
 
 # Do you want to run the analysis for Experiment 3?
-run_exp3 <- TRUE
+run_exp3 <- FALSE
 
@@
 
-How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects which were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
-Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temporal resolution of event-related brain potentials (ERPs).
+How does our perception of an object change as soon as we discover what function it serves?
+In this study, we presented participants with unfamiliar objects that were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
+We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resoluation of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
+It allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
 
 The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world is "cognitively impenetrable" or, in other words, determined solely by the visual input reaching our retina.
-According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @fodor1984; @pylyshyn1999].
-Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @goodale1992; @marr1982].
-
-This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1988; @churchland1994; @lupyan2015; @teufel2017].
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas [e.g., visual areas V1 and V2\; @bullier2001; @gilbert2013]---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+This debate revolves around the question of whether or not our perception of the (visual) world is "cognitively impenetrable" [@pylyshyn1999] or, in other words, determined solely by the visual input reaching our retina.
+According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @pylyshyn1999].
+Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @marr1982].
+
+This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1994; @lupyan2015; @teufel2017].
+The myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas [e.g., V1 and V2\; @bullier2001; @gilbert2013]---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
 For instance, the reverse hierarchy theory [@ahissar2004; @hochstein2002] assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
 Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
-Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
-Finally, an active role of top-down influences is also promoted by theories of vision falling under the umbrella of Bayesian inference and predictive coding [e.g., @lupyan2015; @panichello2013; @yuille2006].
+Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
+Finally, an active role of top-down influences is also promoted by theories of vision in the framework of Bayesian inference and predictive coding [e.g., @clark2013; @lupyan2015; @panichello2013; @yuille2006].
 
 Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition [for review, see @collins2014; @vetter2014].
-These aspects of cognition may include transient states such as emotions [e.g., @bocanegra2009; @phelps2016] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @lin1997; @weller2019].
+These aspects of cognition may include transient states such as emotions [e.g., @bocanegra2009; @phelps2016] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @gauthier2003; @weller2019].
 Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical and pointed out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
-They have argued, for example, that most behavioral paradigms have not been able to discern between perceptual and postperceptual (e.g., memory-related) effects.
-Furthermore, cognitive influences in some studies have been confounded with differences in the lower-level visual input.
+They argue, for example, that most behavioral paradigms have not been able to discern between perceptual and post-perceptual (e.g., memory-related) effects.
+Furthermore, cognitive influences in some studies were confounded with differences in the low-level visual input itself.
 We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our methodology and results.
 
-In general, however, it is important to note that one productive way to circumvent some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+In general, however, it is important to note that one productive way to circumvent at least some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or post-perceptual---are influenced by higher-level capacities such as semantic knowledge.
 This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
@@
 The visual P1 component of the ERP refers to a positive deflection peaking as early as 100--150 ms after stimulus onset at occipital channels.
-It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri [@dirusso2001; @foxe2002; @mangun1995].
+It is generated by multiple sources in the extrastriate cortices of the middle occipital and fusiform gyri [@dirusso2001; @mangun1995].
 The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus [e.g., size, luminance, and contrast\; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated view of visual perception.
@@
 The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
-Here, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
+In this study, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
 This can be taken as further evidence for an influence of semantic knowledge on the early visual perception of unfamiliar objects.
@@
 In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
-When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha power was higher for meaning-trained images than for perceptually-trained images.
+When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha-band power was higher for meaning-trained images than for perceptually-trained images.
 As before, these effects of perceiving objects in a semantically informed way seem to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
@@
 These keywords could either be matching the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could be non-matching by describing the function of a different object, thus keeping the perception of the object semantically naive.
-During this second part, we were able measure the online influence of semantic insight on object-evoked ERPs as it happened.
+During this second part, we were able to measure the online influence of semantic insight on object-evoked ERPs as it happened.
 Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them---thereby mimicking previous studies [e.g., @abdelrahman2008; @samaha2018; @weller2019].
@@
 Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
-No a priori power analysis was carried out and the sample size was chosen in line with other EEG studies in our lab at the time of data collection.
+No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
 All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
@@
 
-For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g., current--measuring, pottery--drumming).
-As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects.
+For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
+As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
 The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
+This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
@@
 
-```{r exp1-models, eval=rerun_models}
+```{r exp1-models, eval=TRUE}
 # Load preprocessed single-trial data
@@
 
-# Compute the models for Experiment 1
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp12,
-  data = data_exp1,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
+# # Compute the models for Experiment 1
+# map(
+#   comps$name,
+#   compute_models,
+#   formula = formula_exp12,
+#   data = data_exp1,
+#   control = control,
+#   specs = specs_exp12
+# ) %>%
+#   set_names(comps$name) %T>%
+#   saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
 ```
@@
 # Load sample time points and electrode montage
-times <- scan("analysis/export/sample_times.tsv", quiet = TRUE)
 montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())
@@
     annotate("text", x = -27, y = 65.3, label = "+", size = 20 / .pt, family = "Helvetica") +
-    annotate("text", x = -9, y = 55, label = "Potato\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
-    annotate("text", x = -9, y = 79, label = "Message\nmorsing", size = 10 / .pt, family = "Helvetica", color = color_naive) +
+    annotate("text", x = -9, y = 55, label = "potatoes\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
+    annotate("text", x = -9, y = 79, label = "message\nsignalling", size = 10 / .pt, family = "Helvetica", color = color_naive) +
     annotate("text", x = 9, y = 67, label = "*", size = 30 / .pt, family = "Helvetica") +
@@
 
-\bigskip\small\emph{Note.} 
+\bigskip\small\textit{Note.} 
 (A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
@@
 (B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
+Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
 Ampl.
 = amplitude.\newline
-*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.
+*\textit{p} \textless{} .05. **\textit{p} \textless{} .01. ***\textit{p} \textless{} .001.
 
@@
 The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the *find\_bads\_eog* function.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find\_bads\_eog* function.
 After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was epoched into segments of 2,000 ms, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
+Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
 The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset.
@@
 This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see the scalp topographies in Figure \@ref(fig:exp1-plot)B).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \@ref(fig:exp1-plot)B).
 
@@
 
-First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded from all further analyses those objects which participants classified as being known to them in the pre-insight part (i.e., before any keywords were presented).
+First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented).
 This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
+Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
 Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
@@
 Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
-This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).
+This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).
 
 The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
-For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
-First, they can account not only for the non-independence of data points coming from the same participant, but also simultaneously for the non-independence of data points coming from the same item.
-In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
-Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable in designs where the assignment of trials to conditions is co-determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone [e.g., @fröber2017].
+For the purpose of the present study, these models have at least three desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+First, they can leverage all of the information that is present in the data set on the single trial level, some of which would be lost when computing averages.
+Second, they can account simultaneously for the non-independence of data points coming from the same participant and/or from the same item.
+In contrast, the neglect of the item as a random variable in by-participant ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
+Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
+Such a situation is inevitable when the assignment of trials to conditions is co-determined by the experimental manipulation and the behavioral responses of the participants to this manipulation [e.g., @fröber2017].
 
@@
 The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`\; @R-buildmer].
-Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts.
+
+Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the semantically informed against the naive condition within the pre-insight, \mbox{insight}, and post-insight parts.
 This was achieved using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
@@
 The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (<https://osf.io/uksbc/>).
-Unfortunately, lack of informed consent prevents us from sharing the raw EEG data.
+Participants' lack of informed consent to do so prevents us from openly sharing the raw EEG data.
 
@@
       bind_cols() %>%
-      set_rownames(c("\\textit{Fixed effects}", stub_anova))
+      set_rownames(c("\\textbf{Fixed effects}", stub_anova))
   )
@@
       bind_cols() %>%
-      set_rownames(c("\\textit{Informed $-$  naive}", stub_contrasts))
+      set_rownames(c("\\textbf{Informed - naive}", stub_contrasts))
   )
@@
   )
-  cnames <- c("\\textit{Fixed effects}", as.character(anov_print[1, ]))
+  cnames <- c("\\textbf{Fixed effects}", as.character(anov_print[1, ]))
   list(anov_print[2:nrow(anov_print), ], conts_print) %>%
@@
 × con.", "N400_f"]`, *p* `r table_exp1$anov["Pt.
-× con.", "N400_p"]`, while also being marginally significant in the P1 component, *F*`r table_exp1$anov["Pt.
+× con.", "N400_p"]`, while also showing a weak statistical trend in the P1 component, *F*`r table_exp1$anov["Pt.
 × con.", "P1_df"]` = `r table_exp1$anov["Pt.
@@
 
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s \> `r table_exp1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:exp1-table) and Figure \@ref(fig:exp1-plot)B).
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s $\ge$ `r table_exp1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:exp1-table) and Figure \@ref(fig:exp1-plot)B).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
@@
 Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report would have made it possible for such visual differences to emerge as a confounding factor.
-If they did, however, one would expect to detect these differences even before any keywords were presented, which we have now seen was not the case.
+If they did, however, one would expect to detect these differences even before any keywords were presented, which was apparently not the case.
 
@@
 
-In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part), to test whether the semantic information had any lasting effects on the processing of the objects.
+In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part).
+This allowed us to test if the semantic information had any lasting effects on the processing of the objects.
 As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Post-insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *p* = `r table_exp1$conts["Post-insight part", "N170_p"]`.
@@
 
-In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-insight part) they were able to understand what kind of object they saw.
+In Experiment 1, we measured the ERPs of participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-insight part) they were able to understand what kind of object they were seeing.
 To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
@@
 
-Because of the novelty of our experimental paradigm and the findings of Experiment 1, we ran a replication study to assess the robustness of these effects in another samples of participants.
+Because of the novelty of our experimental paradigm---measuring the ERPs while rather than after participants received semantic information about unfamiliar objects---and because of the novelty of our findings, we ran a replication study to assess the robustness of these effects with another sample of participants.
 
@@
 An average of `r format(round(objects_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects were assigned to the semantically informed condition (= `r scales::percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects were assigned to the naive condition (= `r scales::percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects was assigned to the semantically informed condition (= `r scales::percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects was assigned to the naive condition (= `r scales::percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
 Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
@@
 
-\bigskip\small\emph{Note.} 
+\bigskip\small\textit{Note.} 
 ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064).
+In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical signficance (\textit{p} = `r table_exp2$conts["Insight part", "N170_p"]`).
 Ampl.
-= amplitude.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.
+= amplitude.\newline*\textit{p} \textless{} .05.
+**\textit{p} \textless{} .01.
+***\textit{p} \textless{} .001.
 
@@
 
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`, and a significant reduction of the N400 component, *b* = `r table_exp2$conts["Insight part", "N400_est"]` µV, *p* `r table_exp2$conts["Insight part", "N400_p"]`.
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with an enhancement of the N170 component, although this effect marginally failed to reach statistical significance, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`.
+The reduction of the N400 component during semantically informed perception remained significant, *b* = `r table_exp2$conts["Insight part", "N400_est"]` µV, *p* `r table_exp2$conts["Insight part", "N400_p"]`.
 
@@
 
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "P1_p"]`.
-Also, N400 amplitudes in response to these objects remained significantly reduced, *b* = `r table_exp2$conts["Post-insight part", "N400_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "N400_p"]`.
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) again led to significantly reduced amplitudes in the N400 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Post-insight part", "N400_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "N400_p"]`.
+Also, P1 amplitudes in response these objects were significantly enlarged, *b* = `r table_exp2$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "P1_p"]`.
 
@@
 Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments\; @schad2020].
-This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
-They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2.
+This factor and its interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
+They were not included as by-participant random slopes because different participants took part in Experiments 1 and 2.
 Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit [@matuschek2017; @R-buildmer].
@@
 
-# Apply the function to compute the joint models for Experiments 1 and 2
-map(
-  comps$name,
-  compute_models,
-  formula = form_joint,
-  data = data_joint_subs,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-models.RDS") -> models_joint
+# # Apply the function to compute the joint models for Experiments 1 and 2
+# map(
+#   comps$name,
+#   compute_models,
+#   formula = form_joint,
+#   data = data_joint_subs,
+#   control = control,
+#   specs = specs_exp12
+# ) %>%
+#   set_names(comps$name) %T>%
+#   saveRDS("analysis/export/joint-models.RDS") -> models_joint
 ```
@@
 )
-```
-
-As shown in Table \@ref(tab:joint-table), the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Condition", "N400_df"]` = `r table_joint$anov["Condition", "N400_f"]`, *p* `r table_joint$anov["Condition", "N400_p"]`.
+
+# Extract the follow-up contrast for the main effect of experiment
+suppressMessages(emmeans::emm_options(lmerTest.limit = Inf))
+suppressMessages(
+  emmeans::emmeans(models_joint$N400$model, specs = pairwise ~ experiment, infer = TRUE)$contrasts %>%
+  as.data.frame() %>%
+  transmute(
+    est = round(estimate, 2) %>%
+      format(nsmall = 2, trim = TRUE),
+    p = round(`p.value`, 3) %>%
+      format(nsmall = 3, trim = TRUE) %>%
+      as.character() %>%
+      substr(2, nchar(.))
+  ) -> conts_N400_joint
+)
+```
+
+As shown in Table \@ref(tab:joint-table), the main effect of part was significant in the P1, N170, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Condition", "N400_df"]` = `r table_joint$anov["Condition", "N400_f"]`, *p* `r table_joint$anov["Condition", "N400_p"]`.
 Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s \> `r table_joint$anov["Pt.
@@
 × con.", "P1_p"]`.
-While there was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
+There was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, with more negative amplitudes in Experiment 1 as compared to Experiment 2, *b* = `r conts_N400_joint$est`.
+However, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
 
@@
 
-\bigskip\small\emph{Note.} 
+\bigskip\small\textit{Note.} 
 The violins and box plots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
@@
 Ampl.
-= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\emph{p} \textless{} .05.
-**\emph{p} \textless{} .01.
-***\emph{p} \textless{} .001.
+= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
+**\textit{p} \textless{} .01.
+***\textit{p} \textless{} .001.
 
@@
 
-```{r control-models, eval=rerun_models}
+```{r control-models, eval=TRUE}
 # # Keep all three conditions
@@
   formula = form_joint,
-  data = data_joint_subs,
+  data = data_joint_control,
   control = control,
@@
   stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of linear mixed-effects regression models with a different baseline",
+  caption = "Results of Linear Mixed-Effects Regression Models With a Different Baseline",
   note = "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval."
@@
 Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of morsing messages.
+Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of signalling messages.
 To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were preceded by matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords but on which participants failed to capitalize.
+Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
+Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
 Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, *b* = `r table_joint_control$conts["Insight part", "N400_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N400_p"]`.
@@
 
-Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400).
+Experiment 2, which was an exact replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400).
 Objects for which participants experienced semantically informed perception via matching keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes.
-When these objects were presented once more, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.
+Note, however, that the effect in the N170 component marginally failed to reach the conventional level for statistical significance in this replication experiment.
+When the objects were presented once more without any semantic information, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.
 
@@
 # Preprocess the EEG for Epxeriment 3 in Python
-map2(
-  .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp3,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp3
-
-# Backup epochs to the export folder
-epochs_exp3$save("analysis/export/exp3-epo.fif")
+fnames_exp3 <- list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE)
+py_run_string(
+  "epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **r.preproc_params)
+                  for fname, meta in zip(r.fnames_exp3, r.behav_exp3)]"
+)
+message("This worked!!!")
+py_run_string("epochs_exp3 = mne.epochs.concatenate_epochs(epochs_exp3)")
+message("This also worked!!!")
+py_run_string("epochs_exp3.save('analysis/export/exp3-epo.fif', overwrite=True)")
+py_run_string("del epochs_exp3")
+
+# Read the epochs that Python has written
+epochs_exp3 <- py$mne$read_epochs("analysis/export/exp3-epo.fif")
+
+# # Preprocess the EEG for Epxeriment 3 in Python
+# map2(
+#   .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
+#   .y = behav_exp3,
+#   ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
+# ) %>%
+#   # Concatenate epochs of all participants
+#   py$mne$epochs$concatenate_epochs() -> epochs_exp3
+# 
+# # Backup epochs to the export folder
+# epochs_exp3$save("analysis/export/exp3-epo.fif")
 
@@
 # Define new formula for LMMs
-form_exp3 <- buildmer::tabulate.formula(
+formula_exp3 <- buildmer::tabulate.formula(
   ~ part * condition * position +
@@
 To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
-For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was non-matching, thus keeping the perception of the object semantically naive.
+For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, the information was non-matching, thus keeping the perception of the object semantically naive.
 We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
 When the same objects were presented again without the semantic information, the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+We will discuss each of these effects in turn, starting with the latest (i.e., post-perceptual) effect and moving backward in time to the earlier (i.e., more perceptual) effects.
 
 The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
-Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing compared to the naive condition [@kutas2011].
+Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) lessened participants' demand for effortful semantic processing in comparison to the naive condition [@kutas2011].
 This replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
@@
 It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous findings using a similar experimental paradigm in the realm of face perception [@bentin2002]: Here, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
-This effect was absent when a visual control stimulus (a non-face object instead of the intact face) was shown between the two presentations of the scrambled face.
-In the realm of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
+This interpretation is supported by previous findings with a similar experimental paradigm in the domain of face perception [@bentin2002]: Here, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
+This effect was absent when a visual control stimulus (a non-face object) was shown between the two presentations of the scrambled face.
+In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
 Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
@@
 
-Unlike the N400 and N170 components, the P1 component (100--150 ms after object onset) was modulated by semantic information only one trial after it had been obtained.
-This is consistent with previous studies showing P1 effects when participants learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
-What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information) but that it can be observed as soon as one trial after semantic insight has happened.
+The P1 component (100--150 ms after object onset), unlike the N400 and N170 components, was modulated by semantic information only one trial after the information had been obtained.
+This is consistent with previous studies showing modulations of the P1 component when participants learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
+What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information).
+Instead, it can be observed as soon as one trial after semantic insight has happened.
 Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
 
-Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects as we perceive them.
-However, the finding that these two components were modulated in different parts of our experiment suggests that they reflect different aspects top-down processing with different time courses and neuroanatomical implementations.
-It has been pointed out that the onset of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem reflect recurrent processing *within* the visual system [@wyatte2014].
-Here we show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
+Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects.
+However, the finding that these two components were modulated in different parts of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
+It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem reflect recurrent processing *within* the visual system [@wyatte2014].
+Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
 
@@
 They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
-This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
+This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital cortex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
 Both of these cortical regions are consistent with the neural generators of the N170 and P1 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
 
-On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999, but see @clarke2020].
-However, proponents of such a modular view have pointed out important conceptual and methodological shortcomings of previous studies claiming to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
-We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was presented (in the pre-insight part).
+On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999; but see @clarke2020].
+However, proponents of such a modular view have pointed out important shortcomings of previous studies that claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
+We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was being presented (in the pre-insight part).
 Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual locus from those with a post-perceptual locus.
@@
 
-An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in machine vision [e.g., @dicarlo2012; @marr1982].
-In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @serre2007].
+In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
 For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this "barrier of meaning" [@mitchell2020].
-Drawing inspiration from cognitive psychology and human neuroscientific data may help making these models more biologically plausible and, at the same time, more resource and data efficient.
+Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.
 
@@
 The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004; @hochstein2002] which posits that objects first enter our visual consciousness at an abstract, conceptual level.
-Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract relevant lower-level features ("vision with scrutiny").
+Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
 This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
-Besides the reverse hierarchy theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories [e.g., @lupyan2015; @panichello2013; @yuille2006].
+Besides this specific theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories [e.g., @clark2013; @lupyan2015; @panichello2013; @yuille2006].
 Despite the theoretical advances, the mechanistic details of these top-down effects at the algorithmic and implementational level [@marr1982] remain to be clarified.
@@
 Another one is our reliance on rare and highly specialized objects (see appendix).
-This was necessary to induce the experience of semantic insight in an adult population of undergraduate students but may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
+This was necessary to induce the experience of semantic insight in a population of undergraduate students but it may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
 Finally, the number participants (*n* = 24 per experiment) and trials (*k* $\approx$ 30 per part in the insight condition and *k* $\approx$ 50 per part in the naive condition) can be considered small by today's standards [@baker2020].
-Our analysis may therefore not have been particularly sensitive, especially since linear mixed-effects regression models often have limited statistical power [see, e.g., the simulations by @matuschek2017].
+Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances [see, e.g., the simulations by @matuschek2017].
+This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r table_exp1$conts["Insight part", "N170_p"]`) failed to reach statisticial signficance in the replication experiment (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
+To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).
+It should be noted, however, that the joint analysis of both data sets yielded a very robust N170 effect (*p* = `r table_joint$conts["Insight part", "N170_p"]`).
+This makes it less likely that the effect observed in Experiment 1 was due to a false positive and instead suggests that statistical power in Experiment 2 was insufficient to render the effect significant.
+Also note that the effect in the P1 component was statistically significant in both experiments individually, making an even stronger case for the susceptibility of early cortical processing to newly acquired knowledge about objects.
 
@@
 
-Nevertheless, this study provides preliminary evidence that whenever we acquire semantic information about a previously unfamiliar object, this information influences multiple stages of processing.
-These influences do not seem to be confined to later, post-perceptual stages---typically associated with semantic processing---but can also be observed at earlier stages---typically reflecting lower levels of visual perception and happening within 200 ms after the object is presented to us.
+Taken together, this study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the processing of the object.
+This influence is immediate in at least two different ways: First, it does not require extensive training and can instead be observed within the same trial in which the information is being presented (and/or one trial later).
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages---typically associated with semantic processing---but also at earlier stages---typically associated with visual perception itself and happenning within less than a fifth of a second after the object is presented to us.
 
@@
 
-\begingroup
 \setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup

### 2021-01-26 analysis/master_thesis.Rmd
proofreading for master thesis, outsource functions for plots and tables, add t values and performance

@@
   - \fancyhead[RE,LO]{Semantic Knowledge and Unfamiliar Objects}
+  - \renewcommand{\headrulewidth}{0.4pt}
   - \usepackage{setspace}
   - \AtBeginEnvironment{tabular}{\doublespacing}
+  - \usepackage{makecell}
+  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
   - \captionsetup[table]{font={stretch=1.5}}
@@
 &\\
-Berlin, den 29.01.2021&\\
+Berlin, den 26.01.2021&\\
 \end{tabular}
@@
 
-\begin{center}\textbf{Acknowledgment}\end{center}
+\vspace*{55mm}
 
-I would like to thank ... (tbc)
+\begin{center}\textbf{Acknowledgments}\end{center}
+
+This thesis presents a re-analysis of the data from two experiments that had already been conducted before I joined the Neurocognitive Psychology Lab at Humboldt-Universität zu Berlin.
+Therefore, it would not have been possible for me to write it without the time and effort that Franziska Süß, Nele Langosch, and Rasha Abdel Rahman have spent conceptualizing and running these experiments, along with the help of all participants, research assistants, and technical staff who contributed to the data collection.
+I would also like to thank all current members of the lab for their guidance and fruitful discussions on the topics of data analysis and reporting.
+Valuable feedback on an earlier draft of this thesis was given by Anna Kuhlen, Annika Just, and Garrett Widener.
+Finally, I am most grateful to my parents, friends, and supervisors: During the journey of writing this thesis, their support has often literally changed my view of the world around me to the better.
 
@@
 \thispagestyle{empty}
+
+\vspace*{45mm}
+
 \begin{flushleft}
@@
 
-Does our perception of an object change as soon as we discover what it is for?
-This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it pertains to the long-standing debate around the (im)penetrability of perception by "higher" cognitive capacities.
-In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with valid information about their function---leading to semantically informed perception---or together with invalid information---resulting in naive perception.
-We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of perceiving objects differed from one another.
+\noindent Does our perception of an object change as soon as we discover what function it serves?
+This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception.
+We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
 We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
@@
 We replicated these novel findings in an independent sample (*n* = 24).
-Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
+Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
 
-<!-- Acutal paper -->
+*Keywords:* objects, semantic knowledge, visual perception, event-related potentials
+
+<!-- Actual paper -->
 \newpage
@@
 
-<!-- Appendix -->
+<!-- Appendix A -->
 \newpage
 
-```{r appendix, child = "appendix.Rmd"}
+# Appendix {.unnumbered}
+
+```{r appendix_a, child = "appendix_a.Rmd"}
+```
+
+<!-- Appendix B -->
+\newpage
+
+```{r appendix_b, child = "appendix_b.Rmd"}
 ```
@@
 Alexander Enge\newline
-Berlin, 29.01.2021
+Berlin, 26.01.2021
 
@@
 \clearpage\mbox{}\thispagestyle{empty}\clearpage
+
+<!-- Empty page -->
+\clearpage\mbox{}\thispagestyle{empty}\clearpage

### 2021-01-26 analysis/manuscript_files/functions_plots_tables.R

@@ -1,0 +1,457 @@
+####################################################################################################
+## FUNCTIONS TO CREATE PLOTS AND TABLES ##
+####################################################################################################
+
+# Function to plot the trial structure
+plot_trials <- function(){
+  suppressMessages(require(magick))
+  color_informed <- viridisLite::viridis(1, begin = 0.1)
+  color_naive <- viridisLite::viridis(1, begin = 0.5)
+  ggplot() +
+    coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
+    ## PART II ##
+    # Title
+    annotate("text", x = 0, y = 97.2, label = "Insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
+    # Arrow
+    annotate("segment", x = -30, xend = 24, y = 79, yend = 85, arrow = arrow(length = unit(0.1, "inches"))) +
+    # Squares
+    annotate("rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75, color = "black", fill = "white") +
+    annotate("rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65, color = color_informed, fill = "white") +
+    annotate("rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89, color = color_naive, fill = "white") +
+    annotate("rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79, color = "black", fill = "white") +
+    annotate("rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81, color = "black", fill = "white") +
+    annotate("text", x = -27, y = 65.3, label = "+", size = 20 / .pt, family = "Helvetica") +
+    annotate("text", x = -9, y = 55, label = "potatoes\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
+    annotate("text", x = -9, y = 79, label = "message\nsignalling", size = 10 / .pt, family = "Helvetica", color = color_naive) +
+    annotate("text", x = 9, y = 67, label = "*", size = 30 / .pt, family = "Helvetica") +
+    draw_image("analysis/manuscript_files/potato_masher.png", x = 18, y = 62, width = 18, height = 18) +
+    # Timings
+    annotate("text", x = -9, y = 67.3, label = "or", size = 10 / .pt, family = "Helvetica") +
[…]

### 2021-01-26 analysis/appendix_a.Rmd
add new appendix

---
title             : "Appendix"
shorttitle        : ""

author: 
  - name        : ""
    affiliation : ""

affiliation:
  - id          : ""
    institution : ""

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
numbersections    : true

documentclass     : "apa7"
classoption       : "man"
output            :
  papaja::apa6_pdf:
    latex_engine  : "xelatex"

header-includes:
  - \usepackage[export]{adjustbox}
  - \usepackage{makecell}
  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
---

## Appendix A: Stimuli {.unnumbered}

\bigskip

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

```{r appendix, include=TRUE, warning=FALSE, message=FALSE, results="asis"}
# Load packages
library(papaja)
library(tidyverse)

# Print table of materials
read_tsv("materials/items.txt", col_types = cols()) %>%
  mutate(
    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  ) %>%
  transmute(
    img = paste0("\\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/", item, ".png}"),
    item = as.character(item),
    match = paste(match_ger, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c("Picture", "ID", "Matching keywords", "Non-matching keywords"),
    escape = FALSE,
    longtable = TRUE,
    caption = "Unfamiliar Object Stimuli\\smallskip",
    font_size = "footnotesize"
  )
```

### 2021-01-26 analysis/appendix_a.tex
add new appendix

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Appendix},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{}
\usepackage{csquotes}
\usepackage[export]{adjustbox}
\usepackage{makecell}
\renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Appendix}
\author{\textsuperscript{}}
\date{}

\affiliation{\vspace{0.5cm}\textsuperscript{} }

\begin{document}
\maketitle

\hypertarget{appendix-a}{%
\section*{Appendix A}\label{appendix-a}}
\addcontentsline{toc}{section}{Appendix A}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\begin{center}
\begin{ThreePartTable}

\footnotesize{

\begin{longtable}{llll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:appendix}Unfamiliar Object Stimuli\smallskip}\\
\toprule
Picture & ID & Matching keywords & Non-matching keywords\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:appendix} continued}}\\
\toprule
Picture & ID & Matching keywords & Non-matching keywords\\
\midrule
\endhead
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/1.png} & 1 & \makecell[l]{elektrische Spannung, prüfen\\{[electric current, measuring]}} & \makecell[l]{Makkaroni, formen\\{[macaroni, forming]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/2.png} & 2 & \makecell[l]{Makkaroni, formen\\{[macaroni, forming]}} & \makecell[l]{Kuh, vom Zaun abhalten\\{[cow, keeping away from the fence]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/3.png} & 3 & \makecell[l]{Knochen, sägen\\{[bones, sawing]}} & \makecell[l]{Streckenmaß, Sonnenlicht nutzen\\{[distance measure, using sunrays]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/4.png} & 4 & \makecell[l]{Unkraut, jäten\\{[weed, removing]}} & \makecell[l]{Uhr, mit Wärme betreiben\\{[clock, operating with heat]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/5.png} & 5 & \makecell[l]{Mausefalle, zuschnappen\\{[mousetrap, snap-shutting]}} & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lense, cutting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/6.png} & 6 & \makecell[l]{Goldmünzen, wiegen\\{[gold coin, weighing]}} & \makecell[l]{Farbe, vom Fenster abschleifen\\{[paint, scraping off the window]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/7.png} & 7 & \makecell[l]{Knie, fixieren\\{[knee, fixating]}} & \makecell[l]{Buchstaben, tippen\\{[letter, typing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/8.png} & 8 & \makecell[l]{Eierkarton, pressen\\{[egg carton, pressing]}} & \makecell[l]{Tabak, zermahlen\\{[tobacco, pulverize]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/9.png} & 9 & \makecell[l]{Baum, erklettern\\{[tree, climbing]}} & \makecell[l]{Rotation, Ladung erzeugen\\{[rotation, creating electric charge]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/10.png} & 10 & \makecell[l]{Buchstaben, tippen\\{[letter, typing]}} & \makecell[l]{Pferdehuf, Halt geben\\{[horse hoof, giving grip]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/11.png} & 11 & \makecell[l]{Akkordeon, spielen\\{[accordion, playing]}} & \makecell[l]{Seil, schneiden\\{[rope, cutting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/12.png} & 12 & \makecell[l]{Körper, trainieren\\{[body, training]}} & \makecell[l]{Buch, offen halten\\{[book, binding]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/13.png} & 13 & \makecell[l]{Farbe, vom Fenster abschleifen\\{[paint, scraping off the window]}} & \makecell[l]{von Hand, zentrifugieren\\{[by hand, centrifugating]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/14.png} & 14 & \makecell[l]{Außenbereich, heizen\\{[outdoor area, heating]}} & \makecell[l]{Rasierklinge, schärfen\\{[razor blade, sharpening]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/15.png} & 15 & \makecell[l]{Pflanzenteile, vergrößern\\{[plant parts, magnifying]}} & \makecell[l]{Katzenklo, sich selbst reinigen\\{[litter box, self-cleaning]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/16.png} & 16 & \makecell[l]{Krawatten, aufhängen\\{[necktie, hanging up]}} & \makecell[l]{Zeichnungen, vermessen\\{[drawings, measuring]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/17.png} & 17 & \makecell[l]{Schallplatte, abtasten\\{[vinyl record, reading]}} & \makecell[l]{Ball, katapultieren\\{[ball, catapulting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/18.png} & 18 & \makecell[l]{Glas, schneiden\\{[glass, cutting]}} & \makecell[l]{Eier, wiegen\\{[eggs, weighing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/19.png} & 19 & \makecell[l]{Briketts, pressen\\{[briquette, pressing]}} & \makecell[l]{Narkosemittel, abgeben\\{[anesthetic, administering]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/20.png} & 20 & \makecell[l]{Orgelton, erzeugen\\{[organ sound, making]}} & \makecell[l]{Bandage, rollen\\{[bandage, rolling]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/21.png} & 21 & \makecell[l]{Spannung, erzeugen\\{[electric current, making]}} & \makecell[l]{Fußstütze, reiten\\{[footrest, horseback riding]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/22.png} & 22 & \makecell[l]{Narkosemittel, abgeben\\{[anesthetic, administering]}} & \makecell[l]{Nüsse, aufbrechen\\{[nuts, cracking]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/23.png} & 23 & \makecell[l]{Bandage, rollen\\{[bandage, rolling]}} & \makecell[l]{Schnee, rodeln\\{[snow, sleighing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/24.png} & 24 & \makecell[l]{Weinfass, Loch einschlagen\\{[wine barrel, smashing a hole]}} & \makecell[l]{Tier, einfangen\\{[animal, trapping]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/25.png} & 25 & \makecell[l]{Flaschenkorken, einführen\\{[bottle cork, inserting]}} & \makecell[l]{Pferd, im Moor laufen\\{[horse, walking in the moor]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/26.png} & 26 & \makecell[l]{Automat, Eier ausbrüten\\{[machine, incubating eggs]}} & \makecell[l]{Windgeschwindigkeit, messen\\{[wind speed, measuring]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/27.png} & 27 & \makecell[l]{Korngarbe, greifen\\{[sheaf, grabbing]}} & \makecell[l]{Treibhaus, heizen\\{[glass house, heating]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/28.png} & 28 & \makecell[l]{Brief, wiegen\\{[letter, weighing]}} & \makecell[l]{Korngarbe, greifen\\{[sheaf, grabbing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/29.png} & 29 & \makecell[l]{Löcher, bohren\\{[hole, drilling]}} & \makecell[l]{Sonnenlicht, Intensität messen\\{[sunlight, measure intensity]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/30.png} & 30 & \makecell[l]{Angelschnur, kurbeln\\{[fishing line, winding]}} & \makecell[l]{Glaskörper, musizieren\\{[glass body, making music]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/31.png} & 31 & \makecell[l]{Kurven, malen\\{[curve, drawing]}} & \makecell[l]{Nussöl, pressen\\{[nut oil, pressing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/32.png} & 32 & \makecell[l]{Radiofrequenz, einstellen\\{[radio frequency, tuning]}} & \makecell[l]{Erektion, helfen\\{[erection, helping]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/33.png} & 33 & \makecell[l]{Zäpfchen, pressen\\{[suppository, pressing]}} & \makecell[l]{Unkraut, jäten\\{[weed, removing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/34.png} & 34 & \makecell[l]{Fass, öffnen\\{[barrel, opening]}} & \makecell[l]{Pflanzenteile, vergrößern\\{[plant parts, magnifying]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/35.png} & 35 & \makecell[l]{Bergbaustollen, beleuchten\\{[mining tunnel, lightening]}} & \makecell[l]{Knie, fixieren\\{[knee, fixating]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/36.png} & 36 & \makecell[l]{Kuh, vom Zaun abhalten\\{[cow, keeping away from the fence]}} & \makecell[l]{Radiofrequenz, einstellen\\{[radio frequency, tuning]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/37.png} & 37 & \makecell[l]{Saatgut, gleichmäßig aussäen\\{[seeds, sowing evenly]}} & \makecell[l]{Fass, öffnen\\{[barrel, opening]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/38.png} & 38 & \makecell[l]{Flaschen, trocknen\\{[bottles, drying]}} & \makecell[l]{Bleistift, anspitzen\\{[pencil, sharpening]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/39.png} & 39 & \makecell[l]{Uhr, mit Wärme betreiben\\{[clock, operating with heat]}} & \makecell[l]{Körper, untersuchen\\{[body, training]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/40.png} & 40 & \makecell[l]{Tonpott, trommeln\\{[clay pot, drumming]}} & \makecell[l]{Piano, stimmen\\{[piano, tuning]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/41.png} & 41 & \makecell[l]{Sprengstoffexplosion, auslösen\\{[dynamite explosion, triggering]}} & \makecell[l]{Fisch, wiegen\\{[fish, weighing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/42.png} & 42 & \makecell[l]{Pferdehuf, Halt geben\\{[horse hoof, giving grip]}} & \makecell[l]{Zäpfchen, pressen\\{[suppository, pressing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/43.png} & 43 & \makecell[l]{Bleistift, anspitzen\\{[pencil, sharpening]}} & \makecell[l]{Angel, Köder markieren\\{[fishing rod, marking bait]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/44.png} & 44 & \makecell[l]{Nussöl, pressen\\{[nut oil, pressing]}} & \makecell[l]{Zeichen, einbrennen\\{[marks, burning in]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/45.png} & 45 & \makecell[l]{Rasierklinge, schärfen\\{[razor blade, sharpening]}} & \makecell[l]{Kurven, malen\\{[curve, drawing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/46.png} & 46 & \makecell[l]{heiße Platten, anheben\\{[hot plates, lifting]}} & \makecell[l]{Kleidung, im Eimer waschen\\{[clothes, washing in a bucket]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/47.png} & 47 & \makecell[l]{Film, aufspulen\\{[film roll, winding]}} & \makecell[l]{Mund, offen halten\\{[mouth, keeping open]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/48.png} & 48 & \makecell[l]{Waffe, entflammen\\{[weapon, inflaming]}} & \makecell[l]{Uhrzeit, anzeigen\\{[time, displaying]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/49.png} & 49 & \makecell[l]{Mikroskop-Proben, schneiden\\{[microscopic samples, slicing]}} & \makecell[l]{heiße Platten, anheben\\{[hot plates, lifting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/50.png} & 50 & \makecell[l]{Glaskörper, musizieren\\{[glass body, making music]}} & \makecell[l]{Kork, flach pressen\\{[cork, pressing flat]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/51.png} & 51 & \makecell[l]{Dampf, zerstäuben\\{[steam, spraying]}} & \makecell[l]{Buch, binden\\{[book, opening]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/52.png} & 52 & \makecell[l]{Mandeln, operieren\\{[kidneys, operating]}} & \makecell[l]{Film, aufspulen\\{[film roll, winding]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/53.png} & 53 & \makecell[l]{Toastbrot, rösten\\{[toast, roasting]}} & \makecell[l]{Autobatterie, Spannung testen\\{[car battery, measuring voltage]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/54.png} & 54 & \makecell[l]{Fußstütze, reiten\\{[footrest, horseback riding]}} & \makecell[l]{Stromstärke, messen\\{[current, measuring]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/55.png} & 55 & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, survining fires]}} & \makecell[l]{Botschaft, telegrafieren\\{[message, telegraphing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/56.png} & 56 & \makecell[l]{Schnee, rodeln\\{[snow, sleighing]}} & \makecell[l]{Dampf, zerstäuben\\{[steam, spraying]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/57.png} & 57 & \makecell[l]{Nüsse, aufbrechen\\{[nuts, cracking]}} & \makecell[l]{Ziegelsteine, formen\\{[bricks, forming]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/58.png} & 58 & \makecell[l]{Radiergummi, mit Strom betreiben\\{[eraser, operating with electricity]}} & \makecell[l]{Münzen, aufbewahren\\{[coins, storing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/59.png} & 59 & \makecell[l]{Treibhaus, heizen\\{[glass house, heating]}} & \makecell[l]{Messer, schleifen\\{[knife, sharpening]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/60.png} & 60 & \makecell[l]{Botschaft, telegrafieren\\{[message, telegraphing]}} & \makecell[l]{Toastbrot, rösten\\{[toast, roasting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/61.png} & 61 & \makecell[l]{Angel, Köder markieren\\{[fishing rod, marking bait]}} & \makecell[l]{Baum, erklettern\\{[tree, climbing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/62.png} & 62 & \makecell[l]{Katzenklo, sich selbst reinigen\\{[litter box, self-cleaning]}} & \makecell[l]{Tankfüllstand, messen\\{[fuel tank level, gauging]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/63.png} & 63 & \makecell[l]{Körper, untersuchen\\{[body, examining]}} & \makecell[l]{Schuhe, auf Eis laufen\\{[shoes, walking on ice]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/64.png} & 64 & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lense, cutting]}} & \makecell[l]{Saatgut, gleichmäßig aussäen\\{[seeds, sowing evenly]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/65.png} & 65 & \makecell[l]{Draht, wickeln\\{[wire, winding]}} & \makecell[l]{Bergbaustollen, beleuchten\\{[mining tunnel, lightening]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/66.png} & 66 & \makecell[l]{Buch, offen halten\\{[book, opening]}} & \makecell[l]{Sprengstoffexplosion, auslösen\\{[dynamite explosion, triggering]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/67.png} & 67 & \makecell[l]{Feldanbau, häckseln\\{[harvest, chopping]}} & \makecell[l]{Draht, wickeln\\{[wire, winding]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/68.png} & 68 & \makecell[l]{Schnurlot, absenken\\{[plummet, letting down]}} & \makecell[l]{Korken, formen\\{[bottle cork, forming]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/69.png} & 69 & \makecell[l]{Sternenbilder, vermessen\\{[stellar constellation, measuring]}} & \makecell[l]{Schnurlot, absenken\\{[plummet, letting down]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/70.png} & 70 & \makecell[l]{Nachricht, morsen\\{[message, signalling]}} & \makecell[l]{Feldanbau, häckseln\\{[harvest, chopping]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/71.png} & 71 & \makecell[l]{Musikgerät, stampfen\\{[musical instrument, stamping]}} & \makecell[l]{Goldmünzen, wiegen\\{[gold coin, weighing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/72.png} & 72 & \makecell[l]{Schuhe, auf Eis laufen\\{[shoes, walking on ice]}} & \makecell[l]{Geschwindigkeit, ermitteln\\{[speed, determining]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/73.png} & 73 & \makecell[l]{Geschwindigkeit, ermitteln\\{[speed, determining]}} & \makecell[l]{Mausefalle, zuschnappen\\{[mousetrap, snap-shutting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/74.png} & 74 & \makecell[l]{Zeichen, einbrennen\\{[marks, burning in]}} & \makecell[l]{Luftdruck, messen\\{[air pressure, measuring]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/75.png} & 75 & \makecell[l]{Tabak, zermahlen\\{[tobacco, pulverize]}} & \makecell[l]{Flaschen, trocknen\\{[bottles, drying]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/76.png} & 76 & \makecell[l]{Stromstärke, messen\\{[current, measuring]}} & \makecell[l]{Mandeln, operieren\\{[kidneys, operating]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/77.png} & 77 & \makecell[l]{Tier, einfangen\\{[animal, trapping]}} & \makecell[l]{Maiskolben, entkörnen\\{[corncob, removing grains]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/78.png} & 78 & \makecell[l]{Messer, schleifen\\{[knife, sharpening]}} & \makecell[l]{Schritte, vergrößern\\{[steps, extending]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/79.png} & 79 & \makecell[l]{Leierkasten, klingen\\{[barrel organ, making sounds]}} & \makecell[l]{Fass, anheben\\{[barrel, lifting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/80.png} & 80 & \makecell[l]{Buch, binden\\{[book, binding]}} & \makecell[l]{Löcher, bohren\\{[hole, drilling]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/81.png} & 81 & \makecell[l]{Kork, flach pressen\\{[cork, pressing flat]}} & \makecell[l]{Elektroschock, spielen\\{[electric shock, playing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/82.png} & 82 & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}} & \makecell[l]{Blumentopf, sich selbst wässern\\{[flower pot, self-watering]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/83.png} & 83 & \makecell[l]{Fass, anheben\\{[barrel, lifting]}} & \makecell[l]{Mikroskop-Proben, schneiden\\{[microscopic samples, slicing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/84.png} & 84 & \makecell[l]{Pferd, im Moor laufen\\{[horse, walking in the moor]}} & \makecell[l]{Luft, abpumpen\\{[air, pumping out]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/85.png} & 85 & \makecell[l]{altes Ritual, hacken\\{[ancient ritual, chopping]}} & \makecell[l]{Spannung, erzeugen\\{[electric current, making]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/86.png} & 86 & \makecell[l]{Kleidung, im Eimer waschen\\{[clothes, washing in a bucket]}} & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, survining fires]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/87.png} & 87 & \makecell[l]{Maiskolben, entkörnen\\{[corncob, removing grains]}} & \makecell[l]{Brief, wiegen\\{[letter, weighing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/88.png} & 88 & \makecell[l]{Ball, katapultieren\\{[ball, catapulting]}} & \makecell[l]{Radiergummi, mit Strom betreiben\\{[eraser, operating with electricity]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/89.png} & 89 & \makecell[l]{Zeichnungen, vermessen\\{[drawings, measuring]}} & \makecell[l]{Brenner, löten\\{[burner, soldering]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/90.png} & 90 & \makecell[l]{Elektroschock, spielen\\{[electric shock, playing]}} & \makecell[l]{Weinfass, Loch einschlagen\\{[wine barrel, smashing a hole]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/91.png} & 91 & \makecell[l]{Lieferungen, abzählen\\{[deliveries, counting]}} & \makecell[l]{Außenbereich, heizen\\{[outdoor area, heating]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/92.png} & 92 & \makecell[l]{Rotation, Ladung erzeugen\\{[rotation, creating electric charge]}} & \makecell[l]{Musikgerät, stampfen\\{[musical instrument, stamping]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/93.png} & 93 & \makecell[l]{Herz, durch Maschine ersetzen\\{[heart, replacing with machine]}} & \makecell[l]{Kerzen, löschen\\{[candles, extinguishing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/94.png} & 94 & \makecell[l]{Seil, schneiden\\{[rope, cutting]}} & \makecell[l]{Akkordeon, spielen\\{[accordion, playing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/95.png} & 95 & \makecell[l]{Fisch, wiegen\\{[fish, weighing]}} & \makecell[l]{Herz, durch Maschine ersetzen\\{[heart, replacing with machine]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/96.png} & 96 & \makecell[l]{Kerzen, löschen\\{[candles, extinguishing]}} & \makecell[l]{Körper, trainieren\\{[body, examining]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/97.png} & 97 & \makecell[l]{Korken, formen\\{[bottle cork, forming]}} & \makecell[l]{Sternenbilder, vermessen\\{[stellar constellation, measuring]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/98.png} & 98 & \makecell[l]{Erektion, helfen\\{[erection, helping]}} & \makecell[l]{Waffe, werfen\\{[weapn, throwing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/99.png} & 99 & \makecell[l]{Streckenmaß, Sonnenlicht nutzen\\{[distance measure, using sunrays]}} & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/100.png} & 100 & \makecell[l]{Luftdruck, messen\\{[air pressure, measuring]}} & \makecell[l]{Knochen, sägen\\{[bones, sawing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/101.png} & 101 & \makecell[l]{Piano, stimmen\\{[piano, tuning]}} & \makecell[l]{Eierkarton, pressen\\{[egg carton, pressing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/102.png} & 102 & \makecell[l]{von Hand, zentrifugieren\\{[by hand, centrifugating]}} & \makecell[l]{Lieferungen, abzählen\\{[deliveries, counting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/103.png} & 103 & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}} & \makecell[l]{Nachricht, morsen\\{[message, signalling]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/104.png} & 104 & \makecell[l]{Waffe, werfen\\{[weapn, throwing]}} & \makecell[l]{elektrische Spannung, prüfen\\{[electric current, measuring]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/105.png} & 105 & \makecell[l]{Tankfüllstand, messen\\{[fuel tank level, gauging]}} & \makecell[l]{Tonpott, trommeln\\{[clay pot, drumming]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/106.png} & 106 & \makecell[l]{Uhrzeit, anzeigen\\{[time, displaying]}} & \makecell[l]{altes Ritual, hacken\\{[ancient ritual, chopping]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/107.png} & 107 & \makecell[l]{Windgeschwindigkeit, messen\\{[wind speed, measuring]}} & \makecell[l]{Waffe, entflammen\\{[weapon, inflaming]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/108.png} & 108 & \makecell[l]{Schlüsselloch, stanzen\\{[keyhole, punching]}} & \makecell[l]{Automat, Eier ausbrüten\\{[machine, incubating eggs]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/109.png} & 109 & \makecell[l]{Ziegelsteine, formen\\{[bricks, forming]}} & \makecell[l]{Schallplatte, abtasten\\{[vinyl record, reading]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/110.png} & 110 & \makecell[l]{Becher, Schall auffangen\\{[drinking cup, picking up sound]}} & \makecell[l]{Schlüsselloch, stanzen\\{[keyhole, punching]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/111.png} & 111 & \makecell[l]{Luft, abpumpen\\{[air, pumping out]}} & \makecell[l]{Briketts, pressen\\{[briquette, pressing]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/112.png} & 112 & \makecell[l]{Mund, offen halten\\{[mouth, keeping open]}} & \makecell[l]{Orgelton, erzeugen\\{[organ sound, making]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/113.png} & 113 & \makecell[l]{Autobatterie, Spannung testen\\{[car battery, measuring voltage]}} & \makecell[l]{Becher, Schall auffangen\\{[drinking cup, picking up sound]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/114.png} & 114 & \makecell[l]{Sonnenlicht, Intensität messen\\{[sunlight, measure intensity]}} & \makecell[l]{Krawatten, aufhängen\\{[necktie, hanging up]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/115.png} & 115 & \makecell[l]{Kutschrad, anschließen\\{[carriage wheel, locking]}} & \makecell[l]{Angelschnur, kurbeln\\{[fishing line, winding]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/116.png} & 116 & \makecell[l]{Eier, wiegen\\{[eggs, weighing]}} & \makecell[l]{Leierkasten, klingen\\{[barrel organ, making sounds]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/117.png} & 117 & \makecell[l]{Blumentopf, sich selbst wässern\\{[flower pot, self-watering]}} & \makecell[l]{Glas, schneiden\\{[glass, cutting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/118.png} & 118 & \makecell[l]{Schritte, vergrößern\\{[steps, extending]}} & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/119.png} & 119 & \makecell[l]{Münzen, aufbewahren\\{[coins, storing]}} & \makecell[l]{Kutschrad, anschließen\\{[carriage wheel, locking]}}\\
\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/120.png} & 120 & \makecell[l]{Brenner, löten\\{[burner, soldering]}} & \makecell[l]{Flaschenkorken einführen, einführen\\{[bottle cork, inserting]}}\\
\bottomrule
\end{longtable}

}

\end{ThreePartTable}
\end{center}

\end{document}

### 2021-01-26 analysis/appendix_b.Rmd
add new appendix

---
title             : "Appendix"
shorttitle        : ""

author: 
  - name        : ""
    affiliation : ""

affiliation:
  - id          : ""
    institution : ""

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
numbersections    : true

documentclass     : "apa7"
classoption       : "man"
output            :
  papaja::apa6_pdf:
    latex_engine  : "xelatex"
---

## Appendix B: Linear Mixed-Effects Models {.unnumbered}

\noindent Linear mixed-effects models after model selection for Experiment 1:

\footnotesize

```{r exp1_formulas, include=TRUE}
# Load packages
library(purrr)

# Define function to print the formulas
print_formula <- function(model) cat(deparse(formula(model), width.cutoff = 75), sep = "\n")

# Formulas for models for Experiment 1
readRDS("analysis/export/exp1-models.RDS") %>% walk(~ print_formula (.x$model))
```

\normalsize

\noindent Linear mixed-effects models after model selection for Experiment 2:

\footnotesize

```{r exp2_formulas, include=TRUE}
# Formulas for models for Experiment 2
readRDS("analysis/export/exp2-models.RDS") %>% walk(~ print_formula (.x$model))
```

\normalsize

\noindent Linear mixed-effects models after model selection for Experiments 1 and 2 combined:

\footnotesize

```{r joint_formulas, include=TRUE}
# Formulas for joint models
readRDS("analysis/export/joint-models.RDS") %>% walk(~ print_formula (.x$model))
```

\normalsize

### 2021-01-26 analysis/appendix_b.tex
add new appendix

--- 2021-01-26 analysis/appendix_a.tex
@@
 \usepackage{csquotes}
-\usepackage[export]{adjustbox}
-\usepackage{makecell}
-\renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
 \ifxetex
@@
 
-\hypertarget{appendix-a}{%
-\section*{Appendix A}\label{appendix-a}}
-\addcontentsline{toc}{section}{Appendix A}
+\hypertarget{appendix-b}{%
+\section*{Appendix B}\label{appendix-b}}
+\addcontentsline{toc}{section}{Appendix B}
 
-\setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
+\noindent Linear mixed-effects models after model selection for Experiment 1:
 
-\begin{center}
-\begin{ThreePartTable}
+\footnotesize
 
-\footnotesize{
+\begin{verbatim}
+## P1 ~ 1 + part + condition + part:condition + (1 + part | participant)
+## N170 ~ 1 + part + condition + part:condition + (1 + part + condition | participant)
+## N400 ~ 1 + part + condition + part:condition + (1 + part + condition | participant)
+\end{verbatim}
 
-\begin{longtable}{llll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:appendix}Unfamiliar Object Stimuli\smallskip}\\
-\toprule
-Picture & ID & Matching keywords & Non-matching keywords\\
-\midrule
-\endfirsthead
-\caption*{\normalfont{Table \ref{tab:appendix} continued}}\\
-\toprule
-Picture & ID & Matching keywords & Non-matching keywords\\
-\midrule
-\endhead
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/1.png} & 1 & \makecell[l]{elektrische Spannung, prüfen\\{[electric current, measuring]}} & \makecell[l]{Makkaroni, formen\\{[macaroni, forming]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/2.png} & 2 & \makecell[l]{Makkaroni, formen\\{[macaroni, forming]}} & \makecell[l]{Kuh, vom Zaun abhalten\\{[cow, keeping away from the fence]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/3.png} & 3 & \makecell[l]{Knochen, sägen\\{[bones, sawing]}} & \makecell[l]{Streckenmaß, Sonnenlicht nutzen\\{[distance measure, using sunrays]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/4.png} & 4 & \makecell[l]{Unkraut, jäten\\{[weed, removing]}} & \makecell[l]{Uhr, mit Wärme betreiben\\{[clock, operating with heat]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/5.png} & 5 & \makecell[l]{Mausefalle, zuschnappen\\{[mousetrap, snap-shutting]}} & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lense, cutting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/6.png} & 6 & \makecell[l]{Goldmünzen, wiegen\\{[gold coin, weighing]}} & \makecell[l]{Farbe, vom Fenster abschleifen\\{[paint, scraping off the window]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/7.png} & 7 & \makecell[l]{Knie, fixieren\\{[knee, fixating]}} & \makecell[l]{Buchstaben, tippen\\{[letter, typing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/8.png} & 8 & \makecell[l]{Eierkarton, pressen\\{[egg carton, pressing]}} & \makecell[l]{Tabak, zermahlen\\{[tobacco, pulverize]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/9.png} & 9 & \makecell[l]{Baum, erklettern\\{[tree, climbing]}} & \makecell[l]{Rotation, Ladung erzeugen\\{[rotation, creating electric charge]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/10.png} & 10 & \makecell[l]{Buchstaben, tippen\\{[letter, typing]}} & \makecell[l]{Pferdehuf, Halt geben\\{[horse hoof, giving grip]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/11.png} & 11 & \makecell[l]{Akkordeon, spielen\\{[accordion, playing]}} & \makecell[l]{Seil, schneiden\\{[rope, cutting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/12.png} & 12 & \makecell[l]{Körper, trainieren\\{[body, training]}} & \makecell[l]{Buch, offen halten\\{[book, binding]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/13.png} & 13 & \makecell[l]{Farbe, vom Fenster abschleifen\\{[paint, scraping off the window]}} & \makecell[l]{von Hand, zentrifugieren\\{[by hand, centrifugating]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/14.png} & 14 & \makecell[l]{Außenbereich, heizen\\{[outdoor area, heating]}} & \makecell[l]{Rasierklinge, schärfen\\{[razor blade, sharpening]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/15.png} & 15 & \makecell[l]{Pflanzenteile, vergrößern\\{[plant parts, magnifying]}} & \makecell[l]{Katzenklo, sich selbst reinigen\\{[litter box, self-cleaning]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/16.png} & 16 & \makecell[l]{Krawatten, aufhängen\\{[necktie, hanging up]}} & \makecell[l]{Zeichnungen, vermessen\\{[drawings, measuring]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/17.png} & 17 & \makecell[l]{Schallplatte, abtasten\\{[vinyl record, reading]}} & \makecell[l]{Ball, katapultieren\\{[ball, catapulting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/18.png} & 18 & \makecell[l]{Glas, schneiden\\{[glass, cutting]}} & \makecell[l]{Eier, wiegen\\{[eggs, weighing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/19.png} & 19 & \makecell[l]{Briketts, pressen\\{[briquette, pressing]}} & \makecell[l]{Narkosemittel, abgeben\\{[anesthetic, administering]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/20.png} & 20 & \makecell[l]{Orgelton, erzeugen\\{[organ sound, making]}} & \makecell[l]{Bandage, rollen\\{[bandage, rolling]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/21.png} & 21 & \makecell[l]{Spannung, erzeugen\\{[electric current, making]}} & \makecell[l]{Fußstütze, reiten\\{[footrest, horseback riding]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/22.png} & 22 & \makecell[l]{Narkosemittel, abgeben\\{[anesthetic, administering]}} & \makecell[l]{Nüsse, aufbrechen\\{[nuts, cracking]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/23.png} & 23 & \makecell[l]{Bandage, rollen\\{[bandage, rolling]}} & \makecell[l]{Schnee, rodeln\\{[snow, sleighing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/24.png} & 24 & \makecell[l]{Weinfass, Loch einschlagen\\{[wine barrel, smashing a hole]}} & \makecell[l]{Tier, einfangen\\{[animal, trapping]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/25.png} & 25 & \makecell[l]{Flaschenkorken, einführen\\{[bottle cork, inserting]}} & \makecell[l]{Pferd, im Moor laufen\\{[horse, walking in the moor]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/26.png} & 26 & \makecell[l]{Automat, Eier ausbrüten\\{[machine, incubating eggs]}} & \makecell[l]{Windgeschwindigkeit, messen\\{[wind speed, measuring]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/27.png} & 27 & \makecell[l]{Korngarbe, greifen\\{[sheaf, grabbing]}} & \makecell[l]{Treibhaus, heizen\\{[glass house, heating]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/28.png} & 28 & \makecell[l]{Brief, wiegen\\{[letter, weighing]}} & \makecell[l]{Korngarbe, greifen\\{[sheaf, grabbing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/29.png} & 29 & \makecell[l]{Löcher, bohren\\{[hole, drilling]}} & \makecell[l]{Sonnenlicht, Intensität messen\\{[sunlight, measure intensity]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/30.png} & 30 & \makecell[l]{Angelschnur, kurbeln\\{[fishing line, winding]}} & \makecell[l]{Glaskörper, musizieren\\{[glass body, making music]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/31.png} & 31 & \makecell[l]{Kurven, malen\\{[curve, drawing]}} & \makecell[l]{Nussöl, pressen\\{[nut oil, pressing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/32.png} & 32 & \makecell[l]{Radiofrequenz, einstellen\\{[radio frequency, tuning]}} & \makecell[l]{Erektion, helfen\\{[erection, helping]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/33.png} & 33 & \makecell[l]{Zäpfchen, pressen\\{[suppository, pressing]}} & \makecell[l]{Unkraut, jäten\\{[weed, removing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/34.png} & 34 & \makecell[l]{Fass, öffnen\\{[barrel, opening]}} & \makecell[l]{Pflanzenteile, vergrößern\\{[plant parts, magnifying]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/35.png} & 35 & \makecell[l]{Bergbaustollen, beleuchten\\{[mining tunnel, lightening]}} & \makecell[l]{Knie, fixieren\\{[knee, fixating]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/36.png} & 36 & \makecell[l]{Kuh, vom Zaun abhalten\\{[cow, keeping away from the fence]}} & \makecell[l]{Radiofrequenz, einstellen\\{[radio frequency, tuning]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/37.png} & 37 & \makecell[l]{Saatgut, gleichmäßig aussäen\\{[seeds, sowing evenly]}} & \makecell[l]{Fass, öffnen\\{[barrel, opening]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/38.png} & 38 & \makecell[l]{Flaschen, trocknen\\{[bottles, drying]}} & \makecell[l]{Bleistift, anspitzen\\{[pencil, sharpening]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/39.png} & 39 & \makecell[l]{Uhr, mit Wärme betreiben\\{[clock, operating with heat]}} & \makecell[l]{Körper, untersuchen\\{[body, training]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/40.png} & 40 & \makecell[l]{Tonpott, trommeln\\{[clay pot, drumming]}} & \makecell[l]{Piano, stimmen\\{[piano, tuning]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/41.png} & 41 & \makecell[l]{Sprengstoffexplosion, auslösen\\{[dynamite explosion, triggering]}} & \makecell[l]{Fisch, wiegen\\{[fish, weighing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/42.png} & 42 & \makecell[l]{Pferdehuf, Halt geben\\{[horse hoof, giving grip]}} & \makecell[l]{Zäpfchen, pressen\\{[suppository, pressing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/43.png} & 43 & \makecell[l]{Bleistift, anspitzen\\{[pencil, sharpening]}} & \makecell[l]{Angel, Köder markieren\\{[fishing rod, marking bait]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/44.png} & 44 & \makecell[l]{Nussöl, pressen\\{[nut oil, pressing]}} & \makecell[l]{Zeichen, einbrennen\\{[marks, burning in]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/45.png} & 45 & \makecell[l]{Rasierklinge, schärfen\\{[razor blade, sharpening]}} & \makecell[l]{Kurven, malen\\{[curve, drawing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/46.png} & 46 & \makecell[l]{heiße Platten, anheben\\{[hot plates, lifting]}} & \makecell[l]{Kleidung, im Eimer waschen\\{[clothes, washing in a bucket]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/47.png} & 47 & \makecell[l]{Film, aufspulen\\{[film roll, winding]}} & \makecell[l]{Mund, offen halten\\{[mouth, keeping open]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/48.png} & 48 & \makecell[l]{Waffe, entflammen\\{[weapon, inflaming]}} & \makecell[l]{Uhrzeit, anzeigen\\{[time, displaying]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/49.png} & 49 & \makecell[l]{Mikroskop-Proben, schneiden\\{[microscopic samples, slicing]}} & \makecell[l]{heiße Platten, anheben\\{[hot plates, lifting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/50.png} & 50 & \makecell[l]{Glaskörper, musizieren\\{[glass body, making music]}} & \makecell[l]{Kork, flach pressen\\{[cork, pressing flat]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/51.png} & 51 & \makecell[l]{Dampf, zerstäuben\\{[steam, spraying]}} & \makecell[l]{Buch, binden\\{[book, opening]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/52.png} & 52 & \makecell[l]{Mandeln, operieren\\{[kidneys, operating]}} & \makecell[l]{Film, aufspulen\\{[film roll, winding]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/53.png} & 53 & \makecell[l]{Toastbrot, rösten\\{[toast, roasting]}} & \makecell[l]{Autobatterie, Spannung testen\\{[car battery, measuring voltage]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/54.png} & 54 & \makecell[l]{Fußstütze, reiten\\{[footrest, horseback riding]}} & \makecell[l]{Stromstärke, messen\\{[current, measuring]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/55.png} & 55 & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, survining fires]}} & \makecell[l]{Botschaft, telegrafieren\\{[message, telegraphing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/56.png} & 56 & \makecell[l]{Schnee, rodeln\\{[snow, sleighing]}} & \makecell[l]{Dampf, zerstäuben\\{[steam, spraying]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/57.png} & 57 & \makecell[l]{Nüsse, aufbrechen\\{[nuts, cracking]}} & \makecell[l]{Ziegelsteine, formen\\{[bricks, forming]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/58.png} & 58 & \makecell[l]{Radiergummi, mit Strom betreiben\\{[eraser, operating with electricity]}} & \makecell[l]{Münzen, aufbewahren\\{[coins, storing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/59.png} & 59 & \makecell[l]{Treibhaus, heizen\\{[glass house, heating]}} & \makecell[l]{Messer, schleifen\\{[knife, sharpening]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/60.png} & 60 & \makecell[l]{Botschaft, telegrafieren\\{[message, telegraphing]}} & \makecell[l]{Toastbrot, rösten\\{[toast, roasting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/61.png} & 61 & \makecell[l]{Angel, Köder markieren\\{[fishing rod, marking bait]}} & \makecell[l]{Baum, erklettern\\{[tree, climbing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/62.png} & 62 & \makecell[l]{Katzenklo, sich selbst reinigen\\{[litter box, self-cleaning]}} & \makecell[l]{Tankfüllstand, messen\\{[fuel tank level, gauging]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/63.png} & 63 & \makecell[l]{Körper, untersuchen\\{[body, examining]}} & \makecell[l]{Schuhe, auf Eis laufen\\{[shoes, walking on ice]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/64.png} & 64 & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lense, cutting]}} & \makecell[l]{Saatgut, gleichmäßig aussäen\\{[seeds, sowing evenly]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/65.png} & 65 & \makecell[l]{Draht, wickeln\\{[wire, winding]}} & \makecell[l]{Bergbaustollen, beleuchten\\{[mining tunnel, lightening]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/66.png} & 66 & \makecell[l]{Buch, offen halten\\{[book, opening]}} & \makecell[l]{Sprengstoffexplosion, auslösen\\{[dynamite explosion, triggering]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/67.png} & 67 & \makecell[l]{Feldanbau, häckseln\\{[harvest, chopping]}} & \makecell[l]{Draht, wickeln\\{[wire, winding]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/68.png} & 68 & \makecell[l]{Schnurlot, absenken\\{[plummet, letting down]}} & \makecell[l]{Korken, formen\\{[bottle cork, forming]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/69.png} & 69 & \makecell[l]{Sternenbilder, vermessen\\{[stellar constellation, measuring]}} & \makecell[l]{Schnurlot, absenken\\{[plummet, letting down]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/70.png} & 70 & \makecell[l]{Nachricht, morsen\\{[message, signalling]}} & \makecell[l]{Feldanbau, häckseln\\{[harvest, chopping]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/71.png} & 71 & \makecell[l]{Musikgerät, stampfen\\{[musical instrument, stamping]}} & \makecell[l]{Goldmünzen, wiegen\\{[gold coin, weighing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/72.png} & 72 & \makecell[l]{Schuhe, auf Eis laufen\\{[shoes, walking on ice]}} & \makecell[l]{Geschwindigkeit, ermitteln\\{[speed, determining]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/73.png} & 73 & \makecell[l]{Geschwindigkeit, ermitteln\\{[speed, determining]}} & \makecell[l]{Mausefalle, zuschnappen\\{[mousetrap, snap-shutting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/74.png} & 74 & \makecell[l]{Zeichen, einbrennen\\{[marks, burning in]}} & \makecell[l]{Luftdruck, messen\\{[air pressure, measuring]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/75.png} & 75 & \makecell[l]{Tabak, zermahlen\\{[tobacco, pulverize]}} & \makecell[l]{Flaschen, trocknen\\{[bottles, drying]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/76.png} & 76 & \makecell[l]{Stromstärke, messen\\{[current, measuring]}} & \makecell[l]{Mandeln, operieren\\{[kidneys, operating]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/77.png} & 77 & \makecell[l]{Tier, einfangen\\{[animal, trapping]}} & \makecell[l]{Maiskolben, entkörnen\\{[corncob, removing grains]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/78.png} & 78 & \makecell[l]{Messer, schleifen\\{[knife, sharpening]}} & \makecell[l]{Schritte, vergrößern\\{[steps, extending]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/79.png} & 79 & \makecell[l]{Leierkasten, klingen\\{[barrel organ, making sounds]}} & \makecell[l]{Fass, anheben\\{[barrel, lifting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/80.png} & 80 & \makecell[l]{Buch, binden\\{[book, binding]}} & \makecell[l]{Löcher, bohren\\{[hole, drilling]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/81.png} & 81 & \makecell[l]{Kork, flach pressen\\{[cork, pressing flat]}} & \makecell[l]{Elektroschock, spielen\\{[electric shock, playing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/82.png} & 82 & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}} & \makecell[l]{Blumentopf, sich selbst wässern\\{[flower pot, self-watering]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/83.png} & 83 & \makecell[l]{Fass, anheben\\{[barrel, lifting]}} & \makecell[l]{Mikroskop-Proben, schneiden\\{[microscopic samples, slicing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/84.png} & 84 & \makecell[l]{Pferd, im Moor laufen\\{[horse, walking in the moor]}} & \makecell[l]{Luft, abpumpen\\{[air, pumping out]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/85.png} & 85 & \makecell[l]{altes Ritual, hacken\\{[ancient ritual, chopping]}} & \makecell[l]{Spannung, erzeugen\\{[electric current, making]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/86.png} & 86 & \makecell[l]{Kleidung, im Eimer waschen\\{[clothes, washing in a bucket]}} & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, survining fires]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/87.png} & 87 & \makecell[l]{Maiskolben, entkörnen\\{[corncob, removing grains]}} & \makecell[l]{Brief, wiegen\\{[letter, weighing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/88.png} & 88 & \makecell[l]{Ball, katapultieren\\{[ball, catapulting]}} & \makecell[l]{Radiergummi, mit Strom betreiben\\{[eraser, operating with electricity]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/89.png} & 89 & \makecell[l]{Zeichnungen, vermessen\\{[drawings, measuring]}} & \makecell[l]{Brenner, löten\\{[burner, soldering]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/90.png} & 90 & \makecell[l]{Elektroschock, spielen\\{[electric shock, playing]}} & \makecell[l]{Weinfass, Loch einschlagen\\{[wine barrel, smashing a hole]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/91.png} & 91 & \makecell[l]{Lieferungen, abzählen\\{[deliveries, counting]}} & \makecell[l]{Außenbereich, heizen\\{[outdoor area, heating]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/92.png} & 92 & \makecell[l]{Rotation, Ladung erzeugen\\{[rotation, creating electric charge]}} & \makecell[l]{Musikgerät, stampfen\\{[musical instrument, stamping]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/93.png} & 93 & \makecell[l]{Herz, durch Maschine ersetzen\\{[heart, replacing with machine]}} & \makecell[l]{Kerzen, löschen\\{[candles, extinguishing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/94.png} & 94 & \makecell[l]{Seil, schneiden\\{[rope, cutting]}} & \makecell[l]{Akkordeon, spielen\\{[accordion, playing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/95.png} & 95 & \makecell[l]{Fisch, wiegen\\{[fish, weighing]}} & \makecell[l]{Herz, durch Maschine ersetzen\\{[heart, replacing with machine]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/96.png} & 96 & \makecell[l]{Kerzen, löschen\\{[candles, extinguishing]}} & \makecell[l]{Körper, trainieren\\{[body, examining]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/97.png} & 97 & \makecell[l]{Korken, formen\\{[bottle cork, forming]}} & \makecell[l]{Sternenbilder, vermessen\\{[stellar constellation, measuring]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/98.png} & 98 & \makecell[l]{Erektion, helfen\\{[erection, helping]}} & \makecell[l]{Waffe, werfen\\{[weapn, throwing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/99.png} & 99 & \makecell[l]{Streckenmaß, Sonnenlicht nutzen\\{[distance measure, using sunrays]}} & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/100.png} & 100 & \makecell[l]{Luftdruck, messen\\{[air pressure, measuring]}} & \makecell[l]{Knochen, sägen\\{[bones, sawing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/101.png} & 101 & \makecell[l]{Piano, stimmen\\{[piano, tuning]}} & \makecell[l]{Eierkarton, pressen\\{[egg carton, pressing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/102.png} & 102 & \makecell[l]{von Hand, zentrifugieren\\{[by hand, centrifugating]}} & \makecell[l]{Lieferungen, abzählen\\{[deliveries, counting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/103.png} & 103 & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}} & \makecell[l]{Nachricht, morsen\\{[message, signalling]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/104.png} & 104 & \makecell[l]{Waffe, werfen\\{[weapn, throwing]}} & \makecell[l]{elektrische Spannung, prüfen\\{[electric current, measuring]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/105.png} & 105 & \makecell[l]{Tankfüllstand, messen\\{[fuel tank level, gauging]}} & \makecell[l]{Tonpott, trommeln\\{[clay pot, drumming]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/106.png} & 106 & \makecell[l]{Uhrzeit, anzeigen\\{[time, displaying]}} & \makecell[l]{altes Ritual, hacken\\{[ancient ritual, chopping]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/107.png} & 107 & \makecell[l]{Windgeschwindigkeit, messen\\{[wind speed, measuring]}} & \makecell[l]{Waffe, entflammen\\{[weapon, inflaming]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/108.png} & 108 & \makecell[l]{Schlüsselloch, stanzen\\{[keyhole, punching]}} & \makecell[l]{Automat, Eier ausbrüten\\{[machine, incubating eggs]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/109.png} & 109 & \makecell[l]{Ziegelsteine, formen\\{[bricks, forming]}} & \makecell[l]{Schallplatte, abtasten\\{[vinyl record, reading]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/110.png} & 110 & \makecell[l]{Becher, Schall auffangen\\{[drinking cup, picking up sound]}} & \makecell[l]{Schlüsselloch, stanzen\\{[keyhole, punching]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/111.png} & 111 & \makecell[l]{Luft, abpumpen\\{[air, pumping out]}} & \makecell[l]{Briketts, pressen\\{[briquette, pressing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/112.png} & 112 & \makecell[l]{Mund, offen halten\\{[mouth, keeping open]}} & \makecell[l]{Orgelton, erzeugen\\{[organ sound, making]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/113.png} & 113 & \makecell[l]{Autobatterie, Spannung testen\\{[car battery, measuring voltage]}} & \makecell[l]{Becher, Schall auffangen\\{[drinking cup, picking up sound]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/114.png} & 114 & \makecell[l]{Sonnenlicht, Intensität messen\\{[sunlight, measure intensity]}} & \makecell[l]{Krawatten, aufhängen\\{[necktie, hanging up]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/115.png} & 115 & \makecell[l]{Kutschrad, anschließen\\{[carriage wheel, locking]}} & \makecell[l]{Angelschnur, kurbeln\\{[fishing line, winding]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/116.png} & 116 & \makecell[l]{Eier, wiegen\\{[eggs, weighing]}} & \makecell[l]{Leierkasten, klingen\\{[barrel organ, making sounds]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/117.png} & 117 & \makecell[l]{Blumentopf, sich selbst wässern\\{[flower pot, self-watering]}} & \makecell[l]{Glas, schneiden\\{[glass, cutting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/118.png} & 118 & \makecell[l]{Schritte, vergrößern\\{[steps, extending]}} & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/119.png} & 119 & \makecell[l]{Münzen, aufbewahren\\{[coins, storing]}} & \makecell[l]{Kutschrad, anschließen\\{[carriage wheel, locking]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/120.png} & 120 & \makecell[l]{Brenner, löten\\{[burner, soldering]}} & \makecell[l]{Flaschenkorken einführen, einführen\\{[bottle cork, inserting]}}\\
-\bottomrule
-\end{longtable}
+\normalsize
 
-}
+\noindent Linear mixed-effects models after model selection for Experiment 2:
 
-\end{ThreePartTable}
-\end{center}
+\footnotesize
+
+\begin{verbatim}
+## P1 ~ 1 + part + condition + part:condition + (1 | participant)
+## N170 ~ 1 + part + condition + part:condition + (1 + part | participant)
+## N400 ~ 1 + part + condition + part:condition + (1 + part | participant)
+\end{verbatim}
+
+\normalsize
+
+\noindent Linear mixed-effects models after model selection for Experiments 1 and 2 combined:
+
+\footnotesize
+
+\begin{verbatim}
+## P1 ~ 1 + part + condition + part:condition + experiment + part:experiment + 
+##     condition:experiment + part:condition:experiment + (1 + part | participant)
+## N170 ~ 1 + part + condition + part:condition + experiment + part:experiment + 
+##     condition:experiment + part:condition:experiment + (1 + part + condition | 
+##     participant)
+## N400 ~ 1 + part + condition + part:condition + experiment + part:experiment + 
+##     condition:experiment + part:condition:experiment + (1 + part | participant)
+\end{verbatim}
+
+\normalsize
 

### 2021-01-26 analysis/manuscript.Rmd
add new appendix

@@
   - \AtBeginEnvironment{tabular}{\doublespacing}
+  - \usepackage{makecell}
+  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
   - \captionsetup[table]{font={stretch=1.5}}
@@
 r_refs("analysis/manuscript_files/r-references.bib")
+
+# Source plotting functions
+source("analysis/manuscript_files/functions_plots_tables.R")
 
@@
 
-How does our perception of an object change as soon as we discover what function it serves?
+Does our perception of an object change as soon as we discover what function it serves?
 In this study, we presented participants with unfamiliar objects that were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
-We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resoluation of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
+We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resolution of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
 It allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
@@
 In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this had not been the case.
-Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
-Interestingly, the ERPs in the in-depth knowledge condition even were qualitatively similar to those for untrained but well-known objects.
+These differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
+Interestingly, the ERPs observed for previously unfamiliar objects with newly acquired in-depth knowledge were qualitatively similar to those for untrained but well-known objects.
 The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
@@
 Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum).
-A list of these unfamiliar objects can be found in the appendix.
+A list of these unfamiliar objects can be found in Appendix A.
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-# Define function to compute single-trial mean ERP ampltiudes from epochs
+# Define function to compute single-trial mean ERP amplitudes from epochs
 def compute_erps(epochs, name, tmin, tmax, roi):
@@
 
-# Preprocess the EEG for Epxeriment 1 in Python
+# Preprocess the EEG for Experiment 1 in Python
 map2(
@@
 
-```{r exp1-models, eval=TRUE}
+```{r exp1-models, eval=rerun_models}
 # Load preprocessed single-trial data
@@
 
-# Trial structure
-plot_trials <- function(){
-  suppressMessages(require(magick))
-  color_informed <- viridisLite::viridis(1, begin = 0.1)
-  color_naive <- viridisLite::viridis(1, begin = 0.5)
-  ggplot() +
-    coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
-    ## PART II ##
-    # Title
-    annotate("text", x = 0, y = 97.2, label = "Insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
-    # Arrow
-    annotate("segment", x = -30, xend = 24, y = 79, yend = 85, arrow = arrow(length = unit(0.1, "inches"))) +
-    # Squares
-    annotate("rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75, color = "black", fill = "white") +
-    annotate("rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65, color = color_informed, fill = "white") +
-    annotate("rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89, color = color_naive, fill = "white") +
-    annotate("rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79, color = "black", fill = "white") +
-    annotate("rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81, color = "black", fill = "white") +
-    annotate("text", x = -27, y = 65.3, label = "+", size = 20 / .pt, family = "Helvetica") +
-    annotate("text", x = -9, y = 55, label = "potatoes\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
-    annotate("text", x = -9, y = 79, label = "message\nsignalling", size = 10 / .pt, family = "Helvetica", color = color_naive) +
-    annotate("text", x = 9, y = 67, label = "*", size = 30 / .pt, family = "Helvetica") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = 18, y = 62, width = 18, height = 18) +
-    # Timings
-    annotate("text", x = -9, y = 67.3, label = "or", size = 10 / .pt, family = "Helvetica") +
-    annotate("text", x = -27, y = 52, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
-    annotate("text", x = -9, y = 42, label = "2.5 s", size = 10 / .pt, family = "Helvetica") +
-    annotate("text", x = 9, y = 56, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
-    annotate("text", x = 27, y = 56.3, label = "3 s or\nresponse", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
-    # Response options
-    annotate("segment", x = 27, y = 39, xend = 27, yend = 51.5) +
-    annotate("segment", x = 0, y = 39, xend = 27, yend = 39) +
-    annotate("segment", x = 0, y = 35, xend = 0, yend = 39) +
-    annotate("segment", x = -32, y = 35, xend = 32, yend = 35) +
-    annotate("segment", x = -32, y = 30.5, xend = -32, yend = 35) +
-    annotate("segment", x = -12, y = 32, xend = -12, yend = 35) +
-    annotate("segment", x = 12, y = 32, xend = 12, yend = 35) +
-    annotate("segment", x = 32, y = 32, xend = 32, yend = 35) +
-    annotate("text", x = -32, y = 26, label = "A. \"I know\nwhat this is\"", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
-    annotate("text", x = -12, y = 26, label = "B. \"I have an\nassumption\nwhat this is\"", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
-    annotate("text", x = 12, y = 26, label = "C. \"I have rather\nno assumption\nwhat this is\"", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
-    annotate("text", x = 32, y = 26, label = "D. \"I don\'t\n know what\nthis is\"", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
-    # Conditions
-    annotate("segment", x = -32, y = 17, xend = -32, yend = 22, color = color_informed) +
-    annotate("segment", x = -12, y = 17, xend = -12, yend = 20, color = color_informed) +
-    annotate("segment", x = 12, y = 17, xend = 12, yend = 20, color = color_naive) +
-    annotate("segment", x = 32, y = 17, xend = 32, yend = 20, color = color_naive) +
-    annotate("segment", x = -32, y = 17, xend = -12, yend = 17, color = color_informed) +
-    annotate("segment", x = 12, y = 17, xend = 32, yend = 17, color = color_naive) +
-    annotate("segment", x = -22, y = 15, xend = -22, yend = 17, color = color_informed) +
-    annotate("segment", x = 22, y = 15, xend = 22, yend = 17, color = color_naive) +
-    annotate("text", x = -22, y = 13, label = "Informed condition", size = 10 / .pt, family = "Helvetica", fontface = "bold", color = color_informed) +
-    annotate("text", x = 22, y = 13, label = "Naive condition", size = 10 / .pt, family = "Helvetica", fontface = "bold", color = color_naive) +
-    annotate("text", x = -22, y = 7.9, label = "Matching keywords\nand response A or B", size = 10 / .pt, family = "Helvetica", color = color_informed, lineheight = 1) +
-    annotate("text", x = 22, y = 7.9, label = "Non-matching keywords\nand response C or D", size = 10 / .pt, family = "Helvetica", color = color_naive, lineheight = 1) +
-    ## PART I ##
-    # Title
-    annotate("text", x = -72, y = 56, label = "Pre-insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
-    # Arrow
-    annotate("segment", x = -84, xend = -66, y = 46, yend = 48, arrow = arrow(length = unit(0.1, "inches"))) +
-    # Squares
-    annotate("rect", xmin = -91, xmax = -71, ymin = 22, ymax = 42, color = "black", fill = "white") +
-    annotate("rect", xmin = -53, xmax = -73, ymin = 24, ymax = 44, color = "black", fill = "white") +
-    annotate("text", x = -81, y = 32.3, label = "+", size = 20 / .pt, family = "Helvetica") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = -72, y = 25, width = 18, height = 18) +
-    # Timings
-    annotate("text", x = -81, y = 19, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
-    annotate("text", x = -63, y = 19.3, label = "3 s or\nresponse", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
-    # Conditions
-    annotate("text", x = -72, y = 7.9, label = "Objects classified according\nto conditions in the insight part", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
-    # PART III
-    # Title
-    annotate("text", x = 72, y = 56, label = "Post-insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
-    # Arrow
-    annotate("segment", x = 60, xend = 78, y = 46, yend = 48, arrow = arrow(length = unit(0.1, "inches"))) +
-    # Squares
-    annotate("rect", xmin = 53, xmax = 73, ymin = 22, ymax = 42, color = "black", fill = "white") +
-    annotate("rect", xmin = 71, xmax = 91, ymin = 24, ymax = 44, color = "black", fill = "white") +
-    annotate("text", x = 63, y = 32.3, label = "+", size = 20 / .pt, family = "Helvetica") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = 72, y = 25, width = 18, height = 18) +
-    # Timings
-    annotate("text", x = 63, y = 19, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
-    annotate("text", x = 81, y = 19.3, label = "3 s or\nresponse", size = 10 / .pt, family = "Helvetica", lineheight = 1) +    
-    # Conditions
-    annotate("text", x = 72, y = 7.9, label = "Objects classified according\nto conditions in the insight part", size = 10 / .pt, family = "Helvetica", lineheight = 1) +    
-    theme_void()
-}
-
-# Define function to plot ERP waveforms and topographies
-plot_erps <- function(comps, evokeds, models, montage) {
-  suppressWarnings(suppressMessages(
-    pmap(comps, function(name, tmin, tmax, roi) {
-      # N400 gets a different scale than P1 and N170
-      ymin <- ifelse(name == "N400", -3, -4)
-      # Loop through parts
-      parts <- map(c("I", "II", "III"), function(part) {
-        # Create (conditions x time points) x electrodes tibble
-        data_plot <- evokeds[[part]] %>%
-          map(function(data) {
-            data %>%
-              t() %>%
-              as_tibble(.name_repair = "unique") %>%
-              set_colnames(montage$electrode) %>%
-              mutate(.time = seq(-500, 1498, 2), roi = rowMeans(select(., all_of(roi))))
-          }) %>% bind_rows(.id = "condition")
-        # Shade background depending on whether the effect is significant or not
-        asterisks <- models[[name]]$contrasts %>%
-          filter(part == !!part) %>%
-          mutate(asterisks = case_when(p.value < .001 ~ "***", p.value < .01 ~ "**", p.value < .05 ~ "*")) %>%
-          pull(asterisks)
-        xasterisks <- case_when(str_length(asterisks) == 1 ~ tmin + 11, str_length(asterisks) == 3 ~ tmin + 15)
-        if (is.na(asterisks)) {
-          shade <- annotate("rect", xmin = tmin, xmax = tmax, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = NA)
-        } else {
-          shade <- annotate("rect", xmin = tmin, xmax = tmax, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = "gray90")
-        }
-
-        # # Prepare waveform
-        # wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
-        #   annotate("rect", xmin = tmin, xmax = tmax, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
-        # # Shade significant area
-        # star <- stars[[name]][[part]]
-        # if (!is.na(star)) {
-        #   wave <- wave + geom_ribbon(
-        #     data = data_plot %>% filter(.time >= tmin & .time <= tmax) %>%
-        #       group_by(.time) %>% summarize(ymin = min(roi), ymax = max(roi)),
-        #     aes(x = .time, xmin = tmin, xmax = tmax, ymin = ymin, ymax = ymax),
-        #     inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1)
-        #   )
-        # } +
-        # annotate("text", label = star, x = tmin + (tmax - tmin)/2, y = -3.2, size = 7, family = "Helvetica")}
-        # Add waves and styling
-
-        # Plot waveform
-        wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
-          shade +
-          annotate("text", label = asterisks, x = xasterisks, y = ymin + 11, size = 6, hjust = 0, family = "Helvetica") +
-          annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
-          annotate("segment", x = 0, xend = 0, y = ymin, yend = ymin + 12) +
-          annotate("segment", x = seq(-100, 700, 200), xend = seq(-100, 700, 200), y = -0.3, yend = 0) +
-          annotate("segment", x = -12, xend = 0, y = seq(-2, 8, 4), yend = seq(-2, 8, 4)) +
-          annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10 / .pt, family = "Helvetica") +
-          annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10 / .pt, family = "Helvetica", hjust = 1) +
-          annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10 / .pt, family = "Helvetica", lineheight = 0.9) +
-          annotate("text", x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10 / .pt, family = "Helvetica", angle = 90, lineheight = 0.9) +
-          geom_line() +
-          scale_color_viridis_d(begin = 0.1, end = 0.5) +
-          coord_cartesian(xlim = c(-200, 800), ylim = c(ymin, ymin + 14), expand = FALSE) +
-          theme_void() +
-          theme(legend.position = "none")
-        # Plot topography
-        topo <- data_plot %>%
-          filter(.time >= tmin & .time <= tmax) %>%
-          group_by(condition) %>%
-          summarise(across(montage$electrode, mean)) %>%
-          pivot_longer(-condition) %>%
-          pivot_wider(names_from = condition) %>%
-          transmute(amplitude = Informed - Naive) %>%
-          bind_cols(montage) %>%
-          eegUtils::topoplot(limits = c(-1, 1), palette = "viridis", contour = FALSE, highlights = roi, scaling = 0.1) +
-          theme(legend.position = "none")
-        topo$layers[[3]]$aes_params$size <- topo$layers[[4]]$aes_params$size <- topo$layers[[5]]$aes_params$size <- 0.6
-        # Combine waveform and topography
-        wave + draw_plot(topo, width = 320, height = 9, x = 500, y = ymin + 6.4)
-      })
-      # Combine plots for the different parts
-      plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
-      # Combine plots for the different components
-    }) %>% plot_grid(plotlist = ., nrow = 3)
-  ))
-}
-
-# Create a combined legend and colorbar
-plot_legends_erps <- function(direction) {
-  if (direction == "vertical") {
-    mar <- margin(l = 12, r = 10, b = 6, t = 7); vjust <- 3.5
-  }
-  else {
-    mar <- margin(l = 8, r = 12, b = 4, t = 6); vjust <- 0.7
-  }
-  get_legend(
-    tibble(amplitude = c(-1, 0, 1), condition = c("Informed", "Naive", "Informed")) %>%
-      ggplot(aes(x = 0, y = 0, color = condition, fill = amplitude)) +
-      geom_line() +
-      geom_raster() +
-      labs(color = "Conditions", fill = "Informed - naive (µV)") +
-      scale_color_viridis_d(begin = 0.1, end = 0.5, guide = guide_legend(direction = "vertical", title.position = "top")) +
-      scale_fill_viridis_c(guide = guide_colorbar(direction = "horizontal", ticks = FALSE, title.position = "top", title.vjust = vjust)) +
-      theme(
-        legend.direction = direction,
-        legend.box = direction,
-        legend.box.background = element_rect(colour = "black", size = 0.5),
-        legend.box.margin = mar,
-        legend.background = element_blank(),
-        legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
-        legend.text = element_text(family = "Helvetica", size = 10),
-        legend.key = element_rect(fill = NA),
-        legend.key.width = unit(0.7, "cm"),
-        legend.key.height = unit(0.4, "cm"),
-        legend.spacing.x = unit(0.3, "cm")
-      )
-  )
-}
-
 # Create plot for Experiment 1
@@
 The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
-For the purpose of the present study, these models have at least three desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+For the purpose of the present study, these models have at least three desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant averages.
 First, they can leverage all of the information that is present in the data set on the single trial level, some of which would be lost when computing averages.
@@
 Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable when the assignment of trials to conditions is co-determined by the experimental manipulation and the behavioral responses of the participants to this manipulation [e.g., @fröber2017].
+Such a situation is inevitable when the assignment of trials to conditions is co-determined by the experimental manipulation and the behavior of participants in response to this manipulation [e.g., @fröber2017].
 
@@
 We then performed a model selection algorithm as proposed by @matuschek2017 in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model [determined by *p* \> .20\; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model.
+Only if the parsimonious model explained the data equally well as the complex model [determined by *p* \> .20\; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
 All models were computed in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4].
@@
 The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (<https://osf.io/uksbc/>).
-Participants' lack of informed consent to do so prevents us from openly sharing the raw EEG data.
+We are not able to share the raw EEG data openly because we did not obtain participants' informed consent to do so.
 
@@
 ```{r exp1-table, include=TRUE, results="asis"}
-# Define function to print ANOVA-style table
-create_table <- function(models, stub_anova, stub_contrasts, caption, note) {
-  anov <- map(models, function(model) {
-    data.frame(
-      "f" = format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2),
-      "df" = paste0("(", model$anova$NumDF, ", ", format(round(model$anova$DenDF, 1), trim = TRUE, nsmall = 1), ")"),
-      "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)
-    ) %>%
-      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
-      set_rownames(c(stub_anova))
-  })
-  suppressMessages(
-    anov_print <- anov %>%
-      map(unite, col = fdf, f, df, sep = " ") %>%
-      map(add_row, fdf = "\\textit{F} (\\textit{df})", p = "\\textit{p}", .before = 1) %>%
-      bind_cols() %>%
-      set_rownames(c("\\textbf{Fixed effects}", stub_anova))
-  )
-  suppressMessages(
-    anov %<>%
-      bind_cols() %>%
-      set_colnames(paste(rep(names(models), each = length(names(models))), c("f", "df", "p"), sep = "_"))
-  )
-  conts <- map(models, function(model) {
-    data.frame(
-      "est" = format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2),
-      "ci" = paste0(
-        "[", format(round(model$contrasts$lower.CL, 2), trim = TRUE, nsmall = 2), ", ",
-        format(round(model$contrasts$upper.CL, 2), trim = TRUE, nsmall = 2), "]"
-      ),
-      "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)
-    ) %>%
-      mutate(p = ifelse(p == "0.000", "< .001", substr(p, 2, nchar(p)))) %>%
-      set_rownames(stub_contrasts)
-  })
-  suppressMessages(
-    conts_print <- conts %>%
-      map(unite, col = estci, est, ci, sep = " ") %>%
-      map(add_row, estci = "Est. [95% CI]", p = "\\textit{p}", .before = 1) %>%
-      bind_cols() %>%
-      set_rownames(c("\\textbf{Informed - naive}", stub_contrasts))
-  )
-  suppressMessages(
-    conts %<>%
-      bind_cols() %>%
-      set_colnames(paste(rep(names(models), each = length(names(models))), c("est", "ci", "p"), sep = "_"))
-  )
-  cnames <- c("\\textbf{Fixed effects}", as.character(anov_print[1, ]))
-  list(anov_print[2:nrow(anov_print), ], conts_print) %>%
-    map(set_colnames, paste0("V", 1:ncol(anov_print))) %>%
-    apa_table(
-      col.names = cnames, col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N170}" = 4:5, "\\textbf{N400}" = 6:7),
-      midrules = nrow(anov_print), font_size = "footnotesize", align = "lcccccc", escape = FALSE,
-      caption = caption, note = note
-    ) %>%
-    cat()
-  return(list("anov" = anov, "conts" = conts))
-}
-
 # Create table of models for Experiment 1
@@
   caption = "Results of Linear Mixed-Effects Regression Models for Experiment 1\\smallskip",
-  note = "Pt. = part, con. = condition, est. = estimate, CI = confidence interval."
-)
-```
-
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s \> `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (see Table \@ref(tab:exp1-table)).
+  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
+)
+```
+
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (see Table \@ref(tab:exp1-table)).
 In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r table_exp1$anov["Condition", "N400_df"]` = `r table_exp1$anov["Condition", "N400_f"]`, *p* = `r table_exp1$anov["Condition", "N400_p"]`.
@@
 
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s $\ge$ `r table_exp1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:exp1-table) and Figure \@ref(fig:exp1-plot)B).
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s ≥ `r table_exp1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:exp1-table) and Figure \@ref(fig:exp1-plot)B).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
 On the other hand, the absence of reliable differences in this part can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in the other two parts cannot be accounted for by visual differences between the objects in the two conditions.
-Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report would have made it possible for such visual differences to emerge as a confounding factor.
+Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self-report would have made it possible for such visual differences to emerge as a confounding factor.
 If they did, however, one would expect to detect these differences even before any keywords were presented, which was apparently not the case.
@@
 When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e., more negative), *b* = `r table_exp1$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Insight part", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e., less negative), *b* = `r table_exp1$conts["Insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Insight part", "N400_p"]`, compared to when the object was viewed naively without relevant semantic information.
-As in the pre-insight part, there were no reliable differences in the P1 component, *p* = `r table_exp1$conts["Insight part", "P1_p"]`.
+As in the pre-insight part, there were no reliable differences in the P1 component, *b* = `r table_exp1$conts["Insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Insight part", "P1_p"]`.
 
@@
 This allowed us to test if the semantic information had any lasting effects on the processing of the objects.
-As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Post-insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *p* = `r table_exp1$conts["Post-insight part", "N170_p"]`.
+As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Post-insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *b* = `r table_exp1$conts["Post-insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "N170_p"]`.
 Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "P1_p"]`.
@@
 
-Because of the novelty of our experimental paradigm---measuring the ERPs while rather than after participants received semantic information about unfamiliar objects---and because of the novelty of our findings, we ran a replication study to assess the robustness of these effects with another sample of participants.
+Because of the novelty of our experimental paradigm---measuring the ERPs while rather than after participants received semantic information about unfamiliar objects---and because of the novelty of our findings, we ran a replication study with another sample of participants to assess the robustness of these effects.
 
@@
 
-# Preprocess the EEG for Epxeriment 2 in Python
+# Preprocess the EEG for Experiment 2 in Python
 map2(
@@
   caption = "Results of Linear Mixed-Effects Regression Models for Experiment 2\\smallskip",
-  note = "Pt. = part, con. = condition, est. = estimate, CI = confidence interval."
-)
-```
-
-As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all *F*s \> `r table_exp2$anov["Part", "N170_f"]`, all *p*s `r table_exp2$anov["Part", "N170_p"]` (see Table \@ref(tab:exp2-table)).
+  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
+)
+```
+
+As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all *F*s ≥ `r table_exp2$anov["Part", "N170_f"]`, all *p*s `r table_exp2$anov["Part", "N170_p"]` (see Table \@ref(tab:exp2-table)).
 Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, *F*`r table_exp2$anov["Condition", "N400_df"]` = `r table_exp2$anov["Condition", "N400_f"]`, *p* `r table_exp2$anov["Condition", "N400_p"]`.
@@
 ```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:figure-2-caption)"}
-# Create headings for Parts I, II, and III
-plot_headings <- function(spacing){
-  plot_grid(
-    ggplot() + annotate("text", label = "Pre-insight part", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(), NULL,
-    ggplot() + annotate("text", label = "Insight part", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(), NULL,
-    ggplot() + annotate("text", label = "Post-insight part", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") + theme_void(),
-    nrow = 1, rel_widths = spacing
-  )
-}
-
 # Create plot for Experiment 2
@@
 ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical signficance (\textit{p} = `r table_exp2$conts["Insight part", "N170_p"]`).
+In an exact replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical significance (\textit{p} = .064).
 Ampl.
@@
 
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all *p*s \> `r table_exp2$conts["Pre-insight part", "P1_p"]` (see Table \@ref(tab:exp2-table) and Figure \@ref(fig:exp2-plot)).
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all *p*s ≥ `r table_exp2$conts["Pre-insight part", "P1_p"]` (see Table \@ref(tab:exp2-table) and Figure \@ref(fig:exp2-plot)).
 
@@
 Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit [@matuschek2017; @R-buildmer].
+The resulting formulas for the models can be found in Appendix B.
 
@@
   models_joint,
-  stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
+  stub_anova = c(
+    "Part", "Condition", "Experiment", "Pt. × con.",
+    "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."
+  ),
   stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\\smallskip",
-  note = "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval."
+  caption =
+    "Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\\smallskip",
+  note =
+    "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\\% confidence interval."
 )
@@
 suppressMessages(
-  emmeans::emmeans(models_joint$N400$model, specs = pairwise ~ experiment, infer = TRUE)$contrasts %>%
+  emmeans::emmeans(
+    models_joint$N400$model,
+    specs = pairwise ~ experiment, infer = TRUE
+  )$contrasts %>%
     as.data.frame() %>%
@@
 
-As shown in Table \@ref(tab:joint-table), the main effect of part was significant in the P1, N170, and N400 component, all *F*s \> `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Condition", "N400_df"]` = `r table_joint$anov["Condition", "N400_f"]`, *p* `r table_joint$anov["Condition", "N400_p"]`.
-Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s \> `r table_joint$anov["Pt.
-× con.", "P1_f"]`, all *p*s \< `r table_joint$anov["Pt.
+As shown in Table \@ref(tab:joint-table), the main effect of part was significant in the P1, N170, and N400 component, all *F*s ≥ `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Condition", "N400_df"]` = `r table_joint$anov["Condition", "N400_f"]`, *p* `r table_joint$anov["Condition", "N400_p"]`.
+Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s ≥ `r table_joint$anov["Pt.
+× con.", "P1_f"]`, all *p*s ≤ `r table_joint$anov["Pt.
 × con.", "P1_p"]`.
@@
 Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \@ref(tab:joint-table) and Figure \@ref(fig:joint-plot)).
-This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all *p*s \> `r table_joint$conts["Pre-insight part", "N400_p"]`, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N170_est"]` µV, *p* = `r table_joint$conts["Insight part", "N170_p"]`, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N400_est"]` µV, *p* `r table_joint$conts["Insight part", "N400_p"]`, and in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "N400_est"]` µV, *p* `r table_joint$conts["Post-insight part", "N400_p"]`, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_joint$conts["Post-insight part", "P1_p"]`.
+This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all *p*s ≥ `r table_joint$conts["Pre-insight part", "N400_p"]`, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N170_est"]` µV, *p* = `r table_joint$conts["Insight part", "N170_p"]`, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N400_est"]` µV, *p* `r table_joint$conts["Insight part", "N400_p"]`, and in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "N400_est"]` µV, *p* `r table_joint$conts["Post-insight part", "N400_p"]`, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_joint$conts["Post-insight part", "P1_p"]`.
 
@@
 \bigskip\small\textit{Note.} 
-The violins and box plots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
+The violins and box plots show the distributions of the by-participant averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
+The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\\% confidence interval.
 Ampl.
-= amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
+= amplitude, 95\\% CI = 95\\% confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
 **\textit{p} \textless{} .01.
@@
 ```{r joint-plot, include=TRUE, fig.height=8, fig.cap = "(ref:figure-3-caption)"}
-# Define two functions for split violin plots (kudos to https://stackoverflow.com/a/45614547)
-GeomSplitViolin <- ggproto(
-  "GeomSplitViolin", GeomViolin,
-  draw_group = function(self, data, ..., draw_quantiles = NULL) {
-    data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
-    grp <- data[1, "group"]
-    newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
-    newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
-    newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
-    if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
-      stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 1))
-      quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
-      aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
-      aesthetics$alpha <- rep(1, nrow(quantiles))
-      both <- cbind(quantiles, aesthetics)
-      quantile_grob <- GeomPath$draw_panel(both, ...)
-      ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
-    }
-    else {
-      ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
-    }
-  }
-)
-geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ...,
-                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE,
-                              show.legend = NA, inherit.aes = TRUE) {
-  layer(
-    data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin,
-    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
-    params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...)
-  )
-}
-
-# Define our custom function for the violin plot
-plot_violins <- function(data, models) {
-  suppressWarnings(suppressMessages(
-    parts <- map(c("I", "II", "III"), function(part) {
-      map(c("P1", "N170", "N400"), function(comp) {
-        modmeans <- models[[comp]]$means %>% filter(part == !!part) %>% rename(amplitude = emmean)
-        ymin <- case_when(comp == "P1" ~ -5, comp == "N170" ~ -11, comp == "N400" ~ -11)
-        asterisks <- models[[comp]]$contrasts %>%
-          filter(part == !!part) %>%
-          mutate(asterisks = case_when(p.value < .001 ~ "***", p.value < .01 ~ "**", p.value < .05 ~ "*")) %>%
-          pull(asterisks)
-        yastersisks <- case_when(
-          comp == "P1" ~ 17.6,
-          comp == "N170" ~ 10,
-          comp == "N400" & part == "II" ~ 9.7,
-          comp == "N400" & part == "III" ~ 8.9
-        )
-        data %>%
-          filter(part == !!part) %>%
-          rename(amplitude = !!comp) %>%
-          group_by(participant, part, condition) %>%
-          summarise(across(amplitude, mean)) %>%
-          ggplot(aes(x = 0, y = amplitude, fill = condition)) +
-          annotate("text", x = 0, y = yastersisks, label = asterisks, size = 6, family = "Helvetica") +
-          geom_split_violin(trim = TRUE, color = "gray70") +
-          geom_boxplot(position = position_dodge(width = 0.8), width = 0.3, color = "gray70") +
-          geom_pointrange(
-            data = modmeans,
-            aes(ymin = lower.CL, ymax = upper.CL),
-            position = position_dodge(width = 0.25),
-            size = 0.4,
-            color = viridisLite::viridis(n = 1, begin = 1)
-          ) +
-          coord_cartesian(ylim = c(ymin, ymin + 25), xlim = c(-0.6, 0.6)) +
-          scale_x_continuous(breaks = c(-0.2, 0.2), labels = c("Informed", "Naive")) +
-          scale_y_continuous(breaks = seq(ymin, ymin + 25, 5)) +
-          ylab(paste(comp, "ampl. (µV)")) +
-          scale_fill_viridis_d(begin = 0.1, end = 0.5) +
-          theme_classic() +
-          theme(
-            legend.position = "none",
-            axis.title.x = element_blank(),
-            axis.title.y = element_text(size = 10, color = "black", family = "Helvetica"),
-            axis.text = element_text(size = 10, color = "black", family = "Helvetica")
-          )
-      }) %>% plot_grid(plotlist = ., align = "v", nrow = 3)
-    })
-  ))
-  plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], ncol = 5, rel_widths = c(10, 2, 10, 2, 10))
-}
-
-# Define function for the legend for the violin plot
-plot_legends_violins <- function() {
-  get_legend(
-    tibble(Conditions = c("Informed", "Naive")) %>%
-      ggplot(aes(x = 0, y = 0, color = "LMM mean\n± 95% CI", fill = Conditions)) +
-      geom_raster() +
-      geom_pointrange(aes(ymin = -1, ymax = 1)) +
-      scale_fill_viridis_d(begin = 0.1, end = 0.5) +
-      scale_color_viridis_d(begin = 1) +
-      guides(
-        fill = guide_legend(override.aes = list(color = NA)),
-        color = guide_legend(title = NULL)
-      ) +
-      theme(
-        legend.box.background = element_rect(colour = "black", size = 0.5),
-        legend.box.margin = margin(l = 9, r = 9, b = 9, t = 7),
-        legend.background = element_blank(),
-        legend.spacing = unit(0.01, "inches"),
-        legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
-        legend.text = element_text(family = "Helvetica", size = 10),
-        legend.key = element_rect(fill = "gray70")
-      )
-  )
-}
-
 # Create violin plot for Experiments 1 and 2 combined
@@
 ) + # Add some lines (to separate the parts)
-  annotate(geom = "segment", x = 11/34*0.85, xend = 11/34*0.85, y = -Inf, yend = Inf, linetype = "dashed") +
-  annotate(geom = "segment", x = 23/34*0.85, xend = 23/34*0.85, y = -Inf, yend = Inf, linetype = "dashed")
+  annotate(
+    geom = "segment", x = 11 / 34 * 0.85, xend = 11 / 34 * 0.85,
+    y = -Inf, yend = Inf, linetype = "dashed"
+  ) +
+  annotate(
+    geom = "segment", x = 23 / 34 * 0.85, xend = 23 / 34 * 0.85,
+    y = -Inf, yend = Inf, linetype = "dashed"
+  )
 ```
@@
 
-```{r control-models, eval=TRUE}
-# # Keep all three conditions
-# data_joint_control %<>% filter(condition %in% c("Informed", "Naive", "Excl_informed")) %>% droplevels()
-# contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1, "Excl_informed" = 0),
-#                                c("Informed" = 1, "Naive" = 0, "Excl_informed" = -1)))
-# contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
-# model_joint_control_N170 <- buildmer::buildmer(
-#   N170 ~ part * condition * experiment + (part * condition | participant) + (part * condition * experiment | item),
-#   REML = FALSE,
-#   control = ctrl_params,
-#   buildmerControl = buildmer::buildmerControl(
-#     data = data_joint_control,
-#     direction = c("order", "backward"),
-#     elim = function(logp) exp(logp) >= .20,
-#     calc.anova = TRUE,
-#     ddf = "Satterthwaite"
-#   )
-# )
-# emmeans::emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-# emmeans::emmeans(model_joint_control_N170@model, pairwise ~ condition | part, infer = TRUE)$contrasts
-
+```{r control-models, eval=rerun_models}
 # This time, we keep only the two conditions with matching keywords
@@
   models = models_joint_control,
-  stub_anova = c("Part", "Condition", "Experiment", "Pt. × con.", "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."),
+  stub_anova = c(
+    "Part", "Condition", "Experiment", "Pt. × con.",
+    "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."
+  ),
   stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of Linear Mixed-Effects Regression Models With a Different Baseline",
-  note = "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval."
+  caption =
+    "Results of Linear Mixed-Effects Regression Models With a Different Baseline",
+  note =
+    "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\\% confidence interval."
 )
@@
 
-[^1]: Note that these percentages do not add up to 100% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).
+[^1]: Note that these percentages do not add up to 100% because some objects were excluded from all analyses if participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).
 
@@
 
-# Preprocess the EEG for Epxeriment 3 in Python
+# Preprocess the EEG for Experiment 3 in Python
 fnames_exp3 <- list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE)
@@
 
-# # Preprocess the EEG for Epxeriment 3 in Python
+# # Preprocess the EEG for Experiment 3 in Python
 # map2(
@@
   models_exp3,
-  stub_anova = c("Part", "Condition", "Position", "Pt. × con.", "Pt. × pos.", "Ins. × pos.", "Pt. × con. × pos."),
+  stub_anova = c(
+    "Part", "Condition", "Position", "Pt. × con.",
+    "Pt. × pos.", "Ins. × pos.", "Pt. × con. × pos."
+  ),
   stub_contrasts = c(
@@
   caption = "Results of linear mixed-effects regression models for Experiment 3",
-  note = "Pt. = part, con. = condition, pos. = position, est. = estimate, CI = confidence interval."
+  note = "Pt. = part, con. = condition, pos. = position, est. = estimate, CI = 95\\% confidence interval."
 )
@@
 It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous findings with a similar experimental paradigm in the domain of face perception [@bentin2002]: Here, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
-This effect was absent when a visual control stimulus (a non-face object) was shown between the two presentations of the scrambled face.
+This interpretation is supported by previous findings with a similar experimental paradigm in the domain of face perception [@bentin2002]: In this study, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
+This effect was absent when a visual control stimulus (a non-face object) was shown instead of the intact face.
 In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
@@
 The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
-Another one is our reliance on rare and highly specialized objects (see appendix).
-This was necessary to induce the experience of semantic insight in a population of undergraduate students but it may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
+Another one is our reliance on rare and highly specialized objects (see Appendix A).
+This was necessary to induce the experience of semantic insight in a population of undergraduate students but the results may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
 Finally, the number participants (*n* = 24 per experiment) and trials (*k* $\approx$ 30 per part in the insight condition and *k* $\approx$ 50 per part in the naive condition) can be considered small by today's standards [@baker2020].
 Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances [see, e.g., the simulations by @matuschek2017].
-This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r table_exp1$conts["Insight part", "N170_p"]`) failed to reach statisticial signficance in the replication experiment (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
+This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r table_exp1$conts["Insight part", "N170_p"]`) failed to reach statistical significance in the replication experiment (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
 To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).
@@
 Taken together, this study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the processing of the object.
-This influence is immediate in at least two different ways: First, it does not require extensive training and can instead be observed within the same trial in which the information is being presented (and/or one trial later).
-Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages---typically associated with semantic processing---but also at earlier stages---typically associated with visual perception itself and happenning within less than a fifth of a second after the object is presented to us.
+This influence is immediate in at least two different ways: First, it does not require extensive training and can instead be observed within the same trial in which the information has been presented (and/or one trial later).
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages---typically associated with semantic processing---but also at earlier stages---typically associated with visual perception itself and happening within less than a fifth of a second after the object is presented to us.
 

### 2021-01-26 analysis/manuscript.tex
add new appendix

--- 2021-01-07 analysis/manuscript.tex
@@
 \raggedbottom
-\usepackage{setspace}
-\AtBeginEnvironment{tabular}{\doublespacing}
-\captionsetup[table]{font={stretch=1.5}}
-\captionsetup[figure]{font={stretch=1.5}}
 \usepackage[all]{nowidow}
@@
 \interfootnotelinepenalty=10000
+\usepackage{setspace}
+\AtBeginEnvironment{tabular}{\doublespacing}
+\usepackage{makecell}
+\renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
+\captionsetup[table]{font={stretch=1.5}}
+\captionsetup[figure]{font={stretch=1.5}}
 \ifxetex
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Humboldt-Universität zu Berlin\\\textsuperscript{2} Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany\\\textsuperscript{3} Fachhochschule des Mittelstands, Bamberg, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Humboldt-Universität zu Berlin\\\textsuperscript{2} Max Planck Institute for Human Cognitive and Brain Sciences\\\textsuperscript{3} Fachhochschule des Mittelstands}
 
 \abstract{
-Does our perception of an object change as soon as we discover what it is for?
-This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it pertains to the long-standing debate around the (im)penetrability of perception by ``higher'' cognitive capacities.
-In this experiment, we showed participants (\emph{n} = 24) pictures of 120 unfamiliar objects either together with valid information about their function---leading to semantically informed perception---or together with invalid information---resulting in naive perception.
-We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of perceiving objects differed from one another.
+Does our perception of an object change as soon as we discover what function it serves?
+This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+In this experiment, we showed participants (\emph{n} = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception.
+We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
 We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
@@
 We replicated these novel findings in an independent sample (\emph{n} = 24).
-Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
+Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
 }
@@
 
-How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects which were preceded either by valid information about their function, leading to semantically informed perception, or by misleading information, leading to naive perception.
-Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temporal resolution of event-related brain potentials (ERPs).
+How does our perception of an object change as soon as we discover what function it serves?
+In this study, we presented participants with unfamiliar objects that were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
+We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resoluation of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
+It allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
 
 The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world is ``cognitively impenetrable'' or, in other words, determined solely by the visual input reaching our retina.
-According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1984, 1983; Pylyshyn, 1999).
-Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects (DiCarlo et al., 2012; Goodale \& Milner, 1992; Marr, 1982).
-
-This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., P.
-M.
-Churchland, 1988; P.
-S.
-Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017).
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas (e.g., visual areas V1 and V2; Bullier, 2001; Gilbert \& Li, 2013)---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+This debate revolves around the question of whether or not our perception of the (visual) world is ``cognitively impenetrable'' (Pylyshyn, 1999) or, in other words, determined solely by the visual input reaching our retina.
+According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1983; Pylyshyn, 1999).
+Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects (DiCarlo et al., 2012; Marr, 1982).
+
+This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017).
+The myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas (e.g., V1 and V2; Bullier, 2001; Gilbert \& Li, 2013)---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
 For instance, the reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002) assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
 Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
-Along similar lines, the label feedback hypothesis (Lupyan, 2012) posits that the activation of an object's name (a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
-Finally, an active role of top-down influences is also promoted by theories of vision falling under the umbrella of Bayesian inference and predictive coding (e.g., Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
+Along similar lines, the label feedback hypothesis (Lupyan, 2012) posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
+Finally, an active role of top-down influences is also promoted by theories of vision in the framework of Bayesian inference and predictive coding (e.g., Clark, 2013; Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
 
 Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition (for review, see Collins \& Olson, 2014; Vetter \& Newen, 2014).
-These aspects of cognition may include transient states such as emotions (e.g., Bocanegra \& Zeelenberg, 2009; Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019).
-Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical, pointing out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).
-
-One productive way to investigate the top-down effects of cognition on perception while addressing some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+These aspects of cognition may include transient states such as emotions (e.g., Bocanegra \& Zeelenberg, 2009; Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Gauthier, James, et al., 2003; Weller et al., 2019).
+Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical and pointed out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).
+They argue, for example, that most behavioral paradigms have not been able to discern between perceptual and post-perceptual (e.g., memory-related) effects.
+Furthermore, cognitive influences in some studies were confounded with differences in the low-level visual input itself.
+We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our methodology and results.
+
+In general, however, it is important to note that one productive way to circumvent at least some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or post-perceptual---are influenced by higher-level capacities such as semantic knowledge.
 This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
@@
 The visual P1 component of the ERP refers to a positive deflection peaking as early as 100--150 ms after stimulus onset at occipital channels.
-It is generated by multiple sources in the extrastriatal cortices of the middle occipital and fusiform gyri (Di Russo et al., 2001; Foxe \& Simpson, 2002; Mangun, 1995).
+It is generated by multiple sources in the extrastriate cortices of the middle occipital and fusiform gyri (Di Russo et al., 2001; Mangun, 1995).
 The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus (e.g., size, luminance, and contrast; Di Russo et al., 2001; Johannes et al., 1995; Luck, 2014), which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated view of visual perception.
@@
 The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm (Weller et al., 2019).
-Here, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
+In this study, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
 This can be taken as further evidence for an influence of semantic knowledge on the early visual perception of unfamiliar objects.
@@
 Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
-These keywords could either correctly describe the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could mislead participants by describing the function of a different object, thus keeping the perception of the object semantically naive.
-During this second part, we were able measure the online influence of semantic insight on object-evoked ERPs as it happened.
+These keywords could either be matching the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could be non-matching by describing the function of a different object, thus keeping the perception of the object semantically naive.
+During this second part, we were able to measure the online influence of semantic insight on object-evoked ERPs as it happened.
 Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them---thereby mimicking previous studies (e.g., Abdel Rahman \& Sommer, 2008; Samaha et al., 2018; Weller et al., 2019).
@@
 Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
-No a priori power analysis was carried out and the sample size was chosen in line with other EEG studies in our lab at the time of data collection.
+No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
 All participants were right-handed according to the Edinburgh inventory (Oldfield, 1971) and reported normal or corrected-to-normal vision.
@@
 
-For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the object's typical function or use in a way that could typically be related to its visual features and their configuration (e.g., current--measuring, pottery--drumming).
-As our central experimental manipulation, the presentation of each unfamiliar object was preceded by its correctly matching keywords for half of the objects, whereas the other half were preceded by non-matching keywords belonging to one of the other objects.
+For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
+As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
 The matching keywords were expected to induce semantically informed perception (i.e.,~participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object would be presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
+This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
@@
 The first 15 components were extracted by the FastICA algorithm (Hyvärinen, 1999) after temporarily low-pass filtering the data at 1 Hz.
-Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 minus Fp1, HEOG: F9 minus F10) were removed automatically using the \emph{find\_bads\_eog} function.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the \emph{find\_bads\_eog} function.
 After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was epoched into segments of 2,000 ms, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
+Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
 The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset.
@@
 This led to the exclusion of an average of 2.4 trials per participant (= 0.7\%; range 0 to 24 trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (see the scalp topographies in Figure \ref{fig:exp1-plot}B).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \ref{fig:exp1-plot}B).
 
@@
 
-First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all further analyses those objects which participants classified as being known to them in the pre-insight part (i.e.,~before any keywords were presented).
+First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e.,~before any keywords were presented).
 This led to the exclusion of an average of 7.5 objects per participant (= 6.3\% of all unfamiliar objects).
-Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \ref{fig:exp1-plot}A).
+Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \ref{fig:exp1-plot}A).
 Objects were assigned to the semantically informed condition only if they were presented with matching keywords \emph{and} if participants indicated knowing what the object was or having an assumption.
@@
 Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
-This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).
+This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).
 
 The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018).
-For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
-First, they can account not only for the non-independence of data points coming from the same participant, but also simultaneously for the non-independence of data points coming from the same item.
-In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
-Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable in designs where the assignment of trials to conditions is co-determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone (e.g., Fröber et al., 2017).
+For the purpose of the present study, these models have at least three desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
+First, they can leverage all of the information that is present in the data set on the single trial level, some of which would be lost when computing averages.
+Second, they can account simultaneously for the non-independence of data points coming from the same participant and/or from the same item.
+In contrast, the neglect of the item as a random variable in by-participant ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
+Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
+Such a situation is inevitable when the assignment of trials to conditions is co-determined by the experimental manipulation and the behavioral responses of the participants to this manipulation (e.g., Fröber et al., 2017).
 
@@
 (2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model.
+Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
 All models were computed in R (Version 4.0.2; R Core Team, 2020) using the lme4 package (Version 1.1.23; Bates et al., 2015).
@@
 The model selection algorithm via likelihood ratio tests was performed using the buildmer package (Version 1.7.1; Voeten, 2020).
-Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts.
+
+Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the semantically informed against the naive condition within the pre-insight, \mbox{insight}, and post-insight parts.
 This was achieved using the emmeans package (Version 1.5.0; Lenth, 2020).
@@
 The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\url{https://osf.io/uksbc/}).
-Unfortunately, lack of informed consent prevents us from sharing the raw EEG data.
+Participants' lack of informed consent to do so prevents us from openly sharing the raw EEG data.
 
@@
 \cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
-\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\textbf{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
 \midrule
-Part & 10.89 (2, 24.5) & < .001 & 14.18 (2, 24.9) & < .001 & 32.85 (2, 25.6) & < .001\\
-Condition & 0.60 (1, 5343.5) & .438 & 0.30 (1, 24.2) & .586 & 13.00 (1, 24.4) & .001\\
-Pt. × con. & 2.30 (2, 4605.0) & .100 & 4.84 (2, 4878.2) & .008 & 10.91 (2, 5120.9) & < .001\\
-\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & -0.03 [-0.53, 0.47] & .913 & -0.12 [-0.68, 0.44] & .665 & -0.20 [-0.65, 0.26] & .400\\
-Insight part & -0.18 [-0.68, 0.32] & .490 & -0.64 [-1.20, -0.08] & .026 & 0.93 [0.48, 1.39] & < .001\\
-Post-insight part & 0.55 [0.05, 1.05] & .031 & 0.43 [-0.14, 0.99] & .136 & 1.00 [0.54, 1.46] & < .001\\
+\,\, Part & 10.89 (2, 24.5) & < .001 & 14.18 (2, 24.9) & < .001 & 32.85 (2, 25.6) & < .001\\
+\,\, Condition & 0.60 (1, 5343.5) & .438 & 0.30 (1, 24.2) & .586 & 13.00 (1, 24.4) & .001\\
+\,\, Pt. × con. & 2.30 (2, 4605.1) & .100 & 4.84 (2, 4878.2) & .008 & 10.91 (2, 5120.9) & < .001\\
+\textbf{Informed - naive} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p}\\ \midrule
+\,\, Pre-insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.03 [-0.53, 0.47]}\\\Gape[-2pt][6pt]{-0.11 (4996.8)}} & .913 & \makecell[c]{\Gape[6pt][-2pt]{-0.12 [-0.68, 0.44]}\\\Gape[-2pt][6pt]{-0.43 (88.8)}} & .665 & \makecell[c]{\Gape[6pt][-2pt]{-0.20 [-0.65, 0.26]}\\\Gape[-2pt][6pt]{-0.85 (102.7)}} & .400\\
+\,\, Insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.18 [-0.68, 0.32]}\\\Gape[-2pt][6pt]{-0.69 (5310.6)}} & .490 & \makecell[c]{\Gape[6pt][-2pt]{-0.64 [-1.20, -0.08]}\\\Gape[-2pt][6pt]{-2.26 (92.4)}} & .026 & \makecell[c]{\Gape[6pt][-2pt]{ 0.93 [0.48, 1.39]}\\\Gape[-2pt][6pt]{ 4.04 (103.7)}} & < .001\\
+\,\, Post-insight part & \makecell[c]{\Gape[6pt][-2pt]{ 0.55 [0.05, 1.05]}\\\Gape[-2pt][6pt]{ 2.16 (4717.7)}} & .031 & \makecell[c]{\Gape[6pt][-2pt]{ 0.43 [-0.14, 0.99]}\\\Gape[-2pt][6pt]{ 1.51 (91.8)}} & .136 & \makecell[c]{\Gape[6pt][-2pt]{ 1.00 [0.54, 1.46]}\\\Gape[-2pt][6pt]{ 4.31 (105.0)}} & < .001\\ \midrule
+logLik (\textit{df}) & -16555.1 (13) &  & -16289.6 (17) &  & -15350.3 (17) & \\
+RMSE & 5.07 &  & 4.79 &  & 4.05 & \\
+Conditional $R^2$ & 0.289 &  & 0.379 &  & 0.207 & \\
+Marginal $R^2$ & 0.007 &  & 0.053 &  & 0.048 & \\
 \bottomrule
@@
 In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}(1, 24.4) = 13.00, \emph{p} = .001.
-Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4605.0) = 2.30, \emph{p} = .100.
+Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also showing a weak statistical trend in the P1 component, \emph{F}(2, 4605.1) = 2.30, \emph{p} = .100.
 To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
@@
 
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .400 (see Table \ref{tab:exp1-table} and Figure \ref{fig:exp1-plot}B).
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \(\ge\) .400 (see Table \ref{tab:exp1-table} and Figure \ref{fig:exp1-plot}B).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs.~naive perception) had not yet taken place.
@@
 
-In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part), to test whether the semantic information had any lasting effects on the processing of the objects.
+In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part).
+This allowed us to test if the semantic information had any lasting effects on the processing of the objects.
 As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the effect in the N170 component did not reoccur, \emph{p} = .136.
@@
 An average of 7.0 objects per participant (= 5.8\% of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of 26.4 objects were assigned to the semantically informed condition (= 44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (= 82.0\% of objects presented with non-matching keywords).
+Based on participants' responses in the insight part, an average of 26.4 objects was assigned to the semantically informed condition (= 44.0\% of objects presented with matching keywords) and an average of 49.2 objects was assigned to the naive condition (= 82.0\% of objects presented with non-matching keywords).
 Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials per participant (= 3.0\%; range 0 to 85 trials).
@@
 \cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
-\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\textbf{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
 \midrule
-Part & 17.45 (2, 5267.1) & < .001 & 16.57 (2, 25.1) & < .001 & 70.12 (2, 25.2) & < .001\\
-Condition & 0.02 (1, 5276.9) & .900 & 0.98 (1, 5228.5) & .322 & 19.95 (1, 5242.5) & < .001\\
-Pt. × con. & 3.60 (2, 5267.1) & .027 & 1.25 (2, 4756.5) & .287 & 7.92 (2, 4714.9) & < .001\\
-\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & -0.16 [-0.71, 0.40] & .582 & -0.03 [-0.53, 0.48] & .920 & 0.04 [-0.43, 0.50] & .877\\
-Insight part & -0.48 [-1.03, 0.08] & .094 & -0.48 [-0.99, 0.03] & .064 & 1.33 [0.87, 1.79] & < .001\\
-Post-insight part & 0.57 [0.01, 1.13] & .047 & 0.06 [-0.45, 0.57] & .818 & 0.47 [0.01, 0.93] & .047\\
+\,\, Part & 17.45 (2, 5267.1) & < .001 & 16.57 (2, 25.1) & < .001 & 70.12 (2, 25.2) & < .001\\
+\,\, Condition & 0.02 (1, 5276.9) & .900 & 0.98 (1, 5228.5) & .322 & 19.95 (1, 5242.5) & < .001\\
+\,\, Pt. × con. & 3.60 (2, 5267.1) & .027 & 1.25 (2, 4756.5) & .287 & 7.92 (2, 4714.9) & < .001\\
+\textbf{Informed - naive} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p}\\ \midrule
+\,\, Pre-insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.16 [-0.71, 0.40]}\\\Gape[-2pt][6pt]{-0.55 (5270.9)}} & .582 & \makecell[c]{\Gape[6pt][-2pt]{-0.03 [-0.53, 0.48]}\\\Gape[-2pt][6pt]{-0.10 (4772.1)}} & .920 & \makecell[c]{\Gape[6pt][-2pt]{0.04 [-0.43, 0.50]}\\\Gape[-2pt][6pt]{0.15 (5177.9)}} & .877\\
+\,\, Insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.48 [-1.03, 0.08]}\\\Gape[-2pt][6pt]{-1.67 (5270.7)}} & .094 & \makecell[c]{\Gape[6pt][-2pt]{-0.48 [-0.99, 0.03]}\\\Gape[-2pt][6pt]{-1.85 (5241.8)}} & .064 & \makecell[c]{\Gape[6pt][-2pt]{1.33 [0.87, 1.79]}\\\Gape[-2pt][6pt]{5.68 (4781.9)}} & < .001\\
+\,\, Post-insight part & \makecell[c]{\Gape[6pt][-2pt]{ 0.57 [0.01, 1.13]}\\\Gape[-2pt][6pt]{ 1.99 (5270.8)}} & .047 & \makecell[c]{\Gape[6pt][-2pt]{ 0.06 [-0.45, 0.57]}\\\Gape[-2pt][6pt]{ 0.23 (5035.9)}} & .818 & \makecell[c]{\Gape[6pt][-2pt]{0.47 [0.01, 0.93]}\\\Gape[-2pt][6pt]{1.98 (5067.3)}} & .047\\ \midrule
+logLik (\textit{df}) & -16707.1 (8) &  & -16174.3 (13) &  & -15648.0 (13) & \\
+RMSE & 5.62 &  & 5.03 &  & 4.58 & \\
+Conditional $R^2$ & 0.242 &  & 0.399 &  & 0.174 & \\
+Marginal $R^2$ & 0.005 &  & 0.037 &  & 0.068 & \\
 \bottomrule
@@
 
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs.~non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, \emph{b} = -0.48 µV, \emph{p} = .064, and a significant reduction of the N400 component, \emph{b} = 0.93 µV, \emph{p} \textless{} .001.
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs.~non-matching keywords) was associated with an enhancement of the N170 component, although this effect marginally failed to reach statistical significance, \emph{b} = -0.48 µV, \emph{p} = .064.
+The reduction of the N400 component during semantically informed perception remained significant, \emph{b} = 1.33 µV, \emph{p} \textless{} .001.
 
@@
 
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.57 µV, \emph{p} = .047.
-Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.47 µV, \emph{p} = .047.
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) again led to significantly reduced amplitudes in the N400 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.47 µV, \emph{p} = .047.
+Also, P1 amplitudes in response these objects were significantly enlarged, \emph{b} = 0.57 µV, \emph{p} = .047.
 
@@
 Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast (i.e.,~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al., 2020).
-This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
-They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2.
-Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit (Matuschek et al., 2017; Voeten, 2020).
+This factor and its interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
+They were not included as by-participant random slopes because different participants took part in Experiments 1 and 2.
+Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit {[}Matuschek et al.
+(2017); Voeten (2020); see Appendix B{]}.
 
@@
 \cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
-\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\textbf{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
 \midrule
-Part & 12.34 (2, 49.1) & < .001 & 30.08 (2, 50.3) & < .001 & 94.61 (2, 50.6) & < .001\\
-Condition & 0.15 (1, 10573.1) & .699 & 1.16 (1, 45.2) & .287 & 41.38 (1, 10593.6) & < .001\\
-Experiment & 0.33 (1, 48.2) & .567 & 2.50 (1, 48.0) & .121 & 4.96 (1, 48.4) & .031\\
-Pt. × con. & 3.90 (2, 9004.9) & .020 & 5.26 (2, 9904.1) & .005 & 15.34 (2, 10091.0) & < .001\\
-Pt. × exp. & 0.04 (2, 49.1) & .966 & 0.58 (2, 50.3) & .565 & 2.55 (2, 50.6) & .088\\
-Ins. × exp. & 0.43 (1, 10573.1) & .514 & 0.06 (1, 45.2) & .805 & 0.07 (1, 10593.6) & .785\\
-Pt. × con. × exp. & 0.03 (2, 9004.9) & .968 & 0.58 (2, 9904.1) & .559 & 2.54 (2, 10091.0) & .079\\
-\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & -0.10 [-0.47, 0.28] & .616 & -0.10 [-0.48, 0.29] & .611 & -0.09 [-0.39, 0.22] & .577\\
-Insight part & -0.24 [-0.62, 0.13] & .202 & -0.57 [-0.96, -0.18] & .004 & 1.10 [0.80, 1.41] & < .001\\
-Post-insight part & 0.47 [0.09, 0.84] & .014 & 0.24 [-0.15, 0.63] & .225 & 0.73 [0.42, 1.04] & < .001\\
+\,\, Part & 12.34 (2, 49.1) & < .001 & 30.08 (2, 50.3) & < .001 & 94.61 (2, 50.6) & < .001\\
+\,\, Condition & 0.15 (1, 10573.1) & .699 & 1.16 (1, 45.2) & .287 & 41.38 (1, 10593.6) & < .001\\
+\,\, Experiment & 0.33 (1, 48.2) & .567 & 2.50 (1, 48.0) & .121 & 4.96 (1, 48.4) & .031\\
+\,\, Pt. × con. & 3.90 (2, 9004.9) & .020 & 5.26 (2, 9904.1) & .005 & 15.34 (2, 10091.0) & < .001\\
+\,\, Pt. × exp. & 0.04 (2, 49.1) & .966 & 0.58 (2, 50.3) & .565 & 2.55 (2, 50.6) & .088\\
+\,\, Ins. × exp. & 0.43 (1, 10573.1) & .514 & 0.06 (1, 45.2) & .805 & 0.07 (1, 10593.6) & .785\\
+\,\, Pt. × con. × exp. & 0.03 (2, 9004.9) & .968 & 0.58 (2, 9904.1) & .559 & 2.54 (2, 10091.0) & .079\\
+\textbf{Informed - naive} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p}\\ \midrule
+\,\, Pre-insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.10 [-0.47, 0.28]}\\\Gape[-2pt][6pt]{-0.50 (9534.6)}} & .616 & \makecell[c]{\Gape[6pt][-2pt]{-0.10 [-0.48, 0.29]}\\\Gape[-2pt][6pt]{-0.51 (208.1)}} & .611 & \makecell[c]{\Gape[6pt][-2pt]{-0.09 [-0.39, 0.22]}\\\Gape[-2pt][6pt]{-0.56 (10459.4)}} & .577\\
+\,\, Insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.24 [-0.62, 0.13]}\\\Gape[-2pt][6pt]{-1.28 (10420.2)}} & .202 & \makecell[c]{\Gape[6pt][-2pt]{-0.57 [-0.96, -0.18]}\\\Gape[-2pt][6pt]{-2.90 (214.4)}} & .004 & \makecell[c]{\Gape[6pt][-2pt]{ 1.10 [0.80, 1.41]}\\\Gape[-2pt][6pt]{ 7.09 (10436.6)}} & < .001\\
+\,\, Post-insight part & \makecell[c]{\Gape[6pt][-2pt]{ 0.47 [0.09, 0.84]}\\\Gape[-2pt][6pt]{ 2.45 (9881.6)}} & .014 & \makecell[c]{\Gape[6pt][-2pt]{ 0.24 [-0.15, 0.63]}\\\Gape[-2pt][6pt]{ 1.22 (211.4)}} & .225 & \makecell[c]{\Gape[6pt][-2pt]{ 0.73 [0.42, 1.04]}\\\Gape[-2pt][6pt]{ 4.67 (10339.5)}} & < .001\\ \midrule
+logLik (\textit{df}) & -33272.6 (19) &  & -32474.6 (23) &  & -31045.5 (19) & \\
+RMSE & 5.32 &  & 4.91 &  & 4.32 & \\
+Conditional $R^2$ & 0.271 &  & 0.400 &  & 0.198 & \\
+Marginal $R^2$ & 0.008 &  & 0.06 &  & 0.07 & \\
 \bottomrule
@@
 
-As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.34, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}(1, 10593.6) = 41.38, \emph{p} \textless{} .001.
+As shown in Table \ref{tab:joint-table}, the main effect of part was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.34, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}(1, 10593.6) = 41.38, \emph{p} \textless{} .001.
 Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 3.90, all \emph{p}s \textless{} .020.
-While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.96, \emph{p} = .031, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
+There was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.96, \emph{p} = .031, with more negative amplitudes in Experiment 1 as compared to Experiment 2, \emph{b} = -1.06.
+However, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
 
@@
 Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages.
+Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of signalling messages.
 To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were preceded by matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for 49.6\% of objects presented with matching keywords as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize.
-Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.
+Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
+Across both experiments, this was the case for 49.6\% of objects presented with matching keywords, as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -0.99 µV, \emph{p} \textless{} .001.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
+Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.19 µV, \emph{p} \textless{} .001.
 
@@
 To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
-For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was misleading, thus keeping the perception of the object semantically naive.
+For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, the information was non-matching, thus keeping the perception of the object semantically naive.
 We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
 When the same objects were presented again without the semantic information, the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+We will discuss each of these effects in turn, starting with the latest (i.e., post-perceptual) effect and moving backward in time to the earlier (i.e., more perceptual) effects.
 
 The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
-Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing compared to the naive condition (Kutas \& Federmeier, 2011).
+Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) lessened participants' demand for effortful semantic processing in comparison to the naive condition (Kutas \& Federmeier, 2011).
 This replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves (e.g., Abdel Rahman \& Sommer, 2008; Supp et al., 2005) or difficult to integrate into the preceding context (e.g., Barrett \& Rugg, 1990; Ganis et al., 1996; Hirschfeld et al., 2011).
@@
 It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous findings using a similar experimental paradigm in the realm of face perception (Bentin \& Golland, 2002): Here, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
-This effect was absent when a visual control stimulus (a non-face object instead of the intact face) was shown between the two presentations of the scrambled face.
-In the realm of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects (Beaucousin et al., 2011).
+This interpretation is supported by previous findings with a similar experimental paradigm in the domain of face perception (Bentin \& Golland, 2002): Here, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
+This effect was absent when a visual control stimulus (a non-face object) was shown between the two presentations of the scrambled face.
+In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects (Beaucousin et al., 2011).
 Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
@@
 
-Unlike the N400 and N170 components, the P1 component (100--150 ms after object onset) was modulated by semantic information only one trial after it had been obtained.
-This is consistent with previous studies showing P1 effects when participants learned meaningful information about previously unfamiliar objects (Abdel Rahman \& Sommer, 2008; Maier \& Abdel Rahman, 2019, 2018; Weller et al., 2019) or about familiar objects that were rendered difficult to recognize (Samaha et al., 2018).
-What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information) but that it can be observed as soon as one trial after semantic insight has happened.
+The P1 component (100--150 ms after object onset), unlike the N400 and N170 components, was modulated by semantic information only one trial after the information had been obtained.
+This is consistent with previous studies showing modulations of the P1 component when participants learned meaningful information about previously unfamiliar objects (Abdel Rahman \& Sommer, 2008; Maier \& Abdel Rahman, 2019, 2018; Weller et al., 2019) or about familiar objects that were rendered difficult to recognize (Samaha et al., 2018).
+What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information).
+Instead, it can be observed as soon as one trial after semantic insight has happened.
 Because the P1 is typically associated with lower-level sensory processing (e.g., Johannes et al., 1995; Luck, 2014; Pratt, 2011), we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
 
-Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects as we perceive them.
-However, the finding that these two components were modulated in different parts of our experiment suggests that they reflect different aspects top-down processing with different time courses and neuroanatomical implementations.
-It has been pointed out that the onset of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem reflect recurrent processing \emph{within} the visual system (Wyatte et al., 2014).
-Here we show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
+Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects.
+However, the finding that these two components were modulated in different parts of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
+It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem reflect recurrent processing \emph{within} the visual system (Wyatte et al., 2014).
+Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
 
@@
 They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
-This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital complex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
+This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital cortex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
 Both of these cortical regions are consistent with the neural generators of the N170 and P1 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
 
-On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception Clarke (2020).
-However, proponents of such a modular view have pointed out important conceptual and methodological shortcomings of previous studies claiming to demonstrate top-down effects of cognition on perception (Firestone \& Scholl, 2016; Machery, 2015).
-We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was presented (in the pre-insight part).
+On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception (Firestone \& Scholl, 2016; Fodor, 1983; Pylyshyn, 1999; but see Clarke, 2020).
+However, proponents of such a modular view have pointed out important shortcomings of previous studies that claimed to demonstrate top-down effects of cognition on perception (Firestone \& Scholl, 2016; Machery, 2015).
+We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was being presented (in the pre-insight part).
 Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual locus from those with a post-perceptual locus.
@@
 
-An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in machine vision (e.g., DiCarlo et al., 2012; Marr, 1982).
-In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision (e.g., Marr, 1982; Serre et al., 2007).
+In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
 For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this ``barrier of meaning'' (Mitchell, 2020).
-Drawing inspiration from cognitive psychology and human neuroscientific data may help making these models more biologically plausible and, at the same time, more resource and data efficient.
+Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.
 
@@
 The effects are consistent, however, with the reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002) which posits that objects first enter our visual consciousness at an abstract, conceptual level.
-Once this initial ``vision at a glance'' has taken place, feedback connections to earlier layers of the visual system are being accessed to extract relevant lower-level features (``vision with scrutiny'').
+Once this initial ``vision at a glance'' has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features (``vision with scrutiny'').
 This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex (Hsieh et al., 2010) as well as (b) the modulations of early visual ERP components observed in the present study and others (Abdel Rahman \& Sommer, 2008; Maier et al., 2014; Maier \& Abdel Rahman, 2019; Samaha et al., 2018; Weller et al., 2019).
-Besides the reverse hierarchy theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories (e.g., Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
+Besides this specific theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories (e.g., Clark, 2013; Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
 Despite the theoretical advances, the mechanistic details of these top-down effects at the algorithmic and implementational level (Marr, 1982) remain to be clarified.
@@
 The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
-Another one is our reliance on rare and highly specialized objects (see appendix).
-This was necessary to induce the experience of semantic insight in an adult population of undergraduate students but may not necessarily generalize to the way in which we learn about everyday objects.\footnote{Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize (Samaha et al., 2018).} One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
+Another one is our reliance on rare and highly specialized objects (see Appendix A).
+This was necessary to induce the experience of semantic insight in a population of undergraduate students but it may not necessarily generalize to the way in which we learn about everyday objects.\footnote{Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize (Samaha et al., 2018).} One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
 Finally, the number participants (\emph{n} = 24 per experiment) and trials (\emph{k} \(\approx\) 30 per part in the insight condition and \emph{k} \(\approx\) 50 per part in the naive condition) can be considered small by today's standards (Baker et al., 2020).
-Our analysis may therefore not have been particularly sensitive, especially since linear mixed-effects regression models often have limited statistical power (see, e.g., the simulations by Matuschek et al., 2017).
-
-Nevertheless, this study provides preliminary evidence that whenever we acquire semantic information about a previously unfamiliar object, this information influences multiple stages of processing.
-These influences do not seem to be confined to later, post-perceptual stages---typically associated with semantic processing---but can also be observed at earlier stages---typically reflecting lower levels of visual perception and happening within 200 ms after the object is presented to us.
+Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances (see, e.g., the simulations by Matuschek et al., 2017).
+This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, \emph{p} = .026) failed to reach statisticial signficance in the replication experiment (\emph{p} = .064).
+To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).
+It should be noted, however, that the joint analysis of both data sets yielded a very robust N170 effect (\emph{p} = .004).
+This makes it less likely that the effect observed in Experiment 1 was due to a false positive and instead suggests that statistical power in Experiment 2 was insufficient to render the effect significant.
+Also note that the effect in the P1 component was statistically significant in both experiments individually, making an even stronger case for the susceptibility of early cortical processing to newly acquired knowledge about objects.
+
+Taken together, this study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the processing of the object.
+This influence is immediate in at least two different ways: First, it does not require extensive training and can instead be observed within the same trial in which the information is being presented (and/or one trial later).
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages---typically associated with semantic processing---but also at earlier stages---typically associated with visual perception itself and happenning within less than a fifth of a second after the object is presented to us.
 
@@
 \setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
 
@@
 \url{https://doi.org/10.1016/j.jneumeth.2018.09.016}
-
-\leavevmode\hypertarget{ref-churchland1988}{}%
-Churchland, P. M. (1988). Perceptual plasticity and theoretical neutrality: A reply to {Jerry} {Fodor}. \emph{Philosophy of Science}, \emph{55}(2), 167--187. \url{https://doi.org/10.1086/289425}
 
@@
 
+\leavevmode\hypertarget{ref-clark2013}{}%
+Clark, A.
+(2013).
+Whatever next?
+{Predictive} brains, situated agents, and the future of cognitive science.
+\emph{Behavioral and Brain Sciences}, \emph{36}(3), 181--204.
+\url{https://doi.org/10.1017/S0140525X12000477}
+
 \leavevmode\hypertarget{ref-clarke2020}{}%
@@
 
-\leavevmode\hypertarget{ref-fodor1984}{}%
-Fodor, J. A. (1984). Observation reconsidered. \emph{Philosophy of Science}, \emph{51}(1), 23--43. \url{https://doi.org/10.1086/289162}
-
 \leavevmode\hypertarget{ref-fodor1983}{}%
 Fodor, J. A. (1983). \emph{The modularity of mind}. MIT Press.
-
-\leavevmode\hypertarget{ref-foxe2002}{}%
-Foxe, J.
-J., \& Simpson, G.
-V.
-(2002).
-Flow of activation from {V1} to frontal cortex in humans.
-\emph{Experimental Brain Research}, \emph{142}(1), 139--150.
-\url{https://doi.org/10.1007/s00221-001-0906-7}
 
@@
 
-\leavevmode\hypertarget{ref-goodale1992}{}%
-Goodale, M. A., \& Milner, A. D. (1992). Separate visual pathways for perception and action. \emph{Trends in Neurosciences}, \emph{15}(1), 20--25. \url{https://doi.org/10.1016/0166-2236(92)90344-8}
-
 \leavevmode\hypertarget{ref-gramfort2013}{}%
@@
 Lenth, R. (2020). \emph{Emmeans: Estimated marginal means, aka least-squares means}. \url{https://CRAN.R-project.org/package=emmeans}
-
-\leavevmode\hypertarget{ref-lin1997}{}%
-Lin, E.
-L., \& Murphy, G.
-L.
-(1997).
-Effects of background knowledge on object categorization and part detection.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{23}(4), 1153--1169.
-\url{https://doi.org/10.1037/0096-1523.23.4.1153}
 
@@
 
+\leavevmode\hypertarget{ref-serre2007}{}%
+Serre, T., Oliva, A., \& Poggio, T.
+(2007).
+A feedforward architecture accounts for rapid categorization.
+\emph{Proceedings of the National Academy of Sciences}, \emph{104}(15), 6424--6429.
+\url{https://doi.org/10.1073/pnas.0700622104}
+
 \leavevmode\hypertarget{ref-suess2015}{}%
@@
 \leavevmode\hypertarget{ref-R-buildmer}{}%
-Voeten, C. C. (2020). \emph{{buildmer}: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
+Voeten, C. C. (2020). \emph{Buildmer: Stepwise elimination and term reordering for mixed-effects regression}. \url{https://CRAN.R-project.org/package=buildmer}
 
 \leavevmode\hypertarget{ref-vogel2000}{}%
-Vogel, E. K., \& Luck, S. J. (2000). The visual {N1} component as an index of a discrimination process. \emph{Psychophysiology}, \emph{37}(2), 190--203.
+Vogel, E. K., \& Luck, S. J. (2000). The visual {N1} component as an index of a discrimination process. \emph{Psychophysiology}, \emph{37}(2), 190--203. \url{https://doi.org/10.1111/1469-8986.3720190}
 

### 2021-01-26 analysis/master_thesis.tex
add new appendix

@@
 \fancyhead[RE,LO]{Semantic Knowledge and Unfamiliar Objects}
+\renewcommand{\headrulewidth}{0.4pt}
 \usepackage{setspace}
 \AtBeginEnvironment{tabular}{\doublespacing}
+\usepackage{makecell}
+\renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
 \captionsetup[table]{font={stretch=1.5}}
@@
 
-\begin{center}\textbf{Acknowledgment}\end{center}
-
-I would like to thank \ldots{} (tbc)
+\vspace*{55mm}
+
+\begin{center}\textbf{Acknowledgments}\end{center}
+
+This thesis presents a re-analysis of the data from two experiments that had already been conducted before I joined the Neurocognitive Psychology Lab at Humboldt-Universität zu Berlin.
+Therefore, it would not have been possible for me to write it without the time and effort that Franziska Süß, Nele Langosch, and Rasha Abdel Rahman have spent conceptualizing and running these experiments, along with the help of all participants, research assistants, and technical staff who contributed to the data collection.
+I would also like to thank all current members of the lab for their guidance and fruitful discussions on the topics of data analysis and reporting.
+Valuable feedback on an earlier draft of this thesis was given by Anna Kuhlen, Annika Just, and Garrett Widener.
+Finally, I am most grateful to my parents, friends, and supervisors: During the journey of writing this thesis, their support has often literally changed my view of the world around me to the better.
 
@@
 
-Does our perception of an object change as soon as we discover what it is for?
-This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it pertains to the long-standing debate around the (im)penetrability of perception by ``higher'' cognitive capacities.
-In this experiment, we showed participants (\emph{n} = 24) pictures of 120 unfamiliar objects either together with valid information about their function---leading to semantically informed perception---or together with invalid information---resulting in naive perception.
-We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of perceiving objects differed from one another.
+\noindent Does our perception of an object change as soon as we discover what function it serves?
+This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+In this experiment, we showed participants (\emph{n} = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception.
+We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
 We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
@@
 We replicated these novel findings in an independent sample (\emph{n} = 24).
-Consistent with previous work, they suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
+Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
+
+\emph{Keywords:} objects, semantic knowledge, visual perception, event-related potentials
 
@@
 
-How does our perception of an object change as soon as we discover what it is for?
-In this study, we presented participants with unfamiliar objects which were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
-Semantically informed perception of objects was expected to differ from naive perception at certain stages in the processing hierarchy and we aimed to identify these stages by capitalizing on the high temporal resolution of event-related brain potentials (ERPs).
+Does our perception of an object change as soon as we discover what function it serves?
+In this study, we presented participants with unfamiliar objects that were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
+We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resolution of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
+It allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
 
 The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world is ``cognitively impenetrable'' or, in other words, determined solely by the visual input reaching our retina.
-According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1984, 1983; Pylyshyn, 1999).
-Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects (DiCarlo et al., 2012; Goodale \& Milner, 1992; Marr, 1982).
-
-This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., P.
-M.
-Churchland, 1988; P.
-S.
-Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017).
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., medial- and inferotemporal areas MT and IT) to early visual areas (e.g., visual areas V1 and V2; Bullier, 2001; Gilbert \& Li, 2013)---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+This debate revolves around the question of whether or not our perception of the (visual) world is ``cognitively impenetrable'' (Pylyshyn, 1999) or, in other words, determined solely by the visual input reaching our retina.
+According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace (e.g., Firestone \& Scholl, 2016; Fodor, 1983; Pylyshyn, 1999).
+Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects (DiCarlo et al., 2012; Marr, 1982).
+
+This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on (e.g., Churchland et al., 1994; Lupyan, 2015; Teufel \& Nanay, 2017).
+The myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas (e.g., V1 and V2; Bullier, 2001; Gilbert \& Li, 2013)---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
 For instance, the reverse hierarchy theory (Ahissar \& Hochstein, 2004; Hochstein \& Ahissar, 2002) assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
 Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
-Along similar lines, the label feedback hypothesis (Lupyan, 2012) posits that the activation of an object's name (a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
-Finally, an active role of top-down influences is also promoted by theories of vision falling under the umbrella of Bayesian inference and predictive coding (e.g., Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
+Along similar lines, the label feedback hypothesis (Lupyan, 2012) posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
+Finally, an active role of top-down influences is also promoted by theories of vision in the framework of Bayesian inference and predictive coding (e.g., Clark, 2013; Lupyan, 2015; Panichello et al., 2013; Yuille \& Kersten, 2006).
 
 Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition (for review, see Collins \& Olson, 2014; Vetter \& Newen, 2014).
-These aspects of cognition may include transient states such as emotions (e.g., Bocanegra \& Zeelenberg, 2009; Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Lin \& Murphy, 1997; Weller et al., 2019).
+These aspects of cognition may include transient states such as emotions (e.g., Bocanegra \& Zeelenberg, 2009; Phelps et al., 2016) or intentions (e.g., Balcetis \& Dunning, 2010; Cole et al., 2012) as well as learned capacities such as language (e.g., Boutonnet \& Lupyan, 2015; Maier \& Abdel Rahman, 2018; Mo et al., 2011) or declarative knowledge about faces (e.g., Abdel Rahman, 2011; Eiserbeck \& Abdel Rahman, 2020; Suess et al., 2015) and objects (e.g., Abdel Rahman \& Sommer, 2008; Gauthier, James, et al., 2003; Weller et al., 2019).
 Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical and pointed out important methodological shortcomings in large parts of this literature (Firestone \& Scholl, 2016; Machery, 2015).
-They have argued, for example, that most behavioral paradigms have not been able to discern between perceptual and postperceptual (e.g., memory-related) effects.
-Furthermore, cognitive influences in some studies have been confounded with differences in the lower-level visual input.
+They argue, for example, that most behavioral paradigms have not been able to discern between perceptual and post-perceptual (e.g., memory-related) effects.
+Furthermore, cognitive influences in some studies were confounded with differences in the low-level visual input itself.
 We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our methodology and results.
 
-In general, however, it is important to note that one productive way to circumvent some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or postperceptual---are influenced by higher-level capacities such as semantic knowledge.
+In general, however, it is important to note that one productive way to circumvent at least some of these concerns is to use neurophysiological recording methods such as ERPs (Luck, 2014): Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or post-perceptual---are influenced by higher-level capacities such as semantic knowledge.
 This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
@@
 In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this had not been the case.
-Crucially, these differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
-Interestingly, the ERPs in the in-depth knowledge condition even were qualitatively similar to those for untrained but well-known objects.
+These differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
+Interestingly, the ERPs observed for previously unfamiliar objects with newly acquired in-depth knowledge were qualitatively similar to those for untrained but well-known objects.
 The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm (Weller et al., 2019).
-Here, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
+In this study, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
 This can be taken as further evidence for an influence of semantic knowledge on the early visual perception of unfamiliar objects.
@@
 These keywords could either be matching the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could be non-matching by describing the function of a different object, thus keeping the perception of the object semantically naive.
-During this second part, we were able measure the online influence of semantic insight on object-evoked ERPs as it happened.
+During this second part, we were able to measure the online influence of semantic insight on object-evoked ERPs as it happened.
 Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them---thereby mimicking previous studies (e.g., Abdel Rahman \& Sommer, 2008; Samaha et al., 2018; Weller et al., 2019).
@@
 Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
-This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).
+This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).
 
 The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018).
-For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages.
-First, they can account not only for the non-independence of data points coming from the same participant, but also simultaneously for the non-independence of data points coming from the same item.
-In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
-Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable in designs where the assignment of trials to conditions is co-determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone (e.g., Fröber et al., 2017).
+For the purpose of the present study, these models have at least three desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant averages.
+First, they can leverage all of the information that is present in the data set on the single trial level, some of which would be lost when computing averages.
+Second, they can account simultaneously for the non-independence of data points coming from the same participant and/or from the same item.
+In contrast, the neglect of the item as a random variable in by-participant ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
+Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
+Such a situation is inevitable when the assignment of trials to conditions is co-determined by the experimental manipulation and the behavior of participants in response to this manipulation (e.g., Fröber et al., 2017).
 
@@
 The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\url{https://osf.io/uksbc/}).
-Unfortunately, lack of informed consent prevents us from sharing the raw EEG data.
+We are not able to share the raw EEG data openly because we did not obtain participants' informed consent to do so.
 
@@
 \cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
-\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\textbf{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
 \midrule
-Part & 10.82 (2, 24.5) & < .001 & 14.15 (2, 24.9) & < .001 & 33.01 (2, 25.5) & < .001\\
-Condition & 0.87 (1, 5302.9) & .351 & 0.89 (1, 114.3) & .349 & 13.09 (1, 24.8) & .001\\
-Pt. × con. & 2.40 (2, 4590.9) & .091 & 5.34 (2, 4853.1) & .005 & 11.18 (2, 5030.2) & < .001\\
-\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & 0.00 [-0.50, 0.49] & .987 & -0.17 [-0.64, 0.30] & .485 & -0.20 [-0.65, 0.26] & .393\\
-Insight part & -0.15 [-0.65, 0.34] & .550 & -0.66 [-1.14, -0.19] & .006 & 0.93 [0.48, 1.39] & < .001\\
-Post-insight part & 0.57 [0.08, 1.07] & .023 & 0.41 [-0.07, 0.88] & .094 & 1.00 [0.55, 1.46] & < .001\\
+\,\, Part & 10.89 (2, 24.5) & < .001 & 14.18 (2, 24.9) & < .001 & 32.85 (2, 25.6) & < .001\\
+\,\, Condition & 0.60 (1, 5343.5) & .438 & 0.30 (1, 24.2) & .586 & 13.00 (1, 24.4) & .001\\
+\,\, Pt. × con. & 2.30 (2, 4605.1) & .100 & 4.84 (2, 4878.2) & .008 & 10.91 (2, 5120.9) & < .001\\
+\textbf{Informed - naive} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p}\\ \midrule
+\,\, Pre-insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.03 [-0.53, 0.47]}\\\Gape[-2pt][6pt]{-0.11 (4996.8)}} & .913 & \makecell[c]{\Gape[6pt][-2pt]{-0.12 [-0.68, 0.44]}\\\Gape[-2pt][6pt]{-0.43 (88.8)}} & .665 & \makecell[c]{\Gape[6pt][-2pt]{-0.20 [-0.65, 0.26]}\\\Gape[-2pt][6pt]{-0.85 (102.7)}} & .400\\
+\,\, Insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.18 [-0.68, 0.32]}\\\Gape[-2pt][6pt]{-0.69 (5310.6)}} & .490 & \makecell[c]{\Gape[6pt][-2pt]{-0.64 [-1.20, -0.08]}\\\Gape[-2pt][6pt]{-2.26 (92.4)}} & .026 & \makecell[c]{\Gape[6pt][-2pt]{ 0.93 [0.48, 1.39]}\\\Gape[-2pt][6pt]{ 4.04 (103.7)}} & < .001\\
+\,\, Post-insight part & \makecell[c]{\Gape[6pt][-2pt]{ 0.55 [0.05, 1.05]}\\\Gape[-2pt][6pt]{ 2.16 (4717.7)}} & .031 & \makecell[c]{\Gape[6pt][-2pt]{ 0.43 [-0.14, 0.99]}\\\Gape[-2pt][6pt]{ 1.51 (91.8)}} & .136 & \makecell[c]{\Gape[6pt][-2pt]{ 1.00 [0.54, 1.46]}\\\Gape[-2pt][6pt]{ 4.31 (105.0)}} & < .001\\ \midrule
+logLik (\textit{df}) & -16555.1 (13) &  & -16289.6 (17) &  & -15350.3 (17) & \\
+RMSE & 5.07 &  & 4.79 &  & 4.05 & \\
+Conditional $R^2$ & 0.289 &  & 0.379 &  & 0.207 & \\
+Marginal $R^2$ & 0.007 &  & 0.053 &  & 0.048 & \\
 \bottomrule
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} Pt. = part, con. = condition, est. = estimate, CI = confidence interval.}
+\normalsize{\textit{Note.} Pt. = part, con. = condition, est. = estimate, CI = 95\% confidence interval.}
 \end{tablenotes}
@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s \textgreater{} 10.82, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp1-table}).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}(1, 24.8) = 13.09, \emph{p} = .001.
-Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4853.1) = 5.34, \emph{p} = .005, and in the N400 component, \emph{F}(2, 5030.2) = 11.18, \emph{p} \textless{} .001, while also being marginally significant in the P1 component, \emph{F}(2, 4590.9) = 2.40, \emph{p} = .091.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all \emph{F}s ≥ 10.89, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp1-table}).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, \emph{F}(1, 24.4) = 13.00, \emph{p} = .001.
+Crucially, the part × condition interaction was significant in the N170 component, \emph{F}(2, 4878.2) = 4.84, \emph{p} = .008, and in the N400 component, \emph{F}(2, 5120.9) = 10.91, \emph{p} \textless{} .001, while also showing a weak statistical trend in the P1 component, \emph{F}(2, 4605.1) = 2.30, \emph{p} = .100.
 To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
@@
 
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .393 (see Table \ref{tab:exp1-table} and Figure \ref{fig:exp1-plot}B).
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all \emph{p}s ≥ .400 (see Table \ref{tab:exp1-table} and Figure \ref{fig:exp1-plot}B).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs.~naive perception) had not yet taken place.
 On the other hand, the absence of reliable differences in this part can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in the other two parts cannot be accounted for by visual differences between the objects in the two conditions.
-Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self report would have made it possible for such visual differences to emerge as a confounding factor.
-If they did, however, one would expect to detect these differences even before any keywords were presented, which we have now seen was not the case.
+Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self-report would have made it possible for such visual differences to emerge as a confounding factor.
+If they did, however, one would expect to detect these differences even before any keywords were presented, which was apparently not the case.
 
@@
 In the insight part, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e.,~more negative), \emph{b} = -0.66 µV, \emph{p} = .006, and the amplitude of the N400 component was significantly reduced (i.e.,~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when the object was viewed naively without relevant semantic information.
-As in the pre-insight part, there were no reliable differences in the P1 component, \emph{p} = .550.
+When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e.,~more negative), \emph{b} = -0.64 µV, \emph{p} = .026, and the amplitude of the N400 component was significantly reduced (i.e.,~less negative), \emph{b} = 0.93 µV, \emph{p} \textless{} .001, compared to when the object was viewed naively without relevant semantic information.
+As in the pre-insight part, there were no reliable differences in the P1 component, \emph{b} = -0.18 µV, \emph{p} = .490.
 
@@
 
-In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part), to test whether the semantic information had any lasting effects on the processing of the objects.
-As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the effect in the N170 component did not reoccur, \emph{p} = .094.
-Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e.,~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.57 µV, \emph{p} = .023.
+In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part).
+This allowed us to test if the semantic information had any lasting effects on the processing of the objects.
+As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, \emph{b} = 1.00 µV, \emph{p} \textless{} .001, whereas the effect in the N170 component did not reoccur, \emph{b} = 0.43 µV, \emph{p} = .136.
+Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e.,~more positive) in response to objects for which semantically informed perception had taken place, \emph{b} = 0.55 µV, \emph{p} = .031.
 
@@
 
-Because of the novelty of our experimental paradigm and the findings of Experiment 1, we ran a replication study to assess the robustness of these effects in another samples of participants.
+Because of the novelty of our experimental paradigm---measuring the ERPs while rather than after participants received semantic information about unfamiliar objects---and because of the novelty of our findings, we ran a replication study with another sample of participants to assess the robustness of these effects.
 
@@
 \cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
-\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\textbf{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
 \midrule
-Part & 18.14 (2, 5151.1) & < .001 & 16.39 (2, 25.0) & < .001 & 70.58 (2, 25.2) & < .001\\
-Condition & 0.03 (1, 5272.5) & .853 & 1.23 (1, 5218.6) & .267 & 18.66 (1, 5207.5) & < .001\\
-Pt. × con. & 3.74 (2, 5151.2) & .024 & 1.34 (2, 4736.8) & .263 & 8.07 (2, 4637.6) & < .001\\
-\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & -0.17 [-0.72, 0.38] & .552 & -0.04 [-0.53, 0.45] & .864 & 0.02 [-0.44, 0.48] & .936\\
-Insight part & -0.49 [-1.04, 0.07] & .084 & -0.50 [-0.99, 0.00] & .050 & 1.31 [0.86, 1.77] & < .001\\
-Post-insight part & 0.56 [0.01, 1.11] & .048 & 0.04 [-0.45, 0.54] & .865 & 0.45 [-0.01, 0.91] & .055\\
+\,\, Part & 17.45 (2, 5267.1) & < .001 & 16.57 (2, 25.1) & < .001 & 70.12 (2, 25.2) & < .001\\
+\,\, Condition & 0.02 (1, 5276.9) & .900 & 0.98 (1, 5228.5) & .322 & 19.95 (1, 5242.5) & < .001\\
+\,\, Pt. × con. & 3.60 (2, 5267.1) & .027 & 1.25 (2, 4756.5) & .287 & 7.92 (2, 4714.9) & < .001\\
+\textbf{Informed - naive} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p}\\ \midrule
+\,\, Pre-insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.16 [-0.71, 0.40]}\\\Gape[-2pt][6pt]{-0.55 (5270.9)}} & .582 & \makecell[c]{\Gape[6pt][-2pt]{-0.03 [-0.53, 0.48]}\\\Gape[-2pt][6pt]{-0.10 (4772.1)}} & .920 & \makecell[c]{\Gape[6pt][-2pt]{0.04 [-0.43, 0.50]}\\\Gape[-2pt][6pt]{0.15 (5177.9)}} & .877\\
+\,\, Insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.48 [-1.03, 0.08]}\\\Gape[-2pt][6pt]{-1.67 (5270.7)}} & .094 & \makecell[c]{\Gape[6pt][-2pt]{-0.48 [-0.99, 0.03]}\\\Gape[-2pt][6pt]{-1.85 (5241.8)}} & .064 & \makecell[c]{\Gape[6pt][-2pt]{1.33 [0.87, 1.79]}\\\Gape[-2pt][6pt]{5.68 (4781.9)}} & < .001\\
+\,\, Post-insight part & \makecell[c]{\Gape[6pt][-2pt]{ 0.57 [0.01, 1.13]}\\\Gape[-2pt][6pt]{ 1.99 (5270.8)}} & .047 & \makecell[c]{\Gape[6pt][-2pt]{ 0.06 [-0.45, 0.57]}\\\Gape[-2pt][6pt]{ 0.23 (5035.9)}} & .818 & \makecell[c]{\Gape[6pt][-2pt]{0.47 [0.01, 0.93]}\\\Gape[-2pt][6pt]{1.98 (5067.3)}} & .047\\ \midrule
+logLik (\textit{df}) & -16707.1 (8) &  & -16174.3 (13) &  & -15648.0 (13) & \\
+RMSE & 5.62 &  & 5.03 &  & 4.58 & \\
+Conditional $R^2$ & 0.242 &  & 0.399 &  & 0.174 & \\
+Marginal $R^2$ & 0.005 &  & 0.037 &  & 0.068 & \\
 \bottomrule
@@
 
-As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s \textgreater{} 16.39, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp2-table}).
-Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}(1, 5207.5) = 18.66, \emph{p} \textless{} .001.
-The part × condition interaction was significant in the P1 component, \emph{F}(2, 5151.2) = 3.74, \emph{p} = .024, and in the N400 component, \emph{F}(2, 4637.6) = 8.07, \emph{p} \textless{} .001, but not in the N170 component, \emph{F}(2, 4736.8) = 1.34, \emph{p} = .263.
+As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all \emph{F}s ≥ 16.57, all \emph{p}s \textless{} .001 (see Table \ref{tab:exp2-table}).
+Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, \emph{F}(1, 5242.5) = 19.95, \emph{p} \textless{} .001.
+The part × condition interaction was significant in the P1 component, \emph{F}(2, 5267.1) = 3.60, \emph{p} = .027, and in the N400 component, \emph{F}(2, 4714.9) = 7.92, \emph{p} \textless{} .001, but not in the N170 component, \emph{F}(2, 4756.5) = 1.25, \emph{p} = .287.
 
@@
 
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all \emph{p}s \textgreater{} .552 (see Table \ref{tab:exp2-table} and Figure \ref{fig:exp2-plot}).
+As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all \emph{p}s ≥ .582 (see Table \ref{tab:exp2-table} and Figure \ref{fig:exp2-plot}).
 
@@
 
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs.~non-matching keywords) was associated with a (marginally) significant enhancement of the N170 component, \emph{b} = -0.50 µV, \emph{p} = .050, and a significant reduction of the N400 component, \emph{b} = 1.31 µV, \emph{p} \textless{} .001.
+As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs.~non-matching keywords) was associated with an enhancement of the N170 component, although this effect marginally failed to reach statistical significance, \emph{b} = -0.48 µV, \emph{p} = .064.
+The reduction of the N400 component during semantically informed perception remained significant, \emph{b} = 1.33 µV, \emph{p} \textless{} .001.
 
@@
 
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) led to significantly larger amplitudes in the P1 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.56 µV, \emph{p} = .048.
-Also, N400 amplitudes in response to these objects remained significantly reduced, \emph{b} = 0.45 µV, \emph{p} = .055.
+As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) again led to significantly reduced amplitudes in the N400 component in response to objects for which semantically informed perception had occurred, \emph{b} = 0.47 µV, \emph{p} = .047.
+Also, P1 amplitudes in response these objects were significantly enlarged, \emph{b} = 0.57 µV, \emph{p} = .047.
 
@@
 Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast (i.e.,~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al., 2020).
-This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
-They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2.
+This factor and its interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
+They were not included as by-participant random slopes because different participants took part in Experiments 1 and 2.
 Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit (Matuschek et al., 2017; Voeten, 2020).
+The resulting formulas for the models can be found in Appendix B.
 
@@
 \cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
-\textit{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
+\textbf{Fixed effects} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
 \midrule
-Part & 12.38 (2, 49.0) & < .001 & 29.90 (2, 50.0) & < .001 & 95.34 (2, 50.6) & < .001\\
-Condition & 0.35 (1, 10560.3) & .552 & 1.65 (1, 125.3) & .202 & 38.72 (1, 10518.8) & < .001\\
-Experiment & 0.35 (1, 48.2) & .555 & 2.38 (1, 48.1) & .129 & 4.75 (1, 48.4) & .034\\
-Pt. × con. & 4.02 (2, 9042.4) & .018 & 5.60 (2, 9877.5) & .004 & 15.73 (2, 10010.1) & < .001\\
-Pt. × exp. & 0.03 (2, 49.0) & .971 & 0.55 (2, 50.0) & .581 & 2.58 (2, 50.6) & .085\\
-Ins. × exp. & 0.62 (1, 10536.2) & .432 & 0.04 (1, 10332.1) & .838 & 0.03 (1, 10574.9) & .865\\
-Pt. × con. × exp. & 0.03 (2, 9042.9) & .972 & 0.62 (2, 9877.8) & .537 & 2.65 (2, 10010.4) & .070\\
-\textit{Informed $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
-Pre-insight part & -0.07 [-0.44, 0.30] & .699 & -0.10 [-0.44, 0.24] & .568 & -0.10 [-0.41, 0.20] & .507\\
-Insight part & -0.22 [-0.59, 0.15] & .248 & -0.56 [-0.90, -0.21] & .002 & 1.09 [0.79, 1.39] & < .001\\
-Post-insight part & 0.49 [0.12, 0.86] & .010 & 0.25 [-0.10, 0.59] & .158 & 0.72 [0.41, 1.02] & < .001\\
+\,\, Part & 12.34 (2, 49.1) & < .001 & 30.08 (2, 50.3) & < .001 & 94.61 (2, 50.6) & < .001\\
+\,\, Condition & 0.15 (1, 10573.1) & .699 & 1.16 (1, 45.2) & .287 & 41.38 (1, 10593.6) & < .001\\
+\,\, Experiment & 0.33 (1, 48.2) & .567 & 2.50 (1, 48.0) & .121 & 4.96 (1, 48.4) & .031\\
+\,\, Pt. × con. & 3.90 (2, 9004.9) & .020 & 5.26 (2, 9904.1) & .005 & 15.34 (2, 10091.0) & < .001\\
+\,\, Pt. × exp. & 0.04 (2, 49.1) & .966 & 0.58 (2, 50.3) & .565 & 2.55 (2, 50.6) & .088\\
+\,\, Ins. × exp. & 0.43 (1, 10573.1) & .514 & 0.06 (1, 45.2) & .805 & 0.07 (1, 10593.6) & .785\\
+\,\, Pt. × con. × exp. & 0.03 (2, 9004.9) & .968 & 0.58 (2, 9904.1) & .559 & 2.54 (2, 10091.0) & .079\\
+\textbf{Informed - naive} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p} & Est. [CI]; \textit{t} (\textit{df}) & \textit{p}\\ \midrule
+\,\, Pre-insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.10 [-0.47, 0.28]}\\\Gape[-2pt][6pt]{-0.50 (9534.6)}} & .616 & \makecell[c]{\Gape[6pt][-2pt]{-0.10 [-0.48, 0.29]}\\\Gape[-2pt][6pt]{-0.51 (208.1)}} & .611 & \makecell[c]{\Gape[6pt][-2pt]{-0.09 [-0.39, 0.22]}\\\Gape[-2pt][6pt]{-0.56 (10459.4)}} & .577\\
+\,\, Insight part & \makecell[c]{\Gape[6pt][-2pt]{-0.24 [-0.62, 0.13]}\\\Gape[-2pt][6pt]{-1.28 (10420.2)}} & .202 & \makecell[c]{\Gape[6pt][-2pt]{-0.57 [-0.96, -0.18]}\\\Gape[-2pt][6pt]{-2.90 (214.4)}} & .004 & \makecell[c]{\Gape[6pt][-2pt]{ 1.10 [0.80, 1.41]}\\\Gape[-2pt][6pt]{ 7.09 (10436.6)}} & < .001\\
+\,\, Post-insight part & \makecell[c]{\Gape[6pt][-2pt]{ 0.47 [0.09, 0.84]}\\\Gape[-2pt][6pt]{ 2.45 (9881.6)}} & .014 & \makecell[c]{\Gape[6pt][-2pt]{ 0.24 [-0.15, 0.63]}\\\Gape[-2pt][6pt]{ 1.22 (211.4)}} & .225 & \makecell[c]{\Gape[6pt][-2pt]{ 0.73 [0.42, 1.04]}\\\Gape[-2pt][6pt]{ 4.67 (10339.5)}} & < .001\\ \midrule
+logLik (\textit{df}) & -33272.6 (19) &  & -32474.6 (23) &  & -31045.5 (19) & \\
+RMSE & 5.32 &  & 4.91 &  & 4.32 & \\
+Conditional $R^2$ & 0.271 &  & 0.400 &  & 0.198 & \\
+Marginal $R^2$ & 0.008 &  & 0.06 &  & 0.07 & \\
 \bottomrule
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = confidence interval.}
+\normalsize{\textit{Note.} Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\% confidence interval.}
 \end{tablenotes}
@@
 
-As shown in Table \ref{tab:joint-table}, the main effect of the part of the experiment was significant in the P1, N170, and N400 component, all \emph{F}s \textgreater{} 12.38, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}(1, 10518.8) = 38.72, \emph{p} \textless{} .001.
-Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s \textgreater{} 4.02, all \emph{p}s \textless{} .018.
-While there was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.75, \emph{p} = .034, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
+As shown in Table \ref{tab:joint-table}, the main effect of part was significant in the P1, N170, and N400 component, all \emph{F}s ≥ 12.34, all \emph{p}s \textless{} .001, as was the main effect of condition in the N400, \emph{F}(1, 10593.6) = 41.38, \emph{p} \textless{} .001.
+Furthermore, the part × condition interaction was now observed reliably in all three components, all \emph{F}s ≥ 3.90, all \emph{p}s ≤ .020.
+There was a main effect of experiment in the N400, \emph{F}(1, 48.4) = 4.96, \emph{p} = .031, with more negative amplitudes in Experiment 1 as compared to Experiment 2, \emph{b} = -1.06.
+However, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
 
 Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \ref{tab:joint-table} and Figure \ref{fig:joint-plot}).
-This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s \textgreater{} .507, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.56 µV, \emph{p} = .002, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.09 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.72 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.49 µV, \emph{p} = .010.
+This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s ≥ .577, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.
 
@@
 Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages.
+Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of signalling messages.
 To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were preceded by matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for 49.6\% of objects presented with matching keywords as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -0.56 µV, \emph{p} .002.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords but on which participants failed to capitalize.
-Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.09 µV, \emph{p} \textless{} .001.
+Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
+Across both experiments, this was the case for 49.6\% of objects presented with matching keywords, as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses if participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001.
+Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
+Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.
 
@@
 To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
-For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, it was non-matching, thus keeping the perception of the object semantically naive.
+For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, the information was non-matching, thus keeping the perception of the object semantically naive.
 We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
 When the same objects were presented again without the semantic information, the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+We will discuss each of these effects in turn, starting with the latest (i.e., post-perceptual) effect and moving backward in time to the earlier (i.e., more perceptual) effects.
 
 The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
-Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) has lessened participants' demand for effortful semantic processing compared to the naive condition (Kutas \& Federmeier, 2011).
+Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) lessened participants' demand for effortful semantic processing in comparison to the naive condition (Kutas \& Federmeier, 2011).
 This replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves (e.g., Abdel Rahman \& Sommer, 2008; Supp et al., 2005) or difficult to integrate into the preceding context (e.g., Barrett \& Rugg, 1990; Ganis et al., 1996; Hirschfeld et al., 2011).
@@
 It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous findings using a similar experimental paradigm in the realm of face perception (Bentin \& Golland, 2002): Here, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
-This effect was absent when a visual control stimulus (a non-face object instead of the intact face) was shown between the two presentations of the scrambled face.
-In the realm of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects (Beaucousin et al., 2011).
+This interpretation is supported by previous findings with a similar experimental paradigm in the domain of face perception (Bentin \& Golland, 2002): In this study, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
+This effect was absent when a visual control stimulus (a non-face object) was shown instead of the intact face.
+In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects (Beaucousin et al., 2011).
 Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
@@
 The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
-Another one is our reliance on rare and highly specialized objects (see appendix).
-This was necessary to induce the experience of semantic insight in an adult population of undergraduate students but may not necessarily generalize to the way in which we learn about everyday objects.\footnote{Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize (Samaha et al., 2018).} One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
+Another one is our reliance on rare and highly specialized objects (see Appendix A).
+This was necessary to induce the experience of semantic insight in a population of undergraduate students but the results may not necessarily generalize to the way in which we learn about everyday objects.\footnote{Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize (Samaha et al., 2018).} One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
 Finally, the number participants (\emph{n} = 24 per experiment) and trials (\emph{k} \(\approx\) 30 per part in the insight condition and \emph{k} \(\approx\) 50 per part in the naive condition) can be considered small by today's standards (Baker et al., 2020).
-Our analysis may therefore not have been particularly sensitive, especially since linear mixed-effects regression models often have limited statistical power (see, e.g., the simulations by Matuschek et al., 2017).
-
-Nevertheless, this study provides preliminary evidence that whenever we acquire semantic information about a previously unfamiliar object, this information influences multiple stages of processing.
-These influences do not seem to be confined to later, post-perceptual stages---typically associated with semantic processing---but can also be observed at earlier stages---typically reflecting lower levels of visual perception and happening within 200 ms after the object is presented to us.
+Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances (see, e.g., the simulations by Matuschek et al., 2017).
+This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, \emph{p} = .026) failed to reach statistical significance in the replication experiment (\emph{p} = .064).
+To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).
+It should be noted, however, that the joint analysis of both data sets yielded a very robust N170 effect (\emph{p} = .004).
+This makes it less likely that the effect observed in Experiment 1 was due to a false positive and instead suggests that statistical power in Experiment 2 was insufficient to render the effect significant.
+Also note that the effect in the P1 component was statistically significant in both experiments individually, making an even stronger case for the susceptibility of early cortical processing to newly acquired knowledge about objects.
+
+Taken together, this study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the processing of the object.
+This influence is immediate in at least two different ways: First, it does not require extensive training and can instead be observed within the same trial in which the information has been presented (and/or one trial later).
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages---typically associated with semantic processing---but also at earlier stages---typically associated with visual perception itself and happening within less than a fifth of a second after the object is presented to us.
 
@@
 
-\setlength{\cslhangindent}{0.5in}
+\setlength{\parindent}{-0.5in}
 
@@
 
-\leavevmode\hypertarget{ref-goodale1992}{}%
-Goodale, M. A., \& Milner, A. D. (1992). Separate visual pathways for perception and action. \emph{Trends in Neurosciences}, \emph{15}(1), 20--25. \url{https://doi.org/10.1016/0166-2236(92)90344-8}
-
 \leavevmode\hypertarget{ref-gramfort2013}{}%
 Gramfort, A., Luessi, M., Larson, E., Engemann, D.
-A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& al., et.
+A., Strohmeier, D., Brodbeck, C., Goj, R., Jas, M., Brooks, T., Parkkonen, L., \& Hämäläinen, M.
 (2013).
@@
 
+\hypertarget{appendix-a-stimuli}{%
+\subsection*{Appendix A: Stimuli}\label{appendix-a-stimuli}}
+\addcontentsline{toc}{subsection}{Appendix A: Stimuli}
+
+\bigskip
+
 \setcounter{table}{0}
@@
 \begin{ThreePartTable}
+
+\footnotesize{
 
@@
 \toprule
- & \# & Matching keywords & Non-matching keywords\\
+Picture & ID & Matching keywords & Non-matching keywords\\
 \midrule
@@
 \toprule
- & \# & Matching keywords & Non-matching keywords\\
+Picture & ID & Matching keywords & Non-matching keywords\\
 \midrule
 \endhead
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/1.png} & 1 & elektrische Spannung prüfen & Makkaroni formen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/2.png} & 2 & Makkaroni formen & Kuh vom Zaun abhalten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/3.png} & 3 & Knochen sägen & Streckenmaß Sonnenlicht nutzen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/4.png} & 4 & Unkraut jäten & Uhr mit Wärme betreiben\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/5.png} & 5 & Mausefalle zuschnappen & Brillenglas zuschneiden\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/6.png} & 6 & Goldmünzen wiegen & Farbe vom Fenster abschleifen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/7.png} & 7 & Knie fixieren & Buchstaben tippen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/8.png} & 8 & Eierkarton pressen & Tabak zermahlen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/9.png} & 9 & Baum erklettern & Rotation Ladung erzeugen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/10.png} & 10 & Buchstaben tippen & Pferdehuf Halt geben\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/11.png} & 11 & Akkordeon spielen & Seil schneiden\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/12.png} & 12 & Körper trainieren & Buch offen halten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/13.png} & 13 & Farbe vom Fenster abschleifen & von Hand zentrifugieren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/14.png} & 14 & Außenbereich heizen & Rasierklinge schärfen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/15.png} & 15 & Pflanzenteile vergrößern & Katzenklo sich selbst reinigen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/16.png} & 16 & Krawatten aufhängen & Zeichnungen vermessen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/17.png} & 17 & Schallplatte abtasten & Ball katapultieren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/18.png} & 18 & Glas schneiden & Eier wiegen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/19.png} & 19 & Briketts pressen & Narkosemittel abgeben\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/20.png} & 20 & Orgelton erzeugen & Bandage rollen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/21.png} & 21 & Spannung erzeugen & Fußstütze reiten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/22.png} & 22 & Narkosemittel abgeben & Nüsse aufbrechen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/23.png} & 23 & Bandage rollen & Schnee rodeln\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/24.png} & 24 & Weinfass Loch einschlagen & Tier einfangen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/25.png} & 25 & Flaschenkorken einführen & Pferd im Moor laufen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/26.png} & 26 & Automat Eier ausbrüten & Windgeschwindigkeit messen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/27.png} & 27 & Korngarbe greifen & Treibhaus heizen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/28.png} & 28 & Brief wiegen & Korngarbe greifen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/29.png} & 29 & Löcher bohren & Sonnenlicht Intensität messen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/30.png} & 30 & Angelschnur kurbeln & Glaskörper musizieren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/31.png} & 31 & Kurven malen & Nussöl pressen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/32.png} & 32 & Radiofrequenz einstellen & Erektion helfen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/33.png} & 33 & Zäpfchen pressen & Unkraut jäten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/34.png} & 34 & Fass öffnen & Pflanzenteile vergrößern\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/35.png} & 35 & Bergbaustollen beleuchten & Knie fixieren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/36.png} & 36 & Kuh vom Zaun abhalten & Radiofrequenz einstellen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/37.png} & 37 & Saatgut gleichmäßig aussäen & Fass öffnen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/38.png} & 38 & Flaschen trocknen & Bleistift anspitzen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/39.png} & 39 & Uhr mit Wärme betreiben & Körper untersuchen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/40.png} & 40 & Tonpott trommeln & Piano stimmen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/41.png} & 41 & Sprengstoffexplosion auslösen & Fisch wiegen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/42.png} & 42 & Pferdehuf Halt geben & Zäpfchen pressen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/43.png} & 43 & Bleistift anspitzen & Angel Köder markieren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/44.png} & 44 & Nussöl pressen & Zeichen einbrennen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/45.png} & 45 & Rasierklinge schärfen & Kurven malen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/46.png} & 46 & heiße Platten anheben & Kleidung im Eimer waschen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/47.png} & 47 & Film aufspulen & Mund offen halten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/48.png} & 48 & Waffe entflammen & Uhrzeit anzeigen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/49.png} & 49 & Mikroskop-Proben schneiden & heiße Platten anheben\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/50.png} & 50 & Glaskörper musizieren & Kork flach pressen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/51.png} & 51 & Dampf zerstäuben & Buch binden\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/52.png} & 52 & Mandeln operieren & Film aufspulen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/53.png} & 53 & Toastbrot rösten & Autobatterie Spannung testen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/54.png} & 54 & Fußstütze reiten & Stromstärke messen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/55.png} & 55 & Türgelenk Feuer überstehen & Botschaft telegrafieren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/56.png} & 56 & Schnee rodeln & Dampf zerstäuben\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/57.png} & 57 & Nüsse aufbrechen & Ziegelsteine formen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/58.png} & 58 & Radiergummi mit Strom betreiben & Münzen aufbewahren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/59.png} & 59 & Treibhaus heizen & Messer schleifen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/60.png} & 60 & Botschaft telegrafieren & Toastbrot rösten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/61.png} & 61 & Angel Köder markieren & Baum erklettern\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/62.png} & 62 & Katzenklo sich selbst reinigen & Tankfüllstand messen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/63.png} & 63 & Körper untersuchen & Schuhe auf Eis laufen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/64.png} & 64 & Brillenglas zuschneiden & Saatgut gleichmäßig aussäen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/65.png} & 65 & Draht wickeln & Bergbaustollen beleuchten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/66.png} & 66 & Buch offen halten & Sprengstoffexplosion auslösen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/67.png} & 67 & Feldanbau häckseln & Draht wickeln\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/68.png} & 68 & Schnurlot absenken & Korken formen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/69.png} & 69 & Sternenbilder vermessen & Schnurlot absenken\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/70.png} & 70 & Nachricht morsen & Feldanbau häckseln\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/71.png} & 71 & Musikgerät stampfen & Goldmünzen wiegen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/72.png} & 72 & Schuhe auf Eis laufen & Geschwindigkeit ermitteln\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/73.png} & 73 & Geschwindigkeit ermitteln & Mausefalle zuschnappen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/74.png} & 74 & Zeichen einbrennen & Luftdruck messen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/75.png} & 75 & Tabak zermahlen & Flaschen trocknen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/76.png} & 76 & Stromstärke messen & Mandeln operieren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/77.png} & 77 & Tier einfangen & Maiskolben entkörnen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/78.png} & 78 & Messer schleifen & Schritte vergrößern\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/79.png} & 79 & Leierkasten klingen & Fass anheben\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/80.png} & 80 & Buch binden & Löcher bohren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/81.png} & 81 & Kork flach pressen & Elektroschock spielen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/82.png} & 82 & Tabletten zerteilen & Blumentopf sich selbst wässern\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/83.png} & 83 & Fass anheben & Mikroskop-Proben schneiden\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/84.png} & 84 & Pferd im Moor laufen & Luft abpumpen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/85.png} & 85 & altes Ritual hacken & Spannung erzeugen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/86.png} & 86 & Kleidung im Eimer waschen & Türgelenk Feuer überstehen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/87.png} & 87 & Maiskolben entkörnen & Brief wiegen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/88.png} & 88 & Ball katapultieren & Radiergummi mit Strom betreiben\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/89.png} & 89 & Zeichnungen vermessen & Brenner löten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/90.png} & 90 & Elektroschock spielen & Weinfass Loch einschlagen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/91.png} & 91 & Lieferungen abzählen & Außenbereich heizen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/92.png} & 92 & Rotation Ladung erzeugen & Musikgerät stampfen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/93.png} & 93 & Herz durch Maschine ersetzen & Kerzen löschen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/94.png} & 94 & Seil schneiden & Akkordeon spielen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/95.png} & 95 & Fisch wiegen & Herz durch Maschine ersetzen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/96.png} & 96 & Kerzen löschen & Körper trainieren\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/97.png} & 97 & Korken formen & Sternenbilder vermessen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/98.png} & 98 & Erektion helfen & Waffe werfen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/99.png} & 99 & Streckenmaß Sonnenlicht nutzen & Kartoffeln stampfen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/100.png} & 100 & Luftdruck messen & Knochen sägen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/101.png} & 101 & Piano stimmen & Eierkarton pressen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/102.png} & 102 & von Hand zentrifugieren & Lieferungen abzählen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/103.png} & 103 & Kartoffeln stampfen & Nachricht morsen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/104.png} & 104 & Waffe werfen & elektrische Spannung prüfen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/105.png} & 105 & Tankfüllstand messen & Tonpott trommeln\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/106.png} & 106 & Uhrzeit anzeigen & altes Ritual hacken\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/107.png} & 107 & Windgeschwindigkeit messen & Waffe entflammen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/108.png} & 108 & Schlüsselloch stanzen & Automat Eier ausbrüten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/109.png} & 109 & Ziegelsteine formen & Schallplatte abtasten\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/110.png} & 110 & Becher Schall auffangen & Schlüsselloch stanzen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/111.png} & 111 & Luft abpumpen & Briketts pressen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/112.png} & 112 & Mund offen halten & Orgelton erzeugen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/113.png} & 113 & Autobatterie Spannung testen & Becher Schall auffangen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/114.png} & 114 & Sonnenlicht Intensität messen & Krawatten aufhängen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/115.png} & 115 & Kutschrad anschließen & Angelschnur kurbeln\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/116.png} & 116 & Eier wiegen & Leierkasten klingen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/117.png} & 117 & Blumentopf sich selbst wässern & Glas schneiden\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/118.png} & 118 & Schritte vergrößern & Tabletten zerteilen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/119.png} & 119 & Münzen aufbewahren & Kutschrad anschließen\\
-\includegraphics[valign=c, scale=0.19]{../materials/unfamiliar/120.png} & 120 & Brenner löten & Flaschenkorken einführen einführen\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/1.png} & 1 & \makecell[l]{elektrische Spannung, prüfen\\{[electric current, measuring]}} & \makecell[l]{Makkaroni, formen\\{[macaroni, forming]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/2.png} & 2 & \makecell[l]{Makkaroni, formen\\{[macaroni, forming]}} & \makecell[l]{Kuh, vom Zaun abhalten\\{[cow, keeping away from the fence]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/3.png} & 3 & \makecell[l]{Knochen, sägen\\{[bones, sawing]}} & \makecell[l]{Streckenmaß, Sonnenlicht nutzen\\{[distance measure, using sunrays]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/4.png} & 4 & \makecell[l]{Unkraut, jäten\\{[weed, removing]}} & \makecell[l]{Uhr, mit Wärme betreiben\\{[clock, operating with heat]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/5.png} & 5 & \makecell[l]{Mausefalle, zuschnappen\\{[mousetrap, snap-shutting]}} & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lense, cutting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/6.png} & 6 & \makecell[l]{Goldmünzen, wiegen\\{[gold coin, weighing]}} & \makecell[l]{Farbe, vom Fenster abschleifen\\{[paint, scraping off the window]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/7.png} & 7 & \makecell[l]{Knie, fixieren\\{[knee, fixating]}} & \makecell[l]{Buchstaben, tippen\\{[letter, typing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/8.png} & 8 & \makecell[l]{Eierkarton, pressen\\{[egg carton, pressing]}} & \makecell[l]{Tabak, zermahlen\\{[tobacco, pulverize]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/9.png} & 9 & \makecell[l]{Baum, erklettern\\{[tree, climbing]}} & \makecell[l]{Rotation, Ladung erzeugen\\{[rotation, creating electric charge]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/10.png} & 10 & \makecell[l]{Buchstaben, tippen\\{[letter, typing]}} & \makecell[l]{Pferdehuf, Halt geben\\{[horse hoof, giving grip]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/11.png} & 11 & \makecell[l]{Akkordeon, spielen\\{[accordion, playing]}} & \makecell[l]{Seil, schneiden\\{[rope, cutting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/12.png} & 12 & \makecell[l]{Körper, trainieren\\{[body, training]}} & \makecell[l]{Buch, offen halten\\{[book, binding]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/13.png} & 13 & \makecell[l]{Farbe, vom Fenster abschleifen\\{[paint, scraping off the window]}} & \makecell[l]{von Hand, zentrifugieren\\{[by hand, centrifugating]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/14.png} & 14 & \makecell[l]{Außenbereich, heizen\\{[outdoor area, heating]}} & \makecell[l]{Rasierklinge, schärfen\\{[razor blade, sharpening]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/15.png} & 15 & \makecell[l]{Pflanzenteile, vergrößern\\{[plant parts, magnifying]}} & \makecell[l]{Katzenklo, sich selbst reinigen\\{[litter box, self-cleaning]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/16.png} & 16 & \makecell[l]{Krawatten, aufhängen\\{[necktie, hanging up]}} & \makecell[l]{Zeichnungen, vermessen\\{[drawings, measuring]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/17.png} & 17 & \makecell[l]{Schallplatte, abtasten\\{[vinyl record, reading]}} & \makecell[l]{Ball, katapultieren\\{[ball, catapulting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/18.png} & 18 & \makecell[l]{Glas, schneiden\\{[glass, cutting]}} & \makecell[l]{Eier, wiegen\\{[eggs, weighing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/19.png} & 19 & \makecell[l]{Briketts, pressen\\{[briquette, pressing]}} & \makecell[l]{Narkosemittel, abgeben\\{[anesthetic, administering]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/20.png} & 20 & \makecell[l]{Orgelton, erzeugen\\{[organ sound, making]}} & \makecell[l]{Bandage, rollen\\{[bandage, rolling]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/21.png} & 21 & \makecell[l]{Spannung, erzeugen\\{[electric current, making]}} & \makecell[l]{Fußstütze, reiten\\{[footrest, horseback riding]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/22.png} & 22 & \makecell[l]{Narkosemittel, abgeben\\{[anesthetic, administering]}} & \makecell[l]{Nüsse, aufbrechen\\{[nuts, cracking]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/23.png} & 23 & \makecell[l]{Bandage, rollen\\{[bandage, rolling]}} & \makecell[l]{Schnee, rodeln\\{[snow, sleighing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/24.png} & 24 & \makecell[l]{Weinfass, Loch einschlagen\\{[wine barrel, smashing a hole]}} & \makecell[l]{Tier, einfangen\\{[animal, trapping]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/25.png} & 25 & \makecell[l]{Flaschenkorken, einführen\\{[bottle cork, inserting]}} & \makecell[l]{Pferd, im Moor laufen\\{[horse, walking in the moor]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/26.png} & 26 & \makecell[l]{Automat, Eier ausbrüten\\{[machine, incubating eggs]}} & \makecell[l]{Windgeschwindigkeit, messen\\{[wind speed, measuring]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/27.png} & 27 & \makecell[l]{Korngarbe, greifen\\{[sheaf, grabbing]}} & \makecell[l]{Treibhaus, heizen\\{[glass house, heating]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/28.png} & 28 & \makecell[l]{Brief, wiegen\\{[letter, weighing]}} & \makecell[l]{Korngarbe, greifen\\{[sheaf, grabbing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/29.png} & 29 & \makecell[l]{Löcher, bohren\\{[hole, drilling]}} & \makecell[l]{Sonnenlicht, Intensität messen\\{[sunlight, measure intensity]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/30.png} & 30 & \makecell[l]{Angelschnur, kurbeln\\{[fishing line, winding]}} & \makecell[l]{Glaskörper, musizieren\\{[glass body, making music]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/31.png} & 31 & \makecell[l]{Kurven, malen\\{[curve, drawing]}} & \makecell[l]{Nussöl, pressen\\{[nut oil, pressing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/32.png} & 32 & \makecell[l]{Radiofrequenz, einstellen\\{[radio frequency, tuning]}} & \makecell[l]{Erektion, helfen\\{[erection, helping]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/33.png} & 33 & \makecell[l]{Zäpfchen, pressen\\{[suppository, pressing]}} & \makecell[l]{Unkraut, jäten\\{[weed, removing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/34.png} & 34 & \makecell[l]{Fass, öffnen\\{[barrel, opening]}} & \makecell[l]{Pflanzenteile, vergrößern\\{[plant parts, magnifying]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/35.png} & 35 & \makecell[l]{Bergbaustollen, beleuchten\\{[mining tunnel, lightening]}} & \makecell[l]{Knie, fixieren\\{[knee, fixating]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/36.png} & 36 & \makecell[l]{Kuh, vom Zaun abhalten\\{[cow, keeping away from the fence]}} & \makecell[l]{Radiofrequenz, einstellen\\{[radio frequency, tuning]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/37.png} & 37 & \makecell[l]{Saatgut, gleichmäßig aussäen\\{[seeds, sowing evenly]}} & \makecell[l]{Fass, öffnen\\{[barrel, opening]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/38.png} & 38 & \makecell[l]{Flaschen, trocknen\\{[bottles, drying]}} & \makecell[l]{Bleistift, anspitzen\\{[pencil, sharpening]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/39.png} & 39 & \makecell[l]{Uhr, mit Wärme betreiben\\{[clock, operating with heat]}} & \makecell[l]{Körper, untersuchen\\{[body, training]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/40.png} & 40 & \makecell[l]{Tonpott, trommeln\\{[clay pot, drumming]}} & \makecell[l]{Piano, stimmen\\{[piano, tuning]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/41.png} & 41 & \makecell[l]{Sprengstoffexplosion, auslösen\\{[dynamite explosion, triggering]}} & \makecell[l]{Fisch, wiegen\\{[fish, weighing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/42.png} & 42 & \makecell[l]{Pferdehuf, Halt geben\\{[horse hoof, giving grip]}} & \makecell[l]{Zäpfchen, pressen\\{[suppository, pressing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/43.png} & 43 & \makecell[l]{Bleistift, anspitzen\\{[pencil, sharpening]}} & \makecell[l]{Angel, Köder markieren\\{[fishing rod, marking bait]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/44.png} & 44 & \makecell[l]{Nussöl, pressen\\{[nut oil, pressing]}} & \makecell[l]{Zeichen, einbrennen\\{[marks, burning in]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/45.png} & 45 & \makecell[l]{Rasierklinge, schärfen\\{[razor blade, sharpening]}} & \makecell[l]{Kurven, malen\\{[curve, drawing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/46.png} & 46 & \makecell[l]{heiße Platten, anheben\\{[hot plates, lifting]}} & \makecell[l]{Kleidung, im Eimer waschen\\{[clothes, washing in a bucket]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/47.png} & 47 & \makecell[l]{Film, aufspulen\\{[film roll, winding]}} & \makecell[l]{Mund, offen halten\\{[mouth, keeping open]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/48.png} & 48 & \makecell[l]{Waffe, entflammen\\{[weapon, inflaming]}} & \makecell[l]{Uhrzeit, anzeigen\\{[time, displaying]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/49.png} & 49 & \makecell[l]{Mikroskop-Proben, schneiden\\{[microscopic samples, slicing]}} & \makecell[l]{heiße Platten, anheben\\{[hot plates, lifting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/50.png} & 50 & \makecell[l]{Glaskörper, musizieren\\{[glass body, making music]}} & \makecell[l]{Kork, flach pressen\\{[cork, pressing flat]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/51.png} & 51 & \makecell[l]{Dampf, zerstäuben\\{[steam, spraying]}} & \makecell[l]{Buch, binden\\{[book, opening]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/52.png} & 52 & \makecell[l]{Mandeln, operieren\\{[kidneys, operating]}} & \makecell[l]{Film, aufspulen\\{[film roll, winding]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/53.png} & 53 & \makecell[l]{Toastbrot, rösten\\{[toast, roasting]}} & \makecell[l]{Autobatterie, Spannung testen\\{[car battery, measuring voltage]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/54.png} & 54 & \makecell[l]{Fußstütze, reiten\\{[footrest, horseback riding]}} & \makecell[l]{Stromstärke, messen\\{[current, measuring]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/55.png} & 55 & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, survining fires]}} & \makecell[l]{Botschaft, telegrafieren\\{[message, telegraphing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/56.png} & 56 & \makecell[l]{Schnee, rodeln\\{[snow, sleighing]}} & \makecell[l]{Dampf, zerstäuben\\{[steam, spraying]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/57.png} & 57 & \makecell[l]{Nüsse, aufbrechen\\{[nuts, cracking]}} & \makecell[l]{Ziegelsteine, formen\\{[bricks, forming]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/58.png} & 58 & \makecell[l]{Radiergummi, mit Strom betreiben\\{[eraser, operating with electricity]}} & \makecell[l]{Münzen, aufbewahren\\{[coins, storing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/59.png} & 59 & \makecell[l]{Treibhaus, heizen\\{[glass house, heating]}} & \makecell[l]{Messer, schleifen\\{[knife, sharpening]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/60.png} & 60 & \makecell[l]{Botschaft, telegrafieren\\{[message, telegraphing]}} & \makecell[l]{Toastbrot, rösten\\{[toast, roasting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/61.png} & 61 & \makecell[l]{Angel, Köder markieren\\{[fishing rod, marking bait]}} & \makecell[l]{Baum, erklettern\\{[tree, climbing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/62.png} & 62 & \makecell[l]{Katzenklo, sich selbst reinigen\\{[litter box, self-cleaning]}} & \makecell[l]{Tankfüllstand, messen\\{[fuel tank level, gauging]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/63.png} & 63 & \makecell[l]{Körper, untersuchen\\{[body, examining]}} & \makecell[l]{Schuhe, auf Eis laufen\\{[shoes, walking on ice]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/64.png} & 64 & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lense, cutting]}} & \makecell[l]{Saatgut, gleichmäßig aussäen\\{[seeds, sowing evenly]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/65.png} & 65 & \makecell[l]{Draht, wickeln\\{[wire, winding]}} & \makecell[l]{Bergbaustollen, beleuchten\\{[mining tunnel, lightening]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/66.png} & 66 & \makecell[l]{Buch, offen halten\\{[book, opening]}} & \makecell[l]{Sprengstoffexplosion, auslösen\\{[dynamite explosion, triggering]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/67.png} & 67 & \makecell[l]{Feldanbau, häckseln\\{[harvest, chopping]}} & \makecell[l]{Draht, wickeln\\{[wire, winding]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/68.png} & 68 & \makecell[l]{Schnurlot, absenken\\{[plummet, letting down]}} & \makecell[l]{Korken, formen\\{[bottle cork, forming]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/69.png} & 69 & \makecell[l]{Sternenbilder, vermessen\\{[stellar constellation, measuring]}} & \makecell[l]{Schnurlot, absenken\\{[plummet, letting down]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/70.png} & 70 & \makecell[l]{Nachricht, morsen\\{[message, signalling]}} & \makecell[l]{Feldanbau, häckseln\\{[harvest, chopping]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/71.png} & 71 & \makecell[l]{Musikgerät, stampfen\\{[musical instrument, stamping]}} & \makecell[l]{Goldmünzen, wiegen\\{[gold coin, weighing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/72.png} & 72 & \makecell[l]{Schuhe, auf Eis laufen\\{[shoes, walking on ice]}} & \makecell[l]{Geschwindigkeit, ermitteln\\{[speed, determining]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/73.png} & 73 & \makecell[l]{Geschwindigkeit, ermitteln\\{[speed, determining]}} & \makecell[l]{Mausefalle, zuschnappen\\{[mousetrap, snap-shutting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/74.png} & 74 & \makecell[l]{Zeichen, einbrennen\\{[marks, burning in]}} & \makecell[l]{Luftdruck, messen\\{[air pressure, measuring]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/75.png} & 75 & \makecell[l]{Tabak, zermahlen\\{[tobacco, pulverize]}} & \makecell[l]{Flaschen, trocknen\\{[bottles, drying]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/76.png} & 76 & \makecell[l]{Stromstärke, messen\\{[current, measuring]}} & \makecell[l]{Mandeln, operieren\\{[kidneys, operating]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/77.png} & 77 & \makecell[l]{Tier, einfangen\\{[animal, trapping]}} & \makecell[l]{Maiskolben, entkörnen\\{[corncob, removing grains]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/78.png} & 78 & \makecell[l]{Messer, schleifen\\{[knife, sharpening]}} & \makecell[l]{Schritte, vergrößern\\{[steps, extending]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/79.png} & 79 & \makecell[l]{Leierkasten, klingen\\{[barrel organ, making sounds]}} & \makecell[l]{Fass, anheben\\{[barrel, lifting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/80.png} & 80 & \makecell[l]{Buch, binden\\{[book, binding]}} & \makecell[l]{Löcher, bohren\\{[hole, drilling]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/81.png} & 81 & \makecell[l]{Kork, flach pressen\\{[cork, pressing flat]}} & \makecell[l]{Elektroschock, spielen\\{[electric shock, playing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/82.png} & 82 & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}} & \makecell[l]{Blumentopf, sich selbst wässern\\{[flower pot, self-watering]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/83.png} & 83 & \makecell[l]{Fass, anheben\\{[barrel, lifting]}} & \makecell[l]{Mikroskop-Proben, schneiden\\{[microscopic samples, slicing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/84.png} & 84 & \makecell[l]{Pferd, im Moor laufen\\{[horse, walking in the moor]}} & \makecell[l]{Luft, abpumpen\\{[air, pumping out]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/85.png} & 85 & \makecell[l]{altes Ritual, hacken\\{[ancient ritual, chopping]}} & \makecell[l]{Spannung, erzeugen\\{[electric current, making]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/86.png} & 86 & \makecell[l]{Kleidung, im Eimer waschen\\{[clothes, washing in a bucket]}} & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, survining fires]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/87.png} & 87 & \makecell[l]{Maiskolben, entkörnen\\{[corncob, removing grains]}} & \makecell[l]{Brief, wiegen\\{[letter, weighing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/88.png} & 88 & \makecell[l]{Ball, katapultieren\\{[ball, catapulting]}} & \makecell[l]{Radiergummi, mit Strom betreiben\\{[eraser, operating with electricity]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/89.png} & 89 & \makecell[l]{Zeichnungen, vermessen\\{[drawings, measuring]}} & \makecell[l]{Brenner, löten\\{[burner, soldering]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/90.png} & 90 & \makecell[l]{Elektroschock, spielen\\{[electric shock, playing]}} & \makecell[l]{Weinfass, Loch einschlagen\\{[wine barrel, smashing a hole]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/91.png} & 91 & \makecell[l]{Lieferungen, abzählen\\{[deliveries, counting]}} & \makecell[l]{Außenbereich, heizen\\{[outdoor area, heating]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/92.png} & 92 & \makecell[l]{Rotation, Ladung erzeugen\\{[rotation, creating electric charge]}} & \makecell[l]{Musikgerät, stampfen\\{[musical instrument, stamping]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/93.png} & 93 & \makecell[l]{Herz, durch Maschine ersetzen\\{[heart, replacing with machine]}} & \makecell[l]{Kerzen, löschen\\{[candles, extinguishing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/94.png} & 94 & \makecell[l]{Seil, schneiden\\{[rope, cutting]}} & \makecell[l]{Akkordeon, spielen\\{[accordion, playing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/95.png} & 95 & \makecell[l]{Fisch, wiegen\\{[fish, weighing]}} & \makecell[l]{Herz, durch Maschine ersetzen\\{[heart, replacing with machine]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/96.png} & 96 & \makecell[l]{Kerzen, löschen\\{[candles, extinguishing]}} & \makecell[l]{Körper, trainieren\\{[body, examining]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/97.png} & 97 & \makecell[l]{Korken, formen\\{[bottle cork, forming]}} & \makecell[l]{Sternenbilder, vermessen\\{[stellar constellation, measuring]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/98.png} & 98 & \makecell[l]{Erektion, helfen\\{[erection, helping]}} & \makecell[l]{Waffe, werfen\\{[weapn, throwing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/99.png} & 99 & \makecell[l]{Streckenmaß, Sonnenlicht nutzen\\{[distance measure, using sunrays]}} & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/100.png} & 100 & \makecell[l]{Luftdruck, messen\\{[air pressure, measuring]}} & \makecell[l]{Knochen, sägen\\{[bones, sawing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/101.png} & 101 & \makecell[l]{Piano, stimmen\\{[piano, tuning]}} & \makecell[l]{Eierkarton, pressen\\{[egg carton, pressing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/102.png} & 102 & \makecell[l]{von Hand, zentrifugieren\\{[by hand, centrifugating]}} & \makecell[l]{Lieferungen, abzählen\\{[deliveries, counting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/103.png} & 103 & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}} & \makecell[l]{Nachricht, morsen\\{[message, signalling]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/104.png} & 104 & \makecell[l]{Waffe, werfen\\{[weapn, throwing]}} & \makecell[l]{elektrische Spannung, prüfen\\{[electric current, measuring]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/105.png} & 105 & \makecell[l]{Tankfüllstand, messen\\{[fuel tank level, gauging]}} & \makecell[l]{Tonpott, trommeln\\{[clay pot, drumming]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/106.png} & 106 & \makecell[l]{Uhrzeit, anzeigen\\{[time, displaying]}} & \makecell[l]{altes Ritual, hacken\\{[ancient ritual, chopping]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/107.png} & 107 & \makecell[l]{Windgeschwindigkeit, messen\\{[wind speed, measuring]}} & \makecell[l]{Waffe, entflammen\\{[weapon, inflaming]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/108.png} & 108 & \makecell[l]{Schlüsselloch, stanzen\\{[keyhole, punching]}} & \makecell[l]{Automat, Eier ausbrüten\\{[machine, incubating eggs]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/109.png} & 109 & \makecell[l]{Ziegelsteine, formen\\{[bricks, forming]}} & \makecell[l]{Schallplatte, abtasten\\{[vinyl record, reading]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/110.png} & 110 & \makecell[l]{Becher, Schall auffangen\\{[drinking cup, picking up sound]}} & \makecell[l]{Schlüsselloch, stanzen\\{[keyhole, punching]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/111.png} & 111 & \makecell[l]{Luft, abpumpen\\{[air, pumping out]}} & \makecell[l]{Briketts, pressen\\{[briquette, pressing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/112.png} & 112 & \makecell[l]{Mund, offen halten\\{[mouth, keeping open]}} & \makecell[l]{Orgelton, erzeugen\\{[organ sound, making]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/113.png} & 113 & \makecell[l]{Autobatterie, Spannung testen\\{[car battery, measuring voltage]}} & \makecell[l]{Becher, Schall auffangen\\{[drinking cup, picking up sound]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/114.png} & 114 & \makecell[l]{Sonnenlicht, Intensität messen\\{[sunlight, measure intensity]}} & \makecell[l]{Krawatten, aufhängen\\{[necktie, hanging up]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/115.png} & 115 & \makecell[l]{Kutschrad, anschließen\\{[carriage wheel, locking]}} & \makecell[l]{Angelschnur, kurbeln\\{[fishing line, winding]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/116.png} & 116 & \makecell[l]{Eier, wiegen\\{[eggs, weighing]}} & \makecell[l]{Leierkasten, klingen\\{[barrel organ, making sounds]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/117.png} & 117 & \makecell[l]{Blumentopf, sich selbst wässern\\{[flower pot, self-watering]}} & \makecell[l]{Glas, schneiden\\{[glass, cutting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/118.png} & 118 & \makecell[l]{Schritte, vergrößern\\{[steps, extending]}} & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/119.png} & 119 & \makecell[l]{Münzen, aufbewahren\\{[coins, storing]}} & \makecell[l]{Kutschrad, anschließen\\{[carriage wheel, locking]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/120.png} & 120 & \makecell[l]{Brenner, löten\\{[burner, soldering]}} & \makecell[l]{Flaschenkorken einführen, einführen\\{[bottle cork, inserting]}}\\
 \bottomrule
@@
 
+}
+
 \end{ThreePartTable}
 \end{center}
+
+\newpage
+
+\hypertarget{appendix-b-linear-mixed-effects-models}{%
+\subsection*{Appendix B: Linear Mixed-Effects Models}\label{appendix-b-linear-mixed-effects-models}}
+\addcontentsline{toc}{subsection}{Appendix B: Linear Mixed-Effects Models}
+
+\noindent Linear mixed-effects models after model selection for Experiment 1:
+
+\footnotesize
+
+\begin{verbatim}
+## P1 ~ 1 + part + condition + part:condition + (1 + part | participant)
+## N170 ~ 1 + part + condition + part:condition + (1 + part + condition | participant)
+## N400 ~ 1 + part + condition + part:condition + (1 + part + condition | participant)
+\end{verbatim}
+
+\normalsize
+
+\noindent Linear mixed-effects models after model selection for Experiment 2:
+
+\footnotesize
+
+\begin{verbatim}
+## P1 ~ 1 + part + condition + part:condition + (1 | participant)
+## N170 ~ 1 + part + condition + part:condition + (1 + part | participant)
+## N400 ~ 1 + part + condition + part:condition + (1 + part | participant)
+\end{verbatim}
+
+\normalsize
+
+\noindent Linear mixed-effects models after model selection for Experiments 1 and 2 combined:
+
+\footnotesize
+
+\begin{verbatim}
+## P1 ~ 1 + part + condition + part:condition + experiment + part:experiment + 
+##     condition:experiment + part:condition:experiment + (1 + part | participant)
+## N170 ~ 1 + part + condition + part:condition + experiment + part:experiment + 
+##     condition:experiment + part:condition:experiment + (1 + part + condition | 
+##     participant)
+## N400 ~ 1 + part + condition + part:condition + experiment + part:experiment + 
+##     condition:experiment + part:condition:experiment + (1 + part | participant)
+\end{verbatim}
+
+\normalsize
 
@@
 
+\clearpage
+
+\mbox{}\thispagestyle{empty}\clearpage
+
 \end{document}

### 2021-01-26 analysis/manuscript.Rmd
master thesis submission

@@
 We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resolution of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
-It allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
+This allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
 
@@
 When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha-band power was higher for meaning-trained images than for perceptually-trained images.
-As before, these effects of perceiving objects in a semantically informed way seem to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
+As before, this effect of perceiving objects in a semantically informed way seems to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
 This alternative approach further corroborates an early influence of semantic information on the visual perception of objects.
@@
 As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive.
+The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to hamper such an understanding and keep the perception of the object semantically naive.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
@@
 
-# # Compute the models for Experiment 1
-# map(
-#   comps$name,
-#   compute_models,
-#   formula = formula_exp12,
-#   data = data_exp1,
-#   control = control,
-#   specs = specs_exp12
-# ) %>%
-#   set_names(comps$name) %T>%
-#   saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
+# Compute the models for Experiment 1
+map(
+  comps$name,
+  compute_models,
+  formula = formula_exp12,
+  data = data_exp1,
+  control = control,
+  specs = specs_exp12
+) %>%
+  set_names(comps$name) %T>%
+  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
 ```
@@
 Second, they can account simultaneously for the non-independence of data points coming from the same participant and/or from the same item.
-In contrast, the neglect of the item as a random variable in by-participant ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
+In contrast, the neglect of the item as a random variable in by-participant ANOVAs can lead to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
 Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
@@
 We then performed a model selection algorithm as proposed by @matuschek2017 in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model [determined by *p* \> .20\; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
+Only if the parsimonious model explained the data equally well as the complex model [determined by *p* ≥ .20\; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
 All models were computed in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4].
@@
 
-# # Apply the function to compute the joint models for Experiments 1 and 2
-# map(
-#   comps$name,
-#   compute_models,
-#   formula = form_joint,
-#   data = data_joint_subs,
-#   control = control,
-#   specs = specs_exp12
-# ) %>%
-#   set_names(comps$name) %T>%
-#   saveRDS("analysis/export/joint-models.RDS") -> models_joint
+# Apply the function to compute the joint models for Experiments 1 and 2
+map(
+  comps$name,
+  compute_models,
+  formula = form_joint,
+  data = data_joint_subs,
+  control = control,
+  specs = specs_exp12
+) %>%
+  set_names(comps$name) %T>%
+  saveRDS("analysis/export/joint-models.RDS") -> models_joint
 ```
@@
 The violins and box plots show the distributions of the by-participant averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\\% confidence interval.
+The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modeling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
 Ampl.
-= amplitude, 95\\% CI = 95\\% confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
+= amplitude, 95\% CI = 95\% confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
 **\textit{p} \textless{} .01.
@@
 Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of signalling messages.
+Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of signaling messages.
 To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
@@
 
-# Read the epochs that Python has written
-epochs_exp3 <- py$mne$read_epochs("analysis/export/exp3-epo.fif")
-
-# # Preprocess the EEG for Experiment 3 in Python
-# map2(
-#   .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
-#   .y = behav_exp3,
-#   ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-# ) %>%
-#   # Concatenate epochs of all participants
-#   py$mne$epochs$concatenate_epochs() -> epochs_exp3
-# 
-# # Backup epochs to the export folder
-# epochs_exp3$save("analysis/export/exp3-epo.fif")
+# Preprocess the EEG for Experiment 3 in Python
+map2(
+  .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
+  .y = behav_exp3,
+  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
+) %>%
+  # Concatenate epochs of all participants
+  py$mne$epochs$concatenate_epochs() -> epochs_exp3
+
+# Backup epochs to the export folder
+epochs_exp3$save("analysis/export/exp3-epo.fif")
 
@@
 
-```{python exp1-tfr, eval=FALSE}
-# TFR
-import numpy as np
-import matplotlib.pyplot as plt
-
-# chans = mne.pick_channels(epochs_exp1.ch_names, include=["PO3", "PO4", "POz", "O1", "O2", "Oz", "P7", "P8", "PO7", "PO8", "PO9", "PO10"])
-# 
-# epochs = mne.channels.combine_channels(epochs_exp1, dict(roi=chans))
-# epochs.metadata = epochs_exp1.metadata
-
-# epochs.plot_psd(fmin=2., fmax=40., average=True, spatial_colors=False); plt.show()
-# epochs.plot_psd_topomap(normalize=True); plt.show()
-
-freqs = np.logspace(*np.log10([4, 30]), num=8)
-n_cycles = freqs / 2.  # different number of cycle per frequency
-
-epochs_informed = epochs_exp1["part == 'II' & condition == 'Informed'"]
-epochs_naive = epochs_exp1["part == 'II' & condition == 'Naive'"]
-
-power_informed = mne.time_frequency.tfr_morlet(epochs_informed, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
-power_naive = mne.time_frequency.tfr_morlet(epochs_naive, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
-
-freqs = np.arange(start=4, stop=30, step=1)
-n_cycles = freqs / 2.  # different number of cycle per frequency
-
-evokeds_informed = evokeds_exp1["I"]["Informed"]
-evokeds_naive = evokeds_exp1["I"]["Naive"]
-
-power_informed = mne.time_frequency.tfr_morlet(evokeds_informed, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
-power_naive = mne.time_frequency.tfr_morlet(evokeds_naive, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True)
-
-power_diff = power_informed - power_naive
-power_diff.plot(baseline=(-0.3, 0), mode = "percent", tmin=-0.3, tmax = 0.7, vmin=-200, vmax=200); plt.show()
-
-power_diff.plot_joint(baseline=(-0.5, 0), mode = "percent", vmin=-100, vmax=100, timefreqs=(0.175, 12)); plt.show()
-
-#power_diff.plot_topomap(fmin=8, fmax=14, baseline=(-0.5, 0), mode="mean", vmin=-200, vmax=200, title="alpha"); plt.show()
-#power_diff.plot_topomap(fmin=15, fmax=30, baseline=(-0.5, 0), mode="mean", vmin=-200, vmax=200, title="beta"); plt.show()
-```
-
 # General Discussion
@@
 However, the finding that these two components were modulated in different parts of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
-It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem reflect recurrent processing *within* the visual system [@wyatte2014].
+It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem to reflect recurrent processing *within* the visual system [@wyatte2014].
 Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
 
-While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
+While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream for object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
 @hsieh2010 showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
@@
 This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital cortex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
-Both of these cortical regions are consistent with the neural generators of the N170 and P1 components of the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
+Both of these cortical regions are consistent with the neural generators of the N170 and P1 components in the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
 

### 2021-01-26 analysis/master_thesis.tex
master thesis submission

@@
 I would also like to thank all current members of the lab for their guidance and fruitful discussions on the topics of data analysis and reporting.
-Valuable feedback on an earlier draft of this thesis was given by Anna Kuhlen, Annika Just, and Garrett Widener.
+Valuable feedback on an earlier draft of this thesis was provided by Anna Kuhlen, Annika Just, and Garrett Widener.
 Finally, I am most grateful to my parents, friends, and supervisors: During the journey of writing this thesis, their support has often literally changed my view of the world around me to the better.
@@
 As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e.,~participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected hamper such an understanding and keep the perception of the object semantically naive.
+The matching keywords were expected to induce semantically informed perception (i.e.,~participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to hamper such an understanding and keep the perception of the object semantically naive.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
@@
 
-\caption{Procedure and Results of Experiment 1\smallskip}\label{fig:exp1-plot}
+\bigskip\small\textit{Note.} 
+(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
+In the post-insight part, the same objects were presented again without the keywords.
+(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
+Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
+Ampl.
+= amplitude.\newline
+*\textit{p} \textless{} .05. **\textit{p} \textless{} .01. ***\textit{p} \textless{} .001.
+
 \end{figure}
@@
 Second, they can account simultaneously for the non-independence of data points coming from the same participant and/or from the same item.
-In contrast, the neglect of the item as a random variable in by-participant ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
+In contrast, the neglect of the item as a random variable in by-participant ANOVAs can lead to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012).
 Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
@@
 (2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
+Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} ≥ .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
 All models were computed in R (Version 4.0.2; R Core Team, 2020) using the lme4 package (Version 1.1.23; Bates et al., 2015).
@@
 
+\vspace*{15mm}
+
+\caption{Results of Experiment 2\smallskip}\label{fig:exp2-plot}
+
 {\centering \includegraphics[width=1\linewidth]{master_thesis_files/figure-latex/exp2-plot-1}
@@
 
-\caption{Results of Experiment 2\smallskip}\label{fig:exp2-plot}
+\bigskip\small\textit{Note.} 
+ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
+In an exact replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical significance (\textit{p} = .064).
+Ampl.
+= amplitude.\newline*\textit{p} \textless{} .05.
+**\textit{p} \textless{} .01.
+***\textit{p} \textless{} .001.
+
 \end{figure}
@@
 
-\caption{Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip}\label{fig:joint-plot}
+\bigskip\small\textit{Note.} 
+The violins and box plots show the distributions of the by-participant averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
+The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modeling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
+Ampl.
+= amplitude, 95\% CI = 95\% confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
+**\textit{p} \textless{} .01.
+***\textit{p} \textless{} .001.
+
 \end{figure}
@@
 Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of signalling messages.
+Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of signaling messages.
 To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
@@
 However, the finding that these two components were modulated in different parts of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
-It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem reflect recurrent processing \emph{within} the visual system (Wyatte et al., 2014).
+It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem to reflect recurrent processing \emph{within} the visual system (Wyatte et al., 2014).
 Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
 
-While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream of object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
+While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream for object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
 Hsieh et al.
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/4.png} & 4 & \makecell[l]{Unkraut, jäten\\{[weed, removing]}} & \makecell[l]{Uhr, mit Wärme betreiben\\{[clock, operating with heat]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/5.png} & 5 & \makecell[l]{Mausefalle, zuschnappen\\{[mousetrap, snap-shutting]}} & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lense, cutting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/5.png} & 5 & \makecell[l]{Mausefalle, zuschnappen\\{[mousetrap, snap-shutting]}} & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lens, cutting]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/6.png} & 6 & \makecell[l]{Goldmünzen, wiegen\\{[gold coin, weighing]}} & \makecell[l]{Farbe, vom Fenster abschleifen\\{[paint, scraping off the window]}}\\
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/54.png} & 54 & \makecell[l]{Fußstütze, reiten\\{[footrest, horseback riding]}} & \makecell[l]{Stromstärke, messen\\{[current, measuring]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/55.png} & 55 & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, survining fires]}} & \makecell[l]{Botschaft, telegrafieren\\{[message, telegraphing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/55.png} & 55 & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, surviving fires]}} & \makecell[l]{Botschaft, telegrafieren\\{[message, telegraphing]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/56.png} & 56 & \makecell[l]{Schnee, rodeln\\{[snow, sleighing]}} & \makecell[l]{Dampf, zerstäuben\\{[steam, spraying]}}\\
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/63.png} & 63 & \makecell[l]{Körper, untersuchen\\{[body, examining]}} & \makecell[l]{Schuhe, auf Eis laufen\\{[shoes, walking on ice]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/64.png} & 64 & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lense, cutting]}} & \makecell[l]{Saatgut, gleichmäßig aussäen\\{[seeds, sowing evenly]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/64.png} & 64 & \makecell[l]{Brillenglas, zuschneiden\\{[eyeglass lens, cutting]}} & \makecell[l]{Saatgut, gleichmäßig aussäen\\{[seeds, sowing evenly]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/65.png} & 65 & \makecell[l]{Draht, wickeln\\{[wire, winding]}} & \makecell[l]{Bergbaustollen, beleuchten\\{[mining tunnel, lightening]}}\\
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/69.png} & 69 & \makecell[l]{Sternenbilder, vermessen\\{[stellar constellation, measuring]}} & \makecell[l]{Schnurlot, absenken\\{[plummet, letting down]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/70.png} & 70 & \makecell[l]{Nachricht, morsen\\{[message, signalling]}} & \makecell[l]{Feldanbau, häckseln\\{[harvest, chopping]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/70.png} & 70 & \makecell[l]{Nachricht, morsen\\{[message, signaling]}} & \makecell[l]{Feldanbau, häckseln\\{[harvest, chopping]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/71.png} & 71 & \makecell[l]{Musikgerät, stampfen\\{[musical instrument, stamping]}} & \makecell[l]{Goldmünzen, wiegen\\{[gold coin, weighing]}}\\
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/81.png} & 81 & \makecell[l]{Kork, flach pressen\\{[cork, pressing flat]}} & \makecell[l]{Elektroschock, spielen\\{[electric shock, playing]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/82.png} & 82 & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}} & \makecell[l]{Blumentopf, sich selbst wässern\\{[flower pot, self-watering]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/82.png} & 82 & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}} & \makecell[l]{Blumentopf, sich selbst wässern\\{[flowerpot, self-watering]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/83.png} & 83 & \makecell[l]{Fass, anheben\\{[barrel, lifting]}} & \makecell[l]{Mikroskop-Proben, schneiden\\{[microscopic samples, slicing]}}\\
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/85.png} & 85 & \makecell[l]{altes Ritual, hacken\\{[ancient ritual, chopping]}} & \makecell[l]{Spannung, erzeugen\\{[electric current, making]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/86.png} & 86 & \makecell[l]{Kleidung, im Eimer waschen\\{[clothes, washing in a bucket]}} & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, survining fires]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/86.png} & 86 & \makecell[l]{Kleidung, im Eimer waschen\\{[clothes, washing in a bucket]}} & \makecell[l]{Türgelenk, Feuer überstehen\\{[door hinge, surviving fires]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/87.png} & 87 & \makecell[l]{Maiskolben, entkörnen\\{[corncob, removing grains]}} & \makecell[l]{Brief, wiegen\\{[letter, weighing]}}\\
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/97.png} & 97 & \makecell[l]{Korken, formen\\{[bottle cork, forming]}} & \makecell[l]{Sternenbilder, vermessen\\{[stellar constellation, measuring]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/98.png} & 98 & \makecell[l]{Erektion, helfen\\{[erection, helping]}} & \makecell[l]{Waffe, werfen\\{[weapn, throwing]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/98.png} & 98 & \makecell[l]{Erektion, helfen\\{[erection, helping]}} & \makecell[l]{Waffe, werfen\\{[weapon, throwing]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/99.png} & 99 & \makecell[l]{Streckenmaß, Sonnenlicht nutzen\\{[distance measure, using sunrays]}} & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}}\\
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/102.png} & 102 & \makecell[l]{von Hand, zentrifugieren\\{[by hand, centrifugating]}} & \makecell[l]{Lieferungen, abzählen\\{[deliveries, counting]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/103.png} & 103 & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}} & \makecell[l]{Nachricht, morsen\\{[message, signalling]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/104.png} & 104 & \makecell[l]{Waffe, werfen\\{[weapn, throwing]}} & \makecell[l]{elektrische Spannung, prüfen\\{[electric current, measuring]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/103.png} & 103 & \makecell[l]{Kartoffeln, stampfen\\{[potatoes, mashing]}} & \makecell[l]{Nachricht, morsen\\{[message, signaling]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/104.png} & 104 & \makecell[l]{Waffe, werfen\\{[weapon, throwing]}} & \makecell[l]{elektrische Spannung, prüfen\\{[electric current, measuring]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/105.png} & 105 & \makecell[l]{Tankfüllstand, messen\\{[fuel tank level, gauging]}} & \makecell[l]{Tonpott, trommeln\\{[clay pot, drumming]}}\\
@@
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/116.png} & 116 & \makecell[l]{Eier, wiegen\\{[eggs, weighing]}} & \makecell[l]{Leierkasten, klingen\\{[barrel organ, making sounds]}}\\
-\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/117.png} & 117 & \makecell[l]{Blumentopf, sich selbst wässern\\{[flower pot, self-watering]}} & \makecell[l]{Glas, schneiden\\{[glass, cutting]}}\\
+\includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/117.png} & 117 & \makecell[l]{Blumentopf, sich selbst wässern\\{[flowerpot, self-watering]}} & \makecell[l]{Glas, schneiden\\{[glass, cutting]}}\\
 \includegraphics[valign=c, scale=0.23]{../materials/unfamiliar/118.png} & 118 & \makecell[l]{Schritte, vergrößern\\{[steps, extending]}} & \makecell[l]{Tabletten, zerteilen\\{[pill, splitting]}}\\
@@
 \end{center}
-
-\newpage
 
@@
 
-\clearpage
-
-\mbox{}\thispagestyle{empty}\clearpage
-
 \end{document}

### 2021-01-26 analysis/manuscript_files/functions_plots_tables.R

@@ -22,7 +22,7 @@ plot_trials <- function(){
     annotate("rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81, color = "black", fill = "white") +
     annotate("text", x = -27, y = 65.3, label = "+", size = 20 / .pt, family = "Helvetica") +
     annotate("text", x = -9, y = 55, label = "potatoes\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
-    annotate("text", x = -9, y = 79, label = "message\nsignalling", size = 10 / .pt, family = "Helvetica", color = color_naive) +
+    annotate("text", x = -9, y = 79, label = "message\nsignaling", size = 10 / .pt, family = "Helvetica", color = color_naive) +
     annotate("text", x = 9, y = 67, label = "*", size = 30 / .pt, family = "Helvetica") +
     draw_image("analysis/manuscript_files/potato_masher.png", x = 18, y = 62, width = 18, height = 18) +
     # Timings

### 2021-04-05 analysis/manuscript.Rmd
add stan and tfr try-outs

@@
 
-In the two experiments subsequently reported, participants were presented with real-word objects that were presumed to be unfamiliar to most of them.
+In the two experiments subsequently reported, participants were presented with real-world objects that were presumed to be unfamiliar to most of them.
 They first viewed each of these objects without any semantic information.
@@
 
+```{r bayes, eval=FALSE}
+library(brms)
+options(mc.cores = 6)
+
+data_joint_subs %>%
+  filter(condition %in% c("Informed", "Naive")) %>%
+  droplevels() %>%
+  select(part, condition, participant, item, P1, N170, N400) %>%
+  na.omit() %>%
+  as.list() -> data_brm
+
+contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
+contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
+contrasts(data_brm$condition) <- MASS::ginv(contrasts_condition)
+contrasts(data_brm$part) <- MASS::ginv(contrasts_part)
+
+formula <- P1 ~ part / condition + (part / condition | participant) + (part / condition | item)
+prior <- set_prior("cauchy(0, 0.707)", class = "b")
+
+mod_brm <- brm(
+  formula = formula,
+  data = data_brm,
+  family = gaussian(),
+  prior = prior,
+  sample_prior = "yes",
+  save_pars = save_pars(all = TRUE),
+  chains = 4,
+  iter = 20000,
+  warmup = 2000,
+  cores = 4,
+  control = list(adapt_delta = 0.9)
+)
+
+# mod_prior <- brm(formula = formula, data = data_brm, prior = prior, sample_prior = "only")
+# prior_summary(mod_prior)
+# mcmc_plot(mod_prior)
+#
+# mod_post <- update(mod_prior, sample_prior = "yes")
+# summary(mod_post)
+# mcmc_plot(mod_post, pars = "b")
+# plot(mod_post)
+
+hypothesis <- paste0("part", c("I", "II", "III"), ":condition1 = 0")
+bf_brms <- hypothesis(mod_post, hypothesis = hypothesis)
+bf_brms$hypothesis$bf10 <- 1 / bf_brms$hypothesis$Evid.Ratio
+bf_brms
+
+bf_bayestest <- bayestestR::bayesfactor(mod_post)
+bf_bayestest
+
+mod_brm_s <- brm(
+  bf(P1 ~ part / condition + (part / condition | participant) + (part / condition | item),
+     sigma ~ 1 + (1 | participant)),
+  prior = c(
+    prior(cauchy(0, 0.707), class = b),
+    prior(student_t(3, 0, 5.7), class = Intercept, dpar = sigma),
+    prior(normal(0, 5), class = sd, group = participant, dpar = sigma)),
+  data = data_brm,
+  family = gaussian(),
+  sample_prior = "yes",
+  save_pars = save_pars(all = TRUE),
+  chains = 4,
+  iter = 20000,
+  warmup = 2000,
+  cores = 4,
+  control = list(adapt_delta = 0.9)
+)
+```
+
+```{python tfr, eval=FALSE}
+import mne
+import numpy as np
+#import matplotlib.pyplot as plt
+
+# epochs = preproc(
+#   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
+#   metadata=r.data_exp1.query("participant == 'VP_04'"),
+#   n_components=15,
+#   method="fastica",
+#   l_freq=None,
+#   h_freq=None,
+#   event_id=dict(match=221, mismatch=222),
+#   tmin=-0.5,
+#   tmax=1.498,
+#   baseline=(-0.2, 0),
+#   reject=dict(eeg=200)
+# )
+# epochs.save("analysis/export/vp04-epo.fif")
+
+epochs = mne.read_epochs("analysis/export/unf-exp1-epo.fif")
+
+evokeds = compute_evokeds(epochs_c, grand=True, data_only=False)
+evokeds_i = evokeds["II"]["Informed"]
+evokeds_n = evokeds["II"]["Naive"]
+
+freqs = np.logspace(*np.log10([6, 35]), num=8)
+n_cycles = freqs / 2.
+power_i = mne.time_frequency.tfr_morlet(evokeds_i, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
+power_n = mne.time_frequency.tfr_morlet(evokeds_n, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
+power_i = power_i.apply_baseline(mode='mean', baseline=(-.400, -.100))
+power_n = power_n.apply_baseline(mode='mean', baseline=(-.400, -.100))
+
+power_d = power_i.copy()
+power_d.data = power_i.data - power_n.data
+
+power_d.plot()
+
+# epochs.resample(250., npad='auto')
+
+roi = r.comps["roi"][0] + r.comps["roi"][1]
+idxs = np.where(np.in1d(epochs.ch_names, roi))
+
+epochs_i = epochs["part == 'II' & condition == 'Informed'"].pick_channels(roi)
+epochs_n = epochs["part == 'II' & condition == 'Naive'"].pick_channels(roi)
+
+epochs_c = mne.channels.combine_channels(epochs, groups=dict(avg=range(62)))
+
+epochs_c.metadata = epochs.metadata
+epochs_s = epochs_c["part == 'II'"]
+# epochs_i = epochs_s["condition == 'Informed'"]
+# epochs_n = epochs_s["condition == 'Naive'"]
+
+# power_i = mne.time_frequency.tfr_morlet(epochs_i, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
+# power_n = mne.time_frequency.tfr_morlet(epochs_n, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
+# power_d = power_i - power_n
+# 
+# power_d.plot([0], baseline=(-0.5, 0), mode='percent', vmin=-1, vmax=1)
+
+# define frequencies of interest (log-spaced)
+#freqs = np.logspace(*np.log10([6, 35]), num=8)
+freqs = np.arange(3, 50, 1.6)
+#n_cycles = freqs / 2.  # different number of cycle per frequency
+n_cycles = np.linspace(3, 10, len(freqs))
+power = mne.time_frequency.tfr_morlet(epochs_c, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
+
+power.plot([0], baseline=(-0.5, 0), mode='percent')
+
+power.plot_topo(baseline=(-0.5, 0), mode='logratio')
+power.plot_topomap(ch_type='eeg', tmin=0.15, tmax=0.2, fmin=8, fmax=12, baseline=(-0.5, 0), mode='logratio', title='Alpha')
+power.plot_topomap(ch_type='eeg', tmin=0.15, tmax=0.2, fmin=13, fmax=25, baseline=(-0.5, 0), mode='logratio', title='Beta')
+
+import numpy as np
+import matplotlib.pyplot as plt
+from mne.baseline import rescale
+from mne.stats import bootstrap_confidence_interval
+iter_freqs = [
+    ('Theta', 4, 7),
+    ('Alpha', 8, 12),
+    ('Beta', 13, 25),
+    ('Gamma', 30, 45)
+]
+raw_fname = "data/exp1/EEG/Vp0004.vhdr"
+tmin, tmax = -0.5, 1.498
+baseline = None
+frequency_map = list()
+event_id = dict(match=222)
+for band, fmin, fmax in iter_freqs:
+    # (re)load the data to save memory
+    raw = mne.io.read_raw_brainvision(raw_fname, scale=1e6, preload=True)
+    raw.filter(fmin, fmax, n_jobs=1,  # use more jobs to speed up.
+               l_trans_bandwidth=1,  # make sure filter params are the same
+               h_trans_bandwidth=1)  # in each band and skip "auto" option.
+    events, _ = mne.events_from_annotations(raw, verbose=False)
+    epochs = mne.Epochs(raw, events, event_id, tmin, tmax, baseline=baseline,
+                        reject=dict(eeg=200), preload=True)
+    # remove evoked response
+    epochs.subtract_evoked()
+    # get analytic signal (envelope)
+    epochs.apply_hilbert(envelope=True)
+    frequency_map.append(((band, fmin, fmax), epochs.average()))
+    del epochs
+del raw
+# Helper function for plotting spread
+def stat_fun(x):
+    """Return sum of squares."""
+    return np.sum(x ** 2, axis=0)
+# Plot
+fig, axes = plt.subplots(4, 1, figsize=(10, 7), sharex=True, sharey=True)
+colors = plt.get_cmap('winter_r')(np.linspace(0, 1, 4))
+for ((freq_name, fmin, fmax), average), color, ax in zip(
+        frequency_map, colors, axes.ravel()[::-1]):
+    times = average.times * 1e3
+    gfp = np.sum(average.data ** 2, axis=0)
+    gfp = mne.baseline.rescale(gfp, times, baseline=(None, 0))
+    ax.plot(times, gfp, label=freq_name, color=color, linewidth=2.5)
+    ax.axhline(0, linestyle='--', color='grey', linewidth=2)
+    ci_low, ci_up = bootstrap_confidence_interval(average.data, random_state=0,
+                                                  stat_fun=stat_fun)
+    ci_low = rescale(ci_low, average.times, baseline=(None, 0))
+    ci_up = rescale(ci_up, average.times, baseline=(None, 0))
+    ax.fill_between(times, gfp + ci_up, gfp - ci_low, color=color, alpha=0.3)
+    ax.grid(True)
+    ax.set_ylabel('GFP')
+    ax.annotate('%s (%d-%dHz)' % (freq_name, fmin, fmax),
+                xy=(0.95, 0.8),
+                horizontalalignment='right',
+                xycoords='axes fraction')
+axes.ravel()[-1].set_xlabel('Time [ms]')
+plt.show()
+```
+
 ```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}

### 2021-04-05 manuscript.Rmd
move manuscript to project root

--- 2021-04-05 analysis/manuscript.Rmd
@@
 # Link to the bibliography file
-r_refs("analysis/manuscript_files/r-references.bib")
+r_refs("manuscript_files/r-references.bib")
 
 # Source plotting functions
-source("analysis/manuscript_files/functions_plots_tables.R")
+source("manuscript_files/functions_plots_tables.R")
 
 # Create an export folder for results
-dir.create("analysis/export", showWarnings = FALSE)
+dir.create("export", showWarnings = FALSE)
 
@@
 # Backup epochs to the export folder
-epochs_exp1$save("analysis/export/exp1-epo.fif")
+epochs_exp1$save("export/exp1-epo.fif")
 
@@
   bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
-  write_tsv("analysis/export/exp1-data.tsv") -> data_exp1
+  write_tsv("export/exp1-data.tsv") -> data_exp1
 
@@
 py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp1-gaverages.RDS")
+  saveRDS("export/exp1-gaverages.RDS")
 
@@
   mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp1-objects.tsv")
+  write_tsv("export/exp1-objects.tsv")
 
@@
   ) %>%
-  write_tsv("analysis/export/montage.tsv")
+  write_tsv("export/montage.tsv")
 
@@
 # Load preprocessed single-trial data
-read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
+read_tsv("export/exp1-data.tsv", col_types = cols()) %>%
   # Factorize columns
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
+  saveRDS("export/exp1-models.RDS") -> models_exp1
 ```
@@
 # Load average number of objects per condition
-(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
+(read_tsv("export/exp1-objects.tsv", col_types = cols()) %>%
    summarise(across(.cols = -Participant, .fns = mean)) %>%
@@
 # Load grand-averaged ERPs and linear mixed models
-evokeds_exp1 <- readRDS("analysis/export/exp1-gaverages.RDS")
-models_exp1 <- readRDS("analysis/export/exp1-models.RDS")
+evokeds_exp1 <- readRDS("export/exp1-gaverages.RDS")
+models_exp1 <- readRDS("export/exp1-models.RDS")
 ```
@@
 # )
-# epochs.save("analysis/export/vp04-epo.fif")
-
-epochs = mne.read_epochs("analysis/export/unf-exp1-epo.fif")
+# epochs.save("export/vp04-epo.fif")
+
+epochs = mne.read_epochs("export/unf-exp1-epo.fif")
 
@@
 # Load sample time points and electrode montage
-montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())
+montage <- read_tsv("export/montage.tsv", col_types = cols())
 
@@
 # Backup epochs to the export folder
-epochs_exp2$save("analysis/export/exp2-epo.fif")
+epochs_exp2$save("export/exp2-epo.fif")
 
@@
   bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
-  write_tsv("analysis/export/exp2-data.tsv") -> data_exp2
+  write_tsv("export/exp2-data.tsv") -> data_exp2
 
@@
 py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp2-gaverages.RDS")
+  saveRDS("export/exp2-gaverages.RDS")
 
@@
   mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp2-objects.tsv")
+  write_tsv("export/exp2-objects.tsv")
 
@@
 # Load preprocessed single-trial data
-read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
+read_tsv("export/exp2-data.tsv", col_types = cols()) %>%
   # Factorize columns
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp2-models.RDS") -> models_exp2
+  saveRDS("export/exp2-models.RDS") -> models_exp2
 ```
@@
 # Load average number of objects per condition
-(read_tsv("analysis/export/exp2-objects.tsv", col_types = cols()) %>%
+(read_tsv("export/exp2-objects.tsv", col_types = cols()) %>%
    summarise(across(.cols = -Participant, .fns = mean)) %>%
@@
 # Load grand-averaged ERPs and linear mixed models
-evokeds_exp2 <- readRDS("analysis/export/exp2-gaverages.RDS")
-models_exp2 <- readRDS("analysis/export/exp2-models.RDS")
+evokeds_exp2 <- readRDS("export/exp2-gaverages.RDS")
+models_exp2 <- readRDS("export/exp2-models.RDS")
 ```
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-models.RDS") -> models_joint
+  saveRDS("export/joint-models.RDS") -> models_joint
 ```
@@
 # Load linear mixed models
-models_joint <- readRDS("analysis/export/joint-models.RDS")
+models_joint <- readRDS("export/joint-models.RDS")
 
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-control-models.RDS") -> models_joint_control
+  saveRDS("export/joint-control-models.RDS") -> models_joint_control
 ```
@@
 # Load linear mixed models
-models_joint_control <- readRDS("analysis/export/joint-control-models.RDS")
+models_joint_control <- readRDS("export/joint-control-models.RDS")
 
@@
 message("This also worked!!!")
-py_run_string("epochs_exp3.save('analysis/export/exp3-epo.fif', overwrite=True)")
+py_run_string("epochs_exp3.save('export/exp3-epo.fif', overwrite=True)")
 py_run_string("del epochs_exp3")
@@
 # Backup epochs to the export folder
-epochs_exp3$save("analysis/export/exp3-epo.fif")
+epochs_exp3$save("export/exp3-epo.fif")
 
@@
   bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
-  write_tsv("analysis/export/exp3-data.tsv") -> data_exp3
+  write_tsv("export/exp3-data.tsv") -> data_exp3
 
@@
 py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp3-gaverages.RDS")
+  saveRDS("export/exp3-gaverages.RDS")
 
@@
   mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp3-objects.tsv")
+  write_tsv("export/exp3-objects.tsv")
 
@@
 # Load preprocessed single-trial data
-read_tsv("analysis/export/exp3-data.tsv", col_types = cols()) %>%
+read_tsv("export/exp3-data.tsv", col_types = cols()) %>%
   # Factorize columns
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp3-models.RDS") -> models_exp3
+  saveRDS("export/exp3-models.RDS") -> models_exp3
 ```

### 2021-04-05 analysis/manuscript.Rmd
update docker

@@
 # Create an export folder for results
-dir.create("analysis/export", showWarnings = FALSE)
+dir.create("export", showWarnings = FALSE)
 
@@
 
-# Read behavioral data for Experiment 1
-list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp1
+# Read behavioral data from two batches of participants
+paste0("data/rt/exp", 1:2) %>%
+  map(list.files, pattern = ".txt", full.names = TRUE) %>%
+  map(map, read_behav) -> behav
+
+# Avoid duplicate participant labels across the two batches
+behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))
+
+# Merge into a single list
+behav %<>% flatten()
 
@@
 # Preprocess the EEG for Experiment 1 in Python
+paste0("data/eeg/exp", 1:2) %>%
+  list.files(pattern = ".vhdr", full.names = TRUE) %>%
   map2(
-  .x = list.files("data/exp1/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp1,
+    .y = behav,
     ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
@@
   # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp1
+  py$mne$epochs$concatenate_epochs() -> epochs
 
 # Backup epochs to the export folder
-epochs_exp1$save("analysis/export/exp1-epo.fif")
+epochs$save("export/aha-epo.fif")
 
@@
 
-An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @serre2007].
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @lindsay2020].
 In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.

### 2021-04-08 install_stan.R
make dockerfile ready for binder

@@ -1,18 +1,0 @@
-# Following instructions from 
-# https://github.com/stan-dev/rstan/wiki/Installing-RStan-on-Linux
-
-print("Running install_stan.R")
-
-## Creating /home/rstudio/.R/Makevars
-
-dotR <- file.path(Sys.getenv("HOME"), ".R")
-if (!file.exists(dotR)) dir.create(dotR)
-M <- file.path(dotR, "Makevars")
-if (!file.exists(M)) file.create(M)
-cat("\nCXX14FLAGS=-O3 -march=native -mtune=native -fPIC",
-    "CXX14=clang++",
-    file = M, sep = "\n", append = TRUE)
-
-## Installing rstan
-
-install.packages("rstan", type = "source")

### 2021-04-14 analysis/manuscript.Rmd
make dockerfile ready for binder
start with merge exps

--- 2021-04-05 analysis/manuscript.Rmd
@@
     latex_engine  : "xelatex"
+
+editor_options: 
+  chunk_output_type: console
 
@@
   )
+)
+
+# Define some filenames for I/O
+fnames <- list(
+  epochs = "analysis/export/aha-epo.fif",
+  trials = "analysis/export/aha-trials.csv",
+  gavgs = "analysis/export/aha-gavgs.RDS",
+  conditions = "analysis/export/aha-obj-per-cond.csv",
+  montage = "analysis/export/aha-montage.csv"
 )
@@
 import mne
-
-# Define function for preprocessing the EEG data
-def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax,
-    baseline, reject):
+import numpy as np
+
+# Define function for preprocessing a single participant
+def preproc(
+    vhdr_fname,
+    metadata,
+    n_components,
+    method,
+    l_freq,
+    h_freq,
+    event_id,
+    tmin,
+    tmax,
+    baseline,
+    reject,
+):
     # Read EEG data in microvolts
@@
 
+# Define function for preprocessing a list of participants
+def preproc_all(
+    vhdr_fnames,
+    metadatas,
+    output_fname,
+    n_components,
+    method,
+    l_freq,
+    h_freq,
+    event_id,
+    tmin,
+    tmax,
+    baseline,
+    reject,
+):
+    # Do the actual preprocessing
+    epochs = [
+        preproc(
+            vhdr_fname=vhdr_fname,
+            metadata=metadata,
+            n_components=n_components,
+            method=method,
+            l_freq=l_freq,
+            h_freq=h_freq,
+            event_id=event_id,
+            tmin=tmin,
+            tmax=tmax,
+            baseline=baseline,
+            reject=reject,
+        )
+        for vhdr_fname, metadata in zip(vhdr_fnames, metadatas)
+    ]
+    # Concatenate all participants and save
+    epochs = mne.epochs.concatenate_epochs(epochs)
+    epochs.save(output_fname, overwrite=True)
+    # Return the epochs without loading the actual data
+    epochs = mne.read_epochs(output_fname, preload=False)
+    return epochs
+
 # Define function to compute averaged waveforms by part and condition
-def compute_evokeds(epochs, grand=True, data_only=True):
+def compute_evokeds(epochs_fname, grand=True, data_only=True):
+    # Read preprocessed epochs
+    epochs = mne.read_epochs(epochs_fname)
     # Define lists of participants, parts, and conditions
@@
         return epochs[query].average()
+
     # Create a dict with by-participant waveforms nested in conditions nested in parts
@@
 # Define function to compute single-trial mean ERP amplitudes from epochs
-def compute_erps(epochs, name, tmin, tmax, roi):
+def compute_erps(epochs_fname, name, tmin, tmax, roi):
+    # Read preprocessed epochs
+    epochs = mne.read_epochs(epochs_fname)
     # Average across electrodes in the ROI
@@
     # Average across samples in the time window
-    import numpy as np
     tmin_s, tmax_s = tmin / 1000, tmax / 1000
@@
 # Preprocess the EEG for Experiment 1 in Python
-map2(
-  .x = list.files("data/exp1/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp1,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp1
-
-# Backup epochs to the export folder
-epochs_exp1$save("analysis/export/exp1-epo.fif")
+paste0("data/eeg/exp", 1:2) %>%
+  list.files(pattern = ".vhdr", full.names = TRUE) %>%
+  exec(
+    .fn = py$preproc_all,
+    vhdr_fnames = .,
+    metadatas = behav,
+    output_fname = fnames$epochs,
+    !!!preproc_params
+  ) -> epochs
 
 # Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs = epochs_exp1) %>%
+pmap_dfc(comps, py$compute_erps, epochs_fname = fnames$epochs) %>%
   set_names(comps$name) %>%
-  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
-  write_tsv("analysis/export/exp1-data.tsv") -> data_exp1
+  bind_cols(epochs$metadata, .) %T>%
+  write_tsv(fnames$trials) -> aha
 
 # Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp1-gaverages.RDS")
+py$compute_evokeds(epochs_fname = fnames$epochs, grand = TRUE, data_only = TRUE) %>%
+  saveRDS(fnames$gavgs)
 
 # Backup number of stimuli assigned to each condition for all participants
-map(behav_exp1, function(x) table(x$condition) / 3) %>%
+map(behav, function(x) table(x$condition) / 3) %>%
   bind_rows() %>%
-  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp1-objects.tsv")
+  mutate(Participant = unique(aha$participant), .before = 1) %>%
+  write_csv(fnames$conditions)
 
@@
   rename(electrode = Site) %>%
-  inner_join(tibble(electrode = epochs_exp1$ch_names), ., by = "electrode") %>%
+  inner_join(tibble(electrode = epochs$ch_names), ., by = "electrode") %>%
   mutate(
@@
   ) %>%
-  write_tsv("analysis/export/montage.tsv")
-
-# Remove the epochs to free up memory
-rm(epochs_exp1)
+  write_csv(fnames$montage)
 ```
@@
   filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> data_exp1
+  droplevels() -> aha
 
@@
 # Apply these contrasts to the factors in the data
-contrasts(data_exp1$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp1$part) <- MASS::ginv(contrasts_part)
+contrasts(aha$condition) <- MASS::ginv(contrasts_condition)
+contrasts(aha$part) <- MASS::ginv(contrasts_part)
 
@@
   formula = formula_exp12,
-  data = data_exp1,
+  data = aha,
   control = control,
@@
     item = factor(item)
-  ) -> data_exp1
+  ) -> aha
 
 # Check number of rejected epochs
-data_exp1 %>%
+aha %>%
   group_by(participant) %>%
@@
 #   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
-#   metadata=r.data_exp1.query("participant == 'VP_04'"),
+#   metadata=r.aha.query("participant == 'VP_04'"),
 #   n_components=15,
@@
   mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
-  bind_rows(data_exp1, ., .id = "experiment") %>%
+  bind_rows(aha, ., .id = "experiment") %>%
   mutate(experiment = as_factor(experiment)) -> data_joint

### 2021-04-20 analysis/manuscript.Rmd
compute maximal freq models

@@
 # Load preprocessed single-trial data
-read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
+read_tsv("analysis/export/aha-trials.csv", col_types = cols()) %>%
   # Factorize columns
@@
 
-# Define formula and parameters for linear mixed-effects regression models (LMMs)
-formula_exp12 <- buildmer::tabulate.formula(
-  ~ part * condition + (part * condition | participant) + (part * condition | item)
-) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-control <- lme4::lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
-
-# Define formula for follow-up contrasts
-specs_exp12 <- pairwise ~ condition | part
-
-# Define function to compute LMMs and follow-up contrasts for each component
-compute_models <- function(dep, formula, data, control, specs) {
-  require(lmerTest)
-  require(buildmer)
+# Specify model formula and follow-up contrasts
+form <- erp ~ part * condition +
+  (part * condition | participant) +
+  (part * condition | item)
+specs <- pairwise ~ condition | part
+
+# Calculate linear mixed-effects models and contrasts
+map(comps$name, function(comp, formula = form, data = aha, specs = specs) {
+  require(afex)
   require(emmeans)
-  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  build <- buildmer(
-    control = control,
-    REML = FALSE,
-    buildmerControl = buildmerControl(
-      formula = formula,
-      data = data,
-      direction = c("backward", "backward"),
-      elim = function(logp) exp(logp) >= .20,
-      calc.anova = TRUE,
-      ddf = "Satterthwaite",
-      dep = dep
-    )
-  )
-  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans
-  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts
+  data %<>% rename(erp = all_of(comp))
+  mod <- mixed(
+    formula,
+    data,
+    method = "S",
+    check_contrasts = FALSE,
+    all_fit = TRUE
+  )
+  em <- emmeans(mod, specs = specs, infer = TRUE, data = data)
   modlist <- list(
-    model = build@model,
-    anova = build@anova,
-    summary = build@summary,
-    means = means %>% as.data.frame(),
-    contrasts = conts %>% as.data.frame()
-  )
-  return(modlist)
-}
-
-# Compute the models for Experiment 1
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp12,
-  data = aha,
-  control = control,
-  specs = specs_exp12
-) %>%
+    model = mod,
+    anova = anova(mod),
+    summary = summary(mod),
+    means = as.data.frame(em$means),
+    contrasts = as.data.frame(em$contrasts)
+  )
+}) %>%
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
+  saveRDS("analysis/export/aha_models_freq.RDS") -> mods_freq
 ```

### 2021-05-04 analysis/manuscript.Rmd
add tfr

@@
 ```{r setup, include=FALSE}
-# Do you want to re-run the EEG preprocessing? Note that this can only be done with the raw data,
-# which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
-rerun_preproc <- TRUE
-
-# Do you want to re-run the linear mixed-effect models? This can be done even if only the
-# preprocessed single-trial data are available (from GitHub and/or the OSF). Note, however, that
-# fitting all models may take 24 hours or more.
-rerun_models <- FALSE
-
-# Do you want to run the analysis for Experiment 3?
-run_exp3 <- FALSE
-
 # Load packages
+library(lmerTest)
+library(emmeans)
 library(papaja)
@@
 
-# Set global chunk options
-knitr::opts_chunk$set(include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10)
-
-# Link to the bibliography file
+# Load helper functions for plots and tables
+source("analysis/manuscript_files/functions_plots_tables.R")
+
+# Load bibliography file
 r_refs("analysis/manuscript_files/r-references.bib")
 
-# Source plotting functions
-source("analysis/manuscript_files/functions_plots_tables.R")
-
-# Create an export folder for results
-dir.create("analysis/export", showWarnings = FALSE)
-
-# Define ERP components of interest
-comps <- tibble(
-  name = c("P1", "N170", "N400"),
-  tmin = c(100, 150, 400),
-  tmax = c(150, 200, 700),
-  roi = list(
-    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
-    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
-    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
-  )
-)
-
-# Define some filenames for I/O
-fnames <- list(
-  epochs = "analysis/export/aha-epo.fif",
-  trials = "analysis/export/aha-trials.csv",
-  gavgs = "analysis/export/aha-gavgs.RDS",
-  conditions = "analysis/export/aha-obj-per-cond.csv",
-  montage = "analysis/export/aha-montage.csv"
+# Set some global chunk options
+knitr::opts_chunk$set(
+  include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10
 )
@@
 
-```{python def_functions, eval=rerun_preproc}
+```{python, erp_funcs}
 # Import libraries
@@
     epochs.save(output_fname, overwrite=True)
+    del epochs
     # Return the epochs without loading the actual data
@@
         return epochs[query].average()
-
     # Create a dict with by-participant waveforms nested in conditions nested in parts
@@
 
-```{r exp1-preproc, eval=rerun_preproc}
-# Define function for reading and formatting the behavioral data
-read_behav <- function(txt_fname) {
-  # Read the log file
-  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
-  # Rename columns for participant and item IDs
-  dat %<>% rename(participant = VPNummer, item = StimID) %>%
-    # Add a column for the part of the experiment
-    mutate(part = case_when(
-      Wdh %in% c(211, 231) ~ "I",
-      Wdh %in% c(212, 232) ~ "II",
-      Wdh %in% c(213, 233) ~ "III",
-      Wdh == 234 ~ "IV"
-    ) %>% as_factor()) %>%
-    # Remove filler stimuli (i.e.,well-known objects)
-    filter(bek_unbek != "bekannt")
-  # Assign stimuli to conditions based on keywords and button presses
-  excl_known <- dat %>%
-    filter(part == "I" & Tastencode %in% c(201, 251)) %>%
-    pull(item)
-  excl_informed <- dat %>%
-    filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
-    pull(item)
-  excl_naive <- dat %>%
-    filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>%
-    pull(item)
-  informed <- dat %>%
-    filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
-    pull(item)
-  naive <- dat %>%
-    filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>%
-    pull(item)
-  # Create a new condition for the experimental condition
-  dat %<>% mutate(condition = case_when(
-    item %in% excl_known ~ "Excl_known",
-    item %in% excl_informed ~ "Excl_informed",
-    item %in% excl_naive ~ "Excl_naive",
-    item %in% informed ~ "Informed",
-    item %in% naive ~ "Naive"
-  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
-  # In Experiment 3, we need an additional column for position (upright vs. inverted)
-  if ("richtig_inv" %in% dat$Bed) {
-    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
-      # Return only relevant columns
-      select(part, position, condition, participant, item, RT)
-  } else {
-    # Return only relevant columns
-    dat %<>% select(part, condition, participant, item, RT)
-  }
-  return(dat)
-}
-
-# Read behavioral data from two batches of participants
-paste0("data/rt/exp", 1:2) %>%
-  map(list.files, pattern = ".txt", full.names = TRUE) %>%
-  map(map, read_behav) -> behav
-
-# Avoid duplicate participant labels across the two batches
-behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))
-
-# Merge into a single list
-behav %<>% flatten()
-
-# Define global parameters for EEG preprocessing
+```{r, preprocessing}
+# Define ERP components of interest
+comps <- tibble(
+  name = c("P1", "N170", "N400"),
+  tmin = c(100, 150, 400),
+  tmax = c(150, 200, 700),
+  roi = list(
+    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
+    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
+    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
+  )
+)
+
+# Define some filenames for I/O
+fnames <- list(
+  epochs = "data/processed/aha-epo.fif",
+  epochs_unf = "data/processed/aha-unf-epo.fif",
+  trials = "data/processed/aha-trials.csv",
+  gavgs = "data/processed/aha-gavgs.RDS",
+  conditions = "data/processed/aha-obj-per-cond.csv",
+  montage = "data/processed/aha-montage.csv",
+  models_freq = "data/processed/aha-models-freq.RDS"
+)
+
+# Define parameters for EEG preprocessing
 preproc_params <- list(
@@
 
-# Preprocess the EEG for Experiment 1 in Python
-paste0("data/eeg/exp", 1:2) %>%
-  list.files(pattern = ".vhdr", full.names = TRUE) %>%
-  exec(
-    .fn = py$preproc_all,
-    vhdr_fnames = .,
-    metadatas = behav,
-    output_fname = fnames$epochs,
-    !!!preproc_params
-  ) -> epochs
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs_fname = fnames$epochs) %>%
-  set_names(comps$name) %>%
-  bind_cols(epochs$metadata, .) %T>%
-  write_tsv(fnames$trials) -> aha
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs_fname = fnames$epochs, grand = TRUE, data_only = TRUE) %>%
-  saveRDS(fnames$gavgs)
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(aha$participant), .before = 1) %>%
-  write_csv(fnames$conditions)
-
-# Get standard EasyCap electrode positions and project to 2D space
-py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
-  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
-  read_tsv(col_types = cols()) %>%
-  rename(electrode = Site) %>%
-  inner_join(tibble(electrode = epochs$ch_names), ., by = "electrode") %>%
-  mutate(
-    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
-    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
-  ) %>%
-  write_csv(fnames$montage)
-```
-
-```{r exp1-models, eval=rerun_models}
-# Load preprocessed single-trial data
-read_tsv("analysis/export/aha-trials.csv", col_types = cols()) %>%
+# Check if single-trial data are available
+if (file.exists(fnames$trials)) {
+
+  # If so, load preprocessed single-trial data
+  read_tsv(fnames$trials, col_types = cols()) %>%
+
     # Factorize columns
@@
       item = factor(item)
-  ) %>%
+    ) -> aha
+
+} else {
+
+  # If not, we preprocess the behvarioral and EEG data
+  paste0("data/raw/rt/exp", 1:2) %>%
+    map(list.files, pattern = ".txt", full.names = TRUE) %>%
+    map(map, function(txt_fname) {
+
+      # Read the behavioral log file
+      suppressWarnings(read_tsv(txt_fname, col_types = cols())) %>%
+
+        # Rename columns for participant and item IDs
+        rename(participant = VPNummer, item = StimID) %>%
+
+        # Add a column for the part of the experiment
+        mutate(part = case_when(
+          Wdh %in% c(211, 231) ~ "I",
+          Wdh %in% c(212, 232) ~ "II",
+          Wdh %in% c(213, 233) ~ "III",
+          Wdh == 234 ~ "IV"
+        ) %>% as_factor()) %>%
+
+        # Remove filler stimuli (i.e.,well-known objects)
+        filter(bek_unbek != "bekannt") -> dat
+
+      # Assign stimuli to conditions based on keywords and button presses in Part II
+      excl_known <- dat %>%
+        filter(part == "I" & Tastencode == 201) %>%
+        pull(item)
+      excl_informed <- dat %>%
+        filter(part == "II" & Bed == "richtig" & !Tastencode %in% c(201, 202)) %>%
+        pull(item)
+      excl_naive <- dat %>%
+        filter(part == "II" & Bed == "falsch" & !Tastencode %in% c(203, 204)) %>%
+        pull(item)
+      informed <- dat %>%
+        filter(part == "II" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>%
+        pull(item)
+      naive <- dat %>%
+        filter(part == "II" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>%
+        pull(item)
+
+      # Create a new condition for these experimental condition
+      dat %<>% mutate(condition = case_when(
+        item %in% excl_known ~ "Excl_known",
+        item %in% excl_informed ~ "Excl_informed",
+        item %in% excl_naive ~ "Excl_naive",
+        item %in% informed ~ "Informed",
+        item %in% naive ~ "Naive"
+      ) %>% factor(levels = c(
+        "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
+      ))) %>%
+
+        # Return only relevant columns
+        select(part, condition, participant, item, RT) %>%
+        return()
+    }) -> behav
+
+  # Avoid duplicate participant labels across the two experiments
+  behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))
+
+  # Merge behavioral data for all participants into a single list
+  behav %<>% flatten()
+
+  # List BrainVision header file names for preprocessing
+  paste0("data/raw/eeg/exp", 1:2) %>%
+    list.files(pattern = ".vhdr", full.names = TRUE) -> fnames$vhdr
+
+  # # Do the actual preprocessing in MNE-Python
+  # exec(
+  #   .fn = py$preproc_all,
+  #   vhdr_fnames = fnames$vhdr,
+  #   metadatas = behav,
+  #   output_fname = fnames$epochs,
+  #   !!!preproc_params
+  # ) -> epochs
+  # 
+  # # Compute mean ERP amplitudes and bind to the behavioral data
+  # pmap_dfc(comps, py$compute_erps, epochs_fname = fnames$epochs) %>%
+  #   set_names(comps$name) %>%
+  #   bind_cols(epochs$metadata, .) %T>%
+  #   write_tsv(fnames$trials) -> aha
+  # 
+  # # Compute grand averages per part and condition
+  # py$compute_evokeds(epochs_fname = fnames$epochs, grand = TRUE, data_only = TRUE) %>%
+  #   saveRDS(fnames$gavgs)
+  # 
+  # # Backup number of stimuli assigned to each condition for all participants
+  # map(behav, function(x) table(x$condition) / 3) %>%
+  #   bind_rows() %>%
+  #   mutate(Participant = unique(aha$participant), .before = 1) %>%
+  #   write_csv(fnames$conditions)
+  # 
+  # # Get standard EasyCap electrode positions and project to 2D space
+  # py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
+  #   list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
+  #   read_tsv(col_types = cols()) %>%
+  #   rename(electrode = Site) %>%
+  #   inner_join(tibble(electrode = epochs$ch_names), ., by = "electrode") %>%
+  #   mutate(
+  #     x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
+  #     y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
+  #   ) %>%
+  #   write_csv(fnames$montage)
+
+  # Do the preprocessing again, this time without filtering (for TFR)
+  preproc_params$l_freq <- py_none()
+  preproc_params$h_freq <- py_none()
+  preproc_params$reject <- py_none()
+  exec(
+    .fn = py$preproc_all,
+    vhdr_fnames = fnames$vhdr,
+    metadatas = behav,
+    output_fname = fnames$epochs_unf,
+    !!!preproc_params
+  ) -> epochs_unf
+}
+
+# Check number of rejected epochs
+aha %>%
+  group_by(participant) %>%
+  tally() %>%
+  mutate(n = 360 - n) %>%
+  pull(n) -> rejected
+mean(rejected)    # Mean
+median(rejected)  # Median
+range(rejected)   # Range
+```
+
+```{r, models_freq}
 # Remove any trials excluded from conditions
+aha %>%
   filter(condition %in% c("Informed", "Naive")) %>%
@@
 
-# Specify model formula and follow-up contrasts
+# Specify model formula
 form <- erp ~ part * condition +
@@
   (part * condition | item)
+
+# Specify follow-up comparisons
 specs <- pairwise ~ condition | part
 
-# Calculate linear mixed-effects models and contrasts
+# Calculate linear mixed-effects models and follow-up comparisons
 map(comps$name, function(comp, formula = form, data = aha, specs = specs) {
-  require(afex)
-  require(emmeans)
   data %<>% rename(erp = all_of(comp))
-  mod <- mixed(
-    formula,
-    data,
-    method = "S",
-    check_contrasts = FALSE,
-    all_fit = TRUE
-  )
+  mod <- lmer(formula, data, all_fit = TRUE)
+  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
   em <- emmeans(mod, specs = specs, infer = TRUE, data = data)
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/aha_models_freq.RDS") -> mods_freq
-```
-
-```{r exp1-import}
-# Load average number of objects per condition
-(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
-   summarise(across(.cols = -Participant, .fns = mean)) %>%
-   slice(1) %>% unlist() -> objects_exp1)
-
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
-    ),
-    participant = factor(participant),
-    item = factor(item)
-  ) -> aha
-
-# Check number of rejected epochs
-aha %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n) -> rejected_exp1
-mean(rejected_exp1)    # Mean
-median(rejected_exp1)  # Median
-range(rejected_exp1)   # Range
-
-# Load grand-averaged ERPs and linear mixed models
-evokeds_exp1 <- readRDS("analysis/export/exp1-gaverages.RDS")
-models_exp1 <- readRDS("analysis/export/exp1-models.RDS")
+  saveRDS(fnames$models_freq) -> mods_freq
 ```
@@
 
-```{python tfr, eval=FALSE}
+```{python, tfr}
+from mne.time_frequency import tfr_morlet
+from mne.channels import find_ch_adjacency
+from mne.stats import spatio_temporal_cluster_test
+
+epochs_unf = mne.read_epochs(r.fnames["epochs_unf"])
+epochs_ptII_informed = epochs_unf["part == 'II' & condition == 'Informed'"]
+epochs_ptII_naive = epochs_unf["part == 'II' & condition == 'Naive'"]
+
+evokeds = compute_evokeds(
+  epochs_fname=r.fnames["epochs_unf"], grand=False, data_only=False
+)
+
+evokeds_informed = evokeds["II"]["Informed"]
+evokeds_naive = evokeds["II"]["Naive"]
+
+X1 = np.array([evokeds.data for evokeds in evokeds_informed])
+X2 = np.array([evokeds.data for evokeds in evokeds_naive])
+X1 = np.transpose(X1, [0, 2, 1])
+X2 = np.transpose(X2, [0, 2, 1])
+X = [X1, X2]
+
+adjacency, ch_names = find_ch_adjacency(evokeds["II"]["Informed"][0].info, ch_type="eeg")
+
+cluster_stats = spatio_temporal_cluster_test(
+  X=X,
+  n_permutations=1000,
+  tail=0,
+  n_jobs=1,
+  buffer_size=None,
+  adjacency=adjacency,
+)
+
+p_accept = 0.05
+T_obs, clusters, p_values, _ = cluster_stats
+good_cluster_inds = np.where(p_values < p_accept)[0]
+
+freqs = np.logspace(*np.log10([6, 35]), num=8)
+n_cycles = freqs / 2.
+
+tfr_ptII_informed = tfr_morlet(
+  epochs_ptII_informed,
+  freqs=freqs,
+  n_cycles=n_cycles,
+  decim=2,
+  return_itc=False,
+  average=False,
+)
+tfr_ptII_naive = tfr_morlet(
+  epochs_ptII_naive,
+  freqs=freqs,
+  n_cycles=n_cycles,
+  decim=2,
+  return_itc=False,
+  average=False,
+)
+
+tfr_ptII_informed.apply_baseline(mode='ratio', baseline=(None, 0))
+tfr_ptII_naive.apply_baseline(mode='ratio', baseline=(None, 0))
+
+adjacency, ch_names = find_ch_adjacency(epochs_ptII_informed.info, ch_type="eeg")
+
+spatio_temporal_cluster_test(X, n_permutations=1000,
+                                             threshold=threshold, tail=1,
+                                             n_jobs=1, buffer_size=None,
+                                             adjacency=adjacency)
+
+```
+
+```{python tfr_old, eval=FALSE}
 import mne
@@
 # )
-# epochs.save("analysis/export/vp04-epo.fif")
-
-epochs = mne.read_epochs("analysis/export/unf-exp1-epo.fif")
+# epochs.save("data/processed/vp04-epo.fif")
+
+epochs = mne.read_epochs("data/processed/unf-exp1-epo.fif")
 
@@
 # Load sample time points and electrode montage
-montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())
+montage <- read_csv("data/processed/aha-montage.csv", col_types = cols())
 
@@
 # Backup epochs to the export folder
-epochs_exp2$save("analysis/export/exp2-epo.fif")
+epochs_exp2$save("data/processed/exp2-epo.fif")
 
@@
   bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
-  write_tsv("analysis/export/exp2-data.tsv") -> data_exp2
+  write_tsv("data/processed/exp2-data.tsv") -> data_exp2
 
@@
 py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp2-gaverages.RDS")
+  saveRDS("data/processed/exp2-gaverages.RDS")
 
@@
   mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp2-objects.tsv")
+  write_tsv("data/processed/exp2-objects.tsv")
 
@@
 # Load preprocessed single-trial data
-read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
+read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
   # Factorize columns
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp2-models.RDS") -> models_exp2
+  saveRDS("data/processed/exp2-models.RDS") -> models_exp2
 ```
@@
 # Load average number of objects per condition
-(read_tsv("analysis/export/exp2-objects.tsv", col_types = cols()) %>%
+(read_tsv("data/processed/exp2-objects.tsv", col_types = cols()) %>%
    summarise(across(.cols = -Participant, .fns = mean)) %>%
@@
 # Load grand-averaged ERPs and linear mixed models
-evokeds_exp2 <- readRDS("analysis/export/exp2-gaverages.RDS")
-models_exp2 <- readRDS("analysis/export/exp2-models.RDS")
+evokeds_exp2 <- readRDS("data/processed/exp2-gaverages.RDS")
+models_exp2 <- readRDS("data/processed/exp2-models.RDS")
 ```
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-models.RDS") -> models_joint
+  saveRDS("data/processed/joint-models.RDS") -> models_joint
 ```
@@
 # Load linear mixed models
-models_joint <- readRDS("analysis/export/joint-models.RDS")
+models_joint <- readRDS("data/processed/joint-models.RDS")
 
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-control-models.RDS") -> models_joint_control
+  saveRDS("data/processed/joint-control-models.RDS") -> models_joint_control
 ```
@@
 # Load linear mixed models
-models_joint_control <- readRDS("analysis/export/joint-control-models.RDS")
+models_joint_control <- readRDS("data/processed/joint-control-models.RDS")
 
@@
 # Backup epochs to the export folder
-epochs_exp3$save("analysis/export/exp3-epo.fif")
+epochs_exp3$save("data/processed/exp3-epo.fif")
 
@@
   bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
-  write_tsv("analysis/export/exp3-data.tsv") -> data_exp3
+  write_tsv("data/processed/exp3-data.tsv") -> data_exp3
 
@@
 py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp3-gaverages.RDS")
+  saveRDS("data/processed/exp3-gaverages.RDS")
 
@@
   mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp3-objects.tsv")
+  write_tsv("data/processed/exp3-objects.tsv")
 
@@
 # Load preprocessed single-trial data
-read_tsv("analysis/export/exp3-data.tsv", col_types = cols()) %>%
+read_tsv("data/processed/exp3-data.tsv", col_types = cols()) %>%
   # Factorize columns
@@
   set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp3-models.RDS") -> models_exp3
+  saveRDS("data/processed/exp3-models.RDS") -> models_exp3
 ```

### 2021-05-04 analysis/sourceloc.py

@@ -1,0 +1,87 @@
+import os.path as op
+import mne
+import numpy as np
+from mne.minimum_norm import make_inverse_operator, apply_inverse
+from pyvistaqt import BackgroundPlotter
+import matplotlib.pyplot as plt
+
+# Download fsaverage files
+fs_dir = mne.datasets.fetch_fsaverage(verbose=True)
+subjects_dir = op.dirname(fs_dir)
+
+# The files live in:
+subject = 'fsaverage'
+trans = 'fsaverage'  # MNE has a built-in fsaverage transformation
+src = op.join(fs_dir, 'bem', 'fsaverage-ico-5-src.fif')
+bem = op.join(fs_dir, 'bem', 'fsaverage-5120-5120-5120-bem-sol.fif')
+
+# Load and process EEG data
+vhdr_fname = "../data/eeg/exp1/Vp0004.vhdr"
+raw = mne.io.read_raw_brainvision(vhdr_fname, scale=1e6, preload=True)
+raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
+raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
+raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
+montage = mne.channels.make_standard_montage("easycap-M1")
+raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
+raw.set_montage(montage=montage)
+raw.set_eeg_reference("average", projection=True)
+
+# # Check that the locations of EEG electrodes is correct with respect to MRI
+# mne.viz.plot_alignment(
+#     raw.info, src=src, eeg=['original', 'projected'], trans=trans,
+#     show_axes=True, mri_fiducials=True, dig='fiducials')
+
+fwd = mne.make_forward_solution(raw.info, trans=trans, src=src, bem=bem, meg=False, eeg=True, n_jobs=1)
+print(fwd)
+
+# Use fwd to compute the sensitivity map for illustration purposes
+eeg_map = mne.sensitivity_map(fwd, ch_type='eeg', mode='fixed')
+brain = eeg_map.plot(time_label='EEG sensitivity', subjects_dir=subjects_dir,clim=dict(lims=[5, 50, 100]))
+
+# Read epochs
+epochs = mne.read_epochs("export/exp1-epo.fif")
[…]

### 2021-05-04 analysis/tfr.R

@@ -1,0 +1,18 @@
+library(reticulate)
+library(tidyverse)
+library(magrittr)
+library(eegUtils)
+
+read_csv("data/processed/aha-montage.csv", col_types = cols()) %>%
+  mutate(amplitude = py$dat_diff) %>%
+  topoplot(limits = c(-10, 10), palette = "viridis", contour = FALSE)
+
+py$avgs["III"][[1]] %>%
+  t() %>%
+  as_tibble() %>%
+  mutate(time = py$tfr$times) %>%
+  pivot_longer(-time, names_to = "frequency", values_to = "power_perc") %>%
+  mutate(frequency = factor(frequency, levels = unique(frequency), labels = py$freqs)) %>%
+  ggplot(aes(x = time, y = frequency, fill = power_perc)) +
+  geom_raster() +
+  scale_fill_viridis_c(limits = c(-1, 1), oob = scales::squish)

### 2021-05-04 analysis/tfr.py

@@ -1,0 +1,175 @@
+# Load modules
+from mne import read_epochs, grand_average
+from mne.channels import combine_channels, find_ch_adjacency
+from mne.stats import spatio_temporal_cluster_test
+from mne.time_frequency import read_tfrs, tfr_morlet
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Define frequencies and number of cycles
+freqs = np.arange(6, 51, step=2)
+# n_cycles = np.linspace(3, 10, num=len(freqs))
+n_cycles = freqs / 2.
+
+# Load epochs
+epochs = read_epochs("data/processed/aha-unf-epo.fif")
+
+# # Remove irrelevant conditions
+# epochs = epochs["condition == ['Informed', 'Naive']"]
+
+# Downsample and crop
+epochs.resample(sfreq=250)
+epochs.crop(tmin=-0.25, tmax=0.85)
+
+# Define custom function to compute single trial power for eqch frequency
+def compute_power(epochs, freq, n_cycles):
+    tfr = tfr_morlet(
+        epochs,
+        freq,
+        n_cycles,
+        use_fft=True,
+        return_itc=False,
+        average=False
+    )
+    tfr.apply_baseline(baseline=(None, 0), mode="percent")
+    return(np.float32(tfr.data))
+
+# Apply to our epochs
+tfr = [
+    compute_power(epochs, [freq], n_cycles) for freq, n_cycles in zip(freqs, n_cycles)
+]
+
+# Combine into one big array
+tfr = np.array(tfr, dtype="float32")
+
+# Compute single trial power
+tfr = tfr_morlet(epochs, freqs, n_cycles, use_fft=True, return_itc=False, average=False)
+del epochs
+
+# Reduce memory by changing the data type
+tfr.data = np.float32(tfr.data)
+
+# Backup
+tfr.save("data/processed/aha-tfr.h5")
+
+# Read preprocessed power
+tfr = read_tfrs("data/processed/aha-tfr.h5")[0]
+
+# Baseline correction
+tfr.apply_baseline(baseline=(None, 0), mode="percent")
+
+# Define helper function to extract averaged TFR data
+def tfr_to_array(tfr, query, axis_flatten=(0, 1)):
+    return(np.mean(tfr[query].data, axis=axis_flatten))
+
[…]

### 2021-05-11 code/manuscript.Rmd
new preprocessing script

--- 2021-05-04 analysis/manuscript.Rmd
@@
 shorttitle        : "Semantic Knowledge and Unfamiliar Objects"
-
 author: 
@@
     email         : "rasha.abdel.rahman@hu-berlin.de"
-
 affiliation:
@@
     institution   : "Fachhochschule des Mittelstands"
-
 authornote: |
@@
 
+  We have no conflict of interest to disclose.
   The preprocessed data and code for this study are openly available at https://osf.io/uksbc/.
-
-  We have no conflict of interest to disclose.
-
 abstract: |
@@
 keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
-
 floatsintext      : yes
@@
 draft             : no
-
-bibliography      : "manuscript_files/r-references.bib"
-csl               : "manuscript_files/apa.csl"
+bibliography      : "misc/bibliography.bib"
+csl               : "misc/apa.csl"
 zotero            : "aha"
@@
     latex_engine  : "xelatex"
-
 editor_options: 
   chunk_output_type: console
-
 header-includes:
@@
 
-# Load helper functions for plots and tables
-source("analysis/manuscript_files/functions_plots_tables.R")
-
-# Load bibliography file
-r_refs("analysis/manuscript_files/r-references.bib")
+# Load custom helper functions and bibliography
+pp <- import_from_path("preprocessing", path = "code")
+source("code/plots_tables.R")
+r_refs("misc/bibliography.bib")
 
@@
 )
+
+# Re-run preprocessing and/or model fitting?
+rerun_preprocessing <- TRUE
+rerun_model_fitting <- TRUE
 ```
@@
 
-```{python, erp_funcs}
-# Import libraries
-import mne
-import numpy as np
-
-# Define function for preprocessing a single participant
-def preproc(
-    vhdr_fname,
-    metadata,
-    n_components,
-    method,
-    l_freq,
-    h_freq,
-    event_id,
-    tmin,
-    tmax,
-    baseline,
-    reject,
-):
-    # Read EEG data in microvolts
-    raw = mne.io.read_raw_brainvision(vhdr_fname, scale=1e6, preload=True)
-    # Create virtual EOG channels
-    raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
-    raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
-    raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
-    # Add EasyCap electrode layout, removing any excessive channels
-    montage = mne.channels.make_standard_montage("easycap-M1")
-    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
-    raw.set_montage(montage=montage)
-    # Re-reference to common average
-    raw, _ = mne.set_eeg_reference(raw, "average")
-    # Run ICA on a copy of the data
-    filt_raw = raw.copy()
-    filt_raw.load_data().filter(l_freq=1, h_freq=None)
-    ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
-    ica.fit(filt_raw)
-    # Remove bad components based on correlations with EOG
-    eog_indices, eog_scores = ica.find_bads_eog(raw)
-    ica.exclude = eog_indices
-    raw = ica.apply(raw)
-    # Apply band-pass filter
-    raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
-    # Epoching including baseline correction
-    events, _ = mne.events_from_annotations(raw, verbose=False)
-    epochs = mne.Epochs(
-        raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True
-    )
-    # Add behavioral data
-    epochs.metadata = metadata
-    # Reject bad epochs
-    epochs = epochs.drop_bad(reject=reject)
-    return epochs
-
-# Define function for preprocessing a list of participants
-def preproc_all(
-    vhdr_fnames,
-    metadatas,
-    output_fname,
-    n_components,
-    method,
-    l_freq,
-    h_freq,
-    event_id,
-    tmin,
-    tmax,
-    baseline,
-    reject,
-):
-    # Do the actual preprocessing
-    epochs = [
-        preproc(
-            vhdr_fname=vhdr_fname,
-            metadata=metadata,
-            n_components=n_components,
-            method=method,
-            l_freq=l_freq,
-            h_freq=h_freq,
-            event_id=event_id,
-            tmin=tmin,
-            tmax=tmax,
-            baseline=baseline,
-            reject=reject,
-        )
-        for vhdr_fname, metadata in zip(vhdr_fnames, metadatas)
-    ]
-    # Concatenate all participants and save
-    epochs = mne.epochs.concatenate_epochs(epochs)
-    epochs.save(output_fname, overwrite=True)
-    del epochs
-    # Return the epochs without loading the actual data
-    epochs = mne.read_epochs(output_fname, preload=False)
-    return epochs
-
-# Define function to compute averaged waveforms by part and condition
-def compute_evokeds(epochs_fname, grand=True, data_only=True):
-    # Read preprocessed epochs
-    epochs = mne.read_epochs(epochs_fname)
-    # Define lists of participants, parts, and conditions
-    ps = epochs.metadata["participant"].unique()
-    pts = ["I", "II", "III"]
-    cns = ["Informed", "Naive"]
-    # Define function to compute a single by-participant waveform
-    def compute_evoked(epochs, pt, cn, p):
-        query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
-        return epochs[query].average()
-    # Create a dict with by-participant waveforms nested in conditions nested in parts
-    avgs = {pt: {cn: [compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
-    # If needed, compute grand-averaged waveforms across participants
-    if grand:
-        avgs = {pt: {cn: mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
-    # If needed, extract only the data from the evoked MNE objects
-    if data_only:
-        if grand:
-            avgs = {pt: {cn: avgs[pt][cn].data for cn in cns} for pt in pts}
-        else:
-            ps_num = range(0, len(ps))
-            avgs = {pt: {cn: [avgs[pt][cn][p].data for p in ps_num] for cn in cns} for pt in pts}
-    return avgs
-
-# Define function to compute single-trial mean ERP amplitudes from epochs
-def compute_erps(epochs_fname, name, tmin, tmax, roi):
-    # Read preprocessed epochs
-    epochs = mne.read_epochs(epochs_fname)
-    # Average across electrodes in the ROI
-    roi_idx = mne.pick_channels(epochs.ch_names, roi)
-    epochs_roi = mne.channels.combine_channels(epochs, dict(roi=roi_idx))
-    # Average across samples in the time window
-    tmin_s, tmax_s = tmin / 1000, tmax / 1000
-    times_idx = np.where(np.logical_and(epochs.times >= tmin_s, epochs.times <= tmax_s))
-    erps = epochs_roi.get_data()[:, 0, times_idx].mean(axis=(1, 2))
-    return erps
-
-```
-
 ```{r, preprocessing}
+# Define ERP components of interest
+erp_components <- tibble(
+  name = c("P1", "N170", "N400"),
+  tmin = c(0.1, 0.15, 0.4),
+  tmax = c(0.15, 0.2, 0.7),
+  roi = list(
+    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
+    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
+    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
+  )
+)
+
+# Define frequencies and # of cycles for TFR analysis
+tfr_freqs <- seq(4, 50, by = 2)
+tfr_cycles <- seq(3, 10, length.out = length(tfr_freqs))
+
+# Run the preprocessing if requested (only works if the raw data are available)
+if (rerun_preprocessing) {
+
+  # List EEG files and behavioral log files
+  fname_vhdr <- c(
+    list.files("data/raw/eeg/exp1", pattern = ".vhdr", full.names = TRUE),
+    list.files("data/raw/eeg/exp2", pattern = ".vhdr", full.names = TRUE)
+  )
+  fname_log <- c(
+    list.files("data/raw/rt/exp1", pattern = ".txt", full.names = TRUE),
+    list.files("data/raw/rt/exp2", pattern = ".txt", full.names = TRUE)
+  )
+
+  # Generate new BIDS-style subject IDs
+  1:length(fname_vhdr) %>%
+    str_pad(width = 2, pad = 0) %>%
+    paste0("sub-", .) -> subject_id
+
+  # Perform preprocessing for all subjects using MNE-Python (see code/preprocessing.py)
+  tibble(fname_vhdr, fname_log, subject_id) %>%
+    pwalk(
+      pp$preprocess,
+      output_dir = "data/preprocessed",
+      eog_names = c("HEOG", "VEOG"),
+      eog_anodes = c("F9", "Auge_u"),
+      eog_cathodes = c("F10", "Fp1"),
+      montage_kind = "easycap-M1",
+      ica_components = as.integer(15),
+      ica_method = "fastica",
+      ica_seed = as.integer(1234),
+      hipass = 0.1,
+      lowpass = 30,
+      event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
+      tmin = -0.5,
+      tmax = 1.489,
+      baseline = tuple(-0.2, 0),
+      reject = dict(eeg = 200e-6),
+      erp_components = erp_components,
+      condition_cols = c("part", "condition"),
+      tfr_freqs = tfr_freqs,
+      tfr_cycles = tfr_cycles,
+      tfr_sfreq_downsampled = 250,
+      tfr_crop = tuple(-0.2, 0.8)
+    )
+}
+
+please_stop_here()
+```
+
+```{r, preprocessing_old}
 # Define ERP components of interest

### 2021-05-11 analysis/preprocessing.py

@@ -1,0 +1,243 @@
+from glob import glob
+from os import makedirs, removedirs
+
+import numpy as np
+import pandas as pd
+from mne import Epochs, events_from_annotations, pick_channels, set_bipolar_reference
+from mne.channels import combine_channels, make_standard_montage
+from mne.io import read_raw_brainvision
+from mne.preprocessing import ICA
+from mne.time_frequency import tfr_morlet
+
+# fnames_vhdr = glob("../data/raw/eeg/exp*/*.vhdr")
+# fnames_log = glob("../data/raw/rt/exp*/*.txt")
+
+# tfr_freqs = np.arange(4, 51, step=2)
+# tfr_cycles = np.linspace(3, 10, num=len(tfr_freqs))
+
+# event_id = {"match": 221, "nonmatch": 222}
+# condition_cols = ["part", "condition"]
+
+# subject_id = "sub-02"
+# output_basedir = "../data/"
+
+# erp_components = pd.DataFrame(
+#     {
+#         "name": ["P1", "N170", "N400"],
+#         "tmin": [0.1, 0.15, 0.4],
+#         "tmax": [0.15, 0.2, 0.7],
+#         "roi": [
+#             ["PO3", "PO4", "POz", "O1", "O2", "Oz"],
+#             ["P7", "P8", "PO7", "PO8", "PO9", "PO10"],
+#             ["C1", "C2", "Cz", "CP1", "CP2", "CPz"],
+#         ],
+#     }
+# )
+
+
+def preprocess(
+    fname_vhdr=None,
+    fname_log=None,
+    subject_id=None,
+    output_basedir=None,
+    eog_names=["HEOG", "VEOG"],
+    eog_anodes=["F9", "Auge_u"],
+    eog_cathodes=["F10", "Fp1"],
+    montage_kind="easycap-M1",
+    ica_components=15,
+    ica_method="fastica",
+    ica_seed=1234,
+    hipass=0.1,
+    lowpass=30,
+    event_id=None,
+    tmin=-0.5,
+    tmax=1.489,
+    baseline=(-0.2, 0),
+    reject={"eeg": 200e-6},
+    erp_components=None,
+    condition_cols=["part", "condition"],
+    tfr_freqs=None,
+    tfr_cycles=None,
+    tfr_sfreq_downsampled=250,
+    tfr_crop=(-0.2, 0.8),
+):
+    """
+    Computes epochs, evoked potentials, and single trial power from a raw EEG data set.
+    """
+
[…]

### 2021-05-11 code/plots_tables.R

@@ -1,0 +1,464 @@
+####################################################################################################
+## FUNCTIONS TO CREATE PLOTS AND TABLES ##
+####################################################################################################
+
+# Function to plot the trial structure
+plot_trials <- function() {
+  suppressMessages(require(magick))
+  color_informed <- viridisLite::viridis(1, begin = 0.1)
+  color_naive <- viridisLite::viridis(1, begin = 0.5)
+  ggplot() +
+    coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
+    ## PART II ##
+    # Title
+    annotate("text", x = 0, y = 97.2, label = "Insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
+    # Arrow
+    annotate("segment", x = -30, xend = 24, y = 79, yend = 85, arrow = arrow(length = unit(0.1, "inches"))) +
+    # Squares
+    annotate("rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75, color = "black", fill = "white") +
+    annotate("rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65, color = color_informed, fill = "white") +
+    annotate("rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89, color = color_naive, fill = "white") +
+    annotate("rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79, color = "black", fill = "white") +
+    annotate("rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81, color = "black", fill = "white") +
+    annotate("text", x = -27, y = 65.3, label = "+", size = 20 / .pt, family = "Helvetica") +
+    annotate("text", x = -9, y = 55, label = "potatoes\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
+    annotate("text", x = -9, y = 79, label = "message\nsignaling", size = 10 / .pt, family = "Helvetica", color = color_naive) +
+    annotate("text", x = 9, y = 67, label = "*", size = 30 / .pt, family = "Helvetica") +
+    draw_image("analysis/manuscript_files/potato_masher.png", x = 18, y = 62, width = 18, height = 18) +
+    # Timings
+    annotate("text", x = -9, y = 67.3, label = "or", size = 10 / .pt, family = "Helvetica") +
[…]

### 2021-05-11 code/preprocessing.py

@@ -1,0 +1,235 @@
+"""
+PREPROCESSING FUNCTIONS
+
+Created May 2021 by Alexander Enge (alexander.enge@hu-berlin.de)
+
+Contains one big function and some smaller helper functions to preprocess the EEG data
+for a single participant. Using the MNE-Python module and friends, it reads the raw EEG
+and behavioral data and extracts (a) the EEG epochs around the presentation of each
+unfamiliar object (b) the single trial mean ERP amplitudes at certain regions of
+interest, (c) averaged evoked potentials from at each electrode, and (d) single trial
+EEG power at a pre-specified range of frequencies.
+
+"""
+
+from glob import glob
+from os import makedirs, removedirs
+
+import numpy as np
+import pandas as pd
+from mne import Epochs, events_from_annotations, pick_channels, set_bipolar_reference
+from mne.channels import combine_channels, make_standard_montage
+from mne.io import read_raw_brainvision
+from mne.preprocessing import ICA
+from mne.time_frequency import tfr_morlet
+
+
+def preprocess(
+    fname_vhdr=None,
+    fname_log=None,
+    subject_id=None,
+    output_dir=None,
+    eog_names=["HEOG", "VEOG"],
+    eog_anodes=["F9", "Auge_u"],
+    eog_cathodes=["F10", "Fp1"],
+    montage_kind="easycap-M1",
+    ica_components=15,
+    ica_method="fastica",
+    ica_seed=1234,
+    hipass=0.1,
+    lowpass=30,
+    event_id=None,
+    tmin=-0.5,
+    tmax=1.489,
+    baseline=(-0.2, 0),
+    erp_components=None,
+    reject={"eeg": 200e-6},
+    condition_cols=["part", "condition"],
+    tfr_freqs=None,
+    tfr_cycles=None,
+    tfr_sfreq_downsampled=250,
+    tfr_crop=(-0.2, 0.8),
+):
+    """
+    Computes epochs, evoked potentials, and single trial power from a raw EEG data set.
+    """
+
+    # Create output directory if it doesn't exist
+    makedirs(output_dir, exist_ok=True)
+
+    # Read raw data in microvolts
+    raw = read_raw_brainvision(fname_vhdr, preload=True)
+
+    # Create virtual EOG channels
+    raw = set_bipolar_reference(
+        raw,
+        anode=eog_anodes,
+        cathode=eog_cathodes,
+        ch_name=eog_names,
+        drop_refs=False,
+    )
[…]

### 2021-05-13 code/manuscript.Rmd
add average tfr

@@
 rerun_model_fitting <- TRUE
+
+# File names for easier I/O
+fnames <- list(
+  montage = "data/processed/montage.csv",
+  evo_gavg = "data/processed/evo_gavg.csv",
+  evo_tfr_gavg = "data/processed/evo-tfr_gavg.csv",
+  evo_tfr_diff = "data/processed/evo-tfr_diff.csv",
+  evo_tfr_gavg_nochans = "data/processed/evo-tfr_gavg-nochans.csv",
+  evo_tfr_diff_nochans = "data/processed/evo-tfr_diff-nochans.csv"
+)
 ```
@@
 ```{r, preprocessing}
+# List EEG files and behavioral log files
+fname_vhdr <- c(
+  list.files("data/raw/eeg/exp1", pattern = ".vhdr", full.names = TRUE),
+  list.files("data/raw/eeg/exp2", pattern = ".vhdr", full.names = TRUE)
+)
+fname_log <- c(
+  list.files("data/raw/rt/exp1", pattern = ".txt", full.names = TRUE),
+  list.files("data/raw/rt/exp2", pattern = ".txt", full.names = TRUE)
+)
+
+# Generate new BIDS-style subject IDs
+seq(length(fname_vhdr)) %>%
+  str_pad(width = 2, pad = 0) %>%
+  paste0("sub-", .) -> subject_id
+
 # Define ERP components of interest
@@
 
-# Define frequencies and # of cycles for TFR analysis
+# Define frequencies and number of cycles for TFR analysis
 tfr_freqs <- seq(4, 50, by = 2)
@@
 
-# Run the preprocessing if requested (only works if the raw data are available)
+# Perform preprocessing for all subjects using MNE-Python (see code/preprocessing.py)
+# This will run only if `rerun_preprocessing = TRUE` and if the raw data are available
 if (rerun_preprocessing) {
 
-  # List EEG files and behavioral log files
-  fname_vhdr <- c(
-    list.files("data/raw/eeg/exp1", pattern = ".vhdr", full.names = TRUE),
-    list.files("data/raw/eeg/exp2", pattern = ".vhdr", full.names = TRUE)
-  )
-  fname_log <- c(
-    list.files("data/raw/rt/exp1", pattern = ".txt", full.names = TRUE),
-    list.files("data/raw/rt/exp2", pattern = ".txt", full.names = TRUE)
-  )
-
-  # Generate new BIDS-style subject IDs
-  1:length(fname_vhdr) %>%
-    str_pad(width = 2, pad = 0) %>%
-    paste0("sub-", .) -> subject_id
-
-  # Perform preprocessing for all subjects using MNE-Python (see code/preprocessing.py)
+  # Do the actual preprocessing
   tibble(fname_vhdr, fname_log, subject_id) %>%
@@
       erp_components = erp_components,
-      condition_cols = c("part", "condition"),
+      average_by = c("part", "condition", "subject_id"),
+      tfr_equalize = "condition == ['Informed', 'Naive']",
+      tfr_resample = py_none(),
       tfr_freqs = tfr_freqs,
       tfr_cycles = tfr_cycles,
-      tfr_sfreq_downsampled = 250,
       tfr_crop = tuple(-0.2, 0.8)
     )
+
+  # Get standard EasyCap electrode positions and project them into 2D space
+  read_csv("data/preprocessed/sub-01_tfr-evo.csv", col_types = cols()) %>%
+    select(-c(part, condition, subject_id, time, freq)) %>%
+    colnames() -> ch_names
+  import("mne.channels._standard_montage_utils")$MONTAGE_PATH %>%
+    paste0("/easycap-M1.txt") %>%
+    read_tsv(col_types = cols()) %>%
+    rename(electrode = Site) %>%
+    inner_join(tibble(electrode = ch_names), ., by = "electrode") %>%
+    mutate(
+      x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
+      y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
+    ) %>%
+    mutate(across(c(x, y), round, 3)) %>%
+    write_csv(fnames$montage)
 }
-
+```
+
+```{python, grand_averaging, eval=rerun_preproc}
+from os import makedirs
+
+import numpy as np
+import pandas as pd
+
+# Create output folder
+makedirs("data/processed", exist_ok=True)
+
+# Read evoked *potentials* for all subjects
+fname_evo_tfr = ["data/preprocessed/" + sub + "_evo.csv" for sub in r.subject_id]
+evo = [pd.read_csv(fname) for fname in fname_evo_tfr]
+evo = pd.concat(evo)
+
+# Average across subjects
+id_vars = ["part", "condition", "time"]
+evo = evo.groupby(id_vars, as_index=False).mean()
+evo.to_csv(r.fnames["evo_gavg"], float_format="%.3f", index=False)
+
+# Read evoked *power* for all subjects
+fname_evo_tfr = ["data/preprocessed/" + sub + "_tfr-evo.csv" for sub in r.subject_id]
+evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
+evo_tfr = pd.concat(evo_tfr)
+
+# Compute difference in power between conditions
+id_vars = ["part", "condition", "subject_id", "time", "freq"]
+electrodes = [col for col in evo_tfr.columns if (col not in id_vars)]
+evo_tfr_diff = (
+    evo_tfr.query("condition == 'Informed'")[electrodes]
+    - evo_tfr.query("condition == 'Naive'")[electrodes].values
+)
+evo_tfr_diff[id_vars] = evo_tfr.query("condition == 'Informed'")[id_vars]
+
+# Average first across subjects, then across electrodes
+id_vars.remove("subject_id")
+fnames = [r.fnames["evo_tfr_gavg"], r.fnames["evo_tfr_diff"]]
+fnames_nochans = [r.fnames["evo_tfr_gavg_nochans"], r.fnames["evo_tfr_diff_nochans"]]
+for df, fname, fname_nochans in zip([evo_tfr, evo_tfr_diff], fnames, fnames_nochans):
+    df = df.groupby(id_vars, as_index=False).mean()
+    df.to_csv(fname, float_format="%.3f", index=False)
+    df["power"] = df[electrodes].mean(axis=1)
+    df.drop(electrodes, axis=1, inplace=True)
+    df.to_csv(fname_nochans, float_format="%.3f", index=False)
+del df, evo_tfr, evo_tfr_diff
+```
+
+```{r, tfr_wip}
 please_stop_here()
-```
-
-```{r, preprocessing_old}
-# Define ERP components of interest
-comps <- tibble(
-  name = c("P1", "N170", "N400"),
-  tmin = c(100, 150, 400),
-  tmax = c(150, 200, 700),
-  roi = list(
-    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
-    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
-    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
-  )
-)
-
-# Define some filenames for I/O
-fnames <- list(
-  epochs = "data/processed/aha-epo.fif",
-  epochs_unf = "data/processed/aha-unf-epo.fif",
-  trials = "data/processed/aha-trials.csv",
-  gavgs = "data/processed/aha-gavgs.RDS",
-  conditions = "data/processed/aha-obj-per-cond.csv",
-  montage = "data/processed/aha-montage.csv",
-  models_freq = "data/processed/aha-models-freq.RDS"
-)
-
-# Define parameters for EEG preprocessing
-preproc_params <- list(
-  # Number of ICA components
-  n_components = as.integer(15),
-  # ICA methods
-  method = "fastica",
-  # Lower edge of pass-band filter
-  l_freq = 0.1,
-  # Upper edge of pass-band filter
-  h_freq = 30,
-  # Event trigger codes
-  event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
-  # Beginning of epochs in s
-  tmin = -0.5,
-  # End of epochs in s
-  tmax = 1.498,
-  # Baseline interval in s
-  baseline = tuple(-0.2, 0),
-  # Artifact rejection threshold in microvolts
-  reject = dict(eeg = 200)
-)
-
-# Check if single-trial data are available
-if (file.exists(fnames$trials)) {
-
-  # If so, load preprocessed single-trial data
-  read_tsv(fnames$trials, col_types = cols()) %>%
-
-    # Factorize columns
+
+# Read evoked power
+paste0("data/preprocessed/", subject_id, "_tfr-evo.csv") %>%
+  map(read_csv, col_types = cols())
+
+  map2(subject_id, function(fname, id) {
+    read_csv(fname, col_types = cols(), progress = FALSE) %>%
+      mutate(participant = id)
+  }) %>%
+  bind_rows() -> evo
+
+# Average across participants
+grouping <- c("part", "condition", "time", "freq")
+evo %<>%
+  group_by(across(all_of(grouping))) %>%
+  summarise(across(-participant, .fns = mean), .groups = "drop")
+
+# Average across channels
+evo %>%
+  pivot_longer(!all_of(grouping), names_to = "channel", values_to = "power") %>%
+  group_by(across(all_of(grouping))) %>%
+  summarise(power = mean(power), .groups = "drop") -> evo_all_channels
+
+# Average across conditions within parts
+evo_all_channels %>%
+  group_by(part, time, freq) %>%
+  summarise(power = mean(power), .groups = "drop") -> evo_all_channels_conds
+
+# Plot
+evo_all_channels_conds %>%
+  ggplot(aes(x = time, y = freq, fill = power)) +
+  facet_wrap(~part) +
+  geom_raster() +
+  scale_fill_viridis_c(limits = c(0, 2), oob = scales::squish) +
+  annotate("rect", xmin = 150, xmax = 400, ymin = 30, ymax = 50, color = "white", fill = NA) +
+  theme(aspect.ratio = 0.5) +
+  theme_minimal() +
+  coord_cartesian(expand = FALSE) +
+  ggsave("evo_all_channels_conds.pdf", width = 7, height = 2)
+
+# Compute differences between conditions
+evo_all_channels %>%
+  group_by(part, time, freq) %>%
+  mutate(power = power - power[condition == "Naive"]) %>%
+  filter(condition == "Informed") %>%
+  ggplot(aes(x = time, y = freq, fill = power)) +
+  facet_wrap(~part) +
+  geom_raster() +
+  scale_fill_viridis_c(limits = c(0, 1), oob = scales::squish) +
+  annotate("rect", xmin = 150, xmax = 400, ymin = 30, ymax = 50, color = "white", fill = NA) +
+  theme(aspect.ratio = 0.5) +
+  theme_minimal() +
+  coord_cartesian(expand = FALSE) +
+  ggsave("evo_all_channels_diff.pdf", width = 7, height = 2)
+```
+
+```{r, models_freq}
+# Read single trial data for all subjects
+paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
+  map(read_csv, col_types = cols()) %>%
+  bind_rows() %>%
   mutate(
     part = factor(part, levels = c("I", "II", "III")),
-      condition = factor(condition, levels = c(
-        "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
-      )),
-      participant = factor(participant),
-      item = factor(item)
-    ) -> aha
-
-} else {
-
-  # If not, we preprocess the behvarioral and EEG data
-  paste0("data/raw/rt/exp", 1:2) %>%
-    map(list.files, pattern = ".txt", full.names = TRUE) %>%
-    map(map, function(txt_fname) {
-
-      # Read the behavioral log file
-      suppressWarnings(read_tsv(txt_fname, col_types = cols())) %>%
-
-        # Rename columns for participant and item IDs
-        rename(participant = VPNummer, item = StimID) %>%
-
-        # Add a column for the part of the experiment
-        mutate(part = case_when(
-          Wdh %in% c(211, 231) ~ "I",
-          Wdh %in% c(212, 232) ~ "II",
-          Wdh %in% c(213, 233) ~ "III",
-          Wdh == 234 ~ "IV"
-        ) %>% as_factor()) %>%
-
-        # Remove filler stimuli (i.e.,well-known objects)
-        filter(bek_unbek != "bekannt") -> dat
-
-      # Assign stimuli to conditions based on keywords and button presses in Part II
-      excl_known <- dat %>%
-        filter(part == "I" & Tastencode == 201) %>%
-        pull(item)
-      excl_informed <- dat %>%
-        filter(part == "II" & Bed == "richtig" & !Tastencode %in% c(201, 202)) %>%
-        pull(item)
-      excl_naive <- dat %>%
-        filter(part == "II" & Bed == "falsch" & !Tastencode %in% c(203, 204)) %>%
-        pull(item)
-      informed <- dat %>%
-        filter(part == "II" & Bed == "richtig" & Tastencode %in% c(201, 202)) %>%
-        pull(item)
-      naive <- dat %>%
-        filter(part == "II" & Bed == "falsch" & Tastencode %in% c(203, 204)) %>%
-        pull(item)
-
-      # Create a new condition for these experimental condition
-      dat %<>% mutate(condition = case_when(
-        item %in% excl_known ~ "Excl_known",
-        item %in% excl_informed ~ "Excl_informed",
-        item %in% excl_naive ~ "Excl_naive",
-        item %in% informed ~ "Informed",
-        item %in% naive ~ "Naive"
-      ) %>% factor(levels = c(
-        "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
-      ))) %>%
-
-        # Return only relevant columns
-        select(part, condition, participant, item, RT) %>%
-        return()
-    }) -> behav
-
-  # Avoid duplicate participant labels across the two experiments
-  behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))
-
-  # Merge behavioral data for all participants into a single list
-  behav %<>% flatten()
-
-  # List BrainVision header file names for preprocessing
-  paste0("data/raw/eeg/exp", 1:2) %>%
-    list.files(pattern = ".vhdr", full.names = TRUE) -> fnames$vhdr
-
-  # # Do the actual preprocessing in MNE-Python
-  # exec(
-  #   .fn = py$preproc_all,
-  #   vhdr_fnames = fnames$vhdr,
-  #   metadatas = behav,
-  #   output_fname = fnames$epochs,
-  #   !!!preproc_params
-  # ) -> epochs
-  # 
-  # # Compute mean ERP amplitudes and bind to the behavioral data
-  # pmap_dfc(comps, py$compute_erps, epochs_fname = fnames$epochs) %>%
-  #   set_names(comps$name) %>%
-  #   bind_cols(epochs$metadata, .) %T>%
-  #   write_tsv(fnames$trials) -> aha
-  # 
-  # # Compute grand averages per part and condition
-  # py$compute_evokeds(epochs_fname = fnames$epochs, grand = TRUE, data_only = TRUE) %>%
-  #   saveRDS(fnames$gavgs)
-  # 
-  # # Backup number of stimuli assigned to each condition for all participants
-  # map(behav, function(x) table(x$condition) / 3) %>%
-  #   bind_rows() %>%
-  #   mutate(Participant = unique(aha$participant), .before = 1) %>%
-  #   write_csv(fnames$conditions)
-  # 
-  # # Get standard EasyCap electrode positions and project to 2D space
-  # py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
-  #   list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
-  #   read_tsv(col_types = cols()) %>%
-  #   rename(electrode = Site) %>%
-  #   inner_join(tibble(electrode = epochs$ch_names), ., by = "electrode") %>%
-  #   mutate(
-  #     x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
-  #     y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
-  #   ) %>%
-  #   write_csv(fnames$montage)
-
-  # Do the preprocessing again, this time without filtering (for TFR)
-  preproc_params$l_freq <- py_none()
-  preproc_params$h_freq <- py_none()
-  preproc_params$reject <- py_none()
-  exec(
-    .fn = py$preproc_all,
-    vhdr_fnames = fnames$vhdr,
-    metadatas = behav,
-    output_fname = fnames$epochs_unf,
-    !!!preproc_params
-  ) -> epochs_unf
-}
-
-# Check number of rejected epochs
-aha %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n) -> rejected
-mean(rejected)    # Mean
-median(rejected)  # Median
-range(rejected)   # Range
-```
-
-```{r, models_freq}
+    condition = factor(condition, levels = c("Informed", "Naive")),
+    subject_id = factor(subject_id),
+    item_id = factor(item_id)
+  ) %>%
+  na.omit() -> trials
+
+contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
+contrasts_part <- t(cbind(
+  c("I" = -1, "II" = 1, "III" = 0),
+  c("I" = 0, "II" = -1, "III" = 1)
+))
+
+# Apply these contrasts to the factors in the data
+contrasts(trials$condition) <- MASS::ginv(contrasts_condition)
+contrasts(trials$part) <- MASS::ginv(contrasts_part)
+
+formula <- N400 ~ part / condition + (1|subject_id) + (1|item_id)
+mod <- lmer(formula, data = trials)
+summary(mod)
+
 # Remove any trials excluded from conditions
@@
 
-```{python, tfr}
-from mne.time_frequency import tfr_morlet
-from mne.channels import find_ch_adjacency
-from mne.stats import spatio_temporal_cluster_test
-
-epochs_unf = mne.read_epochs(r.fnames["epochs_unf"])
-epochs_ptII_informed = epochs_unf["part == 'II' & condition == 'Informed'"]
-epochs_ptII_naive = epochs_unf["part == 'II' & condition == 'Naive'"]
-
-evokeds = compute_evokeds(
-  epochs_fname=r.fnames["epochs_unf"], grand=False, data_only=False
-  )
-
-  evokeds_informed = evokeds["II"]["Informed"]
-  evokeds_naive = evokeds["II"]["Naive"]
-
-  X1 = np.array([evokeds.data for evokeds in evokeds_informed])
-  X2 = np.array([evokeds.data for evokeds in evokeds_naive])
-  X1 = np.transpose(X1, [0, 2, 1])
-  X2 = np.transpose(X2, [0, 2, 1])
-  X = [X1, X2]
-
-  adjacency, ch_names = find_ch_adjacency(evokeds["II"]["Informed"][0].info, ch_type="eeg")
-
-  cluster_stats = spatio_temporal_cluster_test(
-    X=X,
-    n_permutations=1000,
-    tail=0,
-    n_jobs=1,
-    buffer_size=None,
-    adjacency=adjacency,
-    )
-
-    p_accept = 0.05
-    T_obs, clusters, p_values, _ = cluster_stats
-    good_cluster_inds = np.where(p_values < p_accept)[0]
-
-    freqs = np.logspace(*np.log10([6, 35]), num=8)
-    n_cycles = freqs / 2.
-
-    tfr_ptII_informed = tfr_morlet(
-      epochs_ptII_informed,
-      freqs=freqs,
-      n_cycles=n_cycles,
-      decim=2,
-      return_itc=False,
-      average=False,
-      )
-      tfr_ptII_naive = tfr_morlet(
-        epochs_ptII_naive,
-        freqs=freqs,
-        n_cycles=n_cycles,
-        decim=2,
-        return_itc=False,
-        average=False,
-        )
-
-        tfr_ptII_informed.apply_baseline(mode='ratio', baseline=(None, 0))
-        tfr_ptII_naive.apply_baseline(mode='ratio', baseline=(None, 0))
-
-        adjacency, ch_names = find_ch_adjacency(epochs_ptII_informed.info, ch_type="eeg")
-
-        spatio_temporal_cluster_test(X, n_permutations=1000,
-        threshold=threshold, tail=1,
-        n_jobs=1, buffer_size=None,
-        adjacency=adjacency)
-
-        ```
-
-        ```{python tfr_old, eval=FALSE}
-        import mne
-        import numpy as np
-        #import matplotlib.pyplot as plt
-
-        # epochs = preproc(
-        #   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
-        #   metadata=r.aha.query("participant == 'VP_04'"),
-        #   n_components=15,
-        #   method="fastica",
-        #   l_freq=None,
-        #   h_freq=None,
-        #   event_id=dict(match=221, mismatch=222),
-        #   tmin=-0.5,
-        #   tmax=1.498,
-        #   baseline=(-0.2, 0),
-        #   reject=dict(eeg=200)
-        # )
-        # epochs.save("data/processed/vp04-epo.fif")
-
-        epochs = mne.read_epochs("data/processed/unf-exp1-epo.fif")
-
-        evokeds = compute_evokeds(epochs_c, grand=True, data_only=False)
-        evokeds_i = evokeds["II"]["Informed"]
-        evokeds_n = evokeds["II"]["Naive"]
-
-        freqs = np.logspace(*np.log10([6, 35]), num=8)
-        n_cycles = freqs / 2.
-        power_i = mne.time_frequency.tfr_morlet(evokeds_i, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-        power_n = mne.time_frequency.tfr_morlet(evokeds_n, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-        power_i = power_i.apply_baseline(mode='mean', baseline=(-.400, -.100))
-        power_n = power_n.apply_baseline(mode='mean', baseline=(-.400, -.100))
-
-        power_d = power_i.copy()
-        power_d.data = power_i.data - power_n.data
-
-        power_d.plot()
-
-        # epochs.resample(250., npad='auto')
-
-        roi = r.comps["roi"][0] + r.comps["roi"][1]
-        idxs = np.where(np.in1d(epochs.ch_names, roi))
-
-        epochs_i = epochs["part == 'II' & condition == 'Informed'"].pick_channels(roi)
-        epochs_n = epochs["part == 'II' & condition == 'Naive'"].pick_channels(roi)
-
-        epochs_c = mne.channels.combine_channels(epochs, groups=dict(avg=range(62)))
-
-        epochs_c.metadata = epochs.metadata
-        epochs_s = epochs_c["part == 'II'"]
-        # epochs_i = epochs_s["condition == 'Informed'"]
-        # epochs_n = epochs_s["condition == 'Naive'"]
-
-        # power_i = mne.time_frequency.tfr_morlet(epochs_i, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-        # power_n = mne.time_frequency.tfr_morlet(epochs_n, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-        # power_d = power_i - power_n
-        # 
-        # power_d.plot([0], baseline=(-0.5, 0), mode='percent', vmin=-1, vmax=1)
-
-        # define frequencies of interest (log-spaced)
-        #freqs = np.logspace(*np.log10([6, 35]), num=8)
-        freqs = np.arange(3, 50, 1.6)
-        #n_cycles = freqs / 2.  # different number of cycle per frequency
-        n_cycles = np.linspace(3, 10, len(freqs))
-        power = mne.time_frequency.tfr_morlet(epochs_c, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-
-        power.plot([0], baseline=(-0.5, 0), mode='percent')
-
-        power.plot_topo(baseline=(-0.5, 0), mode='logratio')
-        power.plot_topomap(ch_type='eeg', tmin=0.15, tmax=0.2, fmin=8, fmax=12, baseline=(-0.5, 0), mode='logratio', title='Alpha')
-        power.plot_topomap(ch_type='eeg', tmin=0.15, tmax=0.2, fmin=13, fmax=25, baseline=(-0.5, 0), mode='logratio', title='Beta')
-
-        import numpy as np
-        import matplotlib.pyplot as plt
-        from mne.baseline import rescale
-        from mne.stats import bootstrap_confidence_interval
-        iter_freqs = [
-          ('Theta', 4, 7),
-          ('Alpha', 8, 12),
-          ('Beta', 13, 25),
-          ('Gamma', 30, 45)
-          ]
-          raw_fname = "data/exp1/EEG/Vp0004.vhdr"
-          tmin, tmax = -0.5, 1.498
-          baseline = None
-          frequency_map = list()
-          event_id = dict(match=222)
-          for band, fmin, fmax in iter_freqs:
-            # (re)load the data to save memory
-            raw = mne.io.read_raw_brainvision(raw_fname, scale=1e6, preload=True)
-            raw.filter(fmin, fmax, n_jobs=1,  # use more jobs to speed up.
-            l_trans_bandwidth=1,  # make sure filter params are the same
-            h_trans_bandwidth=1)  # in each band and skip "auto" option.
-            events, _ = mne.events_from_annotations(raw, verbose=False)
-            epochs = mne.Epochs(raw, events, event_id, tmin, tmax, baseline=baseline,
-            reject=dict(eeg=200), preload=True)
-            # remove evoked response
-            epochs.subtract_evoked()
-            # get analytic signal (envelope)
-            epochs.apply_hilbert(envelope=True)
-            frequency_map.append(((band, fmin, fmax), epochs.average()))
-            del epochs
-            del raw
-            # Helper function for plotting spread
-            def stat_fun(x):
-              """Return sum of squares."""
-              return np.sum(x ** 2, axis=0)
-            # Plot
-            fig, axes = plt.subplots(4, 1, figsize=(10, 7), sharex=True, sharey=True)
-            colors = plt.get_cmap('winter_r')(np.linspace(0, 1, 4))
-            for ((freq_name, fmin, fmax), average), color, ax in zip(
-              frequency_map, colors, axes.ravel()[::-1]):
-                times = average.times * 1e3
-                gfp = np.sum(average.data ** 2, axis=0)
-                gfp = mne.baseline.rescale(gfp, times, baseline=(None, 0))
-                ax.plot(times, gfp, label=freq_name, color=color, linewidth=2.5)
-                ax.axhline(0, linestyle='--', color='grey', linewidth=2)
-                ci_low, ci_up = bootstrap_confidence_interval(average.data, random_state=0,
-                stat_fun=stat_fun)
-                ci_low = rescale(ci_low, average.times, baseline=(None, 0))
-                ci_up = rescale(ci_up, average.times, baseline=(None, 0))
-                ax.fill_between(times, gfp + ci_up, gfp - ci_low, color=color, alpha=0.3)
-                ax.grid(True)
-                ax.set_ylabel('GFP')
-                ax.annotate('%s (%d-%dHz)' % (freq_name, fmin, fmax),
-                xy=(0.95, 0.8),
-                horizontalalignment='right',
-                xycoords='axes fraction')
-                axes.ravel()[-1].set_xlabel('Time [ms]')
-                plt.show()
-                ```
-
 ```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
-                # Load sample time points and electrode montage
-                montage <- read_csv("data/processed/aha-montage.csv", col_types = cols())
+# Load montage and data
+montage <- read_csv(fnames$montage, col_types = cols())
+evokeds <- read_csv(fnames$evo_gavg, col_types = cols())
 

### 2021-05-13 code/plots_tables.R

@@ -24,7 +24,7 @@ plot_trials <- function() {
     annotate("text", x = -9, y = 55, label = "potatoes\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
     annotate("text", x = -9, y = 79, label = "message\nsignaling", size = 10 / .pt, family = "Helvetica", color = color_naive) +
     annotate("text", x = 9, y = 67, label = "*", size = 30 / .pt, family = "Helvetica") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = 18, y = 62, width = 18, height = 18) +
+    draw_image("misc/potato_masher.png", x = 18, y = 62, width = 18, height = 18) +
     # Timings
     annotate("text", x = -9, y = 67.3, label = "or", size = 10 / .pt, family = "Helvetica") +
     annotate("text", x = -27, y = 52, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
@@ -66,7 +66,7 @@ plot_trials <- function() {
     annotate("rect", xmin = -91, xmax = -71, ymin = 22, ymax = 42, color = "black", fill = "white") +
     annotate("rect", xmin = -53, xmax = -73, ymin = 24, ymax = 44, color = "black", fill = "white") +
     annotate("text", x = -81, y = 32.3, label = "+", size = 20 / .pt, family = "Helvetica") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = -72, y = 25, width = 18, height = 18) +
+    draw_image("misc/potato_masher.png", x = -72, y = 25, width = 18, height = 18) +
     # Timings
     annotate("text", x = -81, y = 19, label = "0.5 s", size = 10 / .pt, family = "Helvetica") +
     annotate("text", x = -63, y = 19.3, label = "3 s or\nresponse", size = 10 / .pt, family = "Helvetica", lineheight = 1) +
@@ -81,7 +81,7 @@ plot_trials <- function() {
     annotate("rect", xmin = 53, xmax = 73, ymin = 22, ymax = 42, color = "black", fill = "white") +
     annotate("rect", xmin = 71, xmax = 91, ymin = 24, ymax = 44, color = "black", fill = "white") +
     annotate("text", x = 63, y = 32.3, label = "+", size = 20 / .pt, family = "Helvetica") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = 72, y = 25, width = 18, height = 18) +
[…]

### 2021-05-13 code/preprocessing.py

@@ -15,9 +15,9 @@ EEG power at a pre-specified range of frequencies.
 from glob import glob
 from os import makedirs, removedirs
 
+import mne
 import numpy as np
 import pandas as pd
-from mne import Epochs, events_from_annotations, pick_channels, set_bipolar_reference
 from mne.channels import combine_channels, make_standard_montage
 from mne.io import read_raw_brainvision
 from mne.preprocessing import ICA
@@ -44,10 +44,11 @@ def preprocess(
     baseline=(-0.2, 0),
     erp_components=None,
     reject={"eeg": 200e-6},
-    condition_cols=["part", "condition"],
+    average_by=None,
+    tfr_equalize=None,
+    tfr_resample=None,
     tfr_freqs=None,
     tfr_cycles=None,
-    tfr_sfreq_downsampled=250,
     tfr_crop=(-0.2, 0.8),
 ):
     """
@@ -57,11 +58,11 @@ def preprocess(
     # Create output directory if it doesn't exist
     makedirs(output_dir, exist_ok=True)
 
-    # Read raw data in microvolts
+    # Read raw EEG data
     raw = read_raw_brainvision(fname_vhdr, preload=True)
 
     # Create virtual EOG channels
-    raw = set_bipolar_reference(
+    raw = mne.set_bipolar_reference(
         raw,
         anode=eog_anodes,
         cathode=eog_cathodes,
@@ -77,10 +78,13 @@ def preprocess(
     raw.drop_channels(drops)
     raw.set_montage(montage=montage)
 
+    # Re-reference to common average
+    raw, _ = mne.set_eeg_reference(raw, "average")
+
     # Run ICA on a copy of the data
     raw_filt_ica = raw.copy()
     raw_filt_ica.load_data().filter(l_freq=1, h_freq=None)
-    ica = ICA(n_components=ica_components, random_state=ica_seed, method=ica_method)
+    ica = ICA(ica_components, random_state=ica_seed, method=ica_method, max_iter="auto")
     ica.fit(raw_filt_ica)
 
     # Remove bad components from the raw data
@@ -92,8 +96,8 @@ def preprocess(
     raw_filt = raw.filter(l_freq=hipass, h_freq=lowpass)
 
     # Epoching and baseline correction
-    events, _ = events_from_annotations(raw, verbose=False)
-    epochs = Epochs(raw_filt, events, event_id, tmin, tmax, baseline, preload=True)
[…]

### 2021-05-15 code/manuscript.Rmd
updated freq models to all_fit

@@
 Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
-
 keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
@@
 # Load packages
-library(lmerTest)
 library(emmeans)
+library(MASS)
+library(afex)
+library(reticulate)
 library(papaja)
-library(reticulate)
+library(cowplot)
+library(scales)
 library(tidyverse)
 library(magrittr)
-library(cowplot)
+library(furrr)
 
@@
 # Re-run preprocessing and/or model fitting?
-rerun_preprocessing <- TRUE
+rerun_preprocessing <- FALSE
 rerun_model_fitting <- TRUE
@@
   montage = "data/processed/montage.csv",
+  objects_per_condition = "data/processed/obj-per-cond.csv",
   evo_gavg = "data/processed/evo_gavg.csv",
-  evo_tfr_gavg = "data/processed/evo-tfr_gavg.csv",
+  evo_tfr_flat = "data/processed/evo-tfr_flat.csv",
   evo_tfr_diff = "data/processed/evo-tfr_diff.csv",
-  evo_tfr_gavg_nochans = "data/processed/evo-tfr_gavg-nochans.csv",
-  evo_tfr_diff_nochans = "data/processed/evo-tfr_diff-nochans.csv"
+  evo_tfr_flat_nochans = "data/processed/evo-tfr_flat-nochans.csv",
+  evo_tfr_diff_nochans = "data/processed/evo-tfr_diff-nochans.csv",
+  models_freq = "data/processed/models_freq.RDS"
 )
@@
   # Get standard EasyCap electrode positions and project them into 2D space
+  dir.create("data/processed")
   read_csv("data/preprocessed/sub-01_tfr-evo.csv", col_types = cols()) %>%
@@
     write_csv(fnames$montage)
+
+  # Determine number of objects per condition for each participant
+  fname_log %>%
+    map2(subject_id, pp$read_log) %>%
+    bind_rows() %>%
+    with(table(subject_id, condition) / 3) %>%
+    as.data.frame.matrix() %>%
+    rownames_to_column("subject_id") %>%
+    write_csv(fnames$objects_per_condition)
 }
@@
 
-```{python, grand_averaging, eval=rerun_preproc}
+```{python, grand_averaging, eval=TRUE}
 from os import makedirs
@@
 
-# Average first across subjects, then across electrodes
+# Compute flat average across conditions
+id_vars.remove("condition")
+evo_tfr_flat = evo_tfr.groupby(id_vars, as_index=False).mean()
+
+# Average across subjects and save
 id_vars.remove("subject_id")
-fnames = [r.fnames["evo_tfr_gavg"], r.fnames["evo_tfr_diff"]]
-fnames_nochans = [r.fnames["evo_tfr_gavg_nochans"], r.fnames["evo_tfr_diff_nochans"]]
-for df, fname, fname_nochans in zip([evo_tfr, evo_tfr_diff], fnames, fnames_nochans):
+dfs = [evo_tfr_flat, evo_tfr_diff]
+fnames_tfr = [r.fnames["evo_tfr_flat"], r.fnames["evo_tfr_diff"]]
+for df, fname in zip(dfs, fnames_tfr):
     df = df.groupby(id_vars, as_index=False).mean()
     df.to_csv(fname, float_format="%.3f", index=False)
-    df["power"] = df[electrodes].mean(axis=1)
-    df.drop(electrodes, axis=1, inplace=True)
-    df.to_csv(fname_nochans, float_format="%.3f", index=False)
-del df, evo_tfr, evo_tfr_diff
-```
-
-```{r, tfr_wip}
-please_stop_here()
-
-# Read evoked power
-paste0("data/preprocessed/", subject_id, "_tfr-evo.csv") %>%
-  map(read_csv, col_types = cols())
-
-  map2(subject_id, function(fname, id) {
-    read_csv(fname, col_types = cols(), progress = FALSE) %>%
-      mutate(participant = id)
-  }) %>%
-  bind_rows() -> evo
-
-# Average across participants
-grouping <- c("part", "condition", "time", "freq")
-evo %<>%
-  group_by(across(all_of(grouping))) %>%
-  summarise(across(-participant, .fns = mean), .groups = "drop")
-
-# Average across channels
-evo %>%
-  pivot_longer(!all_of(grouping), names_to = "channel", values_to = "power") %>%
-  group_by(across(all_of(grouping))) %>%
-  summarise(power = mean(power), .groups = "drop") -> evo_all_channels
-
-# Average across conditions within parts
-evo_all_channels %>%
-  group_by(part, time, freq) %>%
-  summarise(power = mean(power), .groups = "drop") -> evo_all_channels_conds
-
-# Plot
-evo_all_channels_conds %>%
-  ggplot(aes(x = time, y = freq, fill = power)) +
-  facet_wrap(~part) +
-  geom_raster() +
-  scale_fill_viridis_c(limits = c(0, 2), oob = scales::squish) +
-  annotate("rect", xmin = 150, xmax = 400, ymin = 30, ymax = 50, color = "white", fill = NA) +
-  theme(aspect.ratio = 0.5) +
-  theme_minimal() +
-  coord_cartesian(expand = FALSE) +
-  ggsave("evo_all_channels_conds.pdf", width = 7, height = 2)
-
-# Compute differences between conditions
-evo_all_channels %>%
-  group_by(part, time, freq) %>%
-  mutate(power = power - power[condition == "Naive"]) %>%
-  filter(condition == "Informed") %>%
-  ggplot(aes(x = time, y = freq, fill = power)) +
-  facet_wrap(~part) +
-  geom_raster() +
-  scale_fill_viridis_c(limits = c(0, 1), oob = scales::squish) +
-  annotate("rect", xmin = 150, xmax = 400, ymin = 30, ymax = 50, color = "white", fill = NA) +
-  theme(aspect.ratio = 0.5) +
-  theme_minimal() +
-  coord_cartesian(expand = FALSE) +
-  ggsave("evo_all_channels_diff.pdf", width = 7, height = 2)
+del df, dfs, evo, evo_tfr, evo_tfr_diff, evo_tfr_flat
 ```
@@
     subject_id = factor(subject_id),
-    item_id = factor(item_id)
-  ) %>%
-  na.omit() -> trials
-
-contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
-contrasts_part <- t(cbind(
-  c("I" = -1, "II" = 1, "III" = 0),
-  c("I" = 0, "II" = -1, "III" = 1)
-))
-
-# Apply these contrasts to the factors in the data
-contrasts(trials$condition) <- MASS::ginv(contrasts_condition)
-contrasts(trials$part) <- MASS::ginv(contrasts_part)
-
-formula <- N400 ~ part / condition + (1|subject_id) + (1|item_id)
-mod <- lmer(formula, data = trials)
-summary(mod)
-
-# Remove any trials excluded from conditions
-aha %>%
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> aha
-
-# Define contrast coding for condition (informed-naive) and part (2-1, 3-1)
-contrasts_condition <- t(cbind(
-  c("Informed" = 1, "Naive" = -1)
-))
-contrasts_part <- t(cbind(
-  c("I" = -1, "II" = 1, "III" = 0),
-  c("I" = 0, "II" = -1, "III" = 1)
-))
-
-# Apply these contrasts to the factors in the data
-contrasts(aha$condition) <- MASS::ginv(contrasts_condition)
-contrasts(aha$part) <- MASS::ginv(contrasts_part)
-
-# Specify model formula
-form <- erp ~ part * condition +
-  (part * condition | participant) +
-  (part * condition | item)
-
-# Specify follow-up comparisons
+    item_id = factor(item_id),
+    RT = ifelse(RT < 200, NA, RT),
+    logRT = log(RT)
+  ) -> trials
+
+# Remove trials with unrealistically short RTs or invalid conditions
+sum(is.na(trials$RT))
+sum(is.na(trials$RT)) / nrow(trials)
+trials %<>% na.omit()
+
+# Contrast coding for parts
+cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)) %>%
+  t() %>%
+  ginv() -> contrasts(trials$part)
+
+# Contrast coding for conditions
+c("Informed" = 1, "Naive" = -1) %>%
+  t() %>%
+  ginv() -> contrasts(trials$condition)
+
+# Load fitted models or rerun them
+if (!rerun_model_fitting) {
+
+  # Load models
+  models_freq <- readRDS(fnames$models_freq)
+} else {
+
+  # Compute models for dependent variables in parallel
+  dvs <- c("logRT", "P1", "N170", "N400")
+  n_cores <- min(length(dvs), availableCores())
+  plan("multisession", workers = n_cores)
+  future_map(dvs, function(dv, dat = trials) {
+
+    # Define model formula
+    form <- paste0(
+      dv, " ~ part * condition +
+        (part * condition | subject_id) +
+        (part * condition | item_id)"
+    ) %>% formula()
+
+    # Define follow-up comparisons
     specs <- pairwise ~ condition | part
 
-# Calculate linear mixed-effects models and follow-up comparisons
-map(comps$name, function(comp, formula = form, data = aha, specs = specs) {
-  data %<>% rename(erp = all_of(comp))
-  mod <- lmer(formula, data, all_fit = TRUE)
+    # Fit initial model
+    fit <- lmer(form, dat, REML = FALSE)
+
+    # Refit using all available optimizers
+    fits <- all_fit(fit, formula = form, data = dat)
+
+    # See which of the optimizers converged
+    fits_converged <- keep(
+      fits,
+      ~ .x@optinfo$conv$opt == 0 &
+        length(.x@optinfo$conv$lme4) == 0 &
+        length(.x@optinfo$warnings) == 0
+    )
+
+    # Find best model via logLik
+    logliks <- map(fits_converged, logLik)
+    fit_best <- fits[[which.max(logliks)]]
+
+    # Compute follow-up comparisons
     emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  em <- emmeans(mod, specs = specs, infer = TRUE, data = data)
-  modlist <- list(
-    model = mod,
-    anova = anova(mod),
-    summary = summary(mod),
-    means = as.data.frame(em$means),
-    contrasts = as.data.frame(em$contrasts)
+    em <- emmeans(fit_best, specs, infer = TRUE)
+
+    # Return a list of relevant model outputs
+    return(
+      list(
+        fit = fit_best,
+        anova = anova(fit_best),
+        means = em$emmeans,
+        contrasts = em$contrasts,
+        all_fits = fits
+      )
     )
   }) %>%
-  set_names(comps$name) %T>%
-  saveRDS(fnames$models_freq) -> mods_freq
+
+    # Save
+    set_names(dvs) %T>%
+    saveRDS(fnames$models_freq) -> models_freq
+
+  # Stop the workers
+  future:::ClusterRegistry("stop")
+}
+
+please_stop_here()
 ```
@@
 contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
-contrasts(data_brm$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_brm$part) <- MASS::ginv(contrasts_part)
+contrasts(data_brm$condition) <- ginv(contrasts_condition)
+contrasts(data_brm$part) <- ginv(contrasts_part)
 
@@
 
-```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
+```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
 # Load montage and data
@@
   plot_trials(),
-  plot_erps(comps = comps, evokeds = evokeds_exp1, models = models_exp1, montage = montage),
+  plot_erps(erp_components, evokeds, models_freq, montage),
   nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
 ) + # Add some lines (to separate the parts) and the legend
-  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.53, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.53, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.53, yend = 0.58, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.53, yend = 0.58, linetype = "dashed") +  
-  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.58, yend = Inf, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.58, yend = Inf, linetype = "dashed") +
-  draw_plot(plot_legends_erps(direction = "vertical"), x = 0.405, y = 0.422, width = 1, height = 1)
-```
-
-(ref:figure-1-caption) Procedure and Results of Experiment 1\smallskip
+  annotate_line(x = 0.328, xend = 0.328, y = -Inf, yend = 0.53) +
+  annotate_line(x = 0.672, xend = 0.672, y = -Inf, yend = 0.53) +
+  annotate_line(x = 0.328, xend = 0.28, y = 0.53, yend = 0.58) +
+  annotate_line(x = 0.672, xend = 0.72, y = 0.53, yend = 0.58) +
+  annotate_line(x = 0.28, xend = 0.28, y = 0.58, yend = Inf) +
+  annotate_line(x = 0.72, xend = 0.72, y = 0.58, yend = Inf) +
+  draw_plot(
+    plot_legends_erps(direction = "vertical"),
+    x = 0.405, y = 0.422, width = 1, height = 1
+  )
+```
+
+(ref:fig1_caption) Procedure and Results of Experiment 1\smallskip
 
@@
 Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
-This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials).
+This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials).
 Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \@ref(fig:exp1-plot)B).
@@
 First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
+This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
 Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
 Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
-This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
+This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
 Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
 Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
@@
 Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "P1_p"]`.
+
+```{r, fig3, include=TRUE}
+evo_tfr_flat <- read_csv(fnames$evo_tfr_flat, col_types = cols(), progress = FALSE)
+evo_tfr_diff <- read_csv(fnames$evo_tfr_diff, col_types = cols(), progress = FALSE)
+
+# Scaling of power in all plots
+limits_power <- c(0, 2)
+
+# Time-frequency of interest based on visual inspect
+tfoi <- list(tmin = 200, tmax = 400, fmin = 34, fmax = 48)  # Gamma
+# tfoi <- list(tmin = 150, tmax = 350, fmin = 14, fmax = 24)  # Beta
+
+standard_text <- element_text(size = 10, color = "black", family = "Helvetica")
+
+plot_tfr_raster <- function(evo_tfr, limits, tmin, tmax, fmin, fmax, label) {
+  # Average across electrodes
+  evo_tfr %>%
+    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
+    group_by(part, time, freq) %>%
+    summarise(power = mean(power), .groups = "drop") %>%
+    # Create one raster plot per part
+    group_by(part) %>%
+    group_map(function(data_part, part) {
+      ggplot(data_part, aes(x = time, y = freq, fill = power)) +
+        geom_raster() +
+        scale_fill_viridis_c(
+          limits = limits,
+          labels = function(x) x * 100,
+          guide = guide_colorbar(
+            title = "Power (% change\nfrom baseline)",
+            title.position = "left",
+            title.theme = element_text(size = 10, color = "black", angle = 90, lineheight = 1),
+            title.hjust = 0.5,
+            label.theme = element_text(size = 10, color = "black"),
+            barheight = unit(4, "cm"),
+            ticks = FALSE,
+            direction = "vertical"
+          ),
+          oob = squish
+        ) +
+        scale_x_continuous(breaks = seq(-100, 700, 200)) +
+        coord_cartesian(expand = FALSE) +
+        annotate("rect", xmin = tmin, xmax = tmax, ymin = fmin + 1, ymax = fmax + 1, color = "white", fill = NA, linetype = "dotted") +
+        annotate("segment", x = 0, xend = 0, y = -Inf, yend = Inf, color = "white", linetype = "dotted") +
+        labs(x = "Time (ms)", y = "") +
+        theme_minimal() +
+        theme(
+          legend.position = "none",
+          axis.title = standard_text,
+          axis.text = standard_text
+        )
+    }) -> plotlist
+  # Add label and axis title to the first plot
+  plotlist[[1]] <- plotlist[[1]] + annotate(
+    "text",
+    x = -100,
+    y = 27,
+    label = label,
+    size = 10 / .pt,
+    angle = 90,
+    family = "Helvetica",
+    color = "white",
+    lineheight = 0.9
+  ) +
+    ylab("Frequency (ms)")
+  # Extract legend for another subplot
+  current_legend <<- get_legend(plotlist[[1]] + theme(legend.position = "right"))
+  plot_grid(plotlist = plotlist, nrow = 1)
+}
+
+plot_tfr_topo <- function(evo_tfr, limits, tmin, tmax, fmin, fmax, legend) {
+  # Average across times and frequencies of interest
+  evo_tfr_diff %>%
+    # Select time window and frequencies of interest
+    filter(time >= tmin & time <= tmax & freq >= fmin & freq <= fmax) %>%
+    # Convert to long format
+    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
+    # Create one topoplot per part
+    group_by(part) %>%
+    group_map(function(data_part, part) {
+      data_part %>%
+        group_by(electrode) %>%
+        summarise(power = mean(power), .groups = "drop") %>%
+        inner_join(montage, by = "electrode") %>%
+        eegUtils::topoplot(
+          limits = limits,
+          palette = "viridis",
+          contour = FALSE,
+          quantity = "power",
+          scaling = 0.5
+        ) +
+        theme(legend.position = "none",)
+    }) -> plotlist
+  #plotlist <- c(plotlist, list(legend))
+  plot_grid(
+    NULL,
+    plotlist[[1]],
+    NULL,
+    plotlist[[2]],
+    NULL,
+    plotlist[[3]],
+    nrow = 1,
+    rel_widths = c(2, 7, 0, 7, 1, 7))
+}
+
+# Bring it all together
+plot_grid(
+  plot_headings(spacing = c(1, 7, 1, 7, 1, 7)),
+  do.call(
+    plot_tfr_raster, c(tfoi, list(
+      evo_tfr = evo_tfr_flat,
+      limits = limits_power,
+      label = "All channels,\nall conditions"
+    ))
+  ),
+  do.call(
+    plot_tfr_raster, c(tfoi, list(
+      evo_tfr = evo_tfr_diff,
+      limits = limits_power,
+      label = "All channels,\n\u0394 (informed - naive)"
+    ))
+  ),
+  do.call(
+    plot_tfr_topo, c(tfoi, list(
+      evo_tfr = evo_tfr_diff,
+      limits = limits_power,
+      legend = current_legend))
+  ),
+  nrow = 4,
+  rel_heights = c(1, 5, 5, 5),
+  labels = c("", "A", "B", "C"),
+  label_y = c(1, 1.16, 1.1, 1),
+  label_fontfamily = "Helvetica"
+) +
+  draw_plot(current_legend, x = -0.42, y = -0.34) +
+  annotate_line(0.344, 0.344, -Inf, Inf) +
+  annotate_line(0.676, 0.676, -Inf, Inf) +
+  ggsave("data/processed/tfr.pdf", width = unit(10, "cm"), height = unit(7, "cm"), device = cairo_pdf)
+```
 
@@
 # Apply contrasts to the factors in the data
-contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)
+contrasts(data_exp2$condition) <- ginv(contrasts_condition)
+contrasts(data_exp2$part) <- ginv(contrasts_part)
 
@@
 All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
-An average of `r format(round(objects_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects was assigned to the semantically informed condition (= `r scales::percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects was assigned to the naive condition (= `r scales::percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
+An average of `r format(round(objects_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
+Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects was assigned to the semantically informed condition (= `r percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects was assigned to the naive condition (= `r percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
 
@@
 
-```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:figure-2-caption)"}
+```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:fig2_caption)"}
 # Create plot for Experiment 2
@@
 ) + # Add some lines (to separate the parts)
-  annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.672, y = 0.15, yend = Inf, linetype = "dashed")
-```
-
-(ref:figure-2-caption) Results of Experiment 2\smallskip
+  annotate_line(x = 0.328, xend = 0.328, y = 0.15, yend = Inf) +
+  annotate_line(x = 0.672, xend = 0.672, y = 0.15, yend = Inf)
+```
+
+(ref:fig2_caption) Results of Experiment 2\smallskip
 
@@
 t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
-contrasts(data_joint_subs$experiment) <- MASS::ginv(contrasts_experiment)
-contrasts(data_joint_subs$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_joint_subs$part) <- MASS::ginv(contrasts_part)
+contrasts(data_joint_subs$experiment) <- ginv(contrasts_experiment)
+contrasts(data_joint_subs$condition) <- ginv(contrasts_condition)
+contrasts(data_joint_subs$part) <- ginv(contrasts_part)
 
@@
 
-(ref:figure-3-caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip
+(ref:fig3_caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip
 
@@
 
-```{r joint-plot, include=TRUE, fig.height=8, fig.cap = "(ref:figure-3-caption)"}
+```{r joint-plot, include=TRUE, fig.height=8, fig.cap = "(ref:fig3_caption)"}
 # Create violin plot for Experiments 1 and 2 combined
@@
   annotate(
-    geom = "segment", x = 11 / 34 * 0.85, xend = 11 / 34 * 0.85,
-    y = -Inf, yend = Inf, linetype = "dashed"
+    "segment", x = 11 / 34 * 0.85, xend = 11 / 34 * 0.85,
+    y = -Inf, yend = Inf
   ) +
   annotate(
-    geom = "segment", x = 23 / 34 * 0.85, xend = 23 / 34 * 0.85,
-    y = -Inf, yend = Inf, linetype = "dashed"
+    "segment", x = 23 / 34 * 0.85, xend = 23 / 34 * 0.85,
+    y = -Inf, yend = Inf
   )
@@
 # Contrast coding for condition (informed-no_informed) and part (2-1, 3-1)
-contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_joint_control$part) <- MASS::ginv(contrasts_part)
+contrasts(data_joint_control$condition) <- ginv(contrasts_condition)
+contrasts(data_joint_control$part) <- ginv(contrasts_part)
 
@@
 Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
+Across both experiments, this was the case for `r percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
 Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
@@
 t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
-contrasts(data_exp3$position) <- MASS::ginv(contrasts_position)
-contrasts(data_exp3$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp3$part) <- MASS::ginv(contrasts_part)
+contrasts(data_exp3$position) <- ginv(contrasts_position)
+contrasts(data_exp3$condition) <- ginv(contrasts_condition)
+contrasts(data_exp3$part) <- ginv(contrasts_part)
 

### 2021-05-15 analysis/preprocessing.py

@@ -108,7 +108,7 @@ def preprocess(
     epochs = Epochs(filt, events, event_id, tmin, tmax, baseline, preload=True)
 
     # Read behavioral metadata
-    epochs.metadata = _read_log(fname_log)
+    epochs.metadata = read_log(fname_log)
 
     # Compute single trial mean amplitude for ERP components of interest
     for _, component in erp_components.iterrows():
@@ -153,7 +153,7 @@ def preprocess(
     return trials
 
 
-def _read_log(fname_log=None):
+def read_log(fname_log=None):
     """
     Extracts the relevant information from a behavioral log file into a DataFrame.
     """

### 2021-05-15 code/plots_tables.R

@@ -102,19 +102,6 @@ plot_erps <- function(erp_components, evokeds, models, montage) {
       # Loop through parts
       parts <- map(c("I", "II", "III"), function(part) {
         data_plot <- filter(evokeds, part == !!part & condition %in% c("Informed", "Naive"))
-
-        # # Create (conditions x time points) x electrodes tibble
-        # data_plot <- evokeds[[part]] %>%
-        #   map(function(data) {
-        #     data %>%
-        #       t() %>%
-        #       as_tibble(.name_repair = "unique") %>%
-        #       set_colnames(montage$electrode) %>%
-        #       mutate(time = seq(-500, 1498, 2), roi = rowMeans(select(., all_of(roi))))
-        #   }) %>%
-        #   bind_rows(.id = "condition")
-        
-        
         # Shade background depending on whether the effect is significant or not
         asterisks <- models[[name]]$contrasts %>%
           filter(part == !!part) %>%
@@ -148,10 +135,10 @@ plot_erps <- function(erp_components, evokeds, models, montage) {
           filter(time >= tmin & time <= tmax) %>%
           group_by(condition) %>%
           summarise(across(montage$electrode, mean), .groups = "drop") %>%
-          pivot_longer(-condition) %>%
+          pivot_longer(-condition, names_to = "electrode") %>%
           pivot_wider(names_from = condition) %>%
-          transmute(amplitude = Informed - Naive) %>%
-          bind_cols(montage) %>%
+          mutate(amplitude = Informed - Naive) %>%
+          inner_join(montage, by = "electrode") %>%
           eegUtils::topoplot(limits = c(-1, 1), palette = "viridis", contour = FALSE, highlights = roi, scaling = 0.1) +
           theme(legend.position = "none")
         topo$layers[[3]]$aes_params$size <- topo$layers[[4]]$aes_params$size <- topo$layers[[5]]$aes_params$size <- 0.6
@@ -202,12 +189,15 @@ plot_legends_erps <- function(direction) {
 # Function to plot headings for Parts I, II, and III
 plot_headings <- function(spacing) {
   plot_grid(
+    NULL,
     ggplot() +
       annotate("text", label = "Pre-insight part", x = 0, y = 0, size = 14 / .pt, family = "Helvetica", fontface = "bold") +
-      theme_void(), NULL,
+      theme_void(),
+    NULL,
     ggplot() +
[…]

### 2021-05-15 code/preprocessing.py

@@ -100,7 +100,7 @@ def preprocess(
     epochs = mne.Epochs(raw_filt, events, event_id, tmin, tmax, baseline, preload=True)
 
     # Read behavioral metadata
-    epochs.metadata = _read_log(fname_log, subject_id)
+    epochs.metadata = read_log(fname_log, subject_id)
 
     # Compute single trial mean amplitude for ERP components of interest
     for _, component in erp_components.iterrows():
@@ -158,7 +158,7 @@ def preprocess(
     del epochs_unf, evokeds_tfr, tfr
 
 
-def _read_log(fname_log=None, subject_id=None):
+def read_log(fname_log=None, subject_id=None):
     """
     Extracts the relevant information from a behavioral log file into a DataFrame.
     """

### 2021-05-21 code/manuscript.Rmd
prepare all_fit

@@
 
-```{python, grand_averaging, eval=TRUE}
+```{python, grand_averaging, eval=rerun_preprocessing}
 from os import makedirs
@@
   n_cores <- min(length(dvs), availableCores())
-  plan("multisession", workers = n_cores)
+  plan("multicore", workers = n_cores)
   future_map(dvs, function(dv, dat = trials) {
@@
     # Fit initial model
-    fit <- lmer(form, dat, REML = FALSE)
+    fit <- lmer(form, dat, REML = TRUE)
 
@@
       fits,
-      ~ .x@optinfo$conv$opt == 0 &
-        length(.x@optinfo$conv$lme4) == 0 &
-        length(.x@optinfo$warnings) == 0
+      ~ .x@optinfo$conv$opt == 0 & length(.x@optinfo$conv$lme4) == 0
     )
@@
 ```{r, fig3, include=TRUE}
+# Read grand averages of evoked power
 evo_tfr_flat <- read_csv(fnames$evo_tfr_flat, col_types = cols(), progress = FALSE)
@@
 # Time-frequency of interest based on visual inspect
+tfoi <- list(tmin = 150, tmax = 350, fmin = 14, fmax = 24)  # Beta or
 tfoi <- list(tmin = 200, tmax = 400, fmin = 34, fmax = 48)  # Gamma
-# tfoi <- list(tmin = 150, tmax = 350, fmin = 14, fmax = 24)  # Beta
-
+
+# Standard text format
 standard_text <- element_text(size = 10, color = "black", family = "Helvetica")

### 2021-05-23 code/manuscript.Rmd
revert to buildmer

@@
 # Load packages
+library(MASS)
+library(lme4)
+library(buildmer)
 library(emmeans)
-library(MASS)
-library(afex)
+library(brms)
+library(parallel)
 library(reticulate)
@@
 library(magrittr)
-library(furrr)
 
@@
 rerun_model_fitting <- TRUE
+
+# Number of CPU cores for parallel model fitting
+n_cores <- detectCores()
 
@@
   dvs <- c("logRT", "P1", "N170", "N400")
-  n_cores <- min(length(dvs), availableCores())
-  plan("multicore", workers = n_cores)
-  future_map(dvs, function(dv, dat = trials) {
+  map(dvs, function(dv) {
 
     # Define model formula
-    form <- paste0(
+    formula_lme <- paste0(
       dv, " ~ part * condition +
@@
 
-    # Fit initial model
-    fit <- lmer(form, dat, REML = TRUE)
-
-    # Refit using all available optimizers
-    fits <- all_fit(fit, formula = form, data = dat)
-
-    # See which of the optimizers converged
-    fits_converged <- keep(
-      fits,
-      ~ .x@optinfo$conv$opt == 0 & length(.x@optinfo$conv$lme4) == 0
-    )
-
-    # Find best model via logLik
-    logliks <- map(fits_converged, logLik)
-    fit_best <- fits[[which.max(logliks)]]
+    # Automic model selection via likelihood ratio tests
+    # using an alpha level of .20 (see Matuschek et al., 2017, J Mem Lang)
+    cl <- makeCluster(n_cores)
+    build <- buildmer(
+      formula = formula_lme,
+      data = trials,
+      buildmerControl = buildmerControl(
+        direction = c("backward", "backward"),
+        cl = cl,
+        crit = "LRT",
+        elim = function(logp) exp(logp) >= .20,
+        quiet = TRUE,
+        calc.anova = TRUE,
+        ddf = "Satterthwaite",
+        REML = FALSE,
+      ),
+      control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
+    )
+    stopCluster(cl)
 
@@
     emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-    em <- emmeans(fit_best, specs, infer = TRUE)
+    em <- emmeans(build@model, specs, infer = TRUE)
 
@@
       list(
-        fit = fit_best,
-        anova = anova(fit_best),
+        model = build@model,
+        anova = build@anova,
+        summary = build@summary,
         means = em$emmeans,
-        contrasts = em$contrasts,
-        all_fits = fits
+        contrasts = em$contrasts
       )
@@
     saveRDS(fnames$models_freq) -> models_freq
-
-  # Stop the workers
-  future:::ClusterRegistry("stop")
 }
@@
 
-```{r bayes, eval=FALSE}
-library(brms)
-options(mc.cores = 6)
-
-data_joint_subs %>%
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() %>%
-  select(part, condition, participant, item, P1, N170, N400) %>%
-  na.omit() %>%
-  as.list() -> data_brm
-
-contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
-contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
-contrasts(data_brm$condition) <- ginv(contrasts_condition)
-contrasts(data_brm$part) <- ginv(contrasts_part)
-
-formula <- P1 ~ part / condition + (part / condition | participant) + (part / condition | item)
+```{r models_bayes, eval=FALSE}
+# Define model formula
+form <- P1 ~ part * condition +
+  (part * condition | subject_id) +
+  (part * condition | item_id)
+
+# Default prior for slopes
 prior <- set_prior("cauchy(0, 0.707)", class = "b")
 
+# Fit Bayesian mixed model
 mod_brm <- brm(
-  formula = formula,
-  data = data_brm,
+  formula = form,
+  data = trials,
   family = gaussian(),
@@
   chains = 4,
-  iter = 20000,
-  warmup = 2000,
+  # iter = 20000,
+  # warmup = 2000,
   cores = 4,
-  control = list(adapt_delta = 0.9)
+  backend = "cmdstanr"
 )
@@
 evokeds <- read_csv(fnames$evo_gavg, col_types = cols())
+models_freq <- readRDS(fnames$models_freq)
 

### 2021-05-23 code/manuscript.Rmd
small model fixes

@@
         elim = function(logp) exp(logp) >= .20,
-        quiet = TRUE,
         calc.anova = TRUE,
@@
         summary = build@summary,
-        means = em$emmeans,
-        contrasts = em$contrasts
+        means = as.data.frame(em$emmeans),
+        contrasts = as.data.frame(em$contrasts)
       )
@@
   # warmup = 2000,
-  cores = 4,
+  # cores = 4,
   backend = "cmdstanr"

### 2021-06-03 code/manuscript.Rmd
add new plot, sourceloc

@@
 library(reticulate)
+library(magick)
 library(papaja)
@@
 # Re-run preprocessing and/or model fitting?
-rerun_preprocessing <- FALSE
-rerun_model_fitting <- TRUE
+rerun_preprocessing <- TRUE
+rerun_model_fitting <- FALSE
 
@@
 fnames <- list(
-  montage = "data/processed/montage.csv",
-  objects_per_condition = "data/processed/obj-per-cond.csv",
-  evo_gavg = "data/processed/evo_gavg.csv",
-  evo_tfr_flat = "data/processed/evo-tfr_flat.csv",
-  evo_tfr_diff = "data/processed/evo-tfr_diff.csv",
-  evo_tfr_flat_nochans = "data/processed/evo-tfr_flat-nochans.csv",
-  evo_tfr_diff_nochans = "data/processed/evo-tfr_diff-nochans.csv",
-  models_freq = "data/processed/models_freq.RDS"
+  montage = "results/montage.csv",
+  objects_per_condition = "results/obj-per-cond.csv",
+  evo_gavg = "results/evo_gavg.csv",
+  evo_tfr_flat = "results/evo-tfr_flat.csv",
+  evo_tfr_diff = "results/evo-tfr_diff.csv",
+  models_lme = "results/models_lme.RDS"
 )
@@
   dir.create("data/processed")
-  read_csv("data/preprocessed/sub-01_tfr-evo.csv", col_types = cols()) %>%
+  read_csv("data/preprocessed/sub-01_tfr-ave.csv", col_types = cols()) %>%
     select(-c(part, condition, subject_id, time, freq)) %>%
@@
 # Read evoked *potentials* for all subjects
-fname_evo_tfr = ["data/preprocessed/" + sub + "_evo.csv" for sub in r.subject_id]
+fname_evo_tfr = ["data/preprocessed/" + sub + "_ave.csv" for sub in r.subject_id]
 evo = [pd.read_csv(fname) for fname in fname_evo_tfr]
@@
 # Read evoked *power* for all subjects
-fname_evo_tfr = ["data/preprocessed/" + sub + "_tfr-evo.csv" for sub in r.subject_id]
+fname_evo_tfr = ["data/preprocessed/" + sub + "_tfr-ave.csv" for sub in r.subject_id]
 evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
 evo_tfr = pd.concat(evo_tfr)
+
+# Subject 18 is weird!
+evo_tfr = evo_tfr[evo_tfr["subject_id"] != "sub-18"]
 
@@
 
-```{r, models_freq}
+```{r, models_lme}
 # Read single trial data for all subjects
@@
   # Load models
-  models_freq <- readRDS(fnames$models_freq)
+  models_lme <- readRDS(fnames$models_lme)
 } else {
@@
     set_names(dvs) %T>%
-    saveRDS(fnames$models_freq) -> models_freq
+    saveRDS(fnames$models_lme) -> models_lme
 }
-
-please_stop_here()
-```
-
-```{r models_bayes, eval=FALSE}
+```
+
+```{r models_brm, eval=FALSE}
+# Color scheme for plots
+bayesplot::color_scheme_set("purple")
+
 # Define model formula
-form <- P1 ~ part * condition +
+formula_brm <- P1 ~ part * condition +
   (part * condition | subject_id) +
@@
 
-# Fit Bayesian mixed model
-mod_brm <- brm(
-  formula = form,
+# Fit Bayesian mixed model using prior information only
+mod_brm_prior <- brm(
+  formula = formula_brm,
   data = trials,
@@
   prior = prior,
-  sample_prior = "yes",
+  sample_prior = "only",
   save_pars = save_pars(all = TRUE),
   chains = 4,
-  # iter = 20000,
-  # warmup = 2000,
-  # cores = 4,
+  iter = 20000,
+  warmup = 2000,
   backend = "cmdstanr"
 )
+
+# Prior predictive checks for population-level parameters
+prior_summary(mod_brm_prior)
+summary(mod_brm_prior)
+mcmc_plot(mod_brm_prior, "areas", pars = "^b_", prob_outer = 0.95) +
+  theme(text = element_text(family = "Helvetica", size = 10))
+
+# Refit using the actual data
+mod_brm_posterior <- update(mod_brm_prior, sample_prior = "yes")
+
+# Posterior predictive checks for population-level parameters
+summary(mod_brm_posterior)
+mcmc_plot(mod_brm_posterior, "areas", pars = "^b_", prob_outer = 0.95) +
+  theme(text = element_text(family = "Helvetica", size = 10))
+
+# Posterior predictive checks subject by subject
+pp_check(
+  mod_brm_posterior,
+  type = "dens_overlay_grouped",
+  nsamples = 50,
+  group = "subject_id"
+)
+pp_check(
+  mod_brm_posterior,
+  type = "stat_grouped",
+  nsamples = 1000,
+  group = "subject_id",
+  stat = "sd"
+)
+
+# Post-hoc comparisons for informed vs. naive within each part
+hyps <- c(
+  "posthoc_1" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
+  "posthoc_2" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
+  "posthoc_3" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
+)
+hypothesis(mod_brm_posterior, hyps) %>%
+  mutate(.$hypothesis, bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused")
+
+# Alternative with emmeans
+specs <- pairwise ~ condition | part
+emmeans(mod_brm_posterior, specs = specs)
 
@@
 ```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
-# Load montage and data
+# Load montage and evoked data
 montage <- read_csv(fnames$montage, col_types = cols())
 evokeds <- read_csv(fnames$evo_gavg, col_types = cols())
-models_freq <- readRDS(fnames$models_freq)
 
 # Create plot for Experiment 1
-plot_grid(
-  plot_trials(),
-  plot_erps(erp_components, evokeds, models_freq, montage),
-  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
-) + # Add some lines (to separate the parts) and the legend
-  annotate_line(x = 0.328, xend = 0.328, y = -Inf, yend = 0.53) +
-  annotate_line(x = 0.672, xend = 0.672, y = -Inf, yend = 0.53) +
-  annotate_line(x = 0.328, xend = 0.28, y = 0.53, yend = 0.58) +
-  annotate_line(x = 0.672, xend = 0.72, y = 0.53, yend = 0.58) +
-  annotate_line(x = 0.28, xend = 0.28, y = 0.58, yend = Inf) +
-  annotate_line(x = 0.72, xend = 0.72, y = 0.58, yend = Inf) +
-  draw_plot(
-    plot_legends_erps(direction = "vertical"),
-    x = 0.405, y = 0.422, width = 1, height = 1
-  )
+plot_fig1(erp_components, evokeds, trials, models_lme)
 ```

### 2021-06-03 code/plots_tables.R

@@ -1,14 +1,56 @@
-####################################################################################################
+########################################################################################
 ## FUNCTIONS TO CREATE PLOTS AND TABLES ##
-####################################################################################################
+########################################################################################
 
-# Function to plot the trial structure
-plot_trials <- function() {
-  suppressMessages(require(magick))
-  color_informed <- viridisLite::viridis(1, begin = 0.1)
-  color_naive <- viridisLite::viridis(1, begin = 0.5)
-  ggplot() +
+# Function to create Figure 1
+plot_fig1 <- function(erp_components, evokeds, trials, models) {
+
+  # Define colors for conditions
+  colors <- list(
+    Informed = viridisLite::viridis(1, begin = 0.1),
+    Naive = viridisLite::viridis(1, begin = 0.5)
+  )
+
+  # Base object for split violin plots (kudos to https://stackoverflow.com/a/45614547)
+  GeomSplitViolin <- ggproto(
+    "GeomSplitViolin", GeomViolin,
+    draw_group = function(self, data, ..., draw_quantiles = NULL) {
+      data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
+      grp <- data[1, "group"]
+      newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
+      newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
+      newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
+      if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
+        stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 1))
+        quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
+        aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
+        aesthetics$alpha <- rep(1, nrow(quantiles))
+        both <- cbind(quantiles, aesthetics)
+        quantile_grob <- GeomPath$draw_panel(both, ...)
[…]

### 2021-06-03 code/preprocessing.py

@@ -18,6 +18,7 @@ from os import makedirs, removedirs
 import mne
 import numpy as np
 import pandas as pd
+from mne import write_evokeds
 from mne.channels import combine_channels, make_standard_montage
 from mne.io import read_raw_brainvision
 from mne.preprocessing import ICA
@@ -122,18 +123,22 @@ def preprocess(
     epochs.metadata.to_csv(prefix + "trials.csv", float_format="%.3f", index=False)
 
     # Compute evoked potentials
-    evokeds = _evokeds_df_from_epochs(epochs, average_by)
-    evokeds.to_csv(prefix + "evo.csv", float_format="%.3f", index=False)
+    evokeds_list, evokeds_df = _evokeds_df_from_epochs(epochs, average_by)
+    write_evokeds(prefix + "ave.fif", evokeds_list)
+    evokeds_df.to_csv(prefix + "ave.csv", float_format="%.3f", index=False)
 
     # Create unfiltered epochs for time-frequency analysis
-    epochs_unf = mne.Epochs(raw, events, event_id, tmin, tmax, baseline, preload=True)
+    tmin, tmax = -1.0, 1.0
+    epochs_unf = mne.Epochs(
+        raw, events, event_id, tmin, tmax, baseline=None, preload=True
+    )
     epochs_unf.metadata = metadata_backup
     if tfr_equalize is not None:
         epochs_unf = epochs_unf[tfr_equalize]
         epochs_unf.equalize_event_counts()
     if tfr_resample is not None:
         epochs_unf.resample(tfr_resample)
-    del epochs, evokeds, raw, raw_filt, raw_filt_ica
+    del epochs, evokeds_list, evokeds_df, raw, raw_filt, raw_filt_ica
 
     # Compute single trial power
     tfr = tfr_morlet(
@@ -144,6 +149,7 @@ def preprocess(
         return_itc=False,
         average=False,
     )
+    baseline = (-0.9, -0.6)
     tfr.apply_baseline(baseline, mode="percent")
 
     # Reduce size and save
@@ -153,9 +159,9 @@ def preprocess(
     tfr.save(prefix + "tfr.h5")
 
     # Compute evoked power
-    evokeds_tfr = _evokeds_df_from_epochs(tfr, average_by)
-    evokeds_tfr.to_csv(prefix + "tfr-evo.csv", float_format="%.3f", index=False)
-    del epochs_unf, evokeds_tfr, tfr
[…]

### 2021-06-03 code/sourceloc.py

@@ -1,0 +1,239 @@
+# %%
+import os.path as op
+
+import groupmne
+import matplotlib.pyplot as plt
+import mne
+import numpy as np
+
+# Prepare an empty dict to store the evokeds for all subjects
+evokeds_dict = {
+    "I": {"Informed": [], "Naive": [], "Difference": []},
+    "II": {"Informed": [], "Naive": [], "Difference": []},
+    "III": {"Informed": [], "Naive": [], "Difference": []},
+}
+
+# How many subjects to include (min = 1, max = 48)
+nsubs = 48
+
+# Read evokeds for all subjects and organize the relevant conditions in a dict
+subject_id = ["sub-" + "{:02d}".format(s) for s in range(1, nsubs + 1)]
+for s in subject_id:
+    evokeds = mne.read_evokeds("../data/preprocessed/" + s + "_ave.fif", verbose=False)
+    for pt in ["I", "II", "III"]:
+        for ev in evokeds:
+            #ev = ev.copy().drop_channels(["P1", "N170", "N400"])
+            if "part == '" + pt + "' & condition == 'Informed'" in ev.comment:
+                ev_informed = ev
+                evokeds_dict[pt]["Informed"].append(ev)
+            elif "part == '" + pt + "' & condition == 'Naive'" in ev.comment:
+                ev_naive = ev
+                evokeds_dict[pt]["Naive"].append(ev)
+
+        # Compute difference wave between conditions
+        evokeds_dict[pt]["Difference"].append(
+            mne.combine_evoked([ev_informed, ev_naive], weights=[1, -1])
+        )
+
+# # Compute grand averages across subjects and plot
+# for pt in ["I", "II", "III"]:
+#     for cn in ["Informed", "Naive", "Difference"]:
+#         evokeds_dict[pt][cn] = mne.combine_evoked(evokeds_dict[pt][cn], weights="equal")
+#         evokeds_dict[pt][cn].comment = "part-" + pt + "_condition-" + cn
+#         print("Grand average, part " + pt + ", condition " + cn)
+#         evokeds_dict[pt][cn].plot(picks=["P1", "N170", "N400"], hline=[0], show=True)
+
+# Download fsaverage MRI template
+fs_dir = mne.datasets.fetch_fsaverage(verbose=False)
+subjects_dir = op.dirname(fs_dir)
+subject = "fsaverage"
[…]

### 2021-06-12 code/manuscript.Rmd
clean-up preprocessing

@@
 rerun_preprocessing <- TRUE
-rerun_model_fitting <- FALSE
+rerun_model_fitting <- TRUE
 
@@
       average_by = c("part", "condition", "subject_id"),
+      tfr_baseline = tuple(-0.3, -0.1),
       tfr_equalize = "condition == ['Informed', 'Naive']",
@@
 # Scaling of power in all plots
-limits_power <- c(0, 2)
+limits_power <- c(0, 0.5)
 

### 2021-06-12 code/preprocessing.py

@@ -12,17 +12,17 @@ EEG power at a pre-specified range of frequencies.
 
 """
 
-from glob import glob
-from os import makedirs, removedirs
+from os import makedirs
 
 import mne
 import numpy as np
 import pandas as pd
-from mne import write_evokeds
 from mne.channels import combine_channels, make_standard_montage
+from mne.epochs import Epochs
 from mne.io import read_raw_brainvision
 from mne.preprocessing import ICA
 from mne.time_frequency import tfr_morlet
+from mne.time_frequency.tfr import EpochsTFR
 
 
 def preprocess(
@@ -46,6 +46,7 @@ def preprocess(
     erp_components=None,
     reject={"eeg": 200e-6},
     average_by=None,
+    tfr_baseline=None,
     tfr_equalize=None,
     tfr_resample=None,
     tfr_freqs=None,
@@ -98,7 +99,7 @@ def preprocess(
 
     # Epoching and baseline correction
     events, _ = mne.events_from_annotations(raw, verbose=False)
-    epochs = mne.Epochs(raw_filt, events, event_id, tmin, tmax, baseline, preload=True)
+    epochs = Epochs(raw_filt, events, event_id, tmin, tmax, baseline, preload=True)
 
     # Read behavioral metadata
     epochs.metadata = read_log(fname_log, subject_id)
@@ -117,6 +118,10 @@ def preprocess(
     metadata_backup = epochs.metadata
     epochs.drop_bad(reject=reject)
 
+    # Retrieve indices of good epochs
+    good_epochs = [x for x in epochs.drop_log if not x == ("IGNORED",)]
+    good_epochs = [i for i, x in enumerate(good_epochs) if x == ()]
+
     # Save epochs and trials to output folder
     prefix = output_dir + "/" + subject_id + "_"
     epochs.save(prefix + "epo.fif")
@@ -124,15 +129,17 @@ def preprocess(
 
     # Compute evoked potentials
     evokeds_list, evokeds_df = _evokeds_df_from_epochs(epochs, average_by)
-    write_evokeds(prefix + "ave.fif", evokeds_list)
+    mne.write_evokeds(prefix + "ave.fif", evokeds_list)
     evokeds_df.to_csv(prefix + "ave.csv", float_format="%.3f", index=False)
 
     # Create unfiltered epochs for time-frequency analysis
-    tmin, tmax = -1.0, 1.0
-    epochs_unf = mne.Epochs(
[…]

### 2021-06-12 code/tfr.py

@@ -1,0 +1,110 @@
+from os import makedirs
+
+import numpy as np
+import pandas as pd
+
+# Read evoked *potentials* for all subjects
+subject_id = ["sub-" + "{:02d}".format(sid) for sid in range(1, 49)]
+fname_evo_tfr = ["../data/preprocessed/" + sub + "_ave.csv" for sub in subject_id]
+evo = [pd.read_csv(fname) for fname in fname_evo_tfr]
+evo = pd.concat(evo)
+
+# Average across subjects
+id_vars = ["part", "condition", "time"]
+evo = evo.groupby(id_vars, as_index=False).mean()
+
+# Read evoked *power* for all subjects
+fname_evo_tfr = ["../data/preprocessed/" + sub + "_tfr-ave.csv" for sub in subject_id]
+evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
+evo_tfr = pd.concat(evo_tfr)
+
+# Compute difference in power between conditions
+id_vars = ["part", "condition", "subject_id", "time", "freq"]
+electrodes = [col for col in evo_tfr.columns if (col not in id_vars)]
+evo_tfr_diff = (
+    evo_tfr.query("condition == 'Informed'")[electrodes]
+    - evo_tfr.query("condition == 'Naive'")[electrodes].values
+)
+evo_tfr_diff[id_vars] = evo_tfr.query("condition == 'Informed'")[id_vars]
+
+# Compute flat average across conditions
+id_vars.remove("condition")
+evo_tfr_flat = evo_tfr.groupby(id_vars, as_index=False).mean()
+
+# Permutation test on the difference between conditions
+import numpy as np
+from mne import read_epochs
+from mne.channels import find_ch_adjacency
+from mne.stats import permutation_cluster_1samp_test
+epochs = read_epochs("../data/preprocessed/sub-01_epo.fif", preload=False)
+adjacency, ch_names = find_ch_adjacency(epochs.info, ch_type="eeg")
+
+# # Average frequencies in the lower gamma range
+# tmp = evo_tfr_diff[evo_tfr_diff["part"] == "II"].drop(["part", "condition"], axis=1)
+# tmp = tmp[(tmp["time"] >= 200) & (tmp["time"] <= 400)]
[…]

### 2021-06-13 code/manuscript.Rmd
re-run cleaned preprocessing

@@
   objects_per_condition = "results/obj-per-cond.csv",
-  evo_gavg = "results/evo_gavg.csv",
-  evo_tfr_flat = "results/evo-tfr_flat.csv",
-  evo_tfr_diff = "results/evo-tfr_diff.csv",
+  ave_grand = "results/ave_grand.csv",
+  ave_tfr_flat = "results/ave-tfr_flat.csv",
+  ave_tfr_diff = "results/ave-tfr_diff.csv",
   models_lme = "results/models_lme.RDS"
@@
 # Read evoked *potentials* for all subjects
-fname_evo_tfr = ["data/preprocessed/" + sub + "_ave.csv" for sub in r.subject_id]
-evo = [pd.read_csv(fname) for fname in fname_evo_tfr]
+fname_ave_tfr = ["data/preprocessed/" + sub + "_ave.csv" for sub in r.subject_id]
+evo = [pd.read_csv(fname) for fname in fname_ave_tfr]
 evo = pd.concat(evo)
@@
 evo = evo.groupby(id_vars, as_index=False).mean()
-evo.to_csv(r.fnames["evo_gavg"], float_format="%.3f", index=False)
+evo.to_csv(r.fnames["ave_grand"], float_format="%.3f", index=False)
 
 # Read evoked *power* for all subjects
-fname_evo_tfr = ["data/preprocessed/" + sub + "_tfr-ave.csv" for sub in r.subject_id]
-evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
-evo_tfr = pd.concat(evo_tfr)
+fname_ave_tfr = ["data/preprocessed/" + sub + "_tfr-ave.csv" for sub in r.subject_id]
+ave_tfr = [pd.read_csv(fname) for fname in fname_ave_tfr]
+ave_tfr = pd.concat(ave_tfr)
 
 # Subject 18 is weird!
-evo_tfr = evo_tfr[evo_tfr["subject_id"] != "sub-18"]
+ave_tfr = ave_tfr[ave_tfr["subject_id"] != "sub-18"]
 
@@
 id_vars = ["part", "condition", "subject_id", "time", "freq"]
-electrodes = [col for col in evo_tfr.columns if (col not in id_vars)]
-evo_tfr_diff = (
-    evo_tfr.query("condition == 'Informed'")[electrodes]
-    - evo_tfr.query("condition == 'Naive'")[electrodes].values
-)
-evo_tfr_diff[id_vars] = evo_tfr.query("condition == 'Informed'")[id_vars]
+electrodes = [col for col in ave_tfr.columns if (col not in id_vars)]
+ave_tfr_diff = (
+    ave_tfr.query("condition == 'Informed'")[electrodes]
+    - ave_tfr.query("condition == 'Naive'")[electrodes].values
+)
+ave_tfr_diff[id_vars] = ave_tfr.query("condition == 'Informed'")[id_vars]
 
@@
 id_vars.remove("condition")
-evo_tfr_flat = evo_tfr.groupby(id_vars, as_index=False).mean()
+ave_tfr_flat = ave_tfr.groupby(id_vars, as_index=False).mean()
 
@@
 id_vars.remove("subject_id")
-dfs = [evo_tfr_flat, evo_tfr_diff]
-fnames_tfr = [r.fnames["evo_tfr_flat"], r.fnames["evo_tfr_diff"]]
+dfs = [ave_tfr_flat, ave_tfr_diff]
+fnames_tfr = [r.fnames["ave_tfr_flat"], r.fnames["ave_tfr_diff"]]
 for df, fname in zip(dfs, fnames_tfr):
@@
     df.to_csv(fname, float_format="%.3f", index=False)
-del df, dfs, evo, evo_tfr, evo_tfr_diff, evo_tfr_flat
+del df, dfs, evo, ave_tfr, ave_tfr_diff, ave_tfr_flat
 ```
@@
 montage <- read_csv(fnames$montage, col_types = cols())
-evokeds <- read_csv(fnames$evo_gavg, col_types = cols())
+evokeds <- read_csv(fnames$ave_grand, col_types = cols())
 
@@
 # Read grand averages of evoked power
-evo_tfr_flat <- read_csv(fnames$evo_tfr_flat, col_types = cols(), progress = FALSE)
-evo_tfr_diff <- read_csv(fnames$evo_tfr_diff, col_types = cols(), progress = FALSE)
+ave_tfr_flat <- read_csv(fnames$ave_tfr_flat, col_types = cols(), progress = FALSE)
+ave_tfr_diff <- read_csv(fnames$ave_tfr_diff, col_types = cols(), progress = FALSE)
 
@@
 
-plot_tfr_raster <- function(evo_tfr, limits, tmin, tmax, fmin, fmax, label) {
+plot_tfr_raster <- function(ave_tfr, limits, tmin, tmax, fmin, fmax, label) {
   # Average across electrodes
-  evo_tfr %>%
+  ave_tfr %>%
     pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
@@
 
-plot_tfr_topo <- function(evo_tfr, limits, tmin, tmax, fmin, fmax, legend) {
+plot_tfr_topo <- function(ave_tfr, limits, tmin, tmax, fmin, fmax, legend) {
   # Average across times and frequencies of interest
-  evo_tfr_diff %>%
+  ave_tfr_diff %>%
     # Select time window and frequencies of interest
@@
     plot_tfr_raster, c(tfoi, list(
-      evo_tfr = evo_tfr_flat,
+      ave_tfr = ave_tfr_flat,
       limits = limits_power,
@@
     plot_tfr_raster, c(tfoi, list(
-      evo_tfr = evo_tfr_diff,
+      ave_tfr = ave_tfr_diff,
       limits = limits_power,
@@
     plot_tfr_topo, c(tfoi, list(
-      evo_tfr = evo_tfr_diff,
+      ave_tfr = ave_tfr_diff,
       limits = limits_power,

### 2021-06-13 code/preprocessing.py

@@ -137,7 +137,7 @@ def preprocess(
     epochs_unf.metadata = metadata_backup
 
     # Select only good epochs epochs
-    epochs_unf[good_epochs]
+    epochs_unf = epochs_unf[good_epochs]
 
     # Equalize trial count and downsample if requested
     if tfr_equalize is not None:

### 2021-06-16 code/sourceloc.py
volume-based sourceloc

@@ -1,5 +1,6 @@
 # %%
 import os.path as op
+from threading import stack_size
 
 import groupmne
 import matplotlib.pyplot as plt
@@ -74,8 +75,16 @@ info = evokeds_informed[0].info
 ## MNE ##
 #######################################
 
+# Setup volumn source space
+mri = op.join(fs_dir, 'mri', 'T1.mgz')
+vol_src = mne.setup_volume_source_space(
+    subject, mri=mri, pos=10.0, bem=bem,
+    subjects_dir=subjects_dir,
+    add_interpolator=True,
+    verbose=True)
+
 # Compute standard forward solution
-fwd = mne.make_forward_solution(info, trans, src, bem, meg=False, eeg=True, mindist=5.0)
+fwd = mne.make_forward_solution(info, trans, vol_src, bem, eeg=True, mindist=5.0)
 
 # # Use fwd to compute the sensitivity map for illustration purposes
 # eeg_map = mne.sensitivity_map(fwd, ch_type="eeg", mode="fixed")
@@ -101,7 +110,7 @@ for sid, ev_i, ev_n in zip(subject_id, evokeds_informed, evokeds_naive):
     ev_n.set_eeg_reference("average", projection=True)
     noise_cov = mne.compute_covariance(epochs, tmax=0.0, method=["shrunk", "empirical"])
     inverse_operator = mne.minimum_norm.make_inverse_operator(
-        info, fwd, noise_cov, loose=0.2, depth=3.5
+        info, fwd, noise_cov, loose=1.0, depth=3.5
     )
     stc_i = mne.minimum_norm.apply_inverse(
         ev_i,
@@ -133,7 +142,7 @@ for sid, ev_i, ev_n in zip(subject_id, evokeds_informed, evokeds_naive):
 condition = "Difference"
 data = np.array([stc.data for stc in stcs[condition]], dtype="float32")
 data = data.mean(axis=0)
-stc = mne.SourceEstimate(
+stc = mne.VolSourceEstimate(
     data=data,
     vertices=stcs[condition][0].vertices,
     tmin=stcs[condition][0].tmin,
@@ -142,14 +151,18 @@ stc = mne.SourceEstimate(
 )
 
 # Average across time window and plot
-tmin = 0.150
-tmax = 0.200
-stc_twin = stc.copy().crop(tmin, tmax).mean()
-stc_twin.plot(
-    hemi="lh",
-    clim={"kind": "values", "lims": [1, 2, 3]},
[…]

### 2021-06-16 code/manuscript.Rmd

@@
 # Load custom helper functions and bibliography
-pp <- import_from_path("preprocessing", path = "code")
 source("code/plots_tables.R")
@@
 # Re-run preprocessing and/or model fitting?
-rerun_preprocessing <- TRUE
-rerun_model_fitting <- TRUE
+rerun_preprocessing <- FALSE
+rerun_model_fitting <- FALSE
 
@@
   ave_tfr_diff = "results/ave-tfr_diff.csv",
-  models_lme = "results/models_lme.RDS"
+  models_lme = "results/models_lme.RDS",
+  models_brm = paste0("results/model_brm_", c("RT", "P1", "N170", "N400"), ".RDS") %>%
+    set_names(c("RT", "P1", "N170", "N400")),
+  model_brm_prior = "results/model_brm_prior.RDS"
 )
@@
 
-In the two experiments subsequently reported, participants were presented with real-world objects that were presumed to be unfamiliar to most of them.
+In this experiment, participants were presented with real-world objects that were presumed to be unfamiliar to most of them.
 They first viewed each of these objects without any semantic information.
@@
 
-Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
+Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18 to 32) and no history of psychological disorder or treatment.
 No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
@@
 
-Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum).
-A list of these unfamiliar objects can be found in Appendix A.
+Stimuli for this experiment consisted of 240 grayscale photographs of real-world objects.
+Of these, 120 were well-known everyday objects (e.g., a bicycle, a toothbrush) and served as filler stimuli of no interest.
+The other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Appendix A for a full list).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
-As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
+For each unfamiliar object, a pair of German keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
+As the central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
 The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to hamper such an understanding and keep the perception of the object semantically naive.
@@
 
-Each experimental session consisted of three parts (see Figure \@ref(fig:exp1-plot)A).
+The experiment consisted of three parts (see Figure \@ref(fig:exp1-plot)A).
 In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
@@
 if (rerun_preprocessing) {
+
+  # Import the custom Python functions for preprocessing
+  pp <- import_from_path("preprocessing", path = "code")
 
@@
 ```{r, models_lme}
+# Compute average number of objects per condition
+(objects_per_condition <- read_csv(fnames$objects_per_condition, col_types = cols()) %>%
+  summarise(across(.cols = -subject_id, .fns = mean)) %>%
+  as.list())
+
 # Read single trial data for all subjects
@@
 
+# Record number of rejected ERP epochs per participant
+(rejected <- trials %>%
+  count(subject_id) %>%
+  mutate(n = 360 - n) %>%
+  pull(n))
+
 # Remove trials with unrealistically short RTs or invalid conditions
@@
     # Define model formula
-    formula_lme <- paste0(
+    formula_dv <- paste0(
       dv, " ~ part * condition +
@@
     build <- buildmer(
-      formula = formula_lme,
+      formula = formula_dv,
       data = trials,
@@
 
-```{r models_brm, eval=FALSE}
+```{r models_brm, eval=TRUE}
 # Color scheme for plots
@@
 
-# Define model formula
-formula_brm <- P1 ~ part * condition +
+# Define example model formula
+formula_brm <- bf(
+  P1 ~ part * condition +
     (part * condition | subject_id) +
-  (part * condition | item_id)
-
-# Default prior for slopes
-prior <- set_prior("cauchy(0, 0.707)", class = "b")
+    (part * condition | item_id),
+  sigma ~ 1 + (1 | subject_id)
+)
+
+# Default prior for slopes and sigma
+prior <- c(
+  prior(cauchy(0, 0.707), class = b),
+  prior(student_t(3, 0, 5.7), class = Intercept, dpar = sigma),
+  prior(normal(0, 5), class = sd, group = subject_id, dpar = sigma)
+)
+
+# Hypotheses of comparisons for informed vs. naive within each part
+hypotheses <- c(
+  "posthoc_1" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
+  "posthoc_2" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
+  "posthoc_3" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
+)
 
 # Fit Bayesian mixed model using prior information only
-mod_brm_prior <- brm(
+fit_brm_prior <- brm(
   formula = formula_brm,
@@
   warmup = 2000,
-  backend = "cmdstanr"
+  file = fnames$model_brm_prior,
+  file_refit = "on_change"
 )
@@
 # Prior predictive checks for population-level parameters
-prior_summary(mod_brm_prior)
-summary(mod_brm_prior)
-mcmc_plot(mod_brm_prior, "areas", pars = "^b_", prob_outer = 0.95) +
+prior_summary(fit_brm_prior)
+summary(fit_brm_prior)
+mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95) +
   theme(text = element_text(family = "Helvetica", size = 10))
 
-# Refit using the actual data
-mod_brm_posterior <- update(mod_brm_prior, sample_prior = "yes")
+# Compute posterior distributions for dependent variables
+dvs <- c("logRT", "P1", "N170", "N400")
+map(dvs, function(dv) {
+
+  # Define model formula for the current dependent variable
+  formula_dv <- paste0(
+    dv, " ~ part * condition +
+      (part * condition | subject_id) +
+      (part * condition | item_id)"
+  ) %>%
+    formula()
+
+  # # Allow sigma to very for each participant
+  # formula_dv %<>% bf(sigma ~ 1 + (1 | subject_id))
+
+  # Sample from the posterior distribution
+  fit_brm <- update(
+    fit_brm_prior,
+    formula = formula_dv,
+    sample_prior = "yes",
+    file = fnames$models_brm[[dv]],
+    file_refit = "on_change"
+  )
+
+  # Compute follow-up comparisons with Bayes factors
+  hyps <- hypothesis(fit_brm, hypotheses) %>% {
+    mutate(.$hypothesis, bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused")
+  }
+
+  # Return a list of relevant model outputs
+    return(
+      list(
+        model = fit_brm,
+        summary = summary(fit_brm),
+        hypotheses = hyps
+      )
+    )
+
+}) %>%
+  set_names(dvs) -> models_brm
 
 # Posterior predictive checks for population-level parameters
-summary(mod_brm_posterior)
-mcmc_plot(mod_brm_posterior, "areas", pars = "^b_", prob_outer = 0.95) +
+summary(models_brm$P1)
+mcmc_plot(models_brm$P1, "areas", pars = "^b_", prob_outer = 0.95) +
   theme(text = element_text(family = "Helvetica", size = 10))
@@
 pp_check(
-  mod_brm_posterior,
+  models_brm$P1,
   type = "dens_overlay_grouped",
@@
 pp_check(
-  mod_brm_posterior,
+  models_brm$P1,
   type = "stat_grouped",
@@
 
-# Post-hoc comparisons for informed vs. naive within each part
-hyps <- c(
-  "posthoc_1" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
-  "posthoc_2" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
-  "posthoc_3" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
-)
-hypothesis(mod_brm_posterior, hyps) %>%
-  mutate(.$hypothesis, bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused")
-
-# Alternative with emmeans
-specs <- pairwise ~ condition | part
-emmeans(mod_brm_posterior, specs = specs)
-
-# mod_prior <- brm(formula = formula, data = data_brm, prior = prior, sample_prior = "only")
-# prior_summary(mod_prior)
-# mcmc_plot(mod_prior)
-#
-# mod_post <- update(mod_prior, sample_prior = "yes")
-# summary(mod_post)
-# mcmc_plot(mod_post, pars = "b")
-# plot(mod_post)
-
-hypothesis <- paste0("part", c("I", "II", "III"), ":condition1 = 0")
-bf_brms <- hypothesis(mod_post, hypothesis = hypothesis)
-bf_brms$hypothesis$bf10 <- 1 / bf_brms$hypothesis$Evid.Ratio
-bf_brms
-
-bf_bayestest <- bayestestR::bayesfactor(mod_post)
+bf_bayestest <- bayestestR::bayesfactor(models_brm$P1)
 bf_bayestest
-
-mod_brm_s <- brm(
-  bf(P1 ~ part / condition + (part / condition | participant) + (part / condition | item),
-     sigma ~ 1 + (1 | participant)),
-  prior = c(
-    prior(cauchy(0, 0.707), class = b),
-    prior(student_t(3, 0, 5.7), class = Intercept, dpar = sigma),
-    prior(normal(0, 5), class = sd, group = participant, dpar = sigma)),
-  data = data_brm,
-  family = gaussian(),
-  sample_prior = "yes",
-  save_pars = save_pars(all = TRUE),
-  chains = 4,
-  iter = 20000,
-  warmup = 2000,
-  cores = 4,
-  control = list(adapt_delta = 0.9)
-)
 ```
@@
 
-Offline, the data were preprocessed using the MNE software [Version 0.21.0\; @gramfort2013] in Python [Version 3.8.5\; @vanrossum2009].
+Offline, the data were preprocessed using the MNE software [Version `r system("mne --version", intern = TRUE) %>% str_remove("MNE ")`\; @gramfort2013] in Python [Version `r system("python3 --version", intern = TRUE) %>% str_remove("Python ")`\; @vanrossum2009].
 First, all scalp electrodes were re-referenced to the common average.
@@
 Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
-This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials).
+This led to the exclusion of an average of `r format(round(mean(rejected), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected) / 360, accuracy = 0.1)`; range `r min(rejected)` to `r max(rejected)` trials).
 Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \@ref(fig:exp1-plot)B).
@@
 First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
+This led to the exclusion of an average of `r format(round(objects_per_condition[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Excl_known"]] / 120, accuracy = 0.1)` of all unfamiliar objects).
 Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
 Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
-This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
+This was the case for an average of `r format(round(objects_per_condition[["Informed"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Informed"]]/60, accuracy = 0.1)` of objects presented with matching keywords).
 Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+This was the case for an average of `r format(round(objects_per_condition[["Naive"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Naive"]]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
 Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
@@
 table_exp1 <- create_table(
-models = models_exp1,
+  models = models_lme,
   stub_anova = c("Part", "Condition", "Pt. × con."),
@@
 # Calculate average number of objects per condition in Experiments 1 and 2
-(stims_joint <- (objects_exp1 + objects_exp2) / 2)
+(stims_joint <- (objects_per_condition + objects_exp2) / 2)
 

### 2021-06-26 code/manuscript.Rmd
Fix Bayesian model outputs

@@
 library(emmeans)
+library(bayesplot)
 library(brms)
@@
   models_lme = "results/models_lme.RDS",
-  models_brm = paste0("results/model_brm_", c("RT", "P1", "N170", "N400"), ".RDS") %>%
-    set_names(c("RT", "P1", "N170", "N400")),
+  models_brm = paste0(
+    "results/model_brm_", c("logRT", "P1", "N170", "N400"), ".RDS"
+  ) %>%
+    set_names(c("logRT", "P1", "N170", "N400")),
   model_brm_prior = "results/model_brm_prior.RDS"
@@
 ```{r models_brm, eval=TRUE}
-# Color scheme for plots
-bayesplot::color_scheme_set("purple")
+# Theme for plots
+bayesplot_theme_update(text = element_text(family = "Helvetica", size = 10))
+color_scheme_set("purple")
 
@@
 summary(fit_brm_prior)
-mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95) +
-  theme(text = element_text(family = "Helvetica", size = 10))
+mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95)
 
@@
     formula = formula_dv,
+    newdata = trials,
     sample_prior = "yes",
@@
 # Posterior predictive checks for population-level parameters
-summary(models_brm$P1)
-mcmc_plot(models_brm$P1, "areas", pars = "^b_", prob_outer = 0.95) +
+example_model <- models_brm$N400
+example_model$summary
+example_model$hypotheses
+mcmc_plot(example_model$model, "areas", pars = "^b_", prob_outer = 0.95) +
   theme(text = element_text(family = "Helvetica", size = 10))
@@
 pp_check(
-  models_brm$P1,
+  example_model$model,
   type = "dens_overlay_grouped",
@@
 pp_check(
-  models_brm$P1,
+  example_model$model,
   type = "stat_grouped",
@@
 
-bf_bayestest <- bayestestR::bayesfactor(models_brm$P1)
+bf_bayestest <- bayestestR::bayesfactor(example_model$model)
 bf_bayestest

### 2021-06-27 code/manuscript.Rmd
Remove single trials

@@
   objects_per_condition = "results/obj-per-cond.csv",
+  trials = "results/trials.csv",
   ave_grand = "results/ave_grand.csv",
@@
     )
+
+  # Combine single trial data for all subjects
+  paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
+    map(read_csv, col_types = cols()) %>%
+    bind_rows() %>%
+    write_csv(fnames$trials)
 

### 2021-06-27 code/manuscript.Rmd
Code style improvements

@@
 
-```{r setup, include=FALSE}
+```{r, setup, include=FALSE}
 # Load packages
@@
 # Re-run preprocessing and/or model fitting?
-rerun_preprocessing <- FALSE
-rerun_model_fitting <- FALSE
+rerun_preprocessing <- TRUE
+rerun_model_fitting <- TRUE
 
@@
 # File names for easier I/O
+dvs <- c("logRT", "P1", "N170", "N400")
 fnames <- list(
   montage = "results/montage.csv",
-  objects_per_condition = "results/obj-per-cond.csv",
+  obj_per_cond = "results/obj-per-cond.csv",
   trials = "results/trials.csv",
@@
   models_lme = "results/models_lme.RDS",
-  models_brm = paste0(
-    "results/model_brm_", c("logRT", "P1", "N170", "N400"), ".RDS"
-  ) %>%
-    set_names(c("logRT", "P1", "N170", "N400")),
+  models_brm = paste0("results/model_brm_", dvs, ".RDS") %>% set_names(dvs),
   model_brm_prior = "results/model_brm_prior.RDS"
@@
 
-# Perform preprocessing for all subjects using MNE-Python (see code/preprocessing.py)
-# This will run only if `rerun_preprocessing = TRUE` and if the raw data are available
+# Run preprocessing for all subjects using MNE-Python (see preprocessing.py)
+# Will run only if `rerun_preprocessing = TRUE` and if raw data are available
 if (rerun_preprocessing) {
@@
     rownames_to_column("subject_id") %>%
-    write_csv(fnames$objects_per_condition)
+    write_csv(fnames$obj_per_cond)
 }
@@
 # Read evoked *potentials* for all subjects
-fname_ave_tfr = ["data/preprocessed/" + sub + "_ave.csv" for sub in r.subject_id]
-evo = [pd.read_csv(fname) for fname in fname_ave_tfr]
-evo = pd.concat(evo)
+ave = [f"data/preprocessed/{sub}_ave.csv" for sub in r.subject_id]
+ave = [pd.read_csv(fname) for fname in fname_ave]
+ave = pd.concat(ave)
 
@@
 id_vars = ["part", "condition", "time"]
-evo = evo.groupby(id_vars, as_index=False).mean()
-evo.to_csv(r.fnames["ave_grand"], float_format="%.3f", index=False)
+ave = ave.groupby(id_vars, as_index=False).mean()
+ave.to_csv(r.fnames["ave_grand"], float_format="%.3f", index=False)
 
 # Read evoked *power* for all subjects
-fname_ave_tfr = ["data/preprocessed/" + sub + "_tfr-ave.csv" for sub in r.subject_id]
+ave_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in r.subject_id]
 ave_tfr = [pd.read_csv(fname) for fname in fname_ave_tfr]
@@
 
-# Subject 18 is weird!
-ave_tfr = ave_tfr[ave_tfr["subject_id"] != "sub-18"]
+# # Subject 18 is weird!
+# ave_tfr = ave_tfr[ave_tfr["subject_id"] != "sub-18"]
 
@@
     df.to_csv(fname, float_format="%.3f", index=False)
-del df, dfs, evo, ave_tfr, ave_tfr_diff, ave_tfr_flat
+del df, dfs, ave, ave_tfr, ave_tfr_diff, ave_tfr_flat
 ```
@@
 # Compute average number of objects per condition
-(objects_per_condition <- read_csv(fnames$objects_per_condition, col_types = cols()) %>%
+(obj_per_cond <- read_csv(fnames$obj_per_cond, col_types = cols()) %>%
   summarise(across(.cols = -subject_id, .fns = mean)) %>%
@@
   }) %>%
-
     # Save
@@
 
-```{r models_brm, eval=TRUE}
+```{r, models_brm}
 # Theme for plots
@@
 hypotheses <- c(
-  "posthoc_1" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
-  "posthoc_2" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
-  "posthoc_3" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
+  "I" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
+  "II" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
+  "III" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
 )
@@
 
-  # # Allow sigma to very for each participant
-  # formula_dv %<>% bf(sigma ~ 1 + (1 | subject_id))
-
   # Sample from the posterior distribution
@@
   hyps <- hypothesis(fit_brm, hypotheses) %>% {
-    mutate(.$hypothesis, bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused")
+    mutate(
+      .$hypothesis,
+      bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused"
+    )
   }
@@
   )
-
 }) %>%
@@
 
-bf_bayestest <- bayestestR::bayesfactor(example_model$model)
-bf_bayestest
-```
-
-```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
+# bf_bayestest <- bayestestR::bayesfactor(example_model$model)
+# bf_bayestest
+```
+
+```{r, fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
 # Load montage and evoked data
@@
 First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r format(round(objects_per_condition[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Excl_known"]] / 120, accuracy = 0.1)` of all unfamiliar objects).
+This led to the exclusion of an average of `r format(round(obj_per_cond[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Excl_known"]] / 120, accuracy = 0.1)` of all unfamiliar objects).
 Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
 Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
-This was the case for an average of `r format(round(objects_per_condition[["Informed"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Informed"]]/60, accuracy = 0.1)` of objects presented with matching keywords).
+This was the case for an average of `r format(round(obj_per_cond[["Informed"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Informed"]]/60, accuracy = 0.1)` of objects presented with matching keywords).
 Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of `r format(round(objects_per_condition[["Naive"]], 1), nsmall = 1)` objects per participant (= `r percent(objects_per_condition[["Naive"]]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+This was the case for an average of `r format(round(obj_per_cond[["Naive"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Naive"]]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
 Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
@@
 
-```{r exp1-table, include=TRUE, results="asis"}
+```{r, tab1, include=TRUE, results="asis"}
 # Create table of models for Experiment 1
@@
   stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 1\\smallskip",
-  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
+  caption = paste(
+    "Linear Mixed-Effects Regression Models for Experiment 1",
+    "\\smallskip"
+  ),
+  note = paste(
+    "Pt. = part, con. = condition, est. = estimate, CI = 95\\%",
+    "confidence interval."
+  )
 )
@@
         ) +
-        theme(legend.position = "none",)
+        theme(legend.position = "none", )
     }) -> plotlist
-  #plotlist <- c(plotlist, list(legend))
+  # plotlist <- c(plotlist, list(legend))
   plot_grid(
@@
     nrow = 1,
-    rel_widths = c(2, 7, 0, 7, 1, 7))
+    rel_widths = c(2, 7, 0, 7, 1, 7)
+  )
 }
@@
       limits = limits_power,
-      legend = current_legend))
+      legend = current_legend
+    ))
   ),
@@
 plot_grid(
-  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
+  # plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
   plot_headings(spacing = c(10, 1, 10, 1, 10)),
@@
   annotate(
-    "segment", x = 11 / 34 * 0.85, xend = 11 / 34 * 0.85,
+    "segment",
+    x = 11 / 34 * 0.85, xend = 11 / 34 * 0.85,
     y = -Inf, yend = Inf
@@
   annotate(
-    "segment", x = 23 / 34 * 0.85, xend = 23 / 34 * 0.85,
+    "segment",
+    x = 23 / 34 * 0.85, xend = 23 / 34 * 0.85,
     y = -Inf, yend = Inf
@@
 # Calculate average number of objects per condition in Experiments 1 and 2
-(stims_joint <- (objects_per_condition + objects_exp2) / 2)
+(stims_joint <- (obj_per_cond + objects_exp2) / 2)
 

### 2021-06-27 code/manuscript.Rmd
Fix results folder

@@
   # Combine single trial data for all subjects
+  dir.create("results")
   paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
@@
   # Get standard EasyCap electrode positions and project them into 2D space
-  dir.create("data/processed")
   read_csv("data/preprocessed/sub-01_tfr-ave.csv", col_types = cols()) %>%

### 2021-07-04 code/manuscript.Rmd
Small fixes

@@
 # Read evoked *potentials* for all subjects
-ave = [f"data/preprocessed/{sub}_ave.csv" for sub in r.subject_id]
-ave = [pd.read_csv(fname) for fname in fname_ave]
+fnames = [f"data/preprocessed/{sub}_ave.csv" for sub in r.subject_id]
+ave = [pd.read_csv(fname) for fname in fnames]
 ave = pd.concat(ave)
@@
 # Read evoked *power* for all subjects
-ave_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in r.subject_id]
-ave_tfr = [pd.read_csv(fname) for fname in fname_ave_tfr]
+fnames_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in r.subject_id]
+ave_tfr = [pd.read_csv(fname) for fname in fnames_tfr]
 ave_tfr = pd.concat(ave_tfr)

### 2021-07-17 code/manuscript.Rmd
new line per sentence

--- 2021-06-27 code/manuscript.Rmd
@@
 According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @pylyshyn1999].
-Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @marr1982].
+Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @krizhevsky2012; @marr1982].
 
 This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1994; @lupyan2015; @teufel2017].
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas [e.g., V1 and V2\; @bullier2001; @gilbert2013]---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+The myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas [e.g., V1 and V2; @bullier2001; @gilbert2013]---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
 For instance, the reverse hierarchy theory [@ahissar2004; @hochstein2002] assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
@@
 It is generated by multiple sources in the extrastriate cortices of the middle occipital and fusiform gyri [@dirusso2001; @mangun1995].
-The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus [e.g., size, luminance, and contrast\; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated view of visual perception.
+The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus [e.g., size, luminance, and contrast; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated view of visual perception.
 It is well-established that the P1 is enhanced when participants pay attention to the spatial location of a stimulus [@luck2000; @mangun1995; @mangun1991] but there is also more recent evidence for higher-level cognitive influences that go beyond spatial attention (see below).
@@
 Just as the P1, it is influenced by visual parameters of the stimulus [@johannes1995] and by selective attention, especially when participants are required to discriminate between different visual stimuli [@vogel2000; @mangun1991].
-The N170 is enlarged (i.e., more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g., birds, dogs, or cars\; @gauthier2003a; @tanaka2001].
+The N170 is enlarged (i.e., more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g., birds, dogs, or cars; @gauthier2003a; @tanaka2001].
 This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as the holistic configuration of these features [@eimer2011; @jacques2010; @rossion1999; @sagiv2001].
@@
 )
-
-# bf_bayestest <- bayestestR::bayesfactor(example_model$model)
-# bf_bayestest
 ```
@@
 
-Offline, the data were preprocessed using the MNE software [Version `r system("mne --version", intern = TRUE) %>% str_remove("MNE ")`\; @gramfort2013] in Python [Version `r system("python3 --version", intern = TRUE) %>% str_remove("Python ")`\; @vanrossum2009].
+Offline, the data were preprocessed using the MNE software [Version `r system("mne --version", intern = TRUE) %>% str_remove("MNE ")`; @gramfort2013] in Python [Version `r system("python3 --version", intern = TRUE) %>% str_remove("Python ")`; @vanrossum2009].
 First, all scalp electrodes were re-referenced to the common average.
@@
 The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find\_bads\_eog* function.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find_bads_eog* function.
 After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
@@
 We then performed a model selection algorithm as proposed by @matuschek2017 in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model [determined by *p* ≥ .20\; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
-All models were computed in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4].
+Only if the parsimonious model explained the data equally well as the complex model [determined by *p* ≥ .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
+All models were computed in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4].
 The optimizer function *bobyqa* with 20,000 iterations was used for maximum likelihood estimation.
-The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`\; @R-buildmer].
+The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`; @R-buildmer].
 
 Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the semantically informed against the naive condition within the pre-insight, \mbox{insight}, and post-insight parts.
-This was achieved using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
-All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
+This was achieved using the emmeans package [Version `r as.character(packageVersion("emmeans"))`; @R-emmeans].
+All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`; @R-lmerTest].
 
@@
 (ref:fig2_caption) Results of Experiment 2\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\textit{Note.} 
+\\bigskip\\small\\textit{Note.}
 ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In an exact replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical significance (\textit{p} = .064).
+In an exact replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical significance (\\textit{p} = .064).
 Ampl.
-= amplitude.\newline*\textit{p} \textless{} .05.
-**\textit{p} \textless{} .01.
-***\textit{p} \textless{} .001.
-
--->
+= amplitude.\\newline\*\\textit{p} \\textless{} .05.
+\*\*\\textit{p} \\textless{} .01.
+\*\*\*\\textit{p} \\textless{} .001.
 
@@
 This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
-Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments\; @schad2020].
+Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; @schad2020].
 This factor and its interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
@@
 (ref:fig3_caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\textit{Note.} 
+\\bigskip\\small\\textit{Note.}
 The violins and box plots show the distributions of the by-participant averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modeling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
+The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modeling (see main text and Table \\ref{tab:joint-table}), together with their respective 95\\% confidence interval.
 Ampl.
-= amplitude, 95\% CI = 95\% confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
-**\textit{p} \textless{} .01.
-***\textit{p} \textless{} .001.
-
--->
+= amplitude, 95\\% CI = 95\\% confidence interval, LMM = linear mixed-effects model.\\newline\*\\textit{p} \\textless{} .05.
+\*\*\\textit{p} \\textless{} .01.
+\*\*\*\\textit{p} \\textless{} .001.
 
@@
 Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
+Across both experiments, this was the case for `r percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1]
+Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
 Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
@@
 Another one is our reliance on rare and highly specialized objects (see Appendix A).
-This was necessary to induce the experience of semantic insight in a population of undergraduate students but the results may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
+This was necessary to induce the experience of semantic insight in a population of undergraduate students but the results may not necessarily generalize to the way in which we learn about everyday objects.[^2]
+One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
 Finally, the number participants (*n* = 24 per experiment) and trials (*k* $\approx$ 30 per part in the insight condition and *k* $\approx$ 50 per part in the naive condition) can be considered small by today's standards [@baker2020].

### 2021-07-25 code/preprocessing.py
fix scaling of evokeds

@@ -259,7 +259,7 @@ def _evokeds_df_from_epochs(epochs, average_by):
         evokeds.comment = query
 
         # Convert to DataFrame, adding condition info
-        evokeds_df = evokeds.to_data_frame()
+        evokeds_df = evokeds.to_data_frame(scalings={"eeg": 1e6, "misc": 1e6})
         condition_df = pd.concat([condition[["value"]].transpose()] * len(evokeds_df))
         condition_df.reset_index(inplace=True, drop=True)
         evokeds_df = pd.concat([condition_df, evokeds_df], axis=1)

### 2021-07-25 code/manuscript.Rmd
update text, models

@@
 ---
-title             : |
-  | Event-Related Potentials of the Semantically Informed
-  | Perception of Unfamiliar Objects
-shorttitle        : "Semantic Knowledge and Unfamiliar Objects"
+title             : "Instant effects of semantic information on visual perception"
+shorttitle        : "Semantically informed perception"
 author: 
@@
     affiliation   : "1,2"
+    corresponding : yes
+    address       : "Rudower Chaussee 18, 12489 Berlin, Germany"
+    email         : "alexander.enge@hu-berlin.de"
   - name          : "Franziska Süß"
@@
     affiliation   : "1"
-    corresponding : yes
-    address       : "Rudower Chaussee 18, 12489 Berlin"
-    email         : "rasha.abdel.rahman@hu-berlin.de"
 affiliation:
   - id            : "1"
-    institution   : "Humboldt-Universität zu Berlin"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, 12489 Berlin, Germany"
   - id            : "2"
-    institution   : "Max Planck Institute for Human Cognitive and Brain Sciences"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, 04103 Leipzig, Germany"
   - id            : "3"
-    institution   : "Fachhochschule des Mittelstands"
+    institution   : "Fachhochschule des Mittelstands, 96050 Bamberg, Germany"
 authornote: |
@@
 
-  We have no conflict of interest to disclose.
-  The preprocessed data and code for this study are openly available at https://osf.io/uksbc/.
+  The authors declare no competing financial interests.
+  The preprocessed data and analaysis code for this study are openly available at https://osf.io/uksbc/.
 abstract: |
   Does our perception of an object change as soon as we discover what function it serves?
-This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
-In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception.
+  This question matters not only when we encounter novel tools or gadgets in our everyday lives, but also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+  Here, we showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
   We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
-When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place.
-We replicated these novel findings in an independent sample (*n* = 24).
-Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
+  We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms) and reduced amplitudes in the N400 component (400--700 ms).
+  When the same objects were presented once more without any information, the N400 effect persisted and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
+  Consistent with previous work, our results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
+  We demonstrate for the first time that these effects are instantaneous in the sense that they can be observed within the same trial as well as one trial after the information has been given, providing strong evidence that cognition affects perception.
 keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
@@
 # File names for easier I/O
-dvs <- c("logRT", "P1", "N170", "N400")
+deps <- c("logRT", "P1", "N170", "N400")
 fnames <- list(
@@
   models_lme = "results/models_lme.RDS",
-  models_brm = paste0("results/model_brm_", dvs, ".RDS") %>% set_names(dvs),
-  model_brm_prior = "results/model_brm_prior.RDS"
+  models_brm = str_c("results/model_brm_", deps, ".RDS") %>% set_names(deps),
+  model_brm_prior = "results/model_brm_prior.RDS",
+  models_control = "results/models_control.RDS"
 )
@@
 Does our perception of an object change as soon as we discover what function it serves?
-In this study, we presented participants with unfamiliar objects that were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
-We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resolution of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
-This allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
-
-The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world is "cognitively impenetrable" [@pylyshyn1999] or, in other words, determined solely by the visual input reaching our retina.
-According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @pylyshyn1999].
-Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @krizhevsky2012; @marr1982].
-
-This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1994; @lupyan2015; @teufel2017].
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas [e.g., V1 and V2; @bullier2001; @gilbert2013]---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
-For instance, the reverse hierarchy theory [@ahissar2004; @hochstein2002] assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
+In this study, we presented participants with unfamiliar objects that were preceded either by matching information about their function, thus leading to semantically informed perception, or by non-matching information, thus keeping the perception of the object semantically naive.
+We expected semantically informed perception to differ from naive perception and we capitalized on the high temporal resolution of event-related potentials (ERPs) to find out at which stage (or stages) of the visual processing hierarchy this was indeed the case.
+This allowed us to show that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
+
+The question if higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
+According to one position, our perception of the (visual) world is "cognitively impenetrable" [@pylyshyn1999], that is, determined exclusively by the visual input reaching our retina.
+Higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [@firestone2016; @fodor1983; @pylyshyn1999].
+Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
+This feed-forward visual architecture has been mirrored in both classical [e.g., @marr1982] and contemporary [e.g., @krizhevsky2012] computer vision models, allowing them to achieve human-level perfomance in predicting object category label from images.
+
+However, the cognitive impenetrability hypothesis is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on [@churchland1994; @lupyan2015; @teufel2017].
+There are myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas [e.g., V1 and V2; @bullier2001; @gilbert2013].
+These anatomical recurrences as well as behavioral evidence from cognitive psychology have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
+For instance, the reverse hierarchy theory [@ahissar2004; @hochstein2002] proposes that conscious visual perception occurs initially at the level of whole objects or object categories.
 Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
-Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
+Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (i.e., a high-level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
 Finally, an active role of top-down influences is also promoted by theories of vision in the framework of Bayesian inference and predictive coding [e.g., @clark2013; @lupyan2015; @panichello2013; @yuille2006].
 
-Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition [for review, see @collins2014; @vetter2014].
+Empirical findings from experimental psychology have accumulated support to the view that perception can indeed be penetrated by other aspects of cognition [for review, see @collins2014; @vetter2014].
 These aspects of cognition may include transient states such as emotions [e.g., @bocanegra2009; @phelps2016] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @gauthier2003; @weller2019].
 Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical and pointed out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
-They argue, for example, that most behavioral paradigms have not been able to discern between perceptual and post-perceptual (e.g., memory-related) effects.
-Furthermore, cognitive influences in some studies were confounded with differences in the low-level visual input itself.
-We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our methodology and results.
-
-In general, however, it is important to note that one productive way to circumvent at least some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or post-perceptual---are influenced by higher-level capacities such as semantic knowledge.
-This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
+They have argued, for example, that most behavioral paradigms had not been able to discern between perceptual and post-perceptual (e.g., memory-related) effects.
+Furthermore, cognitive influences in some studies had been confounded with differences in the low-level visual input itself.
+We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our research methodology and results.
+
+One productive way of alleviating at least some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a relatively direct test of which processing stages---perceptual and/or post-perceptual---are influenced by higher-level capacities such as semantic knowledge.
+This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain potentials show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
 
@@
 
-Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge about visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
-Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing.
+Previous studies have focused on these ERP components to investigate which processing stages are indeed influenced by knowledge about visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
+Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that are typically taken to reflect bottom-up visual processing.
 This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (i.e., cooking recipes) for the other half of the objects [@abdelrahman2008, Experiment 1].
@@
 The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
-In this study, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
+In this study, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in how likely participants were able to detect the objects during the attentional blink.
 This can be taken as further evidence for an influence of semantic knowledge on the early visual perception of unfamiliar objects.
 
-A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects which were rendered difficult to recognize by converting them to two-tone, "Mooney" images [@samaha2018, Experiment 4].
+A complementary approach has been taken in a recent study that investigated ERPs in response to familiar (rather than unfamiliar) objects that were rendered difficult to recognize by converting them to two-tone, "Mooney" images [@samaha2018, Experiment 4].
 In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
 When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha-band power was higher for meaning-trained images than for perceptually-trained images.
-As before, this effect of perceiving objects in a semantically informed way seems to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
+As before, this effect of perceiving objects in a semantically informed way seemed to be behaviorally relevant because participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the delayed matching task.
 This alternative approach further corroborates an early influence of semantic information on the visual perception of objects.
@@
 The second question is how much learning is actually necessary before reliable top-down effects of knowledge on ERP amplitudes can be obtained: Does it actually take dozens of repetitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is about the nature of the effects of knowledge on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
+The third and closely related question is about the nature of the effects of knowledge on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects that have been altered over the course of the learning process?
 By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we were able to provide tentative answers to all three of these questions.
 
-In this experiment, participants were presented with real-world objects that were presumed to be unfamiliar to most of them.
+In the present experiment, participants were presented with real-world objects that were presumed to be unfamiliar to most of them.
 They first viewed each of these objects without any semantic information.
@@
 
-# Experiment 1
-
-## Method
-
-### Participants
-
-Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18 to 32) and no history of psychological disorder or treatment.
+# Materials and Methods
+
+## Participants
+
+Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18--32) and no history of psychological disorder or treatment.
 No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
 All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
-They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-
-### Materials
-
-Stimuli for this experiment consisted of 240 grayscale photographs of real-world objects.
+They provided written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+
+## Materials
+
+Stimuli consisted of 240 grayscale photographs of real-world objects.
 Of these, 120 were well-known everyday objects (e.g., a bicycle, a toothbrush) and served as filler stimuli of no interest.
@@
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
-At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
+At a standardized viewing distance of 90 cm, the images subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
 
 For each unfamiliar object, a pair of German keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
-As the central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to hamper such an understanding and keep the perception of the object semantically naive.
+As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
+The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically naive.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
@@
 
-### Procedure
-
-The experiment consisted of three parts (see Figure \@ref(fig:exp1-plot)A).
+## Experimental Design
+
+The experiment consisted of three parts (see Figure \@ref(fig:fig1)A).
 In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
 Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
-The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
+The inter-trial interval was 0.5 s and participants took a self-timed break after each block of 60 objects.
 The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
@@
   str_pad(width = 2, pad = 0) %>%
-  paste0("sub-", .) -> subject_id
+  str_c("sub-", .) -> subject_id
 
@@
   dir.create("results")
-  paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
+  str_c("data/preprocessed/", subject_id, "_trials.csv") %>%
     map(read_csv, col_types = cols()) %>%
@@
   import("mne.channels._standard_montage_utils")$MONTAGE_PATH %>%
-    paste0("/easycap-M1.txt") %>%
+    str_c("/easycap-M1.txt") %>%
     read_tsv(col_types = cols()) %>%
@@
 ```{python, grand_averaging, eval=rerun_preprocessing}
-from os import makedirs
-
 import numpy as np
@@
 
-# Create output folder
-makedirs("data/processed", exist_ok=True)
-
 # Read evoked *potentials* for all subjects
-ave = [f"data/preprocessed/{sub}_ave.csv" for sub in r.subject_id]
-ave = [pd.read_csv(fname) for fname in fname_ave]
+subs = r.subject_id
+fnames_ave = [f"data/preprocessed/{sub}_ave.csv" for sub in subs]
+ave = [pd.read_csv(fname) for fname in fnames_ave]
 ave = pd.concat(ave)
@@
 # Read evoked *power* for all subjects
-ave_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in r.subject_id]
-ave_tfr = [pd.read_csv(fname) for fname in fname_ave_tfr]
+fnames_ave_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in subs]
+ave_tfr = [pd.read_csv(fname) for fname in fnames_ave_tfr]
 ave_tfr = pd.concat(ave_tfr)
@@
 # Read single trial data for all subjects
-paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
+str_c("data/preprocessed/", subject_id, "_trials.csv") %>%
   map(read_csv, col_types = cols()) %>%
@@
     part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c("Informed", "Naive")),
     subject_id = factor(subject_id),
@@
 
+# Remove irrelevant conditions for main analysis
+trials_main <- mutate(
+  trials,
+  condition = factor(condition, levels = c("Informed", "Naive")),
+)
+
 # Contrast coding for conditions
@@
   t() %>%
-  ginv() -> contrasts(trials$condition)
+  ginv() -> contrasts(trials_main$condition)
 
@@
 
-  # Compute models for dependent variables in parallel
-  dvs <- c("logRT", "P1", "N170", "N400")
-  map(dvs, function(dv) {
-
-    # Define model formula
-    formula_dv <- paste0(
-      dv, " ~ part * condition +
-        (part * condition | subject_id) +
-        (part * condition | item_id)"
-    ) %>% formula()
-
-    # Define follow-up comparisons
-    specs <- pairwise ~ condition | part
+  # Define function for building a single mixed-effect model
+  build_lme <- function(dep, formula, data, n_cores) {
+
+    # Convert formula to terms list
+    formula <- tabulate.formula(formula)
 
@@
     build <- buildmer(
-      formula = formula_dv,
-      data = trials,
       buildmerControl = buildmerControl(
+        formula,
+        data,
         direction = c("backward", "backward"),
@@
         ddf = "Satterthwaite",
+        dep = dep,
         REML = FALSE,
@@
     emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
+    specs <- pairwise ~ condition | part
     em <- emmeans(build@model, specs, infer = TRUE)
@@
     )
-  }) %>%
-    # Save
-    set_names(dvs) %T>%
+  }
+
+  # Compute models for all dependent variables in parallel
+  form <- RT ~ part * condition +
+    (part * condition | subject_id) +
+    (part * condition | item_id)
+  map(
+    deps,
+    build_lme,
+    formula = form,
+    data = trials_main,
+    n_cores = n_cores
+  ) %>%
+    set_names(deps) %T>%
     saveRDS(fnames$models_lme) -> models_lme
@@
 
-```{r, models_brm}
+```{r, models_brm, eval=FALSE}
 # Theme for plots
@@
 summary(fit_brm_prior)
-mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95)
+# mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95)
 
 # Compute posterior distributions for dependent variables
-dvs <- c("logRT", "P1", "N170", "N400")
-map(dvs, function(dv) {
+deps <- c("logRT", "P1", "N170", "N400")
+map(deps, function(dv) {
 
   # Define model formula for the current dependent variable
-  formula_dv <- paste0(
+  formula_dv <- str_c(
     dv, " ~ part * condition +
@@
 }) %>%
-  set_names(dvs) -> models_brm
+  set_names(deps) -> models_brm
 
@@
 example_model$hypotheses
-mcmc_plot(example_model$model, "areas", pars = "^b_", prob_outer = 0.95) +
-  theme(text = element_text(family = "Helvetica", size = 10))
-
-# Posterior predictive checks subject by subject
-pp_check(
-  example_model$model,
-  type = "dens_overlay_grouped",
-  nsamples = 50,
-  group = "subject_id"
-)
-pp_check(
-  example_model$model,
-  type = "stat_grouped",
-  nsamples = 1000,
-  group = "subject_id",
-  stat = "sd"
-)
+# mcmc_plot(example_model$model, "areas", pars = "^b_", prob_outer = 0.95) +
+#   theme(text = element_text(family = "Helvetica", size = 10))
+
+# # Posterior predictive checks subject by subject
+# pp_check(
+#   example_model$model,
+#   type = "dens_overlay_grouped",
+#   nsamples = 50,
+#   group = "subject_id"
+# )
+# pp_check(
+#   example_model$model,
+#   type = "stat_grouped",
+#   nsamples = 1000,
+#   group = "subject_id",
+#   stat = "sd"
+# )
 ```
@@
 montage <- read_csv(fnames$montage, col_types = cols())
-evokeds <- read_csv(fnames$ave_grand, col_types = cols())
+evokeds <- read_csv(fnames$ave_grand, col_types = cols(), progress = FALSE)
 
 # Create plot for Experiment 1
-plot_fig1(erp_components, evokeds, trials, models_lme)
+plot_fig1(erp_components, evokeds, trials_main, models_lme)
 ```
@@
 (B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
+Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight part, less negative amplitudes in the N400 component during the insight and post-insight parts, and more positive amplitudes in the P1 component during the post-insight part.
 Ampl.
@@
 
-In the *insight* part, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+In the *insight* part, the 120 unfamiliar objects were presented for the second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
 Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
@@
 
-Finally, in the *post-insight* part, the unfamiliar objects were presented for a third time with an identical trial structure as in the pre-insight part, that is, without any keywords.
-Note that the insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight part (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight part (without keywords) before moving on to the next block consisting of 30 different objects.
+In the *post-insight* part, the unfamiliar objects were presented for a third time with the same trial structure as in the pre-insight part, that is, without any keywords.
+The insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight part (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight part (without keywords) before moving on to the next block consisting of 30 different objects.
 They continued like this until all four blocks were completed in both parts.
@@
 
-### EEG Recording and Preprocessing
+## EEG Recording and Preprocessing
 
@@
 Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively.
-During the recording, electrode impedance was kept below 5 kΩ.
+Electrode impedances were kept below 5 kΩ.
 An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
 
-Offline, the data were preprocessed using the MNE software [Version `r system("mne --version", intern = TRUE) %>% str_remove("MNE ")`; @gramfort2013] in Python [Version `r system("python3 --version", intern = TRUE) %>% str_remove("Python ")`; @vanrossum2009].
+The data were preprocessed offline using the MNE software [Version `r system("mne --version", intern = TRUE) %>% str_remove("MNE ")`; @gramfort2013] in Python [Version `r system("python3 --version", intern = TRUE) %>% str_remove("Python ")`; @vanrossum2009].
 First, all scalp electrodes were re-referenced to the common average.
 Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
-The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find_bads_eog* function.
+The first 15 components were extracted with the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the `find_bads_eog` function.
 After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
+Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the presentation of each unfamiliar object.
 The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset.
 Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
-This led to the exclusion of an average of `r format(round(mean(rejected), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected) / 360, accuracy = 0.1)`; range `r min(rejected)` to `r max(rejected)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \@ref(fig:exp1-plot)B).
-
-### Statistical Analysis
-
-First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented).
+This led to the exclusion of an average of `r format(round(mean(rejected), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected) / 360, accuracy = 0.1)`; range `r min(rejected)`--`r max(rejected)` trials).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+
+## Statistical Analyses
+
+First, we excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight part (i.e., before any keywords were presented).
 This led to the exclusion of an average of `r format(round(obj_per_cond[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Excl_known"]] / 120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
-Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
+Next, to delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participant (see Figure \@ref(fig:fig1)A).
+Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if the participant indicated knowing what the object was or having an assumption.
 This was the case for an average of `r format(round(obj_per_cond[["Informed"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Informed"]]/60, accuracy = 0.1)` of objects presented with matching keywords).
-Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
+Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if the participant indicated not knowing what the object was or having rather no assumption.
 This was the case for an average of `r format(round(obj_per_cond[["Naive"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Naive"]]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
+The same assignment of objects to conditions (based on the manipulation and responses in the insight part) was also used for analyzing the pre-insight and post-insight parts.
 This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).
@@
 The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
-For the purpose of the present study, these models have at least three desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant averages.
-First, they can leverage all of the information that is present in the data set on the single trial level, some of which would be lost when computing averages.
-Second, they can account simultaneously for the non-independence of data points coming from the same participant and/or from the same item.
-In contrast, the neglect of the item as a random variable in by-participant ANOVAs can lead to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
-Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable when the assignment of trials to conditions is co-determined by the experimental manipulation and the behavior of participants in response to this manipulation [e.g., @fröber2017].
+Compared to traditional by-participant or by-item analyses of variance, these models allow tighter control over the false positive rate because they simultaneously account for by-participant and by-item non-independencies in the data [@bürki2018; @judd2012].
+Furthermore, they flexibly handle unbalanced data which in our case arose from the rejection of ERP epochs as well as the way we constructed our experimental conditions (see above).
 
 Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
-All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e., subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
-For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to @schad2020.
-To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
-We then performed a model selection algorithm as proposed by @matuschek2017 in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model [determined by *p* ≥ .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
+All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast [i.e., subtracting the first part from the second part and the second part from the third part, the intercept being the grand mean across all three parts; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
+To determine the random effects structure, we always started with the maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
+We then performed a model selection algorithm proposed by @matuschek2017 to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+Only if the parsimonious model explained the data similarly well as the complex model [determined by *p* ≥ .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the resulting formulas after model selection).
 All models were computed in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4].
-The optimizer function *bobyqa* with 20,000 iterations was used for maximum likelihood estimation.
+The optimizer function *bobyqa* with a maximum of 10^6^ iterations was used for maximum likelihood estimation.
 The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`; @R-buildmer].
 
-Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the semantically informed against the naive condition within the pre-insight, \mbox{insight}, and post-insight parts.
-This was achieved using the emmeans package [Version `r as.character(packageVersion("emmeans"))`; @R-emmeans].
+To investiage if semantically informed perception had an influence on the ERPs within each part, planned follow-up comparisons were calculated, contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight parts.
+This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`; @R-emmeans].
 All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`; @R-lmerTest].
 
-The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (<https://osf.io/uksbc/>).
-We are not able to share the raw EEG data openly because we did not obtain participants' informed consent to do so.
-
-## Results
-
-Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
-In the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception.
-The other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
-The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \@ref(fig:exp1-plot)A), thereby making sure that semantically informed and naive perception did indeed occur.
-The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, the N170 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.
+The materials, single trial preprocessed data, and all code for data analysis are openly available at <https://osf.io/uksbc/>.
+
+# Results
 
 ```{r, tab1, include=TRUE, results="asis"}
-# Create table of models for Experiment 1
-table_exp1 <- create_table(
-  models = models_lme,
+# Create table of LMM results
+tab1 <- create_table(
+  models = models_lme[c("P1", "N170", "N400")],
   stub_anova = c("Part", "Condition", "Pt. × con."),
@@
   caption = paste(
-    "Linear Mixed-Effects Regression Models for Experiment 1",
+    "Linear Mixed-Effects Regression Models",
     "\\smallskip"
@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (see Table \@ref(tab:exp1-table)).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r table_exp1$anov["Condition", "N400_df"]` = `r table_exp1$anov["Condition", "N400_f"]`, *p* = `r table_exp1$anov["Condition", "N400_p"]`.
-Crucially, the part × condition interaction was significant in the N170 component, *F*`r table_exp1$anov["Pt.
-× con.", "N170_df"]` = `r table_exp1$anov["Pt.
-× con.", "N170_f"]`, *p* = `r table_exp1$anov["Pt.
-× con.", "N170_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt.
-× con.", "N400_df"]` = `r table_exp1$anov["Pt.
-× con.", "N400_f"]`, *p* `r table_exp1$anov["Pt.
-× con.", "N400_p"]`, while also showing a weak statistical trend in the P1 component, *F*`r table_exp1$anov["Pt.
-× con.", "P1_df"]` = `r table_exp1$anov["Pt.
-× con.", "P1_f"]`, *p* = `r table_exp1$anov["Pt.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r fig1$anov["Part", "P1_f"]`, all *p*s `r fig1$anov["Part", "P1_p"]` (see Table \@ref(tab:tab1)).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r fig1$anov["Condition", "N400_df"]` = `r fig1$anov["Condition", "N400_f"]`, *p* = `r fig1$anov["Condition", "N400_p"]`.
+Crucially, the part × condition interaction was significant in the N170 component, *F*`r tab1$anov["Pt.
+× con.", "N170_df"]` = `r tab1$anov["Pt.
+× con.", "N170_f"]`, *p* = `r tab1$anov["Pt.
+× con.", "N170_p"]`, and in the N400 component, *F*`r tab1$anov["Pt.
+× con.", "N400_df"]` = `r tab1$anov["Pt.
+× con.", "N400_f"]`, *p* `r tab1$anov["Pt.
+× con.", "N400_p"]` but not in the P1 component, *F*`r tab1$anov["Pt.
+× con.", "P1_df"]` = `r tab1$anov["Pt.
+× con.", "P1_f"]`, *p* = `r tab1$anov["Pt.
 × con.", "P1_p"]`.
@@
 
-### ERPs Before Insight Was Occurring
-
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s ≥ `r table_exp1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:exp1-table) and Figure \@ref(fig:exp1-plot)B).
+## ERPs Before Insight Was Occurring
+
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s ≥ `r tab1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:tab1) and Figure \@ref(fig:fig1)B).
 On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
@@
 
-### ERPs While Insight Was Occurring
-
-In the insight part, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e., more negative), *b* = `r table_exp1$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Insight part", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e., less negative), *b* = `r table_exp1$conts["Insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Insight part", "N400_p"]`, compared to when the object was viewed naively without relevant semantic information.
-As in the pre-insight part, there were no reliable differences in the P1 component, *b* = `r table_exp1$conts["Insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Insight part", "P1_p"]`.
-
-### ERPs After Insight Had Occurred
+## ERPs While Insight Was Occurring
+
+In the insight part, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perceptio nof the objects semantically naive.
+During semantically informed perception, the amplitude of the N170 component was significantly enlarged (i.e., more negative), *b* = `r tab1$conts["Insight part", "N170_est"]` µV, *p* = `r tab1$conts["Insight part", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e., less negative), *b* = `r tab1$conts["Insight part", "N400_est"]` µV, *p* `r tab1$conts["Insight part", "N400_p"]`, compared to naive perception.
+As in the pre-insight part, there were no reliable differences in the P1 component, *b* = `r tab1$conts["Insight part", "P1_est"]` µV, *p* = `r tab1$conts["Insight part", "P1_p"]`.
+
+## ERPs After Insight Had Occurred
 
 In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part).
-This allowed us to test if the semantic information had any lasting effects on the processing of the objects.
-As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Post-insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *b* = `r table_exp1$conts["Post-insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "N170_p"]`.
-Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "P1_p"]`.
-
-```{r, fig3, include=TRUE}
+As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r tab1$conts["Post-insight part", "N400_est"]` µV, *p* `r tab1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *b* = `r tab1$conts["Post-insight part", "N170_est"]` µV, *p* = `r tab1$conts["Post-insight part", "N170_p"]`.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, *b* = `r tab1$conts["Post-insight part", "P1_est"]` µV, *p* = `r tab1$conts["Post-insight part", "P1_p"]`.
+
+```{r, fig3, eval=FALSE, include=TRUE}
 # Read grand averages of evoked power
@@
 
-## Discussion
-
-In Experiment 1, we measured the ERPs of participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-insight part) they were able to understand what kind of object they were seeing.
-To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
-
-In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms).
-When the same objects were presented once more in the post-insight part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for which semantically informed perception had taken place.
-
-Because of the novelty of our experimental paradigm---measuring the ERPs while rather than after participants received semantic information about unfamiliar objects---and because of the novelty of our findings, we ran a replication study with another sample of participants to assess the robustness of these effects.
-
-# Experiment 2
-
-## Method
-
-### Participants
-
-Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29 years) who had not participated in Experiment 1.
-They had no history of psychological disorders or treatment, were right-handed, and reported normal or corrected-to-normal vision.
-They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-
-### Materials, Procedure, and Analysis
-
-```{r exp2-preproc, eval=rerun_preproc}
-# Read behavioral data for Experiment 2
-list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp2
-
-# Preprocess the EEG for Experiment 2 in Python
-map2(
-  .x = list.files("data/exp2/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp2,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
+## Control Analysis
+
+```{r models_control, eval=rerun_model_fitting}
+# Use a different control condition ("failed insight")
+trials_control <- mutate(
+  trials,
+  condition = factor(condition, levels = c("Informed", "Excl_informed")),
+)
+
+# Contrast coding for conditions
+c("Informed" = 1, "Excl_informed" = -1) %>%
+  t() %>%
+  ginv() -> contrasts(trials_control$condition)
+
+# Load fitted models or rerun them
+if (!rerun_model_fitting) {
+
+  # Load models
+  models_control <- readRDS(fnames$models_control)
+} else {
+
+  # Compute models for all dependent variables in parallel
+  form <- RT ~ part * condition +
+    (part * condition | subject_id) +
+    (part * condition | item_id)
+  map(
+    deps,
+    build_lme,
+    formula = form,
+    data = trials_control,
+    n_cores = n_cores
   ) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp2
-
-# Backup epochs to the export folder
-epochs_exp2$save("data/processed/exp2-epo.fif")
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
-  set_names(comps$name) %>%
-  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
-  write_tsv("data/processed/exp2-data.tsv") -> data_exp2
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("data/processed/exp2-gaverages.RDS")
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp2, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
-  write_tsv("data/processed/exp2-objects.tsv")
-
-# Remove the epochs to free up memory
-rm(epochs_exp2)
+    set_names(deps) %T>%
+    saveRDS(fnames$models_control) -> models_control
+}
 ```
 
-```{r exp2-models, eval=rerun_models}
-# Load preprocessed single-trial data
-read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
-    )),
-    participant = factor(participant),
-    item = factor(item)
-  ) %>%
-  # Remove any trials excluded from conditions
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> data_exp2
-
-# Apply contrasts to the factors in the data
-contrasts(data_exp2$condition) <- ginv(contrasts_condition)
-contrasts(data_exp2$part) <- ginv(contrasts_part)
-
-# Compute the models for Experiment 2
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp12,
-  data = data_exp2,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("data/processed/exp2-models.RDS") -> models_exp2
-```
-
-```{r exp2-import}
-# Load average number of objects per condition
-(read_tsv("data/processed/exp2-objects.tsv", col_types = cols()) %>%
-  summarise(across(.cols = -Participant, .fns = mean)) %>%
-  slice(1) %>% unlist() -> objects_exp2)
-
-# Load preprocessed single-trial data
-read_tsv("data/processed/exp2-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
-    )),
-    participant = factor(participant),
-    item = factor(item)
-  ) -> data_exp2
-
-# Check number of rejected epochs
-data_exp2 %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n) -> rejected_exp2
-mean(rejected_exp2) # Mean
-median(rejected_exp2) # Median
-range(rejected_exp2) # Range
-
-# Load grand-averaged ERPs and linear mixed models
-evokeds_exp2 <- readRDS("data/processed/exp2-gaverages.RDS")
-models_exp2 <- readRDS("data/processed/exp2-models.RDS")
-```
-
-All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
-An average of `r format(round(objects_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r percent(objects_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects was assigned to the semantically informed condition (= `r percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects was assigned to the naive condition (= `r percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
-
-## Results
-
-```{r exp2-table, include=TRUE, results="asis"}
-# Create table of models for Experiment 2
-table_exp2 <- create_table(
-  models_exp2,
+```{r, tab2, include=TRUE, results="asis"}
+# Create table of LMM results
+tab2 <- create_table(
+  models = models_control[c("P1", "N170", "N400")],
   stub_anova = c("Part", "Condition", "Pt. × con."),
   stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 2\\smallskip",
-  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all *F*s ≥ `r table_exp2$anov["Part", "N170_f"]`, all *p*s `r table_exp2$anov["Part", "N170_p"]` (see Table \@ref(tab:exp2-table)).
-Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, *F*`r table_exp2$anov["Condition", "N400_df"]` = `r table_exp2$anov["Condition", "N400_f"]`, *p* `r table_exp2$anov["Condition", "N400_p"]`.
-The part × condition interaction was significant in the P1 component, *F*`r table_exp2$anov["Pt.
-× con.", "P1_df"]` = `r table_exp2$anov["Pt.
-× con.", "P1_f"]`, *p* = `r table_exp2$anov["Pt.
-× con.", "P1_p"]`, and in the N400 component, *F*`r table_exp2$anov["Pt.
-× con.", "N400_df"]` = `r table_exp2$anov["Pt.
-× con.", "N400_f"]`, *p* `r table_exp2$anov["Pt.
-× con.", "N400_p"]`, but not in the N170 component, *F*`r table_exp2$anov["Pt.
-× con.", "N170_df"]` = `r table_exp2$anov["Pt.
-× con.", "N170_f"]`, *p* = `r table_exp2$anov["Pt.
-× con.", "N170_p"]`.
-
-```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:fig2_caption)"}
-# Create plot for Experiment 2
-plot_grid(
-  # plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
-  plot_headings(spacing = c(10, 1, 10, 1, 10)),
-  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
-  plot_legends_erps(direction = "horizontal"),
-  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
-) + # Add some lines (to separate the parts)
-  annotate_line(x = 0.328, xend = 0.328, y = 0.15, yend = Inf) +
-  annotate_line(x = 0.672, xend = 0.672, y = 0.15, yend = Inf)
-```
-
-(ref:fig2_caption) Results of Experiment 2\smallskip
-\\bigskip\\small\\textit{Note.}
-ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In an exact replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical significance (\\textit{p} = .064).
-Ampl.
-= amplitude.\\newline\*\\textit{p} \\textless{} .05.
-\*\*\\textit{p} \\textless{} .01.
-\*\*\*\\textit{p} \\textless{} .001.
-
-### ERPs Before Insight Was Occurring
-
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all *p*s ≥ `r table_exp2$conts["Pre-insight part", "P1_p"]` (see Table \@ref(tab:exp2-table) and Figure \@ref(fig:exp2-plot)).
-
-### ERPs While Insight Was Occurring
-
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with an enhancement of the N170 component, although this effect marginally failed to reach statistical significance, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`.
-The reduction of the N400 component during semantically informed perception remained significant, *b* = `r table_exp2$conts["Insight part", "N400_est"]` µV, *p* `r table_exp2$conts["Insight part", "N400_p"]`.
-
-### ERPs After Insight Had Occurred
-
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) again led to significantly reduced amplitudes in the N400 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Post-insight part", "N400_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "N400_p"]`.
-Also, P1 amplitudes in response these objects were significantly enlarged, *b* = `r table_exp2$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "P1_p"]`.
-
-### Joint Analysis of Experiments 1 and 2
-
-In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2.
-This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
-Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; @schad2020].
-This factor and its interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
-They were not included as by-participant random slopes because different participants took part in Experiments 1 and 2.
-Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit [@matuschek2017; @R-buildmer].
-The resulting formulas for the models can be found in Appendix B.
-
-```{r joint-import}
-# Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
-data_exp2 %>%
-  mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
-  bind_rows(aha, ., .id = "experiment") %>%
-  mutate(experiment = as_factor(experiment)) -> data_joint
-
-# Subset only the relevant conditions
-data_joint %>%
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> data_joint_subs
-```
-
-```{r joint-models, eval=rerun_models}
-# Contrast coding for experiment (2-1), condition (informed-naive), and part (2-1, 3-1)
-t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
-contrasts(data_joint_subs$experiment) <- ginv(contrasts_experiment)
-contrasts(data_joint_subs$condition) <- ginv(contrasts_condition)
-contrasts(data_joint_subs$part) <- ginv(contrasts_part)
-
-# New formula for LMMs
-form_joint <- buildmer::tabulate.formula(
-  ~ part * condition * experiment +
-    (part * condition | participant) +
-    (part * condition * experiment | item)
-) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-
-# Apply the function to compute the joint models for Experiments 1 and 2
-map(
-  comps$name,
-  compute_models,
-  formula = form_joint,
-  data = data_joint_subs,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("data/processed/joint-models.RDS") -> models_joint
-```
-
-```{r joint-table, include=TRUE, results="asis"}
-# Load linear mixed models
-models_joint <- readRDS("data/processed/joint-models.RDS")
-
-# Create table of models for Experiments 1 and 2 combined
-table_joint <- create_table(
-  models_joint,
-  stub_anova = c(
-    "Part", "Condition", "Experiment", "Pt. × con.",
-    "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."
+  caption = paste(
+    "Control Analysis",
+    "\\smallskip"
   ),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption =
-    "Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\\smallskip",
-  note =
-    "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\\% confidence interval."
-)
-
-# Extract the follow-up contrast for the main effect of experiment
-suppressMessages(emmeans::emm_options(lmerTest.limit = Inf))
-suppressMessages(
-  emmeans::emmeans(
-    models_joint$N400$model,
-    specs = pairwise ~ experiment, infer = TRUE
-  )$contrasts %>%
-    as.data.frame() %>%
-    transmute(
-      est = round(estimate, 2) %>%
-        format(nsmall = 2, trim = TRUE),
-      p = round(`p.value`, 3) %>%
-        format(nsmall = 3, trim = TRUE) %>%
-        as.character() %>%
-        substr(2, nchar(.))
-    ) -> conts_N400_joint
-)
-```
-
-As shown in Table \@ref(tab:joint-table), the main effect of part was significant in the P1, N170, and N400 component, all *F*s ≥ `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Condition", "N400_df"]` = `r table_joint$anov["Condition", "N400_f"]`, *p* `r table_joint$anov["Condition", "N400_p"]`.
-Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s ≥ `r table_joint$anov["Pt.
-× con.", "P1_f"]`, all *p*s ≤ `r table_joint$anov["Pt.
-× con.", "P1_p"]`.
-There was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, with more negative amplitudes in Experiment 1 as compared to Experiment 2, *b* = `r conts_N400_joint$est`.
-However, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
-
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \@ref(tab:joint-table) and Figure \@ref(fig:joint-plot)).
-This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all *p*s ≥ `r table_joint$conts["Pre-insight part", "N400_p"]`, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N170_est"]` µV, *p* = `r table_joint$conts["Insight part", "N170_p"]`, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N400_est"]` µV, *p* `r table_joint$conts["Insight part", "N400_p"]`, and in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "N400_est"]` µV, *p* `r table_joint$conts["Post-insight part", "N400_p"]`, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_joint$conts["Post-insight part", "P1_p"]`.
-
-(ref:fig3_caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip
-\\bigskip\\small\\textit{Note.}
-The violins and box plots show the distributions of the by-participant averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modeling (see main text and Table \\ref{tab:joint-table}), together with their respective 95\\% confidence interval.
-Ampl.
-= amplitude, 95\\% CI = 95\\% confidence interval, LMM = linear mixed-effects model.\\newline\*\\textit{p} \\textless{} .05.
-\*\*\\textit{p} \\textless{} .01.
-\*\*\*\\textit{p} \\textless{} .001.
-
-```{r joint-plot, include=TRUE, fig.height=8, fig.cap = "(ref:fig3_caption)"}
-# Create violin plot for Experiments 1 and 2 combined
-plot_grid(
-  plot_headings(spacing = c(10, 2, 10, 2, 10)),
-  plot_violins(data = data_joint_subs, models = models_joint),
-  nrow = 2, rel_heights = c(0.3, 6.7)
-) %>% plot_grid(
-  plot_legends_violins(),
-  nrow = 1, rel_widths = c(8.5, 1.5)
-) + # Add some lines (to separate the parts)
-  annotate(
-    "segment",
-    x = 11 / 34 * 0.85, xend = 11 / 34 * 0.85,
-    y = -Inf, yend = Inf
-  ) +
-  annotate(
-    "segment",
-    x = 23 / 34 * 0.85, xend = 23 / 34 * 0.85,
-    y = -Inf, yend = Inf
-  )
-```
-
-### Control Analysis
-
-```{r control-models, eval=rerun_models}
-# This time, we keep only the two conditions with matching keywords
-data_joint %>%
-  filter(condition %in% c("Informed", "Excl_informed")) %>%
-  droplevels() -> data_joint_control
-
-# Contrast coding for condition (informed-no_informed) and part (2-1, 3-1)
-contrasts(data_joint_control$condition) <- ginv(contrasts_condition)
-contrasts(data_joint_control$part) <- ginv(contrasts_part)
-
-# Apply the function to re-compute the joint models
-map(
-  comps$name,
-  compute_models,
-  formula = form_joint,
-  data = data_joint_control,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("data/processed/joint-control-models.RDS") -> models_joint_control
-```
-
-```{r control-table}
-# Calculate average number of objects per condition in Experiments 1 and 2
-(stims_joint <- (obj_per_cond + objects_exp2) / 2)
-
-# Load linear mixed models
-models_joint_control <- readRDS("data/processed/joint-control-models.RDS")
-
-# Create a table but don't print
-table_joint_control <- create_table(
-  models = models_joint_control,
-  stub_anova = c(
-    "Part", "Condition", "Experiment", "Pt. × con.",
-    "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."
-  ),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption =
-    "Results of Linear Mixed-Effects Regression Models With a Different Baseline",
-  note =
-    "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\\% confidence interval."
+  note = paste(
+    "Pt. = part, con. = condition, est. = estimate, CI = 95\\%",
+    "confidence interval."
+  )
 )
@@
 Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of signaling messages.
+Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:fig1)A cannot be reconciled with the function of signaling messages.
 To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
 Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1]
-Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
+Across both experiments, this was the case for `r percent(obj_per_cond["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r percent(obj_per_cond["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1]
+Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r tab2$conts["Insight part", "N170_est"]` µV, *p* `r tab2$conts["Insight part", "N170_p"]`.
 Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
-Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, *b* = `r table_joint_control$conts["Insight part", "N400_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N400_p"]`.
+Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, *b* = `r tab2$conts["Insight part", "N400_est"]` µV, *p* `r tab2$conts["Insight part", "N400_p"]`.
 
@@
 
-## Discussion
-
-Experiment 2, which was an exact replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400).
-Objects for which participants experienced semantically informed perception via matching keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes.
-Note, however, that the effect in the N170 component marginally failed to reach the conventional level for statistical significance in this replication experiment.
-When the objects were presented once more without any semantic information, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.
-
-```{r exp3-preproc, eval=run_exp3}
-# Read behavioral data for Experiment 1
-list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp3
-
-# Update stimulus triggers
-preproc_params$event_id <- dict(
-  "match/upright" = as.integer(241),
-  "match/inverted" = as.integer(242),
-  "mismatch/upright" = as.integer(243),
-  "mismatch/inverted" = as.integer(244)
-)
-
-# Preprocess the EEG for Experiment 3 in Python
-fnames_exp3 <- list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE)
-py_run_string(
-  "epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **r.preproc_params)
-                  for fname, meta in zip(r.fnames_exp3, r.behav_exp3)]"
-)
-message("This worked!!!")
-py_run_string("epochs_exp3 = mne.epochs.concatenate_epochs(epochs_exp3)")
-message("This also worked!!!")
-py_run_string("epochs_exp3.save('export/exp3-epo.fif', overwrite=True)")
-py_run_string("del epochs_exp3")
-
-# Preprocess the EEG for Experiment 3 in Python
-map2(
-  .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp3,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp3
-
-# Backup epochs to the export folder
-epochs_exp3$save("data/processed/exp3-epo.fif")
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
-  set_names(comps$name) %>%
-  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
-  write_tsv("data/processed/exp3-data.tsv") -> data_exp3
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("data/processed/exp3-gaverages.RDS")
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp3, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
-  write_tsv("data/processed/exp3-objects.tsv")
-
-# Remove the epochs to free up memory
-rm(epochs_exp3)
-```
-
-```{r exp3-models, eval=run_exp3}
-# Load preprocessed single-trial data
-read_tsv("data/processed/exp3-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    position = factor(position, levels = c("Inverted", "Upright")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
-    )),
-    participant = factor(participant),
-    item = factor(item)
-  ) %>%
-  # Remove any trials excluded from conditions and parts
-  filter(condition %in% c("Informed", "Naive") & part != "IV") %>%
-  droplevels() -> data_exp3
-
-# Define contrasts for position (inverted-upright), condition (informed-naive), and part (2-1, 3-1)
-t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
-contrasts(data_exp3$position) <- ginv(contrasts_position)
-contrasts(data_exp3$condition) <- ginv(contrasts_condition)
-contrasts(data_exp3$part) <- ginv(contrasts_part)
-
-# Define new formula for LMMs
-formula_exp3 <- buildmer::tabulate.formula(
-  ~ part * condition * position +
-    (part * condition * position | participant) +
-    (part * condition * position | item)
-) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-
-# Define new follow-up contrasts
-specs_exp3 <- pairwise ~ condition | position * part
-
-# Compute the models for Experiment 3
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp3,
-  data = data_exp3,
-  control = control,
-  specs = specs_exp3
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("data/processed/exp3-models.RDS") -> models_exp3
-```
-
-```{r exp3-table, include=TRUE, results="asis", eval=run_exp3}
-# Create table of models for Experiment 3
-table_exp3 <- create_table(
-  models_exp3,
-  stub_anova = c(
-    "Part", "Condition", "Position", "Pt. × con.",
-    "Pt. × pos.", "Ins. × pos.", "Pt. × con. × pos."
-  ),
-  stub_contrasts = c(
-    "Part I, inverted", "Part I, upright", "Part II, inverted",
-    "Part II, upright", "Part III, inverted", "Part III, upright"
-  ),
-  caption = "Results of linear mixed-effects regression models for Experiment 3",
-  note = "Pt. = part, con. = condition, pos. = position, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-# General Discussion
+# Discussion
 
@@
 Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances [see, e.g., the simulations by @matuschek2017].
-This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r table_exp1$conts["Insight part", "N170_p"]`) failed to reach statistical significance in the replication experiment (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
+This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r tab1$conts["Insight part", "N170_p"]`) failed to reach statistical significance in the replication experiment (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
 To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).

### 2021-07-25 code/preprocessing.py
Fix evokeds function

@@ -251,15 +251,17 @@ def _evokeds_df_from_epochs(epochs, average_by):
         query = condition["query"].to_list()
         query = " & ".join(query)
 
-        # Average epochs belonging to this condition
+        # Average epochs belonging to this condition and convert to DataFrame
         if isinstance(epochs, Epochs):
             evokeds = epochs[query].average(picks=["eeg", "misc"])
+            scalings = {"eeg": 1e6, "misc": 1e6}
+            evokeds_df = evokeds.to_data_frame(scalings=scalings)
         elif isinstance(epochs, EpochsTFR):
             evokeds = epochs[query].average()
+            evokeds_df = evokeds.to_data_frame()
         evokeds.comment = query
 
-        # Convert to DataFrame, adding condition info
-        evokeds_df = evokeds.to_data_frame(scalings={"eeg": 1e6, "misc": 1e6})
+        # Add info about the current conditions
         condition_df = pd.concat([condition[["value"]].transpose()] * len(evokeds_df))
         condition_df.reset_index(inplace=True, drop=True)
         evokeds_df = pd.concat([condition_df, evokeds_df], axis=1)

### 2021-07-25 code/manuscript.Rmd
Fix tab1 reference

@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r fig1$anov["Part", "P1_f"]`, all *p*s `r fig1$anov["Part", "P1_p"]` (see Table \@ref(tab:tab1)).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r fig1$anov["Condition", "N400_df"]` = `r fig1$anov["Condition", "N400_f"]`, *p* = `r fig1$anov["Condition", "N400_p"]`.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r tab1$anov["Part", "P1_f"]`, all *p*s `r tab1$anov["Part", "P1_p"]` (see Table \@ref(tab:tab1)).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r tab1$anov["Condition", "N400_df"]` = `r tab1$anov["Condition", "N400_f"]`, *p* = `r tab1$anov["Condition", "N400_p"]`.
 Crucially, the part × condition interaction was significant in the N170 component, *F*`r tab1$anov["Pt.

### 2021-08-01 code/manuscript.Rmd
Fix rendering issues

@@
 draft             : no
-bibliography      : "misc/bibliography.bib"
-csl               : "misc/apa.csl"
+bibliography      : "../misc/bibliography.bib"
+csl               : "../misc/apa.csl"
 zotero            : "aha"
@@
 classoption       : "man"
-output            :
+fontsize          : "10pt"
+output:
   papaja::apa6_pdf:
-    latex_engine  : "xelatex"
+    latex_engine: "xelatex"
 editor_options: 
-  chunk_output_type: console
+  chunk_output_type: "console"
 header-includes:
@@
 
-# Set some global chunk options
+# Set global chunk options
 knitr::opts_chunk$set(
-  include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10
+  dev = "cairo_pdf",
+  fig.align = "center",
+  fig.width = 10,
+  include = FALSE,
+  messages = FALSE,
+  out.width = "100%",
+  warnings = FALSE
 )
@@
 
-```{r, fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
+```{r, fig1, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
 # Load montage and evoked data
@@
 
-(ref:fig1_caption) Procedure and Results of Experiment 1\smallskip
+(ref:figure-1-caption) Procedure and Results of Experiment 1\smallskip
 
@@
 
-```{r models_control, eval=rerun_model_fitting}
+```{r models_control}
 # Use a different control condition ("failed insight")
@@
 Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r percent(obj_per_cond["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r percent(obj_per_cond["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1]
+Across both experiments, this was the case for `r percent(obj_per_cond[["Excl_informed"]] / 60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r percent(obj_per_cond[["Informed"]] / 60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1]
 Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r tab2$conts["Insight part", "N170_est"]` µV, *p* `r tab2$conts["Insight part", "N170_p"]`.
@@
 Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances [see, e.g., the simulations by @matuschek2017].
-This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r tab1$conts["Insight part", "N170_p"]`) failed to reach statistical significance in the replication experiment (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
+This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r tab1$conts["Insight part", "N170_p"]`) failed to reach statistical significance in the replication experiment (*p* = `r tab2$conts["Insight part", "N170_p"]`).
 To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).
-It should be noted, however, that the joint analysis of both data sets yielded a very robust N170 effect (*p* = `r table_joint$conts["Insight part", "N170_p"]`).
+It should be noted, however, that the joint analysis of both data sets yielded a very robust N170 effect (*p* = `r tab1$conts["Insight part", "N170_p"]`).
 This makes it less likely that the effect observed in Experiment 1 was due to a false positive and instead suggests that statistical power in Experiment 2 was insufficient to render the effect significant.

### 2021-08-05 code/manuscript.Rmd
Shorten results

@@
 Of these, 120 were well-known everyday objects (e.g., a bicycle, a toothbrush) and served as filler stimuli of no interest.
-The other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Appendix A for a full list).
+The other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Appendix A).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
   file = fnames$model_brm_prior,
-  file_refit = "on_change"
+  file_refit = "never"
 )
@@
 summary(fit_brm_prior)
-# mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95)
+mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95)
 
@@
     file = fnames$models_brm[[dv]],
-    file_refit = "on_change"
+    file_refit = "never"
   )
@@
 example_model$hypotheses
-# mcmc_plot(example_model$model, "areas", pars = "^b_", prob_outer = 0.95) +
-#   theme(text = element_text(family = "Helvetica", size = 10))
-
-# # Posterior predictive checks subject by subject
-# pp_check(
-#   example_model$model,
-#   type = "dens_overlay_grouped",
-#   nsamples = 50,
-#   group = "subject_id"
-# )
-# pp_check(
-#   example_model$model,
-#   type = "stat_grouped",
-#   nsamples = 1000,
-#   group = "subject_id",
-#   stat = "sd"
-# )
+mcmc_plot(example_model$model, "areas", pars = "^b_", prob_outer = 0.95) +
+  theme(text = element_text(family = "Helvetica", size = 10))
+
+# Posterior predictive checks subject by subject
+pp_check(
+  example_model$model,
+  type = "dens_overlay_grouped",
+  nsamples = 50,
+  group = "subject_id"
+)
+pp_check(
+  example_model$model,
+  type = "stat_grouped",
+  nsamples = 1000,
+  group = "subject_id",
+  stat = "sd"
+)
 ```
@@
 The first 15 components were extracted with the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the `find_bads_eog` function.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find_bads_eog* function.
 After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
@@
 First, we excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight part (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r format(round(obj_per_cond[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Excl_known"]] / 120, accuracy = 0.1)` of all unfamiliar objects).
+This led to the exclusion of an average of `r format(round(obj_per_cond[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Excl_known"]] / 120, accuracy = 0.1)` of unfamiliar objects).
 Next, to delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participant (see Figure \@ref(fig:fig1)A).
@@
 Compared to traditional by-participant or by-item analyses of variance, these models allow tighter control over the false positive rate because they simultaneously account for by-participant and by-item non-independencies in the data [@bürki2018; @judd2012].
-Furthermore, they flexibly handle unbalanced data which in our case arose from the rejection of ERP epochs as well as the way we constructed our experimental conditions (see above).
+Furthermore, they flexibly handle unbalanced data.
+This was important in our case because of the rejection of bad ERP epochs as well as the way we constructed our experimental conditions (see above).
 
@@
 
-The materials, single trial preprocessed data, and all code for data analysis are openly available at <https://osf.io/uksbc/>.
+The materials, single trial preprocessed data, and code for data analysis are openly available at <https://osf.io/uksbc/>.
 
@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r tab1$anov["Part", "P1_f"]`, all *p*s `r tab1$anov["Part", "P1_p"]` (see Table \@ref(tab:tab1)).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r tab1$anov["Condition", "N400_df"]` = `r tab1$anov["Condition", "N400_f"]`, *p* = `r tab1$anov["Condition", "N400_p"]`.
-Crucially, the part × condition interaction was significant in the N170 component, *F*`r tab1$anov["Pt.
-× con.", "N170_df"]` = `r tab1$anov["Pt.
-× con.", "N170_f"]`, *p* = `r tab1$anov["Pt.
-× con.", "N170_p"]`, and in the N400 component, *F*`r tab1$anov["Pt.
-× con.", "N400_df"]` = `r tab1$anov["Pt.
-× con.", "N400_f"]`, *p* `r tab1$anov["Pt.
-× con.", "N400_p"]` but not in the P1 component, *F*`r tab1$anov["Pt.
-× con.", "P1_df"]` = `r tab1$anov["Pt.
-× con.", "P1_f"]`, *p* = `r tab1$anov["Pt.
-× con.", "P1_p"]`.
-To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment (see Table \@ref(tab:tab1)).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment.
+Crucially, the part × condition interaction was significant for all three components.
+To answer our main research question, we decomposed these interactions into the simple effects of the semantically informed condition versus the naive condition within each of the three different parts of the experiment.
 
@@
 
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s ≥ `r tab1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:tab1) and Figure \@ref(fig:fig1)B).
-On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
-On the other hand, the absence of reliable differences in this part can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in the other two parts cannot be accounted for by visual differences between the objects in the two conditions.
-Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self-report would have made it possible for such visual differences to emerge as a confounding factor.
-If they did, however, one would expect to detect these differences even before any keywords were presented, which was apparently not the case.
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component (see Table \@ref(tab:tab1) and Figure \@ref(fig:fig1)B).
+This was expected because given that (a) the critical presentation of the keywords (leading either to semantically informed perception or to naive perception) had not yet taken place and (b) the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences between conditions.
 
@@
 In the insight part, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perceptio nof the objects semantically naive.
-During semantically informed perception, the amplitude of the N170 component was significantly enlarged (i.e., more negative), *b* = `r tab1$conts["Insight part", "N170_est"]` µV, *p* = `r tab1$conts["Insight part", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e., less negative), *b* = `r tab1$conts["Insight part", "N400_est"]` µV, *p* `r tab1$conts["Insight part", "N400_p"]`, compared to naive perception.
-As in the pre-insight part, there were no reliable differences in the P1 component, *b* = `r tab1$conts["Insight part", "P1_est"]` µV, *p* = `r tab1$conts["Insight part", "P1_p"]`.
+During semantically informed perception, the amplitude of the N170 component was significantly enlarged (i.e., more negative) and the amplitude of the N400 component was significantly reduced (i.e., less negative).
+There were no reliable differences in the P1 component.
 
@@
 In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part).
-As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r tab1$conts["Post-insight part", "N400_est"]` µV, *p* `r tab1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *b* = `r tab1$conts["Post-insight part", "N170_est"]` µV, *p* = `r tab1$conts["Post-insight part", "N170_p"]`.
-Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, *b* = `r tab1$conts["Post-insight part", "P1_est"]` µV, *p* = `r tab1$conts["Post-insight part", "P1_p"]`.
+As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, whereas the effect in the N170 component did not reoccur.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place.
 
@@
 
-One may raise concerns whether the modulation of the N170 component in the insight part genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it may be driven by the objects in the other, semantically naive condition.
-Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:fig1)A cannot be reconciled with the function of signaling messages.
-To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r percent(obj_per_cond[["Excl_informed"]] / 60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r percent(obj_per_cond[["Informed"]] / 60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1]
-Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r tab2$conts["Insight part", "N170_est"]` µV, *p* `r tab2$conts["Insight part", "N170_p"]`.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
-Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, *b* = `r tab2$conts["Insight part", "N400_est"]` µV, *p* `r tab2$conts["Insight part", "N400_p"]`.
-
-[^1]: Note that these percentages do not add up to 100% because some objects were excluded from all analyses if participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).
+In the main analysis described above, objects in the semantically informed condition (matching keywords) were contrasted against objects in the naive condition (non-matching keywords) as the baseline condition.
+This may raise the question if the N170 and/or N400 effects in the insight part could be due to a mismatch response for objects in the naive condition.
+To rule out this alternative explanation, we repeated the analysis using a different baseline condition, namely those objects that were presented with matching keywords (as in the informed condition) but on which participants failed to capitalize according to their behavioral responses.
+This was the case for `r percent(obj_per_cond[["Excl_informed"]] / 60, accuracy = 0.1)` of objects presented with matching keywords.
+As before, there semantically informed perception led to a reliable increase in the N170 component and a reliable decrease in the N400 component (see Table \@ref(tab:tab2)).
 

### 2021-08-05 code/plots_tables.R
Minor tweaks

@@ -323,7 +323,7 @@ create_table <- function(models, stub_anova, stub_contrasts, caption, note) {
       map(mutate, estt = kableExtra::linebreak(estt, align = "c", linebreaker = "\n")) %>%
       map(add_row, estt = "Est. [CI]; \\textit{t} (\\textit{df})", p = "\\textit{p}", .before = 1) %>%
       bind_cols() %>%
-      set_rownames(c("\\textbf{Informed - naive}", stub_contrasts_indent))
+      set_rownames(c("\\textbf{Follow-up tests}", stub_contrasts_indent))
   )
   suppressMessages(
     conts %<>%

### 2021-08-05 code/rsa.py

@@ -1,0 +1,30 @@
+from mne import read_epochs
+import numpy as np
+import mne_rsa
+import pandas as pd
+
+epochs = read_epochs("../data/preprocessed/sub-01_epo.fif")
+
+epochs_part = epochs["part == 'II'"].pick_types(eeg=True)
+
+# # Sort items
+# item_idxs = np.array(epochs_part.metadata["item_id"])
+# dat_part = dat_part[item_idxs - 1]
+
+
+behav_file = "../data/raw/rt/exp1/VP_01_Tag1.txt"
+behav = pd.read_csv(behav_file, delimiter="\t", usecols=range(14), index_col=False)
+behav_part = behav[behav["Wdh"] == 212]
+
+response = behav_part["Tastencode"]
+
+dsm_model = mne_rsa.compute_dsm(response, metric="sqeuclidean")
+dsm_model.shape
+
+item_ids = epochs_part.metadata["item_id"]
+epochs_part.events[:, 2] = item_ids
+epochs_part.events_id = dict(zip(item_ids, item_ids))
+
+rsa = mne_rsa.rsa_epochs(epochs_part, dsm_model, spatial_radius=None)
+
+rsa.plot()

### 2021-08-05 code/tfr.py

@@ -1,19 +1,8 @@
-from os import makedirs
-
 import numpy as np
 import pandas as pd
 
-# Read evoked *potentials* for all subjects
-subject_id = ["sub-" + "{:02d}".format(sid) for sid in range(1, 49)]
-fname_evo_tfr = ["../data/preprocessed/" + sub + "_ave.csv" for sub in subject_id]
-evo = [pd.read_csv(fname) for fname in fname_evo_tfr]
-evo = pd.concat(evo)
-
-# Average across subjects
-id_vars = ["part", "condition", "time"]
-evo = evo.groupby(id_vars, as_index=False).mean()
-
 # Read evoked *power* for all subjects
+subject_id = ["sub-" + "{:02d}".format(sid) for sid in range(1, 49)]
 fname_evo_tfr = ["../data/preprocessed/" + sub + "_tfr-ave.csv" for sub in subject_id]
 evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
 evo_tfr = pd.concat(evo_tfr)

### 2021-08-09 manuscript/manuscript.Rmd
New manuscript folder

--- 2020-09-02 manuscript/manuscript.Rmd
@@
 ---
-title             : "The title"
-shorttitle        : "Title"
-
+title             : "Instant effects of semantic information on visual perception"
+shorttitle        : "Semantically informed perception"
 author: 
-  - name          : "First Author"
+  - name          : "Alexander Enge"
+    affiliation   : "1,2"
+    corresponding : yes
+    address       : "Rudower Chaussee 18, 12489 Berlin, Germany"
+    email         : "alexander.enge@hu-berlin.de"
+  - name          : "Franziska Süß"
+    affiliation   : "3"
+  - name          : "Rasha Abdel Rahman"
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
-    role:
-      - Writing - Review & Editing
-
 affiliation:
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Humboldt-Universität zu Berlin"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "Max Planck Institute for Human Cognitive and Brain Sciences"
+  - id            : "3"
+    institution   : "Fachhochschule des Mittelstands"
+authornote: |
+  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
 
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+  \addORCIDlink{Rasha Abdel Rahman}{0000-0002-8438-1570}
 
-  Enter author note here.
-
+  The authors declare no competing financial interests.
+  The preprocessed data and analaysis code for this study are openly available at https://osf.io/uksbc/.
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["r-references.bib"]
-
+  Does our perception of an object change as soon as we discover what function it serves?
+  This question matters not only when we encounter novel tools or gadgets in our everyday lives, but also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+  Here, we showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
+  We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
+  We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms) and reduced amplitudes in the N400 component (400--700 ms).
+  When the same objects were presented once more without any information, the N400 effect persisted and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
+  Consistent with previous work, our results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
+  We demonstrate for the first time that these effects are instantaneous in the sense that they can be observed within the same trial as well as one trial after the information has been given, providing strong evidence that cognition affects perception.
+keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
 floatsintext      : yes
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
 draft             : no
-
+bibliography      : ["references.bib", "r-references.bib"]
 csl               : "apa.csl"
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+fontsize          : "10pt"
+output:
+  papaja::apa6_pdf:
+    latex_engine: xelatex
+  papaja::apa6_docx: default
+editor_options: 
+  chunk_output_type: console
+header-includes:
+  - \geometry{a4paper}
+  - \fancyheadoffset[R,L]{0pt}
+  - \raggedbottom
+  - \usepackage[all]{nowidow}
+  - \usepackage[bottom]{footmisc}
+  - \interfootnotelinepenalty=10000
+  - \usepackage{setspace}
+  - \AtBeginEnvironment{tabular}{\doublespacing}
+  - \usepackage{makecell}
+  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
+  - \captionsetup{font={stretch=1}, belowskip=15pt}
 ---
 
-```{r setup, include=FALSE}
+```{r, setup, include=FALSE}
 # Load packages
-library(papaja)
-library(reticulate)
-library(MASS)
-library(Matrix)
+library(buildmer)
+library(cowplot)
+library(emmeans)
+library(here)
+library(knitr)
 library(lme4)
 library(lmerTest)
-library(buildmer)
-library(emmeans)
+library(magick)
+library(MASS)
+library(papaja)
+library(parallel)
+library(reticulate)
+library(scales)
+library(tidyverse)
 library(magrittr)
-library(tidyverse)
-library(cowplot)
 
-# Chunk options
-knitr::opts_chunk$set(include = FALSE, echo = FALSE, fig.out = "100%", fig.width = 10)
+# Load helper functions
+source(here("manuscript", "plots_tables.R"))
 
-# Conda environment for Python
-#use_condaenv("r-reticulate", required = TRUE)
-renv::use_python(python = "/Users/alexander/opt/anaconda3/bin/python", type = "conda")
+# Write R package citations
+r_refs(here("manuscript", "r-references.bib"), append = FALSE)
 
-# Bibliography file
-r_refs("manuscript/r-references.bib")
+# Set global chunk options
+opts_chunk$set(
+  fig.align = "center",
+  fig.width = 10,
+  include = FALSE,
+  out.width = "100%"
+)
+
+# Re-run preprocessing and/or model fitting?
+run <- list(preprocessing = FALSE, model_fitting = FALSE)
+
+# Number of CPU cores for parallel model fitting
+n_cores <- detectCores()
+
+# File names for easier I/O
+deps <- c("logRT", "P1", "N170", "N400")
+fnames <- list(
+  montage = "results/montage.csv",
+  obj_per_cond = "results/obj-per-cond.csv",
+  trials = "results/trials.csv",
+  ave_grand = "results/ave_grand.csv",
+  ave_tfr_flat = "results/ave-tfr_flat.csv",
+  ave_tfr_diff = "results/ave-tfr_diff.csv",
+  models_lme = "results/models_lme.RDS",
+  models_brm = str_c("results/model_brm_", deps, ".RDS") %>% set_names(deps),
+  model_brm_prior = "results/model_brm_prior.RDS",
+  models_control = "results/models_control.RDS"
+)
 ```
 
-```{r exp1-behavior}
-# Function for processing behavioral data
-preproc_behav <- function(txt_fname){
-  # Read log file
-  dat <- suppressMessages(suppressWarnings(read_tsv(txt_fname)))
-  # Rename some columns
-  dat %<>% rename(participant = VPNummer, item = StimID) %>%
-    # Add a column for the part of the experiment
-    mutate(part = as_factor(Wdh - min(Wdh) + 1)) %>%
-    # Remove filler stimuli (i.e. well-known objects)
-    filter(bek_unbek != "bekannt")
-  # Assign stimuli to conditions based on keywords and button presses
-  known <- dat %>% filter(part == "1" & Tastencode %in% c(201, 251)) %>% pull(item)
-  insight <- dat %>% filter(part == "2" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
-  naive <- dat %>% filter(part == "2" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
-  # Create a new condition column, excluding trials with knwon stimuli or without condition
-  dat %<>% mutate(condition = as_factor(case_when(item %in% known ~ "Excl_known",
-                                                  item %in% insight ~ "Insight",
-                                                  item %in% naive ~ "Naive",
-                                                  TRUE ~ "Excl_cond")))
-  # In Experiment 3, we need an additional column for position (upright vs. inverted)
-  if("richtig_inv" %in% dat$Bed){
-    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
-      # Return only relevant columns
-      select(part, position, condition, participant, item, RT)
-  } else {
-    dat %<>% select(part, condition, participant, item, RT)}
-  return(dat)}
+# Introduction
 
-# List of filenames for behavioral data
-fnames_exp1 <- list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE)
+Does our perception of an object change as soon as we discover what function it serves?
+This question speaks not only to our everyday experiences, where we encounter novel tools and gadgets in our dynamic working and private environments.
+It also pertains to the long-standing debate about the cognitive (im)penetrability [@pylyshyn1999] of perception by higher-level capacities such as semantic knowledge or language.
+According to one view, these cognitive capacities kick in only after the retinal input has been processed by a specialized module for visual perception [@firestone2016; @fodor1983].
+This module is encapsulated from higher-level inputs and therefore processes the visual information in a purely feedforward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
+This architecture has been mirrored in classical [e.g., @marr1982] and contemporary [e.g., @krizhevsky2012] computer vision models, allowing them to achieve human-level perfomance in predicting object category labels from images [for review, see @lindsay2020].
 
-# Apply the preprocessing function
-data_exp1 <- map(fnames_exp1, preproc_behav)
+The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different aspects of cognition from early on [@churchland1994; @lupyan2015].
+This view is supported by a variety of theoretical, behavioral, and neurophysiological accounts.
 
-# Tabulate percentage of stimuli per condition
-(stims_exp1 <- bind_rows(data_exp1) %>% filter(condition != "Excl_cond") %>% 
-    group_by(participant, condition) %>% tally() %>%
-    group_by(condition) %>% summarise(mean = mean(n)/(60*3)) %>% # 60 items per condition
-    mutate(mean = if_else(condition == "Excl_known", mean/2, mean))) # 120 items in total
+On the theoretical level, the reverse hierarchy theory [@ahissar2004; @hochstein2002] posits that conscious processing initally occurs at the level of whole objects or object categories.
+Only after this high-level interpretation has been obtained, more fine grained visual details---if relevant for the current task---are being accessed via top-down connections.
+Along similar lines, Bayesian inference and predictive coding theories [e.g., @clark2013; @panichello2013; @yuille2006] propose bi-directional loops of predictions and prediction errors between visual and non-visual processes.
+
+On the behavioral level, these ideas are supported by psychological studies that showed differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] background.
+However, some of these studies confounded tentantive high-level effects with low-level differences between conditions.
+Furthermore, many studies were not able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
+
+On the neurophysiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
+Their excellent temporal resolution allows us to probe how early we can detect influences of high-level (e.g., semantic) information.
+To this end, participants were typically trained to associate visual objects with different amounts of semantic information.
+After training, an orthogonal task was used to compare the ERPs in response to semantically trained objects versus non-semantically trained objects.
+This revealed differences not only in late ERP components associated with semantic processing (i.e., the N400 component) but also in the visual P1 component [@abdelrahman2008; @maier2019; @samaha2018; @weller2019].
+The early peak of this component and its source in the occipital cortex [@abdelrahman2008] point to an immediate effect of semantic knowledge on visual perception.
+
+Here we measured ERPs in response to unfamiliar objects instantly while participants gained an semantic understanding of their function.
+To this end, we presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viweing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
+We then presented the same objects again to test for downstream effects of semantic information as in previous studies.
+We examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
+
+# Materials and Methods
+
+## Participants
+
+Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18--32) and no history of psychological disorder or treatment.
+No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
+All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
+They provided written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+
+## Materials
+
+Stimuli consisted of 240 grayscale photographs of real-world objects.
+Of these, 120 were well-known everyday objects (e.g., a bicycle, a toothbrush) and served as filler stimuli of no interest.
+The other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Appendix A).
+All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
+At a standardized viewing distance of 90 cm, the images subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
+
+For each unfamiliar object, a pair of German keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
+As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
+The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically naive.
+All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
+This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
+The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
+
+## Experimental Design
+
+The experiment consisted of three parts (see Figure \@ref(fig:fig1)A).
+In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
+Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
+The inter-trial interval was 0.5 s and participants took a self-timed break after each block of 60 objects.
+The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
+
+```{r, preprocessing}
+# List EEG files and behavioral log files
+fname_vhdr <- c(
+  list.files("data/raw/eeg/exp1", pattern = ".vhdr", full.names = TRUE),
+  list.files("data/raw/eeg/exp2", pattern = ".vhdr", full.names = TRUE)
+)
+fname_log <- c(
+  list.files("data/raw/rt/exp1", pattern = ".txt", full.names = TRUE),
+  list.files("data/raw/rt/exp2", pattern = ".txt", full.names = TRUE)
+)
+
+# Generate new BIDS-style subject IDs
+seq(length(fname_vhdr)) %>%
+  str_pad(width = 2, pad = 0) %>%
+  str_c("sub-", .) -> subject_id
+
+# Define ERP components of interest
+erp_components <- tibble(
+  name = c("P1", "N170", "N400"),
+  tmin = c(0.1, 0.15, 0.4),
+  tmax = c(0.15, 0.2, 0.7),
+  roi = list(
+    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
+    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
+    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
+  )
+)
+
+# Define frequencies and number of cycles for TFR analysis
+tfr_freqs <- seq(4, 50, by = 2)
+tfr_cycles <- seq(3, 10, length.out = length(tfr_freqs))
+
+# Run preprocessing for all subjects using MNE-Python (see preprocessing.py)
+# Will run only if `run$preprocessing = TRUE` and if raw data are available
+if (run$preprocessing) {
+
+  # Import the custom Python functions for preprocessing
+  pp <- import_from_path("preprocessing", path = "code")
+
+  # Do the actual preprocessing
+  tibble(fname_vhdr, fname_log, subject_id) %>%
+    pwalk(
+      pp$preprocess,
+      output_dir = "data/preprocessed",
+      eog_names = c("HEOG", "VEOG"),
+      eog_anodes = c("F9", "Auge_u"),
+      eog_cathodes = c("F10", "Fp1"),
+      montage_kind = "easycap-M1",
+      ica_components = as.integer(15),
+      ica_method = "fastica",
+      ica_seed = as.integer(1234),
+      hipass = 0.1,
+      lowpass = 30,
+      event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
+      tmin = -0.5,
+      tmax = 1.489,
+      baseline = tuple(-0.2, 0),
+      reject = dict(eeg = 200e-6),
+      erp_components = erp_components,
+      average_by = c("part", "condition", "subject_id"),
+      tfr_baseline = tuple(-0.3, -0.1),
+      tfr_equalize = "condition == ['Informed', 'Naive']",
+      tfr_resample = py_none(),
+      tfr_freqs = tfr_freqs,
+      tfr_cycles = tfr_cycles,
+      tfr_crop = tuple(-0.2, 0.8)
+    )
+
+  # Combine single trial data for all subjects
+  dir.create("results")
+  str_c("data/preprocessed/", subject_id, "_trials.csv") %>%
+    map(read_csv, col_types = cols()) %>%
+    bind_rows() %>%
+    write_csv(fnames$trials)
+
+  # Get standard EasyCap electrode positions and project them into 2D space
+  read_csv("data/preprocessed/sub-01_tfr-ave.csv", col_types = cols()) %>%
+    select(-c(part, condition, subject_id, time, freq)) %>%
+    colnames() -> ch_names
+  import("mne.channels._standard_montage_utils")$MONTAGE_PATH %>%
+    str_c("/easycap-M1.txt") %>%
+    read_tsv(col_types = cols()) %>%
+    rename(electrode = Site) %>%
+    inner_join(tibble(electrode = ch_names), ., by = "electrode") %>%
+    mutate(
+      x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
+      y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
+    ) %>%
+    mutate(across(c(x, y), round, 3)) %>%
+    write_csv(fnames$montage)
+
+  # Determine number of objects per condition for each participant
+  fname_log %>%
+    map2(subject_id, pp$read_log) %>%
+    bind_rows() %>%
+    with(table(subject_id, condition) / 3) %>%
+    as.data.frame.matrix() %>%
+    rownames_to_column("subject_id") %>%
+    write_csv(fnames$obj_per_cond)
+}
 ```
 
-```{python exp1-preprocessing}
-# Import libraries
-import mne
-import glob
-import os
+```{python, grand_averaging, eval=run$preprocessing}
+import numpy as np
+import pandas as pd
 
-# Define parameters for EEG preprocessing
-preproc_params = dict(n_components=15, method='fastica',           # ICA parameters
-                      l_freq=0.1, h_freq=30,                       # Filter edges
-                      event_id={'match': 221, 'mismatch': 222},    # EEG triggers
-                      tmin=-0.5, tmax=1.498,                       # Length of epochs
-                      baseline=(-0.2,0),                           # Baseline correction
-                      reject=dict(eeg=200e-6))                     # Rejection threshold
+# Read evoked *potentials* for all subjects
+subs = r.subject_id
+fnames_ave = [f"data/preprocessed/{sub}_ave.csv" for sub in subs]
+ave = [pd.read_csv(fname) for fname in fnames_ave]
+ave = pd.concat(ave)
 
-# # Debug
-# locals().update(preproc_params)
-# vhdr_fname = 'data/exp1/EEG/Vp0001.vhdr'
-# metadata = metadata_exp1[0]
+# Average across subjects
+id_vars = ["part", "condition", "time"]
+ave = ave.groupby(id_vars, as_index=False).mean()
+ave.to_csv(r.fnames["ave_grand"], float_format="%.3f", index=False)
 
-# Define preprocessing function
-def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax, baseline, reject):
-  # Load EEG data
-  raw = mne.io.read_raw_brainvision(vhdr_fname, preload=True)
-  # Create new virtual EOG channels
-  raw = mne.set_bipolar_reference(raw, 'Auge_u', 'Fp1', ch_name='VEOG', drop_refs=False)
-  raw = mne.set_bipolar_reference(raw, 'F9', 'F10', ch_name='HEOG', drop_refs=False)
-  raw.set_channel_types(mapping={'VEOG': 'eog', 'HEOG': 'eog'})
-  # Add EasyCap electrode layout, removing any excessive channels
-  montage = mne.channels.make_standard_montage('easycap-M1')
-  raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(['VEOG', 'HEOG'])))
-  raw.set_montage(montage=montage)
-  # Re-reference to common average
-  raw, _ = mne.set_eeg_reference(raw, 'average')
-  # Run ICA on a copy of the data
-  filt_raw = raw.copy()
-  filt_raw.load_data().filter(l_freq=1, h_freq=None)
-  ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
-  ica.fit(filt_raw)
-  # Remove bad components based on correlations with EOG
-  eog_indices, eog_scores = ica.find_bads_eog(raw)
-  ica.exclude = eog_indices
-  raw = ica.apply(raw)
-  # Apply band-pass filter
-  raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
-  # Epoching including baseline correction
-  events, _ = mne.events_from_annotations(raw, verbose=False)
-  epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True)
-  # Add behavioral data
-  epochs.metadata = metadata
-  # Reject bad epochs
-  epochs = epochs.drop_bad(reject=reject)
+# Read evoked *power* for all subjects
+fnames_ave_tfr = [f"data/preprocessed/{sub}_tfr-ave.csv" for sub in subs]
+ave_tfr = [pd.read_csv(fname) for fname in fnames_ave_tfr]
+ave_tfr = pd.concat(ave_tfr)
 
-  # # Autoreject                    
-  # import autoreject
-  # 
-  # ar = autoreject.AutoReject(thresh_method='random_search', verbose=False)
-  # epochs = ar.fit_transform(epochs)
-  # 
-  # ransac = autoreject.Ransac(verbose=False)
-  # epochs = ransac.fit_transform(epochs)
-  # 
-  # reject = autoreject.get_rejection_threshold(epochs)
-  # epochs = epochs.drop_bad(reject=reject)
+# # Subject 18 is weird!
+# ave_tfr = ave_tfr[ave_tfr["subject_id"] != "sub-18"]
 
-  return epochs
+# Compute difference in power between conditions
+id_vars = ["part", "condition", "subject_id", "time", "freq"]
+electrodes = [col for col in ave_tfr.columns if (col not in id_vars)]
+ave_tfr_diff = (
+    ave_tfr.query("condition == 'Informed'")[electrodes]
+    - ave_tfr.query("condition == 'Naive'")[electrodes].values
+)
+ave_tfr_diff[id_vars] = ave_tfr.query("condition == 'Informed'")[id_vars]
 
-# List of raw EEG filenames
-fnames_exp1 = sorted(glob.glob('data/exp1/EEG/*.vhdr'))
+# Compute flat average across conditions
+id_vars.remove("condition")
+ave_tfr_flat = ave_tfr.groupby(id_vars, as_index=False).mean()
 
-# Import behavioral data from R
-metadata_exp1 = r.data_exp1
-
-# Check if preprocessing was done already (delete the file to re-run)
-if os.path.exists('output/exp1-epo.fif'):
-  # Load preprocessed data from file
-  epochs_exp1 = mne.read_epochs('output/exp1-epo.fif', preload=True)
-else:
-  # Apply the preprocessing function
-  epochs_exp1 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp1, metadata_exp1)]
-  # Combine epochs into a single data set
-  epochs_exp1 = mne.concatenate_epochs(epochs_exp1)
-  # Backup epochs to the output folder
-  epochs_exp1.save('output/exp1-epo.fif')
-
-# # Get indices of bad epochs despite ICA
-# rej_exp1 = epochs_exp1.drop_log
-# rej_exp1[:] = [item for item in rej_exp1 if item != ['IGNORED']]
-# rej_exp1 = [i for i in range(len(rej_exp1)) if rej_exp1[i] != []]
-
-# Define function to compute grand-averaged ERPs per condition
-def compute_evokeds(epochs):
-  evokeds = dict()
-  evokeds_dat = dict()
-  # Each part becomes a dictionary of conditions
-  for pt in ['1', '2', '3']:
-    evokeds['Pt' + pt] = dict()
-    evokeds_dat['Pt' + pt] = dict()
-    # Each condition becomes a list of participants
-    for cn in ['Insight', 'Naive']:
-      evokeds['Pt' + pt][cn] = list()
-      evokeds_dat['Pt' + pt][cn] = list()
-      # For every participant we average trials separately for all parts and conditions
-      for vp in epochs.metadata['participant'].unique():
-        query = 'participant == "' + vp + '" and part == "' + pt + '" and condition == "' + cn + '"'
-        evokeds['Pt' + pt][cn].append(epochs[query].average())
-      # Compute grand averages across participants for this part and condition
-      evokeds['Pt' + pt][cn] = mne.grand_average(evokeds['Pt' + pt][cn])
-      # Export only the actual data for R
-      evokeds_dat['Pt' + pt][cn] = evokeds['Pt' + pt][cn].data
-  return(evokeds, evokeds_dat)
-
-# Apply the function to compute grand averages
-evokeds_exp1, evokeds_dat_exp1 = compute_evokeds(epochs=epochs_exp1)
-
-# Export electrode positions for R
-elpos = epochs_exp1._get_channel_positions()
-
-# # Plot evoked potentials
-# mne.viz.plot_compare_evokeds(evokeds=evokeds_exp1['Pt1'], picks='P8'); plt.show()
-# mne.viz.plot_evoked_topomap(evoked=evokeds_exp1['Pt2']['Insight']-evokeds_exp1['Pt2']['Naive'])
-# evokeds_exp1['Pt2']['Insight'].data = evokeds_exp1['Pt2']['Insight'].data - evokeds_exp1['Pt2']['Naive'].data
-# evokeds_exp1['Pt2']['Insight'].plot_topomap(times=[0.125, 0.175, 0.5], average=0.05, vmin=-1, vmax=1, cmap='viridis'); plt.show()
+# Average across subjects and save
+id_vars.remove("subject_id")
+dfs = [ave_tfr_flat, ave_tfr_diff]
+fnames_tfr = [r.fnames["ave_tfr_flat"], r.fnames["ave_tfr_diff"]]
+for df, fname in zip(dfs, fnames_tfr):
+    df = df.groupby(id_vars, as_index=False).mean()
+    df.to_csv(fname, float_format="%.3f", index=False)
+del df, dfs, ave, ave_tfr, ave_tfr_diff, ave_tfr_flat
 ```
 
-```{r exp1-analysis}
-# Re-import behavioral data
-data_exp1 <- py$epochs_exp1$metadata
+```{r, models_lme}
+# Compute average number of objects per condition
+(obj_per_cond <- read_csv(fnames$obj_per_cond, col_types = cols()) %>%
+  summarise(across(.cols = -subject_id, .fns = mean)) %>%
+  as.list())
 
-# Factorize some columns
-data_exp1 %<>% mutate(part = factor(part, levels = c("1", "2", "3")),
-                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_known", "Excl_cond")),
-                      participant = factor(participant), item = factor(item))
+# Read single trial data for all subjects
+str_c("data/preprocessed/", subject_id, "_trials.csv") %>%
+  map(read_csv, col_types = cols()) %>%
+  bind_rows() %>%
+  mutate(
+    part = factor(part, levels = c("I", "II", "III")),
+    subject_id = factor(subject_id),
+    item_id = factor(item_id),
+    RT = ifelse(RT < 200, NA, RT),
+    logRT = log(RT)
+  ) -> trials
 
-# Check number of rejected epochs
-rejected_exp1 <- data_exp1 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
-mean(rejected_exp1); median(rejected_exp1); range(rejected_exp1)
+# Record number of rejected ERP epochs per participant
+(rejected <- trials %>%
+  count(subject_id) %>%
+  mutate(n = 360 - n) %>%
+  pull(n))
 
-# Create vectors with sample time points (in ms) and electrodes
-tmin <- py$preproc_params$tmin*1000
-tmax <- py$preproc_params$tmax*1000
-sfreq <- py$epochs_exp1$info['sfreq']
-times <- seq(tmin, tmax, 1000/sfreq)
-els <- py$epochs_exp1$ch_names
+# Remove trials with unrealistically short RTs or invalid conditions
+sum(is.na(trials$RT))
+sum(is.na(trials$RT)) / nrow(trials)
+trials %<>% na.omit()
 
-# Define ERP components of interest
-comps <- tibble(name = c("P1", "N1", "N400"),
-                start = c(100, 150, 400),
-                stop = c(150, 200, 700),
-                roi = list(c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
-                           c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
-                           c("C1", "C2", "Cz", "CP1", "CP2", "CPz")))
+# Contrast coding for parts
+cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)) %>%
+  t() %>%
+  ginv() -> contrasts(trials$part)
 
-# Define function to compute single-trial ERPs
-compute_erps <- function(epochs, els, name, start, stop, roi){
-  erps <- epochs[, which(els %in% roi), which(times %in% start:stop)]
-  erps <- apply(erps, 1, mean, na.rm = TRUE)
-  return(erps)}
+# Remove irrelevant conditions for main analysis
+trials_main <- mutate(
+  trials,
+  condition = factor(condition, levels = c("Informed", "Naive")),
+)
 
-# Check if ERPs were computed already (delete the file to re-run)
-if (file.exists("output/exp1-erps.RDS")){
-  # Load ERPs from file
-  data_exp1 <- readRDS("output/exp1-erps.RDS")
+# Contrast coding for conditions
+c("Informed" = 1, "Naive" = -1) %>%
+  t() %>%
+  ginv() -> contrasts(trials_main$condition)
+
+# Load fitted models or rerun them
+if (!run$model_fitting) {
+
+  # Load models
+  models_lme <- readRDS(fnames$models_lme)
 } else {
-  # Import epochs from Python, converting Volts to Microvolts
-  epochs_exp1 <- py$epochs_exp1$get_data()*1e6
-  # Apply the ERP function and save to output folder
-  data_exp1 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp1, els = els) %>%
-    set_names(comps$name) %>% cbind(data_exp1, .) %T>% saveRDS("output/exp1-erps.RDS")}
 
-# Remove any trials that don't beling to either of the two conditions
-data_exp1 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
+  # Define function for building a single mixed-effect model
+  build_lme <- function(dep, formula, data, n_cores) {
 
-# Sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
-t(contrasts_condition <- t(cbind(c("Insight" = 1, "Naive" = -1))))
-t(contrasts_part <- t(cbind(c("1" = -1, "2" = 1, "3" = 0),
-                            c("1" = 0, "2" = -1, "3" = 1))))
-contrasts(data_exp1$condition) <- ginv(contrasts_condition)
-contrasts(data_exp1$part) <- ginv(contrasts_part)
+    # Convert formula to terms list
+    formula <- tabulate.formula(formula)
 
-# Formula and parameters for linear mixed-effects regression models (LMMs)
-form_exp12 <- tabulate.formula(~ part*condition + (part*condition|participant) + (part*condition|item))
-form_exp12 %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
-ctrl_params <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
+    # Automic model selection via likelihood ratio tests
+    # using an alpha level of .20 (see Matuschek et al., 2017, J Mem Lang)
+    cl <- makeCluster(n_cores)
+    build <- buildmer(
+      buildmerControl = buildmerControl(
+        formula,
+        data,
+        direction = c("backward", "backward"),
+        cl = cl,
+        crit = "LRT",
+        elim = function(logp) exp(logp) >= .20,
+        calc.anova = TRUE,
+        ddf = "Satterthwaite",
+        dep = dep,
+        REML = FALSE,
+      ),
+      control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
+    )
+    stopCluster(cl)
 
-# Formula for follow-up contrasts
-specs_exp12 = pairwise ~ condition|part
+    # Compute follow-up comparisons
+    emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
+    specs <- pairwise ~ condition | part
+    em <- emmeans(build@model, specs, infer = TRUE)
 
-# Define function to compute LMMs and contrasts for each component
-compute_models <- function(dep, formula, data, control, specs){
-  browser()
-  build <- buildmer(dep = dep, formula = formula, data = data, ddf = "Satterthwaite", calc.anova = TRUE, control = control)
-  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts %>% as.data.frame()
-  mod <- list("model" = build@model, "anova" = build@anova, "summary" = build@summary, "contrasts" = conts)
-  return(mod)}
+    # Return a list of relevant model outputs
+    return(
+      list(
+        model = build@model,
+        anova = build@anova,
+        summary = build@summary,
+        means = as.data.frame(em$emmeans),
+        contrasts = as.data.frame(em$contrasts)
+      )
+    )
+  }
 
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("output/exp1-stats.RDS")){
-  # Load models from file
-  models_exp1 <- readRDS("output/exp1-stats.RDS")
-} else {
-  # Apply the modelling function and save to output folder
-  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
-                     specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/exp1-stats.RDS")}
-
-# Store significance levels for plotting
-stars_exp1 = list(P1 = c(Pt1 = NA, Pt2 = NA, Pt3 = "*"),
-                  N1 = c(Pt1 = NA, Pt2 = "**", Pt3 = NA),
-                  N400 = c(Pt1 = NA, Pt2 = "***", Pt3 = "**"))
+  # Compute models for all dependent variables in parallel
+  form <- RT ~ part * condition +
+    (part * condition | subject_id) +
+    (part * condition | item_id)
+  map(
+    deps,
+    build_lme,
+    formula = form,
+    data = trials_main,
+    n_cores = n_cores
+  ) %>%
+    set_names(deps) %T>%
+    saveRDS(fnames$models_lme) -> models_lme
+}
 ```
 
-```{r exp1-table, include=TRUE, results="asis"}
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("output/exp1-stats.RDS")){
-  # Load models from file
-  models_exp1 <- readRDS("output/exp1-stats.RDS")
-} else {
-  # Apply the modelling function and save to output folder
-  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
-                     specs = specs_exp12) %>% set_names(comps$name) %>% saveRDS("output/exp1-stats.RDS")}
+```{r, models_brm, eval=FALSE}
+# Theme for plots
+bayesplot_theme_update(text = element_text(family = "Helvetica", size = 10))
+color_scheme_set("purple")
 
-# Define function to create ANOVA-style table
-create_table <- function(models, stub.anova, stub.contrasts, caption, note){
-  anov <- map(models, function(model){
-    data.frame("stat" = paste0(format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2), " (", model$anova$NumDF,
-                               ", ", format(round(model$anova$DenDF, 1), trim = FALSE, nsmall = 1), ")"),
-               "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)) %>%
-      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p))))}) %>%
-    bind_cols() %>% set_rownames(c(stub.anova))
-  cnames <- c("\\textit{Type III}", rep(c("\\textit{F} (\\textit{df})", "p" = "\\textit{p}"), 3))
-  conts <- map(models, function(model){
-    data.frame("stat" = paste0(format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2), " [",
-                               format(round(model$contrasts$lower.CL, 2), trim = FALSE, nsmall = 2), ", ",
-                               format(round(model$contrasts$upper.CL, 2), trim = FALSE, nsmall = 2), "]"),
-               "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)) %>%
-      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p)))) %>%
-      add_row("stat" = "Est. [95% CI]", "p" = "\\textit{p}", .before = 1)}) %>% 
-    bind_cols() %>% set_rownames(c("\\textit{Insight $-$  naive}", stub.contrasts))
-  apa_table(list(anov, conts), col.names = cnames, escape = FALSE,
-            col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N1}" = 4:5, "\\textbf{N400}" = 6:7),
-            midrules = c(nrow(anov) + 1), font_size = "footnotesize", align = "lcccccc",
-            caption = caption, note = note)}
+# Define example model formula
+formula_brm <- bf(
+  P1 ~ part * condition +
+    (part * condition | subject_id) +
+    (part * condition | item_id),
+  sigma ~ 1 + (1 | subject_id)
+)
 
-# Apply the function to print the table
-create_table(models_exp1, stub.anova = c("Part", "Insight", "Pt. × ins."),
-             stub.contrasts = c("Part 1", "Part 2", "Part 3"),
-             caption = "Results of linear mixed-effects regression models for Experiment 1",
-             note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
+# Default prior for slopes and sigma
+prior <- c(
+  prior(cauchy(0, 0.707), class = b),
+  prior(student_t(3, 0, 5.7), class = Intercept, dpar = sigma),
+  prior(normal(0, 5), class = sd, group = subject_id, dpar = sigma)
+)
+
+# Hypotheses of comparisons for informed vs. naive within each part
+hypotheses <- c(
+  "I" = "condition1 - 2/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
+  "II" = "condition1 + 1/3 * part1:condition1 - 1/3 * part2:condition1 = 0",
+  "III" = "condition1 + 1/3 * part1:condition1 + 2/3 * part2:condition1 = 0"
+)
+
+# Fit Bayesian mixed model using prior information only
+fit_brm_prior <- brm(
+  formula = formula_brm,
+  data = trials,
+  family = gaussian(),
+  prior = prior,
+  sample_prior = "only",
+  save_pars = save_pars(all = TRUE),
+  chains = 4,
+  iter = 20000,
+  warmup = 2000,
+  file = fnames$model_brm_prior,
+  file_refit = "never"
+)
+
+# Prior predictive checks for population-level parameters
+prior_summary(fit_brm_prior)
+summary(fit_brm_prior)
+mcmc_plot(fit_brm_prior, "areas", pars = "^b_", prob_outer = 0.95)
+
+# Compute posterior distributions for dependent variables
+deps <- c("logRT", "P1", "N170", "N400")
+map(deps, function(dv) {
+
+  # Define model formula for the current dependent variable
+  formula_dv <- str_c(
+    dv, " ~ part * condition +
+      (part * condition | subject_id) +
+      (part * condition | item_id)"
+  ) %>%
+    formula()
+
+  # Sample from the posterior distribution
+  fit_brm <- update(
+    fit_brm_prior,
+    formula = formula_dv,
+    newdata = trials,
+    sample_prior = "yes",
+    file = fnames$models_brm[[dv]],
+    file_refit = "never"
+  )
+
+  # Compute follow-up comparisons with Bayes factors
+  hyps <- hypothesis(fit_brm, hypotheses) %>% {
+    mutate(
+      .$hypothesis,
+      bf01 = Evid.Ratio, bf10 = 1 / Evid.Ratio, .keep = "unused"
+    )
+  }
+
+  # Return a list of relevant model outputs
+  return(
+    list(
+      model = fit_brm,
+      summary = summary(fit_brm),
+      hypotheses = hyps
+    )
+  )
+}) %>%
+  set_names(deps) -> models_brm
+
+# Posterior predictive checks for population-level parameters
+example_model <- models_brm$N400
+example_model$summary
+example_model$hypotheses
+mcmc_plot(example_model$model, "areas", pars = "^b_", prob_outer = 0.95) +
+  theme(text = element_text(family = "Helvetica", size = 10))
+
+# Posterior predictive checks subject by subject
+pp_check(
+  example_model$model,
+  type = "dens_overlay_grouped",
+  nsamples = 50,
+  group = "subject_id"
+)
+pp_check(
+  example_model$model,
+  type = "stat_grouped",
+  nsamples = 1000,
+  group = "subject_id",
+  stat = "sd"
+)
 ```
 
-```{r exp1-plotting, include=TRUE, fig.height=12}
-# Import grand averaged evoked potentials from Python
-evokeds_exp1 <- py$evokeds_dat_exp1
+```{r, fig1, include=TRUE, fig.height=10, fig.cap="(ref:figure-1-caption)"}
+# Load montage and evoked data
+montage <- read_csv(fnames$montage, col_types = cols())
+evokeds <- read_csv(fnames$ave_grand, col_types = cols(), progress = FALSE)
 
-# Retrive locations for the relevant electrodes from standard montage
-montage <- py$evokeds_exp1$Pt1$Insight$ch_names %>% as_tibble() %>% rename(electrode = value) %>%
-  left_join(read.delim("renv/python/condaenvs/renv-python/lib/python3.8/site-packages/mne/channels/data/montages/easycap-M1.txt") %>% 
-              as_tibble() %>% rename(electrode = Site)) %>%
-  mutate(x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
-         y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)))
-
-# Define function to plot trial structure
-plot_trial <- function(){
-  colour_insight <- viridisLite::viridis(1, begin = 0, end = 0)
-  colour_naive <- viridisLite::viridis(1, begin = 0.5, end = 0.5)
-  trial_pt1 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
-    geom_text(aes(x = 37, y = 68, label = "Part 1"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
-    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
-    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
-    draw_image("materials/exp1/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
-    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica") +
-    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
-  trial_pt2 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
-    geom_text(aes(x = 37, y = 68, label = "Part 2"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
-    geom_rect(aes(xmin = 0, xmax = 20, ymin = 0, ymax = 20), color = "black", fill = "white") +
-    geom_text(aes(x = 10, y = 10.5, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
-    geom_text(aes(x = 10, y = -3, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = colour_insight, fill = "white") +
-    geom_text(aes(x = 28, y = 23, label = "Potato\nmashing"), color = colour_insight, size = 10/.pt, family = "Helvetica") +
-    geom_text(aes(x = 28, y = 10, label = "2.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 39, ymax = 59), color = colour_naive, fill = "white") +
-    geom_text(aes(x = 28, y = 49, label = "Message\nmorsing"), color = colour_naive, size = 10/.pt, family = "Helvetica") +
-    geom_text(aes(x = 28, y = 36, label = "or"), color = "black", size = 10/.pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
-    geom_text(aes(x = 46, y = 34, label = "*"), size = 8, family = "Helvetica") +
-    geom_text(aes(x = 46, y = 23, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 54, xmax = 74, ymin = 39, ymax = 59), color = "black", fill = "white") +
-    draw_image("materials/exp1/potato_masher.png", x = 54, y = 39, width = 20, height = 20) +
-    geom_text(aes(x = 65, y = 36, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica", lineheight = 1) +
-    geom_segment(aes(x = 28, y = 0, xend = 74, yend = 33.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
-  trial_pt3 <- ggplot() + coord_fixed() + theme_void() + xlim(c(0, 74)) + ylim(c(-5, 68)) +
-    geom_text(aes(x = 37, y = 68, label = "Part 3"), size = 14/.pt, family = "Helvetica", fontface = "bold") +
-    geom_rect(aes(xmin = 18, xmax = 38, ymin = 13, ymax = 33), color = "black", fill = "white") +
-    geom_text(aes(x = 28, y = 23, label = "+"), size = 5, family = "Helvetica", fontface = "bold") +
-    geom_text(aes(x = 28, y = 10, label = "0.5 s"), color = "black", size = 10/.pt, family = "Helvetica") +
-    geom_rect(aes(xmin = 36, xmax = 56, ymin = 26, ymax = 46), color = "black", fill = "white") +
-    draw_image("materials/exp1/potato_masher.png", x = 36, y = 26, width = 20, height = 20) +
-    geom_text(aes(x = 47, y = 23, label = "max. 3 s"), color = "black", size = 10/.pt, family = "Helvetica") +
-    geom_segment(aes(x = 46, y = 13, xend = 56, yend = 20.222), arrow = arrow(length = unit(0.2, "cm")), color = "black")
-  plot_grid(trial_pt1, NULL, trial_pt2, NULL, trial_pt3, nrow = 1, rel_widths = c(10, 1, 10, 1, 10))}
-
-# Define function to plot mean ERP amplitudes
-plot_bars <- function(data, stars, ymin){
-  parts <- map(unique(data$part), function(part){
-    # For which components in the current part do we have a significant effect?
-    sig <- map(stars, paste0("Pt", part)) %>% as.data.frame() %>% t() %>% as.data.frame() %>%
-      set_colnames("label") %>% rownames_to_column("comp") %>% na.omit()
-    # Create bar plot for the current part
-    map(c("P1", "N1", "N400"), function(comp){
-      p <- data %>% filter(part == !!part) %>%
-        Rmisc::summarySEwithin(measurevar = comp, withinvars = "condition", idvar = "participant") %>%
-        mutate(comp = !!comp) %>% rename(amplitude = !!comp)}) %>% bind_rows() %>%
-      mutate(comp = fct_relevel(comp, "P1", "N1", "N400")) %>%
-      ggplot(aes(x = comp, y = amplitude, fill = condition)) +
-      # geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
-      # annotate("tile", x = sig$comp, y = -0.4, width = 0.45, height = 0.8, colour = "black", fill = "white", size = 0.5) +
-      # annotate("rect", xmin = -Inf, xmax = Inf, ymin = -0.2, ymax = Inf, fill = "white") +
-      # geom_bar(aes(y = amplitude - se - 0.2), stat = "identity", position = position_dodge()) + scale_fill_manual(values = c("white", "white")) +
-      # new_scale_fill() +
-      # annotate("label", x = sig$comp, y = -0.96, label = sig$label, size = 7, family = "Helvetica", label.size = 0) +
-      geom_bar(aes(fill = condition), stat = "identity", position = position_dodge()) +
-      scale_fill_viridis_d(end = 0.5) +
-      geom_errorbar(aes(ymin = amplitude - se, ymax = amplitude + se), position = position_dodge(width = 0.9), width = 0.5) +
-      annotate("text", x = sig$comp, y = ymin, label = sig$label, size = 6, family = "Helvetica") +
-      geom_hline(yintercept = 0) +
-      coord_cartesian(ylim = c(ymin, ymin + 7)) +
-      ylab("ROI ampl.\n(µV)") +
-      scale_y_continuous(breaks = seq(trunc(ymin), trunc(ymin) + 6, 2)) +
-      theme_classic() +
-      theme(legend.position = "none",
-            panel.grid = element_blank(),
-            axis.ticks = element_line(color = "black"),
-            axis.title.x = element_blank(),
-            axis.title.y = element_text(family = "Helvetica", color = "black", size = 10),
-            axis.text = element_text(family = "Helvetica", color = "black", size = 10),
-            plot.margin = margin(t = 0.3, r = 0, b = 0.4, l = 0.2, "cm"))})
-  plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))}
-
-# Define function to plot ERP waveforms and topographies
-plot_erps <- function(comps, evokeds, montage, stars){
-  pmap(comps, function(name, start, stop, roi){
-    # N400 gets a different scale than P1 and N1
-    ymin <- ifelse(name == "N400", -3, -4)
-    # Loop through parts
-    parts <- map(c("Pt1", "Pt2", "Pt3"), function(part){
-      # Create (conditions x time points) x electrodes tibble
-      data_plot <- evokeds[[part]] %>% map(function(data){
-        data %>% "*"(1e6) %>% t() %>% as_tibble(.name_repair = "unique") %>% set_colnames(montage$electrode) %>%
-          mutate(.time = times, roi = rowMeans(select(., all_of(roi))))}) %>%
-        bind_rows(.id = "condition")
-      # Prepare waveform
-      wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
-        annotate("rect", xmin = start, xmax = stop, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
-      # Shade significant area
-      star <- stars[[name]][[part]]
-      if (!is.na(star)){
-        wave <- wave + geom_ribbon(data = data_plot %>% filter(.time >= start & .time <= stop) %>%
-                                     group_by(.time) %>% summarise(ymin = min(roi), ymax = max(roi)),
-                                   aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
-                                   inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1))} #+
-          #annotate("text", label = star, x = start + (stop - start)/2, y = -3.2, size = 7, family = "Helvetica")}
-      # Add waves and styling
-      wave <- wave +
-        annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
-        annotate("segment", x = 0, xend = 0, y = ymin, yend = ymin + 12) +
-        annotate("segment", x = seq(-100, 700, 200), xend = seq(-100, 700, 200), y = -0.3, yend = 0) +
-        annotate("segment", x = -12, xend = 0, y = seq(-2, 8, 4), yend = seq(-2, 8, 4)) +
-        annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10/.pt, family = "Helvetica") +
-        annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10/.pt, family = "Helvetica", hjust = 1) +
-        annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10/.pt, family = "Helvetica", lineheight = 0.9) +
-        annotate("text", x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10/.pt, family = "Helvetica", angle = 90, lineheight = 0.9) +
-        geom_line() +
-        scale_color_viridis_d(end = 0.5) +
-        coord_cartesian(xlim = c(-200, 800), ylim = c(ymin, ymin + 14), expand = FALSE) +
-        theme_void() +
-        theme(legend.position = "none")
-      # Plot topography
-      topo <- data_plot %>% filter(.time >= start & .time <= stop) %>%
-        group_by(condition) %>% summarise(across(montage$electrode, mean)) %>%
-        pivot_longer(-condition) %>% pivot_wider(names_from = condition) %>%
-        transmute(amplitude = Insight - Naive) %>% bind_cols(montage) %>%
-        eegUtils::topoplot(limits = c(-1, 1), palette = "viridis", contour = FALSE, highlights = roi, scaling = 0.1) +
-        theme(legend.position = "none")
-      topo$layers[[3]]$aes_params$size <- topo$layers[[4]]$aes_params$size <- topo$layers[[5]]$aes_params$size <- 0.6
-      # Combine waveform and topography
-      wave + draw_plot(topo, width = 320, height = 9, x = 500, y = ymin + 6.4)})
-    # Compbine plots for the different parts
-    plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
-    # Combine plots for the different components
-  }) %>% plot_grid(plotlist = ., nrow = 3)}
-
-# Define functions to plot legends for conditions and topoplots
-plot_legends <- function(){
-  legend_conditions <- get_legend(tibble(Conditions = c("Insight", "Naive")) %>% ggplot(aes(x = 0, y = 0, fill = Conditions)) +
-                                    geom_raster() + scale_fill_viridis_d(end = 0.5) +
-                                    theme(legend.direction = "horizontal", legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
-                                          legend.text = element_text(family = "Helvetica", size = 10), legend.spacing.x = unit(0.3, "cm")))
-  legend_topo <- get_legend(tibble(amplitude = c(-1, 1)) %>% ggplot(aes(x = 0, y = 0, fill = amplitude)) + geom_raster() + labs(fill = "Insight - naive\nampl. (µV)") +
-                              scale_fill_viridis_c(guide = guide_colorbar(ticks = FALSE, title.position = "left", title.vjust = 1, title.hjust = 0.5)) +
-                              theme(legend.direction = "horizontal", legend.title = element_text(family = "Helvetica", size = 10, face = "bold"),
-                                    legend.text = element_text(family = "Helvetica", size = 10), legend.key.width = unit(0.8, "cm"), legend.spacing.x = unit(0.3, "cm")))
-  plot_grid(NULL, legend_conditions, legend_topo, NULL, nrow = 1, rel_widths = c(1, 3, 3, 1))}
-
-# Apply the functions to the data from experiment 1
-plot_grid(plot_trial(),
-          plot_bars(data = data_exp1, stars = stars_exp1, ymin = -1.5),
-          plot_erps(comps = comps, evokeds = evokeds_exp1, montage = montage, stars = stars_exp1),
-          plot_legends(),
-          nrow = 4, rel_heights = c(3, 2, 6, 1), labels = c("A", "B", "C", ""), label_fontfamily = "Helvetica")
+# Create plot for Experiment 1
+plot_fig1(erp_components, evokeds, trials_main, models_lme)
 ```
 
-```{r exp2-behavior}
-# List of filenames for behavioral data
-fnames_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE)
+(ref:figure-1-caption) Procedure and results of Experiment 1.
+(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
+In the post-insight part, the same objects were presented again without keywords.
+(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
+Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight part, less negative amplitudes in the N400 component during the insight and post-insight parts, and more positive amplitudes in the P1 component during the post-insight part.
+Ampl.
+= amplitude.\newline
+\* *p* < .05. \*\* *p* < .01. \*\*\* *p* < .001.
 
-# Apply the preprocessing function
-data_exp2 <- map(fnames_exp2, preproc_behav)
+In the *insight* part, the 120 unfamiliar objects were presented for the second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
+Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
+The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).
 
-# Tabulate percentage of stimuli per condition
-(stims_exp2 <- bind_rows(data_exp2) %>% filter(condition != "Excl_cond") %>%
-    group_by(participant, condition) %>% tally() %>%
-    group_by(condition) %>% summarise(mean = mean(n)/(60*3)) %>% # 60 items per condition
-    mutate(mean = if_else(condition == "Excl_known", mean/2, mean))) # 120 items in total
+In the *post-insight* part, the unfamiliar objects were presented for a third time with the same trial structure as in the pre-insight part, that is, without any keywords.
+The insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight part (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight part (without keywords) before moving on to the next block consisting of 30 different objects.
+They continued like this until all four blocks were completed in both parts.
+In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight part and 120 unfamiliar objects in the pre-insight, insight, and post-insight parts).
+It took participants approximately 35 minutes to complete.
+
+## EEG Recording and Preprocessing
+
+The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system [@americanelectroencephalographicsociety1991] and referenced online to an external electrode placed on the left mastoid (M1).
+Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively.
+Electrode impedances were kept below 5 kΩ.
+An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
+
+The data were preprocessed offline using the MNE software [Version `r system("mne --version", intern = TRUE) %>% str_remove("MNE ")`; @gramfort2013] in Python [Version `r system("python3 --version", intern = TRUE) %>% str_remove("Python ")`; @vanrossum2009].
+First, all scalp electrodes were re-referenced to the common average.
+Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
+The first 15 components were extracted with the FastICA algorithm [@hyvarinen1999] after temporarily low-pass filtering the data at 1 Hz.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find_bads_eog* function.
+After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
+Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the presentation of each unfamiliar object.
+The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset.
+Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
+This led to the exclusion of an average of `r format(round(mean(rejected), 1), nsmall = 1)` trials per participant (= `r percent(mean(rejected) / 360, accuracy = 0.1)`; range `r min(rejected)`--`r max(rejected)` trials).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+
+## Statistical Analyses
+
+First, we excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight part (i.e., before any keywords were presented).
+This led to the exclusion of an average of `r format(round(obj_per_cond[["Excl_known"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Excl_known"]] / 120, accuracy = 0.1)` of unfamiliar objects).
+Next, to delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participant (see Figure \@ref(fig:fig1)A).
+Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if the participant indicated knowing what the object was or having an assumption.
+This was the case for an average of `r format(round(obj_per_cond[["Informed"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Informed"]]/60, accuracy = 0.1)` of objects presented with matching keywords).
+Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if the participant indicated not knowing what the object was or having rather no assumption.
+This was the case for an average of `r format(round(obj_per_cond[["Naive"]], 1), nsmall = 1)` objects per participant (= `r percent(obj_per_cond[["Naive"]]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
+The same assignment of objects to conditions (based on the manipulation and responses in the insight part) was also used for analyzing the pre-insight and post-insight parts.
+This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).
+
+The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @fromer2018].
+Compared to traditional by-participant or by-item analyses of variance, these models allow tighter control over the false positive rate because they simultaneously account for by-participant and by-item non-independencies in the data [@burki2018; @judd2012].
+Furthermore, they flexibly handle unbalanced data.
+This was important in our case because of the rejection of bad ERP epochs as well as the way we constructed our experimental conditions (see above).
+
+Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
+All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast [i.e., subtracting the first part from the second part and the second part from the third part, the intercept being the grand mean across all three parts; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
+To determine the random effects structure, we always started with the maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
+We then performed a model selection algorithm proposed by @matuschek2017 to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+Only if the parsimonious model explained the data similarly well as the complex model [determined by *p* ≥ .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the resulting formulas after model selection).
+All models were computed in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4].
+The optimizer function *bobyqa* with a maximum of 10^6^ iterations was used for maximum likelihood estimation.
+The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`; @R-buildmer].
+
+To investiage if semantically informed perception had an influence on the ERPs within each part, planned follow-up comparisons were calculated, contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight parts.
+This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`; @R-emmeans].
+All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`; @R-lmerTest].
+
+The materials, single trial preprocessed data, and code for data analysis are openly available at <https://osf.io/uksbc/>.
+
+# Results
+
+```{r, tab1, include=TRUE, results="asis"}
+# Create table of LMM results
+tab1 <- create_table(
+  models = models_lme[c("P1", "N170", "N400")],
+  stub_anova = c("Part", "Condition", "Pt. × con."),
+  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
+  caption = paste(
+    "Linear Mixed-Effects Regression Models",
+    "\\smallskip"
+  ),
+  note = paste(
+    "Pt. = part, con. = condition, est. = estimate, CI = 95\\%",
+    "confidence interval."
+  )
+)
 ```
 
-```{python exp2-preprocessing}
-# List of raw EEG filenames
-fnames_exp2 = sorted(glob.glob('data/exp2/EEG/*.vhdr'))
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment (see Table \@ref(tab:tab1)).
+In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment.
+Crucially, the part × condition interaction was significant for all three components.
+To answer our main research question, we decomposed these interactions into the simple effects of the semantically informed condition versus the naive condition within each of the three different parts of the experiment.
 
-# Import behavioral data from R
-metadata_exp2 = r.data_exp2
+## ERPs Before Insight Was Occurring
 
-# Check if preprocessing was done already (delete the file to re-run)
-if os.path.exists('output/exp2-epo.fif'):
-  # Load preprocessed data from file
-  epochs_exp2 = mne.read_epochs('output/exp2-epo.fif', preload=True)
-else:
-  # Apply the preprocessing function
-  epochs_exp2 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp2, metadata_exp2)]
-  # Combine epochs into a single data set
-  epochs_exp2 = mne.concatenate_epochs(epochs_exp2)
-  # Backup epochs to the output folder
-  epochs_exp2.save('output/exp2-epo.fif')
+In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component (see Table \@ref(tab:tab1) and Figure \@ref(fig:fig1)B).
+This was expected because given that (a) the critical presentation of the keywords (leading either to semantically informed perception or to naive perception) had not yet taken place and (b) the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences between conditions.
 
-# # Get indices of bad epochs despite ICA
-# rej_exp2 = epochs_exp2.drop_log
-# rej_exp2[:] = [item for item in rej_exp2 if item != ['IGNORED']]
-# rej_exp2 = [i for i in range(len(rej_exp2)) if rej_exp2[i] != []]
+## ERPs While Insight Was Occurring
 
-# Apply the function to compute grand averages
-evokeds_exp2, evokeds_dat_exp2 = compute_evokeds(epochs=epochs_exp2)
+In the insight part, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perceptio nof the objects semantically naive.
+During semantically informed perception, the amplitude of the N170 component was significantly enlarged (i.e., more negative) and the amplitude of the N400 component was significantly reduced (i.e., less negative).
+There were no reliable differences in the P1 component.
+
+## ERPs After Insight Had Occurred
+
+In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part).
+As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, whereas the effect in the N170 component did not reoccur.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place.
+
+```{r, fig3, eval=FALSE, include=TRUE}
+# Read grand averages of evoked power
+ave_tfr_flat <- read_csv(fnames$ave_tfr_flat, col_types = cols(), progress = FALSE)
+ave_tfr_diff <- read_csv(fnames$ave_tfr_diff, col_types = cols(), progress = FALSE)
+
+# Scaling of power in all plots
+limits_power <- c(0, 0.5)
+
+# Time-frequency of interest based on visual inspect
+tfoi <- list(tmin = 150, tmax = 350, fmin = 14, fmax = 24) # Beta or
+tfoi <- list(tmin = 200, tmax = 400, fmin = 34, fmax = 48) # Gamma
+
+# Standard text format
+standard_text <- element_text(size = 10, color = "black", family = "Helvetica")
+
+plot_tfr_raster <- function(ave_tfr, limits, tmin, tmax, fmin, fmax, label) {
+  # Average across electrodes
+  ave_tfr %>%
+    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
+    group_by(part, time, freq) %>%
+    summarise(power = mean(power), .groups = "drop") %>%
+    # Create one raster plot per part
+    group_by(part) %>%
+    group_map(function(data_part, part) {
+      ggplot(data_part, aes(x = time, y = freq, fill = power)) +
+        geom_raster() +
+        scale_fill_viridis_c(
+          limits = limits,
+          labels = function(x) x * 100,
+          guide = guide_colorbar(
+            title = "Power (% change\nfrom baseline)",
+            title.position = "left",
+            title.theme = element_text(size = 10, color = "black", angle = 90, lineheight = 1),
+            title.hjust = 0.5,
+            label.theme = element_text(size = 10, color = "black"),
+            barheight = unit(4, "cm"),
+            ticks = FALSE,
+            direction = "vertical"
+          ),
+          oob = squish
+        ) +
+        scale_x_continuous(breaks = seq(-100, 700, 200)) +
+        coord_cartesian(expand = FALSE) +
+        annotate("rect", xmin = tmin, xmax = tmax, ymin = fmin + 1, ymax = fmax + 1, color = "white", fill = NA, linetype = "dotted") +
+        annotate("segment", x = 0, xend = 0, y = -Inf, yend = Inf, color = "white", linetype = "dotted") +
+        labs(x = "Time (ms)", y = "") +
+        theme_minimal() +
+        theme(
+          legend.position = "none",
+          axis.title = standard_text,
+          axis.text = standard_text
+        )
+    }) -> plotlist
+  # Add label and axis title to the first plot
+  plotlist[[1]] <- plotlist[[1]] + annotate(
+    "text",
+    x = -100,
+    y = 27,
+    label = label,
+    size = 10 / .pt,
+    angle = 90,
+    family = "Helvetica",
+    color = "white",
+    lineheight = 0.9
+  ) +
+    ylab("Frequency (ms)")
+  # Extract legend for another subplot
+  current_legend <<- get_legend(plotlist[[1]] + theme(legend.position = "right"))
+  plot_grid(plotlist = plotlist, nrow = 1)
+}
+
+plot_tfr_topo <- function(ave_tfr, limits, tmin, tmax, fmin, fmax, legend) {
+  # Average across times and frequencies of interest
+  ave_tfr_diff %>%
+    # Select time window and frequencies of interest
+    filter(time >= tmin & time <= tmax & freq >= fmin & freq <= fmax) %>%
+    # Convert to long format
+    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
+    # Create one topoplot per part
+    group_by(part) %>%
+    group_map(function(data_part, part) {
+      data_part %>%
+        group_by(electrode) %>%
+        summarise(power = mean(power), .groups = "drop") %>%
+        inner_join(montage, by = "electrode") %>%
+        eegUtils::topoplot(
+          limits = limits,
+          palette = "viridis",
+          contour = FALSE,
+          quantity = "power",
+          scaling = 0.5
+        ) +
+        theme(legend.position = "none", )
+    }) -> plotlist
+  # plotlist <- c(plotlist, list(legend))
+  plot_grid(
+    NULL,
+    plotlist[[1]],
+    NULL,
+    plotlist[[2]],
+    NULL,
+    plotlist[[3]],
+    nrow = 1,
+    rel_widths = c(2, 7, 0, 7, 1, 7)
+  )
+}
+
+# Bring it all together
+plot_grid(
+  plot_headings(spacing = c(1, 7, 1, 7, 1, 7)),
+  do.call(
+    plot_tfr_raster, c(tfoi, list(
+      ave_tfr = ave_tfr_flat,
+      limits = limits_power,
+      label = "All channels,\nall conditions"
+    ))
+  ),
+  do.call(
+    plot_tfr_raster, c(tfoi, list(
+      ave_tfr = ave_tfr_diff,
+      limits = limits_power,
+      label = "All channels,\n\u0394 (informed - naive)"
+    ))
+  ),
+  do.call(
+    plot_tfr_topo, c(tfoi, list(
+      ave_tfr = ave_tfr_diff,
+      limits = limits_power,
+      legend = current_legend
+    ))
+  ),
+  nrow = 4,
+  rel_heights = c(1, 5, 5, 5),
+  labels = c("", "A", "B", "C"),
+  label_y = c(1, 1.16, 1.1, 1),
+  label_fontfamily = "Helvetica"
+) +
+  draw_plot(current_legend, x = -0.42, y = -0.34) +
+  annotate_line(0.344, 0.344, -Inf, Inf) +
+  annotate_line(0.676, 0.676, -Inf, Inf) +
+  ggsave("data/processed/tfr.pdf", width = unit(10, "cm"), height = unit(7, "cm"), device = cairo_pdf)
 ```
 
-```{r exp2-analysis}
-# Re-import behavioral data
-data_exp2 <- py$epochs_exp2$metadata
+## Control Analysis
 
-# Factorize some columns
-data_exp2 %<>% mutate(part = factor(part, levels = c("1", "2", "3")),
-                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_known", "Excl_cond")),
-                      participant = factor(participant), item = factor(item))
+```{r models_control}
+# Use a different control condition ("failed insight")
+trials_control <- mutate(
+  trials,
+  condition = factor(condition, levels = c("Informed", "Excl_informed")),
+)
 
-# Check number of rejected epochs
-rejected_exp2 <- data_exp2 %>% group_by(participant) %>% tally() %>% mutate(n = 360 - n) %>% pull(n)
-mean(rejected_exp2); median(rejected_exp2); range(rejected_exp2)
+# Contrast coding for conditions
+c("Informed" = 1, "Excl_informed" = -1) %>%
+  t() %>%
+  ginv() -> contrasts(trials_control$condition)
 
-# Check if ERPs were computed already (delete the file to re-run)
-if (file.exists("output/exp2-erps.RDS")){
-  # Load ERPs from file
-  data_exp2 <- readRDS("output/exp2-erps.RDS")
+# Load fitted models or rerun them
+if (!run$model_fitting) {
+
+  # Load models
+  models_control <- readRDS(fnames$models_control)
 } else {
-  # Import epochs from Python, converting Volts to Microvolts (takes a while)
-  epochs_exp2 <- py$epochs_exp2$get_data()*1e6
-  # Apply the ERP function and save to output folder
-  data_exp2 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp2, els = els) %>%
-    set_names(comps$name) %>% cbind(data_exp2, .) %T>% saveRDS("output/exp2-erps.RDS")}
 
-# Remove any trials that don't beling to either of the two conditions
-data_exp2 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
-
-# Sliding difference coding for condition (insight-naive) and part (2-1, 3-1)
-contrasts(data_exp2$condition) <- ginv(contrasts_condition)
-contrasts(data_exp2$part) <- ginv(contrasts_part)
-
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("output/exp2-stats.RDS")){
-  # Load models from file
-  models_exp2 <- readRDS("output/exp2-stats.RDS")
-} else {
-  # Apply the modelling function and save to output folder
-  models_exp2 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp2, control = ctrl_params,
-                     specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/exp2-stats.RDS")}
-
-# Store significance levels for plotting
-stars_exp2 = list(P1 = c(Pt1 = NA, Pt2 = NA, Pt3 = NA),
-                  N1 = c(Pt1 = NA, Pt2 = "*", Pt3 = NA),
-                  N400 = c(Pt1 = NA, Pt2 = "***", Pt3 = NA))
+  # Compute models for all dependent variables in parallel
+  form <- RT ~ part * condition +
+    (part * condition | subject_id) +
+    (part * condition | item_id)
+  map(
+    deps,
+    build_lme,
+    formula = form,
+    data = trials_control,
+    n_cores = n_cores
+  ) %>%
+    set_names(deps) %T>%
+    saveRDS(fnames$models_control) -> models_control
+}
 ```
 
-```{r exp2-table, include=TRUE, results="asis"}
-# Apply the function to print the table
-create_table(models_exp2, stub.anova = c("Part", "Insight", "Pt. × ins."),
-            stub.contrasts = c("Part 1", "Part 2", "Part 3"),
-            caption = "Results of linear mixed-effects regression models for Experiment 2",
-            note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
+```{r, tab2, include=TRUE, results="asis"}
+# Create table of LMM results
+tab2 <- create_table(
+  models = models_control[c("P1", "N170", "N400")],
+  stub_anova = c("Part", "Condition", "Pt. × con."),
+  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
+  caption = paste(
+    "Control Analysis",
+    "\\smallskip"
+  ),
+  note = paste(
+    "Pt. = part, con. = condition, est. = estimate, CI = 95\\%",
+    "confidence interval."
+  )
+)
 ```
 
-```{r exp2-plotting, include=TRUE, fig.height=9}
-# Import grand averaged evoked potentials from Python
-evokeds_exp2 <- py$evokeds_dat_exp2
+In the main analysis described above, objects in the semantically informed condition (matching keywords) were contrasted against objects in the naive condition (non-matching keywords) as the baseline condition.
+This may raise the question if the N170 and/or N400 effects in the insight part could be due to a mismatch response for objects in the naive condition.
+To rule out this alternative explanation, we repeated the analysis using a different baseline condition, namely those objects that were presented with matching keywords (as in the informed condition) but on which participants failed to capitalize according to their behavioral responses.
+This was the case for `r percent(obj_per_cond[["Excl_informed"]] / 60, accuracy = 0.1)` of objects presented with matching keywords.
+As before, there semantically informed perception led to a reliable increase in the N170 component and a reliable decrease in the N400 component (see Table \@ref(tab:tab2)).
 
-# Apply the plotting functions to the data from experiment 2
-plot_grid(plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
-          plot_erps(comps = comps, evokeds = evokeds_exp2, montage = montage, stars = stars_exp2),
-          plot_legends(),
-          nrow = 3, rel_heights = c(2, 6, 1), labels = c("A", "B", ""), label_fontfamily = "Helvetica")
-```
+# Discussion
 
-```{r joint-analysis}
-# Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
-data_joint <- data_exp2 %>%
-  mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
-  bind_rows(data_exp1, ., .id = "experiment") %>%
-  mutate(experiment = as_factor(experiment))
+Here we investigated if obtaining a semantic understanding of previously unfamiliar objects has an influence on how we perceive them.
+To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
+For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, the information was non-matching, thus keeping the perception of the object semantically naive.
+We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
+When the same objects were presented again without the semantic information, the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+We will discuss each of these effects in turn, starting with the latest (i.e., post-perceptual) effect and moving backward in time to the earlier (i.e., more perceptual) effects.
 
-# Sliding difference coding for experiment (2-1), condition (insight-naive), and part (2-1, 3-1)
-t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
-contrasts(data_joint$experiment) <- ginv(contrasts_experiment)
-contrasts(data_joint$condition) <- ginv(contrasts_condition)
-contrasts(data_joint$part) <- ginv(contrasts_part)
+The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
+Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) lessened participants' demand for effortful semantic processing in comparison to the naive condition [@kutas2011].
+This replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+The time course of this effect and the computational role of the N400 [@lau2008; @rabovsky2018] suggest that it has a post-perceptual locus.
 
-# New formula for LMMs
-form_joint <- tabulate.formula(~ part*condition*experiment + (part*condition|participant) + (part*condition*experiment|item))
-form_joint %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
+In contrast to the N400, the N170 component (150--200 ms after object onset) was modulated while but not after the objects were presented together with the relevant semantic information.
+As such, it can be seen as an online marker of semantic insight, that is, participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
+The N170 is typically associated with the holistic perception of faces [@eimer2011; @sagiv2001] and other stimuli of visual expertise [@rossion2002; @tanaka2001].
+It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
+This interpretation is supported by previous findings with a similar experimental paradigm in the domain of face perception [@bentin2002]: In this study, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
+This effect was absent when a visual control stimulus (a non-face object) was shown instead of the intact face.
+In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
+Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
+Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level (i.e., holistic) perception of visual objects, integrating across their visual features.
 
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("output/joint-stats.RDS")){
-  # Load models from file
-  models_joint <- readRDS("output/joint-stats.RDS")
-} else {
-  # Apply the modelling function and save to output folder
-  models_joint <- map(comps$name, compute_models, formula = form_joint, data = data_joint, control = ctrl_params,
-                      specs = specs_exp12) %>% set_names(comps$name) %T>% saveRDS("output/joint-stats.RDS")}
-```
+The P1 component (100--150 ms after object onset), unlike the N400 and N170 components, was modulated by semantic information only one trial after the information had been obtained.
+This is consistent with previous studies showing modulations of the P1 component when participants learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
+What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information).
+Instead, it can be observed as soon as one trial after semantic insight has happened.
+Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
 
-```{r joint-table, include=TRUE, results="asis"}
-# Apply the function to print the table
-create_table(models_joint, stub.anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.",
-                                         "Ins. × exp.", "Pt. × ins. × exp."),
-            stub.contrasts = c("Part 1", "Part 2", "Part 3"),
-            caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
-            note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.")
-```
+Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects.
+However, the finding that these two components were modulated in different parts of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
+It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem to reflect recurrent processing *within* the visual system [@wyatte2014].
+Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
 
-```{r exp3-behavior}
-# List of filenames for behavioral data
-fnames_exp3 <- list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE)
+While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream for object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
+@hsieh2010 showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
+They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
+This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital cortex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
+Both of these cortical regions are consistent with the neural generators of the N170 and P1 components in the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
 
-# Apply the preprocessing function
-data_exp3 <- map(fnames_exp3, preproc_behav)
+On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999; but see @clarke2020].
+However, proponents of such a modular view have pointed out important shortcomings of previous studies that claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
+We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was being presented (in the pre-insight part).
+Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual locus from those with a post-perceptual locus.
+Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
+Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
+Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order and at the same location.
+Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
+We hope that these procedures have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the cognitive impenetrability of perception.
 
-# Tabulate percentage of stimuli per condition
-(stims_exp3 <- bind_rows(data_exp3) %>% filter(condition != "Excl_cond" & part != "4") %>%
-    group_by(participant, condition) %>% tally() %>%
-    group_by(condition) %>% summarise(mean = mean(n)/(112*3)) %>% # 112 items per condition
-    mutate(mean = if_else(condition == "Excl_known", mean/2, mean))) # 224 items in total
-```
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @lindsay2020].
+In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this "barrier of meaning" [@mitchell2020].
+Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.
 
-```{python exp3-preprocessing}
-# List of raw EEG filenames
-fnames_exp3 = sorted(glob.glob('data/exp3/EEG/*.vhdr'))
+A theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking at present.
+The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004; @hochstein2002] which posits that objects first enter our visual consciousness at an abstract, conceptual level.
+Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
+This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
+Besides this specific theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories [e.g., @clark2013; @lupyan2015; @panichello2013; @yuille2006].
+Despite the theoretical advances, the mechanistic details of these top-down effects at the algorithmic and implementational level [@marr1982] remain to be clarified.
 
-# Import behavioral data from R
-metadata_exp3 = r.data_exp3
+The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
+Another one is our reliance on rare and highly specialized objects (see Appendix A).
+This was necessary to induce the experience of semantic insight in a population of undergraduate students but the results may not necessarily generalize to the way in which we learn about everyday objects.[^2]
+One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
+Finally, the number participants (*n* = 24 per experiment) and trials (*k* $\approx$ 30 per part in the insight condition and *k* $\approx$ 50 per part in the naive condition) can be considered small by today's standards [@baker2020].
+Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances [see, e.g., the simulations by @matuschek2017].
+This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r tab1$conts["Insight part", "N170_p"]`) failed to reach statistical significance in the replication experiment (*p* = `r tab2$conts["Insight part", "N170_p"]`).
+To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).
+It should be noted, however, that the joint analysis of both data sets yielded a very robust N170 effect (*p* = `r tab1$conts["Insight part", "N170_p"]`).
+This makes it less likely that the effect observed in Experiment 1 was due to a false positive and instead suggests that statistical power in Experiment 2 was insufficient to render the effect significant.
+Also note that the effect in the P1 component was statistically significant in both experiments individually, making an even stronger case for the susceptibility of early cortical processing to newly acquired knowledge about objects.
 
-# Update stimulus triggers
-preproc_params['event_id'] = {'match/upright': 241, 'match/inverted': 242, 'mismatch/upright': 243, 'mismatch/inverted': 244}
+[^2]: Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize [@samaha2018].
 
-# Check if preprocessing was done already (delete the file to re-run)
-if os.path.exists('output/exp3-epo.fif'):
-  # Load preprocessed data from file
-  epochs_exp3 = mne.read_epochs('output/exp3-epo.fif', preload=True)
-else:
-  # Apply the preprocessing function
-  epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **preproc_params) for fname, meta in zip(fnames_exp3, metadata_exp3)]
-  # Combine epochs into a single data set
-  epochs_exp3 = mne.concatenate_epochs(epochs_exp3)
-  # Backup epochs and evokeds to the output folder
-  epochs_exp3.save('output/exp3-epo.fif')
-
-# # Get indices of bad epochs despite ICA
-# rej_exp3 = epochs_exp3.drop_log
-# rej_exp3[:] = [item for item in rej_exp3 if item != ['IGNORED']]
-# rej_exp3 = [i for i in range(len(rej_exp3)) if rej_exp3[i] != []]
-```
-
-```{r exp3-analysis}
-# Re-import behavioral data
-data_exp3 <- py$epochs_exp3$metadata
-
-# Factorize some columns
-data_exp3 %<>% mutate(part = factor(part, levels = c("1", "2", "3")),
-                      position = factor(position, levels = c("Inverted", "Upright")),
-                      condition = factor(condition, levels = c("Insight", "Naive", "Excl_known", "Excl_cond")),
-                      participant = factor(participant), item = factor(item))
-
-# Check if ERPs were computed already (delete the file to re-run)
-if (file.exists("output/exp3-erps.RDS")){
-  # Load ERPs from file
-  data_exp3 <- readRDS("output/exp3-erps.RDS")
-} else {
-  # Import epochs from Python, converting Volts to Microvolts (takes a while)
-  epochs_exp3 <- py$epochs_exp3$get_data()*1e6
-  # Apply the ERP function and save to output folder
-  data_exp3 <- pmap_dfc(comps, compute_erps, epochs = epochs_exp3, els = els) %>%
-    set_names(comps$name) %>% cbind(data_exp3, .) %T>% saveRDS("output/exp3-erps.RDS")}
-
-# Remove any trials from part 4
-data_exp3 %<>% filter(part != "4") %>% droplevels()
-
-# Check number of rejected epochs
-rejected_exp3 <- data_exp3 %>% group_by(participant) %>% tally() %>% mutate(n = 672 - n) %>% pull(n)
-mean(rejected_exp3); median(rejected_exp3); range(rejected_exp3)
-
-# Remove any trials that don't beling to either of the two conditions
-data_exp3 %<>% filter(condition %in% c("Insight", "Naive")) %>% droplevels()
-
-# Sliding difference coding for position (inverted-updright), condition (insight-naive), and part (2-1, 3-1)
-t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
-contrasts(data_exp3$position) <- ginv(contrasts_position)
-contrasts(data_exp3$condition) <- ginv(contrasts_condition)
-contrasts(data_exp3$part) <- ginv(contrasts_part)
-
-# New formula for LMMs
-form_exp3 <- tabulate.formula(~ part*condition*position + (part*condition*position|participant) + (part*condition*position|item))
-form_exp3 %<>% mutate(block = replace(block, is.na(grouping), "fixed"))
-
-# New follow-up contrasts
-specs_exp3 = pairwise ~ condition|position*part
-
-# Check if models were computed already (delete the file to re-run)
-if (file.exists("output/exp3-stats.RDS")){
-  # Load models from file
-  models_exp3 <- readRDS("output/exp3-stats.RDS")
-} else {
-  # Apply the modelling function and save to output folder
-  models_exp3 <- map(comps$name, compute_models, formula = form_exp3, data = data_exp3, control = ctrl_params,
-                     specs = specs_exp3) %>% set_names(comps$name) %T>% saveRDS("output/exp3-stats.RDS")}
-```
-
-```{r exp3-table, include=TRUE, results= asis"}
-# Apply the function to print the table
-create_table(models_exp3, stub.anova = c("Part", "Insight", "Position", "Pt. × ins.", "Pt. × pos.",
-                                        "Ins. × pos.", "Pt. × ins. × pos."),
-            stub.contrasts = c("Part 1, inverted", "Part 1, upright", "Part 2, inverted",
-                               "Part 2, upright", "Part 3, inverted", "Part 3, upright"),
-            caption = "Results of linear mixed-effects regression models for Experiment 3",
-            note = "Pt. = part, ins. = insight, pos. = position, est. = estimate, CI = confidence interval.")
-```
+Taken together, this study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the processing of the object.
+This influence is immediate in at least two different ways: First, it does not require extensive training and can instead be observed within the same trial in which the information has been presented (and/or one trial later).
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages---typically associated with semantic processing---but also at earlier stages---typically associated with visual perception itself and happening within less than a fifth of a second after the object is presented to us.
 
@@
 
-```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
 
+<div id="refs" custom-style="Bibliography"></div>
 \endgroup

### 2021-08-09 manuscript/plots_tables.R

@@ -1,0 +1,423 @@
+########################################################################################
+## FUNCTIONS TO CREATE PLOTS AND TABLES ##
+########################################################################################
+
+# Function to create Figure 1
+plot_fig1 <- function(erp_components, evokeds, trials, models) {
+
+  # Define colors for conditions
+  colors <- list(
+    Informed = viridisLite::viridis(1, begin = 0.1),
+    Naive = viridisLite::viridis(1, begin = 0.5)
+  )
+
+  # Base object for split violin plots (kudos to https://stackoverflow.com/a/45614547)
+  GeomSplitViolin <- ggproto(
+    "GeomSplitViolin", GeomViolin,
+    draw_group = function(self, data, ..., draw_quantiles = NULL) {
+      data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
+      grp <- data[1, "group"]
+      newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
+      newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
+      newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
+      if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
+        stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 1))
+        quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
+        aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
+        aesthetics$alpha <- rep(1, nrow(quantiles))
+        both <- cbind(quantiles, aesthetics)
+        quantile_grob <- GeomPath$draw_panel(both, ...)
+        ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
+      }
+      else {
+        ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
+      }
+    }
+  )
+
+  # Base function for split violin plots (kudos to https://stackoverflow.com/a/45614547)
[…]

### 2021-08-14 manuscript/manuscript.Rmd
New equalize_trial_counts, io

@@
 
-# Write R package citations
+# Write R package citations to bibliography
 r_refs(here("manuscript", "r-references.bib"), append = FALSE)
@@
 # Set global chunk options
-opts_chunk$set(
-  fig.align = "center",
-  fig.width = 10,
-  include = FALSE,
-  out.width = "100%"
-)
+opts_chunk$set(fig.width = 10, include = FALSE, out.width = "100%")
 
 # Re-run preprocessing and/or model fitting?
-run <- list(preprocessing = FALSE, model_fitting = FALSE)
+run <- list(preprocessing = TRUE, model_fitting = TRUE)
 
-# Number of CPU cores for parallel model fitting
-n_cores <- detectCores()
-
-# File names for easier I/O
-deps <- c("logRT", "P1", "N170", "N400")
-fnames <- list(
+# File names for easier input/output
+deps <- c("logRT", "P1", "N170", "N400")  # dependent variables
+io <- list(
   montage = "results/montage.csv",
@@
 
-# Generate new BIDS-style subject IDs
-seq(length(fname_vhdr)) %>%
+# Generate new BIDS-style subject IDs (sub-01, sub-02, ...)
+seq_along(fname_vhdr) %>%
   str_pad(width = 2, pad = 0) %>%
@@
   name = c("P1", "N170", "N400"),
-  tmin = c(0.1, 0.15, 0.4),
-  tmax = c(0.15, 0.2, 0.7),
+  tmin = c(0.100, 0.150, 0.400),
+  tmax = c(0.150, 0.200, 0.700),
   roi = list(
@@
   # Import the custom Python functions for preprocessing
-  pp <- import_from_path("preprocessing", path = "code")
+  pp <- import_from_path("preprocessing", path = here("manuscript"))
 
@@
       output_dir = "data/preprocessed",
+      resample_sfreq = 250,
       eog_names = c("HEOG", "VEOG"),
@@
       ica_method = "fastica",
-      ica_seed = as.integer(1234),
+      random_seed = as.integer(1234),
       hipass = 0.1,
@@
       tfr_baseline = tuple(-0.3, -0.1),
-      tfr_equalize = "condition == ['Informed', 'Naive']",
-      tfr_resample = py_none(),
+      tfr_equalize = TRUE,
+      condition_col = "condition",
+      item_col = "item_id",
+      drop_conditions = c("Excl_informed", "Excl_naive", "Excl_known"),
       tfr_freqs = tfr_freqs,
       tfr_cycles = tfr_cycles,
-      tfr_crop = tuple(-0.2, 0.8)
+      tfr_crop = tuple(-0.3, 0.7)
     )
@@
   # Combine single trial data for all subjects
-  dir.create("results")
+  dir.create("results", showWarnings = FALSE)
   str_c("data/preprocessed/", subject_id, "_trials.csv") %>%
@@
     bind_rows() %>%
-    write_csv(fnames$trials)
+    write_csv(io$trials)
 
@@
     mutate(across(c(x, y), round, 3)) %>%
-    write_csv(fnames$montage)
+    write_csv(io$montage)
 
@@
     rownames_to_column("subject_id") %>%
-    write_csv(fnames$obj_per_cond)
+    write_csv(io$obj_per_cond)
 }
@@
 ave = ave.groupby(id_vars, as_index=False).mean()
-ave.to_csv(r.fnames["ave_grand"], float_format="%.3f", index=False)
+ave.to_csv(r.io["ave_grand"], float_format="%.3f", index=False)
 
@@
 dfs = [ave_tfr_flat, ave_tfr_diff]
-fnames_tfr = [r.fnames["ave_tfr_flat"], r.fnames["ave_tfr_diff"]]
+fnames_tfr = [r.io["ave_tfr_flat"], r.io["ave_tfr_diff"]]
 for df, fname in zip(dfs, fnames_tfr):
@@
 # Compute average number of objects per condition
-(obj_per_cond <- read_csv(fnames$obj_per_cond, col_types = cols()) %>%
+(obj_per_cond <- read_csv(io$obj_per_cond, col_types = cols()) %>%
   summarise(across(.cols = -subject_id, .fns = mean)) %>%
@@
   # Load models
-  models_lme <- readRDS(fnames$models_lme)
+  models_lme <- readRDS(io$models_lme)
 } else {
@@
     # using an alpha level of .20 (see Matuschek et al., 2017, J Mem Lang)
+    n_cores <- detectCores()
     cl <- makeCluster(n_cores)
@@
     set_names(deps) %T>%
-    saveRDS(fnames$models_lme) -> models_lme
+    saveRDS(io$models_lme) -> models_lme
 }
@@
   warmup = 2000,
-  file = fnames$model_brm_prior,
+  file = io$model_brm_prior,
   file_refit = "never"
@@
 deps <- c("logRT", "P1", "N170", "N400")
-map(deps, function(dv) {
+map(deps, function(dep) {
 
@@
   formula_dv <- str_c(
-    dv, " ~ part * condition +
+    dep, " ~ part * condition +
       (part * condition | subject_id) +
@@
     sample_prior = "yes",
-    file = fnames$models_brm[[dv]],
+    file = io$models_brm[[dep]],
     file_refit = "never"
@@
 # Load montage and evoked data
-montage <- read_csv(fnames$montage, col_types = cols())
-evokeds <- read_csv(fnames$ave_grand, col_types = cols(), progress = FALSE)
+montage <- read_csv(io$montage, col_types = cols())
+evokeds <- read_csv(io$ave_grand, col_types = cols(), progress = FALSE)
 
@@
 # Read grand averages of evoked power
-ave_tfr_flat <- read_csv(fnames$ave_tfr_flat, col_types = cols(), progress = FALSE)
-ave_tfr_diff <- read_csv(fnames$ave_tfr_diff, col_types = cols(), progress = FALSE)
+ave_tfr_flat <- read_csv(io$ave_tfr_flat, col_types = cols(), progress = FALSE)
+ave_tfr_diff <- read_csv(io$ave_tfr_diff, col_types = cols(), progress = FALSE)
 
@@
   # Load models
-  models_control <- readRDS(fnames$models_control)
+  models_control <- readRDS(io$models_control)
 } else {
@@
     set_names(deps) %T>%
-    saveRDS(fnames$models_control) -> models_control
+    saveRDS(io$models_control) -> models_control
 }

### 2021-08-14 manuscript/preprocessing.py

@@ -1,0 +1,320 @@
+"""
+PREPROCESSING FUNCTIONS
+
+Created 2021 by Alexander Enge (alexander.enge@hu-berlin.de)
+
+Contains one big function and some smaller helper functions to preprocess the EEG data
+for a single participant. Using the MNE-Python module and friends, it reads the raw EEG
+and behavioral data and extracts (a) the EEG epochs around the presentation of each
+unfamiliar object (b) the single trial mean ERP amplitudes at certain regions of
+interest, (c) averaged evoked potentials from at each electrode, and (d) single trial
+EEG power at a pre-specified range of frequencies.
+
+"""
+
+from os import makedirs
+
+import mne
+import numpy as np
+import pandas as pd
+from mne.channels import combine_channels, make_standard_montage
+from mne.epochs import Epochs
+from mne.io import read_raw_brainvision
+from mne.preprocessing import ICA
+from mne.time_frequency import tfr_morlet
+from mne.time_frequency.tfr import EpochsTFR
+
+
+def preprocess(
+    fname_vhdr=None,
+    fname_log=None,
+    subject_id=None,
+    output_dir=None,
+    resample_sfreq=250,
+    eog_names=["HEOG", "VEOG"],
+    eog_anodes=["F9", "Auge_u"],
+    eog_cathodes=["F10", "Fp1"],
+    montage_kind="easycap-M1",
+    ica_components=15,
+    ica_method="fastica",
+    random_seed=None,
+    hipass=0.1,
+    lowpass=30,
+    event_id=None,
+    tmin=-0.5,
+    tmax=1.489,
+    baseline=(-0.2, 0),
+    erp_components=None,
+    reject={"eeg": 200e-6},
+    average_by=None,
+    tfr_baseline=None,
+    tfr_equalize=False,
+    condition_col=None,
+    item_col=None,
+    drop_conditions=[],
+    tfr_freqs=None,
+    tfr_cycles=None,
+    tfr_crop=(-0.2, 0.8),
+):
+    """
+    Computes epochs, evoked potentials, and single trial power from a raw EEG data set.
+    """
+
+    # Create output directory if it doesn't exist
+    makedirs(output_dir, exist_ok=True)
+
+    # Read raw EEG data
+    raw = read_raw_brainvision(fname_vhdr, preload=True)
+
+    # Downsample
+    raw = raw.resample(resample_sfreq)
+
+    # Create virtual EOG channels
+    raw = mne.set_bipolar_reference(
+        raw,
+        anode=eog_anodes,
[…]

### 2021-08-25 manuscript/manuscript.Rmd
Add TFR analysis and plot

@@
 documentclass     : "apa7"
-classoption       : "man"
+classoption       : "man,donotrepeattitle"
 fontsize          : "10pt"
@@
 library(here)
+library(jsonlite)
 library(knitr)
@@
 # Re-run preprocessing and/or model fitting?
-run <- list(preprocessing = TRUE, model_fitting = TRUE)
+run <- list(
+  preprocessing = FALSE,
+  model_fitting = FALSE,
+  time_frequency = FALSE
+)
 
@@
   model_brm_prior = "results/model_brm_prior.RDS",
-  models_control = "results/models_control.RDS"
+  models_control = "results/models_control.RDS",
+  tfr_stats = "results/tfr_stats.json",
+  tfr_grand_ave = "results/tfr_grand_ave.csv"
 )
@@
 
-```{r, fig3, eval=FALSE, include=TRUE}
-# Read grand averages of evoked power
-ave_tfr_flat <- read_csv(io$ave_tfr_flat, col_types = cols(), progress = FALSE)
-ave_tfr_diff <- read_csv(io$ave_tfr_diff, col_types = cols(), progress = FALSE)
-
-# Scaling of power in all plots
-limits_power <- c(0, 0.5)
-
-# Time-frequency of interest based on visual inspect
-tfoi <- list(tmin = 150, tmax = 350, fmin = 14, fmax = 24) # Beta or
-tfoi <- list(tmin = 200, tmax = 400, fmin = 34, fmax = 48) # Gamma
-
-# Standard text format
-standard_text <- element_text(size = 10, color = "black", family = "Helvetica")
-
-plot_tfr_raster <- function(ave_tfr, limits, tmin, tmax, fmin, fmax, label) {
-  # Average across electrodes
-  ave_tfr %>%
-    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
-    group_by(part, time, freq) %>%
-    summarise(power = mean(power), .groups = "drop") %>%
-    # Create one raster plot per part
-    group_by(part) %>%
-    group_map(function(data_part, part) {
-      ggplot(data_part, aes(x = time, y = freq, fill = power)) +
-        geom_raster() +
-        scale_fill_viridis_c(
-          limits = limits,
-          labels = function(x) x * 100,
-          guide = guide_colorbar(
-            title = "Power (% change\nfrom baseline)",
-            title.position = "left",
-            title.theme = element_text(size = 10, color = "black", angle = 90, lineheight = 1),
-            title.hjust = 0.5,
-            label.theme = element_text(size = 10, color = "black"),
-            barheight = unit(4, "cm"),
-            ticks = FALSE,
-            direction = "vertical"
-          ),
-          oob = squish
-        ) +
-        scale_x_continuous(breaks = seq(-100, 700, 200)) +
-        coord_cartesian(expand = FALSE) +
-        annotate("rect", xmin = tmin, xmax = tmax, ymin = fmin + 1, ymax = fmax + 1, color = "white", fill = NA, linetype = "dotted") +
-        annotate("segment", x = 0, xend = 0, y = -Inf, yend = Inf, color = "white", linetype = "dotted") +
-        labs(x = "Time (ms)", y = "") +
-        theme_minimal() +
-        theme(
-          legend.position = "none",
-          axis.title = standard_text,
-          axis.text = standard_text
-        )
-    }) -> plotlist
-  # Add label and axis title to the first plot
-  plotlist[[1]] <- plotlist[[1]] + annotate(
-    "text",
-    x = -100,
-    y = 27,
-    label = label,
-    size = 10 / .pt,
-    angle = 90,
-    family = "Helvetica",
-    color = "white",
-    lineheight = 0.9
-  ) +
-    ylab("Frequency (ms)")
-  # Extract legend for another subplot
-  current_legend <<- get_legend(plotlist[[1]] + theme(legend.position = "right"))
-  plot_grid(plotlist = plotlist, nrow = 1)
-}
-
-plot_tfr_topo <- function(ave_tfr, limits, tmin, tmax, fmin, fmax, legend) {
-  # Average across times and frequencies of interest
-  ave_tfr_diff %>%
-    # Select time window and frequencies of interest
-    filter(time >= tmin & time <= tmax & freq >= fmin & freq <= fmax) %>%
-    # Convert to long format
-    pivot_longer(-c(part, time, freq), names_to = "electrode", values_to = "power") %>%
-    # Create one topoplot per part
-    group_by(part) %>%
-    group_map(function(data_part, part) {
-      data_part %>%
-        group_by(electrode) %>%
-        summarise(power = mean(power), .groups = "drop") %>%
-        inner_join(montage, by = "electrode") %>%
-        eegUtils::topoplot(
-          limits = limits,
-          palette = "viridis",
-          contour = FALSE,
-          quantity = "power",
-          scaling = 0.5
-        ) +
-        theme(legend.position = "none", )
-    }) -> plotlist
-  # plotlist <- c(plotlist, list(legend))
-  plot_grid(
-    NULL,
-    plotlist[[1]],
-    NULL,
-    plotlist[[2]],
-    NULL,
-    plotlist[[3]],
-    nrow = 1,
-    rel_widths = c(2, 7, 0, 7, 1, 7)
-  )
-}
-
-# Bring it all together
-plot_grid(
-  plot_headings(spacing = c(1, 7, 1, 7, 1, 7)),
-  do.call(
-    plot_tfr_raster, c(tfoi, list(
-      ave_tfr = ave_tfr_flat,
-      limits = limits_power,
-      label = "All channels,\nall conditions"
-    ))
-  ),
-  do.call(
-    plot_tfr_raster, c(tfoi, list(
-      ave_tfr = ave_tfr_diff,
-      limits = limits_power,
-      label = "All channels,\n\u0394 (informed - naive)"
-    ))
-  ),
-  do.call(
-    plot_tfr_topo, c(tfoi, list(
-      ave_tfr = ave_tfr_diff,
-      limits = limits_power,
-      legend = current_legend
-    ))
-  ),
-  nrow = 4,
-  rel_heights = c(1, 5, 5, 5),
-  labels = c("", "A", "B", "C"),
-  label_y = c(1, 1.16, 1.1, 1),
-  label_fontfamily = "Helvetica"
-) +
-  draw_plot(current_legend, x = -0.42, y = -0.34) +
-  annotate_line(0.344, 0.344, -Inf, Inf) +
-  annotate_line(0.676, 0.676, -Inf, Inf) +
-  ggsave("data/processed/tfr.pdf", width = unit(10, "cm"), height = unit(7, "cm"), device = cairo_pdf)
-```
-
 ## Control Analysis
@@
 As before, there semantically informed perception led to a reliable increase in the N170 component and a reliable decrease in the N400 component (see Table \@ref(tab:tab2)).
+
+## Time-frequency analysis
+
+```{python, tfr, eval=run$time_frequency}
+import numpy as np
+import pandas as pd
+from mne import read_epochs
+from mne.channels import find_ch_adjacency
+from mne.stats import combine_adjacency, permutation_cluster_1samp_test
+from scipy import sparse
+
+# Read evoked power for all subjects
+fnames = [f"data/preprocessed/{sid}_tfr-ave.csv" for sid in r.subject_id]
+tfrs = [pd.read_csv(fname) for fname in fnames]
+tfrs = pd.concat(tfrs)
+
+# Get electrode names
+electrodes = r.montage["electrode"].tolist()
+
+# Define non-channel columns to sort by
+idx_cols = ["condition", "subject_id", "time", "freq"]
+
+# Prepare empty lists to store outputs of permutation tests
+t_obs = []
+clusters = []
+p_values = []
+h0_max = []
+
+# Loop over parts
+parts = ["I", "II", "III"]
+for part in parts:
+
+    # Get data for the current part
+    df = tfrs[tfrs["part"] == part]
+    df = df.sort_values(idx_cols)
+
+    # Extract TFR data per condition
+    dat_informed = df.loc[df["condition"] == "Informed", electrodes].values
+    dat_naive = df.loc[df["condition"] == "Naive", electrodes].values
+    dat_diff = dat_informed - dat_naive  # Shape (subs x times x freqs) x elecs
+
+    # Reshape to X matrix for permutation test
+    n_subjects = len(df["subject_id"].unique())
+    n_times = len(df["time"].unique())
+    n_freqs = len(df["freq"].unique())
+    X = dat_diff.reshape(n_subjects, n_times, n_freqs, -1)
+
+    # # Plot the data matrix, averaged across participants and channels
+    # import matplotlib.pyplot as plt
+    # plt.imshow(X.mean(axis=(0, 3)).T, aspect="auto", vmin=-0.5, vmax=0.5, origin='lower'); plt.show()
+
+    # Define adjacency matrix for frequencies
+    adjacency_freq = sparse.csr_matrix(np.ones((n_freqs, n_freqs)))
+
+    # Define adjacency matrix for channels based on channel positions
+    example_epochs = read_epochs("data/preprocessed/sub-01_epo.fif", preload=False)
+    adjacency_chan, ch_names = find_ch_adjacency(example_epochs.info, ch_type="eeg")
+
+    # Combine adjacency matrices for frequencies and channels
+    adjacency = combine_adjacency(adjacency_freq, adjacency_chan)
+
+    # # Plot the combined adjacency matrix
+    # plt.imshow(adjacency.toarray(), origin='lower', interpolation='nearest'); plt.show()
+
+    # Run permutation test and save results
+    cluster_stats = permutation_cluster_1samp_test(
+        X, adjacency=adjacency, n_permutations=1000
+    )
+
+    # Store outputs
+    t_obs.append(cluster_stats[0])
+    clusters.append(cluster_stats[1])
+    p_values.append(cluster_stats[2])
+    h0_max.append(cluster_stats[3])
+
+# Gather outputs in DataFrame and save
+cluster_stats_df = pd.DataFrame(
+    {
+        "part": parts,
+        "t_obs": t_obs,
+        "clusters": clusters,
+        "p_values": p_values,
+        "h0_max": h0_max,
+    }
+)
+cluster_stats_df.to_json(r.io["tfr_stats"])
+
+# Export averaged data for plotting
+ave_cols = ["part", "condition", "time", "freq"]
+tfrs_plotting = tfrs.groupby(ave_cols, as_index=False).mean()  # Across subjects
+tfrs_plotting["power"] = tfrs_plotting[electrodes].mean(axis=1)  # Across channels
+tfrs_plotting = tfrs_plotting.drop(electrodes, axis=1)
+tfrs_plotting.to_csv(r.io["tfr_grand_ave"], index=False)
+```
+
+```{r, fig2, include=TRUE, fig.height=4, fig.cap="(ref:figure-2-caption)"}
+# Load permutation test results
+jsonlite::read_json(io$tfr_stats) %>%
+  as_tibble() -> tfr_stats
+
+# Get minimum cluster p value per part
+tfr_stats$p_values %>%
+  map(as.numeric) %>%
+  map(min) %>%
+  set_names(c("I", "II", "III")) -> tfr_min_ps
+
+# Plot time-frequency results per part and condition
+read_csv(io$tfr_grand_ave, col_types = cols(), progress = FALSE) %>%
+  plot_fig2()
+```
+
+(ref:figure-2-caption) Looks great!
 

### 2021-08-25 manuscript/plots_tables.R

@@ -262,7 +262,7 @@ plot_fig1 <- function(erp_components, evokeds, trials, models) {
 
   # Combine evrything
   plot_grid(fig1a, fig1b, nrow = 2, labels = "AUTO", label_fontfamily = "Helvetica", label_y = c(1, 1.03)) +
-    
+
     # Add some lines to separate the three parts
     annotate("segment", x = 0.327, xend = 0.327, y = -Inf, yend = 0.48) +
     annotate("segment", x = 0.667, xend = 0.667, y = -Inf, yend = 0.48) +
@@ -270,10 +270,51 @@ plot_fig1 <- function(erp_components, evokeds, trials, models) {
     annotate("segment", x = 0.667, xend = 0.728, y = 0.48, yend = 0.55) +
     annotate("segment", x = 0.272, xend = 0.272, y = 0.55, yend = Inf) +
     annotate("segment", x = 0.728, xend = 0.728, y = 0.55, yend = Inf) +
-    
+
     # Add legend and colorbar
     draw_plot(leg, x = 0.73, y = 0.82, width = 0.2, height = 0.2) +
     draw_plot(cbar, x = 0.85, y = 0.82, width = 0.2, height = 0.2)
+}
+
+# Function to create Figure ""
+plot_fig2 <- function(tfr_grand_ave) {
+
+  # Create new labels for parts and conditions
+  part_levels <- c("I", "II", "III")
+  part_labels <- c("Pre-insight part", "Insight part", "Post-insight part")
+  cond_levels <- c("Informed", "Naive")
+  cond_labels <- c("Informed condition", "Naive condition")
+  tfr_grand_ave %>%
+    mutate(
+      part = factor(part, levels = part_levels, labels = part_labels),
+      condition = factor(condition, levels = cond_levels, labels = cond_labels)
+    ) %>%
+    # Plot
+    ggplot(aes(x = time, y = freq, fill = power)) +
+    facet_grid(vars(condition), vars(part)) +
+    geom_raster() +
+    scale_x_continuous(breaks = seq(-200, 600, 200)) +
+    scale_y_continuous(breaks = c(4, seq(10, 50, 10))) +
+    scale_fill_viridis_c(limits = c(-1, 3)) +
+    coord_cartesian(expand = FALSE) +
+    labs(x = "Time (ms)", y = "Frequency (Hz)") +
+    guides(
+      fill = guide_colorbar(
+        title.vjust = 4,
+        title = "Power\n(% over\nbaseline)",
[…]

### 2021-08-25 manuscript/manuscript.Rmd
Add TFR text and caption

@@
   model_fitting = FALSE,
-  time_frequency = FALSE
+  time_frequency = TRUE
 )
@@
 
-  # Combine single trial data for all subjects
+  # Combine single-trial data for all subjects
   dir.create("results", showWarnings = FALSE)
@@
 
-# Read single trial data for all subjects
+# Read single-trial data for all subjects
 str_c("data/preprocessed/", subject_id, "_trials.csv") %>%
@@
 
-(ref:figure-1-caption) Procedure and results of Experiment 1.
+(ref:figure-1-caption) Experimental procedure and ERP results.
 (A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
@@
 
-The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @fromer2018].
+The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single-trial level using linear mixed-effects regression models [@baayen2008; @fromer2018].
 Compared to traditional by-participant or by-item analyses of variance, these models allow tighter control over the false positive rate because they simultaneously account for by-participant and by-item non-independencies in the data [@burki2018; @judd2012].
@@
 
-The materials, single trial preprocessed data, and code for data analysis are openly available at <https://osf.io/uksbc/>.
+The materials, single-trial preprocessed data, and code for data analysis are openly available at <https://osf.io/uksbc/>.
+
+## Time-frequency analysis
+
+Semantically informed perception may manifest itself not only in changes in evoked activity (as captured by the ERP analysis), but also in induced activity.
+We therefore carried out an exploratory time-frequency analysis.
+We first created new epochs from the ICA-corrected but unfiltered raw data.
+To avoid differences between conditions due to a difference in noise levels, we equated the number of objects per condition for each participant by discarding a random sample of objects from the semantically naive condition.
+Epochs that were marked as bad for the ERP analysis (defined as peak-to-peak amplitudes exceeding 200 µV) were also removed from the time-frequency analysis.
+The remaining epochs were then convolved with a family of 24 Morlet wavelets using the short-time Fourier transform.
+The frequency of these wavelets increased linearly from 4 Hz to 50 Hz in steps of 2 Hz and the number of cycles increased linearly from 3 cycles to 10 cycles in steps of 0.304 cycles.
+The resulting single-trial time-frequency data were converted into percent signal change by first subtracting and then dividing by the mean acitivity during the baseline period (300--100 ms before object onset).
+
+Because we did not have any a priori hypothesis for the time-frequency domain, we used cluster-based permutation tests [@maris2007] to explore the effects of semantically informed perception as compared to naive perception within each part of the experiment.
+We first created condition averages for each of the participant, part, and condition.
+Separately for each of the three parts, we then computed the by-participant differences between the semantically informed condition and the naive condition.
+The *permutation_cluster_1samp_test* function in MNE was then used to carry out the cluster-based permutation tests.
+This function (a) identified data points where the difference between conditions (one sample *t*-test) was significant *p* < .05, (b) combined neighboring data points where this was the case into observed clusters, and (c) computed a *p* value for each of these observed clusters by comparing its mass to an empirical null distribution of largest cluster masses at each of 1,000 permutations.
+Data points were defined as neighboring each other based on the Delaunay triangulation in 2D channel space (*find_ch_adjacency* function) and based on lattice adjacency matrices in the frequency and time domains (i.e., considering only directly adjacent frequency bands and time points).
+Observed clusters for which the claster mass exceeded 95% of permuted cluster masses were deemed as showing reliable effects of semantically informed perception in each part.
 
@@
 
-# Get minimum cluster p value per part
+# Get smallest cluster p value for each part
 tfr_stats$p_values %>%
-  map(as.numeric) %>%
-  map(min) %>%
+  map(function(p_values, digits = 3) {
+    p_values %>%
+      as.numeric() %>%
+      min() %>%
+      round(digits) %>%
+      format(trim = TRUE, digits = digits, nsmall = digits) -> min_p
+    min_p <- ifelse(min_p == "1.000", "1", str_replace(min_p, "0.", "."))
+  }) %>%
   set_names(c("I", "II", "III")) -> tfr_min_ps
@@
 
-(ref:figure-2-caption) Looks great!
+(ref:figure-2-caption) Time-frequency results.
+Each panel shows the time-frequency representation for a single part of the experiment (left: pre-insight part, middle: insight part, right: post-insight part) for one of the two experimental conditions (top: semantically informed, bottom: naive).
+The time-frequency data were averaged across all 48 participants and all 62 EEG channels.
+According to cluster-based permutation tests, there were no reliable differences between the two conditions in either of the three parts.
+
+Cluster-based permutation tests were run on a time-frequency representation of the ERP data for each part, obtained using Morlet wavelet convolution.
+Always comparing the semantically informed condition to the naive condition, there were no signicantly large clusters in the pre-insight part (all *p*s ≥ `r tfr_min_ps[["I"]]`), the insight part (all *p*s ≥ `r tfr_min_ps[["II"]]`), or the post-insight part (all *p*s ≥ `r tfr_min_ps[["III"]]`).
 

### 2021-08-26 manuscript/manuscript.Rmd
Fix equality signs

@@
   model_fitting = FALSE,
-  time_frequency = TRUE
+  time_frequency = FALSE
 )
@@
 = amplitude.\newline
-\* *p* < .05. \*\* *p* < .01. \*\*\* *p* < .001.
+\* *p* $<$ .05. \*\* *p* $<$ .01. \*\*\* *p* $<$ .001.
 
@@
 We then performed a model selection algorithm proposed by @matuschek2017 to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data similarly well as the complex model [determined by *p* ≥ .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the resulting formulas after model selection).
+Only if the parsimonious model explained the data similarly well as the complex model [determined by *p* $\geq$ .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the resulting formulas after model selection).
 All models were computed in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4].
@@
 The *permutation_cluster_1samp_test* function in MNE was then used to carry out the cluster-based permutation tests.
-This function (a) identified data points where the difference between conditions (one sample *t*-test) was significant *p* < .05, (b) combined neighboring data points where this was the case into observed clusters, and (c) computed a *p* value for each of these observed clusters by comparing its mass to an empirical null distribution of largest cluster masses at each of 1,000 permutations.
+This function (a) identified data points where the difference between conditions (one sample *t*-test) was significant *p* $<$ .05, (b) combined neighboring data points where this was the case into observed clusters, and (c) computed a *p* value for each of these observed clusters by comparing its mass to an empirical null distribution of largest cluster masses at each of 1,000 permutations.
 Data points were defined as neighboring each other based on the Delaunay triangulation in 2D channel space (*find_ch_adjacency* function) and based on lattice adjacency matrices in the frequency and time domains (i.e., considering only directly adjacent frequency bands and time points).
@@
 Cluster-based permutation tests were run on a time-frequency representation of the ERP data for each part, obtained using Morlet wavelet convolution.
-Always comparing the semantically informed condition to the naive condition, there were no signicantly large clusters in the pre-insight part (all *p*s ≥ `r tfr_min_ps[["I"]]`), the insight part (all *p*s ≥ `r tfr_min_ps[["II"]]`), or the post-insight part (all *p*s ≥ `r tfr_min_ps[["III"]]`).
+Always comparing the semantically informed condition to the naive condition, there were no signicantly large clusters in the pre-insight part (all *p*s $\geq$ `r tfr_min_ps[["I"]]`), the insight part (all *p*s $\geq$ `r tfr_min_ps[["II"]]`), or the post-insight part (all *p*s $\geq$ `r tfr_min_ps[["III"]]`).
 

### 2021-08-26 manuscript/manuscript.Rmd
Improve TFR reporting

@@
 The remaining epochs were then convolved with a family of 24 Morlet wavelets using the short-time Fourier transform.
-The frequency of these wavelets increased linearly from 4 Hz to 50 Hz in steps of 2 Hz and the number of cycles increased linearly from 3 cycles to 10 cycles in steps of 0.304 cycles.
-The resulting single-trial time-frequency data were converted into percent signal change by first subtracting and then dividing by the mean acitivity during the baseline period (300--100 ms before object onset).
+The frequency of these wavelets increased linearly from 4 Hz to 50 Hz in steps of 2 Hz and the number of cycles increased linearly from 3 cycles to 10 cycles in steps of 0.304 cycles [see @samaha2018].
+The resulting single-trial time-frequency data were converted into percent signal change to adjust for power-law scaling.
+This was achieved by first subtracting and then dividing by the mean acitivity during the baseline period, defined as 300--100 ms before object onset.
 
 Because we did not have any a priori hypothesis for the time-frequency domain, we used cluster-based permutation tests [@maris2007] to explore the effects of semantically informed perception as compared to naive perception within each part of the experiment.
-We first created condition averages for each of the participant, part, and condition.
+We first created condition averages for each participant, part, and condition.
 Separately for each of the three parts, we then computed the by-participant differences between the semantically informed condition and the naive condition.
-The *permutation_cluster_1samp_test* function in MNE was then used to carry out the cluster-based permutation tests.
-This function (a) identified data points where the difference between conditions (one sample *t*-test) was significant *p* $<$ .05, (b) combined neighboring data points where this was the case into observed clusters, and (c) computed a *p* value for each of these observed clusters by comparing its mass to an empirical null distribution of largest cluster masses at each of 1,000 permutations.
-Data points were defined as neighboring each other based on the Delaunay triangulation in 2D channel space (*find_ch_adjacency* function) and based on lattice adjacency matrices in the frequency and time domains (i.e., considering only directly adjacent frequency bands and time points).
-Observed clusters for which the claster mass exceeded 95% of permuted cluster masses were deemed as showing reliable effects of semantically informed perception in each part.
+Permutation tests were then run on these differences to identify clusters across space (62 electrodes), frequencies (4–40 Hz in steps of 2 Hz), and time (restricted to 0–700 ms after obejct onset), using the *permutation_cluster_1samp_test* function in MNE.
+This function (a) identified data points where the difference between conditions (one sample *t*-test) was significant at *p* $<$ .05, (b) combined neighboring data points where this was the case into observed clusters, and (c) computed a *p* value for each of these observed clusters by comparing its mass to an empirical null distribution of largest cluster masses obtained from 1,000 random permutations.
+Data points were defined as neighboring each other based on the Delaunay triangulation in 2D channel space (function *find_ch_adjacency*) and based on lattice adjacency matrices in the frequency and time domains (i.e., considering only directly adjacent frequency bands and time points).
+Observed clusters for which the cluster mass exceeded 95% of permuted cluster masses (i.e., non-parametric *p* < .05) were deemed as showing reliable effects of semantically informed perception in each part.
 
@@
 
+    # Restrict time points after object onset
+    df = df[(df["time"] >= 0) & (df["time"] <= 700)]
+
     # Extract TFR data per condition
@@
 (ref:figure-2-caption) Time-frequency results.
-Each panel shows the time-frequency representation for a single part of the experiment (left: pre-insight part, middle: insight part, right: post-insight part) for one of the two experimental conditions (top: semantically informed, bottom: naive).
-The time-frequency data were averaged across all 48 participants and all 62 EEG channels.
+Each panel shows the time-frequency representation for one of the three parts of the experiment (left: pre-insight part, middle: insight part, right: post-insight part) and one of the two experimental conditions (top: semantically informed, bottom: naive).
+For plotting, the time-frequency data were averaged across all 48 participants and all 62 EEG channels.
 According to cluster-based permutation tests, there were no reliable differences between the two conditions in either of the three parts.
@@
 Cluster-based permutation tests were run on a time-frequency representation of the ERP data for each part, obtained using Morlet wavelet convolution.
-Always comparing the semantically informed condition to the naive condition, there were no signicantly large clusters in the pre-insight part (all *p*s $\geq$ `r tfr_min_ps[["I"]]`), the insight part (all *p*s $\geq$ `r tfr_min_ps[["II"]]`), or the post-insight part (all *p*s $\geq$ `r tfr_min_ps[["III"]]`).
+Always comparing the semantically informed condition to the naive condition, there were no signicantly large clusters in the pre-insight part (all *p*s $\geq$ `r tfr_min_ps[["I"]]`), in the insight part (all *p*s $\geq$ `r tfr_min_ps[["II"]]`), or in the post-insight part (all *p*s $\geq$ `r tfr_min_ps[["III"]]`).
 

### 2021-08-26 manuscript/plots_tables.R

@@ -276,7 +276,7 @@ plot_fig1 <- function(erp_components, evokeds, trials, models) {
     draw_plot(cbar, x = 0.85, y = 0.82, width = 0.2, height = 0.2)
 }
 
-# Function to create Figure ""
+# Function to create Figure 2
 plot_fig2 <- function(tfr_grand_ave) {
 
   # Create new labels for parts and conditions
@@ -295,13 +295,13 @@ plot_fig2 <- function(tfr_grand_ave) {
     geom_raster() +
     scale_x_continuous(breaks = seq(-200, 600, 200)) +
     scale_y_continuous(breaks = c(4, seq(10, 50, 10))) +
-    scale_fill_viridis_c(limits = c(-1, 3)) +
+    scale_fill_viridis_c(limits = c(-1, 3), labels = scales::percent) +
     coord_cartesian(expand = FALSE) +
     labs(x = "Time (ms)", y = "Frequency (Hz)") +
     guides(
       fill = guide_colorbar(
-        title.vjust = 4,
-        title = "Power\n(% over\nbaseline)",
+        title.vjust = 5,
+        title = "Power\n(change\nfrom\nbaseline)",
         barheight = 6,
         ticks = FALSE
       )
@@ -312,6 +312,7 @@ plot_fig2 <- function(tfr_grand_ave) {
       axis.text = element_text(family = "Helvetica", size = 10),
       legend.title = element_text(family = "Helvetica", size = 10),
       legend.text = element_text(family = "Helvetica", size = 10),
+      panel.border = element_rect(colour = "black", fill = NA, size = 1),
       strip.background = element_rect(color = NA, fill = NA),
       strip.text = element_text(family = "Helvetica", size = 10),
     )

### 2022-01-19 manuscript/manuscript.Rmd
Move TFR analysis to methods
Add stuff

@@
 subs = r.subject_id
-fnames_ave = [f"data/preprocessed/{sub}_ave.csv" for sub in subs]
+fnames_ave = [f"data/preprocessed/{sub}_epo-ave.csv" for sub in subs]
 ave = [pd.read_csv(fname) for fname in fnames_ave]
@@
 
+```{python, tfr, eval=run$time_frequency}
+import numpy as np
+import pandas as pd
+from mne import read_epochs
+from mne.channels import find_ch_adjacency
+from mne.stats import combine_adjacency, permutation_cluster_1samp_test
+from scipy import sparse
+
+# Read evoked power for all subjects
+fnames = [f"data/preprocessed/{sid}_tfr-ave.csv" for sid in r.subject_id]
+tfrs = [pd.read_csv(fname) for fname in fnames]
+tfrs = pd.concat(tfrs)
+
+# Get electrode names
+electrodes = r.montage["electrode"].tolist()
+
+# Define non-channel columns to sort by
+idx_cols = ["condition", "subject_id", "time", "freq"]
+
+# Prepare empty lists to store outputs of permutation tests
+t_obs = []
+clusters = []
+p_values = []
+h0_max = []
+
+# Loop over parts
+parts = ["I", "II", "III"]
+for part in parts:
+
+    # Get data for the current part
+    df = tfrs[tfrs["part"] == part]
+    df = df.sort_values(idx_cols)
+
+    # Restrict time points after object onset
+    df = df[(df["time"] >= 0) & (df["time"] <= 700)]
+
+    # Extract TFR data per condition
+    dat_informed = df.loc[df["condition"] == "Informed", electrodes].values
+    dat_naive = df.loc[df["condition"] == "Naive", electrodes].values
+    dat_diff = dat_informed - dat_naive  # Shape (subs x times x freqs) x elecs
+
+    # Reshape to X matrix for permutation test
+    n_subjects = len(df["subject_id"].unique())
+    n_times = len(df["time"].unique())
+    n_freqs = len(df["freq"].unique())
+    X = dat_diff.reshape(n_subjects, n_times, n_freqs, -1)
+
+    # # Plot the data matrix, averaged across participants and channels
+    # import matplotlib.pyplot as plt
+    # plt.imshow(X.mean(axis=(0, 3)).T, aspect="auto", vmin=-0.5, vmax=0.5, origin='lower'); plt.show()
+
+    # Define adjacency matrix for frequencies
+    adjacency_freq = sparse.csr_matrix(np.ones((n_freqs, n_freqs)))
+
+    # Define adjacency matrix for channels based on channel positions
+    example_epochs = read_epochs("data/preprocessed/sub-01_epo.fif", preload=False)
+    adjacency_chan, ch_names = find_ch_adjacency(example_epochs.info, ch_type="eeg")
+
+    # Combine adjacency matrices for frequencies and channels
+    adjacency = combine_adjacency(adjacency_freq, adjacency_chan)
+
+    # # Plot the combined adjacency matrix
+    # plt.imshow(adjacency.toarray(), origin='lower', interpolation='nearest'); plt.show()
+
+    # Run permutation test and save results
+    cluster_stats = permutation_cluster_1samp_test(
+        X, adjacency=adjacency, n_permutations=1000
+    )
+
+    # Store outputs
+    t_obs.append(cluster_stats[0])
+    clusters.append(cluster_stats[1])
+    p_values.append(cluster_stats[2])
+    h0_max.append(cluster_stats[3])
+
+# Gather outputs in DataFrame and save
+cluster_stats_df = pd.DataFrame(
+    {
+        "part": parts,
+        "t_obs": t_obs,
+        "clusters": clusters,
+        "p_values": p_values,
+        "h0_max": h0_max,
+    }
+)
+cluster_stats_df.to_json(r.io["tfr_stats"])
+
+# Export averaged data for plotting
+ave_cols = ["part", "condition", "time", "freq"]
+tfrs_plotting = tfrs.groupby(ave_cols, as_index=False).mean()  # Across subjects
+tfrs_plotting["power"] = tfrs_plotting[electrodes].mean(axis=1)  # Across channels
+tfrs_plotting = tfrs_plotting.drop(electrodes, axis=1)
+tfrs_plotting.to_csv(r.io["tfr_grand_ave"], index=False)
+```
+
 Because we did not have any a priori hypothesis for the time-frequency domain, we used cluster-based permutation tests [@maris2007] to explore the effects of semantically informed perception as compared to naive perception within each part of the experiment.
@@
 ## Time-frequency analysis
-
-```{python, tfr, eval=run$time_frequency}
-import numpy as np
-import pandas as pd
-from mne import read_epochs
-from mne.channels import find_ch_adjacency
-from mne.stats import combine_adjacency, permutation_cluster_1samp_test
-from scipy import sparse
-
-# Read evoked power for all subjects
-fnames = [f"data/preprocessed/{sid}_tfr-ave.csv" for sid in r.subject_id]
-tfrs = [pd.read_csv(fname) for fname in fnames]
-tfrs = pd.concat(tfrs)
-
-# Get electrode names
-electrodes = r.montage["electrode"].tolist()
-
-# Define non-channel columns to sort by
-idx_cols = ["condition", "subject_id", "time", "freq"]
-
-# Prepare empty lists to store outputs of permutation tests
-t_obs = []
-clusters = []
-p_values = []
-h0_max = []
-
-# Loop over parts
-parts = ["I", "II", "III"]
-for part in parts:
-
-    # Get data for the current part
-    df = tfrs[tfrs["part"] == part]
-    df = df.sort_values(idx_cols)
-
-    # Restrict time points after object onset
-    df = df[(df["time"] >= 0) & (df["time"] <= 700)]
-
-    # Extract TFR data per condition
-    dat_informed = df.loc[df["condition"] == "Informed", electrodes].values
-    dat_naive = df.loc[df["condition"] == "Naive", electrodes].values
-    dat_diff = dat_informed - dat_naive  # Shape (subs x times x freqs) x elecs
-
-    # Reshape to X matrix for permutation test
-    n_subjects = len(df["subject_id"].unique())
-    n_times = len(df["time"].unique())
-    n_freqs = len(df["freq"].unique())
-    X = dat_diff.reshape(n_subjects, n_times, n_freqs, -1)
-
-    # # Plot the data matrix, averaged across participants and channels
-    # import matplotlib.pyplot as plt
-    # plt.imshow(X.mean(axis=(0, 3)).T, aspect="auto", vmin=-0.5, vmax=0.5, origin='lower'); plt.show()
-
-    # Define adjacency matrix for frequencies
-    adjacency_freq = sparse.csr_matrix(np.ones((n_freqs, n_freqs)))
-
-    # Define adjacency matrix for channels based on channel positions
-    example_epochs = read_epochs("data/preprocessed/sub-01_epo.fif", preload=False)
-    adjacency_chan, ch_names = find_ch_adjacency(example_epochs.info, ch_type="eeg")
-
-    # Combine adjacency matrices for frequencies and channels
-    adjacency = combine_adjacency(adjacency_freq, adjacency_chan)
-
-    # # Plot the combined adjacency matrix
-    # plt.imshow(adjacency.toarray(), origin='lower', interpolation='nearest'); plt.show()
-
-    # Run permutation test and save results
-    cluster_stats = permutation_cluster_1samp_test(
-        X, adjacency=adjacency, n_permutations=1000
-    )
-
-    # Store outputs
-    t_obs.append(cluster_stats[0])
-    clusters.append(cluster_stats[1])
-    p_values.append(cluster_stats[2])
-    h0_max.append(cluster_stats[3])
-
-# Gather outputs in DataFrame and save
-cluster_stats_df = pd.DataFrame(
-    {
-        "part": parts,
-        "t_obs": t_obs,
-        "clusters": clusters,
-        "p_values": p_values,
-        "h0_max": h0_max,
-    }
-)
-cluster_stats_df.to_json(r.io["tfr_stats"])
-
-# Export averaged data for plotting
-ave_cols = ["part", "condition", "time", "freq"]
-tfrs_plotting = tfrs.groupby(ave_cols, as_index=False).mean()  # Across subjects
-tfrs_plotting["power"] = tfrs_plotting[electrodes].mean(axis=1)  # Across channels
-tfrs_plotting = tfrs_plotting.drop(electrodes, axis=1)
-tfrs_plotting.to_csv(r.io["tfr_grand_ave"], index=False)
-```
 

### 2022-01-19 analysis/manuscript_files/functions_plots_tables.R

@@ -1,457 +1,0 @@
-####################################################################################################
-## FUNCTIONS TO CREATE PLOTS AND TABLES ##
-####################################################################################################
-
-# Function to plot the trial structure
-plot_trials <- function(){
-  suppressMessages(require(magick))
-  color_informed <- viridisLite::viridis(1, begin = 0.1)
-  color_naive <- viridisLite::viridis(1, begin = 0.5)
-  ggplot() +
-    coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
-    ## PART II ##
-    # Title
-    annotate("text", x = 0, y = 97.2, label = "Insight part", size = 14 / .pt, family = "Helvetica", fontface = "bold") +
-    # Arrow
-    annotate("segment", x = -30, xend = 24, y = 79, yend = 85, arrow = arrow(length = unit(0.1, "inches"))) +
-    # Squares
-    annotate("rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75, color = "black", fill = "white") +
-    annotate("rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65, color = color_informed, fill = "white") +
-    annotate("rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89, color = color_naive, fill = "white") +
-    annotate("rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79, color = "black", fill = "white") +
-    annotate("rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81, color = "black", fill = "white") +
-    annotate("text", x = -27, y = 65.3, label = "+", size = 20 / .pt, family = "Helvetica") +
-    annotate("text", x = -9, y = 55, label = "potatoes\nmashing", size = 10 / .pt, family = "Helvetica", color = color_informed) +
-    annotate("text", x = -9, y = 79, label = "message\nsignaling", size = 10 / .pt, family = "Helvetica", color = color_naive) +
-    annotate("text", x = 9, y = 67, label = "*", size = 30 / .pt, family = "Helvetica") +
-    draw_image("analysis/manuscript_files/potato_masher.png", x = 18, y = 62, width = 18, height = 18) +
-    # Timings
-    annotate("text", x = -9, y = 67.3, label = "or", size = 10 / .pt, family = "Helvetica") +
[…]

### 2022-01-19 analysis/preprocessing.py

@@ -1,243 +1,0 @@
-from glob import glob
-from os import makedirs, removedirs
-
-import numpy as np
-import pandas as pd
-from mne import Epochs, events_from_annotations, pick_channels, set_bipolar_reference
-from mne.channels import combine_channels, make_standard_montage
-from mne.io import read_raw_brainvision
-from mne.preprocessing import ICA
-from mne.time_frequency import tfr_morlet
-
-# fnames_vhdr = glob("../data/raw/eeg/exp*/*.vhdr")
-# fnames_log = glob("../data/raw/rt/exp*/*.txt")
-
-# tfr_freqs = np.arange(4, 51, step=2)
-# tfr_cycles = np.linspace(3, 10, num=len(tfr_freqs))
-
-# event_id = {"match": 221, "nonmatch": 222}
-# condition_cols = ["part", "condition"]
-
-# subject_id = "sub-02"
-# output_basedir = "../data/"
-
-# erp_components = pd.DataFrame(
-#     {
-#         "name": ["P1", "N170", "N400"],
-#         "tmin": [0.1, 0.15, 0.4],
-#         "tmax": [0.15, 0.2, 0.7],
-#         "roi": [
-#             ["PO3", "PO4", "POz", "O1", "O2", "Oz"],
-#             ["P7", "P8", "PO7", "PO8", "PO9", "PO10"],
-#             ["C1", "C2", "Cz", "CP1", "CP2", "CPz"],
-#         ],
-#     }
-# )
-
-
-def preprocess(
-    fname_vhdr=None,
-    fname_log=None,
-    subject_id=None,
-    output_basedir=None,
-    eog_names=["HEOG", "VEOG"],
-    eog_anodes=["F9", "Auge_u"],
-    eog_cathodes=["F10", "Fp1"],
-    montage_kind="easycap-M1",
-    ica_components=15,
-    ica_method="fastica",
-    ica_seed=1234,
-    hipass=0.1,
-    lowpass=30,
-    event_id=None,
-    tmin=-0.5,
-    tmax=1.489,
-    baseline=(-0.2, 0),
-    reject={"eeg": 200e-6},
-    erp_components=None,
-    condition_cols=["part", "condition"],
-    tfr_freqs=None,
-    tfr_cycles=None,
-    tfr_sfreq_downsampled=250,
-    tfr_crop=(-0.2, 0.8),
-):
-    """
-    Computes epochs, evoked potentials, and single trial power from a raw EEG data set.
-    """
-
[…]

### 2022-01-19 analysis/sourceloc.py

@@ -1,87 +1,0 @@
-import os.path as op
-import mne
-import numpy as np
-from mne.minimum_norm import make_inverse_operator, apply_inverse
-from pyvistaqt import BackgroundPlotter
-import matplotlib.pyplot as plt
-
-# Download fsaverage files
-fs_dir = mne.datasets.fetch_fsaverage(verbose=True)
-subjects_dir = op.dirname(fs_dir)
-
-# The files live in:
-subject = 'fsaverage'
-trans = 'fsaverage'  # MNE has a built-in fsaverage transformation
-src = op.join(fs_dir, 'bem', 'fsaverage-ico-5-src.fif')
-bem = op.join(fs_dir, 'bem', 'fsaverage-5120-5120-5120-bem-sol.fif')
-
-# Load and process EEG data
-vhdr_fname = "../data/eeg/exp1/Vp0004.vhdr"
-raw = mne.io.read_raw_brainvision(vhdr_fname, scale=1e6, preload=True)
-raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
-raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
-raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
-montage = mne.channels.make_standard_montage("easycap-M1")
-raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
-raw.set_montage(montage=montage)
-raw.set_eeg_reference("average", projection=True)
-
-# # Check that the locations of EEG electrodes is correct with respect to MRI
-# mne.viz.plot_alignment(
-#     raw.info, src=src, eeg=['original', 'projected'], trans=trans,
-#     show_axes=True, mri_fiducials=True, dig='fiducials')
-
-fwd = mne.make_forward_solution(raw.info, trans=trans, src=src, bem=bem, meg=False, eeg=True, n_jobs=1)
-print(fwd)
-
-# Use fwd to compute the sensitivity map for illustration purposes
-eeg_map = mne.sensitivity_map(fwd, ch_type='eeg', mode='fixed')
-brain = eeg_map.plot(time_label='EEG sensitivity', subjects_dir=subjects_dir,clim=dict(lims=[5, 50, 100]))
-
-# Read epochs
-epochs = mne.read_epochs("export/exp1-epo.fif")
[…]

### 2022-01-19 analysis/tfr.R

@@ -1,18 +1,0 @@
-library(reticulate)
-library(tidyverse)
-library(magrittr)
-library(eegUtils)
-
-read_csv("data/processed/aha-montage.csv", col_types = cols()) %>%
-  mutate(amplitude = py$dat_diff) %>%
-  topoplot(limits = c(-10, 10), palette = "viridis", contour = FALSE)
-
-py$avgs["III"][[1]] %>%
-  t() %>%
-  as_tibble() %>%
-  mutate(time = py$tfr$times) %>%
-  pivot_longer(-time, names_to = "frequency", values_to = "power_perc") %>%
-  mutate(frequency = factor(frequency, levels = unique(frequency), labels = py$freqs)) %>%
-  ggplot(aes(x = time, y = frequency, fill = power_perc)) +
-  geom_raster() +
-  scale_fill_viridis_c(limits = c(-1, 1), oob = scales::squish)

### 2022-01-19 analysis/tfr.py

@@ -1,175 +1,0 @@
-# Load modules
-from mne import read_epochs, grand_average
-from mne.channels import combine_channels, find_ch_adjacency
-from mne.stats import spatio_temporal_cluster_test
-from mne.time_frequency import read_tfrs, tfr_morlet
-import numpy as np
-import matplotlib.pyplot as plt
-
-# Define frequencies and number of cycles
-freqs = np.arange(6, 51, step=2)
-# n_cycles = np.linspace(3, 10, num=len(freqs))
-n_cycles = freqs / 2.
-
-# Load epochs
-epochs = read_epochs("data/processed/aha-unf-epo.fif")
-
-# # Remove irrelevant conditions
-# epochs = epochs["condition == ['Informed', 'Naive']"]
-
-# Downsample and crop
-epochs.resample(sfreq=250)
-epochs.crop(tmin=-0.25, tmax=0.85)
-
-# Define custom function to compute single trial power for eqch frequency
-def compute_power(epochs, freq, n_cycles):
-    tfr = tfr_morlet(
-        epochs,
-        freq,
-        n_cycles,
-        use_fft=True,
-        return_itc=False,
-        average=False
-    )
-    tfr.apply_baseline(baseline=(None, 0), mode="percent")
-    return(np.float32(tfr.data))
-
-# Apply to our epochs
-tfr = [
-    compute_power(epochs, [freq], n_cycles) for freq, n_cycles in zip(freqs, n_cycles)
-]
-
-# Combine into one big array
-tfr = np.array(tfr, dtype="float32")
-
-# Compute single trial power
-tfr = tfr_morlet(epochs, freqs, n_cycles, use_fft=True, return_itc=False, average=False)
-del epochs
-
-# Reduce memory by changing the data type
-tfr.data = np.float32(tfr.data)
-
-# Backup
-tfr.save("data/processed/aha-tfr.h5")
-
-# Read preprocessed power
-tfr = read_tfrs("data/processed/aha-tfr.h5")[0]
-
-# Baseline correction
-tfr.apply_baseline(baseline=(None, 0), mode="percent")
-
-# Define helper function to extract averaged TFR data
-def tfr_to_array(tfr, query, axis_flatten=(0, 1)):
-    return(np.mean(tfr[query].data, axis=axis_flatten))
-
[…]

### 2022-01-19 code/sourceloc.py

@@ -1,48 +1,40 @@
-# %%
 import os.path as op
-from threading import stack_size
 
-import groupmne
-import matplotlib.pyplot as plt
 import mne
 import numpy as np
 
 # Prepare an empty dict to store the evokeds for all subjects
-evokeds_dict = {
-    "I": {"Informed": [], "Naive": [], "Difference": []},
-    "II": {"Informed": [], "Naive": [], "Difference": []},
-    "III": {"Informed": [], "Naive": [], "Difference": []},
-}
+parts = ["I", "II", "III"]
+condition_dict_empty = {"Informed": [], "Naive": [], "Combined": [], "Difference": []}
+evokeds_dict = dict(zip(parts, [condition_dict_empty] * 3))
 
 # How many subjects to include (min = 1, max = 48)
-nsubs = 48
+nsubs = 5
 
-# Read evokeds for all subjects and organize the relevant conditions in a dict
+# Read evokeds for all subjects
 subject_id = ["sub-" + "{:02d}".format(s) for s in range(1, nsubs + 1)]
-for s in subject_id:
-    evokeds = mne.read_evokeds("../data/preprocessed/" + s + "_ave.fif", verbose=False)
+for sid in subject_id:
+    evokeds = mne.read_evokeds(f"../data/preprocessed/{sid}_epo-ave.fif", verbose=False)
+
+    # Find evokeds for each part and condition
     for pt in ["I", "II", "III"]:
         for ev in evokeds:
-            #ev = ev.copy().drop_channels(["P1", "N170", "N400"])
-            if "part == '" + pt + "' & condition == 'Informed'" in ev.comment:
+            if f"part == '{pt}' & condition == 'Informed'" in ev.comment:
                 ev_informed = ev
                 evokeds_dict[pt]["Informed"].append(ev)
-            elif "part == '" + pt + "' & condition == 'Naive'" in ev.comment:
+            elif f"part == '{pt}' & condition == 'Naive'" in ev.comment:
                 ev_naive = ev
                 evokeds_dict[pt]["Naive"].append(ev)
+
+        # Compute flat average across both conditions
+        evokeds_dict[pt]["Combined"].append(
+            mne.combine_evoked([ev_informed, ev_naive], weights="nave")
+        )
 
[…]

### 2022-01-19 manuscript/dipole.py

@@ -1,0 +1,109 @@
+import os.path as op
+
+import numpy as np
+from mne import dipole, fit_dipole, make_ad_hoc_cov
+from mne.datasets import fetch_fsaverage
+from mne.evoked import combine_evoked, read_evokeds
+import matplotlib.pyplot as plt
+
+# Prepare an emparty dict to store the evokeds for all subjects
+parts = ["I", "II", "III"]
+conditions = ["Informed", "Naive", "Combined", "Difference"]
+subjects_dict = {part: {condition: [] for condition in conditions} for part in parts}
+
+# Loop over subject IDs
+n_subs = 5  # max = 48
+subject_id = ["sub-" + "{:02d}".format(s) for s in range(1, n_subs + 1)]
+for sid in subject_id:
+
+    # Read list of evokeds for the current subejct
+    evokeds = read_evokeds(f"../data/preprocessed/{sid}_epo-ave.fif", verbose=False)
+
+    # Search which evokeds belong to the current part
+    for part in parts:
+        for ev in evokeds:
+
+            # Remove non-EEG channels
+            ev = ev.pick_types(eeg=True)
+
+            # Append to the dict for the correct condition
+            if f"part == '{part}' & condition == 'Informed'" in ev.comment:
+                ev_informed = ev
+                subjects_dict[part]["Informed"].append(ev)
+            elif f"part == '{part}' & condition == 'Naive'" in ev.comment:
+                ev_naive = ev
+                subjects_dict[part]["Naive"].append(ev)
+
+        # Compute flat average across both conditions
+        ev_combined = combine_evoked([ev_informed, ev_naive], weights=[0.5, 0.5])
+        subjects_dict[part]["Combined"].append(ev_combined)
+
+        # Compute difference wave between conditions
+        ev_difference = combine_evoked([ev_informed, ev_naive], weights=[0.5, -0.5])
+        subjects_dict[part]["Difference"].append(ev_difference)
+
+# Compute group averages
+group_dict = {
+    part: {
+        condition: combine_evoked(subjects_dict[part][condition], weights="nave")
+        for condition in conditions
+    }
+    for part in parts
+}
+
+# Download standard MRI template and source/head model
+fs_dir = fetch_fsaverage(verbose=False)
+subjects_dir = op.dirname(fs_dir)
+subject = "fsaverage"
+trans = "fsaverage"  # MNE has a built-in fsaverage transformation
[…]

### 2022-01-19 manuscript/dipole_fitting.m

@@ -1,0 +1,140 @@
+% Load FieldTrip and EEGLAB
+addpath /Users/alexander/Documents/MATLAB/Toolboxes/fieldtrip
+addpath /Users/alexander/Documents/MATLAB/Toolboxes/eeglab
+ft_defaults;
+eeglab;
+
+% List preprocessed epoch files from MNE
+preprocessed_dir = '/Users/alexander/Research/aha/data/preprocessed';
+
+kinds = {'flat', 'diff'};
+n_kinds = length(kinds);
+
+% Create empty structure for storing ERPs
+erps = {};
+erps.I.flat = {};
+erps.I.diff = {};
+erps.II.flat = {};
+erps.II.diff = {};
+erps.III.flat = {};
+erps.III.diff = {};
+
+% Loop over subjects
+for ix = 1:48
+    
+    % Load epochs
+    fname_epo = sprintf('%s/sub-%02d_epo.fif', preprocessed_dir, ix);
+    hdr = ft_read_header(fname_epo);
+    dat = ft_read_data(fname_epo);
+    
+    % Convert to EEGLAB
+    EEG = fieldtrip2eeglab(hdr, dat);
+    
+    % Load standard locations for EEG channels
+    EEG = pop_select(EEG, 'channel', 1:62);
+    EEG = pop_chanedit(EEG, 'lookup', 'standard-10-5-cap385.elp');
+    
+    % Load single-trial behavioral data
+    fname_trials = sprintf('%s/sub-%02d_trials.csv', preprocessed_dir, ix);
+    trials = readtable(fname_trials);
+    
+    % Extract ERPs for each part
+    parts = {'I', 'II', 'III'};
+    n_parts = length(parts);
+    for ix_part = 1:n_parts
+        
+        % Get trial indices from behavioral data
+        curr_part = parts{ix_part};
+        is_part = strcmp(trials.part, curr_part);
+        
+        % Compute averaged ERP across all conditions
+        erp_flat = mean(EEG.data(:, :, is_part), 3);
+        erps.(curr_part).flat(end + 1) = {erp_flat};
+        
+        % Compute averaged ERP for the difference between conditions
+        is_informed = is_part & strcmp(trials.condition, 'Informed');
+        is_naive = is_part & strcmp(trials.condition, 'Naive');
+        erp_informed = mean(EEG.data(:, :, is_informed), 3);
+        erp_naive = mean(EEG.data(:, :, is_naive), 3);
[…]

### 2022-01-19 manuscript/preprocessing.py

@@ -13,6 +13,7 @@ EEG power at a pre-specified range of frequencies.
 """
 
 from os import makedirs
+from pathlib import Path
 
 import mne
 import numpy as np
@@ -122,6 +123,10 @@ def preprocess(
             roi=component["roi"],
         )
 
+    # Save epochs to output folder
+    prefix = output_dir + "/" + subject_id + "_"
+    epochs.save(prefix + "epo.fif")
+
     # Reject bad epochs
     metadata_backup = epochs.metadata  # We'll need this later for TFR
     epochs.drop_bad(reject)
@@ -130,9 +135,7 @@ def preprocess(
     good_epochs = [x for x in epochs.drop_log if not x == ("IGNORED",)]
     good_epochs = [i for i, x in enumerate(good_epochs) if x == ()]
 
-    # Save epochs and trials to output folder
-    prefix = output_dir + "/" + subject_id + "_"
-    epochs.save(prefix + "epo.fif")
+    # Save trials to output folder
     epochs.metadata.to_csv(prefix + "trials.csv", float_format="%.3f", index=False)
 
     # Compute evoked potentials
@@ -177,6 +180,15 @@ def preprocess(
     del epochs_unf, evokeds_tfr_df, tfr
 
 
+# def repair_log(fname_log):
+#     """
+#     Removes the last column from the log file since it's producing errors.
+#     """
+#     log = pd.read_csv(fname_log, delimiter="\t", usecols=range(15),
+#                       encoding="ISO-8859-1")
+#     log.to_csv(fname_log, sep="\t", index=False, encoding="ISO-8859-1")
+
+
 def read_log(fname_log=None, subject_id=None):
     """
     Extracts the relevant information from a behavioral log file into a DataFrame.
@@ -197,6 +209,13 @@ def read_log(fname_log=None, subject_id=None):
     log["part"] = pd.Categorical(log["Wdh"])
     log["part"].cat.rename_categories({211: "I", 212: "II", 213: "III"}, inplace=True)
 
+    # Recode button presses
+    # 201: "I know what this is or have a strong assumption"    -> Recode as 3
+    # 202: "I have an assumption what this is"                  -> Recode as 2
+    # 203: "I have rather no assumption what this is"           -> Recode as 1
+    # 204: "I don't know what this is and have no assumption."  -> Recode as 0
+    log["response"] = 4 - (log["Tastencode"] - 200)
+
[…]

### 2022-01-19 manuscript/rsa.py

@@ -1,0 +1,172 @@
+# %%
+import matplotlib.pyplot as plt
+import numpy as np
+from mne import read_epochs
+from scipy.stats import sem, spearmanr
+
+# %%
+# General settings
+tmin, tmax = (-0.2, 0.8)
+
+# Prepare emtpy dictionaries
+parts = ["I", "II", "III"]
+rdms_eeg = {part: [] for part in parts}
+rdms_response = {part: [] for part in parts}
+corrs_eeg_response = {part: [] for part in parts}
+
+combinations = [("I", "II"), ("I", "III"), ("II", "III")]
+corrs_eeg_parts = {combination: [] for combination in combinations}
+
+# Define helper function to correlate two RDMs
+def correlate_rdms(rdm_1, rdm_2):
+    n_items = rdm_1.shape[0]
+    ixs_lower_triangle = np.tril_indices(n_items, -1)
+    lower_triangles = [rdm[ixs_lower_triangle] for rdm in [rdm_1, rdm_2]]
+    corr = spearmanr(*lower_triangles)[0]
+    return corr
+
+
+# %%
+# Loop over subjects
+n_subjects = 48
+subject_id = ["sub-" + "{:02d}".format(n) for n in range(1, n_subjects + 1)]
+for sid in subject_id:
+
+    # Read epochs for the current subject
+    fname = f"../data/preprocessed/{sid}_epo.fif"
+    epochs_subject = read_epochs(fname, verbose=True)
+
+    # Crop to time window of interest
+    _ = epochs_subject.crop(tmin, tmax)
+
+    # Loop over epochs for each part
+    rdms_parts = {part: [] for part in parts}
+    for part in parts:
+        epochs = epochs_subject[f"part == '{part}'"]
+
+        # Compute RDM from behavioral responses
+        response = np.array(epochs.metadata["response"])
+        n_items = len(response)
+        rdm_response = np.zeros((n_items, n_items))
+        for ix_item_1 in range(n_items):
+            for ix_item_2 in range(n_items):
+                dissimilarity = response[ix_item_1] - response[ix_item_2]
+                rdm_response[ix_item_1, ix_item_2] = np.abs(dissimilarity)
+        rdms_response[part].append(rdm_response)
+
+        # Loop over timepoints in the ERP
+        times = epochs.times
+        rdms_times = []
+        corrs_times_response = []
+        for ix, time in enumerate(times):
+
[…]

### 2022-01-19 manuscript/sloc.py

@@ -1,0 +1,157 @@
+import os.path as op
+import pickle
+
+import mne
+import numpy as np
+from mne import VolSourceEstimate, compute_covariance, read_epochs
+from mne.datasets import fetch_fsaverage
+from mne.evoked import combine_evoked
+from mne.minimum_norm import apply_inverse, make_inverse_operator
+
+from preprocessing import _equalize_trial_counts
+
+# Load preprocessed epochs for all subjects
+subject_id = ["sub-" + "{:02d}".format(n) for n in range(1, 49)]
+fnames_epo = [f"../data/preprocessed/{sid}_epo.fif" for sid in subject_id]
+epochs_all_subjects = [read_epochs(fname, verbose=False) for fname in fnames_epo]
+
+# Download standard MRI template and source/head model
+fs_dir = fetch_fsaverage(verbose=False)
+subjects_dir = op.dirname(fs_dir)
+subject = "fsaverage"
+trans = "fsaverage"  # MNE has a built-in fsaverage transformation
+src = op.join(fs_dir, "bem", "fsaverage-ico-5-src.fif")
+bem = op.join(fs_dir, "bem", "fsaverage-5120-5120-5120-bem-sol.fif")
+
+# Compute standard forward solution for all subjects
+info = epochs_all_subjects[0].info  # Info object is similar for all subjects
+
+# Define common parameters for inverse solution
+method = "dSPM"
+snr = 3.0
+lambda2 = 1.0 / snr ** 2
+
+# Setup volumn source space
+mri = op.join(fs_dir, "mri", "T1.mgz")
+vol_src = mne.setup_volume_source_space(
+    subject,
+    mri=mri,
+    pos=10.0,
+    bem=bem,
+    subjects_dir=subjects_dir,
+    add_interpolator=True,
+    verbose=True,
+)
+fwd = mne.make_forward_solution(info, trans, vol_src, bem, eeg=True, mindist=5.0)
+
+# Setup empty dictionary to store the source time courses for all parts and conditions
+parts = ["I", "II", "III"]
+parts_dict = {}
+for part in parts:
+    parts_dict[part] = {}
+    for condition in ["Informed", "Naive", "Combined", "Difference"]:
+        parts_dict[part][condition] = []
+
+# Loop overs subjects
+for epochs in epochs_all_subjects:
+
+    # Exclude any non-EEG channels
+    epochs.pick_types(eeg=True)
+
+    # Pick relevant conditions and channels
[…]

### 2022-01-19 code/plots_tables.R
Clean up

@@ -1,422 +1,0 @@
-########################################################################################
-## FUNCTIONS TO CREATE PLOTS AND TABLES ##
-########################################################################################
-
-# Function to create Figure 1
-plot_fig1 <- function(erp_components, evokeds, trials, models) {
-
-  # Define colors for conditions
-  colors <- list(
-    Informed = viridisLite::viridis(1, begin = 0.1),
-    Naive = viridisLite::viridis(1, begin = 0.5)
-  )
-
-  # Base object for split violin plots (kudos to https://stackoverflow.com/a/45614547)
-  GeomSplitViolin <- ggproto(
-    "GeomSplitViolin", GeomViolin,
-    draw_group = function(self, data, ..., draw_quantiles = NULL) {
-      data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
-      grp <- data[1, "group"]
-      newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
-      newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
-      newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
-      if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
-        stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 1))
-        quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
-        aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
-        aesthetics$alpha <- rep(1, nrow(quantiles))
-        both <- cbind(quantiles, aesthetics)
-        quantile_grob <- GeomPath$draw_panel(both, ...)
-        ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
-      }
-      else {
-        ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
-      }
-    }
-  )
-
-  # Base function for split violin plots (kudos to https://stackoverflow.com/a/45614547)
[…]

### 2022-01-19 code/preprocessing.py

@@ -1,276 +1,0 @@
-"""
-PREPROCESSING FUNCTIONS
-
-Created May 2021 by Alexander Enge (alexander.enge@hu-berlin.de)
-
-Contains one big function and some smaller helper functions to preprocess the EEG data
-for a single participant. Using the MNE-Python module and friends, it reads the raw EEG
-and behavioral data and extracts (a) the EEG epochs around the presentation of each
-unfamiliar object (b) the single trial mean ERP amplitudes at certain regions of
-interest, (c) averaged evoked potentials from at each electrode, and (d) single trial
-EEG power at a pre-specified range of frequencies.
-
-"""
-
-from os import makedirs
-
-import mne
-import numpy as np
-import pandas as pd
-from mne.channels import combine_channels, make_standard_montage
-from mne.epochs import Epochs
-from mne.io import read_raw_brainvision
-from mne.preprocessing import ICA
-from mne.time_frequency import tfr_morlet
-from mne.time_frequency.tfr import EpochsTFR
-
-
-def preprocess(
-    fname_vhdr=None,
-    fname_log=None,
-    subject_id=None,
-    output_dir=None,
-    eog_names=["HEOG", "VEOG"],
-    eog_anodes=["F9", "Auge_u"],
-    eog_cathodes=["F10", "Fp1"],
-    montage_kind="easycap-M1",
-    ica_components=15,
-    ica_method="fastica",
-    ica_seed=1234,
-    hipass=0.1,
-    lowpass=30,
-    event_id=None,
-    tmin=-0.5,
-    tmax=1.489,
-    baseline=(-0.2, 0),
-    erp_components=None,
-    reject={"eeg": 200e-6},
-    average_by=None,
-    tfr_baseline=None,
-    tfr_equalize=None,
-    tfr_resample=None,
-    tfr_freqs=None,
-    tfr_cycles=None,
-    tfr_crop=(-0.2, 0.8),
-):
-    """
-    Computes epochs, evoked potentials, and single trial power from a raw EEG data set.
-    """
-
-    # Create output directory if it doesn't exist
-    makedirs(output_dir, exist_ok=True)
-
-    # Read raw EEG data
-    raw = read_raw_brainvision(fname_vhdr, preload=True)
-
-    # Create virtual EOG channels
-    raw = mne.set_bipolar_reference(
-        raw,
-        anode=eog_anodes,
-        cathode=eog_cathodes,
-        ch_name=eog_names,
-        drop_refs=False,
-    )
[…]

### 2022-01-19 code/rsa.py

@@ -1,30 +1,0 @@
-from mne import read_epochs
-import numpy as np
-import mne_rsa
-import pandas as pd
-
-epochs = read_epochs("../data/preprocessed/sub-01_epo.fif")
-
-epochs_part = epochs["part == 'II'"].pick_types(eeg=True)
-
-# # Sort items
-# item_idxs = np.array(epochs_part.metadata["item_id"])
-# dat_part = dat_part[item_idxs - 1]
-
-
-behav_file = "../data/raw/rt/exp1/VP_01_Tag1.txt"
-behav = pd.read_csv(behav_file, delimiter="\t", usecols=range(14), index_col=False)
-behav_part = behav[behav["Wdh"] == 212]
-
-response = behav_part["Tastencode"]
-
-dsm_model = mne_rsa.compute_dsm(response, metric="sqeuclidean")
-dsm_model.shape
-
-item_ids = epochs_part.metadata["item_id"]
-epochs_part.events[:, 2] = item_ids
-epochs_part.events_id = dict(zip(item_ids, item_ids))
-
-rsa = mne_rsa.rsa_epochs(epochs_part, dsm_model, spatial_radius=None)
-
-rsa.plot()

### 2022-01-19 code/sourceloc.py

@@ -1,242 +1,0 @@
-import os.path as op
-
-import mne
-import numpy as np
-
-# Prepare an empty dict to store the evokeds for all subjects
-parts = ["I", "II", "III"]
-condition_dict_empty = {"Informed": [], "Naive": [], "Combined": [], "Difference": []}
-evokeds_dict = dict(zip(parts, [condition_dict_empty] * 3))
-
-# How many subjects to include (min = 1, max = 48)
-nsubs = 5
-
-# Read evokeds for all subjects
-subject_id = ["sub-" + "{:02d}".format(s) for s in range(1, nsubs + 1)]
-for sid in subject_id:
-    evokeds = mne.read_evokeds(f"../data/preprocessed/{sid}_epo-ave.fif", verbose=False)
-
-    # Find evokeds for each part and condition
-    for pt in ["I", "II", "III"]:
-        for ev in evokeds:
-            if f"part == '{pt}' & condition == 'Informed'" in ev.comment:
-                ev_informed = ev
-                evokeds_dict[pt]["Informed"].append(ev)
-            elif f"part == '{pt}' & condition == 'Naive'" in ev.comment:
-                ev_naive = ev
-                evokeds_dict[pt]["Naive"].append(ev)
-
-        # Compute flat average across both conditions
-        evokeds_dict[pt]["Combined"].append(
-            mne.combine_evoked([ev_informed, ev_naive], weights="nave")
-        )
-
-        # Compute difference wave between conditions
-        evokeds_dict[pt]["Difference"].append(
-            mne.combine_evoked([ev_informed, ev_naive], weights=[1, -1])
-        )
-
-# Download fsaverage MRI template
-fs_dir = mne.datasets.fetch_fsaverage(verbose=False)
-subjects_dir = op.dirname(fs_dir)
-subject = "fsaverage"
-trans = "fsaverage"  # MNE has a built-in fsaverage transformation
-src = op.join(fs_dir, "bem", "fsaverage-ico-5-src.fif")
-bem = op.join(fs_dir, "bem", "fsaverage-5120-5120-5120-bem-sol.fif")
-
-# Compute standard forward solution
-fwd = mne.make_forward_solution(info, trans, src, bem, eeg=True, mindist=5.0)
-
-
-
-
-# %%
-
-# For which evokeds to compute the source time course
-part = "II"
[…]

### 2022-01-19 code/tfr.py

@@ -1,99 +1,0 @@
-import numpy as np
-import pandas as pd
-
-# Read evoked *power* for all subjects
-subject_id = ["sub-" + "{:02d}".format(sid) for sid in range(1, 49)]
-fname_evo_tfr = ["../data/preprocessed/" + sub + "_tfr-ave.csv" for sub in subject_id]
-evo_tfr = [pd.read_csv(fname) for fname in fname_evo_tfr]
-evo_tfr = pd.concat(evo_tfr)
-
-# Compute difference in power between conditions
-id_vars = ["part", "condition", "subject_id", "time", "freq"]
-electrodes = [col for col in evo_tfr.columns if (col not in id_vars)]
-evo_tfr_diff = (
-    evo_tfr.query("condition == 'Informed'")[electrodes]
-    - evo_tfr.query("condition == 'Naive'")[electrodes].values
-)
-evo_tfr_diff[id_vars] = evo_tfr.query("condition == 'Informed'")[id_vars]
-
-# Compute flat average across conditions
-id_vars.remove("condition")
-evo_tfr_flat = evo_tfr.groupby(id_vars, as_index=False).mean()
-
-# Permutation test on the difference between conditions
-import numpy as np
-from mne import read_epochs
-from mne.channels import find_ch_adjacency
-from mne.stats import permutation_cluster_1samp_test
-epochs = read_epochs("../data/preprocessed/sub-01_epo.fif", preload=False)
-adjacency, ch_names = find_ch_adjacency(epochs.info, ch_type="eeg")
-
-# # Average frequencies in the lower gamma range
-# tmp = evo_tfr_diff[evo_tfr_diff["part"] == "II"].drop(["part", "condition"], axis=1)
-# tmp = tmp[(tmp["time"] >= 200) & (tmp["time"] <= 400)]
-# tmp = tmp[(tmp["freq"] >= 34) & (tmp["freq"] <= 48)]
-# id_vars = ["subject_id", "time"]
-# tmp = tmp.groupby(id_vars, as_index=False).mean().drop("freq", axis=1)
-# tmp = tmp.set_index(["subject_id", "time"])
-
-# m, n = len(tmp.index.levels[0]), len(tmp.index.levels[1])
-# X = tmp.values.reshape(m, n, -1)
-
[…]

### 2022-01-19 manuscript/dipole.py

@@ -1,109 +1,0 @@
-import os.path as op
-
-import numpy as np
-from mne import dipole, fit_dipole, make_ad_hoc_cov
-from mne.datasets import fetch_fsaverage
-from mne.evoked import combine_evoked, read_evokeds
-import matplotlib.pyplot as plt
-
-# Prepare an emparty dict to store the evokeds for all subjects
-parts = ["I", "II", "III"]
-conditions = ["Informed", "Naive", "Combined", "Difference"]
-subjects_dict = {part: {condition: [] for condition in conditions} for part in parts}
-
-# Loop over subject IDs
-n_subs = 5  # max = 48
-subject_id = ["sub-" + "{:02d}".format(s) for s in range(1, n_subs + 1)]
-for sid in subject_id:
-
-    # Read list of evokeds for the current subejct
-    evokeds = read_evokeds(f"../data/preprocessed/{sid}_epo-ave.fif", verbose=False)
-
-    # Search which evokeds belong to the current part
-    for part in parts:
-        for ev in evokeds:
-
-            # Remove non-EEG channels
-            ev = ev.pick_types(eeg=True)
-
-            # Append to the dict for the correct condition
-            if f"part == '{part}' & condition == 'Informed'" in ev.comment:
-                ev_informed = ev
-                subjects_dict[part]["Informed"].append(ev)
-            elif f"part == '{part}' & condition == 'Naive'" in ev.comment:
-                ev_naive = ev
-                subjects_dict[part]["Naive"].append(ev)
-
-        # Compute flat average across both conditions
-        ev_combined = combine_evoked([ev_informed, ev_naive], weights=[0.5, 0.5])
-        subjects_dict[part]["Combined"].append(ev_combined)
-
-        # Compute difference wave between conditions
-        ev_difference = combine_evoked([ev_informed, ev_naive], weights=[0.5, -0.5])
-        subjects_dict[part]["Difference"].append(ev_difference)
-
-# Compute group averages
-group_dict = {
-    part: {
-        condition: combine_evoked(subjects_dict[part][condition], weights="nave")
-        for condition in conditions
-    }
-    for part in parts
-}
-
-# Download standard MRI template and source/head model
-fs_dir = fetch_fsaverage(verbose=False)
-subjects_dir = op.dirname(fs_dir)
-subject = "fsaverage"
-trans = "fsaverage"  # MNE has a built-in fsaverage transformation
[…]

### 2022-01-19 manuscript/dipole_fitting.m

@@ -1,140 +1,0 @@
-% Load FieldTrip and EEGLAB
-addpath /Users/alexander/Documents/MATLAB/Toolboxes/fieldtrip
-addpath /Users/alexander/Documents/MATLAB/Toolboxes/eeglab
-ft_defaults;
-eeglab;
-
-% List preprocessed epoch files from MNE
-preprocessed_dir = '/Users/alexander/Research/aha/data/preprocessed';
-
-kinds = {'flat', 'diff'};
-n_kinds = length(kinds);
-
-% Create empty structure for storing ERPs
-erps = {};
-erps.I.flat = {};
-erps.I.diff = {};
-erps.II.flat = {};
-erps.II.diff = {};
-erps.III.flat = {};
-erps.III.diff = {};
-
-% Loop over subjects
-for ix = 1:48
-    
-    % Load epochs
-    fname_epo = sprintf('%s/sub-%02d_epo.fif', preprocessed_dir, ix);
-    hdr = ft_read_header(fname_epo);
-    dat = ft_read_data(fname_epo);
-    
-    % Convert to EEGLAB
-    EEG = fieldtrip2eeglab(hdr, dat);
-    
-    % Load standard locations for EEG channels
-    EEG = pop_select(EEG, 'channel', 1:62);
-    EEG = pop_chanedit(EEG, 'lookup', 'standard-10-5-cap385.elp');
-    
-    % Load single-trial behavioral data
-    fname_trials = sprintf('%s/sub-%02d_trials.csv', preprocessed_dir, ix);
-    trials = readtable(fname_trials);
-    
-    % Extract ERPs for each part
-    parts = {'I', 'II', 'III'};
-    n_parts = length(parts);
-    for ix_part = 1:n_parts
-        
-        % Get trial indices from behavioral data
-        curr_part = parts{ix_part};
-        is_part = strcmp(trials.part, curr_part);
-        
-        % Compute averaged ERP across all conditions
-        erp_flat = mean(EEG.data(:, :, is_part), 3);
-        erps.(curr_part).flat(end + 1) = {erp_flat};
-        
-        % Compute averaged ERP for the difference between conditions
-        is_informed = is_part & strcmp(trials.condition, 'Informed');
-        is_naive = is_part & strcmp(trials.condition, 'Naive');
-        erp_informed = mean(EEG.data(:, :, is_informed), 3);
-        erp_naive = mean(EEG.data(:, :, is_naive), 3);
[…]

### 2022-01-19 manuscript/plots_tables.R

@@ -1,406 +1,0 @@
-########################################################################################
-## FUNCTIONS TO CREATE PLOTS AND TABLES ##
-########################################################################################
-
-# Function to create Figure 1
-plot_fig1 <- function(erp_components, evokeds, trials, models) {
-
-  # Define colors for conditions
-  colors <- list(
-    Informed = viridisLite::viridis(1, begin = 0.1),
-    Naive = viridisLite::viridis(1, begin = 0.5)
-  )
-
-  # Base object for split violin plots (kudos to https://stackoverflow.com/a/45614547)
-  GeomSplitViolin <- ggproto(
-    "GeomSplitViolin", GeomViolin,
-    draw_group = function(self, data, ..., draw_quantiles = NULL) {
-      data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
-      grp <- data[1, "group"]
-      newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
-      newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
-      newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
-      if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
-        stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 1))
-        quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
-        aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
-        aesthetics$alpha <- rep(1, nrow(quantiles))
-        both <- cbind(quantiles, aesthetics)
-        quantile_grob <- GeomPath$draw_panel(both, ...)
-        ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
-      }
-      else {
-        ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
-      }
-    }
-  )
-
-  # Base function for split violin plots (kudos to https://stackoverflow.com/a/45614547)
[…]

### 2022-01-19 manuscript/preprocessing.py

@@ -1,339 +1,0 @@
-"""
-PREPROCESSING FUNCTIONS
-
-Created 2021 by Alexander Enge (alexander.enge@hu-berlin.de)
-
-Contains one big function and some smaller helper functions to preprocess the EEG data
-for a single participant. Using the MNE-Python module and friends, it reads the raw EEG
-and behavioral data and extracts (a) the EEG epochs around the presentation of each
-unfamiliar object (b) the single trial mean ERP amplitudes at certain regions of
-interest, (c) averaged evoked potentials from at each electrode, and (d) single trial
-EEG power at a pre-specified range of frequencies.
-
-"""
-
-from os import makedirs
-from pathlib import Path
-
-import mne
-import numpy as np
-import pandas as pd
-from mne.channels import combine_channels, make_standard_montage
-from mne.epochs import Epochs
-from mne.io import read_raw_brainvision
-from mne.preprocessing import ICA
-from mne.time_frequency import tfr_morlet
-from mne.time_frequency.tfr import EpochsTFR
-
-
-def preprocess(
-    fname_vhdr=None,
-    fname_log=None,
-    subject_id=None,
-    output_dir=None,
-    resample_sfreq=250,
-    eog_names=["HEOG", "VEOG"],
-    eog_anodes=["F9", "Auge_u"],
-    eog_cathodes=["F10", "Fp1"],
-    montage_kind="easycap-M1",
-    ica_components=15,
-    ica_method="fastica",
-    random_seed=None,
-    hipass=0.1,
-    lowpass=30,
-    event_id=None,
-    tmin=-0.5,
-    tmax=1.489,
-    baseline=(-0.2, 0),
-    erp_components=None,
-    reject={"eeg": 200e-6},
-    average_by=None,
-    tfr_baseline=None,
-    tfr_equalize=False,
-    condition_col=None,
-    item_col=None,
-    drop_conditions=[],
-    tfr_freqs=None,
-    tfr_cycles=None,
-    tfr_crop=(-0.2, 0.8),
-):
-    """
-    Computes epochs, evoked potentials, and single trial power from a raw EEG data set.
-    """
-
-    # Create output directory if it doesn't exist
-    makedirs(output_dir, exist_ok=True)
-
-    # Read raw EEG data
-    raw = read_raw_brainvision(fname_vhdr, preload=True)
-
-    # Downsample
-    raw = raw.resample(resample_sfreq)
-
-    # Create virtual EOG channels
[…]

### 2022-01-19 manuscript/rsa.py

@@ -1,172 +1,0 @@
-# %%
-import matplotlib.pyplot as plt
-import numpy as np
-from mne import read_epochs
-from scipy.stats import sem, spearmanr
-
-# %%
-# General settings
-tmin, tmax = (-0.2, 0.8)
-
-# Prepare emtpy dictionaries
-parts = ["I", "II", "III"]
-rdms_eeg = {part: [] for part in parts}
-rdms_response = {part: [] for part in parts}
-corrs_eeg_response = {part: [] for part in parts}
-
-combinations = [("I", "II"), ("I", "III"), ("II", "III")]
-corrs_eeg_parts = {combination: [] for combination in combinations}
-
-# Define helper function to correlate two RDMs
-def correlate_rdms(rdm_1, rdm_2):
-    n_items = rdm_1.shape[0]
-    ixs_lower_triangle = np.tril_indices(n_items, -1)
-    lower_triangles = [rdm[ixs_lower_triangle] for rdm in [rdm_1, rdm_2]]
-    corr = spearmanr(*lower_triangles)[0]
-    return corr
-
-
-# %%
-# Loop over subjects
-n_subjects = 48
-subject_id = ["sub-" + "{:02d}".format(n) for n in range(1, n_subjects + 1)]
-for sid in subject_id:
-
-    # Read epochs for the current subject
-    fname = f"../data/preprocessed/{sid}_epo.fif"
-    epochs_subject = read_epochs(fname, verbose=True)
-
-    # Crop to time window of interest
-    _ = epochs_subject.crop(tmin, tmax)
-
-    # Loop over epochs for each part
-    rdms_parts = {part: [] for part in parts}
-    for part in parts:
-        epochs = epochs_subject[f"part == '{part}'"]
-
-        # Compute RDM from behavioral responses
-        response = np.array(epochs.metadata["response"])
-        n_items = len(response)
-        rdm_response = np.zeros((n_items, n_items))
-        for ix_item_1 in range(n_items):
-            for ix_item_2 in range(n_items):
-                dissimilarity = response[ix_item_1] - response[ix_item_2]
-                rdm_response[ix_item_1, ix_item_2] = np.abs(dissimilarity)
-        rdms_response[part].append(rdm_response)
-
-        # Loop over timepoints in the ERP
-        times = epochs.times
-        rdms_times = []
-        corrs_times_response = []
-        for ix, time in enumerate(times):
-
[…]

### 2022-01-19 manuscript/sloc.py

@@ -1,157 +1,0 @@
-import os.path as op
-import pickle
-
-import mne
-import numpy as np
-from mne import VolSourceEstimate, compute_covariance, read_epochs
-from mne.datasets import fetch_fsaverage
-from mne.evoked import combine_evoked
-from mne.minimum_norm import apply_inverse, make_inverse_operator
-
-from preprocessing import _equalize_trial_counts
-
-# Load preprocessed epochs for all subjects
-subject_id = ["sub-" + "{:02d}".format(n) for n in range(1, 49)]
-fnames_epo = [f"../data/preprocessed/{sid}_epo.fif" for sid in subject_id]
-epochs_all_subjects = [read_epochs(fname, verbose=False) for fname in fnames_epo]
-
-# Download standard MRI template and source/head model
-fs_dir = fetch_fsaverage(verbose=False)
-subjects_dir = op.dirname(fs_dir)
-subject = "fsaverage"
-trans = "fsaverage"  # MNE has a built-in fsaverage transformation
-src = op.join(fs_dir, "bem", "fsaverage-ico-5-src.fif")
-bem = op.join(fs_dir, "bem", "fsaverage-5120-5120-5120-bem-sol.fif")
-
-# Compute standard forward solution for all subjects
-info = epochs_all_subjects[0].info  # Info object is similar for all subjects
-
-# Define common parameters for inverse solution
-method = "dSPM"
-snr = 3.0
-lambda2 = 1.0 / snr ** 2
-
-# Setup volumn source space
-mri = op.join(fs_dir, "mri", "T1.mgz")
-vol_src = mne.setup_volume_source_space(
-    subject,
-    mri=mri,
-    pos=10.0,
-    bem=bem,
-    subjects_dir=subjects_dir,
-    add_interpolator=True,
-    verbose=True,
-)
-fwd = mne.make_forward_solution(info, trans, vol_src, bem, eeg=True, mindist=5.0)
-
-# Setup empty dictionary to store the source time courses for all parts and conditions
-parts = ["I", "II", "III"]
-parts_dict = {}
-for part in parts:
-    parts_dict[part] = {}
-    for condition in ["Informed", "Naive", "Combined", "Difference"]:
-        parts_dict[part][condition] = []
-
-# Loop overs subjects
-for epochs in epochs_all_subjects:
-
-    # Exclude any non-EEG channels
-    epochs.pick_types(eeg=True)
-
-    # Pick relevant conditions and channels
[…]

### 2022-01-20 analysis/manuscript.Rmd
Initialize new pipeline analysis

--- 2021-04-20 analysis/manuscript.Rmd
@@
 ---
-title             : |
-  | Event-Related Potentials of the Semantically Informed
-  | Perception of Unfamiliar Objects
-shorttitle        : "Semantic Knowledge and Unfamiliar Objects"
-
+title             : "Instant effects of semantic information on visual perception"
+shorttitle        : "Semantically informed perception"
 author: 
@@
     affiliation   : "1"
-    corresponding : yes
-    address       : "Rudower Chaussee 18, 12489 Berlin"
-    email         : "rasha.abdel.rahman@hu-berlin.de"
-
 affiliation:
@@
 
-  The preprocessed data and code for this study are openly available at https://osf.io/uksbc/.
-
-  We have no conflict of interest to disclose.
-
+  The authors declare no competing financial interests.
+  The preprocessed data and analaysis code for this study are openly available at https://osf.io/uksbc/.
 abstract: |
   Does our perception of an object change as soon as we discover what function it serves?
-This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
-In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception.
+  This question matters not only when we encounter novel tools or gadgets in our everyday lives, but also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+  Here, we showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
   We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
-When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place.
-We replicated these novel findings in an independent sample (*n* = 24).
-Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
-
+  We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms) and reduced amplitudes in the N400 component (400--700 ms).
+  When the same objects were presented once more without any information, the N400 effect persisted and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
+  Consistent with previous work, our results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
+  We demonstrate for the first time that these effects are instantaneous in the sense that they can be observed within the same trial as well as one trial after the information has been given, providing strong evidence that cognition affects perception.
 keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
-
 floatsintext      : yes
@@
 draft             : no
-
-bibliography      : "manuscript_files/r-references.bib"
-csl               : "manuscript_files/apa.csl"
-zotero            : "aha"
+bibliography      : ["references.bib", "r-references.bib"]
+csl               : "apa.csl"
 documentclass     : "apa7"
-classoption       : "man"
-output            :
+classoption       : "man,donotrepeattitle"
+fontsize          : "10pt"
+output:
   papaja::apa6_pdf:
-    latex_engine  : "xelatex"
-
+    latex_engine: xelatex
+  papaja::apa6_docx: default
 editor_options: 
   chunk_output_type: console
-
 header-includes:
@@
   - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
-  - \captionsetup[table]{font={stretch=1.5}}
-  - \captionsetup[figure]{font={stretch=1.5}}
+  - \captionsetup{font={stretch=1}, belowskip=15pt}
 ---
 
-```{r setup, include=FALSE}
-# Do you want to re-run the EEG preprocessing? Note that this can only be done with the raw data,
-# which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
-rerun_preproc <- TRUE
-
-# Do you want to re-run the linear mixed-effect models? This can be done even if only the
-# preprocessed single-trial data are available (from GitHub and/or the OSF). Note, however, that
-# fitting all models may take 24 hours or more.
-rerun_models <- FALSE
-
-# Do you want to run the analysis for Experiment 3?
-run_exp3 <- FALSE
-
-# Load packages
+```{r, setup, include=FALSE}
+# Load R packages
+library(buildmer)
+library(emmeans)
+library(here)
+library(knitr)
+library(lme4)
+library(lmerTest)
+library(MASS)
 library(papaja)
+library(parallel)
 library(reticulate)
@@
 library(magrittr)
-library(cowplot)
 
 # Set global chunk options
-knitr::opts_chunk$set(include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10)
+opts_chunk$set(fig.width = 10, include = FALSE, out.width = "100%")
 
-# Link to the bibliography file
-r_refs("analysis/manuscript_files/r-references.bib")
+# Write R packages to bibliography
+r_refs(here("analysis", "r-references.bib"), append = FALSE)
 
-# Source plotting functions
-source("analysis/manuscript_files/functions_plots_tables.R")
+# What to (re-)run
+run <- list(
+  "preprocessing" = TRUE,
+  "modeling" = TRUE
+)
 
-# Create an export folder for results
-dir.create("analysis/export", showWarnings = FALSE)
+# Directory paths
+data_dir <- here("data")
+output_dir <- here("output")
+```
 
-# Define ERP components of interest
-comps <- tibble(
-  name = c("P1", "N170", "N400"),
-  tmin = c(100, 150, 400),
-  tmax = c(150, 200, 700),
-  roi = list(
+```{r, preprocessing, eval=run$preprocessing}
+# Process behavioral data
+c(
+  list.files(here(data_dir, "rt/exp1"), "*.txt", full.names = TRUE),
+  list.files(here(data_dir, "rt/exp2"), "*.txt", full.names = TRUE)
+) %>%
+  # Process each log file
+  map(function(log_file) {
+
+    # Read the file
+    read_tsv(
+      log_file,
+      col_types = cols(),
+      locale = locale(encoding = "latin1")
+    ) %>%
+      # Recode some columns
+      transmute(
+
+        # Phase of the experiment
+        phase = factor(Wdh,
+          levels = c(211, 212, 213),
+          labels = c("Pre-insight", "Insight", "Post-insight")
+        ),
+
+        # # Participant ID (unique for Experiments 1 and 2)
+        # participant = ifelse(
+        #   str_detect(log_file, "exp2"), str_c(VPNummer, "_exp2"), VPNummer
+        # ),
+
+        # Keyword conditions
+        keywords = factor(Bed,
+          levels = c("richtig", "falsch"),
+          labels = c("Match", "Non-match")
+        ),
+
+        # Behavioral responses
+        # 201: "I know what this is or have a strong assumption"  -> Recode as 4
+        # 202: "I have an assumption what this is"                -> Recode as 3
+        # 203: "I have rather no assumption what this is"         -> Recode as 2
+        # 204: "I don't know what this is and have no assumption" -> Recode as 1
+        response = 5 - (Tastencode - 200),
+
+        # Reaction times
+        rt = RT,
+        log_rt = log(RT),
+
+        # Item IDs
+        item_id = factor(StimID)
+      ) %>%
+      # Remove filler items
+      drop_na(keywords) -> log
+
+    # Assign items to conditions based on manipulation (matching vs. non-
+    # matching keywords) and the responses of the participants
+    items_per_condition <- with(log, {
+      list(
+
+        # Informed condition: Matching keywords and positive response
+        "Informed" =
+          item_id[phase == "Insight" & keywords == "Match" & response >= 3],
+
+        # Naive condition: Non-matching keywords and negative response
+        "Naive" =
+          item_id[phase == "Insight" & keywords == "Non-match" & response <= 2],
+
+        # Exclude: Matching keywords and negative response
+        "Exclude_informed" =
+          item_id[phase == "Insight" & keywords == "Match" & response <= 2],
+
+        # Exclude: Non-matching keywords and positive response
+        "Exclude_naive" =
+          item_id[phase == "Insight" & keywords == "Non-match" & response >= 3],
+
+        # Exclude: Positive response *before* any info was presented
+        "Exclude_known" = item_id[phase == "Pre-insight" & response == 4]
+      )
+    })
+
+    # Assign these conditions to the trials of all three phases
+    log$condition <- NA
+    for (condition in names(items_per_condition)) {
+      item_id <- items_per_condition[[condition]]
+      log$condition[log$item_id %in% item_id] <- condition
+    }
+
+    # Sort columns
+    log %>%
+      select(item_id, phase, condition, response, rt, log_rt) %>%
+      return()
+  }) -> logs
+
+# Install latest version of the EEG pipeline
+system("pip install --user --upgrade --pre --index https://test.pypi.org/simple/ hu-neuro-pipeline")
+
+# Import EEG pipeline from Python
+pipeline <- import("pipeline")
+
+# Get list of BrainVision EEG header files
+vhdr_files <- c(
+  list.files(here(data_dir, "eeg/exp1"), "*.vhdr", full.names = TRUE),
+  list.files(here(data_dir, "eeg/exp2"), "*.vhdr", full.names = TRUE)
+)
+
+# Process EEG data
+res <- pipeline$group_pipeline(
+  vhdr_files = vhdr_files,
+  log_files = logs,
+  export_dir = output_dir,
+  downsample_sfreq = 250.,
+  # bad_channels = "auto",
+  ocular_correction = "fastica",
+  highpass_freq = 0.1,
+  lowpass_freq = 40.,
+  triggers = c(221, 222),
+  epochs_tmin = -0.5,
+  epochs_tmax = 1.5,
+  baseline = c(-0.2, 0.0),
+  reject_peak_to_peak = 200.,
+  reject_flat = 1.,
+  components = list(
+    "name" = c("P1", "N170", "N400"),
+    "tmin" = c(0.1, 0.15, 0.4),
+    "tmax" = c(0.15, 0.2, 0.7),
+    "roi" = list(
       c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
@@
     )
+  ),
+  average_by = c("phase/condition"),
+  perform_tfr = TRUE,
+  perm_contrasts = list(
+    c("Pre-insight/Informed", "Pre-insight/Naive"),
+    c("Insight/Informed", "Insight/Naive"),
+    c("Post-insight/Informed", "Post-insight/Naive")
+  ),
+  n_jobs = 1
 )
 
-# Define some filenames for I/O
-fnames <- list(
-  epochs = "analysis/export/aha-epo.fif",
-  trials = "analysis/export/aha-trials.csv",
-  gavgs = "analysis/export/aha-gavgs.RDS",
-  conditions = "analysis/export/aha-obj-per-cond.csv",
-  montage = "analysis/export/aha-montage.csv"
-)
+# Extract results
+trials <- tibble(res[[1]])
+evokeds <- tibble(res[[2]])
+clusters <- tibble(res[[3]])
+tfr_evokeds <- tibble(res[[4]])
+tfr_clusters <- tibble(res[[5]])
 ```
 
-Does our perception of an object change as soon as we discover what function it serves?
-In this study, we presented participants with unfamiliar objects that were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
-We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resolution of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
-This allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
+```{r, modeling, eval=run$modeling}
+# Read single trial data
+read_csv(here(output_dir, "all_trials.csv"), col_types = cols(
+  participant_id = col_factor(),
+  item_id = col_factor(),
+  phase = col_factor(),
+  condition = col_factor()
+)) %>%
+  # Subset only the relevant conditions
+  mutate(condition = factor(
+    condition,
+    levels = c("Informed", "Naive", "Excl_informed")
+  )) %>%
+  drop_na() -> trials
 
-The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world is "cognitively impenetrable" [@pylyshyn1999] or, in other words, determined solely by the visual input reaching our retina.
-According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @pylyshyn1999].
-Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @marr1982].
+# Contrast coding for phase
+cbind(
+  c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
+  c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
+) %>%
+  t() %>%
+  ginv() -> contrasts(trials$phase)
 
-This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1994; @lupyan2015; @teufel2017].
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas [e.g., V1 and V2\; @bullier2001; @gilbert2013]---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
-For instance, the reverse hierarchy theory [@ahissar2004; @hochstein2002] assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
-Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
-Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
-Finally, an active role of top-down influences is also promoted by theories of vision in the framework of Bayesian inference and predictive coding [e.g., @clark2013; @lupyan2015; @panichello2013; @yuille2006].
+# Contrast coding for condition
+cbind(
+  c("Informed" = 1, "Naive" = -1, "Excl_informed" = 0),
+  c("Informed" = 1, "Naive" = 0, "Excl_informed" = -1)
+) %>%
+  t() %>%
+  ginv() -> contrasts(trials$condition)
 
-Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition [for review, see @collins2014; @vetter2014].
-These aspects of cognition may include transient states such as emotions [e.g., @bocanegra2009; @phelps2016] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @gauthier2003; @weller2019].
-Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical and pointed out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
-They argue, for example, that most behavioral paradigms have not been able to discern between perceptual and post-perceptual (e.g., memory-related) effects.
-Furthermore, cognitive influences in some studies were confounded with differences in the low-level visual input itself.
-We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our methodology and results.
+# Prepare model formula
+mod_formula <- N170 ~ phase * condition +
+  (phase * condition | participant_id) +
+  (phase * condition | item_id)
 
-In general, however, it is important to note that one productive way to circumvent at least some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or post-perceptual---are influenced by higher-level capacities such as semantic knowledge.
-This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
+# Fit linear mixed models
+deps <- c("P1", "N170", "N400")
+mod_lists <- map(deps, function(dep, mod_formula = form, mod_data = trials) {
 
-The visual P1 component of the ERP refers to a positive deflection peaking as early as 100--150 ms after stimulus onset at occipital channels.
-It is generated by multiple sources in the extrastriate cortices of the middle occipital and fusiform gyri [@dirusso2001; @mangun1995].
-The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus [e.g., size, luminance, and contrast\; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated view of visual perception.
-It is well-established that the P1 is enhanced when participants pay attention to the spatial location of a stimulus [@luck2000; @mangun1995; @mangun1991] but there is also more recent evidence for higher-level cognitive influences that go beyond spatial attention (see below).
+  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
+  # Uses parallelization across all available CPU cores
+  n_cores <- detectCores()
+  cl <- makeCluster(n_cores)
+  build <- buildmer(
+    buildmerControl = buildmerControl(
+      formula = mod_formula,
+      data = mod_data,
+      # args = list("control" = lmerControl(
+      #   optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
+      # )),
+      direction = c("order", "backward"),
+      cl = cl,
+      elim = LRTalpha(.20),
+      calc.anova = TRUE,
+      ddf = "Satterthwaite",
+      dep = dep
+    )
+  )
+  stopCluster(cl)
 
-The visual N170 (or N1) component refers to the negative deflection following the P1 and is maximal around 150--200 ms after stimulus onset at occipito-temporal channels.
-Just as the P1, it is influenced by visual parameters of the stimulus [@johannes1995] and by selective attention, especially when participants are required to discriminate between different visual stimuli [@vogel2000; @mangun1991].
-The N170 is enlarged (i.e., more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g., birds, dogs, or cars\; @gauthier2003a; @tanaka2001].
-This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as the holistic configuration of these features [@eimer2011; @jacques2010; @rossion1999; @sagiv2001].
-Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these capacities having an influence on higher-level, holistic perception of the visual stimulus.
+  # Compute marginal means and contrasts
+  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
+  specs <- pairwise ~ condition | phase
+  em <- emmeans(build@model, specs, infer = TRUE)
 
-Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018].
-It begins approximately 300 ms after stimulus onset and is most pronounced at centro-parietal channels.
-A modulation of the N400 component by cognitive capacities such as knowledge can be taken as evidence for a post-perceptual influence on stimulus processing.
+  # Create list of returns
+  list(
+    "model" = build@model,
+    "summary" = build@summary,
+    "anova" = build@anova,
+    "means" = em$emmeans,
+    "contrasts" = em$contrasts
+  ) %>%
+    return()
+}) %>%
+  # Add ERP component names
+  set_names(deps)
 
-Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge about visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
-Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing.
-This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (i.e., cooking recipes) for the other half of the objects [@abdelrahman2008, Experiment 1].
-After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information.
-In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this had not been the case.
-These differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
-Interestingly, the ERPs observed for previously unfamiliar objects with newly acquired in-depth knowledge were qualitatively similar to those for untrained but well-known objects.
-The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
-In this study, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
-This can be taken as further evidence for an influence of semantic knowledge on the early visual perception of unfamiliar objects.
-
-A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects which were rendered difficult to recognize by converting them to two-tone, "Mooney" images [@samaha2018, Experiment 4].
-In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
-When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha-band power was higher for meaning-trained images than for perceptually-trained images.
-As before, this effect of perceiving objects in a semantically informed way seems to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
-This alternative approach further corroborates an early influence of semantic information on the visual perception of objects.
-
-All the previously mentioned studies have in common that they investigated the effects of semantic knowledge on the visual perception of objects only *after* an extensive learning phase had taken place [@abdelrahman2008; @gauthier2003; @maier2014; @maier2019; @rossion2002; @rossion2004; @samaha2018; @weller2019].
-Participants performed one or multiple training sessions during which they encountered each object together with its respective label or description multiple times.
-The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day [@abdelrahman2008; @maier2014; @maier2019] or were spread out across multiple days or weeks [@rossion2002; @rossion2004].
-While experimental designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they leave at least three conceptual questions unresolved.
-
-The first question is if we can detect any electrophysiological correlates of *semantic insight*, that is, the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on).
-The second question is how much learning is actually necessary before reliable top-down effects of knowledge on ERP amplitudes can be obtained: Does it actually take dozens of repetitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is about the nature of the effects of knowledge on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
-By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we were able to provide tentative answers to all three of these questions.
-
-In the two experiments subsequently reported, participants were presented with real-world objects that were presumed to be unfamiliar to most of them.
-They first viewed each of these objects without any semantic information.
-This first part served as a naive baseline to rule out that ERPs would differ in response to the objects based solely on low-level visual differences.
-Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
-These keywords could either be matching the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could be non-matching by describing the function of a different object, thus keeping the perception of the object semantically naive.
-During this second part, we were able to measure the online influence of semantic insight on object-evoked ERPs as it happened.
-Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them---thereby mimicking previous studies [e.g., @abdelrahman2008; @samaha2018; @weller2019].
-In all three parts, we examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (N400 component, 400--700 ms).
-
-# Experiment 1
-
-## Method
-
-### Participants
-
-Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
-No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
-All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
-They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-
-### Materials
-
-Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum).
-A list of these unfamiliar objects can be found in Appendix A.
-All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
-At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
-
-For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
-As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to hamper such an understanding and keep the perception of the object semantically naive.
-All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
-The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
-
-### Procedure
-
-Each experimental session consisted of three parts (see Figure \@ref(fig:exp1-plot)A).
-In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
-Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
-The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
-The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
-
-```{python def_functions, eval=rerun_preproc}
-# Import libraries
-import mne
-import numpy as np
-
-# Define function for preprocessing a single participant
-def preproc(
-    vhdr_fname,
-    metadata,
-    n_components,
-    method,
-    l_freq,
-    h_freq,
-    event_id,
-    tmin,
-    tmax,
-    baseline,
-    reject,
-):
-    # Read EEG data in microvolts
-    raw = mne.io.read_raw_brainvision(vhdr_fname, scale=1e6, preload=True)
-    # Create virtual EOG channels
-    raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
-    raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
-    raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
-    # Add EasyCap electrode layout, removing any excessive channels
-    montage = mne.channels.make_standard_montage("easycap-M1")
-    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
-    raw.set_montage(montage=montage)
-    # Re-reference to common average
-    raw, _ = mne.set_eeg_reference(raw, "average")
-    # Run ICA on a copy of the data
-    filt_raw = raw.copy()
-    filt_raw.load_data().filter(l_freq=1, h_freq=None)
-    ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
-    ica.fit(filt_raw)
-    # Remove bad components based on correlations with EOG
-    eog_indices, eog_scores = ica.find_bads_eog(raw)
-    ica.exclude = eog_indices
-    raw = ica.apply(raw)
-    # Apply band-pass filter
-    raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
-    # Epoching including baseline correction
-    events, _ = mne.events_from_annotations(raw, verbose=False)
-    epochs = mne.Epochs(
-        raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True
-    )
-    # Add behavioral data
-    epochs.metadata = metadata
-    # Reject bad epochs
-    epochs = epochs.drop_bad(reject=reject)
-    return epochs
-
-# Define function for preprocessing a list of participants
-def preproc_all(
-    vhdr_fnames,
-    metadatas,
-    output_fname,
-    n_components,
-    method,
-    l_freq,
-    h_freq,
-    event_id,
-    tmin,
-    tmax,
-    baseline,
-    reject,
-):
-    # Do the actual preprocessing
-    epochs = [
-        preproc(
-            vhdr_fname=vhdr_fname,
-            metadata=metadata,
-            n_components=n_components,
-            method=method,
-            l_freq=l_freq,
-            h_freq=h_freq,
-            event_id=event_id,
-            tmin=tmin,
-            tmax=tmax,
-            baseline=baseline,
-            reject=reject,
-        )
-        for vhdr_fname, metadata in zip(vhdr_fnames, metadatas)
-    ]
-    # Concatenate all participants and save
-    epochs = mne.epochs.concatenate_epochs(epochs)
-    epochs.save(output_fname, overwrite=True)
-    # Return the epochs without loading the actual data
-    epochs = mne.read_epochs(output_fname, preload=False)
-    return epochs
-
-# Define function to compute averaged waveforms by part and condition
-def compute_evokeds(epochs_fname, grand=True, data_only=True):
-    # Read preprocessed epochs
-    epochs = mne.read_epochs(epochs_fname)
-    # Define lists of participants, parts, and conditions
-    ps = epochs.metadata["participant"].unique()
-    pts = ["I", "II", "III"]
-    cns = ["Informed", "Naive"]
-    # Define function to compute a single by-participant waveform
-    def compute_evoked(epochs, pt, cn, p):
-        query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
-        return epochs[query].average()
-
-    # Create a dict with by-participant waveforms nested in conditions nested in parts
-    avgs = {pt: {cn: [compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
-    # If needed, compute grand-averaged waveforms across participants
-    if grand:
-        avgs = {pt: {cn: mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
-    # If needed, extract only the data from the evoked MNE objects
-    if data_only:
-        if grand:
-            avgs = {pt: {cn: avgs[pt][cn].data for cn in cns} for pt in pts}
-        else:
-            ps_num = range(0, len(ps))
-            avgs = {pt: {cn: [avgs[pt][cn][p].data for p in ps_num] for cn in cns} for pt in pts}
-    return avgs
-
-# Define function to compute single-trial mean ERP amplitudes from epochs
-def compute_erps(epochs_fname, name, tmin, tmax, roi):
-    # Read preprocessed epochs
-    epochs = mne.read_epochs(epochs_fname)
-    # Average across electrodes in the ROI
-    roi_idx = mne.pick_channels(epochs.ch_names, roi)
-    epochs_roi = mne.channels.combine_channels(epochs, dict(roi=roi_idx))
-    # Average across samples in the time window
-    tmin_s, tmax_s = tmin / 1000, tmax / 1000
-    times_idx = np.where(np.logical_and(epochs.times >= tmin_s, epochs.times <= tmax_s))
-    erps = epochs_roi.get_data()[:, 0, times_idx].mean(axis=(1, 2))
-    return erps
-
+# Save models
+saveRDS(mod_lists, here(output_dir, "models.RDS"))
 ```
-
-```{r exp1-preproc, eval=rerun_preproc}
-# Define function for reading and formatting the behavioral data
-read_behav <- function(txt_fname) {
-  # Read the log file
-  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
-  # Rename columns for participant and item IDs
-  dat %<>% rename(participant = VPNummer, item = StimID) %>%
-    # Add a column for the part of the experiment
-    mutate(part = case_when(
-      Wdh %in% c(211, 231) ~ "I",
-      Wdh %in% c(212, 232) ~ "II",
-      Wdh %in% c(213, 233) ~ "III",
-      Wdh == 234 ~ "IV"
-    ) %>% as_factor()) %>%
-    # Remove filler stimuli (i.e.,well-known objects)
-    filter(bek_unbek != "bekannt")
-  # Assign stimuli to conditions based on keywords and button presses
-  excl_known <- dat %>%
-    filter(part == "I" & Tastencode %in% c(201, 251)) %>%
-    pull(item)
-  excl_informed <- dat %>%
-    filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
-    pull(item)
-  excl_naive <- dat %>%
-    filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>%
-    pull(item)
-  informed <- dat %>%
-    filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
-    pull(item)
-  naive <- dat %>%
-    filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>%
-    pull(item)
-  # Create a new condition for the experimental condition
-  dat %<>% mutate(condition = case_when(
-    item %in% excl_known ~ "Excl_known",
-    item %in% excl_informed ~ "Excl_informed",
-    item %in% excl_naive ~ "Excl_naive",
-    item %in% informed ~ "Informed",
-    item %in% naive ~ "Naive"
-  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
-  # In Experiment 3, we need an additional column for position (upright vs. inverted)
-  if ("richtig_inv" %in% dat$Bed) {
-    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
-      # Return only relevant columns
-      select(part, position, condition, participant, item, RT)
-  } else {
-    # Return only relevant columns
-    dat %<>% select(part, condition, participant, item, RT)
-  }
-  return(dat)
-}
-
-# Read behavioral data from two batches of participants
-paste0("data/rt/exp", 1:2) %>%
-  map(list.files, pattern = ".txt", full.names = TRUE) %>%
-  map(map, read_behav) -> behav
-
-# Avoid duplicate participant labels across the two batches
-behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))
-
-# Merge into a single list
-behav %<>% flatten()
-
-# Define global parameters for EEG preprocessing
-preproc_params <- list(
-  # Number of ICA components
-  n_components = as.integer(15),
-  # ICA methods
-  method = "fastica",
-  # Lower edge of pass-band filter
-  l_freq = 0.1,
-  # Upper edge of pass-band filter
-  h_freq = 30,
-  # Event trigger codes
-  event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
-  # Beginning of epochs in s
-  tmin = -0.5,
-  # End of epochs in s
-  tmax = 1.498,
-  # Baseline interval in s
-  baseline = tuple(-0.2, 0),
-  # Artifact rejection threshold in microvolts
-  reject = dict(eeg = 200)
-)
-
-# Preprocess the EEG for Experiment 1 in Python
-paste0("data/eeg/exp", 1:2) %>%
-  list.files(pattern = ".vhdr", full.names = TRUE) %>%
-  exec(
-    .fn = py$preproc_all,
-    vhdr_fnames = .,
-    metadatas = behav,
-    output_fname = fnames$epochs,
-    !!!preproc_params
-  ) -> epochs
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs_fname = fnames$epochs) %>%
-  set_names(comps$name) %>%
-  bind_cols(epochs$metadata, .) %T>%
-  write_tsv(fnames$trials) -> aha
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs_fname = fnames$epochs, grand = TRUE, data_only = TRUE) %>%
-  saveRDS(fnames$gavgs)
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(aha$participant), .before = 1) %>%
-  write_csv(fnames$conditions)
-
-# Get standard EasyCap electrode positions and project to 2D space
-py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
-  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
-  read_tsv(col_types = cols()) %>%
-  rename(electrode = Site) %>%
-  inner_join(tibble(electrode = epochs$ch_names), ., by = "electrode") %>%
-  mutate(
-    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
-    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
-  ) %>%
-  write_csv(fnames$montage)
-```
-
-```{r exp1-models, eval=rerun_models}
-# Load preprocessed single-trial data
-read_tsv("analysis/export/aha-trials.csv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
-    )),
-    participant = factor(participant),
-    item = factor(item)
-  ) %>%
-  # Remove any trials excluded from conditions
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> aha
-
-# Define contrast coding for condition (informed-naive) and part (2-1, 3-1)
-contrasts_condition <- t(cbind(
-  c("Informed" = 1, "Naive" = -1)
-))
-contrasts_part <- t(cbind(
-  c("I" = -1, "II" = 1, "III" = 0),
-  c("I" = 0, "II" = -1, "III" = 1)
-))
-
-# Apply these contrasts to the factors in the data
-contrasts(aha$condition) <- MASS::ginv(contrasts_condition)
-contrasts(aha$part) <- MASS::ginv(contrasts_part)
-
-# Specify model formula and follow-up contrasts
-form <- erp ~ part * condition +
-  (part * condition | participant) +
-  (part * condition | item)
-specs <- pairwise ~ condition | part
-
-# Calculate linear mixed-effects models and contrasts
-map(comps$name, function(comp, formula = form, data = aha, specs = specs) {
-  require(afex)
-  require(emmeans)
-  data %<>% rename(erp = all_of(comp))
-  mod <- mixed(
-    formula,
-    data,
-    method = "S",
-    check_contrasts = FALSE,
-    all_fit = TRUE
-  )
-  em <- emmeans(mod, specs = specs, infer = TRUE, data = data)
-  modlist <- list(
-    model = mod,
-    anova = anova(mod),
-    summary = summary(mod),
-    means = as.data.frame(em$means),
-    contrasts = as.data.frame(em$contrasts)
-  )
-}) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/aha_models_freq.RDS") -> mods_freq
-```
-
-```{r exp1-import}
-# Load average number of objects per condition
-(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
-   summarise(across(.cols = -Participant, .fns = mean)) %>%
-   slice(1) %>% unlist() -> objects_exp1)
-
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
-    ),
-    participant = factor(participant),
-    item = factor(item)
-  ) -> aha
-
-# Check number of rejected epochs
-aha %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n) -> rejected_exp1
-mean(rejected_exp1)    # Mean
-median(rejected_exp1)  # Median
-range(rejected_exp1)   # Range
-
-# Load grand-averaged ERPs and linear mixed models
-evokeds_exp1 <- readRDS("analysis/export/exp1-gaverages.RDS")
-models_exp1 <- readRDS("analysis/export/exp1-models.RDS")
-```
-
-```{r bayes, eval=FALSE}
-library(brms)
-options(mc.cores = 6)
-
-data_joint_subs %>%
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() %>%
-  select(part, condition, participant, item, P1, N170, N400) %>%
-  na.omit() %>%
-  as.list() -> data_brm
-
-contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
-contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
-contrasts(data_brm$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_brm$part) <- MASS::ginv(contrasts_part)
-
-formula <- P1 ~ part / condition + (part / condition | participant) + (part / condition | item)
-prior <- set_prior("cauchy(0, 0.707)", class = "b")
-
-mod_brm <- brm(
-  formula = formula,
-  data = data_brm,
-  family = gaussian(),
-  prior = prior,
-  sample_prior = "yes",
-  save_pars = save_pars(all = TRUE),
-  chains = 4,
-  iter = 20000,
-  warmup = 2000,
-  cores = 4,
-  control = list(adapt_delta = 0.9)
-)
-
-# mod_prior <- brm(formula = formula, data = data_brm, prior = prior, sample_prior = "only")
-# prior_summary(mod_prior)
-# mcmc_plot(mod_prior)
-#
-# mod_post <- update(mod_prior, sample_prior = "yes")
-# summary(mod_post)
-# mcmc_plot(mod_post, pars = "b")
-# plot(mod_post)
-
-hypothesis <- paste0("part", c("I", "II", "III"), ":condition1 = 0")
-bf_brms <- hypothesis(mod_post, hypothesis = hypothesis)
-bf_brms$hypothesis$bf10 <- 1 / bf_brms$hypothesis$Evid.Ratio
-bf_brms
-
-bf_bayestest <- bayestestR::bayesfactor(mod_post)
-bf_bayestest
-
-mod_brm_s <- brm(
-  bf(P1 ~ part / condition + (part / condition | participant) + (part / condition | item),
-     sigma ~ 1 + (1 | participant)),
-  prior = c(
-    prior(cauchy(0, 0.707), class = b),
-    prior(student_t(3, 0, 5.7), class = Intercept, dpar = sigma),
-    prior(normal(0, 5), class = sd, group = participant, dpar = sigma)),
-  data = data_brm,
-  family = gaussian(),
-  sample_prior = "yes",
-  save_pars = save_pars(all = TRUE),
-  chains = 4,
-  iter = 20000,
-  warmup = 2000,
-  cores = 4,
-  control = list(adapt_delta = 0.9)
-)
-```
-
-```{python tfr, eval=FALSE}
-import mne
-import numpy as np
-#import matplotlib.pyplot as plt
-
-# epochs = preproc(
-#   vhdr_fname="data/exp1/eeg/Vp0004.vhdr",
-#   metadata=r.aha.query("participant == 'VP_04'"),
-#   n_components=15,
-#   method="fastica",
-#   l_freq=None,
-#   h_freq=None,
-#   event_id=dict(match=221, mismatch=222),
-#   tmin=-0.5,
-#   tmax=1.498,
-#   baseline=(-0.2, 0),
-#   reject=dict(eeg=200)
-# )
-# epochs.save("analysis/export/vp04-epo.fif")
-
-epochs = mne.read_epochs("analysis/export/unf-exp1-epo.fif")
-
-evokeds = compute_evokeds(epochs_c, grand=True, data_only=False)
-evokeds_i = evokeds["II"]["Informed"]
-evokeds_n = evokeds["II"]["Naive"]
-
-freqs = np.logspace(*np.log10([6, 35]), num=8)
-n_cycles = freqs / 2.
-power_i = mne.time_frequency.tfr_morlet(evokeds_i, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-power_n = mne.time_frequency.tfr_morlet(evokeds_n, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-power_i = power_i.apply_baseline(mode='mean', baseline=(-.400, -.100))
-power_n = power_n.apply_baseline(mode='mean', baseline=(-.400, -.100))
-
-power_d = power_i.copy()
-power_d.data = power_i.data - power_n.data
-
-power_d.plot()
-
-# epochs.resample(250., npad='auto')
-
-roi = r.comps["roi"][0] + r.comps["roi"][1]
-idxs = np.where(np.in1d(epochs.ch_names, roi))
-
-epochs_i = epochs["part == 'II' & condition == 'Informed'"].pick_channels(roi)
-epochs_n = epochs["part == 'II' & condition == 'Naive'"].pick_channels(roi)
-
-epochs_c = mne.channels.combine_channels(epochs, groups=dict(avg=range(62)))
-
-epochs_c.metadata = epochs.metadata
-epochs_s = epochs_c["part == 'II'"]
-# epochs_i = epochs_s["condition == 'Informed'"]
-# epochs_n = epochs_s["condition == 'Naive'"]
-
-# power_i = mne.time_frequency.tfr_morlet(epochs_i, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-# power_n = mne.time_frequency.tfr_morlet(epochs_n, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-# power_d = power_i - power_n
-# 
-# power_d.plot([0], baseline=(-0.5, 0), mode='percent', vmin=-1, vmax=1)
-
-# define frequencies of interest (log-spaced)
-#freqs = np.logspace(*np.log10([6, 35]), num=8)
-freqs = np.arange(3, 50, 1.6)
-#n_cycles = freqs / 2.  # different number of cycle per frequency
-n_cycles = np.linspace(3, 10, len(freqs))
-power = mne.time_frequency.tfr_morlet(epochs_c, freqs=freqs, n_cycles=n_cycles, use_fft=True, return_itc=False, average=True, n_jobs=1)
-
-power.plot([0], baseline=(-0.5, 0), mode='percent')
-
-power.plot_topo(baseline=(-0.5, 0), mode='logratio')
-power.plot_topomap(ch_type='eeg', tmin=0.15, tmax=0.2, fmin=8, fmax=12, baseline=(-0.5, 0), mode='logratio', title='Alpha')
-power.plot_topomap(ch_type='eeg', tmin=0.15, tmax=0.2, fmin=13, fmax=25, baseline=(-0.5, 0), mode='logratio', title='Beta')
-
-import numpy as np
-import matplotlib.pyplot as plt
-from mne.baseline import rescale
-from mne.stats import bootstrap_confidence_interval
-iter_freqs = [
-    ('Theta', 4, 7),
-    ('Alpha', 8, 12),
-    ('Beta', 13, 25),
-    ('Gamma', 30, 45)
-]
-raw_fname = "data/exp1/EEG/Vp0004.vhdr"
-tmin, tmax = -0.5, 1.498
-baseline = None
-frequency_map = list()
-event_id = dict(match=222)
-for band, fmin, fmax in iter_freqs:
-    # (re)load the data to save memory
-    raw = mne.io.read_raw_brainvision(raw_fname, scale=1e6, preload=True)
-    raw.filter(fmin, fmax, n_jobs=1,  # use more jobs to speed up.
-               l_trans_bandwidth=1,  # make sure filter params are the same
-               h_trans_bandwidth=1)  # in each band and skip "auto" option.
-    events, _ = mne.events_from_annotations(raw, verbose=False)
-    epochs = mne.Epochs(raw, events, event_id, tmin, tmax, baseline=baseline,
-                        reject=dict(eeg=200), preload=True)
-    # remove evoked response
-    epochs.subtract_evoked()
-    # get analytic signal (envelope)
-    epochs.apply_hilbert(envelope=True)
-    frequency_map.append(((band, fmin, fmax), epochs.average()))
-    del epochs
-del raw
-# Helper function for plotting spread
-def stat_fun(x):
-    """Return sum of squares."""
-    return np.sum(x ** 2, axis=0)
-# Plot
-fig, axes = plt.subplots(4, 1, figsize=(10, 7), sharex=True, sharey=True)
-colors = plt.get_cmap('winter_r')(np.linspace(0, 1, 4))
-for ((freq_name, fmin, fmax), average), color, ax in zip(
-        frequency_map, colors, axes.ravel()[::-1]):
-    times = average.times * 1e3
-    gfp = np.sum(average.data ** 2, axis=0)
-    gfp = mne.baseline.rescale(gfp, times, baseline=(None, 0))
-    ax.plot(times, gfp, label=freq_name, color=color, linewidth=2.5)
-    ax.axhline(0, linestyle='--', color='grey', linewidth=2)
-    ci_low, ci_up = bootstrap_confidence_interval(average.data, random_state=0,
-                                                  stat_fun=stat_fun)
-    ci_low = rescale(ci_low, average.times, baseline=(None, 0))
-    ci_up = rescale(ci_up, average.times, baseline=(None, 0))
-    ax.fill_between(times, gfp + ci_up, gfp - ci_low, color=color, alpha=0.3)
-    ax.grid(True)
-    ax.set_ylabel('GFP')
-    ax.annotate('%s (%d-%dHz)' % (freq_name, fmin, fmax),
-                xy=(0.95, 0.8),
-                horizontalalignment='right',
-                xycoords='axes fraction')
-axes.ravel()[-1].set_xlabel('Time [ms]')
-plt.show()
-```
-
-```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
-# Load sample time points and electrode montage
-montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())
-
-# Create plot for Experiment 1
-plot_grid(
-  plot_trials(),
-  plot_erps(comps = comps, evokeds = evokeds_exp1, models = models_exp1, montage = montage),
-  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
-) + # Add some lines (to separate the parts) and the legend
-  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.53, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.53, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.53, yend = 0.58, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.53, yend = 0.58, linetype = "dashed") +  
-  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.58, yend = Inf, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.58, yend = Inf, linetype = "dashed") +
-  draw_plot(plot_legends_erps(direction = "vertical"), x = 0.405, y = 0.422, width = 1, height = 1)
-```
-
-(ref:figure-1-caption) Procedure and Results of Experiment 1\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\textit{Note.} 
-(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
-In the post-insight part, the same objects were presented again without the keywords.
-(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
-Ampl.
-= amplitude.\newline
-*\textit{p} \textless{} .05. **\textit{p} \textless{} .01. ***\textit{p} \textless{} .001.
-
--->
-
-In the *insight* part, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
-Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
-Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
-The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).
-
-Finally, in the *post-insight* part, the unfamiliar objects were presented for a third time with an identical trial structure as in the pre-insight part, that is, without any keywords.
-Note that the insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight part (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight part (without keywords) before moving on to the next block consisting of 30 different objects.
-They continued like this until all four blocks were completed in both parts.
-In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight part and 120 unfamiliar objects in the pre-insight, insight, and post-insight parts).
-It took participants approximately 35 minutes to complete.
-
-### EEG Recording and Preprocessing
-
-The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system [@americanelectroencephalographicsociety1991] and referenced online to an external electrode placed on the left mastoid (M1).
-Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively.
-During the recording, electrode impedance was kept below 5 kΩ.
-An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
-
-Offline, the data were preprocessed using the MNE software [Version 0.21.0\; @gramfort2013] in Python [Version 3.8.5\; @vanrossum2009].
-First, all scalp electrodes were re-referenced to the common average.
-Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
-The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find\_bads\_eog* function.
-After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
-The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset.
-Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
-This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \@ref(fig:exp1-plot)B).
-
-### Statistical Analysis
-
-First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
-Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
-This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
-Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
-This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).
-
-The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
-For the purpose of the present study, these models have at least three desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant averages.
-First, they can leverage all of the information that is present in the data set on the single trial level, some of which would be lost when computing averages.
-Second, they can account simultaneously for the non-independence of data points coming from the same participant and/or from the same item.
-In contrast, the neglect of the item as a random variable in by-participant ANOVAs can lead to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
-Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable when the assignment of trials to conditions is co-determined by the experimental manipulation and the behavior of participants in response to this manipulation [e.g., @fröber2017].
-
-Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
-All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e., subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
-For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to @schad2020.
-To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
-We then performed a model selection algorithm as proposed by @matuschek2017 in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model [determined by *p* ≥ .20\; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
-All models were computed in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4].
-The optimizer function *bobyqa* with 20,000 iterations was used for maximum likelihood estimation.
-The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`\; @R-buildmer].
-
-Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the semantically informed against the naive condition within the pre-insight, \mbox{insight}, and post-insight parts.
-This was achieved using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
-All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
-
-The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (<https://osf.io/uksbc/>).
-We are not able to share the raw EEG data openly because we did not obtain participants' informed consent to do so.
-
-## Results
-
-Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
-In the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception.
-The other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
-The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \@ref(fig:exp1-plot)A), thereby making sure that semantically informed and naive perception did indeed occur.
-The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, the N170 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.
-
-```{r exp1-table, include=TRUE, results="asis"}
-# Create table of models for Experiment 1
-table_exp1 <- create_table(
-  models = models_exp1,
-  stub_anova = c("Part", "Condition", "Pt. × con."),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 1\\smallskip",
-  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (see Table \@ref(tab:exp1-table)).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r table_exp1$anov["Condition", "N400_df"]` = `r table_exp1$anov["Condition", "N400_f"]`, *p* = `r table_exp1$anov["Condition", "N400_p"]`.
-Crucially, the part × condition interaction was significant in the N170 component, *F*`r table_exp1$anov["Pt.
-× con.", "N170_df"]` = `r table_exp1$anov["Pt.
-× con.", "N170_f"]`, *p* = `r table_exp1$anov["Pt.
-× con.", "N170_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt.
-× con.", "N400_df"]` = `r table_exp1$anov["Pt.
-× con.", "N400_f"]`, *p* `r table_exp1$anov["Pt.
-× con.", "N400_p"]`, while also showing a weak statistical trend in the P1 component, *F*`r table_exp1$anov["Pt.
-× con.", "P1_df"]` = `r table_exp1$anov["Pt.
-× con.", "P1_f"]`, *p* = `r table_exp1$anov["Pt.
-× con.", "P1_p"]`.
-To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
-
-### ERPs Before Insight Was Occurring
-
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s ≥ `r table_exp1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:exp1-table) and Figure \@ref(fig:exp1-plot)B).
-On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
-On the other hand, the absence of reliable differences in this part can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in the other two parts cannot be accounted for by visual differences between the objects in the two conditions.
-Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self-report would have made it possible for such visual differences to emerge as a confounding factor.
-If they did, however, one would expect to detect these differences even before any keywords were presented, which was apparently not the case.
-
-### ERPs While Insight Was Occurring
-
-In the insight part, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e., more negative), *b* = `r table_exp1$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Insight part", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e., less negative), *b* = `r table_exp1$conts["Insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Insight part", "N400_p"]`, compared to when the object was viewed naively without relevant semantic information.
-As in the pre-insight part, there were no reliable differences in the P1 component, *b* = `r table_exp1$conts["Insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Insight part", "P1_p"]`.
-
-### ERPs After Insight Had Occurred
-
-In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part).
-This allowed us to test if the semantic information had any lasting effects on the processing of the objects.
-As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Post-insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *b* = `r table_exp1$conts["Post-insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "N170_p"]`.
-Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "P1_p"]`.
-
-## Discussion
-
-In Experiment 1, we measured the ERPs of participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-insight part) they were able to understand what kind of object they were seeing.
-To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
-
-In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms).
-When the same objects were presented once more in the post-insight part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for which semantically informed perception had taken place.
-
-Because of the novelty of our experimental paradigm---measuring the ERPs while rather than after participants received semantic information about unfamiliar objects---and because of the novelty of our findings, we ran a replication study with another sample of participants to assess the robustness of these effects.
-
-# Experiment 2
-
-## Method
-
-### Participants
-
-Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29 years) who had not participated in Experiment 1.
-They had no history of psychological disorders or treatment, were right-handed, and reported normal or corrected-to-normal vision.
-They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-
-### Materials, Procedure, and Analysis
-
-```{r exp2-preproc, eval=rerun_preproc}
-# Read behavioral data for Experiment 2
-list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp2
-
-# Preprocess the EEG for Experiment 2 in Python
-map2(
-  .x = list.files("data/exp2/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp2,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp2
-
-# Backup epochs to the export folder
-epochs_exp2$save("analysis/export/exp2-epo.fif")
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
-  set_names(comps$name) %>%
-  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
-  write_tsv("analysis/export/exp2-data.tsv") -> data_exp2
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp2-gaverages.RDS")
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp2, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp2-objects.tsv")
-
-# Remove the epochs to free up memory
-rm(epochs_exp2)
-```
-
-```{r exp2-models, eval=rerun_models}
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
-    ),
-    participant = factor(participant),
-    item = factor(item)
-  ) %>%
-  # Remove any trials excluded from conditions
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> data_exp2
-
-# Apply contrasts to the factors in the data
-contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)
-
-# Compute the models for Experiment 2
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp12,
-  data = data_exp2,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp2-models.RDS") -> models_exp2
-```
-
-```{r exp2-import}
-# Load average number of objects per condition
-(read_tsv("analysis/export/exp2-objects.tsv", col_types = cols()) %>%
-   summarise(across(.cols = -Participant, .fns = mean)) %>%
-   slice(1) %>% unlist() -> objects_exp2)
-
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
-    ),
-    participant = factor(participant),
-    item = factor(item)
-  ) -> data_exp2
-
-# Check number of rejected epochs
-data_exp2 %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n) -> rejected_exp2
-mean(rejected_exp2)    # Mean
-median(rejected_exp2)  # Median
-range(rejected_exp2)   # Range
-
-# Load grand-averaged ERPs and linear mixed models
-evokeds_exp2 <- readRDS("analysis/export/exp2-gaverages.RDS")
-models_exp2 <- readRDS("analysis/export/exp2-models.RDS")
-```
-
-All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
-An average of `r format(round(objects_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects was assigned to the semantically informed condition (= `r scales::percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects was assigned to the naive condition (= `r scales::percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
-
-## Results
-
-```{r exp2-table, include=TRUE, results="asis"}
-# Create table of models for Experiment 2
-table_exp2 <- create_table(
-  models_exp2,
-  stub_anova = c("Part", "Condition", "Pt. × con."),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 2\\smallskip",
-  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all *F*s ≥ `r table_exp2$anov["Part", "N170_f"]`, all *p*s `r table_exp2$anov["Part", "N170_p"]` (see Table \@ref(tab:exp2-table)).
-Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, *F*`r table_exp2$anov["Condition", "N400_df"]` = `r table_exp2$anov["Condition", "N400_f"]`, *p* `r table_exp2$anov["Condition", "N400_p"]`.
-The part × condition interaction was significant in the P1 component, *F*`r table_exp2$anov["Pt.
-× con.", "P1_df"]` = `r table_exp2$anov["Pt.
-× con.", "P1_f"]`, *p* = `r table_exp2$anov["Pt.
-× con.", "P1_p"]`, and in the N400 component, *F*`r table_exp2$anov["Pt.
-× con.", "N400_df"]` = `r table_exp2$anov["Pt.
-× con.", "N400_f"]`, *p* `r table_exp2$anov["Pt.
-× con.", "N400_p"]`, but not in the N170 component, *F*`r table_exp2$anov["Pt.
-× con.", "N170_df"]` = `r table_exp2$anov["Pt.
-× con.", "N170_f"]`, *p* = `r table_exp2$anov["Pt.
-× con.", "N170_p"]`.
-
-```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:figure-2-caption)"}
-# Create plot for Experiment 2
-plot_grid(
-  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
-  plot_headings(spacing = c(10, 1, 10, 1, 10)),
-  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
-  plot_legends_erps(direction = "horizontal"),
-  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
-) + # Add some lines (to separate the parts)
-  annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.672, y = 0.15, yend = Inf, linetype = "dashed")
-```
-
-(ref:figure-2-caption) Results of Experiment 2\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\textit{Note.} 
-ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In an exact replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical significance (\textit{p} = .064).
-Ampl.
-= amplitude.\newline*\textit{p} \textless{} .05.
-**\textit{p} \textless{} .01.
-***\textit{p} \textless{} .001.
-
--->
-
-### ERPs Before Insight Was Occurring
-
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all *p*s ≥ `r table_exp2$conts["Pre-insight part", "P1_p"]` (see Table \@ref(tab:exp2-table) and Figure \@ref(fig:exp2-plot)).
-
-### ERPs While Insight Was Occurring
-
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with an enhancement of the N170 component, although this effect marginally failed to reach statistical significance, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`.
-The reduction of the N400 component during semantically informed perception remained significant, *b* = `r table_exp2$conts["Insight part", "N400_est"]` µV, *p* `r table_exp2$conts["Insight part", "N400_p"]`.
-
-### ERPs After Insight Had Occurred
-
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) again led to significantly reduced amplitudes in the N400 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Post-insight part", "N400_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "N400_p"]`.
-Also, P1 amplitudes in response these objects were significantly enlarged, *b* = `r table_exp2$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "P1_p"]`.
-
-### Joint Analysis of Experiments 1 and 2
-
-In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2.
-This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
-Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments\; @schad2020].
-This factor and its interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
-They were not included as by-participant random slopes because different participants took part in Experiments 1 and 2.
-Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit [@matuschek2017; @R-buildmer].
-The resulting formulas for the models can be found in Appendix B.
-
-```{r joint-import}
-# Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
-data_exp2 %>%
-  mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
-  bind_rows(aha, ., .id = "experiment") %>%
-  mutate(experiment = as_factor(experiment)) -> data_joint
-
-# Subset only the relevant conditions
-data_joint %>%
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> data_joint_subs
-```
-
-```{r joint-models, eval=rerun_models}
-# Contrast coding for experiment (2-1), condition (informed-naive), and part (2-1, 3-1)
-t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
-contrasts(data_joint_subs$experiment) <- MASS::ginv(contrasts_experiment)
-contrasts(data_joint_subs$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_joint_subs$part) <- MASS::ginv(contrasts_part)
-
-# New formula for LMMs
-form_joint <- buildmer::tabulate.formula(
-  ~ part * condition * experiment + 
-    (part * condition | participant) + 
-    (part * condition * experiment | item)
-) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-
-# Apply the function to compute the joint models for Experiments 1 and 2
-map(
-  comps$name,
-  compute_models,
-  formula = form_joint,
-  data = data_joint_subs,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-models.RDS") -> models_joint
-```
-
-```{r joint-table, include=TRUE, results="asis"}
-# Load linear mixed models
-models_joint <- readRDS("analysis/export/joint-models.RDS")
-
-# Create table of models for Experiments 1 and 2 combined
-table_joint <- create_table(
-  models_joint,
-  stub_anova = c(
-    "Part", "Condition", "Experiment", "Pt. × con.",
-    "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."
-  ),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption =
-    "Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\\smallskip",
-  note =
-    "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\\% confidence interval."
-)
-
-# Extract the follow-up contrast for the main effect of experiment
-suppressMessages(emmeans::emm_options(lmerTest.limit = Inf))
-suppressMessages(
-  emmeans::emmeans(
-    models_joint$N400$model,
-    specs = pairwise ~ experiment, infer = TRUE
-  )$contrasts %>%
-    as.data.frame() %>%
-    transmute(
-      est = round(estimate, 2) %>%
-        format(nsmall = 2, trim = TRUE),
-      p = round(`p.value`, 3) %>%
-        format(nsmall = 3, trim = TRUE) %>%
-        as.character() %>%
-        substr(2, nchar(.))
-    ) -> conts_N400_joint
-)
-```
-
-As shown in Table \@ref(tab:joint-table), the main effect of part was significant in the P1, N170, and N400 component, all *F*s ≥ `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Condition", "N400_df"]` = `r table_joint$anov["Condition", "N400_f"]`, *p* `r table_joint$anov["Condition", "N400_p"]`.
-Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s ≥ `r table_joint$anov["Pt.
-× con.", "P1_f"]`, all *p*s ≤ `r table_joint$anov["Pt.
-× con.", "P1_p"]`.
-There was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, with more negative amplitudes in Experiment 1 as compared to Experiment 2, *b* = `r conts_N400_joint$est`.
-However, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
-
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \@ref(tab:joint-table) and Figure \@ref(fig:joint-plot)).
-This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all *p*s ≥ `r table_joint$conts["Pre-insight part", "N400_p"]`, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N170_est"]` µV, *p* = `r table_joint$conts["Insight part", "N170_p"]`, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N400_est"]` µV, *p* `r table_joint$conts["Insight part", "N400_p"]`, and in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "N400_est"]` µV, *p* `r table_joint$conts["Post-insight part", "N400_p"]`, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_joint$conts["Post-insight part", "P1_p"]`.
-
-(ref:figure-3-caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\textit{Note.} 
-The violins and box plots show the distributions of the by-participant averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modeling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
-Ampl.
-= amplitude, 95\% CI = 95\% confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
-**\textit{p} \textless{} .01.
-***\textit{p} \textless{} .001.
-
--->
-
-```{r joint-plot, include=TRUE, fig.height=8, fig.cap = "(ref:figure-3-caption)"}
-# Create violin plot for Experiments 1 and 2 combined
-plot_grid(
-  plot_headings(spacing = c(10, 2, 10, 2, 10)),
-  plot_violins(data = data_joint_subs, models = models_joint),
-  nrow = 2, rel_heights = c(0.3, 6.7)
-) %>% plot_grid(
-  plot_legends_violins(),
-  nrow = 1, rel_widths = c(8.5, 1.5)
-) + # Add some lines (to separate the parts)
-  annotate(
-    geom = "segment", x = 11 / 34 * 0.85, xend = 11 / 34 * 0.85,
-    y = -Inf, yend = Inf, linetype = "dashed"
-  ) +
-  annotate(
-    geom = "segment", x = 23 / 34 * 0.85, xend = 23 / 34 * 0.85,
-    y = -Inf, yend = Inf, linetype = "dashed"
-  )
-```
-
-### Control Analysis
-
-```{r control-models, eval=rerun_models}
-# This time, we keep only the two conditions with matching keywords
-data_joint %>%
-  filter(condition %in% c("Informed", "Excl_informed")) %>%
-  droplevels() -> data_joint_control
-
-# Contrast coding for condition (informed-no_informed) and part (2-1, 3-1)
-contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_joint_control$part) <- MASS::ginv(contrasts_part)
-
-# Apply the function to re-compute the joint models
-map(
-  comps$name,
-  compute_models,
-  formula = form_joint,
-  data = data_joint_control,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-control-models.RDS") -> models_joint_control
-```
-
-```{r control-table}
-# Calculate average number of objects per condition in Experiments 1 and 2
-(stims_joint <- (objects_exp1 + objects_exp2) / 2)
-
-# Load linear mixed models
-models_joint_control <- readRDS("analysis/export/joint-control-models.RDS")
-
-# Create a table but don't print
-table_joint_control <- create_table(
-  models = models_joint_control,
-  stub_anova = c(
-    "Part", "Condition", "Experiment", "Pt. × con.",
-    "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."
-  ),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption =
-    "Results of Linear Mixed-Effects Regression Models With a Different Baseline",
-  note =
-    "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-One may raise concerns whether the modulation of the N170 component in the insight part genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it may be driven by the objects in the other, semantically naive condition.
-Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of signaling messages.
-To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
-Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, *b* = `r table_joint_control$conts["Insight part", "N400_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N400_p"]`.
-
-[^1]: Note that these percentages do not add up to 100% because some objects were excluded from all analyses if participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).
-
-## Discussion
-
-Experiment 2, which was an exact replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400).
-Objects for which participants experienced semantically informed perception via matching keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes.
-Note, however, that the effect in the N170 component marginally failed to reach the conventional level for statistical significance in this replication experiment.
-When the objects were presented once more without any semantic information, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.
-
-```{r exp3-preproc, eval=run_exp3}
-# Read behavioral data for Experiment 1
-list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp3
-
-# Update stimulus triggers
-preproc_params$event_id <- dict(
-  "match/upright" = as.integer(241),
-  "match/inverted" = as.integer(242),
-  "mismatch/upright" = as.integer(243),
-  "mismatch/inverted" = as.integer(244)
-)
-
-# Preprocess the EEG for Experiment 3 in Python
-fnames_exp3 <- list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE)
-py_run_string(
-  "epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **r.preproc_params)
-                  for fname, meta in zip(r.fnames_exp3, r.behav_exp3)]"
-)
-message("This worked!!!")
-py_run_string("epochs_exp3 = mne.epochs.concatenate_epochs(epochs_exp3)")
-message("This also worked!!!")
-py_run_string("epochs_exp3.save('export/exp3-epo.fif', overwrite=True)")
-py_run_string("del epochs_exp3")
-
-# Preprocess the EEG for Experiment 3 in Python
-map2(
-  .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp3,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp3
-
-# Backup epochs to the export folder
-epochs_exp3$save("analysis/export/exp3-epo.fif")
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
-  set_names(comps$name) %>%
-  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
-  write_tsv("analysis/export/exp3-data.tsv") -> data_exp3
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp3-gaverages.RDS")
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp3, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp3-objects.tsv")
-
-# Remove the epochs to free up memory
-rm(epochs_exp3)
-```
-
-```{r exp3-models, eval=run_exp3}
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp3-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    position = factor(position, levels = c("Inverted", "Upright")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
-    )),
-    participant = factor(participant),
-    item = factor(item)
-  ) %>%
-  # Remove any trials excluded from conditions and parts
-  filter(condition %in% c("Informed", "Naive") & part != "IV") %>%
-  droplevels() -> data_exp3
-
-# Define contrasts for position (inverted-upright), condition (informed-naive), and part (2-1, 3-1)
-t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
-contrasts(data_exp3$position) <- MASS::ginv(contrasts_position)
-contrasts(data_exp3$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp3$part) <- MASS::ginv(contrasts_part)
-
-# Define new formula for LMMs
-formula_exp3 <- buildmer::tabulate.formula(
-  ~ part * condition * position +
-    (part * condition * position | participant) +
-    (part * condition * position | item)
-) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-
-# Define new follow-up contrasts
-specs_exp3 <- pairwise ~ condition | position * part
-
-# Compute the models for Experiment 3
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp3,
-  data = data_exp3,
-  control = control,
-  specs = specs_exp3
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp3-models.RDS") -> models_exp3
-```
-
-```{r exp3-table, include=TRUE, results="asis", eval=run_exp3}
-# Create table of models for Experiment 3
-table_exp3 <- create_table(
-  models_exp3,
-  stub_anova = c(
-    "Part", "Condition", "Position", "Pt. × con.",
-    "Pt. × pos.", "Ins. × pos.", "Pt. × con. × pos."
-  ),
-  stub_contrasts = c(
-    "Part I, inverted", "Part I, upright", "Part II, inverted",
-    "Part II, upright", "Part III, inverted", "Part III, upright"
-  ),
-  caption = "Results of linear mixed-effects regression models for Experiment 3",
-  note = "Pt. = part, con. = condition, pos. = position, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-# General Discussion
-
-Here we investigated if obtaining a semantic understanding of previously unfamiliar objects has an influence on how we perceive them.
-To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
-For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, the information was non-matching, thus keeping the perception of the object semantically naive.
-We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
-When the same objects were presented again without the semantic information, the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
-We will discuss each of these effects in turn, starting with the latest (i.e., post-perceptual) effect and moving backward in time to the earlier (i.e., more perceptual) effects.
-
-The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
-Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) lessened participants' demand for effortful semantic processing in comparison to the naive condition [@kutas2011].
-This replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
-The time course of this effect and the computational role of the N400 [@lau2008; @rabovsky2018] suggest that it has a post-perceptual locus.
-
-In contrast to the N400, the N170 component (150--200 ms after object onset) was modulated while but not after the objects were presented together with the relevant semantic information.
-As such, it can be seen as an online marker of semantic insight, that is, participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
-The N170 is typically associated with the holistic perception of faces [@eimer2011; @sagiv2001] and other stimuli of visual expertise [@rossion2002; @tanaka2001].
-It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous findings with a similar experimental paradigm in the domain of face perception [@bentin2002]: In this study, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
-This effect was absent when a visual control stimulus (a non-face object) was shown instead of the intact face.
-In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
-Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
-Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level (i.e., holistic) perception of visual objects, integrating across their visual features.
-
-The P1 component (100--150 ms after object onset), unlike the N400 and N170 components, was modulated by semantic information only one trial after the information had been obtained.
-This is consistent with previous studies showing modulations of the P1 component when participants learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
-What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information).
-Instead, it can be observed as soon as one trial after semantic insight has happened.
-Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
-
-Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects.
-However, the finding that these two components were modulated in different parts of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
-It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem to reflect recurrent processing *within* the visual system [@wyatte2014].
-Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
-
-While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream for object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
-@hsieh2010 showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
-They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
-This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital cortex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
-Both of these cortical regions are consistent with the neural generators of the N170 and P1 components in the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
-
-On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999; but see @clarke2020].
-However, proponents of such a modular view have pointed out important shortcomings of previous studies that claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
-We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was being presented (in the pre-insight part).
-Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual locus from those with a post-perceptual locus.
-Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
-Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
-Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order and at the same location.
-Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these procedures have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the cognitive impenetrability of perception.
-
-An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @lindsay2020].
-In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
-For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this "barrier of meaning" [@mitchell2020].
-Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.
-
-A theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking at present.
-The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004; @hochstein2002] which posits that objects first enter our visual consciousness at an abstract, conceptual level.
-Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
-This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
-Besides this specific theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories [e.g., @clark2013; @lupyan2015; @panichello2013; @yuille2006].
-Despite the theoretical advances, the mechanistic details of these top-down effects at the algorithmic and implementational level [@marr1982] remain to be clarified.
-
-The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
-Another one is our reliance on rare and highly specialized objects (see Appendix A).
-This was necessary to induce the experience of semantic insight in a population of undergraduate students but the results may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
-Finally, the number participants (*n* = 24 per experiment) and trials (*k* $\approx$ 30 per part in the insight condition and *k* $\approx$ 50 per part in the naive condition) can be considered small by today's standards [@baker2020].
-Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances [see, e.g., the simulations by @matuschek2017].
-This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r table_exp1$conts["Insight part", "N170_p"]`) failed to reach statistical significance in the replication experiment (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
-To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).
-It should be noted, however, that the joint analysis of both data sets yielded a very robust N170 effect (*p* = `r table_joint$conts["Insight part", "N170_p"]`).
-This makes it less likely that the effect observed in Experiment 1 was due to a false positive and instead suggests that statistical power in Experiment 2 was insufficient to render the effect significant.
-Also note that the effect in the P1 component was statistically significant in both experiments individually, making an even stronger case for the susceptibility of early cortical processing to newly acquired knowledge about objects.
-
-[^2]: Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize [@samaha2018].
-
-Taken together, this study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the processing of the object.
-This influence is immediate in at least two different ways: First, it does not require extensive training and can instead be observed within the same trial in which the information has been presented (and/or one trial later).
-Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages---typically associated with semantic processing---but also at earlier stages---typically associated with visual perception itself and happening within less than a fifth of a second after the object is presented to us.
 
@@
 
+\begingroup
 \setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2022-01-25 analysis/manuscript.Rmd
Fix condition assignment and models

@@
 output_dir <- here("output")
+
+# File paths
+trials_file <- here(output_dir, "all_trials.csv")
+models_file <- here(output_dir, "models.RDS")
 ```
@@
         # Informed condition: Matching keywords and positive response
-        "Informed" =
-          item_id[phase == "Insight" & keywords == "Match" & response >= 3],
+        "Informed" = item_id[
+          phase == "Insight" & keywords == "Match" & response %in% c(3, 4)
+        ],
 
         # Naive condition: Non-matching keywords and negative response
-        "Naive" =
-          item_id[phase == "Insight" & keywords == "Non-match" & response <= 2],
+        "Naive" = item_id[
+          phase == "Insight" & keywords == "Non-match" & response %in% c(1, 2)
+        ],
 
         # Exclude: Matching keywords and negative response
-        "Exclude_informed" =
-          item_id[phase == "Insight" & keywords == "Match" & response <= 2],
+        "Exclude_informed" = item_id[
+          phase == "Insight" & keywords == "Match" & response %in% c(1, 2)
+        ],
 
         # Exclude: Non-matching keywords and positive response
-        "Exclude_naive" =
-          item_id[phase == "Insight" & keywords == "Non-match" & response >= 3],
+        "Exclude_naive" = item_id[
+          phase == "Insight" & keywords == "Non-match" & response %in% c(3, 4)
+        ],
 
@@
   export_dir = output_dir,
-  downsample_sfreq = 250.,
+  downsample_sfreq = 256.,
   # bad_channels = "auto",
@@
   highpass_freq = 0.1,
-  lowpass_freq = 40.,
+  lowpass_freq = 30.,
   triggers = c(221, 222),
@@
   average_by = c("phase/condition"),
-  perform_tfr = TRUE,
+  perform_tfr = FALSE,
   perm_contrasts = list(
@@
 clusters <- tibble(res[[3]])
-tfr_evokeds <- tibble(res[[4]])
-tfr_clusters <- tibble(res[[5]])
+# tfr_evokeds <- tibble(res[[4]])
+# tfr_clusters <- tibble(res[[5]])
 ```
@@
 # Read single trial data
-read_csv(here(output_dir, "all_trials.csv"), col_types = cols(
+read_csv(trials_file, col_types = cols(
   participant_id = col_factor(),
@@
 )) %>%
-  # Subset only the relevant conditions
-  mutate(condition = factor(
-    condition,
-    levels = c("Informed", "Naive", "Excl_informed")
-  )) %>%
-  drop_na() -> trials
+  # Mark unrealistically short RTs
+  mutate(rt = ifelse(rt < 200, NA, rt))
+
+# Filter relevant conditions for the main analysis
+trials %>%
+  mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
+  drop_na() -> trials_main
 
@@
   t() %>%
-  ginv() -> contrasts(trials$phase)
+  ginv() -> contrasts(trials_main$phase)
 
 # Contrast coding for condition
-cbind(
-  c("Informed" = 1, "Naive" = -1, "Excl_informed" = 0),
-  c("Informed" = 1, "Naive" = 0, "Excl_informed" = -1)
-) %>%
+cbind(c("Informed" = 1, "Naive" = -1)) %>%
   t() %>%
-  ginv() -> contrasts(trials$condition)
+  ginv() -> contrasts(trials_main$condition)
 
-# Prepare model formula
-mod_formula <- N170 ~ phase * condition +
+# Construct model formula
+form <- ~ phase * condition +
   (phase * condition | participant_id) +
@@
 deps <- c("P1", "N170", "N400")
-mod_lists <- map(deps, function(dep, mod_formula = form, mod_data = trials) {
+map(deps, function(dep, model_formula = form, model_data = trials_main) {
+
+  # Modify the formula such that fixed effects are always retained
+  model_formula %<>%
+    tabulate.formula() %>%
+    mutate(block = replace(block, is.na(grouping), "fixed"))
+
+  # Start a CPU cluster so that multiple models can be fitted in parallel
+  n_cores <- detectCores()
+  cl <- makeCluster(n_cores)
 
   # Find the best fitting model (see Matuschek et al., 2017, *JML*)
-  # Uses parallelization across all available CPU cores
-  n_cores <- detectCores()
-  cl <- makeCluster(n_cores)
   build <- buildmer(
     buildmerControl = buildmerControl(
-      formula = mod_formula,
-      data = mod_data,
-      # args = list("control" = lmerControl(
-      #   optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
-      # )),
-      direction = c("order", "backward"),
+      formula = model_formula,
+      data = model_data,
+      args = list("control" = lmerControl(
+        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
+      )),
+      direction = c("backward", "backward"),
       cl = cl,
@@
   # Add ERP component names
-  set_names(deps)
+  set_names(deps) -> models
 
 # Save models
-saveRDS(mod_lists, here(output_dir, "models.RDS"))
+saveRDS(models, models_file)
+```
+
+```{r, table_1, include=TRUE}
+# Read fitted models
+models <- readRDS(models_file)
+
+# View model summaries
+walk(models, function(model) {
+  print(formula(model$model))
+  cat("\n")
+  print(model$anova)
+  cat("\n")
+  print(model$contrasts)
+  cat("\n\n")
+})
 ```

### 2022-01-31 analysis/manuscript.Rmd
Update preprocessing

@@
 output_dir <- here("output")
+report_dir <- here(output_dir, "html_reports")
 
@@
 trials_file <- here(output_dir, "all_trials.csv")
+clusters_file <- here(output_dir, "clusters.csv")
 models_file <- here(output_dir, "models.RDS")
@@
   export_dir = output_dir,
-  downsample_sfreq = 256.,
-  # bad_channels = "auto",
+  report_dir = report_dir,
+  downsample_sfreq = 250.,
+  bad_channels = NULL,
   ocular_correction = "fastica",
   highpass_freq = 0.1,
-  lowpass_freq = 30.,
+  lowpass_freq = 40.,
   triggers = c(221, 222),
@@
   average_by = c("phase/condition"),
-  perform_tfr = FALSE,
+  perform_tfr = TRUE,
   perm_contrasts = list(
@@
 )
-
-# Extract results
-trials <- tibble(res[[1]])
-evokeds <- tibble(res[[2]])
-clusters <- tibble(res[[3]])
-# tfr_evokeds <- tibble(res[[4]])
-# tfr_clusters <- tibble(res[[5]])
 ```
@@
   # Mark unrealistically short RTs
-  mutate(rt = ifelse(rt < 200, NA, rt))
+  mutate(rt = ifelse(rt < 200, NA, rt)) -> trials
 
@@
 
+```{r, clusters, include=TRUE}
+read_csv(clusters_file, col_types = cols(
+  contrast = col_factor(levels = c(
+    "Pre-insight/Informed - Pre-insight/Naive",
+    "Insight/Informed - Insight/Naive",
+    "Post-insight/Informed - Post-insight/Naive"
+  ))
+)) %>%
+  pivot_longer(-c(contrast, stat, time), names_to = "channel") %>%
+  pivot_wider(names_from = stat, values_from = value) %>%
+  ggplot(aes(x = time, y = channel, fill = p_val)) +
+  facet_grid(~contrast) +
+  geom_raster() +
+  scale_fill_viridis_c()
+ggsave("clusters.pdf")
+```
+
 \newpage

### 2022-02-02 analysis/manuscript.Rmd
Update to latest pipeline version

@@
 # File paths
-trials_file <- here(output_dir, "all_trials.csv")
+trials_file <- here(output_dir, "trials.csv")
 clusters_file <- here(output_dir, "clusters.csv")
@@
   log_files = logs,
-  export_dir = output_dir,
+  output_dir = output_dir,
   report_dir = report_dir,
@@
 )) %>%
-  pivot_longer(-c(contrast, stat, time), names_to = "channel") %>%
-  pivot_wider(names_from = stat, values_from = value) %>%
-  ggplot(aes(x = time, y = channel, fill = p_val)) +
+  ggplot(aes(x = time, y = channel, fill = cl_index)) +
   facet_grid(~contrast) +

### 2022-02-04 analysis/manuscript.Rmd
Plot clusters

@@
 trials_file <- here(output_dir, "trials.csv")
+models_file <- here(output_dir, "models.RDS")
 clusters_file <- here(output_dir, "clusters.csv")
-models_file <- here(output_dir, "models.RDS")
+tfr_clusters_file <- here(output_dir, "tfr_clusters.csv")
 ```
@@
   }) -> logs
-
-# Install latest version of the EEG pipeline
-system("pip install --user --upgrade --pre --index https://test.pypi.org/simple/ hu-neuro-pipeline")
 
@@
 
-```{r, clusters, include=TRUE}
+```{r, clusters, include=TRUE, fig.height=8}
+# Read results of cluster-based permutation tests for ERPs
 read_csv(clusters_file, col_types = cols(
@@
   ))
-)) %>%
-  ggplot(aes(x = time, y = channel, fill = cl_index)) +
-  facet_grid(~contrast) +
+)) -> clusters
+
+# Plot thresholded cluster images
+clusters %>%
+  filter(p_val < .05) %>%
+  ggplot(aes(x = time, y = channel, fill = cluster)) +
+  facet_grid(~contrast, drop = FALSE) +
   geom_raster() +
-  scale_fill_viridis_c()
-ggsave("clusters.pdf")
+  theme(legend.position = "top")
+```
+
+```{r, tfr, include=TRUE, fig.height=12}
+# Read results of cluster-based permutation tests for TFR
+read_csv(tfr_clusters_file, col_types = cols(
+  contrast = col_factor(levels = c(
+    "Pre-insight/Informed - Pre-insight/Naive",
+    "Insight/Informed - Insight/Naive",
+    "Post-insight/Informed - Post-insight/Naive"
+  ))
+)) -> tfr_clusters
+
+# Plot thresholded cluster images for the insight phase
+tfr_clusters %>%
+  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
+  ggplot(aes(x = time, y = freq, fill = cluster)) +
+  facet_wrap(~channel) +
+  geom_raster() +
+  theme(legend.position = "top")
+
+# Plot thresholded cluster images for the post-insight phase
+tfr_clusters %>%
+  filter(
+    contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < .05
+  ) %>%
+  ggplot(aes(x = time, y = freq, fill = cluster)) +
+  facet_wrap(~channel) +
+  geom_raster() +
+  theme(legend.position = "top")
 ```

### 2022-05-28 analysis/manuscript.Rmd
Update cluster image

--- 2022-02-02 analysis/manuscript.Rmd
@@
   ))
-)) %>%
+)) -> clusters
+
+clusters %>%
+  filter(p_val < .05) %>%
   ggplot(aes(x = time, y = channel, fill = cl_index)) +
+  facet_grid(~contrast, drop = FALSE) +
+  geom_raster() +
+  scale_fill_viridis_c()
+
+  # Extract significant positive- or negative-going clusters
+  mutate(cl = case_when(
+    p_val < .05 & t_obs < 0 ~ paste0("neg (p = ", p_val, ")"),
+    p_val < .05 & t_obs > 0 ~ paste0("pos (p = ", p_val, ")"),
+    TRUE ~ "n.s."
+  ) %>%
+    factor()) %>%
+  # Plot cluster image
+  ggplot(aes(x = time, y = channel, fill = cl)) +
   facet_grid(~contrast) +
-  geom_raster() +
+  geom_raster()
   scale_fill_viridis_c()

### 2022-05-28 analysis/manuscript.Rmd
Update cluster image

@@
   filter(p_val < .05) %>%
-  ggplot(aes(x = time, y = channel, fill = cl_index)) +
+  ggplot(aes(x = time, y = channel, fill = cluster)) +
   facet_grid(~contrast, drop = FALSE) +
   geom_raster() +
-  scale_fill_viridis_c()
-
-  # Extract significant positive- or negative-going clusters
-  mutate(cl = case_when(
-    p_val < .05 & t_obs < 0 ~ paste0("neg (p = ", p_val, ")"),
-    p_val < .05 & t_obs > 0 ~ paste0("pos (p = ", p_val, ")"),
-    TRUE ~ "n.s."
-  ) %>%
-    factor()) %>%
-  # Plot cluster image
-  ggplot(aes(x = time, y = channel, fill = cl)) +
-  facet_grid(~contrast) +
-  geom_raster()
-  scale_fill_viridis_c()
-ggsave("clusters.pdf")
+  scale_fill_viridis_d()
 ```

### 2022-05-28 manuscript.Rmd
Re-arrange files

--- 2021-01-26 analysis/manuscript.Rmd
@@
 ---
-title             : |
-  | Event-Related Potentials of the Semantically Informed
-  | Perception of Unfamiliar Objects
-shorttitle        : "Semantic Knowledge and Unfamiliar Objects"
+title             : "Instant effects of semantic information on visual perception"
+shorttitle        : "Semantically informed perception"
 
@@
 
-  The preprocessed data and code for this study are openly available at https://osf.io/uksbc/.
-
-  We have no conflict of interest to disclose.
+  The authors declare no competing financial interests.
+  The preprocessed data and analaysis code for this study are openly available at https://osf.io/uksbc/.
 
@@
   Does our perception of an object change as soon as we discover what function it serves?
-This question is relevant not only for our everyday lives, where we may encounter novel tools and gadgets as parts of our dynamic working and private environments; it also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
-In this experiment, we showed participants (*n* = 24) pictures of 120 unfamiliar objects either together with matching information about their function---leading to semantically informed perception---or together with non-matching information---resulting in naive perception.
+  This question matters not only when we encounter novel tools or gadgets in our everyday lives, but also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+  Here, we showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
   We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component and reduced amplitudes in the N400 component.
-When the same objects were presented once more (without any information), the N400 effect persisted and we now also observed enlarged amplitudes in the P1 component in response to objects for which semantically informed perception had taken place.
-We replicated these novel findings in an independent sample (*n* = 24).
-Consistent with previous work, these results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (e.g., holistic perception; N170 component), and semantic processing (N400 component).
+  We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms) and reduced amplitudes in the N400 component (400--700 ms).
+  When the same objects were presented once more without any information, the N400 effect persisted and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
+  Consistent with previous work, our results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
+  We demonstrate for the first time that these effects are instantaneous in the sense that they can be observed within the same trial as well as one trial after the information has been given, providing strong evidence that cognition affects perception.
 
@@
 
-bibliography      : "manuscript_files/r-references.bib"
+bibliography      : ["manuscript_files/references.bib", "manuscript_files/r-references.bib"]
 csl               : "manuscript_files/apa.csl"
-zotero            : "aha"
+
 documentclass     : "apa7"
-classoption       : "man"
-output            :
+classoption       : "man,donotrepeattitle"
+fontsize          : "10pt"
+
+editor_options: 
+  chunk_output_type: console
+
+output:
   papaja::apa6_pdf:
-    latex_engine  : "xelatex"
+    latex_engine: xelatex
+  papaja::apa6_docx:default
 
@@
   - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
-  - \captionsetup[table]{font={stretch=1.5}}
-  - \captionsetup[figure]{font={stretch=1.5}}
+  - \captionsetup{font={stretch=1}, belowskip=15pt}
 ---
 
-```{r setup, include=FALSE}
-# Do you want to re-run the EEG preprocessing? Note that this can only be done with the raw data,
-# which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
-rerun_preproc <- FALSE
-
-# Do you want to re-run the linear mixed-effect models? This can be done even if only the
-# preprocessed single-trial data are available (from GitHub and/or the OSF). Note, however, that
-# fitting all models may take 24 hours or more.
-rerun_models <- FALSE
-
-# Do you want to run the analysis for Experiment 3?
-run_exp3 <- FALSE
-
-# Load packages
+```{r, setup, include=FALSE}
+# Load R packages
+library(buildmer)
+library(emmeans)
+library(here)
+library(knitr)
+library(lme4)
+library(lmerTest)
+library(MASS)
 library(papaja)
+library(parallel)
 library(reticulate)
@@
 library(magrittr)
-library(cowplot)
 
 # Set global chunk options
-knitr::opts_chunk$set(include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10)
+opts_chunk$set(fig.width = 10, include = FALSE, out.width = "100%")
 
-# Link to the bibliography file
-r_refs("analysis/manuscript_files/r-references.bib")
+# Write R packages to bibliography
+r_refs(here("manuscript_files", "r-references.bib"), append = FALSE)
 
-# Source plotting functions
-source("analysis/manuscript_files/functions_plots_tables.R")
+# What to (re-)run
+run <- list(
+  "preprocessing" = TRUE,
+  "modeling" = TRUE
+)
 
-# Create an export folder for results
-dir.create("analysis/export", showWarnings = FALSE)
+# Directory paths
+data_dir <- here("data")
+output_dir <- here("output")
+report_dir <- here(output_dir, "html_reports")
 
-# Define ERP components of interest
-comps <- tibble(
-  name = c("P1", "N170", "N400"),
-  tmin = c(100, 150, 400),
-  tmax = c(150, 200, 700),
-  roi = list(
+# File paths
+trials_file <- here(output_dir, "trials.csv")
+clusters_file <- here(output_dir, "clusters.csv")
+models_file <- here(output_dir, "models.RDS")
+```
+
+```{r, preprocessing, eval=run$preprocessing}
+# Process behavioral data
+c(
+  list.files(here(data_dir, "rt/exp1"), "*.txt", full.names = TRUE),
+  list.files(here(data_dir, "rt/exp2"), "*.txt", full.names = TRUE)
+) %>%
+  # Process each log file
+  map(function(log_file) {
+
+    # Read the file
+    read_tsv(
+      log_file,
+      col_types = cols(),
+      locale = locale(encoding = "latin1")
+    ) %>%
+      # Recode some columns
+      transmute(
+
+        # Phase of the experiment
+        phase = factor(Wdh,
+          levels = c(211, 212, 213),
+          labels = c("Pre-insight", "Insight", "Post-insight")
+        ),
+
+        # # Participant ID (unique for Experiments 1 and 2)
+        # participant = ifelse(
+        #   str_detect(log_file, "exp2"), str_c(VPNummer, "_exp2"), VPNummer
+        # ),
+
+        # Keyword conditions
+        keywords = factor(Bed,
+          levels = c("richtig", "falsch"),
+          labels = c("Match", "Non-match")
+        ),
+
+        # Behavioral responses
+        # 201: "I know what this is or have a strong assumption"  -> Recode as 4
+        # 202: "I have an assumption what this is"                -> Recode as 3
+        # 203: "I have rather no assumption what this is"         -> Recode as 2
+        # 204: "I don't know what this is and have no assumption" -> Recode as 1
+        response = 5 - (Tastencode - 200),
+
+        # Reaction times
+        rt = RT,
+        log_rt = log(RT),
+
+        # Item IDs
+        item_id = factor(StimID)
+      ) %>%
+      # Remove filler items
+      drop_na(keywords) -> log
+
+    # Assign items to conditions based on manipulation (matching vs. non-
+    # matching keywords) and the responses of the participants
+    items_per_condition <- with(log, {
+      list(
+
+        # Informed condition: Matching keywords and positive response
+        "Informed" = item_id[
+          phase == "Insight" & keywords == "Match" & response %in% c(3, 4)
+        ],
+
+        # Naive condition: Non-matching keywords and negative response
+        "Naive" = item_id[
+          phase == "Insight" & keywords == "Non-match" & response %in% c(1, 2)
+        ],
+
+        # Exclude: Matching keywords and negative response
+        "Exclude_informed" = item_id[
+          phase == "Insight" & keywords == "Match" & response %in% c(1, 2)
+        ],
+
+        # Exclude: Non-matching keywords and positive response
+        "Exclude_naive" = item_id[
+          phase == "Insight" & keywords == "Non-match" & response %in% c(3, 4)
+        ],
+
+        # Exclude: Positive response *before* any info was presented
+        "Exclude_known" = item_id[phase == "Pre-insight" & response == 4]
+      )
+    })
+
+    # Assign these conditions to the trials of all three phases
+    log$condition <- NA
+    for (condition in names(items_per_condition)) {
+      item_id <- items_per_condition[[condition]]
+      log$condition[log$item_id %in% item_id] <- condition
+    }
+
+    # Sort columns
+    log %>%
+      select(item_id, phase, condition, response, rt, log_rt) %>%
+      return()
+  }) -> logs
+
+# Import EEG pipeline from Python
+pipeline <- import("pipeline")
+
+# Get list of BrainVision EEG header files
+vhdr_files <- c(
+  list.files(here(data_dir, "eeg/exp1"), "*.vhdr", full.names = TRUE),
+  list.files(here(data_dir, "eeg/exp2"), "*.vhdr", full.names = TRUE)
+)
+
+# Process EEG data
+res <- pipeline$group_pipeline(
+  vhdr_files = vhdr_files,
+  log_files = logs,
+  output_dir = output_dir,
+  report_dir = report_dir,
+  downsample_sfreq = 125,
+  bad_channels = "auto",
+  ocular_correction = "auto",
+  highpass_freq = 0.1,
+  lowpass_freq = 40,
+  triggers = c(221, 222),
+  epochs_tmin = -0.5,
+  epochs_tmax = 1.5,
+  baseline_tmin = -0.2,
+  baseline_tmax = 0.0,
+  reject_peak_to_peak = 200,
+  components = list(
+    "name" = list("P1", "N170", "N400"),
+    "tmin" = list(0.1, 0.15, 0.4),
+    "tmax" = list(0.15, 0.2, 0.7),
+    "roi" = list(
       c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
@@
     )
+  ),
+  average_by = c("phase/condition"),
+  perform_tfr = TRUE,
+  tfr_subtract_evoked = FALSE,
+  tfr_freqs = seq(4, 40, by = 1.0),
+  tfr_cycles = seq(2, 20, by = 0.5),
+  tfr_baseline_tmin = -0.45,
+  tfr_baseline_tmax = -0.05,
+  tfr_baseline_mode = "percent",
+  perm_contrasts = list(
+    c("Pre-insight/Informed", "Pre-insight/Naive"),
+    c("Insight/Informed", "Insight/Naive"),
+    c("Post-insight/Informed", "Post-insight/Naive")
+  ),
+  perm_tmin = 0.0,
+  perm_tmax = 1.0,
+  n_jobs = 1
 )
@@
 
-Does our perception of an object change as soon as we discover what function it serves?
-In this study, we presented participants with unfamiliar objects that were preceded either by matching information about their function, leading to semantically informed perception, or by non-matching information, leading to naive perception.
-We expected semantically informed perception to differ from naive perception within the object processing hierarchy and we capitalized on the high temporal resolution of event-related potentials (ERPs) to find out at which stage (or stages) this was indeed the case.
-This allowed us to show for the first time that knowledge about the function of a previously unfamiliar object alters its early cortical processing in the same trial as it is being discovered and within less than 200 ms after the presentation of the object.
+```{r, modeling, eval=run$modeling}
+# Read single trial data
+read_csv(trials_file, col_types = cols(
+  participant_id = col_factor(),
+  item_id = col_factor(),
+  phase = col_factor(),
+  condition = col_factor()
+)) %>%
+  # Mark unrealistically short RTs
+  mutate(rt = ifelse(rt < 200, NA, rt)) -> trials
 
-The claim that higher-level cognitive capacities such as knowledge or language can modulate lower-level perceptual processes has been the source of a long-running debate.
-This debate revolves around the question of whether or not our perception of the (visual) world is "cognitively impenetrable" [@pylyshyn1999] or, in other words, determined solely by the visual input reaching our retina.
-According to one view, higher-level mental states and functions are not able to penetrate perception and kick in only after lower-level perceptual analysis of the visual input has taken pace [e.g., @firestone2016; @fodor1983; @pylyshyn1999].
-Visual perception itself is treated as an encapsulated module that processes the retinal input in a feed-forward fashion, progressing from lower areas with smaller receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012; @marr1982].
+# Filter relevant conditions for the main analysis
+trials %>%
+  mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
+  drop_na() -> trials_main
 
-This position is challenged by the alternative view that perceptual processing dynamically interacts with other aspects of cognition from early on [e.g., @churchland1994; @lupyan2015; @teufel2017].
-The myriad feedback connections from areas higher up the visual hierarchy (e.g., the middle temporal and lateral occipital cortices) to early visual areas [e.g., V1 and V2\; @bullier2001; @gilbert2013]---as well as behavioral evidence---have inspired theories of visual perception that emphasize the top-down influence of cognitive processes.
-For instance, the reverse hierarchy theory [@ahissar2004; @hochstein2002] assumes that conscious visual perception occurs initially at the level of whole objects or object categories.
-Only after this high-level interpretation of the stimulus has been obtained, its more for fine grained visual details---if relevant for the current task---are being accessed from lower-level areas via top-down connections.
-Along similar lines, the label feedback hypothesis [@lupyan2012] posits that the activation of an object's name (i.e., a high level property) transiently warps perceptual space so that its diagnostic visual features are being processed preferentially.
-Finally, an active role of top-down influences is also promoted by theories of vision in the framework of Bayesian inference and predictive coding [e.g., @clark2013; @lupyan2015; @panichello2013; @yuille2006].
+# Contrast coding for phase
+cbind(
+  c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
+  c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
+) %>%
+  t() %>%
+  ginv() -> contrasts(trials_main$phase)
 
-Empirical findings from experimental psychology have recently added additional support to the view that perception can indeed be penetrated by other aspects of cognition [for review, see @collins2014; @vetter2014].
-These aspects of cognition may include transient states such as emotions [e.g., @bocanegra2009; @phelps2016] or intentions [e.g., @balcetis2010; @cole2012] as well as learned capacities such as language [e.g., @boutonnet2015; @maier2018; @mo2011] or declarative knowledge about faces [e.g., @abdelrahman2011; @suess2015; @eiserbeck2020] and objects [e.g., @abdelrahman2008; @gauthier2003; @weller2019].
-Despite this wealth of empirical evidence, critics of the idea that cognitive functions can penetrate perception have remained skeptical and pointed out important methodological shortcomings in large parts of this literature [@firestone2016; @machery2015].
-They argue, for example, that most behavioral paradigms have not been able to discern between perceptual and post-perceptual (e.g., memory-related) effects.
-Furthermore, cognitive influences in some studies were confounded with differences in the low-level visual input itself.
-We will revisit these and other potential pitfalls with regards to the present study in the Discussion section once we have laid out our methodology and results.
+# Contrast coding for condition
+cbind(c("Informed" = 1, "Naive" = -1)) %>%
+  t() %>%
+  ginv() -> contrasts(trials_main$condition)
 
-In general, however, it is important to note that one productive way to circumvent at least some of these concerns is to use neurophysiological recording methods such as ERPs [@luck2014]: Their high temporal resolution allows for a direct test of which processing stages---perceptual and/or post-perceptual---are influenced by higher-level capacities such as semantic knowledge.
-This is made possible by the fact that when participants are presented with visual stimuli, their averaged brain responses show characteristic deflections (ERP components), each of them with its typical polarity (positive or negative), peak latency, spatial scalp distribution, and functional role(s).
+# Construct model formula
+form <- ~ phase * condition +
+  (phase * condition | participant_id) +
+  (phase * condition | item_id)
 
-The visual P1 component of the ERP refers to a positive deflection peaking as early as 100--150 ms after stimulus onset at occipital channels.
-It is generated by multiple sources in the extrastriate cortices of the middle occipital and fusiform gyri [@dirusso2001; @mangun1995].
-The P1 is thought to reflect the processing of low-level visual characteristics of the stimulus [e.g., size, luminance, and contrast\; @dirusso2001; @luck2014; @johannes1995], which is why it being modulated by higher-level cognitive capacities would challenge a purely bottom-up, encapsulated view of visual perception.
-It is well-established that the P1 is enhanced when participants pay attention to the spatial location of a stimulus [@luck2000; @mangun1995; @mangun1991] but there is also more recent evidence for higher-level cognitive influences that go beyond spatial attention (see below).
+# Fit linear mixed models
+deps <- c("P1", "N170", "N400")
+map(deps, function(dep, model_formula = form, model_data = trials_main) {
 
-The visual N170 (or N1) component refers to the negative deflection following the P1 and is maximal around 150--200 ms after stimulus onset at occipito-temporal channels.
-Just as the P1, it is influenced by visual parameters of the stimulus [@johannes1995] and by selective attention, especially when participants are required to discriminate between different visual stimuli [@vogel2000; @mangun1991].
-The N170 is enlarged (i.e., more negative) in response to faces [@bentin1996; @rossion2011] and other visual stimuli for which one happens to be an expert [e.g., birds, dogs, or cars\; @gauthier2003a; @tanaka2001].
-This category selectivity seems to reflect both the processing of individual visual features of the respective objects (including faces) as well as the holistic configuration of these features [@eimer2011; @jacques2010; @rossion1999; @sagiv2001].
-Thus, a modulation of the N170 by cognitive capacities such as knowledge would suggest these capacities having an influence on higher-level, holistic perception of the visual stimulus.
+  # Modify the formula such that fixed effects are always retained
+  model_formula %<>%
+    tabulate.formula() %>%
+    mutate(block = replace(block, is.na(grouping), "fixed"))
 
-Finally, the N400 component refers to more negative ERP amplitudes when stimuli require more as compared to less resources for semantic processing or integration [@kutas2011; @lau2008; @rabovsky2018].
-It begins approximately 300 ms after stimulus onset and is most pronounced at centro-parietal channels.
-A modulation of the N400 component by cognitive capacities such as knowledge can be taken as evidence for a post-perceptual influence on stimulus processing.
+  # Start a CPU cluster so that multiple models can be fitted in parallel
+  n_cores <- detectCores()
+  cl <- makeCluster(n_cores)
 
-Previous studies have focused on these and other ERP components to investigate which processing stages are indeed influenced by knowledge about visual objects [@abdelrahman2008; @gratton2009; @maier2014; @maier2019; @rossion2002; @rossion2004; @tanaka2001; @samaha2018; @weller2019].
-Together, they suggest that not only higher-level ERPs like the semantic N400 component are influenced by acquiring information about objects, but also earlier components that typically reflect bottom-up visual processing.
-This was the case, for instance, when participants were presented with a range of unfamiliar objects, receiving in-depth verbal descriptions about their function for half of the objects and irrelevant verbal information (i.e., cooking recipes) for the other half of the objects [@abdelrahman2008, Experiment 1].
-After this learning phase, the same objects were presented in three different ERP tasks which did not require explicit access to any of the learned semantic information.
-In all three tasks, ERP amplitudes in response to objects for which in-depth knowledge had been acquired differed from those in response to objects for which this had not been the case.
-These differences occurred not just in the N400 component, indexing a modulation of post-perceptual semantic processing, but also in the P1 component, suggesting a top-down modulation of lower-level perceptual processing.
-Interestingly, the ERPs observed for previously unfamiliar objects with newly acquired in-depth knowledge were qualitatively similar to those for untrained but well-known objects.
-The modulation of the P1 component has recently been replicated when the same objects were presented under circumstances of limited attentional resources in an attentional blink paradigm [@weller2019].
-In this study, the (neurophysiological) differences in P1 amplitudes between objects with in-depth versus minimal knowledge were correlated with (behavioral) differences in their detection rate during the attentional blink.
-This can be taken as further evidence for an influence of semantic knowledge on the early visual perception of unfamiliar objects.
-
-A complementary approach has been taken in a recent study investigating the ERPs in response to familiar (rather than unfamiliar) objects which were rendered difficult to recognize by converting them to two-tone, "Mooney" images [@samaha2018, Experiment 4].
-In this experiment, participants were trained with meaningful verbal cues, telling them what kind of objects they should look for in the images, or with a non-meaningful perceptual task, familiarizing them with the images but not with their semantic content.
-When the EEG was measured in a delayed matching task later on, the two types of training led to differential effects, again suggesting a modulation of lower-level visual perception: Over left posterior electrodes, P1 amplitudes were larger and alpha-band power was higher for meaning-trained images than for perceptually-trained images.
-As before, this effect of perceiving objects in a semantically informed way seems to be behaviorally relevant, as participants tended respond faster and more accurately to meaning-trained as compared to perceptually-trained images in the matching task.
-This alternative approach further corroborates an early influence of semantic information on the visual perception of objects.
-
-All the previously mentioned studies have in common that they investigated the effects of semantic knowledge on the visual perception of objects only *after* an extensive learning phase had taken place [@abdelrahman2008; @gauthier2003; @maier2014; @maier2019; @rossion2002; @rossion2004; @samaha2018; @weller2019].
-Participants performed one or multiple training sessions during which they encountered each object together with its respective label or description multiple times.
-The EEG was usually not measured---or at least not analyzed and reported---during these training sessions, which sometimes took place on a separate day [@abdelrahman2008; @maier2014; @maier2019] or were spread out across multiple days or weeks [@rossion2002; @rossion2004].
-While experimental designs with such substantive training maximize the chances of detecting even subtle top-down effects of the knowledge acquired, they leave at least three conceptual questions unresolved.
-
-The first question is if we can detect any electrophysiological correlates of *semantic insight*, that is, the critical presentation during which an understanding of the previously unfamiliar object is happening (instead of asking if this understanding leads to differential effects in an orthogonal task later on).
-The second question is how much learning is actually necessary before reliable top-down effects of knowledge on ERP amplitudes can be obtained: Does it actually take dozens of repetitions per object or may a single exposure to the object together with the relevant semantic information be enough?
-The third and closely related question is about the nature of the effects of knowledge on perception: Are they reflecting genuine top-down effects of the semantic system altering perception online (while the object is being perceived), or do they merely reflect the (re-)activation of stored representations of the objects which have been altered over the course of the learning process?
-By measuring the ERPs before, during, and after participants received semantic hints about unfamiliar objects, we were able to provide tentative answers to all three of these questions.
-
-In the two experiments subsequently reported, participants were presented with real-word objects that were presumed to be unfamiliar to most of them.
-They first viewed each of these objects without any semantic information.
-This first part served as a naive baseline to rule out that ERPs would differ in response to the objects based solely on low-level visual differences.
-Next, participants viewed each unfamiliar object for a second time, now preceded by verbal keywords.
-These keywords could either be matching the typical function of the object, thus making it possible for participants to understand what kind of object they were viewing, or they could be non-matching by describing the function of a different object, thus keeping the perception of the object semantically naive.
-During this second part, we were able to measure the online influence of semantic insight on object-evoked ERPs as it happened.
-Finally, the objects were presented for a third time (without keywords, as in the first part) to investigate downstream effects of having acquired semantic knowledge about them---thereby mimicking previous studies [e.g., @abdelrahman2008; @samaha2018; @weller2019].
-In all three parts, we examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component, 100--150 ms), higher-level visual perception (N170 component, 150--200 ms), and semantic processing (N400 component, 400--700 ms).
-
-# Experiment 1
-
-## Method
-
-### Participants
-
-Participants for Experiment 1 were 24 German native speakers (13 female, 11 male) with a mean age of 24 years (range 18 to 31) and no history of psychological disorder or treatment.
-No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
-All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
-They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-
-### Materials
-
-Stimuli for Experiments 1 and 2 consisted of 240 grayscale photographs of real-world objects, 120 of which were well-known everyday objects (e.g., a bicycle, a toothbrush), serving as filler stimuli of no interest, whereas the other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum).
-A list of these unfamiliar objects can be found in Appendix A.
-All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
-At a standardized viewing distance of 90 cm, the images of the objects subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
-
-For each unfamiliar object, a pair of keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
-As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to hamper such an understanding and keep the perception of the object semantically naive.
-All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
-The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
-
-### Procedure
-
-Each experimental session consisted of three parts (see Figure \@ref(fig:exp1-plot)A).
-In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
-Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
-The inter-trial interval until the presentation of the next fixation cross was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
-The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
-
-```{python def_functions, eval=rerun_preproc}
-# Import libraries
-import mne
-
-# Define function for preprocessing the EEG data
-def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax,
-    baseline, reject):
-    # Read EEG data in microvolts
-    raw = mne.io.read_raw_brainvision(vhdr_fname, scale=1e6, preload=True)
-    # Create virtual EOG channels
-    raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
-    raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
-    raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
-    # Add EasyCap electrode layout, removing any excessive channels
-    montage = mne.channels.make_standard_montage("easycap-M1")
-    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
-    raw.set_montage(montage=montage)
-    # Re-reference to common average
-    raw, _ = mne.set_eeg_reference(raw, "average")
-    # Run ICA on a copy of the data
-    filt_raw = raw.copy()
-    filt_raw.load_data().filter(l_freq=1, h_freq=None)
-    ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
-    ica.fit(filt_raw)
-    # Remove bad components based on correlations with EOG
-    eog_indices, eog_scores = ica.find_bads_eog(raw)
-    ica.exclude = eog_indices
-    raw = ica.apply(raw)
-    # Apply band-pass filter
-    raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
-    # Epoching including baseline correction
-    events, _ = mne.events_from_annotations(raw, verbose=False)
-    epochs = mne.Epochs(
-        raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True
-    )
-    # Add behavioral data
-    epochs.metadata = metadata
-    # Reject bad epochs
-    epochs = epochs.drop_bad(reject=reject)
-    return epochs
-
-# Define function to compute averaged waveforms by part and condition
-def compute_evokeds(epochs, grand=True, data_only=True):
-    # Define lists of participants, parts, and conditions
-    ps = epochs.metadata["participant"].unique()
-    pts = ["I", "II", "III"]
-    cns = ["Informed", "Naive"]
-    # Define function to compute a single by-participant waveform
-    def compute_evoked(epochs, pt, cn, p):
-        query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
-        return epochs[query].average()
-    # Create a dict with by-participant waveforms nested in conditions nested in parts
-    avgs = {pt: {cn: [compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
-    # If needed, compute grand-averaged waveforms across participants
-    if grand:
-        avgs = {pt: {cn: mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
-    # If needed, extract only the data from the evoked MNE objects
-    if data_only:
-        if grand:
-            avgs = {pt: {cn: avgs[pt][cn].data for cn in cns} for pt in pts}
-        else:
-            ps_num = range(0, len(ps))
-            avgs = {pt: {cn: [avgs[pt][cn][p].data for p in ps_num] for cn in cns} for pt in pts}
-    return avgs
-
-# Define function to compute single-trial mean ERP amplitudes from epochs
-def compute_erps(epochs, name, tmin, tmax, roi):
-    # Average across electrodes in the ROI
-    roi_idx = mne.pick_channels(epochs.ch_names, roi)
-    epochs_roi = mne.channels.combine_channels(epochs, dict(roi=roi_idx))
-    # Average across samples in the time window
-    import numpy as np
-    tmin_s, tmax_s = tmin / 1000, tmax / 1000
-    times_idx = np.where(np.logical_and(epochs.times >= tmin_s, epochs.times <= tmax_s))
-    erps = epochs_roi.get_data()[:, 0, times_idx].mean(axis=(1, 2))
-    return erps
-
-```
-
-```{r exp1-preproc, eval=rerun_preproc}
-# Define function for reading and formatting the behavioral data
-read_behav <- function(txt_fname) {
-  # Read the log file
-  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
-  # Rename columns for participant and item IDs
-  dat %<>% rename(participant = VPNummer, item = StimID) %>%
-    # Add a column for the part of the experiment
-    mutate(part = case_when(
-      Wdh %in% c(211, 231) ~ "I",
-      Wdh %in% c(212, 232) ~ "II",
-      Wdh %in% c(213, 233) ~ "III",
-      Wdh == 234 ~ "IV"
-    ) %>% as_factor()) %>%
-    # Remove filler stimuli (i.e.,well-known objects)
-    filter(bek_unbek != "bekannt")
-  # Assign stimuli to conditions based on keywords and button presses
-  excl_known <- dat %>%
-    filter(part == "I" & Tastencode %in% c(201, 251)) %>%
-    pull(item)
-  excl_informed <- dat %>%
-    filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>%
-    pull(item)
-  excl_naive <- dat %>%
-    filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>%
-    pull(item)
-  informed <- dat %>%
-    filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>%
-    pull(item)
-  naive <- dat %>%
-    filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>%
-    pull(item)
-  # Create a new condition for the experimental condition
-  dat %<>% mutate(condition = case_when(
-    item %in% excl_known ~ "Excl_known",
-    item %in% excl_informed ~ "Excl_informed",
-    item %in% excl_naive ~ "Excl_naive",
-    item %in% informed ~ "Informed",
-    item %in% naive ~ "Naive"
-  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
-  # In Experiment 3, we need an additional column for position (upright vs. inverted)
-  if ("richtig_inv" %in% dat$Bed) {
-    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
-      # Return only relevant columns
-      select(part, position, condition, participant, item, RT)
-  } else {
-    # Return only relevant columns
-    dat %<>% select(part, condition, participant, item, RT)
-  }
-  return(dat)
-}
-
-# Read behavioral data for Experiment 1
-list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp1
-
-# Define global parameters for EEG preprocessing
-preproc_params <- list(
-  # Number of ICA components
-  n_components = as.integer(15),
-  # ICA methods
-  method = "fastica",
-  # Lower edge of pass-band filter
-  l_freq = 0.1,
-  # Upper edge of pass-band filter
-  h_freq = 30,
-  # Event trigger codes
-  event_id = dict(match = as.integer(221), mismatch = as.integer(222)),
-  # Beginning of epochs in s
-  tmin = -0.5,
-  # End of epochs in s
-  tmax = 1.498,
-  # Baseline interval in s
-  baseline = tuple(-0.2, 0),
-  # Artifact rejection threshold in microvolts
-  reject = dict(eeg = 200)
-)
-
-# Preprocess the EEG for Experiment 1 in Python
-map2(
-  .x = list.files("data/exp1/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp1,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp1
-
-# Backup epochs to the export folder
-epochs_exp1$save("analysis/export/exp1-epo.fif")
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs = epochs_exp1) %>%
-  set_names(comps$name) %>%
-  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
-  write_tsv("analysis/export/exp1-data.tsv") -> data_exp1
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp1-gaverages.RDS")
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp1, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp1-objects.tsv")
-
-# Get standard EasyCap electrode positions and project to 2D space
-py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
-  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
-  read_tsv(col_types = cols()) %>%
-  rename(electrode = Site) %>%
-  inner_join(tibble(electrode = epochs_exp1$ch_names), ., by = "electrode") %>%
-  mutate(
-    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
-    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
-  ) %>%
-  write_tsv("analysis/export/montage.tsv")
-
-# Remove the epochs to free up memory
-rm(epochs_exp1)
-```
-
-```{r exp1-models, eval=rerun_models}
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
+  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
+  build <- buildmer(
+    buildmerControl = buildmerControl(
+      formula = model_formula,
+      data = model_data,
+      args = list("control" = lmerControl(
+        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
       )),
-    participant = factor(participant),
-    item = factor(item)
-  ) %>%
-  # Remove any trials excluded from conditions
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> data_exp1
-
-# Define contrast coding for condition (informed-naive) and part (2-1, 3-1)
-contrasts_condition <- t(cbind(
-  c("Informed" = 1, "Naive" = -1)
-))
-contrasts_part <- t(cbind(
-  c("I" = -1, "II" = 1, "III" = 0),
-  c("I" = 0, "II" = -1, "III" = 1)
-))
-
-# Apply these contrasts to the factors in the data
-contrasts(data_exp1$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp1$part) <- MASS::ginv(contrasts_part)
-
-# Define formula and parameters for linear mixed-effects regression models (LMMs)
-formula_exp12 <- buildmer::tabulate.formula(
-  ~ part * condition + (part * condition | participant) + (part * condition | item)
-) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-control <- lme4::lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
-
-# Define formula for follow-up contrasts
-specs_exp12 <- pairwise ~ condition | part
-
-# Define function to compute LMMs and follow-up contrasts for each component
-compute_models <- function(dep, formula, data, control, specs) {
-  require(lmerTest)
-  require(buildmer)
-  require(emmeans)
-  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  build <- buildmer(
-    control = control,
-    REML = FALSE,
-    buildmerControl = buildmerControl(
-      formula = formula,
-      data = data,
       direction = c("backward", "backward"),
-      elim = function(logp) exp(logp) >= .20,
+      cl = cl,
+      elim = LRTalpha(.20),
       calc.anova = TRUE,
@@
   )
-  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans
-  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts
-  modlist <- list(
-    model = build@model,
-    anova = build@anova,
-    summary = build@summary,
-    means = means %>% as.data.frame(),
-    contrasts = conts %>% as.data.frame()
-  )
-  return(modlist)
-}
+  stopCluster(cl)
 
-# Compute the models for Experiment 1
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp12,
-  data = data_exp1,
-  control = control,
-  specs = specs_exp12
+  # Compute marginal means and contrasts
+  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
+  specs <- pairwise ~ condition | phase
+  em <- emmeans(build@model, specs, infer = TRUE)
+
+  # Create list of returns
+  list(
+    "model" = build@model,
+    "summary" = build@summary,
+    "anova" = build@anova,
+    "means" = em$emmeans,
+    "contrasts" = em$contrasts
   ) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
+    return()
+}) %>%
+  # Add ERP component names
+  set_names(deps) -> models
+
+# Save models
+saveRDS(models, models_file)
 ```
 
-```{r exp1-import}
-# Load average number of objects per condition
-(read_tsv("analysis/export/exp1-objects.tsv", col_types = cols()) %>%
-   summarise(across(.cols = -Participant, .fns = mean)) %>%
-   slice(1) %>% unlist() -> objects_exp1)
+```{r, table_1, include=TRUE}
+# Read fitted models
+models <- readRDS(models_file)
 
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
-    ),
-    participant = factor(participant),
-    item = factor(item)
-  ) -> data_exp1
-
-# Check number of rejected epochs
-data_exp1 %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n) -> rejected_exp1
-mean(rejected_exp1)    # Mean
-median(rejected_exp1)  # Median
-range(rejected_exp1)   # Range
-
-# Load grand-averaged ERPs and linear mixed models
-evokeds_exp1 <- readRDS("analysis/export/exp1-gaverages.RDS")
-models_exp1 <- readRDS("analysis/export/exp1-models.RDS")
+# View model summaries
+walk(models, function(model) {
+  print(formula(model$model))
+  cat("\n")
+  print(model$anova)
+  cat("\n")
+  print(model$contrasts)
+  cat("\n\n")
+})
 ```
 
-```{r exp1-plot, include=TRUE, fig.height=11, fig.cap = "(ref:figure-1-caption)"}
-# Load sample time points and electrode montage
-montage <- read_tsv("analysis/export/montage.tsv", col_types = cols())
+```{r, clusters, include=TRUE}
+read_csv(clusters_file, col_types = cols(
+  contrast = col_factor(levels = c(
+    "Pre-insight/Informed - Pre-insight/Naive",
+    "Insight/Informed - Insight/Naive",
+    "Post-insight/Informed - Post-insight/Naive"
+  ))
+)) -> clusters
 
-# Create plot for Experiment 1
-plot_grid(
-  plot_trials(),
-  plot_erps(comps = comps, evokeds = evokeds_exp1, models = models_exp1, montage = montage),
-  nrow = 2, rel_heights = c(5, 6), labels = c("A", "B"), label_fontfamily = "Helvetica"
-) + # Add some lines (to separate the parts) and the legend
-  annotate(geom = "segment", x = 0.328, xend = 0.328, y = -Inf, yend = 0.53, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.672, y = -Inf, yend = 0.53, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.328, xend = 0.28, y = 0.53, yend = 0.58, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.72, y = 0.53, yend = 0.58, linetype = "dashed") +  
-  annotate(geom = "segment", x = 0.28, xend = 0.28, y = 0.58, yend = Inf, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.72, xend = 0.72, y = 0.58, yend = Inf, linetype = "dashed") +
-  draw_plot(plot_legends_erps(direction = "vertical"), x = 0.405, y = 0.422, width = 1, height = 1)
+clusters %>%
+  filter(p_val < .05) %>%
+  ggplot(aes(x = time, y = channel, fill = cluster)) +
+  facet_grid(~contrast, drop = FALSE) +
+  geom_raster() +
+  scale_fill_viridis_d()
 ```
-
-(ref:figure-1-caption) Procedure and Results of Experiment 1\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\textit{Note.} 
-(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception.
-In the post-insight part, the same objects were presented again without the keywords.
-(B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts.
-Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part.
-Ampl.
-= amplitude.\newline
-*\textit{p} \textless{} .05. **\textit{p} \textless{} .01. ***\textit{p} \textless{} .001.
-
--->
-
-In the *insight* part, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
-Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
-Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
-The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).
-
-Finally, in the *post-insight* part, the unfamiliar objects were presented for a third time with an identical trial structure as in the pre-insight part, that is, without any keywords.
-Note that the insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight part (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight part (without keywords) before moving on to the next block consisting of 30 different objects.
-They continued like this until all four blocks were completed in both parts.
-In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight part and 120 unfamiliar objects in the pre-insight, insight, and post-insight parts).
-It took participants approximately 35 minutes to complete.
-
-### EEG Recording and Preprocessing
-
-The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system [@americanelectroencephalographicsociety1991] and referenced online to an external electrode placed on the left mastoid (M1).
-Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively.
-During the recording, electrode impedance was kept below 5 kΩ.
-An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
-
-Offline, the data were preprocessed using the MNE software [Version 0.21.0\; @gramfort2013] in Python [Version 3.8.5\; @vanrossum2009].
-First, all scalp electrodes were re-referenced to the common average.
-Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
-The first 15 components were extracted by the FastICA algorithm [@hyvärinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find\_bads\_eog* function.
-After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the visual presentation of each unfamiliar object.
-The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset.
-Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
-This led to the exclusion of an average of `r format(round(mean(rejected_exp1), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp1)/360, accuracy = 0.1)`; range `r min(rejected_exp1)` to `r max(rejected_exp1)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component (for the positions of these electrodes on the scalp, see the topographies in Figure \@ref(fig:exp1-plot)B).
-
-### Statistical Analysis
-
-First, because we were interested in the effects of knowledge on perceiving *unfamiliar* objects only, we excluded objects from all further analyses when participants classified them as being known in the pre-insight part (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r format(round(objects_exp1["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analysis was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \@ref(fig:exp1-plot)A).
-Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if participants indicated knowing what the object was or having an assumption.
-This was the case for an average of `r format(round(objects_exp1["Informed"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords).
-Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if participants indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of `r format(round(objects_exp1["Naive"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp1["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts.
-This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any down-stream effects on the subsequent perception of the objects (post-insight part).
-
-The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models [@baayen2008; @frömer2018].
-For the purpose of the present study, these models have at least three desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant averages.
-First, they can leverage all of the information that is present in the data set on the single trial level, some of which would be lost when computing averages.
-Second, they can account simultaneously for the non-independence of data points coming from the same participant and/or from the same item.
-In contrast, the neglect of the item as a random variable in by-participant ANOVAs can lead to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study [@bürki2018; @judd2012].
-Finally, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions.
-Such a situation is inevitable when the assignment of trials to conditions is co-determined by the experimental manipulation and the behavior of participants in response to this manipulation [e.g., @fröber2017].
-
-Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
-All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e., subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition.
-For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to @schad2020.
-To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
-We then performed a model selection algorithm as proposed by @matuschek2017 in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data equally well as the complex model [determined by *p* ≥ .20\; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the formulas after model selection).
-All models were computed in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4].
-The optimizer function *bobyqa* with 20,000 iterations was used for maximum likelihood estimation.
-The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`\; @R-buildmer].
-
-Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the semantically informed against the naive condition within the pre-insight, \mbox{insight}, and post-insight parts.
-This was achieved using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
-All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
-
-The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (<https://osf.io/uksbc/>).
-We are not able to share the raw EEG data openly because we did not obtain participants' informed consent to do so.
-
-## Results
-
-Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function.
-In the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception.
-The other half were preceded by non-matching keywords, keeping the perception of the object semantically naive.
-The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \@ref(fig:exp1-plot)A), thereby making sure that semantically informed and naive perception did indeed occur.
-The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, the N170 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.
-
-```{r exp1-table, include=TRUE, results="asis"}
-# Create table of models for Experiment 1
-table_exp1 <- create_table(
-  models = models_exp1,
-  stub_anova = c("Part", "Condition", "Pt. × con."),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 1\\smallskip",
-  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the part of the experiment, all *F*s ≥ `r table_exp1$anov["Part", "P1_f"]`, all *p*s `r table_exp1$anov["Part", "P1_p"]` (see Table \@ref(tab:exp1-table)).
-In addition, N400 amplitudes differed between the informed and the naive condition averaged across the three parts of the experiment, *F*`r table_exp1$anov["Condition", "N400_df"]` = `r table_exp1$anov["Condition", "N400_f"]`, *p* = `r table_exp1$anov["Condition", "N400_p"]`.
-Crucially, the part × condition interaction was significant in the N170 component, *F*`r table_exp1$anov["Pt.
-× con.", "N170_df"]` = `r table_exp1$anov["Pt.
-× con.", "N170_f"]`, *p* = `r table_exp1$anov["Pt.
-× con.", "N170_p"]`, and in the N400 component, *F*`r table_exp1$anov["Pt.
-× con.", "N400_df"]` = `r table_exp1$anov["Pt.
-× con.", "N400_f"]`, *p* `r table_exp1$anov["Pt.
-× con.", "N400_p"]`, while also showing a weak statistical trend in the P1 component, *F*`r table_exp1$anov["Pt.
-× con.", "P1_df"]` = `r table_exp1$anov["Pt.
-× con.", "P1_f"]`, *p* = `r table_exp1$anov["Pt.
-× con.", "P1_p"]`.
-To answer our main research question, we decomposed these interactions into the differences between the semantically informed condition and the naive condition within the three different parts of the experiment.
-
-### ERPs Before Insight Was Occurring
-
-In the pre-insight part, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed and the naive condition in the P1, N170, or N400 component, all *p*s ≥ `r table_exp1$conts["Pre-insight part", "N400_p"]` (see Table \@ref(tab:exp1-table) and Figure \@ref(fig:exp1-plot)B).
-On the one hand, this was to be expected given that the critical presentation of the keywords (leading to semantically informed vs. naive perception) had not yet taken place.
-On the other hand, the absence of reliable differences in this part can be taken as evidence---with the usual caveats when interpreting null effects---that any subsequent effect of the semantic information in the other two parts cannot be accounted for by visual differences between the objects in the two conditions.
-Although the presentation of matching or non-matching keywords for each object was counterbalanced across participants, the fact that different numbers of objects were assigned to the two conditions based on participants' self-report would have made it possible for such visual differences to emerge as a confounding factor.
-If they did, however, one would expect to detect these differences even before any keywords were presented, which was apparently not the case.
-
-### ERPs While Insight Was Occurring
-
-In the insight part, half of the unfamiliar objects were presented with matching keywords (for forming the semantically informed condition) and the other half were presented with non-matching keywords (for forming the naive condition).
-When semantic information informed the perception of the object, the amplitude of the N170 component was significantly enlarged (i.e., more negative), *b* = `r table_exp1$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Insight part", "N170_p"]`, and the amplitude of the N400 component was significantly reduced (i.e., less negative), *b* = `r table_exp1$conts["Insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Insight part", "N400_p"]`, compared to when the object was viewed naively without relevant semantic information.
-As in the pre-insight part, there were no reliable differences in the P1 component, *b* = `r table_exp1$conts["Insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Insight part", "P1_p"]`.
-
-### ERPs After Insight Had Occurred
-
-In the post-insight part, the unfamiliar objects were presented for a third time, again without the keywords (as in the pre-insight part).
-This allowed us to test if the semantic information had any lasting effects on the processing of the objects.
-As in the insight part, the N400 component remained significantly reduced during semantically informed as compared to naive perception, *b* = `r table_exp1$conts["Post-insight part", "N400_est"]` µV, *p* `r table_exp1$conts["Post-insight part", "N400_p"]`, whereas the effect in the N170 component did not reoccur, *b* = `r table_exp1$conts["Post-insight part", "N170_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "N170_p"]`.
-Instead, we now observed an even earlier modulation in the P1 component which was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, *b* = `r table_exp1$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp1$conts["Post-insight part", "P1_p"]`.
-
-## Discussion
-
-In Experiment 1, we measured the ERPs of participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-insight part) they were able to understand what kind of object they were seeing.
-To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.
-
-In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms).
-When the same objects were presented once more in the post-insight part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for which semantically informed perception had taken place.
-
-Because of the novelty of our experimental paradigm---measuring the ERPs while rather than after participants received semantic information about unfamiliar objects---and because of the novelty of our findings, we ran a replication study with another sample of participants to assess the robustness of these effects.
-
-# Experiment 2
-
-## Method
-
-### Participants
-
-Participants for Experiment 2 were 24 German native speakers (15 female, 9 male) with a mean age of 26 years (range 19 to 29 years) who had not participated in Experiment 1.
-They had no history of psychological disorders or treatment, were right-handed, and reported normal or corrected-to-normal vision.
-They gave written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
-
-### Materials, Procedure, and Analysis
-
-```{r exp2-preproc, eval=rerun_preproc}
-# Read behavioral data for Experiment 2
-list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp2
-
-# Preprocess the EEG for Experiment 2 in Python
-map2(
-  .x = list.files("data/exp2/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp2,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp2
-
-# Backup epochs to the export folder
-epochs_exp2$save("analysis/export/exp2-epo.fif")
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
-  set_names(comps$name) %>%
-  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
-  write_tsv("analysis/export/exp2-data.tsv") -> data_exp2
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp2-gaverages.RDS")
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp2, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp2-objects.tsv")
-
-# Remove the epochs to free up memory
-rm(epochs_exp2)
-```
-
-```{r exp2-models, eval=rerun_models}
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
-    ),
-    participant = factor(participant),
-    item = factor(item)
-  ) %>%
-  # Remove any trials excluded from conditions
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> data_exp2
-
-# Apply contrasts to the factors in the data
-contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)
-
-# Compute the models for Experiment 2
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp12,
-  data = data_exp2,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp2-models.RDS") -> models_exp2
-```
-
-```{r exp2-import}
-# Load average number of objects per condition
-(read_tsv("analysis/export/exp2-objects.tsv", col_types = cols()) %>%
-   summarise(across(.cols = -Participant, .fns = mean)) %>%
-   slice(1) %>% unlist() -> objects_exp2)
-
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
-    ),
-    participant = factor(participant),
-    item = factor(item)
-  ) -> data_exp2
-
-# Check number of rejected epochs
-data_exp2 %>%
-  group_by(participant) %>%
-  tally() %>%
-  mutate(n = 360 - n) %>%
-  pull(n) -> rejected_exp2
-mean(rejected_exp2)    # Mean
-median(rejected_exp2)  # Median
-range(rejected_exp2)   # Range
-
-# Load grand-averaged ERPs and linear mixed models
-evokeds_exp2 <- readRDS("analysis/export/exp2-gaverages.RDS")
-models_exp2 <- readRDS("analysis/export/exp2-models.RDS")
-```
-
-All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1.
-An average of `r format(round(objects_exp2["Excl_known"], 1), nsmall = 1)` objects per participant (= `r scales::percent(objects_exp2["Excl_known"]/120, accuracy = 0.1)` of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses.
-Based on participants' responses in the insight part, an average of `r format(round(objects_exp2["Informed"], 1), nsmall = 1)` objects was assigned to the semantically informed condition (= `r scales::percent(objects_exp2["Informed"]/60, accuracy = 0.1)` of objects presented with matching keywords) and an average of `r format(round(objects_exp2["Naive"], 1), nsmall = 1)` objects was assigned to the naive condition (= `r scales::percent(objects_exp2["Naive"]/60, accuracy = 0.1)` of objects presented with non-matching keywords).
-Automatic rejection of EEG epochs containing artifacts led to the exclusion of `r format(round(mean(rejected_exp2), 1), nsmall = 1)` trials per participant (= `r scales::percent(mean(rejected_exp2)/360, accuracy = 0.1)`; range `r min(rejected_exp2)` to `r max(rejected_exp2)` trials).
-
-## Results
-
-```{r exp2-table, include=TRUE, results="asis"}
-# Create table of models for Experiment 2
-table_exp2 <- create_table(
-  models_exp2,
-  stub_anova = c("Part", "Condition", "Pt. × con."),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption = "Results of Linear Mixed-Effects Regression Models for Experiment 2\\smallskip",
-  note = "Pt. = part, con. = condition, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-As in Experiment 1, P1, N170, and N400 amplitudes differed between the three different parts of the experiments, all *F*s ≥ `r table_exp2$anov["Part", "N170_f"]`, all *p*s `r table_exp2$anov["Part", "N170_p"]` (see Table \@ref(tab:exp2-table)).
-Also as in Experiment 1, N400 amplitudes differed between the informed and the naive condition averaged across parts, *F*`r table_exp2$anov["Condition", "N400_df"]` = `r table_exp2$anov["Condition", "N400_f"]`, *p* `r table_exp2$anov["Condition", "N400_p"]`.
-The part × condition interaction was significant in the P1 component, *F*`r table_exp2$anov["Pt.
-× con.", "P1_df"]` = `r table_exp2$anov["Pt.
-× con.", "P1_f"]`, *p* = `r table_exp2$anov["Pt.
-× con.", "P1_p"]`, and in the N400 component, *F*`r table_exp2$anov["Pt.
-× con.", "N400_df"]` = `r table_exp2$anov["Pt.
-× con.", "N400_f"]`, *p* `r table_exp2$anov["Pt.
-× con.", "N400_p"]`, but not in the N170 component, *F*`r table_exp2$anov["Pt.
-× con.", "N170_df"]` = `r table_exp2$anov["Pt.
-× con.", "N170_f"]`, *p* = `r table_exp2$anov["Pt.
-× con.", "N170_p"]`.
-
-```{r exp2-plot, include=TRUE, fig.height=7.5, fig.cap = "(ref:figure-2-caption)"}
-# Create plot for Experiment 2
-plot_grid(
-  #plot_bars(data = data_exp2, stars = stars_exp2, ymin = -2.5),
-  plot_headings(spacing = c(10, 1, 10, 1, 10)),
-  plot_erps(comps = comps, evokeds = evokeds_exp2, models = models_exp2, montage = montage),
-  plot_legends_erps(direction = "horizontal"),
-  nrow = 3, rel_heights = c(0.3, 6, 1.2), labels = NULL
-) + # Add some lines (to separate the parts)
-  annotate(geom = "segment", x = 0.328, xend = 0.328, y = 0.15, yend = Inf, linetype = "dashed") +
-  annotate(geom = "segment", x = 0.672, xend = 0.672, y = 0.15, yend = Inf, linetype = "dashed")
-```
-
-(ref:figure-2-caption) Results of Experiment 2\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\textit{Note.} 
-ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment.
-In an exact replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight parts and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part marginally failed to reach statistical significance (\textit{p} = .064).
-Ampl.
-= amplitude.\newline*\textit{p} \textless{} .05.
-**\textit{p} \textless{} .01.
-***\textit{p} \textless{} .001.
-
--->
-
-### ERPs Before Insight Was Occurring
-
-As in Experiment 1, no differences between objects in the semantically informed and the naive condition emerged in the P1, N170, or N400 component, all *p*s ≥ `r table_exp2$conts["Pre-insight part", "P1_p"]` (see Table \@ref(tab:exp2-table) and Figure \@ref(fig:exp2-plot)).
-
-### ERPs While Insight Was Occurring
-
-As in Experiment 1, semantically informed as compared to naive perception (induced by matching vs. non-matching keywords) was associated with an enhancement of the N170 component, although this effect marginally failed to reach statistical significance, *b* = `r table_exp2$conts["Insight part", "N170_est"]` µV, *p* = `r table_exp2$conts["Insight part", "N170_p"]`.
-The reduction of the N400 component during semantically informed perception remained significant, *b* = `r table_exp2$conts["Insight part", "N400_est"]` µV, *p* `r table_exp2$conts["Insight part", "N400_p"]`.
-
-### ERPs After Insight Had Occurred
-
-As in Experiment 1, the presentation of the same unfamiliar objects for a third time (without keywords, as in the pre-insight part) again led to significantly reduced amplitudes in the N400 component in response to objects for which semantically informed perception had occurred, *b* = `r table_exp2$conts["Post-insight part", "N400_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "N400_p"]`.
-Also, P1 amplitudes in response these objects were significantly enlarged, *b* = `r table_exp2$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_exp2$conts["Post-insight part", "P1_p"]`.
-
-### Joint Analysis of Experiments 1 and 2
-
-In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2.
-This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2.
-Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast [i.e., subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments\; @schad2020].
-This factor and its interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes.
-They were not included as by-participant random slopes because different participants took part in Experiments 1 and 2.
-Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit [@matuschek2017; @R-buildmer].
-The resulting formulas for the models can be found in Appendix B.
-
-```{r joint-import}
-# Combine data from Experiments 1 and 2 (requires changing the participant IDs for Experiment 2)
-data_exp2 %>%
-  mutate(participant = fct_relabel(participant, ~ paste0(., "_2"))) %>%
-  bind_rows(data_exp1, ., .id = "experiment") %>%
-  mutate(experiment = as_factor(experiment)) -> data_joint
-
-# Subset only the relevant conditions
-data_joint %>%
-  filter(condition %in% c("Informed", "Naive")) %>%
-  droplevels() -> data_joint_subs
-```
-
-```{r joint-models, eval=rerun_models}
-# Contrast coding for experiment (2-1), condition (informed-naive), and part (2-1, 3-1)
-t(contrasts_experiment <- t(cbind(c("1" = -1, "2" = 1))))
-contrasts(data_joint_subs$experiment) <- MASS::ginv(contrasts_experiment)
-contrasts(data_joint_subs$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_joint_subs$part) <- MASS::ginv(contrasts_part)
-
-# New formula for LMMs
-form_joint <- buildmer::tabulate.formula(
-  ~ part * condition * experiment + 
-    (part * condition | participant) + 
-    (part * condition * experiment | item)
-) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-
-# Apply the function to compute the joint models for Experiments 1 and 2
-map(
-  comps$name,
-  compute_models,
-  formula = form_joint,
-  data = data_joint_subs,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-models.RDS") -> models_joint
-```
-
-```{r joint-table, include=TRUE, results="asis"}
-# Load linear mixed models
-models_joint <- readRDS("analysis/export/joint-models.RDS")
-
-# Create table of models for Experiments 1 and 2 combined
-table_joint <- create_table(
-  models_joint,
-  stub_anova = c(
-    "Part", "Condition", "Experiment", "Pt. × con.",
-    "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."
-  ),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption =
-    "Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\\smallskip",
-  note =
-    "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\\% confidence interval."
-)
-
-# Extract the follow-up contrast for the main effect of experiment
-suppressMessages(emmeans::emm_options(lmerTest.limit = Inf))
-suppressMessages(
-  emmeans::emmeans(
-    models_joint$N400$model,
-    specs = pairwise ~ experiment, infer = TRUE
-  )$contrasts %>%
-    as.data.frame() %>%
-    transmute(
-      est = round(estimate, 2) %>%
-        format(nsmall = 2, trim = TRUE),
-      p = round(`p.value`, 3) %>%
-        format(nsmall = 3, trim = TRUE) %>%
-        as.character() %>%
-        substr(2, nchar(.))
-    ) -> conts_N400_joint
-)
-```
-
-As shown in Table \@ref(tab:joint-table), the main effect of part was significant in the P1, N170, and N400 component, all *F*s ≥ `r table_joint$anov["Part", "P1_f"]`, all *p*s `r table_joint$anov["Part", "P1_p"]`, as was the main effect of condition in the N400, *F*`r table_joint$anov["Condition", "N400_df"]` = `r table_joint$anov["Condition", "N400_f"]`, *p* `r table_joint$anov["Condition", "N400_p"]`.
-Furthermore, the part × condition interaction was now observed reliably in all three components, all *F*s ≥ `r table_joint$anov["Pt.
-× con.", "P1_f"]`, all *p*s ≤ `r table_joint$anov["Pt.
-× con.", "P1_p"]`.
-There was a main effect of experiment in the N400, *F*`r table_joint$anov["Experiment", "N400_df"]` = `r table_joint$anov["Experiment", "N400_f"]`, *p* = `r table_joint$anov["Experiment", "N400_p"]`, with more negative amplitudes in Experiment 1 as compared to Experiment 2, *b* = `r conts_N400_joint$est`.
-However, the absence of any significant interactions of experiment with part or condition indicated that the effects of our experimental manipulations did not differ between Experiments 1 and 2.
-
-Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \@ref(tab:joint-table) and Figure \@ref(fig:joint-plot)).
-This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all *p*s ≥ `r table_joint$conts["Pre-insight part", "N400_p"]`, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N170_est"]` µV, *p* = `r table_joint$conts["Insight part", "N170_p"]`, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, *b* = `r table_joint$conts["Insight part", "N400_est"]` µV, *p* `r table_joint$conts["Insight part", "N400_p"]`, and in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "N400_est"]` µV, *p* `r table_joint$conts["Post-insight part", "N400_p"]`, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, *b* = `r table_joint$conts["Post-insight part", "P1_est"]` µV, *p* = `r table_joint$conts["Post-insight part", "P1_p"]`.
-
-(ref:figure-3-caption) Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip
-
-<!--
-
-The papaja package does not yet deal with the placement of figure captions above rather than below the figures.
-Therefore, we manually need to post-process the .tex file, moving the caption{} above includegraphics{} and copying the figure note manually below includegraphics{}:
-
-\bigskip\small\textit{Note.} 
-The violins and box plots show the distributions of the by-participant averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred).
-The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modeling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval.
-Ampl.
-= amplitude, 95\% CI = 95\% confidence interval, LMM = linear mixed-effects model.\newline*\textit{p} \textless{} .05.
-**\textit{p} \textless{} .01.
-***\textit{p} \textless{} .001.
-
--->
-
-```{r joint-plot, include=TRUE, fig.height=8, fig.cap = "(ref:figure-3-caption)"}
-# Create violin plot for Experiments 1 and 2 combined
-plot_grid(
-  plot_headings(spacing = c(10, 2, 10, 2, 10)),
-  plot_violins(data = data_joint_subs, models = models_joint),
-  nrow = 2, rel_heights = c(0.3, 6.7)
-) %>% plot_grid(
-  plot_legends_violins(),
-  nrow = 1, rel_widths = c(8.5, 1.5)
-) + # Add some lines (to separate the parts)
-  annotate(
-    geom = "segment", x = 11 / 34 * 0.85, xend = 11 / 34 * 0.85,
-    y = -Inf, yend = Inf, linetype = "dashed"
-  ) +
-  annotate(
-    geom = "segment", x = 23 / 34 * 0.85, xend = 23 / 34 * 0.85,
-    y = -Inf, yend = Inf, linetype = "dashed"
-  )
-```
-
-### Control Analysis
-
-```{r control-models, eval=rerun_models}
-# This time, we keep only the two conditions with matching keywords
-data_joint %>%
-  filter(condition %in% c("Informed", "Excl_informed")) %>%
-  droplevels() -> data_joint_control
-
-# Contrast coding for condition (informed-no_informed) and part (2-1, 3-1)
-contrasts(data_joint_control$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_joint_control$part) <- MASS::ginv(contrasts_part)
-
-# Apply the function to re-compute the joint models
-map(
-  comps$name,
-  compute_models,
-  formula = form_joint,
-  data = data_joint_control,
-  control = control,
-  specs = specs_exp12
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/joint-control-models.RDS") -> models_joint_control
-```
-
-```{r control-table}
-# Calculate average number of objects per condition in Experiments 1 and 2
-(stims_joint <- (objects_exp1 + objects_exp2) / 2)
-
-# Load linear mixed models
-models_joint_control <- readRDS("analysis/export/joint-control-models.RDS")
-
-# Create a table but don't print
-table_joint_control <- create_table(
-  models = models_joint_control,
-  stub_anova = c(
-    "Part", "Condition", "Experiment", "Pt. × con.",
-    "Pt. × exp.", "Ins. × exp.", "Pt. × con. × exp."
-  ),
-  stub_contrasts = c("Pre-insight part", "Insight part", "Post-insight part"),
-  caption =
-    "Results of Linear Mixed-Effects Regression Models With a Different Baseline",
-  note =
-    "Pt. = part, con. = condition, exp. = experiment, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-One may raise concerns whether the modulation of the N170 component in the insight part genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it may be driven by the objects in the other, semantically naive condition.
-Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration.
-Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \@ref(fig:exp1-plot)A cannot be reconciled with the function of signaling messages.
-To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted.
-Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were presented with matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing.
-Across both experiments, this was the case for `r scales::percent(stims_joint["Excl_informed"]/60, accuracy = 0.1)` of objects presented with matching keywords, as compared to `r scales::percent(stims_joint["Informed"]/60, accuracy = 0.1)` of objects which did indeed lead to semantically informed perception.[^1] Just as above, this control analysis revealed a robust N170 effect in the insight part, *b* = `r table_joint_control$conts["Insight part", "N170_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N170_p"]`.
-Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with non-matching keywords or compared to objects presented with matching keywords on which participants failed to capitalize.
-Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, *b* = `r table_joint_control$conts["Insight part", "N400_est"]` µV, *p* `r table_joint_control$conts["Insight part", "N400_p"]`.
-
-[^1]: Note that these percentages do not add up to 100% because some objects were excluded from all analyses if participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).
-
-## Discussion
-
-Experiment 2, which was an exact replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400).
-Objects for which participants experienced semantically informed perception via matching keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes.
-Note, however, that the effect in the N170 component marginally failed to reach the conventional level for statistical significance in this replication experiment.
-When the objects were presented once more without any semantic information, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.
-
-```{r exp3-preproc, eval=run_exp3}
-# Read behavioral data for Experiment 1
-list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp3
-
-# Update stimulus triggers
-preproc_params$event_id <- dict(
-  "match/upright" = as.integer(241),
-  "match/inverted" = as.integer(242),
-  "mismatch/upright" = as.integer(243),
-  "mismatch/inverted" = as.integer(244)
-)
-
-# Preprocess the EEG for Experiment 3 in Python
-fnames_exp3 <- list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE)
-py_run_string(
-  "epochs_exp3 = [preproc(vhdr_fname=fname, metadata=meta, **r.preproc_params)
-                  for fname, meta in zip(r.fnames_exp3, r.behav_exp3)]"
-)
-message("This worked!!!")
-py_run_string("epochs_exp3 = mne.epochs.concatenate_epochs(epochs_exp3)")
-message("This also worked!!!")
-py_run_string("epochs_exp3.save('analysis/export/exp3-epo.fif', overwrite=True)")
-py_run_string("del epochs_exp3")
-
-# Preprocess the EEG for Experiment 3 in Python
-map2(
-  .x = list.files("data/exp3/EEG", pattern = ".vhdr", full.names = TRUE),
-  .y = behav_exp3,
-  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
-) %>%
-  # Concatenate epochs of all participants
-  py$mne$epochs$concatenate_epochs() -> epochs_exp3
-
-# Backup epochs to the export folder
-epochs_exp3$save("analysis/export/exp3-epo.fif")
-
-# Compute mean ERP amplitudes and bind to the behavioral data
-pmap_dfc(comps, py$compute_erps, epochs = epochs_exp3) %>%
-  set_names(comps$name) %>%
-  bind_cols(as_tibble(epochs_exp3$metadata), .) %T>%
-  write_tsv("analysis/export/exp3-data.tsv") -> data_exp3
-
-# Compute grand averages per part and condition
-py$compute_evokeds(epochs = epochs_exp3, grand = TRUE, data_only = TRUE) %>%
-  saveRDS("analysis/export/exp3-gaverages.RDS")
-
-# Backup number of stimuli assigned to each condition for all participants
-map(behav_exp3, function(x) table(x$condition) / 3) %>%
-  bind_rows() %>%
-  mutate(Participant = unique(data_exp3$participant), .before = 1) %>%
-  write_tsv("analysis/export/exp3-objects.tsv")
-
-# Remove the epochs to free up memory
-rm(epochs_exp3)
-```
-
-```{r exp3-models, eval=run_exp3}
-# Load preprocessed single-trial data
-read_tsv("analysis/export/exp3-data.tsv", col_types = cols()) %>%
-  # Factorize columns
-  mutate(
-    part = factor(part, levels = c("I", "II", "III")),
-    position = factor(position, levels = c("Inverted", "Upright")),
-    condition = factor(condition, levels = c(
-      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
-    )),
-    participant = factor(participant),
-    item = factor(item)
-  ) %>%
-  # Remove any trials excluded from conditions and parts
-  filter(condition %in% c("Informed", "Naive") & part != "IV") %>%
-  droplevels() -> data_exp3
-
-# Define contrasts for position (inverted-upright), condition (informed-naive), and part (2-1, 3-1)
-t(contrasts_position <- t(cbind(c("Inverted" = 1, "Upright" = -1))))
-contrasts(data_exp3$position) <- MASS::ginv(contrasts_position)
-contrasts(data_exp3$condition) <- MASS::ginv(contrasts_condition)
-contrasts(data_exp3$part) <- MASS::ginv(contrasts_part)
-
-# Define new formula for LMMs
-formula_exp3 <- buildmer::tabulate.formula(
-  ~ part * condition * position +
-    (part * condition * position | participant) +
-    (part * condition * position | item)
-) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
-
-# Define new follow-up contrasts
-specs_exp3 <- pairwise ~ condition | position * part
-
-# Compute the models for Experiment 3
-map(
-  comps$name,
-  compute_models,
-  formula = formula_exp3,
-  data = data_exp3,
-  control = control,
-  specs = specs_exp3
-) %>%
-  set_names(comps$name) %T>%
-  saveRDS("analysis/export/exp3-models.RDS") -> models_exp3
-```
-
-```{r exp3-table, include=TRUE, results="asis", eval=run_exp3}
-# Create table of models for Experiment 3
-table_exp3 <- create_table(
-  models_exp3,
-  stub_anova = c(
-    "Part", "Condition", "Position", "Pt. × con.",
-    "Pt. × pos.", "Ins. × pos.", "Pt. × con. × pos."
-  ),
-  stub_contrasts = c(
-    "Part I, inverted", "Part I, upright", "Part II, inverted",
-    "Part II, upright", "Part III, inverted", "Part III, upright"
-  ),
-  caption = "Results of linear mixed-effects regression models for Experiment 3",
-  note = "Pt. = part, con. = condition, pos. = position, est. = estimate, CI = 95\\% confidence interval."
-)
-```
-
-# General Discussion
-
-Here we investigated if obtaining a semantic understanding of previously unfamiliar objects has an influence on how we perceive them.
-To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
-For half of the objects, this information was matching the object, thus leading to semantically informed perception, whereas for the other half of the objects, the information was non-matching, thus keeping the perception of the object semantically naive.
-We found semantically informed perception to be accompanied by enlarged (i.e., more negative) N170 amplitudes and reduced (i.e., less negative) N400 amplitudes.
-When the same objects were presented again without the semantic information, the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
-We will discuss each of these effects in turn, starting with the latest (i.e., post-perceptual) effect and moving backward in time to the earlier (i.e., more perceptual) effects.
-
-The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest and most robust effect.
-Perhaps least controversially, this effect indicates that acquiring an understanding of the objects (in the insight part) lessened participants' demand for effortful semantic processing in comparison to the naive condition [@kutas2011].
-This replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
-The time course of this effect and the computational role of the N400 [@lau2008; @rabovsky2018] suggest that it has a post-perceptual locus.
-
-In contrast to the N400, the N170 component (150--200 ms after object onset) was modulated while but not after the objects were presented together with the relevant semantic information.
-As such, it can be seen as an online marker of semantic insight, that is, participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
-The N170 is typically associated with the holistic perception of faces [@eimer2011; @sagiv2001] and other stimuli of visual expertise [@rossion2002; @tanaka2001].
-It being enlarged during semantically informed perception may therefore reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous findings with a similar experimental paradigm in the domain of face perception [@bentin2002]: In this study, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after (but not before) they were primed with the intact version of the same face.
-This effect was absent when a visual control stimulus (a non-face object) was shown instead of the intact face.
-In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
-Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
-Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level (i.e., holistic) perception of visual objects, integrating across their visual features.
-
-The P1 component (100--150 ms after object onset), unlike the N400 and N170 components, was modulated by semantic information only one trial after the information had been obtained.
-This is consistent with previous studies showing modulations of the P1 component when participants learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
-What the present study adds to these findings is that the P1 effect does not take an extensive learning phase to develop (with multiple presentations of the objects together with the respective information).
-Instead, it can be observed as soon as one trial after semantic insight has happened.
-Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
-
-Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects.
-However, the finding that these two components were modulated in different parts of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
-It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seem to reflect recurrent processing *within* the visual system [@wyatte2014].
-Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter seems to take at least one---but apparently also not more than one---additional presentation of the visual object to emerge.
-
-While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream for object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
-@hsieh2010 showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
-They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
-This increase in representational similarity was not just observed in higher-level object-sensitive areas in the lateral occipital cortex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
-Both of these cortical regions are consistent with the neural generators of the N170 and P1 components in the ERP which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
-
-On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999; but see @clarke2020].
-However, proponents of such a modular view have pointed out important shortcomings of previous studies that claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
-We took care to address as many of these shortcomings as possible: First, we showed that no effect had been present before any semantic information was being presented (in the pre-insight part).
-Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with a perceptual locus from those with a post-perceptual locus.
-Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
-Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
-Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order and at the same location.
-Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these procedures have effectively ruled out some of the most important alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the cognitive impenetrability of perception.
-
-An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @serre2007].
-In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
-For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this "barrier of meaning" [@mitchell2020].
-Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.
-
-A theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking at present.
-The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004; @hochstein2002] which posits that objects first enter our visual consciousness at an abstract, conceptual level.
-Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
-This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
-Besides this specific theory, an important role of top-down mechanisms for vision or, more specifically, object recognition is also posited by the family of predictive coding and Bayesian inference theories [e.g., @clark2013; @lupyan2015; @panichello2013; @yuille2006].
-Despite the theoretical advances, the mechanistic details of these top-down effects at the algorithmic and implementational level [@marr1982] remain to be clarified.
-
-The lack of mechanistic insight into the top-down effects that we have observed is one limitation of the present study.
-Another one is our reliance on rare and highly specialized objects (see Appendix A).
-This was necessary to induce the experience of semantic insight in a population of undergraduate students but the results may not necessarily generalize to the way in which we learn about everyday objects.[^2] One way of addressing this issue would be to adapt the present paradigm to younger participants, using everyday objects which they have not yet learned about.
-Finally, the number participants (*n* = 24 per experiment) and trials (*k* $\approx$ 30 per part in the insight condition and *k* $\approx$ 50 per part in the naive condition) can be considered small by today's standards [@baker2020].
-Our analysis may therefore not have been particularly sensitive, especially given that linear mixed-effects regression models tend to have limited statistical power under a wide range of circumstances [see, e.g., the simulations by @matuschek2017].
-This lack of power may also explain why one of the effects that had been observed in the first experiment (i.e., the enlargement of the N170 component, *p* = `r table_exp1$conts["Insight part", "N170_p"]`) failed to reach statistical significance in the replication experiment (*p* = `r table_exp2$conts["Insight part", "N170_p"]`).
-To discern if this was due to a lack of statistical power or due to the actual absence of an effect, it would take yet another (more highly powered) replication study and/or a different data-analytic approach where it is possible to estimate the evidence both for the alternative hypothesis and for the null hypothesis (e.g., Bayesian linear mixed models).
-It should be noted, however, that the joint analysis of both data sets yielded a very robust N170 effect (*p* = `r table_joint$conts["Insight part", "N170_p"]`).
-This makes it less likely that the effect observed in Experiment 1 was due to a false positive and instead suggests that statistical power in Experiment 2 was insufficient to render the effect significant.
-Also note that the effect in the P1 component was statistically significant in both experiments individually, making an even stronger case for the susceptibility of early cortical processing to newly acquired knowledge about objects.
-
-[^2]: Note, however, the converging evidence coming from the complementary approach of rendering images of everyday objects difficult to recognize [@samaha2018].
-
-Taken together, this study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the processing of the object.
-This influence is immediate in at least two different ways: First, it does not require extensive training and can instead be observed within the same trial in which the information has been presented (and/or one trial later).
-Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages---typically associated with semantic processing---but also at earlier stages---typically associated with visual perception itself and happening within less than a fifth of a second after the object is presented to us.
 

### 2022-05-28 manuscript.Rmd

@@
 
+# Plot thresholded cluster images
 clusters %>%
@@
   geom_raster() +
-  scale_fill_viridis_d()
+  theme(legend.position = "top")
+```
+
+```{r, tfr, include=TRUE, fig.height=12}
+# Read results of cluster-based permutation tests for TFR
+read_csv(tfr_clusters_file, col_types = cols(
+  contrast = col_factor(levels = c(
+    "Pre-insight/Informed - Pre-insight/Naive",
+    "Insight/Informed - Insight/Naive",
+    "Post-insight/Informed - Post-insight/Naive"
+  ))
+)) -> tfr_clusters
+
+# Plot thresholded cluster images for the insight phase
+tfr_clusters %>%
+  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
+  ggplot(aes(x = time, y = freq, fill = cluster)) +
+  facet_wrap(~channel) +
+  geom_raster() +
+  theme(legend.position = "top")
+
+# Plot thresholded cluster images for the post-insight phase
+tfr_clusters %>%
+  filter(
+    contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < .05
+  ) %>%
+  ggplot(aes(x = time, y = freq, fill = cluster)) +
+  facet_wrap(~channel) +
+  geom_raster() +
+  theme(legend.position = "top")
 ```

### 2022-05-30 manuscript.Rmd
Small fixes for runtime

@@
     latex_engine: xelatex
-  papaja::apa6_docx:default
 
@@
 run <- list(
-  "preprocessing" = TRUE,
-  "modeling" = TRUE
+  "preprocessing" = FALSE,
+  "modeling" = FALSE
 )
@@
   output_dir = output_dir,
-  report_dir = report_dir,
+  report_dir = NULL,
   downsample_sfreq = 125,

### 2022-06-24 manuscript.Rmd
Update Figure 1

@@
     affiliation   : "1,2"
-    corresponding : yes
+    corresponding : "yes"
     address       : "Rudower Chaussee 18, 12489 Berlin, Germany"
@@
 library(papaja)
+library(cowplot)
 library(parallel)
@@
 
-# Set global chunk options
-opts_chunk$set(fig.width = 10, include = FALSE, out.width = "100%")
+# Set global options
+options(readr.show_col_types = FALSE)
+opts_chunk$set(fig.width = 12, include = FALSE, out.width = "100%")
+
+# Specify directory paths
+data_dir <- here("data")
+files_dir <- here("manuscript_files")
+output_dir <- here("output")
+
+# Load custom helper functions for creating figures and tables
+source(here(files_dir, "helper_functions.R"))
+
+# Re-run steps that take a long time to compute?
+run <- list(
+  eeg_processing = FALSE,
+  mixed_models = FALSE
+)
 
 # Write R packages to bibliography
-r_refs(here("manuscript_files", "r-references.bib"), append = FALSE)
-
-# What to (re-)run
-run <- list(
-  "preprocessing" = FALSE,
-  "modeling" = FALSE
-)
-
-# Directory paths
-data_dir <- here("data")
-output_dir <- here("output")
-report_dir <- here(output_dir, "html_reports")
-
-# File paths
-trials_file <- here(output_dir, "trials.csv")
-models_file <- here(output_dir, "models.RDS")
-clusters_file <- here(output_dir, "clusters.csv")
-tfr_clusters_file <- here(output_dir, "tfr_clusters.csv")
+r_refs(here(files_dir, "r-references.bib"), append = FALSE)
 ```
 
-```{r, preprocessing, eval=run$preprocessing}
+# Introduction
+
+Does our perception of an object change as soon as we discover what function it serves?
+This question speaks not only to our everyday experiences, where we encounter novel tools and gadgets in our dynamic working and private environments.
+It also pertains to the long-standing debate about the cognitive (im)penetrability [@pylyshyn1999] of perception by higher-level capacities such as semantic knowledge or language.
+According to one view, these cognitive capacities kick in only after the retinal input has been processed by a specialized module for visual perception [@firestone2016; @fodor1983].
+This module is encapsulated from higher-level inputs and therefore processes the visual information in a purely feedforward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
+This architecture has been mirrored in classical [e.g., @marr1982] and contemporary [e.g., @krizhevsky2012] computer vision models, allowing them to achieve human-level perfomance in predicting object category labels from images [for review, see @lindsay2020].
+
+The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different aspects of cognition from early on [@churchland1994; @lupyan2015].
+This view is supported by a variety of theoretical, behavioral, and neurophysiological accounts.
+On the theoretical level, the reverse hierarchy theory [@ahissar2004; @hochstein2002] posits that conscious processing initally occurs at the level of whole objects or object categories.
+Only after this high-level interpretation has been obtained, more fine grained visual details---if relevant for the current task---are being accessed via top-down connections.
+Along similar lines, Bayesian inference and predictive coding theories [e.g., @clark2013; @panichello2013; @yuille2006] propose bi-directional loops of predictions and prediction errors between visual and non-visual processes.
+
+On the behavioral level, these ideas are supported by psychological studies that showed differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] background.
+However, some of these studies confounded tentantive high-level effects with low-level differences between conditions.
+Furthermore, many studies were not able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
+
+On the neurophysiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
+Their excellent temporal resolution allows us to probe how early we can detect influences of high-level (e.g., semantic) information.
+To this end, participants were typically trained to associate visual objects with different amounts of semantic information.
+After training, an orthogonal task was used to compare the ERPs in response to semantically trained objects versus non-semantically trained objects.
+This revealed differences not only in late ERP components associated with semantic processing (i.e., the N400 component) but also in the visual P1 component [@abdelrahman2008; @maier2019; @samaha2018; @weller2019].
+The early peak of this component and its source in the occipital cortex [@abdelrahman2008] point to an immediate effect of semantic knowledge on visual perception.
+
+Here we measured ERPs in response to unfamiliar objects instantly while participants gained an semantic understanding of their function.
+To this end, we presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viweing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
+We then presented the same objects again to test for downstream effects of semantic information as in previous studies.
+We examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
+
+# Materials and Methods
+
+## Participants
+
+Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18--32) and no history of psychological disorder or treatment.
+No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
+All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
+They provided written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+
+## Materials
+
+Stimuli consisted of 240 grayscale photographs of real-world objects.
+Of these, 120 were well-known everyday objects (e.g., a bicycle, a toothbrush) and served as filler stimuli of no interest.
+The other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Appendix A).
+All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
+At a standardized viewing distance of 90 cm, the images subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
+
+For each unfamiliar object, a pair of German keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
+As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
+The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically naive.
+All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
+This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
+The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
+
+## Experimental Design
+
+The experiment consisted of three parts (see Figure \@ref(fig:fig1)A).
+In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
+Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
+The inter-trial interval was 0.5 s and participants took a self-timed break after each block of 60 objects.
+The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
+
+```{r, eeg_processing, eval=run$eeg_processing}
 # Process behavioral data
@@
 
-        # # Participant ID (unique for Experiments 1 and 2)
-        # participant = ifelse(
-        #   str_detect(log_file, "exp2"), str_c(VPNummer, "_exp2"), VPNummer
-        # ),
-
         # Keyword conditions
@@
         rt = RT,
-        log_rt = log(RT),
 
@@
     log %>%
-      select(item_id, phase, condition, response, rt, log_rt) %>%
+      select(item_id, phase, condition, response, rt) %>%
       return()
@@
 
-```{r, modeling, eval=run$modeling}
+```{r, mixed_models, eval=run$mixed_models}
 # Read single trial data
@@
 
+```{r, fig1, include=TRUE, fig.height=12, fig.cap="(ref:figure-1-caption)"}
+# Read pipeline configuration
+config <- jsonlite::read_json(here(output_dir, "config.json"))
+
+# Read by-participant ERP averages and channel locations
+evokeds <- read_csv(here(output_dir, "ave.csv"))
+
+# Read channel locations
+channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
+
+# Read fitted models
+models <- readRDS(here(output_dir, "models.RDS"))
+
+# Create Figure 1
+plot_fig1(files_dir, evokeds, config, channel_locations, models)
+```
+
 ```{r, table_1, include=TRUE}
-# Read fitted models
-models <- readRDS(models_file)
-
 # View model summaries
@@
 # Read results of cluster-based permutation tests for ERPs
-read_csv(clusters_file, col_types = cols(
+read_csv(here(output_dir, "clusters.csv"), col_types = cols(
   contrast = col_factor(levels = c(
@@
 # Read results of cluster-based permutation tests for TFR
-read_csv(tfr_clusters_file, col_types = cols(
+read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
   contrast = col_factor(levels = c(
@@
 
+```{r}
+# Read grand-averaged power
+tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv")) %>%
+  mutate(
+    phase = factor(phase, levels = c("Pre-insight", "Insight", "Post-insight")),
+    condition = factor(condition, levels = c("Informed", "Naive"))
+  ) %>%
+  filter(!is.na(condition))
+
+channels <- tfr_grand_ave %>%
+  select(-average_by, -phase, -condition, -time, -freq) %>%
+  colnames()
+
+tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
+tfr_grand_ave_naive <- filter(tfr_grand_ave, condition == "Naive")
+tfr_grand_ave_diff <- mutate(tfr_grand_ave_informed, condition = "Difference")
+tfr_grand_ave_diff[channels] <- tfr_grand_ave_informed[channels] -
+  tfr_grand_ave_naive[channels]
+
+bind_rows(tfr_grand_ave, tfr_grand_ave_diff) %>%
+  mutate(
+    condition = factor(condition, levels = c("Informed", "Naive", "Difference"))
+  ) %>%
+  pivot_longer(
+    cols = all_of(channels), names_to = "electrode", values_to = "amplitude"
+  ) %>%
+  select(-average_by, -electrode) %>%
+  group_by(phase, condition, time, freq) %>%
+  summarise(amplitude = mean(amplitude), .groups = "drop") %>%
+  ggplot(aes(x = time, y = freq, fill = amplitude)) +
+  facet_grid(phase ~ condition) +
+  geom_raster() +
+  scale_fill_viridis_c(option = "turbo", limits = c(-0.6, 0.6)) +
+  coord_cartesian(expand = FALSE)
+
+tmins <- seq(0.0, 1.2, 0.2)
+fmins <- seq(4, 36, 4)
+
+channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
+
+map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {
+  map(tmins, function(tmin, tstep = 0.2) {
+    tmax <- tmin + tstep
+    map(fmins, function(fmin, fstep = 4) {
+      fmax <- fmin + fstep
+      tfr_grand_ave_diff %>%
+        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
+        filter(phase == this_phase) %>%
+        pivot_longer(
+          cols = all_of(channels), names_to = "electrode", values_to = "power"
+        ) %>%
+        left_join(channel_locations, by = c("electrode" = "channel")) %>%
+        group_by(electrode, x, y) %>%
+        summarise(power = mean(power), .groups = "drop") %>%
+        eegUtils::topoplot(
+          quantity = "power",
+          contour = FALSE,
+          interp_limit = "skirt",
+          scaling = 0.7
+        ) +
+        scale_fill_viridis_c(limits = c(-0.3, 0.3), option = "turbo") +
+        theme(legend.position = "none")
+    }) %>%
+      plot_grid(plotlist = ., nrow = 1)
+  }) %>%
+    plot_grid(plotlist = ., nrow = length(tmins))
+})
+```
+
 \newpage

### 2022-06-24 manuscript_files/helper_functions.R

@@ -1,0 +1,450 @@
+# Define colors
+aha_colors <- viridisLite::viridis(2, begin = 0.1, end = 0.6)
+
+# Helper function for text labels
+annotate_text <- function(...) {
+    ggplot2::annotate(
+        geom = "text", size = size, color = "black", family = "Helvetica"
+    )
+}
+
+plot_fig1a <- function(files_dir) {
+    # Trial structure
+    example_stim <- magick::image_read(
+        here::here(files_dir, "example_stim.png")
+    )
+    ggplot() +
+        coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
+        theme_void() +
+        theme(aspect.ratio = 0.5) +
+        ## PART II ##
+        # Title
+        annotate(
+            geom = "text", x = 0, y = 97.2, label = "Insight part",
+            size = 14 / .pt, family = "Helvetica", fontface = "bold"
+        ) +
+        # Arrow
+        annotate(
+            geom = "segment", x = -30, xend = 24, y = 79, yend = 85,
+            arrow = arrow(length = unit(0.1, "inches"))
+        ) +
+        # Squares
+        annotate(
+            geom = "rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75,
+            color = "black", fill = "white"
+        ) +
+        annotate(
+            geom = "rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65,
+            color = aha_colors[1], fill = "white"
+        ) +
+        annotate(
+            geom = "rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89,
+            color = aha_colors[2], fill = "white"
+        ) +
+        annotate(
+            geom = "rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79,
+            color = "black", fill = "white"
+        ) +
+        annotate(
+            geom = "rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81,
+            color = "black", fill = "white"
+        ) +
+        annotate(
+            geom = "text", x = -27, y = 65.3, label = "+", size = 20 / .pt,
+            family = "Helvetica"
+        ) +
+        annotate(
+            geom = "text", x = -9, y = 55, label = "potatoes\nmashing",
+            family = "Helvetica", color = aha_colors[1]
+        ) +
+        annotate(
+            geom = "text", x = -9, y = 79, label = "message\nsignaling",
[…]

### 2022-07-08 manuscript.Rmd
Update manuscript text

@@
   - id            : "1"
-    institution   : "Humboldt-Universität zu Berlin"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, 12489 Berlin, Germany"
   - id            : "2"
-    institution   : "Max Planck Institute for Human Cognitive and Brain Sciences"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, 04103 Leipzig, Germany"
   - id            : "3"
-    institution   : "Fachhochschule des Mittelstands"
+    institution   : "Fachhochschule des Mittelstands, Minna-Neuburger-Straße 3, 96050 Bamberg, Germany"
 
@@
   - \interfootnotelinepenalty=10000
-  - \usepackage{setspace}
-  - \AtBeginEnvironment{tabular}{\doublespacing}
-  - \usepackage{makecell}
-  - \renewcommand{\cellset}{\renewcommand{\arraystretch}{0.7}}
-  - \captionsetup{font={stretch=1}, belowskip=15pt}
+  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=period,name=Figure,textfont=normalfont}
 ---
@@
 library(MASS)
+library(scales)
 library(papaja)
@@
 The experiment consisted of three parts (see Figure \@ref(fig:fig1)A).
-In the *pre-insight* part, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
+In the *pre-insight* phase, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
 Each trial consisted of a fixation cross presented in the middle of the screen for 0.5 s, followed by the presentation of the object until participants made a response or until a time out after 3 s.
@@
 
-```{r, mixed_models, eval=run$mixed_models}
+```{r, read_results}
 # Read single trial data
-read_csv(trials_file, col_types = cols(
+read_csv(here(output_dir, "trials.csv"), col_types = cols(
   participant_id = col_factor(),
@@
 
+# Compute number of objects per condition for each participant
+with(trials, table(participant_id, condition)) %>%
+  `/`(3) %>%
+  as.data.frame.matrix() %>%
+  rownames_to_column("subject_id") -> objects_per_condition
+
+# Read by-participant ERP averages and channel locations
+evokeds <- read_csv(here(output_dir, "ave.csv"))
+
+# Read pipeline configuration
+config <- jsonlite::read_json(
+  here(output_dir, "config.json"),
+  simplifyVector = TRUE, simplifyMatrix = FALSE
+)
+
+# Count number of rejected epochs per participant
+rejected_epochs <- lengths(config$rejected_epochs)
+
+# Read channel locations
+channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
+```
+
+```{r, mixed_models, eval=run$mixed_models}
 # Filter relevant conditions for the main analysis
@@
 ```{r, fig1, include=TRUE, fig.height=12, fig.cap="(ref:figure-1-caption)"}
-# Read pipeline configuration
-config <- jsonlite::read_json(here(output_dir, "config.json"))
-
-# Read by-participant ERP averages and channel locations
-evokeds <- read_csv(here(output_dir, "ave.csv"))
-
-# Read channel locations
-channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
-
 # Read fitted models
@@
 ```
+
+(ref:figure-1-caption) Experimental design and ERP results.
+***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+In the insight phase, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in green color for illustration), leading to naive perception.
+In the post-insight phase, the same objects were presented again without keywords.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies of the P1 component (100--150 ms, ***B***), of the N170 component (150--200 ms, ***C***), and of the N400 component (400--700 ms, ***D***) are shown for objects with semantically informed versus naive perception within the three different parts.
+Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight parts, and more positive amplitudes in the P1 component during the post-insight phase.
+The time windows and channels for quantifying the different ERP components are highlighted by the gray areas in the ERP waveforms and the white markers on the scalp topographies, respectively.
+Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
+Ampl. = amplitude.\newline
+\* *p* $<$ .05. \*\* *p* $<$ .01. \*\*\* *p* $<$ .001.
+
+In the *insight* phase, the 120 unfamiliar objects were presented for the second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
+Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
+The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).
+
+In the *post-insight* phase, the unfamiliar objects were presented for a third time with the same trial structure as in the pre-insight phase, that is, without any keywords.
+The insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight phase (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight phase (without keywords) before moving on to the next block consisting of 30 different objects.
+They continued like this until all four blocks were completed in both parts.
+In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight phase and 120 unfamiliar objects in the pre-insight, insight, and post-insight parts).
+It took participants approximately 35 minutes to complete.
+
+## EEG Recording and Preprocessing
+
+The continuous EEG was recorded from 62 Ag/AgCl scalp electrodes placed according to the extended 10--20 system [@americanelectroencephalographicsociety1991] and referenced online to an external electrode placed on the left mastoid (M1).
+Two additional external electrodes were placed on the right mastoid (M2) and below the left eye (IO1), respectively.
+Electrode impedances were kept below 5 kΩ.
+An online band-pass filter with a high-pass time-constant of 10 s (0.016 Hz) and a low-pass cutoff frequency of 1000 Hz was applied before digitizing the signal at a sampling rate of 500 Hz.
+
+The data were preprocessed offline using the MNE software [Version `r system("mne --version", intern = TRUE) %>% str_remove("MNE ")`\; @gramfort2013] in Python [Version `r system("python3 --version", intern = TRUE) %>% str_remove("Python ")`\; @vanrossum2009].
+First, all scalp electrodes were re-referenced to the common average.
+Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
+The first 15 components were extracted with the FastICA algorithm [@hyvarinen1999] after temporarily low-pass filtering the data at 1 Hz.
+Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find_bads_eog* function.
+After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
+Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the presentation of each unfamiliar object.
+The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset.
+Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
+This led to the exclusion of an average of `r mean(rejected_epochs)` trials per participant (= `r percent(mean(rejected_epochs) / 360, accuracy = 0.1)`; range `r min(rejected_epochs)`--`r max(rejected_epochs)` trials).
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+
+## Statistical Analyses
+
+First, we excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight phase (i.e., before any keywords were presented).
+This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of unfamiliar objects).
+Next, to delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight phase) and the behavioral responses of the participant (see Figure \@ref(fig:fig1)A).
+Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if the participant indicated knowing what the object was or having an assumption.
+This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
+Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if the participant indicated not knowing what the object was or having rather no assumption.
+This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
+The same assignment of objects to conditions (based on the manipulation and responses in the insight phase) was also used for analyzing the pre-insight and post-insight parts.
+This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).
+
+The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single-trial level using linear mixed-effects regression models [@baayen2008; @fromer2018].
+Compared to traditional by-participant or by-item analyses of variance, these models allow tighter control over the false positive rate because they simultaneously account for by-participant and by-item non-independencies in the data [@burki2018; @judd2012].
+Furthermore, they flexibly handle unbalanced data.
+This was important in our case because of the rejection of bad ERP epochs as well as the way we constructed our experimental conditions (see above).
+
+Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
+All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three parts; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
+To determine the random effects structure, we always started with the maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
+We then performed a model selection algorithm proposed by @matuschek2017 to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
+Only if the parsimonious model explained the data similarly well as the complex model [determined by *p* $\geq$ .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the resulting formulas after model selection).
+All models were computed in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4].
+The optimizer function *bobyqa* with a maximum of 10^6^ iterations was used for maximum likelihood estimation.
+The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`; @R-buildmer].
+
+To investiage if semantically informed perception had an influence on the ERPs within each phase, planned follow-up comparisons were calculated, contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight parts.
+This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`; @R-emmeans].
+All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`; @R-lmerTest].
+
+The stimuli and analysis code for this study are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
+Lack of consent prevents us from sharing the raw EEG data.
+
+## Time-frequency analysis
+
+Semantically informed perception may manifest itself not only in changes in evoked activity (as captured by the ERP analysis), but also in induced activity.
+We therefore carried out an exploratory time-frequency analysis.
+We first created new epochs from the ICA-corrected but unfiltered raw data.
+To avoid differences between conditions due to a difference in noise levels, we equated the number of objects per condition for each participant by discarding a random sample of objects from the semantically naive condition.
+Epochs that were marked as bad for the ERP analysis (defined as peak-to-peak amplitudes exceeding 200 µV) were also removed from the time-frequency analysis.
+The remaining epochs were then convolved with a family of 24 Morlet wavelets using the short-time Fourier transform.
+The frequency of these wavelets increased linearly from 4 Hz to 50 Hz in steps of 2 Hz and the number of cycles increased linearly from 3 cycles to 10 cycles in steps of 0.304 cycles [see @samaha2018].
+The resulting single-trial time-frequency data were converted into percent signal change to adjust for power-law scaling.
+This was achieved by first subtracting and then dividing by the mean acitivity during the baseline period, defined as 300--100 ms before object onset.
 

### 2022-07-08 manuscript_files/helper_functions.R

@@ -17,10 +17,10 @@ plot_fig1a <- function(files_dir) {
         coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
         theme_void() +
         theme(aspect.ratio = 0.5) +
-        ## PART II ##
+        ## INSIGHT PHASE ##
         # Title
         annotate(
-            geom = "text", x = 0, y = 97.2, label = "Insight part",
+            geom = "text", x = 0, y = 97.2, label = "Insight phase",
             size = 14 / .pt, family = "Helvetica", fontface = "bold"
         ) +
         # Arrow
@@ -170,10 +170,10 @@ plot_fig1a <- function(files_dir) {
             family = "Helvetica", color = aha_colors[2],
             lineheight = 1
         ) +
-        ## PART I ##
+        ## PRE-INSIGHT PHASE ##
         # Title
         annotate(
-            geom = "text", x = -72, y = 56, label = "Pre-insight part",
+            geom = "text", x = -72, y = 56, label = "Pre-insight phase",
             size = 14 / .pt, family = "Helvetica", fontface = "bold"
         ) +
         # Arrow
@@ -209,15 +209,15 @@ plot_fig1a <- function(files_dir) {
             geom = "text", x = -72, y = 7.9,
             label = paste(
                 "Objects classified according",
-                "to conditions in the insight part",
+                "to conditions in the insight phase",
                 sep = "\n"
             ),
             family = "Helvetica", lineheight = 1
         ) +
-        # PART III
+        ## POST-INSIGHT PHASE ##
         # Title
         annotate(
-            geom = "text", x = 72, y = 56, label = "Post-insight part",
+            geom = "text", x = 72, y = 56, label = "Post-insight phase",
             size = 14 / .pt, family = "Helvetica", fontface = "bold"
         ) +
         # Arrow
@@ -253,7 +253,7 @@ plot_fig1a <- function(files_dir) {
             geom = "text", x = 72, y = 7.9,
             label = paste(
                 "Objects classified according",
-                "to conditions in the insight part",
+                "to conditions in the insight phase",
                 sep = "\n"
             ),
             family = "Helvetica", lineheight = 1
@@ -410,6 +410,9 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
             topo$layers[[5]]$aes_params$size <- 0.5
             topo$layers[[6]]$aes_params$size <- 0.3
             topo$layers[[7]]$aes_params$size <- 0.4
+
[…]

### 2022-07-09 manuscript.Rmd
Update preprocessing

@@
   downsample_sfreq = 125,
-  bad_channels = "auto",
+  bad_channels = NULL,
   ocular_correction = "auto",
   highpass_freq = 0.1,
-  lowpass_freq = 40,
+  lowpass_freq = 30,
   triggers = c(221, 222),
@@
 # Save models
-saveRDS(models, models_file)
+saveRDS(models, here(output_dir, "models.RDS"))
 ```

### 2022-07-13 manuscript_files/helper_functions.R
Add legends to Figure 1

@@ -9,12 +9,19 @@ annotate_text <- function(...) {
 }
 
 plot_fig1a <- function(files_dir) {
+
+    # Make sure that packages are loaded
+    require(tidyverse)
+    require(cowplot)
+
     # Trial structure
     example_stim <- magick::image_read(
         here::here(files_dir, "example_stim.png")
     )
     ggplot() +
-        coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
+        coord_cartesian(
+            xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE
+        ) +
         theme_void() +
         theme(aspect.ratio = 0.5) +
         ## INSIGHT PHASE ##
@@ -35,11 +42,11 @@ plot_fig1a <- function(files_dir) {
         ) +
         annotate(
             geom = "rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65,
-            color = aha_colors[1], fill = "white"
+            color = aha_colors[2], fill = "white"
         ) +
         annotate(
             geom = "rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89,
-            color = aha_colors[2], fill = "white"
+            color = aha_colors[1], fill = "white"
         ) +
         annotate(
             geom = "rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79,
@@ -54,12 +61,12 @@ plot_fig1a <- function(files_dir) {
             family = "Helvetica"
         ) +
         annotate(
-            geom = "text", x = -9, y = 55, label = "potatoes\nmashing",
-            family = "Helvetica", color = aha_colors[1]
+            geom = "text", x = -9, y = 55, label = "message\nsignaling",
+            family = "Helvetica", color = aha_colors[2]
         ) +
         annotate(
-            geom = "text", x = -9, y = 79, label = "message\nsignaling",
-            family = "Helvetica", color = aha_colors[2]
+            geom = "text", x = -9, y = 79, label = "potatoes\nmashing",
+            family = "Helvetica", color = aha_colors[1]
         ) +
         annotate(
             geom = "text", x = 9, y = 67, label = "*", size = 30 / .pt,
@@ -262,6 +269,10 @@ plot_fig1a <- function(files_dir) {
 
 plot_fig1b <- function(evokeds, config, channel_locations, models) {
 
+    # Make sure that packages are loaded
+    require(tidyverse)
+    require(cowplot)
+
     # Loop over ERP components of interest
[…]

### 2022-07-13 manuscript.Rmd
Update layout, references

--- 2022-07-08 manuscript.Rmd
@@
 
-abstract: |
-  Does our perception of an object change as soon as we discover what function it serves?
-  This question matters not only when we encounter novel tools or gadgets in our everyday lives, but also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
-  Here, we showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
-  We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-  We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms) and reduced amplitudes in the N400 component (400--700 ms).
-  When the same objects were presented once more without any information, the N400 effect persisted and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
-  Consistent with previous work, our results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
-  We demonstrate for the first time that these effects are instantaneous in the sense that they can be observed within the same trial as well as one trial after the information has been given, providing strong evidence that cognition affects perception.
-
-keywords          : "objects, semantic knowledge, visual perception, event-related potentials"
-
 floatsintext      : yes
@@
 bibliography      : ["manuscript_files/references.bib", "manuscript_files/r-references.bib"]
-csl               : "manuscript_files/apa.csl"
+csl               : "manuscript_files/citation_style.csl"
 
@@
   - \geometry{a4paper}
-  - \fancyheadoffset[R,L]{0pt}
   - \raggedbottom
   - \usepackage[all]{nowidow}
-  - \usepackage[bottom]{footmisc}
-  - \interfootnotelinepenalty=10000
-  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=period,name=Figure,textfont=normalfont}
+  - \captionsetup[figure]{belowskip=10pt,font={small,stretch=1},labelfont=bf,labelsep=period,name=Figure,textfont=normalfont}
 ---
@@
 ```
+
+# Abstract
+
+Does our perception of an object change as soon as we discover what function it serves?
+This question matters not only when we encounter novel tools or gadgets in our everyday lives, but also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
+Here, we showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
+We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
+We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms) and reduced amplitudes in the N400 component (400--700 ms).
+When the same objects were presented once more without any information, the N400 effect persisted and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
+Consistent with previous work, our results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
+We demonstrate for the first time that these effects are instantaneous in the sense that they can be observed within the same trial as well as one trial after the information has been given, providing strong evidence that cognition affects perception.
+
+*Key words*: objects; semantic knowledge; visual perception; event-related potentials
+
+# Significance statement
+
+There has been a long-standing debate about whether or not higher-level cognitive capacities such as semantic knowledge can influence lower-level perceptual processing in a top-down fashion.
+Here we could show for the first time that information about the function of previously unfamiliar objects immediately influences cortical processing within less than 200 ms.
+Of note, this influence does not require training or experience with the objects and related semantic information.
+Therefore, our study is the first to show effects of cognition on perception while ruling out the possibility that prior knowledge merely acts by pre-activating or altering stored visual representations.
+Instead, this knowledge seems to alter perception online, thus providing a compelling case against the cognitive impenetrability of perception by cognition.
+
+\newpage
 
@@
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\bigskip
 
 <div id="refs" custom-style="Bibliography"></div>
-\endgroup

### 2022-07-19 manuscript.Rmd
Update re-run logic for preprocessing

@@
   The authors declare no competing financial interests.
-  The preprocessed data and analaysis code for this study are openly available at https://osf.io/uksbc/.
+  The code for this study is available at [https://osf.io/uksbc](https://osf.io/uksbc).
 
@@
 
+\bigskip
+
 # Significance statement
@@
 
-For each unfamiliar object, a pair of German keywords---a noun and a verb---was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
 As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
@@
 
-```{r, eeg_processing, eval=run$eeg_processing}
-# Process behavioral data
-c(
-  list.files(here(data_dir, "rt/exp1"), "*.txt", full.names = TRUE),
-  list.files(here(data_dir, "rt/exp2"), "*.txt", full.names = TRUE)
-) %>%
-  # Process each log file
-  map(function(log_file) {
+```{r, eeg_processing}
+# Define function for processing behavioral log files
+read_log <- function(log_file) {
 
@@
   log %>%
-      select(item_id, phase, condition, response, rt) %>%
-      return()
-  }) -> logs
+    select(item_id, phase, condition, response, rt)
+}
 
-# Import EEG pipeline from Python
-pipeline <- import("pipeline")
+# Get list of behavioral log files
+log_files <- c(
+  list.files(here(data_dir, "rt/exp1"), "*.txt", full.names = TRUE),
+  list.files(here(data_dir, "rt/exp2"), "*.txt", full.names = TRUE)
+)
 
@@
 )
+
+# Import EEG pipeline from Python
+pipeline <- import("pipeline")
+
+# Extract versions of Python packages
+pipeline_version <- pipeline$`__version__`
+mne_version <- import("mne")$`__version__`
+
+# Do the actual preprocessing if requested
+if (run$eeg_processing) {
+
+  # Process behavioral data
+  logs <- map(log_files, read_log)
 
@@
   )
-```
+}
 
-```{r, read_results}
 # Read single trial data
@@
 
-The data were preprocessed offline using the MNE software [Version `r system("mne --version", intern = TRUE) %>% str_remove("MNE ")`\; @gramfort2013] in Python [Version `r system("python3 --version", intern = TRUE) %>% str_remove("Python ")`\; @vanrossum2009].
-First, all scalp electrodes were re-referenced to the common average.
+The data were preprocessed offline using custom scripts, packaged in the hu-neuro-pipeline library (Version `r pipeline_version`; https://github.com/alexenge/hu-neuro-pipeline) and based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
+First, the data were were downsampled to `r config$downsample_sfreq` Hz re-referenced to the common average of all scalp channels.
 Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
 The first 15 components were extracted with the FastICA algorithm [@hyvarinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Any components showing substantive correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the *find_bads_eog* function.
-After artifact correction, a zero-phase, non-causal FIR filter with a lower pass-band edge at 0.1 Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at 30 Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was epoched into segments of 2 s, starting 500 ms before the onset of the presentation of each unfamiliar object.
-The epochs were baseline-corrected by subtracting the average voltage during the 200 ms before stimulus onset.
-Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding 200 µV, were removed from further analysis.
+Any components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the MNE-Python's `find_bads_eog` method.
+
+## ERP analysis
+
+For the analysis of ERP voltages, a zero-phase, non-causal FIR filter with a lower pass-band edge at `r config$highpass_freq` Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at `r config$lowpass_freq` Hz (transition bandwidth: 7.5 Hz) was applied.
+Next, the continuous EEG was segmented into epochs ranging from `r config$epochs_tmin` s to `r config$epochs_tmax` relative the onset of the presentation of each unfamiliar object.
+These epochs were baseline-corrected by subtracting the average voltage during the interval of `r config$baseline_tmin` to `r config$baseline_tmax` relative to stimulus onset.
+Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV, were removed from further analysis.
 This led to the exclusion of an average of `r mean(rejected_epochs)` trials per participant (= `r percent(mean(rejected_epochs) / 360, accuracy = 0.1)`; range `r min(rejected_epochs)`--`r max(rejected_epochs)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, PO4, POz, O1, O2, and Oz for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, POz, PO4, O1, Oz, and O2 and for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, Cz, C2, CP1, CPz, and CP2 for the N400 component.
+
+## Time-frequency analysis
+
+For the analysis of event-related power,
+
+Semantically informed perception may manifest itself not only in changes in evoked activity (as captured by the ERP analysis), but also in induced activity.
+We therefore carried out an exploratory time-frequency analysis.
+We first created new epochs from the ICA-corrected but unfiltered raw data.
+To avoid differences between conditions due to a difference in noise levels, we equated the number of objects per condition for each participant by discarding a random sample of objects from the semantically naive condition.
+Epochs that were marked as bad for the ERP analysis (defined as peak-to-peak amplitudes exceeding 200 µV) were also removed from the time-frequency analysis.
+The remaining epochs were then convolved with a family of 24 Morlet wavelets using the short-time Fourier transform.
+The frequency of these wavelets increased linearly from 4 Hz to 50 Hz in steps of 2 Hz and the number of cycles increased linearly from 3 cycles to 10 cycles in steps of 0.304 cycles [see @samaha2018].
+The resulting single-trial time-frequency data were converted into percent signal change to adjust for power-law scaling.
+This was achieved by first subtracting and then dividing by the mean acitivity during the baseline period, defined as 300--100 ms before object onset.
 
@@
 Lack of consent prevents us from sharing the raw EEG data.
-
-## Time-frequency analysis
-
-Semantically informed perception may manifest itself not only in changes in evoked activity (as captured by the ERP analysis), but also in induced activity.
-We therefore carried out an exploratory time-frequency analysis.
-We first created new epochs from the ICA-corrected but unfiltered raw data.
-To avoid differences between conditions due to a difference in noise levels, we equated the number of objects per condition for each participant by discarding a random sample of objects from the semantically naive condition.
-Epochs that were marked as bad for the ERP analysis (defined as peak-to-peak amplitudes exceeding 200 µV) were also removed from the time-frequency analysis.
-The remaining epochs were then convolved with a family of 24 Morlet wavelets using the short-time Fourier transform.
-The frequency of these wavelets increased linearly from 4 Hz to 50 Hz in steps of 2 Hz and the number of cycles increased linearly from 3 cycles to 10 cycles in steps of 0.304 cycles [see @samaha2018].
-The resulting single-trial time-frequency data were converted into percent signal change to adjust for power-law scaling.
-This was achieved by first subtracting and then dividing by the mean acitivity during the baseline period, defined as 300--100 ms before object onset.
 

### 2022-07-31 manuscript.Rmd
Make HPC ready

@@
 output_dir <- here("output")
+report_dir <- here("output/qc_reports")
 
@@
 run <- list(
-  eeg_processing = FALSE,
-  mixed_models = FALSE
+  eeg_processing = TRUE,
+  mixed_models = TRUE
 )
@@
     output_dir = output_dir,
-    report_dir = NULL,
+    epochs_dir = here(output_dir, "epochs"),
+    report_dir = report_dir,
     downsample_sfreq = 125,
@@
     baseline_tmax = 0.0,
-    reject_peak_to_peak = 200,
+    reject_peak_to_peak = 150,
     components = list(

### 2022-07-31 run_slurm.sh

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+# Parse input arguments
+PROJECT_DIR=$1
+REMOTE_DIR=$2
+REMOTE_HOME=$3
+IMAGE_FILE=$4
+
+# Knit the document
+singularity exec \
+    --bind "$PROJECT_DIR":"$REMOTE_DIR" \
+    --cleanenv \
+    --home "$REMOTE_HOME" \
+    --no-home \
+    --pwd "$REMOTE_DIR" \
+    "$IMAGE_FILE" \
+    Rscript -e "rmarkdown::render(input = 'manuscript.Rmd')"

### 2022-08-05 manuscript.Rmd
Upgrade to latest `hu-neuro-pipeline`

@@
     report_dir = report_dir,
-    downsample_sfreq = 125,
+    downsample_sfreq = 125.0,
     bad_channels = NULL,
-    ocular_correction = "auto",
+    ica_method = "fastica",
+    ica_n_components = 0.99,
     highpass_freq = 0.1,
-    lowpass_freq = 30,
+    lowpass_freq = 30.0,
     triggers = c(221, 222),
@@
     baseline_tmax = 0.0,
-    reject_peak_to_peak = 150,
+    reject_peak_to_peak = 150.0,
     components = list(
@@
 # Count number of rejected epochs per participant
-rejected_epochs <- lengths(config$rejected_epochs)
+rejected_epochs <- lengths(config$auto_rejected_epochs)
 

### 2022-08-05 manuscript.Rmd
Use bonferroni correction for contrasts

@@
   specs <- pairwise ~ condition | phase
-  em <- emmeans(build@model, specs, infer = TRUE)
+  means <- emmeans(build@model, specs = c("phase", "condition"))
+  contrasts <- contrast(means, "pairwise", simple = "condition") %>%
+    summary(by = NULL, adjust = "bonferroni")
 
@@
     "anova" = build@anova,
-    "means" = em$emmeans,
-    "contrasts" = em$contrasts
+    "means" = means,
+    "contrasts" = contrasts
   ) %>%

### 2022-08-09 manuscript.Rmd
Fix latest pipeline in Dockerfile

--- 2022-07-31 manuscript.Rmd
@@
 output_dir <- here("output")
-report_dir <- here("output/qc_reports")
 
@@
 run <- list(
-  eeg_processing = TRUE,
-  mixed_models = TRUE
+  eeg_processing = FALSE,
+  mixed_models = FALSE
 )
@@
 
-# Significance statement
+# Significance Statement
 
@@
 
-## Materials
+## Stimuli
 
@@
     output_dir = output_dir,
-    epochs_dir = here(output_dir, "epochs"),
-    report_dir = report_dir,
+    report_dir = NULL,
     downsample_sfreq = 125,
@@
     baseline_tmax = 0.0,
-    reject_peak_to_peak = 150,
+    reject_peak_to_peak = 200,
     components = list(
@@
 channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
+
+channels <- channel_locations$channel
+# evokeds %>%
+#   filter(phase == "Pre-insight" & between(time, 0.4, 0.7)) %>%
+#   select(participant_id, condition, all_of(channels)) %>%
+#   group_by(participant_id, condition) %>%
+#   summarise(across(channels, mean), .groups = "drop") -> means
+
+# diffs <- filter(means, condition == "Informed")[channels] -
+#   filter(means, condition == "Naive")[channels]
+# diffs %>%
+#   as_tibble() %>%
+#   print(n = Inf)
+
+# evokeds %>%
+#   filter(participant_id == "VP0001" & phase == "Pre-insight" & condition == "Informed") %>%
+#   print(n = Inf)
+
+epochs <- read_csv(here(output_dir, "epochs", "VP0001_epo.csv"))
+# epochs %>%
+#   filter(phase == "Pre-insight") %>%
+#   filter(between(time, 0.4, 0.7)) %>%
+#   mutate(epoch = factor(epoch)) %>%
+#   ggplot(aes(x = time, y = AF7, color = epoch, group = epoch)) +
+#   geom_line()
+
+epochs %>%
+  filter(phase == "Pre-insight" & between(time, 0.4, 0.7)) %>%
+  group_by(condition, epoch) %>%
+  summarise(across(all_of(channels), mean)) %>%
+  arrange((AF7))
+
+  # filter(Wdh == 211 & condition == 222) %>%
+  # filter(between(time, 0.4, 0.7)) %>%
+  # group_by(epoch) %>%
+  # summarise(AF7 = mean(AF7)) %>%
+  # print(n = Inf)
 ```
@@
 
+## Behavioral Data Analysis
+
+We first excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight phase (i.e., before any keywords were presented).
+This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of unfamiliar objects).
+Next, to delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral responses of the participant in the insight phase (see Figure \@ref(fig:fig1)A).
+Objects were assigned to the semantically informed condition if they were presented with matching keywords *and* if the participant indicated knowing what the object was or having an assumption.
+This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
+Complementarily, objects were assigned to the naive condition if they were presented with non-matching keywords *and* if the participant indicated not knowing what the object was or having rather no assumption.
+This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
+The same assignment of objects to conditions (based on the manipulation and responses in the insight phase) was also used for analyzing the pre-insight and post-insight parts.
+This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).
+
 ## EEG Recording and Preprocessing
@@
 
-The data were preprocessed offline using custom scripts, packaged in the hu-neuro-pipeline library (Version `r pipeline_version`; https://github.com/alexenge/hu-neuro-pipeline) and based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
-First, the data were were downsampled to `r config$downsample_sfreq` Hz re-referenced to the common average of all scalp channels.
-Next, artifacts resulting from blinks and eye movements were removed using independent component analysis (ICA).
-The first 15 components were extracted with the FastICA algorithm [@hyvarinen1999] after temporarily low-pass filtering the data at 1 Hz.
-Any components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the MNE-Python's `find_bads_eog` method.
+The data were preprocessed offline using custom scripts, available online in the hu-neuro-pipeline package (Version `r pipeline_version`; https://github.com/alexenge/hu-neuro-pipeline) and based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
+First, the data were were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
+Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a low-pass filtered copy of the data (cutoff = 1 Hz).
+A variable number of components per participants were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (median = `r mean(config$auto_ica_n_components)` components, range `r min(config$auto_ica_n_components)`--`r max(config$auto_ica_n_components)`).
+Then the ICA was fitted using the FastICA algorithm [@hyvarinen1999].
+Any independent components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the MNE-Python's `find_bads_eog` method.
 
-## ERP analysis
+## Event-Related Potential Analysis
 
@@
 This led to the exclusion of an average of `r mean(rejected_epochs)` trials per participant (= `r percent(mean(rejected_epochs) / 360, accuracy = 0.1)`; range `r min(rejected_epochs)`--`r max(rejected_epochs)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms after object onset at electrodes PO3, POz, PO4, O1, Oz, and O2 and for the P1 component, 150--200 ms after object onset at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms after object onset at electrodes C1, Cz, C2, CP1, CPz, and CP2 for the N400 component.
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms at electrodes PO3, POz, PO4, O1, Oz, and O2 and for the P1 component, 150--200 ms at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at electrodes C1, Cz, C2, CP1, CPz, and CP2 for the N400 component.
 
-## Time-frequency analysis
+The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because they allow to control for repeated measures of participants and items while also being robust against an unbalanced number of trials per condition [@baayen2008; @burki2018; @fromer2018].
 
-For the analysis of event-related power,
-
-Semantically informed perception may manifest itself not only in changes in evoked activity (as captured by the ERP analysis), but also in induced activity.
-We therefore carried out an exploratory time-frequency analysis.
-We first created new epochs from the ICA-corrected but unfiltered raw data.
-To avoid differences between conditions due to a difference in noise levels, we equated the number of objects per condition for each participant by discarding a random sample of objects from the semantically naive condition.
-Epochs that were marked as bad for the ERP analysis (defined as peak-to-peak amplitudes exceeding 200 µV) were also removed from the time-frequency analysis.
-The remaining epochs were then convolved with a family of 24 Morlet wavelets using the short-time Fourier transform.
-The frequency of these wavelets increased linearly from 4 Hz to 50 Hz in steps of 2 Hz and the number of cycles increased linearly from 3 cycles to 10 cycles in steps of 0.304 cycles [see @samaha2018].
-The resulting single-trial time-frequency data were converted into percent signal change to adjust for power-law scaling.
-This was achieved by first subtracting and then dividing by the mean acitivity during the baseline period, defined as 300--100 ms before object onset.
-
-## Statistical Analyses
-
-First, we excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight phase (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of unfamiliar objects).
-Next, to delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight phase) and the behavioral responses of the participant (see Figure \@ref(fig:fig1)A).
-Objects were assigned to the semantically informed condition only if they were presented with matching keywords *and* if the participant indicated knowing what the object was or having an assumption.
-This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords *and* if the participant indicated not knowing what the object was or having rather no assumption.
-This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
-The same assignment of objects to conditions (based on the manipulation and responses in the insight phase) was also used for analyzing the pre-insight and post-insight parts.
-This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).
-
-The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single-trial level using linear mixed-effects regression models [@baayen2008; @fromer2018].
-Compared to traditional by-participant or by-item analyses of variance, these models allow tighter control over the false positive rate because they simultaneously account for by-participant and by-item non-independencies in the data [@burki2018; @judd2012].
-Furthermore, they flexibly handle unbalanced data.
-This was important in our case because of the rejection of bad ERP epochs as well as the way we constructed our experimental conditions (see above).
-
-Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively.
+We computed three models predicting P1, N170, and N400 amplitudes, respectively.
 All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three parts; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
-To determine the random effects structure, we always started with the maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects [@barr2013].
-We then performed a model selection algorithm proposed by @matuschek2017 to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test.
-Only if the parsimonious model explained the data similarly well as the complex model [determined by *p* $\geq$ .20; @matuschek2017] did we leave the random effect out, otherwise it was kept in the final model (see Appendix B for the resulting formulas after model selection).
-All models were computed in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4].
-The optimizer function *bobyqa* with a maximum of 10^6^ iterations was used for maximum likelihood estimation.
+We determined the most parsimonous random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
+This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20).
+All models were fitted in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4] with the optimizer function *bobyqa* and a maximum of 10^6^ iterations for maximum likelihood estimation.
 The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`; @R-buildmer].
 
-To investiage if semantically informed perception had an influence on the ERPs within each phase, planned follow-up comparisons were calculated, contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight parts.
+To investiage if semantically informed perception had an influence on the ERPs within each phase, planned follow-up comparisons were calculated, contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
 This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`; @R-emmeans].
@@
 
-The stimuli and analysis code for this study are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
-Lack of consent prevents us from sharing the raw EEG data.
+## Time-Frequency Analysis
+
+For our exploratory analysis of event-related power, we first created new epochs from the ICA-corrected but unfiltered raw data.
+Epochs that were marked as bad for the ERP analysis (i.e., with peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV) were also removed from the time-frequency analysis.
+The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their number of cycles from `r min(config$tfr_cycles)` to `r max(config$tfr_cycles)` in steps of `r config$tfr_freqs[2] - config$tfr_cycles[1]` [cf.
+@samaha2018].
+To adjust for the power-law scaling of the human EEG, the power values were transformed into percent signal change by first subtracting and then dividing by the average power at each frequency over the entire epoch [@grandchamp2011].
+We then performed baseline correction by subtracting the average during the pre-stimulus interval from `r config$tfr_baseline_tmin` to `r config$tfr_baseline_tmax` relative to object onset.
+
+## Data and Code Availability
+
+The EEG data are available upon reasonable request from the corresponding author because we did not ask participants for their consent to make the data publicly avaible.
+The stimuli and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
 
@@
 
-```{r}
+```{r, eval=FALSE}
 # Read grand-averaged power
@@
 
+# Results
+
+## Event-Related Potentials
+
 \newpage

### 2022-08-09 manuscript.Rmd

@@
     output_dir = output_dir,
-    report_dir = NULL,
-    downsample_sfreq = 125,
+    epochs_dir = here(output_dir, "epochs"),
+    report_dir = report_dir,
+    downsample_sfreq = 125.0,
     bad_channels = NULL,
-    ocular_correction = "auto",
+    ica_method = "fastica",
+    ica_n_components = 0.99,
     highpass_freq = 0.1,
-    lowpass_freq = 30,
+    lowpass_freq = 30.0,
     triggers = c(221, 222),
@@
     baseline_tmax = 0.0,
-    reject_peak_to_peak = 200,
+    reject_peak_to_peak = 150.0,
     components = list(

### 2022-08-14 manuscript.Rmd
Improve text in methods

@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming).
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage--measuring; clay pot--drumming).
 As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
@@
 
-The experiment consisted of three parts (see Figure \@ref(fig:fig1)A).
+The experiment consisted of three phases (see Figure \@ref(fig:fig1)A).
 In the *pre-insight* phase, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
@@
 The inter-trial interval was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same across all three parts, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same across all three phases, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
@@
 channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
-
-channels <- channel_locations$channel
-# evokeds %>%
-#   filter(phase == "Pre-insight" & between(time, 0.4, 0.7)) %>%
-#   select(participant_id, condition, all_of(channels)) %>%
-#   group_by(participant_id, condition) %>%
-#   summarise(across(channels, mean), .groups = "drop") -> means
-
-# diffs <- filter(means, condition == "Informed")[channels] -
-#   filter(means, condition == "Naive")[channels]
-# diffs %>%
-#   as_tibble() %>%
-#   print(n = Inf)
-
-# evokeds %>%
-#   filter(participant_id == "VP0001" & phase == "Pre-insight" & condition == "Informed") %>%
-#   print(n = Inf)
-
-epochs <- read_csv(here(output_dir, "epochs", "VP0001_epo.csv"))
-# epochs %>%
-#   filter(phase == "Pre-insight") %>%
-#   filter(between(time, 0.4, 0.7)) %>%
-#   mutate(epoch = factor(epoch)) %>%
-#   ggplot(aes(x = time, y = AF7, color = epoch, group = epoch)) +
-#   geom_line()
-
-epochs %>%
-  filter(phase == "Pre-insight" & between(time, 0.4, 0.7)) %>%
-  group_by(condition, epoch) %>%
-  summarise(across(all_of(channels), mean)) %>%
-  arrange((AF7))
-
-  # filter(Wdh == 211 & condition == 222) %>%
-  # filter(between(time, 0.4, 0.7)) %>%
-  # group_by(epoch) %>%
-  # summarise(AF7 = mean(AF7)) %>%
-  # print(n = Inf)
 ```
@@
 In the post-insight phase, the same objects were presented again without keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies of the P1 component (100--150 ms, ***B***), of the N170 component (150--200 ms, ***C***), and of the N400 component (400--700 ms, ***D***) are shown for objects with semantically informed versus naive perception within the three different parts.
-Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight parts, and more positive amplitudes in the P1 component during the post-insight phase.
-The time windows and channels for quantifying the different ERP components are highlighted by the gray areas in the ERP waveforms and the white markers on the scalp topographies, respectively.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies of the P1 component (100--150 ms, ***B***), of the N170 component (150--200 ms, ***C***), and of the N400 component (400--700 ms, ***D***) are shown for objects with semantically informed perception versus naive perception within the three different phases.
+Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
+The time windows and channels for quantifying the different ERP components are highlighted by the gray areas in the ERP waveforms and by the white markers on the scalp topographies, respectively.
 Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
@@
 In the *post-insight* phase, the unfamiliar objects were presented for a third time with the same trial structure as in the pre-insight phase, that is, without any keywords.
-The insight and post-insight parts were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight phase (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight phase (without keywords) before moving on to the next block consisting of 30 different objects.
-They continued like this until all four blocks were completed in both parts.
-In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight phase and 120 unfamiliar objects in the pre-insight, insight, and post-insight parts).
+The insight and post-insight phases were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight phase (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight phase (without keywords) before moving on to the next block consisting of 30 different objects.
+They continued like this until all four blocks were completed in both phases.
+In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight phase and 120 unfamiliar objects in the pre-insight, insight, and post-insight phases).
 It took participants approximately 35 minutes to complete.
@@
 We first excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight phase (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of unfamiliar objects).
-Next, to delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral responses of the participant in the insight phase (see Figure \@ref(fig:fig1)A).
+This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all unfamiliar objects).
+Next, to delineate semantically informed and naive perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral responses of the participant in the insight phase (see Figure \@ref(fig:fig1)A).
 Objects were assigned to the semantically informed condition if they were presented with matching keywords *and* if the participant indicated knowing what the object was or having an assumption.
@@
 This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
-The same assignment of objects to conditions (based on the manipulation and responses in the insight phase) was also used for analyzing the pre-insight and post-insight parts.
+The same assignment of objects to conditions, based on the manipulation and responses in the insight phase, was also used for analyzing the pre-insight and post-insight phases.
 This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).
@@
 Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a low-pass filtered copy of the data (cutoff = 1 Hz).
-A variable number of components per participants were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (median = `r mean(config$auto_ica_n_components)` components, range `r min(config$auto_ica_n_components)`--`r max(config$auto_ica_n_components)`).
+A variable number of components per participants were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (mean = `r mean(unlist(config$auto_ica_n_components))` components, range `r min(unlist(config$auto_ica_n_components))`--`r max(unlist(config$auto_ica_n_components))`).
 Then the ICA was fitted using the FastICA algorithm [@hyvarinen1999].
 Any independent components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the MNE-Python's `find_bads_eog` method.
+This was the case for an average of `r mean(lengths(config$auto_ica_bad_components))` components per participant (range = `r min(lengths(config$auto_ica_bad_components))`--`r max(lengths(config$auto_ica_bad_components))`)
 
@@
 For the analysis of ERP voltages, a zero-phase, non-causal FIR filter with a lower pass-band edge at `r config$highpass_freq` Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at `r config$lowpass_freq` Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was segmented into epochs ranging from `r config$epochs_tmin` s to `r config$epochs_tmax` relative the onset of the presentation of each unfamiliar object.
-These epochs were baseline-corrected by subtracting the average voltage during the interval of `r config$baseline_tmin` to `r config$baseline_tmax` relative to stimulus onset.
+Next, the continuous EEG was segmented into epochs ranging from `r config$epochs_tmin` s to `r config$epochs_tmax` s relative the onset of the presentation of each unfamiliar object.
+These epochs were baseline-corrected by subtracting the average voltage during the interval of `r config$baseline_tmin` s to `r config$baseline_tmax` s relative to stimulus onset.
 Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV, were removed from further analysis.
@@
 
-The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because they allow to control for repeated measures of participants and items while also being robust against an unbalanced number of trials per condition [@baayen2008; @burki2018; @fromer2018].
+The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because they allow controlling for repeated measures of participants and stimuli while also being robust against unbalanced numbers of trials per condition [@baayen2008; @burki2018; @fromer2018].
 
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
-All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three parts; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
+All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
 We determined the most parsimonous random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
 This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20).
-All models were fitted in R [Version `r as.character(packageVersion("base"))`; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`; @R-lme4] with the optimizer function *bobyqa* and a maximum of 10^6^ iterations for maximum likelihood estimation.
-The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`; @R-buildmer].
+All models were fitted in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4] with the optimizer function *bobyqa* and a maximum of 10^6^ iterations for maximum likelihood estimation.
+The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`\; @R-buildmer].
 
 To investiage if semantically informed perception had an influence on the ERPs within each phase, planned follow-up comparisons were calculated, contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
-This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`; @R-emmeans].
-All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`; @R-lmerTest].
+This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
+All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
 
@@
 To adjust for the power-law scaling of the human EEG, the power values were transformed into percent signal change by first subtracting and then dividing by the average power at each frequency over the entire epoch [@grandchamp2011].
-We then performed baseline correction by subtracting the average during the pre-stimulus interval from `r config$tfr_baseline_tmin` to `r config$tfr_baseline_tmax` relative to object onset.
+We then performed baseline correction by subtracting the average during the pre-stimulus interval from `r config$tfr_baseline_tmin` s to `r config$tfr_baseline_tmax` s relative to object onset.
 
@@
 
-The EEG data are available upon reasonable request from the corresponding author because we did not ask participants for their consent to make the data publicly avaible.
+The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly avaible.
 The stimuli and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).

### 2022-08-15 manuscript.Rmd
Initialize TFR topography plot

@@
 
-```{r, tfr, include=TRUE, fig.height=12}
+```{r, tfr, fig.height=12, include=TRUE}
 # Read results of cluster-based permutation tests for TFR
@@
 
-```{r, eval=FALSE}
+```{r, fig2, fig.height=10, include=TRUE}
 # Read grand-averaged power
@@
 
-channels <- tfr_grand_ave %>%
-  select(-average_by, -phase, -condition, -time, -freq) %>%
-  colnames()
-
+# Compute difference between conditions within each phase
+channels <- channel_locations$channel
 tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
@@
 
-bind_rows(tfr_grand_ave, tfr_grand_ave_diff) %>%
-  mutate(
-    condition = factor(condition, levels = c("Informed", "Naive", "Difference"))
-  ) %>%
-  pivot_longer(
-    cols = all_of(channels), names_to = "electrode", values_to = "amplitude"
-  ) %>%
-  select(-average_by, -electrode) %>%
-  group_by(phase, condition, time, freq) %>%
-  summarise(amplitude = mean(amplitude), .groups = "drop") %>%
-  ggplot(aes(x = time, y = freq, fill = amplitude)) +
-  facet_grid(phase ~ condition) +
-  geom_raster() +
-  scale_fill_viridis_c(option = "turbo", limits = c(-0.6, 0.6)) +
-  coord_cartesian(expand = FALSE)
-
-tmins <- seq(0.0, 1.2, 0.2)
-fmins <- seq(4, 36, 4)
-
-channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
-
+# Plot topography at each time and frequency bin
+tstep <- 0.1
+fstep <- 4
+tmins <- seq(0.0, 0.9, tstep)
+fmins <- seq(4, 36, fstep)
 map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {
-  map(tmins, function(tmin, tstep = 0.2) {
+  # map(c("Insight"), function(this_phase) {
+  map(tmins, function(tmin) {
     tmax <- tmin + tstep
-    map(fmins, function(fmin, fstep = 4) {
+    map(fmins, function(fmin) {
       fmax <- fmin + fstep
+      tfr_clusters %>%
+        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
+        filter(str_detect(contrast, this_phase) & p_val < .05) %>%
+        pull(channel) %>%
+        unique() -> significant_channels
       tfr_grand_ave_diff %>%
@@
         eegUtils::topoplot(
+          r = 85,
           quantity = "power",
@@
           interp_limit = "skirt",
-          scaling = 0.7
+          highlights = significant_channels,
+          scaling = 1.1
         ) +
-        scale_fill_viridis_c(limits = c(-0.3, 0.3), option = "turbo") +
-        theme(legend.position = "none")
-    }) %>%
-      plot_grid(plotlist = ., nrow = 1)
-  }) %>%
-    plot_grid(plotlist = ., nrow = length(tmins))
+        scale_fill_distiller(limits = c(-0.25, 0.25), palette = "RdBu") +
+        # scale_fill_viridis_c(limits = c(-0.25, 0.25)) +
+        theme(
+          plot.margin = unit(rep(-0.2, 4), "cm"),
+          legend.position = "none"
+        ) -> topo
+      topo$layers[[3]]$aes_params$size <- 0.7
+      topo$layers[[4]]$aes_params$size <- 0.7
+      topo$layers[[5]]$aes_params$size <- 0.7
+      topo$layers[[6]]$aes_params$colour <- NA
+      topo$layers[[7]]$aes_params$size <- 0.4
+      topo$layers[[7]]$aes_params$colour <- "black"
+      topo
+    }) -> plotlist
+    plotlist <- c(plotlist, list(NULL))
+    rel_heights <- c(rep(1, length(fmins)), 0.15)
+    if (tmin == min(tmins)) {
+      labels <- paste0(fmins, "-", fmins + fstep, " Hz")
+      labels <- c(labels, "")
+      plot_grid(
+        plotlist = plotlist, nrow = length(plotlist),
+        rel_heights = rel_heights, labels = labels,
+        label_size = 10, label_fontfamily = "Helvetica",
+        label_fontface = "plain", label_x = -0.3, label_y = 0.5, vjust = 0.5,
+        hjust = 0.5
+      )
+    } else {
+      plot_grid(
+        plotlist = plotlist, nrow = length(plotlist), rel_heights = rel_heights
+      )
+    }
+  }) -> plotlist
+  tmins_str <- format(tmins, nsmall = 1)
+  tmaxs_str <- format(tmins + tstep, nsmall = 1)
+  labels <- paste0(tmins_str, "-", tmaxs_str, " s")
+  plotlist <- c(list(NULL), plotlist)
+  labels <- c("", labels)
+  plot_grid(
+    plotlist = plotlist, nrow = 1, rel_widths = c(0.6, rep(1, length(tmins))),
+    labels = labels, label_size = 10, label_fontfamily = "Helvetica",
+    label_fontface = "plain", label_x = 0.5, label_y = 0.01, vjust = 0.5,
+    hjust = 0.5
+  )
+  filename <- paste0("tfr_", this_phase, ".pdf")
+  ggsave(filename, width = 12, height = 10)
 })

### 2022-08-15 manuscript.Rmd
Move code for Figure 2 to helper script

--- 2022-08-14 manuscript.Rmd
@@
 
-```{r, eval=FALSE}
+```{r, fig2a, fig.height=10, include=TRUE}
 # Read grand-averaged power
-tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv")) %>%
-  mutate(
-    phase = factor(phase, levels = c("Pre-insight", "Insight", "Post-insight")),
-    condition = factor(condition, levels = c("Informed", "Naive"))
-  ) %>%
-  filter(!is.na(condition))
+tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))
 
-channels <- tfr_grand_ave %>%
-  select(-average_by, -phase, -condition, -time, -freq) %>%
-  colnames()
+# Create topographic plots for event-related power in each phase
+tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)
 
-tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
-tfr_grand_ave_naive <- filter(tfr_grand_ave, condition == "Naive")
-tfr_grand_ave_diff <- mutate(tfr_grand_ave_informed, condition = "Difference")
-tfr_grand_ave_diff[channels] <- tfr_grand_ave_informed[channels] -
-  tfr_grand_ave_naive[channels]
+# Plot Pre-Insight Phase
+tfr_plots[[1]]
+```
 
-bind_rows(tfr_grand_ave, tfr_grand_ave_diff) %>%
-  mutate(
-    condition = factor(condition, levels = c("Informed", "Naive", "Difference"))
-  ) %>%
-  pivot_longer(
-    cols = all_of(channels), names_to = "electrode", values_to = "amplitude"
-  ) %>%
-  select(-average_by, -electrode) %>%
-  group_by(phase, condition, time, freq) %>%
-  summarise(amplitude = mean(amplitude), .groups = "drop") %>%
-  ggplot(aes(x = time, y = freq, fill = amplitude)) +
-  facet_grid(phase ~ condition) +
-  geom_raster() +
-  scale_fill_viridis_c(option = "turbo", limits = c(-0.6, 0.6)) +
-  coord_cartesian(expand = FALSE)
+```{r, fig2b, fig.height=10, include=TRUE}
+# Plot Insight Phase
+tfr_plots[[2]]
+```
 
-tmins <- seq(0.0, 1.2, 0.2)
-fmins <- seq(4, 36, 4)
-
-channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
-
-map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {
-  map(tmins, function(tmin, tstep = 0.2) {
-    tmax <- tmin + tstep
-    map(fmins, function(fmin, fstep = 4) {
-      fmax <- fmin + fstep
-      tfr_grand_ave_diff %>%
-        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
-        filter(phase == this_phase) %>%
-        pivot_longer(
-          cols = all_of(channels), names_to = "electrode", values_to = "power"
-        ) %>%
-        left_join(channel_locations, by = c("electrode" = "channel")) %>%
-        group_by(electrode, x, y) %>%
-        summarise(power = mean(power), .groups = "drop") %>%
-        eegUtils::topoplot(
-          quantity = "power",
-          contour = FALSE,
-          interp_limit = "skirt",
-          scaling = 0.7
-        ) +
-        scale_fill_viridis_c(limits = c(-0.3, 0.3), option = "turbo") +
-        theme(legend.position = "none")
-    }) %>%
-      plot_grid(plotlist = ., nrow = 1)
-  }) %>%
-    plot_grid(plotlist = ., nrow = length(tmins))
-})
+```{r, fig2c, fig.height=10, include=TRUE}
+# Plot Post-Insight Phase
+tfr_plots[[3]]
 ```

### 2022-08-15 manuscript_files/helper_functions.R

@@ -507,3 +507,111 @@ plot_fig1 <- function(files_dir, evokeds, config, channel_locations, models) {
 
 # plot_fig1(files_dir, evokeds, config, channel_locations, models)
 # ggsave("fig1.pdf", width = 12, height = 12)
+
+plot_fig2 <- function(tfr_grand_ave,
+                      tfr_clusters,
+                      channel_locations,
+                      tmin = 0.0,
+                      tmax = 1.0,
+                      tstep = 0.1,
+                      fmin = 4,
+                      fmax = 40,
+                      fstep = 4) {
+
+    # Read grand-averaged power
+    tfr_grand_ave %>%
+        mutate(
+            phase = factor(phase, levels = c("Pre-insight", "Insight", "Post-insight")),
+            condition = factor(condition, levels = c("Informed", "Naive"))
+        ) %>%
+        filter(!is.na(condition))
+
+    # Compute difference between conditions within each phase
+    channels <- channel_locations$channel
+    tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
+    tfr_grand_ave_naive <- filter(tfr_grand_ave, condition == "Naive")
+    tfr_grand_ave_diff <- mutate(tfr_grand_ave_informed, condition = "Difference")
+    tfr_grand_ave_diff[channels] <- tfr_grand_ave_informed[channels] -
+        tfr_grand_ave_naive[channels]
+
+    # Plot topography at each time and frequency bin
+    tstep <- 0.1
+    fstep <- 4
+    tmins <- seq(tmin, tmax - tstep, tstep)
+    fmins <- seq(fmin, fmax - fstep, fstep)
+    map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {
+        # map(c("Insight"), function(this_phase) {
+        map(tmins, function(tmin) {
+            tmax <- tmin + tstep
+            map(fmins, function(fmin) {
+                fmax <- fmin + fstep
+                tfr_clusters %>%
+                    filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
+                    filter(str_detect(contrast, this_phase) & p_val < .05) %>%
+                    pull(channel) %>%
+                    unique() -> significant_channels
+                tfr_grand_ave_diff %>%
+                    filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
+                    filter(phase == this_phase) %>%
+                    pivot_longer(
[…]

### 2022-08-15 manuscript_files/helper_functions.R
Re-format helper functions

@@ -1,508 +1,473 @@
-# Define colors
 aha_colors <- viridisLite::viridis(2, begin = 0.1, end = 0.6)
-
-# Helper function for text labels
-annotate_text <- function(...) {
-    ggplot2::annotate(
-        geom = "text", size = size, color = "black", family = "Helvetica"
-    )
-}
 
 plot_fig1a <- function(files_dir) {
 
-    # Make sure that packages are loaded
-    require(tidyverse)
-    require(cowplot)
+  # Make sure that packages are loaded
+  require(tidyverse)
+  require(cowplot)
 
-    # Trial structure
-    example_stim <- magick::image_read(
-        here::here(files_dir, "example_stim.png")
+  # Trial structure
+  example_stim <- magick::image_read(here::here(files_dir, "example_stim.png"))
+  ggplot() +
+    coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
+    theme_void() +
+    theme(aspect.ratio = 0.5) +
+    ## INSIGHT PHASE ##
+    # Title
+    annotate(
+      geom = "text", x = 0, y = 97.2, label = "Insight phase", size = 14 / .pt,
+      family = "Helvetica", fontface = "bold"
+    ) +
+    # Arrow
+    annotate(
+      geom = "segment", x = -30, xend = 24, y = 79, yend = 85,
+      arrow = arrow(length = unit(0.1, "inches"))
+    ) +
+    # Squares
+    annotate(
+      geom = "rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75,
+      color = "black", fill = "white"
+    ) +
+    annotate(
+      geom = "rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65,
+      color = aha_colors[2], fill = "white"
+    ) +
+    annotate(
+      geom = "rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89,
+      color = aha_colors[1], fill = "white"
+    ) +
+    annotate(
+      geom = "rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79,
+      color = "black", fill = "white"
+    ) +
+    annotate(
+      geom = "rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81,
+      color = "black", fill = "white"
+    ) +
+    annotate(
+      geom = "text", x = -27, y = 65.3, label = "+", size = 20 / .pt,
+      family = "Helvetica"
+    ) +
+    annotate(
[…]

### 2022-08-15 manuscript.Rmd
Update title page

@@
   - id            : "1"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, 12489 Berlin, Germany"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
   - id            : "2"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, 04103 Leipzig, Germany"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig"
   - id            : "3"
-    institution   : "Fachhochschule des Mittelstands, Minna-Neuburger-Straße 3, 96050 Bamberg, Germany"
+    institution   : "Fachhochschule des Mittelstands, Bamberg"
 
 authornote: |
-  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}
+  Alexander Enge \orcidlink{0000-0003-0100-2297} [https://orcid.org/0000-0003-0100-2297](0000-0003-0100-2297)
 
-  \addORCIDlink{Rasha Abdel Rahman}{0000-0002-8438-1570}
+  Rasha Abdel Rahman \orcidlink{0000-0002-8438-1570} [https://orcid.org/0000-0002-8438-1570](0000-0002-8438-1570)
 
   The authors declare no competing financial interests.
-  The code for this study is available at [https://osf.io/uksbc](https://osf.io/uksbc).
+  The materials and code for this study are available at [https://osf.io/uksbc](https://osf.io/uksbc).
 
@@
 
-documentclass     : "apa7"
+documentclass     : "apa6"
 classoption       : "man,donotrepeattitle"
@@
   - \raggedbottom
+  - \usepackage{orcidlink}
   - \usepackage[all]{nowidow}
@@
 The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly avaible.
-The stimuli and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
+The materials and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
 

### 2022-08-15 manuscript_files/helper_functions.R
Use red-blue (RdBu) color scheme

@@ -1,4 +1,4 @@
-aha_colors <- viridisLite::viridis(2, begin = 0.1, end = 0.6)
+aha_colors <- c("#ca0020", "#0571b0")
 
 plot_fig1a <- function(files_dir) {
 
@@ -397,16 +397,20 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
           highlights = roi,
           scaling = 0.9
         ) +
-        scale_fill_viridis_c(
-          option = "viridis", limits = c(-1, 1), oob = scales::squish
+        # scale_fill_viridis_c(
+        #   option = "viridis", limits = c(-1, 1), oob = scales::squish
+        # ) +
+        scale_fill_distiller(
+          palette = "RdBu", limits = c(-1, 1), oob = scales::squish
         ) +
         theme(legend.position = "none") -> topo
       # Adjust size of head elements and channel markers
       topo$layers[[3]]$aes_params$size <- 0.5
       topo$layers[[4]]$aes_params$size <- 0.5
       topo$layers[[5]]$aes_params$size <- 0.5
-      topo$layers[[6]]$aes_params$size <- 0.3
+      topo$layers[[6]]$aes_params$colour <- NA
       topo$layers[[7]]$aes_params$size <- 0.4
+      topo$layers[[7]]$aes_params$colour <- "black"
 
       # Extract colorbar
       colorbar <<- get_legend(

### 2022-08-16 manuscript.Rmd
Update chunk options
Re-format LaTeX header

@@
   - \usepackage[all]{nowidow}
-  - \captionsetup[figure]{belowskip=10pt,font={small,stretch=1},labelfont=bf,labelsep=period,name=Figure,textfont=normalfont}
+  - \captionsetup[figure]{belowskip=10pt}
+  - \captionsetup[figure]{font={small,stretch=1},textfont=normalfont}
+  - \captionsetup[figure]{labelfont=bf,labelsep=period,name=Figure}
 ---
@@
 options(readr.show_col_types = FALSE)
-opts_chunk$set(fig.width = 12, include = FALSE, out.width = "100%")
+opts_chunk$set(
+  fig.width = 12,
+  include = FALSE,
+  message = FALSE,
+  out.width = "100%",
+  warning = FALSE
+)
 

### 2022-08-16 manuscript.Rmd
Add  description for permutation tests

@@
 
+For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, post-insight).
+First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition versus the naive condition for each participant.
+Then, we conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they ocurred at neighbouring time points, frequencies, or channels.
+Neighbouring channels were defined using Delaunay triangulation based on 2D electrode locations as implemented in MNE-Python.
+To obtain family-wise error-corrected $p$ values at the cluster level, we compared the cluster mass (i.e., the sum the $t$ values) of each observed cluster to an empirical null distribution of cluster masses obtained from 5,000 permutations with random sign flips.
+Clusters were considered to be statistically significant if their mass exceeded the 95^th^ percentile of this distribution (i.e., cluster-level treshold $p < .05$).
+
 ## Data and Code Availability

### 2022-08-16 manuscript.Rmd
Add text for ERP results

@@
 
+# Extract relevant statistics to print in the main text
+map(models, function(model) as_tibble(model$anova, rownames = "effect")) %>%
+  bind_rows(.id = "component") %>%
+  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table
+map(models, function(model) as_tibble(model$contrasts)) %>%
+  bind_rows(.id = "component") %>%
+  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table
+
 # Create Figure 1
@@
 
+# Results
+
+## Event-Related Potentials
+
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
+To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.
+
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$ `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
+This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented and that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
+
+In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
+Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
+There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
+
+In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
+As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
+
 ```{r, table_1, include=TRUE}

### 2022-08-16 manuscript.Rmd
Add text for hypotheses

@@
 We examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
+We hypothesized that semantic information would have instant effects on visual perception, by which we mean (a) that these effects can already be observed on the same trial as the semantic information is being presented for the first time, and (b) that these effects are found not only in later, higher-level cognition-related ERP components (i.e., N400), but also in earlier, perception-related ERP components (i.e., P1 and/or N170).
+We furthermore conducted an exploratory time-frequency analysis to test if event-related power also showed instant effects of semantic information.
+This was to make sure that we would also capture any non-phase-locked, putatively oscillatory activity related to semantically informed perception.
 

### 2022-08-17 manuscript.Rmd
Add Supplementary info (stimuli, model outputs)

@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : no
@@
   - \captionsetup[figure]{labelfont=bf,labelsep=period,name=Figure}
+  - \captionsetup[table]{labelfont=bf,labelsep=period,textfont=bf}
+  - \usepackage[export]{adjustbox}
+  - \usepackage{makecell}
+  - \usepackage{setspace}
 ---
@@
 This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20).
+See Supplementary Results 1 for the final model syntax and model outputs.
 All models were fitted in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4] with the optimizer function *bobyqa* and a maximum of 10^6^ iterations for maximum likelihood estimation.
@@
 Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
-
-```{r, table_1, include=TRUE}
-# View model summaries
-walk(models, function(model) {
-  print(formula(model$model))
-  cat("\n")
-  print(model$anova)
-  cat("\n")
-  print(model$contrasts)
-  cat("\n\n")
-})
-```
 
@@
 
-# Results
-
-## Event-Related Potentials
-
 \newpage
@@
 <div id="refs" custom-style="Bibliography"></div>
+
+\newpage
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\setcounter{page}{1}
+
+# Supplementary Information
+
+\bigskip
+
+```{r tabs1, include=TRUE, results="asis"}
+# Print table of materials
+read_tsv(here("materials", "items.txt"), col_types = cols()) %>%
+  mutate(
+    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
+    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
+    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
+    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
+  ) %>%
+  transmute(
+    img = paste0(
+      "\\includegraphics[valign=c,scale=0.245]{materials/unfamiliar/",
+      item,
+      ".png}"
+    ),
+    item = as.character(item),
+    match = paste(match_ger, match_en, sep = "\n") %>%
+      kableExtra::linebreak(align = "l", linebreaker = "\n"),
+    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
+      kableExtra::linebreak(align = "l", linebreaker = "\n")
+  ) %>%
+  apa_table(
+    booktabs = TRUE,
+    col.names = c(
+      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
+    ),
+    escape = FALSE,
+    longtable = TRUE,
+    caption = "Unfamiliar Object Stimuli\\smallskip",
+    font_size = "footnotesize"
+  )
+```
+
+\newpage
+
+## Results S1. *Linear Mixed-Effects Models*
+
+## *P1 Component (100--150 ms)*
+
+\small
+\singlespacing
+
+```{r, ress1a, include=TRUE}
+# Helper function for printing model summary, ANOVA (F tests), and contrasts
+print_model_outputs <- function(model_object) {
+  model <- model_object$model
+  model@call$data <- NULL # Prevents cluttering the `summary` output
+  print(summary(model))
+  cat("\n")
+  print(model_object$anova)
+  cat("\nFollow-Up Contrasts (Simple Effects)\n")
+  print(model_object$contrasts)
+  cat("\n\n")
+}
+
+# Print model outputs
+print_model_outputs(models$P1)
+```
+
+\newpage
+\normalsize
+\doublespacing
+
+## *N170 Component (150--200 ms)*
+
+\small
+\singlespacing
+
+```{r, ress1b, include=TRUE}
+# Print model outputs
+print_model_outputs(models$N170)
+```
+
+\newpage
+\normalsize
+\doublespacing
+
+## *N400 Component (400--700 ms)*
+
+\small
+\singlespacing
+
+```{r, ress1c, include=TRUE}
+# Print model outputs
+print_model_outputs(models$N400)
+```

### 2022-08-17 manuscript_files/helper_functions.R
Fix error in `plot_fig2()`

@@ -511,8 +511,6 @@ plot_fig2 <- function(tfr_grand_ave,
     tfr_grand_ave_naive[channels]
 
   # Plot topography at each time and frequency bin
-  tstep <- 0.1
-  fstep <- 4
   tmins <- seq(tmin, tmax - tstep, tstep)
   fmins <- seq(fmin, fmax - fstep, fstep)
   map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {

### 2022-08-17 manuscript.Rmd
Fix bug with latest buildmer

--- 2022-08-16 manuscript.Rmd
@@
   - \usepackage[all]{nowidow}
-  - \captionsetup[figure]{belowskip=10pt}
-  - \captionsetup[figure]{font={small,stretch=1},textfont=normalfont}
-  - \captionsetup[figure]{labelfont=bf,labelsep=period,name=Figure}
+  - \captionsetup[figure]{belowskip=10pt,font={small,stretch=1},labelfont=bf,labelsep=period,name=Figure,textfont=normalfont}
 ---
@@
 library(knitr)
-library(lme4)
 library(lmerTest)
@@
       data = model_data,
-      args = list("control" = lmerControl(
+      args = list("control" = lme4::lmerControl(
         optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
@@
 models <- readRDS(here(output_dir, "models.RDS"))
-
-# Extract relevant statistics to print in the main text
-map(models, function(model) as_tibble(model$anova, rownames = "effect")) %>%
-  bind_rows(.id = "component") %>%
-  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table
-map(models, function(model) as_tibble(model$contrasts)) %>%
-  bind_rows(.id = "component") %>%
-  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table
 
@@
 
-For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, post-insight).
-First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition versus the naive condition for each participant.
-Then, we conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they ocurred at neighbouring time points, frequencies, or channels.
-Neighbouring channels were defined using Delaunay triangulation based on 2D electrode locations as implemented in MNE-Python.
-To obtain family-wise error-corrected $p$ values at the cluster level, we compared the cluster mass (i.e., the sum the $t$ values) of each observed cluster to an empirical null distribution of cluster masses obtained from 5,000 permutations with random sign flips.
-Clusters were considered to be statistically significant if their mass exceeded the 95^th^ percentile of this distribution (i.e., cluster-level treshold $p < .05$).
-
 ## Data and Code Availability
@@
 The materials and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
-
-# Results
-
-## Event-Related Potentials
-
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
-Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
-To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.
-
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$ `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
-This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented and that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
-
-In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
-Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
-There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
-
-In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
-As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
-Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
 

### 2022-08-19 manuscript.Rmd
Update baseline arguments to latest pipeline

--- 2022-08-17 manuscript.Rmd
@@
     epochs_tmax = 1.5,
-    baseline_tmin = -0.2,
-    baseline_tmax = 0.0,
+    baseline = c(-0.2, 0.0),
     reject_peak_to_peak = 150.0,
@@
     tfr_cycles = seq(2, 20, by = 0.5),
-    tfr_baseline_tmin = -0.45,
-    tfr_baseline_tmax = -0.05,
-    tfr_baseline_mode = "percent",
+    tfr_mode = "percent",
+    tfr_baseline = c(-0.45, -0.05),
     perm_contrasts = list(

### 2022-08-19 manuscript.Rmd
Increase time window for permutation tests

@@
     ),
-    perm_tmin = 0.0,
-    perm_tmax = 1.0,
+    perm_tmin = -0.45,
+    perm_tmax = 1.45,
     n_jobs = 1
@@
 # Create topographic plots for event-related power in each phase
-tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)
+tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations, tmin = -0.4, tmax = 1.4, tstep = 0.2)
 

### 2022-08-19 manuscript.Rmd
Adjust time window for permutation tests

@@
     ),
-    perm_tmin = -0.45,
-    perm_tmax = 1.45,
+    perm_tmin = -0.4,
+    perm_tmax = 1.4,
     n_jobs = 1

### 2022-08-19 manuscript.Rmd
Add text for TFR results

@@
     epochs_tmax = 1.5,
-    baseline = c(-0.2, 0.0),
+    baseline_tmin = -0.2,
+    baseline_tmax = 0.0,
     reject_peak_to_peak = 150.0,
@@
     tfr_cycles = seq(2, 20, by = 0.5),
-    tfr_mode = "percent",
-    tfr_baseline = c(-0.45, -0.05),
+    tfr_baseline_tmin = -0.45,
+    tfr_baseline_tmax = -0.05,
+    tfr_baseline_mode = "percent",
     perm_contrasts = list(
@@
     ),
-    perm_tmin = -0.4,
-    perm_tmax = 1.4,
+    perm_tmin = 0.0,
+    perm_tmax = 1.0,
     n_jobs = 1
@@
 channel_locations <- read_csv(here(output_dir, "channel_locations.csv"))
+
+# Read results of cluster-based permutation tests for ERPs
+clusters <- read_csv(here(output_dir, "clusters.csv"))
+
+# Read results of cluster-based permutation tests for TFR
+tfr_clusters <- read_csv(here(output_dir, "tfr_clusters.csv"))
 ```
@@
 
-```{r, clusters, include=TRUE, fig.height=8}
-# Read results of cluster-based permutation tests for ERPs
-read_csv(here(output_dir, "clusters.csv"), col_types = cols(
-  contrast = col_factor(levels = c(
-    "Pre-insight/Informed - Pre-insight/Naive",
-    "Insight/Informed - Insight/Naive",
-    "Post-insight/Informed - Post-insight/Naive"
-  ))
-)) -> clusters
+## Event-Related Power
 
-# Plot thresholded cluster images
-clusters %>%
-  filter(p_val < .05) %>%
-  ggplot(aes(x = time, y = channel, fill = cluster)) +
-  facet_grid(~contrast, drop = FALSE) +
-  geom_raster() +
-  theme(legend.position = "top")
-```
+In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < 0.05)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < 0.05)$p_val))`.
+These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
+Both clusters had a negative sign, started around 600 ms after object onset and continued all the way until the end of the analyzed period at 1,400 ms.
+They spanned a broad range of frequencies in the alpha and lower beta range as well as a broad set of channels, but appeared to be most focal at around 15 Hz at parietal channels.
+Thus, semantically informed perception seems to alter not only early, evoked activity (see Event-Related Potentials above) but also later, induced activity, in the form of a reduction of post-stimulus power at parietal channels in the range of alpha and lower beta frequencies.
 
-```{r, tfr, fig.height=12, include=TRUE}
-# Read results of cluster-based permutation tests for TFR
-read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
-  contrast = col_factor(levels = c(
-    "Pre-insight/Informed - Pre-insight/Naive",
-    "Insight/Informed - Insight/Naive",
-    "Post-insight/Informed - Post-insight/Naive"
-  ))
-)) -> tfr_clusters
-
-# Plot thresholded cluster images for the insight phase
-tfr_clusters %>%
-  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
-  ggplot(aes(x = time, y = freq, fill = cluster)) +
-  facet_wrap(~channel) +
-  geom_raster() +
-  theme(legend.position = "top")
-
-# Plot thresholded cluster images for the post-insight phase
-tfr_clusters %>%
-  filter(
-    contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < .05
-  ) %>%
-  ggplot(aes(x = time, y = freq, fill = cluster)) +
-  facet_wrap(~channel) +
-  geom_raster() +
-  theme(legend.position = "top")
-```
-
-```{r, fig2a, fig.height=10, include=TRUE}
+```{r, fig2, fig.height=10, include=TRUE, eval=FALSE}
 # Read grand-averaged power
@@
 # Create topographic plots for event-related power in each phase
-tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations, tmin = -0.4, tmax = 1.4, tstep = 0.2)
+tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)
 
@@
 ```
+
+\newpage
+
+```{r, figclusters, include=TRUE, fig.height=8}
+# Read results of cluster-based permutation tests for ERPs
+read_csv(here(output_dir, "clusters.csv"), col_types = cols(
+  contrast = col_factor(levels = c(
+    "Pre-insight/Informed - Pre-insight/Naive",
+    "Insight/Informed - Insight/Naive",
+    "Post-insight/Informed - Post-insight/Naive"
+  ))
+)) -> clusters
+
+# Plot thresholded cluster images
+clusters %>%
+  filter(p_val < .05) %>%
+  ggplot(aes(x = time, y = channel, fill = cluster)) +
+  facet_grid(~contrast, drop = FALSE) +
+  geom_raster() +
+  theme(legend.position = "top")
+```
+
+```{r, figtfrclusters, fig.height=12, include=TRUE}
+# Read results of cluster-based permutation tests for TFR
+read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
+  contrast = col_factor(levels = c(
+    "Pre-insight/Informed - Pre-insight/Naive",
+    "Insight/Informed - Insight/Naive",
+    "Post-insight/Informed - Post-insight/Naive"
+  ))
+)) -> tfr_clusters
+
+# Plot thresholded cluster images for the insight phase
+tfr_clusters %>%
+  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
+  ggplot(aes(x = time, y = freq, fill = cluster)) +
+  facet_wrap(~channel) +
+  geom_raster() +
+  theme(legend.position = "top")
+
+# Plot thresholded cluster images for the post-insight phase
+tfr_clusters %>%
+  filter(
+    contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < .05
+  ) %>%
+  ggplot(aes(x = time, y = freq, fill = cluster)) +
+  facet_wrap(~channel) +
+  geom_raster() +
+  theme(legend.position = "top")
+```

### 2022-08-20 manuscript_files/helper_functions.R
Improve Figure 1 legend labels

@@ -349,7 +349,9 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
         geom_line(size = 0.8) +
         # Styling
         scale_color_manual(
-          values = aha_colors, aesthetics = c("color", "fill")
+          values = aha_colors,
+          labels = c("Informed condition", "Naive condition"),
+          aesthetics = c("color", "fill")
         ) +
         coord_cartesian(ylim = c(-3, 8), expand = TRUE) +
         theme_void() +
@@ -364,9 +366,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
           ) +
           theme(
             legend.position = "right",
-            legend.title = element_text(
-              family = "Helvetica", size = 10, face = "bold"
-            ),
+            legend.title = element_blank(),
             legend.text = element_text(family = "Helvetica", size = 10)
           )
       )
@@ -428,11 +428,8 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
             legend.position = "right",
             legend.title = element_text(
               size = 10, angle = 90, family = "Helvetica",
-              face = "bold"
             ),
-            legend.text = element_text(
-              size = 10, family = "Helvetica"
-            ),
+            legend.text = element_text(size = 10, family = "Helvetica"),
           )
       )
 
@@ -463,7 +460,7 @@ plot_fig1 <- function(files_dir, evokeds, config, channel_locations, models) {
     label_fontfamily = "Helvetica"
   ) +
     # Add legend and colorbar
-    draw_plot(wave_legend, x = 0.354, y = 0.434) +
+    draw_plot(wave_legend, x = 0.330, y = 0.434) +
     draw_plot(colorbar, x = 0.454, y = 0.434) +
     # Add some lines to separate the three experimental parts
     annotate("segment", x = 0.331, xend = 0.331, y = -Inf, yend = 0.48) +

### 2022-08-20 manuscript.Rmd
Add colorbar, caption to TFR plots
Figures 2, 3, 4

@@
 
+# Read grand-averaged power
+tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))
+
 # Read results of cluster-based permutation tests for ERPs
@@
 
-```{r, fig2, fig.height=10, include=TRUE, eval=FALSE}
-# Read grand-averaged power
-tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))
-
+```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE}
 # Create topographic plots for event-related power in each phase
@@
 
-```{r, fig2b, fig.height=10, include=TRUE}
+(ref:figure-2-caption) Time-frequency results for the pre-insight phase.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
+A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`).
+
+```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)", include=TRUE}
 # Plot Insight Phase
@@
 
-```{r, fig2c, fig.height=10, include=TRUE}
+(ref:figure-3-caption) Time-frequency results for the insight phase.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < 0.05)$p_val))`).
+
+```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)", include=TRUE}
 # Plot Post-Insight Phase
@@
 ```
+
+(ref:figure-4-caption) Time-frequency results for the post-insight phase.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < 0.05)$p_val))`).
 

### 2022-08-20 manuscript_files/helper_functions.R

@@ -477,9 +477,9 @@ plot_fig1 <- function(files_dir, evokeds, config, channel_locations, models) {
 plot_fig2 <- function(tfr_grand_ave,
                       tfr_clusters,
                       channel_locations,
-                      tmin = 0.0,
-                      tmax = 1.0,
-                      tstep = 0.1,
+                      tmin = -0.4,
+                      tmax = 1.4,
+                      tstep = 0.2,
                       fmin = 4,
                       fmax = 40,
                       fstep = 4) {
@@ -487,17 +487,6 @@ plot_fig2 <- function(tfr_grand_ave,
   # Make sure that packages are loaded
   require(tidyverse)
   require(cowplot)
-
-  # Read grand-averaged power
-  tfr_grand_ave %>%
-    mutate(
-      phase = factor(
-        phase,
-        levels = c("Pre-insight", "Insight", "Post-insight")
-      ),
-      condition = factor(condition, levels = c("Informed", "Naive"))
-    ) %>%
-    filter(!is.na(condition))
 
   # Compute difference between conditions within each phase
   channels <- channel_locations$channel
@@ -528,6 +517,7 @@ plot_fig2 <- function(tfr_grand_ave,
             cols = all_of(channels), names_to = "electrode",
             values_to = "power"
           ) %>%
+          mutate(power = power * 100) %>% # Convert from decimal to percent
           left_join(channel_locations, by = c("electrode" = "channel")) %>%
           group_by(electrode, x, y) %>%
           summarise(power = mean(power), .groups = "drop") %>%
@@ -539,12 +529,35 @@ plot_fig2 <- function(tfr_grand_ave,
             highlights = significant_channels,
             scaling = 1.1
           ) +
-          scale_fill_distiller(limits = c(-0.25, 0.25), palette = "RdBu") +
+          scale_fill_distiller(limits = c(-25, 25), palette = "RdBu") +
           # scale_fill_viridis_c(limits = c(-0.25, 0.25)) +
           theme(
             plot.margin = unit(rep(-0.2, 4), "cm"),
             legend.position = "none"
           ) -> topo
+        colorbar <<- get_legend(
+          topo +
+            guides(
+              fill = guide_colorbar(
+                title.hjust = 0.5,
+                title.vjust = 0.6,
[…]

### 2022-08-20 manuscript.Rmd
Add code for control models

@@
   eeg_processing = TRUE,
-  mixed_models = TRUE
+  mixed_models = TRUE,
+  control_analysis = TRUE,
 )
@@
 
-# Do the actual preprocessing if requested
+# (Re-)do the actual preprocessing if requested
 if (run$eeg_processing) {
@@
 
-```{r, mixed_models, eval=run$mixed_models}
+```{r, mixed_models}
+# (Re-)do the actual model fitting if requested
+if (run$mixed_models) {
+
   # Filter relevant conditions for the main analysis
@@
 
-# Fit linear mixed models
-deps <- c("P1", "N170", "N400")
-map(deps, function(dep, model_formula = form, model_data = trials_main) {
+  # Helper function for fitting linear mixed models and computing contrasts
+  fit_mixed_models <- function(dep, formula, data) {
 
     # Modify the formula such that fixed effects are always retained
-  model_formula %<>%
+    formula %<>%
       tabulate.formula() %>%
@@
       buildmerControl = buildmerControl(
-      formula = model_formula,
-      data = model_data,
+        formula, data,
         args = list("control" = lme4::lmerControl(
@@
       "contrasts" = contrasts
-  ) %>%
-    return()
-}) %>%
-  # Add ERP component names
+    )
+  }
+
+  # Actually fit the model for each component
+  deps <- config$components$name
+  map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
     set_names(deps) -> models
@@
   saveRDS(models, here(output_dir, "models.RDS"))
-```
+} else {
 
-```{r, fig1, include=TRUE, fig.height=12, fig.cap="(ref:figure-1-caption)"}
   # Read fitted models
   models <- readRDS(here(output_dir, "models.RDS"))
+}
 
@@
   rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table
+```
 
+```{r, fig1, include=TRUE, fig.height=12, fig.cap="(ref:figure-1-caption)"}
 # Create Figure 1
@@
 
+## Control Analysis
+
+```{r, control_analysis}
+# (Re-)do the actual model fitting if requested
+if (run$mixed_models_control) {
+
+  # Filter relevant conditions for the main analysis
+  conditions_control <- c("Informed", "Exclude_informed")
+  trials %>%
+    mutate(condition = factor(condition, levels = conditions_control)) %>%
+    drop_na() -> trials_control
+
+  # Contrast coding for phase
+  cbind(
+    c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
+    c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
+  ) %>%
+    t() %>%
+    ginv() -> contrasts(trials_control$phase)
+
+  # Contrast coding for condition
+  cbind(c("Informed" = 1, "Exclude_informed" = -1)) %>%
+    t() %>%
+    ginv() -> contrasts(trials_control$condition)
+
+  # Fit the model for each component
+  map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
+    set_names(deps) -> models_control
+
+  # Save models
+  saveRDS(models_control, here(output_dir, "models_control.RDS"))
+} else {
+
+  # Read fitted models
+  models_control <- readRDS(here(output_dir, "models_control.RDS"))
+}
+
+# Extract relevant statistics to print in the main text
+map(models_control, function(mod) as_tibble(mod$anova, rownames = "effect")) %>%
+  bind_rows(.id = "component") %>%
+  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table_control
+map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
+  bind_rows(.id = "component") %>%
+  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table_control
+```
+
 \newpage

### 2022-08-20 manuscript.Rmd

@@
     ),
-    perm_tmin = 0.0,
-    perm_tmax = 1.0,
+    perm_tmin = -0.4,
+    perm_tmax = 1.4,
     n_jobs = 1

### 2022-08-20 manuscript.Rmd
Make sure control models can be run independently

@@
 ```{r, mixed_models}
-# (Re-)do the actual model fitting if requested
-if (run$mixed_models) {
-
-  # Filter relevant conditions for the main analysis
-  trials %>%
-    mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
-    drop_na() -> trials_main
-
-  # Contrast coding for phase
-  cbind(
-    c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
-    c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
-  ) %>%
-    t() %>%
-    ginv() -> contrasts(trials_main$phase)
-
-  # Contrast coding for condition
-  cbind(c("Informed" = 1, "Naive" = -1)) %>%
-    t() %>%
-    ginv() -> contrasts(trials_main$condition)
-
 # Construct model formula
@@
 
-  # Helper function for fitting linear mixed models and computing contrasts
+# Define helper function for fitting linear mixed models and computing contrasts
 fit_mixed_models <- function(dep, formula, data) {
@@
 
-  # Actually fit the model for each component
+# (Re-)do the actual model fitting if requested
 deps <- config$components$name
+if (run$mixed_models) {
+
+  # Filter relevant conditions for the main analysis
+  trials %>%
+    mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
+    drop_na() -> trials_main
+
+  # Contrast coding for phase
+  cbind(
+    c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
+    c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
+  ) %>%
+    t() %>%
+    ginv() -> contrasts(trials_main$phase)
+
+  # Contrast coding for condition
+  cbind(c("Informed" = 1, "Naive" = -1)) %>%
+    t() %>%
+    ginv() -> contrasts(trials_main$condition)
+
+  # Actually fit the model for each ERP component
   map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
@@
 
-  # Filter relevant conditions for the main analysis
+  # Filter relevant conditions for the control analysis
   conditions_control <- c("Informed", "Exclude_informed")

### 2022-08-21 manuscript.Rmd
Add text for control analysis

@@
 # (Re-)do the actual model fitting if requested
-if (run$mixed_models_control) {
+if (run$control_analysis) {
 
@@
 ```
+
+There are at least two important alternative explanations for our finding that semantic information instantly affects early ERP responses.
+First, differences in the P1 and/or N170 components might be driven by low-level visual differences between object images rather than by our experimental manipulation (matching versus non-matching keywords in the insight phase).
+We ruled out this alternative explanation by counter-balancing the assignment of objects to conditions across participants, meaning that the same visual object entererd the analysis in both conditions on an approximately equal number of trials, barring differences in participants' classification of the object and differences in the number of rejected EEG trials (see Materials and Methods).
+Furthermore, we did not detect reliable differences between the two conditions in the pre-insight phase, that is, before any keywords had been presented.
+It therefore seems unlikely that low-level differences could account for the tentative effects of semantic information reported above.
+
+Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
+Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the semantically naive condition.
+In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
+These non-matching keywords might have primed participants to expect an approximate set of visual features that, once the actual object was displayed, did not obtain and therefore provoked a fast and strong brain response within the first 200 ms.
+However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the semantically naive condition.
+For this control analysis, we again used the semantically informed condition as defined above, but contrasted it against a different control condition.
+Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and rather indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
+This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
+Contrasting the semantically informed condition and the failed insight conditions, we again observed a significant enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
+Likewise, the reduction of the N400 was also observed in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`.
+This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of semantic insight.
 

### 2022-08-23 manuscript.Rmd
Proofreading

@@
 
-Does our perception of an object change as soon as we discover what function it serves?
+Does our perception of an object change once we discover what function it serves?
 This question matters not only when we encounter novel tools or gadgets in our everyday lives, but also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
@@
 
-Does our perception of an object change as soon as we discover what function it serves?
+Does our perception of an object change once we discover what function it serves?
 This question speaks not only to our everyday experiences, where we encounter novel tools and gadgets in our dynamic working and private environments.
@@
 This module is encapsulated from higher-level inputs and therefore processes the visual information in a purely feedforward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
-This architecture has been mirrored in classical [e.g., @marr1982] and contemporary [e.g., @krizhevsky2012] computer vision models, allowing them to achieve human-level perfomance in predicting object category labels from images [for review, see @lindsay2020].
+This architecture has been mirrored in classical [e.g., @marr1982] and more contemporary [e.g., @krizhevsky2012] computer vision models, allowing them to achieve human-level perfomance in predicting object category labels from images [for review, see @lindsay2020].
 
@@
 
-On the behavioral level, these ideas are supported by psychological studies that showed differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] background.
-However, some of these studies confounded tentantive high-level effects with low-level differences between conditions.
-Furthermore, many studies were not able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
+On the behavioral level, these ideas are supported by psychological studies that showed differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] content.
+However, some of these studies have received legitimate criticism for confounding tentantive high-level effects with low-level differences between conditions as well as for not being able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
 
 On the neurophysiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
-Their excellent temporal resolution allows us to probe how early we can detect influences of high-level (e.g., semantic) information.
-To this end, participants were typically trained to associate visual objects with different amounts of semantic information.
+Their excellent temporal resolution allows us to probe how early one can detect influences of high-level (e.g., semantic) information.
+To this end, participants in previous studies by our lab and others were trained to associate visual objects with different amounts of semantic information.
 After training, an orthogonal task was used to compare the ERPs in response to semantically trained objects versus non-semantically trained objects.
-This revealed differences not only in late ERP components associated with semantic processing (i.e., the N400 component) but also in the visual P1 component [@abdelrahman2008; @maier2019; @samaha2018; @weller2019].
+This contrast revealed differences not only in late ERP components associated with semantic processing (i.e., the N400 component) but also in the visual P1 (or P100) component [@abdelrahman2008; @maier2019; @samaha2018; @weller2019].
 The early peak of this component and its source in the occipital cortex [@abdelrahman2008] point to an immediate effect of semantic knowledge on visual perception.
+It is less clear, however, if these effects arise immediatly once participants obtain semantic information about an object or if, instead, they require more extensive amounts of training.
+Closely related to this question is the debate if tentative top-down effects of semantic cognition on perception act in an online fashion (i.e., directly modulating perceptual processing), or more indirectly by altering stored visual representations over the course of training, which would then get reactivated once the object is reencountered later on.
 
-Here we measured ERPs in response to unfamiliar objects instantly while participants gained an semantic understanding of their function.
+To answer these open questions, we measured ERPs in response to unfamiliar objects instantly while participants gained an semantic understanding of their function.
 To this end, we presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viweing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
-We then presented the same objects again to test for downstream effects of semantic information as in previous studies.
+We then presented the same objects again to test for downstream effects of semantic information, as in previous studies.
 We examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
@@
 Stimuli consisted of 240 grayscale photographs of real-world objects.
-Of these, 120 were well-known everyday objects (e.g., a bicycle, a toothbrush) and served as filler stimuli of no interest.
-The other 120 were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Appendix A).
+Of these, 120 stimuli were well-known everyday objects (e.g., a bicycle, a toothbrush) which served as filler stimuli of no interest.
+The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Appendix A for the full list).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could typically be related to its visual features and their configuration (e.g., voltage--measuring; clay pot--drumming).
-As our central experimental manipulation, the presentation of half of the objects was preceded by keywords that correctly matched their respective function, whereas the presentation of the other half of the objects was preceded by non-matching keywords belonging to one of the other objects.
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming; see Appendix A for the full list).
+As our central experimental manipulation, half of the objects where presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
 The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically naive.
@@
 The inter-trial interval was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same across all three phases, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same across all three phases of the experiment, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
@@
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
-In the insight phase, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in green color for illustration), leading to naive perception.
+In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to naive perception.
 In the post-insight phase, the same objects were presented again without keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies of the P1 component (100--150 ms, ***B***), of the N170 component (150--200 ms, ***C***), and of the N400 component (400--700 ms, ***D***) are shown for objects with semantically informed perception versus naive perception within the three different phases.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus naive perception within the three different phases.
 Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
-The time windows and channels for quantifying the different ERP components are highlighted by the gray areas in the ERP waveforms and by the white markers on the scalp topographies, respectively.
+The time windows and channels for quantifying the ERP components are highlighted by the gray areas in the ERP waveforms and by the black markers on the scalp topographies, respectively.
 Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
@@
 
-In the *insight* phase, the 120 unfamiliar objects were presented for the second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
 Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
 Then, an asterisk was presented in the middle of the screen for another 0.5 s, followed by the presentation of the object until a response was made or until a time out after 3 s.
-The objects were presented in blocks of 30 trials so that within each block (a) there were 15 objects from each of the two experimental conditions and (b) objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).
+The objects were presented in blocks of 30 trials so that within each block there were 15 objects from each of the two experimental conditions and so that objects were heterogeneous in terms of their shape, visual complexity, and functional category (e.g., medical devices, musical instruments).
 
-In the *post-insight* phase, the unfamiliar objects were presented for a third time with the same trial structure as in the pre-insight phase, that is, without any keywords.
+In the *post-insight* phase, the unfamiliar objects were presented for a third time, with the same trial structure as in the pre-insight phase, that is, without any keywords.
 The insight and post-insight phases were presented in an interleaved fashion so that after the presentation of one block of 30 objects in the insight phase (with keywords), participants took a self-timed break and continued with the same block of 30 objects in the post-insight phase (without keywords) before moving on to the next block consisting of 30 different objects.
@@
 In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight phase and 120 unfamiliar objects in the pre-insight, insight, and post-insight phases).
-It took participants approximately 35 minutes to complete.
+It took participants approximately 35 minutes to complete the experiment.
 
@@
 This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to delineate semantically informed and naive perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral responses of the participant in the insight phase (see Figure \@ref(fig:fig1)A).
-Objects were assigned to the semantically informed condition if they were presented with matching keywords *and* if the participant indicated knowing what the object was or having an assumption.
+Next, to delineate semantically informed and naive perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure \@ref(fig:fig1)A).
+Objects were assigned to the semantically informed condition if and only if they were presented with matching keywords and the participant responded with knowing what the object was or having an assumption.
 This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Complementarily, objects were assigned to the naive condition if they were presented with non-matching keywords *and* if the participant indicated not knowing what the object was or having rather no assumption.
+Complementarily, objects were assigned to the naive condition if and only if they were presented with non-matching keywords and the participant responded with not knowing what the object was or having rather no assumption.
 This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
-The same assignment of objects to conditions, based on the manipulation and responses in the insight phase, was also used for analyzing the pre-insight and post-insight phases.
+This same assignment of objects conditions based on the insight phase was carried over to the pre-insight and post-insight phases.
 This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).
@@
 
-The data were preprocessed offline using custom scripts, available online in the hu-neuro-pipeline package (Version `r pipeline_version`; https://github.com/alexenge/hu-neuro-pipeline) and based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
+The data were preprocessed offline using custom scripts, available in the hu-neuro-pipeline package (Version `r pipeline_version`; https://github.com/alexenge/hu-neuro-pipeline) and based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
 First, the data were were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
@@
 A variable number of components per participants were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (mean = `r mean(unlist(config$auto_ica_n_components))` components, range `r min(unlist(config$auto_ica_n_components))`--`r max(unlist(config$auto_ica_n_components))`).
-Then the ICA was fitted using the FastICA algorithm [@hyvarinen1999].
+Then the ICA was fitted based on these components using the FastICA algorithm [@hyvarinen1999].
 Any independent components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the MNE-Python's `find_bads_eog` method.
@@
 
-For the analysis of ERP voltages, a zero-phase, non-causal FIR filter with a lower pass-band edge at `r config$highpass_freq` Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at `r config$lowpass_freq` Hz (transition bandwidth: 7.5 Hz) was applied.
+For the analysis of ERP amplitudes, a zero-phase, non-causal FIR filter with a lower pass-band edge at `r config$highpass_freq` Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at `r config$lowpass_freq` Hz (transition bandwidth: 7.5 Hz) was applied.
 Next, the continuous EEG was segmented into epochs ranging from `r config$epochs_tmin` s to `r config$epochs_tmax` s relative the onset of the presentation of each unfamiliar object.
-These epochs were baseline-corrected by subtracting the average voltage during the interval of `r config$baseline_tmin` s to `r config$baseline_tmax` s relative to stimulus onset.
+These epochs were baseline-corrected by subtracting the average voltage during the interval of `r config$baseline[1]` s to `r config$baseline[2]` s relative to stimulus onset.
 Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV, were removed from further analysis.
 This led to the exclusion of an average of `r mean(rejected_epochs)` trials per participant (= `r percent(mean(rejected_epochs) / 360, accuracy = 0.1)`; range `r min(rejected_epochs)`--`r max(rejected_epochs)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms at electrodes PO3, POz, PO4, O1, Oz, and O2 and for the P1 component, 150--200 ms at electrodes P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at electrodes C1, Cz, C2, CP1, CPz, and CP2 for the N400 component.
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms at channels PO3, POz, PO4, O1, Oz, and O2 and for the P1 component, 150--200 ms at channels P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at channels C1, Cz, C2, CP1, CPz, and CP2 for the N400 component.
 
-The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because they allow controlling for repeated measures of participants and stimuli while also being robust against unbalanced numbers of trials per condition [@baayen2008; @burki2018; @fromer2018].
-
+The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because these models  allow to control for repeated measures of participants and stimuli while also being robust against an unbalanced number of trials per condition [@baayen2008; @burki2018; @fromer2018].
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
@@
 We determined the most parsimonous random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
-This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20).
-See Supplementary Results 1 for the final model syntax and model outputs.
+This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20; see Supplementary Results 1 for the final model syntax and model outputs).
 All models were fitted in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4] with the optimizer function *bobyqa* and a maximum of 10^6^ iterations for maximum likelihood estimation.
@@
 
-To investiage if semantically informed perception had an influence on the ERPs within each phase, planned follow-up comparisons were calculated, contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
+To investiage if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated follow-up comparisons contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
 This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
@@
 Epochs that were marked as bad for the ERP analysis (i.e., with peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV) were also removed from the time-frequency analysis.
-The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their number of cycles from `r min(config$tfr_cycles)` to `r max(config$tfr_cycles)` in steps of `r config$tfr_freqs[2] - config$tfr_cycles[1]` [cf.
-@samaha2018].
-To adjust for the power-law scaling of the human EEG, the power values were transformed into percent signal change by first subtracting and then dividing by the average power at each frequency over the entire epoch [@grandchamp2011].
-We then performed baseline correction by subtracting the average during the pre-stimulus interval from `r config$tfr_baseline_tmin` s to `r config$tfr_baseline_tmax` s relative to object onset.
+The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their number of cycles from `r min(config$tfr_cycles)` to `r max(config$tfr_cycles)` in steps of `r config$tfr_freqs[2] - config$tfr_cycles[1]`.
+To adjust for the typical $1/f$ shape of the EEG, the power values were transformed into percent signal change by first subtracting and then dividing by the average power at each frequency over the entire epoch [@grandchamp2011].
+We then performed baseline correction by subtracting the average during the pre-stimulus interval from `r config$tfr_baseline[1]` s to `r config$tfr_baseline[2]` s relative to object onset.
 
@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
-Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s~>~`r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s~`r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`)~=~`r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$~`r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s~>~`r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s~<~`r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
 To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$ `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
-This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented and that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s~<~`r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$~`r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
+This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
 
 In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
-Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
-There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
+Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$~=~`r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$~=~`r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
+There was no reliable difference between conditions in the P1 component, $b$~=~`r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
 
 In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
-As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
-Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
+As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$~=~`r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$~=~`r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$~=~`r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
 
@@
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
-Both clusters had a negative sign, started around 600 ms after object onset and continued all the way until the end of the analyzed period at 1,400 ms.
-They spanned a broad range of frequencies in the alpha and lower beta range as well as a broad set of channels, but appeared to be most focal at around 15 Hz at parietal channels.
+Both clusters had a negative sign, started around 600 ms after object onset [but see @sassenhagen2019] and continued all the way until the end of the analyzed period at 1,400 ms.
+They spanned a broad range of frequencies in the alpha and lower beta range as well as a broad set of channels, but appeared to be most focal at around 15 Hz and parietal channels.
 Thus, semantically informed perception seems to alter not only early, evoked activity (see Event-Related Potentials above) but also later, induced activity, in the form of a reduction of post-stimulus power at parietal channels in the range of alpha and lower beta frequencies.
@@
 Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
-Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the semantically naive condition.
+Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
 In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
-These non-matching keywords might have primed participants to expect an approximate set of visual features that, once the actual object was displayed, did not obtain and therefore provoked a fast and strong brain response within the first 200 ms.
-However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the semantically naive condition.
+These non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the actual object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
+However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
 For this control analysis, we again used the semantically informed condition as defined above, but contrasted it against a different control condition.
-Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and rather indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
+Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
 This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Contrasting the semantically informed condition and the failed insight conditions, we again observed a significant enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 was also observed in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`.
-This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of semantic insight.
+Contrasting the semantically informed condition and the failed insight conditions, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$~=~`r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
+Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`.
+This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by the semantic information.
 

### 2022-08-23 manuscript.Rmd
Use Bonferroni correction for cluster threshold

@@
 tfr_clusters <- read_csv(here(output_dir, "tfr_clusters.csv"))
+
+# Define Bonferroni-corrected cluster-level p value threshold
+p_cluster <- 0.05 / length(unique(clusters$contrast))
 ```
@@
 
-For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, post-insight).
-First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition versus the naive condition for each participant.
-Then, we conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they ocurred at neighbouring time points, frequencies, or channels.
-Neighbouring channels were defined using Delaunay triangulation based on 2D electrode locations as implemented in MNE-Python.
-To obtain family-wise error-corrected $p$ values at the cluster level, we compared the cluster mass (i.e., the sum the $t$ values) of each observed cluster to an empirical null distribution of cluster masses obtained from 5,000 permutations with random sign flips.
-Clusters were considered to be statistically significant if their mass exceeded the 95^th^ percentile of this distribution (i.e., cluster-level treshold $p < .05$).
+For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, and post-insight).
+First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the naive condition for each participant.
+We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they ocurred at neighbouring time points, frequencies, or channels.
+Neighbouring channels were defined using the Delaunay triangulation based on 2D electrode locations as implemented in MNE-Python.
+To obtain family-wise error-corrected $p$ values at the cluster level, we compared the cluster mass (i.e., the sum of the $t$ values) of each observed cluster to an empirical null distribution of cluster masses obtained from 5,000 permutations with random sign flips.
+Clusters were considered to be statistically significant if their mass exceeded the `r (1 - p_cluster) * 100`^th^ percentile of this distribution (i.e., cluster-level treshold $p < .05$, Bonferroni-corrected for three seperate tests).
 
@@
 In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
-Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < 0.05)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < 0.05)$p_val))`.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s~>~`r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
@@
 # Create topographic plots for event-related power in each phase
-tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)
+tfr_plots <- plot_fig2(
+  tfr_grand_ave, tfr_clusters, p_cluster, channel_locations
+)
 
@@
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < 0.05)$p_val))`).
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`).
 
@@
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < 0.05)$p_val))`).
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`).
 

### 2022-08-23 manuscript_files/helper_functions.R

@@ -476,6 +476,7 @@ plot_fig1 <- function(files_dir, evokeds, config, channel_locations, models) {
 
 plot_fig2 <- function(tfr_grand_ave,
                       tfr_clusters,
+                      p_cluster,
                       channel_locations,
                       tmin = -0.4,
                       tmax = 1.4,
@@ -507,7 +508,7 @@ plot_fig2 <- function(tfr_grand_ave,
         fmax <- fmin + fstep
         tfr_clusters %>%
           filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
-          filter(str_detect(contrast, this_phase) & p_val < .05) %>%
+          filter(str_detect(contrast, this_phase) & p_val < p_cluster) %>%
           pull(channel) %>%
           unique() -> significant_channels
         tfr_grand_ave_diff %>%

### 2022-08-23 manuscript.Rmd
Mention additional R packages

@@
 
+In addition to the software mentioned above, we used the tidyverse set of R packages [Version `r as.character(packageVersion("tidyverse"))`\; @R-tidyverse] for data wrangling, the ggplot2 [Version `r as.character(packageVersion("ggplot2"))`\; @R-ggplot2], cowplot [Version `r as.character(packageVersion("cowplot"))`\; @R-cowplot], and eegUtils [Version `r as.character(packageVersion("eegUtils"))`\; @R-eegUtils] packages for visualization, and the papaja package [Version `r as.character(packageVersion("papaja"))`\; @R-papaja] for statistical reporting.
+We followed the workflow developed by @peikert2021 to ensure the long-term reproducibility of our analysis pipeline.
+
 ## Data and Code Availability

### 2022-08-23 manuscript.Rmd
Add discussion section

@@
 
-\newpage
+# Discussion
+
+We investigated if gaining a semantic understanding of visual objects has an influence on how we perceive them.
+To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
+For half of the objects, this information was matching the function of the object, thus leading to semantically informed perception.
+For the other half of the objects, the information was non-matching, thus keeping the perception of the object semantically naive.
+We found that semantically informed perception was immediately accompanied by enlarged (i.e., more negative) ERP amplitudes in the N170 component and reduced (i.e., less negative) ERP amplitudes in the N400 component.
+When the same objects were presented once more (without the semantic information), the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+Finally, an exploratory time-frequency analysis revealed that semantically informed perception was accompanied by a reduction in event-related power in the alpha and lower beta ranges.
+Like the ERP effects, this difference immediately ocurred on the first trial on which the objects were presented together with the critical semantic information, and it reocurred when the objects were presented once more without any information.
+
+The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest effect.
+It indicates that acquiring an understanding of the objects in the insight phase lessened participants' demand for effortful semantic processing in comparison to the naive condition [@kutas2011].
+This finding replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+The latency of this effect and the computational role of the N400 component [@lau2008; @rabovsky2018] suggest that it has a post-perceptual locus in the semantic system.
+
+In contrast to the N400, the N170 component (150--200 ms after object onset) was modulated only on those initial trials on which the objects were presented together with the relevant semantic information.
+It therefore constitutes an online marker of semantic insight, that is, participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
+The N170 is typically associated with the holistic perception of faces [@eimer2011; @sagiv2001] and other stimuli of visual expertise [@rossion2002; @tanaka2001].
+It being enlarged during semantically informed perception may reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
+This interpretation is supported by previous findings with similar experimental paradigms in the domain of face perception [@bentin2002].
+In this study, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after but not before they were primed with the intact version of the same face.
+This effect was absent when a visual control stimulus (a non-face object) was shown instead of the intact face.
+In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
+Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
+Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level perception of visual objects, integrating across their visual features.
+
+The P1 component (100--150 ms after object onset), unlike the N400 and N170 components, was modulated by semantic information only one trial after this information had been obtained.
+This is consistent with previous studies showing modulations of the P1 component when participants had learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
+What the present study adds to these findings is that the P1 effect does not take an extensive learning history to develop.
+Instead, it can be observed as soon as one trial after semantic insight has happened.
+Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
+
+Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects.
+However, the finding that these two components were modulated in different phases of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
+It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seems to reflect recurrent processing *within* the visual system [@wyatte2014].
+Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter pathway seems to take at least one additional encounter with the visual object to emerge.
+
+While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream for object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
+@hsieh2010 showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
+They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
+This increase in representational similarity was observed not only in higher-level object-sensitive areas in the lateral occipital cortex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
+These cortical regions are consistent with the neural generators of the N170 and P1 components in the ERP, which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
+
+On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999; but see @clarke2020].
+However, proponents of the modular view have pointed out important shortcomings of previous studies that had claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
+We took care to address as many of these shortcomings as possible in the present study:
+First, we showed that no difference between conditions had been present before any semantic information was presented.
+Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with an early, more perceptual locus from those with a late, more post-perceptual locus.
+Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
+Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
+Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order and at the same location.
+Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
+We hope that these measures were effective in rouling out many alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the claim that visually perception would be cognitively impenetrable.
+
+An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @serre2007].
+In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+For these models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until the models overcome this "barrier of meaning" [@mitchell2020].
+Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.
+
+A theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking at present.
+The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004; @hochstein2002], which posits that objects first enter our visual consciousness at an abstract, conceptual level.
+Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
+This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
+Besides this specific theory, an important role of top-down mechanisms for vision, or object recognition more specifically, is also posited by the family of predictive coding and Bayesian inference theories [e.g., @yuille2006; @clark2013; @lupyan2015; @panichello2013].
+Despite the theoretical advances, a detailled description of these top-down effects at the algorithmic and implementational level remains a challenge for future work [@marr1982].
+
+Taken together, the current study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the visual processing of this object.
+The immediacy of this influence is remarkable in at least two different ways:
+First, it does not require extensive training but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (> 400 ms), typically associated with semantic processing, but also at earlier stages (< 200 ms), typically associated with visual perception itself.
 

### 2022-08-23 manuscript.Rmd
Adjust figure positions

@@
 opts_chunk$set(
+  fig.pos = "tp",
   fig.width = 12,

### 2022-08-23 manuscript.Rmd
Fix citations

@@
 library(papaja)
+library(eegUtils)
 library(cowplot)
@@
 Only after this high-level interpretation has been obtained, more fine grained visual details---if relevant for the current task---are being accessed via top-down connections.
-Along similar lines, Bayesian inference and predictive coding theories [e.g., @clark2013; @panichello2013; @yuille2006] propose bi-directional loops of predictions and prediction errors between visual and non-visual processes.
+Along similar lines, Bayesian inference and predictive coding theories [e.g., @yuille2006; @clark2013; @panichello2013] propose bi-directional loops of predictions and prediction errors between visual and non-visual processes.
 

### 2022-08-24 manuscript.Rmd
Remove non-breaking spaces

@@
 
-Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s~>~`r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s~`r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`)~=~`r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$~`r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
-Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s~>~`r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s~<~`r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
+Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
 To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s~<~`r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$~`r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
 This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
@@
 In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
-Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$~=~`r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$~=~`r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
-There was no reliable difference between conditions in the P1 component, $b$~=~`r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`)~=~`r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
+Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
+There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
 
 In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
-As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$~=~`r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$~=~`r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
-Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$~=~`r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`)~=~`r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$~=~`r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
+As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
 
@@
 In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
-Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s~>~`r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.

### 2022-08-24 manuscript.Rmd
Refactor TFR plotting function

@@
 
-# Define Bonferroni-corrected cluster-level p value threshold
-p_cluster <- 0.05 / length(unique(clusters$contrast))
+# Define cluster-level p value threshold
+p_cluster <- 0.05 / 3 # Bonferroni-corrected for three phases
 ```
@@
 
-```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE}
-# Create topographic plots for event-related power in each phase
-tfr_plots <- plot_fig2(
-  tfr_grand_ave, tfr_clusters, p_cluster, channel_locations
+```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE, eval=TRUE}
+# Create topographic plots for event-related power in the pre-insight phase
+plot_tfr_topos(
+  filter(tfr_grand_ave, phase == "Pre-insight"),
+  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
+  p_cluster = p_cluster
 )
-
-# Plot Pre-Insight Phase
-tfr_plots[[1]]
 ```
@@
 
-```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)", include=TRUE}
-# Plot Insight Phase
-tfr_plots[[2]]
+```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)", include=TRUE, eval=TRUE}
+# Create topographic plots for event-related power in the insight phase
+plot_tfr_topos(
+  filter(tfr_grand_ave, phase == "Insight"),
+  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
+  p_cluster = p_cluster
+)
 ```
@@
 
-```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)", include=TRUE}
-# Plot Post-Insight Phase
-tfr_plots[[3]]
+```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)", include=TRUE, eval=TRUE}
+# Create topographic plots for event-related power in the post-insight phase
+plot_tfr_topos(
+  filter(tfr_grand_ave, phase == "Post-insight"),
+  filter(
+    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
+  ),
+  p_cluster = p_cluster
+)
 ```

### 2022-08-24 manuscript_files/helper_functions.R

@@ -474,130 +474,143 @@ plot_fig1 <- function(files_dir, evokeds, config, channel_locations, models) {
 # plot_fig1(files_dir, evokeds, config, channel_locations, models)
 # ggsave("fig1.pdf", width = 12, height = 12)
 
-plot_fig2 <- function(tfr_grand_ave,
-                      tfr_clusters,
-                      p_cluster,
-                      channel_locations,
-                      tmin = -0.4,
-                      tmax = 1.4,
-                      tstep = 0.2,
-                      fmin = 4,
-                      fmax = 40,
-                      fstep = 4) {
+plot_tfr_topos <- function(tfr_grand_ave,
+                           tfr_clusters,
+                           p_cluster,
+                           condition_plus = "Informed",
+                           condition_minus = "Naive",
+                           tmin = -0.4,
+                           tmax = 1.4,
+                           tstep = 0.2,
+                           fmin = 4,
+                           fmax = 40,
+                           fstep = 4) {
 
-  # Make sure that packages are loaded
-  require(tidyverse)
+  # Load required packages
+  require(dplyr)
   require(cowplot)
 
-  # Compute difference between conditions within each phase
-  channels <- channel_locations$channel
+  # Compute time bins and frequency bins to plot
+  tmins <- seq(tmin, tmax - tstep, tstep)
+  fmins <- seq(fmin, fmax - fstep, fstep)
+
+  # Compute difference in power between conditions
+  channels <- unique(tfr_clusters$channel)
   tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
   tfr_grand_ave_naive <- filter(tfr_grand_ave, condition == "Naive")
   tfr_grand_ave_diff <- mutate(tfr_grand_ave_naive, condition = "Difference")
   tfr_grand_ave_diff[channels] <- tfr_grand_ave_informed[channels] -
     tfr_grand_ave_naive[channels]
 
-  # Plot topography at each time and frequency bin
-  tmins <- seq(tmin, tmax - tstep, tstep)
-  fmins <- seq(fmin, fmax - fstep, fstep)
-  map(c("Pre-insight", "Insight", "Post-insight"), function(this_phase) {
-    # map(c("Insight"), function(this_phase) {
-    map(tmins, function(tmin) {
-      tmax <- tmin + tstep
-      map(fmins, function(fmin) {
[…]

### 2022-08-24 manuscript.Rmd
Add TFR results to control analysis

@@
       c("Insight/Informed", "Insight/Naive"),
-      c("Post-insight/Informed", "Post-insight/Naive")
+      c("Post-insight/Informed", "Post-insight/Naive"),
+      c("Insight/Informed", "Insight/Exclude_informed")
     ),
@@
 Contrasting the semantically informed condition and the failed insight conditions, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$~=~`r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`.
+Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as did the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
 This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by the semantic information.
@@
 
+```{r, figs1, fig.height=11, fig.cap="(ref:figure-s1-caption)", include=TRUE, eval=TRUE}
+# Create topographic plots for control analysis of event-related power
+plot_tfr_topos(
+  filter(tfr_grand_ave, phase == "Insight"),
+  filter(
+    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
+  ),
+  p_cluster = p_cluster,
+  condition_plus = "Informeed",
+  condition_minus = "Exclude_informed"
+)
+```
+
+(ref:figure-s1-caption) Time-frequency results for the control analysis.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`).
+
 ## Results S1. *Linear Mixed-Effects Models*

### 2022-08-24 manuscript.Rmd
Small fixes

@@
   mixed_models = TRUE,
-  control_analysis = TRUE,
+  control_analysis = TRUE
 )
@@
 ```{r, figclusters, include=TRUE, fig.height=8}
-# Read results of cluster-based permutation tests for ERPs
-read_csv(here(output_dir, "clusters.csv"), col_types = cols(
-  contrast = col_factor(levels = c(
-    "Pre-insight/Informed - Pre-insight/Naive",
-    "Insight/Informed - Insight/Naive",
-    "Post-insight/Informed - Post-insight/Naive"
-  ))
-)) -> clusters
-
 # Plot thresholded cluster images
@@
 ```{r, figtfrclusters, fig.height=12, include=TRUE}
-# Read results of cluster-based permutation tests for TFR
-read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
-  contrast = col_factor(levels = c(
-    "Pre-insight/Informed - Pre-insight/Naive",
-    "Insight/Informed - Insight/Naive",
-    "Post-insight/Informed - Post-insight/Naive"
-  ))
-)) -> tfr_clusters
-
 # Plot thresholded cluster images for the insight phase
@@
   theme(legend.position = "top")
+
+# Plot thresholded cluster images for the control analysis
+tfr_clusters %>%
+  filter(
+    contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < .05
+  ) %>%
+  ggplot(aes(x = time, y = freq, fill = cluster)) +
+  facet_wrap(~channel) +
+  geom_raster() +
+  theme(legend.position = "top")
 ```

### 2022-08-25 manuscript.Rmd
Remove non-breaking spaces

@@
 This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Contrasting the semantically informed condition and the failed insight conditions, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$~=~`r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as did the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
+Contrasting the semantically informed condition and the failed insight conditions, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
+Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as did the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
 This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by the semantic information.

### 2022-08-25 manuscript.Rmd
Add citations

@@
 This finding replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
-The latency of this effect and the computational role of the N400 component [@lau2008; @rabovsky2018] suggest that it has a post-perceptual locus in the semantic system.
+The latency of this effect and the computational role of the N400 component [@bornkessel-schlesewsky2019; @lau2008; @rabovsky2018] suggest that it has a post-perceptual locus in the semantic system.
 
@@
 This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
-Besides this specific theory, an important role of top-down mechanisms for vision, or object recognition more specifically, is also posited by the family of predictive coding and Bayesian inference theories [e.g., @yuille2006; @clark2013; @lupyan2015; @panichello2013].
+Besides this specific theory, an important role of top-down mechanisms for vision, or object recognition more specifically, is also posited by the family of predictive coding and Bayesian inference theories [e.g., @yuille2006; @clark2013; @lupyan2015; @panichello2013; @xu2007].
 Despite the theoretical advances, a detailled description of these top-down effects at the algorithmic and implementational level remains a challenge for future work [@marr1982].

### 2022-08-25 manuscript.Rmd
Adjust placement of Supplementary Figure S1

@@
 
-```{r, figs1, fig.height=11, fig.cap="(ref:figure-s1-caption)", include=TRUE, eval=TRUE}
-# Create topographic plots for control analysis of event-related power
-plot_tfr_topos(
-  filter(tfr_grand_ave, phase == "Insight"),
-  filter(
-    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
-  ),
-  p_cluster = p_cluster,
-  condition_plus = "Informeed",
-  condition_minus = "Exclude_informed"
-)
-```
-
-(ref:figure-s1-caption) Time-frequency results for the control analysis.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`).
-
 ## Results S1. *Linear Mixed-Effects Models*
@@
 
-```{r, figclusters, include=TRUE, fig.height=8}
+```{r, figs1, fig.height=11, fig.cap="(ref:figure-s1-caption)", eval=TRUE}
+# Create topographic plots for control analysis of event-related power
+plot_tfr_topos(
+  filter(tfr_grand_ave, phase == "Insight"),
+  filter(
+    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
+  ),
+  p_cluster = p_cluster,
+  condition_plus = "Informeed",
+  condition_minus = "Exclude_informed"
+)
+```
+
+(ref:figure-s1-caption) Time-frequency results for the control analysis.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`).
+
+\newpage
+
+```{r, figclusters, fig.height=8, include=FALSE}
 # Plot thresholded cluster images

### 2022-08-25 manuscript.Rmd
Default to not re-run anything
Update author note

@@
 
+  Number of pages: 23
+
+  Number of figures: 4
+
+  Number of tables: 0
+
+  Number of words: ??? (abstract), ??? (introduction), ??? (discussion)
+
   The authors declare no competing financial interests.
+
+  We would like to thank Nele Langosch for assistance with data collection and analysis as well as Guido Kiecker for technical support.
   The materials and code for this study are available at [https://osf.io/uksbc](https://osf.io/uksbc).
@@
 run <- list(
-  eeg_processing = TRUE,
-  mixed_models = TRUE,
-  control_analysis = TRUE
+  eeg_processing = FALSE,
+  mixed_models = FALSE,
+  control_analysis = FALSE
 )

### 2022-08-25 manuscript.Rmd
Update chunk options

@@
   fig.width = 12,
-  include = FALSE,
   message = FALSE,
@@
 
-```{r, eeg_processing}
+```{r, eeg_processing, include=FALSE}
 # Define function for processing behavioral log files
@@
 
-```{r, mixed_models}
+```{r, mixed_models, include=FALSE}
 # Construct model formula
@@
 
-```{r, fig1, include=TRUE, fig.height=12, fig.cap="(ref:figure-1-caption)"}
+```{r, fig1, fig.height=12, fig.cap="(ref:figure-1-caption)"}
 # Create Figure 1
@@
 
-```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE, eval=TRUE}
+```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)"}
 # Create topographic plots for event-related power in the pre-insight phase
@@
 
-```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)", include=TRUE, eval=TRUE}
+```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)"}
 # Create topographic plots for event-related power in the insight phase
@@
 
-```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)", include=TRUE, eval=TRUE}
+```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)"}
 # Create topographic plots for event-related power in the post-insight phase
@@
 
-```{r, control_analysis}
+```{r, control_analysis, include=FALSE}
 # (Re-)do the actual model fitting if requested
@@
 
-```{r tabs1, include=TRUE, results="asis"}
+```{r tabs1, results="asis"}
 # Print table of materials
@@
 
-```{r, ress1a, include=TRUE}
+```{r, ress1a}
 # Helper function for printing model summary, ANOVA (F tests), and contrasts
@@
 
-```{r, ress1b, include=TRUE}
+```{r, ress1b}
 # Print model outputs
@@
 
-```{r, ress1c, include=TRUE}
+```{r, ress1c}
 # Print model outputs
@@
 
-```{r, figtfrclusters, fig.height=12, include=TRUE}
+```{r, figtfrclusters, fig.height=12, include=FALSE}
 # Plot thresholded cluster images for the insight phase

### 2022-08-25 manuscript.Rmd
Proof-reading

@@
 
-  Number of words: ??? (abstract), ??? (introduction), ??? (discussion)
+  Number of words: 251 (abstract), 842 (introduction), 1,847 (discussion)
 
@@
 Does our perception of an object change once we discover what function it serves?
-This question matters not only when we encounter novel tools or gadgets in our everyday lives, but also pertains to the long-standing debate around the (im)penetrability of perception by higher cognitive capacities.
 Here, we showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
 We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms) and reduced amplitudes in the N400 component (400--700 ms).
-When the same objects were presented once more without any information, the N400 effect persisted and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
-Consistent with previous work, our results suggest that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
-We demonstrate for the first time that these effects are instantaneous in the sense that they can be observed within the same trial as well as one trial after the information has been given, providing strong evidence that cognition affects perception.
+We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
+When the same objects were presented once more without any information, the N400 and event-related power effects persisted, and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
+Consistent with previous work, this suggests that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component, event-related power).
+Our study is the first to show that these effects are instantenous, that is, observable within zero to one trials after any semantic information has been presented.
 
@@
 
-On the behavioral level, these ideas are supported by psychological studies that showed differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] content.
-However, some of these studies have received legitimate criticism for confounding tentantive high-level effects with low-level differences between conditions as well as for not being able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
+On the behavioral level, these ideas are supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] content.
+However, some of these studies have received legitimate criticism for confounding tentantive high-level effects with low-level differences between conditions, as well as for not being able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
 
 On the neurophysiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
-Their excellent temporal resolution allows us to probe how early one can detect influences of high-level (e.g., semantic) information.
+Their excellent temporal resolution make it possible probe how early one can detect influences of high-level (e.g., semantic) information.
 To this end, participants in previous studies by our lab and others were trained to associate visual objects with different amounts of semantic information.
@@
 It is less clear, however, if these effects arise immediatly once participants obtain semantic information about an object or if, instead, they require more extensive amounts of training.
-Closely related to this question is the debate if tentative top-down effects of semantic cognition on perception act in an online fashion (i.e., directly modulating perceptual processing), or more indirectly by altering stored visual representations over the course of training, which would then get reactivated once the object is reencountered later on.
+Closely related to this question is the debate if tentative top-down effects of semantic cognition on perception act in an online fashion (i.e., directly modulating perceptual processing), or more indirectly, by altering stored visual representations over the course of training, which would then get reactivated once the object is reencountered later on.
 
-To answer these open questions, we measured ERPs in response to unfamiliar objects instantly while participants gained an semantic understanding of their function.
+To answer these open questions, we measured ERPs in response to unfamiliar objects directly while participants gained an semantic understanding of their function.
 To this end, we presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viweing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
@@
 We hypothesized that semantic information would have instant effects on visual perception, by which we mean (a) that these effects can already be observed on the same trial as the semantic information is being presented for the first time, and (b) that these effects are found not only in later, higher-level cognition-related ERP components (i.e., N400), but also in earlier, perception-related ERP components (i.e., P1 and/or N170).
-We furthermore conducted an exploratory time-frequency analysis to test if event-related power also showed instant effects of semantic information.
-This was to make sure that we would also capture any non-phase-locked, putatively oscillatory activity related to semantically informed perception.
+We furthermore conducted an exploratory time-frequency analysis to test if event-related power would also show instant effects of semantic information, without them having to be tightly phase-locked to stimulus onset (as is the case for ERP effects).
 
@@
 
-Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18--32) and no history of psychological disorder or treatment.
+Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18--32 years) and no history of psychological disorder or treatment.
 No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
@@
 Stimuli consisted of 240 grayscale photographs of real-world objects.
-Of these, 120 stimuli were well-known everyday objects (e.g., a bicycle, a toothbrush) which served as filler stimuli of no interest.
-The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Appendix A for the full list).
+Of these, 120 stimuli were well-known everyday objects (e.g., a bicycle, a toothbrush).
+These served as filler stimuli of no interest.
+The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Supplementary Table 1 for the full list).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming; see Appendix A for the full list).
-As our central experimental manipulation, half of the objects where presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
-The matching keywords were expected to induce semantically informed perception (i.e., participants suddenly understanding what kind of object they were viewing), whereas the non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically naive.
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming; see Supplementary Table 1 for the full list).
+As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
+The matching keywords were expected to induce semantically informed perception, that is, participants suddenly understanding what kind of object they were viewing.
+The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically naive.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
@@
 (ref:figure-1-caption) Experimental design and ERP results.
-***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing.
+***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
 In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to naive perception.
@@
 In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight phase and 120 unfamiliar objects in the pre-insight, insight, and post-insight phases).
-It took participants approximately 35 minutes to complete the experiment.
+Participants took approximately 35 minutes to complete the entire experiment.
 
@@
 Any independent components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the MNE-Python's `find_bads_eog` method.
-This was the case for an average of `r mean(lengths(config$auto_ica_bad_components))` components per participant (range = `r min(lengths(config$auto_ica_bad_components))`--`r max(lengths(config$auto_ica_bad_components))`)
+This was the case for an average of `r mean(lengths(config$auto_ica_bad_components))` components per participant (range = `r min(lengths(config$auto_ica_bad_components))`--`r max(lengths(config$auto_ica_bad_components))` components).
 
@@
 
-The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because these models allow to control for repeated measures of participants and stimuli while also being robust against an unbalanced number of trials per condition [@baayen2008; @burki2018; @fromer2018].
+The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because these models allow to control for repeated measures of participants and stimuli, while also being robust against an unbalanced number of trials per condition [@baayen2008; @burki2018; @fromer2018].
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
@@
 This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
-All *p*-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
+All *p* values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
 
@@
 Epochs that were marked as bad for the ERP analysis (i.e., with peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV) were also removed from the time-frequency analysis.
-The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their number of cycles from `r min(config$tfr_cycles)` to `r max(config$tfr_cycles)` in steps of `r config$tfr_freqs[2] - config$tfr_cycles[1]`.
+The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their width from `r min(config$tfr_cycles)` cycles to `r max(config$tfr_cycles)` cycles in steps of `r config$tfr_cycles[2] - config$tfr_cycles[1]` cycles.
 To adjust for the typical $1/f$ shape of the EEG, the power values were transformed into percent signal change by first subtracting and then dividing by the average power at each frequency over the entire epoch [@grandchamp2011].
-We then performed baseline correction by subtracting the average during the pre-stimulus interval from `r config$tfr_baseline[1]` s to `r config$tfr_baseline[2]` s relative to object onset.
+We then performed baseline correction by subtracting the average power during the pre-stimulus interval from `r config$tfr_baseline[1]` s to `r config$tfr_baseline[2]` s relative to object onset.
 
@@
 
-In addition to the software mentioned above, we used the tidyverse set of R packages [Version `r as.character(packageVersion("tidyverse"))`\; @R-tidyverse] for data wrangling, the ggplot2 [Version `r as.character(packageVersion("ggplot2"))`\; @R-ggplot2], cowplot [Version `r as.character(packageVersion("cowplot"))`\; @R-cowplot], and eegUtils [Version `r as.character(packageVersion("eegUtils"))`\; @R-eegUtils] packages for visualization, and the papaja package [Version `r as.character(packageVersion("papaja"))`\; @R-papaja] for statistical reporting.
-We followed the workflow developed by @peikert2021 to ensure the long-term reproducibility of our analysis pipeline.
-
 ## Data and Code Availability
@@
 The materials and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
+
+In addition to the software mentioned above, our code relies on the tidyverse set of R packages [Version `r as.character(packageVersion("tidyverse"))`\; @R-tidyverse] for data wrangling, the ggplot2 [Version `r as.character(packageVersion("ggplot2"))`\; @R-ggplot2], cowplot [Version `r as.character(packageVersion("cowplot"))`\; @R-cowplot], and eegUtils [Version `r as.character(packageVersion("eegUtils"))`\; @R-eegUtils] packages for visualization, and the papaja package [Version `r as.character(packageVersion("papaja"))`\; @R-papaja] for statistical reporting.
+We followed the workflow developed by @peikert2021 to ensure the long-term reproducibility of our analysis pipeline.
 
@@
 Contrasting the semantically informed condition and the failed insight conditions, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as did the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
+Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the case for the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
 This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by the semantic information.
@@
 When the same objects were presented once more (without the semantic information), the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
-Finally, an exploratory time-frequency analysis revealed that semantically informed perception was accompanied by a reduction in event-related power in the alpha and lower beta ranges.
+Finally, an exploratory time-frequency analysis revealed that semantically informed perception was accompanied by a late reduction in event-related power in the alpha and lower beta ranges.
 Like the ERP effects, this difference immediately ocurred on the first trial on which the objects were presented together with the critical semantic information, and it reocurred when the objects were presented once more without any information.
@@
 Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these measures were effective in rouling out many alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the claim that visually perception would be cognitively impenetrable.
+We hope that these measures were effective in rouling out many alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the claim that visually perception is "cognitively impenetrable."
 
@@
 
-Taken together, the current study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on the visual processing of this object.
+Taken together, the present study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on our visual processing of this object.
 The immediacy of this influence is remarkable in at least two different ways:
 First, it does not require extensive training but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
-Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (> 400 ms), typically associated with semantic processing, but also at earlier stages (< 200 ms), typically associated with visual perception itself.
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (≥ 400 ms), typically associated with semantic processing, but also at much earlier stages (≤ 200 ms), typically associated with visual perception itself.
 

### 2022-08-25 manuscript.Rmd
Add Word/DOCX output
Spellcheck

@@
 output:
+  papaja::apa6_docx: default
   papaja::apa6_pdf:
@@
 Consistent with previous work, this suggests that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component, event-related power).
-Our study is the first to show that these effects are instantenous, that is, observable within zero to one trials after any semantic information has been presented.
+Our study is the first to show that these effects are instantaneous, that is, observable within zero to one trials after any semantic information has been presented.
 
@@
 According to one view, these cognitive capacities kick in only after the retinal input has been processed by a specialized module for visual perception [@firestone2016; @fodor1983].
-This module is encapsulated from higher-level inputs and therefore processes the visual information in a purely feedforward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
-This architecture has been mirrored in classical [e.g., @marr1982] and more contemporary [e.g., @krizhevsky2012] computer vision models, allowing them to achieve human-level perfomance in predicting object category labels from images [for review, see @lindsay2020].
+This module is encapsulated from higher-level inputs and therefore processes the visual information in a purely feed-forward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
+This architecture has been mirrored in classical [e.g., @marr1982] and more contemporary [e.g., @krizhevsky2012] computer vision models, allowing them to achieve human-level performance in predicting object category labels from images [for review, see @lindsay2020].
 
@@
 This view is supported by a variety of theoretical, behavioral, and neurophysiological accounts.
-On the theoretical level, the reverse hierarchy theory [@ahissar2004; @hochstein2002] posits that conscious processing initally occurs at the level of whole objects or object categories.
+On the theoretical level, the reverse hierarchy theory [@ahissar2004; @hochstein2002] posits that conscious processing initially occurs at the level of whole objects or object categories.
 Only after this high-level interpretation has been obtained, more fine grained visual details---if relevant for the current task---are being accessed via top-down connections.
@@
 On the behavioral level, these ideas are supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] content.
-However, some of these studies have received legitimate criticism for confounding tentantive high-level effects with low-level differences between conditions, as well as for not being able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
+However, some of these studies have received legitimate criticism for confounding tentative high-level effects with low-level differences between conditions, as well as for not being able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
 
@@
 The early peak of this component and its source in the occipital cortex [@abdelrahman2008] point to an immediate effect of semantic knowledge on visual perception.
-It is less clear, however, if these effects arise immediatly once participants obtain semantic information about an object or if, instead, they require more extensive amounts of training.
+It is less clear, however, if these effects arise immediately once participants obtain semantic information about an object or if, instead, they require more extensive amounts of training.
 Closely related to this question is the debate if tentative top-down effects of semantic cognition on perception act in an online fashion (i.e., directly modulating perceptual processing), or more indirectly, by altering stored visual representations over the course of training, which would then get reactivated once the object is reencountered later on.
@@
 To answer these open questions, we measured ERPs in response to unfamiliar objects directly while participants gained an semantic understanding of their function.
-To this end, we presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viweing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
+To this end, we presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
 We then presented the same objects again to test for downstream effects of semantic information, as in previous studies.
@@
 All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
-We determined the most parsimonous random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
+We determined the most parsimonious random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
 This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20; see Supplementary Results 1 for the final model syntax and model outputs).
@@
 
-To investiage if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated follow-up comparisons contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
+To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated follow-up comparisons contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
 This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
@@
 First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the naive condition for each participant.
-We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they ocurred at neighbouring time points, frequencies, or channels.
-Neighbouring channels were defined using the Delaunay triangulation based on 2D electrode locations as implemented in MNE-Python.
+We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they ocurred at neighboring time points, frequencies, or channels.
+Neighboring channels were defined using the Delaunay triangulation based on 2D electrode locations as implemented in MNE-Python.
 To obtain family-wise error-corrected $p$ values at the cluster level, we compared the cluster mass (i.e., the sum of the $t$ values) of each observed cluster to an empirical null distribution of cluster masses obtained from 5,000 permutations with random sign flips.
-Clusters were considered to be statistically significant if their mass exceeded the `r (1 - p_cluster) * 100`^th^ percentile of this distribution (i.e., cluster-level treshold $p < .05$, Bonferroni-corrected for three seperate tests).
+Clusters were considered to be statistically significant if their mass exceeded the `r (1 - p_cluster) * 100`^th^ percentile of this distribution (i.e., cluster-level threshold $p < .05$, Bonferroni-corrected for three separate tests).
 
@@
 
-The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly avaible.
+The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
 The materials and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
@@
 
-In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semanitcally informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
+In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
 Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
@@
 First, differences in the P1 and/or N170 components might be driven by low-level visual differences between object images rather than by our experimental manipulation (matching versus non-matching keywords in the insight phase).
-We ruled out this alternative explanation by counter-balancing the assignment of objects to conditions across participants, meaning that the same visual object entererd the analysis in both conditions on an approximately equal number of trials, barring differences in participants' classification of the object and differences in the number of rejected EEG trials (see Materials and Methods).
+We ruled out this alternative explanation by counter-balancing the assignment of objects to conditions across participants, meaning that the same visual object entered the analysis in both conditions on an approximately equal number of trials, barring differences in participants' classification of the object and differences in the number of rejected EEG trials (see Materials and Methods).
 Furthermore, we did not detect reliable differences between the two conditions in the pre-insight phase, that is, before any keywords had been presented.
@@
 Finally, an exploratory time-frequency analysis revealed that semantically informed perception was accompanied by a late reduction in event-related power in the alpha and lower beta ranges.
-Like the ERP effects, this difference immediately ocurred on the first trial on which the objects were presented together with the critical semantic information, and it reocurred when the objects were presented once more without any information.
+Like the ERP effects, this difference immediately ocurred on the first trial on which the objects were presented together with the critical semantic information, and it recurred when the objects were presented once more without any information.
 
@@
 Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these measures were effective in rouling out many alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the claim that visually perception is "cognitively impenetrable."
+We hope that these measures were effective in ruling out many alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the claim that visually perception is "cognitively impenetrable."
 
@@
 Besides this specific theory, an important role of top-down mechanisms for vision, or object recognition more specifically, is also posited by the family of predictive coding and Bayesian inference theories [e.g., @yuille2006; @clark2013; @lupyan2015; @panichello2013; @xu2007].
-Despite the theoretical advances, a detailled description of these top-down effects at the algorithmic and implementational level remains a challenge for future work [@marr1982].
+Despite the theoretical advances, a detailed description of these top-down effects at the algorithmic and implementational level remains a challenge for future work [@marr1982].
 
@@
   p_cluster = p_cluster,
-  condition_plus = "Informeed",
+  condition_plus = "Informed",
   condition_minus = "Exclude_informed"

### 2022-08-26 manuscript.Rmd
Proof-reading

@@
 
-  We would like to thank Nele Langosch for assistance with data collection and analysis as well as Guido Kiecker for technical support.
+  We would like to thank Nele Langosch for assistance with data collection as well as Guido Kiecker for technical support.
   The materials and code for this study are available at [https://osf.io/uksbc](https://osf.io/uksbc).
@@
 Does our perception of an object change once we discover what function it serves?
-Here, we showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
+We showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
 We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
@@
 Consistent with previous work, this suggests that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component, event-related power).
-Our study is the first to show that these effects are instantaneous, that is, observable within zero to one trials after any semantic information has been presented.
+Our study is the first to show that these effects are instantaneous, that is, observable within zero to one trial after any semantic information has been presented.
 
@@
 Therefore, our study is the first to show effects of cognition on perception while ruling out the possibility that prior knowledge merely acts by pre-activating or altering stored visual representations.
-Instead, this knowledge seems to alter perception online, thus providing a compelling case against the cognitive impenetrability of perception by cognition.
+Instead, this knowledge seems to alter perception online, thus providing a compelling case against the impenetrability of perception by cognition.
 
@@
 On the theoretical level, the reverse hierarchy theory [@ahissar2004; @hochstein2002] posits that conscious processing initially occurs at the level of whole objects or object categories.
-Only after this high-level interpretation has been obtained, more fine grained visual details---if relevant for the current task---are being accessed via top-down connections.
+Only after this high-level interpretation has been obtained, more fine-grained visual details---if relevant for the current task---are being accessed via top-down connections.
 Along similar lines, Bayesian inference and predictive coding theories [e.g., @yuille2006; @clark2013; @panichello2013] propose bi-directional loops of predictions and prediction errors between visual and non-visual processes.
@@
 On the neurophysiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
-Their excellent temporal resolution make it possible probe how early one can detect influences of high-level (e.g., semantic) information.
+Their excellent temporal resolution makes it possible to probe how early one can detect influences of high-level (e.g., semantic) information.
 To this end, participants in previous studies by our lab and others were trained to associate visual objects with different amounts of semantic information.
@@
 
-To answer these open questions, we measured ERPs in response to unfamiliar objects directly while participants gained an semantic understanding of their function.
+To answer these open questions, we measured ERPs in response to unfamiliar objects directly while participants gained a semantic understanding of their function.
 To this end, we presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
@@
 We hypothesized that semantic information would have instant effects on visual perception, by which we mean (a) that these effects can already be observed on the same trial as the semantic information is being presented for the first time, and (b) that these effects are found not only in later, higher-level cognition-related ERP components (i.e., N400), but also in earlier, perception-related ERP components (i.e., P1 and/or N170).
-We furthermore conducted an exploratory time-frequency analysis to test if event-related power would also show instant effects of semantic information, without them having to be tightly phase-locked to stimulus onset (as is the case for ERP effects).
+We furthermore conducted an exploratory time-frequency analysis to test if semantic information also has instant effects on event-related power which, unlike ERP effects, do not need to be tightly phase-locked to stimulus onset.
 
@@
 Ampl. = amplitude.\newline
-\* *p* $<$ .05. \*\* *p* $<$ .01. \*\*\* *p* $<$ .001.
+\* $p_\text{corr} < .05$. \*\* $p_\text{corr} < .01$. \*\*\* $p_\text{corr} < .001$.
 
@@
 The data were preprocessed offline using custom scripts, available in the hu-neuro-pipeline package (Version `r pipeline_version`; https://github.com/alexenge/hu-neuro-pipeline) and based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
-First, the data were were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
+First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
 Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a low-pass filtered copy of the data (cutoff = 1 Hz).
-A variable number of components per participants were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (mean = `r mean(unlist(config$auto_ica_n_components))` components, range `r min(unlist(config$auto_ica_n_components))`--`r max(unlist(config$auto_ica_n_components))`).
+A variable number of components per participant were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (mean = `r mean(unlist(config$auto_ica_n_components))` components, range `r min(unlist(config$auto_ica_n_components))`--`r max(unlist(config$auto_ica_n_components))`).
 Then the ICA was fitted based on these components using the FastICA algorithm [@hyvarinen1999].
@@
 For the analysis of ERP amplitudes, a zero-phase, non-causal FIR filter with a lower pass-band edge at `r config$highpass_freq` Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at `r config$lowpass_freq` Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was segmented into epochs ranging from `r config$epochs_tmin` s to `r config$epochs_tmax` s relative the onset of the presentation of each unfamiliar object.
+Next, the continuous EEG was segmented into epochs ranging from `r config$epochs_tmin` s to `r config$epochs_tmax` s relative to the onset of the presentation of each unfamiliar object.
 These epochs were baseline-corrected by subtracting the average voltage during the interval of `r config$baseline[1]` s to `r config$baseline[2]` s relative to stimulus onset.
@@
 First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the naive condition for each participant.
-We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they ocurred at neighboring time points, frequencies, or channels.
+We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they occurred at neighboring time points, frequencies, or channels.
 Neighboring channels were defined using the Delaunay triangulation based on 2D electrode locations as implemented in MNE-Python.
@@
 In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
-These non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the actual object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
+These non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
 However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
@@
 This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Contrasting the semantically informed condition and the failed insight conditions, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the case for the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
-This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by the semantic information.
+Contrasting the semantically informed condition and the failed insight condition, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
+Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
+This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.
 
@@
 Finally, an exploratory time-frequency analysis revealed that semantically informed perception was accompanied by a late reduction in event-related power in the alpha and lower beta ranges.
-Like the ERP effects, this difference immediately ocurred on the first trial on which the objects were presented together with the critical semantic information, and it recurred when the objects were presented once more without any information.
+Like the ERP effects, this difference immediately occurred on the first trial on which the objects were presented together with the critical semantic information, and it recurred when the objects were presented once more without any information.
 
@@
 It indicates that acquiring an understanding of the objects in the insight phase lessened participants' demand for effortful semantic processing in comparison to the naive condition [@kutas2011].
-This finding replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+This finding replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @supp2005; @abdelrahman2008] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
 The latency of this effect and the computational role of the N400 component [@bornkessel-schlesewsky2019; @lau2008; @rabovsky2018] suggest that it has a post-perceptual locus in the semantic system.
@@
 In contrast to the N400, the N170 component (150--200 ms after object onset) was modulated only on those initial trials on which the objects were presented together with the relevant semantic information.
-It therefore constitutes an online marker of semantic insight, that is, participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
+It therefore constitutes an online marker of semantic insight, that is, of participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
 The N170 is typically associated with the holistic perception of faces [@eimer2011; @sagiv2001] and other stimuli of visual expertise [@rossion2002; @tanaka2001].
@@
 Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these measures were effective in ruling out many alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the claim that visually perception is "cognitively impenetrable."
+We hope that these measures were effective in ruling out many alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the claim that visual perception is "cognitively impenetrable."
 

### 2022-08-26 manuscript.Rmd
Proof-reading

@@
 
-  Number of words: 251 (abstract), 842 (introduction), 1,847 (discussion)
+  Number of words: 212 (abstract), 849 (introduction), 1,856 (discussion)
 
@@
 First, it does not require extensive training but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
-Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (≥ 400 ms), typically associated with semantic processing, but also at much earlier stages (≤ 200 ms), typically associated with visual perception itself.
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (> 400 ms), typically associated with semantic processing, but also at much earlier stages (< 200 ms), typically associated with visual perception itself.
 

### 2022-08-26 manuscript.Rmd
Cache figures

@@
   mixed_models = FALSE,
-  control_analysis = FALSE
+  control_analysis = FALSE,
+  figures = FALSE
 )
@@
 
-```{r, fig1, fig.height=12, fig.cap="(ref:figure-1-caption)"}
+```{r, fig1, cache=!run$figures, fig.height=12, fig.cap="(ref:figure-1-caption)"}
 # Create Figure 1
@@
 
-```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)"}
+```{r, fig2, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-2-caption)"}
 # Create topographic plots for event-related power in the pre-insight phase
@@
 
-```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)"}
+```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-3-caption)"}
 # Create topographic plots for event-related power in the insight phase
@@
 
-```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)"}
+```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-4-caption)"}
 # Create topographic plots for event-related power in the post-insight phase
@@
 
-```{r, figs1, fig.height=11, fig.cap="(ref:figure-s1-caption)", eval=TRUE}
+```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-s1-caption)"}
 # Create topographic plots for control analysis of event-related power

### 2022-08-26 manuscript_files/helper_functions.R
Use blue background color for trials

@@ -1,4 +1,5 @@
 aha_colors <- c("#ca0020", "#0571b0")
+stimulus_bg_color <- "#a9d9ff"
 
 plot_fig1a <- function(files_dir) {
 
@@ -7,7 +8,9 @@ plot_fig1a <- function(files_dir) {
   require(cowplot)
 
   # Trial structure
-  example_stim <- magick::image_read(here::here(files_dir, "example_stim.png"))
+  example_stim <- magick::image_read(
+    here::here("materials", "unfamiliar", "103.png")
+  )
   ggplot() +
     coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
     theme_void() +
@@ -26,23 +29,23 @@ plot_fig1a <- function(files_dir) {
     # Squares
     annotate(
       geom = "rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75,
-      color = "black", fill = "white"
+      color = "black", fill = stimulus_bg_color
     ) +
     annotate(
       geom = "rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65,
-      color = aha_colors[2], fill = "white"
+      color = aha_colors[2], fill = stimulus_bg_color
     ) +
     annotate(
       geom = "rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89,
-      color = aha_colors[1], fill = "white"
+      color = aha_colors[1], fill = stimulus_bg_color
     ) +
     annotate(
       geom = "rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79,
-      color = "black", fill = "white"
+      color = "black", fill = stimulus_bg_color
     ) +
     annotate(
       geom = "rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81,
-      color = "black", fill = "white"
+      color = "black", fill = stimulus_bg_color
     ) +
     annotate(
       geom = "text", x = -27, y = 65.3, label = "+", size = 20 / .pt,
@@ -172,11 +175,11 @@ plot_fig1a <- function(files_dir) {
     # Squares
     annotate(
       geom = "rect", xmin = -91, xmax = -71, ymin = 22, ymax = 42,
-      color = "black", fill = "white"
+      color = "black", fill = stimulus_bg_color
     ) +
     annotate(
       geom = "rect", xmin = -53, xmax = -73, ymin = 24, ymax = 44,
-      color = "black", fill = "white"
[…]

### 2022-08-29 rsa.py
Add RSA script

@@ -1,0 +1,90 @@
+from natsort import natsorted
+from glob import glob
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy
+from mne import read_epochs
+
+
+def rsa_spearman(rdm1, rdm2):
+    lt_rdm1 = get_lower_triangular(rdm1)
+    lt_rdm2 = get_lower_triangular(rdm2)
+    return scipy.stats.spearmanr(lt_rdm1, lt_rdm2)[0]
+
+
+def get_lower_triangular(rdm):
+    num_conditions = rdm.shape[0]
+    return rdm[np.tril_indices(num_conditions, -1)]
+
+
+# Process each participant's epochs separately
+epochs_files = sorted(glob("output/epochs/*/*_epo.fif"))
+n_participants = len(epochs_files)
+condition_rdms_list = []
+erp_rdms_list = []
+corrs_list = []
+for participant_ix, epochs_file in enumerate(epochs_files):
+
+    # Read data
+    all_epochs = read_epochs(epochs_file)
+    epochs = all_epochs['condition in ["Informed", "Naive"]']
+
+    # Prepare empty model RDMs for item conditions
+    phases = ["Pre-insight", "Insight", "Post-insight"]
+    n_phases = len(phases)
+    items = np.unique(epochs.metadata["item_id"])
+    n_items = len(items)
+    condition_rdms = np.zeros((n_phases, n_items, n_items))
+
+    # Prepare empty neural RDMs for ERPs
+    times = epochs.times
+    n_times = len(times)
+    erp_rdms = np.zeros((n_phases, n_times, n_items, n_items))
+
+    # Prepare empty matrix for RSA results
+    corrs = np.zeros((n_times, n_phases))
+
+    # Fill RDMs separately for each phase of the epxeriment
+    for phase_ix, phase in enumerate(phases):
+
+        # Sort items so they are in the same order for all participants
+        trials = epochs.metadata.query(f'phase == "{phase}"').reset_index()
+        sort_ixs = np.argsort(np.array(trials["item_id"], dtype=int))
+        items = np.array(trials.iloc[sort_ixs, ]["item_id"])
+        item_conditions = np.array(trials.iloc[sort_ixs, ]["condition"])
+
+        # Fill model RDM based on item conditions (same = 1, different = 0)
+        for row_ix in sort_ixs:
+            for col_ix in sort_ixs:
[…]

### 2022-08-29 mvpa.py
Add MVPA script

@@ -1,0 +1,53 @@
+from glob import glob
+
+import matplotlib.pyplot as plt
+import numpy as np
+from mne import read_epochs
+from mne.decoding import SlidingEstimator, cross_val_multiscore
+from sklearn.pipeline import make_pipeline
+from sklearn.preprocessing import StandardScaler
+from sklearn.svm import LinearSVC
+
+# Do decoding separately for each participant
+epochs_files = sorted(glob("output/epochs/*/*_epo.fif"))
+scores_list = []
+for epochs_file in epochs_files:
+
+    # Do decoding separately for each phase of the experiment
+    all_epochs = read_epochs(epochs_file)['condition in ["Informed", "Naive"]']
+    scores_participant_list = []
+    phases = ["Pre-insight", "Insight", "Post-insight"]
+    for phase in phases:
+
+        # Extract data and labels for the current phase
+        bad_ixs = np.isnan(all_epochs.metadata["N170"])
+        epochs = all_epochs[~bad_ixs][f'phase == "{phase}"']
+        X = epochs.pick_types(eeg=True).get_data()
+        y = epochs.events[:, 2]
+
+        # Run decoding over time
+        # clf = make_pipeline(StandardScaler(), LogisticRegression(solver="liblinear"))
+        clf = make_pipeline(StandardScaler(), LinearSVC(max_iter=10000))
+        time_decod = SlidingEstimator(clf, n_jobs=None, scoring="roc_auc", verbose=True)
+        scores = cross_val_multiscore(time_decod, X, y, cv=5, n_jobs=5)
+
+        # Compute mean scores across cross-validation splits
+        scores = np.mean(scores, axis=0)
+        scores_participant_list.append(scores)
+
+    # Combine scores for the three phases into a single array
+    scores_participant = np.stack(scores_participant_list, axis=1)
+    scores_list.append(scores_participant)
+
+# Average scores per phase across participants
+mean_scores = np.stack(scores_list).mean(axis=0)
+
+# Plot decoding scores for all three phases
+fig, ax = plt.subplots()
+ax.plot(epochs.times, mean_scores, label="score")
+ax.axhline(0.5, color="k", linestyle="--")
+ax.set_xlabel("Times")
+ax.set_ylabel("AUC")  # Area Under the Curve
+plt.legend(labels=phases)
+ax.axvline(0.0, color="k", linestyle="-")
+ax.set_title("Sensor space decoding")

### 2022-10-12 manuscript_files/helper_functions.R
Better translation for response options

@@ -97,12 +97,12 @@ plot_fig1a <- function(files_dir) {
     ) +
     annotate(
       geom = "text", x = -12, y = 26,
-      label = "B. \"I have an\nassumption\nwhat this is\"",
+      label = "B. \"I rather have\nan assumption\nwhat this is\"",
       family = "Helvetica", lineheight = 1
     ) +
     annotate(
       geom = "text", x = 12, y = 26,
-      label = "C. \"I have rather\nno assumption\nwhat this is\"",
+      label = "C. \"I rather have\nno assumption\nwhat this is\"",
       family = "Helvetica", lineheight = 1
     ) +
     annotate(

### 2022-10-12 manuscript_files/helper_functions.R
Show only significant topographies

@@ -317,7 +317,8 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
           fill = "gray90"
         ) +
         annotate(
-          geom = "text", x = (tmin + tmax) / 2, y = 7.9, label = asterisks
+          geom = "text", x = (tmin + tmax) / 2, y = 7.9, label = asterisks,
+          size = 5
         ) +
         # X (time) axis
         annotate(
@@ -437,7 +438,13 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
       )
 
       # Combine time course and topography
-      wave + draw_plot(topo, x = -0.4, y = 2.7, width = 0.6, height = 6.0)
+      if (p_value < 0.05) {
+        wave + draw_plot(
+          plot = topo, x = tmin - 0.46, y = 2.7, width = 0.6, height = 6.0
+        )
+      } else {
+        wave
+      }
     }) %>%
       # Combine plots for the current ERP component and all three phases
       plot_grid(plotlist = ., nrow = 1)

### 2022-10-12 manuscript.Rmd
Add example stimuli

@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., voltage, measuring; clay pot, drumming; see Supplementary Table 1 for the full list).
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., electric current, measuring; clay pot, drumming; see Supplementary Table 1 for the full list).
 As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
@@
 # Print table of materials
-read_tsv(here("materials", "items.txt"), col_types = cols()) %>%
+read_csv(here("example_stimuli", "stimuli.csv")) %>%
   mutate(
-    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
+    match_ger = paste0(
+      "\\textit{", match_noun_ger, "}, \\textit{", match_verb_ger, "}"
+    ),
     match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
-    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
+    nonmatch_ger = paste0(
+      "\\textit{", nonmatch_noun_ger, "}, \\textit{", nonmatch_verb_ger, "}"
+    ),
     nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
@@
     img = paste0(
-      "\\includegraphics[valign=c,scale=0.245]{materials/unfamiliar/",
-      item,
-      ".png}"
+      "\\includegraphics[valign=c,scale=0.25]{example_stimuli/", item, ".png}"
     ),
-    item = as.character(item),
     match = paste(match_ger, match_en, sep = "\n") %>%
@@
     col.names = c(
-      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
+      "Object", "Matching keywords", "Non-matching keywords"
     ),
@@
     longtable = TRUE,
-    caption = "Unfamiliar Object Stimuli\\smallskip",
+    caption = "Example stimuli\\smallskip",
     font_size = "footnotesize"

### 2022-10-14 manuscript.Rmd
Add control analysis for TFR

--- 2022-08-26 manuscript.Rmd
@@
     ),
+    tfr_components = list(
+      name = list("alpha_beta"),
+      tmin = list(0.6),
+      tmax = list(1.2),
+      fmin = list(8.0),
+      fmax = list(20.0),
+      roi = list(c("P3", "Pz", "P4", "PO3", "POz", "PO4"))
+    ),
     perm_tmin = -0.4,
@@
 
-  # Fit the model for each component
+  # Fit the model for each ERP component
   map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
     set_names(deps) -> models_control
+
+  # Fit an additional model for event-related power, controlling for RTs
+  form_rt <- ~ phase * condition + log(rt) +
+    (phase * condition | participant_id) +
+    (phase * condition | item_id)
+  models_control$alpha_beta <-
+    fit_mixed_models(form = form_rt, data = trials_main, dep = "alpha_beta")
 
@@
 # Extract relevant statistics to print in the main text
-map(models_control, function(mod) as_tibble(mod$anova, rownames = "effect")) %>%
-  bind_rows(.id = "component") %>%
-  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table_control
 map(models_control, function(mod) as_tibble(mod$contrasts)) %>%

### 2022-10-14 manuscript.Rmd
Add text for control analysis for TFR

--- 2022-10-12 manuscript.Rmd
@@
 
+Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kivalik2013].
+To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, Pz, P4, PO3, POz, and PO4; see Figures 3 and 4).
+We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
+This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
+
 # Discussion

### 2022-10-14 manuscript.Rmd
Change order of output file types
Clean up code style

@@
 output:
-  papaja::apa6_docx: default
   papaja::apa6_pdf:
     latex_engine: xelatex
+  papaja::apa6_docx: default
 
@@
       # Informed condition: Matching keywords and positive response
-      "Informed" = item_id[
+      Informed = item_id[
         phase == "Insight" & keywords == "Match" & response %in% c(3, 4)
@@
       # Naive condition: Non-matching keywords and negative response
-      "Naive" = item_id[
+      Naive = item_id[
         phase == "Insight" & keywords == "Non-match" & response %in% c(1, 2)
@@
       # Exclude: Matching keywords and negative response
-      "Exclude_informed" = item_id[
+      Exclude_informed = item_id[
         phase == "Insight" & keywords == "Match" & response %in% c(1, 2)
@@
       # Exclude: Non-matching keywords and positive response
-      "Exclude_naive" = item_id[
+      Exclude_naive = item_id[
         phase == "Insight" & keywords == "Non-match" & response %in% c(3, 4)
@@
       # Exclude: Positive response *before* any info was presented
-      "Exclude_known" = item_id[phase == "Pre-insight" & response == 4]
+      Exclude_known = item_id[phase == "Pre-insight" & response == 4]
     )
@@
     output_dir = output_dir,
-    epochs_dir = here(output_dir, "epochs"),
     report_dir = report_dir,
@@
     components = list(
-      "name" = list("P1", "N170", "N400"),
-      "tmin" = list(0.1, 0.15, 0.4),
-      "tmax" = list(0.15, 0.2, 0.7),
-      "roi" = list(
+      name = list("P1", "N170", "N400"),
+      tmin = list(0.1, 0.15, 0.4),
+      tmax = list(0.15, 0.2, 0.7),
+      roi = list(
         c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
@@
     perm_tmin = -0.4,
-    perm_tmax = 1.4,
-    n_jobs = 1
+    perm_tmax = 1.4
   )
@@
       formula, data,
-      args = list("control" = lme4::lmerControl(
+      args = list(control = lme4::lmerControl(
         optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
@@
   emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  specs <- pairwise ~ condition | phase
   means <- emmeans(build@model, specs = c("phase", "condition"))
@@
   list(
-    "model" = build@model,
-    "summary" = build@summary,
-    "anova" = build@anova,
-    "means" = means,
-    "contrasts" = contrasts
+    model = build@model,
+    summary = build@summary,
+    anova = build@anova,
+    means = means,
+    contrasts = contrasts
   )
@@
   cbind(
-    c("Pre-insight" = -1, "Insight" = 1, "Post-insight" = 0),
-    c("Pre-insight" = 0, "Insight" = -1, "Post-insight" = 1)
+    c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
+    c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
   ) %>%
@@
   # Contrast coding for condition
-  cbind(c("Informed" = 1, "Naive" = -1)) %>%
+  cbind(c(`Informed` = 1, `Naive` = -1)) %>%
     t() %>%
@@
   # Contrast coding for condition
-  cbind(c("Informed" = 1, "Exclude_informed" = -1)) %>%
+  cbind(c(`Informed` = 1, `Exclude_informed` = -1)) %>%
     t() %>%

### 2022-10-14 manuscript.Rmd
Fix TFR units

@@
   # Fit an additional model for event-related power, controlling for RTs
+  trials_main$alpha_beta <- trials_main$alpha_beta * 100 # Convert to percent
   form_rt <- ~ phase * condition + log(rt) +

### 2022-10-14 manuscript.Rmd
Fix tiny bugs

--- 2022-10-14 manuscript.Rmd
@@
     ),
-    tfr_components = list(
-      name = list("alpha_beta"),
-      tmin = list(0.6),
-      tmax = list(1.2),
-      fmin = list(8.0),
-      fmax = list(20.0),
-      roi = list(c("P3", "Pz", "P4", "PO3", "POz", "PO4"))
-    ),
     perm_tmin = -0.4,
@@
 
-  # Fit the model for each ERP component
+  # Fit the model for each component
   map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
     set_names(deps) -> models_control
-
-  # Fit an additional model for event-related power, controlling for RTs
-  form_rt <- ~ phase * condition + log(rt) +
-    (phase * condition | participant_id) +
-    (phase * condition | item_id)
-  models_control$alpha_beta <-
-    fit_mixed_models(form = form_rt, data = trials_main, dep = "alpha_beta")
 
@@
 # Extract relevant statistics to print in the main text
+map(models_control, function(mod) as_tibble(mod$anova, rownames = "effect")) %>%
+  bind_rows(.id = "component") %>%
+  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table_control
 map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
@@
 
-Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kivalik2013].
+Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kilavik2013].
 To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, Pz, P4, PO3, POz, and PO4; see Figures 3 and 4).
@@
     img = paste0(
-      "\\includegraphics[valign=c,scale=0.25]{example_stimuli/", item, ".png}"
+      "\\includegraphics[valign=c,scale=0.25]{example_stimuli/",
+      item_id,
+      ".png}"
     ),
@@
 print_model_outputs <- function(model_object) {
-  model <- model_object$model
-  model@call$data <- NULL # Prevents cluttering the `summary` output
-  print(summary(model))
+  model_object$summary$data <- NULL # Prevents cluttering the summary output
+  print(model_object$summary$data)
   cat("\n")

### 2022-10-14 manuscript_files/helper_functions.R

@@ -8,9 +8,7 @@ plot_fig1a <- function(files_dir) {
   require(cowplot)
 
   # Trial structure
-  example_stim <- magick::image_read(
-    here::here("materials", "unfamiliar", "103.png")
-  )
+  example_stim <- magick::image_read(here::here("example_stimuli", "103.png"))
   ggplot() +
     coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
     theme_void() +

### 2022-10-14 manuscript.Rmd
Remove Word (.docx) output
Round degrees of freedom (df) in text

@@
     latex_engine: xelatex
-  papaja::apa6_docx: default
 
@@
 Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r print_df(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_df(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
@@
 In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
-Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
-There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
+Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
+There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "P1" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
 
 In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
-As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
-Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
+As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N400" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N170" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "P1" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
 
@@
 This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Contrasting the semantically informed condition and the failed insight condition, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
+Contrasting the semantically informed condition and the failed insight condition, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
+Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
 This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.
@@
 We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
-This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
+This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_df(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_df(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
 

### 2022-10-14 manuscript_files/helper_functions.R

@@ -622,3 +622,5 @@ plot_tfr_topos <- function(tfr_grand_ave,
   ) +
     draw_plot(colorbar, x = -0.28, y = 0.445)
 }
+
+print_df <- function(x) format(round(x), big.mark = ",")

### 2022-10-14 manuscript.Rmd
Fix model ouputs in supplement

@@
 print_model_outputs <- function(model_object) {
-  model_object$summary$data <- NULL # Prevents cluttering the summary output
-  print(model_object$summary$data)
+  model_object$summary$call$data <- NULL # Prevents cluttering the output
+  print(model_object$summary)
   cat("\n")

### 2022-10-14 manuscript.Rmd
Make electrode ordering consistent

@@
       fmax = list(20.0),
-      roi = list(c("P3", "Pz", "P4", "PO3", "POz", "PO4"))
+      roi = list(c("P3", "P4", "Pz", "PO3", "PO4", "POz"))
     ),
@@
 This led to the exclusion of an average of `r mean(rejected_epochs)` trials per participant (= `r percent(mean(rejected_epochs) / 360, accuracy = 0.1)`; range `r min(rejected_epochs)`--`r max(rejected_epochs)` trials).
-Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms at channels PO3, POz, PO4, O1, Oz, and O2 and for the P1 component, 150--200 ms at channels P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at channels C1, Cz, C2, CP1, CPz, and CP2 for the N400 component.
+Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms at channels PO3, PO4, POz, O1, O2, and Oz and for the P1 component, 150--200 ms at channels P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at channels C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
 
@@
 Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kilavik2013].
-To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, Pz, P4, PO3, POz, and PO4; see Figures 3 and 4).
+To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, P4, Pz, PO3, PO4, and POz; see Figures 3 and 4).
 We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.

### 2022-10-16 manuscript.Rmd
Enable fitting control models independently

@@
 ```{r, mixed_models, include=FALSE}
+# Filter relevant conditions for the main analysis
+trials %>%
+  mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
+  drop_na() -> trials_main
+
+# Contrast coding for phase
+cbind(
+  c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
+  c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
+) %>%
+  t() %>%
+  ginv() -> contrasts(trials_main$phase)
+
+# Contrast coding for condition
+cbind(c(`Informed` = 1, `Naive` = -1)) %>%
+  t() %>%
+  ginv() -> contrasts(trials_main$condition)
+
 # Construct model formula
@@
 
-  # Filter relevant conditions for the main analysis
-  trials %>%
-    mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
-    drop_na() -> trials_main
-
-  # Contrast coding for phase
-  cbind(
-    c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
-    c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
-  ) %>%
-    t() %>%
-    ginv() -> contrasts(trials_main$phase)
-
-  # Contrast coding for condition
-  cbind(c(`Informed` = 1, `Naive` = -1)) %>%
-    t() %>%
-    ginv() -> contrasts(trials_main$condition)
-
-  # Actually fit the model for each ERP component
+  # Fit the model for each ERP component
   map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
@@
 ```{r, control_analysis, include=FALSE}
-# (Re-)do the actual model fitting if requested
-if (run$control_analysis) {
-
   # Filter relevant conditions for the control analysis
@@
     ginv() -> contrasts(trials_control$condition)
+
+# (Re-)do the actual model fitting if requested
+if (run$control_analysis) {
 

### 2022-10-23 manuscript.Rmd
Cutting words + Feedback by Rasha

@@
 authornote: |  
-  Alexander Enge \orcidlink{0000-0003-0100-2297} [https://orcid.org/0000-0003-0100-2297](0000-0003-0100-2297)
-
-  Rasha Abdel Rahman \orcidlink{0000-0002-8438-1570} [https://orcid.org/0000-0002-8438-1570](0000-0002-8438-1570)
-
   Number of pages: 23
@@
 
-  We would like to thank Nele Langosch for assistance with data collection as well as Guido Kiecker for technical support.
-  The materials and code for this study are available at [https://osf.io/uksbc](https://osf.io/uksbc).
+  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Neurocognitive Psychology lab at Humboldt-Universität zu Berlin for insightful discussions, as well as Guido Kiecker for technical support.
+  This work was supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany’s Excellence Strategy (EXC 2002/1 "Science of Intelligence") project number 390523135 and grants AB277-5 and AB277-6 to R.A.R.
 
@@
 Does our perception of an object change once we discover what function it serves?
-This question speaks not only to our everyday experiences, where we encounter novel tools and gadgets in our dynamic working and private environments.
-It also pertains to the long-standing debate about the cognitive (im)penetrability [@pylyshyn1999] of perception by higher-level capacities such as semantic knowledge or language.
+This question speaks to the long-standing debate about the cognitive (im)penetrability [@pylyshyn1999] of perception by higher-level capacities such as semantic knowledge or language.
 According to one view, these cognitive capacities kick in only after the retinal input has been processed by a specialized module for visual perception [@firestone2016; @fodor1983].
-This module is encapsulated from higher-level inputs and therefore processes the visual information in a purely feed-forward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
-This architecture has been mirrored in classical [e.g., @marr1982] and more contemporary [e.g., @krizhevsky2012] computer vision models, allowing them to achieve human-level performance in predicting object category labels from images [for review, see @lindsay2020].
+This module is encapsulated from higher-level inputs and processes visual information in a purely feed-forward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
 
-The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different aspects of cognition from early on [@churchland1994; @lupyan2015].
-This view is supported by a variety of theoretical, behavioral, and neurophysiological accounts.
-On the theoretical level, the reverse hierarchy theory [@ahissar2004; @hochstein2002] posits that conscious processing initially occurs at the level of whole objects or object categories.
-Only after this high-level interpretation has been obtained, more fine-grained visual details---if relevant for the current task---are being accessed via top-down connections.
-Along similar lines, Bayesian inference and predictive coding theories [e.g., @yuille2006; @clark2013; @panichello2013] propose bi-directional loops of predictions and prediction errors between visual and non-visual processes.
+The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different cognitive aspects from early on [@ahissar2004; @churchland1994; @clark2013; @lupyan2015; @lupyan2020; @yuille2006].
+On the behavioral level, this is supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] content.
+However, some studies have received legitimate criticism for confounding tentative high-level effects with low-level differences between conditions, as well as for not being able to discern perceptual from post-perceptual (e.g., memory-related) effects [@firestone2016].
 
-On the behavioral level, these ideas are supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] content.
-However, some of these studies have received legitimate criticism for confounding tentative high-level effects with low-level differences between conditions, as well as for not being able to discern between perceptual and post-perceptual (e.g., memory-related) effects [@firestone2016].
+On the physiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
+Their excellent temporal resolution makes it possible to probe how early one can detect influences of high-level (e.g., semantic) information.
+To this end, participants in previous studies by our lab and others learned to associate visual objects with different amounts of semantic information.
+After learning, an orthogonal task was used to compare ERPs in response to objects learned with versus without semantic information.
+This revealed differences not only in late ERP components associated with semantic processing (i.e., the N400 component) but also in the visual P1 component [@abdelrahman2008; @maier2019; @samaha2018; @weller2019].
+The early peak of this component and its source in the occipital cortex [@abdelrahman2008] point to an immediate effect of semantic knowledge on visual perception.
+It is less clear, however, if this tentative top-down effect of semantic cognition on perception acts in an online fashion (i.e., directly modulating perceptual processing), or more indirectly, by altering stored visual representations over the course of learning, which would then get reactivated once the object is reencountered later on.
 
-On the neurophysiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
-Their excellent temporal resolution makes it possible to probe how early one can detect influences of high-level (e.g., semantic) information.
-To this end, participants in previous studies by our lab and others were trained to associate visual objects with different amounts of semantic information.
-After training, an orthogonal task was used to compare the ERPs in response to semantically trained objects versus non-semantically trained objects.
-This contrast revealed differences not only in late ERP components associated with semantic processing (i.e., the N400 component) but also in the visual P1 (or P100) component [@abdelrahman2008; @maier2019; @samaha2018; @weller2019].
-The early peak of this component and its source in the occipital cortex [@abdelrahman2008] point to an immediate effect of semantic knowledge on visual perception.
-It is less clear, however, if these effects arise immediately once participants obtain semantic information about an object or if, instead, they require more extensive amounts of training.
-Closely related to this question is the debate if tentative top-down effects of semantic cognition on perception act in an online fashion (i.e., directly modulating perceptual processing), or more indirectly, by altering stored visual representations over the course of training, which would then get reactivated once the object is reencountered later on.
-
-To answer these open questions, we measured ERPs in response to unfamiliar objects directly while participants gained a semantic understanding of their function.
-To this end, we presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
-We then presented the same objects again to test for downstream effects of semantic information, as in previous studies.
+To answer this question, we measured ERPs in response to unfamiliar objects directly while participants gained a semantic understanding of their function.
+We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
+We then presented the same objects again to test for downstream effects of semantic information.
 We examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
 We hypothesized that semantic information would have instant effects on visual perception, by which we mean (a) that these effects can already be observed on the same trial as the semantic information is being presented for the first time, and (b) that these effects are found not only in later, higher-level cognition-related ERP components (i.e., N400), but also in earlier, perception-related ERP components (i.e., P1 and/or N170).
-We furthermore conducted an exploratory time-frequency analysis to test if semantic information also has instant effects on event-related power which, unlike ERP effects, do not need to be tightly phase-locked to stimulus onset.
+We furthermore conducted an exploratory time-frequency analysis to test for effects on event-related power which, unlike ERP effects, do not need to be tightly phase-locked to stimulus onset.
 
@@
 All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
-They provided written informed consent before starting the experiment and received a compensation of €8 per hour for participating.
+They provided written informed consent before starting the experiment and received a monetary compensation of €8 per hour for participating.
 
@@
 These served as filler stimuli of no interest.
-The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Supplementary Table 1 for the full list).
+The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Supplementary Table 1 for example images).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., electric current, measuring; clay pot, drumming; see Supplementary Table 1 for the full list).
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; see Supplementary Table 1 for more examples).
 As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
@@
 The inter-trial interval was 0.5 s and participants took a self-timed break after each block of 60 objects.
-The task, which was kept the same across all three phases of the experiment, was to classify each object using one of four response alternatives: (a) "I know what this is or have a strong assumption," (b) "I have an assumption what this is," (c) "I have rather no assumption what this is," or (d) "I don't know what this is and have no assumption." Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
+The task, which was kept the same across all three phases of the experiment, was to classify each object using one of four response alternatives:
+(a) *Ich weiß was das ist oder habe eine starke Vermutung* [I know what this is or have a strong assumption],
+(b) *Ich habe eher eine Vermutung, was das ist* [I rather have an assumption what this is],
+(c) *Ich habe eher keine Vermutung, was das ist* [I rather have no assumption what this is], or
+(d) *Ich weiß nicht, was das ist, und habe auch keine Vermutung* [I don’t know what this is and have no assumption].
+Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
 The mapping of the rating scale to the four buttons (left to right or right to left) was counterbalanced across participants.
@@
 This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
-This same assignment of objects conditions based on the insight phase was carried over to the pre-insight and post-insight phases.
+This same assignment of objects to conditions based on the insight phase was carried over to the pre-insight and post-insight phases for each participant individually.
 This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).
@@
 
-The data were preprocessed offline using custom scripts, available in the hu-neuro-pipeline package (Version `r pipeline_version`; https://github.com/alexenge/hu-neuro-pipeline) and based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
+The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.1](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.1)) based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
 First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
@@
 Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms at channels PO3, PO4, POz, O1, O2, and Oz and for the P1 component, 150--200 ms at channels P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at channels C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
+We chose a later time window for the N400 component than what is typically used in experiments with verbal materials (e.g., 300--500 ms), in accordance with a previously published data set that showed the 400--700 ms time window to be most robustly associated with the semantic processing of visual objects [@kovalenko2012].
 
@@
 To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated follow-up comparisons contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
-This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans].
+This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for the three separate tests.
 All *p* values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
@@
 Furthermore, we did not detect reliable differences between the two conditions in the pre-insight phase, that is, before any keywords had been presented.
-It therefore seems unlikely that low-level differences could account for the tentative effects of semantic information reported above.
+It therefore seems unlikely that low-level differences could account for the effects of semantic information reported above.
 
 Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
-Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
-In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
-These non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
+The N170 modulation might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
+The non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
 However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
-For this control analysis, we again used the semantically informed condition as defined above, but contrasted it against a different control condition.
-Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
+For this control analysis, we contrasted the semantically informed condition (i.e., matching key words and participants indicating in their response that they knew what the object was or had an assumption) against a different control condition, namely, those objects that were presented with matching keywords (as in the semantically informed condition), but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
 This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Contrasting the semantically informed condition and the failed insight condition, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
+Contrasting the semantically informed condition and the failed insight condition with matching key words, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
 Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
@@
 
-We investigated if gaining a semantic understanding of visual objects has an influence on how we perceive them.
-To this end, we measured ERPs while participants viewed unfamiliar objects before, while, and after receiving semantic information about them.
-For half of the objects, this information was matching the function of the object, thus leading to semantically informed perception.
-For the other half of the objects, the information was non-matching, thus keeping the perception of the object semantically naive.
-We found that semantically informed perception was immediately accompanied by enlarged (i.e., more negative) ERP amplitudes in the N170 component and reduced (i.e., less negative) ERP amplitudes in the N400 component.
-When the same objects were presented once more (without the semantic information), the N400 component remained significantly reduced and we also observed a modulation of the P1 component, which was enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+We found that providing participants with semantic information about previously unfamiliar objects instantly led to enlarged (i.e., more negative) ERP amplitudes in the N170 component and reduced (i.e., less negative) ERP amplitudes in the N400 component.
+When the same objects were presented once more (without the semantic information), the N400 component remained reduced and the P1 component was now enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
 Finally, an exploratory time-frequency analysis revealed that semantically informed perception was accompanied by a late reduction in event-related power in the alpha and lower beta ranges.
-Like the ERP effects, this difference immediately occurred on the first trial on which the objects were presented together with the critical semantic information, and it recurred when the objects were presented once more without any information.
 
-The reduction of the N400 component (400--700 ms after object onset) during semantically informed perception was the numerically largest effect.
-It indicates that acquiring an understanding of the objects in the insight phase lessened participants' demand for effortful semantic processing in comparison to the naive condition [@kutas2011].
-This finding replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @supp2005; @abdelrahman2008] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
-The latency of this effect and the computational role of the N400 component [@bornkessel-schlesewsky2019; @lau2008; @rabovsky2018] suggest that it has a post-perceptual locus in the semantic system.
+The N400 effect during semantically informed perception indicates that acquiring an understanding of the objects lessened participants' demand for effortful semantic processing [@kutas2011].
+It replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+The latency of this effect and the computational role of the N400 [@lau2008; @rabovsky2018; @bornkessel-schlesewsky2019] suggest a post-perceptual locus in the semantic system.
 
-In contrast to the N400, the N170 component (150--200 ms after object onset) was modulated only on those initial trials on which the objects were presented together with the relevant semantic information.
-It therefore constitutes an online marker of semantic insight, that is, of participants suddenly understanding the visual objects in the light of the additional information provided by the verbal keywords.
-The N170 is typically associated with the holistic perception of faces [@eimer2011; @sagiv2001] and other stimuli of visual expertise [@rossion2002; @tanaka2001].
-It being enlarged during semantically informed perception may reflect that the additional semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous findings with similar experimental paradigms in the domain of face perception [@bentin2002].
-In this study, participants showed a face-like (i.e., enlarged) N170 response to a scrambled version of a schematic face after but not before they were primed with the intact version of the same face.
-This effect was absent when a visual control stimulus (a non-face object) was shown instead of the intact face.
-In the domain of non-face stimuli, enlarged N170 amplitudes have also been observed when participants were asked to discriminate between composite line drawings of meaningful objects as compared to composite line drawings of non-objects [@beaucousin2011].
-Of note, this effect was present only when participants were asked to decide based on the global shape of the object and it was reversed in polarity when they were asked to decide based on the constituent parts of the object.
+Our exploratory time-frequency analysis revealed a late (> 600 ms) reduction in post-stimulus power in the alpha and lower beta ranges (approx. 8--20 Hz).
+While not predicted in advance, this is consistent with the finding that the dampening of oscillations in this range is associated with a facilitation in representing stimulus-specific information [@griffiths2019] and with successfully forming new semantic memories [@hanslmayr2009].
+Like the N400 effect in the ERP, this reduction in power occurred as soon as participants had received the relevant semantic information and recurred once the same objects were re-encountered without any semantic information.
+
+In contrast to the N400 and event-related power, the N170 component was modulated only on those initial trials on which the relevant semantic information was presented directly before the object.
+It therefore constitutes an online marker of semantic insight, that is, of participants suddenly understanding the visual objects in the light of the information provided by the keywords.
+The N170 is typically associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002].
+It being enlarged during semantically informed perception may reflect that the semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
+This interpretation is supported by previous findings of enlarged N170 amplitudes for scrambled (schematic) face stimuli after participants had been shown the original version of the face [@bentin2002], as well as for line drawings of meaningful objects as compared to non-objects [@beaucousin2011].
 Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level perception of visual objects, integrating across their visual features.
 
-The P1 component (100--150 ms after object onset), unlike the N400 and N170 components, was modulated by semantic information only one trial after this information had been obtained.
-This is consistent with previous studies showing modulations of the P1 component when participants had learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @weller2019] or about familiar objects that were rendered difficult to recognize [@samaha2018].
-What the present study adds to these findings is that the P1 effect does not take an extensive learning history to develop.
+The P1 component, unlike the N400 and N170 components, was modulated by semantic information only one trial after this information had been obtained.
+This is consistent with previous studies showing modulations of the P1 when participants had learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @samaha2018; @weller2019].
+What the present study adds is that the P1 effect does not take an extensive learning history to develop.
 Instead, it can be observed as soon as one trial after semantic insight has happened.
-Because the P1 is typically associated with lower-level sensory processing [e.g., @johannes1995; @luck2014; @pratt2011], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive it visually.
+Because the P1 is typically associated with lower-level sensory processing [@johannes1995; @pratt2011; @luck2014], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive its low-level features.
 
 Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects.
-However, the finding that these two components were modulated in different phases of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
-It has been pointed out that the time course of the N170 component is consistent with a top-down influence of (non-visual) areas in the prefrontal and parietal cortices on visual areas, whereas modulations of the P1 component seems to reflect recurrent processing *within* the visual system [@wyatte2014].
+The finding that these two components were modulated in different phases of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
+The time course of the N170 is consistent with a top-down influence of (non-visual) areas in the prefrontal and temporal-parietal cortices on visual areas, whereas modulations of the P1 component seem to reflect recurrent processing within the visual system [@wyatte2014].
 Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter pathway seems to take at least one additional encounter with the visual object to emerge.
+While the limited spatial resolution of the EEG precludes precise localization, there is converging fMRI evidence showing that semantic information can feed back into higher-level areas in the lateral occipital cortex (LOC) and early retinotopic cortex [areas V1, V2, and V3\; @hsieh2010], consistent with the neural generators of the N170 and P1 components in the ERP.
 
-While the limited spatial resolution of the EEG precludes a precise localization of these effects within the ventral stream for object recognition, there is converging evidence coming from fMRI showing that semantic information can feed back into the earliest of visual areas.
-@hsieh2010 showed participants indiscernible two-tone ("Mooney") versions of images before and after showing them the original versions.
-They found that the brain responses to the original image were correlated more strongly with the second presentation of the Mooney image (after insight had taken place) than with the first presentation of the Mooney image (before insight had taken place).
-This increase in representational similarity was observed not only in higher-level object-sensitive areas in the lateral occipital cortex (LOC), but also in early retinotopic cortex (areas V1, V2, and V3).
-These cortical regions are consistent with the neural generators of the N170 and P1 components in the ERP, which we have found to be sensitive to the semantically informed perception of previously unfamiliar objects.
-
-On a theoretical level, the top-down modulation of these visual ERPs by semantic information challenges a modular view of visual perception [@firestone2016; @fodor1983; @pylyshyn1999; but see @clarke2020].
-However, proponents of the modular view have pointed out important shortcomings of previous studies that had claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
-We took care to address as many of these shortcomings as possible in the present study:
-First, we showed that no difference between conditions had been present before any semantic information was presented.
-Second, we used an objective and time-resolved measure (ERPs) to disentangle effects with an early, more perceptual locus from those with a late, more post-perceptual locus.
+The top-down modulation of visual ERPs by semantic information challenges a modular view of visual perception [@fodor1983; @pylyshyn1999; but see @clarke2020].
+Proponents of this view have pointed out important shortcomings of previous studies that had claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
+We addressed as many of these shortcomings as possible:
+First, no difference between conditions had been present before any semantic information was presented.
+Second, we used ERPs as an objective and time-resolved measure to disentangle perceptual and post-perceptual effects.
 Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
 Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
-Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order and at the same location.
+Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order.
 Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these measures were effective in ruling out many alternative explanations for the top-down effects that we have observed, thus making a more compelling case against the claim that visual perception is "cognitively impenetrable."
+We hope that these measures were effective in ruling out many alternative explanations, thus making a compelling case against the "cognitively impenetrability" of visual perception.
 
-An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @serre2007].
-In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
-For these models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until the models overcome this "barrier of meaning" [@mitchell2020].
-Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.
+A theoretical framework that would explicitly predict the observed P1 and N170 effects in our study is lacking at present.
+The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004], which posits that objects first enter our visual consciousness at an abstract, conceptual level.
+Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
+This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [e.g., @abdelrahman2008; @maier2014; @samaha2018].
+An important role of top-down mechanisms for object recognition is also posited by theories of predictive coding and Bayesian inference [e.g., @clark2013; @lupyan2015; @panichello2013; @xu2007; @yuille2006].
+Despite the theoretical advances, detailed descriptions of these top-down effects at the algorithmic and implementational levels remain a challenge for future work.
 
-A theoretical framework that would explicitly predict or explain the observed P1 and N170 effects in our study is lacking at present.
-The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004; @hochstein2002], which posits that objects first enter our visual consciousness at an abstract, conceptual level.
-Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
-This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [@abdelrahman2008; @maier2014; @maier2019; @samaha2018; @weller2019].
-Besides this specific theory, an important role of top-down mechanisms for vision, or object recognition more specifically, is also posited by the family of predictive coding and Bayesian inference theories [e.g., @yuille2006; @clark2013; @lupyan2015; @panichello2013; @xu2007].
-Despite the theoretical advances, a detailed description of these top-down effects at the algorithmic and implementational level remains a challenge for future work [@marr1982].
+An interactive view of visual object processing with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @krizhevsky2012; @marr1982; @serre2007; for review, see @lindsay2020].
+The lack of semantic knowledge that dynamically interacts with the processing of visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
+For these models, single-trial learning seems to be out of reach until the models overcome this "barrier of meaning" [@mitchell2020].
+Drawing inspiration from neurocognitive data may help to make these models more biologically plausible and, at the same time, more data efficient [@maier2022].
 
@@
 First, it does not require extensive training but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
-Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (> 400 ms), typically associated with semantic processing, but also at much earlier stages (< 200 ms), typically associated with visual perception itself.
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (≥ 400 ms), typically associated with semantic processing, but also at much earlier stages within the first 200 ms, associated with visual perception itself.
 

### 2022-10-23 manuscript.Rmd
Clean up + comment helper functions

@@
 Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r print_df(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_df(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
@@
 In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
-Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
-There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "P1" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
+Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
+There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
 
 In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
-As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N400" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N170" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
-Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "P1" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
+As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
 
@@
 This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Contrasting the semantically informed condition and the failed insight condition with matching key words, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
+Contrasting the semantically informed condition and the failed insight condition with matching key words, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
+Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
 This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.
@@
 We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
-This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_df(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_df(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
+This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
 

### 2022-10-23 manuscript_files/helper_functions.R

@@ -1,6 +1,8 @@
+# Define color scheme
 aha_colors <- c("#ca0020", "#0571b0")
 stimulus_bg_color <- "#a9d9ff"
 
+# Helper function to create Figure 1A (trial structure)
 plot_fig1a <- function(files_dir) {
 
   # Make sure that packages are loaded
@@ -247,6 +249,7 @@ plot_fig1a <- function(files_dir) {
     )
 }
 
+# Helper function to create Figure 1B (ERP results)
 plot_fig1b <- function(evokeds, config, channel_locations, models) {
 
   # Make sure that packages are loaded
@@ -399,9 +402,6 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
           highlights = roi,
           scaling = 0.9
         ) +
-        # scale_fill_viridis_c(
-        #   option = "viridis", limits = c(-1, 1), oob = scales::squish
-        # ) +
         scale_fill_distiller(
           palette = "RdBu", limits = c(-1, 1), oob = scales::squish
         ) +
@@ -454,6 +454,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
     )
 }
 
+# Helper function to create Figure 1 (trial structure + ERP results)
 plot_fig1 <- function(files_dir, evokeds, config, channel_locations, models) {
 
   # Make sure that packages are loaded
@@ -479,9 +480,7 @@ plot_fig1 <- function(files_dir, evokeds, config, channel_locations, models) {
     annotate("segment", x = 0.726, xend = 0.726, y = 0.55, yend = Inf)
 }
 
-# plot_fig1(files_dir, evokeds, config, channel_locations, models)
-# ggsave("fig1.pdf", width = 12, height = 12)
-
+# Helper function to plot time-frequency results
 plot_tfr_topos <- function(tfr_grand_ave,
                            tfr_clusters,
                            p_cluster,
@@ -545,7 +544,6 @@ plot_tfr_topos <- function(tfr_grand_ave,
           scaling = 1.1
         ) +
         scale_fill_distiller(limits = c(-25, 25), palette = "RdBu") +
-        # scale_fill_viridis_c(limits = c(-0.25, 0.25)) +
         theme(
           plot.margin = unit(rep(-0.2, 4), "cm"),
           legend.position = "none"
@@ -623,4 +621,5 @@ plot_tfr_topos <- function(tfr_grand_ave,
     draw_plot(colorbar, x = -0.28, y = 0.445)
 }
 
[…]

### 2022-10-24 manuscript.Rmd
Move Figure 2 to Supplementary Information

@@
 
-The experiment consisted of three phases (see Figure \@ref(fig:fig1)A).
+The experiment consisted of three phases (see Figure 1A).
 In the *pre-insight* phase, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
@@
 
-```{r, fig1, cache=!run$figures, fig.height=12, fig.cap="(ref:figure-1-caption)"}
+```{r, fig1, cache=!run$figures, fig.height=12, fig.cap="(ref:fig1-caption)"}
 # Create Figure 1
@@
 
-(ref:figure-1-caption) Experimental design and ERP results.
+(ref:fig1-caption) Experimental design and ERP results.
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
@@
 This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to delineate semantically informed and naive perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure \@ref(fig:fig1)A).
+Next, to delineate semantically informed and naive perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure 1A).
 Objects were assigned to the semantically informed condition if and only if they were presented with matching keywords and the participant responded with knowing what the object was or having an assumption.
@@
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure \@ref(fig:fig1)B--D).
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure 1B--D).
 This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
@@
 In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
-Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Figure 2), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 2), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
@@
 
-```{r, fig2, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-2-caption)"}
-# Create topographic plots for event-related power in the pre-insight phase
-plot_tfr_topos(
-  filter(tfr_grand_ave, phase == "Pre-insight"),
-  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
-  p_cluster = p_cluster
-)
-```
-
-(ref:figure-2-caption) Time-frequency results for the pre-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
-A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`).
-
-```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-3-caption)"}
+```{r, fig2, cache=!run$figures, fig.height=11, fig.cap="(ref:fig2-caption)"}
 # Create topographic plots for event-related power in the insight phase
@@
 
-(ref:figure-3-caption) Time-frequency results for the insight phase.
+(ref:fig2-caption) Time-frequency results for the insight phase.
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
@@
 
-```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-4-caption)"}
+```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:fig3-caption)"}
 # Create topographic plots for event-related power in the post-insight phase
@@
 
-(ref:figure-4-caption) Time-frequency results for the post-insight phase.
+(ref:fig3-caption) Time-frequency results for the post-insight phase.
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
@@
 Contrasting the semantically informed condition and the failed insight condition with matching key words, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
+Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 2).
 This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.
@@
 
-```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figure-s1-caption)"}
+```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figs1-caption)"}
+# Create topographic plots for event-related power in the pre-insight phase
+plot_tfr_topos(
+  filter(tfr_grand_ave, phase == "Pre-insight"),
+  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
+  p_cluster = p_cluster
+)
+```
+
+(ref:figs1-caption) Time-frequency results for the pre-insight phase.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
+A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`).
+
+```{r, figs2, cache=!run$figures, fig.height=11, fig.cap="(ref:figs2-caption)"}
 # Create topographic plots for control analysis of event-related power
@@
 
-(ref:figure-s1-caption) Time-frequency results for the control analysis.
+(ref:figs2-caption) Time-frequency results for the control analysis.
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.

### 2022-10-25 manuscript.Rmd
Proofreading by AE

@@
 authornote: |  
-  Number of pages: 23
+  Number of pages: 22
 
-  Number of figures: 4
+  Number of figures: 3
 
-  Number of tables: 0
+  Number of words: 212 (abstract), 644 (introduction), 1,487 (discussion)
 
-  Number of words: 212 (abstract), 849 (introduction), 1,856 (discussion)
+  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Abdel Rahman Lab for Neurocognitive Psychology at Humboldt-Universität zu Berlin for insightful discussions, as well as Guido Kiecker for technical support.
+  This work was supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany’s Excellence Strategy (EXC 2002/1 "Science of Intelligence") project number 390523135 as well as grants AB277-5 and AB277-6 to R.A.R.
 
   The authors declare no competing financial interests.
-
-  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Neurocognitive Psychology lab at Humboldt-Universität zu Berlin for insightful discussions, as well as Guido Kiecker for technical support.
-  This work was supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany’s Excellence Strategy (EXC 2002/1 "Science of Intelligence") project number 390523135 and grants AB277-5 and AB277-6 to R.A.R.
 
@@
     latex_engine: xelatex
+  papaja::apa6_docx: default
 
@@
 Does our perception of an object change once we discover what function it serves?
-This question speaks to the long-standing debate about the cognitive (im)penetrability [@pylyshyn1999] of perception by higher-level capacities such as semantic knowledge or language.
+This question speaks to the long-standing debate about the cognitive (im)penetrability of perception by higher-level capacities such as semantic knowledge or language [@pylyshyn1999].
 According to one view, these cognitive capacities kick in only after the retinal input has been processed by a specialized module for visual perception [@firestone2016; @fodor1983].
@@
 The task, which was kept the same across all three phases of the experiment, was to classify each object using one of four response alternatives:
-(a) *Ich weiß was das ist oder habe eine starke Vermutung* [I know what this is or have a strong assumption],
+(a) *Ich weiß, was das ist, oder habe eine starke Vermutung* [I know what this is or have a strong assumption],
 (b) *Ich habe eher eine Vermutung, was das ist* [I rather have an assumption what this is],
@@
 
-## Event-Related Potential Analysis
-
 For the analysis of ERP amplitudes, a zero-phase, non-causal FIR filter with a lower pass-band edge at `r config$highpass_freq` Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at `r config$lowpass_freq` Hz (transition bandwidth: 7.5 Hz) was applied.
-Next, the continuous EEG was segmented into epochs ranging from `r config$epochs_tmin` s to `r config$epochs_tmax` s relative to the onset of the presentation of each unfamiliar object.
-These epochs were baseline-corrected by subtracting the average voltage during the interval of `r config$baseline[1]` s to `r config$baseline[2]` s relative to stimulus onset.
+Next, the continuous EEG was segmented into epochs ranging from -500 ms to 1,500 ms relative to the onset of the presentation of each unfamiliar object.
+These epochs were baseline-corrected by subtracting the average voltage during the interval of -200 ms to 0 ms relative to stimulus onset.
 Epochs containing artifacts despite ICA, defined as peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV, were removed from further analysis.
@@
 
-The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because these models allow to control for repeated measures of participants and stimuli, while also being robust against an unbalanced number of trials per condition [@baayen2008; @burki2018; @fromer2018].
+## Statistical Analysis
+
+The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because these models allow to control for repeated measures of participants and stimuli, while also being robust against an unbalanced number of trials per condition [@brown2021; @burki2018; @fromer2018].
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
@@
 
-To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated follow-up comparisons contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
-This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for the three separate tests.
+To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
+This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for three separate tests.
 All *p* values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
@@
 Epochs that were marked as bad for the ERP analysis (i.e., with peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV) were also removed from the time-frequency analysis.
-The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their width from `r min(config$tfr_cycles)` cycles to `r max(config$tfr_cycles)` cycles in steps of `r config$tfr_cycles[2] - config$tfr_cycles[1]` cycles.
+The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their width from `r min(config$tfr_cycles)` cycles to `r max(config$tfr_cycles)` cycles in steps of `r round(config$tfr_cycles[2] - config$tfr_cycles[1], 1)` cycles.
 To adjust for the typical $1/f$ shape of the EEG, the power values were transformed into percent signal change by first subtracting and then dividing by the average power at each frequency over the entire epoch [@grandchamp2011].
-We then performed baseline correction by subtracting the average power during the pre-stimulus interval from `r config$tfr_baseline[1]` s to `r config$tfr_baseline[2]` s relative to object onset.
+We then performed baseline correction by subtracting the average power during the pre-stimulus interval from -450 ms to -50 ms s relative to object onset.
 
@@
 
-## Data and Code Availability
+## Data and Code Accessibility
 
@@
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
-To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.
+To answer our main research question, we decomposed these interactions into pairwise comparisons of the semantically informed condition versus the naive condition within each of the three phases of the experiment.
 
@@
 
-There are at least two important alternative explanations for our finding that semantic information instantly affects early ERP responses.
+There are at least two alternative explanations for our finding that semantic information instantly affects early ERP responses.
 First, differences in the P1 and/or N170 components might be driven by low-level visual differences between object images rather than by our experimental manipulation (matching versus non-matching keywords in the insight phase).
-We ruled out this alternative explanation by counter-balancing the assignment of objects to conditions across participants, meaning that the same visual object entered the analysis in both conditions on an approximately equal number of trials, barring differences in participants' classification of the object and differences in the number of rejected EEG trials (see Materials and Methods).
+We ruled this out by counterbalancing the assignment of objects to conditions across participants, meaning that the same visual object entered the analysis in both conditions on an approximately equal number of trials, barring differences in participants' classification of the object and differences in the number of rejected EEG trials (see Materials and Methods).
 Furthermore, we did not detect reliable differences between the two conditions in the pre-insight phase, that is, before any keywords had been presented.
@@
 The N170 modulation might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
-The non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
+The non-matching keywords might have primed participants to expect a certain set of visual features that did not actually come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
 However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
@@
 We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
-This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
+This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{cluster}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{cluster}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
 
@@
 The N400 effect during semantically informed perception indicates that acquiring an understanding of the objects lessened participants' demand for effortful semantic processing [@kutas2011].
-It replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+It replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008\; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
 The latency of this effect and the computational role of the N400 [@lau2008; @rabovsky2018; @bornkessel-schlesewsky2019] suggest a post-perceptual locus in the semantic system.
@@
 What the present study adds is that the P1 effect does not take an extensive learning history to develop.
-Instead, it can be observed as soon as one trial after semantic insight has happened.
+Instead, it can be observed as soon as one trial after semantic insight had happened.
 Because the P1 is typically associated with lower-level sensory processing [@johannes1995; @pratt2011; @luck2014], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive its low-level features.
@@
 
-The top-down modulation of visual ERPs by semantic information challenges a modular view of visual perception [@fodor1983; @pylyshyn1999; but see @clarke2020].
+The top-down modulation of visual ERPs by semantic information challenges a modular view of visual perception [@fodor1983; @pylyshyn1999; but see @clarke2021].
 Proponents of this view have pointed out important shortcomings of previous studies that had claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
@@
 Second, we used ERPs as an objective and time-resolved measure to disentangle perceptual and post-perceptual effects.
-Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to the participants and by including well-known objects as filler stimuli.
+Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to participants and by including well-known objects as filler stimuli.
 Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
@@
 A theoretical framework that would explicitly predict the observed P1 and N170 effects in our study is lacking at present.
-The effects are consistent, however, with the reverse hierarchy theory [@ahissar2004], which posits that objects first enter our visual consciousness at an abstract, conceptual level.
+However, the effects are consistent with the reverse hierarchy theory [@ahissar2004], which posits that objects first enter visual consciousness at an abstract, conceptual level.
 Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
 This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [e.g., @abdelrahman2008; @maier2014; @samaha2018].
-An important role of top-down mechanisms for object recognition is also posited by theories of predictive coding and Bayesian inference [e.g., @clark2013; @lupyan2015; @panichello2013; @xu2007; @yuille2006].
+An important role of top-down mechanisms for object recognition is also posited by theories of predictive coding and Bayesian inference [e.g., @clark2013\; @lupyan2015; @panichello2013; @xu2007; @yuille2006].
 Despite the theoretical advances, detailed descriptions of these top-down effects at the algorithmic and implementational levels remain a challenge for future work.
 
-An interactive view of visual object processing with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @krizhevsky2012; @marr1982; @serre2007; for review, see @lindsay2020].
+An interactive view of visual object processing with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @krizhevsky2012\; @marr1982; @serre2007; for review, see @lindsay2021].
 The lack of semantic knowledge that dynamically interacts with the processing of visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
@@
 The immediacy of this influence is remarkable in at least two different ways:
-First, it does not require extensive training but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
-Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (≥ 400 ms), typically associated with semantic processing, but also at much earlier stages within the first 200 ms, associated with visual perception itself.
+First, it does not require an extensive learning history but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (> 400 ms), typically associated with semantic processing, but also at much earlier stages within the first 200 ms, associated with visual perception itself.
 
@@
   print(model_object$anova)
-  cat("\nFollow-Up Contrasts (Simple Effects)\n")
+  cat("\nPairwise Contrasts (Simple Effects)\n")
   print(model_object$contrasts)
@@
 Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`).
-
-\newpage
-
-```{r, figclusters, fig.height=8, include=FALSE}
-# Plot thresholded cluster images
-clusters %>%
-  filter(p_val < .05) %>%
-  ggplot(aes(x = time, y = channel, fill = cluster)) +
-  facet_grid(~contrast, drop = FALSE) +
-  geom_raster() +
-  theme(legend.position = "top")
-```
-
-```{r, figtfrclusters, fig.height=12, include=FALSE}
-# Plot thresholded cluster images for the insight phase
-tfr_clusters %>%
-  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
-  ggplot(aes(x = time, y = freq, fill = cluster)) +
-  facet_wrap(~channel) +
-  geom_raster() +
-  theme(legend.position = "top")
-
-# Plot thresholded cluster images for the post-insight phase
-tfr_clusters %>%
-  filter(
-    contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < .05
-  ) %>%
-  ggplot(aes(x = time, y = freq, fill = cluster)) +
-  facet_wrap(~channel) +
-  geom_raster() +
-  theme(legend.position = "top")
-
-# Plot thresholded cluster images for the control analysis
-tfr_clusters %>%
-  filter(
-    contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < .05
-  ) %>%
-  ggplot(aes(x = time, y = freq, fill = cluster)) +
-  facet_wrap(~channel) +
-  geom_raster() +
-  theme(legend.position = "top")
-```

### 2022-10-25 manuscript_files/helper_functions.R

@@ -333,7 +333,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
           geom = "text", x = xticks, y = -0.6, label = xticks
         ) +
         annotate(
-          geom = "text", x = mean(xticks), y = -1.5, label = "Time (ms)"
+          geom = "text", x = mean(xticks), y = -1.5, label = "Time (s)"
         ) +
         # Y (amplitude) axis
         annotate(

### 2022-10-25 manuscript.Rmd
Use word count from MS Word
Fix label in Supplementary TFR plot

@@
 
-  Number of words: 212 (abstract), 644 (introduction), 1,487 (discussion)
+  Number of words: 215 (abstract), 632 (introduction), 1,443 (discussion)
 
@@
   condition_plus = "Informed",
-  condition_minus = "Exclude_informed"
+  condition_minus = "Exclude_informed",
+  title_conditions = "Informed - failed"
 )

### 2022-10-25 manuscript_files/helper_functions.R

@@ -486,6 +486,7 @@ plot_tfr_topos <- function(tfr_grand_ave,
                            p_cluster,
                            condition_plus = "Informed",
                            condition_minus = "Naive",
+                           title_conditions = "Informed - naive",
                            tmin = -0.4,
                            tmax = 1.4,
                            tstep = 0.2,
@@ -503,11 +504,11 @@ plot_tfr_topos <- function(tfr_grand_ave,
 
   # Compute difference in power between conditions
   channels <- unique(tfr_clusters$channel)
-  tfr_grand_ave_informed <- filter(tfr_grand_ave, condition == "Informed")
-  tfr_grand_ave_naive <- filter(tfr_grand_ave, condition == "Naive")
-  tfr_grand_ave_diff <- mutate(tfr_grand_ave_naive, condition = "Difference")
-  tfr_grand_ave_diff[channels] <- tfr_grand_ave_informed[channels] -
-    tfr_grand_ave_naive[channels]
+  tfr_grand_ave_plus <- filter(tfr_grand_ave, condition == condition_plus)
+  tfr_grand_ave_minus <- filter(tfr_grand_ave, condition == condition_minus)
+  tfr_grand_ave_diff <- mutate(tfr_grand_ave_plus, condition = "Difference")
+  tfr_grand_ave_diff[channels] <- tfr_grand_ave_plus[channels] -
+    tfr_grand_ave_minus[channels]
 
   # Plot each time bin as a column of topographies
   map(tmins, function(tmin) {
@@ -554,7 +555,10 @@ plot_tfr_topos <- function(tfr_grand_ave,
             fill = guide_colorbar(
               title.hjust = 0.5,
               title.vjust = 0.6,
-              title = "Informed - naive\npower\n(% signal change)",
+              title = paste(
+                title_conditions, "power", "(% signal change)",
+                sep = "\n"
+              ),
               title.position = "left",
               barheight = 1.5,
               barwidth = 8.0,

### 2022-10-26 manuscript.Rmd
Proofreading by AE

@@
 Does our perception of an object change once we discover what function it serves?
-We showed human participants (*n* = 48) pictures of unfamiliar objects either together with words matching their function, leading to semantically informed perception, or together with non-matching words, resulting in naive perception.
+We showed human participants (*n* = 48) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in naive perception.
 We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
@@
 To answer this question, we measured ERPs in response to unfamiliar objects directly while participants gained a semantic understanding of their function.
-We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, or together with non-matching keywords, thus keeping the perception of the object semantically naive.
+We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, and the other half together with non-matching keywords, thus keeping the perception of the object semantically naive.
 We then presented the same objects again to test for downstream effects of semantic information.
@@
 Then the ICA was fitted based on these components using the FastICA algorithm [@hyvarinen1999].
-Any independent components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using the MNE-Python's `find_bads_eog` method.
+Any independent components showing significant correlations with either of two virtual EOG channels (VEOG: IO1 - Fp1, HEOG: F9 - F10) were removed automatically using MNE-Python's *find_bads_eog* method.
 This was the case for an average of `r mean(lengths(config$auto_ica_bad_components))` components per participant (range = `r min(lengths(config$auto_ica_bad_components))`--`r max(lengths(config$auto_ica_bad_components))` components).
 
-For the analysis of ERP amplitudes, a zero-phase, non-causal FIR filter with a lower pass-band edge at `r config$highpass_freq` Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at `r config$lowpass_freq` Hz (transition bandwidth: 7.5 Hz) was applied.
+For the analysis of ERP amplitudes, a zero-phase, non-causal FIR filter with a lower pass-band edge at `r format(config$highpass_freq, digits = 1)` Hz (transition bandwidth: 0.1 Hz) and an upper pass-band edge at `r config$lowpass_freq` Hz (transition bandwidth: 7.5 Hz) was applied.
 Next, the continuous EEG was segmented into epochs ranging from -500 ms to 1,500 ms relative to the onset of the presentation of each unfamiliar object.
@@
 Single-trial event-related potentials were computed as the mean amplitude across time windows and regions of interests (ROIs) defined a priori, namely 100--150 ms at channels PO3, PO4, POz, O1, O2, and Oz and for the P1 component, 150--200 ms at channels P7, P8, PO7, PO8, PO9, and PO10 for the N170 component, and 400--700 ms at channels C1, C2, Cz, CP1, CP2, and CPz for the N400 component.
-We chose a later time window for the N400 component than what is typically used in experiments with verbal materials (e.g., 300--500 ms), in accordance with a previously published data set that showed the 400--700 ms time window to be most robustly associated with the semantic processing of visual objects [@kovalenko2012].
+We chose a later time window for the N400 component than what is typically used in experiments with verbal materials (e.g., 300--500 ms), in accordance with a previously published data set which showed that the 400--700 ms time window is most robustly associated with the semantic processing of visual objects [@kovalenko2012].
 
@@
 Epochs that were marked as bad for the ERP analysis (i.e., with peak-to-peak amplitudes exceeding `r config$reject_peak_to_peak` µV) were also removed from the time-frequency analysis.
-The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their width from `r min(config$tfr_cycles)` cycles to `r max(config$tfr_cycles)` cycles in steps of `r round(config$tfr_cycles[2] - config$tfr_cycles[1], 1)` cycles.
+The remaining epochs were convolved with a family of Morlet wavelets, increasing linearly in their frequency from `r min(config$tfr_freqs)` Hz to `r max(config$tfr_freqs)` Hz in steps of `r config$tfr_freqs[2] - config$tfr_freqs[1]` Hz and in their width from `r min(config$tfr_cycles)` cycles to `r max(config$tfr_cycles)` cycles in steps of `r format(config$tfr_cycles[2] - config$tfr_cycles[1], digits = 1)` cycles.
 To adjust for the typical $1/f$ shape of the EEG, the power values were transformed into percent signal change by first subtracting and then dividing by the average power at each frequency over the entire epoch [@grandchamp2011].
@@
 The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
-The materials and code for data analysis are available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
+The code for data analysis is available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
 
@@
 The N400 effect during semantically informed perception indicates that acquiring an understanding of the objects lessened participants' demand for effortful semantic processing [@kutas2011].
-It replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @abdelrahman2008\; @supp2005] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+It replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @supp2005; @abdelrahman2008] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
 The latency of this effect and the computational role of the N400 [@lau2008; @rabovsky2018; @bornkessel-schlesewsky2019] suggest a post-perceptual locus in the semantic system.
@@
 Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these measures were effective in ruling out many alternative explanations, thus making a compelling case against the "cognitively impenetrability" of visual perception.
+We hope that these measures were effective in ruling out many alternative explanations, thus making a compelling case against the "cognitive impenetrability" of visual perception.
 
@@
 This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [e.g., @abdelrahman2008; @maier2014; @samaha2018].
-An important role of top-down mechanisms for object recognition is also posited by theories of predictive coding and Bayesian inference [e.g., @clark2013\; @lupyan2015; @panichello2013; @xu2007; @yuille2006].
+An important role of top-down mechanisms for object recognition is also posited by theories of predictive coding and Bayesian inference [e.g., @yuille2006; @xu2007; @clark2013; @panichello2013; @lupyan2015].
 Despite the theoretical advances, detailed descriptions of these top-down effects at the algorithmic and implementational levels remain a challenge for future work.
 
-An interactive view of visual object processing with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @krizhevsky2012\; @marr1982; @serre2007; for review, see @lindsay2021].
+An interactive view of visual object processing with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @serre2007; @krizhevsky2012; for review, see @lindsay2021].
 The lack of semantic knowledge that dynamically interacts with the processing of visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.

### 2022-10-27 manuscript.Rmd
Update word count
Update title page

@@
 ---
-title             : "Instant effects of semantic information on visual perception"
-shorttitle        : "Semantically informed perception"
+title             : "Instant Effects of Semantic Information on Visual Perception"
+shorttitle        : "Semantically Informed Perception"
 
@@
   - name          : "Rasha Abdel Rahman"
-    affiliation   : "1"
+    affiliation   : "1,4"
 affiliation:
   - id            : "1"
-    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"
+    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Germany"
   - id            : "2"
-    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig"
+    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
   - id            : "3"
-    institution   : "Fachhochschule des Mittelstands, Bamberg"
+    institution   : "Fachhochschule des Mittelstands, Bamberg, Germany"
+  - id            : "4"
+    institution   : "Cluster of Excellence \"Science of Intelligence\", Berlin, Germany"
 
@@
 
-  Number of words: 215 (abstract), 632 (introduction), 1,443 (discussion)
+  Number of words: 212 (abstract), 647 (introduction), 1,486 (discussion)
 

### 2022-10-27 manuscript.Rmd
Add new citations

@@
 
-  Number of words: 212 (abstract), 647 (introduction), 1,486 (discussion)
+  Number of words: 215 (abstract), 641 (introduction), 1,490 (discussion)
 
@@
 
-The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different cognitive aspects from early on [@ahissar2004; @churchland1994; @clark2013; @lupyan2015; @lupyan2020; @yuille2006].
-On the behavioral level, this is supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @boutonnet2015] or semantic [e.g., @gauthier2003] content.
+The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different cognitive aspects from early on [@ahissar2004; @churchland1994; @clark2013; @lupyan2015; @lupyan2020; @thierry2016; @yuille2006].
+On the behavioral level, this is supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @slivac2021] or semantic [e.g., @gauthier2003] content.
 However, some studies have received legitimate criticism for confounding tentative high-level effects with low-level differences between conditions, as well as for not being able to discern perceptual from post-perceptual (e.g., memory-related) effects [@firestone2016].
@@
 On the physiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
-Their excellent temporal resolution makes it possible to probe how early one can detect influences of high-level (e.g., semantic) information.
+Their excellent temporal resolution makes it possible to probe how early one can detect influences of high-level (e.g., semantic) information [@athanasopoulos2020].
 To this end, participants in previous studies by our lab and others learned to associate visual objects with different amounts of semantic information.
@@
 Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter pathway seems to take at least one additional encounter with the visual object to emerge.
-While the limited spatial resolution of the EEG precludes precise localization, there is converging fMRI evidence showing that semantic information can feed back into higher-level areas in the lateral occipital cortex (LOC) and early retinotopic cortex [areas V1, V2, and V3\; @hsieh2010], consistent with the neural generators of the N170 and P1 components in the ERP.
+While the limited spatial resolution of the EEG precludes precise localization, there is converging fMRI and psychophysical evidence that semantic information can feed back into higher-level areas in the lateral occipital cortex (LOC) as well as early retinotopic cortex [areas V1, V2, and V3\; @hsieh2010; @clarke2016; @teufel2018], consistent with the neural generators of the N170 and P1 components in the ERP.
 
@@
 Once this initial "vision at a glance" has taken place, feedback connections to earlier layers of the visual system are being accessed to extract the relevant lower-level features ("vision with scrutiny").
-This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [@hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [e.g., @abdelrahman2008; @maier2014; @samaha2018].
+This reverse trajectory down the visual hierarchy may explain (a) the semantically induced changes to the fMRI signal in LOC and retinotopic cortex [e.g., @hsieh2010] as well as (b) the modulations of early visual ERP components observed in the present study and others [e.g., @abdelrahman2008; @maier2014; @samaha2018].
 An important role of top-down mechanisms for object recognition is also posited by theories of predictive coding and Bayesian inference [e.g., @yuille2006; @xu2007; @clark2013; @panichello2013; @lupyan2015].

### 2022-10-28 manuscript.Rmd
Add citation

@@
 
-  Number of words: 215 (abstract), 641 (introduction), 1,490 (discussion)
+  Number of words: 215 (abstract), 645 (introduction), 1,490 (discussion)
 
@@
 
-The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different cognitive aspects from early on [@ahissar2004; @churchland1994; @clark2013; @lupyan2015; @lupyan2020; @thierry2016; @yuille2006].
+The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different cognitive aspects from early on [@churchland1994; @ahissar2004; @yuille2006; @clark2013; @lupyan2015; @thierry2016; @teufel2017; @lupyan2020].
 On the behavioral level, this is supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @slivac2021] or semantic [e.g., @gauthier2003] content.

### 2022-11-01 manuscript.Rmd
Proofreading by AE

@@
 
-  Number of words: 215 (abstract), 645 (introduction), 1,490 (discussion)
+  Number of words: 215 (abstract), 645 (introduction), 1,494 (discussion)
 
@@
 Consistent with previous work, this suggests that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component, event-related power).
-Our study is the first to show that these effects are instantaneous, that is, observable within zero to one trial after any semantic information has been presented.
+Our study is the first to show that these effects are instantaneous, that is, observable within zero to one trials after any semantic information has been presented.
 
@@
 Instead, it can be observed as soon as one trial after semantic insight had happened.
-Because the P1 is typically associated with lower-level sensory processing [@johannes1995; @pratt2011; @luck2014], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive its low-level features.
+Because the P1 is typically associated with lower-level sensory processing [@johannes1995; @pratt2011; @luck2014], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive its low-level features [@athanasopoulos2020].
 

### 2022-11-01 manuscript.Rmd
Move R references to references
Replace OSF link with DOI

@@
 
-bibliography      : ["manuscript_files/references.bib", "manuscript_files/r-references.bib"]
+bibliography      : "manuscript_files/references.bib"
 csl               : "manuscript_files/citation_style.csl"
@@
 The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
-The code for data analysis is available at [https://osf.io/uksbc/](https://osf.io/uksbc/).
+The code for data analysis is available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
 

### 2023-01-16 manuscript.Rmd
Add all stimuli

@@
   - \usepackage{setspace}
+  - \usepackage{xcolor}
+  - \definecolor{pantone}{HTML}{26629d}
 ---
@@
 These served as filler stimuli of no interest.
-The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; see Supplementary Table 1 for example images).
+The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; **\textcolor{pantone}{see Supplementary Table 1}**).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; see Supplementary Table 1 for more examples).
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; **\textcolor{pantone}{see Supplementary Table 1}**).
 As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
@@
 The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
-The code for data analysis is available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
+**\textcolor{pantone}{The experimental stimuli (object images and keywords) and}** the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
 
@@
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (Figure 1B--D).
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (see Figure 1B--D).
 This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
@@
 # Print table of materials
-read_csv(here("example_stimuli", "stimuli.csv")) %>%
+read_csv(here("materials", "keywords.csv"), col_types = cols()) %>%
   mutate(
-    match_ger = paste0(
-      "\\textit{", match_noun_ger, "}, \\textit{", match_verb_ger, "}"
-    ),
+    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
     match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
-    nonmatch_ger = paste0(
-      "\\textit{", nonmatch_noun_ger, "}, \\textit{", nonmatch_verb_ger, "}"
-    ),
+    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
     nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
@@
     img = paste0(
-      "\\includegraphics[valign=c,scale=0.25]{example_stimuli/",
-      item_id,
-      ".png}"
+      "\\includegraphics[valign=c,width=18mm]{materials/unfamiliar_objects/",
+      filename,
+      "}"
     ),
+    item_id = as.character(item_id),
     match = paste(match_ger, match_en, sep = "\n") %>%
@@
     col.names = c(
-      "Object", "Matching keywords", "Non-matching keywords"
+      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
     ),
@@
     longtable = TRUE,
-    caption = "Example stimuli\\smallskip",
+    caption = "Unfamiliar Object Stimuli\\smallskip",
     font_size = "footnotesize"

### 2023-01-21 manuscript.Rmd
Make `read_log` code and comments clearer

@@
   # Read the file
-  read_tsv(
+  log <- read_tsv(
     log_file,
     col_types = cols(),
-    locale = locale(encoding = "latin1")
+    locale = locale(encoding = "latin1"),
+    progress = FALSE
   ) %>%
@@
       # Phase of the experiment
-      phase = factor(Wdh,
+      phase = factor(
+        Wdh,
         levels = c(211, 212, 213),
@@
 
-      # Keyword conditions
-      keywords = factor(Bed,
+      # Unfamiliar versus familiar objects
+      familiarity = factor(
+        bek_unbek,
+        levels = c("bekannt", "unbekannt"),
+        labels = c("familiar", "unfamiliar")
+      ),
+
+      # Matching versus non-matching keywords for unfamiliar objects
+      keywords = factor(
+        Bed,
         levels = c("richtig", "falsch"),
@@
       # Behavioral responses
-      # 201: "I know what this is or have a strong assumption"  -> Recode as 4
-      # 202: "I have an assumption what this is"                -> Recode as 3
-      # 203: "I have rather no assumption what this is"         -> Recode as 2
-      # 204: "I don't know what this is and have no assumption" -> Recode as 1
-      response = 5 - (Tastencode - 200),
+      # Button code 201: "I know what this is or have a strong assumption"
+      # Button code 202: "I have an assumption what this is"
+      # Button code 203: "I have rather no assumption what this is"
+      # Button code 204: "I don't know what this is and have no assumption"
+      # Button code 0: Technical glitch
+      response = recode(
+        Tastencode,
+        `201` = 4, `202` = 3, `203` = 2, `204` = 1, `0` = NA_real_
+      ),
 
@@
     # Remove filler items
-    drop_na(keywords) -> log
+    filter(familiarity == "unfamiliar")
 
@@
       # Exclude: Positive response *before* any info was presented
-      Exclude_known = item_id[phase == "Pre-insight" & response == 4]
+      Exclude_known = item_id[phase == "Pre-insight" & response == 4],
+
+      # Exclude: Technical glitch
+      Exclude_glitch = item_id[phase == "Insight" & is.na(response)]
     )

### 2023-01-23 manuscript.Rmd
Make `read_log` code and comments clearer

@@
       # Behavioral responses
-      # Button code 201: "I know what this is or have a strong assumption"
-      # Button code 202: "I have an assumption what this is"
-      # Button code 203: "I have rather no assumption what this is"
-      # Button code 204: "I don't know what this is and have no assumption"
-      # Button code 0: Technical glitch
-      response = recode(
-        Tastencode,
-        `201` = 4, `202` = 3, `203` = 2, `204` = 1, `0` = NA_real_
-      ),
+      # Response code 201: "I know what this is or have a strong assumption"
+      # Response code 202: "I have an assumption what this is"
+      # Response code 203: "I have rather no assumption what this is"
+      # Response code 204: "I don't know what this is and have no assumption"
+      # Response code 0: Technical glitch
+      response = Tastencode,
 
@@
       Informed = item_id[
-        phase == "Insight" & keywords == "Match" & response %in% c(3, 4)
+        phase == "Insight" & keywords == "Match" & response %in% c(201, 202)
       ],
@@
       Naive = item_id[
-        phase == "Insight" & keywords == "Non-match" & response %in% c(1, 2)
+        phase == "Insight" & keywords == "Non-match" & response %in% c(203, 204)
       ],
@@
       Exclude_informed = item_id[
-        phase == "Insight" & keywords == "Match" & response %in% c(1, 2)
+        phase == "Insight" & keywords == "Match" & response %in% c(203, 204)
       ],
@@
       Exclude_naive = item_id[
-        phase == "Insight" & keywords == "Non-match" & response %in% c(3, 4)
+        phase == "Insight" & keywords == "Non-match" & response %in% c(201, 202)
       ],
@@
       # Exclude: Positive response *before* any info was presented
-      Exclude_known = item_id[phase == "Pre-insight" & response == 4],
+      Exclude_known = item_id[phase == "Pre-insight" & response == 201],
 
       # Exclude: Technical glitch
-      Exclude_glitch = item_id[phase == "Insight" & is.na(response)]
+      Exclude_glitch = item_id[phase == "Insight" & response == 0]
     )

### 2023-01-25 manuscript.Rmd
Add `Exclude_informed` condition to main model

@@
 # Read single trial data
-read_csv(here(output_dir, "trials.csv"), col_types = cols(
+trials <- read_csv(here(output_dir, "trials.csv"), col_types = cols(
   participant_id = col_factor(),
   item_id = col_factor(),
-  phase = col_factor(),
-  condition = col_factor()
-)) %>%
-  # Mark unrealistically short RTs
-  mutate(rt = ifelse(rt < 200, NA, rt)) -> trials
+  phase = col_factor(levels = c("Pre-insight", "Insight", "Post-insight")),
+  condition = col_factor(levels = c(
+    "Informed", "Naive", "Exclude_informed",
+    "Exclude_naive", "Exclude_known", "Exclude_glitch"
+  ))
+))
 
@@
 trials %>%
-  mutate(condition = factor(condition, levels = c("Informed", "Naive"))) %>%
-  drop_na() -> trials_main
+  filter(condition %in% c("Informed", "Naive", "Exclude_informed")) %>%
+  droplevels() -> trials
 
@@
   t() %>%
-  ginv() -> contrasts(trials_main$phase)
+  ginv() -> contrasts(trials$phase)
 
 # Contrast coding for condition
-cbind(c(`Informed` = 1, `Naive` = -1)) %>%
+cbind(
+  c(`Informed` = 1, `Naive` = -1, `Exclude_informed` = 0),
+  c(`Informed` = 1, `Naive` = 0, `Exclude_informed` = -1)
+) %>%
   t() %>%
-  ginv() -> contrasts(trials_main$condition)
+  ginv() -> contrasts(trials$condition)
 
@@
   emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  means <- emmeans(build@model, specs = c("phase", "condition"))
-  contrasts <- contrast(means, "pairwise", simple = "condition") %>%
-    summary(by = NULL, adjust = "bonferroni")
+  emm_means <- emmeans(build@model, specs = c("phase", "condition"))
+  emm_contrasts <- contrast(
+    emm_means,
+    method = "trt.vs.ctrl", simple = "condition", reverse = TRUE
+  ) %>%
+    summary(by = NULL, adjust = "fdr")
 
@@
     anova = build@anova,
-    means = means,
-    contrasts = contrasts
+    means = emm_means,
+    contrasts = emm_contrasts
   )
@@
   # Fit the model for each ERP component
-  map(deps, fit_mixed_models, formula = form, data = trials_main) %>%
+  map(deps, fit_mixed_models, formula = form, data = trials) %>%
     set_names(deps) -> models
@@
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
-To answer our main research question, we decomposed these interactions into pairwise comparisons of the semantically informed condition versus the naive condition within each of the three phases of the experiment.
+To answer our main research question, we decomposed these interactions into pairwise comparisons between semantic conditions within each of the three phases of the experiment.
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight")$p_value))` (see Figure 1B--D).
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Naive")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Naive")$p_value))` (see Figure 1B--D).
 This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
@@
 In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
-Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
-There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.
+Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Naive")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Naive")$p_value)`.
+There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Naive")$p_value)`.
 
 In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
-As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
-Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.
+As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Naive")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Naive")$p_value)`.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Naive")$p_value)`.
 

### 2023-01-25 manuscript_files/helper_functions.R
Add `Exclude_informed` condition to main model

@@ -291,7 +291,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
 
       # Extract significance from model
       as_tibble(model$contrasts) %>%
-        filter(phase == this_phase) %>%
+        filter(phase == this_phase & contrast == "Informed - Naive") %>%
         pull(p.value) -> p_value
       asterisks <- case_when(
         p_value < 0.001 ~ "***",

### 2023-01-25 manuscript.Rmd
Re-named "naive" condition to "uninformed"

@@
 Does our perception of an object change once we discover what function it serves?
-We showed human participants (*n* = 48) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in naive perception.
+We showed human participants (*n* = 48) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in **\textcolor{pantone}{uninformed}** perception.
 We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-We found that semantically informed as compared to naive perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
+We found that semantically informed as compared to **\textcolor{pantone}{uninformed}** perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
 When the same objects were presented once more without any information, the N400 and event-related power effects persisted, and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
@@
 To answer this question, we measured ERPs in response to unfamiliar objects directly while participants gained a semantic understanding of their function.
-We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, and the other half together with non-matching keywords, thus keeping the perception of the object semantically naive.
+We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, and the other half together with non-matching keywords, **\textcolor{pantone}{thus preventing participants from understanding what kind of object they were viewing}**.
 We then presented the same objects again to test for downstream effects of semantic information.
@@
 The matching keywords were expected to induce semantically informed perception, that is, participants suddenly understanding what kind of object they were viewing.
-The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically naive.
+The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically **\textcolor{pantone}{uninformed}**.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to naive perception) to an equal number of participants.
+This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to **\textcolor{pantone}{uninformed}** perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
@@
 
-      # Naive condition: Non-matching keywords and negative response
-      Naive = item_id[
+      # Uninformed condition: Non-matching keywords and negative response
+      Uninformed = item_id[
         phase == "Insight" & keywords == "Non-match" & response %in% c(203, 204)
@@
       # Exclude: Non-matching keywords and positive response
-      Exclude_naive = item_id[
+      Exclude_uninformed = item_id[
         phase == "Insight" & keywords == "Non-match" & response %in% c(201, 202)
@@
     perm_contrasts = list(
-      c("Pre-insight/Informed", "Pre-insight/Naive"),
-      c("Insight/Informed", "Insight/Naive"),
-      c("Post-insight/Informed", "Post-insight/Naive"),
+      c("Pre-insight/Informed", "Pre-insight/Uninformed"),
+      c("Insight/Informed", "Insight/Uninformed"),
+      c("Post-insight/Informed", "Post-insight/Uninformed"),
       c("Insight/Informed", "Insight/Exclude_informed")
@@
   condition = col_factor(levels = c(
-    "Informed", "Naive", "Exclude_informed",
-    "Exclude_naive", "Exclude_known", "Exclude_glitch"
+    "Informed", "Uninformed", "Exclude_informed",
+    "Exclude_uninformed", "Exclude_known", "Exclude_glitch"
   ))
@@
 trials %>%
-  filter(condition %in% c("Informed", "Naive", "Exclude_informed")) %>%
+  filter(condition %in% c("Informed", "Uninformed", "Exclude_informed")) %>%
   droplevels() -> trials
@@
 cbind(
-  c(`Informed` = 1, `Naive` = -1, `Exclude_informed` = 0),
-  c(`Informed` = 1, `Naive` = 0, `Exclude_informed` = -1)
+  c(`Informed` = 1, `Uninformed` = -1, `Exclude_informed` = 0),
+  c(`Informed` = 1, `Uninformed` = 0, `Exclude_informed` = -1)
 ) %>%
@@
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
-In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to naive perception.
+In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to **\textcolor{pantone}{uninformed}** perception.
 In the post-insight phase, the same objects were presented again without keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus naive perception within the three different phases.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus **\textcolor{pantone}{uninformed}** perception within the three different phases.
 Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
@@
 
-In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to naive perception).
+In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to **\textcolor{pantone}{uninformed}** perception).
 Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
@@
 This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to delineate semantically informed and naive perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure 1A).
+Next, to delineate semantically informed and **\textcolor{pantone}{uninformed}** perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure 1A).
 Objects were assigned to the semantically informed condition if and only if they were presented with matching keywords and the participant responded with knowing what the object was or having an assumption.
 This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Complementarily, objects were assigned to the naive condition if and only if they were presented with non-matching keywords and the participant responded with not knowing what the object was or having rather no assumption.
-This was the case for an average of `r mean(objects_per_condition$Naive)` objects per participant (= `r percent(mean(objects_per_condition$Naive) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
+Complementarily, objects were assigned to the **\textcolor{pantone}{uninformed}** condition if and only if they were presented with non-matching keywords and the participant responded with not knowing what the object was or having rather no assumption.
+This was the case for an average of `r mean(objects_per_condition$Uninformed)` objects per participant (= `r percent(mean(objects_per_condition$Uninformed) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
 This same assignment of objects to conditions based on the insight phase was carried over to the pre-insight and post-insight phases for each participant individually.
@@
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
-All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
+All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the **\textcolor{pantone}{uninformed}** condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
 We determined the most parsimonious random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
@@
 
-To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the naive condition within the pre-insight, insight, and post-insight phases.
+To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the **\textcolor{pantone}{uninformed}** condition within the pre-insight, insight, and post-insight phases.
 This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for three separate tests.
@@
 For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, and post-insight).
-First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the naive condition for each participant.
+First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition for each participant.
 We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they occurred at neighboring time points, frequencies, or channels.
@@
 Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed or **\textcolor{pantone}{uninformed}**), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
@@
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the naive condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Naive")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Naive")$p_value))` (see Figure 1B--D).
-This was expected given that the critical keywords (leading either to semantically informed perception or to naive perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$p_value))` (see Figure 1B--D).
+This was expected given that the critical keywords (leading either to semantically informed perception or **\textcolor{pantone}{uninformed}** perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
 
-In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
-Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Naive")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Naive")$p_value)`.
-There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Naive")$p_value)`.
+In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically **\textcolor{pantone}{uninformed}**.
+Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`.
+There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`.
 
 In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
-As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Naive")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Naive")$p_value)`.
-Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Naive")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Naive")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Naive")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Naive")$p_value)`.
+As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight" & contrast == "Informed - Uninformed")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight" & contrast == "Informed - Uninformed")$p_value)`.
+Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$p_value)`.
 
@@
 
-In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and naive perception within each of the three phases of the experiment.
-Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`, but one significant cluster in the insight phase (see Figure 2), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`.
+In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and **\textcolor{pantone}{uninformed}** perception within each of the three phases of the experiment.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 2), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
@@
   filter(tfr_grand_ave, phase == "Insight"),
-  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
+  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed"),
   p_cluster = p_cluster
@@
 (ref:fig2-caption) Time-frequency results for the insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive" & p_val < p_cluster)$p_val))`).
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition, grand-averaged across participants.
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`).
 
@@
   filter(
-    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
+    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed"
   ),
@@
 (ref:fig3-caption) Time-frequency results for the post-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < p_cluster)$p_val))`).
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition, grand-averaged across participants.
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`).
 
@@
 Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
-The N170 modulation might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
+The N170 modulation might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the **\textcolor{pantone}{uninformed}** condition.
 The non-matching keywords might have primed participants to expect a certain set of visual features that did not actually come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
-However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
+However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the **\textcolor{pantone}{uninformed}** condition.
 For this control analysis, we contrasted the semantically informed condition (i.e., matching key words and participants indicating in their response that they knew what the object was or had an assumption) against a different control condition, namely, those objects that were presented with matching keywords (as in the semantically informed condition), but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
@@
 We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
-This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{cluster}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{cluster}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
+This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the **\textcolor{pantone}{uninformed}** condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{cluster}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{cluster}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
 
@@
   filter(tfr_grand_ave, phase == "Pre-insight"),
-  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
+  filter(
+    tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed"
+  ),
   p_cluster = p_cluster
@@
 (ref:figs1-caption) Time-frequency results for the pre-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the naive condition, grand-averaged across participants.
-A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive")$p_val))`).
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition, grand-averaged across participants.
+A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`).
 

### 2023-01-25 manuscript_files/helper_functions.R

@@ -148,7 +148,7 @@ plot_fig1a <- function(files_dir) {
       family = "Helvetica", fontface = "bold", color = aha_colors[1]
     ) +
     annotate(
-      geom = "text", x = 22, y = 13, label = "Naive condition",
+      geom = "text", x = 22, y = 13, label = "Uninformed condition",
       family = "Helvetica", fontface = "bold", color = aha_colors[2]
     ) +
     annotate(
@@ -276,7 +276,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
       # Select dependent variable, conditions, and time window
       evokeds %>%
         filter(phase == this_phase) %>%
-        filter(condition %in% c("Informed", "Naive")) %>%
+        filter(condition %in% c("Informed", "Uninformed")) %>%
         filter(between(time, xmin, xmax)) -> evokeds_plot
 
       # Create means and SEs across participants for time course
@@ -291,7 +291,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
 
       # Extract significance from model
       as_tibble(model$contrasts) %>%
-        filter(phase == this_phase & contrast == "Informed - Naive") %>%
+        filter(phase == this_phase & contrast == "Informed - Uninformed") %>%
         pull(p.value) -> p_value
       asterisks <- case_when(
         p_value < 0.001 ~ "***",
@@ -355,7 +355,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
         # Styling
         scale_color_manual(
           values = aha_colors,
-          labels = c("Informed condition", "Naive condition"),
+          labels = c("Informed condition", "Uninformed condition"),
           aesthetics = c("color", "fill")
         ) +
         coord_cartesian(ylim = c(-3, 8), expand = TRUE) +
@@ -379,10 +379,10 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
       # Compute difference between conditions for topography
       channels <- channel_locations$channel
       evokeds_informed <- filter(evokeds_plot, condition == "Informed")
-      evokeds_naive <- filter(evokeds_plot, condition == "Naive")
+      evokeds_uninformed <- filter(evokeds_plot, condition == "Uninformed")
       evokeds_diff <- evokeds_informed
       evokeds_diff[channels] <-
-        evokeds_informed[channels] - evokeds_naive[channels]
+        evokeds_informed[channels] - evokeds_uninformed[channels]
       evokeds_diff$condition <- "Difference"
 
       # Plot topography
[…]

### 2023-01-25 manuscript.Rmd
Get rid of `->` assignment

@@
 # Compute number of objects per condition for each participant
-with(trials, table(participant_id, condition)) %>%
+objects_per_condition <- with(trials, table(participant_id, condition)) %>%
   `/`(3) %>%
   as.data.frame.matrix() %>%
-  rownames_to_column("subject_id") -> objects_per_condition
+  rownames_to_column("subject_id")
 
@@
 # Filter relevant conditions for the main analysis
-trials %>%
+trials <- trials %>%
   filter(condition %in% c("Informed", "Uninformed", "Exclude_informed")) %>%
-  droplevels() -> trials
+  droplevels()
 
 # Contrast coding for phase
-cbind(
+contrasts(trials$phase) <- cbind(
   c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
@@
   t() %>%
-  ginv() -> contrasts(trials$phase)
+  ginv()
 
 # Contrast coding for condition
-cbind(
+contrasts(trials$condition) <- cbind(
   c(`Informed` = 1, `Uninformed` = -1, `Exclude_informed` = 0),
@@
   t() %>%
-  ginv() -> contrasts(trials$condition)
+  ginv()
 
@@
   # Fit the model for each ERP component
-  map(deps, fit_mixed_models, formula = form, data = trials) %>%
-    set_names(deps) -> models
+  models <- map(deps, fit_mixed_models, formula = form, data = trials) %>%
+    set_names(deps)
 
@@
 # Extract relevant statistics to print in the main text
-map(models, function(model) as_tibble(model$anova, rownames = "effect")) %>%
+anova_table <- models %>%
+  map(function(model) as_tibble(model$anova, rownames = "effect")) %>%
   bind_rows(.id = "component") %>%
-  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table
-map(models, function(model) as_tibble(model$contrasts)) %>%
+  rename(f_value = `F value`, p_value = `Pr(>F)`)
+contrast_table <- models %>%
+  map(function(model) as_tibble(model$contrasts)) %>%
   bind_rows(.id = "component") %>%
-  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table
+  rename(t_value = `t.ratio`, p_value = `p.value`)
 ```
@@
 conditions_control <- c("Informed", "Exclude_informed")
-trials %>%
+trials_control <- trials %>%
   mutate(condition = factor(condition, levels = conditions_control)) %>%
-  drop_na() -> trials_control
+  drop_na()
 
 # Contrast coding for phase
-cbind(
+contrasts(trials_control$phase) <- cbind(
   c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
@@
   t() %>%
-  ginv() -> contrasts(trials_control$phase)
+  ginv()
 
 # Contrast coding for condition
-cbind(c(`Informed` = 1, `Exclude_informed` = -1)) %>%
+contrasts(trials_control$condition) <- cbind(
+  c(`Informed` = 1, `Exclude_informed` = -1)
+) %>%
   t() %>%
-  ginv() -> contrasts(trials_control$condition)
+  ginv()
 
@@
   # Fit the model for each ERP component
-  map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
-    set_names(deps) -> models_control
+  models_control <- deps %>%
+    map(fit_mixed_models, formula = form, data = trials_control) %>%
+    set_names(deps)
 
@@
 # Extract relevant statistics to print in the main text
-map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
+contrast_table_control <- models_control %>%
+  map(function(mod) as_tibble(mod$contrasts)) %>%
   bind_rows(.id = "component") %>%
-  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table_control
+  rename(t_value = `t.ratio`, p_value = `p.value`)
 ```

### 2023-01-25 manuscript_files/helper_functions.R

@@ -274,25 +274,25 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
       yticks <- c(-3, 3)
 
       # Select dependent variable, conditions, and time window
-      evokeds %>%
+      evokeds_plot <- evokeds %>%
         filter(phase == this_phase) %>%
         filter(condition %in% c("Informed", "Uninformed")) %>%
-        filter(between(time, xmin, xmax)) -> evokeds_plot
+        filter(between(time, xmin, xmax))
 
       # Create means and SEs across participants for time course
-      evokeds_plot %>%
+      evokeds_tc <- evokeds_plot %>%
         mutate(dep = evokeds_plot[[name]]) %>%
         Rmisc::summarySEwithin(
           measurevar = "dep",
           withinvars = c("time", "phase", "condition"),
           idvar = "participant_id"
         ) %>%
-        mutate(time = as.numeric(levels(time))[time]) -> evokeds_tc
+        mutate(time = as.numeric(levels(time))[time])
 
       # Extract significance from model
-      as_tibble(model$contrasts) %>%
+      p_value <- as_tibble(model$contrasts) %>%
         filter(phase == this_phase & contrast == "Informed - Uninformed") %>%
-        pull(p.value) -> p_value
+        pull(p.value)
       asterisks <- case_when(
         p_value < 0.001 ~ "***",
         p_value < 0.01 ~ "**",
@@ -301,7 +301,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
       )
 
       # Plot time course
-      ggplot(
+      wave <- ggplot(
         evokeds_tc,
         aes(
           x = time,
@@ -360,7 +360,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
         ) +
         coord_cartesian(ylim = c(-3, 8), expand = TRUE) +
         theme_void() +
-        theme(legend.position = "none") -> wave
+        theme(legend.position = "none")
 
       # Extract legend
       wave_legend <<- get_legend(
@@ -386,7 +386,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
       evokeds_diff$condition <- "Difference"
 
       # Plot topography
-      evokeds_diff %>%
+      topo <- evokeds_diff %>%
         filter(between(time, tmin, tmax)) %>%
         pivot_longer(
           all_of(channels),
[…]

### 2023-01-25 manuscript.Rmd
Get rid of magrittr's `%<>%` pipe

@@
 library(tidyverse)
-library(magrittr)
 
@@
   # Modify the formula such that fixed effects are always retained
-  formula %<>%
+  formula <- formula %>%
     tabulate.formula() %>%

### 2023-01-25 manuscript.Rmd
Re-name `"Exclude_informed"` to `"Unsuccessful"`

@@
       # Exclude: Matching keywords and negative response
-      Exclude_informed = item_id[
+      Unsucessful = item_id[
         phase == "Insight" & keywords == "Match" & response %in% c(203, 204)
@@
       c("Post-insight/Informed", "Post-insight/Uninformed"),
-      c("Insight/Informed", "Insight/Exclude_informed")
+      c("Insight/Informed", "Insight/Unsucessful")
     ),
@@
   condition = col_factor(levels = c(
-    "Informed", "Uninformed", "Exclude_informed",
+    "Informed", "Uninformed", "Unsucessful",
     "Exclude_uninformed", "Exclude_known", "Exclude_glitch"
@@
 trials <- trials %>%
-  filter(condition %in% c("Informed", "Uninformed", "Exclude_informed")) %>%
+  filter(condition %in% c("Informed", "Uninformed", "Unsucessful")) %>%
   droplevels()
@@
 contrasts(trials$condition) <- cbind(
-  c(`Informed` = 1, `Uninformed` = -1, `Exclude_informed` = 0),
-  c(`Informed` = 1, `Uninformed` = 0, `Exclude_informed` = -1)
+  c(`Informed` = 1, `Uninformed` = -1, `Unsucessful` = 0),
+  c(`Informed` = 1, `Uninformed` = 0, `Unsucessful` = -1)
 ) %>%
@@
 # Filter relevant conditions for the control analysis
-conditions_control <- c("Informed", "Exclude_informed")
+conditions_control <- c("Informed", "Unsucessful")
 trials_control <- trials %>%
@@
 contrasts(trials_control$condition) <- cbind(
-  c(`Informed` = 1, `Exclude_informed` = -1)
+  c(`Informed` = 1, `Unsucessful` = -1)
 ) %>%
@@
 For this control analysis, we contrasted the semantically informed condition (i.e., matching key words and participants indicating in their response that they knew what the object was or had an assumption) against a different control condition, namely, those objects that were presented with matching keywords (as in the semantically informed condition), but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
-This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
+This was the case for an average of `r mean(objects_per_condition$Unsucessful)` objects per participant (= `r percent(mean(objects_per_condition$Unsucessful) / 60, accuracy = 0.1)` of objects presented with matching keywords).
 Contrasting the semantically informed condition and the failed insight condition with matching key words, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 2).
+Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsucessful" & p_val < p_cluster)$p_val))`; see Supplementary Figure 2).
 This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.
@@
   filter(
-    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
+    tfr_clusters, contrast == "Insight/Informed - Insight/Unsucessful"
   ),
@@
   condition_plus = "Informed",
-  condition_minus = "Exclude_informed",
+  condition_minus = "Unsucessful",
   title_conditions = "Informed - failed"
@@
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`).
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsucessful" & p_val < p_cluster)$p_val))`).

### 2023-01-29 manuscript.Rmd
Add Discussion paragraph on priming

@@
 
+**\textcolor{pantone}{One could argue that the effects presented here might be reducible to more basic mechanisms such as semantic priming.
+Indeed, the keywords that were presented before each object in the semantically informed condition were chosen such that they matched the function of the object and often had a direct relationship to certain visual features of the object (see Supplementary Table 1).
+This might have induced semantic priming, which is supported by the reduction in N400 amplitudes in response to ojects in the semantically informed condition, as in previous priming studies [e.g., @bentin1985; @kellenbach2000].
+However, there are at least two arguments why semantic priming cannot account for our main findings, that is, the influence of semantic information on the early P1 and N170 components.
+First, for both of these components, ERP amplitudes were *enlarged* (i.e., more positive for the P1 component and more negative for the N170) during semantically informed perception, whereas an account based on semantic priming would have predicted *reduced* ERP amplitudes.
+Second, these effects were not just observed when comparing semantically informed perception (with matching keywords) and uninformed perception (with non-matching keywords), but also when comparing semantically informed perception with unsucessfully informed perception.
+Whereas priming might have been present in the first comparison, in the second comparison all objects were preceded by keywords that matched the function of the object to a similar degree.
+The fact that P1 and N170 amplitudes still differed between these two conditions makes it unlikely that the semantic effects that we have found are fully reducible to priming.}**
+
 A theoretical framework that would explicitly predict the observed P1 and N170 effects in our study is lacking at present.

### 2023-01-29 manuscript.Rmd
Remove control analysis

@@
   mixed_models = FALSE,
-  control_analysis = FALSE,
   figures = FALSE
@@
 
-# Construct model formula
-form <- ~ phase * condition +
-  (phase * condition | participant_id) +
-  (phase * condition | item_id)
-
 # Define helper function for fitting linear mixed models and computing contrasts
@@
   ) %>%
-    summary(by = NULL, adjust = "fdr")
+    summary(by = "contrast", adjust = "bonferroni")
 
@@
   # Fit the model for each ERP component
-  models <- map(deps, fit_mixed_models, formula = form, data = trials) %>%
+  form_erps <- ~ phase * condition +
+    (phase * condition | participant_id) +
+    (phase * condition | item_id)
+  models <- map(deps, fit_mixed_models, formula = form_erps, data = trials) %>%
     set_names(deps)
+
+  # Fit an additional control analysis model for the alpha/beta power
+  form_alpha_beta <- phase * condition + rt +
+    (phase * condition | participant_id) +
+    (phase * condition | item_id)
+  models$alpha_beta <- fit_mixed_models(
+    dep = "alpha_beta", formula = form_alpha_beta, data = trials
+  )
 
@@
 Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`).
-
-## Control Analysis
-
-```{r, control_analysis, include=FALSE}
-# Filter relevant conditions for the control analysis
-conditions_control <- c("Informed", "Unsucessful")
-trials_control <- trials %>%
-  mutate(condition = factor(condition, levels = conditions_control)) %>%
-  drop_na()
-
-# Contrast coding for phase
-contrasts(trials_control$phase) <- cbind(
-  c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
-  c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
-) %>%
-  t() %>%
-  ginv()
-
-# Contrast coding for condition
-contrasts(trials_control$condition) <- cbind(
-  c(`Informed` = 1, `Unsucessful` = -1)
-) %>%
-  t() %>%
-  ginv()
-
-# (Re-)do the actual model fitting if requested
-if (run$control_analysis) {
-
-  # Fit the model for each ERP component
-  models_control <- deps %>%
-    map(fit_mixed_models, formula = form, data = trials_control) %>%
-    set_names(deps)
-
-  # Fit an additional model for event-related power, controlling for RTs
-  trials_main$alpha_beta <- trials_main$alpha_beta * 100 # Convert to percent
-  form_rt <- ~ phase * condition + log(rt) +
-    (phase * condition | participant_id) +
-    (phase * condition | item_id)
-  models_control$alpha_beta <-
-    fit_mixed_models(form = form_rt, data = trials_main, dep = "alpha_beta")
-
-  # Save models
-  saveRDS(models_control, here(output_dir, "models_control.RDS"))
-} else {
-
-  # Read fitted models
-  models_control <- readRDS(here(output_dir, "models_control.RDS"))
-}
-
-# Extract relevant statistics to print in the main text
-contrast_table_control <- models_control %>%
-  map(function(mod) as_tibble(mod$contrasts)) %>%
-  bind_rows(.id = "component") %>%
-  rename(t_value = `t.ratio`, p_value = `p.value`)
-```
-
-There are at least two alternative explanations for our finding that semantic information instantly affects early ERP responses.
-First, differences in the P1 and/or N170 components might be driven by low-level visual differences between object images rather than by our experimental manipulation (matching versus non-matching keywords in the insight phase).
-We ruled this out by counterbalancing the assignment of objects to conditions across participants, meaning that the same visual object entered the analysis in both conditions on an approximately equal number of trials, barring differences in participants' classification of the object and differences in the number of rejected EEG trials (see Materials and Methods).
-Furthermore, we did not detect reliable differences between the two conditions in the pre-insight phase, that is, before any keywords had been presented.
-It therefore seems unlikely that low-level differences could account for the effects of semantic information reported above.
-
-Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
-The N170 modulation might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the **\textcolor{pantone}{uninformed}** condition.
-The non-matching keywords might have primed participants to expect a certain set of visual features that did not actually come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
-However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the **\textcolor{pantone}{uninformed}** condition.
-For this control analysis, we contrasted the semantically informed condition (i.e., matching key words and participants indicating in their response that they knew what the object was or had an assumption) against a different control condition, namely, those objects that were presented with matching keywords (as in the semantically informed condition), but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
-This was the case for an average of `r mean(objects_per_condition$Unsucessful)` objects per participant (= `r percent(mean(objects_per_condition$Unsucessful) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Contrasting the semantically informed condition and the failed insight condition with matching key words, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
-Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_dof(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsucessful" & p_val < p_cluster)$p_val))`; see Supplementary Figure 2).
-This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.
-
-Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kilavik2013].
-To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, P4, Pz, PO3, PO4, and POz; see Figures 3 and 4).
-We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
-This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the **\textcolor{pantone}{uninformed}** condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{cluster}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_dof(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{cluster}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
 

### 2023-01-29 manuscript.Rmd
Make changes to text non-bold

@@
 csl               : "manuscript_files/citation_style.csl"
+nocite: | 
+  @bentin1985
+  @kellenbach2000
 
@@
 Does our perception of an object change once we discover what function it serves?
-We showed human participants (*n* = 48) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in **\textcolor{pantone}{uninformed}** perception.
+We showed human participants (*n* = 48) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in \textcolor{pantone}{uninformed} perception.
 We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-We found that semantically informed as compared to **\textcolor{pantone}{uninformed}** perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
+We found that semantically informed as compared to \textcolor{pantone}{uninformed} perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
 When the same objects were presented once more without any information, the N400 and event-related power effects persisted, and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
@@
 To answer this question, we measured ERPs in response to unfamiliar objects directly while participants gained a semantic understanding of their function.
-We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, and the other half together with non-matching keywords, **\textcolor{pantone}{thus preventing participants from understanding what kind of object they were viewing}**.
+We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, and the other half together with non-matching keywords, \textcolor{pantone}{thus preventing participants from understanding what kind of object they were viewing}.
 We then presented the same objects again to test for downstream effects of semantic information.
@@
 These served as filler stimuli of no interest.
-The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; **\textcolor{pantone}{see Supplementary Table 1}**).
+The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; \textcolor{pantone}{see Supplementary Table 1}).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; **\textcolor{pantone}{see Supplementary Table 1}**).
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; \textcolor{pantone}{see Supplementary Table 1}).
 As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
 The matching keywords were expected to induce semantically informed perception, that is, participants suddenly understanding what kind of object they were viewing.
-The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically **\textcolor{pantone}{uninformed}**.
+The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically \textcolor{pantone}{uninformed}.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to **\textcolor{pantone}{uninformed}** perception) to an equal number of participants.
+This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to \textcolor{pantone}{uninformed} perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
@@
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
-In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to **\textcolor{pantone}{uninformed}** perception.
+In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to \textcolor{pantone}{uninformed} perception.
 In the post-insight phase, the same objects were presented again without keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus **\textcolor{pantone}{uninformed}** perception within the three different phases.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus \textcolor{pantone}{uninformed} perception within the three different phases.
 Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
@@
 
-In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to **\textcolor{pantone}{uninformed}** perception).
+In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to \textcolor{pantone}{uninformed} perception).
 Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
@@
 This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to delineate semantically informed and **\textcolor{pantone}{uninformed}** perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure 1A).
+Next, to delineate semantically informed and \textcolor{pantone}{uninformed} perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure 1A).
 Objects were assigned to the semantically informed condition if and only if they were presented with matching keywords and the participant responded with knowing what the object was or having an assumption.
 This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Complementarily, objects were assigned to the **\textcolor{pantone}{uninformed}** condition if and only if they were presented with non-matching keywords and the participant responded with not knowing what the object was or having rather no assumption.
+Complementarily, objects were assigned to the \textcolor{pantone}{uninformed} condition if and only if they were presented with non-matching keywords and the participant responded with not knowing what the object was or having rather no assumption.
 This was the case for an average of `r mean(objects_per_condition$Uninformed)` objects per participant (= `r percent(mean(objects_per_condition$Uninformed) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
@@
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
-All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the **\textcolor{pantone}{uninformed}** condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
+All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the \textcolor{pantone}{uninformed} condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
 We determined the most parsimonious random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
@@
 
-To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the **\textcolor{pantone}{uninformed}** condition within the pre-insight, insight, and post-insight phases.
+To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the \textcolor{pantone}{uninformed} condition within the pre-insight, insight, and post-insight phases.
 This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for three separate tests.
@@
 For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, and post-insight).
-First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition for each participant.
+First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the \textcolor{pantone}{uninformed} condition for each participant.
 We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they occurred at neighboring time points, frequencies, or channels.
@@
 The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
-**\textcolor{pantone}{The experimental stimuli (object images and keywords) and}** the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
+\textcolor{pantone}{The experimental stimuli (object images and keywords) and} the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
 
@@
 Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or **\textcolor{pantone}{uninformed}**), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed or \textcolor{pantone}{uninformed}), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
@@
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$p_value))` (see Figure 1B--D).
-This was expected given that the critical keywords (leading either to semantically informed perception or **\textcolor{pantone}{uninformed}** perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the \textcolor{pantone}{uninformed} condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$p_value))` (see Figure 1B--D).
+This was expected given that the critical keywords (leading either to semantically informed perception or \textcolor{pantone}{uninformed} perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
 
-In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically **\textcolor{pantone}{uninformed}**.
+In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically \textcolor{pantone}{uninformed}.
 Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`.
@@
 
-In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and **\textcolor{pantone}{uninformed}** perception within each of the three phases of the experiment.
+In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and \textcolor{pantone}{uninformed} perception within each of the three phases of the experiment.
 Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 2), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
@@
 (ref:fig2-caption) Time-frequency results for the insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the \textcolor{pantone}{uninformed} condition, grand-averaged across participants.
 Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`).
@@
 (ref:fig3-caption) Time-frequency results for the post-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the \textcolor{pantone}{uninformed} condition, grand-averaged across participants.
 Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`).
@@
 
-**\textcolor{pantone}{One could argue that the effects presented here might be reducible to more basic mechanisms such as semantic priming.
+\textcolor{pantone}{One could argue that the effects presented here might be reducible to more basic mechanisms such as semantic priming.
 Indeed, the keywords that were presented before each object in the semantically informed condition were chosen such that they matched the function of the object and often had a direct relationship to certain visual features of the object (see Supplementary Table 1).
-This might have induced semantic priming, which is supported by the reduction in N400 amplitudes in response to ojects in the semantically informed condition, as in previous priming studies [e.g., @bentin1985; @kellenbach2000].
+This might have induced semantic priming, which is supported by the reduction in N400 amplitudes in response to ojects in the semantically informed condition, as in previous priming studies (e.g., Bentin et al., 1985; Kellenbach et al., 2000).
 However, there are at least two arguments why semantic priming cannot account for our main findings, that is, the influence of semantic information on the early P1 and N170 components.
-First, for both of these components, ERP amplitudes were *enlarged* (i.e., more positive for the P1 component and more negative for the N170) during semantically informed perception, whereas an account based on semantic priming would have predicted *reduced* ERP amplitudes.
+First, for both of these components, ERP amplitudes were \textit{enlarged} (i.e., more positive for the P1 component and more negative for the N170) during semantically informed perception, whereas an account based on semantic priming would have predicted \textit{reduced} ERP amplitudes.
 Second, these effects were not just observed when comparing semantically informed perception (with matching keywords) and uninformed perception (with non-matching keywords), but also when comparing semantically informed perception with unsucessfully informed perception.
 Whereas priming might have been present in the first comparison, in the second comparison all objects were preceded by keywords that matched the function of the object to a similar degree.
-The fact that P1 and N170 amplitudes still differed between these two conditions makes it unlikely that the semantic effects that we have found are fully reducible to priming.}**
+The fact that P1 and N170 amplitudes still differed between these two conditions makes it unlikely that the semantic effects that we have found are fully reducible to priming.}
 
@@
 (ref:figs1-caption) Time-frequency results for the pre-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the **\textcolor{pantone}{uninformed}** condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the \textcolor{pantone}{uninformed} condition, grand-averaged across participants.
 A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`).

### 2023-01-30 manuscript.Rmd
Fix typo in unsuccessful condition

@@
       # Exclude: Matching keywords and negative response
-      Unsucessful = item_id[
+      Unsuccessful = item_id[
         phase == "Insight" & keywords == "Match" & response %in% c(203, 204)
@@
       c("Post-insight/Informed", "Post-insight/Uninformed"),
-      c("Insight/Informed", "Insight/Unsucessful")
+      c("Insight/Informed", "Insight/Unsuccessful")
     ),
@@
   condition = col_factor(levels = c(
-    "Informed", "Uninformed", "Unsucessful",
+    "Informed", "Uninformed", "Unsuccessful",
     "Exclude_uninformed", "Exclude_known", "Exclude_glitch"
@@
 trials <- trials %>%
-  filter(condition %in% c("Informed", "Uninformed", "Unsucessful")) %>%
+  filter(condition %in% c("Informed", "Uninformed", "Unsuccessful")) %>%
   droplevels()
@@
 contrasts(trials$condition) <- cbind(
-  c(`Informed` = 1, `Uninformed` = -1, `Unsucessful` = 0),
-  c(`Informed` = 1, `Uninformed` = 0, `Unsucessful` = -1)
+  c(`Informed` = 1, `Uninformed` = -1, `Unsuccessful` = 0),
+  c(`Informed` = 1, `Uninformed` = 0, `Unsuccessful` = -1)
 ) %>%
@@
   filter(
-    tfr_clusters, contrast == "Insight/Informed - Insight/Unsucessful"
+    tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful"
   ),
@@
   condition_plus = "Informed",
-  condition_minus = "Unsucessful",
+  condition_minus = "Unsuccessful",
   title_conditions = "Informed - failed"
@@
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsucessful" & p_val < p_cluster)$p_val))`).
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`).

### 2023-01-30 manuscript.Rmd
Fix bug in formula

--- 2023-01-29 manuscript.Rmd
@@
   # Fit an additional control analysis model for the alpha/beta power
-  form_alpha_beta <- phase * condition + rt +
+  form_alpha_beta <- ~ phase * condition + rt +
     (phase * condition | participant_id) +

### 2023-01-30 manuscript.Rmd
Run 4 jobs in parallel

@@
     perm_tmax = 1.4
-  )
+  ),
+  n_jobs = 4
 }

### 2023-01-30 manuscript.Rmd
Run 4 jobs in parallel

@@
     perm_tmin = -0.4,
-    perm_tmax = 1.4
-  ),
+    perm_tmax = 1.4,
     n_jobs = 4
+  )
 }

### 2023-01-31 manuscript.Rmd
Use filter for `average_by` / evokeds

@@
     ),
-    average_by = c("phase/condition"),
+    average_by = list(
+      pre_informed = "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
+      pre_uninformed = "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
+      pre_unsuccessful = "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
+      ins_informed = "phase == 'Insight' & condition == 'Informed' & rt > 200",
+      ins_uninformed = "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
+      ins_unsuccessful = "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
+      post_informed = "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
+      post_uninformed = "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
+      post_unsuccessful = "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
+    ),
     perform_tfr = TRUE,
@@
     perm_tmin = -0.4,
-    perm_tmax = 1.4,
-    n_jobs = 4
+    perm_tmax = 1.4
   )
@@
   # Fit an additional control analysis model for the alpha/beta power
-  form_alpha_beta <- ~ phase * condition + rt +
+  form_alpha_beta <- phase * condition + rt +
     (phase * condition | participant_id) +

### 2023-01-31 manuscript.Rmd

--- 2023-01-30 manuscript.Rmd
@@
     perm_tmin = -0.4,
-    perm_tmax = 1.4,
+    perm_tmax = 1.4
+  ),
   n_jobs = 4
-  )
 }

### 2023-01-31 manuscript.Rmd
Update descriptions of condition assignment

@@
 
-We first excluded from all further analyses those objects for which the participant had responded with "I know what this is" in the pre-insight phase (i.e., before any keywords were presented).
-This led to the exclusion of an average of `r mean(objects_per_condition$Exclude_known)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all unfamiliar objects).
-Next, to delineate semantically informed and \textcolor{pantone}{uninformed} perception, the assignment of the remaining objects to one of these two conditions was co-determined by our experimental manipulation (matching versus non-matching keywords) and the behavioral response of the participant in the insight phase (see Figure 1A).
-Objects were assigned to the semantically informed condition if and only if they were presented with matching keywords and the participant responded with knowing what the object was or having an assumption.
-This was the case for an average of `r mean(objects_per_condition$Informed)` objects per participant (= `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
-Complementarily, objects were assigned to the \textcolor{pantone}{uninformed} condition if and only if they were presented with non-matching keywords and the participant responded with not knowing what the object was or having rather no assumption.
-This was the case for an average of `r mean(objects_per_condition$Uninformed)` objects per participant (= `r percent(mean(objects_per_condition$Uninformed) / 60, accuracy = 0.1)` of objects presented with non-matching keywords).
-This same assignment of objects to conditions based on the insight phase was carried over to the pre-insight and post-insight phases for each participant individually.
-This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic understanding acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).
+[We used participants' behavioral responses to verify our experimental manipulation and to assign each object to a semantic condition.
+First, we used participants' responses from the pre-insight phase (when objects were presented for the first time and without keywords) to make sure that objects were indeed unfamiliar to them.
+That is, we excluded any objects for which participants responded with "I know what this is" in the pre-insight phase.
+Next, we used participants' responses from the insight phase (when objects were presented for the second time, now preceded by keywords) to assign the remaining objects to different semantic conditions: Semantically informed, uninformed, and unsuccessfully informed.
+The semantically informed condition consisted of objects that were presented with matching keywords and for which the participant responded with knowing what the object was or having an assumption.
+The uninformed condition consisted of objects that were presented with non-matching keywords and for which the participant responded with not knowing what the object was or having rather no assumption.
+The unsuccessfully informed condition consisted of objects that were presented with matching keywords but for which the participant responded with not knowing what the object was or having rather no assumption.
+The few objects that were presented with non-matching keywords but for which participants responded with knowing what the object was or having an assumption (i.e., an unsuccessfully uninformed condition) were dropped from all further analyses.
+This assignment of objects to semantic conditions (informed, uninformed, or unsuccesfully informed) was carried over from the insight phase to the other two phases (pre-insight and post-insight).
+This allowed us to test, on the one hand, if the objects differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic information acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).]{color="blue"}
 
@@
 # Results
+
+## Behavioral Data
+
+[We used participants' behavioral data to verify our experimental manipulation and to assign objects to different semantic conditions (see Materials and Methods).
+First we excluded an average of `r mean(objects_per_condition$Exclude_known)` objects per participant for which participants indicated that they knew the objects even before any keywords had been presented (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all objects).
+Next, `r mean(objects_per_condition$Informed)` objects per participant could be assigned to the semantically informed condition (i.e., matching keywords and a positive response; `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of all objects presented with matching keywords) and `r mean(objects_per_condition$Uninformed)` objects per participant could be assigned to the uninformed condition (i.e., non-matching keywords and a negative response; `r percent(mean(objects_per_condition$Uninformed) / 60, accuracy = 0.1)` of all objects presented with non-matching keywords).
+Finally, `r mean(objects_per_condition$Unsuccessful)` objects per participant could be assigned to the unsuccessfully informed condition (i.e., matching keywords but a negative response; `r percent(mean(objects_per_condition$Unsuccessful) / 60, accuracy = 0.1)` of all objects presented with matching keywords).]{color="blue"}
 

### 2023-01-31 manuscript.Rmd
Use lua filter for colored text

@@
 csl               : "manuscript_files/citation_style.csl"
-nocite: | 
-  @bentin1985
-  @kellenbach2000
 
@@
     latex_engine: xelatex
+    pandoc_args: ["--lua-filter=manuscript_files/color_text.lua"]
 
@@
   - \usepackage{setspace}
-  - \usepackage{xcolor}
-  - \definecolor{pantone}{HTML}{26629d}
 ---
@@
 Does our perception of an object change once we discover what function it serves?
-We showed human participants (*n* = 48) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in \textcolor{pantone}{uninformed} perception.
+We showed human participants (*n* = 48) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in [uninformed]{color="blue"} perception.
 We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-We found that semantically informed as compared to \textcolor{pantone}{uninformed} perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
+We found that semantically informed as compared to [uninformed]{color="blue"} perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
 When the same objects were presented once more without any information, the N400 and event-related power effects persisted, and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
@@
 To answer this question, we measured ERPs in response to unfamiliar objects directly while participants gained a semantic understanding of their function.
-We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, and the other half together with non-matching keywords, \textcolor{pantone}{thus preventing participants from understanding what kind of object they were viewing}.
+We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, and the other half together with non-matching keywords, [thus preventing participants from understanding what kind of object they were viewing]{color="blue"}.
 We then presented the same objects again to test for downstream effects of semantic information.
@@
 These served as filler stimuli of no interest.
-The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; \textcolor{pantone}{see Supplementary Table 1}).
+The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; [see Supplementary Table 1]{color="blue"}).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; \textcolor{pantone}{see Supplementary Table 1}).
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; [see Supplementary Table 1]{color="blue"}).
 As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
 The matching keywords were expected to induce semantically informed perception, that is, participants suddenly understanding what kind of object they were viewing.
-The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically \textcolor{pantone}{uninformed}.
+The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically [uninformed]{color="blue"}.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to \textcolor{pantone}{uninformed} perception) to an equal number of participants.
+This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to [uninformed]{color="blue"} perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
@@
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
-In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to \textcolor{pantone}{uninformed} perception.
+In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to [uninformed]{color="blue"} perception.
 In the post-insight phase, the same objects were presented again without keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus \textcolor{pantone}{uninformed} perception within the three different phases.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus [uninformed]{color="blue"} perception within the three different phases.
 Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
@@
 
-In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to \textcolor{pantone}{uninformed} perception).
+In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to [uninformed]{color="blue"} perception).
 Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
@@
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
-All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the \textcolor{pantone}{uninformed} condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
+All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the [uninformed]{color="blue"} condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
 We determined the most parsimonious random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
@@
 
-To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the \textcolor{pantone}{uninformed} condition within the pre-insight, insight, and post-insight phases.
+To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the [uninformed]{color="blue"} condition within the pre-insight, insight, and post-insight phases.
 This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for three separate tests.
@@
 For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, and post-insight).
-First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the \textcolor{pantone}{uninformed} condition for each participant.
+First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the [uninformed]{color="blue"} condition for each participant.
 We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they occurred at neighboring time points, frequencies, or channels.
@@
 The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
-\textcolor{pantone}{The experimental stimuli (object images and keywords) and} the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
+[The experimental stimuli (object images and keywords) and]{color="blue"} the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
 
@@
 Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or \textcolor{pantone}{uninformed}), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed or [uninformed]{color="blue"}), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
@@
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the \textcolor{pantone}{uninformed} condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$p_value))` (see Figure 1B--D).
-This was expected given that the critical keywords (leading either to semantically informed perception or \textcolor{pantone}{uninformed} perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the [uninformed]{color="blue"} condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$p_value))` (see Figure 1B--D).
+This was expected given that the critical keywords (leading either to semantically informed perception or [uninformed]{color="blue"} perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
 
-In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically \textcolor{pantone}{uninformed}.
+In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically [uninformed]{color="blue"}.
 Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`.
@@
 
-In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and \textcolor{pantone}{uninformed} perception within each of the three phases of the experiment.
+In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and [uninformed]{color="blue"} perception within each of the three phases of the experiment.
 Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 2), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
@@
 (ref:fig2-caption) Time-frequency results for the insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the \textcolor{pantone}{uninformed} condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
 Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`).
@@
 (ref:fig3-caption) Time-frequency results for the post-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the \textcolor{pantone}{uninformed} condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
 Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`).
@@
 
-\textcolor{pantone}{One could argue that the effects presented here might be reducible to more basic mechanisms such as semantic priming.
+[One could argue that the effects presented here might be reducible to more basic mechanisms such as semantic priming.
 Indeed, the keywords that were presented before each object in the semantically informed condition were chosen such that they matched the function of the object and often had a direct relationship to certain visual features of the object (see Supplementary Table 1).
-This might have induced semantic priming, which is supported by the reduction in N400 amplitudes in response to ojects in the semantically informed condition, as in previous priming studies (e.g., Bentin et al., 1985; Kellenbach et al., 2000).
+This might have induced semantic priming, which is supported by the reduction in N400 amplitudes in response to ojects in the semantically informed condition, as in previous priming studies [e.g., @bentin1985; @kellenbach2000].
 However, there are at least two arguments why semantic priming cannot account for our main findings, that is, the influence of semantic information on the early P1 and N170 components.
-First, for both of these components, ERP amplitudes were \textit{enlarged} (i.e., more positive for the P1 component and more negative for the N170) during semantically informed perception, whereas an account based on semantic priming would have predicted \textit{reduced} ERP amplitudes.
+First, for both of these components, ERP amplitudes were *enlarged* (i.e., more positive for the P1 component and more negative for the N170) during semantically informed perception, whereas an account based on semantic priming would have predicted *reduced* ERP amplitudes.
 Second, these effects were not just observed when comparing semantically informed perception (with matching keywords) and uninformed perception (with non-matching keywords), but also when comparing semantically informed perception with unsucessfully informed perception.
 Whereas priming might have been present in the first comparison, in the second comparison all objects were preceded by keywords that matched the function of the object to a similar degree.
-The fact that P1 and N170 amplitudes still differed between these two conditions makes it unlikely that the semantic effects that we have found are fully reducible to priming.}
+The fact that P1 and N170 amplitudes still differed between these two conditions makes it unlikely that the semantic effects that we have found are fully reducible to priming.]{color="blue"}
 
@@
 (ref:figs1-caption) Time-frequency results for the pre-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the \textcolor{pantone}{uninformed} condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
 A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`).

### 2023-01-31 manuscript_files/helper_functions.R
Fix usage of models in Figure 1

@@ -258,7 +258,7 @@ plot_fig1b <- function(evokeds, config, channel_locations, models) {
 
   # Loop over ERP components of interest
   components <- config$components
-  components$model <- models
+  components$model <- models[components$name]
   pmap(components, function(name, tmin, tmax, roi, model) {
 
     # Loop over phases of the experiment

### 2023-02-07 manuscript.Rmd
Fix ICA description

@@
 First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
-Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a low-pass filtered copy of the data (cutoff = 1 Hz).
+Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a high-pass filtered copy of the data (cutoff = 1 Hz).
 A variable number of components per participant were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (mean = `r mean(unlist(config$auto_ica_n_components))` components, range `r min(unlist(config$auto_ica_n_components))`--`r max(unlist(config$auto_ica_n_components))`).

### 2023-02-12 manuscript.Rmd
Add first draft for rating analysis

@@
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
+
+```{r, ratings}
+options(rgl.useNULL = TRUE)
+load(here(data_dir, "ratings", "dewak100k_lsa.rda"))
+
+rating <- read_csv(
+  here(data_dir, "ratings", "rating_data.csv"),
+  col_types = cols(), locale = locale(encoding = "latin1")
+)
+
+rating_n <- nrow(rating)
+
+rating_substantives <- select(rating, S001_01:S242_01)
+rating_verbs <- select(rating, V001_01:V242_01)
+
+keywords <- read_csv(here("materials", "keywords.csv"), col_types = cols()) %>%
+  mutate(
+    match_ger = str_c(match_noun_ger, ", ", match_verb_ger),
+    match_en = str_c("{[", match_noun_en, ", ", match_verb_en, "]}"),
+    nonmatch_ger = str_c(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
+    nonmatch_en = str_c("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
+  )
+
+keywords_for_rating <- keywords %>%
+  arrange(familiarity, filename) %>%
+  select(item_id, filename, match_ger, nonmatch_ger) %>%
+  replicate(rating_n, ., simplify = FALSE) %>%
+  bind_rows()
+
+rating_cosine <-
+  map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
+  mutate(participant_id = rating$CASE) %>%
+  pivot_longer(
+    cols = -participant_id, names_to = "question_id", values_to = "response"
+  ) %>%
+  bind_cols(keywords_for_rating, .) %>%
+  filter(response != "NA NA") %>%
+  rowwise() %>%
+  mutate(
+    across(c(match_ger, nonmatch_ger, response), str_to_lower),
+    cosine_match = LSAfun::costring(match_ger, response, dewak100k_lsa),
+    cosine_nonmatch = LSAfun::costring(nonmatch_ger, response, dewak100k_lsa),
+    cosine_diff = cosine_match - cosine_nonmatch
+  )
+
+write_excel_csv(rating_cosine, here(output_dir, "rating_results.csv"))
+
+# sum(is.na(rating_cosine$cosine_diff))
+# t.test(rating_cosine$cosine_diff)
+
+# model_rating <- lmerTest::lmer(diff_cosine ~ 1 + (1 | participant_id), rating_cosine)
+```
 
@@
 # Print table of materials
-read_csv(here("materials", "keywords.csv"), col_types = cols()) %>%
-  mutate(
-    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
-    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
-    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
-    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
-  ) %>%
+keywords %>%
   transmute(

### 2023-02-23 manuscript.Rmd
Add rating cosine results

--- 2023-02-07 manuscript.Rmd
@@
 data_dir <- here("data")
+rating_dir <- here(data_dir, "ratings")
 files_dir <- here("manuscript_files")
 output_dir <- here("output")
-report_dir <- here("output/qc_reports")
+report_dir <- here(output_dir, "qc_reports")
 
@@
 run <- list(
+  rating_semantic_analysis = FALSE,
   eeg_processing = FALSE,
@@
 
-For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; [see Supplementary Table 1]{color="blue"}).
+For each unfamiliar object, we created a pair of German keywords (a noun and a verb), describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; [see Supplementary Table 1]{color="blue"}).
 As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
@@
 
+```{r, ratings}
+# Read table of object stimuli + keywords for the main experiment
+keywords <- read_csv(
+  here("materials", "keywords.csv"),
+  col_types = cols(
+    familiarity = col_factor(levels = c("familiar", "unfamiliar")),
+    item_id = col_factor()
+  )
+) %>%
+  mutate(
+    match = str_c(match_noun, ", ", match_verb),
+    match_en = str_c("{[", match_noun_en, ", ", match_verb_en, "]}"),
+    nonmatch = str_c(nonmatch_noun, ", ", nonmatch_verb),
+    nonmatch_en = str_c("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
+  )
+
+# (Re-)do latent semantic analysis of online rating study data
+rating_file <- here(output_dir, "rating.csv")
+if (run$rating_semantic_analysis) {
+  # Load pre-trained German word2vec embedding
+  word2vec <- load_word2vec(rating_dir)
+
+  # Read online rating study data
+  rating_raw <- read_csv(
+    here(data_dir, "ratings", "rating_data.csv"),
+    col_types = cols(), locale = locale(encoding = "latin1")
+  )
+  rating_substantives <- select(rating_raw, S001_01:S242_01)
+  rating_verbs <- select(rating_raw, V001_01:V242_01)
+
+  # Prepare a copy of the keywords to add to the rating study data
+  rating_n <- nrow(rating_raw)
+  keywords_for_rating <- keywords %>%
+    arrange(familiarity, filename) %>%
+    select(item_id, familiarity, filename, match, nonmatch) %>%
+    replicate(rating_n, ., simplify = FALSE) %>%
+    bind_rows()
+
+  # Compute cosine similarities between rating study responses and keywords
+  rating <-
+    map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
+    mutate(participant_id = rating_raw$CASE) %>%
+    pivot_longer(
+      -participant_id,
+      names_to = "question_id", values_to = "response"
+    ) %>%
+    bind_cols(keywords_for_rating, .) %>%
+    pivot_longer(
+      c(match, nonmatch),
+      names_to = "condition", values_to = "keywords"
+    ) %>%
+    mutate(across(c(keywords, response), str_to_lower)) %>%
+    mutate(cosine = compute_cosine(keywords, response, word2vec))
+
+  # Save to file
+  write_csv(rating, rating_file)
+}
+
+# Read the rating study results incl. cosine similarities
+rating <- read_csv(
+  rating_file,
+  col_types = cols(item_id = col_factor(), participant_id = col_factor())
+) %>%
+  filter(!is.na(cosine)) %>%
+  mutate(
+    fam_condition = paste(familiarity, condition) %>%
+      factor(
+        levels = c("familiar match", "unfamiliar match", "unfamiliar nonmatch"),
+        labels = c("familiar", "matching", "nonmatching")
+      )
+  )
+
+# Compare cosine similarities between object conditions
+contrasts(rating$fam_condition) <- contr.sdif(3)
+model_rating <- lmer(
+  cosine ~ fam_condition +
+    (fam_condition | participant_id) +
+    (1 | item_id),
+  data = rating,
+  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
+)
+(summary_rating <- summary(model_rating))
+
+# Compute condition means and pairwise contrasts
+emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
+emm_rating <- emmeans(
+  model_rating,
+  specs = consec ~ fam_condition,
+  rev = TRUE,
+  adjust = "bonferroni"
+)
+rating_means <- as.data.frame(emm_rating$emmeans)
+rating_contrasts <- as.data.frame(emm_rating$contrasts) %>%
+  rename(t_value = `t.ratio`, p_value = `p.value`)
+
+# rating_pairwise <- rating$participant_id %>%
+#   unique() %>%
+#   combn(m = 2) %>%
+#   data.frame() %>%
+#   map_dfr(function(pair) {
+#     id_1 <- pair[1]
+#     id_2 <- pair[2]
+#     response_1 <- filter(rating, participant_id == id_1)$response
+#     response_2 <- filter(rating, participant_id == id_2)$response
+#     tibble(
+#       item_id = keywords$item_id,
+#       familiarity = keywords$familiarity,
+#       filename = keywords$filename,
+#       pair_id = str_c(id_1, id_2, sep = "_"),
+#       participant_id_1 = id_1,
+#       participant_id_2 = id_2,
+#       response_1,
+#       response_2,
+#       cosine = compute_cosine(response_1, response_2, word2vec)
+#     )
+#   })
+
+# write_csv(rating_pairwise, here(output_dir, "rating_pairwise.csv"))
+
+# mod_pairwise <- lmer(
+#   cosine ~ familiarity + (familiarity | pair_id) + (1 | filename),
+#   data = rating_pairwise
+# )
+# (summary_pairwise <- summary(mod_pairwise))
+
+# Rmisc::summarySEwithin(
+#   data = rating_pairwise, measurevar = "cosine", withinvars = "familiarity",
+#   idvar = "pair_id", na.rm = TRUE
+# ) %>%
+#   ggplot(aes(x = familiarity, y = cosine, color = familiarity)) +
+#   geom_violin(data = rating_pairwise) +
+#   coord_cartesian(ylim = c(0.0, 1.0)) +
+#   geom_pointrange(aes(ymin = cosine - se, ymax = cosine + se)) +
+#   theme_classic()
+```
+
+As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
+We used latent semantic analysis with a word2vec embedding pre-trained on the German Wikipedia (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) to estimate semantic distances between these participant-generated keywords and the keywords used in our experiment (Supplementary Methods; Supplementary Figures 1 and 2).
+In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± SE = `r filter(rating_means, fam_condition == "familiar")$emmean` ± `r filter(rating_means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_means, fam_condition == "matching")$emmean` ± `r filter(rating_means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
+In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r filter(rating_contrasts, contrast == "matching - nonmatching")$p_value` (linear mixed-effects model).
+
 ## Experimental Design
 
-The experiment consisted of three phases (see Figure 1A).
+The main EEG experiment consisted of three phases (see Figure 1A).
 In the *pre-insight* phase, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
@@
 
+```{r, ratingfigs}
+rating %>%
+  filter(!is.na(cosine)) %>%
+  mutate(condition_comb = paste(familiarity, condition)) %>%
+  ggplot(aes(x = condition_comb, y = cosine, color = condition_comb)) +
+  geom_violin() +
+  geom_boxplot(width = 0.2) +
+  scale_color_manual(values = c("#984ea3", "#e41a1c", "#377eb8")) +
+  labs(x = NULL, y = "Cosine distance") +
+  coord_cartesian(ylim = c(0.0, 1.0)) +
+  theme_classic() +
+  theme(legend.position = "none")
+
+rating %>%
+  filter(
+    !is.na(cosine) & familiarity == "unfamiliar" & condition == "match"
+  ) %>%
+  select(item_id, condition, cosine) %>%
+  group_by(item_id, condition) %>%
+  summarize(
+    mean = mean(cosine),
+    sd = sd(cosine),
+    n = n(),
+    se = sd / sqrt(n),
+    .groups = "drop"
+  ) %>%
+  mutate(item_id = fct_reorder(item_id, desc(mean))) %>%
+  # filter(mean > 0.7) %>%
+  ggplot(
+    aes(
+      x = item_id, y = mean, color = condition,
+      ymin = mean - se, ymax = mean + se
+    )
+  ) +
+  geom_pointrange() +
+  labs(x = "Stimulus ID", y = "Cosine distance to keywords") +
+  theme_classic() +
+  theme(
+    axis.text.x = element_text(angle = 90),
+    legend.position = "none"
+  )
+```
+
 ```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figs1-caption)"}

### 2023-02-23 manuscript_files/helper_functions.R

@@ -627,3 +627,49 @@ plot_tfr_topos <- function(tfr_grand_ave,
 
 # Helper function to create print degrees of freedom
 print_dof <- function(x) format(round(x), big.mark = ",")
+
+# Helper function to load pre-trained word2vec model from deepset
+# See https://www.deepset.ai/german-word-embeddings
+load_word2vec <- function(directory_path) {
+  vectors_file <- here::here(directory_path, "vectors.txt")
+  if (!file.exists(vectors_file)) {
+    options(timeout = 1800)
+    vectors_url <- "https://int-emb-word2vec-de-wiki.s3.eu-central-1.amazonaws.com/vectors.txt"
+    download.file(vectors_url, vectors_file)
+  }
+  word2vec <- as.matrix(read.table(vectors_file, row.names = 1))
+  rownames(word2vec) <- purrr::map_chr(
+    rownames(word2vec),
+    ~stringr::str_sub(unescape_unicode(.x), start = 3, end = -2)
+  )
+  return(word2vec)
+}
+
+# Helper functions to decode unicode characters
+unescape_unicode <- function(x) {
+  stopifnot(is.character(x) && length(x) == 1)
+  m <- gregexpr("(\\\\)+x[0-9a-z]{2}", x, ignore.case = TRUE)
+  if (m[[1]][1] > -1) {
+    p <- vapply(regmatches(x, m)[[1]], function(txt){
+      gsub(
+        "\\", "\\\\", parse(text = paste0('"', txt, '"'))[[1]],
+        fixed = TRUE, useBytes = TRUE
+      )
+    }, character(1), USE.NAMES = FALSE)
+    regmatches(x, m) <- list(p)
+  }
+  x
+}
+
+# Helper function to compute element-wise cosine distance between vectors
+compute_cosine <- function(x, y, tvectors) {
+  require(purrr)
+  options(rgl.useNULL = TRUE)
+  res_list <- map2(x, y, quietly(LSAfun::costring), tvectors)
+  map_dbl(res_list, function(res) {
+    cosine <- res$result
+    warning <- res$output
+    cosine[warning != ""] <- NA
+    cosine
+  })
+}

### 2023-02-25 manuscript.Rmd
Add rating cosine results

@@
 )
-(summary_rating <- summary(model_rating))
 
@@
 In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± SE = `r filter(rating_means, fam_condition == "familiar")$emmean` ± `r filter(rating_means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_means, fam_condition == "matching")$emmean` ± `r filter(rating_means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
-In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r filter(rating_contrasts, contrast == "matching - nonmatching")$p_value` (linear mixed-effects model).
+In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "matching - nonmatching")$p_value)` (linear mixed-effects model).
 
@@
 keywords %>%
+  filter(familiarity == "unfamiliar") %>%
   transmute(
@@
     item_id = as.character(item_id),
-    match = paste(match_ger, match_en, sep = "\n") %>%
+    match_translated = paste(match, match_en, sep = "\n") %>%
       kableExtra::linebreak(align = "l", linebreaker = "\n"),
-    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
+    nonmatch_translated = paste(nonmatch, nonmatch_en, sep = "\n") %>%
       kableExtra::linebreak(align = "l", linebreaker = "\n")

### 2023-02-26 manuscript.Rmd
Parse evoked conditions after pipeline update

@@
 # Read by-participant ERP averages and channel locations
-evokeds <- read_csv(here(output_dir, "ave.csv"))
+evokeds <- read_csv(here(output_dir, "ave.csv")) %>%
+  separate(label, into = c("phase", "condition"), sep = "/")
 
@@
 # Read grand-averaged power
-tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))
+tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv")) %>%
+  separate(label, into = c("phase", "condition"), sep = "/")
 

### 2023-02-26 manuscript.Rmd
Auto-formatting

@@
 read_log <- function(log_file) {
-
   # Read the file
@@
 if (run$eeg_processing) {
-
   # Process behavioral data
@@
 fit_mixed_models <- function(dep, formula, data) {
-
   # Modify the formula such that fixed effects are always retained
@@
 if (run$mixed_models) {
-
   # Fit the model for each ERP component
@@
 } else {
-
   # Read fitted models

### 2023-02-26 manuscript_files/helper_functions.R
Auto-formatting

@@ -493,7 +493,6 @@ plot_tfr_topos <- function(tfr_grand_ave,
                            fmin = 4,
                            fmax = 40,
                            fstep = 4) {
-
   # Load required packages
   require(dplyr)
   require(cowplot)
@@ -640,7 +639,7 @@ load_word2vec <- function(directory_path) {
   word2vec <- as.matrix(read.table(vectors_file, row.names = 1))
   rownames(word2vec) <- purrr::map_chr(
     rownames(word2vec),
-    ~stringr::str_sub(unescape_unicode(.x), start = 3, end = -2)
+    ~ stringr::str_sub(unescape_unicode(.x), start = 3, end = -2)
   )
   return(word2vec)
 }
@@ -650,7 +649,7 @@ unescape_unicode <- function(x) {
   stopifnot(is.character(x) && length(x) == 1)
   m <- gregexpr("(\\\\)+x[0-9a-z]{2}", x, ignore.case = TRUE)
   if (m[[1]][1] > -1) {
-    p <- vapply(regmatches(x, m)[[1]], function(txt){
+    p <- vapply(regmatches(x, m)[[1]], function(txt) {
       gsub(
         "\\", "\\\\", parse(text = paste0('"', txt, '"'))[[1]],
         fixed = TRUE, useBytes = TRUE

### 2023-02-27 manuscript.Rmd
Add Figure 2 for Informed - unsuccessful

@@
 
-(ref:fig1-caption) Experimental design and ERP results.
+(ref:fig1-caption) Experimental design and ERP results contrasting semantically informed perception and uninformed perception.
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
@@
 
+```{r, fig2, cache=!run$figures, fig.height=8.6, fig.cap="(ref:fig2-caption)"}
+# Create Figure 2
+plot_fig2(files_dir, evokeds, config, channel_locations, models)
+```
+
+(ref:fig2-caption) [ERP results contrasting semantically informed perception and unsuccessfully informed perception.
+***A***, Assignment of objects to conditions based on participants' response in the insight phase of the experiment to unfamiliar objects presented with matching keywords.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus perception within the three different phases.
+Semantically informed perception was associated with more negative amplitudes in the N170 component and less negative amplitudes in the N400 component during the insight phase.
+The time windows and channels for quantifying the ERP components are highlighted by the gray areas in the ERP waveforms and by the black markers on the scalp topographies, respectively.
+Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
+Ampl. = amplitude.\newline
+\*\*\* $p_\text{corr} < .001$.]{color="blue"}
+
 In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically [uninformed]{color="blue"}.
@@
 In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and [uninformed]{color="blue"} perception within each of the three phases of the experiment.
-Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 2), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
@@
 
-```{r, fig2, cache=!run$figures, fig.height=11, fig.cap="(ref:fig2-caption)"}
+```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:fig3-caption)"}
 # Create topographic plots for event-related power in the insight phase
@@
 
-(ref:fig2-caption) Time-frequency results for the insight phase.
+(ref:fig3-caption) Time-frequency results for the insight phase.
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
@@
 
-```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:fig3-caption)"}
+```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:fig4-caption)"}
 # Create topographic plots for event-related power in the post-insight phase
@@
 
-(ref:fig3-caption) Time-frequency results for the post-insight phase.
+(ref:fig4-caption) Time-frequency results for the post-insight phase.
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
@@
   p_cluster = p_cluster,
-  condition_plus = "Informed",
-  condition_minus = "Unsuccessful",
-  title_conditions = "Informed - failed"
+  conditions = c("Informed", "Unsuccessful")
 )

### 2023-02-27 manuscript_files/helper_functions.R

@@ -1,16 +1,12 @@
-# Define color scheme
-aha_colors <- c("#ca0020", "#0571b0")
-stimulus_bg_color <- "#a9d9ff"
-
-# Helper function to create Figure 1A (trial structure)
-plot_fig1a <- function(files_dir) {
-
+# Helper function to create trial structure plots (Figure 1A)
+plot_fig1a <- function(files_dir, condition_colors) {
   # Make sure that packages are loaded
   require(tidyverse)
   require(cowplot)
 
   # Trial structure
   example_stim <- magick::image_read(here::here("example_stimuli", "103.png"))
+  stim_bg_color <- "#a9d9ff"
   ggplot() +
     coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
     theme_void() +
@@ -29,23 +25,23 @@ plot_fig1a <- function(files_dir) {
     # Squares
     annotate(
       geom = "rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75,
-      color = "black", fill = stimulus_bg_color
+      color = "black", fill = stim_bg_color
     ) +
     annotate(
       geom = "rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65,
-      color = aha_colors[2], fill = stimulus_bg_color
+      color = condition_colors[2], fill = stim_bg_color
     ) +
     annotate(
       geom = "rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89,
-      color = aha_colors[1], fill = stimulus_bg_color
+      color = condition_colors[1], fill = stim_bg_color
     ) +
     annotate(
       geom = "rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79,
-      color = "black", fill = stimulus_bg_color
+      color = "black", fill = stim_bg_color
     ) +
     annotate(
       geom = "rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81,
-      color = "black", fill = stimulus_bg_color
+      color = "black", fill = stim_bg_color
     ) +
     annotate(
       geom = "text", x = -27, y = 65.3, label = "+", size = 20 / .pt,
@@ -53,11 +49,11 @@ plot_fig1a <- function(files_dir) {
     ) +
     annotate(
       geom = "text", x = -9, y = 55, label = "message\nsignaling",
-      family = "Helvetica", color = aha_colors[2]
+      family = "Helvetica", color = condition_colors[2]
     ) +
[…]

### 2023-03-02 manuscript.Rmd
Shorten long code lines
Make sure all keywords are in word2vec

@@
     ) %>%
-    mutate(across(c(keywords, response), str_to_lower)) %>%
-    mutate(cosine = compute_cosine(keywords, response, word2vec))
+    mutate(
+      across(c(keywords, response), str_to_lower),
+      keywords = str_replace_all(
+        keywords, c(
+          aufstemmen = "aufbrechen",
+          tierkäfig = "käfig",
+          wegkehren = "kehren",
+          verühren = "rühren",
+          schraubenschlüssel = "werkzeug",
+          verquirlen = "rühren",
+          tackern = "tacker",
+          sprengstoffexplosion = "explosion",
+          tankfüllstand = "füllstand",
+          tonpott = "tongefäß",
+          eierkarton = "eier verpackung",
+          musikgerät = "musikinstrument",
+          türgelenk = "scharnier",
+          telegrafieren = "telegraf",
+          sternenbilder = "sternbild",
+          aufspulen = "aufwickeln",
+          häckseln = "zerkleinern",
+          `mikroskop-proben` = "mikroskop proben",
+          streckenmaß = "maß",
+          windgeschwindigkeit = "windstärke",
+          nussöl = "nuss öl",
+          entkörnen = "entkernen",
+          katzenklo = "katze klo",
+          kutschrad = "kutsche rad"
+        )
+      ),
+      response = str_replace_all(
+        response, c(
+          aufhebeln = "aufbrechen",
+          föhnen = "föhn",
+          kasette = "kassette",
+          aufkehren = "kehren",
+          tackern = "tacker",
+          sprayapparat = "spray apparat",
+          anästhesieren = "betäuben",
+          reaktionsspiel = "reaktion spiel",
+          mulchgerät = "mulch gerät",
+          makierung = "markierung",
+          wissenschaftlich = "wissenschaft",
+          spannwerkzeug = "werkzeug",
+          wärmestab = "wärme stab",
+          ampfel = "ampel",
+          scheere = "schere",
+          pflägen = "pflügen",
+          knetten = "kneten",
+          pfandkuchen = "pfannkuchen",
+          anmacher = "anmachen",
+          injezieren = "injizieren",
+          telfon = "telefon",
+          beschrifter = "beschriften",
+          aufbewaren = "aufbewahren",
+          spähne = "späne",
+          separator = "trennen",
+          stämpfer = "stampfen",
+          fliente = "flinte",
+          tromphete = "trompete",
+          makieren = "markieren",
+          stöbseln = "stöpsel",
+          hiernwellen = "gehirnwellen",
+          kartofeln = "kartoffeln",
+          vaccum = "vakuum",
+          saubermachen = "putzen",
+          ankeln = "anker",
+          schuessel = "schüssel",
+          `zangen\\\\` = "zange",
+          kleiderbuegel = "kleiderbügel",
+          buerste = "bürste",
+          buersten = "bürsten",
+          druecken = "drücken",
+          obstscheider = "obst schneiden",
+          àumachen = "ausmachen",
+          bieroeffner = "flaschenöffner",
+          oeffnen = "öffnen",
+          giesskanne = "gießkanne",
+          gluehbirne = "glühbirne",
+          schettem = "manschetten",
+          kurzhantel = "kurzhanteln",
+          tierekiste = "tiere kiste",
+          kaffekocher = "kaffeemaschine",
+          kinderwaagen = "kinderwagen",
+          klobürste = "toilette bürste",
+          orangenpresser = "orangen presse",
+          foodmixer = "essen mixer",
+          schuessel = "schüssel",
+          naehen = "nähen",
+          teigwalze = "nudelholz",
+          pffefern = "pfeffer",
+          maehen = "mähen",
+          gesichtsbürste = "gesicht bürste",
+          regenchirm = "regenschirm",
+          kaesegratin = "käse gratin",
+          slotsmaschine = "slot maschine",
+          piggybank = "sparschwein",
+          stampen = "kleben",
+          arztwekzeug = "arzt werkzeug",
+          gradskala = "grad skala",
+          trichten = "trichter",
+          spulsmaschine = "spülmaschine",
+          zahnbrueste = "zahnbürste",
+          bruesten = "bürsten",
+          foltermaschine = "folter maschine",
+          bieröffner = "flaschenöffner",
+          oeffnen = "öffnen",
+          pizzacutter = "pizza schneider",
+          kerzestande = "kerzenständer",
+          naehen = "nähen",
+          geruest = "gerüst",
+          nagelschneider = "nagel schere",
+          burste = "bürste",
+          bursten = "bürsten",
+          loefel = "löffel",
+          hamsterspielzeug = "hamster spielzeug",
+          breadboard = "schneide brett",
+          druceken = "drücken",
+          nussknacnker = "nussknacker",
+          ueberwachen = "überwachen",
+          trainingsmaschine = "training maschine",
+          padeln = "paddeln",
+          schäumer = "aufschäumen",
+          aufhanger = "aufhänger",
+          hangt = "hängen",
+          `eier-guillotine` = "eier messer",
+          ruhrgerat = "rührgerät",
+          katzentrager = "katzen träger",
+          hinzufugen = "hinzufügen",
+          kuchenform = "backform",
+          nagelfeile = "nagel feile",
+          fondues = "fondue",
+          zuhoren = "zuhören",
+          rasenmaher = "rasenmäher",
+          geschlitzter = "schlitz",
+          breifmarke = "briefmarke",
+          bimmeln = "läuten",
+          rasma = "",
+          kassete = "kassette",
+          nudelmaschine = "nudel maschine",
+          ruhrer = "rührer",
+          feuerloscher = "feuerlöscher",
+          entfernungsmesser = "entfernung messer",
+          heißluftpistole = "heißluft pistole",
+          schuhlöffel = "schuhe anziehen",
+          uben = "üben",
+          naturlich = "natürlich",
+          schißen = "schießen",
+          rührgerät = "mixer",
+          aufkehren = "kehren",
+          rausziehen = "herausziehen",
+          `mini-meißel` = "mini meißel",
+          kaffeemischer = "kaffee mischer",
+          nachttischlampe = "nachttisch lampe",
+          arbeitsschlüssel = "arbeit schlüssel",
+          `boom-box` = "lautsprecher",
+          feststampfen = "fest stampfen",
+          `casino-maschine` = "casino maschine",
+          `herzfrequenz-test` = "herzfrequenz test",
+          zaichnen = "zeichnen",
+          schneidin = "schneiden",
+          vergleichsmaschine = "vergleich maschine",
+          rosenabzeichen = "rosen abzeichen",
+          `dummy-stecker` = "dummy stecker",
+          `post-punk-sanduhr` = "post punk sanduhr",
+          schneidemaschine = "schneiden maschine",
+          fusszeile = "fußzeile",
+          gartenlampe = "garten lampe",
+          trenneimer = "trennen eimer",
+          fußabstreifer = "fußmatte",
+          wichten = "gewicht",
+          perlenständer = "perlen ständer",
+          briefmarker = "briefmarke",
+          `elektronische-schaltung` = "elektronische schaltung",
+          fläschchenheizung = "flächen heizung",
+          elektrodrucker = "elektro drucker",
+          metalllinse = "metall linse",
+          kugelheizung = "kugel heizung",
+          abschrauber = "abschrauben",
+          `mini-korb` = "mini korb",
+          elektronenrechner = "elektronen rechner",
+          spießfaum = "spieß",
+          tierträger = "tier träger",
+          rührgerät = "rührgerät",
+          kuchenform = "backform",
+          friteuse = "fritteuse",
+          `ein-` = "ein",
+          greigfen = "greifen",
+          zerknittern = "falten bekommen",
+          salatzange = "salat zange",
+          wwrm = "wurm",
+          duschwasser = "dusche wasser",
+          verbreitene = "verbreiten",
+          aufpieksen = "anstechen",
+          restriktieren = "einschränken",
+          rückgeld = "wechselgeld",
+          aufkehren = "zusammenkehren",
+          bratgut = "grillgut",
+          bepinseln = "bestreichen",
+          verquirlen = "vermischen",
+          temparatur = "temperatur",
+          aufspulen = "aufwickeln",
+          elekronik = "elektronik",
+          festnieten = "fest nieten",
+          festspannen = "fest spannen",
+          hebelkräfte = "hebelkraft",
+          meiseln = "meißeln",
+          betäüben = "betäuben",
+          verschraüben = "verschrauben",
+          schraüben = "schrauben",
+          seperator = "trennen",
+          schraübendreher = "schraubendreher",
+          gegewicht = "gewicht"
+        )
+      ),
+      cosine = compute_cosine(keywords, response, word2vec)
+    )
 
@@
 }
+
+# # Test if all keywords and responses are in the embedding
+# for (keywords in c(unique(rating$keywords), unique(rating$response))) {
+#   if (!is.na(keywords)) {
+#     for (word in (str_split(keywords, pattern = " |, ")[[1]])) {
+#       if (!(word %in% rownames(word2vec))) {
+#         cat(paste0(word, ' = "",\n'))
+#       }
+#     }
+#   }
+# }
 
@@
     average_by = list(
-      pre_informed = "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
-      pre_uninformed = "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
-      pre_unsuccessful = "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
-      ins_informed = "phase == 'Insight' & condition == 'Informed' & rt > 200",
-      ins_uninformed = "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
-      ins_unsuccessful = "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
-      post_informed = "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
-      post_uninformed = "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
-      post_unsuccessful = "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
+      pre_informed =
+        "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
+      pre_uninformed =
+        "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
+      pre_unsuccessful =
+        "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
+      ins_informed =
+        "phase == 'Insight' & condition == 'Informed' & rt > 200",
+      ins_uninformed =
+        "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
+      ins_unsuccessful =
+        "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
+      post_informed =
+        "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
+      post_uninformed =
+        "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
+      post_unsuccessful =
+        "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
     ),

### 2023-03-02 manuscript.Rmd
Add cosine similarities to models

@@
 
+# Compute each item's average cosine distance across participants
+cosines <- rating %>%
+  group_by(item_id) %>%
+  summarize(cosine = mean(cosine)) %>%
+  mutate(cosine = scale(cosine))
+
 # rating_pairwise <- rating$participant_id %>%
@@
   ))
-))
+)) %>%
+  # Add cosine similarities (i.e., predictability of keywords) from rating study
+  left_join(cosines, by = "item_id")
 
@@
   # Fit the model for each ERP component
-  form_erps <- ~ phase * condition +
+  form_erps <- ~ phase * condition + cosine +
     (phase * condition | participant_id) +
@@
   # Fit an additional control analysis model for the alpha/beta power
-  form_alpha_beta <- ~ phase * condition + rt +
+  form_alpha_beta <- ~ phase * condition + rt + cosine +
     (phase * condition | participant_id) +

### 2023-03-02 manuscript.Rmd
Update pipeline call

--- 2023-02-27 manuscript.Rmd
@@
 data_dir <- here("data")
-rating_dir <- here(data_dir, "ratings")
 files_dir <- here("manuscript_files")
 output_dir <- here("output")
-report_dir <- here(output_dir, "qc_reports")
+report_dir <- here("output/qc_reports")
 
@@
 run <- list(
-  rating_semantic_analysis = FALSE,
   eeg_processing = FALSE,
@@
 
-For each unfamiliar object, we created a pair of German keywords (a noun and a verb), describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; [see Supplementary Table 1]{color="blue"}).
+For each unfamiliar object, a pair of German keywords (a noun and a verb) was selected, describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; [see Supplementary Table 1]{color="blue"}).
 As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
@@
 
-```{r, ratings}
-# Read table of object stimuli + keywords for the main experiment
-keywords <- read_csv(
-  here("materials", "keywords.csv"),
-  col_types = cols(
-    familiarity = col_factor(levels = c("familiar", "unfamiliar")),
-    item_id = col_factor()
-  )
-) %>%
-  mutate(
-    match = str_c(match_noun, ", ", match_verb),
-    match_en = str_c("{[", match_noun_en, ", ", match_verb_en, "]}"),
-    nonmatch = str_c(nonmatch_noun, ", ", nonmatch_verb),
-    nonmatch_en = str_c("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
-  )
-
-# (Re-)do latent semantic analysis of online rating study data
-rating_file <- here(output_dir, "rating.csv")
-if (run$rating_semantic_analysis) {
-  # Load pre-trained German word2vec embedding
-  word2vec <- load_word2vec(rating_dir)
-
-  # Read online rating study data
-  rating_raw <- read_csv(
-    here(data_dir, "ratings", "rating_data.csv"),
-    col_types = cols(), locale = locale(encoding = "latin1")
-  )
-  rating_substantives <- select(rating_raw, S001_01:S242_01)
-  rating_verbs <- select(rating_raw, V001_01:V242_01)
-
-  # Prepare a copy of the keywords to add to the rating study data
-  rating_n <- nrow(rating_raw)
-  keywords_for_rating <- keywords %>%
-    arrange(familiarity, filename) %>%
-    select(item_id, familiarity, filename, match, nonmatch) %>%
-    replicate(rating_n, ., simplify = FALSE) %>%
-    bind_rows()
-
-  # Compute cosine similarities between rating study responses and keywords
-  rating <-
-    map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
-    mutate(participant_id = rating_raw$CASE) %>%
-    pivot_longer(
-      -participant_id,
-      names_to = "question_id", values_to = "response"
-    ) %>%
-    bind_cols(keywords_for_rating, .) %>%
-    pivot_longer(
-      c(match, nonmatch),
-      names_to = "condition", values_to = "keywords"
-    ) %>%
-    mutate(across(c(keywords, response), str_to_lower)) %>%
-    mutate(cosine = compute_cosine(keywords, response, word2vec))
-
-  # Save to file
-  write_csv(rating, rating_file)
-}
-
-# Read the rating study results incl. cosine similarities
-rating <- read_csv(
-  rating_file,
-  col_types = cols(item_id = col_factor(), participant_id = col_factor())
-) %>%
-  filter(!is.na(cosine)) %>%
-  mutate(
-    fam_condition = paste(familiarity, condition) %>%
-      factor(
-        levels = c("familiar match", "unfamiliar match", "unfamiliar nonmatch"),
-        labels = c("familiar", "matching", "nonmatching")
-      )
-  )
-
-# Compare cosine similarities between object conditions
-contrasts(rating$fam_condition) <- contr.sdif(3)
-model_rating <- lmer(
-  cosine ~ fam_condition +
-    (fam_condition | participant_id) +
-    (1 | item_id),
-  data = rating,
-  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
-)
-
-# Compute condition means and pairwise contrasts
-emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-emm_rating <- emmeans(
-  model_rating,
-  specs = consec ~ fam_condition,
-  rev = TRUE,
-  adjust = "bonferroni"
-)
-rating_means <- as.data.frame(emm_rating$emmeans)
-rating_contrasts <- as.data.frame(emm_rating$contrasts) %>%
-  rename(t_value = `t.ratio`, p_value = `p.value`)
-
-# rating_pairwise <- rating$participant_id %>%
-#   unique() %>%
-#   combn(m = 2) %>%
-#   data.frame() %>%
-#   map_dfr(function(pair) {
-#     id_1 <- pair[1]
-#     id_2 <- pair[2]
-#     response_1 <- filter(rating, participant_id == id_1)$response
-#     response_2 <- filter(rating, participant_id == id_2)$response
-#     tibble(
-#       item_id = keywords$item_id,
-#       familiarity = keywords$familiarity,
-#       filename = keywords$filename,
-#       pair_id = str_c(id_1, id_2, sep = "_"),
-#       participant_id_1 = id_1,
-#       participant_id_2 = id_2,
-#       response_1,
-#       response_2,
-#       cosine = compute_cosine(response_1, response_2, word2vec)
-#     )
-#   })
-
-# write_csv(rating_pairwise, here(output_dir, "rating_pairwise.csv"))
-
-# mod_pairwise <- lmer(
-#   cosine ~ familiarity + (familiarity | pair_id) + (1 | filename),
-#   data = rating_pairwise
-# )
-# (summary_pairwise <- summary(mod_pairwise))
-
-# Rmisc::summarySEwithin(
-#   data = rating_pairwise, measurevar = "cosine", withinvars = "familiarity",
-#   idvar = "pair_id", na.rm = TRUE
-# ) %>%
-#   ggplot(aes(x = familiarity, y = cosine, color = familiarity)) +
-#   geom_violin(data = rating_pairwise) +
-#   coord_cartesian(ylim = c(0.0, 1.0)) +
-#   geom_pointrange(aes(ymin = cosine - se, ymax = cosine + se)) +
-#   theme_classic()
-```
-
-As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
-We used latent semantic analysis with a word2vec embedding pre-trained on the German Wikipedia (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) to estimate semantic distances between these participant-generated keywords and the keywords used in our experiment (Supplementary Methods; Supplementary Figures 1 and 2).
-In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± SE = `r filter(rating_means, fam_condition == "familiar")$emmean` ± `r filter(rating_means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_means, fam_condition == "matching")$emmean` ± `r filter(rating_means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
-In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "matching - nonmatching")$p_value)` (linear mixed-effects model).
-
 ## Experimental Design
 
-The main EEG experiment consisted of three phases (see Figure 1A).
+The experiment consisted of three phases (see Figure 1A).
 In the *pre-insight* phase, after written informed consent had been obtained and the EEG had been prepared, all 240 familiar and unfamiliar objects were presented once in random order and without any keywords.
@@
 read_log <- function(log_file) {
+
   # Read the file
@@
 if (run$eeg_processing) {
+
   # Process behavioral data
@@
     average_by = list(
-      pre_informed = "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
-      pre_uninformed = "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
-      pre_unsuccessful = "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
-      ins_informed = "phase == 'Insight' & condition == 'Informed' & rt > 200",
-      ins_uninformed = "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
-      ins_unsuccessful = "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
-      post_informed = "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
-      post_uninformed = "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
-      post_unsuccessful = "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
+      `Pre-insight/Informed` =
+        "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
+      `Pre-insight/Uninformed` =
+        "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
+      `Pre-insight/Unsuccessful` =
+        "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
+      `Insight/Informed` =
+        "phase == 'Insight' & condition == 'Informed' & rt > 200",
+      `Insight/Uninformed` =
+        "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
+      `Insight/Unsuccessful` =
+        "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
+      `Post-insight/Informed` =
+        "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
+      `Post-insight/Uninformed` =
+        "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
+      `Post-insight/Unsuccessful` =
+        "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
     ),
@@
       c("Pre-insight/Informed", "Pre-insight/Uninformed"),
+      c("Pre-insight/Informed", "Pre-insight/Unsuccessful"),
       c("Insight/Informed", "Insight/Uninformed"),
+      c("Insight/Informed", "Insight/Unsuccessful"),
       c("Post-insight/Informed", "Post-insight/Uninformed"),
-      c("Insight/Informed", "Insight/Unsuccessful")
+      c("Post-insight/Informed", "Post-insight/Unsuccessful")
     ),
@@
     perm_tmax = 1.4,
-    n_jobs = 4
+    n_jobs = 8
   )
@@
 # Read by-participant ERP averages and channel locations
-evokeds <- read_csv(here(output_dir, "ave.csv")) %>%
-  separate(label, into = c("phase", "condition"), sep = "/")
+evokeds <- read_csv(here(output_dir, "ave.csv"))
 
@@
 # Read grand-averaged power
-tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv")) %>%
-  separate(label, into = c("phase", "condition"), sep = "/")
+tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))
 
@@
 fit_mixed_models <- function(dep, formula, data) {
+
   # Modify the formula such that fixed effects are always retained
@@
 if (run$mixed_models) {
+
   # Fit the model for each ERP component
@@
 } else {
+
   # Read fitted models
@@
 
-(ref:fig1-caption) Experimental design and ERP results contrasting semantically informed perception and uninformed perception.
+(ref:fig1-caption) Experimental design and ERP results.
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
@@
 First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
-Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a high-pass filtered copy of the data (cutoff = 1 Hz).
+Next, artifacts resulting from blinks and eye movements were removed via independent component analysis (ICA) on a low-pass filtered copy of the data (cutoff = 1 Hz).
 A variable number of components per participant were extracted from an initial principal component analysis (PCA) so that they explained at least `r percent(config$ica_n_components)` of the variance in the data (mean = `r mean(unlist(config$auto_ica_n_components))` components, range `r min(unlist(config$auto_ica_n_components))`--`r max(unlist(config$auto_ica_n_components))`).
@@
 
-```{r, fig2, cache=!run$figures, fig.height=8.6, fig.cap="(ref:fig2-caption)"}
-# Create Figure 2
-plot_fig2(files_dir, evokeds, config, channel_locations, models)
-```
-
-(ref:fig2-caption) [ERP results contrasting semantically informed perception and unsuccessfully informed perception.
-***A***, Assignment of objects to conditions based on participants' response in the insight phase of the experiment to unfamiliar objects presented with matching keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus perception within the three different phases.
-Semantically informed perception was associated with more negative amplitudes in the N170 component and less negative amplitudes in the N400 component during the insight phase.
-The time windows and channels for quantifying the ERP components are highlighted by the gray areas in the ERP waveforms and by the black markers on the scalp topographies, respectively.
-Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
-Ampl. = amplitude.\newline
-\*\*\* $p_\text{corr} < .001$.]{color="blue"}
-
 In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically [uninformed]{color="blue"}.
@@
 In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and [uninformed]{color="blue"} perception within each of the three phases of the experiment.
-Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 2), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
@@
 
-```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:fig3-caption)"}
+```{r, fig2, cache=!run$figures, fig.height=11, fig.cap="(ref:fig2-caption)"}
 # Create topographic plots for event-related power in the insight phase
@@
 
-(ref:fig3-caption) Time-frequency results for the insight phase.
+(ref:fig2-caption) Time-frequency results for the insight phase.
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
@@
 
-```{r, fig4, cache=!run$figures, fig.height=11, fig.cap="(ref:fig4-caption)"}
+```{r, fig3, cache=!run$figures, fig.height=11, fig.cap="(ref:fig3-caption)"}
 # Create topographic plots for event-related power in the post-insight phase
@@
 
-(ref:fig4-caption) Time-frequency results for the post-insight phase.
+(ref:fig3-caption) Time-frequency results for the post-insight phase.
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
@@
 # Print table of materials
-keywords %>%
-  filter(familiarity == "unfamiliar") %>%
+read_csv(here("materials", "keywords.csv"), col_types = cols()) %>%
+  mutate(
+    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
+    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
+    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
+    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
+  ) %>%
   transmute(
@@
     item_id = as.character(item_id),
-    match_translated = paste(match, match_en, sep = "\n") %>%
+    match = paste(match_ger, match_en, sep = "\n") %>%
       kableExtra::linebreak(align = "l", linebreaker = "\n"),
-    nonmatch_translated = paste(nonmatch, nonmatch_en, sep = "\n") %>%
+    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
       kableExtra::linebreak(align = "l", linebreaker = "\n")
@@
 
-```{r, ratingfigs}
-rating %>%
-  filter(!is.na(cosine)) %>%
-  mutate(condition_comb = paste(familiarity, condition)) %>%
-  ggplot(aes(x = condition_comb, y = cosine, color = condition_comb)) +
-  geom_violin() +
-  geom_boxplot(width = 0.2) +
-  scale_color_manual(values = c("#984ea3", "#e41a1c", "#377eb8")) +
-  labs(x = NULL, y = "Cosine distance") +
-  coord_cartesian(ylim = c(0.0, 1.0)) +
-  theme_classic() +
-  theme(legend.position = "none")
-
-rating %>%
-  filter(
-    !is.na(cosine) & familiarity == "unfamiliar" & condition == "match"
-  ) %>%
-  select(item_id, condition, cosine) %>%
-  group_by(item_id, condition) %>%
-  summarize(
-    mean = mean(cosine),
-    sd = sd(cosine),
-    n = n(),
-    se = sd / sqrt(n),
-    .groups = "drop"
-  ) %>%
-  mutate(item_id = fct_reorder(item_id, desc(mean))) %>%
-  # filter(mean > 0.7) %>%
-  ggplot(
-    aes(
-      x = item_id, y = mean, color = condition,
-      ymin = mean - se, ymax = mean + se
-    )
-  ) +
-  geom_pointrange() +
-  labs(x = "Stimulus ID", y = "Cosine distance to keywords") +
-  theme_classic() +
-  theme(
-    axis.text.x = element_text(angle = 90),
-    legend.position = "none"
-  )
-```
-
 ```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figs1-caption)"}
@@
   p_cluster = p_cluster,
-  conditions = c("Informed", "Unsuccessful")
+  condition_plus = "Informed",
+  condition_minus = "Unsuccessful",
+  title_conditions = "Informed - failed"
 )

### 2023-03-02 manuscript.Rmd

--- 2023-03-02 manuscript.Rmd
@@
     average_by = list(
-      pre_informed =
+      `Pre-insight/Informed` =
         "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
-      pre_uninformed =
+      `Pre-insight/Uninformed` =
         "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
-      pre_unsuccessful =
+      `Pre-insight/Unsuccessful` =
         "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
-      ins_informed =
+      `Insight/Informed` =
         "phase == 'Insight' & condition == 'Informed' & rt > 200",
-      ins_uninformed =
+      `Insight/Uninformed` =
         "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
-      ins_unsuccessful =
+      `Insight/Unsuccessful` =
         "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
-      post_informed =
+      `Post-insight/Informed` =
         "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
-      post_uninformed =
+      `Post-insight/Uninformed` =
         "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
-      post_unsuccessful =
+      `Post-insight/Unsuccessful` =
         "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"

### 2023-03-07 manuscript.Rmd
Update text

--- 2023-03-02 manuscript.Rmd
@@
 
-  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Abdel Rahman Lab for Neurocognitive Psychology at Humboldt-Universität zu Berlin for insightful discussions, as well as Guido Kiecker for technical support.
+  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Abdel Rahman Lab for Neurocognitive Psychology for insightful discussions, Guido Kiecker for technical support, as well as Guillaume Thierry and one anonymous reviewer for their comments on previous versions of the paper.
   This work was supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany’s Excellence Strategy (EXC 2002/1 "Science of Intelligence") project number 390523135 as well as grants AB277-5 and AB277-6 to R.A.R.
@@
 Consistent with previous work, this suggests that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component, event-related power).
-Our study is the first to show that these effects are instantaneous, that is, observable within zero to one trials after any semantic information has been presented.
+Our study is the first to show that these effects [do not require an extensive learning history but are rather observed immediately after semantic information has been provided for the first time.]{color="blue"}
 
@@
 Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18--32 years) and no history of psychological disorder or treatment.
-No a priori power analysis was carried out and the sample size was chosen in line with previous EEG studies on object processing in our lab.
+No a priori power analysis was carried out.
 All participants were right-handed according to the Edinburgh inventory [@oldfield1971] and reported normal or corrected-to-normal vision.
@@
 For each unfamiliar object, we created a pair of German keywords (a noun and a verb), describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; [see Supplementary Table 1]{color="blue"}).
-As our central experimental manipulation, half of the objects were presented together with keywords that correctly matched their respective function, whereas the other half of the objects were presented together with non-matching keywords belonging to one of the other objects.
+As our central experimental manipulation, half of the objects were presented together with keywords that matched their respective function, whereas the other half of the objects were presented together with non-matching keywords [that would have matched another object]{color="blue"}.
 The matching keywords were expected to induce semantically informed perception, that is, participants suddenly understanding what kind of object they were viewing.
@@
 
-As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
-We used latent semantic analysis with a word2vec embedding pre-trained on the German Wikipedia (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) to estimate semantic distances between these participant-generated keywords and the keywords used in our experiment (Supplementary Methods; Supplementary Figures 1 and 2).
+[As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
+We used latent semantic analysis with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Methods; Supplementary Figures 1 and 2).
 In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± SE = `r filter(rating_means, fam_condition == "familiar")$emmean` ± `r filter(rating_means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_means, fam_condition == "matching")$emmean` ± `r filter(rating_means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
-In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "matching - nonmatching")$p_value)` (linear mixed-effects model).
+In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "matching - nonmatching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.]{color="blue"}
 
@@
 
-(ref:fig1-caption) Experimental design and ERP results contrasting semantically informed perception and uninformed perception.
+(ref:fig1-caption) Experimental design and ERP results [contrasting semantically informed perception and uninformed perception]{color="blue"}.
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
@@
 In the post-insight phase, the same objects were presented again without keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus [uninformed]{color="blue"} perception within the three different phases.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (***B***), for the N170 component (***C***), and for the N400 component (***D***) for objects with semantically informed perception versus [uninformed]{color="blue"} perception within the three different phases.
 Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
-The time windows and channels for quantifying the ERP components are highlighted by the gray areas in the ERP waveforms and by the black markers on the scalp topographies, respectively.
+[Waveform plots show the ERP amplitudes averaged across channels in the regions of interest (P1: PO3, PO4, POz, O1, O2, Oz; N170: P7, P8, PO7, PO8, PO9, PO10; N400: C1, C2, Cz, CP1, CP2, CPz; see black dots in the scalp topographies).]{color="blue"}
 Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
-Ampl. = amplitude.\newline
+[Topographies show the difference in ERP amplitudes at all channels on the scalp, averaged across the time windows of interest (P1: 100--150 ms, N170: 150--200 ms, N400: 400--700 ms; see gray areas in the ERP waveforms).]{color="blue"}
+Ampl. = amplitude.
 \* $p_\text{corr} < .05$. \*\* $p_\text{corr} < .01$. \*\*\* $p_\text{corr} < .001$.
@@
 [We used participants' behavioral responses to verify our experimental manipulation and to assign each object to a semantic condition.
-First, we used participants' responses from the pre-insight phase (when objects were presented for the first time and without keywords) to make sure that objects were indeed unfamiliar to them.
+First, we used participants' responses from the pre-insight phase (when objects were presented for the first time, without keywords) to make sure that objects were indeed unfamiliar to them.
 That is, we excluded any objects for which participants responded with "I know what this is" in the pre-insight phase.
-Next, we used participants' responses from the insight phase (when objects were presented for the second time, now preceded by keywords) to assign the remaining objects to different semantic conditions: Semantically informed, uninformed, and unsuccessfully informed.
+Next, we used participants' responses from the insight phase (when objects were presented for the second time, preceded by keywords) to assign the remaining objects to different semantic conditions: Semantically informed, uninformed, and unsuccessfully informed.
 The semantically informed condition consisted of objects that were presented with matching keywords and for which the participant responded with knowing what the object was or having an assumption.
@@
 
-[We used participants' behavioral data to verify our experimental manipulation and to assign objects to different semantic conditions (see Materials and Methods).
-First we excluded an average of `r mean(objects_per_condition$Exclude_known)` objects per participant for which participants indicated that they knew the objects even before any keywords had been presented (= `r percent(mean(objects_per_condition$Exclude_known) / 120, accuracy = 0.1)` of all objects).
-Next, `r mean(objects_per_condition$Informed)` objects per participant could be assigned to the semantically informed condition (i.e., matching keywords and a positive response; `r percent(mean(objects_per_condition$Informed) / 60, accuracy = 0.1)` of all objects presented with matching keywords) and `r mean(objects_per_condition$Uninformed)` objects per participant could be assigned to the uninformed condition (i.e., non-matching keywords and a negative response; `r percent(mean(objects_per_condition$Uninformed) / 60, accuracy = 0.1)` of all objects presented with non-matching keywords).
-Finally, `r mean(objects_per_condition$Unsuccessful)` objects per participant could be assigned to the unsuccessfully informed condition (i.e., matching keywords but a negative response; `r percent(mean(objects_per_condition$Unsuccessful) / 60, accuracy = 0.1)` of all objects presented with matching keywords).]{color="blue"}
+[Based on the experimental manipulation (matching or non-matching keywords) and each individual participant's behavioral response (positive or negative regarding knowing what the object was), we assigned `r mean(objects_per_condition$Informed)` ± `r sd(objects_per_condition$Informed)` (mean ± standard deviation) objects to the semantically informed condition (i.e., matching keywords and positive response), `r mean(objects_per_condition$Uninformed)` ± `r sd(objects_per_condition$Uninformed)` objects to the uninformed condition (i.e., non-matching keywords and negative response), and `r mean(objects_per_condition$Unsuccessful)` ± `r sd(objects_per_condition$Unsuccessful)` objects to the unsuccessfully informed condition (i.e., matching keywords but negative response).
+This assignment of objects to conditions was based solely on the insight phase of the experiment, when objects were presented with keywords for the first time, and carried over unchanged to analyze the data from the pre-insight and post-insight phases as well.
+The remaining objects were excluded due to an implausible response pattern (i.e., non-matching keywords but positive response; `r mean(objects_per_condition$Exclude_uninformed)` ± `r sd(objects_per_condition$Exclude_uninformed)` objects), due to being known to the participant in the pre-insight phase (i.e., before any keywords had been presented; `r mean(objects_per_condition$Exclude_known)` ± `r sd(objects_per_condition$Exclude_known)` objects), or because of technical errors (i.e., reaction times of 0 ms recorded by the presentation software, `r mean(objects_per_condition$Exclude_glitch)` ± `r sd(objects_per_condition$Exclude_glitch)` objects).]{color="blue"}
 
@@
 Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed or [uninformed]{color="blue"}), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed[, uninformed, or unsuccessfully informed]{color="blue"}), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
@@
 In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the [uninformed]{color="blue"} condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$p_value))` (see Figure 1B--D).
-This was expected given that the critical keywords (leading either to semantically informed perception or [uninformed]{color="blue"} perception) had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
+[Likewise, there were no differences between the semantically informed condition and the unsuccessfully informed condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Unsuccessful")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Unsuccessful")$p_value))` (see Figure 2B--D).]{color="blue"}
+This was expected given that the keywords that would [provide additional semantic information]{color="blue"} had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
 
@@
 ***A***, Assignment of objects to conditions based on participants' response in the insight phase of the experiment to unfamiliar objects presented with matching keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (100--150 ms, ***B***), for the N170 component (150--200 ms, ***C***), and for the N400 component (400--700 ms, ***D***) for objects with semantically informed perception versus perception within the three different phases.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (***B***), for the N170 component (***C***), and for the N400 component (***D***) for objects with semantically informed perception versus perception within the three different phases.
 Semantically informed perception was associated with more negative amplitudes in the N170 component and less negative amplitudes in the N400 component during the insight phase.
-The time windows and channels for quantifying the ERP components are highlighted by the gray areas in the ERP waveforms and by the black markers on the scalp topographies, respectively.
+Waveform plots show the ERP amplitudes averaged across channels in the regions of interest (P1: PO3, PO4, POz, O1, O2, Oz; N170: P7, P8, PO7, PO8, PO9, PO10; N400: C1, C2, Cz, CP1, CP2, CPz; see black dots in the scalp topographies).
 Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
-Ampl. = amplitude.\newline
+Topographies show the difference in ERP amplitudes at all channels on the scalp, averaged across the time windows of interest (P1: 100--150 ms, N170: 150--200 ms, N400: 400--700 ms; see gray areas in the ERP waveforms).
+Ampl. = amplitude.
 \*\*\* $p_\text{corr} < .001$.]{color="blue"}
@@
 There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`.
+[The same effects where found when comparing objects with semantically informed perception to those objects that were also presented with matching keywords but for which participants still indicated not knowing what the object was (i.e., the unsuccessfully informed condition).
+Compared to these objects, semantically informed perception was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`, while there was no reliable difference in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`.]{color="blue"}
 
@@
 Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$p_value)`.
+[These effects did not replicate when comparing the semantically informed condition to the unsuccessfully informed condition, with no reliable differences in the P1, N170, or N400 components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Post-insight" & contrast == "Informed - Unsuccessful")$t_value))`, all $p$s > `r print_p(min(filter(contrast_table, phase == "Post-insight" & contrast == "Informed - Unsuccessful")$p_value))`.]{color="blue"}
 
@@
 
+[We repeated this analysis to look for differences between semantically informed perception and unsuccessfully informed perception within each of the three phases of the experiment.
+There were no significant clusters in the pre- or post-insight phases (see Supplementary Figures 2 and 4), all $p$s > `r print_p(min(filter(tfr_clusters, contrast %in% c("Pre-insight/Informed - Pre-insight/Unsuccessful", "Post-insight/Informed - Post-insight/Unsuccessful"))$p_val))` but one significant cluster in the insight phase (see Supplementary Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`.
+This cluster was similar to the ones described above in its latency, frequency range, and topographic distribution.]{color="blue"}
+
 # Discussion
@@
 Our exploratory time-frequency analysis revealed a late (> 600 ms) reduction in post-stimulus power in the alpha and lower beta ranges (approx. 8--20 Hz).
-While not predicted in advance, this is consistent with the finding that the dampening of oscillations in this range is associated with a facilitation in representing stimulus-specific information [@griffiths2019] and with successfully forming new semantic memories [@hanslmayr2009].
-Like the N400 effect in the ERP, this reduction in power occurred as soon as participants had received the relevant semantic information and recurred once the same objects were re-encountered without any semantic information.
+Like the N400 effect in the ERP, this change in event-related power occurred as soon as participants had received the relevant semantic information and recurred once the same objects were re-encountered without any semantic information.
+[Reductions in alpha/beta power have been shown to correlate with clearer representations of stimulus specific information, as measured using representational similarity analysis [@griffiths2019], and with successfully forming new semantic memories [@hanslmayr2009].
+This may be due to a dampening of alpha/beta oscillations which creates favourable conditions for high-level cortical information processing and encoding.]{color="blue"}
 
@@
 It therefore constitutes an online marker of semantic insight, that is, of participants suddenly understanding the visual objects in the light of the information provided by the keywords.
-The N170 is typically associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002].
+The N170 is typically associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002][, that is, it is sensitive to factors that go beyond structural encoding and categorical perception [@thierry2007; @thierry2007a; @dering2011\; but see also @rossion2008].]{color="blue"}.
 It being enlarged during semantically informed perception may reflect that the semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
@@
 ```
-
-\newpage
 
@@
 
-\newpage
 \normalsize
@@
 plot_tfr_topos(
+  filter(tfr_grand_ave, phase == "Pre-insight"),
+  filter(
+    tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful"
+  ),
+  p_cluster = p_cluster,
+  conditions = c("Informed", "Unsuccessful")
+)
+```
+
+(ref:figs2-caption) [Time-frequency results for the pre-insight phase (informed minus unsuccessful).
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.
+A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful")$p_val))`).]{color="blue"}
+
+```{r, figs3, cache=!run$figures, fig.height=11, fig.cap="(ref:figs3-caption)"}
+# Create topographic plots for control analysis of event-related power
+plot_tfr_topos(
   filter(tfr_grand_ave, phase == "Insight"),
@@
 
-(ref:figs2-caption) Time-frequency results for the control analysis.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the "failed insight" condition (see Results: Control Analysis in the main text), grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`).
+(ref:figs3-caption) [Time-frequency results for the insight phase (informed minus unsuccessful).
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`).]{color="blue"}
+
+```{r, figs4, cache=!run$figures, fig.height=11, fig.cap="(ref:figs4-caption)"}
+# Create topographic plots for control analysis of event-related power
+plot_tfr_topos(
+  filter(tfr_grand_ave, phase == "Post-insight"),
+  filter(
+    tfr_clusters,
+    contrast == "Post-insight/Informed - Post-insight/Unsuccessful"
+  ),
+  p_cluster = p_cluster,
+  conditions = c("Informed", "Unsuccessful")
+)
+```
+
+(ref:figs4-caption) [Time-frequency results for the post-insight phase (informed minus unsuccessful).
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.
+A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Unsuccessful")$p_val))`).]{color="blue"}

### 2023-03-09 manuscript.Rmd
Update text, references

@@
 authornote: |  
-  Number of pages: 22
-
-  Number of figures: 3
-
-  Number of words: 215 (abstract), 645 (introduction), 1,494 (discussion)
-
-  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Abdel Rahman Lab for Neurocognitive Psychology for insightful discussions, Guido Kiecker for technical support, as well as Guillaume Thierry and one anonymous reviewer for their comments on previous versions of the paper.
+  Number of pages: ???
+
+  Number of figures: 4
+
+  Number of words: ??? (abstract), ??? (introduction), ??? (discussion)
+
+  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Abdel Rahman Lab for Neurocognitive Psychology for insightful discussions, Guido Kiecker for technical support, as well as Guillaume Thierry and one anonymous reviewer for their comments on a previous version of the paper.
   This work was supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany’s Excellence Strategy (EXC 2002/1 "Science of Intelligence") project number 390523135 as well as grants AB277-5 and AB277-6 to R.A.R.
@@
   mixed_models = FALSE,
-  figures = FALSE
+  figures = TRUE
 )
@@
 On the behavioral level, this is supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @slivac2021] or semantic [e.g., @gauthier2003] content.
-However, some studies have received legitimate criticism for confounding tentative high-level effects with low-level differences between conditions, as well as for not being able to discern perceptual from post-perceptual (e.g., memory-related) effects [@firestone2016].
+[However, some studies have received legitimate criticism for a number of reasons [@firestone2016].
+For example, tentative high-level effects (e.g., the emotional difference between a smiling and a neutral facial expressions) were sometimes confounded with low-level visual differences (e.g., the difference in visual contrast introduced by one face showing their teeth and the other one not).
+As another example, studies that relied on behavioral measures such as rection times were not abel to discern effects of higher-level cognition on perception from effects that occur in later, post-perceptual stages of processing [e.g., easier recognition from memory for semantically meaningful stimuli, despite no change in how they are perceived visually\; @firestone2016].]{color="blue"}
 
@@
 The early peak of this component and its source in the occipital cortex [@abdelrahman2008] point to an immediate effect of semantic knowledge on visual perception.
-It is less clear, however, if this tentative top-down effect of semantic cognition on perception acts in an online fashion (i.e., directly modulating perceptual processing), or more indirectly, by altering stored visual representations over the course of learning, which would then get reactivated once the object is reencountered later on.
+It is less clear, however, if this tentative top-down effect of semantic cognition on perception acts in an online fashion (i.e., directly modulating perceptual processing), or more indirectly, by altering stored visual [memory]{color="blue"} representations over the course of learning, which would then get reactivated once the object is reencountered later on.
+[The first account (i.e., an online top-down effect) would be in accordance with predictive processing theories that posit that higher-level areas influence ongoing perceptual processing by sending predictions down to lower-level areas [e.g., @rao1999; @friston2009; @clark2013; @lupyan2015].
+The second account (i.e., re-activation of stored memory representations) woud argue against such online effects, positing that differences in ERPs emerge merely due to comparisons with visual memory representations or prototypes that have been built up over the course of learning [see, e.g., @palmeri2008].]{color="blue"}
 
@@
 We hypothesized that semantic information would have instant effects on visual perception, by which we mean (a) that these effects can already be observed on the same trial as the semantic information is being presented for the first time, and (b) that these effects are found not only in later, higher-level cognition-related ERP components (i.e., N400), but also in earlier, perception-related ERP components (i.e., P1 and/or N170).
+[Oberserving these effects immediately after participants have received the relevant semantic information, instead of after an extensive learning phase as in previous studies, would speak for theories that posit an online influence of higher-level cognitive areas on lower-level visual perception [e.g., predictive coding\; @friston2009].]{color="blue"}
 We furthermore conducted an exploratory time-frequency analysis to test for effects on event-related power which, unlike ERP effects, do not need to be tightly phase-locked to stimulus onset.
@@
 [As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
-We used latent semantic analysis with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Methods; Supplementary Figures 1 and 2).
-In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± SE = `r filter(rating_means, fam_condition == "familiar")$emmean` ± `r filter(rating_means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_means, fam_condition == "matching")$emmean` ± `r filter(rating_means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
+We used latent semantic analysis with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Figures 1 and 2).
+In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_means, fam_condition == "familiar")$emmean` ± `r filter(rating_means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_means, fam_condition == "matching")$emmean` ± `r filter(rating_means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
 In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "matching - nonmatching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.]{color="blue"}
@@
 Ampl. = amplitude.
-\* $p_\text{corr} < .05$. \*\* $p_\text{corr} < .01$. \*\*\* $p_\text{corr} < .001$.
+\* $p_\text{corr} < .05$. \*\*\* $p_\text{corr} < .001$.
 
@@
 That is, we excluded any objects for which participants responded with "I know what this is" in the pre-insight phase.
-Next, we used participants' responses from the insight phase (when objects were presented for the second time, preceded by keywords) to assign the remaining objects to different semantic conditions: Semantically informed, uninformed, and unsuccessfully informed.
+Next, we used participants' responses from the insight phase (when objects were presented for the second time, preceded by keywords) to assign the remaining objects to different semantic conditions: Semantically informed perception, uninformed perception, and unsuccessfully informed perception (see Figure 1A and 2A).
 The semantically informed condition consisted of objects that were presented with matching keywords and for which the participant responded with knowing what the object was or having an assumption.
@@
 The unsuccessfully informed condition consisted of objects that were presented with matching keywords but for which the participant responded with not knowing what the object was or having rather no assumption.
-The few objects that were presented with non-matching keywords but for which participants responded with knowing what the object was or having an assumption (i.e., an unsuccessfully uninformed condition) were dropped from all further analyses.
+The few objects that were presented with non-matching keywords but for which participants responded with knowing what the object was or having an assumption (i.e., "unsuccessfully uninformed" perception) were dropped from all further analyses.
 This assignment of objects to semantic conditions (informed, uninformed, or unsuccesfully informed) was carried over from the insight phase to the other two phases (pre-insight and post-insight).
@@
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
-All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the [uninformed]{color="blue"} condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
+All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a custom contrast (i.e., subtracting the [uninformed]{color="blue"} condition from the informed condition [and the unsuccessfully informed condition from the informed condition]{color="blue"}, the intercept being the grand mean across [all three conditions]{color="blue"}), and (c) the two-way interaction of phase and condition.
 We determined the most parsimonious random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
@@
 To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the [uninformed]{color="blue"} condition within the pre-insight, insight, and post-insight phases.
-This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for three separate tests.
+[In the same way, we computed pairwise comparisons contrasting the semantically informed condition against the unsuccessfully informed condition.]{color="blue"}
+This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for the three phases.
 All *p* values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
@@
 For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, and post-insight).
-First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the [uninformed]{color="blue"} condition for each participant.
+First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the [uninformed (or unsuccessfully informed)]{color="blue"} condition for each participant.
 We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they occurred at neighboring time points, frequencies, or channels.
@@
 In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and [uninformed]{color="blue"} perception within each of the three phases of the experiment.
-Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 1), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 3), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
@@
 [We repeated this analysis to look for differences between semantically informed perception and unsuccessfully informed perception within each of the three phases of the experiment.
-There were no significant clusters in the pre- or post-insight phases (see Supplementary Figures 2 and 4), all $p$s > `r print_p(min(filter(tfr_clusters, contrast %in% c("Pre-insight/Informed - Pre-insight/Unsuccessful", "Post-insight/Informed - Post-insight/Unsuccessful"))$p_val))` but one significant cluster in the insight phase (see Supplementary Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`.
+There were no significant clusters in the pre- or post-insight phases (see Supplementary Figures 4 and 6), all $p$s > `r print_p(min(filter(tfr_clusters, contrast %in% c("Pre-insight/Informed - Pre-insight/Unsuccessful", "Post-insight/Informed - Post-insight/Unsuccessful"))$p_val))` but one significant cluster in the insight phase (see Supplementary Figure 5), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`.
 This cluster was similar to the ones described above in its latency, frequency range, and topographic distribution.]{color="blue"}
@@
 It therefore constitutes an online marker of semantic insight, that is, of participants suddenly understanding the visual objects in the light of the information provided by the keywords.
-The N170 is typically associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002][, that is, it is sensitive to factors that go beyond structural encoding and categorical perception [@thierry2007; @thierry2007a; @dering2011\; but see also @rossion2008].]{color="blue"}.
+The N170 is typically associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002], [that is, it is sensitive to factors that go beyond structural encoding and categorical perception [@thierry2007; @thierry2007a; @dering2011; but see also @rossion2008]]{color="blue"}.
 It being enlarged during semantically informed perception may reflect that the semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
@@
 
-```{r, ratingfigs}
+```{r, figs1, cache=!run$figures, fig.height=5, fig.width=6, out.width="50%", fig.cap="(ref:figs1-caption)"}
 rating %>%
   filter(!is.na(cosine)) %>%
-  mutate(condition_comb = paste(familiarity, condition)) %>%
+  mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
   ggplot(aes(x = condition_comb, y = cosine, color = condition_comb)) +
-  geom_violin() +
+  geom_violin(fill = NA) +
   geom_boxplot(width = 0.2) +
-  scale_color_manual(values = c("#984ea3", "#e41a1c", "#377eb8")) +
-  labs(x = NULL, y = "Cosine distance") +
+  scale_y_continuous(limits = c(0.0, 1.0), breaks = seq(0.0, 1.0, by = 0.2)) +
+  scale_color_manual(values = c("#5e3c99", "#ca0020", "#0571b0")) +
+  labs(x = NULL, y = "Cosine distance to keywords") +
   coord_cartesian(ylim = c(0.0, 1.0)) +
   theme_classic() +
-  theme(legend.position = "none")
-
+  theme(
+    axis.title = element_text(color = "black", size = 10.9),
+    axis.text = element_text(color = "black", size = 10.9),
+    legend.position = "none",
+    panel.grid.major.y = element_line(),
+    panel.grid.minor.y = element_line()
+  )
+```
+
+(ref:figs1-caption) [Online pre-rating study results.
+Participants were presented with 240 objects in random order, 120 of which were familiar everyday objects and the other 120 were presumed to be unfamiliar to most people.
+Participants were asked to describe or guess the function of each object by typing a pair of German keywords.
+Violins show the distributions of the similarities between these participant-generated keywords and the keywords that we had created (see Materials and Methds; Supplementary Table 1).
+We computed these similarities separately for (a) participant-generated keywords for the familiar objects and keywords that we had created to match the familiar objects (though these were not part of the main EEG experiment; red), (b) participant-generated keywords for the unfamiliar objects and keywords that we had created to match the unfamiliar objects (blue), and (c) participant-generated keywords for the unfamiliar objects and keywords that we had created to not match the unfamiliar objects (by selecting keywords that matched one of the other unfamiliar objects; purple).
+Semantic similarities were computed as the cosine similarity between the sums of the two word vectors in a word2vec emebdding space pre-trained on the German Wikipedia.
+Boxplots show the median (thick line), 25th and 75th percentiles (hinges), 1.5 times the interquartile range above and below the hinges (whiskers), and any outlier data points that fall outside of the whiskers (dots).]{color="blue"}
+
+```{r, figs2, cache=!run$figures, fig.height=5.5, fig.cap="(ref:figs2-caption)"}
 rating %>%
-  filter(
-    !is.na(cosine) & familiarity == "unfamiliar" & condition == "match"
-  ) %>%
-  select(item_id, condition, cosine) %>%
-  group_by(item_id, condition) %>%
+  filter(!is.na(cosine) & condition == "match") %>%
+  mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
+  select(item_id, condition_comb, cosine) %>%
+  group_by(item_id, condition_comb) %>%
   summarize(
@@
   mutate(item_id = fct_reorder(item_id, desc(mean))) %>%
-  # filter(mean > 0.7) %>%
   ggplot(
     aes(
-      x = item_id, y = mean, color = condition,
+      x = item_id, y = mean, color = condition_comb, group = 1,
       ymin = mean - se, ymax = mean + se
@@
   ) +
-  geom_pointrange() +
-  labs(x = "Stimulus ID", y = "Cosine distance to keywords") +
+  geom_linerange(show.legend = FALSE) +
+  geom_line() +
+  labs(x = "Stimulus ID", y = "Cosine distance to keywords", color = NULL) +
+  scale_x_discrete(guide = guide_axis(angle = 90, n.dodge = 3)) +
+  scale_y_continuous(limits = c(0.0, 1.0), breaks = seq(0.0, 1.0, by = 0.2)) +
+  scale_color_manual(values = c("#5e3c99", "#ca0020")) +
   theme_classic() +
   theme(
-    axis.text.x = element_text(angle = 90),
-    legend.position = "none"
-  )
-```
-
-```{r, figs1, cache=!run$figures, fig.height=11, fig.cap="(ref:figs1-caption)"}
+    axis.title = element_text(color = "black", size = 10.9),
+    axis.text = element_text(color = "black", size = 10.9),
+    legend.position = c(0.95, 0.92),
+    panel.grid.major.x = element_line(),
+    panel.grid.major.y = element_line(),
+    panel.grid.minor.y = element_line()
+  )
+```
+
+(ref:figs2-caption) [Online pre-rating study results on the level of individual object stimuli.
+Same as Supplementary Figure 1, but showing, for each object stimulus separately, the mean (horizontal line) ± 1 $SE$ (vertical lines) of the semantic similarities between participant-generated keywords and the keywords that we had generated.
+Semantic similarities were generally higher for the familiar objects than for the unfamiliar objects, indicating that it was either for participants to come up with the correct function for the familiar objects.
+This mean cosine similarity for each object (i.e., a measure of the difficulty of guessing its function) was entered as a covariate of no interest in all linear mixed-effects models for analyzing the data of the main EEG experiment (see Materials and Methods; Results).]{color="blue"}
+
+```{r, figs3, cache=!run$figures, fig.height=11, fig.cap="(ref:figs3-caption)"}
 # Create topographic plots for event-related power in the pre-insight phase
@@
 
-(ref:figs1-caption) Time-frequency results for the pre-insight phase.
+(ref:figs3-caption) Time-frequency results for the pre-insight phase.
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
@@
 
-```{r, figs2, cache=!run$figures, fig.height=11, fig.cap="(ref:figs2-caption)"}
+```{r, figs4, cache=!run$figures, fig.height=11, fig.cap="(ref:figs4-caption)"}
 # Create topographic plots for control analysis of event-related power
@@
 
-(ref:figs2-caption) [Time-frequency results for the pre-insight phase (informed minus unsuccessful).
+(ref:figs4-caption) [Time-frequency results for the pre-insight phase (informed minus unsuccessful).
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.
@@
 
-```{r, figs3, cache=!run$figures, fig.height=11, fig.cap="(ref:figs3-caption)"}
+```{r, figs5, cache=!run$figures, fig.height=11, fig.cap="(ref:figs5-caption)"}
 # Create topographic plots for control analysis of event-related power
@@
 
-(ref:figs3-caption) [Time-frequency results for the insight phase (informed minus unsuccessful).
+(ref:figs5-caption) [Time-frequency results for the insight phase (informed minus unsuccessful).
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.
@@
 
-```{r, figs4, cache=!run$figures, fig.height=11, fig.cap="(ref:figs4-caption)"}
+```{r, figs6, cache=!run$figures, fig.height=11, fig.cap="(ref:figs6-caption)"}
 # Create topographic plots for control analysis of event-related power
@@
 
-(ref:figs4-caption) [Time-frequency results for the post-insight phase (informed minus unsuccessful).
+(ref:figs6-caption) [Time-frequency results for the post-insight phase (informed minus unsuccessful).
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.

### 2023-03-13 manuscript.Rmd
Proofreading

@@
   mixed_models = FALSE,
-  figures = TRUE
+  figures = FALSE
 )
@@
 Consistent with previous work, this suggests that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component, event-related power).
-Our study is the first to show that these effects [do not require an extensive learning history but are rather observed immediately after semantic information has been provided for the first time.]{color="blue"}
+Our study is the first to show that such effects [do not require an extensive learning history but are rather observed immediately after semantic information has been provided for the first time.]{color="blue"}
 
@@
 According to one view, these cognitive capacities kick in only after the retinal input has been processed by a specialized module for visual perception [@firestone2016; @fodor1983].
-This module is encapsulated from higher-level inputs and processes visual information in a purely feed-forward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
+This module is supposed to be encapsulated from higher-level inputs and processes visual information in a purely feed-forward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
 
@@
 [However, some studies have received legitimate criticism for a number of reasons [@firestone2016].
-For example, tentative high-level effects (e.g., the emotional difference between a smiling and a neutral facial expressions) were sometimes confounded with low-level visual differences (e.g., the difference in visual contrast introduced by one face showing their teeth and the other one not).
-As another example, studies that relied on behavioral measures such as rection times were not abel to discern effects of higher-level cognition on perception from effects that occur in later, post-perceptual stages of processing [e.g., easier recognition from memory for semantically meaningful stimuli, despite no change in how they are perceived visually\; @firestone2016].]{color="blue"}
+For example, tentative high-level effects (e.g., the emotional difference between a smiling and a neutral facial expression) were sometimes confounded with low-level visual differences (e.g., the difference in visual contrast introduced by one face showing their teeth and the other one not).
+As another example, studies that relied on behavioral measures such as reaction times were not able to discern effects of higher-level cognition on perception from effects that occur in later, post-perceptual stages of processing [e.g., easier recognition from memory for semantically meaningful stimuli, despite no change in how they are perceived visually\; @firestone2016].]{color="blue"}
 
 On the physiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
-Their excellent temporal resolution makes it possible to probe how early one can detect influences of high-level (e.g., semantic) information [@athanasopoulos2020].
+Their temporal resolution makes it possible to probe how early one can detect influences of high-level (e.g., semantic) information [@athanasopoulos2020].
 To this end, participants in previous studies by our lab and others learned to associate visual objects with different amounts of semantic information.
@@
 [The first account (i.e., an online top-down effect) would be in accordance with predictive processing theories that posit that higher-level areas influence ongoing perceptual processing by sending predictions down to lower-level areas [e.g., @rao1999; @friston2009; @clark2013; @lupyan2015].
-The second account (i.e., re-activation of stored memory representations) woud argue against such online effects, positing that differences in ERPs emerge merely due to comparisons with visual memory representations or prototypes that have been built up over the course of learning [see, e.g., @palmeri2008].]{color="blue"}
+The second account (i.e., re-activation of stored memory representations) would argue against such online effects, positing that differences in ERPs emerge merely due to comparisons with visual memory representations or prototypes that have been built up over the course of learning [e.g., @palmeri2008].]{color="blue"}
 
@@
 We hypothesized that semantic information would have instant effects on visual perception, by which we mean (a) that these effects can already be observed on the same trial as the semantic information is being presented for the first time, and (b) that these effects are found not only in later, higher-level cognition-related ERP components (i.e., N400), but also in earlier, perception-related ERP components (i.e., P1 and/or N170).
-[Oberserving these effects immediately after participants have received the relevant semantic information, instead of after an extensive learning phase as in previous studies, would speak for theories that posit an online influence of higher-level cognitive areas on lower-level visual perception [e.g., predictive coding\; @friston2009].]{color="blue"}
+[Observing these effects immediately after participants have received the relevant semantic information, instead of after an extensive learning phase as in previous studies, would speak for theories that posit an online influence of higher-level cognitive areas on lower-level visual perception [e.g., predictive coding\; @friston2009].]{color="blue"}
 We furthermore conducted an exploratory time-frequency analysis to test for effects on event-related power which, unlike ERP effects, do not need to be tightly phase-locked to stimulus onset.
@@
     mutate(
+      condition = ifelse(condition == "match", "matching", "non-matching"),
       across(c(keywords, response), str_to_lower),
@@
       factor(
-        levels = c("familiar match", "unfamiliar match", "unfamiliar nonmatch"),
+        levels = c(
+          "familiar matching", "unfamiliar matching", "unfamiliar non-matching"
+        ),
         labels = c("familiar", "matching", "nonmatching")
@@
 The few objects that were presented with non-matching keywords but for which participants responded with knowing what the object was or having an assumption (i.e., "unsuccessfully uninformed" perception) were dropped from all further analyses.
-This assignment of objects to semantic conditions (informed, uninformed, or unsuccesfully informed) was carried over from the insight phase to the other two phases (pre-insight and post-insight).
+This assignment of objects to semantic conditions (informed, uninformed, or unsuccessfully informed) was carried over from the insight phase to the other two phases (pre-insight and post-insight).
 This allowed us to test, on the one hand, if the objects differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic information acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).]{color="blue"}
@@
 
-The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.1](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.1)) based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
+The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4)) based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
 First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
@@
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
-All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a custom contrast (i.e., subtracting the [uninformed]{color="blue"} condition from the informed condition [and the unsuccessfully informed condition from the informed condition]{color="blue"}, the intercept being the grand mean across [all three conditions]{color="blue"}), and (c) the two-way interaction of phase and condition.
-We determined the most parsimonious random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
+All models included three fixed effects [of interest]{color="blue"}: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a custom contrast (i.e., subtracting the [uninformed]{color="blue"} condition from the informed condition [and the unsuccessfully informed condition from the informed condition]{color="blue"}, the intercept being the grand mean across [all three conditions]{color="blue"}), and (c) the two-way interaction of phase and condition.
+[We also added the results from the online pre-rating study (mean cosine distance between rating study-generated keywords and keywords presented in the main experiment) as an additional covariate of no interest (see Supplementary Figure 2).
+This was to control for the possibility that participants might have been partly familiar with some of the objects and/or able to guess their function from their visual appearance alone.]{color="blue"}
+For the random effects, we determined the most parsimonious structure supported by the data using the automatic procedure proposed by @matuschek2017.
 This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20; see Supplementary Results 1 for the final model syntax and model outputs).
@@
 For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, and post-insight).
-First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and the [uninformed (or unsuccessfully informed)]{color="blue"} condition for each participant.
+First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and [each of two control conditions (uninformed or unsuccessfully informed)]{color="blue"} for each participant.
 We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they occurred at neighboring time points, frequencies, or channels.
@@
 To obtain family-wise error-corrected $p$ values at the cluster level, we compared the cluster mass (i.e., the sum of the $t$ values) of each observed cluster to an empirical null distribution of cluster masses obtained from 5,000 permutations with random sign flips.
-Clusters were considered to be statistically significant if their mass exceeded the `r (1 - p_cluster) * 100`^th^ percentile of this distribution (i.e., cluster-level threshold $p < .05$, Bonferroni-corrected for three separate tests).
+Clusters were considered to be statistically significant if their mass exceeded the `r (1 - p_cluster) * 100`^th^ percentile of this distribution (i.e., cluster-level threshold $p < .05$, Bonferroni-corrected for three phases of the experiment).
 
@@
 In addition to the software mentioned above, our code relies on the tidyverse set of R packages [Version `r as.character(packageVersion("tidyverse"))`\; @R-tidyverse] for data wrangling, the ggplot2 [Version `r as.character(packageVersion("ggplot2"))`\; @R-ggplot2], cowplot [Version `r as.character(packageVersion("cowplot"))`\; @R-cowplot], and eegUtils [Version `r as.character(packageVersion("eegUtils"))`\; @R-eegUtils] packages for visualization, and the papaja package [Version `r as.character(packageVersion("papaja"))`\; @R-papaja] for statistical reporting.
-We followed the workflow developed by @peikert2021 to ensure the long-term reproducibility of our analysis pipeline.
+We used the workflow developed by @peikert2021 to ensure the long-term reproducibility of our analysis pipeline.
 
@@
 [Based on the experimental manipulation (matching or non-matching keywords) and each individual participant's behavioral response (positive or negative regarding knowing what the object was), we assigned `r mean(objects_per_condition$Informed)` ± `r sd(objects_per_condition$Informed)` (mean ± standard deviation) objects to the semantically informed condition (i.e., matching keywords and positive response), `r mean(objects_per_condition$Uninformed)` ± `r sd(objects_per_condition$Uninformed)` objects to the uninformed condition (i.e., non-matching keywords and negative response), and `r mean(objects_per_condition$Unsuccessful)` ± `r sd(objects_per_condition$Unsuccessful)` objects to the unsuccessfully informed condition (i.e., matching keywords but negative response).
-This assignment of objects to conditions was based solely on the insight phase of the experiment, when objects were presented with keywords for the first time, and carried over unchanged to analyze the data from the pre-insight and post-insight phases as well.
+This assignment of objects to conditions was based solely on the insight phase of the experiment, when objects were presented with keywords for the first time, and carried over to analyze the data from the pre-insight and post-insight phases as well.
 The remaining objects were excluded due to an implausible response pattern (i.e., non-matching keywords but positive response; `r mean(objects_per_condition$Exclude_uninformed)` ± `r sd(objects_per_condition$Exclude_uninformed)` objects), due to being known to the participant in the pre-insight phase (i.e., before any keywords had been presented; `r mean(objects_per_condition$Exclude_known)` ± `r sd(objects_per_condition$Exclude_known)` objects), or because of technical errors (i.e., reaction times of 0 ms recorded by the presentation software, `r mean(objects_per_condition$Exclude_glitch)` ± `r sd(objects_per_condition$Exclude_glitch)` objects).]{color="blue"}
@@
 There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`.
-[The same effects where found when comparing objects with semantically informed perception to those objects that were also presented with matching keywords but for which participants still indicated not knowing what the object was (i.e., the unsuccessfully informed condition).
+[The same effects were found when comparing objects with semantically informed perception to those objects that were also presented with matching keywords but for which participants still indicated not knowing what the object was (i.e., the unsuccessfully informed condition).
 Compared to these objects, semantically informed perception was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`, while there was no reliable difference in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`.]{color="blue"}
@@
 [Reductions in alpha/beta power have been shown to correlate with clearer representations of stimulus specific information, as measured using representational similarity analysis [@griffiths2019], and with successfully forming new semantic memories [@hanslmayr2009].
-This may be due to a dampening of alpha/beta oscillations which creates favourable conditions for high-level cortical information processing and encoding.]{color="blue"}
+This may be due to a dampening of alpha/beta oscillations which creates favorable conditions for high-level cortical information processing and encoding.]{color="blue"}
 
@@
 What the present study adds is that the P1 effect does not take an extensive learning history to develop.
-Instead, it can be observed as soon as one trial after semantic insight had happened.
+Instead, it can be observed as soon as one trial after semantic insight has happened.
 Because the P1 is typically associated with lower-level sensory processing [@johannes1995; @pratt2011; @luck2014], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive its low-level features [@athanasopoulos2020].
@@
 Indeed, the keywords that were presented before each object in the semantically informed condition were chosen such that they matched the function of the object and often had a direct relationship to certain visual features of the object (see Supplementary Table 1).
-This might have induced semantic priming, which is supported by the reduction in N400 amplitudes in response to ojects in the semantically informed condition, as in previous priming studies [e.g., @bentin1985; @kellenbach2000].
+This might have induced semantic priming, which is supported by the reduction in N400 amplitudes in response to objects in the semantically informed condition, as in previous priming studies [e.g., @bentin1985; @kellenbach2000].
 However, there are at least two arguments why semantic priming cannot account for our main findings, that is, the influence of semantic information on the early P1 and N170 components.
 First, for both of these components, ERP amplitudes were *enlarged* (i.e., more positive for the P1 component and more negative for the N170) during semantically informed perception, whereas an account based on semantic priming would have predicted *reduced* ERP amplitudes.
-Second, these effects were not just observed when comparing semantically informed perception (with matching keywords) and uninformed perception (with non-matching keywords), but also when comparing semantically informed perception with unsucessfully informed perception.
+Second, these effects were not just observed when comparing semantically informed perception (with matching keywords) and uninformed perception (with non-matching keywords), but also when comparing semantically informed perception with unsuccessfully informed perception.
 Whereas priming might have been present in the first comparison, in the second comparison all objects were preceded by keywords that matched the function of the object to a similar degree.
@@
 
-```{r, figs1, cache=!run$figures, fig.height=5, fig.width=6, out.width="50%", fig.cap="(ref:figs1-caption)"}
+```{r, figs1, cache=FALSE, fig.height=5, fig.width=6, out.width="50%", fig.cap="(ref:figs1-caption)"}
 rating %>%
@@
 Participants were asked to describe or guess the function of each object by typing a pair of German keywords.
-Violins show the distributions of the similarities between these participant-generated keywords and the keywords that we had created (see Materials and Methds; Supplementary Table 1).
+Violins show the distributions of the similarities between these participant-generated keywords and the keywords that we had created for our main EEG experiment (see Materials and Methods; Supplementary Table 1).
 We computed these similarities separately for (a) participant-generated keywords for the familiar objects and keywords that we had created to match the familiar objects (though these were not part of the main EEG experiment; red), (b) participant-generated keywords for the unfamiliar objects and keywords that we had created to match the unfamiliar objects (blue), and (c) participant-generated keywords for the unfamiliar objects and keywords that we had created to not match the unfamiliar objects (by selecting keywords that matched one of the other unfamiliar objects; purple).
-Semantic similarities were computed as the cosine similarity between the sums of the two word vectors in a word2vec emebdding space pre-trained on the German Wikipedia.
+Semantic similarities were computed as the cosine similarity between the sums of the two word vectors in a word2vec emebedding space pre-trained on the German Wikipedia.
 Boxplots show the median (thick line), 25th and 75th percentiles (hinges), 1.5 times the interquartile range above and below the hinges (whiskers), and any outlier data points that fall outside of the whiskers (dots).]{color="blue"}
 
-```{r, figs2, cache=!run$figures, fig.height=5.5, fig.cap="(ref:figs2-caption)"}
+```{r, figs2, cache=FALSE, fig.height=5.5, fig.cap="(ref:figs2-caption)"}
 rating %>%
-  filter(!is.na(cosine) & condition == "match") %>%
+  filter(!is.na(cosine) & condition == "matching") %>%
   mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
@@
     axis.text = element_text(color = "black", size = 10.9),
-    legend.position = c(0.95, 0.92),
+    legend.position = c(0.93, 0.92),
     panel.grid.major.x = element_line(),
@@
 (ref:figs2-caption) [Online pre-rating study results on the level of individual object stimuli.
-Same as Supplementary Figure 1, but showing, for each object stimulus separately, the mean (horizontal line) ± 1 $SE$ (vertical lines) of the semantic similarities between participant-generated keywords and the keywords that we had generated.
-Semantic similarities were generally higher for the familiar objects than for the unfamiliar objects, indicating that it was either for participants to come up with the correct function for the familiar objects.
+Same as Supplementary Figure 1, but showing, for each object stimulus separately, the mean (horizontal line) ± 1 standard error (vertical lines) of the semantic similarities between participant-generated keywords and the keywords that we had generated.
+Semantic similarities were generally higher for the familiar objects than for the unfamiliar objects, indicating that it was easier for participants to come up with the correct function for the familiar objects.
 This mean cosine similarity for each object (i.e., a measure of the difficulty of guessing its function) was entered as a covariate of no interest in all linear mixed-effects models for analyzing the data of the main EEG experiment (see Materials and Methods; Results).]{color="blue"}

### 2023-03-13 manuscript.Rmd
Re-factor file structure, rating functions

@@
 
-bibliography      : "manuscript_files/references.bib"
-csl               : "manuscript_files/citation_style.csl"
+bibliography      : "misc/references.bib"
+csl               : "misc/citation_style.csl"
 
@@
     latex_engine: xelatex
-    pandoc_args: ["--lua-filter=manuscript_files/color_text.lua"]
+    pandoc_args: ["--lua-filter=misc/color_text.lua"]
 
@@
 ```{r, setup, include=FALSE}
-# Load R packages
+# Load packages
 library(buildmer)
@@
 
-# Set global options
+# Load custom helper functions
+walk(list.files(here("src"), full.names = TRUE), source)
+
+# Set options
 options(readr.show_col_types = FALSE)
+emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
 opts_chunk$set(
@@
 
-# Specify directory paths
+# Directory paths
 data_dir <- here("data")
-rating_dir <- here(data_dir, "ratings")
-files_dir <- here("manuscript_files")
+materials_dir <- here("materials")
+misc_dir <- here("misc")
 output_dir <- here("output")
@@
 
-# Load custom helper functions for creating figures and tables
-source(here(files_dir, "helper_functions.R"))
-
-# Re-run steps that take a long time to compute?
+# Write R package references
+r_refs(here(misc_dir, "r-references.bib"), append = FALSE)
+
+# Re-run steps that take a long time?
 run <- list(
-  rating_semantic_analysis = FALSE,
+  rating_lsa = FALSE,
   eeg_processing = FALSE,
   mixed_models = FALSE,
-  figures = FALSE
-)
-
-# Write R packages to bibliography
-r_refs(here(files_dir, "r-references.bib"), append = FALSE)
+  figures = TRUE
+)
 ```
@@
 ```{r, ratings}
-# Read table of object stimuli + keywords for the main experiment
+# Load rating study data and keywords
+rating_raw <- read_csv(
+  here(data_dir, "rating", "rating_data.csv"),
+  col_types = cols(), locale = locale(encoding = "latin1")
+)
 keywords <- read_csv(
-  here("materials", "keywords.csv"),
+  here(materials_dir, "keywords.csv"),
   col_types = cols(
@@
   )
-) %>%
-  mutate(
-    match = str_c(match_noun, ", ", match_verb),
-    match_en = str_c("{[", match_noun_en, ", ", match_verb_en, "]}"),
-    nonmatch = str_c(nonmatch_noun, ", ", nonmatch_verb),
-    nonmatch_en = str_c("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
-  )
-
-# (Re-)do latent semantic analysis of online rating study data
-rating_file <- here(output_dir, "rating.csv")
-if (run$rating_semantic_analysis) {
-  # Load pre-trained German word2vec embedding
-  word2vec <- load_word2vec(rating_dir)
-
-  # Read online rating study data
-  rating_raw <- read_csv(
-    here(data_dir, "ratings", "rating_data.csv"),
-    col_types = cols(), locale = locale(encoding = "latin1")
-  )
-  rating_substantives <- select(rating_raw, S001_01:S242_01)
-  rating_verbs <- select(rating_raw, V001_01:V242_01)
-
-  # Prepare a copy of the keywords to add to the rating study data
-  rating_n <- nrow(rating_raw)
-  keywords_for_rating <- keywords %>%
-    arrange(familiarity, filename) %>%
-    select(item_id, familiarity, filename, match, nonmatch) %>%
-    replicate(rating_n, ., simplify = FALSE) %>%
-    bind_rows()
-
-  # Compute cosine similarities between rating study responses and keywords
-  rating <-
-    map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
-    mutate(participant_id = rating_raw$CASE) %>%
-    pivot_longer(
-      -participant_id,
-      names_to = "question_id", values_to = "response"
-    ) %>%
-    bind_cols(keywords_for_rating, .) %>%
-    pivot_longer(
-      c(match, nonmatch),
-      names_to = "condition", values_to = "keywords"
-    ) %>%
-    mutate(
-      condition = ifelse(condition == "match", "matching", "non-matching"),
-      across(c(keywords, response), str_to_lower),
-      keywords = str_replace_all(
-        keywords, c(
-          aufstemmen = "aufbrechen",
-          tierkäfig = "käfig",
-          wegkehren = "kehren",
-          verühren = "rühren",
-          schraubenschlüssel = "werkzeug",
-          verquirlen = "rühren",
-          tackern = "tacker",
-          sprengstoffexplosion = "explosion",
-          tankfüllstand = "füllstand",
-          tonpott = "tongefäß",
-          eierkarton = "eier verpackung",
-          musikgerät = "musikinstrument",
-          türgelenk = "scharnier",
-          telegrafieren = "telegraf",
-          sternenbilder = "sternbild",
-          aufspulen = "aufwickeln",
-          häckseln = "zerkleinern",
-          `mikroskop-proben` = "mikroskop proben",
-          streckenmaß = "maß",
-          windgeschwindigkeit = "windstärke",
-          nussöl = "nuss öl",
-          entkörnen = "entkernen",
-          katzenklo = "katze klo",
-          kutschrad = "kutsche rad"
-        )
-      ),
-      response = str_replace_all(
-        response, c(
-          aufhebeln = "aufbrechen",
-          föhnen = "föhn",
-          kasette = "kassette",
-          aufkehren = "kehren",
-          tackern = "tacker",
-          sprayapparat = "spray apparat",
-          anästhesieren = "betäuben",
-          reaktionsspiel = "reaktion spiel",
-          mulchgerät = "mulch gerät",
-          makierung = "markierung",
-          wissenschaftlich = "wissenschaft",
-          spannwerkzeug = "werkzeug",
-          wärmestab = "wärme stab",
-          ampfel = "ampel",
-          scheere = "schere",
-          pflägen = "pflügen",
-          knetten = "kneten",
-          pfandkuchen = "pfannkuchen",
-          anmacher = "anmachen",
-          injezieren = "injizieren",
-          telfon = "telefon",
-          beschrifter = "beschriften",
-          aufbewaren = "aufbewahren",
-          spähne = "späne",
-          separator = "trennen",
-          stämpfer = "stampfen",
-          fliente = "flinte",
-          tromphete = "trompete",
-          makieren = "markieren",
-          stöbseln = "stöpsel",
-          hiernwellen = "gehirnwellen",
-          kartofeln = "kartoffeln",
-          vaccum = "vakuum",
-          saubermachen = "putzen",
-          ankeln = "anker",
-          schuessel = "schüssel",
-          `zangen\\\\` = "zange",
-          kleiderbuegel = "kleiderbügel",
-          buerste = "bürste",
-          buersten = "bürsten",
-          druecken = "drücken",
-          obstscheider = "obst schneiden",
-          àumachen = "ausmachen",
-          bieroeffner = "flaschenöffner",
-          oeffnen = "öffnen",
-          giesskanne = "gießkanne",
-          gluehbirne = "glühbirne",
-          schettem = "manschetten",
-          kurzhantel = "kurzhanteln",
-          tierekiste = "tiere kiste",
-          kaffekocher = "kaffeemaschine",
-          kinderwaagen = "kinderwagen",
-          klobürste = "toilette bürste",
-          orangenpresser = "orangen presse",
-          foodmixer = "essen mixer",
-          schuessel = "schüssel",
-          naehen = "nähen",
-          teigwalze = "nudelholz",
-          pffefern = "pfeffer",
-          maehen = "mähen",
-          gesichtsbürste = "gesicht bürste",
-          regenchirm = "regenschirm",
-          kaesegratin = "käse gratin",
-          slotsmaschine = "slot maschine",
-          piggybank = "sparschwein",
-          stampen = "kleben",
-          arztwekzeug = "arzt werkzeug",
-          gradskala = "grad skala",
-          trichten = "trichter",
-          spulsmaschine = "spülmaschine",
-          zahnbrueste = "zahnbürste",
-          bruesten = "bürsten",
-          foltermaschine = "folter maschine",
-          bieröffner = "flaschenöffner",
-          oeffnen = "öffnen",
-          pizzacutter = "pizza schneider",
-          kerzestande = "kerzenständer",
-          naehen = "nähen",
-          geruest = "gerüst",
-          nagelschneider = "nagel schere",
-          burste = "bürste",
-          bursten = "bürsten",
-          loefel = "löffel",
-          hamsterspielzeug = "hamster spielzeug",
-          breadboard = "schneide brett",
-          druceken = "drücken",
-          nussknacnker = "nussknacker",
-          ueberwachen = "überwachen",
-          trainingsmaschine = "training maschine",
-          padeln = "paddeln",
-          schäumer = "aufschäumen",
-          aufhanger = "aufhänger",
-          hangt = "hängen",
-          `eier-guillotine` = "eier messer",
-          ruhrgerat = "rührgerät",
-          katzentrager = "katzen träger",
-          hinzufugen = "hinzufügen",
-          kuchenform = "backform",
-          nagelfeile = "nagel feile",
-          fondues = "fondue",
-          zuhoren = "zuhören",
-          rasenmaher = "rasenmäher",
-          geschlitzter = "schlitz",
-          breifmarke = "briefmarke",
-          bimmeln = "läuten",
-          rasma = "",
-          kassete = "kassette",
-          nudelmaschine = "nudel maschine",
-          ruhrer = "rührer",
-          feuerloscher = "feuerlöscher",
-          entfernungsmesser = "entfernung messer",
-          heißluftpistole = "heißluft pistole",
-          schuhlöffel = "schuhe anziehen",
-          uben = "üben",
-          naturlich = "natürlich",
-          schißen = "schießen",
-          rührgerät = "mixer",
-          aufkehren = "kehren",
-          rausziehen = "herausziehen",
-          `mini-meißel` = "mini meißel",
-          kaffeemischer = "kaffee mischer",
-          nachttischlampe = "nachttisch lampe",
-          arbeitsschlüssel = "arbeit schlüssel",
-          `boom-box` = "lautsprecher",
-          feststampfen = "fest stampfen",
-          `casino-maschine` = "casino maschine",
-          `herzfrequenz-test` = "herzfrequenz test",
-          zaichnen = "zeichnen",
-          schneidin = "schneiden",
-          vergleichsmaschine = "vergleich maschine",
-          rosenabzeichen = "rosen abzeichen",
-          `dummy-stecker` = "dummy stecker",
-          `post-punk-sanduhr` = "post punk sanduhr",
-          schneidemaschine = "schneiden maschine",
-          fusszeile = "fußzeile",
-          gartenlampe = "garten lampe",
-          trenneimer = "trennen eimer",
-          fußabstreifer = "fußmatte",
-          wichten = "gewicht",
-          perlenständer = "perlen ständer",
-          briefmarker = "briefmarke",
-          `elektronische-schaltung` = "elektronische schaltung",
-          fläschchenheizung = "flächen heizung",
-          elektrodrucker = "elektro drucker",
-          metalllinse = "metall linse",
-          kugelheizung = "kugel heizung",
-          abschrauber = "abschrauben",
-          `mini-korb` = "mini korb",
-          elektronenrechner = "elektronen rechner",
-          spießfaum = "spieß",
-          tierträger = "tier träger",
-          rührgerät = "rührgerät",
-          kuchenform = "backform",
-          friteuse = "fritteuse",
-          `ein-` = "ein",
-          greigfen = "greifen",
-          zerknittern = "falten bekommen",
-          salatzange = "salat zange",
-          wwrm = "wurm",
-          duschwasser = "dusche wasser",
-          verbreitene = "verbreiten",
-          aufpieksen = "anstechen",
-          restriktieren = "einschränken",
-          rückgeld = "wechselgeld",
-          aufkehren = "zusammenkehren",
-          bratgut = "grillgut",
-          bepinseln = "bestreichen",
-          verquirlen = "vermischen",
-          temparatur = "temperatur",
-          aufspulen = "aufwickeln",
-          elekronik = "elektronik",
-          festnieten = "fest nieten",
-          festspannen = "fest spannen",
-          hebelkräfte = "hebelkraft",
-          meiseln = "meißeln",
-          betäüben = "betäuben",
-          verschraüben = "verschrauben",
-          schraüben = "schrauben",
-          seperator = "trennen",
-          schraübendreher = "schraubendreher",
-          gegewicht = "gewicht"
-        )
-      ),
-      cosine = compute_cosine(keywords, response, word2vec)
-    )
-
-  # Save to file
-  write_csv(rating, rating_file)
+)
+
+# Compute or load latent semantic analysis (LSA) results
+if (run$rating_lsa) {
+  word2vec_file <- here::here(data_dir, "rating", "vectors.txt")
+  word2vec <- load_word2vec(word2vec_file)
+  rating <- compute_lsa(rating_raw, keywords, word2vec)
+} else {
+  rating <- read_csv(
+    here(output_dir, "rating.csv"),
+    col_types = cols(item_id = col_factor(), participant_id = col_factor())
+  )
 }
 
-# # Test if all keywords and responses are in the embedding
-# for (keywords in c(unique(rating$keywords), unique(rating$response))) {
-#   if (!is.na(keywords)) {
-#     for (word in (str_split(keywords, pattern = " |, ")[[1]])) {
-#       if (!(word %in% rownames(word2vec))) {
-#         cat(paste0(word, ' = "",\n'))
-#       }
-#     }
-#   }
-# }
-
-# Read the rating study results incl. cosine similarities
-rating <- read_csv(
-  rating_file,
-  col_types = cols(item_id = col_factor(), participant_id = col_factor())
-) %>%
-  filter(!is.na(cosine)) %>%
-  mutate(
-    fam_condition = paste(familiarity, condition) %>%
-      factor(
-        levels = c(
-          "familiar matching", "unfamiliar matching", "unfamiliar non-matching"
-        ),
-        labels = c("familiar", "matching", "nonmatching")
-      )
-  )
-
-# Compare cosine similarities between object conditions
-contrasts(rating$fam_condition) <- contr.sdif(3)
-model_rating <- lmer(
-  cosine ~ fam_condition +
-    (fam_condition | participant_id) +
-    (1 | item_id),
-  data = rating,
-  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
-)
-
-# Compute condition means and pairwise contrasts
-emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-emm_rating <- emmeans(
-  model_rating,
-  specs = consec ~ fam_condition,
-  rev = TRUE,
-  adjust = "bonferroni"
-)
-rating_means <- as.data.frame(emm_rating$emmeans)
-rating_contrasts <- as.data.frame(emm_rating$contrasts) %>%
-  rename(t_value = `t.ratio`, p_value = `p.value`)
-
-# Compute each item's average cosine distance across participants
-cosines <- rating %>%
-  group_by(item_id) %>%
-  summarize(cosine = mean(cosine)) %>%
-  mutate(cosine = scale(cosine))
-
-# rating_pairwise <- rating$participant_id %>%
-#   unique() %>%
-#   combn(m = 2) %>%
-#   data.frame() %>%
-#   map_dfr(function(pair) {
-#     id_1 <- pair[1]
-#     id_2 <- pair[2]
-#     response_1 <- filter(rating, participant_id == id_1)$response
-#     response_2 <- filter(rating, participant_id == id_2)$response
-#     tibble(
-#       item_id = keywords$item_id,
-#       familiarity = keywords$familiarity,
-#       filename = keywords$filename,
-#       pair_id = str_c(id_1, id_2, sep = "_"),
-#       participant_id_1 = id_1,
-#       participant_id_2 = id_2,
-#       response_1,
-#       response_2,
-#       cosine = compute_cosine(response_1, response_2, word2vec)
-#     )
-#   })
-
-# write_csv(rating_pairwise, here(output_dir, "rating_pairwise.csv"))
-
-# mod_pairwise <- lmer(
-#   cosine ~ familiarity + (familiarity | pair_id) + (1 | filename),
-#   data = rating_pairwise
-# )
-# (summary_pairwise <- summary(mod_pairwise))
-
-# Rmisc::summarySEwithin(
-#   data = rating_pairwise, measurevar = "cosine", withinvars = "familiarity",
-#   idvar = "pair_id", na.rm = TRUE
-# ) %>%
-#   ggplot(aes(x = familiarity, y = cosine, color = familiarity)) +
-#   geom_violin(data = rating_pairwise) +
-#   coord_cartesian(ylim = c(0.0, 1.0)) +
-#   geom_pointrange(aes(ymin = cosine - se, ymax = cosine + se)) +
-#   theme_classic()
+# Compare cosine similarities between conditions
+rating_stats <- compute_rating_stats(rating)
+
+# Compute average cosine similarity for each item
+cosines <- compute_average_cosines(rating)
 ```
@@
 We used latent semantic analysis with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Figures 1 and 2).
-In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_means, fam_condition == "familiar")$emmean` ± `r filter(rating_means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_means, fam_condition == "matching")$emmean` ± `r filter(rating_means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
-In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_means, fam_condition == "nonmatching")$emmean` ± `r filter(rating_means, fam_condition == "nonmatching")$SE`), $t$(`r print_dof(filter(rating_contrasts, contrast == "matching - nonmatching")$df)`) = `r filter(rating_contrasts, contrast == "matching - nonmatching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_contrasts, contrast == "matching - nonmatching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.]{color="blue"}
+In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_stats$means, fam_condition == "familiar")$emmean` ± `r filter(rating_stats$means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_stats$means, fam_condition == "matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
+In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_stats$means, fam_condition == "non-matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "non-matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "matching - non-matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "matching - non-matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "matching - non-matching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.]{color="blue"}
 
@@
 # Create Figure 1
-plot_fig1(files_dir, evokeds, config, channel_locations, models)
+plot_fig1(misc_dir, evokeds, config, channel_locations, models)
 ```
@@
 # Create Figure 2
-plot_fig2(files_dir, evokeds, config, channel_locations, models)
+plot_fig2(misc_dir, evokeds, config, channel_locations, models)
 ```

### 2023-03-13 src/plot_erps.R

@@ -1,0 +1,638 @@
+plot_fig1a <- function(files_dir, condition_colors) {
+  #' Creates a plot showing the trial structure of the EEG experiment
+
+  require(tidyverse)
+  require(cowplot)
+
+  example_stim <- magick::image_read(here::here("example_stimuli", "103.png"))
+  stim_bg_color <- "#a9d9ff"
+  ggplot() +
+    coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
+    theme_void() +
+    theme(aspect.ratio = 0.5) +
+    ## INSIGHT PHASE ##
+    # Title
+    annotate(
+      geom = "text", x = 0, y = 97.2, label = "Insight phase", size = 14 / .pt,
+      family = "Helvetica", fontface = "bold"
+    ) +
+    # Arrow
+    annotate(
+      geom = "segment", x = -30, xend = 24, y = 79, yend = 85,
+      arrow = arrow(length = unit(0.1, "inches"))
+    ) +
+    # Squares
+    annotate(
+      geom = "rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75,
+      color = "black", fill = stim_bg_color
+    ) +
+    annotate(
+      geom = "rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65,
+      color = condition_colors[2], fill = stim_bg_color
+    ) +
+    annotate(
+      geom = "rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89,
+      color = condition_colors[1], fill = stim_bg_color
+    ) +
+    annotate(
+      geom = "rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79,
+      color = "black", fill = stim_bg_color
+    ) +
+    annotate(
+      geom = "rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81,
+      color = "black", fill = stim_bg_color
+    ) +
+    annotate(
+      geom = "text", x = -27, y = 65.3, label = "+", size = 20 / .pt,
+      family = "Helvetica"
+    ) +
+    annotate(
+      geom = "text", x = -9, y = 55, label = "message\nsignaling",
+      family = "Helvetica", color = condition_colors[2]
+    ) +
+    annotate(
+      geom = "text", x = -9, y = 79, label = "potatoes\nmashing",
+      family = "Helvetica", color = condition_colors[1]
+    ) +
+    annotate(
+      geom = "text", x = 9, y = 67, label = "*", size = 30 / .pt,
[…]

### 2023-03-13 src/plot_tfr.R

@@ -1,0 +1,133 @@
+plot_tfr_topos <- function(tfr_grand_ave,
+                           tfr_clusters,
+                           p_cluster,
+                           conditions = c("Informed", "Uninformed"),
+                           condition_colors = c("#ca0020", "#0571b0"),
+                           topo_palette = "RdBu",
+                           tmin = -0.4,
+                           tmax = 1.4,
+                           tstep = 0.2,
+                           fmin = 4,
+                           fmax = 40,
+                           fstep = 4) {
+  #' Plots a grid of topographies for all time windows and frequency bins
+
+  require(dplyr)
+  require(cowplot)
+
+  tmins <- seq(tmin, tmax - tstep, tstep)
+  fmins <- seq(fmin, fmax - fstep, fstep)
+
+  channels <- unique(tfr_clusters$channel)
+  tfr_grand_ave_plus <- filter(tfr_grand_ave, condition == conditions[1])
+  tfr_grand_ave_minus <- filter(tfr_grand_ave, condition == conditions[2])
+  tfr_grand_ave_diff <- mutate(tfr_grand_ave_plus, condition = "Difference")
+  tfr_grand_ave_diff[channels] <- tfr_grand_ave_plus[channels] -
+    tfr_grand_ave_minus[channels]
+
+  plotlist <- map(tmins, function(tmin) {
+    tmax <- tmin + tstep
+
+    plotlist <- map(fmins, function(fmin) {
+      fmax <- fmin + fstep
+
+      significant_channels <- tfr_clusters %>%
+        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
+        filter(p_val < p_cluster) %>%
+        pull(channel) %>%
+        unique()
+
+      topo <- tfr_grand_ave_diff %>%
+        filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
+        pivot_longer(
+          cols = all_of(channels), names_to = "electrode",
+          values_to = "power"
+        ) %>%
+        mutate(power = power * 100) %>% # Convert from decimal to percent
+        left_join(channel_locations, by = c("electrode" = "channel")) %>%
+        group_by(electrode, x, y) %>%
+        summarise(power = mean(power), .groups = "drop") %>%
+        eegUtils::topoplot(
+          r = 85,
+          quantity = "power",
+          contour = FALSE,
+          interp_limit = "skirt",
[…]

### 2023-03-13 src/ratings.R

@@ -1,0 +1,364 @@
+compute_lsa <- function(rating_file, keywords, word2vec_file) {
+  #' Computes cosine similarities between rating study and experiment keywords
+
+  require(here)
+  require(readr)
+  require(dplyr)
+  require(stringr)
+  require(purrr)
+  require(tidyr)
+
+  rating_substantives <- select(rating_raw, S001_01:S242_01)
+  rating_verbs <- select(rating_raw, V001_01:V242_01)
+
+  rating_n <- nrow(rating_raw)
+  keywords_for_rating <- keywords %>%
+    arrange(familiarity, filename) %>%
+    select(item_id, familiarity, filename, match, nonmatch) %>%
+    replicate(rating_n, ., simplify = FALSE) %>%
+    bind_rows()
+
+  word2vec <- load_word2vec(word2vec_file)
+
+  rating <-
+    map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
+    mutate(participant_id = rating_raw$CASE) %>%
+    pivot_longer(
+      -participant_id,
+      names_to = "question_id", values_to = "response"
+    ) %>%
+    bind_cols(keywords_for_rating, .) %>%
+    pivot_longer(
+      c(match, nonmatch),
+      names_to = "condition", values_to = "keywords"
+    ) %>%
+    mutate(
+      condition = ifelse(condition == "match", "matching", "non-matching"),
+      across(c(keywords, response), str_to_lower),
+      keywords = str_replace_all(keywords, keywords_corrections),
+      response = str_replace_all(response, response_corrections),
+      cosine = compute_cosine(keywords, response, word2vec)
+    )
+
+  write_csv(rating, rating_file)
+}
+
+load_word2vec <- function(vectors_file) {
+  #' Loads a word2vec embedding space trained on the German wikipedia
+  #'
+  #' See https://www.deepset.ai/german-word-embeddings
+
+  if (!file.exists(vectors_file)) {
+    options(timeout = 1800)
+    vectors_url <- "https://int-emb-word2vec-de-wiki.s3.eu-central-1.amazonaws.com/vectors.txt"
+    download.file(vectors_url, vectors_file)
+  }
+
[…]

### 2023-03-13 src/utls.R

@@ -1,0 +1,2 @@
+#' Helper function to format degrees of freedom in the paper
+print_dof <- function(x) format(round(x), big.mark = ",")

### 2023-03-16 manuscript.Rmd
Proofreading

@@
 Consistent with previous work, this suggests that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component, event-related power).
-Our study is the first to show that such effects [do not require an extensive learning history but are rather observed immediately after semantic information has been provided for the first time.]{color="blue"}
+Our study is the first to show that such effects [occur instantly after semantic information has been provided for the first time, without requiring  extensive learning.]{color="blue"}
 
@@
 It is less clear, however, if this tentative top-down effect of semantic cognition on perception acts in an online fashion (i.e., directly modulating perceptual processing), or more indirectly, by altering stored visual [memory]{color="blue"} representations over the course of learning, which would then get reactivated once the object is reencountered later on.
-[The first account (i.e., an online top-down effect) would be in accordance with predictive processing theories that posit that higher-level areas influence ongoing perceptual processing by sending predictions down to lower-level areas [e.g., @rao1999; @friston2009; @clark2013; @lupyan2015].
+[The first account (i.e., an online top-down effect) would be in accordance with predictive coding theories that posit that higher-level areas influence ongoing perceptual processing by sending predictions down to lower-level areas [e.g., @rao1999; @friston2009; @clark2013; @lupyan2015].
 The second account (i.e., re-activation of stored memory representations) would argue against such online effects, positing that differences in ERPs emerge merely due to comparisons with visual memory representations or prototypes that have been built up over the course of learning [e.g., @palmeri2008].]{color="blue"}
@@
 
-[As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
-We used latent semantic analysis with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Figures 1 and 2).
+[As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years; none took part in the main study) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
+We used latent semantic analysis [@gunther2019] with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Figures 1 and 2).
 In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_stats$means, fam_condition == "familiar")$emmean` ± `r filter(rating_stats$means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_stats$means, fam_condition == "matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
@@
 
-In addition to the software mentioned above, our code relies on the tidyverse set of R packages [Version `r as.character(packageVersion("tidyverse"))`\; @R-tidyverse] for data wrangling, the ggplot2 [Version `r as.character(packageVersion("ggplot2"))`\; @R-ggplot2], cowplot [Version `r as.character(packageVersion("cowplot"))`\; @R-cowplot], and eegUtils [Version `r as.character(packageVersion("eegUtils"))`\; @R-eegUtils] packages for visualization, and the papaja package [Version `r as.character(packageVersion("papaja"))`\; @R-papaja] for statistical reporting.
+In addition to the software mentioned above, our code relies on the tidyverse set of R packages [Version `r as.character(packageVersion("tidyverse"))`\; @R-tidyverse] for data wrangling, the ggplot2 [Version `r as.character(packageVersion("ggplot2"))`\; @R-ggplot2], cowplot [Version `r as.character(packageVersion("cowplot"))`\; @R-cowplot], and eegUtils [Version `r as.character(packageVersion("eegUtils"))`\; @R-eegUtils] packages for visualization, the papaja package [Version `r as.character(packageVersion("papaja"))`\; @R-papaja] for statistical reporting, [and the LSAfun package [Version `r as.character(packageVersion("LSAfun"))`\; @gunther2015] for the latent semantic analysis of the online rating study data]{color="blue"}.
 We used the workflow developed by @peikert2021 to ensure the long-term reproducibility of our analysis pipeline.
@@
 Second, these effects were not just observed when comparing semantically informed perception (with matching keywords) and uninformed perception (with non-matching keywords), but also when comparing semantically informed perception with unsuccessfully informed perception.
-Whereas priming might have been present in the first comparison, in the second comparison all objects were preceded by keywords that matched the function of the object to a similar degree.
-The fact that P1 and N170 amplitudes still differed between these two conditions makes it unlikely that the semantic effects that we have found are fully reducible to priming.]{color="blue"}
+Whereas priming might have been present in the first comparison, in the second comparison all objects were preceded by keywords that matched the function of the object to a similar degree, making semantic priming less likely.
+Third, the results from an online rating study (see Materials and Methods; Supplementary Figure 1) indicated that people by and large did not spontaneously associate the unfamiliar objects with a particular function, and also allowed us to statistically control for the closeness of peoples’ guesses and the true function of each object.]{color="blue"}
 

### 2023-03-16 misc/helper_functions.R
Clean up old files

@@ -1,873 +1,0 @@
-# Helper function to create trial structure plots (Figure 1A)
-plot_fig1a <- function(files_dir, condition_colors) {
-  # Make sure that packages are loaded
-  require(tidyverse)
-  require(cowplot)
-
-  # Trial structure
-  example_stim <- magick::image_read(here::here("example_stimuli", "103.png"))
-  stim_bg_color <- "#a9d9ff"
-  ggplot() +
-    coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
-    theme_void() +
-    theme(aspect.ratio = 0.5) +
-    ## INSIGHT PHASE ##
-    # Title
-    annotate(
-      geom = "text", x = 0, y = 97.2, label = "Insight phase", size = 14 / .pt,
-      family = "Helvetica", fontface = "bold"
-    ) +
-    # Arrow
-    annotate(
-      geom = "segment", x = -30, xend = 24, y = 79, yend = 85,
-      arrow = arrow(length = unit(0.1, "inches"))
-    ) +
-    # Squares
-    annotate(
-      geom = "rect", xmin = -37, xmax = -17, ymin = 55, ymax = 75,
-      color = "black", fill = stim_bg_color
-    ) +
-    annotate(
-      geom = "rect", xmin = -19, xmax = 1, ymin = 45, ymax = 65,
-      color = condition_colors[2], fill = stim_bg_color
-    ) +
-    annotate(
-      geom = "rect", xmin = -19, xmax = 1, ymin = 69, ymax = 89,
-      color = condition_colors[1], fill = stim_bg_color
-    ) +
-    annotate(
-      geom = "rect", xmin = -1, xmax = 19, ymin = 59, ymax = 79,
-      color = "black", fill = stim_bg_color
-    ) +
-    annotate(
-      geom = "rect", xmin = 17, xmax = 37, ymin = 61, ymax = 81,
-      color = "black", fill = stim_bg_color
-    ) +
-    annotate(
-      geom = "text", x = -27, y = 65.3, label = "+", size = 20 / .pt,
-      family = "Helvetica"
-    ) +
-    annotate(
-      geom = "text", x = -9, y = 55, label = "message\nsignaling",
-      family = "Helvetica", color = condition_colors[2]
-    ) +
-    annotate(
-      geom = "text", x = -9, y = 79, label = "potatoes\nmashing",
-      family = "Helvetica", color = condition_colors[1]
-    ) +
-    annotate(
[…]

### 2023-03-16 manuscript.Rmd
Refactor code to source files

--- 2023-03-16 manuscript.Rmd
@@
 ```{r, eeg_processing, include=FALSE}
-# Define function for processing behavioral log files
-read_log <- function(log_file) {
-  # Read the file
-  log <- read_tsv(
-    log_file,
-    col_types = cols(),
-    locale = locale(encoding = "latin1"),
-    progress = FALSE
-  ) %>%
-    # Recode some columns
-    transmute(
-
-      # Phase of the experiment
-      phase = factor(
-        Wdh,
-        levels = c(211, 212, 213),
-        labels = c("Pre-insight", "Insight", "Post-insight")
-      ),
-
-      # Unfamiliar versus familiar objects
-      familiarity = factor(
-        bek_unbek,
-        levels = c("bekannt", "unbekannt"),
-        labels = c("familiar", "unfamiliar")
-      ),
-
-      # Matching versus non-matching keywords for unfamiliar objects
-      keywords = factor(
-        Bed,
-        levels = c("richtig", "falsch"),
-        labels = c("Match", "Non-match")
-      ),
-
-      # Behavioral responses
-      # Response code 201: "I know what this is or have a strong assumption"
-      # Response code 202: "I have an assumption what this is"
-      # Response code 203: "I have rather no assumption what this is"
-      # Response code 204: "I don't know what this is and have no assumption"
-      # Response code 0: Technical glitch
-      response = Tastencode,
-
-      # Reaction times
-      rt = RT,
-
-      # Item IDs
-      item_id = factor(StimID)
-    ) %>%
-    # Remove filler items
-    filter(familiarity == "unfamiliar")
-
-  # Assign items to conditions based on manipulation (matching vs. non-
-  # matching keywords) and the responses of the participants
-  items_per_condition <- with(log, {
-    list(
-
-      # Informed condition: Matching keywords and positive response
-      Informed = item_id[
-        phase == "Insight" & keywords == "Match" & response %in% c(201, 202)
-      ],
-
-      # Uninformed condition: Non-matching keywords and negative response
-      Uninformed = item_id[
-        phase == "Insight" & keywords == "Non-match" & response %in% c(203, 204)
-      ],
-
-      # Exclude: Matching keywords and negative response
-      Unsuccessful = item_id[
-        phase == "Insight" & keywords == "Match" & response %in% c(203, 204)
-      ],
-
-      # Exclude: Non-matching keywords and positive response
-      Exclude_uninformed = item_id[
-        phase == "Insight" & keywords == "Non-match" & response %in% c(201, 202)
-      ],
-
-      # Exclude: Positive response *before* any info was presented
-      Exclude_known = item_id[phase == "Pre-insight" & response == 201],
-
-      # Exclude: Technical glitch
-      Exclude_glitch = item_id[phase == "Insight" & response == 0]
-    )
-  })
-
-  # Assign these conditions to the trials of all three phases
-  log$condition <- NA
-  for (condition in names(items_per_condition)) {
-    item_id <- items_per_condition[[condition]]
-    log$condition[log$item_id %in% item_id] <- condition
-  }
-
-  # Sort columns
-  log %>%
-    select(item_id, phase, condition, response, rt)
-}
-
-# Get list of behavioral log files
+# (Re-)do the EEG preprocessing if requested
+if (run$eeg_processing) {
+  # List behavioral log files and raw EEG files
   log_files <- c(
@@
   )
-
-# Get list of BrainVision EEG header files
   vhdr_files <- c(
@@
 
-# Import EEG pipeline from Python
-pipeline <- import("pipeline")
-
-# Extract versions of Python packages
-pipeline_version <- pipeline$`__version__`
-mne_version <- import("mne")$`__version__`
-
-# (Re-)do the actual preprocessing if requested
-if (run$eeg_processing) {
   # Process behavioral data
@@
   # Process EEG data
+  pipeline <- import("pipeline")
   res <- pipeline$group_pipeline(
@@
 # Compute number of objects per condition for each participant
-objects_per_condition <- with(trials, table(participant_id, condition)) %>%
-  `/`(3) %>%
+objects_per_condition <- table(trials$participant_id, trials$condition) %>%
+  `/`(3) %>% # Each object is shown three times
   as.data.frame.matrix() %>%
@@
 
-# Read by-participant ERP averages and channel locations
+# Read by-participant ERP averages
 evokeds <- read_csv(here(output_dir, "ave.csv")) %>%
@@
 
-# Define helper function for fitting linear mixed models and computing contrasts
-fit_mixed_models <- function(dep, formula, data) {
-  # Modify the formula such that fixed effects are always retained
-  formula <- formula %>%
-    tabulate.formula() %>%
-    mutate(block = replace(block, is.na(grouping), "fixed"))
-
-  # Start a CPU cluster so that multiple models can be fitted in parallel
-  n_cores <- detectCores()
-  cl <- makeCluster(n_cores)
-
-  # Find the best fitting model (see Matuschek et al., 2017, *JML*)
-  build <- buildmer(
-    buildmerControl = buildmerControl(
-      formula, data,
-      args = list(control = lme4::lmerControl(
-        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
-      )),
-      direction = c("backward", "backward"),
-      cl = cl,
-      elim = LRTalpha(.20),
-      calc.anova = TRUE,
-      ddf = "Satterthwaite",
-      dep = dep
-    )
-  )
-  stopCluster(cl)
-
-  # Compute marginal means and contrasts
-  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
-  emm_means <- emmeans(build@model, specs = c("phase", "condition"))
-  emm_contrasts <- contrast(
-    emm_means,
-    method = "trt.vs.ctrl", simple = "condition", reverse = TRUE
-  ) %>%
-    summary(by = "contrast", adjust = "bonferroni")
-
-  # Create list of returns
-  list(
-    model = build@model,
-    summary = build@summary,
-    anova = build@anova,
-    means = emm_means,
-    contrasts = emm_contrasts
-  )
-}
-
-# (Re-)do the actual model fitting if requested
-deps <- config$components$name
+# (Re-)fit linear mixed models if requested
 if (run$mixed_models) {
   # Fit the model for each ERP component
-  form_erps <- ~ phase * condition + cosine +
+  deps <- config$components$name
+  formula_erps <- ~ phase * condition + cosine +
     (phase * condition | participant_id) +
     (phase * condition | item_id)
-  models <- map(deps, fit_mixed_models, formula = form_erps, data = trials) %>%
+  models <- map(deps, fit_mixed_model, formula_erps, trials) %>%
     set_names(deps)
@@
   # Fit an additional control analysis model for the alpha/beta power
-  form_alpha_beta <- ~ phase * condition + rt + cosine +
+  formula_tfr <- ~ phase * condition + rt + cosine +
     (phase * condition | participant_id) +
     (phase * condition | item_id)
-  models$alpha_beta <- fit_mixed_models(
-    dep = "alpha_beta", formula = form_alpha_beta, data = trials
-  )
+  models$alpha_beta <- fit_mixed_model("alpha_beta", formula_tfr, trials)
 
@@
 # Extract relevant statistics to print in the main text
-anova_table <- models %>%
-  map(function(model) as_tibble(model$anova, rownames = "effect")) %>%
-  bind_rows(.id = "component") %>%
-  rename(f_value = `F value`, p_value = `Pr(>F)`)
-contrast_table <- models %>%
-  map(function(model) as_tibble(model$contrasts)) %>%
-  bind_rows(.id = "component") %>%
-  rename(t_value = `t.ratio`, p_value = `p.value`)
+anova_table <- extract_anova_table(models)
+contrast_table <- extract_contrast_table(models)
 ```
@@
 
-The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4)) based on the MNE-Python software [Version `r mne_version`\; @gramfort2013] in Python [Version `r py_version()`\; @vanrossum2009].
+The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4)) based on the MNE-Python software [Version `r config$package_versions$mne`\; @gramfort2013] in Python [Version `r config$package_versions$python`\; @vanrossum2009].
 First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
@@
   filter(tfr_grand_ave, phase == "Post-insight"),
-  filter(
-    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed"
-  ),
+  filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed"),
   p_cluster = p_cluster
@@
 # Print table of materials
-keywords %>%
-  filter(familiarity == "unfamiliar") %>%
-  transmute(
-    img = paste0(
-      "\\includegraphics[valign=c,width=18mm]{materials/unfamiliar_objects/",
-      filename,
-      "}"
-    ),
-    item_id = as.character(item_id),
-    match_translated = paste(match, match_en, sep = "\n") %>%
-      kableExtra::linebreak(align = "l", linebreaker = "\n"),
-    nonmatch_translated = paste(nonmatch, nonmatch_en, sep = "\n") %>%
-      kableExtra::linebreak(align = "l", linebreaker = "\n")
-  ) %>%
-  apa_table(
-    booktabs = TRUE,
-    col.names = c(
-      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
-    ),
-    escape = FALSE,
-    longtable = TRUE,
-    caption = "Unfamiliar Object Stimuli\\smallskip",
-    font_size = "footnotesize"
-  )
+print_materials_table(keywords)
 ```
@@
 ```{r, ress1a}
-# Helper function for printing model summary, ANOVA (F tests), and contrasts
-print_model_outputs <- function(model_object) {
-  model_object$summary$call$data <- NULL # Prevents cluttering the output
-  print(model_object$summary)
-  cat("\n")
-  print(model_object$anova)
-  cat("\nPairwise Contrasts (Simple Effects)\n")
-  print(model_object$contrasts)
-  cat("\n\n")
-}
-
-# Print model outputs
+# Print model outputs for P1
 print_model_outputs(models$P1)
@@
 ```{r, ress1b}
-# Print model outputs
+# Print model outputs for N170
 print_model_outputs(models$N170)
@@
 ```{r, ress1c}
-# Print model outputs
+# Print model outputs for N400
 print_model_outputs(models$N400)
@@
 ```{r, figs1, cache=FALSE, fig.height=5, fig.width=6, out.width="50%", fig.cap="(ref:figs1-caption)"}
-rating %>%
-  filter(!is.na(cosine)) %>%
-  mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
-  ggplot(aes(x = condition_comb, y = cosine, color = condition_comb)) +
-  geom_violin(fill = NA) +
-  geom_boxplot(width = 0.2) +
-  scale_y_continuous(limits = c(0.0, 1.0), breaks = seq(0.0, 1.0, by = 0.2)) +
-  scale_color_manual(values = c("#5e3c99", "#ca0020", "#0571b0")) +
-  labs(x = NULL, y = "Cosine distance to keywords") +
-  coord_cartesian(ylim = c(0.0, 1.0)) +
-  theme_classic() +
-  theme(
-    axis.title = element_text(color = "black", size = 10.9),
-    axis.text = element_text(color = "black", size = 10.9),
-    legend.position = "none",
-    panel.grid.major.y = element_line(),
-    panel.grid.minor.y = element_line()
-  )
+# Plot rating study results
+plot_figs1(rating)
 ```
@@
 ```{r, figs2, cache=FALSE, fig.height=5.5, fig.cap="(ref:figs2-caption)"}
-rating %>%
-  filter(!is.na(cosine) & condition == "matching") %>%
-  mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
-  select(item_id, condition_comb, cosine) %>%
-  group_by(item_id, condition_comb) %>%
-  summarize(
-    mean = mean(cosine),
-    sd = sd(cosine),
-    n = n(),
-    se = sd / sqrt(n),
-    .groups = "drop"
-  ) %>%
-  mutate(item_id = fct_reorder(item_id, desc(mean))) %>%
-  ggplot(
-    aes(
-      x = item_id, y = mean, color = condition_comb, group = 1,
-      ymin = mean - se, ymax = mean + se
-    )
-  ) +
-  geom_linerange(show.legend = FALSE) +
-  geom_line() +
-  labs(x = "Stimulus ID", y = "Cosine distance to keywords", color = NULL) +
-  scale_x_discrete(guide = guide_axis(angle = 90, n.dodge = 3)) +
-  scale_y_continuous(limits = c(0.0, 1.0), breaks = seq(0.0, 1.0, by = 0.2)) +
-  scale_color_manual(values = c("#5e3c99", "#ca0020")) +
-  theme_classic() +
-  theme(
-    axis.title = element_text(color = "black", size = 10.9),
-    axis.text = element_text(color = "black", size = 10.9),
-    legend.position = c(0.93, 0.92),
-    panel.grid.major.x = element_line(),
-    panel.grid.major.y = element_line(),
-    panel.grid.minor.y = element_line()
-  )
+# Plot rating study result on the item level
+plot_figs2(rating)
 ```
@@
   filter(tfr_grand_ave, phase == "Pre-insight"),
-  filter(
-    tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed"
-  ),
+  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed"),
   p_cluster = p_cluster
@@
   filter(tfr_grand_ave, phase == "Pre-insight"),
-  filter(
-    tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful"
-  ),
+  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful"),
   p_cluster = p_cluster,
@@
   filter(tfr_grand_ave, phase == "Insight"),
-  filter(
-    tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful"
-  ),
+  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful"),
   p_cluster = p_cluster,
@@
   filter(tfr_grand_ave, phase == "Post-insight"),
-  filter(
-    tfr_clusters,
-    contrast == "Post-insight/Informed - Post-insight/Unsuccessful"
-  ),
+  filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Unsuccessful"),
   p_cluster = p_cluster,

### 2023-03-16 src/behavior.R

@@ -1,0 +1,67 @@
+read_log <- function(log_file) {
+  #' Read and preprocess a behavioral log file from Presentation
+
+  require(readr)
+  require(dplyr)
+
+  log <- read_tsv(
+    log_file,
+    col_types = cols(),
+    locale = locale(encoding = "latin1"),
+    progress = FALSE
+  ) %>%
+    transmute(
+      phase = factor(
+        Wdh,
+        levels = c(211, 212, 213),
+        labels = c("Pre-insight", "Insight", "Post-insight")
+      ),
+      familiarity = factor(
+        bek_unbek,
+        levels = c("bekannt", "unbekannt"),
+        labels = c("familiar", "unfamiliar")
+      ),
+      keywords = factor(
+        Bed,
+        levels = c("richtig", "falsch"),
+        labels = c("Match", "Non-match")
+      ),
+      # Response code 201: "I know what this is or have a strong assumption"
+      # Response code 202: "I have an assumption what this is"
+      # Response code 203: "I have rather no assumption what this is"
+      # Response code 204: "I don't know what this is and have no assumption"
+      # Response code 0: Technical glitch
+      response = Tastencode,
+      rt = RT,
+      item_id = factor(StimID)
+    ) %>%
+    filter(familiarity == "unfamiliar")
+
+  items_per_condition <- with(log, {
+    list(
+      Informed = item_id[
+        phase == "Insight" & keywords == "Match" & response %in% c(201, 202)
+      ],
+      Uninformed = item_id[
+        phase == "Insight" & keywords == "Non-match" & response %in% c(203, 204)
+      ],
+      Unsuccessful = item_id[
+        phase == "Insight" & keywords == "Match" & response %in% c(203, 204)
+      ],
+      Exclude_uninformed = item_id[
+        phase == "Insight" & keywords == "Non-match" & response %in% c(201, 202)
+      ],
+      Exclude_known = item_id[phase == "Pre-insight" & response == 201],
+      Exclude_glitch = item_id[phase == "Insight" & response == 0]
+    )
+  })
+
+  log$condition <- NA
+  for (condition in names(items_per_condition)) {
+    item_id <- items_per_condition[[condition]]
+    log$condition[log$item_id %in% item_id] <- condition
+  }
+
+  log %>%
+    select(item_id, phase, condition, response, rt)
+}

### 2023-03-16 src/mixed_models.R

@@ -1,0 +1,70 @@
+fit_mixed_model <- function(dep, formula, data) {
+  #' Computes a parsimonious mixed model and follow up contrasts
+
+  require(buildmer)
+  require(emmeans)
+  require(parallel)
+  require(dplyr)
+
+  formula <- formula %>%
+    tabulate.formula() %>%
+    mutate(block = replace(block, is.na(grouping), "fixed"))
+
+  n_cores <- detectCores()
+  cl <- makeCluster(n_cores)
+
+  # See Matuschek et al. (2017), https://doi.org/10.1016/j.jml.2017.01.001
+  build <- buildmer(
+    buildmerControl = buildmerControl(
+      formula, data,
+      args = list(control = lme4::lmerControl(
+        optimizer = "bobyqa", optCtrl = list(maxfun = 1e6)
+      )),
+      direction = c("backward", "backward"),
+      cl = cl,
+      elim = LRTalpha(.20),
+      calc.anova = TRUE,
+      ddf = "Satterthwaite",
+      dep = dep
+    )
+  )
+  stopCluster(cl)
+
+  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
+  emm_means <- emmeans(build@model, specs = c("phase", "condition"))
+  emm_contrasts <- contrast(
+    emm_means,
+    method = "trt.vs.ctrl", simple = "condition", reverse = TRUE
+  ) %>%
+    summary(by = "contrast", adjust = "bonferroni")
+
+  list(
+    model = build@model,
+    summary = build@summary,
+    anova = build@anova,
+    means = emm_means,
+    contrasts = emm_contrasts
+  )
+}
+
+extract_anova_table <- function(models) {
+  #' Extracts table of ANOVA (Type III) outputs from fitted models
+
+  require(dplyr)
+  require(purrr)
+
+  map(models, function(model) as_tibble(model$anova, rownames = "effect")) %>%
+    bind_rows(.id = "component") %>%
+    rename(f_value = `F value`, p_value = `Pr(>F)`)
+}
+
+extract_contrast_table <- function(models) {
+  #' Extracts table of follow-up contrast outputs from fitted models
+
+  require(dplyr)
+  require(purrr)
+
+  map(models, function(model) as_tibble(model$contrasts)) %>%
+    bind_rows(.id = "component") %>%
+    rename(t_value = `t.ratio`, p_value = `p.value`)
+}

### 2023-03-16 src/plot_rating.R

@@ -1,0 +1,70 @@
+plot_figs1 <- function(rating) {
+  #' Plots rating study results as a violin plot
+
+  require(dplyr)
+  require(stringr)
+  require(ggplot2)
+
+  rating %>%
+    filter(!is.na(cosine)) %>%
+    mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
+    ggplot(aes(x = condition_comb, y = cosine, color = condition_comb)) +
+    geom_violin(fill = NA) +
+    geom_boxplot(width = 0.2) +
+    scale_y_continuous(limits = c(0.0, 1.0), breaks = seq(0.0, 1.0, by = 0.2)) +
+    scale_color_manual(values = c("#5e3c99", "#ca0020", "#0571b0")) +
+    labs(x = NULL, y = "Cosine distance to keywords") +
+    coord_cartesian(ylim = c(0.0, 1.0)) +
+    theme_classic() +
+    theme(
+      axis.title = element_text(color = "black", size = 10.9),
+      axis.text = element_text(color = "black", size = 10.9),
+      legend.position = "none",
+      panel.grid.major.y = element_line(),
+      panel.grid.minor.y = element_line()
+    )
+}
+
+plot_figs2 <- function(rating) {
+  #' Plots rating study results on the item level (mean +/- standard error)
+
+  require(dplyr)
+  require(forcats)
+  require(stringr)
+  require(ggplot2)
+
+  rating %>%
+    filter(!is.na(cosine) & condition == "matching") %>%
+    mutate(condition_comb = str_to_sentence(paste(familiarity, condition))) %>%
+    select(item_id, condition_comb, cosine) %>%
+    group_by(item_id, condition_comb) %>%
+    summarize(
+      mean = mean(cosine),
+      sd = sd(cosine),
+      n = n(),
+      se = sd / sqrt(n),
+      .groups = "drop"
+    ) %>%
+    mutate(item_id = fct_reorder(item_id, desc(mean))) %>%
+    ggplot(
+      aes(
+        x = item_id, y = mean, color = condition_comb, group = 1,
+        ymin = mean - se, ymax = mean + se
+      )
+    ) +
+    geom_linerange(show.legend = FALSE) +
+    geom_line() +
+    labs(x = "Stimulus ID", y = "Cosine distance to keywords", color = NULL) +
+    scale_x_discrete(guide = guide_axis(angle = 90, n.dodge = 3)) +
[…]

### 2023-03-16 src/utils.R

@@ -1,0 +1,45 @@
+#' Helper function to format degrees of freedom in the paper
+print_dof <- function(x) format(round(x), big.mark = ",")
+
+print_materials_table <- function(keywords) {
+  #' Prints an APA-style formatted table of object stimuli and keywords
+
+  require(dplyr)
+
+  keywords %>%
+    filter(familiarity == "unfamiliar") %>%
+    transmute(
+      img = paste0(
+        "\\includegraphics[valign=c,width=18mm]{materials/unfamiliar_objects/",
+        filename,
+        "}"
+      ),
+      item_id = as.character(item_id),
+      match_translated = paste(match, match_en, sep = "\n") %>%
+        kableExtra::linebreak(align = "l", linebreaker = "\n"),
+      nonmatch_translated = paste(nonmatch, nonmatch_en, sep = "\n") %>%
+        kableExtra::linebreak(align = "l", linebreaker = "\n")
+    ) %>%
+    papaja::apa_table(
+      booktabs = TRUE,
+      col.names = c(
+        "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
+      ),
+      escape = FALSE,
+      longtable = TRUE,
+      caption = "Unfamiliar Object Stimuli\\smallskip",
+      font_size = "footnotesize"
+    )
+}
+
+print_model_outputs <- function(model_object) {
+  #' Prints model summary, ANOVA (F tests), and contrasts
+
+  model_object$summary$call$data <- NULL # Don't want to print the raw data
+  print(model_object$summary)
+  cat("\n")
+  print(model_object$anova)
+  cat("\nPairwise Contrasts (Simple Effects)\n")
+  print(model_object$contrasts)
+  cat("\n\n")
+}

### 2023-03-16 src/utls.R

@@ -1,2 +1,0 @@
-#' Helper function to format degrees of freedom in the paper
-print_dof <- function(x) format(round(x), big.mark = ",")

### 2023-03-21 manuscript.Rmd
Refactor `plot_tfr`

@@
   filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed"),
+  channel_locations = channel_locations,
   p_cluster = p_cluster
@@
   filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed"),
+  channel_locations = channel_locations,
   p_cluster = p_cluster
@@
   filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed"),
+  channel_locations = channel_locations,
   p_cluster = p_cluster
@@
   filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful"),
+  channel_locations = channel_locations,
   p_cluster = p_cluster,
@@
   filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful"),
+  channel_locations = channel_locations,
   p_cluster = p_cluster,
@@
   filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Unsuccessful"),
+  channel_locations = channel_locations,
   p_cluster = p_cluster,

### 2023-03-21 src/plot_tfr.R

@@ -1,9 +1,8 @@
 plot_tfr_topos <- function(tfr_grand_ave,
                            tfr_clusters,
-                           p_cluster,
+                           channel_locations,
+                           p_cluster = 0.05,
                            conditions = c("Informed", "Uninformed"),
-                           condition_colors = c("#ca0020", "#0571b0"),
-                           topo_palette = "RdBu",
                            tmin = -0.4,
                            tmax = 1.4,
                            tstep = 0.2,
@@ -13,12 +12,16 @@ plot_tfr_topos <- function(tfr_grand_ave,
   #' Plots a grid of topographies for all time windows and frequency bins
 
   require(dplyr)
+  require(tidyr)
+  require(purrr)
+  require(stringr)
+  require(ggplot2)
   require(cowplot)
 
   tmins <- seq(tmin, tmax - tstep, tstep)
   fmins <- seq(fmin, fmax - fstep, fstep)
 
-  channels <- unique(tfr_clusters$channel)
+  channels <- unique(channel_locations$channel)
   tfr_grand_ave_plus <- filter(tfr_grand_ave, condition == conditions[1])
   tfr_grand_ave_minus <- filter(tfr_grand_ave, condition == conditions[2])
   tfr_grand_ave_diff <- mutate(tfr_grand_ave_plus, condition = "Difference")
@@ -40,8 +43,7 @@ plot_tfr_topos <- function(tfr_grand_ave,
       topo <- tfr_grand_ave_diff %>%
         filter(time >= tmin & time < tmax & freq >= fmin & freq < fmax) %>%
         pivot_longer(
-          cols = all_of(channels), names_to = "electrode",
-          values_to = "power"
+          cols = all_of(channels), names_to = "electrode", values_to = "power"
         ) %>%
         mutate(power = power * 100) %>% # Convert from decimal to percent
         left_join(channel_locations, by = c("electrode" = "channel")) %>%
@@ -55,12 +57,10 @@ plot_tfr_topos <- function(tfr_grand_ave,
           highlights = significant_channels,
           scaling = 1.1
         ) +
-        scale_fill_distiller(limits = c(-25.0, 25.0), palette = topo_palette) +
-        theme(
-          plot.margin = unit(rep(-0.2, 4), "cm"),
-          legend.position = "none"
-        )
[…]

### 2023-04-17 src/plot_erps.R
Fix example image file path

@@ -1,10 +1,12 @@
-plot_fig1a <- function(files_dir, condition_colors) {
+plot_fig1a <- function(materials_dir, condition_colors) {
   #' Creates a plot showing the trial structure of the EEG experiment
 
   require(tidyverse)
   require(cowplot)
 
-  example_stim <- magick::image_read(here::here("example_stimuli", "103.png"))
+  example_stim <- magick::image_read(
+    here::here(materials_dir, "unfamiliar_objects", "Kartoffelstampfer.png")
+  )
   stim_bg_color <- "#a9d9ff"
   ggplot() +
     coord_cartesian(xlim = c(-100, 100), ylim = c(0, 100), expand = FALSE) +
@@ -563,7 +565,7 @@ plot_erps <- function(evokeds,
     )
 }
 
-plot_fig1 <- function(files_dir,
+plot_fig1 <- function(materials_dir,
                       evokeds,
                       config,
                       channel_locations,
@@ -577,7 +579,7 @@ plot_fig1 <- function(files_dir,
   require(cowplot)
 
   plot_grid(
-    plot_fig1a(files_dir, condition_colors),
+    plot_fig1a(materials_dir, condition_colors),
     plot_erps(
       evokeds,
       config,
@@ -600,7 +602,7 @@ plot_fig1 <- function(files_dir,
     annotate("segment", x = 0.726, xend = 0.726, y = 0.55, yend = Inf)
 }
 
-plot_fig2 <- function(files_dir,
+plot_fig2 <- function(materials_dir,
                       evokeds,
                       config,
                       channel_locations,
@@ -614,7 +616,7 @@ plot_fig2 <- function(files_dir,
   require(cowplot)
 
   plot_grid(
-    plot_fig2a(files_dir, condition_colors),
+    plot_fig2a(materials_dir, condition_colors),
     plot_erps(
       evokeds,
       config,

### 2023-04-19 manuscript.Rmd
Update text to match revision

@@
 authornote: |  
-  Number of pages: ???
-
-  Number of figures: 4
-
-  Number of words: ??? (abstract), ??? (introduction), ??? (discussion)
+  Alexander Enge \orcidlink{0000-0003-0100-2297} [0000-0003-0100-2297](https://orcid.org/0000-0003-0100-2297), Rasha Abdel Rahman \orcidlink{0000-0002-8438-1570} [0000-0002-8438-1570](https://orcid.org/0000-0002-8438-1570).
 
   We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Abdel Rahman Lab for Neurocognitive Psychology for insightful discussions, Guido Kiecker for technical support, as well as Guillaume Thierry and one anonymous reviewer for their comments on a previous version of the paper.
-  This work was supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany’s Excellence Strategy (EXC 2002/1 "Science of Intelligence") project number 390523135 as well as grants AB277-5 and AB277-6 to R.A.R.
-
+  This work was supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany's Excellence Strategy (EXC 2002/1 "Science of Intelligence") project number 390523135 as well as grants AB277-5 and AB277-6 to R.A.R.
   The authors declare no competing financial interests.
@@
 documentclass     : "apa6"
-classoption       : "man,donotrepeattitle"
+classoption       : "doc,donotrepeattitle"
 fontsize          : "10pt"
@@
   - \usepackage{orcidlink}
+  - \usepackage{tcolorbox}
   - \usepackage[all]{nowidow}
-  - \captionsetup[figure]{belowskip=10pt}
-  - \captionsetup[figure]{font={small,stretch=1},textfont=normalfont}
+  - \captionsetup[figure]{aboveskip=10pt}
+  - \captionsetup[figure]{font={scriptsize,stretch=1},textfont=normalfont}
   - \captionsetup[figure]{labelfont=bf,labelsep=period,name=Figure}
@@
 opts_chunk$set(
+  fig.align = "center",
   fig.pos = "tp",
@@
 
+\smallskip\begin{center}\parbox{12.7cm}{
 Does our perception of an object change once we discover what function it serves?
-We showed human participants (*n* = 48) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in [uninformed]{color="blue"} perception.
+We showed human participants (\textit{n} = 48, 31 females and 17 males) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in uninformed perception.
 We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
-We found that semantically informed as compared to [uninformed]{color="blue"} perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
+We found that semantically informed as compared to uninformed perception was associated with larger amplitudes in the N170 component (150--200 ms), reduced amplitudes in the N400 component (400--700 ms), and a late decrease in alpha/beta band power.
 When the same objects were presented once more without any information, the N400 and event-related power effects persisted, and we also observed enlarged amplitudes in the P1 component (100--150 ms) in response to objects for which semantically informed perception had taken place.
 Consistent with previous work, this suggests that obtaining semantic information about previously unfamiliar objects alters aspects of their lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component, event-related power).
-Our study is the first to show that such effects [occur instantly after semantic information has been provided for the first time, without requiring  extensive learning.]{color="blue"}
-
-*Key words*: objects; semantic knowledge; visual perception; event-related potentials
-
-\bigskip
+Our study is the first to show that such effects occur instantly after semantic information has been provided for the first time, without requiring extensive learning.
+}\end{center}\bigskip
 
@@
 Does our perception of an object change once we discover what function it serves?
-This question speaks to the long-standing debate about the cognitive (im)penetrability of perception by higher-level capacities such as semantic knowledge or language [@pylyshyn1999].
-According to one view, these cognitive capacities kick in only after the retinal input has been processed by a specialized module for visual perception [@firestone2016; @fodor1983].
-This module is supposed to be encapsulated from higher-level inputs and processes visual information in a purely feed-forward fashion, progressing from lower areas with small receptive field sizes to areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
+This question speaks to the long-standing debate about the cognitive (im)penetrability of perception by higher-level capacities such as semantic knowledge or language.
+According to one view, these cognitive capacities kick in only after the retinal input has been processed by a specialized module for visual perception [@fodor1983].
+This module is supposed to be encapsulated from higher-level inputs and processes visual information in a feed-forward fashion, progressing from lower to higher areas representing increasingly complex shapes and, eventually, whole objects [@dicarlo2012].
+This cognitive impenetrability hypothesis is challenged by another view, namely predictive coding theories that posit that higher-level areas influence ongoing perceptual processing early on by sending predictions down to lower-level areas [@churchland1994; @ahissar2004; @friston2009; @yuille2006; @clark2013; @lupyan2015; @thierry2016; @teufel2017; @lupyan2020].
+This view is supported by differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], linguistic [e.g., @slivac2021] or semantic [e.g., @gauthier2003] content.
+However, some of these studies received legitimate criticism, e.g., because comparisons between critical conditions included the confound of additionally comparing different visual stimuli, or for not being able to distinguish between perceptual or post-perceptual loci of tentative top-down effects based on behavioral measures [@firestone2016].
 
-The cognitive impenetrability hypothesis is challenged by the alternative view that perception dynamically interacts with different cognitive aspects from early on [@churchland1994; @ahissar2004; @yuille2006; @clark2013; @lupyan2015; @thierry2016; @teufel2017; @lupyan2020].
-On the behavioral level, this is supported by psychological studies that found differences in ratings, detection rates, or reaction times for visual stimuli depending on their emotional [e.g., @phelps2016], motivational [e.g., @balcetis2010], linguistic [e.g., @slivac2021] or semantic [e.g., @gauthier2003] content.
-[However, some studies have received legitimate criticism for a number of reasons [@firestone2016].
-For example, tentative high-level effects (e.g., the emotional difference between a smiling and a neutral facial expression) were sometimes confounded with low-level visual differences (e.g., the difference in visual contrast introduced by one face showing their teeth and the other one not).
-As another example, studies that relied on behavioral measures such as reaction times were not able to discern effects of higher-level cognition on perception from effects that occur in later, post-perceptual stages of processing [e.g., easier recognition from memory for semantically meaningful stimuli, despite no change in how they are perceived visually\; @firestone2016].]{color="blue"}
-
-On the physiological level, event-related potentials (ERPs) measured from the human EEG can mitigate most of these concerns:
-Their temporal resolution makes it possible to probe how early one can detect influences of high-level (e.g., semantic) information [@athanasopoulos2020].
-To this end, participants in previous studies by our lab and others learned to associate visual objects with different amounts of semantic information.
-After learning, an orthogonal task was used to compare ERPs in response to objects learned with versus without semantic information.
-This revealed differences not only in late ERP components associated with semantic processing (i.e., the N400 component) but also in the visual P1 component [@abdelrahman2008; @maier2019; @samaha2018; @weller2019].
-The early peak of this component and its source in the occipital cortex [@abdelrahman2008] point to an immediate effect of semantic knowledge on visual perception.
-It is less clear, however, if this tentative top-down effect of semantic cognition on perception acts in an online fashion (i.e., directly modulating perceptual processing), or more indirectly, by altering stored visual [memory]{color="blue"} representations over the course of learning, which would then get reactivated once the object is reencountered later on.
-[The first account (i.e., an online top-down effect) would be in accordance with predictive coding theories that posit that higher-level areas influence ongoing perceptual processing by sending predictions down to lower-level areas [e.g., @rao1999; @friston2009; @clark2013; @lupyan2015].
-The second account (i.e., re-activation of stored memory representations) would argue against such online effects, positing that differences in ERPs emerge merely due to comparisons with visual memory representations or prototypes that have been built up over the course of learning [e.g., @palmeri2008].]{color="blue"}
+Here we employ event-related potentials (ERPs) measured from the human EEG to mitigate most of these concerns: The temporal resolution of ERPs makes it possible to probe how early influences of high-level (e.g., semantic) information can be detected [@athanasopoulos2020].
+When comparing objects after learning different amounts of semantic information about them, previous studies by our lab and others revealed differences in late ERP components associated with semantic processing (N400 component) and also in the visual P1 component [@abdelrahman2008; @samaha2018; @maier2019; @weller2019].
+The early peak of the P1 and its source in the occipital cortex [@abdelrahman2008] point to an early effect of semantic knowledge on visual perception.
+It is less clear, however, if this effect acts in an online fashion (i.e., directly modulating perceptual processing, in accordance with predictive coding theories), or more indirectly, by altering stored visual object representations over the course of learning, which would then get reactivated once the object is reencountered later on [i.e., reflecting offline differences in visual object representations or prototypes that have been built up over the course of learning\; @palmeri2008].
 
 To answer this question, we measured ERPs in response to unfamiliar objects directly while participants gained a semantic understanding of their function.
-We presented half of the objects together with matching keywords, thus allowing participants to understand what kind of object they were viewing, and the other half together with non-matching keywords, [thus preventing participants from understanding what kind of object they were viewing]{color="blue"}.
+We presented half of the objects with matching keywords, allowing participants to understand what kind of object they were viewing, and the other half with non-matching keywords, preventing participants from understanding what kind of object they were viewing.
 We then presented the same objects again to test for downstream effects of semantic information.
 We examined the influence of semantic information on ERPs associated with lower-level visual perception (P1 component), higher-level visual perception (N170 component), and semantic processing (N400 component).
-We hypothesized that semantic information would have instant effects on visual perception, by which we mean (a) that these effects can already be observed on the same trial as the semantic information is being presented for the first time, and (b) that these effects are found not only in later, higher-level cognition-related ERP components (i.e., N400), but also in earlier, perception-related ERP components (i.e., P1 and/or N170).
-[Observing these effects immediately after participants have received the relevant semantic information, instead of after an extensive learning phase as in previous studies, would speak for theories that posit an online influence of higher-level cognitive areas on lower-level visual perception [e.g., predictive coding\; @friston2009].]{color="blue"}
+We hypothesized that semantic information would have instant effects on visual perception, by which we mean (a) that these effects can be observed on the same trial as the semantic information is being presented for the first time, and (b) that these effects are found not only in later, higher-level cognition-related ERP components (N400), but also in earlier, perception-related ERP components (P1 and/or N170), which would speak for predictive coding theories.
 We furthermore conducted an exploratory time-frequency analysis to test for effects on event-related power which, unlike ERP effects, do not need to be tightly phase-locked to stimulus onset.
@@
 
-Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18--32 years) and no history of psychological disorder or treatment.
+Participants were 48 German native speakers (31 females and 17 males) with a mean age of 23.5 years (range 18--32 years) and no history of psychological disorder or treatment.
 No a priori power analysis was carried out.
@@
 These served as filler stimuli of no interest.
-The other 120 stimuli were rare objects presumed to be unfamiliar to the majority of participants (e.g., a galvanometer, an udu drum; [see Supplementary Table 1]{color="blue"}).
+The other 120 stimuli were rare objects presumed to be unfamiliar to most participants (e.g., a galvanometer, an udu drum; see Supplementary Table 1 at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc)).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
 At a standardized viewing distance of 90 cm, the images subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
-
-For each unfamiliar object, we created a pair of German keywords (a noun and a verb), describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., *Stromstärke, messen* [electric current, measuring]; *Tonpott, trommeln* [clay pot, drumming]; [see Supplementary Table 1]{color="blue"}).
-As our central experimental manipulation, half of the objects were presented together with keywords that matched their respective function, whereas the other half of the objects were presented together with non-matching keywords [that would have matched another object]{color="blue"}.
+For each unfamiliar object, we created a pair of German keywords (a noun and a verb), describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., Stromstärke, messen [electric current, measuring]; Tonpott, trommeln [clay pot, drumming]; see Supplementary Table 1).
+As our central experimental manipulation, half of the objects were presented together with keywords that matched their respective function, whereas the other half of the objects were presented together with non-matching keywords (which would have matched a different object).
 The matching keywords were expected to induce semantically informed perception, that is, participants suddenly understanding what kind of object they were viewing.
-The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically [uninformed]{color="blue"}.
+The non-matching keywords were expected to prevent such an understanding and keep the perception of the object semantically uninformed.
 All participants saw each unfamiliar object with only one type of keywords (matching or non-matching).
-This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to [uninformed]{color="blue"} perception) to an equal number of participants.
+This assignment of keywords to objects was counterbalanced across participants so that each object was presented with matching keywords (leading to semantically informed perception) and non-matching keywords (leading to uninformed perception) to an equal number of participants.
 The experiment was programmed and displayed using Presentation® software (Neurobehavioral Systems, Inc., Berkeley, CA, www.neurobs.com).
@@
 
-[As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years; none took part in the main study) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
-We used latent semantic analysis [@gunther2019] with a word2vec embedding (deepset GmbH, Berlin, Germany, www.deepset.ai/german-word-embeddings) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (Supplementary Figures 1 and 2).
+As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years; none took part in the main study) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
+We used latent semantic analysis [@gunther2019] with a word2vec embedding (deepset GmbH, Berlin, Germany, [www.deepset.ai/german-word-embeddings](www.deepset.ai/german-word-embeddings)) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (see Supplementary Figures 1 and 2).
 In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_stats$means, fam_condition == "familiar")$emmean` ± `r filter(rating_stats$means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_stats$means, fam_condition == "matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
-In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_stats$means, fam_condition == "non-matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "non-matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "matching - non-matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "matching - non-matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "matching - non-matching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.]{color="blue"}
+In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_stats$means, fam_condition == "non-matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "non-matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "matching - non-matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "matching - non-matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "matching - non-matching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.
 
@@
 (c) *Ich habe eher keine Vermutung, was das ist* [I rather have no assumption what this is], or
-(d) *Ich weiß nicht, was das ist, und habe auch keine Vermutung* [I don’t know what this is and have no assumption].
+(d) *Ich weiß nicht, was das ist, und habe auch keine Vermutung* [I don't know what this is and have no assumption].
 Participants were asked to respond as quickly and as accurately as possible by pressing one out of four buttons with the index or middle finger of their left or right hand, respectively.
@@
 # Create Figure 1
-plot_fig1(misc_dir, evokeds, config, channel_locations, models)
+plot_fig1(materials_dir, evokeds, config, channel_locations, models)
 ```
 
-(ref:fig1-caption) Experimental design and ERP results [contrasting semantically informed perception and uninformed perception]{color="blue"}.
+(ref:fig1-caption) Experimental design and ERP results contrasting semantically informed perception and uninformed perception.
 ***A***, In the pre-insight phase, participants were presented with 120 unfamiliar objects and indicated if they knew what kind of object they were viewing.
-In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to [uninformed]{color="blue"} perception.
+In the insight phase, half of these objects were presented with matching keywords (in red color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in blue color for illustration), leading to uninformed perception.
 In the post-insight phase, the same objects were presented again without keywords.
-***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (***B***), for the N170 component (***C***), and for the N400 component (***D***) for objects with semantically informed perception versus [uninformed]{color="blue"} perception within the three different phases.
+***B***, ***C***, ***D***, ERP waveforms and scalp topographies for the P1 component (***B***), for the N170 component (***C***), and for the N400 component (***D***) for objects with semantically informed perception versus uninformed perception within the three different phases.
 Semantically informed perception was associated with more negative amplitudes in the N170 component during the insight phase, less negative amplitudes in the N400 component during the insight and post-insight phases, and more positive amplitudes in the P1 component during the post-insight phase.
-[Waveform plots show the ERP amplitudes averaged across channels in the regions of interest (P1: PO3, PO4, POz, O1, O2, Oz; N170: P7, P8, PO7, PO8, PO9, PO10; N400: C1, C2, Cz, CP1, CP2, CPz; see black dots in the scalp topographies).]{color="blue"}
+Waveform plots show the ERP amplitudes averaged across channels in the regions of interest (P1: PO3, PO4, POz, O1, O2, Oz; N170: P7, P8, PO7, PO8, PO9, PO10; N400: C1, C2, Cz, CP1, CP2, CPz; see black dots in the scalp topographies).
 Colored ribbons around the ERP waveforms show ± 1 standard error of the mean across participants.
-[Topographies show the difference in ERP amplitudes at all channels on the scalp, averaged across the time windows of interest (P1: 100--150 ms, N170: 150--200 ms, N400: 400--700 ms; see gray areas in the ERP waveforms).]{color="blue"}
+Topographies show the difference in ERP amplitudes at all channels on the scalp, averaged across the time windows of interest (P1: 100--150 ms, N170: 150--200 ms, N400: 400--700 ms; see gray areas in the ERP waveforms).
 Ampl. = amplitude.
@@
 
-In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to [uninformed]{color="blue"} perception).
+In the *insight* phase, the 120 unfamiliar objects were presented for a second time, now preceded either by matching keywords (leading to semantically informed perception) or by non-matching keywords (leading to uninformed perception).
 Each trial consisted of a fixation cross presented for 0.5 s, followed by the presentation of the keywords for 2.5 s.
@@
 In total, the experiment consisted of 480 trials (120 familiar objects in the pre-insight phase and 120 unfamiliar objects in the pre-insight, insight, and post-insight phases).
-Participants took approximately 35 minutes to complete the entire experiment.
+Participants took approximately 35 minutes to complete the experiment.
 
@@
 
-[We used participants' behavioral responses to verify our experimental manipulation and to assign each object to a semantic condition.
+We used participants' behavioral responses to verify our experimental manipulation and to assign each object to a semantic condition.
 First, we used participants' responses from the pre-insight phase (when objects were presented for the first time, without keywords) to make sure that objects were indeed unfamiliar to them.
 That is, we excluded any objects for which participants responded with "I know what this is" in the pre-insight phase.
-Next, we used participants' responses from the insight phase (when objects were presented for the second time, preceded by keywords) to assign the remaining objects to different semantic conditions: Semantically informed perception, uninformed perception, and unsuccessfully informed perception (see Figure 1A and 2A).
+Next, we used participants' responses from the insight phase (when objects were presented for the second time, preceded by keywords) to assign the remaining objects to different semantic conditions: Semantically informed perception, uninformed perception, and unsuccessfully informed perception.
 The semantically informed condition consisted of objects that were presented with matching keywords and for which the participant responded with knowing what the object was or having an assumption.
@@
 The unsuccessfully informed condition consisted of objects that were presented with matching keywords but for which the participant responded with not knowing what the object was or having rather no assumption.
-The few objects that were presented with non-matching keywords but for which participants responded with knowing what the object was or having an assumption (i.e., "unsuccessfully uninformed" perception) were dropped from all further analyses.
 This assignment of objects to semantic conditions (informed, uninformed, or unsuccessfully informed) was carried over from the insight phase to the other two phases (pre-insight and post-insight).
-This allowed us to test, on the one hand, if the objects differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic information acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).]{color="blue"}
+This allowed us to test, on the one hand, if the objects differed in important aspects even before any keywords were presented (pre-insight phase) and, on the other hand, if the semantic information acquired in the insight phase had any down-stream effects on the subsequent perception of the objects (post-insight phase).
 
@@
 
-The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.4)) based on the MNE-Python software [Version `r config$package_versions$mne`\; @gramfort2013] in Python [Version `r config$package_versions$python`\; @vanrossum2009].
+The data were preprocessed offline using custom functions (available at [https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.5](https://github.com/alexenge/hu-neuro-pipeline/tree/v0.6.5)) based on the MNE-Python software [Version `r config$package_versions$mne`\; @gramfort2013] in Python [Version `r config$package_versions$python`\; @vanrossum2009].
 First, the data were downsampled to `r config$downsample_sfreq` Hz and re-referenced to the common average of all scalp channels.
@@
 
-The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because these models allow to control for repeated measures of participants and stimuli, while also being robust against an unbalanced number of trials per condition [@brown2021; @burki2018; @fromer2018].
+The resulting mean ERP amplitudes were analyzed on the single-trial level using linear mixed-effects regression models because these models allow to control for repeated measures of participants and stimuli, while also being robust against an unbalanced number of trials per condition [@burki2018; @fromer2018; @brown2021].
 We computed three models predicting P1, N170, and N400 amplitudes, respectively.
-All models included three fixed effects [of interest]{color="blue"}: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a custom contrast (i.e., subtracting the [uninformed]{color="blue"} condition from the informed condition [and the unsuccessfully informed condition from the informed condition]{color="blue"}, the intercept being the grand mean across [all three conditions]{color="blue"}), and (c) the two-way interaction of phase and condition.
-[We also added the results from the online pre-rating study (mean cosine distance between rating study-generated keywords and keywords presented in the main experiment) as an additional covariate of no interest (see Supplementary Figure 2).
-This was to control for the possibility that participants might have been partly familiar with some of the objects and/or able to guess their function from their visual appearance alone.]{color="blue"}
+All models included the following fixed effects of interest: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a custom contrast (i.e., subtracting the uninformed condition from the informed condition and the unsuccessfully informed condition from the informed condition, the intercept being the grand mean across all three conditions), and (c) the two-way interaction of phase and condition.
+We also added the results from the online pre-rating study (mean cosine distance between rating study-generated keywords and keywords presented in the main experiment) as an additional covariate of no interest (see Supplementary Figure 2).
+This was to control for the possibility that participants might have been partly familiar with some of the objects and/or able to guess their function from their visual appearance alone.
 For the random effects, we determined the most parsimonious structure supported by the data using the automatic procedure proposed by @matuschek2017.
@@
 
-To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the [uninformed]{color="blue"} condition within the pre-insight, insight, and post-insight phases.
-[In the same way, we computed pairwise comparisons contrasting the semantically informed condition against the unsuccessfully informed condition.]{color="blue"}
-This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for the three phases.
-All *p* values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
+To investigate if semantically informed perception had an influence on the ERPs within each phase of the experiment, we calculated pairwise comparisons contrasting the semantically informed condition against the uninformed condition within the pre-insight, insight, and post-insight phases.
+In the same way, we computed pairwise comparisons contrasting the semantically informed condition against the unsuccessfully informed condition.
+This was done using the emmeans package [Version `r as.character(packageVersion("emmeans"))`\; @R-emmeans] and with Bonferroni correction for the three phases of the experiment.
+All $p$ values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package [Version `r as.character(packageVersion("lmerTest"))`\; @R-lmerTest].
 
@@
 For statistical analysis of event-related power, we conducted cluster-based permutation tests [@maris2007], separately for each of the three phases of the experiment (pre-insight, insight, and post-insight).
-First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and [each of two control conditions (uninformed or unsuccessfully informed)]{color="blue"} for each participant.
+First, we averaged trials belonging to the same condition and then subtracted these average responses from one another to compute the difference between the semantically informed condition and each of two control conditions (uninformed or unsuccessfully informed) for each participant.
 We then conducted one-sample $t$ tests in a mass-univariate fashion and grouped significant results (cluster-forming threshold $p < .05$) into clusters if they occurred at neighboring time points, frequencies, or channels.
@@
 The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
-[The experimental stimuli (object images and keywords) and]{color="blue"} the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
+The experimental stimuli (object images and keywords) the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
 
-In addition to the software mentioned above, our code relies on the tidyverse set of R packages [Version `r as.character(packageVersion("tidyverse"))`\; @R-tidyverse] for data wrangling, the ggplot2 [Version `r as.character(packageVersion("ggplot2"))`\; @R-ggplot2], cowplot [Version `r as.character(packageVersion("cowplot"))`\; @R-cowplot], and eegUtils [Version `r as.character(packageVersion("eegUtils"))`\; @R-eegUtils] packages for visualization, the papaja package [Version `r as.character(packageVersion("papaja"))`\; @R-papaja] for statistical reporting, [and the LSAfun package [Version `r as.character(packageVersion("LSAfun"))`\; @gunther2015] for the latent semantic analysis of the online rating study data]{color="blue"}.
+In addition to the software mentioned above, our code relies on the tidyverse set of R packages [Version `r as.character(packageVersion("tidyverse"))`\; @R-tidyverse] for data wrangling, the ggplot2 [Version `r as.character(packageVersion("ggplot2"))`\; @R-ggplot2], cowplot [Version `r as.character(packageVersion("cowplot"))`\; @R-cowplot], and eegUtils [Version `r as.character(packageVersion("eegUtils"))`\; @R-eegUtils] packages for visualization, the papaja package [Version `r as.character(packageVersion("papaja"))`\; @R-papaja] for statistical reporting, and the LSAfun package [Version `r as.character(packageVersion("LSAfun"))`\; @gunther2015] for the latent semantic analysis of the online rating study data.
 We used the workflow developed by @peikert2021 to ensure the long-term reproducibility of our analysis pipeline.
@@
 
-[Based on the experimental manipulation (matching or non-matching keywords) and each individual participant's behavioral response (positive or negative regarding knowing what the object was), we assigned `r mean(objects_per_condition$Informed)` ± `r sd(objects_per_condition$Informed)` (mean ± standard deviation) objects to the semantically informed condition (i.e., matching keywords and positive response), `r mean(objects_per_condition$Uninformed)` ± `r sd(objects_per_condition$Uninformed)` objects to the uninformed condition (i.e., non-matching keywords and negative response), and `r mean(objects_per_condition$Unsuccessful)` ± `r sd(objects_per_condition$Unsuccessful)` objects to the unsuccessfully informed condition (i.e., matching keywords but negative response).
+Based on the experimental manipulation (matching or non-matching keywords) and each individual participant's behavioral response (positive or negative regarding knowing what the object was), we assigned `r mean(objects_per_condition$Informed)` ± `r sd(objects_per_condition$Informed)` (mean ± standard deviation) objects to the semantically informed condition (i.e., matching keywords and positive response), `r mean(objects_per_condition$Uninformed)` ± `r sd(objects_per_condition$Uninformed)` objects to the uninformed condition (i.e., non-matching keywords and negative response), and `r mean(objects_per_condition$Unsuccessful)` ± `r sd(objects_per_condition$Unsuccessful)` objects to the unsuccessfully informed condition (i.e., matching keywords but negative response).
 This assignment of objects to conditions was based solely on the insight phase of the experiment, when objects were presented with keywords for the first time, and carried over to analyze the data from the pre-insight and post-insight phases as well.
-The remaining objects were excluded due to an implausible response pattern (i.e., non-matching keywords but positive response; `r mean(objects_per_condition$Exclude_uninformed)` ± `r sd(objects_per_condition$Exclude_uninformed)` objects), due to being known to the participant in the pre-insight phase (i.e., before any keywords had been presented; `r mean(objects_per_condition$Exclude_known)` ± `r sd(objects_per_condition$Exclude_known)` objects), or because of technical errors (i.e., reaction times of 0 ms recorded by the presentation software, `r mean(objects_per_condition$Exclude_glitch)` ± `r sd(objects_per_condition$Exclude_glitch)` objects).]{color="blue"}
+The remaining objects were excluded due to an implausible response pattern (i.e., non-matching keywords but positive response; `r mean(objects_per_condition$Exclude_uninformed)` ± `r sd(objects_per_condition$Exclude_uninformed)` objects), due to being known to the participant in the pre-insight phase (i.e., before any keywords had been presented; `r mean(objects_per_condition$Exclude_known)` ± `r sd(objects_per_condition$Exclude_known)` objects), or because of technical errors (i.e., reaction times of 0 ms recorded by the presentation software, `r mean(objects_per_condition$Exclude_glitch)` ± `r sd(objects_per_condition$Exclude_glitch)` objects).
 
@@
 Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
-In addition, N400 amplitudes differed as a function of the condition (semantically informed[, uninformed, or unsuccessfully informed]{color="blue"}), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
+In addition, N400 amplitudes differed as a function of the condition (semantically informed, uninformed, or unsuccessfully informed), averaged across the three phases of the experiment, $F$(`r print_dof(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_dof(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
 Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
@@
 
-In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the [uninformed]{color="blue"} condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$p_value))` (see Figure 1B--D).
-[Likewise, there were no differences between the semantically informed condition and the unsuccessfully informed condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Unsuccessful")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Unsuccessful")$p_value))` (see Figure 2B--D).]{color="blue"}
-This was expected given that the keywords that would [provide additional semantic information]{color="blue"} had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
+In the pre-insight phase, when objects were unfamiliar to participants and presented without keywords, no differences emerged between the semantically informed condition and the uninformed condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Uninformed")$p_value))` (see Figure 1B--D).
+Likewise, there were no differences between the semantically informed condition and the unsuccessfully informed condition in any of the the ERP components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Unsuccessful")$t_value))`, all $p$s `r print_p(min(filter(contrast_table, phase == "Pre-insight" & contrast == "Informed - Unsuccessful")$p_value))` (see Figure 2B--D).
+This was expected given that the keywords that would provide additional semantic information had not yet been presented, and given that the assignment of objects to conditions was counterbalanced across participants as to control for low-level visual differences.
 
@@
 # Create Figure 2
-plot_fig2(misc_dir, evokeds, config, channel_locations, models)
+plot_fig2(materials_dir, evokeds, config, channel_locations, models)
 ```
 
-(ref:fig2-caption) [ERP results contrasting semantically informed perception and unsuccessfully informed perception.
+(ref:fig2-caption) ERP results contrasting semantically informed perception and unsuccessfully informed perception.
 ***A***, Assignment of objects to conditions based on participants' response in the insight phase of the experiment to unfamiliar objects presented with matching keywords.
@@
 Ampl. = amplitude.
-\*\*\* $p_\text{corr} < .001$.]{color="blue"}
+\*\*\* $p_\text{corr} < .001$.
 
-In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically [uninformed]{color="blue"}.
+In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically uninformed.
 Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`.
 There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Uninformed")$p_value)`.
-[The same effects were found when comparing objects with semantically informed perception to those objects that were also presented with matching keywords but for which participants still indicated not knowing what the object was (i.e., the unsuccessfully informed condition).
-Compared to these objects, semantically informed perception was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`, while there was no reliable difference in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`.]{color="blue"}
+The same effects were found when comparing objects with semantically informed perception to those objects that were also presented with matching keywords but for which participants still indicated not knowing what the object was (i.e., the unsuccessfully informed condition).
+Compared to these objects, semantically informed perception was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`, while there was no reliable difference in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight" & contrast == "Informed - Unsuccessful")$p_value)`.
 
@@
 Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$estimate` µV, $t$(`r print_dof(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight" & contrast == "Informed - Uninformed")$p_value)`.
-[These effects did not replicate when comparing the semantically informed condition to the unsuccessfully informed condition, with no reliable differences in the P1, N170, or N400 components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Post-insight" & contrast == "Informed - Unsuccessful")$t_value))`, all $p$s > `r print_p(min(filter(contrast_table, phase == "Post-insight" & contrast == "Informed - Unsuccessful")$p_value))`.]{color="blue"}
+These effects did not replicate when comparing the semantically informed condition to the unsuccessfully informed condition, with no reliable differences in the P1, N170, or N400 components, all $|t|$s < `r max(abs(filter(contrast_table, phase == "Post-insight" & contrast == "Informed - Unsuccessful")$t_value))`, all $p$s > `r print_p(min(filter(contrast_table, phase == "Post-insight" & contrast == "Informed - Unsuccessful")$p_value))`.
 
@@
 
-In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and [uninformed]{color="blue"} perception within each of the three phases of the experiment.
+In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and uninformed perception within each of the three phases of the experiment.
 Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 3), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
@@
 (ref:fig3-caption) Time-frequency results for the insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the uninformed condition, grand-averaged across participants.
 Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`).
@@
 (ref:fig4-caption) Time-frequency results for the post-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the uninformed condition, grand-averaged across participants.
 Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`).
 
-[We repeated this analysis to look for differences between semantically informed perception and unsuccessfully informed perception within each of the three phases of the experiment.
+We repeated this analysis to look for differences between semantically informed perception and unsuccessfully informed perception within each of the three phases of the experiment.
 There were no significant clusters in the pre- or post-insight phases (see Supplementary Figures 4 and 6), all $p$s > `r print_p(min(filter(tfr_clusters, contrast %in% c("Pre-insight/Informed - Pre-insight/Unsuccessful", "Post-insight/Informed - Post-insight/Unsuccessful"))$p_val))` but one significant cluster in the insight phase (see Supplementary Figure 5), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`.
-This cluster was similar to the ones described above in its latency, frequency range, and topographic distribution.]{color="blue"}
+This cluster was similar to the ones described above in its latency, frequency range, and topographic distribution.
 
@@
 
-We found that providing participants with semantic information about previously unfamiliar objects instantly led to enlarged (i.e., more negative) ERP amplitudes in the N170 component and reduced (i.e., less negative) ERP amplitudes in the N400 component.
-When the same objects were presented once more (without the semantic information), the N400 component remained reduced and the P1 component was now enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
-Finally, an exploratory time-frequency analysis revealed that semantically informed perception was accompanied by a late reduction in event-related power in the alpha and lower beta ranges.
+We found that providing participants once with semantic information about previously unfamiliar objects instantly led to enlarged (i.e., more negative) ERP amplitudes in the N170 component and reduced (i.e., less negative) ERP amplitudes in the N400 component.
+When the same objects were presented again, the N400 component remained reduced and the P1 component was now enlarged (i.e., more positive) in response to objects that had previously triggered semantically informed perception.
+An exploratory time-frequency analysis revealed that semantically informed perception was accompanied by a late reduction in event-related power in the alpha and lower beta ranges.
 
-The N400 effect during semantically informed perception indicates that acquiring an understanding of the objects lessened participants' demand for effortful semantic processing [@kutas2011].
-It replicates previous work showing that N400 amplitudes are larger in response to pictures when they are either difficult to understand in and of themselves [e.g., @supp2005; @abdelrahman2008] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
-The latency of this effect and the computational role of the N400 [@lau2008; @rabovsky2018; @bornkessel-schlesewsky2019] suggest a post-perceptual locus in the semantic system.
+The N400 effect indicates that acquiring an understanding of the object lessened participants' demand for semantic processing [@kutas2011].
+It replicates previous work showing larger N400 amplitudes for pictures when they are difficult to understand in and of themselves [e.g., @supp2005; @abdelrahman2008] or difficult to integrate into the preceding context [e.g., @barrett1990; @ganis1996; @hirschfeld2011].
+The latency of this effect suggests a post-perceptual locus in the semantic system.
 
-Our exploratory time-frequency analysis revealed a late (> 600 ms) reduction in post-stimulus power in the alpha and lower beta ranges (approx. 8--20 Hz).
-Like the N400 effect in the ERP, this change in event-related power occurred as soon as participants had received the relevant semantic information and recurred once the same objects were re-encountered without any semantic information.
-[Reductions in alpha/beta power have been shown to correlate with clearer representations of stimulus specific information, as measured using representational similarity analysis [@griffiths2019], and with successfully forming new semantic memories [@hanslmayr2009].
-This may be due to a dampening of alpha/beta oscillations which creates favorable conditions for high-level cortical information processing and encoding.]{color="blue"}
+Our exploratory time-frequency analysis revealed a late (> 600 ms) reduction in power in the alpha and lower beta ranges (approx. 8--20 Hz).
+Like the N400 effect, this occurred as soon as participants had received the semantic information and recurred once the objects were re-encountered without any semantic information.
+Reductions in alpha/beta power have been shown to correlate with clearer representations of stimulus specific information, as measured using representational similarity analysis [@griffiths2019], and with successfully forming new semantic memories [@hanslmayr2009].
+This may be due to a dampening of alpha/beta oscillations which creates favorable conditions for high-level cortical information processing and encoding.
 
-In contrast to the N400 and event-related power, the N170 component was modulated only on those initial trials on which the relevant semantic information was presented directly before the object.
+In contrast to the N400 and event-related power, the N170 was modulated only on those initial trials on which the relevant semantic information was presented directly before the object.
 It therefore constitutes an online marker of semantic insight, that is, of participants suddenly understanding the visual objects in the light of the information provided by the keywords.
-The N170 is typically associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002], [that is, it is sensitive to factors that go beyond structural encoding and categorical perception [@thierry2007; @thierry2007a; @dering2011; but see also @rossion2008]]{color="blue"}.
-It being enlarged during semantically informed perception may reflect that the semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
-This interpretation is supported by previous findings of enlarged N170 amplitudes for scrambled (schematic) face stimuli after participants had been shown the original version of the face [@bentin2002], as well as for line drawings of meaningful objects as compared to non-objects [@beaucousin2011].
-Together with the present study, these findings suggest an online impact of meaningfulness on the higher-level perception of visual objects, integrating across their visual features.
+The N170 is associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002], that is, it is sensitive to factors that go beyond structural encoding and categorical perception [@thierry2007, @thierry2007a; @dering2011].
+It being enlarged may reflect that the semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
+This is supported by previous findings of enlarged N170 amplitudes for scrambled face stimuli after participants had been shown the original version of the face [@bentin2002], as well as for line drawings of meaningful objects as compared to non-objects [@beaucousin2011].
+Together, this suggests an online impact of meaningfulness on the higher-level perception of visual objects, integrating across their visual features.
 
-The P1 component, unlike the N400 and N170 components, was modulated by semantic information only one trial after this information had been obtained.
-This is consistent with previous studies showing modulations of the P1 when participants had learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @samaha2018; @weller2019].
-What the present study adds is that the P1 effect does not take an extensive learning history to develop.
-Instead, it can be observed as soon as one trial after semantic insight has happened.
-Because the P1 is typically associated with lower-level sensory processing [@johannes1995; @pratt2011; @luck2014], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive its low-level features [@athanasopoulos2020].
+The P1, unlike the N400 and N170, was modulated by semantic information only one trial after this information had been obtained.
+This replicates previous studies showing modulations of the P1 when participants had learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018, @maier2019; @samaha2018; @weller2019].
+The present study adds that the P1 effect does not take an extensive learning history to develop; instead, it can be observed as soon as one trial after semantic insight has happened.
+Because the P1 is associated with lower-level sensory processing [@johannes1995; @pratt2011; @luck2014], we take its susceptibility to semantic information as an indicator that knowledge about the function of an object can change how we perceive its low-level features [@athanasopoulos2020].
 
-Both the N170 and the P1 components therefore seem to be sensitive to the semantic meaningfulness of visual objects.
-The finding that these two components were modulated in different phases of our experimental design suggests that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
-The time course of the N170 is consistent with a top-down influence of (non-visual) areas in the prefrontal and temporal-parietal cortices on visual areas, whereas modulations of the P1 component seem to reflect recurrent processing within the visual system [@wyatte2014].
-Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter pathway seems to take at least one additional encounter with the visual object to emerge.
-While the limited spatial resolution of the EEG precludes precise localization, there is converging fMRI and psychophysical evidence that semantic information can feed back into higher-level areas in the lateral occipital cortex (LOC) as well as early retinotopic cortex [areas V1, V2, and V3\; @hsieh2010; @clarke2016; @teufel2018], consistent with the neural generators of the N170 and P1 components in the ERP.
+The P1 and N170 were modulated in different phases of our study, suggesting that they reflect different aspects of top-down processing with different time courses and neuroanatomical implementations.
+The time course of the N170 is consistent with a top-down influence of non-visual areas in the prefrontal and temporo-parietal cortices on visual areas, whereas modulations of the P1 component may reflect recurrent processing within the visual system [@wyatte2014].
+Here we could show that the former pathway seems to be able to convey semantic information instantaneously (i.e., within the same trial), whereas the latter pathway seems to take at least one additional encounter with the object to emerge.
+While the limited spatial resolution of the EEG precludes localization, there is converging fMRI and psychophysical evidence that semantic information can feed back into areas in the lateral occipital cortex (LOC) as well as early retinotopic cortex [areas V1, V2, and V3\; @hsieh2010; @clarke2016; @teufel2018], consistent with the neural generators of the N170 and P1 in the ERP.
 
-The top-down modulation of visual ERPs by semantic information challenges a modular view of visual perception [@fodor1983; @pylyshyn1999; but see @clarke2021].
-Proponents of this view have pointed out important shortcomings of previous studies that had claimed to demonstrate top-down effects of cognition on perception [@firestone2016; @machery2015].
-We addressed as many of these shortcomings as possible:
-First, no difference between conditions had been present before any semantic information was presented.
-Second, we used ERPs as an objective and time-resolved measure to disentangle perceptual and post-perceptual effects.
-Third, we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to participants and by including well-known objects as filler stimuli.
-Fourth, we precluded low-level visual differences between conditions by counterbalancing the assignment of objects to conditions across participants.
-Fifth, we reduced priming and attentional effects by presenting all objects in a randomized order.
-Sixth, we reduced memory effects by using only unfamiliar objects and by measuring online ERPs rather than delayed behavioral responses.
-We hope that these measures were effective in ruling out many alternative explanations, thus making a compelling case against the "cognitive impenetrability" of visual perception.
+The top-down modulation of visual ERPs by semantic information challenges a modular view of visual perception [@fodor1983; @pylyshyn1999].
+Proponents of this view have pointed out important shortcomings of previous studies that had claimed to demonstrate top-down effects of cognition on perception [@machery2015; @firestone2016].
+We addressed as many of these shortcomings as possible: We ensured that there were no visual differences between conditions (with counterbalancing and the pre-insight phase as a negative control), we used ERPs as an objective and time-resolved measure to disentangle perceptual and post-perceptual effects, and we reduced response and demand biases by keeping the manipulation (i.e., matching or non-matching keywords) obscure to participants and by including well-known objects as filler stimuli.
 
-[One could argue that the effects presented here might be reducible to more basic mechanisms such as semantic priming.
-Indeed, the keywords that were presented before each object in the semantically informed condition were chosen such that they matched the function of the object and often had a direct relationship to certain visual features of the object (see Supplementary Table 1).
-This might have induced semantic priming, which is supported by the reduction in N400 amplitudes in response to objects in the semantically informed condition, as in previous priming studies [e.g., @bentin1985; @kellenbach2000].
-However, there are at least two arguments why semantic priming cannot account for our main findings, that is, the influence of semantic information on the early P1 and N170 components.
-First, for both of these components, ERP amplitudes were *enlarged* (i.e., more positive for the P1 component and more negative for the N170) during semantically informed perception, whereas an account based on semantic priming would have predicted *reduced* ERP amplitudes.
+One could argue that the effects presented here might be reducible to more basic mechanisms such as semantic priming.
+Indeed, the keywords that were presented before each object in the semantically informed condition were chosen such that they matched the function of the object and often had a direct relationship to certain visual features of the object.
+This might have induced semantic priming, which is supported by the reduction in N400 amplitudes [e.g., @bentin1985; @kellenbach2000].
+However, there are at least three arguments why semantic priming cannot account for our main findings, that is, the influence of semantic information on the P1 and N170.
+First, for both components, ERP amplitudes were enlarged (i.e., more positive for the P1 and more negative for the N170) during semantically informed perception, whereas semantic priming typically leads to reduced ERP amplitudes.
 Second, these effects were not just observed when comparing semantically informed perception (with matching keywords) and uninformed perception (with non-matching keywords), but also when comparing semantically informed perception with unsuccessfully informed perception.
-Whereas priming might have been present in the first comparison, in the second comparison all objects were preceded by keywords that matched the function of the object to a similar degree, making semantic priming less likely.
-Third, the results from an online rating study (see Materials and Methods; Supplementary Figure 1) indicated that people by and large did not spontaneously associate the unfamiliar objects with a particular function, and also allowed us to statistically control for the closeness of peoples’ guesses and the true function of each object.]{color="blue"}
+In the latter case, all objects were preceded by keywords that matched the function of the object to a similar degree, making semantic priming less likely.
+Third, the results from an online rating study (see Materials and Methods; Supplementary Figure 1) indicated that people by and large did not spontaneously associate the unfamiliar objects with a particular function, and also allowed us to statistically control for the closeness of peoples' guesses and the true function of each object.
 
@@
 
-An interactive view of visual object processing with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @serre2007; @krizhevsky2012; for review, see @lindsay2021].
-The lack of semantic knowledge that dynamically interacts with the processing of visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition.
-For these models, single-trial learning seems to be out of reach until the models overcome this "barrier of meaning" [@mitchell2020].
-Drawing inspiration from neurocognitive data may help to make these models more biologically plausible and, at the same time, more data efficient [@maier2022].
+Taken together, the present study provides preliminary evidence that whenever we receive semantic information about a previously unfamiliar object, this information has an immediate influence on our visual processing of this object.
+The immediacy of this influence is remarkable in at least two different ways: First, it does not require an extensive learning history but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
+Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (> 400 ms), typically associated with semantic processing, but also at much earlier stages within the first 200 ms, associated with visual perception itself.
 
-Taken together, the present study provides preliminary evidence that whenever we receive meaningful semantic information about a previously unfamiliar object, this information has an immediate influence on our visual processing of this object.
-The immediacy of this influence is remarkable in at least two different ways:
-First, it does not require an extensive learning history but can instead be observed within the same trial in which the information has been presented and/or a single trial later.
-Second, the time course of this influence suggests that it manifests itself not only at later, post-perceptual stages (> 400 ms), typically associated with semantic processing, but also at much earlier stages within the first 200 ms, associated with visual perception itself.
+\newpage
 
@@
 \newpage
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thetable}{S\arabic{table}}
+
+# Instant Effects of Semantic Information on Visual Perception
+
+# Online Supplementary Information
+
+\bigskip
+
+\begin{center}
+Alexander Enge, Franziska Süß, \& Rasha Abdel Rahman
+\end{center}
+
+\captionsetup[figure]{name=Online Figure}
 \setcounter{figure}{0}
+
+\captionsetup[table]{name=Online Table}
 \setcounter{table}{0}
+
+\renewcommand{\thepage}{ONLINE SI \arabic{page}}
 \setcounter{page}{1}
-
-# Supplementary Information
 
@@
 
-## Results S1. *Linear Mixed-Effects Models*
+## Online Results 1. *Linear Mixed-Effects Models*
 
@@
 \small
-\singlespacing
 
@@
 \normalsize
-\doublespacing
 
@@
 
-\newpage
-
 ```{r, figs1, cache=FALSE, fig.height=5, fig.width=6, out.width="50%", fig.cap="(ref:figs1-caption)"}
@@
 
-(ref:figs1-caption) [Online pre-rating study results.
+(ref:figs1-caption) Online pre-rating study results.
 Participants were presented with 240 objects in random order, 120 of which were familiar everyday objects and the other 120 were presumed to be unfamiliar to most people.
@@
 Semantic similarities were computed as the cosine similarity between the sums of the two word vectors in a word2vec emebedding space pre-trained on the German Wikipedia.
-Boxplots show the median (thick line), 25th and 75th percentiles (hinges), 1.5 times the interquartile range above and below the hinges (whiskers), and any outlier data points that fall outside of the whiskers (dots).]{color="blue"}
+Boxplots show the median (thick line), 25th and 75th percentiles (hinges), 1.5 times the interquartile range above and below the hinges (whiskers), and any outlier data points that fall outside of the whiskers (dots).
 
@@
 
-(ref:figs2-caption) [Online pre-rating study results on the level of individual object stimuli.
+(ref:figs2-caption) Online pre-rating study results on the level of individual object stimuli.
 Same as Supplementary Figure 1, but showing, for each object stimulus separately, the mean (horizontal line) ± 1 standard error (vertical lines) of the semantic similarities between participant-generated keywords and the keywords that we had generated.
 Semantic similarities were generally higher for the familiar objects than for the unfamiliar objects, indicating that it was easier for participants to come up with the correct function for the familiar objects.
-This mean cosine similarity for each object (i.e., a measure of the difficulty of guessing its function) was entered as a covariate of no interest in all linear mixed-effects models for analyzing the data of the main EEG experiment (see Materials and Methods; Results).]{color="blue"}
+This mean cosine similarity for each object (i.e., a measure of the difficulty of guessing its function) was entered as a covariate of no interest in all linear mixed-effects models for analyzing the data of the main EEG experiment (see Materials and Methods; Results).
 
@@
 (ref:figs3-caption) Time-frequency results for the pre-insight phase.
-Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the [uninformed]{color="blue"} condition, grand-averaged across participants.
+Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the uninformed condition, grand-averaged across participants.
 A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`).
@@
 
-(ref:figs4-caption) [Time-frequency results for the pre-insight phase (informed minus unsuccessful).
+(ref:figs4-caption) Time-frequency results for the pre-insight phase (informed minus unsuccessful).
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.
-A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful")$p_val))`).]{color="blue"}
+A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Unsuccessful")$p_val))`).
 
@@
 
-(ref:figs5-caption) [Time-frequency results for the insight phase (informed minus unsuccessful).
+(ref:figs5-caption) Time-frequency results for the insight phase (informed minus unsuccessful).
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.
-Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`).]{color="blue"}
+Black dots highlight EEG channels that were part of a cluster for which this difference was statistically significant ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`).
 
@@
 
-(ref:figs6-caption) [Time-frequency results for the post-insight phase (informed minus unsuccessful).
+(ref:figs6-caption) Time-frequency results for the post-insight phase (informed minus unsuccessful).
 Each topographic plot shows the difference in event-related power (in units of percent signal change) between the semantically informed condition and the unsuccessfully informed condition, grand-averaged across participants.
-A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Unsuccessful")$p_val))`).]{color="blue"}
+A cluster-based permutation test indicated no clusters for which this difference was statistically significant (all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Unsuccessful")$p_val))`).

### 2023-04-19 manuscript.Rmd
Replace "supplementary" with "online"

@@
 These served as filler stimuli of no interest.
-The other 120 stimuli were rare objects presumed to be unfamiliar to most participants (e.g., a galvanometer, an udu drum; see Supplementary Table 1 at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc)).
+The other 120 stimuli were rare objects presumed to be unfamiliar to most participants (e.g., a galvanometer, an udu drum; see Online Table 1 at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc)).
 All stimuli were presented on a light blue background with a size of 207 × 207 pixels on a 19-inch LCD monitor with a resolution of 1,280 × 1,024 pixels and a refresh rate of 75 Hz.
 At a standardized viewing distance of 90 cm, the images subtended approximately 3.9 degrees of participants' horizontal and vertical visual angle.
-For each unfamiliar object, we created a pair of German keywords (a noun and a verb), describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., Stromstärke, messen [electric current, measuring]; Tonpott, trommeln [clay pot, drumming]; see Supplementary Table 1).
+For each unfamiliar object, we created a pair of German keywords (a noun and a verb), describing the typical function or use of the object in a way that could be related to its visual features and their configuration (e.g., Stromstärke, messen [electric current, measuring]; Tonpott, trommeln [clay pot, drumming]; see Online Table 1).
 As our central experimental manipulation, half of the objects were presented together with keywords that matched their respective function, whereas the other half of the objects were presented together with non-matching keywords (which would have matched a different object).
@@
 As a manipulation check, we ran an online rating study where we presented 10 German speakers (3 female, 7 male, mean age = 25.3 years, range 20--35 years; none took part in the main study) with all 240 visual objects in random order and asked them to generate their own keywords that would describe the presumed function of the object.
-We used latent semantic analysis [@gunther2019] with a word2vec embedding (deepset GmbH, Berlin, Germany, [www.deepset.ai/german-word-embeddings](www.deepset.ai/german-word-embeddings)) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (see Supplementary Figures 1 and 2).
+We used latent semantic analysis [@gunther2019] with a word2vec embedding (deepset GmbH, Berlin, Germany, [www.deepset.ai/german-word-embeddings](www.deepset.ai/german-word-embeddings)) pre-trained on the German Wikipedia to estimate semantic distances between these participant-generated keywords and the keywords used in our main EEG experiment (see Online Figures 1 and 2).
 In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_stats$means, fam_condition == "familiar")$emmean` ± `r filter(rating_stats$means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_stats$means, fam_condition == "matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
@@
 All models included the following fixed effects of interest: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a custom contrast (i.e., subtracting the uninformed condition from the informed condition and the unsuccessfully informed condition from the informed condition, the intercept being the grand mean across all three conditions), and (c) the two-way interaction of phase and condition.
-We also added the results from the online pre-rating study (mean cosine distance between rating study-generated keywords and keywords presented in the main experiment) as an additional covariate of no interest (see Supplementary Figure 2).
+We also added the results from the online pre-rating study (mean cosine distance between rating study-generated keywords and keywords presented in the main experiment) as an additional covariate of no interest (see Online Figure 2).
 This was to control for the possibility that participants might have been partly familiar with some of the objects and/or able to guess their function from their visual appearance alone.
 For the random effects, we determined the most parsimonious structure supported by the data using the automatic procedure proposed by @matuschek2017.
-This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20; see Supplementary Results 1 for the final model syntax and model outputs).
+This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20; see Online Results 1 for the final model syntax and model outputs).
 All models were fitted in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4] with the optimizer function *bobyqa* and a maximum of 10^6^ iterations for maximum likelihood estimation.
@@
 In an exploratory time-frequency analysis, we checked for differences in event-related power between semantically informed perception and uninformed perception within each of the three phases of the experiment.
-Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Supplementary Figure 3), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
+Cluster-based permutation tests [@maris2007] revealed no significant clusters in the pre-insight phase (see Online Figure 3), all $p$s > `r print_p(min(filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Uninformed")$p_val))`, but one significant cluster in the insight phase (see Figure 3), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Uninformed" & p_val < p_cluster)$p_val))`, and one significant cluster in the post-insight phase (see Figure 4), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Uninformed" & p_val < p_cluster)$p_val))`.
 These two significant clusters in the insight and post-insight phases were similar in their direction, latency, frequency range, and topographic distribution.
@@
 We repeated this analysis to look for differences between semantically informed perception and unsuccessfully informed perception within each of the three phases of the experiment.
-There were no significant clusters in the pre- or post-insight phases (see Supplementary Figures 4 and 6), all $p$s > `r print_p(min(filter(tfr_clusters, contrast %in% c("Pre-insight/Informed - Pre-insight/Unsuccessful", "Post-insight/Informed - Post-insight/Unsuccessful"))$p_val))` but one significant cluster in the insight phase (see Supplementary Figure 5), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`.
+There were no significant clusters in the pre- or post-insight phases (see Online Figures 4 and 6), all $p$s > `r print_p(min(filter(tfr_clusters, contrast %in% c("Pre-insight/Informed - Pre-insight/Unsuccessful", "Post-insight/Informed - Post-insight/Unsuccessful"))$p_val))` but one significant cluster in the insight phase (see Online Figure 5), $p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Unsuccessful" & p_val < p_cluster)$p_val))`.
 This cluster was similar to the ones described above in its latency, frequency range, and topographic distribution.
@@
 In the latter case, all objects were preceded by keywords that matched the function of the object to a similar degree, making semantic priming less likely.
-Third, the results from an online rating study (see Materials and Methods; Supplementary Figure 1) indicated that people by and large did not spontaneously associate the unfamiliar objects with a particular function, and also allowed us to statistically control for the closeness of peoples' guesses and the true function of each object.
+Third, the results from an online rating study (see Materials and Methods; Online Figure 1) indicated that people by and large did not spontaneously associate the unfamiliar objects with a particular function, and also allowed us to statistically control for the closeness of peoples' guesses and the true function of each object.
 
@@
 Participants were asked to describe or guess the function of each object by typing a pair of German keywords.
-Violins show the distributions of the similarities between these participant-generated keywords and the keywords that we had created for our main EEG experiment (see Materials and Methods; Supplementary Table 1).
+Violins show the distributions of the similarities between these participant-generated keywords and the keywords that we had created for our main EEG experiment (see Materials and Methods; Online Table 1).
 We computed these similarities separately for (a) participant-generated keywords for the familiar objects and keywords that we had created to match the familiar objects (though these were not part of the main EEG experiment; red), (b) participant-generated keywords for the unfamiliar objects and keywords that we had created to match the unfamiliar objects (blue), and (c) participant-generated keywords for the unfamiliar objects and keywords that we had created to not match the unfamiliar objects (by selecting keywords that matched one of the other unfamiliar objects; purple).
@@
 (ref:figs2-caption) Online pre-rating study results on the level of individual object stimuli.
-Same as Supplementary Figure 1, but showing, for each object stimulus separately, the mean (horizontal line) ± 1 standard error (vertical lines) of the semantic similarities between participant-generated keywords and the keywords that we had generated.
+Same as Online Figure 1, but showing, for each object stimulus separately, the mean (horizontal line) ± 1 standard error (vertical lines) of the semantic similarities between participant-generated keywords and the keywords that we had generated.
 Semantic similarities were generally higher for the familiar objects than for the unfamiliar objects, indicating that it was easier for participants to come up with the correct function for the familiar objects.

### 2023-04-19 manuscript.Rmd
Fix typos

@@
 
-  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Abdel Rahman Lab for Neurocognitive Psychology for insightful discussions, Guido Kiecker for technical support, as well as Guillaume Thierry and one anonymous reviewer for their comments on a previous version of the paper.
+  We would like to thank Nele Langosch for assistance with the preparation of materials and data collection, Olaf Dimigen and the Abdel Rahman Lab for Neurocognitive Psychology for insightful discussions, Guido Kiecker for technical support, as well as two reviewers for their comments on a previous version of the paper.
   This work was supported by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) under Germany's Excellence Strategy (EXC 2002/1 "Science of Intelligence") project number 390523135 as well as grants AB277-5 and AB277-6 to R.A.R.
@@
     latex_engine: xelatex
-    pandoc_args: ["--lua-filter=misc/color_text.lua"]
 
@@
 
-# Write R package references
-r_refs(here(misc_dir, "r-references.bib"), append = FALSE)
-
 # Re-run steps that take a long time?
@@
 Does our perception of an object change once we discover what function it serves?
-We showed human participants (\textit{n} = 48, 31 females and 17 males) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in uninformed perception.
+We showed human participants (\textit{n} = 48, 31 female, 17 male) pictures of unfamiliar objects either together with keywords matching their function, leading to semantically informed perception, or together with non-matching keywords, resulting in uninformed perception.
 We measured event-related potentials (ERPs) to investigate at which stages in the visual processing hierarchy these two types of object perception differed from one another.
@@
 
-Participants were 48 German native speakers (31 females and 17 males) with a mean age of 23.5 years (range 18--32 years) and no history of psychological disorder or treatment.
+Participants were 48 German native speakers (31 female, 17 male) with a mean age of 23.5 years (range 18--32 years) and no history of psychological disorder or treatment.
 No a priori power analysis was carried out.
@@
 In brief, it was substantially easier for participants to come with correct descriptions of familiar objects (mean cosine distance ± standard error = `r filter(rating_stats$means, fam_condition == "familiar")$emmean` ± `r filter(rating_stats$means, fam_condition == "familiar")$SE`) than for unfamiliar objects (`r filter(rating_stats$means, fam_condition == "matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "familiar - matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "familiar - matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "familiar - matching")$p_value)` (linear mixed-effects model).
-In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_stats$means, fam_condition == "non-matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "non-matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "matching - non-matching")$df)`) = `r filter(rating_stats$contrasts, contrast == "matching - non-matching")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "matching - non-matching")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.
+In fact, this similarity between participant-generated keywords for the unfamiliar objects and the object-matching keywords presented in the main experiment was only slightly higher than the similarity between participant-generated keywords and the object-non-matching keywords presented in the main experiment (`r filter(rating_stats$means, fam_condition == "non-matching")$emmean` ± `r filter(rating_stats$means, fam_condition == "non-matching")$SE`), $t$(`r print_dof(filter(rating_stats$contrasts, contrast == "matching - (non-matching)")$df)`) = `r filter(rating_stats$contrasts, contrast == "matching - (non-matching)")$t_value`, $p_\text{corr}$ `r print_p(filter(rating_stats$contrasts, contrast == "matching - (non-matching)")$p_value)` (linear mixed-effects model), indicating that it was difficult for participants to know or guess the correct function of the unfamiliar objects.
 
@@
 The EEG data are available upon reasonable request from the corresponding author because we had not asked participants for their consent to make the data publicly available.
-The experimental stimuli (object images and keywords) the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
+The experimental stimuli (object images and keywords) and the code for data analysis are available at [https://doi.org/10.17605/osf.io/uksbc](https://doi.org/10.17605/osf.io/uksbc).
 
@@
 It therefore constitutes an online marker of semantic insight, that is, of participants suddenly understanding the visual objects in the light of the information provided by the keywords.
-The N170 is associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002], that is, it is sensitive to factors that go beyond structural encoding and categorical perception [@thierry2007, @thierry2007a; @dering2011].
+The N170 is associated with the holistic perception of faces [@sagiv2001; @eimer2011] and other stimuli of visual expertise [@tanaka2001; @rossion2002], that is, it is sensitive to factors that go beyond structural encoding and categorical perception [@thierry2007; @thierry2007a; @dering2011].
 It being enlarged may reflect that the semantic information made participants experience the configuration of the visual features of the objects in a new and meaningful way.
@@
 The P1, unlike the N400 and N170, was modulated by semantic information only one trial after this information had been obtained.
-This replicates previous studies showing modulations of the P1 when participants had learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018, @maier2019; @samaha2018; @weller2019].
+This replicates previous studies showing modulations of the P1 when participants had learned meaningful information about previously unfamiliar objects [@abdelrahman2008; @maier2018; @maier2019; @samaha2018; @weller2019].
 The present study adds that the P1 effect does not take an extensive learning history to develop; instead, it can be observed as soon as one trial after semantic insight has happened.
